### 2015-12-06 protest-auth-content.tex
Adds initial thoughts

\title{Authenticating Protests}
\author{%
  Daniel Bosk\inst{1}
  \and
  Sébastien Gambs\inst{2}
  \and
  Sonja Buchegger\inst{1}
}
\institute{%
  School of Computer Science and Communication\\
  KTH Royal Institute of Technology, Stockholm\\
  \texttt{\{dbosk,buc\}@kth.se}
  \and
  Université de Rennes 1 and Inria, Rennes\\
  \texttt{sgambs@irisa.fr}
}

\maketitle

\begin{abstract}
  \dots

  \keywords{\dots}
\end{abstract}

\section{Introduction}
\label{Introduction}

There are different possibilities for a protest: e.g.\ one performed online or 
one performed in the physical reality.
Purely online protests are essentially petitions.
This case can use digital signatures to verify the authenticity of a list of 
names.
It can also be compared to electronic voting --- to vote for or against 
something.
In this case all participants and third-parties can verify the authenticity of 
the result, but cannot verify the vote of an individual.

We are interested in real-world protests, for these we need to bind all 
participants to the same physical location at a reasonably similar time (within 
the duration of the protest).
\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
which provides a participant with a proof of being at the location.
However, we would like that any participant can prove the demonstration's 
authenticity to a third-party, e.g.\ the UN or a human-rights 
organization.
The reason this is an interesting property is the following scenario:
Imagine there is a demonstration, the police shows up and tries to apprehend 
every participant.
However, one demonstrator survives and manages to flee the country, here the 
demonstrator wants to prove that there was a protest of a certain size.

There are at least two reasons we are interested in authenticating a protest in 
this way:
\begin{enumerate}
\item for a third-party can verify the authenticity of the protest, e.g.\ that 
  there were \(n\) participants;
\item for the organizers to use the participation as feedback into a reputation 
  system.
\end{enumerate}
We want to do this in a privacy-preserving way:
We want to verify the participation of a protest, but not identifying 
individuals who participated.
If a demonstrator flees the country, that demonstrator should be able to prove 
to the e.g.\ the UN that there were \(n\) participants.
But if the demonstrator is caught by the secret police before leaving, then the 
secret police should not learn the identities of the other participants.

\section{Adapting PROPS}

\subsection{The \acs*{CA} Problems}

One issue is the \ac{CA}.
One direction we can take to solve this is by threshold signatures, e.g.\ 
\cite{FSThresholdSignatures}.
This way the participants can jointly issue new certificates, by signing them 
using the threshold signature scheme.
This should solve part of the problems related to Sybil attacks too.
But, if \(k > t\) participants collude, they can create multiple identities for 
themselves.
The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
too, to change with the number of participants.
I'm not sure, but in what I've read about threshold schemes, they generally 
keep \(n\) and \(t\) fixed.

Another direction on solving the \ac{CA} problem, is if we can use already 
existing \acp{PKI} instead.
E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
running everything through a hash function and the sign that value.
Due to the use of the hash function we cannot prove in zero knowledge that we 
have a signed certificate.
But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
they do not reveal the identity, but that we can if needed --- similar to 
a commitment which we reveal only in emergencies.

It would be interesting to solve the W--P collusion attack, where the witness 
reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
individuals fake this information at home.
One possibility in our scenario is that e.g.\ an external journalist on 
location can create \iac{LPS}, because a journalist is generally trusted.
This would be useful as occasionally journalists are also captured, and anyone 
that escaped should be able to show a convincing proof.
However, one problem with this is that the journalist will not necessarily have 
a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
\ac{PKI}.

In relation to the previous, it would be interesting to be able to tie the 
\acp{LP} (or \acp{LPS}) to a reputation system.
Then, even if no external journalist is on location, the participants can rely 
on their online reputation.
One option would be to have a reputation system in a global location-proof 
system, another would be to tie it to a reputation system already used in e.g.\ 
\iac{OSN}.
One possible solution would be to include a commitment in the \ac{LPS} and when 
necessary use it to tie it to the online identity.

\subsection{One Proof for All}

The naïve approach would be that everyone generates \acp{LPS} for everyone 
else, but this would be computationally and communicatively expensive 
(\(O(n^2)\)).
A better approach would be \iac{SMC} scheme where several witnesses participate 
to compute a joint \ac{LPS} for one prover.
This would reduce the need for pairwise communication.
In our scenario each witness will also want to participate as a prover, if the 
jointly computed \ac{LPS} could further be used by all participants in the 
computation, this would reduce the complexity further.

To make it even more efficient, it would be desirable to make the proofs 
\enquote{transitive}.
I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
Speaking in graphs, we want to be able to join sub-graphs instead of having to 
join node-by-node.

\subsubsection*{\ackname}

This work was funded by the Swedish Foundation for Strategic Research grant SSF 
FFL09-0086 and the Swedish Research Council grant VR 2009-3793.

\printbibliography{}

### 2016-02-03 PPProtestAuth-slides.tex
Adds slides target
The slides structure is taken from the 30% seminar, so it's the same
theme and structure.

\documentclass[ignorenonframetext]{beamer}
%\documentclass[handout,ignorenonframetext]{beamer}
%\usepackage{pgfpages}
%\pgfpagesuselayout{4 on 1}[a4paper,border shrink=5mm]

\usetheme{Berlin}
\setbeamercovered{transparent}
\setbeamertemplate{bibliography item}[text]

\setbeamertemplate{footline}%{miniframes theme}
{%
  \begin{beamercolorbox}[colsep=1.5pt]{upper separation line foot}
  \end{beamercolorbox}
  \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
    leftskip=.3cm,rightskip=.3cm plus1fil]{author in head/foot}%
    \leavevmode{\usebeamerfont{author in head/foot}\insertshortauthor}%
    \hfill%
    {\usebeamerfont{institute in head/foot}\usebeamercolor[fg]{institute in head/foot}\insertshortinstitute}%
  \end{beamercolorbox}%
  \begin{beamercolorbox}[ht=2.5ex,dp=1.125ex,%
    leftskip=.3cm,rightskip=.3cm plus1fil]{title in head/foot}%
    {\usebeamerfont{title in head/foot}\insertshorttitle} \hfill     \insertframenumber%
  \end{beamercolorbox}%
  \begin{beamercolorbox}[colsep=1.5pt]{lower separation line foot}
  \end{beamercolorbox}
}

\AtBeginSection[]{%
  \begin{frame}<beamer>
    \tableofcontents[currentsection]
  \end{frame}
}

\let\email\texttt

\input{PPProtestAuth-preamble.tex}

\begin{document}
\mode<all>
\input{PPProtestAuth-content.tex}
\mode*
\end{document}

### 2016-04-19 PPProtestAuth-content.tex
Adds slides target
The slides structure is taken from the 30% seminar, so it's the same
theme and structure.
There is no longer any \ackname in llncs
Adds comments from meetings with Sébastien

--- 2015-12-06 protest-auth-content.tex
@@
-\title{Authenticating Protests}
-\author{%
+\title{%
+  Verifying Demonstrations
+}
+\author[D.~Bosk et al.]{%
   Daniel Bosk\inst{1}
@@
 }
-\institute{%
+\institute[KTH, UQAM]{%
   School of Computer Science and Communication\\
@@
   \and
-  Université de Rennes 1 and Inria, Rennes\\
-  \texttt{sgambs@irisa.fr}
+  Université de Quebec à Montreal\\
+  \texttt{sgambs@uqam.ca}
 }
@@
 \maketitle
+
+\mode*
 
@@
 \begin{enumerate}
-\item for a third-party can verify the authenticity of the protest, e.g.\ that 
-  there were \(n\) participants;
-\item for the organizers to use the participation as feedback into a reputation 
-  system.
+  \item for a third-party can verify the authenticity of the protest, e.g.\ 
+    that there were \(n\) participants;
+  \item for the organizers to use the participation as feedback into 
+    a reputation system.
 \end{enumerate}
@@
 
+\subsection{The Problem}
+
+Usually the count by the organizers and count by police differs, we want to 
+solve this problem.
+
+We can divide the problem into three parts:
+\begin{itemize}
+  \item Register participants in the system.
+  \item Collect the necessary data.
+  \item Perform the counting and verification.
+\end{itemize}
+
+To register the participants we might be able to piggy-back on existing 
+\acp{PKI} and blind signatures --- similarly as for voting systems.
+
+We have the verifiability properties in voting:
+\begin{description}
+  \item[Individual] Individual verifiability allows a voter to verify her own 
+    vote was included in the election outcome.
+  \item[Universal] Universal verifiability allows voters or observers to check 
+    that the election outcome corresponds to the votes cast.
+  \item[Eligibility] Eligibility verifiability allows voters and observers to 
+    check that each vote in the election outcome was cast by a uniquely 
+    registered voter.
+\end{description}
+
 \section{Adapting PROPS}
+\label{AdaptingPROPS}
 
@@
 
-\subsubsection*{\ackname}
+\section{System Model}
+\label{SystemModel}
+
+The model will be a public anonymous blackboard.
+We will use this blackboard to publish locations proofs after the protest.
+
+We want the following properties:
+\begin{description}
+  \item[Correctness] We want to count everyone once and only once.
+  \item[Unforgeability] Participation should not be possible to forge.
+    I.e.\ non-participants should not be able to say they were present.
+    This together with correctness will provide authenticity to the protest 
+    verification.
+  \item[Anonymity] Given the data published on the blackboard, the adversary 
+    should not be able to tell two participants apart.
+  \item[Decentralized] There should be no central authority.
+\end{description}
+
+Can the adversary publish a public-key looking random string to sabotage the 
+blackboard?
+
+Basically the properties that we are interested in are similar to those of 
+electronic voting, so we would like to reuse as many definitions from there as 
+possible.
+
+\subsection{Decentralization}
+
+In \ac{PROPS} the prover must have a secret signed by \iac{CA}.
+This \ac{CA} can be implemented as a secret-sharing scheme.
+Usually these have a fixed threshold \((t, n)\).
+This can be achieved by commitments, then the shared secret is computed.
+However, it would be interesting to have the threshold dynamically adapt to the 
+number of participants, i.e.\ participants can join later too.
+
+Can the adversary then \enquote{join} enough many to throw off the threshold?
+
+\subsection{Correctness and Unforgeability}
+
+Each prover must reach a threshold of witnesses \(k\).
+We must be able to prevent a prover to collect \(2k\) witnesses and then 
+publishing two proofs.
+We therefore must achieve conditional linkability between the \acp{LP} 
+published on the blackboard.
+If a second \ac{LP} for a secret is published, then those should be linkable.
+This might be possible to achieve with unique group 
+signatures~\cite{UniqueGroupSignatures,UniqueRingSignatures,ListSignatures}.
+
+\section{Useful Primitives}
+\label{UsefulPrimitives}
+
+\dots
+
+\subsubsection*{Acknowledgements}
 

### 2016-07-18 ProtestVerif-content.tex
Adds notes on issues

--- 2016-04-19 PPProtestAuth-content.tex
@@
 \end{description}
+
+There are several issues that must be treated:
+\begin{itemize}
+  \item Each location proof must be bound to one individual's participation.
+    One protester must not be able to create two unique location proofs and be 
+    able to increase the number of participants, that would violate 
+    \cref{VerifEligibility} above.
+    In other words, we must prevent the Sybil attack.
+
+  \item A group of people should not be able to generate \acp{LP} to make it 
+    look as if they participated in the protest but actually stayed at home.
+    This means that all \acp{LP} must be linked to each other.
+    If a protest has hundreds of thousands of participants, then this linking 
+    must be achieved efficiently.
+\end{itemize}
 

### 2016-07-18 AdaptingPROPS.tex
Splits content into subfiles

--- 2015-12-06 protest-auth-content.tex
@@
-\title{Authenticating Protests}
-\author{%
-  Daniel Bosk\inst{1}
-  \and
-  Sébastien Gambs\inst{2}
-  \and
-  Sonja Buchegger\inst{1}
-}
-\institute{%
-  School of Computer Science and Communication\\
-  KTH Royal Institute of Technology, Stockholm\\
-  \texttt{\{dbosk,buc\}@kth.se}
-  \and
-  Université de Rennes 1 and Inria, Rennes\\
-  \texttt{sgambs@irisa.fr}
-}
-
-\maketitle
-
-\begin{abstract}
-  \dots
-
-  \keywords{\dots}
-\end{abstract}
-
-\section{Introduction}
-\label{Introduction}
-
-There are different possibilities for a protest: e.g.\ one performed online or 
-one performed in the physical reality.
-Purely online protests are essentially petitions.
-This case can use digital signatures to verify the authenticity of a list of 
-names.
-It can also be compared to electronic voting --- to vote for or against 
-something.
-In this case all participants and third-parties can verify the authenticity of 
-the result, but cannot verify the vote of an individual.
-
-We are interested in real-world protests, for these we need to bind all 
-participants to the same physical location at a reasonably similar time (within 
-the duration of the protest).
-\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
-which provides a participant with a proof of being at the location.
-However, we would like that any participant can prove the demonstration's 
-authenticity to a third-party, e.g.\ the UN or a human-rights 
-organization.
-The reason this is an interesting property is the following scenario:
-Imagine there is a demonstration, the police shows up and tries to apprehend 
-every participant.
-However, one demonstrator survives and manages to flee the country, here the 
-demonstrator wants to prove that there was a protest of a certain size.
-
-There are at least two reasons we are interested in authenticating a protest in 
-this way:
-\begin{enumerate}
-\item for a third-party can verify the authenticity of the protest, e.g.\ that 
-  there were \(n\) participants;
-\item for the organizers to use the participation as feedback into a reputation 
-  system.
-\end{enumerate}
-We want to do this in a privacy-preserving way:
-We want to verify the participation of a protest, but not identifying 
-individuals who participated.
-If a demonstrator flees the country, that demonstrator should be able to prove 
-to the e.g.\ the UN that there were \(n\) participants.
-But if the demonstrator is caught by the secret police before leaving, then the 
-secret police should not learn the identities of the other participants.
-
 \section{Adapting PROPS}
+\label{AdaptingPROPS}
 
@@
 (\(O(n^2)\)).
-A better approach would be \iac{SMC} scheme where several witnesses participate 
+A better approach would be \iac{MPC} scheme where several witnesses participate 
 to compute a joint \ac{LPS} for one prover.
@@
 join node-by-node.
-
-\subsubsection*{\ackname}
-
-This work was funded by the Swedish Foundation for Strategic Research grant SSF 
-FFL09-0086 and the Swedish Research Council grant VR 2009-3793.
-
-\printbibliography{}

### 2016-07-18 content.tex
Updates submodules
Splits content into subfiles

--- 2015-12-06 protest-auth-content.tex
@@
 
-\section{Introduction}
-\label{Introduction}
+\input{intro.tex}
+\input{AdaptingPROPS.tex}
+\input{SystemModel.tex}
+\input{primitives.tex}
 
-There are different possibilities for a protest: e.g.\ one performed online or 
-one performed in the physical reality.
-Purely online protests are essentially petitions.
-This case can use digital signatures to verify the authenticity of a list of 
-names.
-It can also be compared to electronic voting --- to vote for or against 
-something.
-In this case all participants and third-parties can verify the authenticity of 
-the result, but cannot verify the vote of an individual.
-
-We are interested in real-world protests, for these we need to bind all 
-participants to the same physical location at a reasonably similar time (within 
-the duration of the protest).
-\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
-which provides a participant with a proof of being at the location.
-However, we would like that any participant can prove the demonstration's 
-authenticity to a third-party, e.g.\ the UN or a human-rights 
-organization.
-The reason this is an interesting property is the following scenario:
-Imagine there is a demonstration, the police shows up and tries to apprehend 
-every participant.
-However, one demonstrator survives and manages to flee the country, here the 
-demonstrator wants to prove that there was a protest of a certain size.
-
-There are at least two reasons we are interested in authenticating a protest in 
-this way:
-\begin{enumerate}
-\item for a third-party can verify the authenticity of the protest, e.g.\ that 
-  there were \(n\) participants;
-\item for the organizers to use the participation as feedback into a reputation 
-  system.
-\end{enumerate}
-We want to do this in a privacy-preserving way:
-We want to verify the participation of a protest, but not identifying 
-individuals who participated.
-If a demonstrator flees the country, that demonstrator should be able to prove 
-to the e.g.\ the UN that there were \(n\) participants.
-But if the demonstrator is caught by the secret police before leaving, then the 
-secret police should not learn the identities of the other participants.
-
-\section{Adapting PROPS}
-
-\subsection{The \acs*{CA} Problems}
-
-One issue is the \ac{CA}.
-One direction we can take to solve this is by threshold signatures, e.g.\ 
-\cite{FSThresholdSignatures}.
-This way the participants can jointly issue new certificates, by signing them 
-using the threshold signature scheme.
-This should solve part of the problems related to Sybil attacks too.
-But, if \(k > t\) participants collude, they can create multiple identities for 
-themselves.
-The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
-too, to change with the number of participants.
-I'm not sure, but in what I've read about threshold schemes, they generally 
-keep \(n\) and \(t\) fixed.
-
-Another direction on solving the \ac{CA} problem, is if we can use already 
-existing \acp{PKI} instead.
-E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
-DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
-running everything through a hash function and the sign that value.
-Due to the use of the hash function we cannot prove in zero knowledge that we 
-have a signed certificate.
-But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
-they do not reveal the identity, but that we can if needed --- similar to 
-a commitment which we reveal only in emergencies.
-
-It would be interesting to solve the W--P collusion attack, where the witness 
-reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
-individuals fake this information at home.
-One possibility in our scenario is that e.g.\ an external journalist on 
-location can create \iac{LPS}, because a journalist is generally trusted.
-This would be useful as occasionally journalists are also captured, and anyone 
-that escaped should be able to show a convincing proof.
-However, one problem with this is that the journalist will not necessarily have 
-a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
-\ac{PKI}.
-
-In relation to the previous, it would be interesting to be able to tie the 
-\acp{LP} (or \acp{LPS}) to a reputation system.
-Then, even if no external journalist is on location, the participants can rely 
-on their online reputation.
-One option would be to have a reputation system in a global location-proof 
-system, another would be to tie it to a reputation system already used in e.g.\ 
-\iac{OSN}.
-One possible solution would be to include a commitment in the \ac{LPS} and when 
-necessary use it to tie it to the online identity.
-
-\subsection{One Proof for All}
-
-The naïve approach would be that everyone generates \acp{LPS} for everyone 
-else, but this would be computationally and communicatively expensive 
-(\(O(n^2)\)).
-A better approach would be \iac{SMC} scheme where several witnesses participate 
-to compute a joint \ac{LPS} for one prover.
-This would reduce the need for pairwise communication.
-In our scenario each witness will also want to participate as a prover, if the 
-jointly computed \ac{LPS} could further be used by all participants in the 
-computation, this would reduce the complexity further.
-
-To make it even more efficient, it would be desirable to make the proofs 
-\enquote{transitive}.
-I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
-act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
-Speaking in graphs, we want to be able to join sub-graphs instead of having to 
-join node-by-node.
-
-\subsubsection*{\ackname}
+\subsubsection*{Acknowledgements}
 

### 2016-07-18 intro.tex
Splits content into subfiles

--- 2015-12-06 protest-auth-content.tex
@@
-\title{Authenticating Protests}
-\author{%
-  Daniel Bosk\inst{1}
-  \and
-  Sébastien Gambs\inst{2}
-  \and
-  Sonja Buchegger\inst{1}
-}
-\institute{%
-  School of Computer Science and Communication\\
-  KTH Royal Institute of Technology, Stockholm\\
-  \texttt{\{dbosk,buc\}@kth.se}
-  \and
-  Université de Rennes 1 and Inria, Rennes\\
-  \texttt{sgambs@irisa.fr}
-}
-
-\maketitle
-
-\begin{abstract}
-  \dots
-
-  \keywords{\dots}
-\end{abstract}
-
 \section{Introduction}
@@
 
-\section{Adapting PROPS}
+\subsection{The Problem}
 
-\subsection{The \acs*{CA} Problems}
+Usually the count by the organizers and count by police differs, we want to 
+solve this problem.
 
-One issue is the \ac{CA}.
-One direction we can take to solve this is by threshold signatures, e.g.\ 
-\cite{FSThresholdSignatures}.
-This way the participants can jointly issue new certificates, by signing them 
-using the threshold signature scheme.
-This should solve part of the problems related to Sybil attacks too.
-But, if \(k > t\) participants collude, they can create multiple identities for 
-themselves.
-The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
-too, to change with the number of participants.
-I'm not sure, but in what I've read about threshold schemes, they generally 
-keep \(n\) and \(t\) fixed.
+We can divide the problem into three parts:
+\begin{itemize}
+  \item Register participants in the system.
+  \item Collect the necessary data.
+  \item Perform the counting and verification.
+\end{itemize}
 
-Another direction on solving the \ac{CA} problem, is if we can use already 
-existing \acp{PKI} instead.
-E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
-DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
-running everything through a hash function and the sign that value.
-Due to the use of the hash function we cannot prove in zero knowledge that we 
-have a signed certificate.
-But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
-they do not reveal the identity, but that we can if needed --- similar to 
-a commitment which we reveal only in emergencies.
+To register the participants we might be able to piggy-back on existing 
+\acp{PKI} and blind signatures --- similarly as for voting systems.
 
-It would be interesting to solve the W--P collusion attack, where the witness 
-reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
-individuals fake this information at home.
-One possibility in our scenario is that e.g.\ an external journalist on 
-location can create \iac{LPS}, because a journalist is generally trusted.
-This would be useful as occasionally journalists are also captured, and anyone 
-that escaped should be able to show a convincing proof.
-However, one problem with this is that the journalist will not necessarily have 
-a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
-\ac{PKI}.
+We have the verifiability properties in voting:
+\begin{description}
+  \item[Individual] Individual verifiability allows a voter to verify her own 
+    vote was included in the election outcome.
+  \item[Universal] Universal verifiability allows voters or observers to check 
+    that the election outcome corresponds to the votes cast.
+  \item[Eligibility] Eligibility verifiability allows voters and observers to 
+    check that each vote in the election outcome was cast by a uniquely 
+    registered voter.
+\end{description}
 
-In relation to the previous, it would be interesting to be able to tie the 
-\acp{LP} (or \acp{LPS}) to a reputation system.
-Then, even if no external journalist is on location, the participants can rely 
-on their online reputation.
-One option would be to have a reputation system in a global location-proof 
-system, another would be to tie it to a reputation system already used in e.g.\ 
-\iac{OSN}.
-One possible solution would be to include a commitment in the \ac{LPS} and when 
-necessary use it to tie it to the online identity.
+There are several issues that must be treated:
+\begin{itemize}
+  \item Each location proof must be bound to one individual's participation.
+    One protester must not be able to create two unique location proofs and be 
+    able to increase the number of participants, that would violate 
+    \cref{VerifEligibility} above.
+    In other words, we must prevent the Sybil attack.
 
-\subsection{One Proof for All}
-
-The naïve approach would be that everyone generates \acp{LPS} for everyone 
-else, but this would be computationally and communicatively expensive 
-(\(O(n^2)\)).
-A better approach would be \iac{SMC} scheme where several witnesses participate 
-to compute a joint \ac{LPS} for one prover.
-This would reduce the need for pairwise communication.
-In our scenario each witness will also want to participate as a prover, if the 
-jointly computed \ac{LPS} could further be used by all participants in the 
-computation, this would reduce the complexity further.
-
-To make it even more efficient, it would be desirable to make the proofs 
-\enquote{transitive}.
-I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
-act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
-Speaking in graphs, we want to be able to join sub-graphs instead of having to 
-join node-by-node.
-
-\subsubsection*{\ackname}
-
-This work was funded by the Swedish Foundation for Strategic Research grant SSF 
-FFL09-0086 and the Swedish Research Council grant VR 2009-3793.
-
-\printbibliography{}
+  \item A group of people should not be able to generate \acp{LP} to make it 
+    look as if they participated in the protest but actually stayed at home.
+    This means that all \acp{LP} must be linked to each other.
+    If a protest has hundreds of thousands of participants, then this linking 
+    must be achieved efficiently.
+\end{itemize}

### 2016-07-18 primitives.tex
Splits content into subfiles

--- 2015-12-06 protest-auth-content.tex
@@
-\title{Authenticating Protests}
-\author{%
-  Daniel Bosk\inst{1}
-  \and
-  Sébastien Gambs\inst{2}
-  \and
-  Sonja Buchegger\inst{1}
-}
-\institute{%
-  School of Computer Science and Communication\\
-  KTH Royal Institute of Technology, Stockholm\\
-  \texttt{\{dbosk,buc\}@kth.se}
-  \and
-  Université de Rennes 1 and Inria, Rennes\\
-  \texttt{sgambs@irisa.fr}
-}
+\section{Useful Primitives}
+\label{UsefulPrimitives}
 
-\maketitle
-
-\begin{abstract}
 \dots
-
-  \keywords{\dots}
-\end{abstract}
-
-\section{Introduction}
-\label{Introduction}
-
-There are different possibilities for a protest: e.g.\ one performed online or 
-one performed in the physical reality.
-Purely online protests are essentially petitions.
-This case can use digital signatures to verify the authenticity of a list of 
-names.
-It can also be compared to electronic voting --- to vote for or against 
-something.
-In this case all participants and third-parties can verify the authenticity of 
-the result, but cannot verify the vote of an individual.
-
-We are interested in real-world protests, for these we need to bind all 
-participants to the same physical location at a reasonably similar time (within 
-the duration of the protest).
-\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
-which provides a participant with a proof of being at the location.
-However, we would like that any participant can prove the demonstration's 
-authenticity to a third-party, e.g.\ the UN or a human-rights 
-organization.
-The reason this is an interesting property is the following scenario:
-Imagine there is a demonstration, the police shows up and tries to apprehend 
-every participant.
-However, one demonstrator survives and manages to flee the country, here the 
-demonstrator wants to prove that there was a protest of a certain size.
-
-There are at least two reasons we are interested in authenticating a protest in 
-this way:
-\begin{enumerate}
-\item for a third-party can verify the authenticity of the protest, e.g.\ that 
-  there were \(n\) participants;
-\item for the organizers to use the participation as feedback into a reputation 
-  system.
-\end{enumerate}
-We want to do this in a privacy-preserving way:
-We want to verify the participation of a protest, but not identifying 
-individuals who participated.
-If a demonstrator flees the country, that demonstrator should be able to prove 
-to the e.g.\ the UN that there were \(n\) participants.
-But if the demonstrator is caught by the secret police before leaving, then the 
-secret police should not learn the identities of the other participants.
-
-\section{Adapting PROPS}
-
-\subsection{The \acs*{CA} Problems}
-
-One issue is the \ac{CA}.
-One direction we can take to solve this is by threshold signatures, e.g.\ 
-\cite{FSThresholdSignatures}.
-This way the participants can jointly issue new certificates, by signing them 
-using the threshold signature scheme.
-This should solve part of the problems related to Sybil attacks too.
-But, if \(k > t\) participants collude, they can create multiple identities for 
-themselves.
-The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
-too, to change with the number of participants.
-I'm not sure, but in what I've read about threshold schemes, they generally 
-keep \(n\) and \(t\) fixed.
-
-Another direction on solving the \ac{CA} problem, is if we can use already 
-existing \acp{PKI} instead.
-E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
-DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
-running everything through a hash function and the sign that value.
-Due to the use of the hash function we cannot prove in zero knowledge that we 
-have a signed certificate.
-But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
-they do not reveal the identity, but that we can if needed --- similar to 
-a commitment which we reveal only in emergencies.
-
-It would be interesting to solve the W--P collusion attack, where the witness 
-reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
-individuals fake this information at home.
-One possibility in our scenario is that e.g.\ an external journalist on 
-location can create \iac{LPS}, because a journalist is generally trusted.
-This would be useful as occasionally journalists are also captured, and anyone 
-that escaped should be able to show a convincing proof.
-However, one problem with this is that the journalist will not necessarily have 
-a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
-\ac{PKI}.
-
-In relation to the previous, it would be interesting to be able to tie the 
-\acp{LP} (or \acp{LPS}) to a reputation system.
-Then, even if no external journalist is on location, the participants can rely 
-on their online reputation.
-One option would be to have a reputation system in a global location-proof 
-system, another would be to tie it to a reputation system already used in e.g.\ 
-\iac{OSN}.
-One possible solution would be to include a commitment in the \ac{LPS} and when 
-necessary use it to tie it to the online identity.
-
-\subsection{One Proof for All}
-
-The naïve approach would be that everyone generates \acp{LPS} for everyone 
-else, but this would be computationally and communicatively expensive 
-(\(O(n^2)\)).
-A better approach would be \iac{SMC} scheme where several witnesses participate 
-to compute a joint \ac{LPS} for one prover.
-This would reduce the need for pairwise communication.
-In our scenario each witness will also want to participate as a prover, if the 
-jointly computed \ac{LPS} could further be used by all participants in the 
-computation, this would reduce the complexity further.
-
-To make it even more efficient, it would be desirable to make the proofs 
-\enquote{transitive}.
-I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
-act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
-Speaking in graphs, we want to be able to join sub-graphs instead of having to 
-join node-by-node.
-
-\subsubsection*{\ackname}
-
-This work was funded by the Swedish Foundation for Strategic Research grant SSF 
-FFL09-0086 and the Swedish Research Council grant VR 2009-3793.
-
-\printbibliography{}

### 2016-07-18 SystemModel.tex
Renames Model to SystemModel.tex

--- 2016-04-19 PPProtestAuth-content.tex
@@
-\title{%
-  Verifying Demonstrations
-}
-\author[D.~Bosk et al.]{%
-  Daniel Bosk\inst{1}
-  \and
-  Sébastien Gambs\inst{2}
-  \and
-  Sonja Buchegger\inst{1}
-}
-\institute[KTH, UQAM]{%
-  School of Computer Science and Communication\\
-  KTH Royal Institute of Technology, Stockholm\\
-  \texttt{\{dbosk,buc\}@kth.se}
-  \and
-  Université de Quebec à Montreal\\
-  \texttt{sgambs@uqam.ca}
-}
-
-\maketitle
-
-\mode*
-
-\begin{abstract}
-  \dots
-
-  \keywords{\dots}
-\end{abstract}
-
-\section{Introduction}
-\label{Introduction}
-
-There are different possibilities for a protest: e.g.\ one performed online or 
-one performed in the physical reality.
-Purely online protests are essentially petitions.
-This case can use digital signatures to verify the authenticity of a list of 
-names.
-It can also be compared to electronic voting --- to vote for or against 
-something.
-In this case all participants and third-parties can verify the authenticity of 
-the result, but cannot verify the vote of an individual.
-
-We are interested in real-world protests, for these we need to bind all 
-participants to the same physical location at a reasonably similar time (within 
-the duration of the protest).
-\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
-which provides a participant with a proof of being at the location.
-However, we would like that any participant can prove the demonstration's 
-authenticity to a third-party, e.g.\ the UN or a human-rights 
-organization.
-The reason this is an interesting property is the following scenario:
-Imagine there is a demonstration, the police shows up and tries to apprehend 
-every participant.
-However, one demonstrator survives and manages to flee the country, here the 
-demonstrator wants to prove that there was a protest of a certain size.
-
-There are at least two reasons we are interested in authenticating a protest in 
-this way:
-\begin{enumerate}
-  \item for a third-party can verify the authenticity of the protest, e.g.\ 
-    that there were \(n\) participants;
-  \item for the organizers to use the participation as feedback into 
-    a reputation system.
-\end{enumerate}
-We want to do this in a privacy-preserving way:
-We want to verify the participation of a protest, but not identifying 
-individuals who participated.
-If a demonstrator flees the country, that demonstrator should be able to prove 
-to the e.g.\ the UN that there were \(n\) participants.
-But if the demonstrator is caught by the secret police before leaving, then the 
-secret police should not learn the identities of the other participants.
-
-\subsection{The Problem}
-
-Usually the count by the organizers and count by police differs, we want to 
-solve this problem.
-
-We can divide the problem into three parts:
-\begin{itemize}
-  \item Register participants in the system.
-  \item Collect the necessary data.
-  \item Perform the counting and verification.
-\end{itemize}
-
-To register the participants we might be able to piggy-back on existing 
-\acp{PKI} and blind signatures --- similarly as for voting systems.
-
-We have the verifiability properties in voting:
-\begin{description}
-  \item[Individual] Individual verifiability allows a voter to verify her own 
-    vote was included in the election outcome.
-  \item[Universal] Universal verifiability allows voters or observers to check 
-    that the election outcome corresponds to the votes cast.
-  \item[Eligibility] Eligibility verifiability allows voters and observers to 
-    check that each vote in the election outcome was cast by a uniquely 
-    registered voter.
-\end{description}
-
-\section{Adapting PROPS}
-\label{AdaptingPROPS}
-
-\subsection{The \acs*{CA} Problems}
-
-One issue is the \ac{CA}.
-One direction we can take to solve this is by threshold signatures, e.g.\ 
-\cite{FSThresholdSignatures}.
-This way the participants can jointly issue new certificates, by signing them 
-using the threshold signature scheme.
-This should solve part of the problems related to Sybil attacks too.
-But, if \(k > t\) participants collude, they can create multiple identities for 
-themselves.
-The main problem to solve, however, is that we want \(n\), and possibly \(t\) 
-too, to change with the number of participants.
-I'm not sure, but in what I've read about threshold schemes, they generally 
-keep \(n\) and \(t\) fixed.
-
-Another direction on solving the \ac{CA} problem, is if we can use already 
-existing \acp{PKI} instead.
-E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
-DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
-running everything through a hash function and the sign that value.
-Due to the use of the hash function we cannot prove in zero knowledge that we 
-have a signed certificate.
-But maybe we can use the keys \((pq, e)\) and \((p, q, d)\) in such a way that 
-they do not reveal the identity, but that we can if needed --- similar to 
-a commitment which we reveal only in emergencies.
-
-It would be interesting to solve the W--P collusion attack, where the witness 
-reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
-individuals fake this information at home.
-One possibility in our scenario is that e.g.\ an external journalist on 
-location can create \iac{LPS}, because a journalist is generally trusted.
-This would be useful as occasionally journalists are also captured, and anyone 
-that escaped should be able to show a convincing proof.
-However, one problem with this is that the journalist will not necessarily have 
-a key signed by the \ac{CA} of our scheme, but rather a \ac{CA} of say a UN 
-\ac{PKI}.
-
-In relation to the previous, it would be interesting to be able to tie the 
-\acp{LP} (or \acp{LPS}) to a reputation system.
-Then, even if no external journalist is on location, the participants can rely 
-on their online reputation.
-One option would be to have a reputation system in a global location-proof 
-system, another would be to tie it to a reputation system already used in e.g.\ 
-\iac{OSN}.
-One possible solution would be to include a commitment in the \ac{LPS} and when 
-necessary use it to tie it to the online identity.
-
-\subsection{One Proof for All}
-
-The naïve approach would be that everyone generates \acp{LPS} for everyone 
-else, but this would be computationally and communicatively expensive 
-(\(O(n^2)\)).
-A better approach would be \iac{SMC} scheme where several witnesses participate 
-to compute a joint \ac{LPS} for one prover.
-This would reduce the need for pairwise communication.
-In our scenario each witness will also want to participate as a prover, if the 
-jointly computed \ac{LPS} could further be used by all participants in the 
-computation, this would reduce the complexity further.
-
-To make it even more efficient, it would be desirable to make the proofs 
-\enquote{transitive}.
-I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
-act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.
-Speaking in graphs, we want to be able to join sub-graphs instead of having to 
-join node-by-node.
-
 \section{System Model}
@@
 signatures~\cite{UniqueGroupSignatures,UniqueRingSignatures,ListSignatures}.
-
-\section{Useful Primitives}
-\label{UsefulPrimitives}
-
-\dots
-
-\subsubsection*{Acknowledgements}
-
-This work was funded by the Swedish Foundation for Strategic Research grant SSF 
-FFL09-0086 and the Swedish Research Council grant VR 2009-3793.
-
-\printbibliography{}

### 2017-06-01 DataAuthenticity.tex
Adds material from Protesting Chapter
Adapts material so that it compiles, but no editing.

\section{Data authenticity}
\label{DataAuthenticity}

The problem of authentically associating data with a physical event is 
difficult.
We can essentially divide it into the following requirements:
\begin{requirements}[A]
  \item\label{CreatedAfterStart} Prove that the data was created after the 
    start of the event.
  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
    of the event.
  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
    physical location of the event.
\end{requirements} %TODO: A4 accurate/not fabricated?
\Cref{CreatedBeforeEnd,CreatedAfterStart} together bind the data to the time of 
the event whereas \cref{SpatiallyRelated} binds the data spatially to the 
event.

Now, consider the scenario of Alice taking a photo during the demonstration and 
posting it online.
What can we say about this photo?
First, we can say that it was created before we viewed it, so 
\cref{CreatedBeforeEnd} is fulfilled if we view it in relation to the event.
If it was submitted to a service that we trust, e.g.\ a blockchain, then we can 
also trust the time-stamp of the service for fulfilling 
\cref{CreatedBeforeEnd}.
Furthermore, we can also consider it spatially related to the physical location
(\cref{SpatiallyRelated}) if we can convince ourselves that the photo is 
depicting the physical location and not any kind of \enquote{reconstruction}, 
e.g.\ it is not computer generated or a photo of a similarly looking location.

\Cref{CreatedAfterStart} is more difficult to achieve.
In the above scenario, there is nothing that prevents Alice from submitting an 
older photo which is spatially related to the event.
In the security field \cref{CreatedAfterStart} is captured by a property called 
\emph{freshness}.
The freshness property is usually achieved by requiring that the data depend on
an unpredictable value.
The unpredictable value is commonly a value chosen randomly by the verifier, 
but there are ways to do this without the verifier too --- the basic 
requirement is that it is not under the prover's control, i.e.\ Alice in this 
scenario.
The idea is illustrated by the following example: we require Alice to include 
the front-page of a particular newspaper in the photo, since the exact 
front-page is difficult for Alice to predict in advance.
This particular example would of course not work in practice, since Alice can 
manipulate the photo afterwards to superimpose the required newspaper 
front-page\footnote{%
  There is, however, a subfield of digital forensics that works with image 
  manipulation detection, so there are methods that would prevent at least 
  Alice's easiest manipulation attempts.
}.
But this illustrates another important requirement for freshness: that the 
operation binding the unpredicatble value to the data must be difficult to redo 
later to change the value.

### 2017-06-01 Verification.tex
Adds material from Protesting Chapter
Adapts material so that it compiles, but no editing.

\section{Verification}
\label{Verification}

In general, protesting is very similar to voting: both are many individuals 
expressing their opinion.
Hence we desire to have similar properties of verification and privacy for 
participation in a protest as there is for voting.
As was pointed out in the introduction, an online protest can be modelled as 
a petition, which in turn can use electronic voting protocols.
We are interested in translating these properties into a demonstration, i.e.\ 
a street-protest.

In the context of (electronic) voting protocols, there are three requirements 
for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
We can translate these to the case of participation in a demonstration, then 
each vote would be replaced by a proof of participation (in either the protest 
or any counter-protest).
\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
each participation proof belongs to a unique individual, i.e.\ to prevent any 
Sybil attack.

The three verifiability properties above are indeed desirable, e.g.\ then the 
\ac{UN} can verify protests happening in a country and the country cannot deny 
it, thus the \ac{UN} can apply pressure if needed.
However, these properties are difficult to accomplish with computer vision 
methods, especially if nobody that the \ac{UN} can trust has been on location 
to collect the image material for the analysis --- otherwise the authenticity 
can be questioned (as discussed in \cref{DataAuthenticity}).

We also need privacy in addition to the verification requirements.
In voting, we have the following requirements:
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the vote does not reveal any individual 
  vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
We can see that \cref{VotePrivacy,ReceiptFreeness} are desirable in Alice's 
situation: there should not be any proof which binds Alice to the participation 
of the demonstration (\cref{ReceiptFreeness}), because she does not want to 
explicitly reveal her opinions to the government (\cref{VotePrivacy}) due to 
the risk of reprimands.
\Cref{ReceiptFreeness} implies that even if Alice is arrested, the data should 
not provide any proof to the regime's agents that can reveal Alice's opinion.

A demonstration is very different from voting in one sense: Alice must be 
physically present and that very precense shows her support for the cause.
In voting, on the other hand, Alice has multiple options which are not revealed
by her mere precense.
As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
and Bob by the data.
So as long as Alice and Bob can conceal their identities at the demonstration 
and escape without arrest, their support is recorded in the data while their 
privacy is not violated.
(Following this line of thinking, it can actually be beneficial for the privacy of 
the demonstrators to mix with the participants from any counter-demonstrations 
--- as long as the correct counts for each demonstration can still be ensured, 
which is the idea.)

The main problem is how to ensure the connection between the physical location 
and the data used for verification, i.e.\ fulfil all the requirements for 
authenticity, verification and privacy given above.
We must bind participants to the same physical location at a reasonably similar 
time, i.e.\ within the area and duration of the demonstration.
In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
was in one place during an entire day and then repeated for several 
weekends.
In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
were in several locations at the same time.

%This means that for a system like this to work, we also need the requirements 
%from \cref{DataAuthenticity}: proof that the data was created after the start 
%of the protest, proof that it was created before the end, and proof of spatial 
%relation to the location.

\textcite{PROPS} developed a decentralized \ac{LPS} which provides 
a participant with a verifiable proof of having been at a location at a certain 
time, something we call \iac{LP}.
It is decentralized because there is no central authority that vouches for the 
location, instead peers act as witnesses.
Then a third-party can verify the authenticity of the \ac{LP}, by verifying the 
witnesses' signatures, and can thus be sure that the person has indeed been in 
the location.
Bosk, Gambs and Buchegger are currently exploring (work in progress) the 
possibility of combining such \iac{LPS} with the verifiability and privacy 
requirements discussed above.
The overall idea is that each participant generates \iac{LP} during the 
demonstration, where (some of) the other protesters act as witnesses, then the 
\acp{LP} can be used to compute the participation count with all the 
authenticity, verifiability and privacy requirements above.
%TODO: reviewer: what about cellphones to count attendance
% This is actually done in \cite{2016DemonstrationsInSeoul}, it requires some 
% assumptions --- but they use wifi signals instead of the mobile network.
% In either case, we pointed out that one wants the phone in flight mode due to
% surveillance.

### 2017-06-01 intro.tex
Adds material from Protesting Chapter
Adapts material so that it compiles, but no editing.

@@
 
+One problem in real-world demonstrations that has not yet been entirely solved 
+is the crowd-counting problem, i.e.\ the verification of the participation in 
+a demonstration.
+After many demonstrations the count by police and that by the organizers 
+differ, in some instances the difference can be hundreds of thousands.
+There are numerous examples, e.g.\ the demonstrations in South 
+Korea~\cite{2016DemonstrationsInSeoul} or the women's marches in the 
+US~\cite{2017WomensMarchesInUS}, where there is difficulty in establishing the 
+actual number of participants.
+The methods for counting the crowds vary.
+There are some techniques using computer vision found in the research 
+literature, e.g.\ by~\textcite{CVCrowdCounting}.
+These require images from the demonstration and provide no way to verify the 
+authenticity of the count (except re-running the algorithm on one's own input 
+data).
+However, as is illustrated by 
+\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the methods used in 
+practice are manual and prone to errors.
+
+The main goal for Alice after a protest is to provide verifiable data.
+For example, how can she ensure that photos from a demonstration are authentic?
+We can probably recognize the place the photo is portraying, however, this 
+might just as well be a reconstruction or entirely computer generated.
+We cannot trust the meta-data of the photo, such as time-stamps of the file, 
+because these can easily be manipulated.
+So the only thing we can say for sure is that the photo was taken at the latest 
+at the time of publication.
+Now, if we cannot trust these photos, how can we determine the number of 
+participants of a demonstration?
+Many of the techniques require photos for doing this.
+Furthermore, as is shown by 
+\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the numbers 
+determined by these techniques have rather large margins.
+
+Alice also has another problem.
+Assume that she can provide this verifiable data.
+Alice and Bob do not want that this data ties them to the demonstration, 
+because then Eve can use this data to find out about Alice and Bob and arrest 
+them.
+Thus, what Alice and Bob need is a system which can provide data authenticity 
+and user privacy, i.e.\ that the data can be correctly tied to the 
+demonstration without outing Alice and Bob as supporters.
+
 \subsection{The Problem}

### 2017-06-01 DataAuthenticity.tex
Edits data authenticity

@@
 In the above scenario, there is nothing that prevents Alice from submitting an 
-older photo which is spatially related to the event.
-In the security field \cref{CreatedAfterStart} is captured by a property called 
-\emph{freshness}.
-The freshness property is usually achieved by requiring that the data depend on
-an unpredictable value.
-The unpredictable value is commonly a value chosen randomly by the verifier, 
-but there are ways to do this without the verifier too --- the basic 
-requirement is that it is not under the prover's control, i.e.\ Alice in this 
-scenario.
-The idea is illustrated by the following example: we require Alice to include 
-the front-page of a particular newspaper in the photo, since the exact 
-front-page is difficult for Alice to predict in advance.
-This particular example would of course not work in practice, since Alice can 
-manipulate the photo afterwards to superimpose the required newspaper 
-front-page\footnote{%
-  There is, however, a subfield of digital forensics that works with image 
-  manipulation detection, so there are methods that would prevent at least 
-  Alice's easiest manipulation attempts.
-}.
-But this illustrates another important requirement for freshness: that the 
-operation binding the unpredicatble value to the data must be difficult to redo 
-later to change the value.
+older photo which is spatially related to the event --- i.e.\ to ensure 
+\cref{CreatedAfterStart} we must ensure some sort of freshness.
+% XXX Verify that this can be done using Fiat-Shamir heuristic
+This can (probably) be solved using the Fiat--Shamir 
+heuristic~\cite{FiatShamirHeuristic} (or something similar).
+The main idea is that the operation binding the unpredictable value to the data 
+must be difficult to redo later to change the value.
+
+Instead of a photo, we will use \acp{LP}, more specifically, we will use 
+\ac{PROPS}.
+This will allow us to fulfil \cref{SpatiallyRelated}.
+Since a location proof is a cryptographic value, it is easier to adapt it to 
+fulfil \cref{CreatedAfterStart} too (compared to a photo).

### 2017-06-01 SystemModel.tex
Edits intro

@@
 \label{SystemModel}
+
+We can divide the problem into three parts:
+\begin{itemize}
+  \item Register participants in the system.
+  \item Collect the necessary data.
+  \item Perform the counting and verification.
+\end{itemize}
+
+To register the participants we might be able to piggy-back on existing 
+\acp{PKI} and blind signatures --- similarly as for voting systems.
+
+There are several issues that must be treated:
+\begin{itemize}
+  \item Each location proof must be bound to one individual's participation.
+    One protester must not be able to create two unique location proofs and be 
+    able to increase the number of participants, that would violate 
+    \cref{EligibilityVerif} above.
+    In other words, we must prevent the Sybil attack.
+
+  \item A group of people should not be able to generate \acp{LP} to make it 
+    look as if they participated in the protest but actually stayed at home.
+    This means that all \acp{LP} must be linked to each other.
+    If a protest has hundreds of thousands of participants, then this linking 
+    must be achieved efficiently.
+\end{itemize}
 

### 2017-06-01 intro.tex
Edits intro

@@
 one performed in the physical reality.
-Purely online protests are essentially petitions.
-This case can use digital signatures to verify the authenticity of a list of 
-names.
-It can also be compared to electronic voting --- to vote for or against 
-something.
-In this case all participants and third-parties can verify the authenticity of 
-the result, but cannot verify the vote of an individual.
-
-We are interested in real-world protests, for these we need to bind all 
-participants to the same physical location at a reasonably similar time (within 
-the duration of the protest).
-\citeauthor{PROPS} developed a decentralized location-proof system, \ac{PROPS}, 
-which provides a participant with a proof of being at the location.
-However, we would like that any participant can prove the demonstration's 
-authenticity to a third-party, e.g.\ the UN or a human-rights 
-organization.
-The reason this is an interesting property is the following scenario:
-Imagine there is a demonstration, the police shows up and tries to apprehend 
-every participant.
-However, one demonstrator survives and manages to flee the country, here the 
-demonstrator wants to prove that there was a protest of a certain size.
-
-There are at least two reasons we are interested in authenticating a protest in 
-this way:
-\begin{enumerate}
-  \item for a third-party can verify the authenticity of the protest, e.g.\ 
-    that there were \(n\) participants;
-  \item for the organizers to use the participation as feedback into 
-    a reputation system.
-\end{enumerate}
-We want to do this in a privacy-preserving way:
-We want to verify the participation of a protest, but not identifying 
-individuals who participated.
-If a demonstrator flees the country, that demonstrator should be able to prove 
-to the e.g.\ the UN that there were \(n\) participants.
-But if the demonstrator is caught by the secret police before leaving, then the 
-secret police should not learn the identities of the other participants.
-
+We are interested in real-world protests, specifically to verify a protest.
 One problem in real-world demonstrations that has not yet been entirely solved 
@@
 There are some techniques using computer vision found in the research 
-literature, e.g.\ by~\textcite{CVCrowdCounting}.
+literature, e.g.\ by \textcite{CVCrowdCounting}.
 These require images from the demonstration and provide no way to verify the 
@@
 practice are manual and prone to errors.
+In this paper, we combine electronic voting with location-proof systems.
 
-The main goal for Alice after a protest is to provide verifiable data.
-For example, how can she ensure that photos from a demonstration are authentic?
+Alice is an activist who organizes a demonstration for some cause.
+Her main goal after the protest is to provide verifiable data.
+Alice several problems:
+\begin{itemize}
+  \item She must prove that the data is related to the event, that it is not 
+    reused data from previous demonstrations.
+  \item She must provide data which can be used for the desired verification of 
+    the event.
+  \item She must also consider the privacy of the participating individuals.
+\end{itemize}
+Since many of the current techniques are based on photos, we will give an 
+example of Alice's problems in that setting.
+How can she ensure that photos from a demonstration are authentic?
 We can probably recognize the place the photo is portraying, however, this 
@@
 participants of a demonstration?
-Many of the techniques require photos for doing this.
-Furthermore, as is shown by 
-\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the numbers 
-determined by these techniques have rather large margins.
+This is discussed further in \cref{DataAuthenticity}.
 
-Alice also has another problem.
-Assume that she can provide this verifiable data.
+Assume that Alice can provide this authenticated data.
 Alice and Bob do not want that this data ties them to the demonstration, 
-because then Eve can use this data to find out about Alice and Bob and arrest 
-them.
+because then the autocrat Eve can use this data to find out about Alice and Bob 
+and arrest them.
 Thus, what Alice and Bob need is a system which can provide data authenticity 
 and user privacy, i.e.\ that the data can be correctly tied to the 
-demonstration without outing Alice and Bob as supporters.
+demonstration without outing Alice and Bob as supporters but still ensuring 
+that Alice is Alice and Bob is Bob.
+As a protest can be compared to voting (either voting for or against the 
+cause), we will adapt the security and privacy properties of electronic 
+voting.
+We will discuss this further in \cref{Verification}.
 
-\subsection{The Problem}
-
-Usually the count by the organizers and count by police differs, we want to 
-solve this problem.
-
-We can divide the problem into three parts:
-\begin{itemize}
-  \item Register participants in the system.
-  \item Collect the necessary data.
-  \item Perform the counting and verification.
-\end{itemize}
-
-To register the participants we might be able to piggy-back on existing 
-\acp{PKI} and blind signatures --- similarly as for voting systems.
-
-We have the verifiability properties in voting:
-\begin{description}
-  \item[Individual] Individual verifiability allows a voter to verify her own 
-    vote was included in the election outcome.
-  \item[Universal] Universal verifiability allows voters or observers to check 
-    that the election outcome corresponds to the votes cast.
-  \item[Eligibility] Eligibility verifiability allows voters and observers to 
-    check that each vote in the election outcome was cast by a uniquely 
-    registered voter.
-\end{description}
-
-There are several issues that must be treated:
-\begin{itemize}
-  \item Each location proof must be bound to one individual's participation.
-    One protester must not be able to create two unique location proofs and be 
-    able to increase the number of participants, that would violate 
-    \cref{VerifEligibility} above.
-    In other words, we must prevent the Sybil attack.
-
-  \item A group of people should not be able to generate \acp{LP} to make it 
-    look as if they participated in the protest but actually stayed at home.
-    This means that all \acp{LP} must be linked to each other.
-    If a protest has hundreds of thousands of participants, then this linking 
-    must be achieved efficiently.
-\end{itemize}
+It can also be compared to electronic voting --- to vote for or against the 
+cause.
+In this case all participants and third-parties can verify the authenticity of 
+the result, this would inherit all the desirable properties of the electronic 
+voting system (these properties are discussed in \cref{Verification}).
+We are interested in real-world protests, i.e.\ demonstrations where 
+participants gather in a physical location.
+For these we need to bind all participants to the same physical location at 
+a reasonably similar time (within the duration of the protest).

### 2017-07-13 intro.tex
Moves auth and verif properties to properties.tex

@@
 In this paper, we combine electronic voting with location-proof systems.
-
-Alice is an activist who organizes a demonstration for some cause.
-Her main goal after the protest is to provide verifiable data.
-Alice several problems:
-\begin{itemize}
-  \item She must prove that the data is related to the event, that it is not 
-    reused data from previous demonstrations.
-  \item She must provide data which can be used for the desired verification of 
-    the event.
-  \item She must also consider the privacy of the participating individuals.
-\end{itemize}
-Since many of the current techniques are based on photos, we will give an 
-example of Alice's problems in that setting.
-How can she ensure that photos from a demonstration are authentic?
-We can probably recognize the place the photo is portraying, however, this 
-might just as well be a reconstruction or entirely computer generated.
-We cannot trust the meta-data of the photo, such as time-stamps of the file, 
-because these can easily be manipulated.
-So the only thing we can say for sure is that the photo was taken at the latest 
-at the time of publication.
-Now, if we cannot trust these photos, how can we determine the number of 
-participants of a demonstration?
-This is discussed further in \cref{DataAuthenticity}.
-
-Assume that Alice can provide this authenticated data.
-Alice and Bob do not want that this data ties them to the demonstration, 
-because then the autocrat Eve can use this data to find out about Alice and Bob 
-and arrest them.
-Thus, what Alice and Bob need is a system which can provide data authenticity 
-and user privacy, i.e.\ that the data can be correctly tied to the 
-demonstration without outing Alice and Bob as supporters but still ensuring 
-that Alice is Alice and Bob is Bob.
-As a protest can be compared to voting (either voting for or against the 
-cause), we will adapt the security and privacy properties of electronic 
-voting.
-We will discuss this further in \cref{Verification}.
-
-It can also be compared to electronic voting --- to vote for or against the 
-cause.
-In this case all participants and third-parties can verify the authenticity of 
-the result, this would inherit all the desirable properties of the electronic 
-voting system (these properties are discussed in \cref{Verification}).
-We are interested in real-world protests, i.e.\ demonstrations where 
-participants gather in a physical location.
-For these we need to bind all participants to the same physical location at 
-a reasonably similar time (within the duration of the protest).

### 2017-07-13 properties.tex
Moves auth and verif properties to properties.tex

--- 2017-06-01 Verification.tex
@@
-\section{Verification}
+\mode*
+\section{Data authenticity and verification}
+
+Alice is an activist who organizes a demonstration for some cause.
+Her main goal after the protest is to provide verifiable data.
+There are several problems:
+\begin{itemize}
+  \item Alice must prove that the data is related to the event, that it is not 
+    reused data from previous demonstrations.
+  \item Alice must provide data which can be used for the desired verification 
+    of the event.
+  \item Alice must also consider the privacy of the participating individuals.
+\end{itemize}
+Since many of the current techniques are based on photos, we will give an 
+example of Alice's problems in that setting.
+How can she ensure that photos from a demonstration are authentic?
+We can probably recognize the place the photo is portraying, however, this 
+might just as well be a reconstruction or entirely computer generated.
+We cannot trust the meta-data of the photo, such as time-stamps of the file, 
+because these can easily be manipulated.
+So the only thing we can say for sure is that the photo was taken at the latest 
+at the time of publication.
+Now, if we cannot trust these photos, how can we determine the number of 
+participants of a demonstration?
+This is discussed further in \cref{DataAuthenticity}.
+
+Assume that Alice can provide this authenticated data.
+Alice and Bob do not want that this data ties them to the demonstration, 
+because then the autocrat Eve can use this data to find out about Alice and Bob 
+and arrest them.
+Thus, what Alice and Bob need is a system which can provide data authenticity 
+and user privacy, i.e.\ that the data can be correctly tied to the 
+demonstration without outing Alice and Bob as supporters but still ensuring 
+that Alice is Alice and Bob is Bob.
+As a protest can be compared to voting (either voting for or against the 
+cause), we will adapt the security and privacy properties of electronic 
+voting.
+We will discuss this further in \cref{Verification}.
+
+It can also be compared to electronic voting --- to vote for or against the 
+cause.
+In this case all participants and third-parties can verify the authenticity of 
+the result, this would inherit all the desirable properties of the electronic 
+voting system (these properties are discussed in \cref{Verification}).
+We are interested in real-world protests, i.e.\ demonstrations where 
+participants gather in a physical location.
+For these we need to bind all participants to the same physical location at 
+a reasonably similar time (within the duration of the protest).
+
+\subsection{Data authenticity}
+\label{DataAuthenticity}
+
+The problem of authentically associating data with a physical event is 
+difficult.
+We can essentially divide it into the following requirements:
+\begin{frame}
+\begin{requirements}[A]
+  \item\label{CreatedAfterStart} Prove that the data was created after the 
+    start of the event.
+  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
+    of the event.
+  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
+    physical location of the event.
+\end{requirements} %TODO: A4 accurate/not fabricated?
+\end{frame}
+\Cref{CreatedBeforeEnd,CreatedAfterStart} together bind the data to the time of 
+the event whereas \cref{SpatiallyRelated} binds the data spatially to the 
+event.
+
+Now, consider the scenario of Alice taking a photo during the demonstration and 
+posting it online.
+What can we say about this photo?
+First, we can say that it was created before we viewed it, so 
+\cref{CreatedBeforeEnd} is fulfilled if we view it in relation to the event.
+If it was submitted to a service that we trust, e.g.\ a blockchain, then we can 
+also trust the time-stamp of the service for fulfilling 
+\cref{CreatedBeforeEnd}.
+Furthermore, we can also consider it spatially related to the physical location
+(\cref{SpatiallyRelated}) if we can convince ourselves that the photo is 
+depicting the physical location and not any kind of \enquote{reconstruction}, 
+e.g.\ it is not computer generated or a photo of a similarly looking location.
+
+\Cref{CreatedAfterStart} is more difficult to achieve.
+In the above scenario, there is nothing that prevents Alice from submitting an 
+older photo which is spatially related to the event --- i.e.\ to ensure 
+\cref{CreatedAfterStart} we must ensure some sort of freshness.
+% XXX Verify that this can be done using Fiat-Shamir heuristic
+This can (probably) be solved using the Fiat--Shamir 
+heuristic~\cite{FiatShamirHeuristic} (or something similar).
+The main idea is that the operation binding the unpredictable value to the data 
+must be difficult to redo later to change the value.
+
+Instead of a photo, we will use \acp{LP}, more specifically, we will use 
+\ac{PROPS}.
+This will allow us to fulfil \cref{SpatiallyRelated}.
+Since a location proof is a cryptographic value, it is easier to adapt it to 
+fulfil \cref{CreatedAfterStart} too (compared to a photo).
+
+\subsection{Verification}
 \label{Verification}
@@
 for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\begin{frame}
 \begin{requirements}[V]
@@
 \end{requirements}
+\end{frame}
 We can translate these to the case of participation in a demonstration, then 
@@
 In voting, we have the following requirements:
+\begin{frame}
 \begin{requirements}[P]
@@
 \end{requirements}
+\end{frame}
 \Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 

### 2017-07-13 abstract.tex
Fixes affil and abstract

Alice organizes a protest for some change in government.
The protest is held in some location(s).
Alice wants to estimate the number of participants to prove certain support for
her change.
Current methods have wide margins for error.
In addition, Alice's incentive is to estimate the number of participants as 
high as possible whereas the government's incentive is to estimate the number 
of participants as low as possible.

We are interested in combining location proofs with electronic voting.
Since the parties' have incentives to cheat, we require transparency: we desire 
a decentralized scheme that provides the verifiability and privacy properties 
of electronic voting.
The scheme must be scalable to handle large protests.

\keywords{%
  crowd-counting; protesting; electronic voting; location proofs; privacy
}

### 2017-07-13 intro.tex
Fixes so that beamerarticle modes are correct
Adds some slides

@@
+\mode*
+
 \section{Introduction}
@@
 a demonstration.
+
+\subsection<presentation>{What's the problem?}
+
+\begin{frame}<presentation>
+  \begin{block}{The crowd-counting problem}
+    \begin{itemize}
+      \item Alice organizes a protest against Eve's regime.
+      \item Bob, Carol and others show up.
+      \item We want to know how many showed up to support Alice.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{example}
+    \begin{itemize}
+      \item Computer Vision to do object recognition.
+      \item Requires photos that cover the entire location, all the time.
+    \end{itemize}
+  \end{example}
+
+  \pause
+
+  \begin{example}
+    \begin{itemize}
+      \item Scan active mobile phones in the area.
+      \item This requires some extra equipment.
+      \item This catches bystanders who are not protesting.
+    \end{itemize}
+  \end{example}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{example}
+    \begin{itemize}
+      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
+        approximate count by imagery.
+
+      \item US 2017~\cite{2017WomensMarchesInUS}:
+        sum up people's approximations.
+    \end{itemize}
+  \end{example}
+\end{frame}
+
+\subsection<presentation>{Why is it a problem?}
+
+\begin{frame}<presentation>
+  \begin{block}{Verifying protest participation}
+    \begin{itemize}
+      \item Alice organizes a protest against Eve's regime.
+      \item Bob, Carol and others show up.
+
+        \pause
+
+      \item {\color{green} Alice wants to show that many support her cause.}
+
+        \pause
+
+      \item {\color{red} Eve wants to show that few support Alice's cause.}
+
+        \pause
+
+      \item It's an adversarial setting!
+      \item We need verifiable results.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
 After many demonstrations the count by police and that by the organizers 

### 2017-07-17 intro.tex
Improves summarizing paragraph of introduction

@@
 practice are manual and prone to errors.
-In this paper, we combine electronic voting with location-proof systems.
+
+We can make one important observation about this problem that has seemingly 
+been ignored in the past: it is an adversarial setting.
+The protesters (organizers and participants) have an incentive to increase the 
+tallied number of participants, whereas other interests might have an incentive 
+to decrease the tallied number of participants, e.g.\ an authoritarian regime.
+To solve this problem, we need a verifiable participation count.
+In this paper, we combine the verifiability and privacy properties of 
+electronic voting with location-proof systems to provide a verifiable 
+participation count.

### 2017-07-17 properties.tex
Adds some slides
Adds slides and notes for properties

@@
 \mode*
-\section{Data authenticity and verification}
+\section{Authenticity, verification and privacy}
 
@@
 There are several problems:
+\begin{frame}
 \begin{itemize}
@@
 \end{itemize}
+\end{frame}
 Since many of the current techniques are based on photos, we will give an 
@@
 
-Now, consider the scenario of Alice taking a photo during the demonstration and 
-posting it online.
-What can we say about this photo?
-First, we can say that it was created before we viewed it, so 
-\cref{CreatedBeforeEnd} is fulfilled if we view it in relation to the event.
-If it was submitted to a service that we trust, e.g.\ a blockchain, then we can 
-also trust the time-stamp of the service for fulfilling 
-\cref{CreatedBeforeEnd}.
-Furthermore, we can also consider it spatially related to the physical location
-(\cref{SpatiallyRelated}) if we can convince ourselves that the photo is 
-depicting the physical location and not any kind of \enquote{reconstruction}, 
-e.g.\ it is not computer generated or a photo of a similarly looking location.
+\begin{frame}<presentation>
+  \begin{solution}[A\ref{CreatedAfterStart}, after start]
+    \begin{itemize}
+      \item Include an unpredictable value in the proof.
+      \item This could be e.g.\ the (hash of the) head of block chain.
+      \item This prevents creating proofs for future protests.
+    \end{itemize}
+  \end{solution}
 
-\Cref{CreatedAfterStart} is more difficult to achieve.
-In the above scenario, there is nothing that prevents Alice from submitting an 
-older photo which is spatially related to the event --- i.e.\ to ensure 
-\cref{CreatedAfterStart} we must ensure some sort of freshness.
-% XXX Verify that this can be done using Fiat-Shamir heuristic
-This can (probably) be solved using the Fiat--Shamir 
-heuristic~\cite{FiatShamirHeuristic} (or something similar).
-The main idea is that the operation binding the unpredictable value to the data 
-must be difficult to redo later to change the value.
+  \pause
 
-Instead of a photo, we will use \acp{LP}, more specifically, we will use 
-\ac{PROPS}.
-This will allow us to fulfil \cref{SpatiallyRelated}.
-Since a location proof is a cryptographic value, it is easier to adapt it to 
-fulfil \cref{CreatedAfterStart} too (compared to a photo).
+  \begin{question}
+    \begin{itemize}
+      \item Is this hard?
+      \item I think we can show that it is.
+      \item What assumptions do we need for this?
+    \end{itemize}
+  \end{question}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{solution}[A\ref{CreatedBeforeEnd}, before end]
+    \begin{itemize}
+      \item Make the proof part of the block chain.
+      \item The proof must've been created before it was included.
+    \end{itemize}
+  \end{solution}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{solution}[A\ref{SpatiallyRelated}, correct location]
+    \begin{itemize}
+      \item The proof includes \iac{LP}.
+      \item The proof is \enquote{witnessed} (signed) by other participants.
+      \item We have a coarse location, just within protest area.
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{question}
+    \begin{itemize}
+      \item How can we do 1000s of \acp{LP} with 1000s of witnesses each?
+    \end{itemize}
+  \end{question}
+\end{frame}
+
+One primitive that provides the properties 
+\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
+consensus protocol.
+\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
+block chain in relation to the event.
+For \cref{CreatedAfterStart} we must include an unpredictable value in the 
+proof, e.g.\ the head of the block chain.
+
+If we include \iac{LP}, this will tie the proof to the physical location and, 
+thus, solve \cref{SpatiallyRelated}.
 
@@
 \label{Verification}
+
+We have an adversarial setting between Alice the activist and Eve the evil 
+regime: Alice wants to show large support against Eve, Eve wants to show little
+support for Alice.
+In this case we have two options:
+either we trust Alice or Eve, or we must verify their claims.
+We aim for verifiable claims.
 
@@
 participation in a protest as there is for voting.
-As was pointed out in the introduction, an online protest can be modelled as 
-a petition, which in turn can use electronic voting protocols.
-We are interested in translating these properties into a demonstration, i.e.\ 
-a street-protest.
-
 In the context of (electronic) voting protocols, there are three requirements 
@@
 We can translate these to the case of participation in a demonstration, then 
-each vote would be replaced by a proof of participation (in either the protest 
-or any counter-protest).
+each vote would be replaced by a proof of participation.
+
+If the proofs are included in a public block chain (as suggested in 
+\cref{DataAuthenticity}), then an individual can check that their proof has 
+been included in the chain.
+Thus \cref{IndividualVerif} is fulfilled.
+
+Anyone can count the proofs included in the block chain.
+They can also verify the proofs and thus verify the result, which fulfils 
+\cref{UniversalVerif}.
+
 \Cref{EligibilityVerif} would in this case mean that anyone can verify that 
-each participation proof belongs to a unique individual, i.e.\ to prevent any 
-Sybil attack.
+each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
+attacks.
 
-The three verifiability properties above are indeed desirable, e.g.\ then the 
-\ac{UN} can verify protests happening in a country and the country cannot deny 
-it, thus the \ac{UN} can apply pressure if needed.
-However, these properties are difficult to accomplish with computer vision 
-methods, especially if nobody that the \ac{UN} can trust has been on location 
-to collect the image material for the analysis --- otherwise the authenticity 
-can be questioned (as discussed in \cref{DataAuthenticity}).
+\subsection{Privacy}
+\label{Privacy}
 
@@
 \end{requirements}
+\mode<presentation>{
+\pause
+\begin{remark}
+  \begin{itemize}
+    \item Coercion resistance is difficult to achieve for voting.
+    \item It doesn't make much sense for protests.
+    \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
+      participate in.
+  \end{itemize}
+\end{remark}
+}
 \end{frame}

### 2017-07-19 properties.tex
Works through text and slides
Privacy section not work through entirely yet.

@@
 \end{requirements} %TODO: A4 accurate/not fabricated?
+
+\pause
+
+\mode<presentation>{
+\begin{idea}
+  \begin{itemize}
+    \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
+      A\ref{CreatedBeforeEnd}: a block chain.
+
+    \item Add a consensus protocol and Eve must subvert a majority to change 
+      the outcome.
+
+      \pause
+
+    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
+  \end{itemize}
+\end{idea}
+}
 \end{frame}
@@
 
+One primitive that provides the properties 
+\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
+consensus protocol.
+
+\begin{frame}
+  \begin{question}
+    Are there other strucutres than block chains?
+    E.g.~\cite{BlockchainFreeCryptocurrencies}.
+  \end{question}
+\end{frame}
+
+\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
+block chain \emph{in (time-wise) relation to the event}.
+Then we know that it cannot have been created after the event.
+
 \begin{frame}<presentation>
-  \begin{solution}[A\ref{CreatedAfterStart}, after start]
+  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
     \begin{itemize}
-      \item Include an unpredictable value in the proof.
-      \item This could be e.g.\ the (hash of the) head of block chain.
+      \item Make the \ac{LP} part of the block chain.
+      \item The proof must've been created before it was included (duh!).
+      \item (Also related to V\ref{EligibilityVerif}.)
+    \end{itemize}
+  \end{solution}
+\end{frame}
+
+For \cref{CreatedAfterStart} we must include an unpredictable value in the 
+proof, e.g.\ the head of the block chain.
+This means that we cannot create a proof and keep it for a future protest.
+This also prevents us from reusing proofs from previous protests.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
+    \begin{itemize}
+      \item Include an unpredictable value in the \ac{LP}.
+      \item This could be e.g.\ the hash of the head of the block chain.
       \item This prevents creating proofs for future protests.
     \end{itemize}
-  \end{solution}
+  \end{idea}
+  }
 
@@
   \begin{question}
-    \begin{itemize}
-      \item Is this hard?
-      \item I think we can show that it is.
-      \item What assumptions do we need for this?
-    \end{itemize}
+    How will this prevent us from reusing proofs from previous protests in 
+    the same location(s)?
+    (Related to V\ref{EligibilityVerif}.)
+    What are the assumptions?
+  \end{question}
+  \begin{question}
+    How hard is it to reuse old proofs?
   \end{question}
@@
 
-\begin{frame}<presentation>
-  \begin{solution}[A\ref{CreatedBeforeEnd}, before end]
+If we include \iac{LP}, this will tie the proof to the physical location and, 
+thus, solve \cref{SpatiallyRelated}.
+The \ac{LP} is \enquote{witnessed} (signed) by other participants.
+The \ac{LP} contains coarse coordinates of the location, which must be within 
+the protest area to be valid.
+This allows Bob the protester to move within the protest area to collect 
+witnesses (signatures).
+It also provides privacy since the location cannot be used to deanonymize Bob's 
+proof --- e.g.\ to correlate the location in his proof with captured 
+surveillance footage.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[A\ref{SpatiallyRelated} Correct location]
     \begin{itemize}
-      \item Make the proof part of the block chain.
-      \item The proof must've been created before it was included.
+      \item The \ac{LP} is \enquote{witnessed} (signed) by other participants.
+      \item We have a coarse location, just within protest area.
+      \item This allows protesters to move around to collect signatures.
+      \item This provides privacy for the location, e.g.\ cannot map to 
+        surveillance cameras.
     \end{itemize}
-  \end{solution}
-\end{frame}
-
-\begin{frame}<presentation>
-  \begin{solution}[A\ref{SpatiallyRelated}, correct location]
-    \begin{itemize}
-      \item The proof includes \iac{LP}.
-      \item The proof is \enquote{witnessed} (signed) by other participants.
-      \item We have a coarse location, just within protest area.
-    \end{itemize}
-  \end{solution}
+  \end{idea}
+  }
 
@@
   \begin{question}
-    \begin{itemize}
-      \item How can we do 1000s of \acp{LP} with 1000s of witnesses each?
-    \end{itemize}
+    How can we do \acp{LP} with 1000s of witnesses each?
+    And then 1000s of such \acp{LP}?
+  \end{question}
+  \begin{question}
+    Why should anyone trust these witnesses?
+    What are the assumptions?
   \end{question}
 \end{frame}
-
-One primitive that provides the properties 
-\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
-consensus protocol.
-\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
-block chain in relation to the event.
-For \cref{CreatedAfterStart} we must include an unpredictable value in the 
-proof, e.g.\ the head of the block chain.
-
-If we include \iac{LP}, this will tie the proof to the physical location and, 
-thus, solve \cref{SpatiallyRelated}.
 
@@
 each vote would be replaced by a proof of participation.
+To have any verifiability, we need the storage (i.e.\ block chain) to be 
+immutable.
+So we need a consensus protocol which prevents malicious changes.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{remark}
+    \begin{itemize}
+      \item For valid verification we must have an immutable block chain.
+      \item We need something like a consensus protocol to prevent malicious 
+        changes.
+    \end{itemize}
+  \end{remark}
+  }
+
+  \begin{question}
+    What can we achieve with a consensus protocol?
+    Majority must be honest?
+  \end{question}
+  \begin{question}
+    What is a suitable proof-of-work?
+    See e.g.~\cite{FairProofOfWork}.
+  \end{question}
+\end{frame}
 
@@
 
-Anyone can count the proofs included in the block chain.
-They can also verify the proofs and thus verify the result, which fulfils 
-\cref{UniversalVerif}.
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
+    \begin{itemize}
+      \item Proofs are stored publicly (block chain).
+      \item Each participant can check that their proof is indeed included.
+    \end{itemize}
+  \end{idea}
+  }
+
+  \pause
+
+  \begin{question}
+    Malicious nodes want to provide Alice with a view that her proof is 
+    included.
+    Everyone else is provided a view without Alice.
+    How can we ensure a consistent view for everyone?
+    (Probably similar to the solution in Joakim's thesis.)
+  \end{question}
+\end{frame}
 
@@
 attacks.
+They must also be able to detect if the proof is reused from a previous protest 
+(i.e.\ related to \cref{CreatedAfterStart,CreatedBeforeEnd}).
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
+    \begin{itemize}
+      \item Must verify that the proof is not reused from before 
+        (A\ref{CreatedAfterStart} and A\ref{CreatedBeforeEnd}).
+      \item Must verify that each proof belongs to a unique individual (not 
+        only Sybil).
+    \end{itemize}
+  \end{idea}
+  }
+
+  \pause
+
+  \begin{question}
+    How to solve the Sybil problem?
+  \end{question}
+  \begin{question}
+    This is similar to the double-spending problem for cryptocurrencies, can 
+    we reuse any such techniques?
+  \end{question}
+\end{frame}
+
+If the block chain is public, then anyone can download all the proofs, verify 
+them (eligibility) and count them.
+Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
+    \begin{itemize}
+      \item Proofs are stored publicly.
+      \item Anyone can download all proofs, verify them and then count them.
+    \end{itemize}
+  \end{idea}
+  }
+
+  \pause
+
+  \begin{question}
+    Similar as before: how can we ensure consistent views for everyone?
+  \end{question}
+\end{frame}
 
@@
 We also need privacy in addition to the verification requirements.
-In voting, we have the following requirements:
+As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
+and Bob by the data.
+So as long as Alice and Bob can conceal their identities at the demonstration 
+and escape without arrest, their support is recorded in the data while their 
+privacy is not violated.
+(Following this line of thinking, it can actually be beneficial for the privacy 
+of the demonstrators to mix with the participants from any 
+counter-demonstrations --- since the counts will still be correct.)
+
+In voting, we have the following alternative requirements:
 \begin{frame}
 \begin{requirements}[P]
-\item\label{VotePrivacy} Vote privacy: the vote does not reveal any individual 
-  vote.
+\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
+  individual vote.
 \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
@@
 \end{requirements}
+\pause
 \mode<presentation>{
-\pause
+  \begin{remark}
+    P\ref{CoercionResistance} \(\implies\)
+    P\ref{ReceiptFreeness} \(\implies\)
+    P\ref{VotePrivacy}
+  \end{remark}
+}
+\end{frame}
+\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
+\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
+\cref{VotePrivacy}.
+\Cref{CoercionResistance} is probably not possible to achieve for protests:
+e.g.\ Eve can simply physically bring Alice to a protest against her will.
+This leaves us with \cref{ReceiptFreeness,VotePrivacy}.
+
+\begin{frame}<presentation>
   \begin{remark}
@@
         participate in.
+      \item That leaves us with receipt freeness and vote privacy.
     \end{itemize}
   \end{remark}
-}
 \end{frame}
-\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
-\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
-\cref{VotePrivacy}.
-We can see that \cref{VotePrivacy,ReceiptFreeness} are desirable in Alice's 
-situation: there should not be any proof which binds Alice to the participation 
-of the demonstration (\cref{ReceiptFreeness}), because she does not want to 
-explicitly reveal her opinions to the government (\cref{VotePrivacy}) due to 
-the risk of reprimands.
-\Cref{ReceiptFreeness} implies that even if Alice is arrested, the data should 
-not provide any proof to the regime's agents that can reveal Alice's opinion.
 
 A demonstration is very different from voting in one sense: Alice must be 
-physically present and that very precense shows her support for the cause.
+physically present and that very presence shows her support for the cause.
 In voting, on the other hand, Alice has multiple options which are not revealed
-by her mere precense.
-As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
-and Bob by the data.
-So as long as Alice and Bob can conceal their identities at the demonstration 
-and escape without arrest, their support is recorded in the data while their 
-privacy is not violated.
-(Following this line of thinking, it can actually be beneficial for the privacy of 
-the demonstrators to mix with the participants from any counter-demonstrations 
---- as long as the correct counts for each demonstration can still be ensured, 
-which is the idea.)
-
-The main problem is how to ensure the connection between the physical location 
-and the data used for verification, i.e.\ fulfil all the requirements for 
-authenticity, verification and privacy given above.
-We must bind participants to the same physical location at a reasonably similar 
-time, i.e.\ within the area and duration of the demonstration.
-In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
-was in one place during an entire day and then repeated for several 
-weekends.
-In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
-were in several locations at the same time.
-
-%This means that for a system like this to work, we also need the requirements 
-%from \cref{DataAuthenticity}: proof that the data was created after the start 
-%of the protest, proof that it was created before the end, and proof of spatial 
-%relation to the location.
-
-\textcite{PROPS} developed a decentralized \ac{LPS} which provides 
-a participant with a verifiable proof of having been at a location at a certain 
-time, something we call \iac{LP}.
-It is decentralized because there is no central authority that vouches for the 
-location, instead peers act as witnesses.
-Then a third-party can verify the authenticity of the \ac{LP}, by verifying the 
-witnesses' signatures, and can thus be sure that the person has indeed been in 
-the location.
-Bosk, Gambs and Buchegger are currently exploring (work in progress) the 
-possibility of combining such \iac{LPS} with the verifiability and privacy 
-requirements discussed above.
-The overall idea is that each participant generates \iac{LP} during the 
-demonstration, where (some of) the other protesters act as witnesses, then the 
-\acp{LP} can be used to compute the participation count with all the 
-authenticity, verifiability and privacy requirements above.
-%TODO: reviewer: what about cellphones to count attendance
-% This is actually done in \cite{2016DemonstrationsInSeoul}, it requires some 
-% assumptions --- but they use wifi signals instead of the mobile network.
-% In either case, we pointed out that one wants the phone in flight mode due to
-% surveillance.
+by her mere presence.
+% XXX Check if unlinkable is the correct term
+Hence, if Alice submits a proof to the block chain, it must be unlinkable to 
+Alice yet if Alice submits another proof, those two proofs must be linkable.

### 2017-07-19 properties.tex
Adds short title for section auth, verif and priv
Works through privacy properties

@@
 \mode*
-\section{Authenticity, verification and privacy}
+\section[Verification and privacy]{Authenticity, verification and privacy}
 
@@
 
-In voting, we have the following alternative requirements:
+In voting, we have the following requirements:
 \begin{frame}
@@
 % XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof to the block chain, it must be unlinkable to 
-Alice yet if Alice submits another proof, those two proofs must be linkable.
+Hence, if Alice submits a proof to the block chain, the proof must be 
+unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
+be linkable (due to eligibility verification, \cref{EligibilityVerif}).
+E.g.\ Eve compromises Alice's device (and private keys).
+Anyone can verify any proof.
+With the inputs that Eve can extract from the published proof and the keys she 
+can find on Alice's device, she should not be able to reproduce the same 
+signatures on the proof.
+
+\begin{frame}<presentation>
+  \begin{remark}
+    \begin{itemize}
+      \item Voting: different alternatives when participating.
+      \item Protesting: participation implies the alternative.
+    \end{itemize}
+  \end{remark}
+
+  \pause
+
+  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness]
+    \begin{itemize}
+      \item If Eve compromises Alice's device, she should not be able to use 
+        it to verify that she participated.
+
+      \item But Alice should not be able to participate twice.
+
+      \item We need a signature scheme that cannot reproduce the same 
+        signature when run on the same inputs.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    Will such a signature scheme solve both problems?
+  \end{question}
+  \begin{question}
+    Is there such a signature scheme?
+    Can we construct it?
+  \end{question}
+\end{frame}

### 2017-07-20 properties.tex
Adds comments on partial order for authenticity

@@
 \end{frame}
-\Cref{CreatedBeforeEnd,CreatedAfterStart} together bind the data to the time of 
-the event whereas \cref{SpatiallyRelated} binds the data spatially to the 
-event.
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
+  order}\footnote{%
+  A relation \(<\) which is irreflexive, antisymmetric and transitive.
+}.
+If some objects in the set relate to known points in time, then the partial 
+order allows to relate the data to the time of the event.
+\Cref{SpatiallyRelated} binds the data spatially to the event.
 
-One primitive that provides the properties 
-\cref{CreatedAfterStart,CreatedBeforeEnd} is a block chain with a distributed 
-consensus protocol.
+One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
+chain.
 
@@
   \begin{question}
-    Are there other strucutres than block chains?
+    Are there other structures than block chains?
     E.g.~\cite{BlockchainFreeCryptocurrencies}.

### 2017-07-20 RelatedWork.tex
Adds WIP on related work

\mode*
\section{Related work}

\Textcite{2016DemonstrationsInSeoul} discusses various approaches to crowd 
counting.

\Textcite{HowToEstimateCrowdSize} \dots

\Textcite{WifiCrowdCounting} \dots

\Textcite{CVCrowdCounting} \dots

\Textcite{NNCrowdCounting} \dots

The most closely related work is \textcite{CrowdCount.org}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
There is no verification, i.e.\ the service must be trusted, nor anything 
preventing Bob from submitting twice.
The service also requires an Internet connection during the event to register 
as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against government, who shuts down the cellular network and Internet backbone 
as a means to censor the protest.

### 2017-07-21 news.tex
Adds quotes from news articles

\Textcite{2016DemonstrationsInSeoul} discusses various approaches to crowd 
counting and the problems they face:

\blockcquote{2016DemonstrationsInSeoul}{%
  The rally renewed what has become a weekly back-and-forth between police and 
  protest organizers, whose crowd estimates have differed widely. Police said 
  about 270,000 people turned out on Saturday, making it the largest anti-Park 
  rally yet. Organizers estimated the crowd at 1.5 million.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  The rallies stretch from midday to late night --- some people stay for 
  several hours, others just several minutes.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  The demonstrators not only gather in open space, but also small alleys and 
  between buildings.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  For the police, the aim is to measure the maximum crowd occupying a certain 
  space at any given time so that they could determine the size of police 
  personnel and resources to deploy%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  Police presume that, when sitting, six people would fill a space of 3.3 
  square meters
  [\dots]
  The same area would hold nine or 10 people when standing%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  Based on this, police consider the 32,100-square-meter (345,525-square-foot) 
  boulevard in front of the Gwanghwamun palace gate, which has been the center 
  of the protests, as accommodating close to 600,000 people when fully packed.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  Organizers seek to track the entire flow of people from the protest’s start 
  to its finish. They collect estimates given by counters deployed at different 
  locations to size up the crowds in each area and update the numbers 
  throughout the duration of the protest.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  One South Korean retail analytics company measured the number of protesters 
  by counting the number of smartphone signals.
  [\dots]
  Zoyi Corp. deployed about 60 people, each carrying a backpack with the 
  company’s Wi-Fi signal-detecting sensor, to the rally on Nov. 19.
  [\dots]
  They collected Wi-Fi and Bluetooth signals from smartphones for about seven 
  hours from 2 p.m. at 53 spots and found about 369,372 smartphones that had 
  their wireless signals on during the rally.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  The company presumed that about half of smartphone users usually leave their 
  Wi-Fi feature on and the other half switch it off, based on a separate survey 
  on smartphone usage.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  They collected Wi-Fi and Bluetooth signals from smartphones for about seven 
  hours from 2 p.m. at 53 spots and found about 369,372 smartphones that had 
  their wireless signals on during the rally. The company presumed that about 
  half of smartphone users usually leave their Wi-Fi feature on and the other 
  half switch it off, based on a separate survey on smartphone usage. It also 
  assumed that about 20 percent of the smartphone signals were repetition from 
  the same device. Based on this, Zoyi concluded that about 738,700 people 
  joined the rally.%
}

\blockcquote{TheCrowdNumbersGame}{%
  square footage divided by occupation density%
}

\blockcquote{TheCrowdNumbersGame}{%
  Clark McPhail, professor emeritus of sociology at the University of Illinois at 
  Urbana-Champaign, is one of America’s preeminent authorities on protest crowds.
  [\dots]
  studying D.C. demonstrations since 1967, using a fairly simple mathematical 
  formula --- square footage divided by occupation density --- to count 
  everything from antiwar gatherings to the annual March for Life to the 
  Million Man March to Promise Keepers%
}

\blockcquote{TheCrowdNumbersGame}{%
  The crowd-counting method he uses, he says, was devised by Berkeley 
  journalism professor Herbert Jacobs in the 1960s during the Free Speech 
  movement.%
}

\blockcquote{TheCrowdNumbersGame}{%
  Farouk El-Baz, director of the Center for Remote Sensing at Boston 
  University, says that the methodology is well known and well respected by 
  scientists.%
}

\blockcquote{TheCrowdNumbersGame}{%
  McPhail took the measurements leading to that conclusion at 1 p.m., two hours 
  after the rally began. While he was measuring, a few last busloads of people 
  were still coming in --- as much as 10 percent of the rally.
  [\dots]
  So to be on the safe side, he added 20 percent to his 1 p.m. total%
}

\blockcquote{TheCrowdNumbersGame}{%
  According to El-Baz, who has worked with the Park Service, aerial photographs 
  would have given a more accurate estimate.%
}

\blockcquote{TheCrowdNumbersGame}{%
  After viewing aerial photographs of the crowds on the streets leading into the 
  plaza, the police upped their estimate to between 50,000 and 100,000, and 
  then said it could have been as large as 150,000.%
}

\blockcquote{TheCrowdNumbersGame}{%
  In fact, he says, he thinks they do themselves a disservice by exaggerating. 
  “While hyperbole is to be expected from organizers — it has always been higher 
  than the estimates of the police — this can work to their disadvantage,”
  [\dots]
  in the antiwar demonstrations of the ’60s and early ’70s, the protests became 
  effective once Middle America started turning out. At that point, the size of 
  the rallies mattered less than who attended. Once the mainstream turned against 
  the war, it had to end.
  [\dots]
  “In the Vietnam era, it was when middle-aged folks and middle-class folks, 
  doctors and lawyers began coming out and participating that public opinion 
  began to turn,”%
}

\Textcite{HowToEstimateCrowdSize} \dots

\blockcquote[Interview with Stephen Doig, ASU]{HowToEstimateCrowdSize}{%
  I would say the most accurate way to estimate the number of people in a large 
  outdoor crowd is to get good aerial imagery, break it into regions of similar 
  density, measure the square footage of each region, apply a reasonable value 
  for the density in each region%
}
\blockcquote{HowToEstimateCrowdSize}{%
  Stephen Doig, a census expert at Arizona State University.%
}

\blockcquote{HowToEstimateCrowdSize}{%
  Doig uses his crowd-counting experience and techniques to help companies like 
  AirPhotosLive.com (which covered President Obama's 2009 Inauguration ceremony
  [\dots]
  the company uses a 360-degree, spherical panoramic camera that can capture 
  shots of the crowd from every direction all at once during the \enquote{peak} 
  time of an event, or when attendance is at its highest%
}

\blockcquote{HowToEstimateCrowdSize}{%
  Crowd size is also needed for media news reports and to historically record 
  the event%
}

\blockcquote{HowToEstimateCrowdSize}{%
  Boston University Center for Remote Sensing.%
}

\blockcquote{HowToEstimateCrowdSize}{%
  the more widely that a crowd is spread out, the more challenging it can be to 
  get an accurate estimate of those attending, as it can become difficult to 
  determine whether people near the event's perimeter are there for the event 
  or are in the area for other reasons,%
}

### 2017-07-21 RelatedWork.tex
Adds quotes related to Related Work

@@
 \Textcite{2016DemonstrationsInSeoul} discusses various approaches to crowd 
-counting.
+counting and the problems they face:
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The rallies stretch from midday to late night --- some people stay for 
+  several hours, others just several minutes.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The demonstrators not only gather in open space, but also small alleys and 
+  between buildings.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  For the police, the aim is to measure the maximum crowd occupying a certain 
+  space at any given time so that they could determine the size of police 
+  personnel and resources to deploy%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  Police presume that, when sitting, six people would fill a space of 3.3 
+  square meters
+  [\dots]
+  The same area would hold nine or 10 people when standing%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  Based on this, police consider the 32,100-square-meter (345,525-square-foot) 
+  boulevard in front of the Gwanghwamun palace gate, which has been the center 
+  of the protests, as accommodating close to 600,000 people when fully packed.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  Organizers seek to track the entire flow of people from the protest’s start 
+  to its finish. They collect estimates given by counters deployed at different 
+  locations to size up the crowds in each area and update the numbers 
+  throughout the duration of the protest.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  One South Korean retail analytics company measured the number of protesters 
+  by counting the number of smartphone signals.
+  [\dots]
+  Zoyi Corp. deployed about 60 people, each carrying a backpack with the 
+  company’s Wi-Fi signal-detecting sensor, to the rally on Nov. 19.
+  [\dots]
+  They collected Wi-Fi and Bluetooth signals from smartphones for about seven 
+  hours from 2 p.m. at 53 spots and found about 369,372 smartphones that had 
+  their wireless signals on during the rally.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The company presumed that about half of smartphone users usually leave their 
+  Wi-Fi feature on and the other half switch it off, based on a separate survey 
+  on smartphone usage.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  They collected Wi-Fi and Bluetooth signals from smartphones for about seven 
+  hours from 2 p.m. at 53 spots and found about 369,372 smartphones that had 
+  their wireless signals on during the rally. The company presumed that about 
+  half of smartphone users usually leave their Wi-Fi feature on and the other 
+  half switch it off, based on a separate survey on smartphone usage. It also 
+  assumed that about 20 percent of the smartphone signals were repetition from 
+  the same device. Based on this, Zoyi concluded that about 738,700 people 
+  joined the rally.%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  square footage divided by occupation density%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  Clark McPhail, professor emeritus of sociology at the University of Illinois at 
+  Urbana-Champaign, is one of America’s preeminent authorities on protest crowds.
+  [\dots]
+  studying D.C. demonstrations since 1967, using a fairly simple mathematical 
+  formula --- square footage divided by occupation density --- to count 
+  everything from antiwar gatherings to the annual March for Life to the 
+  Million Man March to Promise Keepers%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  The crowd-counting method he uses, he says, was devised by Berkeley 
+  journalism professor Herbert Jacobs in the 1960s during the Free Speech 
+  movement.%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  Farouk El-Baz, director of the Center for Remote Sensing at Boston 
+  University, says that the methodology is well known and well respected by 
+  scientists.%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  McPhail took the measurements leading to that conclusion at 1 p.m., two hours 
+  after the rally began. While he was measuring, a few last busloads of people 
+  were still coming in --- as much as 10 percent of the rally.
+  [\dots]
+  So to be on the safe side, he added 20 percent to his 1 p.m. total%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  According to El-Baz, who has worked with the Park Service, aerial photographs 
+  would have given a more accurate estimate.%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  After viewing aerial photographs of the crowds on the streets leading into the 
+  plaza, the police upped their estimate to between 50,000 and 100,000, and 
+  then said it could have been as large as 150,000.%
+}
+
+\blockcquote{TheCrowdNumbersGame}{%
+  In fact, he says, he thinks they do themselves a disservice by exaggerating. 
+  “While hyperbole is to be expected from organizers — it has always been higher 
+  than the estimates of the police — this can work to their disadvantage,”
+  [\dots]
+  in the antiwar demonstrations of the ’60s and early ’70s, the protests became 
+  effective once Middle America started turning out. At that point, the size of 
+  the rallies mattered less than who attended. Once the mainstream turned against 
+  the war, it had to end.
+  [\dots]
+  “In the Vietnam era, it was when middle-aged folks and middle-class folks, 
+  doctors and lawyers began coming out and participating that public opinion 
+  began to turn,”%
+}
 
 \Textcite{HowToEstimateCrowdSize} \dots
+
+\blockcquote[Interview with Stephen Doig, ASU]{HowToEstimateCrowdSize}{%
+  I would say the most accurate way to estimate the number of people in a large 
+  outdoor crowd is to get good aerial imagery, break it into regions of similar 
+  density, measure the square footage of each region, apply a reasonable value 
+  for the density in each region%
+}
+\blockcquote{HowToEstimateCrowdSize}{%
+  Stephen Doig, a census expert at Arizona State University.%
+}
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  Doig uses his crowd-counting experience and techniques to help companies like 
+  AirPhotosLive.com (which covered President Obama's 2009 Inauguration ceremony
+  [\dots]
+  the company uses a 360-degree, spherical panoramic camera that can capture 
+  shots of the crowd from every direction all at once during the \enquote{peak} 
+  time of an event, or when attendance is at its highest%
+}
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  Crowd size is also needed for media news reports and to historically record 
+  the event%
+}
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  Boston University Center for Remote Sensing.%
+}
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  the more widely that a crowd is spread out, the more challenging it can be to 
+  get an accurate estimate of those attending, as it can become difficult to 
+  determine whether people near the event's perimeter are there for the event 
+  or are in the area for other reasons,%
+}
 

### 2017-07-24 RelatedWork.tex
Writes up Related Work, notes and slides

--- 2017-07-20 RelatedWork.tex
@@
 
-\Textcite{2016DemonstrationsInSeoul} discusses various approaches to crowd 
-counting.
+\subsection<presentation>{Image-based methods}
 
-\Textcite{HowToEstimateCrowdSize} \dots
+The seemingly most commonly used method for counting crowds at protests is 
+Jacob's method~\cite[c.f.][]{%
+  2016DemonstrationsInSeoul,%
+  BBCHowToCountProtestNumbers,%
+  HowWillWeKnowTrumpInauguralCrowdSize,%
+  TheXManMarch,%
+  TheCrowdNumbersGame,%
+}.
+It is a manual method devised in the 1960s which relies on aerial photos of the 
+event.
+The verifier divides the protest venue into regions, then estimates the crowd 
+density in the different regions and finally sums them up to get an estimate of 
+the total.
+This method is prone to errors, since it is based on estimates.
+However, it allows for verification, since anyone can redo the counting using 
+the same photos.
 
-\Textcite{WifiCrowdCounting} \dots
+\begin{frame}<presentation>
+  \begin{solution}[Jacob's method]
+    \begin{itemize}
+      \item Take aerial photos of the event.
+      \item Divide area into regions.
+      \item Estimate density in the regions.
+      \item Sum up to an estimate of the total.
+    \end{itemize}
+  \end{solution}
 
-\Textcite{CVCrowdCounting} \dots
+  \pause
 
-\Textcite{NNCrowdCounting} \dots
+  \begin{remark}
+    \begin{itemize}
+      \item Prone to errors, due to estimations.
+      \item Verifiable, anyone with the photos can redo the estimate.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+
+There is a body of work in the computer vision community, e.g.\ the work of 
+\textcite{NNCrowdCounting}.
+This class of methods requires photos or video surveillance of the protest 
+location during the entire protest.
+They generally include machine learning, and thus also require a training 
+dataset to train the algorithms.
+In the work by \textcite{NNCrowdCounting}, they actually train and evaluate 
+their algorithm on different scenes, which might make this method easier to use 
+for protesting.
+We can provide verifiability with this method, since someone can always recount
+the participants using the recorded video material.
+However, it is still difficult capture the entire location on surveillance 
+video.
+Also, it is difficult (if not impossible) to not count people twice.
+
+\begin{frame}<presentation>
+  \begin{solution}[Computer vision]
+    \begin{itemize}
+      \item Record video of the event.
+      \item Train algorithms on part of the data.
+      \item Run algorithm to count the total.
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{remark}
+    \begin{itemize}
+      \item Requires video-recording of the entire event.
+      \item Difficult to record every part.
+      \item Difficult (impossible?) to not record someone twice.
+      \item Is verifiable though, if the video is public.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+
+\subsection<presentation>{Signal-based methods}
+
+During the protests in Seoul~\cite{2016DemonstrationsInSeoul} there was one 
+retail analytics company that tried to estimate the number of participants 
+using their technology.
+They scanned for MAC addresses emitted from the Wi-Fi of participants' 
+smartphones.
+However, this method required many assumptions:
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The company presumed that about half of smartphone users usually leave their 
+  Wi-Fi feature on and the other half switch it off, based on a separate survey 
+  on smartphone usage. It also assumed that about 20 percent of the smartphone 
+  signals were repetition from the same device.
+}
+This method cannot provide any verifiability, we must trust the company to do 
+the measurements correctly.
+As MAC address randomization get wider adoption this will be even more 
+difficult, although tracking will still be 
+possible~\cite{WhyMACRandomizationIsNotEnough}.
+
+\begin{frame}<presentation>
+  \begin{solution}[Wi-Fi tracking]
+    \begin{itemize}
+      \item Record unique Wi-Fi MAC addresses from people's smartphones.
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{remark}
+    \begin{itemize}
+      \item Imprecise, requires assumptions.
+      \item Half of smartphone users turn Wi-Fi off.
+      \item MAC address randomization.
+      \item Cannot verify.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+
+A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
+towers of the mobile network) to count unique phones at the location.
+However, there are several problems with this approach.
+First, it will be difficult to register only the participants' phones, many 
+bystanders will also be counted.
+Second, since the phone is a unique identifier, participants might be 
+uncomfortable to be registered in association with the event and might thus 
+turn the device off.
+Finally, there will be limited verifiability, as the data recorder must be 
+trusted to record all data.
+
+\begin{frame}<presentation>
+  \begin{solution}[IMSI catchers]
+    \begin{itemize}
+      \item Use IMSI catchers to register unique phones.
+      \item (Or use the network cell towers.)
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{remark}
+    \begin{itemize}
+      \item Will include bystanders into the count.
+      \item Privacy-invading due to phones being uniquely identifying.
+      \item Cannot verify.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+
+\Textcite{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the 
+Wi-Fi signal as a sonar to detect people.
+However this method is designed for indoor use and does not scale to more than 
+a crowd of 20 people.
+
+In general for all of the above methods, the more a crowd spreads out, the more
+difficult it will be to determine its size:
+the problem is determining whether people near the event's perimeter are 
+participants of simply bystanders~\cite{HowToEstimateCrowdSize}.
+These methods also have difficulty capturing the actual attendance of an event,
+i.e.\ the cumulative participation, not just the count at a snapshot around the 
+peak.
+
+\subsection<presentation>{More exact methods}
 
@@
 location to register that he is in Alice's event.
-There is no verification, i.e.\ the service must be trusted, nor anything 
-preventing Bob from submitting twice.
-The service also requires an Internet connection during the event to register 
-as a participant.
+This solves the problem that it counts everyone (who submitted), not just the 
+count at the snapshot of the photos.
+However, there is no verification, i.e.\ the service must be trusted, nor 
+anything preventing Bob from submitting twice (eligibility verification).
+Another downside is that the service also requires an Internet connection 
+during the event to register as a participant.
 This can make it difficult to use if e.g.\ Alice has organized a protest 
-against government, who shuts down the cellular network and Internet backbone 
-as a means to censor the protest.
+against the government, who shuts down the cellular network or Internet 
+backbone as a means to censor the protest.
+
+\begin{frame}<presentation>
+  \begin{solution}[CrowdCount\footfullcite{CrowdCount.org}]
+    \begin{itemize}
+      \item Register an upcoming event.
+      \item Let people \enquote{check-in} by submitting their location.
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{remark}
+    \begin{itemize}
+      \item No verification, the service must be trusted.
+      \item Nothing prevents Bob from checking in twice.
+      \item Requires an Internet connection during the event.
+    \end{itemize}
+  \end{remark}
+\end{frame}

### 2017-07-24 intro.tex
Works through text and slides
Privacy section not work through entirely yet.
Adds useful quotes to intro

@@
 
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The rallies stretch from midday to late night --- some people stay for 
+  several hours, others just several minutes.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  The demonstrators not only gather in open space, but also small alleys and 
+  between buildings.%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  For the police, the aim is to measure the maximum crowd occupying a certain 
+  space at any given time so that they could determine the size of police 
+  personnel and resources to deploy%
+}
+
+\blockcquote{2016DemonstrationsInSeoul}{%
+  Organizers seek to track the entire flow of people from the protest’s start 
+  to its finish. They collect estimates given by counters deployed at different 
+  locations to size up the crowds in each area and update the numbers 
+  throughout the duration of the protest.%
+}
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  the more widely that a crowd is spread out, the more challenging it can be to 
+  get an accurate estimate of those attending, as it can become difficult to 
+  determine whether people near the event's perimeter are there for the event 
+  or are in the area for other reasons,%
+}
+
 We can make one important observation about this problem that has seemingly 
@@
 participation count.
+
+%In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
+%was in one place during an entire day and then repeated for several weekends.
+%In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
+%were in several locations at the same time.
+
+\blockcquote{HowToEstimateCrowdSize}{%
+  Crowd size is also needed for media news reports and to historically record 
+  the event%
+}

### 2017-07-24 RelatedWork.tex
Changes refkey for CrowdCount
Adds CrowdSize app to Related Work

@@
 \end{frame}
+
+There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
+based on a selected space.
+Then the user selects one of three pre-set density estimates: light, medium or 
+dense.
+This is similar to the method usually used by police, e.g.\ for the protests in
+Seoul
+\blockcquote{2016DemonstrationsInSeoul}{%
+  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
+  fill a space of 
+  3.3 square meters
+  \textelp{}
+  The same area would hold nine or 10 people when standing%
+}.
 
@@
 
-The most closely related work is \textcite{CrowdCount.org}.
+The most closely related work is \textcite{CrowdCount}.
 This is a web service which lets Alice create an event and Bob can submit his 
@@
 \begin{frame}<presentation>
-  \begin{solution}[CrowdCount\footfullcite{CrowdCount.org}]
+  \begin{solution}[CrowdCount\footfullcite{CrowdCount}]
     \begin{itemize}

### 2017-07-25 RelatedWork.tex
Adds slide for CrowdSize
Clarifies discussion about limits of related works

@@
 the same photos.
+This provides universal verifiability (\cref{UniversalVerif})).
+It is difficult to achieve individual verifiability (\cref{IndividualVerif}) 
+since it is hard to verify that oneself is indeed in any of the photos.
+We can argue eligibility verifiability (\cref{EligibilityVerif}) if all the 
+photos are taken at the same point in time with no overlap, since then no one 
+can be counted twice.
+Unfortunately, we can only get the peak participation with this method.
+
+When it comes to authenticity, we have to rely on the photos.
+We can try to determine from the photos themselves when and where the they were 
+taken.
+However, the best we can do is to employ forensic methods to try to detect any 
+modifications.
 
@@
       \item Prone to errors, due to estimations.
-      \item Verifiable, anyone with the photos can redo the estimate.
+      \item Universally verifiable (\cref{UniversalVerif}), anyone with the 
+        photos can redo the estimate.
+      \item Eligibility verifiability (\cref{EligibilityVerif}) if photos at 
+        one snapshot in time and no overlap.
     \end{itemize}
@@
 }.
+This method is not verifiable unless the user takes a picture of the crowd, 
+then it inherits the verifiability properties of the previous method.
+The same for authenticity.
+
+\begin{frame}<presentation>
+  \begin{solution}[CrowdSize app\footfullcite{CrowdSize}]
+    \begin{itemize}
+      \item User selects area on map.
+      \item User selects an estimate for crowd density: light, medium or dense.
+      \item App gives crowd size estimate based on size of the area and 
+        density.
+    \end{itemize}
+  \end{solution}
+
+  \pause
+
+  \begin{remark}
+    \begin{itemize}
+      \item This is the same method as used by police.
+      \item Not verifiable unless the user takes a picture of the crowd.
+      \item The it will be reduced to the previous method.
+    \end{itemize}
+  \end{remark}
+\end{frame}
 
@@
 for protesting.
-We can provide verifiability with this method, since someone can always recount
-the participants using the recorded video material.
-However, it is still difficult capture the entire location on surveillance 
+We can provide universal verifiability (\cref{UniversalVerif}) with this 
+method, since someone can always recount the participants using the recorded 
+video material.
+We might be able to provide some degree of individual verifiability 
+(\cref{IndividualVerif}), but this might still be difficult.
+Also, it is difficult (if not impossible) to not count people twice, thus we 
+cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
+Furthermore, it is still difficult capture the entire location on surveillance 
 video.
-Also, it is difficult (if not impossible) to not count people twice.
+The authenticity properties are reduced to those of the video, which should be 
+similar as in our discussion about the authenticity of photos.
 
@@
       \item Difficult (impossible?) to not record someone twice.
-      \item Is verifiable though, if the video is public.
+      \item Is verifiable, though limited, if the video is public.
+      \item Authenticity can be questioned as with the photos.
     \end{itemize}
@@
 }
-This method cannot provide any verifiability, we must trust the company to do 
-the measurements correctly.
+This method cannot provide any verifiability nor authenticity, we must trust 
+the company to do the measurements correctly and to be honest about when and 
+where they did them.
 As MAC address randomization get wider adoption this will be even more 
-difficult, although tracking will still be 
+difficult, although some tracking of smartphones will still be 
 possible~\cite{WhyMACRandomizationIsNotEnough}.
@@
       \item MAC address randomization.
-      \item Cannot verify.
+      \item Cannot verify, nor authenticate.
     \end{itemize}
@@
 turn the device off.
-Finally, there will be limited verifiability, as the data recorder must be 
-trusted to record all data.
+Finally, there will be limited verifiability and authenticity, as the data 
+recorder must be trusted to record all data and do it in the relation to the 
+event.
 
@@
       \item Privacy-invading due to phones being uniquely identifying.
-      \item Cannot verify.
+      \item Cannot verify, nor authenticate.
     \end{itemize}
@@
 a crowd of 20 people.
+In either case, this type of data cannot provide verifiability nor 
+authenticity.
 
@@
 count at the snapshot of the photos.
-However, there is no verification, i.e.\ the service must be trusted, nor 
-anything preventing Bob from submitting twice (eligibility verification).
+However, there is no verification nor authenticity, i.e.\ the service must be 
+trusted to behave honestly, but even then, nothing prevents Bob from submitting 
+twice (violating eligibility verification, \cref{EligibilityVerif}).
 Another downside is that the service also requires an Internet connection 
@@
     \begin{itemize}
-      \item No verification, the service must be trusted.
+      \item No verification, nor authenticity, the service must be trusted.
       \item Nothing prevents Bob from checking in twice.

### 2017-07-25 conclusions.tex
Clarifies discussion about limits of related works

\mode*
\section{Conclusions}

In general, none of the related works fulfils the authenticity requirements 
(\cref{%
  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated%
}).
Some of the schemes provide some limited verifiability, i.e.\ mostly universal 
verifiability (\cref{UniversalVerif}), but not individual verifiability 
(\cref{IndividualVerif}) nor eligibility verifiability 
(\cref{EligibilityVerif}).

\begin{frame}<presentation>
  \begin{remark}
    \begin{itemize}
      \item All current methods lack authenticity and verifiability.
      \item Some provide universal verifiability (V\ref{UniversalVerif}).
    \end{itemize}
  \end{remark}
\end{frame}

### 2017-07-26 properties.tex
Fixes typo
Adds notes from paper

@@
   \end{question}
+  \begin{question}
+    What about distributed voting/polling protocols?
+    A tree should give a strict partial order?
+  \end{question}
 \end{frame}
@@
     the same location(s)?
-    (Related to V\ref{EligibilityVerif}.)
     What are the assumptions?
@@
     How hard is it to reuse old proofs?
+    Forge all signatures due to changed values?
   \end{question}
@@
     And then 1000s of such \acp{LP}?
+    Ad-hoc networks, broadcast \acp{LP}?
   \end{question}
@@
     What are the assumptions?
+    Signed over a short period of time?\footnote{%
+      In a sense, if they collude they have shown support for the cause.
+      As long as they are not Sybil it should be fine?
+    }
   \end{question}
@@
     How to solve the Sybil problem?
+    Can we piggyback on existing \acp{PKI}?
+    E.g.~\cite{Cinderella}.
   \end{question}
@@
   \end{question}
+  \begin{question}
+    What Alice submits her proof, stores the hash of the block, removes proof 
+    and signature key?
+  \end{question}
 \end{frame}
+
+From a computational-complexity perspective, operations that must be done on 
+the phone must be cheap, other operations may be expensive.

### 2017-07-28 properties.tex
Adds solution/implementation section
Starts generalizing to T-POSETs, s/block chain/blockchain/

@@
     \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
-      A\ref{CreatedBeforeEnd}: a block chain.
+      A\ref{CreatedBeforeEnd}: a blockchain.
+
+    \item There are also other structures, e.g.\ a directed 
+      graph~\cite{BlockchainFreeCryptocurrencies}.
 
@@
 
-    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
+    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
   \end{itemize}
@@
 
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
-chain.
+One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
+blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}.
+For generality, we will use the terminology of 
+\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
+structure \iac{tposet}.
 
 \begin{frame}
-  \begin{question}
-    Are there other structures than block chains?
-    E.g.~\cite{BlockchainFreeCryptocurrencies}.
-  \end{question}
   \begin{question}
@@
   \end{question}
+  \begin{question}
+    Can linear blockchains also fit in the framework of 
+    \textcite{BlockchainFreeCryptocurrencies}?
+    Can we generalize it?
+  \end{question}
 \end{frame}
 
-\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
-block chain \emph{in (time-wise) relation to the event}.
-Then we know that it cannot have been created after the event.
+\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
+proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
+Then we know that they cannot have been created after the event.
 
@@
     \begin{itemize}
-      \item Make the \ac{LP} part of the block chain.
+      \item Make the \ac{LP} part of the \ac{tposet}.
       \item The proof must've been created before it was included (duh!).
@@
 
-For \cref{CreatedAfterStart} we must include an unpredictable value in the 
-proof, e.g.\ the head of the block chain.
-This means that we cannot create a proof and keep it for a future protest.
-This also prevents us from reusing proofs from previous protests.
+For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
+in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
+This means that they cannot create a proof and keep it for a future protest.
+
+They can use an older value (pick one from the history of the \ac{tposet}) when 
+they create their proofs.
+This will only expand the interval of possible creation into the past.
+This will not help their cause, as anyone will recognize that the proof could 
+be created at any time in that interval.
 
@@
       \item Include an unpredictable value in the \ac{LP}.
-      \item This could be e.g.\ the hash of the head of the block chain.
+      \item This could be e.g.\ the hash of the \enquote{head} of the 
+        \ac{tposet}.
       \item This prevents creating proofs for future protests.
@@
 each vote would be replaced by a proof of participation.
-To have any verifiability, we need the storage (i.e.\ block chain) to be 
+To have any verifiability, we need the storage (i.e.\ blockchain) to be 
 immutable.
@@
     \begin{itemize}
-      \item For valid verification we must have an immutable block chain.
+      \item For valid verification we must have an immutable blockchain.
       \item We need something like a consensus protocol to prevent malicious 
@@
 
-If the proofs are included in a public block chain (as suggested in 
+If the proofs are included in a public blockchain (as suggested in 
 \cref{DataAuthenticity}), then an individual can check that their proof has 
@@
     \begin{itemize}
-      \item Proofs are stored publicly (block chain).
+      \item Proofs are stored publicly (blockchain).
       \item Each participant can check that their proof is indeed included.
@@
 
-If the block chain is public, then anyone can download all the proofs, verify 
+If the blockchain is public, then anyone can download all the proofs, verify 
 them (eligibility) and count them.
@@
 % XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof to the block chain, the proof must be 
+Hence, if Alice submits a proof to the blockchain, the proof must be 
 unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
@@
 \end{frame}
-
-From a computational-complexity perspective, operations that must be done on 
-the phone must be cheap, other operations may be expensive.

### 2017-07-28 properties.tex
Changes relation from < to \prec

@@
   order}\footnote{%
-  A relation \(<\) which is irreflexive, antisymmetric and transitive.
+  A relation \(\prec\) which is irreflexive, antisymmetric and transitive.
 }.

### 2017-07-31 abstract.tex
Adjusts keywords
Adapts abstract for FOSAD

@@
-Alice organizes a protest for some change in government.
+Say Alice organizes a protest against the current regime leader Eve.
 The protest is held in some location(s).
 Alice wants to estimate the number of participants to prove certain support for
-her change.
+her cause.
 Current methods have wide margins for error.
@@
 high as possible whereas the government's incentive is to estimate the number 
-of participants as low as possible.
+of participants as low as possible to support Eve.
 
@@
 Since the parties' have incentives to cheat, we require transparency: we desire 
-a decentralized scheme that provides the verifiability and privacy properties 
-of electronic voting.
-The scheme must be scalable to handle large protests.
+a decentralized scheme that provides authenticity, verifiability and privacy.
+More specifically:
+The scheme must be decentralized to not depend on any authority.
+We must ensure that the data is time-wise related to the event (authenticity), 
+which can be provided by blockchain-like structures.
+The data must also be related to the location, something a location proof can 
+solve.
+As all things policital, privacy is critical.
+Similar to e-voting schemes, we need what corresponds to vote privacy and 
+receipt freeness --- Alice does not want Eve's agents to verify that she is a 
+critic of Eve.
+Furthermore, we need verifiability: that every participant can verify that 
+their participation has been included --- individual verifiability, to prevent 
+Eve from dropping data --- and that anyone can verify the correctness of the 
+result --- universal and eligibility verifiability, to prevent any malicious 
+actor (e.g.\ Sybil) from affecting the result.
+Finally, the scheme must be scalable to handle large protests (millions of 
+participants).
+
+In this talk we will discuss this work in progress and elicit input from the 
+participants.
 
 \keywords{%
-  crowd-counting; protesting; electronic voting; location proofs; privacy
+  crowd counting;
+  protesting;
+  electronic voting;
+  location proof;
+  privacy
 }

### 2017-08-01 abstract.tex
Removes "In this talk" line from abstract
Adapts abstract and title to Sébastien's comments

--- 2017-07-13 abstract.tex
@@
-Alice organizes a protest for some change in government.
-The protest is held in some location(s).
-Alice wants to estimate the number of participants to prove certain support for
-her change.
+Say Alice organizes a protest against the current regime leader Eve.
+The protest is held in some location(s) and Alice wants to estimate the number 
+of participants to prove a certain support to her cause.
 Current methods have wide margins for error.
-In addition, Alice's incentive is to estimate the number of participants as 
-high as possible whereas the government's incentive is to estimate the number 
-of participants as low as possible.
+In addition, Alice may be tempted to cheat by estimating the number of 
+participants as high as possible whereas the government's incentive is to make 
+this estimation as low as possible to support Eve.
 
-We are interested in combining location proofs with electronic voting.
-Since the parties' have incentives to cheat, we require transparency: we desire 
-a decentralized scheme that provides the verifiability and privacy properties 
-of electronic voting.
-The scheme must be scalable to handle large protests.
+In this work, we are interested in combining location proofs with electronic 
+voting to solve this issue.
+Since the parties have incentives to cheat, we require transparency: in 
+particular we are aiming at a decentralized scheme that provides authenticity, 
+verifiability and privacy.
+More specifically, the scheme should be distributed and not depend on any 
+authority.
+We must also ensure that the data is time-wise related to the event (i.e.\ 
+authenticity), which can be provided by blockchain-like structures.
+The data must also be related to the location, something a location proof can 
+achieve.
+Finally, as all things policital, privacy is critical.
+Similar to e-voting schemes, we need to guarantee properties close to vote 
+privacy and receipt freeness --- Alice does not want Eve's agents to be able to 
+infer that she is critical of Eve.
+Furthermore, we need verifiability, which means that every participant can 
+verify that their participation has been included --- i.e.\ individual 
+verifiability, to prevent Eve from dropping data --- and that anyone
+can verify the correctness of the result --- i.e.\ universal and eligibility
+verifiability, to prevent any malicious actor (e.g. Sybil) from affecting the 
+result.
+Finally, the scheme must be scalable to handle large protests (millions of 
+participants).
+
+In this talk we will discuss this work in progress and elicit input from the 
+participants.
 
 \keywords{%
-  crowd-counting; protesting; electronic voting; location proofs; privacy
+  crowd counting;
+  protesting;
+  electronic voting;
+  location proof;
+  privacy
 }

### 2017-08-01 abstract.tex
Adds Sonja's questions as comments in the abstract
I.e. what's the problem, why is it a problem, what's the approach. Since
it's work-in-progress we can't answer all the questions.
Edits abstract, moves verifiability before privacy

@@
+% What's the problem?
 Say Alice organizes a protest against the current regime leader Eve.
@@
 of participants to prove a certain support to her cause.
+% Why is it a problem?
 Current methods have wide margins for error.
@@
 
+% What's the approach?
 In this work, we are interested in combining location proofs with electronic 
@@
 achieve.
+We need verifiability, which means that every participant can verify that their 
+participation has been included --- i.e.\ individual verifiability, to prevent 
+Eve from dropping data --- and that anyone can verify the correctness of the 
+result --- i.e.\ universal and eligibility verifiability, to prevent any 
+malicious actor (e.g. Sybil) from affecting the result.
 Finally, as all things policital, privacy is critical.
@@
 infer that she is critical of Eve.
-Furthermore, we need verifiability, which means that every participant can 
-verify that their participation has been included --- i.e.\ individual 
-verifiability, to prevent Eve from dropping data --- and that anyone
-can verify the correctness of the result --- i.e.\ universal and eligibility
-verifiability, to prevent any malicious actor (e.g. Sybil) from affecting the 
-result.
 Finally, the scheme must be scalable to handle large protests (millions of 

### 2017-08-01 properties.tex
Adds note about vote privacy, need of mix-nets
Removes question which is answered and a bit duplicate
Adds questions regarding blockchains

@@
   \begin{question}
-    How will this prevent us from reusing proofs from previous protests in 
-    the same location(s)?
-    What are the assumptions?
-  \end{question}
-  \begin{question}
     How hard is it to reuse old proofs?
@@
   \end{question}
+
+  \begin{question}
+    Under the protest conditions, we might have natural network splits.
+    Is this a useful scenario?
+  \end{question}
+
+  \begin{question}
+    How can we do blockchain branch and merge?
+    That is needed to recover from the above attack.
+  \end{question}
 \end{frame}
@@
     we reuse any such techniques?
+    Specifically ecash~\cite{ecash} and the like.
   \end{question}
@@
 \begin{frame}<presentation>
+  \begin{question}
+    How do we submit the proofs to storage?
+    Voting normally uses mix-nets.
+  \end{question}
+
+  \begin{remark}
+    Without anonymous submission we don't get vote pricacy, thus no receipt 
+    freeness either.
+  \end{remark}
+\end{frame}
+
+\begin{frame}<presentation>
   \begin{remark}

### 2017-08-02 properties.tex
Adds comments from meeting

--- 2017-07-28 properties.tex
@@
     \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
-      A\ref{CreatedBeforeEnd}: a blockchain.
-
-    \item There are also other structures, e.g.\ a directed 
-      graph~\cite{BlockchainFreeCryptocurrencies}.
+      A\ref{CreatedBeforeEnd}: a block chain.
 
@@
 
-    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
+    \item A\ref{SpatiallyRelated} is provided by \iacf{LP}.
   \end{itemize}
@@
 \end{frame}
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
   order}\footnote{%
-  A relation \(<\) which is irreflexive, antisymmetric and transitive.
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
 }.
@@
 order allows to relate the data to the time of the event.
-\Cref{SpatiallyRelated} binds the data spatially to the event.
+This allows us to \emph{authenticate the data temporally}.
+\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
+us to \emph{authenticate the data spatially}.
 
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
-blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}.
-For generality, we will use the terminology of 
-\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
-structure \iac{tposet}.
+One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
+chain.
 
 \begin{frame}
+  \begin{question}
+    Are there other structures than block chains?
+    E.g.~\cite{BlockchainFreeCryptocurrencies}.
+  \end{question}
   \begin{question}
@@
   \end{question}
-  \begin{question}
-    Can linear blockchains also fit in the framework of 
-    \textcite{BlockchainFreeCryptocurrencies}?
-    Can we generalize it?
-  \end{question}
 \end{frame}
 
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
-proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
-Then we know that they cannot have been created after the event.
+\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
+block chain \emph{in (time-wise) relation to the event}.
+Then we know that it cannot have been created after the event.
 
@@
     \begin{itemize}
-      \item Make the \ac{LP} part of the \ac{tposet}.
+      \item Make the \ac{LP} part of the block chain.
       \item The proof must've been created before it was included (duh!).
@@
 
-For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
-in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
-This means that they cannot create a proof and keep it for a future protest.
-
-They can use an older value (pick one from the history of the \ac{tposet}) when 
-they create their proofs.
-This will only expand the interval of possible creation into the past.
-This will not help their cause, as anyone will recognize that the proof could 
-be created at any time in that interval.
+For \cref{CreatedAfterStart} we must include an unpredictable value in the 
+proof, e.g.\ the head of the block chain.
+This means that we cannot create a proof and keep it for a future protest.
+This also prevents us from reusing proofs from previous protests.
 
@@
       \item Include an unpredictable value in the \ac{LP}.
-      \item This could be e.g.\ the hash of the \enquote{head} of the 
-        \ac{tposet}.
+      \item This could be e.g.\ the hash of the head of the block chain.
       \item This prevents creating proofs for future protests.
@@
     How can we do \acp{LP} with 1000s of witnesses each?
-    And then 1000s of such \acp{LP}?
+    Can we do some preprocessing?
     Ad-hoc networks, broadcast \acp{LP}?
@@
     }
+  \end{question}
+  \begin{question}
+    Trusted party for the group signatures?
+  \end{question}
+  \begin{question}
+    Must tie credentials to something unique: phone, phone subscription?
+    Cannot register twice, government control?
   \end{question}
@@
 each vote would be replaced by a proof of participation.
-To have any verifiability, we need the storage (i.e.\ blockchain) to be 
+To have any verifiability, we need the storage (i.e.\ block chain) to be 
 immutable.
@@
     \begin{itemize}
-      \item For valid verification we must have an immutable blockchain.
+      \item For valid verification we must have an immutable block chain.
       \item We need something like a consensus protocol to prevent malicious 
@@
 
-If the proofs are included in a public blockchain (as suggested in 
+If the proofs are included in a public block chain (as suggested in 
 \cref{DataAuthenticity}), then an individual can check that their proof has 
@@
     \begin{itemize}
-      \item Proofs are stored publicly (blockchain).
+      \item Proofs are stored publicly (block chain).
       \item Each participant can check that their proof is indeed included.
@@
 
-If the blockchain is public, then anyone can download all the proofs, verify 
+If the block chain is public, then anyone can download all the proofs, verify 
 them (eligibility) and count them.
@@
 % XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof to the blockchain, the proof must be 
+Hence, if Alice submits a proof to the block chain, the proof must be 
 unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
@@
 signatures on the proof.
+So Alice needs a long-term and a short-term credential, but she should not be 
+able to create two short-term credentials to participate twice.
+
+\begin{frame}
+  \begin{question}
+    How do we submit the proofs to storage?
+    Voting normally uses mix-nets.
+    Submit over Tor~\cite{Tor}?
+  \end{question}
+
+  \mode<presentation>{
+  \begin{remark}
+    Without anonymous submission we don't get vote privacy, thus no receipt 
+    freeness either.
+  \end{remark}
+  }
+\end{frame}
 

### 2017-08-02 primitives.tex
Fixes so that beamerarticle modes are correct
Changes solution section to primitives
Changes section title for primitives
Moves implementation related stuff

@@
-\section{Useful Primitives}
-\label{UsefulPrimitives}
+\mode*
+
+\section{Primitives}
+\label{Primitives}
 
 \dots
+
+From a computational-complexity perspective, operations that must be done on 
+the phone must be cheap, other operations may be expensive.
+
+\subsection{Authenticity}
+
+One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
+blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}.
+For generality, we will use the terminology of 
+\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
+structure \iac{tposet}.
+
+\begin{frame}
+  \begin{question}
+    What about distributed voting/polling protocols?
+    A tree should give a strict partial order?
+  \end{question}
+  \begin{question}
+    Can linear blockchains also fit in the framework of 
+    \textcite{BlockchainFreeCryptocurrencies}?
+    Can we generalize it?
+  \end{question}
+\end{frame}
+
+\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
+proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
+Then we know that they cannot have been created after the event.
+
+\begin{frame}<presentation>
+  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
+    \begin{itemize}
+      \item Make the \ac{LP} part of the \ac{tposet}.
+      \item The proof must've been created before it was included (duh!).
+      \item (Also related to V\ref{EligibilityVerif}.)
+    \end{itemize}
+  \end{solution}
+\end{frame}
+
+For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
+in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
+This means that they cannot create a proof and keep it for a future protest.
+
+They can use an older value (pick one from the history of the \ac{tposet}) when 
+they create their proofs.
+This will only expand the interval of possible creation into the past.
+This will not help their cause, as anyone will recognize that the proof could 
+be created at any time in that interval.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
+    \begin{itemize}
+      \item Include an unpredictable value in the \ac{LP}.
+      \item This could be e.g.\ the hash of the \enquote{head} of the 
+        \ac{tposet}.
+      \item This prevents creating proofs for future protests.
+    \end{itemize}
+  \end{idea}
+  }
+
+  \pause
+
+  \begin{question}
+    How hard is it to reuse old proofs?
+    Forge all signatures due to changed values?
+  \end{question}
+\end{frame}
+
+\subsection{Location proofs}
+
+If we include \iac{LP}, this will tie the proof to the physical location and, 
+thus, solve \cref{SpatiallyRelated}.
+The \ac{LP} is \enquote{witnessed} (signed) by other participants.
+The \ac{LP} contains coarse coordinates of the location, which must be within 
+the protest area to be valid.
+This allows Bob the protester to move within the protest area to collect 
+witnesses (signatures).
+It also provides privacy since the location cannot be used to deanonymize Bob's 
+proof --- e.g.\ to correlate the location in his proof with captured 
+surveillance footage.
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{idea}[A\ref{SpatiallyRelated} Correct location]
+    \begin{itemize}
+      \item The \ac{LP} is \enquote{witnessed} (signed) by other participants.
+      \item We have a coarse location, just within protest area.
+      \item This allows protesters to move around to collect signatures.
+      \item This provides privacy for the location, e.g.\ cannot map to 
+        surveillance cameras.
+    \end{itemize}
+  \end{idea}
+  }
+
+  \pause
+
+  \begin{question}
+    How can we do \acp{LP} with 1000s of witnesses each?
+    Can we do some preprocessing?
+    Ad-hoc networks, broadcast \acp{LP}?
+  \end{question}
+  \begin{question}
+    Why should anyone trust these witnesses?
+    What are the assumptions?
+    Signed over a short period of time?\footnote{%
+      In a sense, if they collude they have shown support for the cause.
+      As long as they are not Sybil it should be fine?
+    }
+  \end{question}
+  \begin{question}
+    Trusted party for the group signatures?
+  \end{question}
+  \begin{question}
+    Must tie credentials to something unique: phone, phone subscription?
+    Cannot register twice, government control?
+  \end{question}
+\end{frame}
+
+\subsection{Storage}
+
+\begin{frame}
+  \begin{question}
+    Malicious nodes want to provide Alice with a view that her proof is 
+    included.
+    Everyone else is provided a view without Alice.
+    How can we ensure a consistent view for everyone?
+    (Probably similar to the solution in Joakim's thesis.)
+  \end{question}
+
+  \begin{question}
+    Under the protest conditions, we might have natural network splits.
+    Is this a useful scenario?
+  \end{question}
+
+  \begin{question}
+    How can we do blockchain branch and merge?
+    That is needed to recover from the above attack.
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    What can we achieve with a consensus protocol?
+    Majority must be honest?
+  \end{question}
+  \begin{question}
+    What is a suitable proof-of-work?
+    See e.g.~\cite{FairProofOfWork}.
+  \end{question}
+\end{frame}
+
+\subsection{Verifiability}
+
+\begin{frame}
+  \begin{question}
+    How to solve the Sybil problem?
+    Can we piggyback on existing \acp{PKI}?
+    E.g.~\cite{Cinderella}.
+  \end{question}
+  \begin{question}
+    This is similar to the double-spending problem for cryptocurrencies, can 
+    we reuse any such techniques?
+    Specifically ecash~\cite{ecash} and the like.
+  \end{question}
+\end{frame}

### 2017-08-02 properties.tex
Moves implementation related stuff

@@
 us to \emph{authenticate the data spatially}.
-
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a block 
-chain.
-
-\begin{frame}
-  \begin{question}
-    Are there other structures than block chains?
-    E.g.~\cite{BlockchainFreeCryptocurrencies}.
-  \end{question}
-  \begin{question}
-    What about distributed voting/polling protocols?
-    A tree should give a strict partial order?
-  \end{question}
-\end{frame}
-
-\Cref{CreatedBeforeEnd} is straight-forward, we simply add the proof to the 
-block chain \emph{in (time-wise) relation to the event}.
-Then we know that it cannot have been created after the event.
-
-\begin{frame}<presentation>
-  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
-    \begin{itemize}
-      \item Make the \ac{LP} part of the block chain.
-      \item The proof must've been created before it was included (duh!).
-      \item (Also related to V\ref{EligibilityVerif}.)
-    \end{itemize}
-  \end{solution}
-\end{frame}
-
-For \cref{CreatedAfterStart} we must include an unpredictable value in the 
-proof, e.g.\ the head of the block chain.
-This means that we cannot create a proof and keep it for a future protest.
-This also prevents us from reusing proofs from previous protests.
-
-\begin{frame}
-  \mode<presentation>{
-  \begin{idea}[A\ref{CreatedAfterStart} Created after start]
-    \begin{itemize}
-      \item Include an unpredictable value in the \ac{LP}.
-      \item This could be e.g.\ the hash of the head of the block chain.
-      \item This prevents creating proofs for future protests.
-    \end{itemize}
-  \end{idea}
-  }
-
-  \pause
-
-  \begin{question}
-    How will this prevent us from reusing proofs from previous protests in 
-    the same location(s)?
-    What are the assumptions?
-  \end{question}
-  \begin{question}
-    How hard is it to reuse old proofs?
-    Forge all signatures due to changed values?
-  \end{question}
-\end{frame}
-
-If we include \iac{LP}, this will tie the proof to the physical location and, 
-thus, solve \cref{SpatiallyRelated}.
-The \ac{LP} is \enquote{witnessed} (signed) by other participants.
-The \ac{LP} contains coarse coordinates of the location, which must be within 
-the protest area to be valid.
-This allows Bob the protester to move within the protest area to collect 
-witnesses (signatures).
-It also provides privacy since the location cannot be used to deanonymize Bob's 
-proof --- e.g.\ to correlate the location in his proof with captured 
-surveillance footage.
-
-\begin{frame}
-  \mode<presentation>{
-  \begin{idea}[A\ref{SpatiallyRelated} Correct location]
-    \begin{itemize}
-      \item The \ac{LP} is \enquote{witnessed} (signed) by other participants.
-      \item We have a coarse location, just within protest area.
-      \item This allows protesters to move around to collect signatures.
-      \item This provides privacy for the location, e.g.\ cannot map to 
-        surveillance cameras.
-    \end{itemize}
-  \end{idea}
-  }
-
-  \pause
-
-  \begin{question}
-    How can we do \acp{LP} with 1000s of witnesses each?
-    Can we do some preprocessing?
-    Ad-hoc networks, broadcast \acp{LP}?
-  \end{question}
-  \begin{question}
-    Why should anyone trust these witnesses?
-    What are the assumptions?
-    Signed over a short period of time?\footnote{%
-      In a sense, if they collude they have shown support for the cause.
-      As long as they are not Sybil it should be fine?
-    }
-  \end{question}
-  \begin{question}
-    Trusted party for the group signatures?
-  \end{question}
-  \begin{question}
-    Must tie credentials to something unique: phone, phone subscription?
-    Cannot register twice, government control?
-  \end{question}
-\end{frame}
 
@@
 each vote would be replaced by a proof of participation.
-To have any verifiability, we need the storage (i.e.\ block chain) to be 
-immutable.
-So we need a consensus protocol which prevents malicious changes.
+To have any verifiability, we need the storage (e.g.\ blockchain) to be 
+immutable --- i.e.\ it prevents malicious changes.
 
-\begin{frame}
-  \mode<presentation>{
+\begin{frame}<presentation>
   \begin{remark}
     \begin{itemize}
-      \item For valid verification we must have an immutable block chain.
-      \item We need something like a consensus protocol to prevent malicious 
-        changes.
+      \item For valid verification we must have immutable storage.
+      \item We need to prevent or detect malicious changes.
     \end{itemize}
   \end{remark}
-  }
-
-  \begin{question}
-    What can we achieve with a consensus protocol?
-    Majority must be honest?
-  \end{question}
-  \begin{question}
-    What is a suitable proof-of-work?
-    See e.g.~\cite{FairProofOfWork}.
-  \end{question}
 \end{frame}
 
-If the proofs are included in a public block chain (as suggested in 
-\cref{DataAuthenticity}), then an individual can check that their proof has 
-been included in the chain.
+If the proofs are stored publicly, then an individual can check that their 
+proof has been included there.
 Thus \cref{IndividualVerif} is fulfilled.
 
-\begin{frame}
-  \mode<presentation>{
+\begin{frame}<presentation>
   \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
     \begin{itemize}
-      \item Proofs are stored publicly (block chain).
+      \item Proofs are stored publicly (e.g.\ blockchain).
       \item Each participant can check that their proof is indeed included.
@@
   \end{idea}
-  }
-
-  \pause
-
-  \begin{question}
-    Malicious nodes want to provide Alice with a view that her proof is 
-    included.
-    Everyone else is provided a view without Alice.
-    How can we ensure a consistent view for everyone?
-    (Probably similar to the solution in Joakim's thesis.)
-  \end{question}
 \end{frame}
@@
 
-\begin{frame}
-  \mode<presentation>{
+\begin{frame}<presentation>
   \begin{idea}[V\ref{EligibilityVerif} Eligibility]
@@
   \end{idea}
-  }
-
-  \pause
-
-  \begin{question}
-    How to solve the Sybil problem?
-    Can we piggyback on existing \acp{PKI}?
-    E.g.~\cite{Cinderella}.
-  \end{question}
-  \begin{question}
-    This is similar to the double-spending problem for cryptocurrencies, can 
-    we reuse any such techniques?
-  \end{question}
 \end{frame}
 
-If the block chain is public, then anyone can download all the proofs, verify 
+If the blockchain is public, then anyone can download all the proofs, verify 
 them (eligibility) and count them.
@@
 
-\begin{frame}
-  \mode<presentation>{
+\begin{frame}<presentation>
   \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
@@
   \end{idea}
-  }
-
-  \pause
-
-  \begin{question}
-    Similar as before: how can we ensure consistent views for everyone?
-  \end{question}
 \end{frame}

### 2017-08-03 intro.tex
Adds more comments
Adds limitations on methods, todo for Venezuelan protests

@@
 practice are manual and prone to errors.
+Additionally, none of these techniques can estimate the cumulative 
+participation count without counting some people multiple times.
 
@@
 
+% XXX Add the 2017 Venezuelan protests
+
 We can make one important observation about this problem that has seemingly 
@@
 to decrease the tallied number of participants, e.g.\ an authoritarian regime.
+(Or the other way around, an authoritarian regime wants to organize a 
+pro-regime protest to demonstrate its \enquote{wide support}.)
 To solve this problem, we need a verifiable participation count.

### 2017-08-03 properties.tex

--- 2017-08-01 properties.tex
@@
 \end{frame}
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{strict partial 
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
   order}\footnote{%
-  A relation \(\prec\) which is irreflexive, antisymmetric and transitive.
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
 }.
@@
 order allows to relate the data to the time of the event.
-\Cref{SpatiallyRelated} binds the data spatially to the event.
+This allows us to \emph{authenticate the data temporally}.
+\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
+us to \emph{authenticate the data spatially}.
 
@@
 signatures on the proof.
+So Alice needs a long-term and a short-term credential, but she should not be 
+able to create two short-term credentials to participate twice.
 
-\begin{frame}<presentation>
+\begin{frame}
   \begin{question}
@@
     Voting normally uses mix-nets.
+    Submit over Tor~\cite{Tor}?
   \end{question}
 
+  \mode<presentation>{
   \begin{remark}
-    Without anonymous submission we don't get vote pricacy, thus no receipt 
+    Without anonymous submission we don't get vote privacy, thus no receipt 
     freeness either.
   \end{remark}
+  }
 \end{frame}

### 2017-08-04 properties.tex
Merges authenticity with verification
Makes the authenticity requirements part of eligibility verification.

--- 2017-08-02 properties.tex
@@
 \mode*
-\section[Verification and privacy]{Authenticity, verification and privacy}
+\section{Verification and privacy}
 
@@
 
-\subsection{Data authenticity}
-\label{DataAuthenticity}
-
-The problem of authentically associating data with a physical event is 
-difficult.
-We can essentially divide it into the following requirements:
-\begin{frame}
-\begin{requirements}[A]
-  \item\label{CreatedAfterStart} Prove that the data was created after the 
-    start of the event.
-  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
-    of the event.
-  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
-    physical location of the event.
-\end{requirements} %TODO: A4 accurate/not fabricated?
-
-\pause
-
-\mode<presentation>{
-\begin{idea}
-  \begin{itemize}
-    \item There is a mechanism that provides A\ref{CreatedAfterStart} and 
-      A\ref{CreatedBeforeEnd}: a blockchain.
-
-    \item There are also other structures, e.g.\ a directed 
-      graph~\cite{BlockchainFreeCryptocurrencies}.
-
-    \item Add a consensus protocol and Eve must subvert a majority to change 
-      the outcome.
-
-      \pause
-
-    \item A\ref{SpatiallyRelated} can be provided by \iacf{LP}.
-  \end{itemize}
-\end{idea}
-}
-\end{frame}
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
-  order}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-}.
-If some objects in the set relate to known points in time, then the partial 
-order allows to relate the data to the time of the event.
-This allows us to \emph{authenticate the data temporally}.
-\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
-us to \emph{authenticate the data spatially}.
-
 \subsection{Verification}
@@
 each vote would be replaced by a proof of participation.
-To have any verifiability, we need the storage (e.g.\ blockchain) to be 
-immutable --- i.e.\ it prevents malicious changes.
 
@@
 Thus \cref{IndividualVerif} is fulfilled.
+To have any verifiability, we need the storage (e.g.\ blockchain) to be 
+immutable --- i.e.\ it prevents malicious changes.
 
@@
 attacks.
-They must also be able to detect if the proof is reused from a previous protest 
-(i.e.\ related to \cref{CreatedAfterStart,CreatedBeforeEnd}).
+They must also be able to verify that each proof is indeed related to the 
+event.
+We must associate the proof to the event both spatially (the correct location) 
+and temporally (it is related to the time-interval of the event).
+We can essentially divide it into the following requirements:
+\begin{frame}
+\begin{requirements}[\ref*{EligibilityVerif}.]
+  \item\label{UniqueIndividual} Prove that the data is unique for an 
+    individual.
+  \item\label{CreatedAfterStart} Prove that the data was created after the 
+    start of the event.
+  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
+    of the event.
+  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
+    physical location of the event.
+\end{requirements}
+\end{frame}
+
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
+  order}\footnote{%
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
+}.
+If some objects in the set relate to known points in time, then the partial 
+order allows to relate the data to the time of the event.
+This allows us to \emph{verify the data temporally}.
+\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
+us to \emph{verify the data spatially}.
 
@@
 
-If the blockchain is public, then anyone can download all the proofs, verify 
-them (eligibility) and count them.
+If the storage is public, then anyone can download all the proofs, verify them 
+and count them.
 Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

### 2017-08-04 primitives.tex
Merges authenticity with verification
Makes the authenticity requirements part of eligibility verification.
Edits properties, make implementation independent

@@
   \begin{question}
+    How do we submit the proofs to storage?
+    Voting normally uses mix-nets.
+    Submit over Tor~\cite{Tor}?
+  \end{question}
+
+  \mode<presentation>{
+  \begin{remark}
+    Without anonymous submission we don't get vote privacy, thus no receipt 
+    freeness either.
+  \end{remark}
+  }
+\end{frame}
+
+\begin{frame}
+  \begin{question}
     Malicious nodes want to provide Alice with a view that her proof is 
@@
 
+\begin{frame}<presentation>
+\begin{idea}
+  \begin{itemize}
+    \item There is a mechanism that provides V\ref{CreatedAfterStart} and 
+      V\ref{CreatedBeforeEnd}: a blockchain.
+
+    \item There are also other structures, e.g.\ a directed 
+      graph~\cite{BlockchainFreeCryptocurrencies}.
+
+      \pause
+
+    \item V\ref{SpatiallyRelated} can be provided by \iacf{LP}.
+  \end{itemize}
+\end{idea}
+\end{frame}
+
 \begin{frame}
@@
 \end{frame}
+
+So Alice needs a long-term and a short-term credential, but she should not be 
+able to create two short-term credentials to participate twice.
+
+\begin{frame}
+  \begin{question}
+    Will such a signature scheme solve both problems?
+  \end{question}
+  \begin{question}
+    Is there such a signature scheme?
+    Can we construct it?
+  \end{question}
+  \begin{question}
+    What Alice submits her proof, stores the hash of the block, removes proof 
+    and signature key?
+  \end{question}
+\end{frame}

### 2017-08-04 properties.tex
Edits properties, make implementation independent

@@
 How can she ensure that photos from a demonstration are authentic?
-We can probably recognize the place the photo is portraying, however, this 
-might just as well be a reconstruction or entirely computer generated.
+We can probably recognize the location that the photo is portraying, however, 
+this might just as well be a reconstruction or entirely computer generated.
 We cannot trust the meta-data of the photo, such as time-stamps of the file, 
@@
 participants of a demonstration?
-This is discussed further in \cref{DataAuthenticity}.
-
-Assume that Alice can provide this authenticated data.
-Alice and Bob do not want that this data ties them to the demonstration, 
-because then the autocrat Eve can use this data to find out about Alice and Bob 
-and arrest them.
-Thus, what Alice and Bob need is a system which can provide data authenticity 
-and user privacy, i.e.\ that the data can be correctly tied to the 
-demonstration without outing Alice and Bob as supporters but still ensuring 
-that Alice is Alice and Bob is Bob.
-As a protest can be compared to voting (either voting for or against the 
-cause), we will adapt the security and privacy properties of electronic 
-voting.
-We will discuss this further in \cref{Verification}.
-
-It can also be compared to electronic voting --- to vote for or against the 
-cause.
-In this case all participants and third-parties can verify the authenticity of 
-the result, this would inherit all the desirable properties of the electronic 
-voting system (these properties are discussed in \cref{Verification}).
-We are interested in real-world protests, i.e.\ demonstrations where 
-participants gather in a physical location.
-For these we need to bind all participants to the same physical location at 
-a reasonably similar time (within the duration of the protest).
+Furthermore, how can Alice protect the privacy of those in the photos?
 
@@
 expressing their opinion.
-Hence we desire to have similar properties of verification and privacy for 
-participation in a protest as there is for voting.
+These opinions can be sensitive, hence we desire to have similar properties of 
+verification and privacy for participation in a protest as there is for voting.
 In the context of (electronic) voting protocols, there are three requirements 
@@
     physical location of the event.
+  \item\label{DesignatedEvent} Prove that the data is designated for the event.
 \end{requirements}
@@
 
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partial 
-  order}\footnote{%
+\Cref{UniqueIndividual} is required to prevent Sybil attacks.
+I.e.\ that one individual can provide two proofs of participation and thus be 
+counted twice, this situation should be detectable.
+
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
+  set}\footnote{%
   A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-}.
+} of objects.
 If some objects in the set relate to known points in time, then the partial 
-order allows to relate the data to the time of the event.
+order relates the data to the time of the event.
 This allows us to \emph{verify the data temporally}.
@@
 us to \emph{verify the data spatially}.
+Finally, there might be the case that there is also a counter protest at the 
+same time, these would have the same spatial and temporal properties.
+To distinguish them, we also need to prove for which of these events that a 
+proof is designated (\cref{DesignatedEvent}).
 
@@
 (Following this line of thinking, it can actually be beneficial for the privacy 
-of the demonstrators to mix with the participants from any 
-counter-demonstrations --- since the counts will still be correct.)
+of the demonstrators to mix with the participants of any counter-demonstrations 
+--- since the counts will still be correct.)
 
@@
 
-A demonstration is very different from voting in one sense: Alice must be 
-physically present and that very presence shows her support for the cause.
-In voting, on the other hand, Alice has multiple options which are not revealed
-by her mere presence.
+A demonstration is very different from voting in one sense: at a demonstration, 
+Alice must be physically present and that very presence shows her support for 
+the cause.
+In voting, on the other hand, everyone is present and Alice has multiple 
+options which are not revealed by her mere presence.
 % XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof to the blockchain, the proof must be 
-unlinkable to Alice, yet, if Alice submits another proof, those two proofs must 
-be linkable (due to eligibility verification, \cref{EligibilityVerif}).
-E.g.\ Eve compromises Alice's device (and private keys).
-Anyone can verify any proof.
-With the inputs that Eve can extract from the published proof and the keys she 
-can find on Alice's device, she should not be able to reproduce the same 
-signatures on the proof.
-So Alice needs a long-term and a short-term credential, but she should not be 
-able to create two short-term credentials to participate twice.
-
-\begin{frame}
-  \begin{question}
-    How do we submit the proofs to storage?
-    Voting normally uses mix-nets.
-    Submit over Tor~\cite{Tor}?
-  \end{question}
-
-  \mode<presentation>{
-  \begin{remark}
-    Without anonymous submission we don't get vote privacy, thus no receipt 
-    freeness either.
-  \end{remark}
-  }
-\end{frame}
+Hence, if Alice submits a proof of participation, the proof must be unlinkable 
+to Alice, yet, if Alice submits another proof, those two proofs must be 
+linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
+Alice is not counted twice.
+Receipt freeness implies that Alice enjoys deniability against Eve:
+Eve should not be able to use the published proof to tie it to Alice, even if 
+Eve has access to Alice's device (i.e.\ all her private keys).
+I.e.\ Eve should not be able to reproduce the same proof.
 
@@
         signature when run on the same inputs.
+
+        \item E.g.\ a short-term and a long-term credential, then Alice can 
+          drop the short-term credential.
     \end{itemize}
@@
 \end{frame}
-
-\begin{frame}
-  \begin{question}
-    Will such a signature scheme solve both problems?
-  \end{question}
-  \begin{question}
-    Is there such a signature scheme?
-    Can we construct it?
-  \end{question}
-  \begin{question}
-    What Alice submits her proof, stores the hash of the block, removes proof 
-    and signature key?
-  \end{question}
-\end{frame}

### 2017-08-04 design.tex
Renames primitives section to design
Edits design section, merges architecture

--- 2017-08-04 primitives.tex
@@
 
-\section{Primitives}
-\label{Primitives}
+\section{Design}
+\label{Design}
 
@@
 
-\subsection{Authenticity}
+\subsection{Eligibility verifiability}
+
+We have the five requirements for eligibility verifiability.
+
+\subsubsection{Temporal eligibility}
 
@@
     What about distributed voting/polling protocols?
-    A tree should give a strict partial order?
+    They must be complemented by time-stamping.
   \end{question}
@@
 \begin{frame}<presentation>
-  \begin{solution}[A\ref{CreatedBeforeEnd} Created before end]
+  \begin{solution}[V\ref{CreatedBeforeEnd} Created before end]
     \begin{itemize}
@@
       \item The proof must've been created before it was included (duh!).
-      \item (Also related to V\ref{EligibilityVerif}.)
     \end{itemize}
@@
 
-\subsection{Location proofs}
+\subsubsection{Spatial eligibility}
 
@@
 
-\subsection{Storage}
+\subsubsection{Count only once}
+
+We also need to ensure that proofs made by the same person must be linkable 
+(\cref{UniqueIndividual}).
+
+\begin{frame}
+  \begin{question}
+    How to solve the Sybil problem?
+    Can we piggyback on existing \acp{PKI}?
+    E.g.~\cite{Cinderella}.
+  \end{question}
+  \begin{question}
+    This is similar to the double-spending problem for cryptocurrencies, can 
+    we reuse any such techniques?
+    Specifically ecash~\cite{ecash} and the like.
+  \end{question}
+\end{frame}
+
+\subsubsection{Designated event}
+
+We must ensure that the data is designated to the event 
+(\cref{DesignatedEvent}), otherwise a counter-protest can copy the proofs and 
+reuse them.
+
+\begin{frame}
+  \begin{question}
+    How to designate a proof to an event?
+    Include an event specific value?
+  \end{question}
+  \begin{question}
+    How must this value be chosen?
+    By the organizer?
+    Randomly?
+    Deterministically but unpredictably?
+  \end{question}
+\end{frame}
+
+\subsection{Privacy}
+
+\subsubsection{Architecture}
+
+\begin{frame}
+  \begin{question}
+    Shall we offer a platform that is run by a variety of institutions who 
+    offers to verify protests?
+    Or go strictly peer-to-peer?
+  \end{question}
+  \begin{question}
+    If strictly peer-to-peer, and only run by protesters, one can infer that 
+    they are protesters by running such a node.
+    Can this be mitigated?
+  \end{question}
+\end{frame}
+
+\subsubsection{Storage}
 
@@
 
-\subsection{Verifiability}
-
-\begin{frame}<presentation>
-\begin{idea}
-  \begin{itemize}
-    \item There is a mechanism that provides V\ref{CreatedAfterStart} and 
-      V\ref{CreatedBeforeEnd}: a blockchain.
-
-    \item There are also other structures, e.g.\ a directed 
-      graph~\cite{BlockchainFreeCryptocurrencies}.
-
-      \pause
-
-    \item V\ref{SpatiallyRelated} can be provided by \iacf{LP}.
-  \end{itemize}
-\end{idea}
-\end{frame}
-
-\begin{frame}
-  \begin{question}
-    How to solve the Sybil problem?
-    Can we piggyback on existing \acp{PKI}?
-    E.g.~\cite{Cinderella}.
-  \end{question}
-  \begin{question}
-    This is similar to the double-spending problem for cryptocurrencies, can 
-    we reuse any such techniques?
-    Specifically ecash~\cite{ecash} and the like.
-  \end{question}
-\end{frame}
+\subsubsection{Sybil}
 

### 2017-08-04 properties.tex
Some more editing
Syncs conclusions with previous edits

@@
 \begin{requirements}[\ref*{EligibilityVerif}.]
-  \item\label{UniqueIndividual} Prove that the data is unique for an 
-    individual.
+  \item\label{CountOnce} Prove that no individual can be counted more than 
+    once.
   \item\label{CreatedAfterStart} Prove that the data was created after the 
@@
 
-\Cref{UniqueIndividual} is required to prevent Sybil attacks.
+\Cref{CountOnce} is required to prevent Sybil attacks.
 I.e.\ that one individual can provide two proofs of participation and thus be 
@@
     \begin{itemize}
-      \item Must verify that the proof is not reused from before 
-        (A\ref{CreatedAfterStart} and A\ref{CreatedBeforeEnd}).
+      \item Must verify that the proof is not reused from before.
       \item Must verify that each proof belongs to a unique individual (not 

### 2017-08-04 RelatedWork.tex
Fixes typo in Related Work
Syncs related work to other edits

@@
 the same photos.
-This provides universal verifiability (\cref{UniversalVerif})).
+This provides universal verifiability (\cref{UniversalVerif}).
 It is difficult to achieve individual verifiability (\cref{IndividualVerif}) 
@@
       \item Prone to errors, due to estimations.
-      \item Universally verifiable (\cref{UniversalVerif}), anyone with the 
-        photos can redo the estimate.
-      \item Eligibility verifiability (\cref{EligibilityVerif}) if photos at 
-        one snapshot in time and no overlap.
+      \item Universally verifiable, anyone with the photos can redo the 
+        estimate.
+      \item Eligibility verifiability if photos at one snapshot in time and no 
+        overlap.
     \end{itemize}
@@
       \item Not verifiable unless the user takes a picture of the crowd.
-      \item The it will be reduced to the previous method.
+      \item Then it will be reduced to the previous method.
     \end{itemize}
@@
       \item MAC address randomization.
-      \item Cannot verify, nor authenticate.
+      \item Cannot verify.
     \end{itemize}
@@
       \item Privacy-invading due to phones being uniquely identifying.
-      \item Cannot verify, nor authenticate.
+      \item Cannot verify.
     \end{itemize}
@@
 peak.
+
+%\subsection<presentation>{Crowd sensing}
+%
+%\dots
 
@@
     \begin{itemize}
-      \item No verification, nor authenticity, the service must be trusted.
+      \item No verification, the service must be trusted.
       \item Nothing prevents Bob from checking in twice.

### 2017-08-08 intro.tex
Adds another comment about Venezuela
Minor edit to intro about governments organizing protests

@@
 to decrease the tallied number of participants, e.g.\ an authoritarian regime.
-(Or the other way around, an authoritarian regime wants to organize a 
-pro-regime protest to demonstrate its \enquote{wide support}.)
-To solve this problem, we need a verifiable participation count.
+Or the other way around, sometimes an authoritarian regime wants to organize a 
+pro-regime protest to demonstrate its \enquote{wide support}.
+% XXX Wasn't this the case in Venezuela?
+(This makes it difficult to rely on government-issued credentials to prevent a 
+Sybil attack --- government can issue arbitrarily many such credentials for its 
+own protests.)
+To solve this problem, we need a verifiable participation count which is 
+protected from Sybil attacks.
 In this paper, we combine the verifiability and privacy properties of 

### 2017-08-09 SystemModel.tex
Fixes so that beamerarticle modes are correct
Adds notes and questions since meeting

@@
-\section{System Model}
+\mode*
+
+\section{System model}
 \label{SystemModel}
+
+\begin{frame}
+\begin{question}
+  What is participating in a protest?
+  We need a definition.
+\end{question}
+\mode<presentation>{
+\begin{remark}
+  \begin{itemize}
+    \item This depends on the unique ring/list signature schemes.
+    \item I.e.\ when we can no longer guarantee uniqueness.
+    \item The one setting up that signature scheme decides.
+    \item We don't know how this will be done, nor by whom.
+  \end{itemize}
+\end{remark}
+}
+\end{frame}
+This sort of depends on the unique ring/list signature scheme that we use.
+As long as we can provide linkability between a user's proofs, we can consider 
+it the same protest.
+When we cannot, it must be a new protest.
+So this is supposedly decided by the one setting up the unique ring/list 
+signature scheme --- which we do not know yet how it will be done.
+
+\begin{frame}
+\begin{remark}
+  We provide a lower bound, since there might be participants without phones.
+\end{remark}
+\begin{remark}
+  I.e.\ provided we can prevent Sybil.
+\end{remark}
+\end{frame}
+
+\begin{frame}
+\begin{question}
+  What assumptions do we need?
+\end{question}
+
+We assume that
+\begin{itemize}
+  \item Everyone has a smartphone.
+  \item Can use ad-hoc networks during the event.
+\end{itemize}
+\end{frame}
+
+\subsection{Adversary model}
+
+We have two types of adversaries:
+\begin{frame}
+\begin{itemize}
+  \item Eve tries to lower the count.
+  \item Eve tries to deanonymize protesters.
+\end{itemize}
+\end{frame}
+
+\mode<all>\endinput
+
+\section{Old stuff}
 

### 2017-08-10 intro.tex
Edits intro and related work

@@
 
-There are different possibilities for a protest: e.g.\ one performed online or 
-one performed in the physical reality.
-We are interested in real-world protests, specifically to verify a protest.
-One problem in real-world demonstrations that has not yet been entirely solved 
-is the crowd-counting problem, i.e.\ the verification of the participation in 
-a demonstration.
+Alice organizes a street protest against Eve's regime.
+Bob, Carol and many others participate in the demonstration.
+One problem that has not yet been entirely solved is the crowd-counting 
+problem, i.e.\ to verify how many participated in Alice's protest.
 
@@
     \begin{itemize}
-      \item Computer Vision to do object recognition.
-      \item Requires photos that cover the entire location, all the time.
+      \item Computer vision does object recognition.
+      \item Requires photos/video that cover the entire location, all the time.
+      \item This will count people twice.
     \end{itemize}
@@
 
+\subsection<presentation>{Why is it a problem?}
+
 \begin{frame}<presentation>
@@
         approximate count by imagery.
+        \begin{description}
+          \item[Police] X
+          \item[Organizers] Y
+        \end{description}
+
+        \pause
 
@@
         sum up people's approximations.
+      \item This makes it even difficult to estimate the error.
     \end{itemize}
@@
 
-\subsection<presentation>{Why is it a problem?}
+After many demonstrations the count by police and that by the organizers 
+differ, in some instances the difference can be hundreds of thousands.
+There are numerous examples, e.g.\ the demonstrations in South 
+Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
+inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
+in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
+establishing the actual number of participants.
+The methods for counting the crowds vary.
+Most of the available methods lack precision, i.e.\ they have large error 
+margins.
+They can only give an estimate for a particular snapshot in time, e.g.\ at the 
+peak of the event, not the cumulative participation count --- at least not 
+without counting some people multiple times, which in turn increases the error 
+of the estimation.
+Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
+does the counting.
+We will discuss them in more detail in \cref{RelatedWork}.
 

### 2017-08-10 intro.tex
Adds discussion of what is a protest, Venezuela
This fixes #5.

@@
 
-After many demonstrations the count by police and that by the organizers 
-differ, in some instances the difference can be hundreds of thousands.
-There are numerous examples, e.g.\ the demonstrations in South 
-Korea~\cite{2016DemonstrationsInSeoul} or the women's marches in the 
-US~\cite{2017WomensMarchesInUS}, where there is difficulty in establishing the 
-actual number of participants.
-The methods for counting the crowds vary.
-There are some techniques using computer vision found in the research 
-literature, e.g.\ by \textcite{CVCrowdCounting}.
-These require images from the demonstration and provide no way to verify the 
-authenticity of the count (except re-running the algorithm on one's own input 
-data).
-However, as is illustrated by 
-\textcite{2016DemonstrationsInSeoul,2017WomensMarchesInUS}, the methods used in 
-practice are manual and prone to errors.
-Additionally, none of these techniques can estimate the cumulative 
-participation count without counting some people multiple times.
+We can make one important observation about this problem that has seemingly 
+been ignored in the past: it is an adversarial setting.
+The protesters (organizers and participants) have an incentive to increase the 
+tallied number of participants, whereas other interests might have an incentive 
+to decrease the tallied number of participants, e.g.\ Eve's authoritarian 
+regime in our example above.
+Or the other way around, sometimes Eve's authoritarian regime wants to organize 
+a pro-regime protest to demonstrate its \enquote{wide 
+  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+(This makes it difficult to rely on government-issued credentials to prevent a 
+Sybil attack --- government can issue arbitrarily many such credentials for its 
+own protests.)
+To solve this problem, we need a verifiable participation count which is 
+protected from Sybil attacks.
 
+\subsection{What is \protect\emph{a} protest?}
+
+Protests can vary considerably.
+To be able to estimate the participation count for one, we first need to define
+what should be counted.
+
+Let us start by considering some examples.
+During the demonstrations against the South Korean president in Seoul
 \blockcquote{2016DemonstrationsInSeoul}{%
-  The rallies stretch from midday to late night --- some people stay for 
-  several hours, others just several minutes.%
-}
-
-\blockcquote{2016DemonstrationsInSeoul}{%
-  The demonstrators not only gather in open space, but also small alleys and 
-  between buildings.%
-}
+  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
+  people stay\textins{ed} for several hours, others just several minutes%
+}.
+These rallies were all in the same location in the capital and repeated every 
+weekend for the duration of a few weeks.
+The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
+in parallel in many locations.
+We also have the Venezuelan demonstrations where
+\blockcquote{2017VenezuelaProtestFrequency}{%
+  anti-government demonstrators have staged daily protests across Venezuela%
+} while
+\blockcquote{AlJazeeraOnVenezuela2017}{%
+  pro-government workers sang and danced as they staged a rival march to show 
+  their support for the president's controversial plan to rewrite the 
+  constitution%
+}.
+Judging from these examples, the minimal common part is the cause.
 
@@
 
-\blockcquote{HowToEstimateCrowdSize}{%
-  the more widely that a crowd is spread out, the more challenging it can be to 
-  get an accurate estimate of those attending, as it can become difficult to 
-  determine whether people near the event's perimeter are there for the event 
-  or are in the area for other reasons,%
-}
+%However, to complicate things further,
+%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
+%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
+%  getting text messages, phone calls and being required to attend political 
+%  rallies during work hours
+%}.
+%
+%\blockcquote{BBConVenezuelaProtestBan}{%
+%  Venezuela is banning protests that could "disturb or affect" Sunday's 
+%  controversial election for a new constituent assembly.
+%}
+%
+%\blockcquote{BBConVenezuelaProtestBan}{%
+%  Prison terms of between five and 10 years could be imposed on those 
+%  contravening the ban,
+%}
+%
+%\blockcquote{VenezuelanGovtBansProtesting}{%
+%  Venezuelans are planning to defy a government ban on public demonstrations 
+%  and risk deadly repression with marches across the country to protest against 
+%  a vote Sunday that opposition forces say will mark the end of democracy
+%}
 
-% XXX Add the 2017 Venezuelan protests
+\subsection{Contributions}
 
-We can make one important observation about this problem that has seemingly 
-been ignored in the past: it is an adversarial setting.
-The protesters (organizers and participants) have an incentive to increase the 
-tallied number of participants, whereas other interests might have an incentive 
-to decrease the tallied number of participants, e.g.\ an authoritarian regime.
-Or the other way around, sometimes an authoritarian regime wants to organize a 
-pro-regime protest to demonstrate its \enquote{wide support}.
-% XXX Wasn't this the case in Venezuela?
-(This makes it difficult to rely on government-issued credentials to prevent a 
-Sybil attack --- government can issue arbitrarily many such credentials for its 
-own protests.)
-To solve this problem, we need a verifiable participation count which is 
-protected from Sybil attacks.
 In this paper, we combine the verifiability and privacy properties of 

### 2017-08-10 RelatedWork.tex

--- 2017-07-25 RelatedWork.tex
@@
 \section{Related work}
+\label{RelatedWork}
 
@@
 
+Another problem for all the above methods is exemplified by the demonstrations 
+in Seoul:
+\blockcquote{2016DemonstrationsInSeoul}{%
+  \textins*{t}he demonstrators not only gather in open space, but also small 
+  alleys and between buildings%
+}.
+This is difficult to fully capture.
+If photo material is taken from angles we will additionally have problems not 
+counting people twice.
+
 \subsection<presentation>{Signal-based methods}
@@
 
+%\subsection<presentation>{Crowd sensing}
+%
+%\dots
+
 \subsection<presentation>{More exact methods}

### 2017-08-10 intro.tex

@@
 
-\blockcquote{2016DemonstrationsInSeoul}{%
-  For the police, the aim is to measure the maximum crowd occupying a certain 
-  space at any given time so that they could determine the size of police 
-  personnel and resources to deploy%
-}
+The organizers want to count everyone who participated at any time and in any 
+of the locations~\cite{2016DemonstrationsInSeoul}.
+(Whereas police are only interested in the maximum crowd at any point in time, 
+to deploy enough personnel for crowd-control.)
+We thus settle for the following definition.
 
-\blockcquote{2016DemonstrationsInSeoul}{%
-  Organizers seek to track the entire flow of people from the protest’s start 
-  to its finish. They collect estimates given by counters deployed at different 
-  locations to size up the crowds in each area and update the numbers 
-  throughout the duration of the protest.%
-}
+\begin{definition}[A protest]
+  A protest is an event identified by its cause.
+\end{definition}
 

### 2017-08-10 intro.tex
Adds slides for protest def
Rewrites using Alice as subject

@@
 
-The organizers want to count everyone who participated at any time and in any 
-of the locations~\cite{2016DemonstrationsInSeoul}.
+\begin{frame}<presentation>
+  \begin{example}[Seoul 2016]
+    \begin{itemize}
+      \item Rallies every weekend.
+      \item Starting midday, lasting to late night.
+      \item Some stayed for several hours, some for only minutes.
+    \end{itemize}
+  \end{example}
+
+  \pause
+
+  \begin{example}[US 2017]
+    \begin{itemize}
+      \item Women's Marches in several locations.
+      \item Marched some distance.
+      \item One-time occurrence.
+    \end{itemize}
+  \end{example}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{example}[Venezuela 2017]
+    \begin{itemize}
+      \item Daily anti-government rallies.
+      \item Multiple locations.
+      \item Pro-government rallies too.
+    \end{itemize}
+  \end{example}
+\end{frame}
+
+The organizer Alice want to count everyone who participated at any time and in 
+any of the locations~\cite{2016DemonstrationsInSeoul}.
 (Whereas police are only interested in the maximum crowd at any point in time, 
@@
 
+\begin{frame}<presentation>
+  \begin{remark}
+    \begin{itemize}
+      \item Organizers want to count anyone who participated \dots
+      \item \dots at any time
+      \item \dots in any location
+    \end{itemize}
+  \end{remark}
+\end{frame}
+
+\begin{frame}
 \begin{definition}[A protest]
@@
 \end{definition}
+\end{frame}
 

### 2017-08-11 conclusions.tex

@@
 
-In general, none of the related works fulfils the authenticity requirements 
-(\cref{%
-  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated%
-}).
-Some of the schemes provide some limited verifiability, i.e.\ mostly universal 
-verifiability (\cref{UniversalVerif}), but not individual verifiability 
-(\cref{IndividualVerif}) nor eligibility verifiability 
-(\cref{EligibilityVerif}).
+In general, none of the related works fulfils the eligibility verifiability 
+\cref{%
+  CountOnce,%
+  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated,%
+}.
+To some extent, some techniques do fulfil \cref{DesignatedEvent}, since people 
+usually use placards in the protests.
+Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
+not individual verifiability (\cref{IndividualVerif}).
+If they would provide individual verifiability, they would likely violate the 
+privacy requirements.
+And finally, most of the current methods are estimates, with quite some error 
+margins, so they cannot give the correct participation count.
 
@@
     \begin{itemize}
-      \item All current methods lack authenticity and verifiability.
+      \item All current methods lack most of verifiability.
       \item Some provide universal verifiability (V\ref{UniversalVerif}).
+
+        \pause
+
+      \item Most cannot estimate the correct participation count.
     \end{itemize}

### 2017-08-11 intro.tex
Moves properties into introduction

@@
 After many demonstrations the count by police and that by the organizers 
-differ, in some instances the difference can be hundreds of thousands.
+differ\footnote{%
+  This is actually quite natural, they have different goals.
+  The organizers want to count everyone who ever participated.
+  Police want to estimate the count at the peak of participation, due to crowd 
+  control~\cite{2016DemonstrationsInSeoul}.
+}, in some instances the difference can be hundreds of thousands.
 There are numerous examples, e.g.\ the demonstrations in South 
@@
 
-%However, to complicate things further,
-%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
-%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
-%  getting text messages, phone calls and being required to attend political 
-%  rallies during work hours
-%}.
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Venezuela is banning protests that could "disturb or affect" Sunday's 
-%  controversial election for a new constituent assembly.
-%}
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Prison terms of between five and 10 years could be imposed on those 
-%  contravening the ban,
-%}
-%
-%\blockcquote{VenezuelanGovtBansProtesting}{%
-%  Venezuelans are planning to defy a government ban on public demonstrations 
-%  and risk deadly repression with marches across the country to protest against 
-%  a vote Sunday that opposition forces say will mark the end of democracy
-%}
+% Verifiability and privacy
+\mode<all>
+\input{properties.tex}
 

### 2017-08-11 abstract.tex
Edits abstract
Edits abstract, adapts to merging auth and verifiability

@@
 Since the parties have incentives to cheat, we require transparency: in 
-particular we are aiming at a decentralized scheme that provides authenticity, 
-verifiability and privacy.
+particular we are aiming at a decentralized scheme that provides verifiability 
+and privacy.
 More specifically, the scheme should be distributed and not depend on any 
 authority.
-We must also ensure that the data is time-wise related to the event (i.e.\ 
-authenticity), which can be provided by blockchain-like structures.
-The data must also be related to the location, something a location proof can 
-achieve.
 We need verifiability, which means that every participant can verify that their 
@@
 malicious actor (e.g. Sybil) from affecting the result.
-Finally, as all things policital, privacy is critical.
+Eligibility verifiability also requires that the data is time-wise related to 
+the event (temporal eligibility), which can be provided by blockchain-like 
+structures.
+The data must also be related to the location (spatial eligibility), something 
+a location proof can achieve.
+As all things policital, privacy is critical.
 Similar to e-voting schemes, we need to guarantee properties close to vote 
@@
 infer that she is critical of Eve.
-Finally, the scheme must be scalable to handle large protests (millions of 
-participants).
+Finally, the scheme must be scalable to handle large protests (i.e.\ millions 
+of participants).
 

### 2017-08-11 design.tex
Fixes depth level for TOC in slides
Splits storage into related to privacy, verifiability

@@
 
+\begin{frame}
+  \begin{question}
+    What if Alice acts as a witness for Eve's agents?
+    Can that violate her privacy?
+  \end{question}
+  \begin{question}
+    What if Eve's agents act as witnesses?
+    Can they track their signatures to track users?
+    Can Alice detect if this happens?
+  \end{question}
+\end{frame}
+
 \subsubsection{Count only once}
@@
 We also need to ensure that proofs made by the same person must be linkable 
-(\cref{UniqueIndividual}).
+(\cref{CountOnce}).
 
@@
     Deterministically but unpredictably?
+  \end{question}
+\end{frame}
+
+\subsection{Individual and universal verifiability}
+
+\begin{frame}
+  \begin{question}
+    Malicious nodes want to provide Alice with a view that her proof is 
+    included.
+    Everyone else is provided a view without Alice.
+    How can we ensure a consistent view for everyone?
+    (Probably similar to the solution in Joakim's thesis.)
+  \end{question}
+
+  \begin{question}
+    Under the protest conditions, we might have natural network splits.
+    Is this a useful scenario?
+  \end{question}
+
+  \begin{question}
+    How can we do blockchain branch and merge?
+    That is needed to recover from the above attack.
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    What can we achieve with a consensus protocol?
+    Majority must be honest?
+  \end{question}
+  \begin{question}
+    What is a suitable proof-of-work?
+    See e.g.~\cite{FairProofOfWork}.
   \end{question}
@@
 
-\begin{frame}
-  \begin{question}
-    Malicious nodes want to provide Alice with a view that her proof is 
-    included.
-    Everyone else is provided a view without Alice.
-    How can we ensure a consistent view for everyone?
-    (Probably similar to the solution in Joakim's thesis.)
-  \end{question}
-
-  \begin{question}
-    Under the protest conditions, we might have natural network splits.
-    Is this a useful scenario?
-  \end{question}
-
-  \begin{question}
-    How can we do blockchain branch and merge?
-    That is needed to recover from the above attack.
-  \end{question}
-\end{frame}
-
-\begin{frame}
-  \begin{question}
-    What can we achieve with a consensus protocol?
-    Majority must be honest?
-  \end{question}
-  \begin{question}
-    What is a suitable proof-of-work?
-    See e.g.~\cite{FairProofOfWork}.
-  \end{question}
-\end{frame}
-
 \subsubsection{Sybil}

### 2017-08-11 intro.tex

@@
 to deploy enough personnel for crowd-control.)
-We thus settle for the following definition.
+We thus settle for the following informal definition:
+a protest is an event identified by its cause.
 
@@
       \item \dots in any location
+      \item A protest is thus identified by its cause.
     \end{itemize}
   \end{remark}
-\end{frame}
-
-\begin{frame}
-\begin{definition}[A protest]
-  A protest is an event identified by its cause.
-\end{definition}
 \end{frame}

### 2017-08-17 SystemModel.tex
Adds Rusuk adversary
Adds WIP on system model

@@
 
-\begin{frame}
-\begin{question}
-  What is participating in a protest?
-  We need a definition.
-\end{question}
-\mode<presentation>{
-\begin{remark}
+\subsection{Assumptions}
+
+We assume that every participant has a device similar to a smartphone.
+It must be a portable device which can perform cryptographic operations and 
+communicate with other devices during the protest, e.g.\ through an ad-hoc 
+network.
+I.e.\ no connection to the Internet is necessary during the protest.
+During the protest these devices are computationally limited by their 
+batteries.
+Before and after the protest, we assume that the devices have Internet 
+connections and are not computationally limited by any battery.
+
+\begin{frame}<presentation>
+  \begin{assumption}[During protest]
     \begin{itemize}
-    \item This depends on the unique ring/list signature schemes.
-    \item I.e.\ when we can no longer guarantee uniqueness.
-    \item The one setting up that signature scheme decides.
-    \item We don't know how this will be done, nor by whom.
+      \item Everyone has a smartphone.
+      \item Can use ad-hoc networks during the event.
+      \item Computations bounded by battery life.
     \end{itemize}
-\end{remark}
-}
+  \end{assumption}
+
+  \pause
+
+  \begin{assumption}[Before and after protest]
+    \begin{itemize}
+      \item Internet connection available.
+      \item Computations not bounded by battery life.
+    \end{itemize}
+  \end{assumption}
 \end{frame}
-This sort of depends on the unique ring/list signature scheme that we use.
-As long as we can provide linkability between a user's proofs, we can consider 
-it the same protest.
-When we cannot, it must be a new protest.
-So this is supposedly decided by the one setting up the unique ring/list 
-signature scheme --- which we do not know yet how it will be done.
 
+This means that we essentially provide a lower bound for the participation 
+count, since some participants might not have any smartphone.
 \begin{frame}
@@
 
+\subsection{Adversary model}
+
+We have three adversaries: Alice herself, Eve and Rusuk.
+Alice the protest organizer tries to increase the count.
+Eve the totalitarian dictator tries to decrease the count.
+Additionally, Eve tries to deanonymize the participants.
+Finally, we have Rusuk who is the head of another nation state.
+Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
+gain, thus supporting either Eve or Alice.
+Rusuk will thus also try to either increase or decrease the count.
+
+\begin{frame}<presentation>
+  \begin{block}{Alice the activist}
+    \begin{itemize}
+      \item Alice organizes the protest against Eve's regime.
+      \item Alice wants to have a high participation count.
+      \item She tries to increase it.
+    \end{itemize}
+  \end{block}
+
+  \pause
+
+  \begin{block}{Eve the fake-news populist}
+    \begin{itemize}
+      \item Eve's regime is target of the protest.
+      \item She wants to have a low participation count.
+      \item She tries to decrease it.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{block}{Eve the totalitarian dictator}
+    \begin{itemize}
+      \item Eve wants to \enquote{convince} activists to support her.
+      \item She wants to find all activists.
+      \item She tries to identify (deanonymize) participants.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{block}{Rusuk the nation state}
+    \begin{itemize}
+      \item Rusuk benefits from the situation in Evestan.
+      \item He wants the outcome to be the most beneficial.
+      \item He will try to increase or decrease the participation count.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\subsection{System model}
+
+We will define a protest as an event that is uniquely identified by its cause, 
+its time and its location.
+More specifically, we will use the following definition.
+
+\begin{definition}[Protest]
+  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
+  \(id\in \Z_{2^\lambda}\) is an identifier,
+  \((t_s, t_e)\in \R^2\) is a time interval,
+  \((x, y)\in \R^2\) are the coordinates of the location.
+  A \emph{protest} is a set of subprotests.
+\end{definition}
+
+\begin{frame}<presentation>
+\begin{definition}[Protest]
+  \begin{itemize}
+    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
+    \item \(id\in \Z_{2^\lambda}\) is an identifier,
+    \item \((t_s, t_e)\in \R^2\) is a time interval,
+    \item \((x, y)\in \R^2\) are the coordinates of the location.
+    \item A \emph{protest} is a set of subprotests.
+  \end{itemize}
+\end{definition}
+\end{frame}
+
+The protests described in \cref{WhatIsAProtest} can be captured using this 
+definition by splitting them up into subprotests.
+Each subprotest will then be captured by our definition and to find the total 
+we can just sum up the results.
+
 \begin{frame}
 \begin{question}
-  What assumptions do we need?
+  With this definition, can we participate in two sub-protests and be counted 
+  twice?
 \end{question}
-
-We assume that
-\begin{itemize}
-  \item Everyone has a smartphone.
-  \item Can use ad-hoc networks during the event.
-\end{itemize}
+\begin{remark}
+  Perhaps not if linkability is tied to the cause.
+\end{remark}
 \end{frame}
-
-\subsection{Adversary model}
-
-We have two types of adversaries:
-\begin{frame}
-\begin{itemize}
-  \item Eve tries to lower the count.
-  \item Eve tries to deanonymize protesters.
-\end{itemize}
-\end{frame}
+\begin{remark}
+  This sort of depends on the unique ring/list signature scheme that we use.
+  As long as we can provide linkability between a user's proofs, we can consider 
+  it the same protest.
+  When we cannot, it must be a new protest.
+  So this is supposedly decided by the one setting up the unique ring/list 
+  signature scheme --- which we do not know yet how it will be done.
+\end{remark}
 

### 2017-08-18 SystemModel.tex
Adds def of participation proof

@@
 
-\begin{definition}[Protest]
+\begin{definition}[Protest]\label{DefProtest}
   A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
@@
   \((x, y)\in \R^2\) are the coordinates of the location.
-  A \emph{protest} is a set of subprotests.
+  A \emph{protest} is a set of subprotests sharing the same \(id\).
 \end{definition}
@@
     \item \((x, y)\in \R^2\) are the coordinates of the location.
-    \item A \emph{protest} is a set of subprotests.
+    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
   \end{itemize}
@@
 \end{remark}
+
+Each participant who want to be counted must submit a participation proof.
+The proof must be associated with the protest, i.e.\ contain its \(id\).
+Furthermore it must provide the time and the location of the participation.
+More formally, we define a participation proof as follows.
+
+\begin{definition}[Participation proof]
+  A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; \sigma)\), 
+  where
+  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest}.
+  \(\sigma\) is a signature vouching for participation.
+\end{definition}
+
+\begin{frame}
+  \mode<presentation>{
+  \begin{definition}[Participation proof]
+    \begin{itemize}
+      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
+          \sigma)\), where
+      \item \(id, t_s, t_e, x, y\) are as before.
+      \item \(\sigma\) is a signature vouching for participation.
+    \end{itemize}
+  \end{definition}
+
+  \pause
+  }
+\begin{question}
+  How should this one relate to the \acp{LP} and blockchain?
+\end{question}
+\end{frame}
 

### 2017-08-18 properties.tex
Cleans up contents

@@
 \mode*
-\section{Verification and privacy}
+\subsection{Verification and privacy}
+\label{VerificationAndPrivacy}
 
@@
   \item Alice must prove that the data is related to the event, that it is not 
-    reused data from previous demonstrations.
+    reused data from previous protests.
   \item Alice must provide data which can be used for the desired verification 
@@
 
-\subsection{Verification}
+%However, to complicate things further,
+%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
+%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
+%  getting text messages, phone calls and being required to attend political 
+%  rallies during work hours
+%}.
+%
+%\blockcquote{BBConVenezuelaProtestBan}{%
+%  Venezuela is banning protests that could "disturb or affect" Sunday's 
+%  controversial election for a new constituent assembly.
+%}
+%
+%\blockcquote{BBConVenezuelaProtestBan}{%
+%  Prison terms of between five and 10 years could be imposed on those 
+%  contravening the ban,
+%}
+%
+%\blockcquote{VenezuelanGovtBansProtesting}{%
+%  Venezuelans are planning to defy a government ban on public demonstrations 
+%  and risk deadly repression with marches across the country to protest against 
+%  a vote Sunday that opposition forces say will mark the end of democracy
+%}
+
+\subsubsection{Verification}
 \label{Verification}
@@
 each vote would be replaced by a proof of participation.
-
-\begin{frame}<presentation>
-  \begin{remark}
-    \begin{itemize}
-      \item For valid verification we must have immutable storage.
-      \item We need to prevent or detect malicious changes.
-    \end{itemize}
-  \end{remark}
-\end{frame}
 
@@
 
-\begin{frame}<presentation>
-  \begin{idea}[V\ref{EligibilityVerif} Eligibility]
-    \begin{itemize}
-      \item Must verify that the proof is not reused from before.
-      \item Must verify that each proof belongs to a unique individual (not 
-        only Sybil).
-    \end{itemize}
-  \end{idea}
-\end{frame}
-
 If the storage is public, then anyone can download all the proofs, verify them 
@@
 
-\subsection{Privacy}
+\subsubsection{Privacy}
 \label{Privacy}

### 2017-08-18 properties.tex
Breaks privacy out of intro (again)
Improves slides for properties

@@
 \mode*
-\subsection{Verification and privacy}
+\section{Verification and privacy}
 \label{VerificationAndPrivacy}
@@
 
-\subsubsection{Verification}
+\subsection{Verification}
 \label{Verification}
@@
 Thus \cref{IndividualVerif} is fulfilled.
-To have any verifiability, we need the storage (e.g.\ blockchain) to be 
-immutable --- i.e.\ it prevents malicious changes.
+To have any verifiability, we need the storage to be immutable --- i.e.\ it 
+prevents malicious changes.
 
@@
     \begin{itemize}
-      \item Proofs are stored publicly (e.g.\ blockchain).
+      \item Proofs are stored publicly (e.g.\ anonymous blackboard).
       \item Each participant can check that their proof is indeed included.
@@
 We can essentially divide it into the following requirements:
-\begin{frame}
 \begin{requirements}[\ref*{EligibilityVerif}.]
+  \item\label{CountOnce} Prove that no individual can be counted more than 
+    once.
+  \item\label{CreatedAfterStart} Prove that the data was created after the 
+    start of the event.
+  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
+    of the event.
+  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
+    physical location of the event.
+  \item\label{DesignatedEvent} Prove that the data is designated for the event.
+\end{requirements}
+
+\begin{frame}<presentation>
+  \begin{requirements}[V\ref*{EligibilityVerif}.]
   \item\label{CountOnce} Prove that no individual can be counted more than 
@@
 
+\begin{frame}<presentation>
+  \begin{idea}[Count once]
+    \begin{itemize}
+      \item Any two proofs by the same individual are linkable.
+      \item Includes signature made by a verified key.
+    \end{itemize}
+  \end{idea}
+
+  \pause
+
+  \begin{idea}[Designated event]
+    \begin{itemize}
+      \item Include a protest-specific identifier.
+      \item E.g.\ hash of the \enquote{manifesto}.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
 \Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
@@
 
+\begin{frame}<presentation>
+  \begin{idea}[Created after start, before end]
+    \begin{itemize}
+      \item This implies a partially ordered set.
+      \item Can be provided by blockchains.
+      \item \dots or transactional 
+        posets~\cite{BlockchainFreeCryptocurrencies}.
+    \end{itemize}
+  \end{idea}
+
+  \pause
+
+  \begin{idea}[At location]
+    \begin{itemize}
+      \item Use \iac{LP}.
+      \item Witnessed (signed) by other participants.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
 If the storage is public, then anyone can download all the proofs, verify them 
@@
       \item Proofs are stored publicly.
-      \item Anyone can download all proofs, verify them and then count them.
+      \item Anyone can download all proofs, verify eligibility and then count 
+        them.
     \end{itemize}
@@
 
-\subsubsection{Privacy}
+\subsection{Privacy}
 \label{Privacy}
@@
 
-  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness]
+  \begin{idea}[P\ref{VotePrivacy} Vote privacy]
+    \begin{itemize}
+      \item Eve shouldn't be able to link Alice's published proof back to 
+        Alice.
+      \item But if Alice publishes two proofs, those two are linkable.
+      \item We're not interested in unmasking trolls, just not count them more 
+        than once.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
+\begin{frame}<presentation>
+  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness (deniability)]
     \begin{itemize}
@@
 
-      \item But Alice should not be able to participate twice.
-
-      \item We need a signature scheme that cannot reproduce the same 
-        signature when run on the same inputs.
+      \item We need a signature scheme that cannot reproduce the same signature 
+        when run on the same inputs.
 
@@
         drop the short-term credential.
+
+      \item But Alice should still not be able to participate twice.
     \end{itemize}

### 2017-08-18 properties.tex
Moves some stuff back from design to properties

@@
 \mode*
-\section{Verification and privacy}
-\label{VerificationAndPrivacy}
+\section{The idea}
+\label{TheIdea}
 
@@
 
-If the proofs are stored publicly, then an individual can check that their 
-proof has been included there.
-Thus \cref{IndividualVerif} is fulfilled.
-To have any verifiability, we need the storage to be immutable --- i.e.\ it 
-prevents malicious changes.
-
-\begin{frame}<presentation>
-  \begin{idea}[V\ref{IndividualVerif} Individual verifiability]
-    \begin{itemize}
-      \item Proofs are stored publicly (e.g.\ anonymous blackboard).
-      \item Each participant can check that their proof is indeed included.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-
 \Cref{EligibilityVerif} would in this case mean that anyone can verify that 
@@
 
+\subsubsection{Temporal eligibility}
+
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
+  set}\footnote{%
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
+} of objects.
+If some objects in the set relate to known points in time, then the partial 
+order relates the data to the time of the event.
+This allows us to \emph{verify the data temporally}.
+
+One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
+blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}.
+For generality, we will use the terminology of 
+\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
+structure \iac{tposet}.
+
+\begin{frame}<presentation>
+\begin{idea}[Temporal eligibility]
+  \begin{itemize}
+    \item There is a mechanism that provides the properties of a poset: a 
+      blockchain.
+
+    \item There are also other structures, e.g.\ a directed 
+      graph~\cite{BlockchainFreeCryptocurrencies}.
+  \end{itemize}
+\end{idea}
+\end{frame}
+
+\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
+proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
+Then we know that they cannot have been created after the event.
+
+\begin{frame}<presentation>
+  \begin{idea}[Created before end]
+    \begin{itemize}
+      \item Submit the proof to storage.
+      \item The proof must've been created before it was included (duh!).
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
+For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
+in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
+This means that they cannot create a proof and keep it for a future protest.
+
+They can use an older value (pick one from the history of the \ac{tposet}) when 
+they create their proofs.
+This will only expand the interval of possible creation into the past.
+This will not help their cause, as anyone will recognize that the proof could 
+be created at any time in that interval.
+
+\begin{frame}<presentation>
+  \begin{idea}[Created after start]
+    \begin{itemize}
+      \item Include an unpredictable value in the proof.
+      \item This could be e.g.\ the hash of the \enquote{head} of the 
+        \ac{tposet}.
+      \item This prevents creating proofs for future protests.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
+\begin{question}
+  How hard is it to reuse old proofs?
+  Forge all signatures due to changed values?
+\end{question}
+
+\subsubsection{Spatial eligibility}
+
+\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
+us to \emph{verify the data spatially}.
+
+If we include \iac{LP}, this will tie the proof to the physical location and, 
+thus, solve \cref{SpatiallyRelated}.
+The \ac{LP} is \enquote{witnessed} (signed) by other participants.
+The \ac{LP} contains coarse coordinates of the location, which must be within 
+the protest area to be valid.
+This allows Bob the protester to move within the protest area to collect 
+witnesses (signatures).
+It also provides privacy since the location cannot be used to deanonymize Bob's 
+proof --- e.g.\ to correlate the location in his proof with captured 
+surveillance footage.
+
+\begin{frame}<presentation>
+  \begin{idea}[Spatial eligibility]
+    \begin{itemize}
+      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
+        participants.
+      \item We have a coarse location, just within protest area.
+      \item This allows protesters to move around to collect signatures.
+      \item This provides privacy for the location, e.g.\ cannot map to 
+        surveillance cameras.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+
+\begin{question}
+  How can we do \acp{LP} with 1000s of witnesses each?
+  Can we do some preprocessing?
+  Ad-hoc networks, broadcast \acp{LP}?
+\end{question}
+\begin{question}
+  Why should anyone trust these witnesses?
+  What are the assumptions?
+  Signed over a short period of time?\footnote{%
+    In a sense, if they collude they have shown support for the cause.
+    As long as they are not Sybil it should be fine?
+  }
+\end{question}
+\begin{question}
+  Trusted party for the group signatures?
+\end{question}
+\begin{question}
+  Must tie credentials to something unique: phone, phone subscription?
+  Cannot register twice, government control?
+\end{question}
+
+\begin{question}
+  What if Alice acts as a witness for Eve's agents?
+  Can that violate her privacy?
+\end{question}
+\begin{question}
+  What if Eve's agents act as witnesses?
+  Can they track their signatures to track users?
+  Can Alice detect if this happens?
+\end{question}
+
+\subsubsection{Linkability and designated protest}
+
 \Cref{CountOnce} is required to prevent Sybil attacks.
@@
 counted twice, this situation should be detectable.
+We can do this by ensuring that Alice cannot produce two valid proofs which
+are unlinkable.
+This can be done by including a signature made by a verified key.
+
+There might be the case that there is also a counter protest at the same time, 
+these would have the same spatial and temporal properties.
+To distinguish them, we also need to prove for which of these events that a 
+proof is designated (\cref{DesignatedEvent}).
+This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
+its \enquote{manifesto}.
 
@@
 
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
-us to \emph{verify the data spatially}.
-Finally, there might be the case that there is also a counter protest at the 
-same time, these would have the same spatial and temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated (\cref{DesignatedEvent}).
+\subsubsection{Individual and universal verifiability}
+
+If the proofs are stored publicly, then an individual can check that their 
+proof has been included there.
+Thus \cref{IndividualVerif} is fulfilled.
+Similarly for universal verifiability.
+If the storage is public, then anyone can download all the proofs, verify their 
+eligibility and count them.
+Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
+To have any verifiability, we need the storage to be immutable --- i.e.\ it 
+prevents malicious changes.
 
 \begin{frame}<presentation>
-  \begin{idea}[Created after start, before end]
+  \begin{idea}[Individual verifiability]
     \begin{itemize}
-      \item This implies a partially ordered set.
-      \item Can be provided by blockchains.
-      \item \dots or transactional 
-        posets~\cite{BlockchainFreeCryptocurrencies}.
+      \item Proofs are stored publicly.
+      \item Each participant can check that their proof is indeed included.
     \end{itemize}
@@
 
-  \begin{idea}[At location]
-    \begin{itemize}
-      \item Use \iac{LP}.
-      \item Witnessed (signed) by other participants.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-
-If the storage is public, then anyone can download all the proofs, verify them 
-and count them.
-Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
-
-\begin{frame}<presentation>
-  \begin{idea}[V\ref{UniversalVerif} Universal verifiability]
+  \begin{idea}[Universal verifiability]
     \begin{itemize}
@@
 
-  \begin{idea}[P\ref{VotePrivacy} Vote privacy]
+  \begin{idea}[Vote privacy]
     \begin{itemize}
@@
 \begin{frame}<presentation>
-  \begin{idea}[P\ref{ReceiptFreeness} Receipt freeness (deniability)]
+  \begin{idea}[Receipt freeness (deniability)]
     \begin{itemize}

### 2017-08-18 conclusions.tex
Adds open problems to conclusions

@@
 \section{Conclusions}
+
+\subsection<presentation>{Related work}
 
@@
       \item All current methods lack most of verifiability.
-      \item Some provide universal verifiability (V\ref{UniversalVerif}).
+      \item Some provide universal verifiability.
 
@@
 \end{frame}
+
+\subsection{Open problems}
+
+\begin{frame}
+  \begin{question}
+    \begin{itemize}
+      \item How to avoid Sybil?
+      \item Government can sign as many certificates as they like using their 
+        national ID systems.
+      \item Tie to something unique: phone, phone subscription?
+      \item Register twice?
+    \end{itemize}
+  \end{question}
+
+  \begin{question}
+    Can we piggyback on existing \acp{PKI}?
+    E.g.~\cite{Cinderella}.
+  \end{question}
+
+  \begin{question}
+    This is similar to the double-spending problem for cryptocurrencies, can 
+    we reuse any such techniques?
+    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
+  \end{question}
+\end{frame}
+
+\begin{frame}
+\begin{question}
+  How can we do \acp{LP} with 1000s of witnesses each?
+  Can we do some preprocessing?
+  Ad-hoc networks, broadcast \acp{LP}?
+\end{question}
+\end{frame}
+
+\begin{frame}
+\begin{question}
+  Why should anyone trust these witnesses?
+  What are the assumptions?
+  Signed over a short period of time?\footnote{%
+    In a sense, if they collude they have shown support for the cause.
+    As long as they are not Sybil it should be fine?
+  }
+\end{question}
+
+\pause
+
+\begin{question}
+  What if Alice acts as a witness for Eve's agents?
+  Can that violate her privacy?
+\end{question}
+
+\pause
+
+\begin{question}
+  What if Eve's agents act as witnesses?
+  Can they track their signatures to track users?
+  Can Alice detect if this happens?
+\end{question}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    Malicious nodes want to provide Alice with a view that her proof is 
+    included.
+    Everyone else is provided a view without Alice.
+    How can we ensure a consistent view for everyone?
+    (Probably similar to the solution in Joakim's thesis.)
+  \end{question}
+
+  \begin{question}
+    Under the protest conditions, we might have natural network splits.
+    Is this a useful scenario?
+  \end{question}
+
+  \begin{question}
+    How can we do blockchain branch and merge?
+    That is needed to recover from the above attack.
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    Shall we offer a platform that is run by a variety of institutions who 
+    offers to verify protests?
+    Or go strictly peer-to-peer?
+  \end{question}
+  \begin{question}
+    If strictly peer-to-peer, and only run by protesters, one can infer that 
+    they are protesters by running such a node.
+    Can this be mitigated?
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \begin{question}
+    How do we submit the proofs to storage?
+    Voting normally uses mix-nets.
+    Submit over Tor~\cite{Tor}?
+  \end{question}
+
+  \mode<presentation>{
+  \begin{remark}
+    Without anonymous submission we don't get vote privacy, thus no receipt 
+    freeness either.
+  \end{remark}
+  }
+\end{frame}

### 2017-08-21 properties.tex
Fixes warnings from Syntastic
Changes to use \mode to hide frames, fixes #10

@@
 \mode*
-\section{The idea}
+\section{The idea}%
 \label{TheIdea}
@@
 
-\subsection{Verification}
+\subsection{Verification}%
 \label{Verification}
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{requirements}[V\ref*{EligibilityVerif}.]
@@
 \end{frame}
+}
 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
 \begin{idea}[Temporal eligibility]
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Created before end]
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Created after start]
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Spatial eligibility]
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Count once]
@@
 
-  \pause
+  \pause{}
 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Individual verifiability]
@@
 \end{frame}
+}
 
-\subsection{Privacy}
+\subsection{Privacy}%
 \label{Privacy}
@@
 \end{requirements}
-\pause
-\mode<presentation>{
+\pause{}
+\mode<presentation>{%
   \begin{remark}
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{remark}
@@
 \end{frame}
+}
+
+\subsubsection{Vote privacy}
 
@@
 Alice is not counted twice.
-Receipt freeness implies that Alice enjoys deniability against Eve:
-Eve should not be able to use the published proof to tie it to Alice, even if 
-Eve has access to Alice's device (i.e.\ all her private keys).
-I.e.\ Eve should not be able to reproduce the same proof.
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{remark}
@@
 \end{frame}
+}
 
-\begin{frame}<presentation>
+\subsubsection{Receipt freeness}
+
+Receipt freeness implies that Alice enjoys deniability against Eve:
+Eve should not be able to use the published proof to tie it to Alice, even if 
+Eve has access to Alice's device (i.e.\ all her private keys).
+I.e.\ Eve should not be able to reproduce the same proof and thus verify that 
+Alice has created one of the proofs.
+
+\mode<presentation>{%
+\begin{frame}
   \begin{idea}[Receipt freeness (deniability)]
@@
 \end{frame}
+}
+
+\begin{frame}
+  \begin{question}
+    Will such a signature scheme solve both problems?
+  \end{question}
+  \begin{question}
+    Is there such a signature scheme?
+    Can we construct it?
+  \end{question}
+  \begin{question}
+    What Alice submits her proof, stores the hash of the block, removes proof 
+    and signature key?
+  \end{question}
+\end{frame}
+
+\subsubsection{Architecture}
+
+We also have an architectural problem.
+If the system is only run by volunteering activists, then Eve can simply 
+analyse network traffic to detect who is running nodes in the system.
+
+\begin{frame}
+  \begin{question}
+    Shall we offer a platform that is run by a variety of institutions who 
+    offers to verify protests?
+    Or go strictly peer-to-peer?
+  \end{question}
+  \begin{question}
+    If strictly peer-to-peer, and only run by protesters, one can infer that 
+    they are protesters by running such a node.
+    Can this be mitigated?
+  \end{question}
+\end{frame}
+
+We would still have the problem of how protesters submit their proofs to the 
+system.
+This must be done anonymously.
+
+\begin{frame}
+  \begin{question}
+    How do we submit the proofs to storage?
+    Voting normally uses mix-nets.
+    Submit over Tor~\cite{Tor}?
+  \end{question}
+
+  \begin{remark}
+    Without anonymous submission we don't get vote privacy, thus no receipt 
+    freeness either.
+  \end{remark}
+\end{frame}

### 2017-08-23 conclusions.tex
Fixes some warnings from Syntastic

@@
 
-        \pause
+        \pause{}
 
@@
   \begin{question}
-    \begin{itemize}
-      \item How to avoid Sybil?
-      \item Government can sign as many certificates as they like using their 
-        national ID systems.
-      \item Tie to something unique: phone, phone subscription?
-      \item Register twice?
-    \end{itemize}
+    How to solve Sybil, can we piggyback on existing \acp{PKI}?
+    E.g.~\cite{Cinderella}.
   \end{question}
@@
   \begin{question}
-    Can we piggyback on existing \acp{PKI}?
-    E.g.~\cite{Cinderella}.
+    Government can sign as many certificates as they like using their national 
+    ID systems.
+    How to deal with this?
+  \end{question}
+
+  \begin{question}
+    Tie to something unique: phone, phone subscription?
+    Register twice?
   \end{question}
@@
 
-\pause
+\pause{}
 
@@
 
-  \mode<presentation>{
+  \mode<presentation>{%
   \begin{remark}

### 2017-08-23 SystemModel.tex
Changes to use \mode to hide frames, fixes #10
Edits system model, intro
Moves def of protest to system model

@@
 
-\section{System model}
+\section{System model}%
 \label{SystemModel}
@@
 We assume that every participant has a device similar to a smartphone.
+(This means that we essentially provide a lower bound for the participation 
+count, since some participants might not have any smartphone.)
 It must be a portable device which can perform cryptographic operations and 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{assumption}[During protest]
@@
   \end{assumption}
-\end{frame}
 
-This means that we essentially provide a lower bound for the participation 
-count, since some participants might not have any smartphone.
-\begin{frame}
+  \pause{}
+
   \begin{remark}
@@
   \end{remark}
+\end{frame}
+}
+
+We further assume that every participant has a digital certificate signed by 
+some logically centralized certificate authority.
+E.g.\ that we can use the cryptographic keys stored in the chip of the national 
+identity card or passport.
+We need this to prevent Sybil attacks~\cite{SybilAttack}.
+\begin{frame}
 \begin{remark}
@@
 
-\subsection{Adversary model}
+\subsection{What is \protect\emph{a} protest?}%
+\label{WhatIsAProtest}
 
-We have three adversaries: Alice herself, Eve and Rusuk.
-Alice the protest organizer tries to increase the count.
-Eve the totalitarian dictator tries to decrease the count.
-Additionally, Eve tries to deanonymize the participants.
-Finally, we have Rusuk who is the head of another nation state.
-Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
-gain, thus supporting either Eve or Alice.
-Rusuk will thus also try to either increase or decrease the count.
+Protests can vary considerably.
+To be able to estimate the participation count for one, we first need to define
+what should be counted.
 
-\begin{frame}<presentation>
-  \begin{block}{Alice the activist}
+Let us start by considering some examples.
+During the demonstrations against the South Korean president in Seoul
+\blockcquote{2016DemonstrationsInSeoul}{%
+  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
+  people stay\textins{ed} for several hours, others just several minutes%
+}.
+These rallies were all in the same location in the capital and repeated every 
+weekend for the duration of a few weeks.
+The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
+in parallel in many locations.
+We also have the Venezuelan demonstrations where
+\blockcquote{2017VenezuelaProtestFrequency}{%
+  anti-government demonstrators have staged daily protests across Venezuela%
+} while
+\blockcquote{AlJazeeraOnVenezuela2017}{%
+  pro-government workers sang and danced as they staged a rival march to show 
+  their support for the president's controversial plan to rewrite the 
+  constitution%
+}.
+Judging from these examples, the minimal common part is the cause.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{example}[Seoul 2016]
     \begin{itemize}
-      \item Alice organizes the protest against Eve's regime.
-      \item Alice wants to have a high participation count.
-      \item She tries to increase it.
+      \item Rallies every weekend.
+      \item Starting midday, lasting to late night.
+      \item Some stayed for several hours, some for only minutes.
     \end{itemize}
-  \end{block}
+  \end{example}
 
-  \pause
+  \pause{}
 
-  \begin{block}{Eve the fake-news populist}
+  \begin{example}[US 2017]
     \begin{itemize}
-      \item Eve's regime is target of the protest.
-      \item She wants to have a low participation count.
-      \item She tries to decrease it.
+      \item Women's Marches in several locations.
+      \item Marched some distance.
+      \item One-time occurrence.
     \end{itemize}
-  \end{block}
+  \end{example}
 \end{frame}
+}
 
-\begin{frame}<presentation>
-  \begin{block}{Eve the totalitarian dictator}
+\mode<presentation>{%
+\begin{frame}
+  \begin{example}[Venezuela 2017]
     \begin{itemize}
-      \item Eve wants to \enquote{convince} activists to support her.
-      \item She wants to find all activists.
-      \item She tries to identify (deanonymize) participants.
+      \item Daily anti-government rallies.
+      \item Multiple locations.
+      \item Pro-government rallies too.
     \end{itemize}
-  \end{block}
+  \end{example}
 \end{frame}
+}
 
-\begin{frame}<presentation>
-  \begin{block}{Rusuk the nation state}
-    \begin{itemize}
-      \item Rusuk benefits from the situation in Evestan.
-      \item He wants the outcome to be the most beneficial.
-      \item He will try to increase or decrease the participation count.
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\subsection{System model}
-
+The organizer Alice want to count everyone who participated at any time and in 
+any of the locations~\cite{2016DemonstrationsInSeoul}.
+(Whereas police are only interested in the maximum crowd at any point in time, 
+to deploy enough personnel for crowd-control.)
 We will define a protest as an event that is uniquely identified by its cause, 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
 \begin{definition}[Protest]
@@
 \end{frame}
+}
 
-The protests described in \cref{WhatIsAProtest} can be captured using this 
-definition by splitting them up into subprotests.
+The protests described above can be captured using this definition by splitting 
+them up into subprotests.
 Each subprotest will then be captured by our definition and to find the total 
@@
 \begin{frame}
-  \mode<presentation>{
+  \mode<presentation>{%
   \begin{definition}[Participation proof]
@@
 
-  \pause
+  \pause{}
   }
@@
 \end{frame}
+
+\subsection{Adversary model}
+
+We have three adversaries: Alice herself, Eve and Rusuk.
+Alice the protest organizer tries to increase the count.
+Eve the totalitarian dictator tries to decrease the count.
+Additionally, Eve tries to deanonymize the participants.
+Finally, we have Rusuk who is the head of another nation state.
+Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
+gain, thus supporting either Eve or Alice.
+Rusuk will thus also try to either increase or decrease the count.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Alice the activist}
+    \begin{itemize}
+      \item Alice organizes the protest against Eve's regime.
+      \item Alice wants to have a high participation count.
+      \item She tries to increase it.
+    \end{itemize}
+  \end{block}
+
+  \pause{}
+
+  \begin{block}{Eve the fake-news populist}
+    \begin{itemize}
+      \item Eve's regime is target of the protest.
+      \item She wants to have a low participation count.
+      \item She tries to decrease it.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Eve the totalitarian dictator}
+    \begin{itemize}
+      \item Eve wants to \enquote{convince} activists to support her.
+      \item She wants to find all activists.
+      \item She tries to identify (deanonymize) participants.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Rusuk the nation state}
+    \begin{itemize}
+      \item Rusuk benefits from the situation in Evestan.
+      \item He wants the outcome to be the most beneficial.
+      \item He will try to increase or decrease the participation count.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
 

### 2017-08-23 intro.tex
Cleans up contents
Adds WIP on system model
Removes what's a protest from slides
Adapts intro: moves why it's a problem
Breaks privacy out of intro (again)
Changes to use \mode to hide frames, fixes #10
Edits system model, intro
Moves def of protest to system model

--- 2017-08-11 intro.tex
@@
 
-\section{Introduction}
+\section{Introduction}%
 \label{Introduction}
@@
 
-\begin{frame}<presentation>
+\subsection<presentation>{Why is it a problem?}
+
+\mode<presentation>{%
+\begin{frame}
   \begin{example}
@@
 \end{frame}
+}
 
-\subsection<presentation>{Why is it a problem?}
-
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{example}
@@
         \begin{description}
-          \item[Police] X
-          \item[Organizers] Y
+          \item[Organizers] 1\,000\,000
+          \item[Police] 260\,000
         \end{description}
 
-        \pause
+        \pause{}
 
@@
 
-\subsection{What is \protect\emph{a} protest?}
-
-Protests can vary considerably.
-To be able to estimate the participation count for one, we first need to define
-what should be counted.
-
-Let us start by considering some examples.
-During the demonstrations against the South Korean president in Seoul
-\blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
-  people stay\textins{ed} for several hours, others just several minutes%
-}.
-These rallies were all in the same location in the capital and repeated every 
-weekend for the duration of a few weeks.
-The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
-in parallel in many locations.
-We also have the Venezuelan demonstrations where
-\blockcquote{2017VenezuelaProtestFrequency}{%
-  anti-government demonstrators have staged daily protests across Venezuela%
-} while
-\blockcquote{AlJazeeraOnVenezuela2017}{%
-  pro-government workers sang and danced as they staged a rival march to show 
-  their support for the president's controversial plan to rewrite the 
-  constitution%
-}.
-Judging from these examples, the minimal common part is the cause.
-
-\begin{frame}<presentation>
-  \begin{example}[Seoul 2016]
-    \begin{itemize}
-      \item Rallies every weekend.
-      \item Starting midday, lasting to late night.
-      \item Some stayed for several hours, some for only minutes.
-    \end{itemize}
-  \end{example}
-
-  \pause
-
-  \begin{example}[US 2017]
-    \begin{itemize}
-      \item Women's Marches in several locations.
-      \item Marched some distance.
-      \item One-time occurrence.
-    \end{itemize}
-  \end{example}
-\end{frame}
-
-\begin{frame}<presentation>
-  \begin{example}[Venezuela 2017]
-    \begin{itemize}
-      \item Daily anti-government rallies.
-      \item Multiple locations.
-      \item Pro-government rallies too.
-    \end{itemize}
-  \end{example}
-\end{frame}
-
-The organizer Alice want to count everyone who participated at any time and in 
-any of the locations~\cite{2016DemonstrationsInSeoul}.
-(Whereas police are only interested in the maximum crowd at any point in time, 
-to deploy enough personnel for crowd-control.)
-We thus settle for the following definition.
-
-\begin{frame}<presentation>
-  \begin{remark}
-    \begin{itemize}
-      \item Organizers want to count anyone who participated \dots
-      \item \dots at any time
-      \item \dots in any location
-    \end{itemize}
-  \end{remark}
-\end{frame}
-
-\begin{frame}
-\begin{definition}[A protest]
-  A protest is an event identified by its cause.
-\end{definition}
-\end{frame}
-
-% Verifiability and privacy
-\mode<all>
-\input{properties.tex}
-
-\subsection{Contributions}
+\subsection<article>{Contributions}
 
@@
 participation count.
+We can only provide a verifiable participation count for non-government 
+protests:
+In any pro-government protest we cannot prevent the government from doing a 
+Sybil attack, since the government controls the identity system.
 
@@
 
-\blockcquote{HowToEstimateCrowdSize}{%
-  Crowd size is also needed for media news reports and to historically record 
-  the event%
-}
+%\blockcquote{HowToEstimateCrowdSize}{%
+%  Crowd size is also needed for media news reports and to historically record 
+%  the event%
+%}

### 2017-08-23 properties.tex
Edits properties

@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks.
-I.e.\ that one individual can provide two proofs of participation and thus be 
-counted twice, this situation should be detectable.
+\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
+individual can provide two proofs of participation and thus be counted twice.
+That situation should be detectable.
 We can do this by ensuring that Alice cannot produce two valid proofs which
@@
 This can be done by including a signature made by a verified key.
+(We will discuss the privacy aspects in \cref{Privacy}.)
 
-There might be the case that there is also a counter protest at the same time, 
-these would have the same spatial and temporal properties.
+\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
+protest at the same time and place, these would have the same spatial and 
+temporal properties.
 To distinguish them, we also need to prove for which of these events that a 
-proof is designated (\cref{DesignatedEvent}).
+proof is designated.
 This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
@@
 Alice is not counted twice.
+This is fine, since we do not want to catch any cheater, we just do not want to
+count them more than once.
 
@@
 Eve has access to Alice's device (i.e.\ all her private keys).
-I.e.\ Eve should not be able to reproduce the same proof and thus verify that 
+E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
 Alice has created one of the proofs.
@@
 If the system is only run by volunteering activists, then Eve can simply 
-analyse network traffic to detect who is running nodes in the system.
+analyse network traffic and look for people running nodes in the system.
 
@@
 
-We would still have the problem of how protesters submit their proofs to the 
+Similarly, we have the problem of how protesters submit their proofs to the 
 system.
 This must be done anonymously.
+Otherwise Eve can analyse the network traffic to find out who submitted proofs 
+to the system.
 

### 2017-08-23 security.tex
Adds stealing participation to security section

\mode*

\section{Security}

\subsection{Stealing participation}

The Eve (possibly with Rusuk's aid) wants to arrange a counter-protest in Eve's 
favour.
One way to get a higher participation count is to use the same identifier as 
Alice's protest.
Since the identifier for the protest is the hash value of the manifest, Eve 
must find a second pre-image for the hash function.

\mode<presentation>{%
\begin{frame}
  \begin{itemize}
    \item Eve wants to arrange a counter-protest.
    \item She wants to steal some of Alice's participants' proofs.
    \item To do this she must have an identifier that matches.
    \item I.e.\ she must find a second pre-image for the hash function.
  \end{itemize}
\end{frame}
}

% XXX Rephrase identifier problem as a game
\begin{proposition}
  Given \(x\) and \(H(x) = y\), the probability of finding an \(x'\) such that 
  \(H(x') = y\) is \(\frac{1}{\lambda-1}\).
\end{proposition}

### 2017-08-23 SystemModel.tex
Updates def of proofs, adds dependency tree

@@
 \begin{definition}[Participation proof]
-  A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; \sigma)\), 
-  where
-  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest}.
-  \(\sigma\) is a signature vouching for participation.
+  A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; \sigma)\), where
+  \(id, t_s, t_e\) are as in \cref{DefProtest},
+  \(lp\) is a location proof and
+  \(\sigma\) is a signature over the proof.
 \end{definition}
@@
     \begin{itemize}
-      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; x, y; 
+      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; 
           \sigma)\), where
-      \item \(id, t_s, t_e, x, y\) are as before.
-      \item \(\sigma\) is a signature vouching for participation.
+      \item \(id, t_s, t_e\) are as before,
+      \item \(lp\) is a location proof and
+      \item \(\sigma\) is a signature over the proof.
     \end{itemize}
@@
 \end{question}
+\end{frame}
+
+\begin{frame}
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \tikzset{grow'=right,level distance=5em}
+    \Tree [.Proof
+      [.{wsig} {\(x,y\)} [.{osig} [.{\(id\)} manifesto ] head ] [.tsig head'' ] ]
+      {\dots}
+      [.{wsig} {\dots} ]
+    ]
+  \end{tikzpicture}
+  \mode<article>{%
+    \caption{%
+      The proof depends on several witness signatures (wsig), each of which 
+      depends on the owner's signature (osig), which depends on the \(id\) of the
+      protest and the head of the blockchain.
+      Whenever possible, the witness signature should include proof that the 
+      witness themself has been witnesses by a trusted witness (tsig).
+    }
+  }
+\end{figure}
 \end{frame}

### 2017-08-23 properties.tex
Adds discussion of transitivity notion for witness trust

@@
 \begin{question}
-  How can we do \acp{LP} with 1000s of witnesses each?
-  Can we do some preprocessing?
-  Ad-hoc networks, broadcast \acp{LP}?
-\end{question}
-\begin{question}
   Why should anyone trust these witnesses?
@@
 \end{question}
+
+We will introduce a notion of transitivity for trust in these proofs.
+The \emph{trusted} journalist Jane the protest to report on it.
+She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
+Now Alice's \ac{LP} can be trusted as correct at that point in time.
+Alice's ability to travel is physically limited.
+Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
+the time that has passed since Jane witnessed Alice's \ac{LP}.
+We can apply this argument recursively for any other participant's \ac{LP} that 
+Alice has witnessed.
+However, this requires some assumptions:
+\begin{itemize}
+  \item It is actually Alice's signing key must have physically limited travel.
+    This can be assumed for signing keys that are embedded into hardware by 
+    some trusted person.
+  \item Alice's witness signature must depend on Jane's witness signature, to 
+    prove that Alice signed after Jane.
+\end{itemize}
+\begin{remark}
+  This probably requires high-precision timestamps, i.e.\ a trusted 
+  time-stamping server must be available during the protest.
+  Or the proofs must be submitted to the blockchain during the protest.
+\end{remark}
+
 \begin{question}
   Trusted party for the group signatures?
+\end{question}
+\begin{question}
+  How can we do \acp{LP} with 1000s of witnesses each?
+  Can we do some preprocessing?
+  Ad-hoc networks, broadcast \acp{LP}?
 \end{question}

### 2017-08-24 security.tex
Adds question about Merkle tree
s/pre-image/preimage/g, adds reuse attacks in security

@@
 
-\subsection{Stealing participation}
+\subsection{Reusing participation proofs}
+
+We consider two ways of reusing participation proofs:
+\begin{enumerate}
+  \item Alice and Bob can reuse old proofs by modifying the identifiers.
+  \item Eve can reuse proofs by creating a manifesto which yields the same 
+    identifier as Alice's protest, then try to create new nodes in the 
+    \ac{tposet} that matches the ones used in the old proofs.
+\end{enumerate}
+We will now estimate the difficulty of both types of attacks.
+
+\subsubsection{Forging new proofs}
+
+\dots
+
+\subsubsection{Finding second preimages}
 
@@
 Since the identifier for the protest is the hash value of the manifest, Eve 
-must find a second pre-image for the hash function.
+must find a second preimage for the hash function.
 
@@
     \item To do this she must have an identifier that matches.
-    \item I.e.\ she must find a second pre-image for the hash function.
+    \item I.e.\ she must find a second preimage for the hash function.
   \end{itemize}
@@
 \end{proposition}
+
+\begin{question}
+  What if we use a Merkle tree instead of only a hash, will that change the 
+  second preimage property?
+\end{question}

### 2017-08-24 properties.tex
Adds figure illustrating t-poset

@@
 converges~\cite{BlockchainFreeCryptocurrencies}.
+(See \cref{PosetGraph}.)
 For generality, we will use the terminology of 
@@
 
+\begin{figure}
+  \centering
+  \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
+    proof node/.style={rectangle,draw},
+    time node/.style={circle,draw}]
+
+    \node (prev) {\dots};
+    \node[time node] (ts) [right of=prev] {$t_s$};
+    \node[proof node] (pA) [right of=ts] {$p_A$};
+    \node[proof node] (pB) [below of=pA] {$p_B$};
+    \node[time node] (te) [right of=pA] {$t_e$};
+    \node (succ) [right of=te] {\dots};
+
+    \path
+    (prev) edge node [right] {} (ts)
+    (ts) edge node {} (pA)
+    (pA) edge node {} (te)
+    (ts) edge node {} (pB)
+    (pB) edge node {} (te)
+    (te) edge node {} (succ);
+
+  \end{tikzpicture}
+  \mode<article>{%
+    \caption{%
+      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
+      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
+      are incomparable.
+    }\label{PosetGraph}
+  }
+\end{figure}
+
 \Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
 proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
+In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
+protest, then the relation will guarantee that \(p_A, p_B\) were created before 
+the end of the protest.
 Then we know that they cannot have been created after the event.
@@
       \item The proof must've been created before it was included (duh!).
+      \item If included before \(t_e\), then it was created before \(t_e\).
     \end{itemize}
@@
 For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
-in their proofs, e.g.\ the \enquote{head} of the \ac{tposet}.
-This means that they cannot create a proof and keep it for a future protest.
+in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
+This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
+has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
+it for a future protest.
 
@@
 This will not help their cause, as anyone will recognize that the proof could 
-be created at any time in that interval.
+be created at any time in that interval, i.e.\ possibly before the protest.
 
@@
       \item This could be e.g.\ the hash of the \enquote{head} of the 
-        \ac{tposet}.
+        \ac{tposet}, (\(t_s\) in the figure).
       \item This prevents creating proofs for future protests.

### 2017-08-24 SystemModel.tex
Adds question about Merkle tree
Replaces blockchain with t-poset

@@
 \begin{question}
-  How should this one relate to the \acp{LP} and blockchain?
+  How should this one relate to the \acp{LP} and \ac{tposet}?
 \end{question}
@@
       depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the blockchain.
+      protest and the head of the \ac{tposet}.
       Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnesses by a trusted witness (tsig).
+      witness themself has been witnessed by a trusted witness (tsig).
     }
@@
 }
+
+More formally \dots
 

### 2017-08-25 RelatedWork.tex
Changes to use \mode to hide frames, fixes #10
Edits out authenticity from related work section

@@
 \mode*
-\section{Related work}
+\section{Related work}%
 \label{RelatedWork}
@@
 
-When it comes to authenticity, we have to rely on the photos.
+When it comes to spatial and temporal verifiability, we have to rely on the 
+photos.
 We can try to determine from the photos themselves when and where the they were 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[Jacob's method]
@@
 then it inherits the verifiability properties of the previous method.
-The same for authenticity.
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[CrowdSize app\footfullcite{CrowdSize}]
@@
 cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
-Furthermore, it is still difficult capture the entire location on surveillance 
-video.
-The authenticity properties are reduced to those of the video, which should be 
-similar as in our discussion about the authenticity of photos.
+In theory, this class of methods will provide an upper bound, whereas our 
+method provides a lower bound.
+However, it is still difficult capture the entire location on surveillance 
+video, which diminishes the argument for an upper bound.
+The spatial and temporal verifiability properties are reduced to those of the 
+video, which should be similar as in our discussion about the verifiability of 
+photos above.
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[Computer vision]
@@
 }
-This method cannot provide any verifiability nor authenticity, we must trust 
-the company to do the measurements correctly and to be honest about when and 
-where they did them.
+This method cannot provide any verifiability, we must trust the company to do 
+the measurements correctly and to be honest about when and where they did them.
 As MAC address randomization get wider adoption this will be even more 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[Wi-Fi tracking]
@@
 turn the device off.
-Finally, there will be limited verifiability and authenticity, as the data 
-recorder must be trusted to record all data and do it in the relation to the 
-event.
+Finally, there will be limited verifiability, as the data recorder must be 
+trusted to record all data and do it in the relation to the event.
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[IMSI catchers]
@@
 a crowd of 20 people.
-In either case, this type of data cannot provide verifiability nor 
-authenticity.
+In either case, this type of data cannot provide verifiability.
 
@@
 count at the snapshot of the photos.
-However, there is no verification nor authenticity, i.e.\ the service must be 
-trusted to behave honestly, but even then, nothing prevents Bob from submitting 
-twice (violating eligibility verification, \cref{EligibilityVerif}).
+However, there is no verification, i.e.\ the service must be trusted to behave 
+honestly, but even then, nothing prevents Bob from submitting twice (violating 
+eligibility verification, \cref{EligibilityVerif}).
 Another downside is that the service also requires an Internet connection 
@@
 
-\begin{frame}<presentation>
+\mode<presentation>{%
+\begin{frame}
   \begin{solution}[CrowdCount\footfullcite{CrowdCount}]
@@
 \end{frame}
+}

### 2017-08-25 SystemModel.tex
Moves dependency tree figure

@@
 
-\begin{frame}
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \tikzset{grow'=right,level distance=5em}
-    \Tree [.Proof
-      [.{wsig} {\(x,y\)} [.{osig} [.{\(id\)} manifesto ] head ] [.tsig head'' ] ]
-      {\dots}
-      [.{wsig} {\dots} ]
-    ]
-  \end{tikzpicture}
-  \mode<article>{%
-    \caption{%
-      The proof depends on several witness signatures (wsig), each of which 
-      depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
-      Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnessed by a trusted witness (tsig).
-    }
-  }
-\end{figure}
-\end{frame}
-
 \subsection{Adversary model}

### 2017-08-25 properties.tex
Replaces blockchain with t-poset
Adds t-poset figure to slides
Moves dependency tree figure

@@
 
+\begin{frame}
 \begin{figure}
@@
 \end{figure}
+\end{frame}
 
@@
   time-stamping server must be available during the protest.
-  Or the proofs must be submitted to the blockchain during the protest.
+  Or the proofs must be submitted to the \ac{tposet} during the protest.
 \end{remark}
@@
 
+\begin{frame}
+\begin{figure}
+  \centering
+  \begin{tikzpicture}
+    \tikzset{grow'=right,level distance=5em}
+    \Tree [.Proof
+      [.{wsig} {\(x,y\)} [.{\mode<presentation>{\only<1>{\color{red}}} osig} 
+      [.{\mode<presentation>{\only<2>{\color{red}}}\(id\)} manifesto ] head ] 
+      [.tsig head$'$ ] ]
+      {\dots}
+      [.{wsig} {\dots} ]
+    ]
+  \end{tikzpicture}
+  \mode<article>{%
+    \caption{%
+      The proof depends on several witness signatures (wsig), each of which 
+      depends on the owner's signature (osig), which depends on the \(id\) of the
+      protest and the head of the \ac{tposet}.
+      Whenever possible, the witness signature should include proof that the 
+      witness themself has been witnessed by a trusted witness (tsig).
+    }
+  }
+\end{figure}
+
 \mode<presentation>{%
-\begin{frame}
+  \only<1>{%
     \begin{idea}[Count once]
@@
     \end{idea}
+  }
 
-  \pause{}
-
+  \only<2>{%
     \begin{idea}[Designated event]
@@
     \end{idea}
+  }
+}
 \end{frame}
-}
 

### 2017-08-25 properties.tex
Minor edits
Merges ideas with figure slide, adds transitive trust

@@
     reused data from previous protests.
-  \item Alice must provide data which can be used for the desired verification 
-    of the event.
+  \item Alice must provide data which can be used for the desired verification.
   \item Alice must also consider the privacy of the participating individuals.
@@
 \end{figure}
+
+\mode<presentation>{%
+  \only<1>{%
+    \begin{idea}[Created before end]
+      \begin{itemize}
+        \item Submit the proof to storage.
+        \item The proof must've been created before it was included (duh!).
+        \item If included before \(t_e\), then it was created before \(t_e\).
+      \end{itemize}
+    \end{idea}
+  }
+  \only<2>{%
+    \begin{idea}[Created after start]
+      \begin{itemize}
+        \item Include an unpredictable value in the proof.
+        \item This could be e.g.\ the hash of the \enquote{head} of the 
+          \ac{tposet}, (\(t_s\) in the figure).
+        \item This prevents creating proofs for future protests.
+      \end{itemize}
+    \end{idea}
+  }
+}
 \end{frame}
@@
 Then we know that they cannot have been created after the event.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Created before end]
-    \begin{itemize}
-      \item Submit the proof to storage.
-      \item The proof must've been created before it was included (duh!).
-      \item If included before \(t_e\), then it was created before \(t_e\).
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
 
@@
 be created at any time in that interval, i.e.\ possibly before the protest.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Created after start]
-    \begin{itemize}
-      \item Include an unpredictable value in the proof.
-      \item This could be e.g.\ the hash of the \enquote{head} of the 
-        \ac{tposet}, (\(t_s\) in the figure).
-      \item This prevents creating proofs for future protests.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
 
@@
 
+\mode<presentation>{%
+\begin{frame}
+  \begin{idea}[Transitive trust]
+    \begin{itemize}
+      \item Trusted journalist Jane attends to report.
+      \item She witnesses Alice's and Bob's proofs.
+
+        \pause{}
+
+      \item Physical transportation is limited.
+      \item Accuracy of Alice's witnessing is proportional to time from Jane's 
+        witnessing.
+    \end{itemize}
+  \end{idea}
+
+  \pause{}
+
+  \begin{remark}
+    \begin{itemize}
+      \item Alice's signature key must have the physical travel properties, 
+        embedded in hardware.
+      \item Alice's witness signature must depend on Jane's.
+      \item High-precision relation to time?
+    \end{itemize}
+  \end{remark}
+\end{frame}
+}
+
 We will introduce a notion of transitivity for trust in these proofs.
-The \emph{trusted} journalist Jane the protest to report on it.
+The \emph{trusted} journalist Jane attends the protest to report on it.
 She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.

### 2017-08-25 properties.tex
Edits privacy section

@@
 
+\begin{frame}
+  \begin{remark}
+    \begin{itemize}
+      \item Unique ring signatures~\cite{UniqueRingSignatures} has this 
+        property: two signatures are linked with high probability.
+      \item We need keys strongly tied to identities to prevent Sybil.
+    \end{itemize}
+  \end{remark}
+
+  \begin{question}
+    Can we link a verified key to a unique ring signature key?
+  \end{question}
+\end{frame}
+
 \subsubsection{Receipt freeness}
@@
   \begin{question}
-    Will such a signature scheme solve both problems?
-  \end{question}
-  \begin{question}
     Is there such a signature scheme?
@@
   \end{question}
-  \begin{question}
-    What Alice submits her proof, stores the hash of the block, removes proof 
-    and signature key?
-  \end{question}
+
+  \pause{}
+
+  \begin{remark}
+    \begin{itemize}
+      \item Alice submits her proof.
+      \item She stores the hash of the head of the \ac{tposet}.
+      \item She removes the proof and signature key.
+    \end{itemize}
+  \end{remark}
 \end{frame}
@@
 
-\begin{frame}
 \begin{question}
@@
 \end{question}
+
 \begin{question}
@@
 \end{question}
-\end{frame}
 

### 2017-08-25 security.tex
Fixes typo
adds section on spoofing locations, just stub
Adds stuff to security section

@@
 \section{Security}
+
+\subsection{Forging new proofs}
+
+It follows from the digital signatures used that proofs are difficult to forge.
 
@@
 
-\subsubsection{Forging new proofs}
-
-\dots
-
 \subsubsection{Finding second preimages}
 
-The Eve (possibly with Rusuk's aid) wants to arrange a counter-protest in Eve's 
-favour.
+Eve (possibly with Rusuk's aid) wants to arrange a counter-protest.
 One way to get a higher participation count is to use the same identifier as 
@@
 \end{question}
+
+Alice wants to arrange another protest against Eve.
+Her manifesto can remain the same, thus the protest identifier remains the 
+same.
+She wants to reuse some old proofs.
+The head value that are included in the proofs extend them too far back into 
+time.
+The digital signatures prevents her from changing them.
+So an alternative is to create nodes in the \ac{tposet} which has the same 
+hashes.
+
+\subsection{Spoofing locations}
+
+\subsubsection{Trust propagation for witnesses}
+
+\dots
+
+\subsection{Individual verifiability}
+
+Eve and Rusuk has an incentive to lower the confidence in the result.
+One way they can do this is to say that the result does not contain all 
+participation proofs.
+Statements such as this should be proved: provide a valid but missing proof.

### 2017-08-27 conclusions.tex
Edits conclusion

--- 2017-08-11 conclusions.tex
@@
 \begin{frame}<presentation>
+  \begin{block}{Verifiability}
+    \begin{itemize}
+      \item All current methods lack most of verifiability.
+      \item Some can provide universal verifiability.
+    \end{itemize}
+  \end{block}
+
+  \pause{}
+
+  \begin{block}{Correctness}
+    \begin{itemize}
+      \item Most cannot estimate the correct participation count.
+      \item Some can (theoretically) give an upper bound.
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\subsection{Open problems}
+
+\begin{frame}
+  \frametitle{Sybil}
+  \begin{question}
+    How to solve Sybil, can we piggyback on existing \acp{PKI}?
+    E.g.\ through~\cite{Cinderella}.
+  \end{question}
+
+  \begin{question}
+    Can we otherwise bind identifiable keys to unique ring signature keys?
+  \end{question}
+
+  \begin{question}
+    This is similar to the double-spending problem for cryptocurrencies, can 
+    we reuse any such techniques?
+    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Distributed systems}
+  \begin{question}
+    \begin{itemize}
+      \item Malicious nodes want to provide Alice with a view that her proof is 
+        included.
+      \item Everyone else is provided a view without Alice.
+      \item How can we ensure a consistent view for everyone?
+    \end{itemize}
+  \end{question}
+
+  \begin{question}
+    How can we do blockchain branch and merge?
+    That is needed to recover from the above attack.
+  \end{question}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Anonymous communication}
+  \begin{question}
+    How do we submit the proofs to storage?
+  \end{question}
+
+  \mode<presentation>{%
     \begin{remark}
       \begin{itemize}
-      \item All current methods lack most of verifiability.
-      \item Some provide universal verifiability (V\ref{UniversalVerif}).
-
-        \pause
-
-      \item Most cannot estimate the correct participation count.
+        \item Without anonymous submission we don't get proof privacy, thus no 
+          receipt freeness either.
+        \item Voting normally uses mix-nets.
+        \item Submit over Tor~\cite{Tor}?
       \end{itemize}
     \end{remark}
+  }
 \end{frame}

### 2017-08-27 fig-tposet.tex
Breaks out figure t-poset to own file

--- 2017-08-25 properties.tex
@@
-\mode*
-\section{The idea}%
-\label{TheIdea}
-
-Alice is an activist who organizes a demonstration for some cause.
-Her main goal after the protest is to provide verifiable data.
-There are several problems:
-\begin{frame}
-\begin{itemize}
-  \item Alice must prove that the data is related to the event, that it is not 
-    reused data from previous protests.
-  \item Alice must provide data which can be used for the desired verification 
-    of the event.
-  \item Alice must also consider the privacy of the participating individuals.
-\end{itemize}
-\end{frame}
-Since many of the current techniques are based on photos, we will give an 
-example of Alice's problems in that setting.
-How can she ensure that photos from a demonstration are authentic?
-We can probably recognize the location that the photo is portraying, however, 
-this might just as well be a reconstruction or entirely computer generated.
-We cannot trust the meta-data of the photo, such as time-stamps of the file, 
-because these can easily be manipulated.
-So the only thing we can say for sure is that the photo was taken at the latest 
-at the time of publication.
-Now, if we cannot trust these photos, how can we determine the number of 
-participants of a demonstration?
-Furthermore, how can Alice protect the privacy of those in the photos?
-
-%However, to complicate things further,
-%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
-%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
-%  getting text messages, phone calls and being required to attend political 
-%  rallies during work hours
-%}.
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Venezuela is banning protests that could "disturb or affect" Sunday's 
-%  controversial election for a new constituent assembly.
-%}
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Prison terms of between five and 10 years could be imposed on those 
-%  contravening the ban,
-%}
-%
-%\blockcquote{VenezuelanGovtBansProtesting}{%
-%  Venezuelans are planning to defy a government ban on public demonstrations 
-%  and risk deadly repression with marches across the country to protest against 
-%  a vote Sunday that opposition forces say will mark the end of democracy
-%}
-
-\subsection{Verification}%
-\label{Verification}
-
-We have an adversarial setting between Alice the activist and Eve the evil 
-regime: Alice wants to show large support against Eve, Eve wants to show little
-support for Alice.
-In this case we have two options:
-either we trust Alice or Eve, or we must verify their claims.
-We aim for verifiable claims.
-
-In general, protesting is very similar to voting: both are many individuals 
-expressing their opinion.
-These opinions can be sensitive, hence we desire to have similar properties of 
-verification and privacy for participation in a protest as there is for voting.
-In the context of (electronic) voting protocols, there are three requirements 
-for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{frame}
-\begin{requirements}[V]
-\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
-  cast is legitimate.
-\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-  result is according to the cast votes.
-\item\label{IndividualVerif} Individual verifiability: every voter can verify 
-  that their vote is included in the result.
-\end{requirements}
-\end{frame}
-We can translate these to the case of participation in a demonstration, then 
-each vote would be replaced by a proof of participation.
-
-\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
-each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
-attacks.
-They must also be able to verify that each proof is indeed related to the 
-event.
-We must associate the proof to the event both spatially (the correct location) 
-and temporally (it is related to the time-interval of the event).
-We can essentially divide it into the following requirements:
-\begin{requirements}[\ref*{EligibilityVerif}.]
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
-  \item\label{CreatedAfterStart} Prove that the data was created after the 
-    start of the event.
-  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
-    of the event.
-  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
-    physical location of the event.
-  \item\label{DesignatedEvent} Prove that the data is designated for the event.
-\end{requirements}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{requirements}[V\ref*{EligibilityVerif}.]
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
-  \item\label{CreatedAfterStart} Prove that the data was created after the 
-    start of the event.
-  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
-    of the event.
-  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
-    physical location of the event.
-  \item\label{DesignatedEvent} Prove that the data is designated for the event.
-\end{requirements}
-\end{frame}
-}
-
-\subsubsection{Temporal eligibility}
-
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
-blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}.
-(See \cref{PosetGraph}.)
-For generality, we will use the terminology of 
-\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
-structure \iac{tposet}.
-
-\mode<presentation>{%
-\begin{frame}
-\begin{idea}[Temporal eligibility]
-  \begin{itemize}
-    \item There is a mechanism that provides the properties of a poset: a 
-      blockchain.
-
-    \item There are also other structures, e.g.\ a directed 
-      graph~\cite{BlockchainFreeCryptocurrencies}.
-  \end{itemize}
-\end{idea}
-\end{frame}
-}
-
-\begin{frame}
-\begin{figure}
-  \centering
 \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
@@
 \end{tikzpicture}
-  \mode<article>{%
-    \caption{%
-      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
-      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
-      are incomparable.
-    }\label{PosetGraph}
-  }
-\end{figure}
-\end{frame}
-
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
-proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
-In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
-protest, then the relation will guarantee that \(p_A, p_B\) were created before 
-the end of the protest.
-Then we know that they cannot have been created after the event.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Created before end]
-    \begin{itemize}
-      \item Submit the proof to storage.
-      \item The proof must've been created before it was included (duh!).
-      \item If included before \(t_e\), then it was created before \(t_e\).
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
-in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
-This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
-has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
-it for a future protest.
-
-They can use an older value (pick one from the history of the \ac{tposet}) when 
-they create their proofs.
-This will only expand the interval of possible creation into the past.
-This will not help their cause, as anyone will recognize that the proof could 
-be created at any time in that interval, i.e.\ possibly before the protest.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Created after start]
-    \begin{itemize}
-      \item Include an unpredictable value in the proof.
-      \item This could be e.g.\ the hash of the \enquote{head} of the 
-        \ac{tposet}, (\(t_s\) in the figure).
-      \item This prevents creating proofs for future protests.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\begin{question}
-  How hard is it to reuse old proofs?
-  Forge all signatures due to changed values?
-\end{question}
-
-\subsubsection{Spatial eligibility}
-
-\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
-us to \emph{verify the data spatially}.
-
-If we include \iac{LP}, this will tie the proof to the physical location and, 
-thus, solve \cref{SpatiallyRelated}.
-The \ac{LP} is \enquote{witnessed} (signed) by other participants.
-The \ac{LP} contains coarse coordinates of the location, which must be within 
-the protest area to be valid.
-This allows Bob the protester to move within the protest area to collect 
-witnesses (signatures).
-It also provides privacy since the location cannot be used to deanonymize Bob's 
-proof --- e.g.\ to correlate the location in his proof with captured 
-surveillance footage.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Spatial eligibility]
-    \begin{itemize}
-      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
-        participants.
-      \item We have a coarse location, just within protest area.
-      \item This allows protesters to move around to collect signatures.
-      \item This provides privacy for the location, e.g.\ cannot map to 
-        surveillance cameras.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\begin{question}
-  Why should anyone trust these witnesses?
-  What are the assumptions?
-  Signed over a short period of time?\footnote{%
-    In a sense, if they collude they have shown support for the cause.
-    As long as they are not Sybil it should be fine?
-  }
-\end{question}
-
-We will introduce a notion of transitivity for trust in these proofs.
-The \emph{trusted} journalist Jane the protest to report on it.
-She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
-Now Alice's \ac{LP} can be trusted as correct at that point in time.
-Alice's ability to travel is physically limited.
-Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
-the time that has passed since Jane witnessed Alice's \ac{LP}.
-We can apply this argument recursively for any other participant's \ac{LP} that 
-Alice has witnessed.
-However, this requires some assumptions:
-\begin{itemize}
-  \item It is actually Alice's signing key must have physically limited travel.
-    This can be assumed for signing keys that are embedded into hardware by 
-    some trusted person.
-  \item Alice's witness signature must depend on Jane's witness signature, to 
-    prove that Alice signed after Jane.
-\end{itemize}
-\begin{remark}
-  This probably requires high-precision timestamps, i.e.\ a trusted 
-  time-stamping server must be available during the protest.
-  Or the proofs must be submitted to the \ac{tposet} during the protest.
-\end{remark}
-
-\begin{question}
-  Trusted party for the group signatures?
-\end{question}
-\begin{question}
-  How can we do \acp{LP} with 1000s of witnesses each?
-  Can we do some preprocessing?
-  Ad-hoc networks, broadcast \acp{LP}?
-\end{question}
-\begin{question}
-  Must tie credentials to something unique: phone, phone subscription?
-  Cannot register twice, government control?
-\end{question}
-
-\begin{question}
-  What if Alice acts as a witness for Eve's agents?
-  Can that violate her privacy?
-\end{question}
-\begin{question}
-  What if Eve's agents act as witnesses?
-  Can they track their signatures to track users?
-  Can Alice detect if this happens?
-\end{question}
-
-\subsubsection{Linkability and designated protest}
-
-\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
-individual can provide two proofs of participation and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
-This can be done by including a signature made by a verified key.
-(We will discuss the privacy aspects in \cref{Privacy}.)
-
-\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
-protest at the same time and place, these would have the same spatial and 
-temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
-its \enquote{manifesto}.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \begin{tikzpicture}
-    \tikzset{grow'=right,level distance=5em}
-    \Tree [.Proof
-      [.{wsig} {\(x,y\)} [.{\mode<presentation>{\only<1>{\color{red}}} osig} 
-      [.{\mode<presentation>{\only<2>{\color{red}}}\(id\)} manifesto ] head ] 
-      [.tsig head$'$ ] ]
-      {\dots}
-      [.{wsig} {\dots} ]
-    ]
-  \end{tikzpicture}
-  \mode<article>{%
-    \caption{%
-      The proof depends on several witness signatures (wsig), each of which 
-      depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
-      Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnessed by a trusted witness (tsig).
-    }
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1>{%
-    \begin{idea}[Count once]
-      \begin{itemize}
-        \item Any two proofs by the same individual are linkable.
-        \item Includes signature made by a verified key.
-      \end{itemize}
-    \end{idea}
-  }
-
-  \only<2>{%
-    \begin{idea}[Designated event]
-      \begin{itemize}
-        \item Include a protest-specific identifier.
-        \item E.g.\ hash of the \enquote{manifesto}.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
-
-\subsubsection{Individual and universal verifiability}
-
-If the proofs are stored publicly, then an individual can check that their 
-proof has been included there.
-Thus \cref{IndividualVerif} is fulfilled.
-Similarly for universal verifiability.
-If the storage is public, then anyone can download all the proofs, verify their 
-eligibility and count them.
-Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
-To have any verifiability, we need the storage to be immutable --- i.e.\ it 
-prevents malicious changes.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Individual verifiability]
-    \begin{itemize}
-      \item Proofs are stored publicly.
-      \item Each participant can check that their proof is indeed included.
-    \end{itemize}
-  \end{idea}
-
-  \pause{}
-
-  \begin{idea}[Universal verifiability]
-    \begin{itemize}
-      \item Proofs are stored publicly.
-      \item Anyone can download all proofs, verify eligibility and then count 
-        them.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\subsection{Privacy}%
-\label{Privacy}
-
-We also need privacy in addition to the verification requirements.
-As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
-and Bob by the data.
-So as long as Alice and Bob can conceal their identities at the demonstration 
-and escape without arrest, their support is recorded in the data while their 
-privacy is not violated.
-(Following this line of thinking, it can actually be beneficial for the privacy 
-of the demonstrators to mix with the participants of any counter-demonstrations 
---- since the counts will still be correct.)
-
-In voting, we have the following requirements:
-\begin{frame}
-\begin{requirements}[P]
-\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
-  individual vote.
-\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
-  provide any data that can be used as a proof of how the voter voted.
-\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
-  with a coercer to prove the vote was cast in any particular way.
-\end{requirements}
-\pause{}
-\mode<presentation>{%
-  \begin{remark}
-    P\ref{CoercionResistance} \(\implies\)
-    P\ref{ReceiptFreeness} \(\implies\)
-    P\ref{VotePrivacy}
-  \end{remark}
-}
-\end{frame}
-\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
-\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
-\cref{VotePrivacy}.
-\Cref{CoercionResistance} is probably not possible to achieve for protests:
-e.g.\ Eve can simply physically bring Alice to a protest against her will.
-This leaves us with \cref{ReceiptFreeness,VotePrivacy}.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item Coercion resistance is difficult to achieve for voting.
-      \item It doesn't make much sense for protests.
-      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
-        participate in.
-      \item That leaves us with receipt freeness and vote privacy.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
-\subsubsection{Vote privacy}
-
-A demonstration is very different from voting in one sense: at a demonstration, 
-Alice must be physically present and that very presence shows her support for 
-the cause.
-In voting, on the other hand, everyone is present and Alice has multiple 
-options which are not revealed by her mere presence.
-% XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof of participation, the proof must be unlinkable 
-to Alice, yet, if Alice submits another proof, those two proofs must be 
-linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
-Alice is not counted twice.
-This is fine, since we do not want to catch any cheater, we just do not want to
-count them more than once.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item Voting: different alternatives when participating.
-      \item Protesting: participation implies the alternative.
-    \end{itemize}
-  \end{remark}
-
-  \pause{}
-
-  \begin{idea}[Vote privacy]
-    \begin{itemize}
-      \item Eve shouldn't be able to link Alice's published proof back to 
-        Alice.
-      \item But if Alice publishes two proofs, those two are linkable.
-      \item We're not interested in unmasking trolls, just not count them more 
-        than once.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\subsubsection{Receipt freeness}
-
-Receipt freeness implies that Alice enjoys deniability against Eve:
-Eve should not be able to use the published proof to tie it to Alice, even if 
-Eve has access to Alice's device (i.e.\ all her private keys).
-E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
-Alice has created one of the proofs.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Receipt freeness (deniability)]
-    \begin{itemize}
-      \item If Eve compromises Alice's device, she should not be able to use 
-        it to verify that she participated.
-
-      \item We need a signature scheme that cannot reproduce the same signature 
-        when run on the same inputs.
-
-      \item E.g.\ a short-term and a long-term credential, then Alice can 
-        drop the short-term credential.
-
-      \item But Alice should still not be able to participate twice.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\begin{frame}
-  \begin{question}
-    Will such a signature scheme solve both problems?
-  \end{question}
-  \begin{question}
-    Is there such a signature scheme?
-    Can we construct it?
-  \end{question}
-  \begin{question}
-    What Alice submits her proof, stores the hash of the block, removes proof 
-    and signature key?
-  \end{question}
-\end{frame}
-
-\subsubsection{Architecture}
-
-We also have an architectural problem.
-If the system is only run by volunteering activists, then Eve can simply 
-analyse network traffic and look for people running nodes in the system.
-
-\begin{frame}
-  \begin{question}
-    Shall we offer a platform that is run by a variety of institutions who 
-    offers to verify protests?
-    Or go strictly peer-to-peer?
-  \end{question}
-  \begin{question}
-    If strictly peer-to-peer, and only run by protesters, one can infer that 
-    they are protesters by running such a node.
-    Can this be mitigated?
-  \end{question}
-\end{frame}
-
-Similarly, we have the problem of how protesters submit their proofs to the 
-system.
-This must be done anonymously.
-Otherwise Eve can analyse the network traffic to find out who submitted proofs 
-to the system.
-
-\begin{frame}
-  \begin{question}
-    How do we submit the proofs to storage?
-    Voting normally uses mix-nets.
-    Submit over Tor~\cite{Tor}?
-  \end{question}
-
-  \begin{remark}
-    Without anonymous submission we don't get vote privacy, thus no receipt 
-    freeness either.
-  \end{remark}
-\end{frame}

### 2017-08-27 properties.tex
Minor edits based on Sébastien's comments
Breaks out figure t-poset to own file

@@
   \centering
-  \begin{tikzpicture}[->,auto,node distance=1.5cm,thick,
-    proof node/.style={rectangle,draw},
-    time node/.style={circle,draw}]
-
-    \node (prev) {\dots};
-    \node[time node] (ts) [right of=prev] {$t_s$};
-    \node[proof node] (pA) [right of=ts] {$p_A$};
-    \node[proof node] (pB) [below of=pA] {$p_B$};
-    \node[time node] (te) [right of=pA] {$t_e$};
-    \node (succ) [right of=te] {\dots};
-
-    \path
-    (prev) edge node [right] {} (ts)
-    (ts) edge node {} (pA)
-    (pA) edge node {} (te)
-    (ts) edge node {} (pB)
-    (pB) edge node {} (te)
-    (te) edge node {} (succ);
-
-  \end{tikzpicture}
+  \input{fig-tposet.tex}
   \mode<article>{%
@@
 
-\subsubsection{Vote privacy}
+\subsubsection{Participation-proof privacy}
 
@@
 
-  \begin{idea}[Vote privacy]
+  \begin{idea}[Proof privacy]
     \begin{itemize}
@@
   \begin{remark}
-    Without anonymous submission we don't get vote privacy, thus no receipt 
+    Without anonymous submission we don't get proof privacy, thus no receipt 
     freeness either.

### 2017-08-27 properties.tex
Edits properties, shortens text, improves temporal with fig

@@
 There are several problems:
-\begin{frame}
 \begin{itemize}
@@
 \end{itemize}
+
+\begin{frame}<presentation>
+  \begin{itemize}
+    \item Alice must prove that the data is related to the event.
+    \item Alice must provide data with verifiable properties.
+    \item Alice must consider the privacy of the participants.
+  \end{itemize}
 \end{frame}
+
 Since many of the current techniques are based on photos, we will give an 
@@
 
-\mode<presentation>{%
-\begin{frame}
-\begin{idea}[Temporal eligibility]
-  \begin{itemize}
-    \item There is a mechanism that provides the properties of a poset: a 
-      blockchain.
-
-    \item There are also other structures, e.g.\ a directed 
-      graph~\cite{BlockchainFreeCryptocurrencies}.
-  \end{itemize}
-\end{idea}
-\end{frame}
-}
-
 \begin{frame}
@@
   \centering
-  \input{fig-tposet.tex}
+  \input{fig/tposet.tex}
   \mode<article>{%
@@
   \only<1>{%
+    \begin{idea}[Temporal eligibility]
+      \begin{itemize}
+        \item We need a partially ordered set (poset).
+        \item There is a mechanism that provides this property: a blockchain.
+        \item There are also other structures, e.g.\ a directed 
+          graph~\cite{BlockchainFreeCryptocurrencies}.
+      \end{itemize}
+    \end{idea}
+  }
+  \only<2>{%
     \begin{idea}[Created before end]
@@
   }
-  \only<2>{%
+  \only<3>{%
     \begin{idea}[Created after start]

### 2017-08-27 conclusions.tex
Edits conclusions

@@
   \begin{question}
-    This is similar to the double-spending problem for cryptocurrencies, can 
-    we reuse any such techniques?
-    (Not like in Bitcoin, but more like ecash~\cite{ecash} and the like.)
-  \end{question}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Distributed systems}
-  \begin{question}
-    \begin{itemize}
-      \item Malicious nodes want to provide Alice with a view that her proof is 
-        included.
-      \item Everyone else is provided a view without Alice.
-      \item How can we ensure a consistent view for everyone?
-    \end{itemize}
-  \end{question}
-
-  \begin{question}
-    How can we do blockchain branch and merge?
-    That is needed to recover from the above attack.
+    Can we achieve receipt freeness and protect from Sybil?
   \end{question}
@@
 \end{frame}
+
+\begin{frame}
+  \frametitle{Blockchains, distributed systems}
+  \begin{question}
+    \begin{itemize}
+      \item Malicious nodes want to provide Alice with a view that her proof is 
+        included.
+      \item Everyone else is provided a view without Alice.
+      \item How can we ensure a consistent view for everyone?
+    \end{itemize}
+  \end{question}
+
+  \begin{question}
+    Can we do blockchain branch and merge?
+  \end{question}
+\end{frame}

### 2017-08-27 fig/tposet.tex
Fixes arrows in poset graph
The arrows should be the other direction, since it links backwards, not
forwards.

--- 2017-08-27 fig-tposet.tex
@@
   \path
-  (prev) edge node [right] {} (ts)
-  (ts) edge node {} (pA)
-  (pA) edge node {} (te)
-  (ts) edge node {} (pB)
-  (pB) edge node {} (te)
-  (te) edge node {} (succ);
+  (succ) edge node {} (te)
+  (te) edge node {} (pB)
+  (pB) edge node {} (ts)
+  (te) edge node {} (pA)
+  (pA) edge node {} (ts)
+  (ts) edge node {} (prev);
 

### 2017-08-27 properties.tex
Improves slides by successively constructing fig

@@
 \begin{frame}
+  \begin{figure}
+    \centering
+    \begin{tikzpicture}
+      \tikzset{grow'=right,level distance=5em}
+      \Tree [.Proof
+      [.{wsig} {\(x,y\)} {$t_s$} ]
+      {\dots}
+      [.{wsig} {\dots} ]
+      ]
+    \end{tikzpicture}
+  \end{figure}
+
   \begin{idea}[Spatial eligibility]
@@
         participants.
-      \item We have a coarse location, just within protest area.
+      \item We have a coarse location, just within the protest area.
       \item This allows protesters to move around to collect signatures.
@@
       \item Trusted journalist Jane attends to report.
-      \item She witnesses Alice's and Bob's proofs.
+      \item She witnesses Alice's proof.
 
@@
 
-      \item Physical transportation is limited.
-      \item Accuracy of Alice's witnessing is proportional to time from Jane's 
-        witnessing.
+      \item Alice witnesses Bob's proof.
+      \item Alice's (secret key's) transportation is physically limited.
+      \item Trust on Bob's proof is proportional to time from when Jane 
+        witnessed Alice's proof.
     \end{itemize}
   \end{idea}
+\end{frame}
 
-  \pause{}
+\begin{frame}
+  \begin{figure}
+    \centering
+    \begin{tikzpicture}
+      \tikzset{grow'=right,level distance=5em}
+      \Tree [.Proof
+      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
+      {\dots}
+      [.{wsig} {\dots} ]
+      ]
+    \end{tikzpicture}
+  \end{figure}
 
@@
     \begin{itemize}
-      \item Alice's signature key must have the physical travel properties, 
-        embedded in hardware.
+      \item Secret key in hardware.
       \item Alice's witness signature must depend on Jane's.
@@
   \centering
+  \mode<presentation>{%
+    \only<1>{%
       \begin{tikzpicture}
@@
         \Tree [.Proof
-      [.{wsig} {\(x,y\)} [.{\mode<presentation>{\only<1>{\color{red}}} osig} 
-      [.{\mode<presentation>{\only<2>{\color{red}}}\(id\)} manifesto ] head ] 
-      [.tsig head$'$ ] ]
+        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ] [.tsig 
+        {$t_s''$} ] ]
         {\dots}
@@
       \end{tikzpicture}
+    }
+  }
+  \only<2>{%
+    \begin{tikzpicture}
+      \tikzset{grow'=right,level distance=5em}
+      \Tree [.Proof
+      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
+      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ] [.tsig 
+      {$t_s''$} ] ]
+      {\dots}
+      [.{wsig} {\dots} ]
+      ]
+    \end{tikzpicture}
+  }
   \mode<article>{%

### 2017-08-27 properties.tex
Edits text to be better in text and slides

@@
   \begin{remark}
-    \begin{itemize}
-      \item Unique ring signatures~\cite{UniqueRingSignatures} has this 
-        property: two signatures are linked with high probability.
-      \item We need keys strongly tied to identities to prevent Sybil.
-    \end{itemize}
+    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
+    signatures are linked with high probability.
   \end{remark}
@@
 
+  \mode<presentation>{%
     \begin{remark}
@@
     \end{remark}
+  }
 \end{frame}
+
+Say that Alice submits her proof and stores the hash of the head of the 
+\ac{tposet} after her proof is included.
+Now she can remove her proof and just keep the hash to verify that her proof is 
+still there.
+She can also remove her signature key, so that Eve cannot use it to reproduce 
+the signature using the same inputs.
 

### 2017-08-29 conclusions.tex
Adds clarifications, improves slides

@@
   \begin{question}
-    Can we achieve receipt freeness and protect from Sybil?
+    Can we achieve receipt freeness (deniability) and protect from Sybil?
   \end{question}
@@
     \begin{remark}
-      \begin{itemize}
-        \item Without anonymous submission we don't get proof privacy, thus no 
+      Without anonymous submission we don't get proof privacy, thus no 
       receipt freeness either.
-        \item Voting normally uses mix-nets.
-        \item Submit over Tor~\cite{Tor}?
-      \end{itemize}
     \end{remark}

### 2017-08-29 properties.tex
Removes one of Sébastien's suggested slides
Adds clarifications, improves slides

@@
         \item We need a partially ordered set (poset).
+
+          \pause{}
+
         \item There is a mechanism that provides this property: a blockchain.
@@
   }
-  \only<2>{%
+  \only<3>{%
     \begin{idea}[Created before end]
@@
   }
-  \only<3>{%
+  \only<4>{%
     \begin{idea}[Created after start]
@@
 If the proofs are stored publicly, then an individual can check that their 
-proof has been included there.
+proof has been included (committed) there.
 Thus \cref{IndividualVerif} is fulfilled.
@@
     \begin{itemize}
-      \item Proofs are stored publicly.
+      \item Proofs are stored (committed) publicly.
       \item Each participant can check that their proof is indeed included.
@@
     \begin{itemize}
-      \item Proofs are stored publicly.
+      \item Proofs are stored (committed) publicly.
       \item Anyone can download all proofs, verify eligibility and then count 
@@
 
-\mode<presentation>{%
+\mode<none>{%
 \begin{frame}
@@
   \end{question}
+
+  \pause{}
+
+  \begin{question}
+    How to submit the proofs to the system?
+  \end{question}
 \end{frame}
@@
 \begin{frame}
+  \begin{remark}
+    The proof itself is a sort of receipt.
+  \end{remark}
+
+  \pause{}
+
   \begin{idea}[Receipt freeness (deniability)]
     \begin{itemize}
-      \item If Eve compromises Alice's device, she should not be able to use 
-        it to verify that she participated.
+      \item Alice submits her proof.
+      \item She stores the hash of the head of the \ac{tposet}.
+      \item She removes the proof and signature key.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+}
+
+\begin{frame}
+\mode<presentation>{%
+  \begin{idea}
+    \begin{itemize}
+      \item If Eve compromises Alice's device, she should not be able to use it 
+        to verify that she participated.
 
@@
   \end{idea}
-\end{frame}
 }
 
-\begin{frame}
+  \pause{}
+
   \begin{question}
@@
   \end{question}
-
-  \pause{}
-
-  \mode<presentation>{%
-    \begin{remark}
-      \begin{itemize}
-        \item Alice submits her proof.
-        \item She stores the hash of the head of the \ac{tposet}.
-        \item She removes the proof and signature key.
-      \end{itemize}
-    \end{remark}
-  }
 \end{frame}
@@
 to the system.
+The main problem here is that the participants must be indistinguishable from 
+non-participants.
+This means that we cannot use special-purpose anonymizing 
+technologies.
 
-\begin{frame}
 \begin{question}
   How do we submit the proofs to storage?
-    Voting normally uses mix-nets.
-    Submit over Tor~\cite{Tor}?
+  Voting normally uses mix-nets (provable shuffles).
 \end{question}
@@
 \begin{remark}
-    Without anonymous submission we don't get proof privacy, thus no receipt 
-    freeness either.
+  We must mix participants with non-participants.
 \end{remark}
-\end{frame}

### 2017-08-29 properties.tex
Removes transitive trust, excessive examples

@@
         \Tree [.Proof
-        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ] [.tsig 
-        {$t_s''$} ] ]
+        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
+        %[.tsig {$t_s''$} ]
+        ]
         {\dots}
@@
       [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
-      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ] [.tsig 
-      {$t_s''$} ] ]
+      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
+      %[.tsig {$t_s''$} ]
+      ]
       {\dots}

### 2017-08-31 properties.tex
Improves order or properties
Uses term blockchain instead of t-poset

@@
 \begin{requirements}[\ref*{EligibilityVerif}.]
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
   \item\label{CreatedAfterStart} Prove that the data was created after the 
@@
     physical location of the event.
+  \item\label{CountOnce} Prove that no individual can be counted more than 
+    once.
   \item\label{DesignatedEvent} Prove that the data is designated for the event.
@@
   \begin{requirements}[V\ref*{EligibilityVerif}.]
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
   \item\label{CreatedAfterStart} Prove that the data was created after the 
@@
 \mode<presentation>{%
-  \only<1>{%
+  \only<1,2>{%
     \begin{idea}[Temporal eligibility]
@@
         \item Submit the proof to storage.
-        \item The proof must've been created before it was included (duh!).
+        \item The proof must've been created before it was included.
         \item If included before \(t_e\), then it was created before \(t_e\).
@@
         \item This could be e.g.\ the hash of the \enquote{head} of the 
-          \ac{tposet}, (\(t_s\) in the figure).
+          blockchain, (\(t_s\) in the figure).
         \item This prevents creating proofs for future protests.
@@
 \Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
-proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
+proofs to the blockchain \emph{in (time-wise) relation to the event}.
 In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
@@
 
-They can use an older value (pick one from the history of the \ac{tposet}) when 
+They can use an older value (pick one from the history of the blockchain) when 
 they create their proofs.
@@
   time-stamping server must be available during the protest.
-  Or the proofs must be submitted to the \ac{tposet} during the protest.
+  Or the proofs must be submitted to the blockchain during the protest.
 \end{remark}
@@
       depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
+      protest and the head of the blockchain.
       Whenever possible, the witness signature should include proof that the 
@@
       \item But if Alice publishes two proofs, those two are linkable.
+
+        \pause{}
+
       \item We're not interested in unmasking trolls, just not count them more 
@@
   \begin{remark}
-    The proof itself is a sort of receipt.
-  \end{remark}
+    \begin{itemize}
+      \item The proof itself is a sort of receipt.
 
@@
 
-  \begin{idea}[Receipt freeness (deniability)]
-    \begin{itemize}
-      \item Alice submits her proof.
-      \item She stores the hash of the head of the \ac{tposet}.
-      \item She removes the proof and signature key.
+      \item If Eve compromises Alice's device, she can use it to verify that 
+        she participated.
+
+        \pause{}
+
+      \item We need a signature scheme that cannot reproduce the same signature 
+        when run on the same inputs.
     \end{itemize}
-  \end{idea}
+  \end{remark}
 \end{frame}
@@
 \mode<presentation>{%
-  \begin{idea}
+  \begin{idea}[Receipt freeness (deniability)]
     \begin{itemize}
-      \item If Eve compromises Alice's device, she should not be able to use it 
-        to verify that she participated.
+      \item Alice submits her proof.
+      \item She stores the hash of the head of the blockchain.
+      \item She removes the proof and signature key.
 
-      \item We need a signature scheme that cannot reproduce the same signature 
-        when run on the same inputs.
+        \pause{}
 
@@
 Say that Alice submits her proof and stores the hash of the head of the 
-\ac{tposet} after her proof is included.
+blockchain after her proof is included.
 Now she can remove her proof and just keep the hash to verify that her proof is 

### 2017-08-31 properties.tex

--- 2017-08-29 properties.tex
@@
 
+      \item If Eve compromises Alice's device, she can use it to verify that 
+        she participated.
+
+        \pause{}
+
+      \item We need a signature scheme that cannot reproduce the same signature 
+        when run on the same inputs.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+}
+
+\begin{frame}
+\mode<presentation>{%
   \begin{idea}[Receipt freeness (deniability)]
@@
       \item She removes the proof and signature key.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
 
-\begin{frame}
-\mode<presentation>{%
-  \begin{idea}
-    \begin{itemize}
-      \item If Eve compromises Alice's device, she should not be able to use it 
-        to verify that she participated.
-
-      \item We need a signature scheme that cannot reproduce the same signature 
-        when run on the same inputs.
+        \pause{}
 

### 2017-09-15 abstract.tex
Fixes warnings from Syntastic
Starts to adapt to PoPETS format

@@
 Say Alice organizes a protest against the current regime leader Eve.
-The protest is held in some location(s) and Alice wants to estimate the number 
-of participants to prove a certain support to her cause.
+The protest is held in some location (or locations) and Alice wants to estimate 
+the number of participants to prove a certain support to her cause.
 % Why is it a problem?
@@
 participants.
-
-\keywords{%
-  crowd counting;
-  protesting;
-  electronic voting;
-  location proof;
-  privacy
-}

### 2017-09-20 intro.tex
Minor edits
Adds clarifications, improves slides
Removes transitive trust, excessive examples
Changes to use \mode instead of implicit specs
Moves things around in the intro and to the intro
Moves overview of desired properties to intro, then the desired
properties section will be rewritten as more technically detailed.

@@
 
-Alice organizes a street protest against Eve's regime.
-Bob, Carol and many others participate in the demonstration.
+Alice is an activist who organizes a protest for some cause.
+Eve is an autocrat who opposes Alice's cause.
+Bob, Carol and many others participate in the protest against Eve.
 One problem that has not yet been entirely solved is the crowd-counting 
 problem, i.e.\ to verify how many participated in Alice's protest.
+Our main goal is to provide a tool which prevents both Alice and Eve from 
+cheating.
 
-\subsection<presentation>{What's the problem?}
+\mode<presentation>{%
+\subsection{What's the problem?}
+}
 
@@
 
-\subsection<presentation>{Why is it a problem?}
+\mode<presentation>{%
+\subsection{Why is it a problem?}
+}
 
 \mode<presentation>{%
+\begin{frame}
+  \begin{figure}
+    \includegraphics[height=0.9\textheight]{fig/Jacobs-method.jpg}
+  \end{figure}
+\end{frame}
+
 \begin{frame}
@@
 does the counting.
-We will discuss them in more detail in \cref{RelatedWork}.
+(We will discuss them in more detail in \cref{RelatedWork}.)
 
@@
       \item {\color{red} Eve wants to show that few support Alice's cause.}
-
-        \pause{}
-
       \item It's an adversarial setting!
@@
 regime in our example above.
-Or the other way around, sometimes Eve's authoritarian regime wants to organize 
-a pro-regime protest to demonstrate its \enquote{wide 
-  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-(This makes it difficult to rely on government-issued credentials to prevent a 
-Sybil attack --- government can issue arbitrarily many such credentials for its 
-own protests.)
 To solve this problem, we need a verifiable participation count which is 
@@
 
-\subsection<article>{Contributions}
+\subsection{Combining electronic voting and location proofs}
+
+Electronic voting (and voting in general) require strong verifiability and 
+privacy properties.
+We will adapt these requirements to the setting of protests.
+
+There are three requirements for 
+verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\begin{frame}
+\begin{requirements}[V]
+\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
+  cast is legitimate.
+\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
+  result is according to the cast votes.
+\item\label{IndividualVerif} Individual verifiability: every voter can verify 
+  that their vote is included in the result.
+\end{requirements}
+\end{frame}
+We translate the votes into \emph{proofs of participation}.
+Both universal and individual verifiability remain the same.
+The eligibility requirement is slightly different:
+for protests the eligibility requirement must include temporal and spatial 
+eligibility --- that each proof of participation satisfies some temporal and 
+spatial relation to the protest.
+We will define these more formally in \cref{Verification}.
+
+There are also three requirements for 
+privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\begin{frame}
+\begin{requirements}[P]
+\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
+  individual vote.
+\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
+  provide any data that can be used as a proof of how the voter voted.
+\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
+  with a coercer to prove the vote was cast in any particular way.
+\end{requirements}
+\pause{}
+\mode<presentation>{%
+  \begin{remark}
+    P\ref{CoercionResistance} \(\implies\)
+    P\ref{ReceiptFreeness} \(\implies\)
+    P\ref{VotePrivacy}
+  \end{remark}
+}
+\end{frame}
+\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
+\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
+\cref{VotePrivacy}.
+We note that we cannot improve the privacy of participating protesters, if they 
+are caught during a protest there is nothing we can do.
+But if they participate and they are not caught, then using our proposed tool 
+should not incur any additional risk.
+Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
+detailed definition).
+In essence, upon completing the protocol, Alice will have nothing that Eve can 
+use to tie her to her participation proof.
+
+\subsection{Contributions}
 
@@
 %}
+
+Sometimes Eve's authoritarian regime wants to organize a pro-regime protest to 
+demonstrate its \enquote{wide 
+  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+If we rely on government-issued credentials, we cannot prevent the government 
+from performing Sybil attacks --- since it can issue arbitrarily many 
+\enquote{valid} credentials.
+This means that we cannot verify any pro-government protests.

### 2017-09-20 properties.tex
Changes section title of security analysis
Moves things around in the intro and to the intro
Moves overview of desired properties to intro, then the desired
properties section will be rewritten as more technically detailed.

@@
 \mode*
-\section{The idea}%
+\section{Desired properties}%
 \label{TheIdea}
-
-Alice is an activist who organizes a demonstration for some cause.
-Her main goal after the protest is to provide verifiable data.
-There are several problems:
-\begin{itemize}
-  \item Alice must prove that the data is related to the event, that it is not 
-    reused data from previous protests.
-  \item Alice must provide data which can be used for the desired verification.
-  \item Alice must also consider the privacy of the participating individuals.
-\end{itemize}
-
-\begin{frame}<presentation>
-  \begin{itemize}
-    \item Alice must prove that the data is related to the event.
-    \item Alice must provide data with verifiable properties.
-    \item Alice must consider the privacy of the participants.
-  \end{itemize}
-\end{frame}
-
-Since many of the current techniques are based on photos, we will give an 
-example of Alice's problems in that setting.
-How can she ensure that photos from a demonstration are authentic?
-We can probably recognize the location that the photo is portraying, however, 
-this might just as well be a reconstruction or entirely computer generated.
-We cannot trust the meta-data of the photo, such as time-stamps of the file, 
-because these can easily be manipulated.
-So the only thing we can say for sure is that the photo was taken at the latest 
-at the time of publication.
-Now, if we cannot trust these photos, how can we determine the number of 
-participants of a demonstration?
-Furthermore, how can Alice protect the privacy of those in the photos?
-
-%However, to complicate things further,
-%\blockcquote{VenezuelanStateWorkersCalledToParticipate}{%
-%  \textins*{m}any of Venezuela’s 2.8 million state workers have reported 
-%  getting text messages, phone calls and being required to attend political 
-%  rallies during work hours
-%}.
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Venezuela is banning protests that could "disturb or affect" Sunday's 
-%  controversial election for a new constituent assembly.
-%}
-%
-%\blockcquote{BBConVenezuelaProtestBan}{%
-%  Prison terms of between five and 10 years could be imposed on those 
-%  contravening the ban,
-%}
-%
-%\blockcquote{VenezuelanGovtBansProtesting}{%
-%  Venezuelans are planning to defy a government ban on public demonstrations 
-%  and risk deadly repression with marches across the country to protest against 
-%  a vote Sunday that opposition forces say will mark the end of democracy
-%}
 

### 2017-09-20 intro.tex
Prepares contributions for later filling

@@
 
-In this paper, we combine the verifiability and privacy properties of 
-electronic voting with location-proof systems to provide a verifiable 
-participation count.
-We can only provide a verifiable participation count for non-government 
-protests:
-In any pro-government protest we cannot prevent the government from doing a 
-Sybil attack, since the government controls the identity system.
+We propose a protocol which provides a way for protests to be securely verified.
+Additionally, this verification system does not incur any additional risk to 
+protesters' privacy than participating in the physical protest itself.
 
-%In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
-%was in one place during an entire day and then repeated for several weekends.
-%In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
-%were in several locations at the same time.
-
-%\blockcquote{HowToEstimateCrowdSize}{%
-%  Crowd size is also needed for media news reports and to historically record 
-%  the event%
-%}
+\dots
 

### 2017-09-21 intro.tex
Improves overview of the idea

@@
 
-There are three requirements for 
-verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{frame}
-\begin{requirements}[V]
-\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
-  cast is legitimate.
-\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-  result is according to the cast votes.
-\item\label{IndividualVerif} Individual verifiability: every voter can verify 
-  that their vote is included in the result.
-\end{requirements}
-\end{frame}
+Voting has three requirements for 
+verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
+\begin{itemize}
+  \item Eligibility: anyone can verify that each vote cast is legitimate.
+  \item Universal verifiability: anyone can verify that the result is according 
+    to the cast votes.
+  \item Individual verifiability: every voter can verify that their vote is 
+    included in the result.
+\end{itemize}
 We translate the votes into \emph{proofs of participation}.
-Both universal and individual verifiability remain the same.
+Universal and individual verifiability remain the same: anyone can verify the 
+participation count by counting the proofs.
 The eligibility requirement is slightly different:
 for protests the eligibility requirement must include temporal and spatial 
-eligibility --- that each proof of participation satisfies some temporal and 
+eligibility, i.e.\ that each proof of participation satisfies some temporal and 
 spatial relation to the protest.
+In essence, the proof must bind the person to the time and location of the 
+protest.
 We will define these more formally in \cref{Verification}.
 
-There are also three requirements for 
+There are also three levels of 
 privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{frame}
-\begin{requirements}[P]
+\begin{itemize}
   \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
@@
     with a coercer to prove the vote was cast in any particular way.
-\end{requirements}
-\pause{}
-\mode<presentation>{%
-  \begin{remark}
-    P\ref{CoercionResistance} \(\implies\)
-    P\ref{ReceiptFreeness} \(\implies\)
-    P\ref{VotePrivacy}
-  \end{remark}
-}
-\end{frame}
-\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
-\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
-\cref{VotePrivacy}.
+\end{itemize}
 We note that we cannot improve the privacy of participating protesters, if they 
 are caught during a protest there is nothing we can do.
-But if they participate and they are not caught, then using our proposed tool 
-should not incur any additional risk.
+But if they are not caught in the act, then using our proposed tool should not 
+incur any additional risk.
 Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
-detailed definition).
-In essence, upon completing the protocol, Alice will have nothing that Eve can 
-use to tie her to her participation proof.
+detailed definition) to the protest context.
+In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
+participation proof --- even with Alice's cooperation.
 

### 2017-09-21 SystemModel.tex
Clarifies intro to assumptions

@@
 We assume that every participant has a device similar to a smartphone.
+Throughout this text, when we refer to a participant, say Alice, we actually 
+mean a principal which can perform cryptographic operations and communicate with 
+other local devices on Alice's behalf.
 (This means that we essentially provide a lower bound for the participation 
-count, since some participants might not have any smartphone.)
-It must be a portable device which can perform cryptographic operations and 
-communicate with other devices during the protest, e.g.\ through an ad-hoc 
-network.
-I.e.\ no connection to the Internet is necessary during the protest.
+count, since some participants might not have such a device.)
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{center}
+    Alice $:=$ Alice's cryptographic device
+  \end{center}
+\end{frame}
+}
+
+No connection to any global network the Internet is necessary during the 
+protest.
 During the protest these devices are computationally limited by their 
@@
 We need this to prevent Sybil attacks~\cite{SybilAttack}.
-\begin{frame}
-\begin{remark}
-  I.e.\ provided we can prevent Sybil.
-\end{remark}
-\end{frame}
 

### 2017-09-21 intro.tex
Edits properties, moves some things to intro

@@
 been ignored in the past: it is an adversarial setting.
-The protesters (organizers and participants) have an incentive to increase the 
-tallied number of participants, whereas other interests might have an incentive 
-to decrease the tallied number of participants, e.g.\ Eve's authoritarian 
-regime in our example above.
+Alice the activist has an incentive to increase the tallied number of 
+participants, whereas Eve (and possibly other interests) have an incentive to 
+decrease the tallied number of participants.
+In this case we have two options:
+either we trust Alice or Eve, or we must verify their claims.
+We aim for verifiable claims.
 To solve this problem, we need a verifiable participation count which is 
@@
 
-Electronic voting (and voting in general) require strong verifiability and 
-privacy properties.
-We will adapt these requirements to the setting of protests.
+In general, protesting is very similar to voting: both are many individuals 
+expressing their opinion.
+These opinions can be sensitive, hence we desire to have similar properties of 
+verification and privacy for participation in a protest as there is for voting.
 

### 2017-09-21 properties.tex
Edits properties, moves some things to intro

@@
 \section{Desired properties}%
-\label{TheIdea}
+\label{Properties}
+
+We categorize the desired properties into verifiability and privacy.
 
@@
 
-We have an adversarial setting between Alice the activist and Eve the evil 
-regime: Alice wants to show large support against Eve, Eve wants to show little
-support for Alice.
-In this case we have two options:
-either we trust Alice or Eve, or we must verify their claims.
-We aim for verifiable claims.
-
-In general, protesting is very similar to voting: both are many individuals 
-expressing their opinion.
-These opinions can be sensitive, hence we desire to have similar properties of 
-verification and privacy for participation in a protest as there is for voting.
-In the context of (electronic) voting protocols, there are three requirements 
-for verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{frame}
+We desire three verifiability requirements:
 \begin{requirements}[V]
-\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
-  cast is legitimate.
+\item\label{EligibilityVerif} Eligibility: anyone can verify that each 
+  participation proof provides temporal and spatial eligibility and that it has 
+  not been counted before.
 \item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-  result is according to the cast votes.
-\item\label{IndividualVerif} Individual verifiability: every voter can verify 
-  that their vote is included in the result.
+  result is according to the submitted participation proofs.
+\item\label{IndividualVerif} Individual verifiability: every participant can 
+  verify that their participation proof is included in the global count.
 \end{requirements}
-\end{frame}
 We can translate these to the case of participation in a demonstration, then 

### 2017-09-27 SystemModel.tex
Updates definition of participation proof

@@
 \begin{definition}[Participation proof]
-  A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; \sigma)\), where
-  \(id, t_s, t_e\) are as in \cref{DefProtest},
-  \(lp\) is a location proof and
-  \(\sigma\) is a signature over the proof.
+  A \emph{witness signature}\footnote{%
+    \Iac{LPS}?
+  }is a tuple \[(pid; id; t_s, t_e; x, y; \sigma),\] where
+  \(pid\) is a protester's identity,
+  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest} and
+  \(\sigma\) is a signature over the values in the tuple.
+  A \emph{participation proof} \[P_{i, j} = \{ (pid; id; t_s, t_e; x, y; \sigma) 
+    \mid pid = i, id = j\}\] for a protester \(i\) participating in protest 
+  \(j\) is the set of all witness signatures with the same protester and protest 
+  identifiers.
 \end{definition}
 
+\mode<presentation>{%
   \begin{frame}
-  \mode<presentation>{%
     \begin{definition}[Participation proof]
       \begin{itemize}
-      \item A \emph{participation proof} is a tuple \((id; t_s, t_e; lp; 
+        \item A \emph{witness signature} is a tuple \((pid; id; t_s, t_e; x, y; 
             \sigma)\), where
-      \item \(id, t_s, t_e\) are as before,
-      \item \(lp\) is a location proof and
-      \item \(\sigma\) is a signature over the proof.
+        \item \(pid\) is a protester's identity,
+        \item \(id, t_s, t_e, x, y\) are as before,
+        \item \(\sigma\) is a signature over the values.
+        \item A \emph{participation proof} \(P_{i, j} = \{ (pid; id; t_s, t_e; x, 
+            y; \sigma) \mid pid = i, id = j\}\).
       \end{itemize}
     \end{definition}
-
-  \pause{}
+  \end{frame}
 }
-\begin{question}
-  How should this one relate to the \acp{LP} and \ac{tposet}?
-\end{question}
-\end{frame}
 

### 2017-09-27 SystemModel.tex
Removes questions that have moved to issues or no longer relevant

@@
 we can just sum up the results.
-
-\begin{frame}
-\begin{question}
-  With this definition, can we participate in two sub-protests and be counted 
-  twice?
-\end{question}
-\begin{remark}
-  Perhaps not if linkability is tied to the cause.
-\end{remark}
-\end{frame}
-\begin{remark}
-  This sort of depends on the unique ring/list signature scheme that we use.
-  As long as we can provide linkability between a user's proofs, we can consider 
-  it the same protest.
-  When we cannot, it must be a new protest.
-  So this is supposedly decided by the one setting up the unique ring/list 
-  signature scheme --- which we do not know yet how it will be done.
-\end{remark}
+The same for marches, the marching path can be divided into subprotests with 
+coarse coordinates that slightly overlap.
 

### 2017-09-27 properties.tex
Removes questions that have moved to issues or no longer relevant

@@
 
-\begin{question}
-  How hard is it to reuse old proofs?
-  Forge all signatures due to changed values?
-\end{question}
-
 \subsubsection{Spatial eligibility}
@@
 }
-
-\begin{question}
-  Why should anyone trust these witnesses?
-  What are the assumptions?
-  Signed over a short period of time?\footnote{%
-    In a sense, if they collude they have shown support for the cause.
-    As long as they are not Sybil it should be fine?
-  }
-\end{question}
 
@@
 \end{remark}
-
-\begin{question}
-  Trusted party for the group signatures?
-\end{question}
-\begin{question}
-  How can we do \acp{LP} with 1000s of witnesses each?
-  Can we do some preprocessing?
-  Ad-hoc networks, broadcast \acp{LP}?
-\end{question}
-\begin{question}
-  Must tie credentials to something unique: phone, phone subscription?
-  Cannot register twice, government control?
-\end{question}
-
-\begin{question}
-  What if Alice acts as a witness for Eve's agents?
-  Can that violate her privacy?
-\end{question}
-\begin{question}
-  What if Eve's agents act as witnesses?
-  Can they track their signatures to track users?
-  Can Alice detect if this happens?
-\end{question}
 
@@
 Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
-To have any verifiability, we need the storage to be immutable --- i.e.\ it 
-prevents malicious changes.
 

### 2017-09-27 properties.tex
Merges some eligibility properties
Makes them:
- temporal eligibility
- spatial eligibility
- one-proof-per-person
- designated event

@@
 \begin{requirements}[\ref*{EligibilityVerif}.]
-  \item\label{CreatedAfterStart} Prove that the data was created after the 
-    start of the event.
-  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
-    of the event.
-  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
+  \item Temporal egligibility:%
+    \label{CreatedAfterStart} prove that the data was created after the start of 
+    the event;%
+    \label{CreatedBeforeEnd} prove that the data was created before the end of 
+    the event.
+  \item Spatial eligibility:%
+    \label{SpatiallyRelated} prove that the data is spatially related to the 
     physical location of the event.
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
-  \item\label{DesignatedEvent} Prove that the data is designated for the event.
+  \item One-proof-per-person:%
+    \label{CountOnce} prove that no individual can be counted more than once.
+  \item Designated event:%
+    \label{DesignatedEvent} prove that the data is designated for the event.
 \end{requirements}

### 2017-09-27 properties.tex
Moves implementation ideas from properties to protocol
WIP on #25, #26, #31

@@
 
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
-blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}.
-(See \cref{PosetGraph}.)
-For generality, we will use the terminology of 
-\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
-structure \iac{tposet}.
-
 \begin{frame}
-\begin{figure}
-  \centering
-  \input{fig/tposet.tex}
-  \mode<article>{%
-    \caption{%
-      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
-      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
-      are incomparable.
-    }\label{PosetGraph}
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1,2>{%
-    \begin{idea}[Temporal eligibility]
-      \begin{itemize}
-        \item We need a partially ordered set (poset).
-
-          \pause{}
-
-        \item There is a mechanism that provides this property: a blockchain.
-        \item There are also other structures, e.g.\ a directed 
-          graph~\cite{BlockchainFreeCryptocurrencies}.
-      \end{itemize}
-    \end{idea}
-  }
-  \only<3>{%
-    \begin{idea}[Created before end]
-      \begin{itemize}
-        \item Submit the proof to storage.
-        \item The proof must've been created before it was included.
-        \item If included before \(t_e\), then it was created before \(t_e\).
-      \end{itemize}
-    \end{idea}
-  }
-  \only<4>{%
-    \begin{idea}[Created after start]
-      \begin{itemize}
-        \item Include an unpredictable value in the proof.
-        \item This could be e.g.\ the hash of the \enquote{head} of the 
-          \ac{tposet}, (\(t_s\) in the figure).
-        \item This prevents creating proofs for future protests.
-      \end{itemize}
-    \end{idea}
-  }
-}
+\begin{definition}[Forging temporal eligibility]
+  \dots
+\end{definition}
 \end{frame}
-
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
-proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
-In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
-protest, then the relation will guarantee that \(p_A, p_B\) were created before 
-the end of the protest.
-Then we know that they cannot have been created after the event.
-
-For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
-in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
-This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
-has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
-it for a future protest.
-
-They can use an older value (pick one from the history of the \ac{tposet}) when 
-they create their proofs.
-This will only expand the interval of possible creation into the past.
-This will not help their cause, as anyone will recognize that the proof could 
-be created at any time in that interval, i.e.\ possibly before the protest.
 
@@
 
-\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
-us to \emph{verify the data spatially}.
-
-If we include \iac{LP}, this will tie the proof to the physical location and, 
-thus, solve \cref{SpatiallyRelated}.
-The \ac{LP} is \enquote{witnessed} (signed) by other participants.
-The \ac{LP} contains coarse coordinates of the location, which must be within 
-the protest area to be valid.
-This allows Bob the protester to move within the protest area to collect 
-witnesses (signatures).
-It also provides privacy since the location cannot be used to deanonymize Bob's 
-proof --- e.g.\ to correlate the location in his proof with captured 
-surveillance footage.
-
-\mode<presentation>{%
 \begin{frame}
-  \begin{figure}
-    \centering
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  \end{figure}
-
-  \begin{idea}[Spatial eligibility]
-    \begin{itemize}
-      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
-        participants.
-      \item We have a coarse location, just within the protest area.
-      \item This allows protesters to move around to collect signatures.
-      \item This provides privacy for the location, e.g.\ cannot map to 
-        surveillance cameras.
-    \end{itemize}
-  \end{idea}
+\begin{definition}[Forging spatial eligibility]
+  \dots
+\end{definition}
 \end{frame}
-}
-
-\mode<none>{%
-\begin{frame}
-  \begin{idea}[Transitive trust]
-    \begin{itemize}
-      \item Trusted journalist Jane attends to report.
-      \item She witnesses Alice's proof.
-
-        \pause{}
-
-      \item Alice witnesses Bob's proof.
-      \item Alice's (secret key's) transportation is physically limited.
-      \item Trust on Bob's proof is proportional to time from when Jane 
-        witnessed Alice's proof.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-
-\begin{frame}
-  \begin{figure}
-    \centering
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  \end{figure}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Secret key in hardware.
-      \item Alice's witness signature must depend on Jane's.
-      \item High-precision relation to time?
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
-We will introduce a notion of transitivity for trust in these proofs.
-The \emph{trusted} journalist Jane attends the protest to report on it.
-She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
-Now Alice's \ac{LP} can be trusted as correct at that point in time.
-Alice's ability to travel is physically limited.
-Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
-the time that has passed since Jane witnessed Alice's \ac{LP}.
-We can apply this argument recursively for any other participant's \ac{LP} that 
-Alice has witnessed.
-However, this requires some assumptions:
-\begin{itemize}
-  \item It is actually Alice's signing key must have physically limited travel.
-    This can be assumed for signing keys that are embedded into hardware by 
-    some trusted person.
-  \item Alice's witness signature must depend on Jane's witness signature, to 
-    prove that Alice signed after Jane.
-\end{itemize}
-\begin{remark}
-  This probably requires high-precision timestamps, i.e.\ a trusted 
-  time-stamping server must be available during the protest.
-  Or the proofs must be submitted to the \ac{tposet} during the protest.
-\end{remark}
 
@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
-individual can provide two proofs of participation and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
-This can be done by including a signature made by a verified key.
-(We will discuss the privacy aspects in \cref{Privacy}.)
-
-\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
-protest at the same time and place, these would have the same spatial and 
-temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
-its \enquote{manifesto}.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \mode<presentation>{%
-    \only<1>{%
-      \begin{tikzpicture}
-        \tikzset{grow'=right,level distance=5em}
-        \Tree [.Proof
-        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
-        %[.tsig {$t_s''$} ]
-        ]
-        {\dots}
-        [.{wsig} {\dots} ]
-        ]
-      \end{tikzpicture}
-    }
-  }
-  \only<2>{%
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
-      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
-      %[.tsig {$t_s''$} ]
-      ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  }
-  \mode<article>{%
-    \caption{%
-      The proof depends on several witness signatures (wsig), each of which 
-      depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
-      Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnessed by a trusted witness (tsig).
-    }
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1>{%
-    \begin{idea}[Count once]
-      \begin{itemize}
-        \item Any two proofs by the same individual are linkable.
-        \item Includes signature made by a verified key.
-      \end{itemize}
-    \end{idea}
-  }
-
-  \only<2>{%
-    \begin{idea}[Designated event]
-      \begin{itemize}
-        \item Include a protest-specific identifier.
-        \item E.g.\ hash of the \enquote{manifesto}.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
+\dots
 
@@
 
-If the proofs are stored publicly, then an individual can check that their 
-proof has been included (committed) there.
-Thus \cref{IndividualVerif} is fulfilled.
-Similarly for universal verifiability.
-If the storage is public, then anyone can download all the proofs, verify their 
-eligibility and count them.
-Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Individual verifiability]
-    \begin{itemize}
-      \item Proofs are stored (committed) publicly.
-      \item Each participant can check that their proof is indeed included.
-    \end{itemize}
-  \end{idea}
-
-  \pause{}
-
-  \begin{idea}[Universal verifiability]
-    \begin{itemize}
-      \item Proofs are stored (committed) publicly.
-      \item Anyone can download all proofs, verify eligibility and then count 
-        them.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
+\dots
 

### 2017-09-27 protocol.tex
Moves implementation ideas from properties to protocol
WIP on #25, #26, #31

\section{Protocol}

\dots

\subsubsection{Temporal eligibility}

\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
  set}\footnote{%
  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
} of objects.
If some objects in the set relate to known points in time, then the partial 
order relates the data to the time of the event.
This allows us to \emph{verify the data temporally}.

One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
blockchain.
There are also other structures, e.g.\ a directed graph that 
converges~\cite{BlockchainFreeCryptocurrencies}.
(See \cref{PosetGraph}.)
For generality, we will use the terminology of 
\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
structure \iac{tposet}.

\begin{frame}
\begin{figure}
  \centering
  \input{fig/tposet.tex}
  \mode<article>{%
    \caption{%
      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
      are incomparable.
    }\label{PosetGraph}
  }
\end{figure}

\mode<presentation>{%
  \only<1,2>{%
    \begin{idea}[Temporal eligibility]
      \begin{itemize}
        \item We need a partially ordered set (poset).

          \pause{}

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included.
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
protest, then the relation will guarantee that \(p_A, p_B\) were created before 
the end of the protest.
Then we know that they cannot have been created after the event.

For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
it for a future protest.

They can use an older value (pick one from the history of the \ac{tposet}) when 
they create their proofs.
This will only expand the interval of possible creation into the past.
This will not help their cause, as anyone will recognize that the proof could 
be created at any time in that interval, i.e.\ possibly before the protest.

\subsubsection{Spatial eligibility}

\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
us to \emph{verify the data spatially}.

If we include \iac{LP}, this will tie the proof to the physical location and, 
thus, solve \cref{SpatiallyRelated}.
The \ac{LP} is \enquote{witnessed} (signed) by other participants.
The \ac{LP} contains coarse coordinates of the location, which must be within 
the protest area to be valid.
This allows Bob the protester to move within the protest area to collect 
witnesses (signatures).
It also provides privacy since the location cannot be used to deanonymize Bob's 
proof --- e.g.\ to correlate the location in his proof with captured 
surveillance footage.

\mode<presentation>{%
\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{idea}[Spatial eligibility]
    \begin{itemize}
      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
        participants.
      \item We have a coarse location, just within the protest area.
      \item This allows protesters to move around to collect signatures.
      \item This provides privacy for the location, e.g.\ cannot map to 
        surveillance cameras.
    \end{itemize}
  \end{idea}
\end{frame}
}

\mode<none>{%
\begin{frame}
  \begin{idea}[Transitive trust]
    \begin{itemize}
      \item Trusted journalist Jane attends to report.
      \item She witnesses Alice's proof.

        \pause{}

      \item Alice witnesses Bob's proof.
      \item Alice's (secret key's) transportation is physically limited.
      \item Trust on Bob's proof is proportional to time from when Jane 
        witnessed Alice's proof.
    \end{itemize}
  \end{idea}
\end{frame}

\begin{frame}
  \begin{figure}
    \centering
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  \end{figure}

  \begin{remark}
    \begin{itemize}
      \item Secret key in hardware.
      \item Alice's witness signature must depend on Jane's.
      \item High-precision relation to time?
    \end{itemize}
  \end{remark}
\end{frame}
}

We will introduce a notion of transitivity for trust in these proofs.
The \emph{trusted} journalist Jane attends the protest to report on it.
She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
Now Alice's \ac{LP} can be trusted as correct at that point in time.
Alice's ability to travel is physically limited.
Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
the time that has passed since Jane witnessed Alice's \ac{LP}.
We can apply this argument recursively for any other participant's \ac{LP} that 
Alice has witnessed.
However, this requires some assumptions:
\begin{itemize}
  \item It is actually Alice's signing key must have physically limited travel.
    This can be assumed for signing keys that are embedded into hardware by 
    some trusted person.
  \item Alice's witness signature must depend on Jane's witness signature, to 
    prove that Alice signed after Jane.
\end{itemize}
\begin{remark}
  This probably requires high-precision timestamps, i.e.\ a trusted 
  time-stamping server must be available during the protest.
  Or the proofs must be submitted to the \ac{tposet} during the protest.
\end{remark}

\subsubsection{Linkability and designated protest}

\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
individual can provide two proofs of participation and thus be counted twice.
That situation should be detectable.
We can do this by ensuring that Alice cannot produce two valid proofs which
are unlinkable.
This can be done by including a signature made by a verified key.
(We will discuss the privacy aspects in \cref{Privacy}.)

\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
protest at the same time and place, these would have the same spatial and 
temporal properties.
To distinguish them, we also need to prove for which of these events that a 
proof is designated.
This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
its \enquote{manifesto}.

\begin{frame}
\begin{figure}
  \centering
  \mode<presentation>{%
    \only<1>{%
      \begin{tikzpicture}
        \tikzset{grow'=right,level distance=5em}
        \Tree [.Proof
        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
        %[.tsig {$t_s''$} ]
        ]
        {\dots}
        [.{wsig} {\dots} ]
        ]
      \end{tikzpicture}
    }
  }
  \only<2>{%
    \begin{tikzpicture}
      \tikzset{grow'=right,level distance=5em}
      \Tree [.Proof
      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
      %[.tsig {$t_s''$} ]
      ]
      {\dots}
      [.{wsig} {\dots} ]
      ]
    \end{tikzpicture}
  }
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}

\mode<presentation>{%
  \only<1>{%
    \begin{idea}[Count once]
      \begin{itemize}
        \item Any two proofs by the same individual are linkable.
        \item Includes signature made by a verified key.
      \end{itemize}
    \end{idea}
  }

  \only<2>{%
    \begin{idea}[Designated event]
      \begin{itemize}
        \item Include a protest-specific identifier.
        \item E.g.\ hash of the \enquote{manifesto}.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

\subsubsection{Individual and universal verifiability}

If the proofs are stored publicly, then an individual can check that their 
proof has been included (committed) there.
Thus \cref{IndividualVerif} is fulfilled.
Similarly for universal verifiability.
If the storage is public, then anyone can download all the proofs, verify their 
eligibility and count them.
Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.

\mode<presentation>{%
\begin{frame}
  \begin{idea}[Individual verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Each participant can check that their proof is indeed included.
    \end{itemize}
  \end{idea}

  \pause{}

  \begin{idea}[Universal verifiability]
    \begin{itemize}
      \item Proofs are stored (committed) publicly.
      \item Anyone can download all proofs, verify eligibility and then count 
        them.
    \end{itemize}
  \end{idea}
\end{frame}
}

### 2017-09-27 properties.tex
Moves implementation specifics from properties to protocol
WIP on #30, #29, #23

@@
 
-A demonstration is very different from voting in one sense: at a demonstration, 
-Alice must be physically present and that very presence shows her support for 
-the cause.
-In voting, on the other hand, everyone is present and Alice has multiple 
-options which are not revealed by her mere presence.
-% XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof of participation, the proof must be unlinkable 
-to Alice, yet, if Alice submits another proof, those two proofs must be 
-linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
-Alice is not counted twice.
-This is fine, since we do not want to catch any cheater, we just do not want to
-count them more than once.
-
-\mode<presentation>{%
 \begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item Voting: different alternatives when participating.
-      \item Protesting: participation implies the alternative.
-    \end{itemize}
-  \end{remark}
-
-  \pause{}
-
-  \begin{idea}[Proof privacy]
-    \begin{itemize}
-      \item Eve shouldn't be able to link Alice's published proof back to 
-        Alice.
-      \item But if Alice publishes two proofs, those two are linkable.
-
-        \pause{}
-
-      \item We're not interested in unmasking trolls, just not count them more 
-        than once.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\begin{frame}
-  \begin{remark}
-    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
-    signatures are linked with high probability.
-  \end{remark}
-
-  \begin{question}
-    Can we link a verified key to a unique ring signature key?
-  \end{question}
-
-  \pause{}
-
-  \begin{question}
-    How to submit the proofs to the system?
-  \end{question}
+\begin{definition}[Proof indistinguishability]
+  \dots
+\end{definition}
 \end{frame}
@@
 
-Receipt freeness implies that Alice enjoys deniability against Eve:
-Eve should not be able to use the published proof to tie it to Alice, even if 
-Eve has access to Alice's device (i.e.\ all her private keys).
-E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
-Alice has created one of the proofs.
-
-\mode<presentation>{%
 \begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item The proof itself is a sort of receipt.
-
-        \pause{}
-
-      \item If Eve compromises Alice's device, she can use it to verify that 
-        she participated.
-
-        \pause{}
-
-      \item We need a signature scheme that cannot reproduce the same signature 
-        when run on the same inputs.
-    \end{itemize}
-  \end{remark}
+\begin{definition}[Receipt freeness/deniability]
+  \dots
+\end{definition}
 \end{frame}
-}
-
-\begin{frame}
-\mode<presentation>{%
-  \begin{idea}[Receipt freeness (deniability)]
-    \begin{itemize}
-      \item Alice submits her proof.
-      \item She stores the hash of the head of the \ac{tposet}.
-      \item She removes the proof and signature key.
-
-        \pause{}
-
-      \item E.g.\ a short-term and a long-term credential, then Alice can 
-        drop the short-term credential.
-
-      \item But Alice should still not be able to participate twice.
-    \end{itemize}
-  \end{idea}
-}
-
-  \pause{}
-
-  \begin{question}
-    Is there such a signature scheme?
-    Can we construct it?
-  \end{question}
-\end{frame}
-
-Say that Alice submits her proof and stores the hash of the head of the 
-\ac{tposet} after her proof is included.
-Now she can remove her proof and just keep the hash to verify that her proof is 
-still there.
-She can also remove her signature key, so that Eve cannot use it to reproduce 
-the signature using the same inputs.
 

### 2017-09-27 protocol.tex
Moves implementation specifics from properties to protocol
WIP on #30, #29, #23

@@
 }
+
+\subsubsection{Participation-proof privacy}
+
+A demonstration is very different from voting in one sense: at a demonstration, 
+Alice must be physically present and that very presence shows her support for 
+the cause.
+In voting, on the other hand, everyone is present and Alice has multiple 
+options which are not revealed by her mere presence.
+% XXX Check if unlinkable is the correct term
+Hence, if Alice submits a proof of participation, the proof must be unlinkable 
+to Alice, yet, if Alice submits another proof, those two proofs must be 
+linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
+Alice is not counted twice.
+This is fine, since we do not want to catch any cheater, we just do not want to
+count them more than once.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{remark}
+    \begin{itemize}
+      \item Voting: different alternatives when participating.
+      \item Protesting: participation implies the alternative.
+    \end{itemize}
+  \end{remark}
+
+  \pause{}
+
+  \begin{idea}[Proof privacy]
+    \begin{itemize}
+      \item Eve shouldn't be able to link Alice's published proof back to 
+        Alice.
+      \item But if Alice publishes two proofs, those two are linkable.
+
+        \pause{}
+
+      \item We're not interested in unmasking trolls, just not count them more 
+        than once.
+    \end{itemize}
+  \end{idea}
+\end{frame}
+}
+
+\begin{frame}
+  \begin{remark}
+    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
+    signatures are linked with high probability.
+  \end{remark}
+
+  \begin{question}
+    Can we link a verified key to a unique ring signature key?
+  \end{question}
+
+  \pause{}
+
+  \begin{question}
+    How to submit the proofs to the system?
+  \end{question}
+\end{frame}
+
+\subsubsection{Receipt freeness}
+
+Receipt freeness implies that Alice enjoys deniability against Eve:
+Eve should not be able to use the published proof to tie it to Alice, even if 
+Eve has access to Alice's device (i.e.\ all her private keys).
+E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
+Alice has created one of the proofs.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{remark}
+    \begin{itemize}
+      \item The proof itself is a sort of receipt.
+
+        \pause{}
+
+      \item If Eve compromises Alice's device, she can use it to verify that 
+        she participated.
+
+        \pause{}
+
+      \item We need a signature scheme that cannot reproduce the same signature 
+        when run on the same inputs.
+    \end{itemize}
+  \end{remark}
+\end{frame}
+}
+
+\begin{frame}
+\mode<presentation>{%
+  \begin{idea}[Receipt freeness (deniability)]
+    \begin{itemize}
+      \item Alice submits her proof.
+      \item She stores the hash of the head of the \ac{tposet}.
+      \item She removes the proof and signature key.
+
+        \pause{}
+
+      \item E.g.\ a short-term and a long-term credential, then Alice can 
+        drop the short-term credential.
+
+      \item But Alice should still not be able to participate twice.
+    \end{itemize}
+  \end{idea}
+}
+
+  \pause{}
+
+  \begin{question}
+    Is there such a signature scheme?
+    Can we construct it?
+  \end{question}
+\end{frame}
+
+Say that Alice submits her proof and stores the hash of the head of the 
+\ac{tposet} after her proof is included.
+Now she can remove her proof and just keep the hash to verify that her proof is 
+still there.
+She can also remove her signature key, so that Eve cannot use it to reproduce 
+the signature using the same inputs.

### 2017-09-27 SystemModel.tex
Moves assumptions to security analysis

@@
 \label{SystemModel}
-
-\subsection{Assumptions}
-
-We assume that every participant has a device similar to a smartphone.
-Throughout this text, when we refer to a participant, say Alice, we actually 
-mean a principal which can perform cryptographic operations and communicate with 
-other local devices on Alice's behalf.
-(This means that we essentially provide a lower bound for the participation 
-count, since some participants might not have such a device.)
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{center}
-    Alice $:=$ Alice's cryptographic device
-  \end{center}
-\end{frame}
-}
-
-No connection to any global network the Internet is necessary during the 
-protest.
-During the protest these devices are computationally limited by their 
-batteries.
-Before and after the protest, we assume that the devices have Internet 
-connections and are not computationally limited by any battery.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{assumption}[During protest]
-    \begin{itemize}
-      \item Everyone has a smartphone.
-      \item Can use ad-hoc networks during the event.
-      \item Computations bounded by battery life.
-    \end{itemize}
-  \end{assumption}
-
-  \pause{}
-
-  \begin{assumption}[Before and after protest]
-    \begin{itemize}
-      \item Internet connection available.
-      \item Computations not bounded by battery life.
-    \end{itemize}
-  \end{assumption}
-
-  \pause{}
-
-  \begin{remark}
-    We provide a lower bound, since there might be participants without phones.
-  \end{remark}
-\end{frame}
-}
-
-We further assume that every participant has a digital certificate signed by 
-some logically centralized certificate authority.
-E.g.\ that we can use the cryptographic keys stored in the chip of the national 
-identity card or passport.
-We need this to prevent Sybil attacks~\cite{SybilAttack}.
 

### 2017-09-27 properties.tex
Moves architecture to protocol section

@@
 \end{frame}
-
-\subsubsection{Architecture}
-
-We also have an architectural problem.
-If the system is only run by volunteering activists, then Eve can simply 
-analyse network traffic and look for people running nodes in the system.
-
-\begin{question}
-  Shall we offer a platform that is run by a variety of institutions who 
-  offers to verify protests?
-  Or go strictly peer-to-peer?
-\end{question}
-
-\begin{question}
-  If strictly peer-to-peer, and only run by protesters, one can infer that 
-  they are protesters by running such a node.
-  Can this be mitigated?
-\end{question}
-
-Similarly, we have the problem of how protesters submit their proofs to the 
-system.
-This must be done anonymously.
-Otherwise Eve can analyse the network traffic to find out who submitted proofs 
-to the system.
-The main problem here is that the participants must be indistinguishable from 
-non-participants.
-This means that we cannot use special-purpose anonymizing 
-technologies.
-
-\begin{question}
-  How do we submit the proofs to storage?
-  Voting normally uses mix-nets (provable shuffles).
-\end{question}
-
-\begin{remark}
-  We must mix participants with non-participants.
-\end{remark}

### 2017-09-27 SystemModel.tex
Writes up system model, moves adversary model to properties

@@
 
+\begin{frame}
 \begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
+  A \emph{subprotest} is a tuple \((id, t, l)\) where
   \(id\in \Z_{2^\lambda}\) is an identifier,
-  \((t_s, t_e)\in \R^2\) is a time interval,
-  \((x, y)\in \R^2\) are the coordinates of the location.
+  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
+  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
+  \(\epsilon\)-neighbourhood of \((x,y)\)).
   A \emph{protest} is a set of subprotests sharing the same \(id\).
 \end{definition}
-
-\mode<presentation>{%
-\begin{frame}
-\begin{definition}[Protest]
-  \begin{itemize}
-    \item A \emph{subprotest} is a tuple \((id; t_s, t_e; x, y)\), where
-    \item \(id\in \Z_{2^\lambda}\) is an identifier,
-    \item \((t_s, t_e)\in \R^2\) is a time interval,
-    \item \((x, y)\in \R^2\) are the coordinates of the location.
-    \item A \emph{protest} is a set of subprotests sharing the same \(id\).
-  \end{itemize}
-\end{definition}
 \end{frame}
-}
 
@@
 
+\subsection{Participation and count}
+
 Each participant who want to be counted must submit a participation proof.
-The proof must be associated with the protest, i.e.\ contain its \(id\).
-Furthermore it must provide the time and the location of the participation.
-More formally, we define a participation proof as follows.
+The proof must be associated with the protest, i.e.\ its \(id\), time and 
+location.
+We use witnesses to associate the proof to the location.
+The proof and its witnesses are stored in a set, as there should be only unique 
+witnesses.
 
-\begin{definition}[Participation proof]
-  A \emph{witness signature}\footnote{%
-    \Iac{LPS}?
-  }is a tuple \[(pid; id; t_s, t_e; x, y; \sigma),\] where
-  \(pid\) is a protester's identity,
-  \(id, t_s, t_e, x, y\) are as in \cref{DefProtest} and
-  \(\sigma\) is a signature over the values in the tuple.
-  A \emph{participation proof} \[P_{i, j} = \{ (pid; id; t_s, t_e; x, y; \sigma) 
-    \mid pid = i, id = j\}\] for a protester \(i\) participating in protest 
-  \(j\) is the set of all witness signatures with the same protester and protest 
-  identifiers.
+\begin{frame}
+\begin{definition}[Witness]
+  A \emph{witness} \(w = (pid, id, t, l, wid)\) is a tuple where
+  \(id, t, l\) are as in \cref{DefProtest},
+  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
+  person who issued the witness.
+  We let \(W\) be the set of all witnesses.
 \end{definition}
+\end{frame}
 
-\mode<presentation>{%
+A subset of the witnesses forms a participation proof for a protester.
+
 \begin{frame}
 \begin{definition}[Participation proof]
-      \begin{itemize}
-        \item A \emph{witness signature} is a tuple \((pid; id; t_s, t_e; x, y; 
-            \sigma)\), where
-        \item \(pid\) is a protester's identity,
-        \item \(id, t_s, t_e, x, y\) are as before,
-        \item \(\sigma\) is a signature over the values.
-        \item A \emph{participation proof} \(P_{i, j} = \{ (pid; id; t_s, t_e; x, 
-            y; \sigma) \mid pid = i, id = j\}\).
-      \end{itemize}
+  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
+  is the set
+  \begin{align}
+    \nonumber
+    p_{i, j} =
+    \left\{ (pid, id, t, l, wid)\in W \mid
+    %\right. &
+    pid = i, id = j,
+    %\\ & \left.
+    t \subseteq t_j, l\subseteq l_j \right\},
+  \end{align}
+  of all witnesses with the same protester and protest identifiers, witness time 
+  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
+  \(t_j\) and \(l_j\)).
 \end{definition}
 \end{frame}
-}
 
-\subsection{Adversary model}
-
-We have three adversaries: Alice herself, Eve and Rusuk.
-Alice the protest organizer tries to increase the count.
-Eve the totalitarian dictator tries to decrease the count.
-Additionally, Eve tries to deanonymize the participants.
-Finally, we have Rusuk who is the head of another nation state.
-Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
-gain, thus supporting either Eve or Alice.
-Rusuk will thus also try to either increase or decrease the count.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Alice the activist}
-    \begin{itemize}
-      \item Alice organizes the protest against Eve's regime.
-      \item Alice wants to have a high participation count.
-      \item She tries to increase it.
-    \end{itemize}
-  \end{block}
-
-  \pause{}
-
-  \begin{block}{Eve the fake-news populist}
-    \begin{itemize}
-      \item Eve's regime is target of the protest.
-      \item She wants to have a low participation count.
-      \item She tries to decrease it.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Eve the totalitarian dictator}
-    \begin{itemize}
-      \item Eve wants to \enquote{convince} activists to support her.
-      \item She wants to find all activists.
-      \item She tries to identify (deanonymize) participants.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Rusuk the nation state}
-    \begin{itemize}
-      \item Rusuk benefits from the situation in Evestan.
-      \item He wants the outcome to be the most beneficial.
-      \item He will try to increase or decrease the participation count.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
-
-More formally \dots
-
-\mode<all>\endinput
-
-\section{Old stuff}
-
-We can divide the problem into three parts:
-\begin{itemize}
-  \item Register participants in the system.
-  \item Collect the necessary data.
-  \item Perform the counting and verification.
-\end{itemize}
-
-To register the participants we might be able to piggy-back on existing 
-\acp{PKI} and blind signatures --- similarly as for voting systems.
-
-There are several issues that must be treated:
-\begin{itemize}
-  \item Each location proof must be bound to one individual's participation.
-    One protester must not be able to create two unique location proofs and be 
-    able to increase the number of participants, that would violate 
-    \cref{EligibilityVerif} above.
-    In other words, we must prevent the Sybil attack.
-
-  \item A group of people should not be able to generate \acp{LP} to make it 
-    look as if they participated in the protest but actually stayed at home.
-    This means that all \acp{LP} must be linked to each other.
-    If a protest has hundreds of thousands of participants, then this linking 
-    must be achieved efficiently.
-\end{itemize}
-
-The model will be a public anonymous blackboard.
-We will use this blackboard to publish locations proofs after the protest.
-
-We want the following properties:
-\begin{description}
-  \item[Correctness] We want to count everyone once and only once.
-  \item[Unforgeability] Participation should not be possible to forge.
-    I.e.\ non-participants should not be able to say they were present.
-    This together with correctness will provide authenticity to the protest 
-    verification.
-  \item[Anonymity] Given the data published on the blackboard, the adversary 
-    should not be able to tell two participants apart.
-  \item[Decentralized] There should be no central authority.
-\end{description}
-
-Can the adversary publish a public-key looking random string to sabotage the 
-blackboard?
-
-Basically the properties that we are interested in are similar to those of 
-electronic voting, so we would like to reuse as many definitions from there as 
-possible.
-
-\subsection{Decentralization}
-
-In \ac{PROPS} the prover must have a secret signed by \iac{CA}.
-This \ac{CA} can be implemented as a secret-sharing scheme.
-Usually these have a fixed threshold \((t, n)\).
-This can be achieved by commitments, then the shared secret is computed.
-However, it would be interesting to have the threshold dynamically adapt to the 
-number of participants, i.e.\ participants can join later too.
-
-Can the adversary then \enquote{join} enough many to throw off the threshold?
-
-\subsection{Correctness and Unforgeability}
-
-Each prover must reach a threshold of witnesses \(k\).
-We must be able to prevent a prover to collect \(2k\) witnesses and then 
-publishing two proofs.
-We therefore must achieve conditional linkability between the \acp{LP} 
-published on the blackboard.
-If a second \ac{LP} for a secret is published, then those should be linkable.
-This might be possible to achieve with unique group 
-signatures~\cite{UniqueGroupSignatures,UniqueRingSignatures,ListSignatures}.
+We can now define the participation count as follows.
+\begin{definition}[Participation count]
+  We define the \emph{participation count} of a protest \(id\) as the 
+  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
+    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
+      j = id, s(p_{i,j})\geq \theta \right\}
+  \] for some strength function \(s\colon \powerset(W)\to \interval{0}{1}\) and 
+  a threshold \(\theta\).
+\end{definition}

### 2017-09-27 properties.tex
Writes up system model, moves adversary model to properties

@@
 \mode*
-\section{Desired properties}%
+\section{Desired security properties}%
 \label{Properties}
 
+%\subsection{An overview of the adversary}
+
+We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
+Alice the activist (and all the protesters) try to increase the count.
+Eve the totalitarian dictator tries to decrease the count.
+Additionally, Eve tries to deanonymize the participants to arrest them or 
+\enquote{convince} them to change their minds.
+Finally, we have Rusuk who is represents another nation state.
+Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
+gain, thus supporting either Eve or Alice as he see fits.
+Rusuk will thus also try to either increase or decrease the count.
+We will now formally define some security properties specifying the 
+computational effort needed by the adversaries to succeed.
 We categorize the desired properties into verifiability and privacy.
 
-\subsection{Verification}%
-\label{Verification}
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Alice the activist}
+    \begin{itemize}
+      \item Alice organizes the protest against Eve's regime.
+      \item Alice wants to have a high participation count.
+      \item She tries to increase it.
+      \item So does \emph{all the protesters}.
+    \end{itemize}
+  \end{block}
+
+  \pause{}
+
+  \begin{block}{Eve the fake-news populist}
+    \begin{itemize}
+      \item Eve's regime is target of the protest.
+      \item She wants to have a low participation count.
+      \item She tries to decrease it.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Eve the totalitarian dictator}
+    \begin{itemize}
+      \item Eve wants to \enquote{convince} activists to support her.
+      \item She wants to find all activists.
+      \item She tries to identify (deanonymize) participants.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{block}{Rusuk the nation state}
+    \begin{itemize}
+      \item Rusuk benefits from the situation in Evestan.
+      \item He wants the outcome to be the most beneficial.
+      \item He will try to increase or decrease the participation count.
+    \end{itemize}
+  \end{block}
+\end{frame}
+}
+
+\subsection{Verifiability}%
+\label{Verifiability}
 

### 2017-09-27 conclusions.tex
Makes minor improvements in disposition of slides
Removes open problems from conclusions
This part was only for FOSAD anyway.

@@
 
-\subsection<presentation>{Related work}
+\mode<presentation>{%
+\subsection{Related work}
+}
 
@@
 \end{frame}
-
-\subsection{Open problems}
-
-\begin{frame}
-  \frametitle{Sybil}
-  \begin{question}
-    How to solve Sybil, can we piggyback on existing \acp{PKI}?
-    E.g.\ through~\cite{Cinderella}.
-  \end{question}
-
-  \begin{question}
-    Can we otherwise bind identifiable keys to unique ring signature keys?
-  \end{question}
-
-  \begin{question}
-    Can we achieve receipt freeness (deniability) and protect from Sybil?
-  \end{question}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Anonymous communication}
-  \begin{question}
-    How do we submit the proofs to storage?
-  \end{question}
-
-  \mode<presentation>{%
-    \begin{remark}
-      Without anonymous submission we don't get proof privacy, thus no 
-      receipt freeness either.
-    \end{remark}
-  }
-\end{frame}
-
-\begin{frame}
-  \frametitle{Blockchains, distributed systems}
-  \begin{question}
-    \begin{itemize}
-      \item Malicious nodes want to provide Alice with a view that her proof is 
-        included.
-      \item Everyone else is provided a view without Alice.
-      \item How can we ensure a consistent view for everyone?
-    \end{itemize}
-  \end{question}
-
-  \begin{question}
-    Can we do blockchain branch and merge?
-  \end{question}
-\end{frame}

### 2017-09-28 SystemModel.tex
Generalizes, clarifies strength function
This fixes a part of #25, #26.

@@
       j = id, s(p_{i,j})\geq \theta \right\}
-  \] for some strength function \(s\colon \powerset(W)\to \interval{0}{1}\) and 
-  a threshold \(\theta\).
+  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
+  \(\theta\).
 \end{definition}
+
+The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
+A trivial example would be for \(s\) to return the number of witnesses and thus 
+let \(\theta\) to be the threshold of the number of required witnesses.

### 2017-09-28 properties.tex
Adds def of hardness of predicting future values

@@
 
+There are two aspects of temporal eligibility.
+The adversary can try to forge a witness for a future protest and the adversary 
+can try to forge a witness for a past protest.
+
+We first introduce something we call a \emph{time-authenticator tag}.
+This is an unpredictable value \(\tau_t\) which is published at time \(t\).
+The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
+advance, i.e.\ the use of \(\tau_t\) must have happened after time \(t\) with 
+high probability.
+
+\begin{definition}[Predicting the future]
+  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
+  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
+  (\(\lambda\) is the security parameter.)
+  Let \A be \iac{PPT} adversary.
+  The challenger gives \(T_{t-1}\) to \A.
+  \A is allowed to query an oracle \(O\) which returns whether a guess is 
+  correct or not.
+  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
+  the adversary wins.
+\end{definition}
+
+We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
+chance of winning will be
+\begin{equation}
+  \label{SuccessOfPrediction}
+  \Prob{%
+    \A^O(T_{t-1}, \lambda) = \tau_t
+  } = \frac{p(\lambda)}{2^\lambda}
+\end{equation}
+for some polynomial \(p(\cdot)\).
+This will be negligible for sufficiently a large \(\lambda\).
+
+\begin{definition}[Forging past witnesses]
+  \dots
+\end{definition}
+
 \begin{frame}

### 2017-09-28 properties.tex
Clarifies the idea for unpredictable future, adds two more problems

@@
 
-We first introduce something we call a \emph{time-authenticator tag}.
+The first thing we want to do is to prevent Alice from collecting witnesses for 
+a future protest.
+For this, we introduce something we call a \emph{time-authenticator tag}.
 This is an unpredictable value \(\tau_t\) which is published at time \(t\).
 The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
-advance, i.e.\ the use of \(\tau_t\) must have happened after time \(t\) with 
+advance, i.e.\ any use of \(\tau_t\) must have happened after time \(t\) with 
 high probability.
@@
 This will be negligible for sufficiently a large \(\lambda\).
+
+\begin{definition}[Collision]
+  Given tag \(\tau\), probability of collision?
+\end{definition}
+
+\begin{definition}[Changing the past]
+  Given a witness for time \(t\), change it to time \(t'\).
+  \dots
+\end{definition}
 

### 2017-09-28 protocol.tex

@@
 the signature using the same inputs.
+
+\subsubsection{Architecture}
+
+We also have an architectural problem.
+If the system is only run by volunteering activists, then Eve can simply 
+analyse network traffic and look for people running nodes in the system.
+
+\begin{question}
+  Shall we offer a platform that is run by a variety of institutions who 
+  offers to verify protests?
+  Or go strictly peer-to-peer?
+\end{question}
+
+\begin{question}
+  If strictly peer-to-peer, and only run by protesters, one can infer that 
+  they are protesters by running such a node.
+  Can this be mitigated?
+\end{question}
+
+Similarly, we have the problem of how protesters submit their proofs to the 
+system.
+This must be done anonymously.
+Otherwise Eve can analyse the network traffic to find out who submitted proofs 
+to the system.
+The main problem here is that the participants must be indistinguishable from 
+non-participants.
+This means that we cannot use special-purpose anonymizing 
+technologies.
+
+\begin{question}
+  How do we submit the proofs to storage?
+  Voting normally uses mix-nets (provable shuffles).
+\end{question}
+
+\begin{remark}
+  We must mix participants with non-participants.
+\end{remark}

### 2017-09-28 security.tex
Changes section title of security analysis

@@
 
-\section{Security}
+\section{Security and privacy analysis}%
+\label{SecurityAnalysis}
+
+\subsection{Assumptions}
+
+We assume that every participant has a device similar to a smartphone.
+Throughout this text, when we refer to a participant, say Alice, we actually 
+mean a principal which can perform cryptographic operations and communicate with 
+other local devices on Alice's behalf.
+(This means that we essentially provide a lower bound for the participation 
+count, since some participants might not have such a device.)
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{center}
+    Alice $:=$ Alice's cryptographic device
+  \end{center}
+\end{frame}
+}
+
+No connection to any global network the Internet is necessary during the 
+protest.
+During the protest these devices are computationally limited by their 
+batteries.
+Before and after the protest, we assume that the devices have Internet 
+connections and are not computationally limited by any battery.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{assumption}[During protest]
+    \begin{itemize}
+      \item Everyone has a smartphone.
+      \item Can use ad-hoc networks during the event.
+      \item Computations bounded by battery life.
+    \end{itemize}
+  \end{assumption}
+
+  \pause{}
+
+  \begin{assumption}[Before and after protest]
+    \begin{itemize}
+      \item Internet connection available.
+      \item Computations not bounded by battery life.
+    \end{itemize}
+  \end{assumption}
+
+  \pause{}
+
+  \begin{remark}
+    We provide a lower bound, since there might be participants without phones.
+  \end{remark}
+\end{frame}
+}
+
+We further assume that every participant has a digital certificate signed by 
+some logically centralized certificate authority.
+E.g.\ that we can use the cryptographic keys stored in the chip of the national 
+identity card or passport.
+We need this to prevent Sybil attacks~\cite{SybilAttack}.
 

### 2017-09-29 protocol.tex
Starts outlining the roles
Adds more roles in protocol
Adds intro, storage and temporal solution to protocol

@@
 
-\dots
+We will start by giving an overview of the protocol.
+We have a number of participants.
+We have a cothority who provide the storage in a decentralized manner.
+The cothority should consist of independent actors, preferably with conflicting 
+interests so that they will not collude.
+We have Alice the organizer and Bob the participant who are both protesters.
+We have the trustworthy journalist Jane who is present but not participating in 
+the protest.
+The protesters will witness each others participation proofs, e.g.\ Alice will 
+witness Bob's proof and Bob will witness Alice's proof.
+The result of witnessing a proof is a proof share (essentially a witness 
+signature).
+Jane will also participate in witnessing the protesters' proofs.
+The witnessing is done through local interaction.
+As soon as Alice and Bob have departed from the protest they upload their proofs 
+(i.e.\ all proof shares) to the cothority for indefinite storage.
+Since each proof consists of one proof share for each witness, each witness 
+could potentially upload the proof share themselves to the cothority.
+This would have the same effect but with added redundancy, in case Alice or Bob 
+cannot upload them themselves.
 
-\subsubsection{Temporal eligibility}
-
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-
-One primitive that fulfils \cref{CreatedAfterStart,CreatedBeforeEnd} is a 
-blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}.
-(See \cref{PosetGraph}.)
-For generality, we will use the terminology of 
-\textcite{BlockchainFreeCryptocurrencies} and simply call this storage 
-structure \iac{tposet}.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \input{fig/tposet.tex}
-  \mode<article>{%
-    \caption{%
-      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
-      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
-      are incomparable.
-    }\label{PosetGraph}
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1,2>{%
-    \begin{idea}[Temporal eligibility]
-      \begin{itemize}
-        \item We need a partially ordered set (poset).
-
-          \pause{}
-
-        \item There is a mechanism that provides this property: a blockchain.
-        \item There are also other structures, e.g.\ a directed 
-          graph~\cite{BlockchainFreeCryptocurrencies}.
-      \end{itemize}
-    \end{idea}
-  }
-  \only<3>{%
-    \begin{idea}[Created before end]
-      \begin{itemize}
-        \item Submit the proof to storage.
-        \item The proof must've been created before it was included.
-        \item If included before \(t_e\), then it was created before \(t_e\).
-      \end{itemize}
-    \end{idea}
-  }
-  \only<4>{%
-    \begin{idea}[Created after start]
-      \begin{itemize}
-        \item Include an unpredictable value in the proof.
-        \item This could be e.g.\ the hash of the \enquote{head} of the 
-          \ac{tposet}, (\(t_s\) in the figure).
-        \item This prevents creating proofs for future protests.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
-
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply add their 
-proofs to the \ac{tposet} \emph{in (time-wise) relation to the event}.
-In \cref{PosetGraph}, if \(t_e\) is verifiably related to the end of the 
-protest, then the relation will guarantee that \(p_A, p_B\) were created before 
-the end of the protest.
-Then we know that they cannot have been created after the event.
-
-For \cref{CreatedAfterStart} Alice and Bob must include an unpredictable value 
-in their proofs, e.g.\ \(t_s\) in \cref{PosetGraph}.
-This means that if \(t_s\) is sufficiently close (time-wise) to the protest and 
-has sufficiently high entropy, then Alice or Bob cannot create a proof and keep 
-it for a future protest.
-
-They can use an older value (pick one from the history of the \ac{tposet}) when 
-they create their proofs.
-This will only expand the interval of possible creation into the past.
-This will not help their cause, as anyone will recognize that the proof could 
-be created at any time in that interval, i.e.\ possibly before the protest.
-
-\subsubsection{Spatial eligibility}
+\subsection{Location proofs and spatial eligibility}
 
@@
 \end{frame}
+
+\subsection{Storage and temporal eligibility}
+
+We will use the storage to provide temporal eligibility.
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
+  set}\footnote{%
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
+} of objects.
+(See \cref{PosetGraph}.)
+If some objects in the set relate to known points in time, then the partial 
+order relates the data to the time of the event.
+This allows us to \emph{verify the data temporally}.
+One primitive that fulfils these requirements is a blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
+properties.
+However, we will use the blockchain in our discussion for simplicity.
+
+There are exactly two properties that we need.
+The first property we need is decentralized, immutable storage with a general 
+form of time-stamping.
+I.e.\ once we commit something to the blockchain it will remain there and we do 
+not have to trust any central authority.
+We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
+block appears approximately every 10 minutes.
+
+The second property we need is an unpredictable number whose time of publication 
+can be verified.
+For this property, we will use the head of the blockchain.
+The hash value of the head of the blockchain at a given time will be difficult 
+to predict ahead of time.
+%(See \cref{SecurityAnalysis} for a security analysis.)
+We want to use this to ensure that proofs are created after a certain point in 
+time.
+
+\begin{frame}
+\begin{figure}
+  \centering
+  \input{fig/tposet.tex}
+  \mode<article>{%
+    \caption{%
+      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
+      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
+      are incomparable.
+    }\label{PosetGraph}
+  }
+\end{figure}
+
+\mode<presentation>{%
+  \only<1,2>{%
+    \begin{idea}[Temporal eligibility]
+      \begin{itemize}
+        \item We need a partially ordered set (poset).
+
+          \pause{}
+
+        \item There is a mechanism that provides this property: a blockchain.
+        \item There are also other structures, e.g.\ a directed 
+          graph~\cite{BlockchainFreeCryptocurrencies}.
+      \end{itemize}
+    \end{idea}
+  }
+  \only<3>{%
+    \begin{idea}[Created before end]
+      \begin{itemize}
+        \item Submit the proof to storage.
+        \item The proof must've been created before it was included.
+        \item If included before \(t_e\), then it was created before \(t_e\).
+      \end{itemize}
+    \end{idea}
+  }
+  \only<4>{%
+    \begin{idea}[Created after start]
+      \begin{itemize}
+        \item Include an unpredictable value in the proof.
+        \item This could be e.g.\ the hash of the \enquote{head} of the 
+          \ac{tposet}, (\(t_s\) in the figure).
+        \item This prevents creating proofs for future protests.
+      \end{itemize}
+    \end{idea}
+  }
+}
+\end{frame}
+
+\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
+proofs to the blockchain as soon as possible after they have participated in the 
+protest.
+Thus we can infer that a proof (or proof share) was created at the latest when 
+it was committed.
+For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
+block in the blockchain.
+Then it is clear that the proof must have been created after that block (since 
+predicting such a value is hard).
 

### 2017-09-30 protocol.tex
Changes disposition of protocol section

@@
 cannot upload them themselves.
+
+We will now describe the protocol in more details.
+We will describe it in the same order as outlined above:
+starting with the storage and its required properties, then constructing the 
+participation proof (shares) and submitting the proof shares to storage.
+Finally, we will conclude with how to verify the proofs and produce the 
+participation count.
+
+\subsection{Storage and temporal eligibility}
+
+We will use the storage to provide temporal eligibility.
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
+  set}\footnote{%
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
+} of objects.
+(See \cref{PosetGraph}.)
+If some objects in the set relate to known points in time, then the partial 
+order relates the data to the time of the event.
+This allows us to \emph{verify the data temporally}.
+One primitive that fulfils these requirements is a blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
+properties.
+However, we will use the blockchain in our discussion for simplicity.
+
+There are exactly two properties that we need.
+The first property we need is decentralized, immutable storage with a general 
+form of time-stamping.
+I.e.\ once we commit something to the blockchain it will remain there and we do 
+not have to trust any central authority.
+We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
+block appears approximately every 10 minutes.
+
+The second property we need is an unpredictable number whose time of publication 
+can be verified.
+For this property, we will use the head of the blockchain.
+The hash value of the head of the blockchain at a given time will be difficult 
+to predict ahead of time.
+%(See \cref{SecurityAnalysis} for a security analysis.)
+We want to use this to ensure that proofs are created after a certain point in 
+time.
+
+\begin{frame}
+\begin{figure}
+  \centering
+  \input{fig/tposet.tex}
+  \mode<article>{%
+    \caption{%
+      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
+      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
+      are incomparable.
+    }\label{PosetGraph}
+  }
+\end{figure}
+
+\mode<presentation>{%
+  \only<1,2>{%
+    \begin{idea}[Temporal eligibility]
+      \begin{itemize}
+        \item We need a partially ordered set (poset).
+
+          \pause{}
+
+        \item There is a mechanism that provides this property: a blockchain.
+        \item There are also other structures, e.g.\ a directed 
+          graph~\cite{BlockchainFreeCryptocurrencies}.
+      \end{itemize}
+    \end{idea}
+  }
+  \only<3>{%
+    \begin{idea}[Created before end]
+      \begin{itemize}
+        \item Submit the proof to storage.
+        \item The proof must've been created before it was included.
+        \item If included before \(t_e\), then it was created before \(t_e\).
+      \end{itemize}
+    \end{idea}
+  }
+  \only<4>{%
+    \begin{idea}[Created after start]
+      \begin{itemize}
+        \item Include an unpredictable value in the proof.
+        \item This could be e.g.\ the hash of the \enquote{head} of the 
+          \ac{tposet}, (\(t_s\) in the figure).
+        \item This prevents creating proofs for future protests.
+      \end{itemize}
+    \end{idea}
+  }
+}
+\end{frame}
+
+\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
+proofs to the blockchain as soon as possible after they have participated in the 
+protest.
+Thus we can infer that a proof (or proof share) was created at the latest when 
+it was committed.
+For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
+block in the blockchain.
+Then it is clear that the proof must have been created after that block (since 
+predicting such a value is hard).
+
+\subsection{Constructing the participation-proof shares}
 
@@
 
-\subsection{Storage and temporal eligibility}
-
-We will use the storage to provide temporal eligibility.
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-(See \cref{PosetGraph}.)
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-One primitive that fulfils these requirements is a blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
-properties.
-However, we will use the blockchain in our discussion for simplicity.
-
-There are exactly two properties that we need.
-The first property we need is decentralized, immutable storage with a general 
-form of time-stamping.
-I.e.\ once we commit something to the blockchain it will remain there and we do 
-not have to trust any central authority.
-We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
-block appears approximately every 10 minutes.
-
-The second property we need is an unpredictable number whose time of publication 
-can be verified.
-For this property, we will use the head of the blockchain.
-The hash value of the head of the blockchain at a given time will be difficult 
-to predict ahead of time.
-%(See \cref{SecurityAnalysis} for a security analysis.)
-We want to use this to ensure that proofs are created after a certain point in 
-time.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \input{fig/tposet.tex}
-  \mode<article>{%
-    \caption{%
-      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
-      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
-      are incomparable.
-    }\label{PosetGraph}
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1,2>{%
-    \begin{idea}[Temporal eligibility]
-      \begin{itemize}
-        \item We need a partially ordered set (poset).
-
-          \pause{}
-
-        \item There is a mechanism that provides this property: a blockchain.
-        \item There are also other structures, e.g.\ a directed 
-          graph~\cite{BlockchainFreeCryptocurrencies}.
-      \end{itemize}
-    \end{idea}
-  }
-  \only<3>{%
-    \begin{idea}[Created before end]
-      \begin{itemize}
-        \item Submit the proof to storage.
-        \item The proof must've been created before it was included.
-        \item If included before \(t_e\), then it was created before \(t_e\).
-      \end{itemize}
-    \end{idea}
-  }
-  \only<4>{%
-    \begin{idea}[Created after start]
-      \begin{itemize}
-        \item Include an unpredictable value in the proof.
-        \item This could be e.g.\ the hash of the \enquote{head} of the 
-          \ac{tposet}, (\(t_s\) in the figure).
-        \item This prevents creating proofs for future protests.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
-
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
-proofs to the blockchain as soon as possible after they have participated in the 
-protest.
-Thus we can infer that a proof (or proof share) was created at the latest when 
-it was committed.
-For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
-block in the blockchain.
-Then it is clear that the proof must have been created after that block (since 
-predicting such a value is hard).
-
 \subsubsection{Individual and universal verifiability}

### 2017-09-30 protocol.tex
Adds a third required property for storage

@@
 
-There are exactly two properties that we need.
+There are three properties that we need from the storage system.
 The first property we need is decentralized, immutable storage with a general 
@@
 time.
+
+The third property is that once we have committed some data, we do not need to 
+keep the data itself, but we can store some confirmation value instead.
+E.g.\ using blockchains, we can store the hash of the block where our data was 
+committed, while this block remains we are sure that our data remains committed 
+--- even if we no longer remember what our data looked like.
+We will use this property to approximate the property of receipt freeness.
 

### 2017-09-30 protocol.tex
Edits temporal eligibility and moves up linkability

@@
 
-\Cref{CreatedBeforeEnd} is straight-forward, Alice and Bob simply commit their 
-proofs to the blockchain as soon as possible after they have participated in the 
-protest.
+With the above properties, \cref{CreatedBeforeEnd} is straight-forward: Alice 
+and Bob simply commit their proofs to the blockchain as soon as possible after 
+they have participated in the protest.
 Thus we can infer that a proof (or proof share) was created at the latest when 
 it was committed.
-For \cref{CreatedAfterStart} Alice and Bob must include the hash value of a 
-block in the blockchain.
+For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
+existing block in the blockchain.
 Then it is clear that the proof must have been created after that block (since 
@@
 
-\subsection{Location proofs and spatial eligibility}
+\subsubsection{Linkability and designated protest}
+
+\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
+individual can provide two proofs of participation and thus be counted twice.
+That situation should be detectable.
+We can do this by ensuring that Alice cannot produce two valid proofs which
+are unlinkable.
+This can be done by including a signature made by a verified key.
+(We will discuss the privacy aspects in \cref{Privacy}.)
+
+\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
+protest at the same time and place, these would have the same spatial and 
+temporal properties.
+To distinguish them, we also need to prove for which of these events that a 
+proof is designated.
+This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
+its \enquote{manifesto}.
+
+\begin{frame}
+\begin{figure}
+  \centering
+  \mode<presentation>{%
+    \only<1>{%
+      \begin{tikzpicture}
+        \tikzset{grow'=right,level distance=5em}
+        \Tree [.proof
+        {share}
+        [.{share} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
+        %[.tsig {$t_s''$} ]
+        ]
+        {share}
+        ]
+      \end{tikzpicture}
+    }
+  }
+  \only<2>{%
+    \begin{tikzpicture}
+      \tikzset{grow'=right,level distance=5em}
+      \Tree [.proof
+      {share}
+      [.{share} {\(x,y\)} {$t_s$} [.{osig} 
+      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
+      %[.tsig {$t_s''$} ]
+      ]
+      {share}
+      ]
+    \end{tikzpicture}
+  }
+  \mode<article>{%
+    \caption{%
+      The proof depends on several witness signatures (share), each of which 
+      depends on the owner's signature (osig), which depends on the \(id\) of the
+      protest and the head of the \ac{tposet}.
+      Whenever possible, the witness signature should include proof that the 
+      witness themself has been witnessed by a trusted witness (tsig).
+    }
+  }
+\end{figure}
+
+\mode<presentation>{%
+  \only<1>{%
+    \begin{idea}[Count once]
+      \begin{itemize}
+        \item Any two proofs by the same individual are linkable.
+        \item Includes signature made by a verified key.
+      \end{itemize}
+    \end{idea}
+  }
+
+  \only<2>{%
+    \begin{idea}[Designated event]
+      \begin{itemize}
+        \item Include a protest-specific identifier.
+        \item E.g.\ hash of the \enquote{manifesto}.
+      \end{itemize}
+    \end{idea}
+  }
+}
+\end{frame}
+
+\subsubsection{Location proofs and spatial eligibility}
 
@@
 \end{remark}
-
-\subsubsection{Linkability and designated protest}
-
-\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
-individual can provide two proofs of participation and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
-This can be done by including a signature made by a verified key.
-(We will discuss the privacy aspects in \cref{Privacy}.)
-
-\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
-protest at the same time and place, these would have the same spatial and 
-temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
-its \enquote{manifesto}.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \mode<presentation>{%
-    \only<1>{%
-      \begin{tikzpicture}
-        \tikzset{grow'=right,level distance=5em}
-        \Tree [.Proof
-        [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
-        %[.tsig {$t_s''$} ]
-        ]
-        {\dots}
-        [.{wsig} {\dots} ]
-        ]
-      \end{tikzpicture}
-    }
-  }
-  \only<2>{%
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} [.{osig} 
-      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
-      %[.tsig {$t_s''$} ]
-      ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  }
-  \mode<article>{%
-    \caption{%
-      The proof depends on several witness signatures (wsig), each of which 
-      depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
-      Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnessed by a trusted witness (tsig).
-    }
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1>{%
-    \begin{idea}[Count once]
-      \begin{itemize}
-        \item Any two proofs by the same individual are linkable.
-        \item Includes signature made by a verified key.
-      \end{itemize}
-    \end{idea}
-  }
-
-  \only<2>{%
-    \begin{idea}[Designated event]
-      \begin{itemize}
-        \item Include a protest-specific identifier.
-        \item E.g.\ hash of the \enquote{manifesto}.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
 

### 2017-09-30 primitives.tex
Changes section title of security analysis
Changes section title to locations proofs and distance bounding
Moves the description of storage to building blocks

--- 2016-07-18 primitives.tex
@@
-\section{Useful Primitives}
-\label{UsefulPrimitives}
+\section{Building blocks}%
+\label{Primitives}\label{BuildingBlocks}
 
 \dots
+
+\subsection{Zero-knowledge proofs}
+
+Briefly describe zero-knowledge proofs and what type of properties can be proved 
+efficiently using them, e.g.\ algebraic structures but not one-way functions.
+
+\dots
+
+\subsection{Location proofs and distance bounding}
+
+Briefly describe location proofs and distance bounding protocols.
+Describe the different desirable properties for distance bounding:
+\begin{itemize}
+  \item Mafia-fraud resistance,
+  \item terrorist-fraud resistance,
+  \item impersonation-fraud resistance,
+  \item distance-fraud resistance.
+\end{itemize}
+
+\subsection{Storage}
+
+We will use the storage to provide the temporal eligibility property.
+\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
+  set}\footnote{%
+  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
+} of objects.
+If some objects in the set relate to known points in time, then the partial 
+order relates the data to the time of the event.
+This allows us to \emph{verify the data temporally}.
+One primitive that fulfils these requirements is a blockchain.
+There are also other structures, e.g.\ a directed graph that 
+converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
+properties.
+However, we will use the blockchain in our discussion for simplicity.
+
+There are three properties that we need from the storage system.
+The first property we need is decentralized, immutable storage with a general 
+form of time-stamping.
+I.e.\ once we commit something to the blockchain it will remain there and we do 
+not have to trust any central authority.
+We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
+block appears approximately every 10 minutes.
+
+The second property we need is an unpredictable number whose time of publication 
+can be verified.
+For this property, we will use the head of the blockchain.
+The hash value of the head of the blockchain at a given time will be difficult 
+to predict ahead of time.
+%(See \cref{SecurityAnalysis} for a security analysis.)
+We want to use this to ensure that proofs are created after a certain point in 
+time.
+
+The third property is that once we have committed some data, we do not need to 
+keep the data itself, but we can store some confirmation value instead.
+E.g.\ using blockchains, we can store the hash of the block where our data was 
+committed, while this block remains we are sure that our data remains committed 
+--- even if we no longer remember what our data looked like.
+We will use this property to approximate the property of receipt freeness.

### 2017-09-30 protocol.tex
Moves the description of storage to building blocks

@@
 We will describe it in the same order as outlined above:
-starting with the storage and its required properties, then constructing the 
-participation proof (shares) and submitting the proof shares to storage.
-Finally, we will conclude with how to verify the proofs and produce the 
+starting with the construction of the participation proof (shares) and 
+submitting the proof shares to storage.
+Then we will conclude with how to verify the proofs and produce the 
 participation count.
-
-\subsection{Storage and temporal eligibility}
-
-We will use the storage to provide temporal eligibility.
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-(See \cref{PosetGraph}.)
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-One primitive that fulfils these requirements is a blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
-properties.
-However, we will use the blockchain in our discussion for simplicity.
-
-There are three properties that we need from the storage system.
-The first property we need is decentralized, immutable storage with a general 
-form of time-stamping.
-I.e.\ once we commit something to the blockchain it will remain there and we do 
-not have to trust any central authority.
-We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
-block appears approximately every 10 minutes.
-
-The second property we need is an unpredictable number whose time of publication 
-can be verified.
-For this property, we will use the head of the blockchain.
-The hash value of the head of the blockchain at a given time will be difficult 
-to predict ahead of time.
-%(See \cref{SecurityAnalysis} for a security analysis.)
-We want to use this to ensure that proofs are created after a certain point in 
-time.
-
-The third property is that once we have committed some data, we do not need to 
-keep the data itself, but we can store some confirmation value instead.
-E.g.\ using blockchains, we can store the hash of the block where our data was 
-committed, while this block remains we are sure that our data remains committed 
---- even if we no longer remember what our data looked like.
-We will use this property to approximate the property of receipt freeness.
 
@@
 
+\subsection{Constructing the participation-proof shares}
+
 With the above properties, \cref{CreatedBeforeEnd} is straight-forward: Alice 
@@
 predicting such a value is hard).
-
-\subsection{Constructing the participation-proof shares}
 
@@
 
-\subsubsection{Individual and universal verifiability}
+\subsection{Verifying the proofs}
 

### 2017-10-03 protocol.tex
Removes outdated slides

@@
 participation count.
-
-\begin{frame}
-\begin{figure}
-  \centering
-  \input{fig/tposet.tex}
-  \mode<article>{%
-    \caption{%
-      Alice submits proof \(p_A\) and Bob submits proof \(p_B\).
-      We have \(t_s\prec p_A, p_B\prec t_e\), but \((p_A, p_B)\notin \prec\) 
-      are incomparable.
-    }\label{PosetGraph}
-  }
-\end{figure}
-
-\mode<presentation>{%
-  \only<1,2>{%
-    \begin{idea}[Temporal eligibility]
-      \begin{itemize}
-        \item We need a partially ordered set (poset).
-
-          \pause{}
-
-        \item There is a mechanism that provides this property: a blockchain.
-        \item There are also other structures, e.g.\ a directed 
-          graph~\cite{BlockchainFreeCryptocurrencies}.
-      \end{itemize}
-    \end{idea}
-  }
-  \only<3>{%
-    \begin{idea}[Created before end]
-      \begin{itemize}
-        \item Submit the proof to storage.
-        \item The proof must've been created before it was included.
-        \item If included before \(t_e\), then it was created before \(t_e\).
-      \end{itemize}
-    \end{idea}
-  }
-  \only<4>{%
-    \begin{idea}[Created after start]
-      \begin{itemize}
-        \item Include an unpredictable value in the proof.
-        \item This could be e.g.\ the hash of the \enquote{head} of the 
-          \ac{tposet}, (\(t_s\) in the figure).
-        \item This prevents creating proofs for future protests.
-      \end{itemize}
-    \end{idea}
-  }
-}
-\end{frame}
 

### 2017-10-03 protocol.tex
Edits and moves temporal eligibility of protocol, adds overview

@@
 
-With the above properties, \cref{CreatedBeforeEnd} is straight-forward: Alice 
-and Bob simply commit their proofs to the blockchain as soon as possible after 
-they have participated in the protest.
-Thus we can infer that a proof (or proof share) was created at the latest when 
-it was committed.
-For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
-existing block in the blockchain.
-Then it is clear that the proof must have been created after that block (since 
-predicting such a value is hard).
-
-\subsubsection{Linkability and designated protest}
-
-\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one 
-individual can provide two proofs of participation and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
-This can be done by including a signature made by a verified key.
-(We will discuss the privacy aspects in \cref{Privacy}.)
-
-\Cref{DesignatedEvent} focuses on the problem that there might be a counter 
-protest at the same time and place, these would have the same spatial and 
-temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-This can be achieved by a unique identifier for a protest, e.g.\ the hash of 
-its \enquote{manifesto}.
+An overview of the structure of a proof is available in \cref{ProofFig}.
 
@@
       \begin{tikzpicture}
-        \tikzset{grow'=right,level distance=5em}
+        \tikzset{grow'=left,level distance=5em}
         \Tree [.proof
         {share}
-        [.{share} {\(x,y\)} {$t_s$} [.{\color{red}osig} {$t_s'$} ]
+        [.{share} {\(x,y\)} {$t_s'$} [.{\color{red}osig} {$t_s$} ]
         %[.tsig {$t_s''$} ]
@@
     \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
+      \tikzset{grow'=left,level distance=5em}
       \Tree [.proof
       {share}
-      [.{share} {\(x,y\)} {$t_s$} [.{osig} 
-      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s'$} ]
+      [.{share} {\(x,y\)} {$t_s'$} [.{osig} 
+      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s$} ]
       %[.tsig {$t_s''$} ]
@@
       witness themself has been witnessed by a trusted witness (tsig).
-    }
+    }%
+    \label{ProofFig}
   }
@@
 \end{frame}
+
+\subsubsection{Temporal eligibility}
+
+Given the properties of the storage (in \cref{StorageProperties}), 
+\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
+proofs to the blockchain as soon as possible after they have participated in the 
+protest.
+Thus we can infer that a proof (or proof share) was created at the latest when 
+it was committed.
+For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
+existing block in the blockchain (\(t_s\) in \cref{ProofFig}).
+Then it is clear that the proof must have been created after that block (since 
+predicting such a value is hard).
 

### 2017-10-03 SystemModel.tex
Fixes slides for system model
Adds WIP on linkability and designated protest (WIP #27)

@@
 }.
-Judging from these examples, the minimal common part is the cause.
+Judging from these examples, the minimal common part is the cause.%
+\label{CauseIsTheCommonDenominator}
 
@@
 to deploy enough personnel for crowd-control.)
-We will define a protest as an event that is uniquely identified by its cause, 
-its time and its location.
+We will define a protest as an event that is uniquely identified by its cause 
+(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
 More specifically, we will use the following definition.
@@
 We can now define the participation count as follows.
+\begin{frame}
 \begin{definition}[Participation count]
@@
 
+\pause{}
+
+\mode<presentation>{%
+  \begin{example}
+    \begin{itemize}
+      \item The strength function can regulate trust in witnesses.
+      \item E.g.\ return the number of witnesses.
+      \item \(\theta\) would control threshold of number of witnesses.
+    \end{itemize}
+  \end{example}
+}
+\end{frame}
+
 The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.

### 2017-10-03 protocol.tex
Adds WIP on linkability and designated protest (WIP #27)

@@
 \end{frame}
+
+\subsubsection{Linkability and designated protest}
+
+\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one individual 
+can provide two participation proofs and thus be counted twice.
+That situation should be detectable.
+We can do this by ensuring that Alice cannot produce two valid proofs which
+are unlinkable.
+\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
+share) for another event.
+E.g.\ there might be a counter protest at the same time and place, these would 
+have the same spatial and temporal properties.
+To distinguish them, we also need to prove for which of these events that a 
+proof is designated.
+The idea is to construct a unique identifier for a protest.
+
+We will start with the latter.
+The identifier of the protest must be regulated, for the same reasons as for the 
+user identifiers --- otherwise a counter-protest can simply choose the same 
+protest identifier.
+As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
+root of what defines a protest.
+The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
+the hash value of the manifesto as identifier of the protest.
+(As shown in \cref{ProofFig}.)
+
+\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
+which allows anonymous authentication at most \(n\) times\footnote{%
+  Possibly there is another system that makes it non-interactive, see issue 
+  \#27.
+}.
 

### 2017-10-04 protocol.tex
Updates ProofFig, adds identifier construction to protocol

@@
   \centering
-  \mode<presentation>{%
-    \only<1>{%
   \begin{tikzpicture}
@@
     {share}
-        [.{share} {\(x,y\)} {$t_s'$} [.{\color{red}osig} {$t_s$} ]
+    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
     %[.tsig {$t_s''$} ]
@@
   \end{tikzpicture}
-    }
-  }
-  \only<2>{%
-    \begin{tikzpicture}
-      \tikzset{grow'=left,level distance=5em}
-      \Tree [.proof
-      {share}
-      [.{share} {\(x,y\)} {$t_s'$} [.{osig} 
-      [.{\mode<presentation>{\color{red}}\(id\)} manifesto ] {$t_s$} ]
-      %[.tsig {$t_s''$} ]
-      ]
-      {share}
-      ]
-    \end{tikzpicture}
-  }
   \mode<article>{%
   \caption{%
-      The proof depends on several witness signatures (share), each of which 
-      depends on the owner's signature (osig), which depends on the \(id\) of the
-      protest and the head of the \ac{tposet}.
-      Whenever possible, the witness signature should include proof that the 
-      witness themself has been witnessed by a trusted witness (tsig).
-    }%
+    The proof depends on several proof shares.
+    Each share depends on the protester's identifier (\(pid\), which depends on 
+    the cause identifier, \(cid\)),
+    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
+    identifier (\(wid\)).
+  }}%
   \label{ProofFig}
-  }
 \end{figure}
-
-\mode<presentation>{%
-  \only<1>{%
-    \begin{idea}[Count once]
-      \begin{itemize}
-        \item Any two proofs by the same individual are linkable.
-        \item Includes signature made by a verified key.
-      \end{itemize}
-    \end{idea}
-  }
-
-  \only<2>{%
-    \begin{idea}[Designated event]
-      \begin{itemize}
-        \item Include a protest-specific identifier.
-        \item E.g.\ hash of the \enquote{manifesto}.
-      \end{itemize}
-    \end{idea}
-  }
-}
 \end{frame}
@@
 the hash value of the manifesto as identifier of the protest.
-(As shown in \cref{ProofFig}.)
+(As shown as manifesto and \(id\) in \cref{ProofFig}.)
 
@@
 which allows anonymous authentication at most \(n\) times\footnote{%
-  Possibly there is another system that makes it non-interactive, see issue 
-  \#27.
+  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
+  \Textcite{Psignatures}, see issue \#27.
 }.
+Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
+national identity-card (by assumption).
+She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
+identity during the protest.
+She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
+knows a signature by the identity authority on \(k\).
+Thus \(pid\) will be used as the unique identifier in the proof shares and the 
+\ac{NIZK} proof will prove the eligibility of \(pid\).
 

### 2017-10-04 protocol.tex
Adds how to propagate protest ID (fixes #40)

@@
 The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
-the hash value of the manifesto as identifier of the protest.
-(As shown as manifesto and \(id\) in \cref{ProofFig}.)
+the hash value of the manifesto as identifier of the protest (cause).
+(As shown as manifesto and cause identifier \(cid\) in \cref{ProofFig}.)
 
+To practically propagate this identifier to the protesters the organizer can 
+have a placard with a large QR code that either contains the entire manifesto or 
+at least links to a website hosting the manifesto.
+The user can scan this QR code with a protesting app which will automatically 
+fetch it, show it to the protester for approval and then compute the identifier 
+\(cid\).
+
+Next we need to consider the protesters' identifiers to prevent Sybil attacks.
 \Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 

### 2017-10-04 protocol.tex
Splits temporal eligibility in protocol in two parts

@@
 knows a signature by the identity authority on \(k\).
-Thus \(pid\) will be used as the unique identifier in the proof shares and the 
-\ac{NIZK} proof will prove the eligibility of \(pid\).
+Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
+computations below) whereas the \ac{NIZK} proof will be used separately to prove 
+the validity (eligibility) of \(pid\).
 
-\subsubsection{Temporal eligibility}
+\subsubsection{Temporal eligibility, created after start}
 
-Given the properties of the storage (in \cref{StorageProperties}), 
-\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
-proofs to the blockchain as soon as possible after they have participated in the 
-protest.
-Thus we can infer that a proof (or proof share) was created at the latest when 
-it was committed.
-For \cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
-existing block in the blockchain (\(t_s\) in \cref{ProofFig}).
+Given the properties of the storage (in \cref{StorageProperties}), for 
+\cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
+existing block in the blockchain in each proof share (shown as \(t_s\) in 
+\cref{ProofFig}).
 Then it is clear that the proof must have been created after that block (since 
@@
 \end{remark}
+
+\subsubsection{Temporal eligibility, created before end}
+
+Given the properties of the storage system in \cref{StorageProperties}, 
+\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
+proofs to the blockchain as soon as possible after they have participated in the 
+protest.
+Thus we can infer that a proof (or proof share) was created at the latest when 
+it was committed.
 

### 2017-10-04 protocol.tex
Renames labels of figs, adds stub for protocol diagram

@@
 
-An overview of the structure of a proof is available in \cref{ProofFig}.
+An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
+and an overview of the communication is given in \cref{fig:ProtocolOverview}.
 
@@
   }}%
-  \label{ProofFig}
+  \label{fig:ProofFig}
 \end{figure}
 \end{frame}
+
+\begin{figure}
+  \centering
+  \dots
+  \caption{%
+    \dots
+  }%
+  \label{fig:ProtocolOverview}
+\end{figure}
 
@@
 the hash value of the manifesto as identifier of the protest (cause).
-(As shown as manifesto and cause identifier \(cid\) in \cref{ProofFig}.)
+(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)
 
@@
 existing block in the blockchain in each proof share (shown as \(t_s\) in 
-\cref{ProofFig}).
+\cref{fig:ProofFig}).
 Then it is clear that the proof must have been created after that block (since 

### 2017-10-04 protocol.tex
Moves discussion of NIZK proof to submission time
Improves proof overview figure (fixes #41)

@@
   \centering
-  \begin{tikzpicture}
-    \tikzset{grow'=left,level distance=5em}
-    \Tree [.proof
-    {share}
-    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
-    %[.tsig {$t_s''$} ]
-    ]
-    {share}
-    ]
+  \begin{tikzpicture}[<-,item/.style={rectangle,draw}]
+    \tikzset{%
+      %grow'=left,%
+      %level distance=5em%
+    }
+    \node[item] (proof) {Proof share}
+      child {%
+        node[item] (pid) {$pid$}
+        child {%
+          node[item] (cid) {$cid$}
+          child {%
+            node[item] (manifesto) {Manifesto}
+          }
+        }
+      }
+      child {%
+        node[item] (ts) {$t_s$}
+      }
+      child {%
+        node[item] (l) {$l$}
+      }
+      child {%
+        node[item] (wid) {$wid$}
+      }
+      ;
+
+      \path[every node/.style={font=\small}]
+      (wid) edge[bend left] node [anchor=north] {$PRF_{k_w}(\cdot)$} (pid)
+      (cid) edge node [anchor=east] {$H(\cdot)$} (manifesto)
+      (pid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (cid)
+      ;
+
+%    \Tree [.proof
+%    {share}
+%    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
+%    %[.tsig {$t_s''$} ]
+%    ]
+%    {share}
+%    ]
   \end{tikzpicture}
@@
 identity during the protest.
-She must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
-knows a signature by the identity authority on \(k\).
-Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
-computations below) whereas the \ac{NIZK} proof will be used separately to prove 
-the validity (eligibility) of \(pid\).
 
@@
 \subsection{Verifying the proofs}
+
+Alice must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
+knows a signature by the identity authority on \(k\).
+Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
+computations below) whereas the \ac{NIZK} proof will be used separately to prove 
+the validity (eligibility) of \(pid\).
 

### 2017-10-04 protocol.tex
Changes arrow tips in proof-share overview
Completes proof-share diagram

--- 2017-10-04 protocol.tex
@@
   \centering
-  \begin{tikzpicture}
-    \tikzset{grow'=left,level distance=5em}
-    \Tree [.proof
-    {share}
-    [.{share} {\(wid\)} {\(l\)} {$t_s$} [.{\(pid\)} [.{\(cid\)} manifesto ] ]
-    %[.tsig {$t_s''$} ]
+  \begin{tikzpicture}[%
+    -Latex,
+    item/.style={rectangle,draw},
+    edge from parent/.style={}
     ]
-    {share}
-    ]
+    \tikzset{%
+      %grow'=left,%
+      %level distance=5em%
+    }
+    \node[item] (proof) {Proof share}
+      child {%
+        node[item] (pid) {$pid$}
+        child {%
+          node[item] (cid) {$cid$}
+          child {%
+            node[item] (manifesto) {Manifesto}
+          }
+        }
+      }
+      child {%
+        node[item] (wid) {$wid$}
+      }
+      child {%
+        node[item] (ts) {$t_s$}
+      }
+      child {%
+        node[item] (l) {$l$}
+      }
+      child {%
+        node[item] (wsig) {$wsig$}
+      }
+      ;
+
+      \path[every node/.style={font=\small}]
+      (pid) edge node [anchor=east] {$\in$} (proof)
+      (ts) edge node [anchor=east] {$\in$} (proof)
+      (l) edge node [anchor=east] {$\in$} (proof)
+      (wid) edge node [anchor=east] {$\in$} (proof)
+      (wsig) edge node [anchor=east] {$\in$} (proof)
+      ;
+
+      \path[every node/.style={font=\small}]
+      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
+      (cid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (pid)
+      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot)$} (wid)
+      % wsig
+      (l) edge[bend right] (wsig)
+      (ts) edge[bend right] (wsig)
+      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot, \cdot, 
+        \cdot)$} (wsig)
+      ;
+
   \end{tikzpicture}
@@
   \caption{%
-    The proof depends on several proof shares.
-    Each share depends on the protester's identifier (\(pid\), which depends on 
-    the cause identifier, \(cid\)),
-    the head of the blockchain (\(t_s\)), the location (\(l\)) and the witness 
-    identifier (\(wid\)).
+    Structure of a proof share.
+    The protester's identifier \(pid\) is computed using the protester's key 
+    \(k_p\).
+    The witness's identifier \(wid\) is computed using the witness's key 
+    \(k_w\).
+    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
   }}%

### 2017-10-04 protocol.tex
Adds placeholder caption for protocol message sequence diagram
Fixes minor details in proof-share figure

@@
       \path[every node/.style={font=\small}]
-      (pid) edge node [anchor=east] {$\in$} (proof)
+      (pid) edge node [anchor=south east] {$\in$} (proof)
+      (wid) edge node [anchor=east] {$\in$} (proof)
       (ts) edge node [anchor=east] {$\in$} (proof)
-      (l) edge node [anchor=east] {$\in$} (proof)
-      (wid) edge node [anchor=east] {$\in$} (proof)
-      (wsig) edge node [anchor=east] {$\in$} (proof)
+      (l) edge node [anchor=west] {$\in$} (proof)
+      (wsig) edge node [anchor=south west] {$\in$} (proof)
       ;
@@
   \caption{%
-    \dots
+    An overview of message exchanges.
   }%

### 2017-10-04 protocol.tex
Adds sketch of protocol diagram
This diagram should be rewritten using a nice protocol diagram package.

@@
     Structure of a proof share.
-    The protester's identifier \(pid\) is computed using the protester's key 
-    \(k_p\).
-    The witness's identifier \(wid\) is computed using the witness's key 
-    \(k_w\).
+    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
+    key \(k_P\).
+    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
+    \(k_W\).
     \(t_s\) is a time interval and \(l\) is the coordinates of an area.
+    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
   }}%
   \label{fig:ProofFig}
-\end{figure}
+\end{figure}%
 \end{frame}
 
+\begin{frame}
 \begin{figure}
   \centering
-  \dots
+  \begin{minipage}{\linewidth}
+    \begin{align*}
+      O\to \text{all}\colon & \text{manifesto} \\
+      P\colon & pid\gets PRF_{k_P}(cid) \\
+      P\to W\colon & pid \\
+      W\colon & wid\gets PRF_{k_W}(pid), \\
+        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
+      W\to P\colon & (wid, t_s, l, wsig) \\
+      W\to S\colon & (pid, wid, t_s, l, wsig) \\
+      P\to S\colon & (pid, wid, t_s, l, wsig)
+    \end{align*}
+  \end{minipage}
   \caption{%
     An overview of message exchanges.
+    The organizer \(O\) broadcasts the manifesto.
+    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
+    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
   }%

### 2017-10-04 protocol.tex
Adds clarification and fixes typo
Clarifies committing of proof shares

@@
   \Textcite{Psignatures}, see issue \#27.
-}.
+}, where \(n = 1\) in our scenario.
 Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
 national identity-card (by assumption).
-She will use \(k\) to compute \(pid\gets PRF_k(id)\), which is her anonymous 
-identity during the protest.
+She will use \(k\) to compute \(pid\gets PRF_k(cid)\), which is her anonymous 
+identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
 
@@
 
+The proofs (shares) can be submitted to storage in two steps:
+first, committing them to the blockchain; second, to submit all the required 
+data.
+This will allow some time for computing all the required \ac{NIZK} proofs 
+(discussed in the following section).
+
 Given the properties of the storage system in \cref{StorageProperties}, 
-\cref{CreatedBeforeEnd} is straight-forward: Alice and Bob simply commit their 
-proofs to the blockchain as soon as possible after they have participated in the 
-protest.
+\cref{CreatedBeforeEnd} is straight-forward: once a proof share is created it 
+should be committed to the blockchain as soon as possible.
 Thus we can infer that a proof (or proof share) was created at the latest when 
 it was committed.
+
+We note that there are at least two entities who know each proof share, the 
+protester and the witness.
+Alice and Bob simply commit their proofs (i.e.\ all proof shares of their 
+proofs) to the blockchain as soon as possible after they have participated in 
+the protest.
+The witnesses do the same, they commit all the proof shares that they helped 
+create.
+(Shown in \cref{fig:ProtocolOverview}.)
 

### 2017-10-05 protocol.tex
Clarifies that hash must be included in each share

@@
 Given the properties of the storage (in \cref{StorageProperties}), for 
-\cref{CreatedAfterStart}, Alice and Bob must include the hash value of an 
+\cref{CreatedAfterStart}, each witness must include the hash value of an 
 existing block in the blockchain in each proof share (shown as \(t_s\) in 
@@
 predicting such a value is hard).
+This value can either be provided to the witness by the protester or the witness 
+uses the value of the last known block.
 

### 2017-10-05 protocol.tex
Adds details to protocol overview fig, prepares for distance bounding

@@
       O\to \text{all}\colon & \text{manifesto} \\
-      P\colon & pid\gets PRF_{k_P}(cid) \\
+      P\colon & cid\gets H(\text{manifesto}), \\
+        & pid\gets PRF_{k_P}(cid) \\
       P\to W\colon & pid \\
+      W\leftrightarrow P\colon & \text{perform distance bounding} \\
       W\colon & wid\gets PRF_{k_W}(pid), \\
@@
 
-\Cref{SpatiallyRelated} binds the data spatially to the location, which allows 
-us to \emph{verify the data spatially}.
+According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
+(shares) spatially to the location, which would allow us to verify that they 
+were actually in that location.
+The role of the witnesses, e.g.\ Jane, is to provide this property.
+Jane can do this by using a distance-bounding protocol to ensure that the secret 
+associated with Alice or Bob must be within limited physical distance.
 
-If we include \iac{LP}, this will tie the proof to the physical location and, 
-thus, solve \cref{SpatiallyRelated}.
-The \ac{LP} is \enquote{witnessed} (signed) by other participants.
-The \ac{LP} contains coarse coordinates of the location, which must be within 
-the protest area to be valid.
-This allows Bob the protester to move within the protest area to collect 
-witnesses (signatures).
-It also provides privacy since the location cannot be used to deanonymize Bob's 
-proof --- e.g.\ to correlate the location in his proof with captured 
-surveillance footage.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{figure}
-    \centering
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  \end{figure}
-
-  \begin{idea}[Spatial eligibility]
-    \begin{itemize}
-      \item Include \iac{LP} which is \enquote{witnessed} (signed) by other 
-        participants.
-      \item We have a coarse location, just within the protest area.
-      \item This allows protesters to move around to collect signatures.
-      \item This provides privacy for the location, e.g.\ cannot map to 
-        surveillance cameras.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\mode<none>{%
-\begin{frame}
-  \begin{idea}[Transitive trust]
-    \begin{itemize}
-      \item Trusted journalist Jane attends to report.
-      \item She witnesses Alice's proof.
-
-        \pause{}
-
-      \item Alice witnesses Bob's proof.
-      \item Alice's (secret key's) transportation is physically limited.
-      \item Trust on Bob's proof is proportional to time from when Jane 
-        witnessed Alice's proof.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-
-\begin{frame}
-  \begin{figure}
-    \centering
-    \begin{tikzpicture}
-      \tikzset{grow'=right,level distance=5em}
-      \Tree [.Proof
-      [.{wsig} {\(x,y\)} {$t_s$} [.{\color{red}tsig} {$t_s'$} ] ]
-      {\dots}
-      [.{wsig} {\dots} ]
-      ]
-    \end{tikzpicture}
-  \end{figure}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Secret key in hardware.
-      \item Alice's witness signature must depend on Jane's.
-      \item High-precision relation to time?
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
-We will introduce a notion of transitivity for trust in these proofs.
-The \emph{trusted} journalist Jane attends the protest to report on it.
-She witnesses some participants' \acp{LP}, say Alice's \ac{LP} for example.
-Now Alice's \ac{LP} can be trusted as correct at that point in time.
-Alice's ability to travel is physically limited.
-Thus a verifier can trust any \ac{LP} that Alice witnesses proportionally to 
-the time that has passed since Jane witnessed Alice's \ac{LP}.
-We can apply this argument recursively for any other participant's \ac{LP} that 
-Alice has witnessed.
-However, this requires some assumptions:
-\begin{itemize}
-  \item It is actually Alice's signing key must have physically limited travel.
-    This can be assumed for signing keys that are embedded into hardware by 
-    some trusted person.
-  \item Alice's witness signature must depend on Jane's witness signature, to 
-    prove that Alice signed after Jane.
-\end{itemize}
-\begin{remark}
-  This probably requires high-precision timestamps, i.e.\ a trusted 
-  time-stamping server must be available during the protest.
-  Or the proofs must be submitted to the \ac{tposet} during the protest.
-\end{remark}
+Alice will send her \(pid\) to Jane to start the witness protocol.
+Then they do the distance bounding \dots
+If Jane is convinced that Alice's secret is within the desired proximity, she 
+will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
+send them to Alice.
 

### 2017-10-05 protocol.tex
Fixes typos in ProofFig

@@
       (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
-      (cid) edge node [anchor=east] {$PRF_{k_p}(\cdot)$} (pid)
-      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot)$} (wid)
+      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
+      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
       % wsig
@@
       (ts) edge[bend right] (wsig)
-      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_w}(\cdot, \cdot, 
+      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
         \cdot)$} (wsig)

### 2017-10-06 protocol.tex
Adapts disposition of protocol sect, adapts to slides

@@
+\mode*
 \section{Protocol}
@@
   \end{minipage}
+  \mode<article>{%
   \caption{%
@@
     Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
-  }%
+  }}%
   \label{fig:ProtocolOverview}
@@
 
-\subsection{Verifying the proofs}
+\subsection{Verifying the participation count}
+
+There are three parts to verifying the participation count.
+First, we must verify the eligibility of each proof, i.e.\ of all its shares.
+
+\subsubsection{Verifying eligibility}
+
+To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
+and \(wsig\) are not just randomly generated numbers but they actually depend on 
+the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
+We will do this with \ac{NIZK} proofs.
 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{idea}[Individual verifiability]
-    \begin{itemize}
-      \item Proofs are stored (committed) publicly.
-      \item Each participant can check that their proof is indeed included.
-    \end{itemize}
-  \end{idea}
+\subsubsection{Universal verifiability}
 
-  \pause{}
+\dots
 
-  \begin{idea}[Universal verifiability]
-    \begin{itemize}
-      \item Proofs are stored (committed) publicly.
-      \item Anyone can download all proofs, verify eligibility and then count 
-        them.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
+\subsubsection{Individual verifiability and receipt freeness}
 
-\subsubsection{Participation-proof privacy}
-
-A demonstration is very different from voting in one sense: at a demonstration, 
-Alice must be physically present and that very presence shows her support for 
-the cause.
-In voting, on the other hand, everyone is present and Alice has multiple 
-options which are not revealed by her mere presence.
-% XXX Check if unlinkable is the correct term
-Hence, if Alice submits a proof of participation, the proof must be unlinkable 
-to Alice, yet, if Alice submits another proof, those two proofs must be 
-linkable (due to eligibility verification, \cref{EligibilityVerif}) so that 
-Alice is not counted twice.
-This is fine, since we do not want to catch any cheater, we just do not want to
-count them more than once.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item Voting: different alternatives when participating.
-      \item Protesting: participation implies the alternative.
-    \end{itemize}
-  \end{remark}
-
-  \pause{}
-
-  \begin{idea}[Proof privacy]
-    \begin{itemize}
-      \item Eve shouldn't be able to link Alice's published proof back to 
-        Alice.
-      \item But if Alice publishes two proofs, those two are linkable.
-
-        \pause{}
-
-      \item We're not interested in unmasking trolls, just not count them more 
-        than once.
-    \end{itemize}
-  \end{idea}
-\end{frame}
-}
-
-\begin{frame}
-  \begin{remark}
-    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
-    signatures are linked with high probability.
-  \end{remark}
-
-  \begin{question}
-    Can we link a verified key to a unique ring signature key?
-  \end{question}
-
-  \pause{}
-
-  \begin{question}
-    How to submit the proofs to the system?
-  \end{question}
-\end{frame}
-
-\subsubsection{Receipt freeness}
+\dots
 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item The proof itself is a sort of receipt.
-
-        \pause{}
-
-      \item If Eve compromises Alice's device, she can use it to verify that 
-        she participated.
-
-        \pause{}
-
-      \item We need a signature scheme that cannot reproduce the same signature 
-        when run on the same inputs.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
-\begin{frame}
-\mode<presentation>{%
-  \begin{idea}[Receipt freeness (deniability)]
-    \begin{itemize}
-      \item Alice submits her proof.
-      \item She stores the hash of the head of the \ac{tposet}.
-      \item She removes the proof and signature key.
-
-        \pause{}
-
-      \item E.g.\ a short-term and a long-term credential, then Alice can 
-        drop the short-term credential.
-
-      \item But Alice should still not be able to participate twice.
-    \end{itemize}
-  \end{idea}
-}
-
-  \pause{}
-
-  \begin{question}
-    Is there such a signature scheme?
-    Can we construct it?
-  \end{question}
-\end{frame}
-
 Say that Alice submits her proof and stores the hash of the head of the 
@@
 the signature using the same inputs.
-
-\subsubsection{Architecture}
-
-We also have an architectural problem.
-If the system is only run by volunteering activists, then Eve can simply 
-analyse network traffic and look for people running nodes in the system.
-
-\begin{question}
-  Shall we offer a platform that is run by a variety of institutions who 
-  offers to verify protests?
-  Or go strictly peer-to-peer?
-\end{question}
-
-\begin{question}
-  If strictly peer-to-peer, and only run by protesters, one can infer that 
-  they are protesters by running such a node.
-  Can this be mitigated?
-\end{question}
-
-Similarly, we have the problem of how protesters submit their proofs to the 
-system.
-This must be done anonymously.
-Otherwise Eve can analyse the network traffic to find out who submitted proofs 
-to the system.
-The main problem here is that the participants must be indistinguishable from 
-non-participants.
-This means that we cannot use special-purpose anonymizing 
-technologies.
-
-\begin{question}
-  How do we submit the proofs to storage?
-  Voting normally uses mix-nets (provable shuffles).
-\end{question}
-
-\begin{remark}
-  We must mix participants with non-participants.
-\end{remark}

### 2017-10-06 protocol.tex
Restructures eligibility and universal verifiability
Adds refs to issues, fixes eligibility and universal

@@
 Then they do the distance bounding \dots
+[See issue \#22 for the discussion.]
 If Jane is convinced that Alice's secret is within the desired proximity, she 
@@
 First, we must verify the eligibility of each proof, i.e.\ of all its shares.
+Second, we must count these valid proofs.
+Third, each protester must check that their proof is indeed registered so that 
+it can be counted.
 
-\subsubsection{Verifying eligibility}
+\subsubsection{Eligibility and universal verifiability}
 
+Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
+to count the valid proofs.
+To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
+its shares) and then count it if valid.
 To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
@@
 We will do this with \ac{NIZK} proofs.
+We note that these proofs are not needed until the verification step after the 
+protest.
+Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
+above) whereas their respective \ac{NIZK} proof can be computed and published 
+after the protest.
 
-Alice must also provide \iac{NIZK} proof that \(pid = PRF_k(id)\) and that she 
-knows a signature by the identity authority on \(k\).
-Thus \(pid\) will be used as the unique identifier in the proof shares (and all 
-computations below) whereas the \ac{NIZK} proof will be used separately to prove 
-the validity (eligibility) of \(pid\).
+Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
+that she knows a signature by the identity authority on \(k_P\).
+\dots
+[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
+issue \#27 for discussion.]
 
-If the proofs are stored publicly, then an individual can check that their 
-proof has been included (committed) there.
-Thus \cref{IndividualVerif} is fulfilled.
-Similarly for universal verifiability.
-If the storage is public, then anyone can download all the proofs, verify their 
-eligibility and count them.
-Thus anyone can verify the result, which fulfils \cref{UniversalVerif}.
-
-\subsubsection{Universal verifiability}
-
-\dots
+In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
+  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
+witness knows a signature by the identity authority on \(k_W\).
+With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
+eligibility, of the proof shares and thus also count them.
 
 \subsubsection{Individual verifiability and receipt freeness}
+
+If the proofs are stored publicly, then an individual can check that their proof 
+has been included (committed) there.
+Thus \cref{IndividualVerif} is fulfilled.
 

### 2017-10-09 protocol.tex
Clarifies commit and submission of proofs in protocol fig

@@
       W\to P\colon & (wid, t_s, l, wsig) \\
-      W\to S\colon & (pid, wid, t_s, l, wsig) \\
-      P\to S\colon & (pid, wid, t_s, l, wsig)
+      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
+      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
+      W\to S\colon & (pid, wid, t_s, l, wsig),\\
+        & NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
+        sign(k_W)) \\
+      P\to S\colon & (pid, wid, t_s, l, wsig),\\
+        & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
     \end{align*}

### 2017-10-09 protocol.tex
Adds individual verif and receipt freeness to protocol

@@
 
-If the proofs are stored publicly, then an individual can check that their proof 
-has been included (committed) there.
-Thus \cref{IndividualVerif} is fulfilled.
+The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
+an adversary from dropping participation proofs.
+Thus each protester must verify that their own proof is indeed included.
+This can be accomplished as follows.
+After Alice commited to her proof (share) in the blockchain, she stores the hash 
+of the block.
+At a later time, she can still verify that the block is indeed still there.
+At this point, this hash value is the only thing she must store for individual 
+verifiability.
 
-\dots
-
-Receipt freeness implies that Alice enjoys deniability against Eve:
-Eve should not be able to use the published proof to tie it to Alice, even if 
-Eve has access to Alice's device (i.e.\ all her private keys).
-E.g.\ Eve should not be able to reproduce the same proof and thus verify that 
-Alice has created one of the proofs.
-
-Say that Alice submits her proof and stores the hash of the head of the 
-\ac{tposet} after her proof is included.
-Now she can remove her proof and just keep the hash to verify that her proof is 
-still there.
-She can also remove her signature key, so that Eve cannot use it to reproduce 
-the signature using the same inputs.
+More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
+must remove her secret PRF key, \(k_A\).
+With this key Eve can verify that Alice has submitted a proof by computing 
+\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).

### 2017-10-09 SystemModel.tex
Syncs notation of system model with protocol

@@
 \begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((id, t, l)\) where
-  \(id\in \Z_{2^\lambda}\) is an identifier,
+  A \emph{subprotest} is a tuple \((cid, t, l)\) where
+  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
+    I.e.\ the cause of the protest.
+  } identifier,
   \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
@@
 \begin{definition}[Witness]
-  A \emph{witness} \(w = (pid, id, t, l, wid)\) is a tuple where
-  \(id, t, l\) are as in \cref{DefProtest},
+  A \emph{witness} \(w = (pid, cid, t, l, wid)\) is a tuple where
+  \(cid, t, l\) are as in \cref{DefProtest},
   \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
@@
     p_{i, j} =
-    \left\{ (pid, id, t, l, wid)\in W \mid
+    \left\{ (pid, cid, t, l, wid)\in W \mid
     %\right. &
-    pid = i, id = j,
+    pid = i, cid = j,
     %\\ & \left.
@@
 \begin{definition}[Participation count]
-  We define the \emph{participation count} of a protest \(id\) as the 
-  cardinality \(|P_{id}^{s,\theta}|\) of the set of participation proofs \[
-    P_{id}^{s,\theta} = \left\{ p_{i,j} \mid
-      j = id, s(p_{i,j})\geq \theta \right\}
+  We define the \emph{participation count} of a protest \(cid\) as the 
+  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
+    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
+      j = cid, s(p_{i,j})\geq \theta \right\}
   \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 

### 2017-10-19 primitives.tex
Splits and clarifies storage requirements

@@
 
-\subsection{Storage}
+\subsection{Storage}%
+\label{StorageProperties}
 
@@
 
-There are three properties that we need from the storage system.
-The first property we need is decentralized, immutable storage with a general 
-form of time-stamping.
-I.e.\ once we commit something to the blockchain it will remain there and we do 
-not have to trust any central authority.
-We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
-block appears approximately every 10 minutes.
+There are five properties that we need from the storage system, all of which 
+makes a blockchain-like structure suitable.
+First, we need immutability.
+I.e.\ once we commit something to the blockchain it will remain there.
+We will use this to ensure verifiability, the data must remain to be verifiable.
 
-The second property we need is an unpredictable number whose time of publication 
-can be verified.
+Second, we need a general form of time-stamping.
+I.e.\ we must be able to relate commitments to time, e.g.\ in 
+Bitcoin~\cite{Bitcoin} a new block appears approximately every 10 minutes.
+This coarse-grained form of time-stamping is enough for our purposes.
+We will use this property to ensure that proofs are created before a certain 
+point in time.
+
+Third, we need an unpredictable number whose time of publication can be 
+verified.
 For this property, we will use the head of the blockchain.
@@
 
-The third property is that once we have committed some data, we do not need to 
-keep the data itself, but we can store some confirmation value instead.
+Fourth, once we have committed some data, we do not need to keep the data 
+itself, but we can store some confirmation value instead.
 E.g.\ using blockchains, we can store the hash of the block where our data was 
@@
 We will use this property to approximate the property of receipt freeness.
+
+Finally, if the storage is decentralized we do not have to trust any central 
+authority, which is the usual case for blockchains.

### 2017-11-14 contents-poster.tex
Adds files for poster

\begin{center}
  \Huge Securely and Privately Verifiable Protests
\end{center}
\begin{center}
  Daniel Bosk $\bullet$ Sonja Buchegger $\bullet$ Sébastien Gambs
\end{center}
\vspace{1.5em}

\begin{columns}

  \begin{column}{0.49\linewidth}

    \begin{block}{Test}
      Testing
    \end{block}

  \end{column}
  \hfill
  \begin{column}{0.49\linewidth}

    \begin{block}{Test again}
      Testing again
    \end{block}

  \end{column}

\end{columns}

### 2017-11-15 contents-poster.tex
Updates design
Makes columns top-aligned, adds contents to poster

@@
 \begin{center}
-  \Huge Securely and Privately Verifiable Protests
+  \Huge\bfseries
+  Securely and Privately Verifiable Protests
 \end{center}
 \begin{center}
+  \large
   Daniel Bosk $\bullet$ Sonja Buchegger $\bullet$ Sébastien Gambs
@@
 
-\begin{columns}
+\begin{columns}[t]
 
-  \begin{column}{0.49\linewidth}
+  \begin{column}{0.32\linewidth}
 
-    \begin{block}{Test}
-      Testing
+    \begin{block}{Scenario: The crowd-counting problem}
+      \begin{itemize}
+        \item Alice organizes a protest against Eve's regime.
+        \item Bob, Carol and others show up.
+        \item We want to know how many showed up to support Alice.
+      \end{itemize}
     \end{block}
 
+    \begin{figure}
+      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
+    \end{figure}
+
+    \begin{example}[Current methods]
+      \begin{itemize}
+        \item Computer vision does object recognition.
+        \item Requires photos/video that cover the entire location, all the time.
+        \item This will count people twice.
+      \end{itemize}
+    \end{example}
+
+    \begin{example}[Suggested ideas]
+      \begin{itemize}
+        \item Scan active mobile phones in the area.
+        \item This requires some extra equipment.
+        \item This catches bystanders who are not protesting.
+      \end{itemize}
+    \end{example}
+
+    \begin{redblock}{Verifying protest participation}
+      \begin{itemize}
+        \item Alice organizes a protest against Eve's regime.
+        \item Bob, Carol and others show up.
+        \item {\color{olive!10!green!90} Alice wants to show that many support 
+            her cause.}
+        \item {\color{red} Eve wants to show that few support Alice's cause.}
+        \item It's an adversarial setting!
+        \item We need verifiable results.
+      \end{itemize}
+    \end{redblock}
+
+    \begin{requirements}[V]
+    \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
+      participation proof provides temporal and spatial eligibility and that it 
+      has not been counted before.
+
+    \item\label{UniversalVerif} Universal verifiability: anyone can verify that 
+      the result is according to the submitted participation proofs.
+
+    \item\label{IndividualVerif} Individual verifiability: every participant can 
+      verify that their participation proof is included in the global count.
+    \end{requirements}
+
   \end{column}
+
   \hfill
-  \begin{column}{0.49\linewidth}
 
-    \begin{block}{Test again}
-      Testing again
+  \begin{column}{0.32\linewidth}
+
+    \begin{block}{Designated protest}
+      \begin{itemize}
+        \item A protest is identified by its cause, captured in a 
+          manifesto.
+        \item The hash of the manifesto provides an unpredictable identifier 
+          (\(cid\) in figures).
+        \item It's difficult to create a second manifesto that disagrees but 
+          gets the same identifier.
+      \end{itemize}
+    \end{block}
+
+    \begin{block}{Privacy-preserving linkability}
+      \begin{itemize}
+        \item We want linkability to prevent Sybil attacks.
+        \item We also want privacy.
+        \item We use techniques from anonymous credentials to create identifiers 
+          (\(pid, wid\) in figures).
+        \item The identifiers are random but unique per protest, i.e.\ depends 
+          on \(cid\).
+        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
+          verification).
+      \end{itemize}
+    \end{block}
+
+    \begin{block}{Temporal eligibility}
+      \begin{itemize}
+        \item We use a blockchain for commitments, freshness.
+        \item Freshness: a protester must include the head (hash value) of the 
+          blockchain in their proof shares (\(t_s\) in figures).
+        \item This value is difficult to guess and prevents preparing proofs too 
+          long in advance.
+        \item Commitments: when a proof share is prepared, it is committed to 
+          the blockchain for timestamping.
+      \end{itemize}
+    \end{block}
+
+    \begin{block}{Location proofs and spatial eligibility}
+      \begin{itemize}
+        \item Each proof must be bound to the location.
+        \item This is done using witnesses.
+        \item A witness runs a distance-bounding protocol to ensure proximity.
+        \item If in proximity, the witness will issue a witness identifier and 
+          signature (\(wid, wsig\)).
+      \end{itemize}
+    \end{block}
+
+\begin{block}{Verifying the participation count}
+
+There are three parts to verifying the participation count.
+First, we must verify the eligibility of each proof, i.e.\ of all its shares.
+Second, we must count these valid proofs.
+Third, each protester must check that their proof is indeed registered so that 
+it can be counted.
+
+\end{block}
+
+\begin{block}{Eligibility and universal verifiability}
+
+Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
+to count the valid proofs.
+To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
+its shares) and then count it if valid.
+To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
+and \(wsig\) are not just randomly generated numbers but they actually depend on 
+the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
+We will do this with \ac{NIZK} proofs.
+We note that these proofs are not needed until the verification step after the 
+protest.
+Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
+above) whereas their respective \ac{NIZK} proof can be computed and published 
+after the protest.
+
+Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
+that she knows a signature by the identity authority on \(k_P\).
+\dots
+[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
+issue \#27 for discussion.]
+
+In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
+  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
+witness knows a signature by the identity authority on \(k_W\).
+With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
+eligibility, of the proof shares and thus also count them.
+
+\end{block}
+
+\begin{block}{Individual verifiability and receipt freeness}
+
+The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
+an adversary from dropping participation proofs.
+Thus each protester must verify that their own proof is indeed included.
+This can be accomplished as follows.
+After Alice commited to her proof (share) in the blockchain, she stores the hash 
+of the block.
+At a later time, she can still verify that the block is indeed still there.
+At this point, this hash value is the only thing she must store for individual 
+verifiability.
+
+More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
+must remove her secret PRF key, \(k_A\).
+With this key Eve can verify that Alice has submitted a proof by computing 
+\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).
+
 \end{block}
@@
 
+  \hfill
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{figure}
+      \centering
+      \begin{tikzpicture}[%
+        -Latex,
+        item/.style={rectangle,draw},
+        edge from parent/.style={},
+        ]
+        \tikzset{%
+          %grow'=left,%
+          %level distance=5em%
+        }
+        \node[item] (proof) {Proof share}
+        child {%
+          node[item] (pid) {$pid$}
+          child {%
+            node[item] (cid) {$cid$}
+            child {%
+              node[item] (manifesto) {Manifesto}
+            }
+          }
+        }
+        child {%
+          node[item] (wid) {$wid$}
+        }
+        child {%
+          node[item] (ts) {$t_s$}
+        }
+        child {%
+          node[item] (l) {$l$}
+        }
+        child {%
+          node[item] (wsig) {$wsig$}
+        }
+        ;
+
+        \path[every node/.style={font=\small}]
+        (pid) edge node [anchor=south east] {$\in$} (proof)
+        (wid) edge node [anchor=east] {$\in$} (proof)
+        (ts) edge node [anchor=east] {$\in$} (proof)
+        (l) edge node [anchor=west] {$\in$} (proof)
+        (wsig) edge node [anchor=south west] {$\in$} (proof)
+        ;
+
+        \path[every node/.style={font=\small}]
+        (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
+        (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
+        (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
+        % wsig
+        (l) edge[bend right] (wsig)
+        (ts) edge[bend right] (wsig)
+        (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
+          \cdot)$} (wsig)
+        ;
+
+      \end{tikzpicture}
+      \caption{%
+        Structure of a proof share.
+        The protester \(P\)'s identifier \(pid\) is computed using the protester's 
+        key \(k_P\).
+        The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
+        \(k_W\).
+        \(t_s\) is a time interval and \(l\) is the coordinates of an area.
+        The protest (cause) identifier \(cid\) is the hash value of the manifesto.
+      }%
+      \label{fig:ProofFig}
+    \end{figure}%
+
+    \begin{figure}
+      \centering
+      \begin{minipage}{\linewidth}
+        \begin{align*}
+          O\to \text{all}\colon & \text{manifesto} \\
+          P\colon & cid\gets H(\text{manifesto}), \\
+          & pid\gets PRF_{k_P}(cid) \\
+          P\to W\colon & pid \\
+          W\leftrightarrow P\colon & \text{perform distance bounding} \\
+          W\colon & wid\gets PRF_{k_W}(pid), \\
+          & wsig\gets PRF_{k_W}(wid, t_s, l) \\
+          W\to P\colon & (wid, t_s, l, wsig) \\
+          W\to S\colon & H(pid, wid, t_s, l, wsig) \\
+          P\to S\colon & H(pid, wid, t_s, l, wsig) \\
+          W\to S\colon & (pid, wid, t_s, l, wsig),\\
+          & NIZK(wid = PRF_{k_W}(pid), \\
+          & wsig = PRF_{k_W}(wid, t_s, l), \exists sign(k_W)) \\
+          P\to S\colon & (pid, wid, t_s, l, wsig),\\
+          & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
+        \end{align*}
+      \end{minipage}
+      \caption{%
+        An overview of message exchanges.
+        The organizer \(O\) broadcasts the manifesto.
+        \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
+        Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
+      }%
+      \label{fig:ProtocolOverview}
+    \end{figure}
+
+    \begin{purpleblock}{Conclusions}
+      \dots
+    \end{purpleblock}
+
+    \printbibliography[heading=none]
+
+  \end{column}
+
 \end{columns}

### 2017-11-15 contents-poster.tex
Breaks long line in protocol figure

@@
           & NIZK(wid = PRF_{k_W}(pid), \\
-          & wsig = PRF_{k_W}(wid, t_s, l), \exists sign(k_W)) \\
+            & wsig = PRF_{k_W}(wid, t_s, l), \\
+            & \exists sign(k_W)) \\
           P\to S\colon & (pid, wid, t_s, l, wsig),\\

### 2017-11-15 contents-poster.tex
Updates colouring of blocks

@@
 
-    \begin{block}{Scenario: The crowd-counting problem}
+    \begin{blueblock}{Scenario: The crowd-counting problem}
       \begin{itemize}
@@
         \item Bob, Carol and others show up.
-        \item We want to know how many showed up to support Alice.
+        \item We want to know how many showed up to support Alice's cause.
       \end{itemize}
-    \end{block}
+    \end{blueblock}
 
@@
       \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
+      \caption{%
+        Mostly used method, Jacob's method: divide the area into regions, 
+        estimate the density in each region, sum them up.
+      }
     \end{figure}
 
-    \begin{example}[Current methods]
+    \begin{orangeblock}{Computer vision methods}
       \begin{itemize}
@@
       \end{itemize}
-    \end{example}
+    \end{orangeblock}
 
-    \begin{example}[Suggested ideas]
+    \begin{orangeblock}{Other methods}
       \begin{itemize}
@@
       \end{itemize}
-    \end{example}
+    \end{orangeblock}
 
@@
 
-    \begin{requirements}[V]
+    \begin{blueblock}{Requirements}
+      \begin{itemize}
         \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
-      participation proof provides temporal and spatial eligibility and that it 
-      has not been counted before.
+          participation proof provides temporal and spatial eligibility and that 
+          it has not been counted before.
 
-    \item\label{UniversalVerif} Universal verifiability: anyone can verify that 
-      the result is according to the submitted participation proofs.
+        \item\label{UniversalVerif} Universal verifiability: anyone can verify 
+          that the result is according to the submitted participation proofs.
 
-    \item\label{IndividualVerif} Individual verifiability: every participant can 
-      verify that their participation proof is included in the global count.
-    \end{requirements}
+        \item\label{IndividualVerif} Individual verifiability: every participant 
+          can verify that their participation proof is included in the global 
+          count.
+      \end{itemize}
+    \end{blueblock}
+
+    \begin{greenblock}{Our approach}
+      \dots
+    \end{greenblock}
 

### 2017-11-15 contents-poster.tex
Improves colour coding of blocks

@@
 
-    \begin{blueblock}{Requirements}
+    \begin{blueblock}{Requirements for verifiability}
       \begin{itemize}
@@
 
+    \begin{blueblock}{Requirements for privacy}
+      \begin{itemize}
+        \item The verifiability protocol should not increase the risk already 
+          incurred by attending.
+      \end{itemize}
+    \end{blueblock}
+
     \begin{greenblock}{Our approach}
@@
 
-    \begin{block}{Designated protest}
+    \begin{blackblock}{Designated protest}
       \begin{itemize}
@@
       \end{itemize}
-    \end{block}
+    \end{blackblock}
 
-    \begin{block}{Privacy-preserving linkability}
+    \begin{blackblock}{Privacy-preserving linkability}
       \begin{itemize}
@@
       \end{itemize}
-    \end{block}
+    \end{blackblock}
 
-    \begin{block}{Temporal eligibility}
+    \begin{blackblock}{Temporal eligibility}
       \begin{itemize}
@@
       \end{itemize}
-    \end{block}
+    \end{blackblock}
 
-    \begin{block}{Location proofs and spatial eligibility}
+    \begin{blackblock}{Location proofs and spatial eligibility}
       \begin{itemize}
@@
       \end{itemize}
-    \end{block}
+    \end{blackblock}
 
-\begin{block}{Verifying the participation count}
+    \begin{blueblock}{Verifying the participation count}
+      \begin{enumerate}
+        \item We must verify the eligibility of each proof, i.e.\ of all its 
+          shares.
+        \item We must count these valid proofs.
+        \item Each protester must check that their proof is indeed registered so 
+          that it can be counted.
+      \end{enumerate}
+    \end{blueblock}
 
-There are three parts to verifying the participation count.
-First, we must verify the eligibility of each proof, i.e.\ of all its shares.
-Second, we must count these valid proofs.
-Third, each protester must check that their proof is indeed registered so that 
-it can be counted.
-
-\end{block}
-
-\begin{block}{Eligibility and universal verifiability}
+\begin{blackblock}{Eligibility and universal verifiability}
 
@@
 
-\end{block}
+\end{blackblock}
 
-\begin{block}{Individual verifiability and receipt freeness}
+\begin{blackblock}{Individual verifiability and receipt freeness}
 
@@
 
-\end{block}
+\end{blackblock}
 

### 2017-11-15 contents-poster.tex
Adds our approach

@@
     \begin{greenblock}{Our approach}
-      \dots
+      \begin{itemize}
+        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
+          placard).
+        \item Each protester scans the QR code, computes a protest (cause) 
+          identifier (\(cid\)).
+        \item Each protester computes a personal identifier (\(pid\)), 
+          unlinkable between protests,
+        \item Each protester acts as witness (unlinkable between protesters) for 
+          other protesters by creating participation-proof shares.
+        \item Proof shares are committed to a blockchain.
+        \item Anyone can verify the proofs (all shares) and count them.
+      \end{itemize}
     \end{greenblock}

### 2017-11-15 contents-poster.tex
Clarifies and shortens first column

@@
         \item Bob, Carol and others show up.
-        \item We want to know how many showed up to support Alice's cause.
+        \item Must know how many showed up to support Alice's cause.
       \end{itemize}
@@
 
-    \begin{figure}
+    \begin{orangeblock}{Currently most popular method}
+      \centering
       \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
-      \caption{%
-        Mostly used method, Jacob's method: divide the area into regions, 
-        estimate the density in each region, sum them up.
-      }
-    \end{figure}
+      \begin{itemize}
+        \item Mostly used method, Jacob's method.
+        \item Divide the area into regions, estimate the density in each 
+          region, sum them up.
+        \item \color{red} Cannot handle cumulative counts.
+      \end{itemize}
+    \end{orangeblock}
 
@@
         \item Requires photos/video that cover the entire location, all the time.
-        \item This will count people twice.
+        \item \color{red} This will count people twice.
       \end{itemize}
@@
         \item This requires some extra equipment.
-        \item This catches bystanders who are not protesting.
+        \item \color{red} This catches bystanders who are not protesting.
       \end{itemize}
@@
       \begin{itemize}
-        \item Alice organizes a protest against Eve's regime.
-        \item Bob, Carol and others show up.
         \item {\color{olive!10!green!90} Alice wants to show that many support 
@@
         \item {\color{red} Eve wants to show that few support Alice's cause.}
-        \item It's an adversarial setting!
-        \item We need verifiable results.
+        \item Adversarial setting, requires verifiable results!
       \end{itemize}

### 2017-11-16 contents-poster.tex
Fixes typo, minor edits

@@
       \begin{itemize}
-        \item Mostly used method, Jacob's method.
+        \item Most used method, Jacob's method.
         \item Divide the area into regions, estimate the density in each 
@@
       \begin{itemize}
-        \item {\color{olive!10!green!90} Alice wants to show that many support 
-            her cause.}
-        \item {\color{red} Eve wants to show that few support Alice's cause.}
-        \item Adversarial setting, requires verifiable results!
+        \item Alice wants to show that many support her cause.
+        \item Eve wants to show that few support Alice's cause.
+        \item \color{red} Adversarial setting, requires verifiable results!
       \end{itemize}

### 2017-11-16 contents-poster.tex
Adds whiteblock and changes blocks, edits middle column

@@
 
-    \begin{blackblock}{Designated protest}
+    \begin{greenblock}{Our approach: during protest}
+      \begin{itemize}
+        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
+          placard).
+        \item Each protester scans the QR code, computes a protest (cause) 
+          identifier (\(cid\)) to designate their participation.
+        \item Each protester computes a personal identifier (\(pid\)), 
+          unlinkable between protests,
+        \item Each protester acts as witness (unlinkable between protesters) for 
+          other protesters by creating participation-proof shares.
+        \item Proof shares vouches for temporal and spatial eligibility.
+      \end{itemize}
+    \end{greenblock}
+
+    \begin{whiteblock}{Designated protest}
       \begin{itemize}
@@
       \end{itemize}
-    \end{blackblock}
+    \end{whiteblock}
 
-    \begin{blackblock}{Privacy-preserving linkability}
+    \begin{whiteblock}{Privacy-preserving linkability}
       \begin{itemize}
-        \item We want linkability to prevent Sybil attacks.
-        \item We also want privacy.
-        \item We use techniques from anonymous credentials to create identifiers 
+        \item Need linkability during a protest to prevent Sybil attacks.
+        \item Also need privacy.
+        \item Uses techniques from anonymous credentials to create identifiers 
           (\(pid, wid\) in figures).
@@
       \end{itemize}
-    \end{blackblock}
+    \end{whiteblock}
 
-    \begin{blackblock}{Temporal eligibility}
+    \begin{whiteblock}{Temporal eligibility}
       \begin{itemize}
@@
       \end{itemize}
-    \end{blackblock}
+    \end{whiteblock}
 
-    \begin{blackblock}{Location proofs and spatial eligibility}
+    \begin{whiteblock}{Location proofs and spatial eligibility}
       \begin{itemize}
@@
       \end{itemize}
-    \end{blackblock}
+    \end{whiteblock}
 
-    \begin{blueblock}{Verifying the participation count}
-      \begin{enumerate}
-        \item We must verify the eligibility of each proof, i.e.\ of all its 
-          shares.
-        \item We must count these valid proofs.
-        \item Each protester must check that their proof is indeed registered so 
-          that it can be counted.
-      \end{enumerate}
-    \end{blueblock}
+    \begin{greenblock}{Our approach: after the protest}
+      \begin{itemize}
+        \item Proof shares are committed to a blockchain as soon as possible.
+        \item \ac{NIZK} proofs are submitted whenever convenient.
+        \item Anyone can verify the proofs: eligibility, universal and 
+          individual verifiability.
+        \item Must be done for all shares and their \ac{NIZK} proofs.
+        \item Count all \(pid\)s with valid proofs.
+      \end{itemize}
+    \end{greenblock}
 
-\begin{blackblock}{Eligibility and universal verifiability}
+    \begin{whiteblock}{Eligibility and universal verifiability}
+      \begin{itemize}
+        \item Verify that \(pid\), \(wid\) and \(wsig\) are correct, i.e.\ verify 
+          their \ac{NIZK} proofs.
+        \item \ac{NIZK} proofs must show \(pid = PRF_{k_P}(id)\) and \(k_P\) is 
+          signed by \iac{CA}.
+        \item \ac{NIZK} proofs must show \(wid = PRF_{k_W}(pid), wsig = 
+            PRF_{k_W}(wid, t_s, l)\) and \(k_W\) is signed by \iac{CA}.
+      \end{itemize}
+    \end{whiteblock}
 
-Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
-to count the valid proofs.
-To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
-its shares) and then count it if valid.
-To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
-and \(wsig\) are not just randomly generated numbers but they actually depend on 
-the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
-We will do this with \ac{NIZK} proofs.
-We note that these proofs are not needed until the verification step after the 
-protest.
-Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
-above) whereas their respective \ac{NIZK} proof can be computed and published 
-after the protest.
-
-Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
-that she knows a signature by the identity authority on \(k_P\).
-\dots
-[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
-issue \#27 for discussion.]
-
-In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
-  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
-witness knows a signature by the identity authority on \(k_W\).
-With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
-eligibility, of the proof shares and thus also count them.
-
-\end{blackblock}
-
-\begin{blackblock}{Individual verifiability and receipt freeness}
-
-The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
-an adversary from dropping participation proofs.
-Thus each protester must verify that their own proof is indeed included.
-This can be accomplished as follows.
-After Alice commited to her proof (share) in the blockchain, she stores the hash 
-of the block.
-At a later time, she can still verify that the block is indeed still there.
-At this point, this hash value is the only thing she must store for individual 
-verifiability.
-
-More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
-must remove her secret PRF key, \(k_A\).
-With this key Eve can verify that Alice has submitted a proof by computing 
-\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).
-
-\end{blackblock}
+    \begin{whiteblock}{Individual verifiability and receipt freeness}
+      \begin{itemize}
+        \item Each protester can verify that their proof is available on the 
+          blockchain.
+        \item Protester no longer needs to keep the proof, just the hash.
+        \item Eve can use \(k_P\) to redo the computations to verify 
+          participation:
+          \[pid'\gets PRF_{k_A}(cid) \text{ and compare } pid = pid'.\]
+        \item However, requires arrest.
+      \end{itemize}
+    \end{whiteblock}
 

### 2017-11-16 contents-poster.tex
Changes related methods to whiteblocks
Updates approach

@@
 
-    \begin{orangeblock}{Currently most popular method}
+    \begin{figure}
       \centering
       \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
+      \caption{%
+        Jacob's method. Image: popularmechanics.com
+      }\label{JacobsMethod}
+    \end{figure}
+
+    \begin{whiteblock}{Jacob's method, most used method}
       \begin{itemize}
-        \item Most used method, Jacob's method.
+        \item Most used method, Jacob's method (\cref{JacobsMethod}).
         \item Divide the area into regions, estimate the density in each 
@@
       \end{itemize}
-    \end{orangeblock}
+    \end{whiteblock}
 
-    \begin{orangeblock}{Computer vision methods}
+    \begin{whiteblock}{Computer vision methods}
       \begin{itemize}
@@
       \end{itemize}
-    \end{orangeblock}
+    \end{whiteblock}
 
-    \begin{orangeblock}{Other methods}
+    \begin{whiteblock}{Other methods}
       \begin{itemize}
@@
       \end{itemize}
-    \end{orangeblock}
+    \end{whiteblock}
 
@@
 
-    \begin{greenblock}{Our approach}
+    \begin{greenblock}{Our approach: user's perspective}
       \begin{itemize}
-        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
-          placard).
-        \item Each protester scans the QR code, computes a protest (cause) 
-          identifier (\(cid\)).
-        \item Each protester computes a personal identifier (\(pid\)), 
-          unlinkable between protests,
-        \item Each protester acts as witness (unlinkable between protesters) for 
-          other protesters by creating participation-proof shares.
-        \item Proof shares are committed to a blockchain.
-        \item Anyone can verify the proofs (all shares) and count them.
+        \item The organizer publishes the protest's manifesto, e.g.\ QR-code on 
+          placard.
+        \item Each protester has a smartphone with a protest app.
+        \item Each protester scans the QR code with the app.
+        \item The app communicates with other apps locally, e.g.\ ad-hoc network 
+          or Bluetooth.
+        \item The apps issues participation proofs to each other.
+        \item Once there is an Internet connection, the proofs are submitted to 
+          a blockchain.
+        \item Anyone can verify the proofs on the blockchain and count the valid 
+          ones.
       \end{itemize}
@@
       \begin{itemize}
-        \item The organizer publishes the protest's manifesto (e.g.\ QR-code on 
-          placard).
-        \item Each protester scans the QR code, computes a protest (cause) 
-          identifier (\(cid\)) to designate their participation.
+        \item The organizer publishes the protest's manifesto.
+        \item Each protester reads it, approves it, computes a protest (cause) 
+          identifier (\(cid\)) to designate which protest they participate in.
         \item Each protester computes a personal identifier (\(pid\)), 
@@
         \item Proof shares vouches for temporal and spatial eligibility.
+        \item A threshold-based number of valid shares is a valid proof.
       \end{itemize}
@@
         \item The hash of the manifesto provides an unpredictable identifier 
-          (\(cid\) in figures).
+          (\(cid\) in \cref{ProofShare,Protocol}).
         \item It's difficult to create a second manifesto that disagrees but 
@@
         \item Uses techniques from anonymous credentials to create identifiers 
-          (\(pid, wid\) in figures).
+          (\(pid, wid\) in \cref{ProofShare,Protocol}).
         \item The identifiers are random but unique per protest, i.e.\ depends 
@@
         \item Freshness: a protester must include the head (hash value) of the 
-          blockchain in their proof shares (\(t_s\) in figures).
+          blockchain in their proof shares (\(t_s\) in 
+          \cref{ProofShare,Protocol}).
         \item This value is difficult to guess and prevents preparing proofs too 
@@
       \begin{itemize}
-        \item Each proof must be bound to the location.
+        \item Each proof must be bound to the location (\(l\) in 
+          \cref{ProofShare,Protocol}).
         \item This is done using witnesses.
@@
           participation:
-          \[pid'\gets PRF_{k_A}(cid) \text{ and compare } pid = pid'.\]
-        \item However, requires arrest.
+          \[pid'\gets PRF_{k_P}(cid) \text{ and compare } pid = pid'.\]
+        \item However, requires arrest and access to key.
       \end{itemize}
@@
       }%
-      \label{fig:ProofFig}
+      \label{ProofShare}
     \end{figure}%
@@
       }%
-      \label{fig:ProtocolOverview}
+      \label{Protocol}
     \end{figure}
@@
     \begin{purpleblock}{Conclusions}
-      \dots
+      \begin{itemize}
+        \item \dots
+      \end{itemize}
     \end{purpleblock}

### 2017-11-16 contents-poster.tex
Adds logos
Adds QR-code, fixes spacing for logos
Adds some conclusions

@@
+\begin{columns}
+  \begin{column}{0.17\linewidth}
+    \includegraphics[width=0.5\linewidth]{fig/kth_cmyk.eps}
+    \hfill
+  \end{column}
+  \hfill
+  \begin{column}{0.64\linewidth}
     \begin{center}
@@
       \large
-  Daniel Bosk $\bullet$ Sonja Buchegger $\bullet$ Sébastien Gambs
+      Daniel Bosk <dbosk@kth.se>
+      $\bullet$
+      Sonja Buchegger
+      $\bullet$
+      Sébastien Gambs
     \end{center}
     \vspace{1.5em}
+  \end{column}
+  \hfill
+  \begin{column}{0.17\linewidth}
+    \hfill
+    \includegraphics[width=0.8\linewidth]{fig/uqam.pdf}
+  \end{column}
+\end{columns}
 
@@
       \begin{itemize}
-        \item \dots
+        \item Provides a \emph{lower bound} of the participation count.
+        \item Provides a verifiable participation count, as strong as the 
+          blockchain is immutable.
+        \item Provides privacy based on anonymous credentials.
+        \item The only added risk (over not using this) is if someone can use 
+          your secret key (\(k_P\)).
+        \item Requires only local connectivity during the protest.
       \end{itemize}
@@
 
+    %\vspace{10cm}
+    \begin{center}
+      \includegraphics[width=0.5\linewidth]{fig/qr.eps}
+    \end{center}
+
   \end{column}

### 2017-11-16 contents-poster.tex
Changes "user's perspective" to "overview"
Adds line to protocol showing what's during and after

@@
 
-    \begin{greenblock}{Our approach: user's perspective}
+    \begin{greenblock}{Our approach: overview}
       \begin{itemize}
@@
           & wsig\gets PRF_{k_W}(wid, t_s, l) \\
-          W\to P\colon & (wid, t_s, l, wsig) \\
+          W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
+          && \text{during} \\ \hline && \text{after} \\[-1em]
           W\to S\colon & H(pid, wid, t_s, l, wsig) \\

### 2017-11-17 contents-poster.tex
Adds xkcd style comic explanations

--- 2017-11-16 contents-poster.tex
@@
 
+\includegraphics[width=\linewidth]{art/ProtestVerif.png}
+
 \begin{columns}[t]
@@
   \begin{column}{0.32\linewidth}
-
-    \begin{blueblock}{Scenario: The crowd-counting problem}
-      \begin{itemize}
-        \item Alice organizes a protest against Eve's regime.
-        \item Bob, Carol and others show up.
-        \item Must know how many showed up to support Alice's cause.
-      \end{itemize}
-    \end{blueblock}
-
-    \begin{figure}
-      \centering
-      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
-      \caption{%
-        Jacob's method. Image: popularmechanics.com
-      }\label{JacobsMethod}
-    \end{figure}
-
-    \begin{whiteblock}{Jacob's method, most used method}
-      \begin{itemize}
-        \item Most used method, Jacob's method (\cref{JacobsMethod}).
-        \item Divide the area into regions, estimate the density in each 
-          region, sum them up.
-        \item \color{red} Cannot handle cumulative counts.
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Computer vision methods}
-      \begin{itemize}
-        \item Computer vision does object recognition.
-        \item Requires photos/video that cover the entire location, all the time.
-        \item \color{red} This will count people twice.
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Other methods}
-      \begin{itemize}
-        \item Scan active mobile phones in the area.
-        \item This requires some extra equipment.
-        \item \color{red} This catches bystanders who are not protesting.
-      \end{itemize}
-    \end{whiteblock}
 
@@
     \end{redblock}
+
+    \begin{figure}
+      \centering
+      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
+      \caption{%
+        Jacobs Method, currently most used method.
+        Divide into regions, estimate density in each region, sum up.
+        Image: popularmechanics.com
+      }\label{JacobsMethod}
+    \end{figure}
+
+  \end{column}
+
+  \begin{column}{0.32\linewidth}
 
@@
 
-    \begin{greenblock}{Our approach: user's perspective}
+  \end{column}
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{greenblock}{Our approach}
       \begin{itemize}
-        \item The organizer publishes the protest's manifesto, e.g.\ QR-code on 
-          placard.
-        \item Each protester has a smartphone with a protest app.
-        \item Each protester scans the QR code with the app.
-        \item The app communicates with other apps locally, e.g.\ ad-hoc network 
-          or Bluetooth.
-        \item The apps issues participation proofs to each other.
-        \item Once there is an Internet connection, the proofs are submitted to 
-          a blockchain.
-        \item Anyone can verify the proofs on the blockchain and count the valid 
-          ones.
+        \item Provides a \emph{lower bound} of the participation count.
+        \item Provides a verifiable participation count.
+        \item Provides privacy based on anonymous credentials.
+        \item The only added risk (over not using this) is if someone can use 
+          your secret key.
+        \item Requires only local connectivity during the protest.
       \end{itemize}
@@
 
-  \end{column}
-
-  \hfill
-
-  \begin{column}{0.32\linewidth}
-
-    \begin{greenblock}{Our approach: during protest}
-      \begin{itemize}
-        \item The organizer publishes the protest's manifesto.
-        \item Each protester reads it, approves it, computes a protest (cause) 
-          identifier (\(cid\)) to designate which protest they participate in.
-        \item Each protester computes a personal identifier (\(pid\)), 
-          unlinkable between protests,
-        \item Each protester acts as witness (unlinkable between protesters) for 
-          other protesters by creating participation-proof shares.
-        \item Proof shares vouches for temporal and spatial eligibility.
-        \item A threshold-based number of valid shares is a valid proof.
-      \end{itemize}
-    \end{greenblock}
-
-    \begin{whiteblock}{Designated protest}
-      \begin{itemize}
-        \item A protest is identified by its cause, captured in a 
-          manifesto.
-        \item The hash of the manifesto provides an unpredictable identifier 
-          (\(cid\) in \cref{ProofShare,Protocol}).
-        \item It's difficult to create a second manifesto that disagrees but 
-          gets the same identifier.
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Privacy-preserving linkability}
-      \begin{itemize}
-        \item Need linkability during a protest to prevent Sybil attacks.
-        \item Also need privacy.
-        \item Uses techniques from anonymous credentials to create identifiers 
-          (\(pid, wid\) in \cref{ProofShare,Protocol}).
-        \item The identifiers are random but unique per protest, i.e.\ depends 
-          on \(cid\).
-        \item The accompanying \ac{NIZK} proof prevents cheating (used during 
-          verification).
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Temporal eligibility}
-      \begin{itemize}
-        \item We use a blockchain for commitments, freshness.
-        \item Freshness: a protester must include the head (hash value) of the 
-          blockchain in their proof shares (\(t_s\) in 
-          \cref{ProofShare,Protocol}).
-        \item This value is difficult to guess and prevents preparing proofs too 
-          long in advance.
-        \item Commitments: when a proof share is prepared, it is committed to 
-          the blockchain for timestamping.
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Location proofs and spatial eligibility}
-      \begin{itemize}
-        \item Each proof must be bound to the location (\(l\) in 
-          \cref{ProofShare,Protocol}).
-        \item This is done using witnesses.
-        \item A witness runs a distance-bounding protocol to ensure proximity.
-        \item If in proximity, the witness will issue a witness identifier and 
-          signature (\(wid, wsig\)).
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{greenblock}{Our approach: after the protest}
-      \begin{itemize}
-        \item Proof shares are committed to a blockchain as soon as possible.
-        \item \ac{NIZK} proofs are submitted whenever convenient.
-        \item Anyone can verify the proofs: eligibility, universal and 
-          individual verifiability.
-        \item Must be done for all shares and their \ac{NIZK} proofs.
-        \item Count all \(pid\)s with valid proofs.
-      \end{itemize}
-    \end{greenblock}
-
-    \begin{whiteblock}{Eligibility and universal verifiability}
-      \begin{itemize}
-        \item Verify that \(pid\), \(wid\) and \(wsig\) are correct, i.e.\ verify 
-          their \ac{NIZK} proofs.
-        \item \ac{NIZK} proofs must show \(pid = PRF_{k_P}(id)\) and \(k_P\) is 
-          signed by \iac{CA}.
-        \item \ac{NIZK} proofs must show \(wid = PRF_{k_W}(pid), wsig = 
-            PRF_{k_W}(wid, t_s, l)\) and \(k_W\) is signed by \iac{CA}.
-      \end{itemize}
-    \end{whiteblock}
-
-    \begin{whiteblock}{Individual verifiability and receipt freeness}
-      \begin{itemize}
-        \item Each protester can verify that their proof is available on the 
-          blockchain.
-        \item Protester no longer needs to keep the proof, just the hash.
-        \item Eve can use \(k_P\) to redo the computations to verify 
-          participation:
-          \[pid'\gets PRF_{k_P}(cid) \text{ and compare } pid = pid'.\]
-        \item However, requires arrest and access to key.
-      \end{itemize}
-    \end{whiteblock}
+    \includegraphics[width=\linewidth]{art/ProtestVerif-UN.png}
 
@@
 
-  \hfill
+\end{columns}
+
+\vspace{5em}
+
+\begin{columns}[t]
 
@@
           & wsig\gets PRF_{k_W}(wid, t_s, l) \\
-          W\to P\colon & (wid, t_s, l, wsig) \\
+          W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
+          && \text{during protest} \\ \hline && \text{after protest} \\[-1em]
           W\to S\colon & H(pid, wid, t_s, l, wsig) \\
@@
           W\to S\colon & (pid, wid, t_s, l, wsig),\\
-          & NIZK(wid = PRF_{k_W}(pid), \\
+            & NIZK( wid = PRF_{k_W}(pid), \\
             & wsig = PRF_{k_W}(wid, t_s, l), \\
@@
 
-    \begin{purpleblock}{Conclusions}
-      \begin{itemize}
-        \item Provides a \emph{lower bound} of the participation count.
-        \item Provides a verifiable participation count, as strong as the 
-          blockchain is immutable.
-        \item Provides privacy based on anonymous credentials.
-        \item The only added risk (over not using this) is if someone can use 
-          your secret key (\(k_P\)).
-        \item Requires only local connectivity during the protest.
-      \end{itemize}
-    \end{purpleblock}
-
     \printbibliography[heading=none]
 
-    %\vspace{10cm}
+  \end{column}
+
+  \hfill
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{blackblock}{Technically, during protest}
+      \begin{itemize}
+        \item The organizer publishes the protest's manifesto.
+        \item Each protester reads it, approves it, computes a protest (cause) 
+          identifier (\(cid\)) to designate which protest they participate in.
+        \item Each protester computes a personal identifier (\(pid\)), 
+          unlinkable between protests,
+        \item Each protester acts as witness (unlinkable between protesters) for 
+          other protesters by creating participation-proof shares.
+        \item Proof shares vouches for temporal and spatial eligibility.
+        \item A threshold-based number of valid shares is a valid proof.
+      \end{itemize}
+    \end{blackblock}
+
+    \begin{blackblock}{Technically, after the protest}
+      \begin{itemize}
+        \item Proof shares are committed to a blockchain as soon as possible.
+        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
+          validity of keys are submitted whenever convenient.
+        \item Anyone can verify the proofs: eligibility, universal and 
+          individual verifiability.
+        \item Must be done for all shares and their \ac{NIZK} proofs.
+        \item Count all \(pid\)s with valid proofs.
+      \end{itemize}
+    \end{blackblock}
+
+  \end{column}
+
+  \hfill
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{block}{More info}
       \begin{center}
-      \includegraphics[width=0.5\linewidth]{fig/qr.eps}
+        \includegraphics[width=0.4\linewidth]{fig/qr.eps}
       \end{center}
+    \end{block}
 
@@
 \end{columns}
+
+\flushright
+Special thanks to xkcd.com who, over many years, has inspired the stylistic 
+presentation of this poster.

### 2017-11-17 contents-poster.tex
Refactors poster
- Adds figure of Trumps inauguration fiasco.
- Adds where other methods are failing.

@@
 
+\vfill
+
 \includegraphics[width=\linewidth]{art/ProtestVerif.png}
+
+\vfill
 
@@
         \item Eve wants to show that few support Alice's cause.
-        \item \color{red} Adversarial setting, requires verifiable results!
+        \item {\color{red} Adversarial setting, requires verifiable results!}
+          (E.g.\ \cref{TrumpInauguration}.)
       \end{itemize}
     \end{redblock}
-
-    \begin{figure}
-      \centering
-      \includegraphics[width=0.9\linewidth]{fig/Jacobs-method.jpg}
-      \caption{%
-        Jacobs Method, currently most used method.
-        Divide into regions, estimate density in each region, sum up.
-        Image: popularmechanics.com
-      }\label{JacobsMethod}
-    \end{figure}
-
-  \end{column}
-
-  \begin{column}{0.32\linewidth}
 
@@
 
+  \hfill
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{figure}
+      \centering
+      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
+      \caption{%
+        What can we trust?
+        (Hint: not much.)
+        Image: Reddit/The\_Donald, Twitter.
+      }\label{TrumpInauguration}
+    \end{figure}
+
+  \end{column}
+
+  \hfill
+
   \begin{column}{0.32\linewidth}
@@
 
-\vspace{5em}
+\vfill
 
@@
   \begin{column}{0.32\linewidth}
-
     \begin{figure}
@@
 
-    \printbibliography[heading=none]
-
   \end{column}
@@
 
+    \begin{block}{More info}
+      \centering
+      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
+    \end{block}
+
+    \printbibliography[heading=none]
+
   \end{column}
@@
 
-    \begin{block}{More info}
-      \begin{center}
-        \includegraphics[width=0.4\linewidth]{fig/qr.eps}
-      \end{center}
-    \end{block}
+    \begin{figure}
+      \centering
+      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
+      \caption{%
+        Jacobs Method, currently most used method.
+        Divide into regions, estimate density in each region, sum up.
+        Image: popularmechanics.com
+      }\label{JacobsMethod}
+    \end{figure}
+
+    \begin{purpleblock}{Current crowd-counting methods}
+      \begin{itemize}
+        \item Most used method, Jacobs Method (\cref{JacobsMethod}).
+        \item {\color{red} Cannot handle cumulative counts, faces problems 
+            illustrated by \cref{TrumpInauguration}.}
+        \item Computer vision does object recognition; requires photos/video 
+          that cover the entire location, all the time.
+        \item {\color{red} This will still count people twice.}
+        \item Scan active mobile phones (or similar) in the area.
+        \item This requires some extra equipment.
+        \item {\color{red} This catches bystanders who are not protesting.}
+        \item {\color{red} Neither method can distinguish two close but 
+            different protests (e.g.\ pro- and anti-protests).}
+      \end{itemize}
+    \end{purpleblock}
 
@@
 \flushright
-Special thanks to xkcd.com who, over many years, has inspired the stylistic 
+Special thanks to xkcd.com which, over many years, has inspired the stylistic 
 presentation of this poster.

### 2017-11-20 contents-poster.tex
Adapts to automatic scaling of tikz, changes to A0 paper

@@
       \centering
-      \begin{tikzpicture}[%
-        -Latex,
-        item/.style={rectangle,draw},
-        edge from parent/.style={},
-        ]
-        \tikzset{%
-          %grow'=left,%
-          %level distance=5em%
-        }
-        \node[item] (proof) {Proof share}
-        child {%
-          node[item] (pid) {$pid$}
-          child {%
-            node[item] (cid) {$cid$}
-            child {%
-              node[item] (manifesto) {Manifesto}
-            }
-          }
-        }
-        child {%
-          node[item] (wid) {$wid$}
-        }
-        child {%
-          node[item] (ts) {$t_s$}
-        }
-        child {%
-          node[item] (l) {$l$}
-        }
-        child {%
-          node[item] (wsig) {$wsig$}
-        }
-        ;
-
-        \path[every node/.style={font=\small}]
-        (pid) edge node [anchor=south east] {$\in$} (proof)
-        (wid) edge node [anchor=east] {$\in$} (proof)
-        (ts) edge node [anchor=east] {$\in$} (proof)
-        (l) edge node [anchor=west] {$\in$} (proof)
-        (wsig) edge node [anchor=south west] {$\in$} (proof)
-        ;
-
-        \path[every node/.style={font=\small}]
-        (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
-        (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
-        (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
-        % wsig
-        (l) edge[bend right] (wsig)
-        (ts) edge[bend right] (wsig)
-        (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
-          \cdot)$} (wsig)
-        ;
-
-      \end{tikzpicture}
+      \includegraphics[width=\linewidth]{fig/proofshare.tikz}
       \caption{%
@@
 
-\flushright
+\vfill
+\flushright{}
 Special thanks to xkcd.com which, over many years, has inspired the stylistic 

### 2017-11-20 contents-poster.tex
Minor updates
- Removes hint from fig 1.
- Adds location icon and "Protest ended" to comic for clarification.
Adds space in the middle

@@
         What can we trust?
-        (Hint: not much.)
+        This picture was posted on Twitter (and linked from Reddit) to argue 
+        that the news reporting on the participation count was \enquote{fake 
+          news} and that Trump's supporters arrived later.
+        Even if the picture labelled \enquote{REALITY} would be from the same 
+        event (difficult to verify), it is difficult to accurately compare due 
+        to the angle.
         Image: Reddit/The\_Donald, Twitter.
@@
         \item Provides a \emph{lower bound} of the participation count.
-        \item Provides a verifiable participation count.
+        \item This lower bound is cryptographically verifiable.
         \item Provides privacy based on anonymous credentials.
@@
         \item Requires only local connectivity during the protest.
+        \item Requires no trust in the source (as in \cref{TrumpInauguration}), 
+          only that IDs are issued correctly.
       \end{itemize}
@@
 \vfill
+\vspace{8cm}
 

### 2017-11-21 contents-poster.tex
Fixes Sébastien's comments

@@
       \begin{itemize}
-        \item The verifiability protocol should not increase the risk already 
-          incurred by attending.
+        \item Protocol should not harm the privacy of the protester, i.e.\  not 
+          diclose any information about them other than what can already be 
+          learnt from their physical attendance.
       \end{itemize}
@@
         \item This lower bound is cryptographically verifiable.
-        \item Provides privacy based on anonymous credentials.
+        \item Provides privacy based on anonymous credentials and 
+          privacy-preserving proximity testing.
         \item The only added risk (over not using this) is if someone can use 
@@
 \vfill
-\vspace{8cm}
 
 \begin{columns}[t]
+
+  \begin{column}{0.32\linewidth}
+
+    \begin{figure}
+      \centering
+      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
+      \caption{%
+        Jacobs Method, currently most used method.
+        Divide into regions, estimate density in each region, sum up.
+        Image: popularmechanics.com
+      }\label{JacobsMethod}
+    \end{figure}
+
+    \begin{purpleblock}{Current crowd-counting methods}
+      \begin{itemize}
+        \item Most used method, Jacobs Method (\cref{JacobsMethod}).
+        \item {\color{red} Cannot handle cumulative counts, faces problems 
+            illustrated by \cref{TrumpInauguration}.}
+        \item Computer vision does object recognition; requires photos/video 
+          that cover the entire location, all the time.
+        \item {\color{red} This will still count people twice.}
+        \item Scan active mobile phones (or similar) in the area.
+        \item This requires some extra equipment.
+        \item {\color{red} This catches bystanders who are not protesting.}
+        \item {\color{red} Neither method can distinguish two close but 
+            different protests (e.g.\ pro- and anti-protests).}
+      \end{itemize}
+    \end{purpleblock}
+
+  \end{column}
+
+  \hfill
 
@@
           W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
-          && \text{during protest} \\ \hline && \text{after protest} \\[-1em]
+          && \text{during protest} \\ \midrule && \text{after protest} \\[-1em]
           W\to S\colon & H(pid, wid, t_s, l, wsig) \\
@@
         The organizer \(O\) broadcasts the manifesto.
-        \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
+        \(P\), \(W\) and their computations are as in \cref{ProofShare}.
         Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
@@
 
-  \hfill
-
-  \begin{column}{0.32\linewidth}
-
-    \begin{figure}
-      \centering
-      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
-      \caption{%
-        Jacobs Method, currently most used method.
-        Divide into regions, estimate density in each region, sum up.
-        Image: popularmechanics.com
-      }\label{JacobsMethod}
-    \end{figure}
-
-    \begin{purpleblock}{Current crowd-counting methods}
-      \begin{itemize}
-        \item Most used method, Jacobs Method (\cref{JacobsMethod}).
-        \item {\color{red} Cannot handle cumulative counts, faces problems 
-            illustrated by \cref{TrumpInauguration}.}
-        \item Computer vision does object recognition; requires photos/video 
-          that cover the entire location, all the time.
-        \item {\color{red} This will still count people twice.}
-        \item Scan active mobile phones (or similar) in the area.
-        \item This requires some extra equipment.
-        \item {\color{red} This catches bystanders who are not protesting.}
-        \item {\color{red} Neither method can distinguish two close but 
-            different protests (e.g.\ pro- and anti-protests).}
-      \end{itemize}
-    \end{purpleblock}
-
-\end{column}
-
 \end{columns}

### 2017-11-22 poster/contents-poster.tex
Removes files into separate directories

--- 2017-11-21 contents-poster.tex
@@
   \begin{column}{0.32\linewidth}
+
+    \begin{blackblock}{Our scheme, during protest (\cref{ProofShare}, top of 
+        \cref{Protocol})}
+      \begin{itemize}
+        \item The organizer publishes the protest's manifesto.
+        \item Each protester reads it, approves it, computes a protest (cause) 
+          identifier (\(cid\)) to designate which protest they participate in.
+        \item Each protester computes a personal identifier (\(pid\)), 
+          unlinkable between protests,
+        \item Each protester acts as witness (\(wid\), unlinkable between 
+          protesters, \(wsig\)) for other protesters by creating 
+          participation-proof shares.
+        \item Proof shares vouches for temporal and spatial eligibility.
+        \item A threshold-based number of valid shares is a valid proof.
+      \end{itemize}
+    \end{blackblock}
+
+    \begin{blackblock}{Our scheme, after the protest (bottom of 
+        \cref{Protocol})}
+      \begin{itemize}
+        \item Proof shares are committed to a blockchain as soon as possible.
+        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
+          validity of keys are submitted whenever convenient.
+        \item Anyone can verify the proofs: eligibility, universal and 
+          individual verifiability.
+        \item Must be done for all shares and their \ac{NIZK} proofs.
+        \item Count all \(pid\)s with valid proofs.
+      \end{itemize}
+    \end{blackblock}
+
+    \begin{block}{More info}
+      \centering
+      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
+    \end{block}
+
+    \printbibliography[heading=none]
+
+  \end{column}
+
+  \hfill
+
+  \begin{column}{0.32\linewidth}
     \begin{figure}
@@
 
-  \hfill
-
-  \begin{column}{0.32\linewidth}
-
-    \begin{blackblock}{Technically, during protest}
-      \begin{itemize}
-        \item The organizer publishes the protest's manifesto.
-        \item Each protester reads it, approves it, computes a protest (cause) 
-          identifier (\(cid\)) to designate which protest they participate in.
-        \item Each protester computes a personal identifier (\(pid\)), 
-          unlinkable between protests,
-        \item Each protester acts as witness (unlinkable between protesters) for 
-          other protesters by creating participation-proof shares.
-        \item Proof shares vouches for temporal and spatial eligibility.
-        \item A threshold-based number of valid shares is a valid proof.
-      \end{itemize}
-    \end{blackblock}
-
-    \begin{blackblock}{Technically, after the protest}
-      \begin{itemize}
-        \item Proof shares are committed to a blockchain as soon as possible.
-        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
-          validity of keys are submitted whenever convenient.
-        \item Anyone can verify the proofs: eligibility, universal and 
-          individual verifiability.
-        \item Must be done for all shares and their \ac{NIZK} proofs.
-        \item Count all \(pid\)s with valid proofs.
-      \end{itemize}
-    \end{blackblock}
-
-    \begin{block}{More info}
-      \centering
-      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
-    \end{block}
-
-    \printbibliography[heading=none]
-
-  \end{column}
-
 \end{columns}

### 2017-11-24 paper/protocol.tex
Adapts paper to new repo structure

--- 2017-10-09 protocol.tex
@@
   \centering
-  \begin{tikzpicture}[%
-    -Latex,
-    item/.style={rectangle,draw},
-    edge from parent/.style={}
-    ]
-    \tikzset{%
-      %grow'=left,%
-      %level distance=5em%
-    }
-    \node[item] (proof) {Proof share}
-      child {%
-        node[item] (pid) {$pid$}
-        child {%
-          node[item] (cid) {$cid$}
-          child {%
-            node[item] (manifesto) {Manifesto}
-          }
-        }
-      }
-      child {%
-        node[item] (wid) {$wid$}
-      }
-      child {%
-        node[item] (ts) {$t_s$}
-      }
-      child {%
-        node[item] (l) {$l$}
-      }
-      child {%
-        node[item] (wsig) {$wsig$}
-      }
-      ;
-
-      \path[every node/.style={font=\small}]
-      (pid) edge node [anchor=south east] {$\in$} (proof)
-      (wid) edge node [anchor=east] {$\in$} (proof)
-      (ts) edge node [anchor=east] {$\in$} (proof)
-      (l) edge node [anchor=west] {$\in$} (proof)
-      (wsig) edge node [anchor=south west] {$\in$} (proof)
-      ;
-
-      \path[every node/.style={font=\small}]
-      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
-      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
-      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
-      % wsig
-      (l) edge[bend right] (wsig)
-      (ts) edge[bend right] (wsig)
-      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
-        \cdot)$} (wsig)
-      ;
-
-  \end{tikzpicture}
+  \includegraphics{proofshare.tikz}
+%  \begin{tikzpicture}[%
+%    -Latex,
+%    item/.style={rectangle,draw},
+%    edge from parent/.style={}
+%    ]
+%    \tikzset{%
+%      %grow'=left,%
+%      %level distance=5em%
+%    }
+%    \node[item] (proof) {Proof share}
+%      child {%
+%        node[item] (pid) {$pid$}
+%        child {%
+%          node[item] (cid) {$cid$}
+%          child {%
+%            node[item] (manifesto) {Manifesto}
+%          }
+%        }
+%      }
+%      child {%
+%        node[item] (wid) {$wid$}
+%      }
+%      child {%
+%        node[item] (ts) {$t_s$}
+%      }
+%      child {%
+%        node[item] (l) {$l$}
+%      }
+%      child {%
+%        node[item] (wsig) {$wsig$}
+%      }
+%      ;
+%
+%      \path[every node/.style={font=\small}]
+%      (pid) edge node [anchor=south east] {$\in$} (proof)
+%      (wid) edge node [anchor=east] {$\in$} (proof)
+%      (ts) edge node [anchor=east] {$\in$} (proof)
+%      (l) edge node [anchor=west] {$\in$} (proof)
+%      (wsig) edge node [anchor=south west] {$\in$} (proof)
+%      ;
+%
+%      \path[every node/.style={font=\small}]
+%      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
+%      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
+%      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
+%      % wsig
+%      (l) edge[bend right] (wsig)
+%      (ts) edge[bend right] (wsig)
+%      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
+%        \cdot)$} (wsig)
+%      ;
+%
+%  \end{tikzpicture}
   \mode<article>{%
@@
 
-Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
+Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(cid)\) and 
 that she knows a signature by the identity authority on \(k_P\).

### 2017-11-24 SystemModel.tex

@@
 Each participant who want to be counted must submit a participation proof.
-The proof must be associated with the protest, i.e.\ its \(id\), time and 
-location.
-We use witnesses to associate the proof to the location.
-The proof and its witnesses are stored in a set, as there should be only unique 
-witnesses.
+The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
+time and location.
+We use witnesses to associate the proof to the location by creating a proof 
+share.
+A witness is only allowed to create one proof share per protester.
+The proof and its proof shares are stored in a set, as there should be only 
+unique proof shares.
 
 \begin{frame}
-\begin{definition}[Witness]
-  A \emph{witness} \(w = (pid, cid, t, l, wid)\) is a tuple where
+\begin{definition}[Participation-proof share]
+  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
+  where
   \(cid, t, l\) are as in \cref{DefProtest},
-  \(pid\) uniquely identifies the protester and \(wid\) uniquely identifies the 
-  person who issued the witness.
-  We let \(W\) be the set of all witnesses.
+  \(pid\) is unique for a protester and \(cid\) pair, and
+  \(wid\) is unique for a witness--protester pair.
+  We let \(W\) be the set of all proof shares.
 \end{definition}
@@
 
-A subset of the witnesses forms a participation proof for a protester.
+A subset of the proof shares forms a participation proof for a protester.
 
@@
   \end{align}
-  of all witnesses with the same protester and protest identifiers, witness time 
-  interval \(t\) and location \(l\) is within those of the protest \(j\) (i.e.\ 
-  \(t_j\) and \(l_j\)).
+  of all proof shares with the same protester and protest identifiers, witness 
+  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
+  (i.e.\ \(t_j\) and \(l_j\)).
 \end{definition}
@@
 
-The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
-A trivial example would be for \(s\) to return the number of witnesses and thus 
-let \(\theta\) to be the threshold of the number of required witnesses.
+The strength function \(s\) can be used to e.g.\ regulate trust in 
+witnesses.
+A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
+witnesses) and thus let \(\theta\) to be the threshold of the number of required 
+witnesses.

### 2017-11-24 abstract.tex
Removes WIP comment from abstract, fixes title in security section

@@
 % What's the approach?
-In this work, we are interested in combining location proofs with electronic 
-voting to solve this issue.
+In this work, we are interested in combining location proofs with some 
+properties of electronic voting to provide verifiable participation counts.
 Since the parties have incentives to cheat, we require transparency: in 
@@
 and privacy.
-More specifically, the scheme should be distributed and not depend on any 
-authority.
-We need verifiability, which means that every participant can verify that their 
-participation has been included --- i.e.\ individual verifiability, to prevent 
-Eve from dropping data --- and that anyone can verify the correctness of the 
-result --- i.e.\ universal and eligibility verifiability, to prevent any 
+More specifically, the scheme should be distributed, not depend on any authority 
+and it must scale to handle large protests (i.e.\ millions of participants).
+
+In our scheme each participant creates a participation proof with the help of 
+other participants.
+We use blockchains to commit and timestamp the participation proofs, location 
+proofs to prove connection to the physical location.
+% What's the result?
+The scheme provides verifiability, which means that every participant can verify 
+that their participation has been included --- i.e.\ individual verifiability, 
+to prevent Eve from dropping data --- and that anyone can verify the correctness 
+of the result --- i.e.\ universal and eligibility verifiability, to prevent any 
 malicious actor (e.g. Sybil) from affecting the result.
-Eligibility verifiability also requires that the data is time-wise related to 
-the event (temporal eligibility), which can be provided by blockchain-like 
-structures.
-The data must also be related to the location (spatial eligibility), something 
-a location proof can achieve.
-As all things policital, privacy is critical.
-Similar to e-voting schemes, we need to guarantee properties close to vote 
-privacy and receipt freeness --- Alice does not want Eve's agents to be able to 
-infer that she is critical of Eve.
-Finally, the scheme must be scalable to handle large protests (i.e.\ millions 
-of participants).
+Our scheme is privacy preserving in the sense that it adds no risk to a 
+participant that was not already present when not using our scheme.
 
-In this talk we will discuss this work in progress and elicit input from the
-participants.
+\keywords{%
+  crowd counting;
+  protesting;
+  electronic voting;
+  location proof;
+  privacy
+}

### 2017-12-14 paper/intro.tex
Removes files into separate directories
Adds Makefile and adapts files for paper
Adds slides, distance bounding still to do

--- 2017-09-21 intro.tex
@@
   \begin{figure}
-    \includegraphics[height=0.9\textheight]{fig/Jacobs-method.jpg}
+    \includegraphics[height=0.9\textheight]{Jacobs-method.jpg}
   \end{figure}
@@
 verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
-\begin{itemize}
-  \item Eligibility: anyone can verify that each vote cast is legitimate.
-  \item Universal verifiability: anyone can verify that the result is according 
+\begin{frame}
+\begin{description}
+  \item[Eligibility] anyone can verify that each vote cast is legitimate.
+  \item[Universal verifiability] anyone can verify that the result is according 
     to the cast votes.
-  \item Individual verifiability: every voter can verify that their vote is 
+  \item[Individual verifiability] every voter can verify that their vote is 
     included in the result.
-\end{itemize}
+\end{description}
+\end{frame}
 We translate the votes into \emph{proofs of participation}.
@@
 protest.
-We will define these more formally in \cref{Verification}.
+We will define these more formally in \cref{Verifiability}.
+
+\mode<presentation>{%
+\begin{frame}
+  \begin{description}
+    \item[Privacy] no increased risk to participants.
+  \end{description}
+\end{frame}
+}
 
@@
 
+\mode<article>{%
 \subsection{Contributions}
+}
 

### 2018-02-01 paper/RelatedWork.tex
Removes beamerarticle and changes citations to natbib syntax

--- 2017-08-25 RelatedWork.tex
@@
-\mode*
 \section{Related work}%
 \label{RelatedWork}
-
-\subsection<presentation>{Image-based methods}
 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[Jacob's method]
-    \begin{itemize}
-      \item Take aerial photos of the event.
-      \item Divide area into regions.
-      \item Estimate density in the regions.
-      \item Sum up to an estimate of the total.
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Prone to errors, due to estimations.
-      \item Universally verifiable, anyone with the photos can redo the 
-        estimate.
-      \item Eligibility verifiability if photos at one snapshot in time and no 
-        overlap.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
 There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[CrowdSize app\footfullcite{CrowdSize}]
-    \begin{itemize}
-      \item User selects area on map.
-      \item User selects an estimate for crowd density: light, medium or dense.
-      \item App gives crowd size estimate based on size of the area and 
-        density.
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item This is the same method as used by police.
-      \item Not verifiable unless the user takes a picture of the crowd.
-      \item Then it will be reduced to the previous method.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
 There is a body of work in the computer vision community, e.g.\ the work of 
-\textcite{NNCrowdCounting}.
+\citet{NNCrowdCounting}.
 This class of methods requires photos or video surveillance of the protest 
@@
 dataset to train the algorithms.
-In the work by \textcite{NNCrowdCounting}, they actually train and evaluate 
-their algorithm on different scenes, which might make this method easier to use 
-for protesting.
+In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
+algorithm on different scenes, which might make this method easier to use for 
+protesting.
 We can provide universal verifiability (\cref{UniversalVerif}) with this 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[Computer vision]
-    \begin{itemize}
-      \item Record video of the event.
-      \item Train algorithms on part of the data.
-      \item Run algorithm to count the total.
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Requires video-recording of the entire event.
-      \item Difficult to record every part.
-      \item Difficult (impossible?) to not record someone twice.
-      \item Is verifiable, though limited, if the video is public.
-      \item Authenticity can be questioned as with the photos.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
 Another problem for all the above methods is exemplified by the demonstrations 
@@
 
-\subsection<presentation>{Signal-based methods}
-
 During the protests in Seoul~\cite{2016DemonstrationsInSeoul} there was one 
-retail analytics company that tried to estimate the number of participants 
-using their technology.
+retail analytics company that tried to estimate the number of participants using 
+their technology.
 They scanned for MAC addresses emitted from the Wi-Fi of participants' 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[Wi-Fi tracking]
-    \begin{itemize}
-      \item Record unique Wi-Fi MAC addresses from people's smartphones.
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Imprecise, requires assumptions.
-      \item Half of smartphone users turn Wi-Fi off.
-      \item MAC address randomization.
-      \item Cannot verify.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
 A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[IMSI catchers]
-    \begin{itemize}
-      \item Use IMSI catchers to register unique phones.
-      \item (Or use the network cell towers.)
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item Will include bystanders into the count.
-      \item Privacy-invading due to phones being uniquely identifying.
-      \item Cannot verify.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
-\Textcite{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the 
-Wi-Fi signal as a sonar to detect people.
+\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi 
+signal as a sonar to detect people.
 However this method is designed for indoor use and does not scale to more than 
@@
 
-%\subsection<presentation>{Crowd sensing}
-%
-%\dots
-
-\subsection<presentation>{More exact methods}
-
-The most closely related work is \textcite{CrowdCount}.
+The most closely related work is \citet{CrowdCount}.
 This is a web service which lets Alice create an event and Bob can submit his 
@@
 backbone as a means to censor the protest.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{solution}[CrowdCount\footfullcite{CrowdCount}]
-    \begin{itemize}
-      \item Register an upcoming event.
-      \item Let people \enquote{check-in} by submitting their location.
-    \end{itemize}
-  \end{solution}
-
-  \pause{}
-
-  \begin{remark}
-    \begin{itemize}
-      \item No verification, the service must be trusted.
-      \item Nothing prevents Bob from checking in twice.
-      \item Requires an Internet connection during the event.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}

### 2018-02-01 paper/SystemModel.tex
Removes beamerarticle and changes citations to natbib syntax

--- 2017-11-24 SystemModel.tex
@@
-\mode*
-
 \section{System model}%
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{example}[Seoul 2016]
-    \begin{itemize}
-      \item Rallies every weekend.
-      \item Starting midday, lasting to late night.
-      \item Some stayed for several hours, some for only minutes.
-    \end{itemize}
-  \end{example}
-
-  \pause{}
-
-  \begin{example}[US 2017]
-    \begin{itemize}
-      \item Women's Marches in several locations.
-      \item Marched some distance.
-      \item One-time occurrence.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{example}[Venezuela 2017]
-    \begin{itemize}
-      \item Daily anti-government rallies.
-      \item Multiple locations.
-      \item Pro-government rallies too.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
-
 The organizer Alice want to count everyone who participated at any time and in 
@@
 
-\begin{frame}
 \begin{definition}[Protest]\label{DefProtest}
@@
 \end{definition}
-\end{frame}
 
@@
 
-\begin{frame}
 \begin{definition}[Participation-proof share]
@@
 
-\begin{frame}
 \begin{definition}[Participation proof]
@@
 \end{definition}
-\end{frame}
 
 We can now define the participation count as follows.
-\begin{frame}
 \begin{definition}[Participation count]
@@
 \end{definition}
-
-\pause{}
-
-\mode<presentation>{%
-  \begin{example}
-    \begin{itemize}
-      \item The strength function can regulate trust in witnesses.
-      \item E.g.\ return the number of witnesses.
-      \item \(\theta\) would control threshold of number of witnesses.
-    \end{itemize}
-  \end{example}
-}
-\end{frame}
-
-The strength function \(s\) can be used to e.g.\ regulate trust in 
-witnesses.
+The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
 A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 

### 2018-02-01 paper/intro.tex
Removes beamerarticle and changes citations to natbib syntax

@@
-\mode*
-
 \section{Introduction}%
@@
 cheating.
-
-\mode<presentation>{%
-\subsection{What's the problem?}
-}
-
-\begin{frame}<presentation>
-  \begin{block}{The crowd-counting problem}
-    \begin{itemize}
-      \item Alice organizes a protest against Eve's regime.
-      \item Bob, Carol and others show up.
-      \item We want to know how many showed up to support Alice.
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\mode<presentation>{%
-\subsection{Why is it a problem?}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{Jacobs-method.jpg}
-  \end{figure}
-\end{frame}
-
-\begin{frame}
-  \begin{example}
-    \begin{itemize}
-      \item Computer vision does object recognition.
-      \item Requires photos/video that cover the entire location, all the time.
-      \item This will count people twice.
-    \end{itemize}
-  \end{example}
-
-  \pause{}
-
-  \begin{example}
-    \begin{itemize}
-      \item Scan active mobile phones in the area.
-      \item This requires some extra equipment.
-      \item This catches bystanders who are not protesting.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
-
-\mode<none>{%
-\begin{frame}
-  \begin{example}
-    \begin{itemize}
-      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
-        approximate count by imagery.
-        \begin{description}
-          \item[Organizers] 1\,000\,000
-          \item[Police] 260\,000
-        \end{description}
-
-        \pause{}
-
-      \item US 2017~\cite{2017WomensMarchesInUS}:
-        sum up people's approximations.
-      \item This makes it even difficult to estimate the error.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
 
@@
 
-\begin{frame}<presentation>
-  \begin{block}{Verifying protest participation}
-    \begin{itemize}
-      \item Alice organizes a protest against Eve's regime.
-      \item Bob, Carol and others show up.
-
-        \pause{}
-
-      \item {\color{green} Alice wants to show that many support her cause.}
-
-        \pause{}
-
-      \item {\color{red} Eve wants to show that few support Alice's cause.}
-      \item It's an adversarial setting!
-      \item We need verifiable results.
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-We can make one important observation about this problem that has seemingly 
-been ignored in the past: it is an adversarial setting.
+We can make one important observation about this problem that has seemingly been 
+ignored in the past: it is an adversarial setting.
 Alice the activist has an incentive to increase the tallied number of 
@@
 verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
-\begin{frame}
 \begin{description}
@@
 \end{description}
-\end{frame}
 We translate the votes into \emph{proofs of participation}.
@@
 We will define these more formally in \cref{Verifiability}.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{description}
-    \item[Privacy] no increased risk to participants.
-  \end{description}
-\end{frame}
-}
 
@@
 
-\mode<article>{%
 \subsection{Contributions}
-}
 

### 2018-02-01 paper/properties.tex
Removes beamerarticle and changes citations to natbib syntax

--- 2017-09-27 properties.tex
@@
-\mode*
 \section{Desired security properties}%
@@
 We categorize the desired properties into verifiability and privacy.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Alice the activist}
-    \begin{itemize}
-      \item Alice organizes the protest against Eve's regime.
-      \item Alice wants to have a high participation count.
-      \item She tries to increase it.
-      \item So does \emph{all the protesters}.
-    \end{itemize}
-  \end{block}
-
-  \pause{}
-
-  \begin{block}{Eve the fake-news populist}
-    \begin{itemize}
-      \item Eve's regime is target of the protest.
-      \item She wants to have a low participation count.
-      \item She tries to decrease it.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Eve the totalitarian dictator}
-    \begin{itemize}
-      \item Eve wants to \enquote{convince} activists to support her.
-      \item She wants to find all activists.
-      \item She tries to identify (deanonymize) participants.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{block}{Rusuk the nation state}
-    \begin{itemize}
-      \item Rusuk benefits from the situation in Evestan.
-      \item He wants the outcome to be the most beneficial.
-      \item He will try to increase or decrease the participation count.
-    \end{itemize}
-  \end{block}
-\end{frame}
-}
 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{requirements}[V\ref*{EligibilityVerif}.]
-  \item\label{CreatedAfterStart} Prove that the data was created after the 
-    start of the event.
-  \item\label{CreatedBeforeEnd} Prove that the data was created before the end 
-    of the event.
-  \item\label{SpatiallyRelated} Prove that the data is spatially related to the 
-    physical location of the event.
-  \item\label{CountOnce} Prove that no individual can be counted more than 
-    once.
-  \item\label{DesignatedEvent} Prove that the data is designated for the event.
-\end{requirements}
-\end{frame}
-}
-
 \subsubsection{Temporal eligibility}
 
-\begin{frame}
 \begin{definition}[Forging temporal eligibility]
@@
 
-\begin{frame}
 \begin{definition}[Forging spatial eligibility]
@@
 In voting, we have the following requirements:
-\begin{frame}
 \begin{requirements}[P]
@@
 \end{requirements}
-\pause{}
-\mode<presentation>{%
-  \begin{remark}
-    P\ref{CoercionResistance} \(\implies\)
-    P\ref{ReceiptFreeness} \(\implies\)
-    P\ref{VotePrivacy}
-  \end{remark}
-}
-\end{frame}
-\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
+\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
 \cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
@@
 
-\mode<none>{%
-\begin{frame}
-  \begin{remark}
-    \begin{itemize}
-      \item Coercion resistance is difficult to achieve for voting.
-      \item It doesn't make much sense for protests.
-      \item E.g.\ Eve physically brings Alice to a protest she doesn't want to 
-        participate in.
-      \item That leaves us with receipt freeness and vote privacy.
-    \end{itemize}
-  \end{remark}
-\end{frame}
-}
-
 \subsubsection{Participation-proof privacy}
 
-\begin{frame}
 \begin{definition}[Proof indistinguishability]
@@
 
-\begin{frame}
 \begin{definition}[Receipt freeness/deniability]
@@
 \end{definition}
-\end{frame}

### 2018-02-01 paper/protocol.tex
Removes beamerarticle and changes citations to natbib syntax

@@
-\mode*
 \section{Protocol}
@@
 
-\begin{frame}
 \begin{figure}
@@
   \includegraphics{proofshare.tikz}
-%  \begin{tikzpicture}[%
-%    -Latex,
-%    item/.style={rectangle,draw},
-%    edge from parent/.style={}
-%    ]
-%    \tikzset{%
-%      %grow'=left,%
-%      %level distance=5em%
-%    }
-%    \node[item] (proof) {Proof share}
-%      child {%
-%        node[item] (pid) {$pid$}
-%        child {%
-%          node[item] (cid) {$cid$}
-%          child {%
-%            node[item] (manifesto) {Manifesto}
-%          }
-%        }
-%      }
-%      child {%
-%        node[item] (wid) {$wid$}
-%      }
-%      child {%
-%        node[item] (ts) {$t_s$}
-%      }
-%      child {%
-%        node[item] (l) {$l$}
-%      }
-%      child {%
-%        node[item] (wsig) {$wsig$}
-%      }
-%      ;
-%
-%      \path[every node/.style={font=\small}]
-%      (pid) edge node [anchor=south east] {$\in$} (proof)
-%      (wid) edge node [anchor=east] {$\in$} (proof)
-%      (ts) edge node [anchor=east] {$\in$} (proof)
-%      (l) edge node [anchor=west] {$\in$} (proof)
-%      (wsig) edge node [anchor=south west] {$\in$} (proof)
-%      ;
-%
-%      \path[every node/.style={font=\small}]
-%      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
-%      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
-%      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
-%      % wsig
-%      (l) edge[bend right] (wsig)
-%      (ts) edge[bend right] (wsig)
-%      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
-%        \cdot)$} (wsig)
-%      ;
-%
-%  \end{tikzpicture}
-  \mode<article>{%
   \caption{%
@@
     The protest (cause) identifier \(cid\) is the hash value of the manifesto.
-  }}%
+  }%
   \label{fig:ProofFig}
 \end{figure}%
-\end{frame}
 
-\begin{frame}
 \begin{figure}
@@
       W\to S\colon & (pid, wid, t_s, l, wsig),\\
-        & NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
-        sign(k_W)) \\
+        & NIZK(wid = PRF_{k_W}(pid),\\
+        & wsig = PRF_{k_W}(wid, t_s, l),\\
+        & \exists sign(k_W)) \\
       P\to S\colon & (pid, wid, t_s, l, wsig),\\
@@
   \end{minipage}
-  \mode<article>{%
   \caption{%
@@
     Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
-  }}%
+  }%
   \label{fig:ProtocolOverview}
 \end{figure}
-\end{frame}
 
@@
 Next we need to consider the protesters' identifiers to prevent Sybil attacks.
-\Textcite{HowToWinTheCloneWars} created an \emph{interactive} credential system 
+\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
 which allows anonymous authentication at most \(n\) times\footnote{%
   Possibly there is another scheme that makes it non-interactive, e.g.\ by 
-  \Textcite{Psignatures}, see issue \#27.
+  \citet{Psignatures}, see issue \#27.
 }, where \(n = 1\) in our scenario.

### 2018-02-01 paper/security.tex
Removes beamerarticle and changes citations to natbib syntax

--- 2017-09-28 security.tex
@@
-\mode*
-
 \section{Security and privacy analysis}%
 \label{SecurityAnalysis}
+
+We note that Alice and Bob do not trust each other, for all they know one or the 
+other could be an agent of Eve the autocrat.
+\begin{itemize}
+  \item Eve the evil autocrat,
+  \item Rusuk the foreign nation state, and finally
+\end{itemize}
 
@@
 
-\mode<presentation>{%
-\begin{frame}
-  \begin{center}
-    Alice $:=$ Alice's cryptographic device
-  \end{center}
-\end{frame}
-}
-
 No connection to any global network the Internet is necessary during the 
@@
 connections and are not computationally limited by any battery.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{assumption}[During protest]
-    \begin{itemize}
-      \item Everyone has a smartphone.
-      \item Can use ad-hoc networks during the event.
-      \item Computations bounded by battery life.
-    \end{itemize}
-  \end{assumption}
-
-  \pause{}
-
-  \begin{assumption}[Before and after protest]
-    \begin{itemize}
-      \item Internet connection available.
-      \item Computations not bounded by battery life.
-    \end{itemize}
-  \end{assumption}
-
-  \pause{}
-
-  \begin{remark}
-    We provide a lower bound, since there might be participants without phones.
-  \end{remark}
-\end{frame}
-}
 
@@
 must find a second preimage for the hash function.
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{itemize}
-    \item Eve wants to arrange a counter-protest.
-    \item She wants to steal some of Alice's participants' proofs.
-    \item To do this she must have an identifier that matches.
-    \item I.e.\ she must find a second preimage for the hash function.
-  \end{itemize}
-\end{frame}
-}
 

### 2018-02-02 paper/SystemModel.tex
Minor edits to system model

--- 2017-11-24 SystemModel.tex
@@
 }.
-Judging from these examples, the minimal common part is the cause.%
+Judging from these examples, the minimal common part is the cause,%
 \label{CauseIsTheCommonDenominator}
+but there is also a location (or area) that varies over time.
 
@@
 The same for marches, the marching path can be divided into subprotests with 
-coarse coordinates that slightly overlap.
+locations (or areas) that slightly overlap.
 
@@
 The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
-time and location.
+time and location must coincide with any of its subprotests.
 We use witnesses to associate the proof to the location by creating a proof 
 share.
+% XXX what is a witness?
 A witness is only allowed to create one proof share per protester.
@@
   \(cid, t, l\) are as in \cref{DefProtest},
-  \(pid\) is unique for a protester and \(cid\) pair, and
+  \(pid\) is unique for a protester--\(cid\) pair, and
   \(wid\) is unique for a witness--protester pair.
@@
 witnesses.
-A trivial example would be for \(s\) to return the number of proof shares (i.e.\ 
+One example would be for \(s\) to return the number of proof shares (i.e.\ 
 witnesses) and thus let \(\theta\) to be the threshold of the number of required 

### 2018-02-05 paper/properties.tex
Edits security properties

--- 2017-09-28 properties.tex
@@
 We desire three verifiability requirements:
+
 \begin{requirements}[V]
   \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
-  participation proof provides temporal and spatial eligibility and that it has 
-  not been counted before.
-\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-  result is according to the submitted participation proofs.
-\item\label{IndividualVerif} Individual verifiability: every participant can 
-  verify that their participation proof is included in the global count.
-\end{requirements}
-We can translate these to the case of participation in a demonstration, then 
-each vote would be replaced by a proof of participation.
-
-\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
-each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
-attacks.
-They must also be able to verify that each proof is indeed related to the 
-event.
-We must associate the proof to the event both spatially (the correct location) 
-and temporally (it is related to the time-interval of the event).
-We can essentially divide it into the following requirements:
-\begin{requirements}[\ref*{EligibilityVerif}.]
+    participation proof provides temporal and spatial eligibility and that it 
+    has not been counted before.
+    \begin{requirements}[]
     \item Temporal egligibility:%
@@
     \end{requirements}
+
+  \item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
+    result is according to the submitted participation proofs.
+  \item\label{IndividualVerif} Individual verifiability: every participant can 
+    verify that their participation proof is included in the global count.
+\end{requirements}
+We will now discuss these in more detail.
 
@@
 \subsubsection{Temporal eligibility}
-
-There are two aspects of temporal eligibility.
-The adversary can try to forge a witness for a future protest and the adversary 
-can try to forge a witness for a past protest.
-
-We first introduce something we call a \emph{time-authenticator tag}.
-This is an unpredictable value \(\tau_t\) which is published at time \(t\).
-The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
-advance, i.e.\ the use of \(\tau_t\) must have happened after time \(t\) with 
-high probability.
-
-\begin{definition}[Predicting the future]
-  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
-  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
-  (\(\lambda\) is the security parameter.)
-  Let \A be \iac{PPT} adversary.
-  The challenger gives \(T_{t-1}\) to \A.
-  \A is allowed to query an oracle \(O\) which returns whether a guess is 
-  correct or not.
-  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
-  the adversary wins.
-\end{definition}
-
-We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
-chance of winning will be
-\begin{equation}
-  \label{SuccessOfPrediction}
-  \Prob{%
-    \A^O(T_{t-1}, \lambda) = \tau_t
-  } = \frac{p(\lambda)}{2^\lambda}
-\end{equation}
-for some polynomial \(p(\cdot)\).
-This will be negligible for sufficiently a large \(\lambda\).
-
-\begin{definition}[Forging past witnesses]
-  \dots
-\end{definition}
 
@@
 \begin{definition}[Proof indistinguishability]
-  \dots
+  Adversary chooses two messages \(m_0, m_1\) and gives them to the challenger.
+  Challenger uniformly randomly selects \(b\rgets \bin\) and runs \(c_b \gets 
+    PRF_k(m_0), c_{1-b} \gets PRF_k(m_1)\).
+  The challenger gives \(c_0, c_1\) to adversary.
+  If the adversary outputs \(b' = b\) she wins.
+  (The property should be similar to key privacy~\cite{KeyPrivacy}.)
 \end{definition}
@@
 \begin{definition}[Receipt freeness/deniability]
-  \dots
+  Adversary gets oracle access to the user?
+  User provides a witness?
 \end{definition}

### 2018-02-05 paper/RelatedWork.tex
Minor edits in Related Work

--- 2017-08-25 RelatedWork.tex
@@
 
-\subsection<presentation>{Image-based methods}
+\mode<presentation>{%
+\subsection{Image-based methods}
+}
 
@@
 since it is hard to verify that oneself is indeed in any of the photos.
+(It is of course possible with very detailed photos, but not currently realistic 
+to do with aerial photos.)
 We can argue eligibility verifiability (\cref{EligibilityVerif}) if all the 
@@
 However, the best we can do is to employ forensic methods to try to detect any 
-modifications.
+modifications or other attempts at fraud.
 
@@
 We might be able to provide some degree of individual verifiability 
-(\cref{IndividualVerif}), but this might still be difficult.
+(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
+this might still be difficult.
 Also, it is difficult (if not impossible) to not count people twice, thus we 
 cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
-In theory, this class of methods will provide an upper bound, whereas our 
-method provides a lower bound.
-However, it is still difficult capture the entire location on surveillance 
+In theory, this class of methods will provide an upper bound, whereas our method 
+can provide a lower bound.
+However, it is still difficult to capture the entire location on surveillance 
 video, which diminishes the argument for an upper bound.
@@
 video, which should be similar as in our discussion about the verifiability of 
-photos above.
+photos above, i.e.\ forensic methods.
 
@@
 
-\subsection<presentation>{Signal-based methods}
+\mode<presentation>{%
+\subsection{Signal-based methods}
+}
 
@@
 bystanders will also be counted.
+It is also difficult to differentiate between the protesters and the 
+counter-protesters.
 Second, since the phone is a unique identifier, participants might be 
@@
 the problem is determining whether people near the event's perimeter are 
-participants of simply bystanders~\cite{HowToEstimateCrowdSize}.
+participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
 These methods also have difficulty capturing the actual attendance of an event,
@@
 
-%\subsection<presentation>{Crowd sensing}
+%\mode<presentation>{%
+%\subsection{Crowd sensing}
+%}
 %
@@
 
-\subsection<presentation>{More exact methods}
+\mode<presentation>{%
+\subsection{More exact methods}
+}
 
@@
 honestly, but even then, nothing prevents Bob from submitting twice (violating 
-eligibility verification, \cref{EligibilityVerif}).
+eligibility, \cref{EligibilityVerif}).
 Another downside is that the service also requires an Internet connection 

### 2018-02-05 paper/properties.tex
Improves {requirements} and {properties} environments

--- 2018-02-01 paper/properties.tex
@@
 We desire three verifiability requirements:
+
 \begin{requirements}[V]
   \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
-  participation proof provides temporal and spatial eligibility and that it has 
-  not been counted before.
-\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-  result is according to the submitted participation proofs.
-\item\label{IndividualVerif} Individual verifiability: every participant can 
-  verify that their participation proof is included in the global count.
-\end{requirements}
-We can translate these to the case of participation in a demonstration, then 
-each vote would be replaced by a proof of participation.
-
-\Cref{EligibilityVerif} would in this case mean that anyone can verify that 
-each participation proof belongs to a unique individual, i.e.\ to prevent Sybil 
-attacks.
-They must also be able to verify that each proof is indeed related to the 
-event.
-We must associate the proof to the event both spatially (the correct location) 
-and temporally (it is related to the time-interval of the event).
-We can essentially divide it into the following requirements:
-\begin{requirements}[\ref*{EligibilityVerif}.]
+    participation proof provides temporal and spatial eligibility and that it 
+    has not been counted before.
+    \begin{requirements}
     \item Temporal egligibility:%

### 2018-02-05 paper/SystemModel.tex

@@
 \end{definition}
-
-\pause{}
-
-\mode<presentation>{%
-  \begin{example}
-    \begin{itemize}
-      \item The strength function can regulate trust in witnesses.
-      \item E.g.\ return the number of witnesses.
-      \item \(\theta\) would control threshold of number of witnesses.
-    \end{itemize}
-  \end{example}
-}
-\end{frame}
-
-The strength function \(s\) can be used to e.g.\ regulate trust in 
-witnesses.
+The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
 One example would be for \(s\) to return the number of proof shares (i.e.\ 

### 2018-02-06 paper/NIZK-anon-cred.tex
Adds description of P-signatures

\subsection{Non-interactive anonymous credentials}%
\label{NIZK-proofs}

\NewScheme{\Psig}{Psig}

\Citet{Psignatures} proposes P-signatures (\Psig), which provides a signature 
scheme and a commitment scheme with a protocol to obtain a signature on a 
committed value and two non-interactive proof systems, one for proving that a 
committed value has been signed and the other for proving that a pair of 
commitments are commitments to the same value.

\NewFunction{\PSetup}{\Psig.\!Setup}

\(params\gets \PSetup[1^\lambda]\): generates the global parameters \(params\), 
which contains parameters for the underlying algorithms.
For ease of notation we will omit \(params\) from all functions.

\NewFunction{\PCommit}{\Psig.\!Commit}

\(comm\gets \PCommit[m, open]\): takes a message \(m\) and an opening value 
\(open\) and returns a commitment.
The commitment scheme must be \emph{perfectly binding} and \emph{strongly 
  computationally hiding}.
Perfectly binding means that for every bit string \(comm\) there exists at most 
one value \(x\) such that there exists a value \(open\) with \(comm = 
  \PCommit[x, open]\).
Strongly computationally hiding means that there exists an alternate setup 
algorithm which generates indistinguishable parameters which yields 
information-theoretically hiding commitments.
I.e.\ the adversary cannot tell which setup algorithm has been used.

\NewFunction{\PObtainSig}{\Psig.\!ObtainSig}
\NewFunction{\PIssueSig}{\Psig.\!IssueSig}

\(\sigma\gets \PObtainSig[pk, m, comm, open]\leftrightarrow
  \PIssueSig[sk, comm]\): obtains a signature \(\sigma\) on the message 
\(m\) hiding it in the commitment \(comm\) with the opening value \(open\).
The function \(\PObtainSig\) is run by the user and \(\PIssueSig\) is run by the 
signature issuer.

\NewFunction{\PProve}{\Psig.\!Prove}

\((comm, \pi, open)\gets \PProve[pk, m, \sigma]\): outputs a commitment 
\(comm\) on the message \(m\) and can be opened using \(open\).
\(\pi\) is a proof of knowledge of the signature \(\sigma\) on the message \(m\) 
made by the owner of \(pk\).

\NewFunction{\PVerifyProof}{\Psig.\!VerifyProof}

\(\bin\ni \PVerifyProof[pk, comm, \pi]\): verifies the proof \(\pi\) that \(m\) 
has been signed by the owner of \(pk\).
(\(comm\) is a commitment to \(m\).)
It outputs \(1\) (accept) if \(\pi\) is a proof of knowledge of \(F(m)\) and a 
signature on \(m\).

\NewFunction{\PEqCommProve}{\Psig.\!EqCommProve}

\(\pi\gets \PEqCommProve[m, open, open']\): outputs a proof \(\pi\) saying that 
\(comm = \PCommit[m, open]\) is a commitment to the same value as \(comm' = 
  \PCommit[m, open']\).
This can be used to tie ephemeral commitments to long-term commitments.

\NewFunction{\PVerEqComm}{\Psig.\!VerEqComm}

\(\bin\ni \PVerEqComm[comm, comm', \pi]\): outputs \(1\) (accept) if the proof 
\(pi\) is a proof saying that \(comm, comm'\) are commitments to the same value.

### 2018-02-06 paper/NIZK-anon-cred.tex
Updates bibsp, clarifies intro to NIZK-anon-cred

@@
 \subsection{Non-interactive anonymous credentials}%
-\label{NIZK-proofs}
+\label{NIZK-anon-cred}
 
-\NewScheme{\Psig}{Psig}
+\NewCryptoScheme{\Psig}{Psig}
 
-\Citet{Psignatures} proposes P-signatures (\Psig), which provides a signature 
-scheme and a commitment scheme with a protocol to obtain a signature on a 
-committed value and two non-interactive proof systems, one for proving that a 
-committed value has been signed and the other for proving that a pair of 
-commitments are commitments to the same value.
+\Citet{Psignatures} presents a class of signatures, commitments and 
+non-interactive proof protocols named P-signatures (\Psig), which yields for 
+creating non-interactive anonymous credentials.
+P-signatures provides a signature scheme and a commitment scheme with a protocol 
+to obtain a signature on a committed value and two non-interactive proof 
+systems, one for proving that a committed value has been signed and the other 
+for proving that a pair of commitments are commitments to the same value.
 
-\NewFunction{\PSetup}{\Psig.\!Setup}
+\NewCryptoFunction{\PSetup}{\Psig.\!Setup}
 
@@
 
-\NewFunction{\PCommit}{\Psig.\!Commit}
+\NewCryptoFunction{\PCommit}{\Psig.\!Commit}
 
@@
 
-\NewFunction{\PObtainSig}{\Psig.\!ObtainSig}
-\NewFunction{\PIssueSig}{\Psig.\!IssueSig}
+\NewCryptoFunction{\PObtainSig}{\Psig.\!ObtainSig}
+\NewCryptoFunction{\PIssueSig}{\Psig.\!IssueSig}
 
@@
 
-\NewFunction{\PProve}{\Psig.\!Prove}
+\NewCryptoFunction{\PProve}{\Psig.\!Prove}
 
@@
 
-\NewFunction{\PVerifyProof}{\Psig.\!VerifyProof}
+\NewCryptoFunction{\PVerifyProof}{\Psig.\!VerifyProof}
 
@@
 
-\NewFunction{\PEqCommProve}{\Psig.\!EqCommProve}
+\NewCryptoFunction{\PEqCommProve}{\Psig.\!EqCommProve}
 
@@
 
-\NewFunction{\PVerEqComm}{\Psig.\!VerEqComm}
+\NewCryptoFunction{\PVerEqComm}{\Psig.\!VerEqComm}
 

### 2018-02-06 paper/intro.tex

--- 2017-12-14 paper/intro.tex
@@
 problem, i.e.\ to verify how many participated in Alice's protest.
-Our main goal is to provide a tool which prevents both Alice and Eve from 
-cheating.
 
@@
 }, in some instances the difference can be hundreds of thousands.
-There are numerous examples, e.g.\ the demonstrations in South 
-Korea~\cite{2016DemonstrationsInSeoul}, Trump's 
-inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize} or the Women's Marches 
-in the US~\cite{2017WomensMarchesInUS}, where there is difficulty in 
-establishing the actual number of participants.
+There are numerous examples where there is difficulty in establishing the actual 
+number of participants, e.g.:\@ the demonstrations against the president in 
+South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration 
+attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March 
+in the US~\cite{2017WomensMarchesInUS}, the demonstrations against changing the 
+constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the 
+independence of Catalonia~\cite{CataloniaDemonstrations}.
 The methods for counting the crowds vary.
@@
 either we trust Alice or Eve, or we must verify their claims.
-We aim for verifiable claims.
+Our main goal is to provide a scheme which prevents both Alice and Eve from 
+cheating, i.e.\ we aim for verifiable claims.
 To solve this problem, we need a verifiable participation count which is 
@@
 
-In general, protesting is very similar to voting: both are many individuals 
-expressing their opinion.
-These opinions can be sensitive, hence we desire to have similar properties of 
-verification and privacy for participation in a protest as there is for voting.
+In general, protesting is very similar to petitions, which in turn are similar 
+to voting: all three are many individuals expressing their opinion.
+These opinions can be sensitive, e.g.\ cause for discrimination or persecution, 
+hence we desire to have similar properties of verification and privacy for 
+verifying a protest as there is for voting.
 
-Voting has three requirements for 
+Voting has (generally) three desirable requirements for 
 verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
@@
 \end{itemize}
-We note that we cannot improve the privacy of participating protesters, if they 
-are caught during a protest there is nothing we can do.
-But if they are not caught in the act, then using our proposed tool should not 
-incur any additional risk.
-Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
-detailed definition) to the protest context.
+We note that we cannot improve the privacy of participating protesters during 
+the protest: if Alice is caught during a protest there is nothing we can do.
+Actually, if there are several protests in the \emph{same location at the same 
+  time}, Alice could blend into another crowd and argue that she participated in 
+a different protest than she actually did --- and the counts would still be 
+correct afterwards.
+However, even if there is only one protest and she is not caught in the act, 
+then using our proposed tool should not incur any additional risk.
+Thus we need at least participation-proof privacy but receipt freeness (see 
+\cref{Privacy} for a detailed definition) is desired.
 In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
-participation proof --- even with Alice's cooperation.
+participation proof --- even if she would compromise Alice's devices.
 
@@
 protesters' privacy than participating in the physical protest itself.
+
+We can achieve privacy, but not receipt freeness.
+This means that there is a way for Eve to efficiently verify that Alice has 
+participated.
+However, this requires that Eve gets a copy of Alice's secret key so that she 
+can simply re-do the (deterministic) computations on the same inputs --- the 
+probability of collisions is negligible.
 

### 2018-02-06 paper/properties.tex

--- 2018-02-05 paper/properties.tex
@@
     has not been counted before.
-    \begin{requirements}[]
+    \begin{requirements}
     \item Temporal egligibility:%
@@
 \subsubsection{Temporal eligibility}
+
+There are two aspects of temporal eligibility.
+The adversary can try to forge a witness for a future protest and the adversary 
+can try to forge a witness for a past protest.
+
+The first thing we want to do is to prevent Alice from collecting witnesses for 
+a future protest.
+For this, we introduce something we call a \emph{time-authenticator tag}.
+This is an unpredictable value \(\tau_t\) which is published at time \(t\).
+The idea is that it is difficult to guess \(\tau_t\) for a given \(t\) in 
+advance, i.e.\ any use of \(\tau_t\) must have happened after time \(t\) with 
+high probability.
+
+\begin{definition}[Predicting the future]
+  Let \(T_t = (\tau_i)_{i=0}^{t}\) be the sequence of time-authenticator tags up 
+  until time \(t\), where \(\tau_i\in \Z_{2^\lambda}\) for all \(i\).
+  (\(\lambda\) is the security parameter.)
+  Let \A be \iac{PPT} adversary.
+  The challenger gives \(T_{t-1}\) to \A.
+  \A is allowed to query an oracle \(O\) which returns whether a guess is 
+  correct or not.
+  If \(\A^O(T_{t-1},1^\lambda)\) outputs \(\tau\) such that \(\tau = \tau_t\) 
+  the adversary wins.
+\end{definition}
+
+We can see that if \(\tau_t\) is chosen uniformly randomly then the adversary's 
+chance of winning will be
+\begin{equation}
+  \label{SuccessOfPrediction}
+  \Prob{%
+    \A^O(T_{t-1}, \lambda) = \tau_t
+  } = \frac{p(\lambda)}{2^\lambda}
+\end{equation}
+for some polynomial \(p(\cdot)\).
+This will be negligible for sufficiently a large \(\lambda\).
+
+\begin{definition}[Collision]
+  Given tag \(\tau\), probability of collision?
+\end{definition}
+
+\begin{definition}[Changing the past]
+  Given a witness for time \(t\), change it to time \(t'\).
+  \dots
+\end{definition}
+
+\begin{definition}[Forging past witnesses]
+  \dots
+\end{definition}
 

### 2018-02-12 paper/ZKPK.tex
Adds start of proof-of-knowledge section

\subsection{Zero-knowledge proofs of knowledge}%
\label{ZKPK}

Briefly describe zero-knowledge proofs and what type of properties can be proved 
using them, e.g.\ algebraic structures but not one-way functions.

We will use the notation introduced by \citet{PKnotation}:
\begin{equation*}
  \PK{\alpha, \beta, \gamma}
  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
\end{equation*}
which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that 
\(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), 
respectively.
When a proof of knowledge is turned into a signature using the Fiat-Shamir 
heuristic~\cite{FiatShamirHeuristic}, we will denote it as
\begin{equation*}
  \SPK{\alpha, \beta, \gamma}
  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
  {m},
\end{equation*}
which yields a signature on \(m\), ensuring that the issuer knew \(\alpha, 
  \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\).

\paragraph{Implementations}

There are various implementations.

### 2018-02-13 paper/protocol.tex
Updates to PKnotation in protocol figure

--- 2017-11-24 paper/protocol.tex
@@
       W\to S\colon & (pid, wid, t_s, l, wsig),\\
-        & NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
-        sign(k_W)) \\
+        & \SPK{k_W, \sigma_W}
+          {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
+            \Sign[k]{k_W}}{\top} \\
+        %& NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
+        %sign(k_W)) \\
       P\to S\colon & (pid, wid, t_s, l, wsig),\\
-        & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
+        & \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
+          \Sign[k]{k_P}}{\top}
     \end{align*}

### 2018-02-14 paper/protocol.tex
Fixes some PRF to \PRF in protocol

@@
       P\colon & cid\gets H(\text{manifesto}), \\
-        & pid\gets PRF_{k_P}(cid) \\
+        & pid\gets \PRF_{k_P}(cid) \\
       P\to W\colon & pid \\
       W\leftrightarrow P\colon & \text{perform distance bounding} \\
-      W\colon & wid\gets PRF_{k_W}(pid), \\
-        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
+      W\colon & wid\gets \PRF_{k_W}(pid), \\
+        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
       W\to P\colon & (wid, t_s, l, wsig) \\

### 2018-02-14 paper/ZKPK.tex
ZKPK: Adds start on implementations

@@
 We will use the notation introduced by \citet{PKnotation}:
-\begin{equation*}
+\begin{equation}\label{PKexample}
   \PK{\alpha, \beta, \gamma}
   {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
-\end{equation*}
+\end{equation}
 which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that 
@@
 respectively.
+Greek letters are known only to the prover and for which the prover wishes to 
+prove knowledge, all other letters are known by the verifier.
+
 When a proof of knowledge is turned into a signature using the Fiat-Shamir 
 heuristic~\cite{FiatShamirHeuristic}, we will denote it as
-\begin{equation*}
-  \SPK{\alpha, \beta, \gamma}
+\begin{equation*}\label{SPKexample}
+  \sigma\gets \SPK{\alpha, \beta, \gamma}
   {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
@@
 \end{equation*}
-which yields a signature on \(m\), ensuring that the issuer knew \(\alpha, 
-  \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\).
+which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knew 
+\(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = 
+  \hat{g}^\gamma\).
 
@@
 There are various implementations.
+We will rely on the Schnorr identification scheme~\cite{Schnorr}.
+
+\NewAlgorithm{\PKprove}{PK.\!Prove}
+\NewAlgorithm{\PKverify}{PK.\!Verify}
+
+The notation in \cref{PKexample} could equivalently be seen as
+\begin{equation*}
+  \PKprove[g,h,y,y',q,\alpha,\beta,\gamma] \leftrightarrow
+  \PKverify[g,h,y,y',q],
+\end{equation*}
+where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
+verifier.
+\(\PKverify\) outputs accept (1) or reject (0).

### 2018-02-14 paper/DB-anon-cred.tex
Adds DBPK, DB, anon-cred

\mode*
\section{Distance bounding anonymous credentials}%
\label{DB-anon-cred}

\ProvideDocumentCommand{\DBPK}{m m}{\ensuremath{%
    \operatorname{DBPK}\mleft\{\mleft(#1\mright) : #2\mright\}%
  }}

\dots

\subsection{Impersonating-verifier distance bounding}

\dots

### 2018-02-14 paper/protocol.tex

--- 2018-02-13 paper/protocol.tex
@@
 \mode*
-\section{Protocol}
+\section{PRIVO: A protocol for protest outcome verification}
 
@@
       P\colon & cid\gets H(\text{manifesto}), \\
-        & pid\gets PRF_{k_P}(cid) \\
+        & pid\gets \PRF_{k_P}(cid) \\
       P\to W\colon & pid \\
-      W\leftrightarrow P\colon & \text{perform distance bounding} \\
-      W\colon & wid\gets PRF_{k_W}(pid), \\
-        & wsig\gets PRF_{k_W}(wid, t_s, l) \\
+      W\leftrightarrow P\colon &
+        \DBPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}} \\
+      W\colon & wid\gets \PRF_{k_W}(pid), \\
+        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
       W\to P\colon & (wid, t_s, l, wsig) \\
@@
       P\to S\colon & H(pid, wid, t_s, l, wsig) \\
-      W\to S\colon & (pid, wid, t_s, l, wsig),\\
-        & \SPK{k_W, \sigma_W}
+      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
+        & \pi_W = \SPK{k_W, \sigma_W}
           {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
-            \Sign[k]{k_W}}{\top} \\
+            \Sign[k]{k_W}}{pid, wid, t_s, l, wsig} \\
         %& NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
         %sign(k_W)) \\
-      P\to S\colon & (pid, wid, t_s, l, wsig),\\
-        & \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
-          \Sign[k]{k_P}}{\top}
+      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
+        & \pi_P = \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
+          \Sign[k]{k_P}}{pid, wid, t_s, l, wsig}
     \end{align*}

### 2018-02-14 paper/protocol.tex

@@
-\mode*
 \section{PRIVO: A protocol for protest outcome verification}

### 2018-02-16 paper/DistanceBounding.tex
Breaks out locations proofs to own file

--- 2017-09-30 primitives.tex
@@
-\section{Building blocks}%
-\label{Primitives}\label{BuildingBlocks}
-
-\dots
-
-\subsection{Zero-knowledge proofs}
-
-Briefly describe zero-knowledge proofs and what type of properties can be proved 
-efficiently using them, e.g.\ algebraic structures but not one-way functions.
-
-\dots
-
-\subsection{Location proofs and distance bounding}
+\subsection{Distance bounding}
 
@@
 \end{itemize}
-
-\subsection{Storage}
-
-We will use the storage to provide the temporal eligibility property.
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-One primitive that fulfils these requirements is a blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
-properties.
-However, we will use the blockchain in our discussion for simplicity.
-
-There are three properties that we need from the storage system.
-The first property we need is decentralized, immutable storage with a general 
-form of time-stamping.
-I.e.\ once we commit something to the blockchain it will remain there and we do 
-not have to trust any central authority.
-We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
-block appears approximately every 10 minutes.
-
-The second property we need is an unpredictable number whose time of publication 
-can be verified.
-For this property, we will use the head of the blockchain.
-The hash value of the head of the blockchain at a given time will be difficult 
-to predict ahead of time.
-%(See \cref{SecurityAnalysis} for a security analysis.)
-We want to use this to ensure that proofs are created after a certain point in 
-time.
-
-The third property is that once we have committed some data, we do not need to 
-keep the data itself, but we can store some confirmation value instead.
-E.g.\ using blockchains, we can store the hash of the block where our data was 
-committed, while this block remains we are sure that our data remains committed 
---- even if we no longer remember what our data looked like.
-We will use this property to approximate the property of receipt freeness.

### 2018-02-16 paper/DB-anon-cred.tex
Starts writing about our distance bounding Schnorr

@@
-\mode*
 \section{Distance bounding anonymous credentials}%
@@
 
+We pointed out in \cref{DistanceBounding} that all security properties 
+concerning \ac{DB} assume an \emph{honest} verifier.
+This assumption does not hold in our setting, where every verifier at some point 
+also might be a (malicious) prover.
+We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
+Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
+\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
+
+\subsection{\Acl{DBIV} distance bounding}
+
 \dots
 
-\subsection{Impersonating-verifier distance bounding}
+\subsection{Reattempting \iacl{DB} Schnorr protocol}
 
-\dots
+In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
+make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
+That \ac{DB} Schnorr protocol was shown to be prone to distance 
+hijacking~\cite{DistanceHijacking}.
+We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
+which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
+It will not protect against terrorist fraud, in fact, we suspect that \ac{DBIV} 
+and \ac{DBTF} resistance are mutually exclusive.

### 2018-02-18 paper/DB-anon-cred.tex
Adds motivation for the new DBZKPK protocol
Adds DB Schnorr protocol figure

@@
 \ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
+The protocol is based on the Schnorr identification scheme and thus allows us to 
+do \ac{DB} \ac{ZKPK}, which allows us to form distance-bounding anonymous 
+credentials.
 
@@
 \subsection{Reattempting \iacl{DB} Schnorr protocol}
+
+\NewCryptoScheme{\DBS}{DBS}
+\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
+\NewAlgorithm{\DBSverify}{\DBS.\!Verify}
 
@@
 and \ac{DBTF} resistance are mutually exclusive.
+
+We present the protocol in \cref{SchnorrFigure}.
+The difference from the original Schnorr protocol is that the prover commits to 
+two random values and the verifier sends two challenges.
+Then the verifier decides which commitment and challenge to use in the \ac{DB} 
+phase.
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{lcl}
+    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
+    & &
+    \(\DBSverify[g, q, A]\): \\
+    \toprule
+
+    \multicolumn{3}{c}{\textbf{Setup}} \\
+
+    \(\rho_0\rgets \Z_q, \rho_1\rgets \Z_q\)
+    &
+    & \\
+
+    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
+    & \(\ProtoSendRight{R}\)
+    & \\
+
+    % null
+    & \(\ProtoSendLeft{c}\)
+    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\) \\
+
+    % null
+    &
+    & \(b\rgets \bin\) \\
+
+    \(s_0\gets \rho_0 + c_0\alpha\)
+    &
+    & \\
+
+    \(s_1\gets \rho_1 + c_1\alpha\)
+    &
+    & \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
+        \ceil{\log_2 q}\)} \\
+
+%    % null
+%    &
+%    & Random delay \\
+
+    % null
+    & \(\ProtoSendLeft{b_i}\)
+    & \(b_i\gets b\), random delay \\
+
+    \(r_i\gets s_{b_i}[i]\)
+    & \(\ProtoSendRight{r_i}\)
+    & \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Verification}} \\
+
+    % null
+    &
+    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\) \\
+
+    % null
+    &
+    & \(R_b \stackrel{?}{=} g^r A^{c_b}\) \\
+
+    \bottomrule
+  \end{tabular}
+  \caption{%
+    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
+    \ac{DB} Schnorr protocol for \(\PK{\alpha}{A = g^\alpha}\).
+    The protocol should be repeated in full to achieve the desired knowledge 
+    error and distance-bounding error.
+  }%
+  \label{SchnorrFigure}
+\end{figure*}
+
+The intuition behind the protocol security is as follows.
+The random delay in the \ac{DB} phase is important to prevent distance fraud.
+Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
+round-trip time without waiting for the challenges.
+
+Concerning Mafia fraud, the \ac{DBMF} adversary does not know which challenge 
+the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} 
+adversary will guess it correctly.
+The prover will only provide one of the responses: even if the adversary re-runs 
+the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
+will have changed --- which thus yields another \(R_b\) in the end of the 
+protocol.
+
+Distance hijacking, \ac{DBDH} \dots

### 2018-02-19 paper/DB-anon-cred.tex
DBS: improves protocol fig, adds analysis

@@
     & &
-    \(\DBSverify[g, q, A]\): \\
+    \(\DBSverify[g, q, A]\):
+    \\
     \toprule
@@
     &
-    & \\
+    &
+    \\
 
     \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
-    & \(\ProtoSendRight{R}\)
-    & \\
+    & \(\ProtoSendRight{R_0, R_1}\)
+    &
+    \\
 
     % null
-    & \(\ProtoSendLeft{c}\)
-    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\) \\
+    & \(\ProtoSendLeft{c_0, c_1}\)
+    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
+    \\
+
+    \(s_0\gets \rho_0 + c_0\alpha\)
+    &
+    &
+    \\
+
+    \(s_1\gets \rho_1 + c_1\alpha\)
+    &
+    &
+    \\
 
@@
     &
-    & \(b\rgets \bin\) \\
-
-    \(s_0\gets \rho_0 + c_0\alpha\)
-    &
-    & \\
-
-    \(s_1\gets \rho_1 + c_1\alpha\)
-    &
-    & \\
+    & \(b\rgets \bin\)
+    \\
 
@@
 %    &
-%    & Random delay \\
+%    & Random delay
+%    \\
 
@@
     & \(\ProtoSendRight{r_i}\)
-    & \\
+    & Record \(\Delta t_i\)
+    \\
 
     \midrule
-    \multicolumn{3}{c}{\textbf{Verification}} \\
+    \multicolumn{3}{c}{\textbf{Verification}}
+    \\
 
@@
     &
-    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\) \\
+    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\)
+    \\
 
@@
     &
-    & \(R_b \stackrel{?}{=} g^r A^{c_b}\) \\
+    & \(R_b \stackrel{?}{=} g^r A^{c_b}\)
+    \\
 
@@
 The intuition behind the protocol security is as follows.
-The random delay in the \ac{DB} phase is important to prevent distance fraud.
-Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
-round-trip time without waiting for the challenges.
-
-Concerning Mafia fraud, the \ac{DBMF} adversary does not know which challenge 
-the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} 
-adversary will guess it correctly.
+To achieve malicious-verifier zero-knowledge we must choose \(k\) 
+logarithmically in the security parameter \(\lambda\) and repeat the protocol 
+until the knowledge error is small enough.
+This will actually also decrease the success probability of \iac{DBMF} adversary 
+in the \ac{DB} step.
+The \ac{DBMF} adversary does not know which challenge the verifier will use, 
+thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
+correctly.
 The prover will only provide one of the responses: even if the adversary re-runs 
@@
 protocol.
+By repeating the protocol we can bring this probability down as much as desired.
+
+The random delay in the \ac{DB} phase is important to prevent distance fraud.
+Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
+round-trip time without waiting for the challenges.
+On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
+adversary to buffer the responses from the prover.
 

### 2018-02-19 paper/DB-anon-cred.tex
DBS: Adds to security discussion

@@
 protocol.
-By repeating the protocol we can bring this probability down as much as desired.
+By repeating the protocol we decrease this probability.
 
@@
 adversary to buffer the responses from the prover.
+However, in the worst case, the \ac{DBMF} adversary will be detected in the 
+first round, since he cannot buffer any response from the prover.
+After the first round though, the adversary knows \(b\) and can get those 
+requests as quickly as possible from the prover.
+By repeating the protocol we decrease this probability.
 
-Distance hijacking, \ac{DBDH} \dots
+The protocol is also secure against distance hijacking.
+This follows from the fact that it is the authenticating bit string that is used 
+during the \ac{DB} phase.

### 2018-02-19 paper/DB-anon-cred.tex
Changes from k to k+1 rounds

@@
 
+    % null
+    &
+    & Prepare \(B\in \bin^{k+l}\),
+    \\
+
+    % null
+    &
+    & with \(k\) bits set to \(b\)
+    \\
+
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
-        \ceil{\log_2 q}\)} \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < k+l\)} 
+    \\
 
@@
     & \(\ProtoSendLeft{b_i}\)
-    & \(b_i\gets b\), random delay \\
+    & \(b_i\gets B[i]\)
+    \\
 
@@
 
-The random delay in the \ac{DB} phase is important to prevent distance fraud.
-Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
-round-trip time without waiting for the challenges.
-On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
-adversary to buffer the responses from the prover.
-However, in the worst case, the \ac{DBMF} adversary will be detected in the 
-first round, since he cannot buffer any response from the prover.
-After the first round though, the adversary knows \(b\) and can get those 
-requests as quickly as possible from the prover.
-By repeating the protocol we decrease this probability.
+The \ac{DB} phase protects against distance fraud.
+\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with 
+\(r_i\).
+
+The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
+phase for at least one round.
+The verifier will send \(k+l < 2k\) challenges.
+Thus the prover reveals the \(k\) bits of either \(s_0\) or \(s_1\) and only 
+\(l\) bits of the other.
+Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
+them from the prover.
+But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
+then relay that challenge to the prover to receive the correct \(r_i\) --- this 
+relay will be detected.
 

### 2018-02-19 paper/ZKPK.tex
Adds Schnorr algorithm as instantiation of SPK

@@
 
-\paragraph{Implementations}
-
-There are various implementations.
-We will rely on the Schnorr identification scheme~\cite{Schnorr}.
+\subsection{Instantiations}
 
@@
 
-The notation in \cref{PKexample} could equivalently be seen as
+We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
+original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
+The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
+    \prod_{i=1}^n g_i^{\alpha_i}}\).
+This could equivalently be written as
 \begin{equation*}
-  \PKprove[g,h,y,y',q,\alpha,\beta,\gamma] \leftrightarrow
-  \PKverify[g,h,y,y',q],
+  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
+  \PKverify[\{g_i\}_i, q, A],
 \end{equation*}
@@
 \(\PKverify\) outputs accept (1) or reject (0).
+We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
+
+\begin{figure*}
+  \centering
+  \begin{tabular}{lcl}
+    \(\PKprove[g, q, A, \alpha]\):
+    &
+    & \(\PKverify[g, q, A]\):
+    \\
+
+  \end{tabular}
+  \caption{%
+    \(\PK{\alpha}{A = g^\alpha}\) using the Schnorr identification scheme.
+  }%
+  \label{PKalgorithms}
+\end{figure*}
+
+\NewAlgorithm{\SPKprove}{SPK.\!Prove}
+\NewAlgorithm{\SPKverify}{SPK.\!Verify}
+
+For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
+Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
+illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
+
+\begin{figure*}
+  \begin{minipage}[t]{0.48\linewidth}
+    \begin{algorithmic}
+      \Function{$\SPKprove$}{$g, q, A, \alpha, m$}
+        \State{$\rho\rgets \Z_q, R\gets g^\rho$}
+        \State{$c \gets H(g|A|R|m)$}
+        \State{$s \gets \rho - c\alpha$}
+        \State{\Return{$(s, c)$}}
+      \EndFunction{}
+    \end{algorithmic}
+  \end{minipage}
+  \hfill
+  \begin{minipage}[t]{0.48\linewidth}
+    \begin{algorithmic}
+      \Function{$\SPKverify$}{$g, q, A, m, s, c$}
+        \State{$\hat R \gets g^s A^c$}
+        \If{$c = H(g|A|\hat R|m)$}
+          \State{\Return{1}}
+        \Else{}
+          \State{\Return{0}}
+        \EndIf{}
+      \EndFunction{}
+    \end{algorithmic}
+  \end{minipage}
+  \caption{%
+    \(\SPK{\alpha}{A = g^\alpha}{m}\) using the Fiat-Shamir heuristic on the 
+    Schnorr identification scheme.
+  }%
+  \label{SPKalgorithms}
+\end{figure*}

### 2018-02-20 paper/LocationProofs.tex

\subsection{Location proofs}

Describe location proofs.

### 2018-02-20 paper/DB-anon-cred.tex

--- 2018-02-19 paper/DB-anon-cred.tex
@@
 
-We pointed out in \cref{DistanceBounding} that all security properties 
-concerning \ac{DB} assume an \emph{honest} verifier.
-This assumption does not hold in our setting, where every verifier at some point 
-also might be a (malicious) prover.
-We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
-Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
-The protocol is based on the Schnorr identification scheme and thus allows us to 
-do \ac{DB} \ac{ZKPK}, which allows us to form distance-bounding anonymous 
-credentials.
+\dots
 
-\subsection{\Acl{DBIV} distance bounding}
+\subsection{Impersonating-verifier distance bounding}
 
 \dots
-
-\subsection{Reattempting \iacl{DB} Schnorr protocol}
-
-\NewCryptoScheme{\DBS}{DBS}
-\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
-\NewAlgorithm{\DBSverify}{\DBS.\!Verify}
-
-In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
-make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
-That \ac{DB} Schnorr protocol was shown to be prone to distance 
-hijacking~\cite{DistanceHijacking}.
-We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
-which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
-It will not protect against terrorist fraud, in fact, we suspect that \ac{DBIV} 
-and \ac{DBTF} resistance are mutually exclusive.
-
-We present the protocol in \cref{SchnorrFigure}.
-The difference from the original Schnorr protocol is that the prover commits to 
-two random values and the verifier sends two challenges.
-Then the verifier decides which commitment and challenge to use in the \ac{DB} 
-phase.
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{lcl}
-    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
-    & &
-    \(\DBSverify[g, q, A]\):
-    \\
-    \toprule
-
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    \(\rho_0\rgets \Z_q, \rho_1\rgets \Z_q\)
-    &
-    &
-    \\
-
-    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
-    & \(\ProtoSendRight{R_0, R_1}\)
-    &
-    \\
-
-    % null
-    & \(\ProtoSendLeft{c_0, c_1}\)
-    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
-    \\
-
-    \(s_0\gets \rho_0 + c_0\alpha\)
-    &
-    &
-    \\
-
-    \(s_1\gets \rho_1 + c_1\alpha\)
-    &
-    &
-    \\
-
-    % null
-    &
-    & \(b\rgets \bin\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
-        \ceil{\log_2 q}\)} \\
-
-%    % null
-%    &
-%    & Random delay
-%    \\
-
-    % null
-    & \(\ProtoSendLeft{b_i}\)
-    & \(b_i\gets b\), random delay \\
-
-    \(r_i\gets s_{b_i}[i]\)
-    & \(\ProtoSendRight{r_i}\)
-    & Record \(\Delta t_i\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\)
-    \\
-
-    % null
-    &
-    & \(R_b \stackrel{?}{=} g^r A^{c_b}\)
-    \\
-
-    \bottomrule
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
-    \ac{DB} Schnorr protocol for \(\PK{\alpha}{A = g^\alpha}\).
-    The protocol should be repeated in full to achieve the desired knowledge 
-    error and distance-bounding error.
-  }%
-  \label{SchnorrFigure}
-\end{figure*}
-
-The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge we must choose \(k\) 
-logarithmically in the security parameter \(\lambda\) and repeat the protocol 
-until the knowledge error is small enough.
-This will actually also decrease the success probability of \iac{DBMF} adversary 
-in the \ac{DB} step.
-The \ac{DBMF} adversary does not know which challenge the verifier will use, 
-thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
-correctly.
-The prover will only provide one of the responses: even if the adversary re-runs 
-the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
-will have changed --- which thus yields another \(R_b\) in the end of the 
-protocol.
-By repeating the protocol we can bring this probability down as much as desired.
-
-The random delay in the \ac{DB} phase is important to prevent distance fraud.
-Otherwise \iac{DBDF} prover could just send all bits timed to the expected 
-round-trip time without waiting for the challenges.
-On the other hand, these delays must not be long enough to allow the \ac{DBMF} 
-adversary to buffer the responses from the prover.
-
-Distance hijacking, \ac{DBDH} \dots

### 2018-02-20 paper/ZKPK.tex
Adds Schnorr for PK protocol figure
Generalizes PK.{Prove,Verify}, SPK to generalized Schnorr

@@
 We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
+We also note that
+\begin{equation*}
+  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
+  \land \PK{\beta}{B = g^\beta},
+\end{equation*}
+however, the challenge \(c\) must be the same in both sub-protocols.
 
@@
   \begin{tabular}{lcl}
-    \(\PKprove[g, q, A, \alpha]\):
+    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
     &
-    & \(\PKverify[g, q, A]\):
+    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
+    \\
+    \toprule
+
+    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)
+    &
+    &
     \\
 
+    \(R\gets \prod_{i=1}^n g_i^{\rho_i}\)
+    & \(\ProtoSendRight{R}\)
+    &
+    \\
+
+    % null
+    & \(\ProtoSendLeft{c}\)
+    & \(c\rgets \bin^k\)
+    \\
+
+    \(1\leq i\leq n\colon s_i\gets \rho_i - c\alpha_i \mod q\)
+    & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
+    &
+    \\
+
+    % null
+    &
+    & \(R \stackrel{?}{=} A^c \prod_{i=1}^n g^{s_i}\)
+    \\
+
+    \bottomrule
   \end{tabular}
   \caption{%
-    \(\PK{\alpha}{A = g^\alpha}\) using the Schnorr identification scheme.
+    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
+    the Schnorr identification scheme.
   }%
@@
 \begin{figure*}
-  \begin{minipage}[t]{0.48\linewidth}
+  \begin{minipage}[t]{0.49\linewidth}
     \begin{algorithmic}
-      \Function{$\SPKprove$}{$g, q, A, \alpha, m$}
-        \State{$\rho\rgets \Z_q, R\gets g^\rho$}
-        \State{$c \gets H(g|A|R|m)$}
-        \State{$s \gets \rho - c\alpha$}
-        \State{\Return{$(s, c)$}}
+      \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
+        \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)}
+        \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
+        \State{$c \gets H(\{g_i\}_i|A|R|m)$}
+        \For{$1\leq i\leq n$}
+          \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
+        \EndFor{}
+        \State{\Return{$(\{s_i\}_i, c)$}}
       \EndFunction{}
@@
   \hfill
-  \begin{minipage}[t]{0.48\linewidth}
+  \begin{minipage}[t]{0.49\linewidth}
     \begin{algorithmic}
-      \Function{$\SPKverify$}{$g, q, A, m, s, c$}
-        \State{$\hat R \gets g^s A^c$}
-        \If{$c = H(g|A|\hat R|m)$}
+      \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
+        \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
+        \If{$c = H(\{g_i\}_i|A|\hat R|m)$}
           \State{\Return{1}}
@@
   \caption{%
-    \(\SPK{\alpha}{A = g^\alpha}{m}\) using the Fiat-Shamir heuristic on the 
-    Schnorr identification scheme.
+    \(\SPK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}{m}\) 
+    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
   }%

### 2018-02-20 paper/ZKPK.tex
Adds description of malicious ZKPK

@@
 
-\NewAlgorithm{\PKprove}{PK.\!Prove}
-\NewAlgorithm{\PKverify}{PK.\!Verify}
+\NewCryptoScheme{\Schn}{Schn}
+\NewAlgorithm{\SchnProve}{\Schn.\!Prove}
+\NewAlgorithm{\SchnVerify}{\Schn.\!Verify}
 
-We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
-original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
+We will rely on the Schnorr identification scheme~\cite{Schnorr} (\Schn), which 
+in its original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
 The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
@@
 \begin{equation*}
-  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
-  \PKverify[\{g_i\}_i, q, A],
+  \SchnProve[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
+  \SchnVerify[\{g_i\}_i, q, A],
 \end{equation*}
-where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
+where \(\SchnProve\) is run by the prover and \(\SchnVerify\) is run by the 
 verifier.
-\(\PKverify\) outputs accept (1) or reject (0).
-We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
+\(\SchnVerify\) outputs accept (1) or reject (0).
+We give an instance of \(\SchnProve\) and \(\SchnVerify\) in \cref{PKalgorithms}.
 We also note that
@@
   \begin{tabular}{lcl}
-    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
+    \(\SchnProve[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
     &
-    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
+    & \(\SchnVerify[\{g_i\}_{i=1}^n, q, A]\):
     \\
@@
 
-\NewAlgorithm{\SPKprove}{SPK.\!Prove}
-\NewAlgorithm{\SPKverify}{SPK.\!Verify}
+\NewCryptoScheme{\PKscheme}{PK}
+\NewAlgorithm{\PKprove}{\PKscheme.\!Prove}
+\NewAlgorithm{\PKverify}{\PKscheme.\!Verify}
+
+Schnorr (\(\Schn\)) in itself only provides honest-verifier zero-knowledge.
+To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
+the challenge) logarithmic in the security parameter \(\lambda\) and repeat the 
+protocol sufficiently many times.
+
+\NewAlgorithm{\Prove}{Prove}
+\NewAlgorithm{\Verify}{Verify}
+\NewCryptoSet{\PKG}{G}
+\NewCryptoSet{\PKA}{A}
+\NewCryptoSet{\PKS}{S}
+
+\begin{figure*}
+  \begin{minipage}{0.49\linewidth}
+    \begin{algorithmic}
+      \Function{$\PKprove^S$}{$\PKG, q, A, \PKA$}
+        \For{$0\leq i\leq \log\lambda$}
+          \State{$\method{S}{\Prove[\PKG, q, A, \PKA][_{k = \log\lambda}]}$}
+        \EndFor{}
+      \EndFunction{}
+    \end{algorithmic}
+  \end{minipage}
+  \begin{minipage}{0.49\linewidth}
+    \begin{algorithmic}
+      \Function{$\PKverify^S$}{$\PKG, q, A$}
+        \For{$0\leq i\leq \log\lambda$}
+          \State{$\method{S}{\Verify[\PKG, q, A][_{k=\log\lambda}]}$}
+        \EndFor{}
+      \EndFunction{}
+    \end{algorithmic}
+  \end{minipage}
+  \caption{%
+    Transforming honest-verifier zero-knowledge to malicious-verifier 
+    zero-knowledge.
+  }%
+  \label{ZKPKalgorithms}
+\end{figure*}
+
+\NewCryptoScheme{\SSchn}{SSchn}
+\NewAlgorithm{\SPKprove}{\SSchn.\!Prove}
+\NewAlgorithm{\SPKverify}{\SSchn.\!Verify}
 
 For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
-Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
-illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
+Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on \Schn, illustrated as 
+\(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
 

### 2018-02-20 paper/ZKPK.tex
Adds description of how to make Schnorr malicious verifier ZK

--- 2018-02-20 paper/ZKPK.tex
@@
 
+The Schnorr protocol in itself only provides honest-verifier zero-knowledge.
+To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
+the challenge) logarithmic in the security parameter \(\lambda\) and repeat the 
+protocol sufficiently many times (also logarithmic in the security parameter).
+
 \NewAlgorithm{\SPKprove}{SPK.\!Prove}

### 2018-02-20 paper/ZKPK.tex

--- 2018-02-20 paper/ZKPK.tex
@@
 
+The Schnorr protocol in itself only provides honest-verifier zero-knowledge.
+To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
+the challenge, see \cref{PKalgorithms}) logarithmic in the security parameter 
+\(\lambda\) and repeat the protocol sufficiently many times (also logarithmic in 
+the security parameter).
+
 \NewAlgorithm{\SPKprove}{SPK.\!Prove}

### 2018-02-21 paper/conclusions.tex

--- 2017-09-27 conclusions.tex
@@
-\mode*
 \section{Conclusions}
-
-\mode<presentation>{%
-\subsection{Related work}
-}
 
@@
 And finally, most of the current methods are estimates, with quite some error 
-margins, so they cannot give the correct participation count.
-
-\begin{frame}<presentation>
-  \begin{block}{Verifiability}
-    \begin{itemize}
-      \item All current methods lack most of verifiability.
-      \item Some can provide universal verifiability.
-    \end{itemize}
-  \end{block}
-
-  \pause{}
-
-  \begin{block}{Correctness}
-    \begin{itemize}
-      \item Most cannot estimate the correct participation count.
-      \item Some can (theoretically) give an upper bound.
-    \end{itemize}
-  \end{block}
-\end{frame}
+margins.

### 2018-02-21 paper/intro.tex

@@
 problem, i.e.\ to verify how many participated in Alice's protest.
-
-\mode<presentation>{%
-\subsection{What's the problem?}
-}
-
-\begin{frame}<presentation>
-  \begin{block}{The crowd-counting problem}
-    \begin{itemize}
-      \item Alice organizes a protest against Eve's regime.
-      \item Bob, Carol and others show up.
-      \item We want to know how many showed up to support Alice.
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\mode<presentation>{%
-\subsection{Why is it a problem?}
-}
-
-\mode<presentation>{%
-\begin{frame}
-  \begin{figure}
-    \includegraphics[height=0.9\textheight]{Jacobs-method.jpg}
-  \end{figure}
-\end{frame}
-
-\begin{frame}
-  \begin{example}
-    \begin{itemize}
-      \item Computer vision does object recognition.
-      \item Requires photos/video that cover the entire location, all the time.
-      \item This will count people twice.
-    \end{itemize}
-  \end{example}
-
-  \pause{}
-
-  \begin{example}
-    \begin{itemize}
-      \item Scan active mobile phones in the area.
-      \item This requires some extra equipment.
-      \item This catches bystanders who are not protesting.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
-
-\mode<none>{%
-\begin{frame}
-  \begin{example}
-    \begin{itemize}
-      \item South Korea 2016~\cite{2016DemonstrationsInSeoul}:
-        approximate count by imagery.
-        \begin{description}
-          \item[Organizers] 1\,000\,000
-          \item[Police] 260\,000
-        \end{description}
-
-        \pause{}
-
-      \item US 2017~\cite{2017WomensMarchesInUS}:
-        sum up people's approximations.
-      \item This makes it even difficult to estimate the error.
-    \end{itemize}
-  \end{example}
-\end{frame}
-}
 

### 2018-02-21 paper/SystemModel.tex
Breaks too long equation over two lines

@@
   is the set
-  \begin{align}
+  \begin{multline}
     \nonumber
     p_{i, j} =
-    \left\{ (pid, cid, t, l, wid)\in W \mid
-    %\right. &
-    pid = i, cid = j,
-    %\\ & \left.
+    \left\{ (pid, cid, t, l, wid)\in W \mid \right. \\
+    \left. pid = i, cid = j,
     t \subseteq t_j, l\subseteq l_j \right\},
-  \end{align}
+  \end{multline}
   of all proof shares with the same protester and protest identifiers, witness 

### 2018-02-21 paper/protocol.tex
Changes order of sections, changes PRF to \PRF

@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
             \Sign[k]{k_W}}{pid, wid, t_s, l, wsig} \\
-        %& NIZK(wid = PRF_{k_W}(pid), wsig = PRF_{k_W}(wid, t_s, l), \exists 
-        %sign(k_W)) \\
       P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
@@
   \label{fig:ProtocolOverview}
-\end{figure}
+\end{figure*}
 
@@
 }, where \(n = 1\) in our scenario.
-Alice has a \ac{PRF} key \(k\) and a blind signature on \(k\) included in her 
+Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
 national identity-card (by assumption).
-She will use \(k\) to compute \(pid\gets PRF_k(cid)\), which is her anonymous 
+She will use \(k\) to compute \(pid\gets \PRF_k(cid)\), which is her anonymous 
 identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
@@
 
-Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(cid)\) and 
+Alice must provide \iac{NIZK} proof showing that \(pid = \PRF_{k_P}(cid)\) and 
 that she knows a signature by the identity authority on \(k_P\).
@@
 In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
-  PRF_{k_W}(pid)\) and \(wsig = PRF_{k_W}(wid, t_s, l)\) as well as that the 
+  \PRF_{k_W}(pid)\) and \(wsig = \PRF_{k_W}(wid, t_s, l)\) as well as that the 
 witness knows a signature by the identity authority on \(k_W\).
@@
 More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
-must remove her secret PRF key, \(k_A\).
+must remove her secret \ac{PRF} key, \(k_A\).
 With this key Eve can verify that Alice has submitted a proof by computing 
-\(pid'\gets PRF_{k_A}(cid)\) and compare \(pid = pid'\).
+\(pid'\gets \PRF_{k_A}(cid)\) and compare \(pid = pid'\).

### 2018-02-22 paper/BuildingBlocks.tex
Renames primitives.tex to BuildingBlocks.tex
Rearranges Building Blocks section

--- 2017-09-30 primitives.tex
@@
 
-\subsection{Zero-knowledge proofs}
-
-Briefly describe zero-knowledge proofs and what type of properties can be proved 
-efficiently using them, e.g.\ algebraic structures but not one-way functions.
-
-\dots
-
-\subsection{Location proofs and distance bounding}
-
-Briefly describe location proofs and distance bounding protocols.
-Describe the different desirable properties for distance bounding:
-\begin{itemize}
-  \item Mafia-fraud resistance,
-  \item terrorist-fraud resistance,
-  \item impersonation-fraud resistance,
-  \item distance-fraud resistance.
-\end{itemize}
-
-\subsection{Storage}
-
-We will use the storage to provide the temporal eligibility property.
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-One primitive that fulfils these requirements is a blockchain.
-There are also other structures, e.g.\ a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
-properties.
-However, we will use the blockchain in our discussion for simplicity.
-
-There are three properties that we need from the storage system.
-The first property we need is decentralized, immutable storage with a general 
-form of time-stamping.
-I.e.\ once we commit something to the blockchain it will remain there and we do 
-not have to trust any central authority.
-We can also relate commitments to time, e.g.\ in Bitcoin~\cite{Bitcoin} a new 
-block appears approximately every 10 minutes.
-
-The second property we need is an unpredictable number whose time of publication 
-can be verified.
-For this property, we will use the head of the blockchain.
-The hash value of the head of the blockchain at a given time will be difficult 
-to predict ahead of time.
-%(See \cref{SecurityAnalysis} for a security analysis.)
-We want to use this to ensure that proofs are created after a certain point in 
-time.
-
-The third property is that once we have committed some data, we do not need to 
-keep the data itself, but we can store some confirmation value instead.
-E.g.\ using blockchains, we can store the hash of the block where our data was 
-committed, while this block remains we are sure that our data remains committed 
---- even if we no longer remember what our data looked like.
-We will use this property to approximate the property of receipt freeness.
+\input{anon-cred.tex}
+\input{DistanceBounding.tex}
+\input{LocationProofs.tex}
+\input{TimeStamp.tex}

### 2018-02-25 paper/DistanceBounding.tex
Writes shortly about distance bounding and our needs

@@
-\subsection{Distance bounding}
+\subsection{Distance bounding}%
+\label{DistanceBounding}
 
-Briefly describe location proofs and distance bounding protocols.
-Describe the different desirable properties for distance bounding:
+% XXX Better intro to distance bounding
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding}.
+Over the years the desirable properties of \ac{DB} protocols can be summarized 
+as follows:
 \begin{itemize}
-  \item Mafia-fraud resistance,
-  \item terrorist-fraud resistance,
-  \item impersonation-fraud resistance,
-  \item distance-fraud resistance.
+    % XXX Describe the DB frauds in more detail, i.e. explain them.
+  \item \ac{DBMF} resistance,
+  \item \ac{DBDF} resistance,
+  \item \ac{DBDH} resistance,
+  \item \ac{DBTF} resistance,
+  \item \ac{DBIF} resistance,
 \end{itemize}
+There are two lines of attempts at formalizing the above properties: one by 
+\citet{DB-BMV} and another by \citet{DB-DFKO}.
+
+The majority of the existing \ac{DB} protocols are symmetric and thus requires 
+an honest verifier.
+There has been less work done in the domain of asymmetric (or public-key) 
+\ac{DB} protocols.
+Unfortunately, our setting requires a public-key \ac{DB} protocol with a 
+\emph{malicious verifier} who will try to \emph{impersonate the prover}.
+The verifier might also try to track the provers and map their identities to 
+their actions, thus we also require privacy.
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}.
+More specifically, we must combine \ac{DB} with anonymous credentials, which we 
+will describe next.

### 2018-02-25 paper/BuildingBlocks.tex
Changes order: distance bounding before anon creds
Writes about our needed hash functions

@@
 
-\dots
+We need a few primitives with special properties to build our protocol.
 
+\subsection{Collision-resistant hash functions}
+
+\NewAlgorithm{\Hash}{H}
+\NewAlgorithm{\algA}{A}
+
+One primitive that we need is a collision-resistant hash function, \Hash.
+
+\begin{definition}[Collision resistance]
+  Let \(\lambda\) denote the security parameter.
+  We say that a hash function, \(\Hash\), is collision resistant if for any 
+  \ac{PPT} algorithm \(\algA\) we have that
+  \begin{multline*}
+    \Pr\left[ x_1, x_2\gets \algA[1^\lambda] :
+      \right. \\ \left.
+      \Hash[x_1] = \Hash[x_2] \land x_1\neq x_2 \right] < \negl[\lambda].
+  \end{multline*}
+\end{definition}
+
+Thus we can instantiate \(\Hash\) with any algorithm from the SHA-2 or SHA-3 
+families.
+
+\input{DistanceBounding.tex}
 \input{anon-cred.tex}
-\input{DistanceBounding.tex}
 \input{LocationProofs.tex}

### 2018-02-25 paper/DistanceBounding.tex
Clarifies our need for the distance bounding

@@
 their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}.
-More specifically, we must combine \ac{DB} with anonymous credentials, which we 
-will describe next.
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with 
+resistance to all the frauds mentioned above as well as against this verifier 
+who will attempt to impersonate the prover.
+More specifically, we must combine such \iac{DB} with anonymous credentials, 
+which we will describe next.

### 2018-02-25 paper/analysis.tex
Adds AnonPass, thus we can use their performance evals

--- 2018-02-01 paper/security.tex
@@
 Statements such as this should be proved: provide a valid but missing proof.
+
+\subsection{Threshold of witnesses}
+
+Assume that every person has 5000 contacts in their contact 
+book~\cite{DifficultyOfPrivateContactDiscovery}.
+Then it would be reasonable to set the threshold of at least 6000 witnesses.
+According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
+signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
+\SI{2.66}{\giga\hertz} Core 2 processor.
+This yields \(
+  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+  \SI{48}{\second}.
+\) of processing.

### 2018-02-26 paper/SystemModel.tex
system model edits and some questions in comments regarding the identifiers in the definitions. only a label added in the protocol for referencing.

@@
 
-The organizer Alice want to count everyone who participated at any time and in 
+The organizer Alice wants to count everyone who participated at any time and in 
 any of the locations~\cite{2016DemonstrationsInSeoul}.
@@
   A \emph{subprotest} is a tuple \((cid, t, l)\) where
-  \(cid\in \Z_{2^\lambda}\) is the cause\footnote{%
-    I.e.\ the cause of the protest.
-  } identifier,
+  \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
   \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
@@
 
-\subsection{Participation and count}
+\subsection{What is a proper count?}
 
-Each participant who want to be counted must submit a participation proof.
+Each participant who wants to be counted must submit a participation proof.
 The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
 time and location must coincide with any of its subprotests.
-We use witnesses to associate the proof to the location by creating a proof 
+
+In practical terms, participants witness each other's particpation
+using their smartphones running the protocol described in
+Section~\ref{protocol} and uploading their testimony to a blockchain
+after the protest.
+
+More formally, we use witnesses to associate the proof to the location by creating a proof 
 share.
@@
 \end{definition}
+%Sonja asks: do the same pair of people (witness-protester) get the
+%same wid on a different protest? The pid is unique for protester-cid
+%pair thus the id of a protester at a particular protest. Pid is thus
+%derived from the protester id (which has no term) and the protest id
+%(cid)? In analogy, wid is derived from pid (and thus cid) of both
+%participants, protesters i and j, say, where i witnesses j at cid and
+%simultaneously symmetrically j witnesses i?
+%Using wid and w is confusing since we changed the terminology to use
+%proof shares instead of the previous witness (as in testimony, not
+%person). wid sounds like it would be the id of the witness person,
+%pid sounds like it would be the id of the protester being witnessed,
+%we have defined neither and they might not be needed, but it is
+%confusing to read.
 

### 2018-02-26 paper/ZKPK.tex
Breaks up long equation
Breaks out ZKPK

@@
-\subsection{Zero-knowledge proofs of knowledge}%
+\subsubsection{Zero-knowledge proofs of knowledge}%
 \label{ZKPK}
-
-Briefly describe zero-knowledge proofs and what type of properties can be proved 
-using them, e.g.\ algebraic structures but not one-way functions.
 
@@
 
-\subsection{Instantiations}
+\subsubsection{Instantiations of the \acs{ZKPK} protocols}
 
@@
 We also note that
-\begin{equation*}
-  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \PK{\alpha}{A = g^\alpha} 
-  \land \PK{\beta}{B = g^\beta},
-\end{equation*}
+\begin{multline*}
+  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \\
+  \PK{\alpha}{A = g^\alpha} \land \PK{\beta}{B = g^\beta},
+\end{multline*}
 however, the challenge \(c\) must be the same in both sub-protocols.
@@
     \\
-    \toprule
+    \midrule
 
@@
 
-    \bottomrule
   \end{tabular}

### 2018-02-26 paper/RelatedWork.tex
edited and added urban count and divote

@@
 (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
-this might still be difficult.
+this might still be difficult. Automatic face recognition can help
+verifiability but at the price of privacy.
 Also, it is difficult (if not impossible) to not count people twice, thus we 
@@
 uncomfortable to be registered in association with the event and might thus 
-turn the device off.
+turn the device off, even though, at least with 5G, the IMSI will not be
+transmitted in plaintext anymore. %need to cite?
 Finally, there will be limited verifiability, as the data recorder must be 
@@
 
-The most closely related work is \citet{CrowdCount}.
+One of the most closely related work is \citet{CrowdCount}.
 This is a web service which lets Alice create an event and Bob can submit his 
@@
 backbone as a means to censor the protest.
+
+Another related approach based on devices is \citet{UrbanCount} which
+uses epidemic spreading of crowd-size estimates by device-to-device
+communication to count crowds in dense urban environments with high
+node mobility and churn. There is, however, no consideration of a potentially
+adverserial setting and thus no verification or checks on
+eligibility. \citet{DiVote}, a prior work by the same authors for
+polling in dense areas, avoids double counting but again only for
+honest participants.

### 2018-02-26 paper/intro.tex

@@
 
-Alice is an activist who organizes a protest for some cause.
+Elaborating on the scenario sketched in the abstract, Alice is an
+activist who organizes a protest for some cause.
 Eve is an autocrat who opposes Alice's cause.
-Bob, Carol and many others participate in the protest against Eve.
-One problem that has not yet been entirely solved is the crowd-counting 
-problem, i.e.\ to verify how many participated in Alice's protest.
+Bob, Carol and many others participate in the protest for Alice's
+cause and thus against Eve. To verify how many participated in Alice's
+protest, a reliable crowd-counting mechanism is needed which is a 
+problem that has not yet been entirely solved.
 
 After many demonstrations the count by police and that by the organizers 
-differ\footnote{%
-  This is actually quite natural, they have different goals.
+differ, for legitimate\footnote{%
+  A difference is actually quite natural, as the counts have different goals.
   The organizers want to count everyone who ever participated.
@@
   control~\cite{2016DemonstrationsInSeoul}.
-}, in some instances the difference can be hundreds of thousands.
+} or other reasons, in some instances the difference can be hundreds of thousands.
 There are numerous examples where there is difficulty in establishing the actual 
@@
 
-We can make one important observation about this problem that has seemingly been 
-ignored in the past: it is an adversarial setting.
+We can make one important observation about this problem that has not
+been adequately addressed in the design of existing crowd-counting solutions: it is an adversarial setting.
 Alice the activist has an incentive to increase the tallied number of 
@@
 To solve this problem, we need a verifiable participation count which is 
-protected from Sybil attacks.
+protected from Sybil attacks while still preserving the participants'
+privacy to the extent possible given their physical presence at the protest.
 
-\subsection{Combining electronic voting and location proofs}
+\subsection{Combining properties of electronic voting with location proofs}
 
@@
 \end{itemize}
-We note that we cannot improve the privacy of participating protesters during 
-the protest: if Alice is caught during a protest there is nothing we can do.
-Actually, if there are several protests in the \emph{same location at the same 
-  time}, Alice could blend into another crowd and argue that she participated in 
+We note that we cannot actually improve the privacy of participating protesters during 
+the protest: if Alice is caught during a protest or other
+crowd-counting mechanisms based on photographic or video evidence are
+used to identify Alice, there is nothing we
+can do. In our proposed solution, however, we aim at verifiable
+participation count that does not add any threats to the participants'
+privacy. For instance, if there are counter-protests in the \emph{same location at the same 
+  time}, Alice could even blend into another crowd and argue that she participated in 
 a different protest than she actually did --- and the counts would still be 
@@
 However, even if there is only one protest and she is not caught in the act, 
-then using our proposed tool should not incur any additional risk.
+then using our proposed mechanism should not incur any additional risk.
 Thus we need at least participation-proof privacy but receipt freeness (see 
@@
 In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
-participation proof --- even if she would compromise Alice's devices.
+participation proof --- even if she were to compromise Alice's
+devices.
+%Sonja says: I'm confused: can we or can we not provide this?
 
@@
 protesters' privacy than participating in the physical protest itself.
+
+In contrast to the traditional assumption of honest verifiers in
+distance-bounding algorithms, we propose a way to turn the Schnorr
+protocol into a distance-bounding protocol that allows for a malicious
+verifier. In addition, this allows us to form distance-bounding
+anonymous credentials.
+
+\subsection{Limitations and Assumptions}
 
@@
 
-\dots
+%\dots
 
-Sometimes Eve's authoritarian regime wants to organize a pro-regime protest to 
+Some of our assumptions (see Section \ref{assumptions} for more
+detailed descriptions) are not yet
+realized. Not all (or even many) protesters, especially in countries
+with oppressive regimes, currently possess smartphones. Digital
+certificates signed by a central authority are not yet widely
+available and if we rely on government-issued credentials, we cannot prevent the government 
+from performing Sybil attacks --- since it can issue arbitrarily many 
+\enquote{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
 demonstrate its \enquote{wide 
   support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-If we rely on government-issued credentials, we cannot prevent the government 
-from performing Sybil attacks --- since it can issue arbitrarily many 
-\enquote{valid} credentials.
-This means that we cannot verify any pro-government protests.
+Distance bounding on phones is currently not feasible within a
+meaningful range of distance for our scenario.
+
+The assumptions might
+become sufficiently realistic in the near future, though, with
+smartphone penetration on the rise, increased digitalization and government-issued credentials
+available in some countries already now (e.g., Estonia, Germany), and
+distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
+might not unrealistically be integrated in phones or smartcards in the
+future.
+
+\subsection{Roadmap}
+The rest of the paper is organized as follows. First, we define the
+system model for verifiable privacy-preserving crowd counting.  We then
+present the desired security properties for such a system and subsequently discuss related
+work in terms of these properties. We give the relevant background on
+the building blocks of our solution and then describe our proposal for
+distance-bounding anonymous credentials that copes with a malicious
+(impersonating) verifier. We then present the protocol constructed
+from the building blocks, its security and privacy analysis, and
+finally our conclusions.

### 2018-02-26 paper/RelatedWork.tex
references for urbancount, divote

@@
 
-Another related approach based on devices is \citet{UrbanCount} which
+Another related approach based on devices is UrbanCount~\cite{UrbanCount} which
 uses epidemic spreading of crowd-size estimates by device-to-device
@@
 adverserial setting and thus no verification or checks on
-eligibility. \citet{DiVote}, a prior work by the same authors for
+eligibility. DiVote~\cite{DiVote}, a prior work by the same authors for
 polling in dense areas, avoids double counting but again only for

### 2018-02-26 paper/SystemModel.tex
manet references, MANETs.tex, issue 28, included in system model

@@
 
-In practical terms, participants witness each other's particpation
-using their smartphones running the protocol described in
-Section~\ref{protocol} and uploading their testimony to a blockchain
-after the protest.
-
-More formally, we use witnesses to associate the proof to the location by creating a proof 
+We use witnesses to associate the proof to the location by creating a proof 
 share.
@@
 witnesses.
+
+\subsection{Physical System Model}
+In practical terms, participants witness each other's particpation
+using their smartphones running the protocol described in
+Section~\ref{protocol} and uploading their testimony to a blockchain
+after the protest. They thus need connectivity at least to each other
+during the protest and Internet connectivity after.
+
+\include*{MANETs}

### 2018-02-26 paper/intro.tex
coincoin

@@
 
-Elaborating on the scenario sketched in the abstract, Alice is an
-activist who organizes a protest for some cause.
-Eve is an autocrat who opposes Alice's cause.
-Bob, Carol and many others participate in the protest for Alice's
-cause and thus against Eve. To verify how many participated in Alice's
-protest, a reliable crowd-counting mechanism is needed which is a 
-problem that has not yet been entirely solved.
+Consider the following scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
+On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
+On the other hand, Eve is an autocrat who opposes Alice's cause.
+Bob, Carol and many others participate in the protest for Alice's cause against Eve.
+However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
+To verify how many participated in Alice's protest, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
@@
 from performing Sybil attacks --- since it can issue arbitrarily many 
-\enquote{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
-demonstrate its \enquote{wide 
+\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
+demonstrate its \emph{wide 
   support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.

### 2018-02-26 paper/intro.tex
change to intro

@@
 
-Consider the following scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
+\emph{Context.} Consider the following illustrative scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
 On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
@@
 However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
-To verify how many participated in Alice's protest, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
+To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
-After many demonstrations the count by police and that by the organizers 
-differ, for legitimate\footnote{%
-  A difference is actually quite natural, as the counts have different goals.
-  The organizers want to count everyone who ever participated.
-  Police want to estimate the count at the peak of participation, due to crowd 
-  control~\cite{2016DemonstrationsInSeoul}.
-} or other reasons, in some instances the difference can be hundreds of thousands.
-There are numerous examples where there is difficulty in establishing the actual 
-number of participants, e.g.:\@ the demonstrations against the president in 
-South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration 
-attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March 
-in the US~\cite{2017WomensMarchesInUS}, the demonstrations against changing the 
-constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the 
-independence of Catalonia~\cite{CataloniaDemonstrations}.
-The methods for counting the crowds vary.
-Most of the available methods lack precision, i.e.\ they have large error 
-margins.
-They can only give an estimate for a particular snapshot in time, e.g.\ at the 
-peak of the event, not the cumulative participation count --- at least not 
-without counting some people multiple times, which in turn increases the error 
-of the estimation.
-Finally, they also lack verifiability, i.e.\ everyone must trust the entity who
-does the counting.
-(We will discuss them in more detail in \cref{RelatedWork}.)
+Historically, there are many examples of protests in which the count estimated by police and that by the organizers 
+differ significantly, sometimes in the order of hundreds of thousands.
+The difference is actually quite natural as both parties have different objectives.
+More precisely, the organizers want to count everyone who have participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
+Among the numerous recent examples in which it is difficult to establish the actual number of participants, we can cite the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
-We can make one important observation about this problem that has not
-been adequately addressed in the design of existing crowd-counting solutions: it is an adversarial setting.
-Alice the activist has an incentive to increase the tallied number of 
-participants, whereas Eve (and possibly other interests) have an incentive to 
-decrease the tallied number of participants.
-In this case we have two options:
-either we trust Alice or Eve, or we must verify their claims.
-Our main goal is to provide a scheme which prevents both Alice and Eve from 
-cheating, i.e.\ we aim for verifiable claims.
-To solve this problem, we need a verifiable participation count which is 
-protected from Sybil attacks while still preserving the participants'
+Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
+However, most of them lack precision (\emph{i.e.}, they have large error margins) and they can only give an estimate for a particular snapshot in time (\emph{e.g.}, at the peak of the event). 
+In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
+In addition, they also lack verifiability as everyone has to trust the entity responsible for performing the counting.
+Finally, one important observation about crowd-counting that has been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting.
+
+Indeed, going back to our example Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease the tallied number of participants.
+In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
+In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\emph{i.e.}, their claim should be verifiable).
+To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
 privacy to the extent possible given their physical presence at the protest. 
+More precisely, our solution will not be able to prevent a physical eavesdropper from recognizing a particular individual in a protest. 
+Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated to his identity and that his actions are also unlinkable.
 
+%Seb: I suggest that we give a name to the protocol to be able to refer to it more adequately
+\emph{Contributions} We propose a scheme that provides a way for protests to be securely verified.
+Additionally, this verification system does not incur any additional risk to 
+protesters' privacy than participating in the physical protest itself.
+
+In contrast to the traditional assumption of honest verifiers in
+distance-bounding algorithms, we propose a way to turn the Schnorr
+protocol into a distance-bounding protocol that allows for a malicious
+verifier. In addition, this allows us to form distance-bounding
+anonymous credentials.
+
+\subsection{Limitations and Assumptions}
+
+We can achieve privacy, but not receipt freeness.
+This means that there is a way for Eve to efficiently verify that Alice has 
+participated.
+However, this requires that Eve gets a copy of Alice's secret key so that she 
+can simply re-do the (deterministic) computations on the same inputs --- the 
+probability of collisions is negligible.
+
+%\dots
+
+Some of our assumptions (see Section \ref{assumptions} for more
+detailed descriptions) are not yet
+realized. Not all (or even many) protesters, especially in countries
+with oppressive regimes, currently possess smartphones. Digital
+certificates signed by a central authority are not yet widely
+available and if we rely on government-issued credentials, we cannot prevent the government 
+from performing Sybil attacks --- since it can issue arbitrarily many 
+\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
+demonstrate its \emph{wide 
+  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+Distance bounding on phones is currently not feasible within a
+meaningful range of distance for our scenario.
+
+The assumptions might
+become sufficiently realistic in the near future, though, with
+smartphone penetration on the rise, increased digitalization and government-issued credentials
+available in some countries already now (e.g., Estonia, Germany), and
+distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
+might not unrealistically be integrated in phones or smartcards in the
+future.
+
+\emph{Outline.} The paper is organized as follows. 
+First, we define the system model for verifiable privacy-preserving crowd counting.  We then
+present the desired security properties for such a system and subsequently discuss related
+work in terms of these properties. We give the relevant background on
+the building blocks of our solution and then describe our proposal for
+distance-bounding anonymous credentials that copes with a malicious
+(impersonating) verifier. We then present the protocol constructed
+from the building blocks, its security and privacy analysis, and
+finally our conclusions.
+
+%Seb: I suggest that we move this part to system model
 \subsection{Combining properties of electronic voting with location proofs}
@@
 %Sonja says: I'm confused: can we or can we not provide this?
-
-\subsection{Contributions}
-
-We propose a protocol which provides a way for protests to be securely verified.
-Additionally, this verification system does not incur any additional risk to 
-protesters' privacy than participating in the physical protest itself.
-
-In contrast to the traditional assumption of honest verifiers in
-distance-bounding algorithms, we propose a way to turn the Schnorr
-protocol into a distance-bounding protocol that allows for a malicious
-verifier. In addition, this allows us to form distance-bounding
-anonymous credentials.
-
-\subsection{Limitations and Assumptions}
-
-We can achieve privacy, but not receipt freeness.
-This means that there is a way for Eve to efficiently verify that Alice has 
-participated.
-However, this requires that Eve gets a copy of Alice's secret key so that she 
-can simply re-do the (deterministic) computations on the same inputs --- the 
-probability of collisions is negligible.
-
-%\dots
-
-Some of our assumptions (see Section \ref{assumptions} for more
-detailed descriptions) are not yet
-realized. Not all (or even many) protesters, especially in countries
-with oppressive regimes, currently possess smartphones. Digital
-certificates signed by a central authority are not yet widely
-available and if we rely on government-issued credentials, we cannot prevent the government 
-from performing Sybil attacks --- since it can issue arbitrarily many 
-\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
-demonstrate its \emph{wide 
-  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Distance bounding on phones is currently not feasible within a
-meaningful range of distance for our scenario.
-
-The assumptions might
-become sufficiently realistic in the near future, though, with
-smartphone penetration on the rise, increased digitalization and government-issued credentials
-available in some countries already now (e.g., Estonia, Germany), and
-distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
-might not unrealistically be integrated in phones or smartcards in the
-future.
-
-\subsection{Roadmap}
-The rest of the paper is organized as follows. First, we define the
-system model for verifiable privacy-preserving crowd counting.  We then
-present the desired security properties for such a system and subsequently discuss related
-work in terms of these properties. We give the relevant background on
-the building blocks of our solution and then describe our proposal for
-distance-bounding anonymous credentials that copes with a malicious
-(impersonating) verifier. We then present the protocol constructed
-from the building blocks, its security and privacy analysis, and
-finally our conclusions.

### 2018-02-26 paper/MANETs.tex

%@sbuc: Can you write a few words about MANETs (file MANETs.tex)?
%More specifically, why we can assume there is a way for the
%protesters to communicate locally at the protest without relying on the
%Internet. Also mention potential privacy problems at this layer, e.g.\
%MAC-address tracking etc. which is outside of our protocol (this should
%cover part of issue #58).

Since the cellular network can be shut down to keep protesters from
accessing the Internet, making phone calls or texting, we require a
different means of communications between protesters. This can be
accomplished by Bluetooth or WiFi, as demonstrated by
Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of apps
for communication during protests via wireless mesh networking. An
alternative, although originally designed to work within 5G cellular
networks, is device-to-device communication (D2D)~\cite{D2D}. Specifically, the
outband and autonomous version D2D fits our scenario thanks to using
unlicensed spectrum and working without cellular coverage.

### 2018-02-26 paper/SystemModel.tex

@@
 using their smartphones running the protocol described in
-Section~\ref{protocol} and uploading their testimony to a blockchain
+\cref{protocol} and uploading their testimony to a blockchain
 after the protest. They thus need connectivity at least to each other

### 2018-02-27 paper/ZKPK-instantiations.tex
Updates anonymous credentials

--- 2018-02-26 paper/ZKPK.tex
@@
-\subsubsection{Zero-knowledge proofs of knowledge}%
-\label{ZKPK}
-
-We will use the notation introduced by \citet{PKnotation}:
-\begin{equation}\label{PKexample}
-  \PK{\alpha, \beta, \gamma}
-  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
-\end{equation}
-which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that 
-\(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), 
-respectively.
-Greek letters are known only to the prover and for which the prover wishes to 
-prove knowledge, all other letters are known by the verifier.
-
-When a proof of knowledge is turned into a signature using the Fiat-Shamir 
-heuristic~\cite{FiatShamirHeuristic}, we will denote it as
-\begin{equation*}\label{SPKexample}
-  \sigma\gets \SPK{\alpha, \beta, \gamma}
-  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
-  {m},
-\end{equation*}
-which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knew 
-\(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = 
-  \hat{g}^\gamma\).
-
 \subsubsection{Instantiations of the \acs{ZKPK} protocols}

### 2018-02-27 paper/ZKPK.tex
Updates anonymous credentials

@@
   \hat{g}^\gamma\).
-
-\subsubsection{Instantiations of the \acs{ZKPK} protocols}
-
-\NewAlgorithm{\PKprove}{PK.\!Prove}
-\NewAlgorithm{\PKverify}{PK.\!Verify}
-
-We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
-original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
-The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
-    \prod_{i=1}^n g_i^{\alpha_i}}\).
-This could equivalently be written as
-\begin{equation*}
-  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
-  \PKverify[\{g_i\}_i, q, A],
-\end{equation*}
-where \(\PKprove\) is run by the prover and \(\PKverify\) is run by the 
-verifier.
-\(\PKverify\) outputs accept (1) or reject (0).
-We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
-We also note that
-\begin{multline*}
-  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \\
-  \PK{\alpha}{A = g^\alpha} \land \PK{\beta}{B = g^\beta},
-\end{multline*}
-however, the challenge \(c\) must be the same in both sub-protocols.
-
-\begin{figure*}
-  \centering
-  \begin{tabular}{lcl}
-    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
-    &
-    & \(\PKverify[\{g_i\}_{i=1}^n, q, A]\):
-    \\
-    \midrule
-
-    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)
-    &
-    &
-    \\
-
-    \(R\gets \prod_{i=1}^n g_i^{\rho_i}\)
-    & \(\ProtoSendRight{R}\)
-    &
-    \\
-
-    % null
-    & \(\ProtoSendLeft{c}\)
-    & \(c\rgets \bin^k\)
-    \\
-
-    \(1\leq i\leq n\colon s_i\gets \rho_i - c\alpha_i \mod q\)
-    & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
-    &
-    \\
-
-    % null
-    &
-    & \(R \stackrel{?}{=} A^c \prod_{i=1}^n g^{s_i}\)
-    \\
-
-  \end{tabular}
-  \caption{%
-    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
-    the Schnorr identification scheme.
-  }%
-  \label{PKalgorithms}
-\end{figure*}
-
-The Schnorr protocol in itself only provides honest-verifier zero-knowledge.
-To achieve malicious-verifier zero-knowledge, we have to choose \(k\) (size of 
-the challenge, see \cref{PKalgorithms}) logarithmic in the security parameter 
-\(\lambda\) and repeat the protocol sufficiently many times (also logarithmic in 
-the security parameter).
-
-\NewAlgorithm{\SPKprove}{SPK.\!Prove}
-\NewAlgorithm{\SPKverify}{SPK.\!Verify}
-
-For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
-Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
-illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
-
-\begin{figure*}
-  \begin{minipage}[t]{0.49\linewidth}
-    \begin{algorithmic}
-      \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
-        \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)}
-        \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
-        \State{$c \gets H(\{g_i\}_i|A|R|m)$}
-        \For{$1\leq i\leq n$}
-          \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
-        \EndFor{}
-        \State{\Return{$(\{s_i\}_i, c)$}}
-      \EndFunction{}
-    \end{algorithmic}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{0.49\linewidth}
-    \begin{algorithmic}
-      \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
-        \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
-        \If{$c = H(\{g_i\}_i|A|\hat R|m)$}
-          \State{\Return{1}}
-        \Else{}
-          \State{\Return{0}}
-        \EndIf{}
-      \EndFunction{}
-    \end{algorithmic}
-  \end{minipage}
-  \caption{%
-    \(\SPK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}{m}\) 
-    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
-  }%
-  \label{SPKalgorithms}
-\end{figure*}

### 2018-02-27 paper/protocol.tex
Changes to \S?PK optional notation

@@
 \section{PRIVO: A protocol for protest outcome verification}
+\label{protocol}
 
@@
       W\leftrightarrow P\colon &
-        \DBPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}} \\
+        \DBPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}] \\
       W\colon & wid\gets \PRF_{k_W}(pid), \\
@@
       W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
-        & \pi_W = \SPK{k_W, \sigma_W}
-          {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
-            \Sign[k]{k_W}}{pid, wid, t_s, l, wsig} \\
+        & \pi_W = \SPK[k_W, \sigma_W]%
+          [wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
+            \Sign[k]{k_W}][pid, wid, t_s, l, wsig] \\
       P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
-        & \pi_P = \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
-          \Sign[k]{k_P}}{pid, wid, t_s, l, wsig}
+        & \pi_P = \SPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = 
+          \Sign[k]{k_P}][pid, wid, t_s, l, wsig]
     \end{align*}
@@
 root of what defines a protest.
-The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
+The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
 the hash value of the manifesto as identifier of the protest (cause).

### 2018-02-27 paper/TimeStamp.tex
Adds description of blockchain, TS

--- 2017-10-19 primitives.tex
@@
-\section{Building blocks}%
-\label{Primitives}\label{BuildingBlocks}
+\subsection{Time-stamping service, or, blockchains}%
+\label{StorageProperties}
 
-\dots
+\NewCryptoScheme{\TS}{TS}
+\NewAlgorithm{\TSget}{\TS.\!Get}
+\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
+\NewAlgorithm{\TSverify}{\TS.\!Verify}
+\NewAlgorithm{\TStime}{\TS.\!Time}
 
-\subsection{Zero-knowledge proofs}
-
-Briefly describe zero-knowledge proofs and what type of properties can be proved 
-efficiently using them, e.g.\ algebraic structures but not one-way functions.
-
-\dots
-
-\subsection{Location proofs and distance bounding}
-
-Briefly describe location proofs and distance bounding protocols.
-Describe the different desirable properties for distance bounding:
+We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
+\(\TSstamp\) and \(\TStime\) such that
 \begin{itemize}
-  \item Mafia-fraud resistance,
-  \item terrorist-fraud resistance,
-  \item impersonation-fraud resistance,
-  \item distance-fraud resistance.
+  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is 
+    difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
+  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
+    \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
 \end{itemize}
 
-\subsection{Storage}%
-\label{StorageProperties}
+With these building blocks we can ensure that a message \(m\) was created within 
+the time interval \(\interval{t_0}{t_1}\).
+After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
+Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping 
+service to get \(\pi_{t_1}\gets \TSstamp[h]\).
+
+Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created 
+within the time interval \(\interval{t_0}{t_1}\).
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
+\(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land 
+  \TStime[\pi_{t_1}] = t_1\).
+
+We can instantiate \(\TS\) using a blockchain.
+The \(\TSstamp[x]\) algorithm will simply include \(x\)
+
+\(\TSget\) will return the hash of the current head of the chain.
+This value is difficult to predict since it depends on all submitted 
+transactions.
+This forces us to make the assumption that the adversary cannot control 
+\emph{all} transactions that are submitted to the blockchain.
+As long as one non-adversarial transaction is submitted it will be 
+unpredictable.
 

### 2018-02-27 paper/intro.tex
Changes \ref to \cref

@@
 
-Some of our assumptions (see Section \ref{assumptions} for more
+Some of our assumptions (see \cref{assumptions} for more
 detailed descriptions) are not yet
@@
 available in some countries already now (e.g., Estonia, Germany), and
-distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
+distance-bounding chips\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
 might not unrealistically be integrated in phones or smartcards in the
-future.
+future, and even phones with off-the-shelf hardware running in
+RFID-emulation mode have shown
+promising results~\cite{dbonsmartphones}.
 

### 2018-02-27 paper/intro.tex
Fixes typo in refs

@@
 RFID-emulation mode have shown
-promising results~\cite{dbonsmartphones}.
+promising results~\cite{DBonSmartphones}.
 

### 2018-02-27 paper/protocol.tex
Adds \PRIVO macro for the name

--- 2018-02-21 paper/protocol.tex
@@
-\section{PRIVO: A protocol for protest outcome verification}
+\section{\PRIVO:\@ A protocol for protest outcome verification}%
+\label{protocol}
 

### 2018-02-27 paper/ZKPK-instantiations.tex

@@
 We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
-original form can be written as \(\PK{\alpha}{A = g^\alpha}\).
-The generalized form would be \(\PK{\alpha_1, \dotsc, \alpha_n}{A = 
-    \prod_{i=1}^n g_i^{\alpha_i}}\).
+original form can be written as \(\PK[\alpha][A = g^\alpha]\).
+The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
+    \prod_{i=1}^n g_i^{\alpha_i}]\).
 This could equivalently be written as
@@
 \begin{multline*}
-  \PK{\alpha, \beta}{A = g^\alpha \land B = g^\beta} = \\
-  \PK{\alpha}{A = g^\alpha} \land \PK{\beta}{B = g^\beta},
+  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
+  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
 \end{multline*}
@@
   \caption{%
-    \(\PK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}\) using 
+    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1]^n g_i^{\alpha_i}}\) using 
     the Schnorr identification scheme.
@@
 
-For the non-interactive instance, \(\SPK{\alpha}{A = g^\alpha}{m}\), we use the 
+For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
 Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
@@
   \caption{%
-    \(\SPK{\alpha_1, \dotsc, \alpha_n}{A = \prod_{i=1}^n g_i^{\alpha_i}}{m}\) 
+    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
     using the Fiat-Shamir heuristic on the Schnorr identification scheme.

### 2018-02-27 paper/analysis.tex
Adding performance section
Adding two new subsections

@@
 
-\subsection{Assumptions}
+\subsection{Assumptions} \label{assumptions}
 
@@
 
+\section{Performance and implementation}
+
+\subsection{Implementation on smartphones}
+Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}.
+However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix  (taking between \SI{4}{\second} and \SI{8}{\second} to process it), despite promising efforts such as the IRMA project.
+
 \subsection{Threshold of witnesses}
@@
 \) of processing.
+
+\subsection{Blockchain feasability}

### 2018-02-27 paper/analysis.tex
Adding citations for IRMA, Idemix and benchmarks

--- 2018-02-25 paper/analysis.tex
@@
 
+\section{Performance and implementation}
+
+\subsection{Implementation on smartphones or smart-cards}
+Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}.
+However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them).
+While the limited processing power of many embarked systems has been a challenge, Idemix has been succesfully implemented to prove the posession of credentials on Java Cards by Bichsel et al.
+in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation « suitable for real life transactions »~\cite{IRMA} while maintaining security and privacy for its users.
+
 \subsection{Threshold of witnesses}

### 2018-02-27 paper/SystemModel.tex
change to intro and system model

--- 2018-02-26 paper/SystemModel.tex
@@
-\section{System model}%
+\section{Defining and formalizing protest and crowd estimation}%
 \label{SystemModel}
 
-\subsection{What is \protect\emph{a} protest?}%
-\label{WhatIsAProtest}
+%\subsection{What is \protect\emph{a} protest?}%
+%\label{WhatIsAProtest}
 
-Protests can vary considerably.
-To be able to estimate the participation count for one, we first need to define
-what should be counted.
-
+\emph{Defining the concept of protest.} To be able to estimate the participation count for a protest, we first need to define this concept and what should be counted.
 Let us start by considering some examples.
@@
 \blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some 
-  people stay\textins{ed} for several hours, others just several minutes%
+  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
 }.
@@
 weekend for the duration of a few weeks.
-The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred 
-in parallel in many locations.
-We also have the Venezuelan demonstrations where
+The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
+We also have the Venezuelan demonstrations in which
 \blockcquote{2017VenezuelaProtestFrequency}{%
@@
 \blockcquote{AlJazeeraOnVenezuela2017}{%
-  pro-government workers sang and danced as they staged a rival march to show 
-  their support for the president's controversial plan to rewrite the 
-  constitution%
+  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
 }.
 Judging from these examples, the minimal common part is the cause,%
-\label{CauseIsTheCommonDenominator}
-but there is also a location (or area) that varies over time.
+\label{CauseIsTheCommonDenominator} but there is also a location (or area) that varies over time.
 
-The organizer Alice wants to count everyone who participated at any time and in 
-any of the locations~\cite{2016DemonstrationsInSeoul}.
-(Whereas police are only interested in the maximum crowd at any point in time, 
-to deploy enough personnel for crowd-control.)
-We will define a protest as an event that is uniquely identified by its cause 
-(\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
+For the rest of the paper, we will refer to the organizer as Alice.
+Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Note that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time, to deploy enough personnel for crowd-control.}.
+Formally, we define a protest as an event that is uniquely identified by its cause (\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
 More specifically, we will use the following definition.
@@
 \begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((cid, t, l)\) where
-  \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
-  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and
-  \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an 
-  \(\epsilon\)-neighbourhood of \((x,y)\)).
+  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
+  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an \(\epsilon\)-neighbourhood of \((x,y)\)).
   A \emph{protest} is a set of subprotests sharing the same \(id\).
@@
 
-The protests described above can be captured using this definition by splitting 
+The protests described in the previous examples can be captured using this definition by splitting 
 them up into subprotests.
-Each subprotest will then be captured by our definition and to find the total 
-we can just sum up the results.
-The same for marches, the marching path can be divided into subprotests with 
-locations (or areas) that slightly overlap.
+Each subprotest will then be captured by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
+Similarly for march, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.
 
-\subsection{What is a proper count?}
+\emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
+The proof must be associated with the protest (\emph{i.e.}, its identifier \(cid\)), time and location must coincide with any of its subprotests.
 
-Each participant who wants to be counted must submit a participation proof.
-The proof must be associated with the protest, i.e.\ its identifier \(cid\), 
-time and location must coincide with any of its subprotests.
-
-In practical terms, participants witness each other's particpation
-using their smartphones running the protocol described in
-Section~\ref{protocol} and uploading their testimony to a blockchain
-after the protest.
-
-More formally, we use witnesses to associate the proof to the location by creating a proof 
+We use other participants, that we called \emph{witnesses} to associate the proof to the location by creating a proof 
 share.
-% XXX what is a witness?
-A witness is only allowed to create one proof share per protester.
-The proof and its proof shares are stored in a set, as there should be only 
-unique proof shares.
+A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
+The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.
 
@@
 \begin{definition}[Participation count]
-  We define the \emph{participation count} of a protest \(cid\) as the 
-  cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
+  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
     P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
@@
 \end{definition}
-The strength function \(s\) can be used to e.g.\ regulate trust in witnesses.
-One example would be for \(s\) to return the number of proof shares (i.e.\ 
-witnesses) and thus let \(\theta\) to be the threshold of the number of required 
-witnesses.
+The strength function \(s\) can be used to regulate trust in witnesses.
+One example would be for \(s\) to return the number of proof shares (\emph{i.e.}, witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
+
+\emph{System model and physical assumptions.}
+In practical terms, participants witness each other's particpation using their smartphones running the protocol described in \cref{protocol} and uploading their testimony to a blockchain after the protest.
+Thus, they need connectivity at least to each other during the protest and Internet connectivity after.
+
+\include*{MANETs}

### 2018-02-27 paper/intro.tex
change to intro and system model

--- 2018-02-26 paper/intro.tex
@@
 
-%Seb: I suggest that we give a name to the protocol to be able to refer to it more adequately
-\emph{Contributions} We propose a scheme that provides a way for protests to be securely verified.
-Additionally, this verification system does not incur any additional risk to 
-protesters' privacy than participating in the physical protest itself.
+%Seb: I suggest that we move this part to system model
+%\subsection{Combining properties of electronic voting with location proofs}
+\emph{Relationship between protesting and electronic voting}.
+In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
+These opinions can be sensitive (\emph{e.g.}, be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
 
-In contrast to the traditional assumption of honest verifiers in
-distance-bounding algorithms, we propose a way to turn the Schnorr
-protocol into a distance-bounding protocol that allows for a malicious
-verifier. In addition, this allows us to form distance-bounding
-anonymous credentials.
-
-\subsection{Limitations and Assumptions}
-
-We can achieve privacy, but not receipt freeness.
-This means that there is a way for Eve to efficiently verify that Alice has 
-participated.
-However, this requires that Eve gets a copy of Alice's secret key so that she 
-can simply re-do the (deterministic) computations on the same inputs --- the 
-probability of collisions is negligible.
-
-%\dots
-
-Some of our assumptions (see Section \ref{assumptions} for more
-detailed descriptions) are not yet
-realized. Not all (or even many) protesters, especially in countries
-with oppressive regimes, currently possess smartphones. Digital
-certificates signed by a central authority are not yet widely
-available and if we rely on government-issued credentials, we cannot prevent the government 
-from performing Sybil attacks --- since it can issue arbitrarily many 
-\emph{valid} credentials. In this case we cannot verify any pro-government protests where Eve's authoritarian regime wants to organize a pro-regime protest to 
-demonstrate its \emph{wide 
-  support}~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Distance bounding on phones is currently not feasible within a
-meaningful range of distance for our scenario.
-
-The assumptions might
-become sufficiently realistic in the near future, though, with
-smartphone penetration on the rise, increased digitalization and government-issued credentials
-available in some countries already now (e.g., Estonia, Germany), and
-distance-bounding chips~\footnote{ https://www.3db-access.com } currently available with a range of 200 m that
-might not unrealistically be integrated in phones or smartcards in the
-future.
-
-\emph{Outline.} The paper is organized as follows. 
-First, we define the system model for verifiable privacy-preserving crowd counting.  We then
-present the desired security properties for such a system and subsequently discuss related
-work in terms of these properties. We give the relevant background on
-the building blocks of our solution and then describe our proposal for
-distance-bounding anonymous credentials that copes with a malicious
-(impersonating) verifier. We then present the protocol constructed
-from the building blocks, its security and privacy analysis, and
-finally our conclusions.
-
-%Seb: I suggest that we move this part to system model
-\subsection{Combining properties of electronic voting with location proofs}
-
-In general, protesting is very similar to petitions, which in turn are similar 
-to voting: all three are many individuals expressing their opinion.
-These opinions can be sensitive, e.g.\ cause for discrimination or persecution, 
-hence we desire to have similar properties of verification and privacy for 
-verifying a protest as there is for voting.
-
-Voting has (generally) three desirable requirements for 
-verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
+Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
 \begin{description}
-  \item[Eligibility] anyone can verify that each vote cast is legitimate.
-  \item[Universal verifiability] anyone can verify that the result is according 
-    to the cast votes.
-  \item[Individual verifiability] every voter can verify that their vote is 
-    included in the result.
+  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
+  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
+  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
 \end{description}
 We translate the votes into \emph{proofs of participation}.
-Universal and individual verifiability remain the same: anyone can verify the 
-participation count by counting the proofs.
-The eligibility requirement is slightly different:
-for protests the eligibility requirement must include temporal and spatial 
-eligibility, i.e.\ that each proof of participation satisfies some temporal and 
-spatial relation to the protest.
-In essence, the proof must bind the person to the time and location of the 
-protest.
+Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
+The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
+eligibility (\emph{i.e.}, each proof of participation satisfies some temporal and spatial relation to the protest).
+In essence, the proof must bind the person to the time and location of the protest.
 We will define these more formally in \cref{Verifiability}.
 
-There are also three levels of 
-privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{itemize}
-  \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
-    individual vote.
-  \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
-    provide any data that can be used as a proof of how the voter voted.
-  \item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
-    with a coercer to prove the vote was cast in any particular way.
-\end{itemize}
-We note that we cannot actually improve the privacy of participating protesters during 
-the protest: if Alice is caught during a protest or other
-crowd-counting mechanisms based on photographic or video evidence are
-used to identify Alice, there is nothing we
-can do. In our proposed solution, however, we aim at verifiable
-participation count that does not add any threats to the participants'
-privacy. For instance, if there are counter-protests in the \emph{same location at the same 
-  time}, Alice could even blend into another crowd and argue that she participated in 
-a different protest than she actually did --- and the counts would still be 
-correct afterwards.
-However, even if there is only one protest and she is not caught in the act, 
-then using our proposed mechanism should not incur any additional risk.
-Thus we need at least participation-proof privacy but receipt freeness (see 
-\cref{Privacy} for a detailed definition) is desired.
-In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
-participation proof --- even if she were to compromise Alice's
-devices.
+There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\begin{description}
+  \item[VotePrivacy]: the voting does not reveal the individual vote.
+  \item[ReceiptFreeness]: the voting system does not provide any data that can be used as a proof of how the voter voted.
+  \item[CoercionResistance]: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
+\end{description}
+We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
+%Seb: suggestion maybe we should put the following part in the discussion
+However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
+For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
+However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
+Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
+In essence, upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
 %Sonja says: I'm confused: can we or can we not provide this?
+%Seb: I agree with Sonja, it is not clear whether we achieve it or not
+
+%Seb: to do complete the contributions
+\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+Additionally, this verification system does not incur any additional risk to protesters' privacy apart from the ones related to participating physically to the protest itself.
+
+In contrast to the traditional assumption of honest verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.
+%Seb: above, we should put the reference to the Schnorr protocol 
+In addition, this allows us to form distance-bounding anonymous credentials.
+
+\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized (see \cref{assumptions} for more detailed descriptions). 
+In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
+In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
+%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
+In this case, it does not make sense to verify any pro-government protests in which Eve's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance for our scenario.
+
+However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\emph{e.g.}, Estonia and Germany)
+In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
+One of the short-term objective is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
+
+\PRIVO achieve privacy, but not receipt freeness.
+This means that there is a way for Eve to efficiently verify that Alice has to the participated.
+However, this requires Eve to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
+
+%Seb: to do, update the outline
+\emph{Outline.} The paper is organized as follows. 
+First, we define and formalize the notion of protest and discuss how is relationship with electronic voting in \cref{SystemModel}.  
+We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
+We give the relevant background on the building blocks of our solution \PRIVO and then describe our proposal for distance-bounding anonymous credentials that copes with a malicious (impersonating) verifier.
+Finally, we present the protocol constructed from the building blocks, its security and privacy analysis, and finally we conclude by a discussion.

### 2018-02-28 paper/DB-anon-cred.tex
Starts discussing related DB protocols
Makes DB anon creds a subsection, as it should
Updates bibsp, removes DBIV (it's public key anyway)
Improves discussion about DB and DBPK

--- 2018-02-19 paper/DB-anon-cred.tex
@@
-\section{Distance bounding anonymous credentials}%
+\subsection{Distance bounding anonymous credentials}%
 \label{DB-anon-cred}
 
-\ProvideDocumentCommand{\DBPK}{m m}{\ensuremath{%
-    \operatorname{DBPK}\mleft\{\mleft(#1\mright) : #2\mright\}%
+\ProvideDocumentCommand{\DBPK}{o o}{\ensuremath{%
+    \operatorname{DBPK}%
+    \IfValueT{#1}{%
+      \IfValueTF{#2}{%
+        \mleft\{\mleft(#1\mright) : #2\mright\}%
+      }{%
+        \mleft\{#1\mright\}%
+      }%
+    }%
   }}
 
-We pointed out in \cref{DistanceBounding} that all security properties 
-concerning \ac{DB} assume an \emph{honest} verifier.
+We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} 
+protocols that provide the above security properties assume an \emph{honest} 
+verifier.
 This assumption does not hold in our setting, where every verifier at some point 
 also might be a (malicious) prover.
-We will introduce a new property for \ac{DB} protocols, the \ac{DBIV}.
-Then we will propose a protocol that is \ac{DBIV}, \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} resistant but \emph{not} \ac{DBTF} resistant.
-The protocol is based on the Schnorr identification scheme and thus allows us to 
-do \ac{DB} \ac{ZKPK}, which allows us to form distance-bounding anonymous 
-credentials.
+We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.
 
-\subsection{\Acl{DBIV} distance bounding}
+There is a protocol which provide \ac{DBPK} with all the desired properties from 
+above, ProProx~\cite{ProProx}.
+(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
+Knowledge.)
+However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
+proving \(\DBPK[\alpha][a = \alpha^2]\).
+We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
+We will now introduce such a protocol which will allow us to do \ac{DB} 
+anonymous credentials.
+We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
+\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.
 
-\dots
-
-\subsection{Reattempting \iacl{DB} Schnorr protocol}
+\subsubsection{Reattempting \iacl{DB} Schnorr protocol}
 
@@
 which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
-It will not protect against terrorist fraud, in fact, we suspect that \ac{DBIV} 
-and \ac{DBTF} resistance are mutually exclusive.
+It will not protect against terrorist fraud, although this would be desirable.
 
@@
 two random values and the verifier sends two challenges.
-Then the verifier decides which commitment and challenge to use in the \ac{DB} 
-phase.
+Then the verifier presents to the prover which commitment and challenge to use 
+during the \ac{DB} phase.
 
@@
     &
-    & Prepare \(B\in \bin^{k+l}\),
+    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\),
     \\
@@
     &
-    & with \(k\) bits set to \(b\)
+    & with \(\ceil{\log_2 q}\) bits set to \(b\)
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < k+l\)} 
-    \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
+        \ceil{\log_2 q} + l\)} \\
 
@@
     One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
-    \ac{DB} Schnorr protocol for \(\PK{\alpha}{A = g^\alpha}\).
+    \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
     The protocol should be repeated in full to achieve the desired knowledge 
@@
 phase for at least one round.
-The verifier will send \(k+l < 2k\) challenges.
-Thus the prover reveals the \(k\) bits of either \(s_0\) or \(s_1\) and only 
-\(l\) bits of the other.
+The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
+Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) 
+bits of the other.
 Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 

### 2018-02-28 paper/LocationProofs.tex

@@
 
-Describe location proofs.
+Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
+In most current schemes, the location of a user/device is determined by the device itself (\emph{e.g.}, through GPS) and forwarded to the LBS provider. 
+One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
+Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
+
+To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
+In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time.
+A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\emph{e.g.}, trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
+Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
+%Seb: to do add the corresponding reference
+However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
+\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\emph{i.e.}, crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

### 2018-02-28 paper/AdaptingPROPS.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

--- 2016-07-18 AdaptingPROPS.tex
@@
 One issue is the \ac{CA}.
-One direction we can take to solve this is by threshold signatures, e.g.\ 
+One direction we can take to solve this is by threshold signatures, \eg 
 \cite{FSThresholdSignatures}.
@@
 existing \acp{PKI} instead.
-E.g.\ Sweden has a deployed national \ac{eID} system; usually these are RSA or 
+\Eg Sweden has a deployed national \ac{eID} system; usually these are RSA or 
 DSA keys --- \((pq, e), (p, q, d): ed = 1\pmod{(p-1)(q-1)}\) --- signed by 
@@
 It would be interesting to solve the W--P collusion attack, where the witness 
-reports false \acp{LPS}, e.g.\ we would need to prevent that a group of 
+reports false \acp{LPS}, \eg we would need to prevent that a group of 
 individuals fake this information at home.
-One possibility in our scenario is that e.g.\ an external journalist on 
+One possibility in our scenario is that \eg an external journalist on 
 location can create \iac{LPS}, because a journalist is generally trusted.
@@
 One option would be to have a reputation system in a global location-proof 
-system, another would be to tie it to a reputation system already used in e.g.\ 
+system, another would be to tie it to a reputation system already used in \eg 
 \iac{OSN}.
@@
 \enquote{transitive}.
-I.e.\ if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
+\Ie if Alice the prover has \acp{LPS} from a set of witnesses, then she can 
 act as a witness and issue \iac{LPS} which includes her previous \acp{LPS}.

### 2018-02-28 paper/RelatedWork.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

@@
 dense.
-This is similar to the method usually used by police, e.g.\ for the protests in
+This is similar to the method usually used by police, \eg for the protests in
 Seoul
@@
 
-There is a body of work in the computer vision community, e.g.\ the work of 
+There is a body of work in the computer vision community, \eg the work of 
 \citet{NNCrowdCounting}.
@@
 video, which should be similar as in our discussion about the verifiability of 
-photos above, i.e.\ forensic methods.
+photos above, \ie forensic methods.
 
@@
 
-A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
+A better proposal would be to use \emph{IMSI catchers} (or the real cell 
 towers of the mobile network) to count unique phones at the location.
@@
 These methods also have difficulty capturing the actual attendance of an event,
-i.e.\ the cumulative participation, not just the count at a snapshot around the 
+\ie the cumulative participation, not just the count at a snapshot around the 
 peak.
@@
 count at the snapshot of the photos.
-However, there is no verification, i.e.\ the service must be trusted to behave 
+However, there is no verification, \ie the service must be trusted to behave 
 honestly, but even then, nothing prevents Bob from submitting twice (violating 
@@
 during the event to register as a participant.
-This can make it difficult to use if e.g.\ Alice has organized a protest 
+This can make it difficult to use if \eg Alice has organized a protest 
 against the government, who shuts down the cellular network or Internet 

### 2018-02-28 paper/SystemModel.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

@@
   time interval \(t\) and location \(l\) is within those of the protest \(j\) 
-  (i.e.\ \(t_j\) and \(l_j\)).
+  (\ie \(t_j\) and \(l_j\)).
 \end{definition}

### 2018-02-28 paper/TimeStamp.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

@@
 One primitive that fulfils these requirements is a blockchain.
-There are also other structures, e.g.\ a directed graph that 
+There are also other structures, \eg a directed graph that 
 converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
@@
 First, we need immutability.
-I.e.\ once we commit something to the blockchain it will remain there.
+\Ie once we commit something to the blockchain it will remain there.
 We will use this to ensure verifiability, the data must remain to be verifiable.
@@
 Second, we need a general form of time-stamping.
-I.e.\ we must be able to relate commitments to time, e.g.\ in 
+\Ie we must be able to relate commitments to time, \eg in 
 Bitcoin~\cite{Bitcoin} a new block appears approximately every 10 minutes.
@@
 itself, but we can store some confirmation value instead.
-E.g.\ using blockchains, we can store the hash of the block where our data was 
+\Eg using blockchains, we can store the hash of the block where our data was 
 committed, while this block remains we are sure that our data remains committed 

### 2018-02-28 paper/properties.tex
Changes order of sections, changes PRF to \PRF
coincoin
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

--- 2018-02-05 paper/properties.tex
@@
 Additionally, Eve tries to deanonymize the participants to arrest them or 
-\enquote{convince} them to change their minds.
+\emph{convince} them to change their minds.
 Finally, we have Rusuk who is represents another nation state.
@@
 \Cref{CoercionResistance} is probably not possible to achieve for protests:
-e.g.\ Eve can simply physically bring Alice to a protest against her will.
+\eg Eve can simply physically bring Alice to a protest against her will.
 This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

### 2018-02-28 paper/protocol.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg

--- 2018-02-27 paper/protocol.tex
@@
-\section{PRIVO: A protocol for protest outcome verification}
+\section{\PRIVO:\@ A protocol for protest outcome verification}%
 \label{protocol}
@@
 the protest.
-The protesters will witness each others participation proofs, e.g.\ Alice will 
+The protesters will witness each others participation proofs, \eg Alice will 
 witness Bob's proof and Bob will witness Alice's proof.
@@
 As soon as Alice and Bob have departed from the protest they upload their proofs 
-(i.e.\ all proof shares) to the cothority for indefinite storage.
+(\ie all proof shares) to the cothority for indefinite storage.
 Since each proof consists of one proof share for each witness, each witness 
@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks, i.e.\ that one individual 
+\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
 can provide two participation proofs and thus be counted twice.
@@
 share) for another event.
-E.g.\ there might be a counter protest at the same time and place, these would 
+\Eg there might be a counter protest at the same time and place, these would 
 have the same spatial and temporal properties.
@@
 which allows anonymous authentication at most \(n\) times\footnote{%
-  Possibly there is another scheme that makes it non-interactive, e.g.\ by 
+  Possibly there is another scheme that makes it non-interactive, \eg by 
   \citet{Psignatures}, see issue \#27.
@@
 were actually in that location.
-The role of the witnesses, e.g.\ Jane, is to provide this property.
+The role of the witnesses, \eg Jane, is to provide this property.
 Jane can do this by using a distance-bounding protocol to ensure that the secret 
@@
 protester and the witness.
-Alice and Bob simply commit their proofs (i.e.\ all proof shares of their 
+Alice and Bob simply commit their proofs (\ie all proof shares of their 
 proofs) to the blockchain as soon as possible after they have participated in 
@@
 There are three parts to verifying the participation count.
-First, we must verify the eligibility of each proof, i.e.\ of all its shares.
+First, we must verify the eligibility of each proof, \ie of all its shares.
 Second, we must count these valid proofs.
@@
 to count the valid proofs.
-To do this we must be able to verify the eligibility of a proof (i.e.\ of all 
+To do this we must be able to verify the eligibility of a proof (\ie of all 
 its shares) and then count it if valid.
@@
 witness knows a signature by the identity authority on \(k_W\).
-With these \ac{NIZK} proofs anyone can verify the validity, i.e.\ the 
+With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
 eligibility, of the proof shares and thus also count them.

### 2018-02-28 paper/LocationProofs.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

@@
 Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
-In most current schemes, the location of a user/device is determined by the device itself (\emph{e.g.}, through GPS) and forwarded to the LBS provider. 
+In most current schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
 One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
@@
 In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time.
-A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\emph{e.g.}, trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
+A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
 Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
@@
 However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
-\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\emph{i.e.}, crowd estimation) in contrast to checking the location claim made a user, which is an individual property.
+\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.

### 2018-02-28 paper/SystemModel.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

@@
 \emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
-The proof must be associated with the protest (\emph{i.e.}, its identifier \(cid\)), time and location must coincide with any of its subprotests.
+The proof must be associated with the protest (\ie its identifier \(cid\)), time and location must coincide with any of its subprotests.
 
@@
 The strength function \(s\) can be used to regulate trust in witnesses.
-One example would be for \(s\) to return the number of proof shares (\emph{i.e.}, witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
+One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
 

### 2018-02-28 paper/intro.tex
Changes "\emph{e.g.}," to "\eg" and "\emph{i.e.}," to "\ie"

@@
 Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
-However, most of them lack precision (\emph{i.e.}, they have large error margins) and they can only give an estimate for a particular snapshot in time (\emph{e.g.}, at the peak of the event). 
+However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
 In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
@@
 In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
-In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\emph{i.e.}, their claim should be verifiable).
+In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\ie their claim should be verifiable).
 To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
@@
 In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
-These opinions can be sensitive (\emph{e.g.}, be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
+These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
 
@@
 The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
-eligibility (\emph{i.e.}, each proof of participation satisfies some temporal and spatial relation to the protest).
+eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
 In essence, the proof must bind the person to the time and location of the protest.
@@
 
-However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\emph{e.g.}, Estonia and Germany)
+However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\eg Estonia and Germany)
 In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.

### 2018-02-28 paper/protocol.tex
Updates protocol, changes \PRF to \ACprf

@@
 
-\begin{figure*}
+\begin{figure}
   \centering
@@
       O\to \text{all}\colon & \text{manifesto} \\
-      P\colon & cid\gets H(\text{manifesto}), \\
-        & pid\gets \PRF_{k_P}(cid) \\
+      P\colon & t_s\gets \TSget \\
+      W\colon & t_s'\gets \TSget \\
+      P\colon & cid\gets \Hash[\text{manifesto}], \\
+        & pid\gets \ACprf[_{k_P}][cid]
+      & \text{\small Join} \\ \midrule && \text{\small Participation} \\[-1.5em]
       P\to W\colon & pid \\
-      W\leftrightarrow P\colon &
-        \DBPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}] \\
-      W\colon & wid\gets \PRF_{k_W}(pid), \\
-        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
-      W\to P\colon & (wid, t_s, l, wsig) \\
-      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
-      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
-      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
-        & \pi_W = \SPK[k_W, \sigma_W]%
-          [wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
-            \Sign[k]{k_W}][pid, wid, t_s, l, wsig] \\
-      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
-        & \pi_P = \SPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = 
-          \Sign[k]{k_P}][pid, wid, t_s, l, wsig]
+      P\leftrightarrow W\colon &
+        \DBPK\mleft\{ (k_P) : \mright. \\
+        & \qquad pid = \ACprf[_{k_P}][cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
+      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
+        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
+      W\to P\colon & (wid, t_s, t_s', l, wsig)
+      & \text{\small Participation} \\ \midrule && \text{\small Submission} 
+      \\[-1.5em]
+      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
+      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
+      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
+      \text{where} \\
+        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
+        & \qquad wid = \ACprf[_{k_W}][pid], \\
+        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
+        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
+        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
+      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
+      \text{where}\\
+        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
+        & \qquad pid = \ACprf[_{k_P}][cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
+        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
     \end{align*}
@@
   \caption{%
-    An overview of message exchanges.
+    An overview of of the Join, Participation and Submission phases of \PRIVO\@.
     The organizer \(O\) broadcasts the manifesto.
@@
   \label{fig:ProtocolOverview}
-\end{figure*}
+\end{figure}
 
@@
 national identity-card (by assumption).
-She will use \(k\) to compute \(pid\gets \PRF_k(cid)\), which is her anonymous 
-identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
+She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
+anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
 
@@
 
-Alice must provide \iac{NIZK} proof showing that \(pid = \PRF_{k_P}(cid)\) and 
-that she knows a signature by the identity authority on \(k_P\).
+Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
+and that she knows a signature by the identity authority on \(k_P\).
 \dots
@@
 In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
-  \PRF_{k_W}(pid)\) and \(wsig = \PRF_{k_W}(wid, t_s, l)\) as well as that the 
-witness knows a signature by the identity authority on \(k_W\).
+  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
+that the witness knows a signature by the identity authority on \(k_W\).
 With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
@@
 With this key Eve can verify that Alice has submitted a proof by computing 
-\(pid'\gets \PRF_{k_A}(cid)\) and compare \(pid = pid'\).
+\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).

### 2018-02-28 paper/intro.tex
Fixes spacing and colons in intro desc environments

@@
 \begin{description}
-  \item[Eligibility]: anyone can verify that each vote cast is legitimate.
-  \item[Universal verifiability]: anyone can verify that the result is according to the cast votes.
-  \item[Individual verifiability]: every voter can verify that their vote is included in the result.
+  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
+  \item[Universal verifiability:] anyone can verify that the result is according 
+    to the cast votes.
+  \item[Individual verifiability:] every voter can verify that their vote is 
+    included in the result.
 \end{description}
@@
 \begin{description}
-  \item[VotePrivacy]: the voting does not reveal the individual vote.
-  \item[ReceiptFreeness]: the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[CoercionResistance]: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
+  \item[Vote privacy:] the voting does not reveal the individual vote.
+  \item[Receipt freeness:] the voting system does not provide any data that can 
+    be used as a proof of how the voter voted.
+  \item[Coercion pesistance:] a voter cannot cooperate with a coercer to prove 
+    the vote was cast in any particular way.
 \end{description}

### 2018-02-28 paper/TimeStamp.tex
Fixes the blockchain section

@@
 We can instantiate \(\TS\) using a blockchain.
-The \(\TSstamp[x]\) algorithm will simply include \(x\)
-
+The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain.
 \(\TSget\) will return the hash of the current head of the chain.
@@
 unpredictable.
+The blockchain must also be continuously extended, \eg as in
+Bitcoin~\cite{Bitcoin}, where a new block appears approximately every 10 
+minutes.
+This coarse-grained form of time-stamping is enough for our purposes.
 
-We will use the storage to provide the temporal eligibility property.
-\Cref{CreatedBeforeEnd,CreatedAfterStart} requires a \emph{partially ordered 
-  set}\footnote{%
-  A relation \(\preceq\) which is reflexive, antisymmetric and transitive.
-} of objects.
-If some objects in the set relate to known points in time, then the partial 
-order relates the data to the time of the event.
-This allows us to \emph{verify the data temporally}.
-One primitive that fulfils these requirements is a blockchain.
-There are also other structures, \eg a directed graph that 
-converges~\cite{BlockchainFreeCryptocurrencies}, that also provides the required 
-properties.
-However, we will use the blockchain in our discussion for simplicity.
-
-There are five properties that we need from the storage system, all of which 
-makes a blockchain-like structure suitable.
-First, we need immutability.
-\Ie once we commit something to the blockchain it will remain there.
+There are some additional properties that we need from \(\TS\).
+First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
+it will remain there.
+This is usually true for blockchains.
 We will use this to ensure verifiability, the data must remain to be verifiable.
 
-Second, we need a general form of time-stamping.
-\Ie we must be able to relate commitments to time, \eg in 
-Bitcoin~\cite{Bitcoin} a new block appears approximately every 10 minutes.
-This coarse-grained form of time-stamping is enough for our purposes.
-We will use this property to ensure that proofs are created before a certain 
-point in time.
-
-Third, we need an unpredictable number whose time of publication can be 
-verified.
-For this property, we will use the head of the blockchain.
-The hash value of the head of the blockchain at a given time will be difficult 
-to predict ahead of time.
-%(See \cref{SecurityAnalysis} for a security analysis.)
-We want to use this to ensure that proofs are created after a certain point in 
-time.
-
-Fourth, once we have committed some data, we do not need to keep the data 
+Second, once we have committed some data, we do not need to keep the data 
 itself, but we can store some confirmation value instead.
@@
 We will use this property to approximate the property of receipt freeness.
-
-Finally, if the storage is decentralized we do not have to trust any central 
-authority, which is the usual case for blockchains.

### 2018-02-28 paper/intro.tex
edited intro

@@
 Bob, Carol and many others participate in the protest for Alice's cause against Eve.
-However, they might also be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
+However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
 To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
@@
 The difference is actually quite natural as both parties have different objectives.
-More precisely, the organizers want to count everyone who have participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
+More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
 Among the numerous recent examples in which it is difficult to establish the actual number of participants, we can cite the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
-Existing methods for crowd-counting varies significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
+Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
 However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
-In particular, the existing methods cannot estimate reliably the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
-In addition, they also lack verifiability as everyone has to trust the entity responsible for performing the counting.
-Finally, one important observation about crowd-counting that has been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting.
+In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
+In addition, they also lack verifiability. 
+%as everyone has to trust the entity responsible for performing the counting.
+%Sonja says: I commented this out as it doesn't apply to all.
+Sometimes you have to trust the data but can count yourself (pictures) or can even take pictures yourself but that's not really verifiability either.
 
-Indeed, going back to our example Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease the tallied number of participants.
+Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
+Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease it.
 In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
 In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\ie their claim should be verifiable).
-To solve this issue, we need a verifiable participation count that can resist to Sybil attacks while still preserving the participants'
+To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
 privacy to the extent possible given their physical presence at the protest. 
-More precisely, our solution will not be able to prevent a physical eavesdropper from recognizing a particular individual in a protest. 
-Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated to his identity and that his actions are also unlinkable.
+More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
+Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
+%Sonja says: what actions do we refer to here?
 
@@
 \emph{Relationship between protesting and electronic voting}.
-In general, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
+In general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
 These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
@@
 Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
-In essence, upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
+In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
 %Sonja says: I'm confused: can we or can we not provide this?
@@
 \emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
-Additionally, this verification system does not incur any additional risk to protesters' privacy apart from the ones related to participating physically to the protest itself.
+Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
 
@@
 In this case, it does not make sense to verify any pro-government protests in which Eve's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance for our scenario.
+Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.
 
@@
 In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
-One of the short-term objective is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
+One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
 
-\PRIVO achieve privacy, but not receipt freeness.
+\PRIVO achieves privacy, but not receipt freeness.
 This means that there is a way for Eve to efficiently verify that Alice has to the participated.
@@
 We give the relevant background on the building blocks of our solution \PRIVO and then describe our proposal for distance-bounding anonymous credentials that copes with a malicious (impersonating) verifier.
-Finally, we present the protocol constructed from the building blocks, its security and privacy analysis, and finally we conclude by a discussion.
+Finally, we present the protocol constructed from the building blocks, its security and privacy analysis, and conclude with a discussion.

### 2018-02-28 paper/TimeStamp.tex

@@
 
-We can instantiate \(\TS\) using a blockchain.
-The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain.
+We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
+The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
+return the block into which \(x\) was included.
 \(\TSget\) will return the hash of the current head of the chain.
 This value is difficult to predict since it depends on all submitted 
-transactions.
-This forces us to make the assumption that the adversary cannot control 
-\emph{all} transactions that are submitted to the blockchain.
-As long as one non-adversarial transaction is submitted it will be 
-unpredictable.
+transactions and usually some randomness, \eg nonces and miners' secrets.
 The blockchain must also be continuously extended, \eg as in
@@
 minutes.
-This coarse-grained form of time-stamping is enough for our purposes.
+So having a dedicated blockchain for a protest will not do, it is better to use 
+a blockchain which is also used for other things too.
 
-There are some additional properties that we need from \(\TS\).
+There are some additional properties that we need from \(\TS\), which are 
+implied by blockchains.
 First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
 it will remain there.
-This is usually true for blockchains.
 We will use this to ensure verifiability, the data must remain to be verifiable.

### 2018-02-28 paper/DB-anon-cred.tex
Removes \subsubsections, turns into \emphs

@@
 
-\subsubsection{Reattempting \iacl{DB} Schnorr protocol}
-
 \NewCryptoScheme{\DBS}{DBS}
@@
 
+\emph{Reattempting \iacl{DB} Schnorr protocol.}
 In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 

### 2018-02-28 paper/protocol.tex
Removes \subsubsections, turns into \emphs
Fixes protocol figure, splits between parts

@@
       P\colon & cid\gets \Hash[\text{manifesto}], \\
-        & pid\gets \ACprf[_{k_P}][cid]
-      & \text{\small Join} \\ \midrule && \text{\small Participation} \\[-1.5em]
+        & pid\gets \ACprf[_{k_P}][cid] \\[-1em]
+      \noalign{\hfill\small Join}
+      \midrule
+      \noalign{\hfill\small Participation}
+      \\[-3em]
       P\to W\colon & pid \\
@@
         & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
-      W\to P\colon & (wid, t_s, t_s', l, wsig)
-      & \text{\small Participation} \\ \midrule && \text{\small Submission} 
-      \\[-1.5em]
+      W\to P\colon & (wid, t_s, t_s', l, wsig) \\[-1em]
+      \noalign{\hfill\small Participation}
+      \midrule
+      \noalign{\hfill\small Submission}
+      \\[-2em]
       W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
@@
   \caption{%
-    An overview of of the Join, Participation and Submission phases of \PRIVO\@.
+    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
     The organizer \(O\) broadcasts the manifesto.

### 2018-02-28 paper/protocol.tex
Restructures protocol fig slightly

@@
       P\colon & t_s\gets \TSget \\
-      W\colon & t_s'\gets \TSget \\
-      P\colon & cid\gets \Hash[\text{manifesto}], \\
-        & pid\gets \ACprf[_{k_P}][cid] \\[-1em]
+        & cid\gets \Hash[\text{manifesto}], \\
+        & pid\gets \ACprf[_{k_P}][cid] \\
+      W\colon & t_s'\gets \TSget
+      \\[-1em]
       \noalign{\hfill\small Join}
@@
         & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
-      W\to P\colon & (wid, t_s, t_s', l, wsig) \\[-1em]
+      W\to P\colon & (wid, t_s, t_s', l, wsig)
+      \\[-1em]
       \noalign{\hfill\small Participation}

### 2018-02-28 paper/DB-anon-cred.tex
Clarifies PoPoK and DBPK

@@
 (Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
-Knowledge.)
+Knowledge, instead of \ac{DBPK}.)
 However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 

### 2018-02-28 paper/protocol.tex
Starts rewrite of protocol section

@@
 \label{protocol}
+
+\NewCryptoScheme{\PRIVOscheme}{PRIVO}
+\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
+\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
+\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
+\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}
+
+We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
+The protocol consists of four phases: the setup, join, participation and 
+submission phases.
+We have an identification authority \(\ID\), an organizer Oscar, \(\O\), a 
+protester Alice (\(\A\)) and a witness Bob \(\B\).
+
+\NewCryptoEntity{\ID}{ID}
+
+\emph{Setup.}
+During the setup phase, we set up the needed keys.
 

### 2018-02-28 paper/intro.tex
Eve to Grace, impersonating verifier implicitly covered in public-key db, tone down claim by including honest-but-curious for symmetric db

@@
 
-\emph{Context.} Consider the following illustrative scenario in which Alice is an activist that organizes a protest against the current regime leader Eve in some location(s).
-On one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
-On the other hand, Eve is an autocrat who opposes Alice's cause.
-Bob, Carol and many others participate in the protest for Alice's cause against Eve.
-However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Eve's regime. 
+\emph{Context.} Consider the following illustrative scenario in which Alice is an activist that organizes a protest against the current regime leader Grace in some location(s).
+On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
+On the other hand, Grace is an autocrat who opposes Alice's cause.
+Bob, Carol and many others participate in the protest for Alice's cause against Grace.
+However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
 To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
@@
 Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
-Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Eve (and possibly other entities) have an incentive to decrease it.
-In this case, we are left with two options: either we trust Alice or Eve or we have to be able to verify their claims.
-In this paper, our main objective is to provide a scheme preventing both Alice and Eve from cheating (\ie their claim should be verifiable).
+Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
+In this case, we are left with two options: either we trust Alice or Grace or we have to be able to verify their claims.
+In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
@@
 Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
-In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
+In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
 %Sonja says: I'm confused: can we or can we not provide this?
@@
 
-In contrast to the traditional assumption of honest verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.
+In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}
 %Seb: above, we should put the reference to the Schnorr protocol 
@@
 %Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
-In this case, it does not make sense to verify any pro-government protests in which Eve's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
 Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.
@@
 \PRIVO achieves privacy, but not receipt freeness.
-This means that there is a way for Eve to efficiently verify that Alice has to the participated.
-However, this requires Eve to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
+This means that there is a way for Grace to efficiently verify that Alice has to the participated.
+However, this requires Grace to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
 
@@
 We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
-We give the relevant background on the building blocks of our solution \PRIVO and then describe our proposal for distance-bounding anonymous credentials that copes with a malicious (impersonating) verifier.
-Finally, we present the protocol constructed from the building blocks, its security and privacy analysis, and conclude with a discussion.
+We give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier.
+\PRIVO, the protocol constructed from the building blocks, is presented next and we analyze its security and privacy as well as performance and implementation issues.
+We conclude with a discussion.

### 2018-02-28 paper/analysis.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg
removes assumptions from analysis, to be merged with system model

@@
 \end{itemize}
-
-\subsection{Assumptions} \label{assumptions}
-
-We assume that every participant has a device similar to a smartphone.
-Throughout this text, when we refer to a participant, say Alice, we actually 
-mean a principal which can perform cryptographic operations and communicate with 
-other local devices on Alice's behalf.
-(This means that we essentially provide a lower bound for the participation 
-count, since some participants might not have such a device.)
-
-No connection to any global network the Internet is necessary during the 
-protest.
-During the protest these devices are computationally limited by their 
-batteries.
-Before and after the protest, we assume that the devices have Internet 
-connections and are not computationally limited by any battery.
-
-We further assume that every participant has a digital certificate signed by 
-some logically centralized certificate authority.
-E.g.\ that we can use the cryptographic keys stored in the chip of the national 
-identity card or passport.
-We need this to prevent Sybil attacks~\cite{SybilAttack}.
 

### 2018-02-28 paper/SystemModel.tex
moved and rephrased assumptions

@@
 
-\emph{System model and physical assumptions.}
-In practical terms, participants witness each other's particpation using their smartphones running the protocol described in \cref{protocol} and uploading their testimony to a blockchain after the protest.
-Thus, they need connectivity at least to each other during the protest and Internet connectivity after.
+\emph{System model and physical assumptions.} \label{assumptions}
+Throughout this text, when we refer to a participant, say Alice, we actually 
+mean an agent which can perform cryptographic operations and communicate with 
+other local devices on Alice's behalf. We assume that every participant has a digital certificate signed by 
+some logically centralized certificate authority.
+\Eg that we can use the cryptographic keys stored in the chip of the national 
+identity card or passport.
+We need this to prevent Sybil attacks~\cite{SybilAttack}.
+
+In practical terms, participants witness each other's particpation
+using their smartphones (or similar devices) running the protocol described in
+\cref{protocol} and uploading their testimony (\ie proof shares) to the blockchain after the protest. 
+During the protest the devices are computationally limited by their 
+batteries and need connectivity at to each other but no connection to
+any global network or the Internet is necessary. Before and
+after the protest, we assume that the devices have Internet  
+connections and are not computationally limited by any battery.
 
 \include*{MANETs}
+
+%assumptions about smartphones:
+%(This means that we essentially provide a lower bound for the participation 
+%count, since some participants might not have such a device.)
+%Sonja says: is this still true? Given mafia fraud we can't guarantee
+%that, right?

### 2018-02-28 paper/analysis.tex
Eve to Grace, Rusuk to Mallory

@@
 We note that Alice and Bob do not trust each other, for all they know one or the 
-other could be an agent of Eve the autocrat.
+other could be an agent of Grace the autocrat.
 \begin{itemize}
-  \item Eve the evil autocrat,
-  \item Rusuk the foreign nation state, and finally
+  \item Grace the evil autocrat,
+  \item Mallory the foreign nation state, and finally
 \end{itemize}
@@
   \item Alice and Bob can reuse old proofs by modifying the identifiers.
-  \item Eve can reuse proofs by creating a manifesto which yields the same 
+  \item Grace can reuse proofs by creating a manifesto which yields the same 
     identifier as Alice's protest, then try to create new nodes in the 
@@
 
-Eve (possibly with Rusuk's aid) wants to arrange a counter-protest.
+Grace (possibly with Mallory's aid) wants to arrange a counter-protest.
 One way to get a higher participation count is to use the same identifier as 
 Alice's protest.
-Since the identifier for the protest is the hash value of the manifest, Eve 
+Since the identifier for the protest is the hash value of the manifest, Grace 
 must find a second preimage for the hash function.
@@
 
-Alice wants to arrange another protest against Eve.
+Alice wants to arrange another protest against Grace.
 Her manifesto can remain the same, thus the protest identifier remains the 
@@
 
-Eve and Rusuk has an incentive to lower the confidence in the result.
+Grace and Mallory have an incentive to lower the confidence in the result.
 One way they can do this is to say that the result does not contain all 

### 2018-02-28 paper/properties.tex
Eve to Grace, Rusuk to Mallory

@@
 
-We have three \emph{malicious} adversaries: Alice, Eve and Rusuk.
+We have three \emph{malicious} adversaries: Alice, Grace and Mallory.
 Alice the activist (and all the protesters) try to increase the count.
-Eve the totalitarian dictator tries to decrease the count.
-Additionally, Eve tries to deanonymize the participants to arrest them or 
+Grace the totalitarian dictator tries to decrease the count.
+Additionally, Grace tries to deanonymize the participants to arrest them or 
 \emph{convince} them to change their minds.
-Finally, we have Rusuk who is represents another nation state.
-Rusuk has some interest in affecting the state of Eve's regime, for Rusuk's own 
-gain, thus supporting either Eve or Alice as he see fits.
-Rusuk will thus also try to either increase or decrease the count.
+Finally, we have Mallory who is represents another nation state.
+Mallory has some interest in affecting the state of Grace's regime, for Mallory's own 
+gain, thus supporting either Grace or Alice as he see fits.
+Mallory will thus also try to either increase or decrease the count.
 We will now formally define some security properties specifying the 
@@
     \item Designated event:%
-      \label{DesignatedEvent} prove that the data is designated for the event.
+      \label{DesignatedGracent} prove that the data is designated for the event.
     \end{requirements}
@@
 \Cref{CoercionResistance} is probably not possible to achieve for protests:
-\eg Eve can simply physically bring Alice to a protest against her will.
+\eg Grace can simply physically bring Alice to a protest against her will.
 This leaves us with \cref{ReceiptFreeness,VotePrivacy}.

### 2018-02-28 paper/conclusions.tex
conclusions draft

@@
 
+We have introduced \PRIVO, a protocol for verifiably counting
+participants at protests. Despite the verification, the privacy of the
+participants is preserved to the extent possible by their physical
+presence at the protest. To achieve that, we adapted the Schnorr
+protocol to develop distance-bounding anonymous credentials. Except for receipt
+freeness (\cref{ReceiptFreeness}), which we cannot guarantee if the adversary gets access to
+Alice's device and cryptographic secret, \PRIVO
+fulfills all verification and privacy properties we derived from those
+of electronic voting complemented by the specific constraints on time
+and location required for protests. 
 In general, none of the related works fulfils the eligibility verifiability 
@@
 privacy requirements.
-And finally, most of the current methods are estimates, with quite some error 
-margins.
+
+Finally, most of the current methods are estimates, with quite some error 
+margins. While \PRIVO is an actual count and not an estimate, its
+accuracy for the total number of participants hinges on the
+participants having the necessary equipment (a smartphone or similar
+device), some sort of trustworthy credential, and the willingness to
+run the protocol. If used today, \PRIVO would result in a
+considerable undercount in most scenarios, but it presents a first
+step toward accurate verifiable yet privacy-preserving crowd counting
+by showing how it can be done in theory at least and in practice once
+some assumptions become more realistic.

### 2018-02-28 paper/protocol.tex
last Eve to Grace, in protocol section and abstract.

--- 2018-02-28 paper/protocol.tex
@@
       P\colon & t_s\gets \TSget \\
-        & cid\gets \Hash[\text{manifesto}], \\
-        & pid\gets \ACprf[_{k_P}][cid] \\
-      W\colon & t_s'\gets \TSget
-      \\[-1em]
-      \noalign{\hfill\small Join}
-      \midrule
-      \noalign{\hfill\small Participation}
-      \\[-3em]
+      W\colon & t_s'\gets \TSget \\
+      P\colon & cid\gets \Hash[\text{manifesto}], \\
+        & pid\gets \ACprf[_{k_P}][cid]
+      & \text{\small Join} \\ \midrule && \text{\small Participation} \\[-1.5em]
       P\to W\colon & pid \\
@@
       W\to P\colon & (wid, t_s, t_s', l, wsig)
-      \\[-1em]
-      \noalign{\hfill\small Participation}
-      \midrule
-      \noalign{\hfill\small Submission}
-      \\[-2em]
+      & \text{\small Participation} \\ \midrule && \text{\small Submission} 
+      \\[-1.5em]
       W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
@@
   \caption{%
-    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
+    An overview of of the Join, Participation and Submission phases of \PRIVO\@.
     The organizer \(O\) broadcasts the manifesto.
@@
 must remove her secret \ac{PRF} key, \(k_A\).
-With this key Eve can verify that Alice has submitted a proof by computing 
+With this key Grace can verify that Alice has submitted a proof by computing 
 \(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).

### 2018-02-28 paper/conclusions.tex
fulfil to fulfill for American English

@@
 and location required for protests. 
-In general, none of the related works fulfils the eligibility verifiability 
+In general, none of the related works fulfills the eligibility verifiability 
 \cref{%
@@
 }.
-To some extent, some techniques do fulfil \cref{DesignatedEvent}, since people 
+To some extent, some techniques do fulfill \cref{DesignatedEvent}, since people 
 usually use placards in the protests.

### 2018-02-28 paper/intro.tex
update of properties.tex

@@
 
-%Seb: I suggest that we move this part to system model
-%\subsection{Combining properties of electronic voting with location proofs}
-\emph{Relationship between protesting and electronic voting}.
-In general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
-
-Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
-\begin{description}
-  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according 
-    to the cast votes.
-  \item[Individual verifiability:] every voter can verify that their vote is 
-    included in the result.
-\end{description}
-We translate the votes into \emph{proofs of participation}.
-Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
-eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
-In essence, the proof must bind the person to the time and location of the protest.
-We will define these more formally in \cref{Verifiability}.
-
-There are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{description}
-  \item[Vote privacy:] the voting does not reveal the individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can 
-    be used as a proof of how the voter voted.
-  \item[Coercion pesistance:] a voter cannot cooperate with a coercer to prove 
-    the vote was cast in any particular way.
-\end{description}
-We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
-%Seb: suggestion maybe we should put the following part in the discussion
-However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
-For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
-However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
-Thus we need at least participation-proof privacy but receipt freeness (see \cref{Privacy} for a detailed definition) is desired.
-In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
-%Sonja says: I'm confused: can we or can we not provide this?
-%Seb: I agree with Sonja, it is not clear whether we achieve it or not
-
 %Seb: to do complete the contributions
@@
 
-In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol that allows for a malicious verifier.\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}
+In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
 %Seb: above, we should put the reference to the Schnorr protocol 

### 2018-02-28 paper/properties.tex
typo
update of properties.tex

@@
-\section{Desired security properties}%
+\section{Security requirements}%
 \label{Properties}
@@
 
-We have three \emph{malicious} adversaries: Alice, Grace and Mallory.
-Alice the activist (and all the protesters) try to increase the count.
-Grace the totalitarian dictator tries to decrease the count.
-Additionally, Grace tries to deanonymize the participants to arrest them or 
-\emph{convince} them to change their minds.
-Finally, we have Mallory who is represents another nation state.
-Mallory has some interest in affecting the state of Grace's regime, for Mallory's own 
-gain, thus supporting either Grace or Alice as he see fits.
-Mallory will thus also try to either increase or decrease the count.
-We will now formally define some security properties specifying the 
-computational effort needed by the adversaries to succeed.
-We categorize the desired properties into verifiability and privacy.
+On our setting, we have three potential adversaries: Alice, Eve and Mallory.
+%Seb: I changed the name of Grace to Eve to be consistent with the introduction
+Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
+In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
+Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
+gain, thus supporting either Eve or Alice as he see fits.
+Thus, the objective of Mallory will also be to either increase or decrease the count.
+%Seb: we have to justify why Mallory is not captured either by Alice or Eve
+In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
+In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.
+
+Note that in general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
+To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.
 
@@
 
-We desire three verifiability requirements:
+Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
+\begin{description}
+  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
+  \item[Universal verifiability:] anyone can verify that the result is according 
+    to the cast votes.
+  \item[Individual verifiability:] every voter can verify that their vote is 
+    included in the result.
+\end{description}
+We translate the votes into \emph{proofs of participation}.
+Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
+The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
+eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
+In essence, the proof must bind the person to the time and location of the protest.
 
+To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
 \begin{requirements}[V]
-  \item\label{EligibilityVerif} Eligibility: anyone can verify that each 
-    participation proof provides temporal and spatial eligibility and that it 
-    has not been counted before.
+  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that it has not been counted before.
     \begin{requirements}
-    \item Temporal egligibility:%
-      \label{CreatedAfterStart} prove that the data was created after the start of 
-      the event;%
-      \label{CreatedBeforeEnd} prove that the data was created before the end of 
-      the event.
-    \item Spatial eligibility:%
-      \label{SpatiallyRelated} prove that the data is spatially related to the 
-      physical location of the event.
-    \item One-proof-per-person:%
-      \label{CountOnce} prove that no individual can be counted more than once.
-    \item Designated event:%
-      \label{DesignatedGracent} prove that the data is designated for the event.
+    \item \emph{Temporal eligibility}:%
+      \label{CreatedAfterStart} prove that the proof was created after the start of the protest and
+      %\label{CreatedBeforeEnd} prove that the proof was created 
+      before the end of the protest.
+    \item \emph{Spatial eligibility}
+      \label{SpatiallyRelated} prove that the proof is spatially related to the physical location or journey of the protest.
+    \item \emph{One-proof-per-person}:%
+      \label{CountOnce} prove that no individual can be counted more than once for a particular protest.
+    \item \emph{Designated event}:%
+      \label{DesignatedEvent} prove that the proof is designated for the protest.
     \end{requirements}
 
-  \item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
-    result is according to the submitted participation proofs.
-  \item\label{IndividualVerif} Individual verifiability: every participant can 
-    verify that their participation proof is included in the global count.
+  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
+  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that their participation proof is included in the global count.
 \end{requirements}
-We will now discuss these in more detail.
 
+We will now discuss these properties in more details focusing in particular to the one related specifically to the protest.
+
+%Seb: to complete
 \subsubsection{Temporal eligibility}
@@
 
-We also need privacy in addition to the verification requirements.
-As we indirectly pointed out earlier, we focus on the privacy provided to Alice 
-and Bob by the data.
-So as long as Alice and Bob can conceal their identities at the demonstration 
-and escape without arrest, their support is recorded in the data while their 
-privacy is not violated.
-(Following this line of thinking, it can actually be beneficial for the privacy 
-of the demonstrators to mix with the participants of any counter-demonstrations 
---- since the counts will still be correct.)
+In addition to the verification requirements, we also need to formalize the privacy properties.
+As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
+In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
+%Seb: I think this sentence should be clarified
+(Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)
 
-In voting, we have the following requirements:
+In voting protocols, there are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{requirements}[P]
-\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
-  individual vote.
-\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
-  provide any data that can be used as a proof of how the voter voted.
-\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
-  with a coercer to prove the vote was cast in any particular way.
+\item\label{VotePrivacy} \emph{Vote privacy}: the voting does not reveal any individual vote.
+\item\label{ReceiptFreeness} \emph{Receipt freeness}: the voting system does not provide any data that can be used as a proof of how the voter voted.
+\item\label{CoercionResistance} \emph{Coercion resistance}: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
 \end{requirements}
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
-\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
-\cref{VotePrivacy}.
+
+\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that \cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies \cref{VotePrivacy}. 
 \Cref{CoercionResistance} is probably not possible to achieve for protests:
@@
 This leaves us with \cref{ReceiptFreeness,VotePrivacy}.
+
+We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
+%Seb: suggestion maybe we should put the following part in the discussion
+However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
+For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
+However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
+Thus we need at least participation-proof privacy but receipt freeness is also desired.
+In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
+%Sonja says: I'm confused: can we or can we not provide this?
+%Seb: I agree with Sonja, it is not clear whether we achieve it or not
 

### 2018-03-01 paper/RelatedWork.tex
update of related work

@@
 
-The seemingly most commonly used method for counting crowds at protests is 
-Jacob's method~\cite[c.f.][]{%
+The seemingly most commonly used method for counting crowds at protests is \emph{Jacob's method}~\cite[c.f.][]{%
   2016DemonstrationsInSeoul,%
@@
 }.
-It is a manual method devised in the 1960s which relies on aerial photos of the 
-event.
-The verifier divides the protest venue into regions, then estimates the crowd 
-density in the different regions and finally sums them up to get an estimate of 
-the total.
-This method is prone to errors, since it is based on estimates.
-However, it allows for verification, since anyone can redo the counting using 
-the same photos.
-This provides universal verifiability (\cref{UniversalVerif}).
-It is difficult to achieve individual verifiability (\cref{IndividualVerif}) 
-since it is hard to verify that oneself is indeed in any of the photos.
-(It is of course possible with very detailed photos, but not currently realistic 
-to do with aerial photos.)
-We can argue eligibility verifiability (\cref{EligibilityVerif}) if all the 
-photos are taken at the same point in time with no overlap, since then no one 
-can be counted twice.
+It is a manual method devised in the 1960s relying on aerial photos of the event.
+The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
+Clearly this method is prone to errors as it is based on estimates.
+It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
+However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
+We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
 Unfortunately, we can only get the peak participation with this method.
+When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
+However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
+%Seb: maybe we should also give information about the privacy level reached by this different method
 
-When it comes to spatial and temporal verifiability, we have to rely on the 
-photos.
-We can try to determine from the photos themselves when and where the they were 
-taken.
-However, the best we can do is to employ forensic methods to try to detect any 
-modifications or other attempts at fraud.
-
-There is an app CrowdSize~\cite{CrowdSize} which estimates the size of a crowd 
+Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
 based on a selected space.
-Then the user selects one of three pre-set density estimates: light, medium or 
-dense.
-This is similar to the method usually used by police, \eg for the protests in
-Seoul
+Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
+%Seb: what are the meaning of the choice of density estimates, it is a way to specify an apriori assumption about the density of the crowd or to choose between a min, average, max estimates?
+This is similar to the method usually used by police (\eg for the protests in Seoul):
 \blockcquote{2016DemonstrationsInSeoul}{%
@@
 }.
-This method is not verifiable unless the user takes a picture of the crowd, 
-then it inherits the verifiability properties of the previous method.
+This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.
 
-There is a body of work in the computer vision community, \eg the work of 
-\citet{NNCrowdCounting}.
-This class of methods requires photos or video surveillance of the protest 
-location during the entire protest.
-They generally include machine learning, and thus also require a training 
-dataset to train the algorithms.
-In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
-algorithm on different scenes, which might make this method easier to use for 
-protesting.
-We can provide universal verifiability (\cref{UniversalVerif}) with this 
-method, since someone can always recount the participants using the recorded 
-video material.
-We might be able to provide some degree of individual verifiability 
-(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
-this might still be difficult. Automatic face recognition can help
-verifiability but at the price of privacy.
-Also, it is difficult (if not impossible) to not count people twice, thus we 
-cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
-In theory, this class of methods will provide an upper bound, whereas our method 
-can provide a lower bound.
-However, it is still difficult to capture the entire location on surveillance 
-video, which diminishes the argument for an upper bound.
-The spatial and temporal verifiability properties are reduced to those of the 
-video, which should be similar as in our discussion about the verifiability of 
-photos above, \ie forensic methods.
+In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
+\citet{NNCrowdCounting}).
+This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
+They generally based on machine learning, and thus also require a training dataset to work.
+In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
+Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
+Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but this might still be difficult. 
+Note also that while automatic face recognition can help verifiability, it has a high impact on privacy.
+Also, it is difficult (if not impossible) to not count people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
+In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
+However, it is still difficult to capture the entire location on surveillance video, which diminishes the argument for an upper bound.
+The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
 
@@
 }.
-This is difficult to fully capture.
-If photo material is taken from angles we will additionally have problems not 
-counting people twice.
+In this situation it is very difficult to faithfully capture the situation.
+Even if the photo material is taken from different angles, we will have the additional problem of not counting people twice.
 
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul} there was one 
-retail analytics company that tried to estimate the number of participants using 
-their technology.
-They scanned for MAC addresses emitted from the Wi-Fi of participants' 
-smartphones.
+During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company has tried to estimate the number of participants using their technology.
+They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
 However, this method required many assumptions:
 \blockcquote{2016DemonstrationsInSeoul}{%
-  The company presumed that about half of smartphone users usually leave their 
-  Wi-Fi feature on and the other half switch it off, based on a separate survey 
-  on smartphone usage. It also assumed that about 20 percent of the smartphone 
-  signals were repetition from the same device.
+  The company presumed that about half of smartphone users usually leave their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
+It also assumed that about 20\% of the smartphone signals were repetition from the same device.
 }
-This method cannot provide any verifiability, we must trust the company to do 
-the measurements correctly and to be honest about when and where they did them.
-As MAC address randomization get wider adoption this will be even more 
-difficult, although some tracking of smartphones will still be 
-possible~\cite{WhyMACRandomizationIsNotEnough}.
+This method cannot provide any verifiability, as we must trust the company in doing the measurements correctly and to be honest about when and where they did them.
+As MAC address randomization get wider adoption, this will be even more difficult, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.
 
-A better proposal would be to use \emph{IMSI catchers} (or the real cell 
-towers of the mobile network) to count unique phones at the location.
+A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
 However, there are several problems with this approach.
-First, it will be difficult to register only the participants' phones, many 
-bystanders will also be counted.
-It is also difficult to differentiate between the protesters and the 
-counter-protesters.
-Second, since the phone is a unique identifier, participants might be 
-uncomfortable to be registered in association with the event and might thus 
-turn the device off, even though, at least with 5G, the IMSI will not be
+First, it will be difficult to register only the participants' phones and many bystanders will also be counted.
+It is also difficult to differentiate between the protesters and the counter-protesters.
+Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI will not be
 transmitted in plaintext anymore. %need to cite?
-Finally, there will be limited verifiability, as the data recorder must be 
-trusted to record all data and do it in the relation to the event.
+Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in the relation to the protest.
 
-\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi 
-signal as a sonar to detect people.
-However this method is designed for indoor use and does not scale to more than 
-a crowd of 20 people.
-In either case, this type of data cannot provide verifiability.
+\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
+Howeve,r this method is designed for indoor use and does not scale to more than a crowd of 20 persons, which makes it unfit to use in protest.
+In addition, this type of data does not provide verifiability.
 
-In general for all of the above methods, the more a crowd spreads out, the more
-difficult it will be to determine its size:
-the problem is determining whether people near the event's perimeter are 
-participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulty capturing the actual attendance of an event,
-\ie the cumulative participation, not just the count at a snapshot around the 
-peak.
+In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
+In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
+These methods also have difficulty capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
 
-One of the most closely related work is \citet{CrowdCount}.
-This is a web service which lets Alice create an event and Bob can submit his 
-location to register that he is in Alice's event.
-This solves the problem that it counts everyone (who submitted), not just the 
-count at the snapshot of the photos.
-However, there is no verification, \ie the service must be trusted to behave 
-honestly, but even then, nothing prevents Bob from submitting twice (violating 
-eligibility, \cref{EligibilityVerif}).
-Another downside is that the service also requires an Internet connection 
-during the event to register as a participant.
-This can make it difficult to use if \eg Alice has organized a protest 
-against the government, who shuts down the cellular network or Internet 
-backbone as a means to censor the protest.
+One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
+This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the photos.
+However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
+Another downside is that the service also requires an Internet connection during the event to register as a participant.
+This makes it prone to some form of denial-of-service attack.
+For instance, if Alice has organized a protest against Eve's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.
 
-Another related approach based on devices is UrbanCount~\cite{UrbanCount} which
-uses epidemic spreading of crowd-size estimates by device-to-device
-communication to count crowds in dense urban environments with high
-node mobility and churn. There is, however, no consideration of a potentially
-adverserial setting and thus no verification or checks on
-eligibility. DiVote~\cite{DiVote}, a prior work by the same authors for
-polling in dense areas, avoids double counting but again only for
+Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which uses epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with highnode mobility and churn.
+There is, however, no consideration of a potentially adverserial setting and thus no verification or checks on eligibility.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting but again only work for
 honest participants.

### 2018-03-01 paper/BuildingBlocks.tex
Moves DB-anon-cred into building blocks
Updates anonymous credentials
coincoin

@@
 
-We need a few primitives with special properties to build our protocol.
+In this section, we will briefly review the primitives that form the building blocks of \PRIVO.
 
+%Seb: I am not sure that to explain hash functions as they are really basic primitives
 \subsection{Collision-resistant hash functions}
@@
   Let \(\lambda\) denote the security parameter.
-  We say that a hash function, \(\Hash\), is collision resistant if for any 
-  \ac{PPT} algorithm \(\algA\) we have that
+  We say that a hash function, \(\Hash\), is collision resistant if for any \ac{PPT} algorithm \(\algA\) we have that
   \begin{multline*}
@@
 
-Thus we can instantiate \(\Hash\) with any algorithm from the SHA-2 or SHA-3 
-families.
+\(\Hash\) can be instantiated with any algorithm from the SHA-2 or SHA-3 families.
+
+\input{ZKPK.tex}
+
+\input{anon-cred.tex}
+
+%\input{LocationProofs.tex}
+%Seb: I have mode the location proofs to the
 
 \input{DistanceBounding.tex}
-\input{anon-cred.tex}
-\input{LocationProofs.tex}
+
+\input{DB-anon-cred.tex}
+
 \input{TimeStamp.tex}

### 2018-03-01 paper/DB-anon-cred.tex
coincoin

--- 2018-02-28 paper/DB-anon-cred.tex
@@
 
-We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} 
-protocols that provide the above security properties assume an \emph{honest} 
-verifier.
-This assumption does not hold in our setting, where every verifier at some point 
-also might be a (malicious) prover.
+We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} protocols that provide the above security properties assume an \emph{honest} verifier.
+This assumption does not hold in our setting, in which every verifier might also be at some point a (malicious) prover.
 We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.
 
-There is a protocol which provide \ac{DBPK} with all the desired properties from 
-above, ProProx~\cite{ProProx}.
-(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
-Knowledge.)
-However, ProProx provides \iac{DBPK} protocol for quadratic residues, \ie for 
-proving \(\DBPK[\alpha][a = \alpha^2]\).
-We, on the other hand, need \iac{DBPK} protocol for discrete logarithms.
-We will now introduce such a protocol which will allow us to do \ac{DB} 
-anonymous credentials.
-We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} and \ac{DBIF} resistance --- \ie not \ac{DBTF} resistance.
+There is a protocol which provide \ac{DBPK} with all the desired properties from above, ProProx~\cite{ProProx}.
+(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge.)
+However, ProProx provides \iac{DBPK} protocol only for quadratic residues (\ie for proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need a \iac{DBPK} protocol for discrete logarithms.
+To realize this, we will now introduce such a protocol that will allow us to do \ac{DB} anonymous credentials.
+We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.
 
@@
 
-\emph{Reattempting \iacl{DB} Schnorr protocol.}
-In the original \ac{DB} paper by \citet{DistanceBounding}, they proposed how to 
-make the Schnorr identification scheme~\cite{Schnorr} distance bounding.
+\emph{New attempt of \iacl{DB} Schnorr protocol.} In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to design a distance bounding protocol based on the Schnorr identification scheme~\cite{Schnorr}.
 That \ac{DB} Schnorr protocol was shown to be prone to distance 
@@
 which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
-It will not protect against terrorist fraud, although this would be desirable.
+It will not protect against terrorist fraud, although ideally this property should be desirable.
 
 We present the protocol in \cref{SchnorrFigure}.
-The difference from the original Schnorr protocol is that the prover commits to 
-two random values and the verifier sends two challenges.
-Then the verifier presents to the prover which commitment and challenge to use 
-during the \ac{DB} phase.
+The difference from the original Schnorr protocol is that the prover commits to two random values and the verifier sends two challenges.
+Afterwards, the verifier presents to the prover which commitment and challenge to use during the \ac{DB} phase.
 
@@
   \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
-    \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired knowledge 
-    error and distance-bounding error.
+    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
+    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
   }%
@@
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge we must choose \(k\) 
-logarithmically in the security parameter \(\lambda\) and repeat the protocol 
-until the knowledge error is small enough.
-This will actually also decrease the success probability of \iac{DBMF} adversary 
-in the \ac{DB} step.
-The \ac{DBMF} adversary does not know which challenge the verifier will use, 
-thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it 
-correctly.
-The prover will only provide one of the responses: even if the adversary re-runs 
-the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) 
-will have changed --- which thus yields another \(R_b\) in the end of the 
-protocol.
-By repeating the protocol we decrease this probability.
+To achieve malicious-verifier zero-knowledge we must choose \(k\) logarithmically in the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
+This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
+Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
+The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
+A sequential repetition of protocol will decrease this probability.
 
 The \ac{DB} phase protects against distance fraud.
-\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with 
-\(r_i\).
+\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with \(r_i\).
 
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
-phase for at least one round.
+The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
 The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
-Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) 
-bits of the other.
-Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
-them from the prover.
-But at this point the adversary must wait for \(b_{l+1}\) from the verifier and 
-then relay that challenge to the prover to receive the correct \(r_i\) --- this 
-relay will be detected.
+Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
+Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
+However at this point the adversary must wait for \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
 
-The protocol is also secure against distance hijacking.
-This follows from the fact that it is the authenticating bit string that is used 
+The protocol is also secure against distance hijacking due to the fact that it is the authenticating bit string that is used 
 during the \ac{DB} phase.

### 2018-03-01 paper/DistanceBounding.tex
change to intro and system model
Changes "i.e.\ " and "e.g.\ " to \ie and \eg
coincoin

@@
 
-% XXX Better intro to distance bounding
-\Ac{DB} protocols were first suggested by \citet{DistanceBounding}.
-Over the years the desirable properties of \ac{DB} protocols can be summarized 
-as follows:
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks contactless communications in which the adversary forwards a communication between a prover and a possibility far-away verifier to authenticate.
+These attacks cannot be prevented by cryptographic tools as they are independent of the semantics of the messages exchanged and mechanisms ensuring the physical proximity between a verifier and a prover must be used.
+\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
+Time critical phases are complemented by slow phases during which the time is not taking into account.
+At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.
+
+The main security requirements of \ac{DB} protocols can be summarized as follows:
 \begin{itemize}
     % XXX Describe the DB frauds in more detail, i.e. explain them.
-  \item \ac{DBMF} resistance,
-  \item \ac{DBDF} resistance,
-  \item \ac{DBDH} resistance,
-  \item \ac{DBTF} resistance,
-  \item \ac{DBIF} resistance,
+  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
+    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
+  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
+  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by 
-\citet{DB-BMV} and another by \citet{DB-DFKO}.
+There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
-The majority of the existing \ac{DB} protocols are symmetric and thus requires 
-an honest verifier.
-There has been less work done in the domain of asymmetric (or public-key) 
-\ac{DB} protocols.
-Unfortunately, our setting requires a public-key \ac{DB} protocol with a 
-\emph{malicious verifier} who will try to \emph{impersonate the prover}.
-The verifier might also try to track the provers and map their identities to 
-their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with 
-resistance to all the frauds mentioned above as well as against this verifier 
+The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
+Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
+There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
+Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
+The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
 who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials, 
-which we will describe next.
+More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
+The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
+%Seb: I have created the acronym DBPK in bibsp.sty

### 2018-03-01 paper/properties.tex
coincoin

@@
 Thus we need at least participation-proof privacy but receipt freeness is also desired.
-In essence, this means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
+In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
 %Sonja says: I'm confused: can we or can we not provide this?

### 2018-03-02 paper/DB-anon-cred.tex

@@
 
-There is a protocol which provide \ac{DBPK} with all the desired properties from above, ProProx~\cite{ProProx}.
-(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge.)
-However, ProProx provides \iac{DBPK} protocol only for quadratic residues (\ie for proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need a \iac{DBPK} protocol for discrete logarithms.
-To realize this, we will now introduce such a protocol that will allow us to do \ac{DB} anonymous credentials.
-We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.
+There is a protocol which provide \ac{DBPK} with all the desired properties from 
+above, ProProx~\cite{ProProx}.
+(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
+Knowledge, instead of \ac{DBPK}.)
+However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie for 
+proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need 
+\iac{DBPK} protocol for discrete logarithms.
+To realize this, we will now introduce such a protocol that will allow us to do 
+\ac{DB} anonymous credentials.
+We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
+\ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.
 
@@
 
-\emph{New attempt of \iacl{DB} Schnorr protocol.} In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to design a distance bounding protocol based on the Schnorr identification scheme~\cite{Schnorr}.
+\emph{Reattempting \iacl{DB} Schnorr protocol.}
+In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
+design a distance-bounding protocol based on the Schnorr identification 
+scheme~\cite{Schnorr}.
 That \ac{DB} Schnorr protocol was shown to be prone to distance 

### 2018-03-02 paper/TimeStamp.tex

@@
-\subsection{Time-stamping service, or, blockchains}%
+\subsection{Time-stamping service -- blockchains}%
 \label{StorageProperties}
@@
 \begin{itemize}
-  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is 
-    difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
-  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
-    \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
+  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
+  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
 \end{itemize}
 
-With these building blocks we can ensure that a message \(m\) was created within 
-the time interval \(\interval{t_0}{t_1}\).
+With these building blocks we can ensure that a message \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
 After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
-Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping 
-service to get \(\pi_{t_1}\gets \TSstamp[h]\).
+Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).
 
-Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created 
-within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
-\(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land 
-  \TStime[\pi_{t_1}] = t_1\).
+Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).
 
 We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
-The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
-return the block into which \(x\) was included.
+The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the block into which \(x\) was included.
 \(\TSget\) will return the hash of the current head of the chain.
-This value is difficult to predict since it depends on all submitted 
-transactions and usually some randomness, \eg nonces and miners' secrets.
-The blockchain must also be continuously extended, \eg as in
-Bitcoin~\cite{Bitcoin}, where a new block appears approximately every 10 
-minutes.
-So having a dedicated blockchain for a protest will not do, it is better to use 
-a blockchain which is also used for other things too.
+This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
+The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
+Having a dedicated blockchain for a protest will not do, and thus it is better to use a blockchain which is also used for other things too.
 
-There are some additional properties that we need from \(\TS\), which are 
-implied by blockchains.
-First, we need immutability, \ie once we commit something (through \(\TSstamp\)) 
-it will remain there.
-We will use this to ensure verifiability, the data must remain to be verifiable.
-
-Second, once we have committed some data, we do not need to keep the data 
-itself, but we can store some confirmation value instead.
-\Eg using blockchains, we can store the hash of the block where our data was 
-committed, while this block remains we are sure that our data remains committed 
---- even if we no longer remember what our data looked like.
+There are some additional properties that we need from \(\TS\), which are implied by blockchains.
+First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
+We will use this to ensure verifiability as the data must remain to be verifiable.
+Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
+For instance using blockchains, we can store the hash of the block in which our data was committed, while this block remains we are sure that our data remains committed --- even if we no longer remember what our data looked like.
 We will use this property to approximate the property of receipt freeness.

### 2018-03-02 paper/conclusions.tex

@@
 freeness (\cref{ReceiptFreeness}), which we cannot guarantee if the adversary gets access to
-Alice's device and cryptographic secret, \PRIVO
+Alice's device and secret PRF key after her participation has
+been witnessed and before she had a chance to
+delete it, \PRIVO
 fulfills all verification and privacy properties we derived from those

### 2018-03-15 paper/protocol.tex
Starts writing the protocol details

--- 2018-02-28 paper/protocol.tex
@@
 \NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
+\NewAlgorithm{\PRIVOreg}{\PRIVOscheme.\!Register}
 \NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
@@
 
+\NewCryptoEntity{\Alice}{A}
+\NewCryptoEntity{\Bob}{B}
+\NewCryptoEntity{\Carol}{C}
+
 We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
@@
 submission phases.
-We have an identification authority \(\ID\), an organizer Oscar, \(\O\), a 
-protester Alice (\(\A\)) and a witness Bob \(\B\).
+We have several roles.
+We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
+identity and a cryptographic key.
+We have the protesters Alice (\(\Alice\)), Bob (\(\Bob\)) and Carol (\(\Carol\)) 
+who want to participate in a given protest.
 
-\NewCryptoEntity{\ID}{ID}
-
-\emph{Setup.}
-During the setup phase, we set up the needed keys.
+\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
+The setup phase is for the \ac{CA} to set up all the needed keys.
+The \ac{CA} starts by generating a service public-private key-pair \((spk, 
+  ssk)\) by the following.
+\(\gets \PRIVOsetup[1^\lambda]\), where \(\lambda\) is the security parameter, 
+and then publishes \(spk\).
+\begin{algorithmic}
+  \Function{\PRIVOsetup}{$1^\lambda$}
+    \State{$spk\gets (g, G, q, \dots)$}
+    \State{$ssk\gets (g, G, q, \dots)$}
+    \State{\Return{$(spk, ssk)$}}
+  \EndFunction
+\end{algorithmic}
 

### 2018-03-16 paper/protocol.tex
Converts paper to IEEEtran
Smaller font size in protocol and proofshare figures
Fixes fontsizes in protocol figures
Writes up setup and registration

@@
 \NewCryptoScheme{\PRIVOscheme}{PRIVO}
-\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
-\NewAlgorithm{\PRIVOreg}{\PRIVOscheme.\!Register}
-\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
-\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
-\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}
+\NewAlgorithm{\PRIVOsetup}{Setup}
+\NewAlgorithm{\PRIVOreg}{Register}
+\NewAlgorithm{\PRIVOjoin}{Join}
+\NewAlgorithm{\PRIVOparticipate}{Participate}
+\NewAlgorithm{\PRIVOsubmit}{Submit}
 
@@
 
+The setup and registration phases are the same as in Anon-Pass~\cite{AnonPass}.
+We have simply adapted their description for our notation, but tried to keep 
+them as similar as possible.
+
 \emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
 The setup phase is for the \ac{CA} to set up all the needed keys.
-The \ac{CA} starts by generating a service public-private key-pair \((spk, 
-  ssk)\) by the following.
-\(\gets \PRIVOsetup[1^\lambda]\), where \(\lambda\) is the security parameter, 
-and then publishes \(spk\).
-\begin{algorithmic}
-  \Function{\PRIVOsetup}{$1^\lambda$}
-    \State{$spk\gets (g, G, q, \dots)$}
-    \State{$ssk\gets (g, G, q, \dots)$}
-    \State{\Return{$(spk, ssk)$}}
-  \EndFunction
-\end{algorithmic}
+The \ac{CA} generates a service public-private key-pair \((spk, ssk)\) as 
+follows.
+Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
+Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times 
+  G\to G_T\)\footnote{%
+  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
+    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
+}.
+Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = 
+  g^z\).
+Then the service public key \(spk = (q, G, G_T, g, X, Y, Z)\) and the service 
+private key \(ssk = (x, y, z)\).
+
+\emph{Registration: \(sk\gets 
+    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
+During the registration phase, each protester will generate a secret key and 
+obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
+Thus each protester will have a signed secret key, the \ac{CA} will issue only 
+one signature per protester but will not know who has which key.
+The protester chooses \(d, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^d 
+  Z^r\) and send \(M\) to the server.
+The protester acts as prover and the \ac{CA} as verifier while they perform the 
+following \ac{ZKPK} protocol: \(\PK[d,r][M = g^d Z^r]\).
+If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
+  g^a\).
+Then it forms the signature \(s = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
+  M^{axy})\) and sends it to the protester.
+The protester verifies that the following equations hold:
+\begin{align*}
+  A &\neq 1 \\
+  e(g, B) &= e(Y, A) \\
+  e(g, Z_B) &= e(Z, B) \\
+  e(g, C) &= e(X, A) e(X, B)^d e(X, Z_B)^r.
+\end{align*}
+Upon success, the protester uses \(sk = (s, d, r)\).
+
+The setup and registration phases can be done once and the keys reused for an 
+arbitrary number of protests.
+Thus it would be suitable to have the registration phase as part of the issuance 
+of \eg national identity cards, passports or \acp{eID}.
+
+\subsection{Old}
 
@@
   \centering
+  \footnotesize
   \includegraphics{proofshare.tikz}
@@
   \centering
+  \footnotesize
   \begin{minipage}{\linewidth}
@@
       \\[-1em]
-      \noalign{\hfill\small Join}
+      \noalign{\hfill Join}
       \midrule
-      \noalign{\hfill\small Participation}
+      \noalign{\hfill Participation}
       \\[-3em]
@@
       \\[-1em]
-      \noalign{\hfill\small Participation}
+      \noalign{\hfill Participation}
       \midrule
-      \noalign{\hfill\small Submission}
+      \noalign{\hfill Submission}
       \\[-2em]

### 2018-03-16 paper/protocol.tex
Writes up more details of protocol (up to submission)

@@
 \NewCryptoScheme{\PRIVOscheme}{PRIVO}
-\NewAlgorithm{\PRIVOsetup}{Setup}
-\NewAlgorithm{\PRIVOreg}{Register}
-\NewAlgorithm{\PRIVOjoin}{Join}
-\NewAlgorithm{\PRIVOparticipate}{Participate}
-\NewAlgorithm{\PRIVOsubmit}{Submit}
-
-\NewCryptoEntity{\Alice}{A}
-\NewCryptoEntity{\Bob}{B}
-\NewCryptoEntity{\Carol}{C}
 
@@
 identity and a cryptographic key.
-We have the protesters Alice (\(\Alice\)), Bob (\(\Bob\)) and Carol (\(\Carol\)) 
-who want to participate in a given protest.
+We have the protesters who want to participate in a given protest.
+A protester can assume three different roles:
+\begin{enumerate*}
+\item We have the \emph{organizer} who will simply write a manifesto for the 
+  protest and spread to others.
+\item A \emph{participant} participates in the protest (and asks witnesses to 
+  vouch for his presence).
+\item A \emph{witness} provides proofs to participants that state the 
+  participant was indeed participating and the proofs are verifiable by third 
+  parties.
+\end{enumerate*}
+In general, there is one organizer and every protester will act as both 
+participant and witness.
 
@@
 them as similar as possible.
+
+\NewAlgorithm{\PRIVOsetup}{Setup}
 
@@
 
+\NewAlgorithm{\PRIVOreg}{Register}
+
 \emph{Registration: \(sk\gets 
@@
 one signature per protester but will not know who has which key.
-The protester chooses \(d, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^d 
+The protester chooses \(k, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^k 
   Z^r\) and send \(M\) to the server.
 The protester acts as prover and the \ac{CA} as verifier while they perform the 
-following \ac{ZKPK} protocol: \(\PK[d,r][M = g^d Z^r]\).
+following \ac{ZKPK} protocol: \(\PK[k,r][M = g^k Z^r]\).
 If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
   g^a\).
-Then it forms the signature \(s = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
+Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
   M^{axy})\) and sends it to the protester.
@@
   e(g, Z_B) &= e(Z, B) \\
-  e(g, C) &= e(X, A) e(X, B)^d e(X, Z_B)^r.
+  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
 \end{align*}
-Upon success, the protester uses \(sk = (s, d, r)\).
+Upon success, the protester uses \(sk = (\sigma, k, r)\).
 
@@
 of \eg national identity cards, passports or \acp{eID}.
+
+\emph{Creating a protest: the manifesto.}
+The organizer will write a manifesto for the protest, \ie to capture the cause.
+This manifesto is simply any intelligible text.
+He will distribute this manifesto to people: on the Web, on placards, \etc.
+If they agree, they will use it to join the protest.
+
+\NewAlgorithm{\PRIVOjoin}{Join}
+
+\emph{Joining participant: \((pid, t_s)\gets 
+    \PRIVOjoin[_P][\text{manifesto}]\).}
+A participant who wants to join the protest will use the manifesto to compute an 
+identifier for the cause, \(cid\gets \Hash[\text{manifesto}]\).
+Then this identifier is used to create the participant's protest-specific 
+identifier, \(pid\gets \ACprf[_{sk}][cid]\) (in 
+\cref{fig:ProofFig,fig:ProtocolOverview}).
+More specifically, \(pid = g_T^{1/(k+cid)}\) (remember that \(sk = (\sigma, k, 
+  r)\)).
+The participant should also get a time-correlated random value from the 
+time-stamping service, \(t_s\gets \TSget\).
+
+\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
+The witness simply should simply get a time-correlated random value from the 
+time-stamping service, \(t_s'\gets \TSget\).
+(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
+start of the time interval of creation for the proof share.).
+
+\NewAlgorithm{\PRIVOparticipate}{Participate}
+\NewAlgorithm{\PRIVOwitness}{Witness}
+
+\emph{Participating: \(\pi\gets
+    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
+The participant reblinds its signature \(\sigma\) on its secret key: choose 
+\(r_1, r_2\gets \ZZ_q^*\) and let \(
+  \hat\sigma = (\hat A = A^{r_1},
+                \hat B = B^{r_1},
+                \hat Z_B = Z_B^{r_1},
+                \hat C = C^{r_1 r_2}).
+\) (It is not necessary to compute a new \(\hat\sigma\) more than once per 
+\(pid\).)
+The participant sends \((pid, \hat\sigma)\) to the witness.
+The witness verifies that
+\begin{align*}
+  \hat A &\neq 1 \\
+  e(g, \hat B) &= e(Y, \hat A) \\
+  e(g, \hat Z_B) &= e(Z, \hat B).
+\end{align*}
+Both the participant and the witness compute
+\begin{align*}
+  v &= e(g, \hat C) \\
+  v_x &= e(X, \hat A) \\
+  v_{xy} &= e(X, \hat B) \\
+  v_{xy}' &= e(X, \hat Z_B).
+\end{align*}
+Then they run the following \ac{DBPK} with the participant as the prover and the 
+witness as the verifier:
+\begin{multline*}
+  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+    pid = g_T^{1/(k+cid)} \right\}.
+\end{multline*}
+
+\NewAlgorithm{\PRIVOsubmit}{Submit}
 
@@
         & cid\gets \Hash[\text{manifesto}], \\
-        & pid\gets \ACprf[_{k_P}][cid] \\
+        & pid\gets \ACprf[_{sk_P}][cid] \\
       W\colon & t_s'\gets \TSget
@@
       P\leftrightarrow W\colon &
-        \DBPK\mleft\{ (k_P) : \mright. \\
-        & \qquad pid = \ACprf[_{k_P}][cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
-      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
-        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
+        \DBPK\mleft\{ (sk_P) : \mright. \\
+        & \qquad pid = \ACprf[_{sk_P}][cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
+        \\
+      W\colon & wid\gets \ACprf[_{sk_W}][pid], \\
+        & wsig\gets \ACprf[_{sk_W}][wid, t_s, t_s', l] \\
       W\to P\colon & (wid, t_s, t_s', l, wsig)
@@
       \\[-2em]
-      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
       P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
+      W\colon & t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
       W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
       \text{where} \\
-        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
-        & \qquad wid = \ACprf[_{k_W}][pid], \\
-        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
-        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
+        & \pi_W = \SPK\mleft\{ (sk_W) : \mright. \\
+        & \qquad wid = \ACprf[_{sk_W}][pid], \\
+        & \qquad wsig = \ACprf[_{sk_W}][wid, t_s, t_s', l], \\
+        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][sk_W]]\mright\} \\
         & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
@@
       \text{where}\\
-        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
-        & \qquad pid = \ACprf[_{k_P}][cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
+        & \pi_P = \SPK\mleft\{ (sk_P) : \mright. \\
+        & \qquad pid = \ACprf[_{sk_P}][cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
+        \\
         & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
@@
     The organizer \(O\) broadcasts the manifesto.
-    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
+    The protester \(P\), witness \(W\) and their computations are as in 
+    \cref{fig:ProofFig}.
     Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).

### 2018-03-19 paper/protocol.tex
Minor clarifications, \hat -> \tilde

@@
 The protester acts as prover and the \ac{CA} as verifier while they perform the 
-following \ac{ZKPK} protocol: \(\PK[k,r][M = g^k Z^r]\).
+following \ac{ZKPK} protocol:
+\[
+  \PK[k,r][M = g^k Z^r].
+\]
 If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
@@
 \emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
-The witness simply should simply get a time-correlated random value from the 
+The witness should simply get a time-correlated random value from the 
 time-stamping service, \(t_s'\gets \TSget\).
@@
 \(r_1, r_2\gets \ZZ_q^*\) and let \(
-  \hat\sigma = (\hat A = A^{r_1},
-                \hat B = B^{r_1},
-                \hat Z_B = Z_B^{r_1},
+  \tilde\sigma = (\tilde A = A^{r_1},
+                  \tilde B = B^{r_1},
+                  \tilde Z_B = Z_B^{r_1},
                   \hat C = C^{r_1 r_2}).
-\) (It is not necessary to compute a new \(\hat\sigma\) more than once per 
+\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
 \(pid\).)
-The participant sends \((pid, \hat\sigma)\) to the witness.
+The participant sends \((pid, \tilde\sigma)\) to the witness.
 The witness verifies that
 \begin{align*}
-  \hat A &\neq 1 \\
-  e(g, \hat B) &= e(Y, \hat A) \\
-  e(g, \hat Z_B) &= e(Z, \hat B).
+  \tilde A          &\neq 1 \\
+  e(g, \tilde B)    &= e(Y, \tilde A) \\
+  e(g, \tilde Z_B)  &= e(Z, \tilde B).
 \end{align*}
@@
   v &= e(g, \hat C) \\
-  v_x &= e(X, \hat A) \\
-  v_{xy} &= e(X, \hat B) \\
-  v_{xy}' &= e(X, \hat Z_B).
+  v_x &= e(X, \tilde A) \\
+  v_{xy} &= e(X, \tilde B) \\
+  v_{xy}' &= e(X, \tilde Z_B).
 \end{align*}

### 2018-03-21 paper/protocol.tex
Defines r' in the DBPK
Writes up the DBPK, moves figures to earlier

@@
 
-\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
-The witness should simply get a time-correlated random value from the 
-time-stamping service, \(t_s'\gets \TSget\).
-(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
-start of the time interval of creation for the proof share.).
-
-\NewAlgorithm{\PRIVOparticipate}{Participate}
-\NewAlgorithm{\PRIVOwitness}{Witness}
-
-\emph{Participating: \(\pi\gets
-    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
-The participant reblinds its signature \(\sigma\) on its secret key: choose 
-\(r_1, r_2\gets \ZZ_q^*\) and let \(
-  \tilde\sigma = (\tilde A = A^{r_1},
-                  \tilde B = B^{r_1},
-                  \tilde Z_B = Z_B^{r_1},
-                  \hat C = C^{r_1 r_2}).
-\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
-\(pid\).)
-The participant sends \((pid, \tilde\sigma)\) to the witness.
-The witness verifies that
-\begin{align*}
-  \tilde A          &\neq 1 \\
-  e(g, \tilde B)    &= e(Y, \tilde A) \\
-  e(g, \tilde Z_B)  &= e(Z, \tilde B).
-\end{align*}
-Both the participant and the witness compute
-\begin{align*}
-  v &= e(g, \hat C) \\
-  v_x &= e(X, \tilde A) \\
-  v_{xy} &= e(X, \tilde B) \\
-  v_{xy}' &= e(X, \tilde Z_B).
-\end{align*}
-Then they run the following \ac{DBPK} with the participant as the prover and the 
-witness as the verifier:
-\begin{multline*}
-  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    pid = g_T^{1/(k+cid)} \right\}.
-\end{multline*}
-
-\NewAlgorithm{\PRIVOsubmit}{Submit}
-
-\subsection{Old}
-
-We will start by giving an overview of the protocol.
-We have a number of participants.
-We have a cothority who provide the storage in a decentralized manner.
-The cothority should consist of independent actors, preferably with conflicting 
-interests so that they will not collude.
-We have Alice the organizer and Bob the participant who are both protesters.
-We have the trustworthy journalist Jane who is present but not participating in 
-the protest.
-The protesters will witness each others participation proofs, \eg Alice will 
-witness Bob's proof and Bob will witness Alice's proof.
-The result of witnessing a proof is a proof share (essentially a witness 
-signature).
-Jane will also participate in witnessing the protesters' proofs.
-The witnessing is done through local interaction.
-As soon as Alice and Bob have departed from the protest they upload their proofs 
-(\ie all proof shares) to the cothority for indefinite storage.
-Since each proof consists of one proof share for each witness, each witness 
-could potentially upload the proof share themselves to the cothority.
-This would have the same effect but with added redundancy, in case Alice or Bob 
-cannot upload them themselves.
-
-We will now describe the protocol in more details.
-We will describe it in the same order as outlined above:
-starting with the construction of the participation proof (shares) and 
-submitting the proof shares to storage.
-Then we will conclude with how to verify the proofs and produce the 
-participation count.
-
-\subsection{Constructing the participation-proof shares}
-
-An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
-and an overview of the communication is given in \cref{fig:ProtocolOverview}.
-
 \begin{figure}
@@
         & wsig\gets \ACprf[_{sk_W}][wid, t_s, t_s', l] \\
-      W\to P\colon & (wid, t_s, t_s', l, wsig)
+      W\to P\colon & (wid, t_s', l, wsig)
       \\[-1em]
@@
 \end{figure}
+
+\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
+The witness should simply get a time-correlated random value from the 
+time-stamping service, \(t_s'\gets \TSget\).
+(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
+start of the time interval of creation for the proof share.).
+
+\NewAlgorithm{\PRIVOparticipate}{Participate}
+\NewAlgorithm{\PRIVOwitness}{Witness}
+
+\emph{Participating: \(\pi\gets
+    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
+In the participating phase the participant and the witness constructs the proof 
+share of the participant (\cref{fig:ProofFig}).
+The participant reblinds its signature \(\sigma\) on its secret key: choose 
+\(r_1, r_2\gets \ZZ_q^*\) and let \(
+  \tilde\sigma = (\tilde A = A^{r_1},
+                  \tilde B = B^{r_1},
+                  \tilde Z_B = Z_B^{r_1},
+                  \hat C = C^{r_1 r_2}).
+\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
+\(pid\).)
+The participant sends \((pid, \tilde\sigma)\) to the witness.
+The witness verifies that
+\begin{align*}
+  \tilde A          &\neq 1 \\
+  e(g, \tilde B)    &= e(Y, \tilde A) \\
+  e(g, \tilde Z_B)  &= e(Z, \tilde B).
+\end{align*}
+Both the participant and the witness compute
+\begin{align*}
+  v &= e(g, \hat C) \\
+  v_x &= e(X, \tilde A) \\
+  v_{xy} &= e(X, \tilde B) \\
+  v_{xy}' &= e(X, \tilde Z_B).
+\end{align*}
+Then they run the following \ac{DBPK} with the participant as the prover and the 
+witness as the verifier:
+\begin{multline*}
+  \mleftright
+  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+    pid = g_T^{1/(k+cid)} \right\}.
+\end{multline*}
+where \(r' = 1/r_2\).
+We can rewrite \(pid = g_T^{1/(k+cid)}\) as \(pid^k = g_T g_T^{-cid}\).
+Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
+be run as \iac{DBPK} and be repeated multiple times to achieve security).
+The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
+sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
+  pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+The witness replies with a challenge \(c\).
+The participant then computes
+\begin{align*}
+s_k &= -ck + r_k, \\
+s_r &= -cr + r_r, \\
+s_{r'} &= cr' + r_{r'}
+\end{align*}
+and sends them to the witness.
+The witness checks whether
+\begin{align*}
+  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
+    s_r}, \\
+  \mleft(g_T pid^{-cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} pid^{s_k}.
+\end{align*}
+If the proof succeeds the witness will compute \(wid\gets \ACprf[_{sk_W}][pid] = 
+  g_T^{1/(k_W+pid)}\) (as above) and in the same way \(wsig\gets 
+  \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]\).
+Then the witness returns \((wid, t_s', l, wsig)\) to the participant.
+Now both the participant and the witness have the tuple \(\pi = (pid, wid, t_s, 
+  t_s', l, wsig)\) which constitutes a proof share of the participant 
+(\cref{fig:ProofFig}).
+
+\NewAlgorithm{\PRIVOsubmit}{Submit}
+
+\emph{Submission: \(\pi'\gets \PRIVOsubmit[cid, pid, wid, t_s, t_s', l, 
+    wsig]\).}
+\dots
+
+\subsection{Old}
+
+We will start by giving an overview of the protocol.
+We have a number of participants.
+We have a cothority who provide the storage in a decentralized manner.
+The cothority should consist of independent actors, preferably with conflicting 
+interests so that they will not collude.
+We have Alice the organizer and Bob the participant who are both protesters.
+We have the trustworthy journalist Jane who is present but not participating in 
+the protest.
+The protesters will witness each others participation proofs, \eg Alice will 
+witness Bob's proof and Bob will witness Alice's proof.
+The result of witnessing a proof is a proof share (essentially a witness 
+signature).
+Jane will also participate in witnessing the protesters' proofs.
+The witnessing is done through local interaction.
+As soon as Alice and Bob have departed from the protest they upload their proofs 
+(\ie all proof shares) to the cothority for indefinite storage.
+Since each proof consists of one proof share for each witness, each witness 
+could potentially upload the proof share themselves to the cothority.
+This would have the same effect but with added redundancy, in case Alice or Bob 
+cannot upload them themselves.
+
+We will now describe the protocol in more details.
+We will describe it in the same order as outlined above:
+starting with the construction of the participation proof (shares) and 
+submitting the proof shares to storage.
+Then we will conclude with how to verify the proofs and produce the 
+participation count.
+
+\subsection{Constructing the participation-proof shares}
+
+An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
+and an overview of the communication is given in \cref{fig:ProtocolOverview}.
 

### 2018-03-21 paper/analysis-performance.tex
Splits analysis.tex into analysis-security and analysis-performance

--- 2018-02-28 paper/analysis.tex
@@
-\section{Security and privacy analysis}%
-\label{SecurityAnalysis}
-
-We note that Alice and Bob do not trust each other, for all they know one or the 
-other could be an agent of Eve the autocrat.
-\begin{itemize}
-  \item Eve the evil autocrat,
-  \item Rusuk the foreign nation state, and finally
-\end{itemize}
-
-\subsection{Forging new proofs}
-
-It follows from the digital signatures used that proofs are difficult to forge.
-
-\subsection{Reusing participation proofs}
-
-We consider two ways of reusing participation proofs:
-\begin{enumerate}
-  \item Alice and Bob can reuse old proofs by modifying the identifiers.
-  \item Eve can reuse proofs by creating a manifesto which yields the same 
-    identifier as Alice's protest, then try to create new nodes in the 
-    \ac{tposet} that matches the ones used in the old proofs.
-\end{enumerate}
-We will now estimate the difficulty of both types of attacks.
-
-\subsubsection{Finding second preimages}
-
-Eve (possibly with Rusuk's aid) wants to arrange a counter-protest.
-One way to get a higher participation count is to use the same identifier as 
-Alice's protest.
-Since the identifier for the protest is the hash value of the manifest, Eve 
-must find a second preimage for the hash function.
-
-% XXX Rephrase identifier problem as a game
-\begin{proposition}
-  Given \(x\) and \(H(x) = y\), the probability of finding an \(x'\) such that 
-  \(H(x') = y\) is \(\frac{1}{\lambda-1}\).
-\end{proposition}
-
-\begin{question}
-  What if we use a Merkle tree instead of only a hash, will that change the 
-  second preimage property?
-\end{question}
-
-Alice wants to arrange another protest against Eve.
-Her manifesto can remain the same, thus the protest identifier remains the 
-same.
-She wants to reuse some old proofs.
-The head value that are included in the proofs extend them too far back into 
-time.
-The digital signatures prevents her from changing them.
-So an alternative is to create nodes in the \ac{tposet} which has the same 
-hashes.
-
-\subsection{Spoofing locations}
-
-\subsubsection{Trust propagation for witnesses}
-
-\dots
-
-\subsection{Individual verifiability}
-
-Eve and Rusuk has an incentive to lower the confidence in the result.
-One way they can do this is to say that the result does not contain all 
-participation proofs.
-Statements such as this should be proved: provide a valid but missing proof.
-
 \section{Performance and implementation}
@@
 \) of processing.
-
-\subsection{Blockchain feasability}

### 2018-03-21 paper/analysis-security.tex
Splits analysis.tex into analysis-security and analysis-performance

--- 2018-02-28 paper/analysis.tex
@@
 Statements such as this should be proved: provide a valid but missing proof.
-
-\section{Performance and implementation}
-
-\subsection{Implementation on smartphones or smart-cards}
-Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}.
-However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them).
-While the limited processing power of many embarked systems has been a challenge, Idemix has been succesfully implemented to prove the posession of credentials on Java Cards by Bichsel et al.
-in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation « suitable for real life transactions »~\cite{IRMA} while maintaining security and privacy for its users.
-
-\subsection{Threshold of witnesses}
-
-Assume that every person has 5000 contacts in their contact 
-book~\cite{DifficultyOfPrivateContactDiscovery}.
-Then it would be reasonable to set the threshold of at least 6000 witnesses.
-According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
-signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
-\SI{2.66}{\giga\hertz} Core 2 processor.
-This yields \(
-  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-  \SI{48}{\second}.
-\) of processing.
-
-\subsection{Blockchain feasability}

### 2018-03-21 paper/analysis-security.tex
Moves old parts of protocol description to security analysis
These parts should be edited for integration.

@@
 \label{SecurityAnalysis}
+
+We will start by giving an overview of the protocol.
+We have a number of participants.
+We have a cothority who provide the storage in a decentralized manner.
+The cothority should consist of independent actors, preferably with conflicting 
+interests so that they will not collude.
+We have Alice the organizer and Bob the participant who are both protesters.
+We have the trustworthy journalist Jane who is present but not participating in 
+the protest.
+The protesters will witness each others participation proofs, \eg Alice will 
+witness Bob's proof and Bob will witness Alice's proof.
+The result of witnessing a proof is a proof share (essentially a witness 
+signature).
+Jane will also participate in witnessing the protesters' proofs.
+The witnessing is done through local interaction.
+As soon as Alice and Bob have departed from the protest they upload their proofs 
+(\ie all proof shares) to the cothority for indefinite storage.
+Since each proof consists of one proof share for each witness, each witness 
+could potentially upload the proof share themselves to the cothority.
+This would have the same effect but with added redundancy, in case Alice or Bob 
+cannot upload them themselves.
+
+We will now describe the protocol in more details.
+We will describe it in the same order as outlined above:
+starting with the construction of the participation proof (shares) and 
+submitting the proof shares to storage.
+Then we will conclude with how to verify the proofs and produce the 
+participation count.
+
+\subsection{Constructing the participation-proof shares}
+
+An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
+and an overview of the communication is given in \cref{fig:ProtocolOverview}.
+
+\subsubsection{Linkability and designated protest}
+
+\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
+can provide two participation proofs and thus be counted twice.
+That situation should be detectable.
+We can do this by ensuring that Alice cannot produce two valid proofs which
+are unlinkable.
+\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
+share) for another event.
+\Eg there might be a counter protest at the same time and place, these would 
+have the same spatial and temporal properties.
+To distinguish them, we also need to prove for which of these events that a 
+proof is designated.
+The idea is to construct a unique identifier for a protest.
+
+We will start with the latter.
+The identifier of the protest must be regulated, for the same reasons as for the 
+user identifiers --- otherwise a counter-protest can simply choose the same 
+protest identifier.
+As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
+root of what defines a protest.
+The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
+the hash value of the manifesto as identifier of the protest (cause).
+(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)
+
+To practically propagate this identifier to the protesters the organizer can 
+have a placard with a large QR code that either contains the entire manifesto or 
+at least links to a website hosting the manifesto.
+The user can scan this QR code with a protesting app which will automatically 
+fetch it, show it to the protester for approval and then compute the identifier 
+\(cid\).
+
+Next we need to consider the protesters' identifiers to prevent Sybil attacks.
+\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
+which allows anonymous authentication at most \(n\) times\footnote{%
+  Possibly there is another scheme that makes it non-interactive, \eg by 
+  \citet{Psignatures}, see issue \#27.
+}, where \(n = 1\) in our scenario.
+Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
+national identity-card (by assumption).
+She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
+anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
+
+\subsubsection{Temporal eligibility, created after start}
+
+Given the properties of the storage (in \cref{StorageProperties}), for 
+\cref{CreatedAfterStart}, each witness must include the hash value of an 
+existing block in the blockchain in each proof share (shown as \(t_s\) in 
+\cref{fig:ProofFig}).
+Then it is clear that the proof must have been created after that block (since 
+predicting such a value is hard).
+This value can either be provided to the witness by the protester or the witness 
+uses the value of the last known block.
+
+\subsubsection{Location proofs and spatial eligibility}
+
+According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
+(shares) spatially to the location, which would allow us to verify that they 
+were actually in that location.
+The role of the witnesses, \eg Jane, is to provide this property.
+Jane can do this by using a distance-bounding protocol to ensure that the secret 
+associated with Alice or Bob must be within limited physical distance.
+
+Alice will send her \(pid\) to Jane to start the witness protocol.
+Then they do the distance bounding \dots
+[See issue \#22 for the discussion.]
+If Jane is convinced that Alice's secret is within the desired proximity, she 
+will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
+send them to Alice.
+
+\subsubsection{Temporal eligibility, created before end}
+
+The proofs (shares) can be submitted to storage in two steps:
+first, committing them to the blockchain; second, to submit all the required 
+data.
+This will allow some time for computing all the required \ac{NIZK} proofs 
+(discussed in the following section).
+
+Given the properties of the storage system in \cref{StorageProperties}, 
+\cref{CreatedBeforeEnd} is straight-forward: once a proof share is created it 
+should be committed to the blockchain as soon as possible.
+Thus we can infer that a proof (or proof share) was created at the latest when 
+it was committed.
+
+We note that there are at least two entities who know each proof share, the 
+protester and the witness.
+Alice and Bob simply commit their proofs (\ie all proof shares of their 
+proofs) to the blockchain as soon as possible after they have participated in 
+the protest.
+The witnesses do the same, they commit all the proof shares that they helped 
+create.
+(Shown in \cref{fig:ProtocolOverview}.)
+
+\subsection{Verifying the participation count}
+
+There are three parts to verifying the participation count.
+First, we must verify the eligibility of each proof, \ie of all its shares.
+Second, we must count these valid proofs.
+Third, each protester must check that their proof is indeed registered so that 
+it can be counted.
+
+\subsubsection{Eligibility and universal verifiability}
+
+Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
+to count the valid proofs.
+To do this we must be able to verify the eligibility of a proof (\ie of all 
+its shares) and then count it if valid.
+To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
+and \(wsig\) are not just randomly generated numbers but they actually depend on 
+the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
+We will do this with \ac{NIZK} proofs.
+We note that these proofs are not needed until the verification step after the 
+protest.
+Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
+above) whereas their respective \ac{NIZK} proof can be computed and published 
+after the protest.
+
+Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
+and that she knows a signature by the identity authority on \(k_P\).
+\dots
+[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
+issue \#27 for discussion.]
+
+In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
+  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
+that the witness knows a signature by the identity authority on \(k_W\).
+With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
+eligibility, of the proof shares and thus also count them.
+
+\subsubsection{Individual verifiability and receipt freeness}
+
+The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
+an adversary from dropping participation proofs.
+Thus each protester must verify that their own proof is indeed included.
+This can be accomplished as follows.
+After Alice commited to her proof (share) in the blockchain, she stores the hash 
+of the block.
+At a later time, she can still verify that the block is indeed still there.
+At this point, this hash value is the only thing she must store for individual 
+verifiability.
+
+More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
+must remove her secret \ac{PRF} key, \(k_A\).
+With this key Grace can verify that Alice has submitted a proof by computing 
+\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).
+
+\subsection{Old}
 

### 2018-03-21 paper/protocol.tex
Adds comment on overview in figures in proto intro
Moves old parts of protocol description to security analysis
These parts should be edited for integration.

@@
 them as similar as possible.
+
+The join, participation and submission phases are illustrated in 
+\cref{fig:ProtocolOverview}.
+The participation proof share that will be constructed in the participation 
+phase is illustrated in \cref{fig:ProofFig}.
 
@@
       W\colon & t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
-      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
+      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_{wid, wsig}),\quad 
       \text{where} \\
-        & \pi_W = \SPK\mleft\{ (sk_W) : \mright. \\
+        & \pi_{wid, wsig} = \SPK\mleft\{ (sk_W) : \mright. \\
         & \qquad wid = \ACprf[_{sk_W}][pid], \\
@@
         & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
-      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
+      P\to S\colon & (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid}),\quad 
       \text{where}\\
-        & \pi_P = \SPK\mleft\{ (sk_P) : \mright. \\
+        & \pi_{pid} = \SPK\mleft\{ (sk_P) : \mright. \\
         & \qquad pid = \ACprf[_{sk_P}][cid], \\
@@
         \\
-        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
+        & \qquad\qquad (cid, pid, wid, t_s, t_s', l, wsig)
     \end{align*}
@@
 
-\emph{Submission: \(\pi'\gets \PRIVOsubmit[cid, pid, wid, t_s, t_s', l, 
+\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
     wsig]\).}
-\dots
+The participant should as soon as possible commit the proof-share data to the 
+time-stamping service and receive the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
+The remaining operations are not time critical.
+The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
+correctness of \(pid\).
+More specifically,
+\begin{multline*}
+  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
+    \begin{aligned}
+      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
+      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
+    \end{aligned} \\
+      (cid, pid, wid, t_s, t_s', l, wsig).
+\end{multline*}
+Finally, the participant uploads the tuple \[
+  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
+\] for permanent storage.
 
-\subsection{Old}
-
-We will start by giving an overview of the protocol.
-We have a number of participants.
-We have a cothority who provide the storage in a decentralized manner.
-The cothority should consist of independent actors, preferably with conflicting 
-interests so that they will not collude.
-We have Alice the organizer and Bob the participant who are both protesters.
-We have the trustworthy journalist Jane who is present but not participating in 
-the protest.
-The protesters will witness each others participation proofs, \eg Alice will 
-witness Bob's proof and Bob will witness Alice's proof.
-The result of witnessing a proof is a proof share (essentially a witness 
-signature).
-Jane will also participate in witnessing the protesters' proofs.
-The witnessing is done through local interaction.
-As soon as Alice and Bob have departed from the protest they upload their proofs 
-(\ie all proof shares) to the cothority for indefinite storage.
-Since each proof consists of one proof share for each witness, each witness 
-could potentially upload the proof share themselves to the cothority.
-This would have the same effect but with added redundancy, in case Alice or Bob 
-cannot upload them themselves.
-
-We will now describe the protocol in more details.
-We will describe it in the same order as outlined above:
-starting with the construction of the participation proof (shares) and 
-submitting the proof shares to storage.
-Then we will conclude with how to verify the proofs and produce the 
-participation count.
-
-\subsection{Constructing the participation-proof shares}
-
-An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
-and an overview of the communication is given in \cref{fig:ProtocolOverview}.
-
-\subsubsection{Linkability and designated protest}
-
-\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
-can provide two participation proofs and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
-\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
-share) for another event.
-\Eg there might be a counter protest at the same time and place, these would 
-have the same spatial and temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-The idea is to construct a unique identifier for a protest.
-
-We will start with the latter.
-The identifier of the protest must be regulated, for the same reasons as for the 
-user identifiers --- otherwise a counter-protest can simply choose the same 
-protest identifier.
-As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
-root of what defines a protest.
-The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
-the hash value of the manifesto as identifier of the protest (cause).
-(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)
-
-To practically propagate this identifier to the protesters the organizer can 
-have a placard with a large QR code that either contains the entire manifesto or 
-at least links to a website hosting the manifesto.
-The user can scan this QR code with a protesting app which will automatically 
-fetch it, show it to the protester for approval and then compute the identifier 
-\(cid\).
-
-Next we need to consider the protesters' identifiers to prevent Sybil attacks.
-\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
-which allows anonymous authentication at most \(n\) times\footnote{%
-  Possibly there is another scheme that makes it non-interactive, \eg by 
-  \citet{Psignatures}, see issue \#27.
-}, where \(n = 1\) in our scenario.
-Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
-national identity-card (by assumption).
-She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
-anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
-
-\subsubsection{Temporal eligibility, created after start}
-
-Given the properties of the storage (in \cref{StorageProperties}), for 
-\cref{CreatedAfterStart}, each witness must include the hash value of an 
-existing block in the blockchain in each proof share (shown as \(t_s\) in 
-\cref{fig:ProofFig}).
-Then it is clear that the proof must have been created after that block (since 
-predicting such a value is hard).
-This value can either be provided to the witness by the protester or the witness 
-uses the value of the last known block.
-
-\subsubsection{Location proofs and spatial eligibility}
-
-According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
-(shares) spatially to the location, which would allow us to verify that they 
-were actually in that location.
-The role of the witnesses, \eg Jane, is to provide this property.
-Jane can do this by using a distance-bounding protocol to ensure that the secret 
-associated with Alice or Bob must be within limited physical distance.
-
-Alice will send her \(pid\) to Jane to start the witness protocol.
-Then they do the distance bounding \dots
-[See issue \#22 for the discussion.]
-If Jane is convinced that Alice's secret is within the desired proximity, she 
-will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
-send them to Alice.
-
-\subsubsection{Temporal eligibility, created before end}
-
-The proofs (shares) can be submitted to storage in two steps:
-first, committing them to the blockchain; second, to submit all the required 
-data.
-This will allow some time for computing all the required \ac{NIZK} proofs 
-(discussed in the following section).
-
-Given the properties of the storage system in \cref{StorageProperties}, 
-\cref{CreatedBeforeEnd} is straight-forward: once a proof share is created it 
-should be committed to the blockchain as soon as possible.
-Thus we can infer that a proof (or proof share) was created at the latest when 
-it was committed.
-
-We note that there are at least two entities who know each proof share, the 
-protester and the witness.
-Alice and Bob simply commit their proofs (\ie all proof shares of their 
-proofs) to the blockchain as soon as possible after they have participated in 
-the protest.
-The witnesses do the same, they commit all the proof shares that they helped 
-create.
-(Shown in \cref{fig:ProtocolOverview}.)
-
-\subsection{Verifying the participation count}
-
-There are three parts to verifying the participation count.
-First, we must verify the eligibility of each proof, \ie of all its shares.
-Second, we must count these valid proofs.
-Third, each protester must check that their proof is indeed registered so that 
-it can be counted.
-
-\subsubsection{Eligibility and universal verifiability}
-
-Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
-to count the valid proofs.
-To do this we must be able to verify the eligibility of a proof (\ie of all 
-its shares) and then count it if valid.
-To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
-and \(wsig\) are not just randomly generated numbers but they actually depend on 
-the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
-We will do this with \ac{NIZK} proofs.
-We note that these proofs are not needed until the verification step after the 
-protest.
-Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
-above) whereas their respective \ac{NIZK} proof can be computed and published 
-after the protest.
-
-Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
-and that she knows a signature by the identity authority on \(k_P\).
-\dots
-[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
-issue \#27 for discussion.]
-
-In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
-  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
-that the witness knows a signature by the identity authority on \(k_W\).
-With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
-eligibility, of the proof shares and thus also count them.
-
-\subsubsection{Individual verifiability and receipt freeness}
-
-The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
-an adversary from dropping participation proofs.
-Thus each protester must verify that their own proof is indeed included.
-This can be accomplished as follows.
-After Alice commited to her proof (share) in the blockchain, she stores the hash 
-of the block.
-At a later time, she can still verify that the block is indeed still there.
-At this point, this hash value is the only thing she must store for individual 
-verifiability.
-
-More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
-must remove her secret \ac{PRF} key, \(k_A\).
-With this key Grace can verify that Alice has submitted a proof by computing 
-\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).
+\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][pid, wid, t_s, t_s', l, 
+    wsig]\).}
+The witness should, just as the participant, commit the proof-share data to the 
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, 
+  wsig]]\).
+Then, without any time requirements, the witness computes \iac{NIZK} proof 
+\(\pi_{wid, wsig}\) as follows:
+\begin{multline*}
+  \pi_{wid, wsig}\gets \SPK\left\{ (sk_W) : \right. \\
+    \begin{aligned}
+      wid &= \ACprf[_{sk_W}][pid] \quad \land \\
+      wsig &= \ACprf[_{sk_W}][wid, t_s, t_s', l] \quad \land \\
+      \sigma_W' &= \left. \ACblind[\ACsign[_{ssk}][sk_W]] \right\}
+    \end{aligned} \\
+      (pid, wid, t_s, t_s', l, wsig).
+\end{multline*}
+Finally, the witness uploads the tuple \[
+  (pid, wid, t_s, t_s', t_e', l, wsig, \pi_{wid, wsig})
+\] for permanent storage.

### 2018-03-21 paper/DB-anon-cred.tex

@@
 We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
-which is secure against \ac{DBIV}, \ac{DBMF}, \ac{DBDF} and \ac{DBDH}.
+which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and an impersonating 
+verifier (\ie public-key).
 It will not protect against terrorist fraud, although ideally this property should be desirable.
@@
 
-    \(\rho_0\rgets \Z_q, \rho_1\rgets \Z_q\)
+    \(\rho_0\rgets \ZZ_q, \rho_1\rgets \ZZ_q\)
     &

### 2018-03-21 paper/SystemModel.tex

@@
 \begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in \Z_{2^\lambda}\) is the identifier of the cause of the protest,
-  \(t = \interval{t_s}{t_e}\subseteq \R\) is a time interval and \(l = N_\epsilon(x, y)\subseteq \R^2\) is the location (an \(\epsilon\)-neighbourhood of \((x,y)\)).
+  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in 
+    \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
+  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l = 
+    N_\epsilon(x, y)\subseteq \RR^2\) is the location (an 
+  \(\epsilon\)-neighbourhood of \((x,y)\)).
   A \emph{protest} is a set of subprotests sharing the same \(id\).
@@
       j = cid, s(p_{i,j})\geq \theta \right\}
-  \] for some strength function \(s\colon \powerset(W)\to \R_+\) and a threshold 
-  \(\theta\).
+  \] for some strength function \(s\colon \powerset(W)\to \RR_+\) and a 
+  threshold \(\theta\).
 \end{definition}

### 2018-03-21 paper/protocol.tex

--- 2018-03-21 paper/protocol.tex
@@
 
-\emph{Submission: \(\pi'\gets \PRIVOsubmit[cid, pid, wid, t_s, t_s', l, 
+\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
     wsig]\).}
-\dots
+The participant should as soon as possible commit the proof-share data to the 
+time-stamping service and receive the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
+The remaining operations are not time critical.
+The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
+correctness of \(pid\).
+More specifically,
+\begin{multline*}
+  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
+    \begin{aligned}
+      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
+      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
+    \end{aligned} \\
+      (cid, pid, wid, t_s, t_s', l, wsig).
+\end{multline*}
+Finally, the participant uploads the tuple \[
+  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
+\] for permanent storage.
+
+\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][pid, wid, t_s, t_s', l, 
+    wsig]\).}
+The witness should, just as the participant, commit the proof-share data to the 
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, 
+  wsig]]\).
+Then, without any time requirements, the witness computes \iac{NIZK} proof 
+\(\pi_{wid, wsig}\) as follows:
+\begin{multline*}
+  \pi_{wid, wsig}\gets \SPK\left\{ (sk_W) : \right. \\
+    \begin{aligned}
+      wid &= \ACprf[_{sk_W}][pid] \quad \land \\
+      wsig &= \ACprf[_{sk_W}][wid, t_s, t_s', l] \quad \land \\
+      \sigma_W' &= \left. \ACblind[\ACsign[_{ssk}][sk_W]] \right\}
+    \end{aligned} \\
+      (pid, wid, t_s, t_s', l, wsig).
+\end{multline*}
+Finally, the witness uploads the tuple \[
+  (pid, wid, t_s, t_s', t_e', l, wsig, \pi_{wid, wsig})
+\] for permanent storage.
 

### 2018-03-21 paper/protocol.tex
Removes ref to DBPK eqn, adds SPK explicitly

--- 2018-03-21 paper/protocol.tex
@@
 witness as the verifier:
-\begin{multline*}
-  \mleftright
-  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    pid = g_T^{1/(k+cid)} \right\}.
+\begin{multline*}\label{eq:DBPK}
+  \DBPK\left\{(k, r, r') :
+    v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \quad \land \right. \\
+      \left. pid = g_T^{1/(k+cid)} \right\}.
 \end{multline*}
@@
 \end{align*}
-If the proof succeeds the witness will compute \(wid\gets \ACprf[_{sk_W}][pid] = 
-  g_T^{1/(k_W+pid)}\) (as above) and in the same way \(wsig\gets 
-  \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]\).
-Then the witness returns \((wid, t_s', l, wsig)\) to the participant.
-Now both the participant and the witness have the tuple \(\pi = (pid, wid, t_s, 
-  t_s', l, wsig)\) which constitutes a proof share of the participant 
-(\cref{fig:ProofFig}).
+If the proof succeeds the witness will compute \(
+  wid\gets \ACprf[_{sk_W}][pid] = g_T^{1/(k_W+pid)}
+\) (as above) and in the same way \(
+  wsig\gets \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]
+\).
+Then the witness returns \(
+  (wid, t_s', l, wsig)
+\) to the participant.
+Now both the participant and the witness have the tuple \(
+  \pi = (pid, wid, t_s, t_s', l, wsig)
+\) which constitutes a proof share of the participant (\cref{fig:ProofFig}).
 
@@
 The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
-correctness of \(pid\).
+correctness of \(pid\), \ie we simply use the Fiat-Shamir heuristic to turn the 
+\ac{DBPK} above into \iac{NIZK} proof.
 More specifically,
 \begin{multline*}
-  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
-    \begin{aligned}
-      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
-      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
-    \end{aligned} \\
+  \pi_{pid}\gets \SPK\left\{(k, r, r') : \phantom{g_T^{1/(k+cid)}}\right. \\
+      v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+      pid = \left. g_T^{1/(k+cid)} \right\} \\
         (cid, pid, wid, t_s, t_s', l, wsig).

### 2018-03-21 paper/TimeStamp.tex

@@
 
-With these building blocks we can ensure that a message \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
+With these building blocks we can ensure that a message \(m\) was created within 
+the time interval \(\intrvl{t_0}{t_1}\).
 After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
@@
 
-Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
+Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created 
+within the time interval \(\intrvl{t_0}{t_1}\).
 The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).

### 2018-05-22 paper/intro.tex
Minor edits in intro (only labels in other files)

@@
 
-\emph{Context.} Consider the following illustrative scenario in which Alice is an activist that organizes a protest against the current regime leader Grace in some location(s).
+\emph{Context.} Consider the following illustrative scenario.
+Alice is an activist that organizes a protest in some location(s) against the 
+current regime leader Grace.
 On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
@@
 Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
-In this case, we are left with two options: either we trust Alice or Grace or we have to be able to verify their claims.
+In this case, we are left with two options: either we trust Alice or Grace (or 
+another third party), or we have to be able to verify their claims ourselves.
 In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
@@
 
-In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
-%Seb: above, we should put the reference to the Schnorr protocol 
-In addition, this allows us to form distance-bounding anonymous credentials.
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
+for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our adaptation fulfils all the requirements for modern \ac{DB} protocols, 
+including \ac{DBDH} (which was an attach against Brands-Chaum).
+More importantly, it is public key (\ie handles malicious, impersonating 
+verifiers), fulfils \ac{DBTF} and provides a \ac{PK} for discrete logarithms.
+The latter allows us to replace the use of the plain Schnorr protocol in the 
+\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
+knowledge, the first to provide \ac{DB} anonymous credentials.
 
-\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized (see \cref{assumptions} for more detailed descriptions). 
-In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
+\emph{Limitations and assumptions.} Some of the assumptions that are required 
+for implementing our proposition are not yet realized (see \cref{assumptions} 
+for more detailed descriptions). In particular, not all (or even many) 
+protesters, especially in countries with oppressive regimes, currently possess 
+smartphones.
 In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
 %Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
-In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.
+In this case, it does not make sense to verify any pro-government protests in 
+which Grace's authoritarian regime wants to organize a pro-regime protest to 
+demonstrate its wide support, 
+\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+Finally, achieving distance-bounding protocols on smartphones is currently not 
+feasible within a meaningful range of distance needed for our scenario.
+They lack the required hardware to do the distance bounding fast enough.
 
-However, we believe that some assumptions might become sufficiently realistic in the near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\eg Estonia and Germany)
-In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available can already enable proofs of proximity with a range of 200 meters.
+However, we believe that some assumptions might become sufficiently realistic in 
+the near future, due to the smartphone penetration being on the rise and the 
+increased digitalization and government-issued credentials available in some 
+countries already now (\eg Estonia, Germany and Sweden).
+In addition, the distance-bounding 
+chips\footnote{\url{https://www.3db-access.com}} currently available can already 
+enable proofs of proximity for any range of up to 200 meters.
 One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
@@
 \PRIVO achieves privacy, but not receipt freeness.
-This means that there is a way for Grace to efficiently verify that Alice has to the participated.
+This means that there is a way for Grace to efficiently verify that Alice has 
+participated.
 However, this requires Grace to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
@@
 %Seb: to do, update the outline
-\emph{Outline.} The paper is organized as follows. 
-First, we define and formalize the notion of protest and discuss how is relationship with electronic voting in \cref{SystemModel}.  
-We then present the desired security properties for such a system and subsequently discuss related work in terms of these properties. 
-We give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier.
-\PRIVO, the protocol constructed from the building blocks, is presented next and we analyze its security and privacy as well as performance and implementation issues.
-We conclude with a discussion.
+\emph{Outline.} The paper is organized as follows. First, we define and 
+formalize the notion of protest and discuss its relationship with electronic 
+voting (\cref{SystemModel}).  We then present the desired security properties 
+for such a system (\cref{Properties}) and subsequently discuss related work in 
+terms of these properties (\cref{RelatedWork}). We give the relevant background 
+on the building blocks of our solution, including our proposal for 
+distance-bounding anonymous credentials that cope with a malicious 
+(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
+constructed from the building blocks, is presented next (\cref{Protocol}) and we 
+analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
+performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
+with a discussion.

### 2018-05-22 paper/LocationProofs.tex
Transforms comments in code to visible comments

@@
 Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-%Seb: to do add the corresponding reference
+\seb{to do add the corresponding reference}
 However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 

### 2018-05-22 paper/intro.tex
Transforms comments in code to visible comments

--- 2018-02-28 paper/intro.tex
@@
 In addition, they also lack verifiability.
-%as everyone has to trust the entity responsible for performing the counting.
-%Sonja says: I commented this out as it doesn't apply to all.
-Sometimes you have to trust the data but can count yourself (pictures) or can even take pictures yourself but that's not really verifiability either.
 
@@
 Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
-%Sonja says: what actions do we refer to here?
+\sonja{what actions do we refer to here?}
 
-%Seb: to do complete the contributions
+\seb{to do complete the contributions}
 \emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
@@
 In contrast to the traditional assumption of honest (or at most honest-but-curious) verifiers in distance-bounding algorithms, we propose a way to turn the Schnorr protocol into a distance-bounding protocol resistant against a malicious verifier\footnote{The particular adversary we have in mind here, a verifier impersonating a prover, is actually implicitly covered in public-key distance-bounding protocols such as ProProx~\cite{ProProx}, even though they do not explicitly consider malicious verifiers.}.
-%Seb: above, we should put the reference to the Schnorr protocol 
+\seb{above, we should put the reference to the Schnorr protocol}
 In addition, this allows us to form distance-bounding anonymous credentials.
@@
 In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
-%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
+\seb{maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)}
 In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to organize a pro-regime protest to demonstrate its wide support~\cite[e.g.][]{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
@@
 
-%Seb: to do, update the outline
+\seb{to do, update the outline}
 \emph{Outline.} The paper is organized as follows. 

### 2018-05-22 paper/properties.tex
Transforms comments in code to visible comments

@@
 On our setting, we have three potential adversaries: Alice, Eve and Mallory.
-%Seb: I changed the name of Grace to Eve to be consistent with the introduction
+\seb{I changed the name of Grace to Eve to be consistent with the introduction}
 Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
@@
 Thus, the objective of Mallory will also be to either increase or decrease the count.
-%Seb: we have to justify why Mallory is not captured either by Alice or Eve
+\seb{we have to justify why Mallory is not captured either by Alice or Eve}
 In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
@@
 
-%Seb: to complete
+\seb{to complete}
 \subsubsection{Temporal eligibility}
@@
 In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
-%Seb: I think this sentence should be clarified
+\seb{I think this sentence should be clarified}
 (Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)
@@
 We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
-%Seb: suggestion maybe we should put the following part in the discussion
+\seb{suggestion maybe we should put the following part in the discussion}
 However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
@@
 In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
-%Sonja says: I'm confused: can we or can we not provide this?
-%Seb: I agree with Sonja, it is not clear whether we achieve it or not
+\sonja{I'm confused: can we or can we not provide this?}
+\seb{I agree with Sonja, it is not clear whether we achieve it or not}
 

### 2018-05-22 paper/DistanceBounding.tex

@@
 \begin{itemize}
-    % XXX Describe the DB frauds in more detail, i.e. explain them.
-  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
+    far-away honest prover.
   \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
@@
 \end{itemize}
+\daniel{Describe the DB frauds in more detail, i.e. explain them.}
 There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
@@
 The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
-%Seb: I have created the acronym DBPK in bibsp.sty

### 2018-05-22 paper/RelatedWork.tex
coincoin

@@
 \label{RelatedWork}
+
+\subsection{Crowd counting methods}
 
@@
 However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
-%Seb: maybe we should also give information about the privacy level reached by this different method
+\seb{maybe we should also give information about the privacy level reached by 
+  this different method}
 
@@
 Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
-%Seb: what are the meaning of the choice of density estimates, it is a way to specify an apriori assumption about the density of the crowd or to choose between a min, average, max estimates?
+\seb{what are the meaning of the choice of density estimates, it is a way to 
+  specify an apriori assumption about the density of the crowd or to choose 
+  between a min, average, max estimates?}
 This is similar to the method usually used by police (\eg for the protests in Seoul):
@@
 honest participants.
+
+\input{LocationProofs.tex}

### 2018-05-22 paper/SystemModel.tex

@@
 \end{definition}
-%Sonja asks: do the same pair of people (witness-protester) get the
-%same wid on a different protest? The pid is unique for protester-cid
-%pair thus the id of a protester at a particular protest. Pid is thus
-%derived from the protester id (which has no term) and the protest id
-%(cid)? In analogy, wid is derived from pid (and thus cid) of both
-%participants, protesters i and j, say, where i witnesses j at cid and
-%simultaneously symmetrically j witnesses i?
-%Using wid and w is confusing since we changed the terminology to use
-%proof shares instead of the previous witness (as in testimony, not
-%person). wid sounds like it would be the id of the witness person,
-%pid sounds like it would be the id of the protester being witnessed,
-%we have defined neither and they might not be needed, but it is
-%confusing to read.
+\sonja{do the same pair of people (witness-protester) get the
+same wid on a different protest? The pid is unique for protester-cid
+pair thus the id of a protester at a particular protest. Pid is thus
+derived from the protester id (which has no term) and the protest id
+(cid)? In analogy, wid is derived from pid (and thus cid) of both
+participants, protesters i and j, say, where i witnesses j at cid and
+simultaneously symmetrically j witnesses i?
+Using wid and w is confusing since we changed the terminology to use
+proof shares instead of the previous witness (as in testimony, not
+person). wid sounds like it would be the id of the witness person,
+pid sounds like it would be the id of the protester being witnessed,
+we have defined neither and they might not be needed, but it is
+confusing to read.}
 

### 2018-05-22 paper/intro.tex

--- 2018-05-22 paper/intro.tex
@@
 In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
-%Seb: maybe to prevent the above issue, we could require the individual to generate his secret key and only use the authority to obtain a certification on his public key (in the spirit of blind signature)
+\seb{maybe to prevent the above issue, we could require the individual to 
+  generate his secret key and only use the authority to obtain a certification 
+  on his public key (in the spirit of blind signature)}
 In this case, it does not make sense to verify any pro-government protests in 
@@
 
-%Seb: to do, update the outline
+\seb{to do, update the outline}
+\daniel{done?}
 \emph{Outline.} The paper is organized as follows. First, we define and 

### 2018-05-22 paper/SystemModel.tex
Edits system model

@@
 Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Note that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time, to deploy enough personnel for crowd-control.}.
-Formally, we define a protest as an event that is uniquely identified by its cause (\(id\) below), its time interval (\(t\)) and its location (area \(l\)).
+
+\NewVariable{\cid}{cid}
+
+Formally, we define a protest as an event that is uniquely identified by its 
+cause (\(\cid\) below), its time interval (\(t\)) and its location (area \(l\)).
 More specifically, we will use the following definition.
@@
 \begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((cid, t, l)\) in which \(cid\in 
+  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
     \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
-  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l = 
-    N_\epsilon(x, y)\subseteq \RR^2\) is the location (an 
-  \(\epsilon\)-neighbourhood of \((x,y)\)).
-  A \emph{protest} is a set of subprotests sharing the same \(id\).
+  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l \subseteq 
+    \RR^2\) is the location.
+  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
 \end{definition}
@@
 Each subprotest will then be captured by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
-Similarly for march, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.
+Similarly for marches, the marching path can be divided into subprotests with 
+locations (or areas) that slightly overlap.
 
-\emph{Formalizing the notion of crowd estimation.} Each participant who wants to be counted must submit a participation proof.
+\emph{Formalizing the notion of crowd estimation.} Each participant who wants to 
+be counted must submit a \emph{participation proof}.
 The proof must be associated with the protest (\ie its identifier \(cid\)), time and location must coincide with any of its subprotests.
 
-We use other participants, that we called \emph{witnesses} to associate the proof to the location by creating a proof 
-share.
-A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
+We use other participants, that we called \emph{witnesses} to associate the 
+proof to the location by creating a \emph{proof share}.
+A witness is only allowed to create one proof share per protester to avoid the 
+risk of inflation.
 The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.
 
+\NewVariable{\pid}{pid}
+\NewVariable{\wid}{wid}
+
 \begin{definition}[Participation-proof share]
-  A \emph{participation-proof share} \(w = (pid, cid, t, l, wid)\) is a tuple 
-  where
-  \(cid, t, l\) are as in \cref{DefProtest},
-  \(pid\) is unique for a protester--\(cid\) pair, and
-  \(wid\) is unique for a witness--protester pair.
+  A \emph{participation-proof share} \((\pid, \cid, t, l, \wid)\) is a tuple 
+  where:
+  \(\cid, t, l\) are as in \cref{DefProtest};
+  \(\pid\) is a function of the protester's identity and \(\cid\); and
+  \(\wid\) is a function of the witness' identity and 
+  \(\pid\).
   We let \(W\) be the set of all proof shares.
@@
 confusing to read.}
+\daniel{I made some minor changes, any better?}
 
@@
     p_{i, j} =
-    \left\{ (pid, cid, t, l, wid)\in W \mid \right. \\
-    \left. pid = i, cid = j,
+    \left\{ (\pid, \cid, t, l, \wid)\in W \mid \right. \\
+    \left. \pid = i, \cid = j,
     t \subseteq t_j, l\subseteq l_j \right\},
@@
 \begin{definition}[Participation count]
-  We define the \emph{participation count} of a protest \(cid\) as the cardinality \(|P_{cid}^{s,\theta}|\) of the set of participation proofs \[
-    P_{cid}^{s,\theta} = \left\{ p_{i,j} \mid
-      j = cid, s(p_{i,j})\geq \theta \right\}
+  We define the \emph{participation count} of a protest \(\cid\) as the 
+  cardinality \(|P_{\cid}^{s,\theta}|\) of the set of participation proofs \[
+    P_{\cid}^{s,\theta} = \left\{ p_{i,j} \mid
+      j = \cid, s(p_{i,j})\geq \theta \right\}
   \] for some strength function \(s\colon \powerset(W)\to \RR_+\) and a 
@@
 One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
+Another example would be to return the number of proof shares issued by trusted 
+witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
+trusted witness.
 
-\emph{System model and physical assumptions.} \label{assumptions}
+\emph{System model and physical assumptions.}\label{assumptions}
 Throughout this text, when we refer to a participant, say Alice, we actually 
@@
 some logically centralized certificate authority.
-\Eg that we can use the cryptographic keys stored in the chip of the national 
-identity card or passport.
+\Eg that we can use the cryptographic keys of any national electronic identity 
+system, identity card or passport.
 We need this to prevent Sybil attacks~\cite{SybilAttack}.
 
-In practical terms, participants witness each other's particpation
+In practical terms, participants witness each other's participation
 using their smartphones (or similar devices) running the protocol described in
-\cref{protocol} and uploading their testimony (\ie proof shares) to the blockchain after the protest. 
-During the protest the devices are computationally limited by their 
-batteries and need connectivity at to each other but no connection to
-any global network or the Internet is necessary. Before and
-after the protest, we assume that the devices have Internet  
-connections and are not computationally limited by any battery.
+\cref{protocol} and uploading their testimony (\ie proof shares) to a blockchain 
+after the protest. During the protest the devices are computationally limited by 
+their batteries and need local connectivity to each other but no connection to
+any global network such as the Internet is necessary. Before and
+after the protest, we assume that the devices have global connectivity, \ie 
+Internet  connections, and are not computationally limited by any battery.
 

### 2018-05-22 paper/properties.tex
Edits beginning of desired properties

@@
 
-On our setting, we have three potential adversaries: Alice, Eve and Mallory.
+In our setting, we have three potential adversaries: Alice, Grace and Mallory.
 \seb{I changed the name of Grace to Eve to be consistent with the introduction}
+\daniel{Changed back to Grace since that's what's in the intro now.}
 Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
-In contrast, the aim of Eve, the totalitarian dictator, is to decrease the count but also additionally to deanonymize some of the participants in order to arrest them or convince them to change their minds.
-Finally, Mallory represents another nation state and has some interest in affecting the stability of Eve's regime, for Mallory's own 
-gain, thus supporting either Eve or Alice as he see fits.
+In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
+count but also additionally to deanonymize some of the participants in order to 
+arrest them or forcefully convince them to change their minds.
+Finally, Mallory represents another nation state and has some interest in 
+affecting the stability of Grace's regime, for Mallory's own gain, thus 
+supporting either Grace or Alice as she see fits.
 Thus, the objective of Mallory will also be to either increase or decrease the count.
-\seb{we have to justify why Mallory is not captured either by Alice or Eve}
-In addition, Mallory could also have simply for objective to cause a denial-of-service attack on the architecture of \PRIVO.
-In the following two subsections, we will now formally define some security properties specifying the computational effort needed by the adversaries to succeed.
-
-Note that in general terms, protesting is very similar to petitions, which in turn are similar to voting: all three situations correspond to many individuals expressing their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
-To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.
+\seb{we have to justify why Mallory is not captured either by Alice or Grace}
+In addition, Mallory could also have simply as her objective to cause a 
+denial-of-service attack on the architecture of \PRIVO.
+In the following two subsections, we will formally define some security 
+properties specifying the computational effort needed by the adversaries to 
+succeed.
 
@@
 \label{Verifiability}
+
+Note that in general terms, protesting is very similar to petitions, which in 
+turn are similar to voting: all three situations correspond to many individuals 
+expressing their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
+To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.
 
@@
 \end{description}
-We translate the votes into \emph{proofs of participation}.
+We translate the votes into \emph{participation proofs}.
 Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
@@
 \begin{requirements}[V]
-  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that it has not been counted before.
+  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each 
+    participation proof provides temporal and spatial eligibility and that only 
+    one participation proof is counted per individual.
     \begin{requirements}

### 2018-05-23 paper/conclusions.tex
Edits receipt freeness

@@
-\section{Conclusions}
+\section{Conclusions}%
+\label{Conclusions}
 
@@
 some assumptions become more realistic.
+
+When it comes to receipt freeness, our construction does not allow it.
+The very property that prevents Alice from cheating by creating \(\pid, \pid'\), 
+such that \(\pid \neq \pid'\), is the property that allows Grace to verify 
+Alice's participation proof.
+If Grace can perform computations using Alice's key, Grace can input the 
+\(\cid\) of interest and see if the resulting \(\pid\) is available on the 
+blockchain.
+To mitigate this situation, Alice could delete her key, in which case she cannot 
+participate in any future protest.

### 2018-05-23 paper/properties.tex
Edits receipt freeness

@@
 \begin{requirements}[V]
-  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each 
-    participation proof provides temporal and spatial eligibility and that only 
-    one participation proof is counted per individual.
+  \item\label{EligibilityVerif} \emph{Eligibility}:
+    anyone can verify that each participation proof provides temporal and 
+    spatial eligibility and that only one participation proof is counted per 
+    individual.
     \begin{requirements}
-    \item \emph{Temporal eligibility}:%
-      \label{CreatedAfterStart} prove that the proof was created after the start of the protest and
+    \item\label{CreatedAfterStart} \emph{Temporal eligibility}:
+      prove that the proof was created after the start of the protest and
       %\label{CreatedBeforeEnd} prove that the proof was created 
       before the end of the protest.
-    \item \emph{Spatial eligibility}
-      \label{SpatiallyRelated} prove that the proof is spatially related to the physical location or journey of the protest.
-    \item \emph{One-proof-per-person}:%
-      \label{CountOnce} prove that no individual can be counted more than once for a particular protest.
-    \item \emph{Designated event}:%
-      \label{DesignatedEvent} prove that the proof is designated for the protest.
+    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
+      prove that the proof is spatially related to the physical location or 
+      journey of the protest.
+    \item\label{CountOnce} \emph{One-proof-per-person}:
+      prove that no individual can be counted more than once for a particular 
+      protest.
+    \item\label{DesignatedEvent} \emph{Designated event}:
+      prove that the proof is designated for the protest.
     \end{requirements}
 
-  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
-  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that their participation proof is included in the global count.
+  \item\label{UniversalVerif} \emph{Universal verifiability}:
+    anyone can verify that the result obtained match the submitted participation 
+    proofs.
+
+  \item\label{IndividualVerif} \emph{Individual verifiability}:
+    each participant can verify that their participation proof is included in 
+    the global count.
 \end{requirements}
-
-We will now discuss these properties in more details focusing in particular to the one related specifically to the protest.
-
-\seb{to complete}
-\subsubsection{Temporal eligibility}
-
-\begin{definition}[Forging temporal eligibility]
-  \dots
-\end{definition}
-
-\subsubsection{Spatial eligibility}
-
-\begin{definition}[Forging spatial eligibility]
-  \dots
-\end{definition}
-
-\subsubsection{Linkability and designated protest}
-
-\dots
-
-\subsubsection{Individual and universal verifiability}
-
-\dots
 
@@
 As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
-In particular our objective is that as long as Alice can conceal her identity at the demonstration and escape without arrest, her support is recorded in the data without her privacy being violated.
+In particular, our objective is that as long as Alice can conceal her identity 
+at the demonstration and escape without arrest, her support is recorded in the 
+data without her privacy being violated.
 \seb{I think this sentence should be clarified}
-(Following this line of thinking, it can actually be beneficial for the privacy of the protesters to mix with the participants of any counter-protests --- since the counts will still be correct.)
 
 In voting protocols, there are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{requirements}[P]
-\item\label{VotePrivacy} \emph{Vote privacy}: the voting does not reveal any individual vote.
-\item\label{ReceiptFreeness} \emph{Receipt freeness}: the voting system does not provide any data that can be used as a proof of how the voter voted.
-\item\label{CoercionResistance} \emph{Coercion resistance}: a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
-\end{requirements}
+\begin{description}
+\item[Vote privacy:] the voting does not reveal any individual vote.
+\item\label[Receipt freeness:] the voting system does not provide any data that 
+  can be used as a proof of how the voter voted.
+\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the 
+  vote was cast in any particular way.
+\end{description}
+\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion 
+resistance implies receipt freeness, which in turn implies vote privacy.
+Coercion resistance is probably not possible to achieve for protests:
+\eg Grace can simply physically bring Alice to a protest against her will.
 
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that \cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies \cref{VotePrivacy}. 
-\Cref{CoercionResistance} is probably not possible to achieve for protests:
-\eg Grace can simply physically bring Alice to a protest against her will.
-This leaves us with \cref{ReceiptFreeness,VotePrivacy}.
+In essence, receipt freeness means that upon completing the protocol, Grace 
+cannot link Alice to Alice's participation proof --- even if she were to 
+compromise Alice's device or Alice collaborates with Grace.
+As we will see, if Grace gets Alice's device, she can re-do the computations on 
+the same inputs.
+Since, in our case, the algorithms are deterministic and collisions are 
+negligible she will get the same result and can thus conclude that Alice is 
+indeed the one she is looking for.
+Thus we cannot provide receipt freeness.
+(See \cref{Conclusions} for further discussion.)
 

### 2018-05-23 paper/conclusions.tex
Adds discussion: cred renewal, deployment (fixes #86)

@@
 participate in any future protest.
+
+As implied by the last statement, there is the problem of renewing credentials.
+As with all identity cards, passports \etc, they have a limited lifetime and 
+must be renewed at regular intervals.
+The rate at which Alice is allowed to renew her credentials affects to what 
+extent she can perform Sybil attacks.
+
+Currently, the only problem preventing wide deployment is the lacking hardware 
+in smartphones.
+However, due to the rapid development of \enquote{smart} solutions, we believe 
+this is only a matter of time.
+\Eg mobile payments and public transport tickets that can be used over \ac{NFC} 
+will eventually require \iac{DB} chip.
+Without \ac{DB} for these applications, the user must manually confirm on the 
+screen to prevent attacks.
+We believe that the drive for increased usability will replace this type of 
+confirmation by distance bounding.
+
+The deployment of the needed credentials should not be a problem either.
+There are already countries where national \ac{eID} systems are widely deployed.
+The speed of adoption will depend on the architecture of these systems.
+For instance, the system used in Sweden, BankID, is implemented in software and 
+can thus be easily upgraded to include the anonymous credentials we need.
+As for coverage of the population: more than \SI{95}{\%} of people in the ages 
+21--50 uses BankID, it is \SI{88}{\%} for ages 51--60 and \SI{76}{\%} for ages 
+61--70\footnote{%
+  Official statistics, in Swedish:
+  \url{https://www.bankid.com/assets/bankid/stats/2018/statistik-2018-04.pdf}.
+}.
+
+While the deployment of the necessary technologies are not yet available in 
+authoritarian regimes, they are in several democracies.
+We believe that it as important to implement systems such as ours to prevent any 
+democracy of slipping down the slope towards dictatorship.

### 2018-05-23 paper/properties.tex
Finishes editing of properties

@@
 
-We note that we cannot actually improve the privacy of participating protesters during the protest: if Alice is caught during a protest or other crowd-counting mechanisms based on photographic or video evidence are used to identify Alice, there is nothing we can do.
-\seb{suggestion maybe we should put the following part in the discussion}
-However, in \PRIVO, we aim at verifiable participation count that does not add any threats to the participants' privacy. 
-For instance, if there are counter-protests in the \emph{same location at the same time}, Alice could even blend into another crowd and argue that she participated in a different protest than she actually did --- and the counts would still be correct afterwards.
-However, even if there is only one protest and she is not caught in the act, then using our proposed mechanism should not incur any additional risk.
-Thus we need at least participation-proof privacy but receipt freeness is also desired.
-In essence, this means that upon completing the protocol, Eve cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device.
-\sonja{I'm confused: can we or can we not provide this?}
-\seb{I agree with Sonja, it is not clear whether we achieve it or not}
-
-\subsubsection{Participation-proof privacy}
-
-\begin{definition}[Proof indistinguishability]
-  Adversary chooses two messages \(m_0, m_1\) and gives them to the challenger.
-  Challenger uniformly randomly selects \(b\rgets \bin\) and runs \(c_b \gets 
-    PRF_k(m_0), c_{1-b} \gets PRF_k(m_1)\).
-  The challenger gives \(c_0, c_1\) to adversary.
-  If the adversary outputs \(b' = b\) she wins.
-  (The property should be similar to key privacy~\cite{KeyPrivacy}.)
-\end{definition}
-
-\subsubsection{Receipt freeness}
-
-\begin{definition}[Receipt freeness/deniability]
-  Adversary gets oracle access to the user?
-  User provides a witness?
-\end{definition}
+This leaves us with what should correspond to vote privacy.
+We need unlinkability between Alice's identity and Alice's participation proof.
+Given a participation proof, Grace will not be able to tell if it belongs to 
+Alice or Bob.
+This is stronger than vote privacy, where Grace may know that Alice voted but 
+not what she voted, whereas here she may not know whether Alice \enquote{voted} 
+or not.
+Thus participants and non-participants must be indistinguishable.
+As this is quite difficult to achieve, we settle for something slightly weaker:
+\begin{requirements}[P]
+\item\label{ProtestInd} Participants of two different protests must be 
+  indistinguishable.
+\end{requirements}
+Thus Alice can always argue to be part of any counter-protest while actually 
+supporting the protest, which, in fact, is a slight increase in privacy over 
+ordinary protests.

### 2018-05-23 paper/LocationProofs.tex
Edits related work

--- 2018-02-28 paper/LocationProofs.tex
@@
 
-Some Location-Based Services (\emph{LBS}) only grant access to resources to users located at a particular location,  thus raising the issue of verifying the position claimed by a particular user. 
-In most current schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
-One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
-Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
+Some \ac{LBS} only grant access to resources to users located at a particular 
+location,  thus raising the issue of verifying the position claimed by a 
+particular user. In most current schemes, the location of a user/device is 
+determined by the device itself (\eg through GPS) and forwarded to the \ac{LBS} 
+provider. One of the main drawback of this approach is that a user can cheat by 
+having his device transmitting a false location. Therefore, it is possible for a 
+user to be inappropriately granted access to a particular resource while being 
+thousands of kilometers away.
 
-To counter this threat, a LBS should ask the requesting device to formally prove that it really is at the claimed location. This notion can be formalized through the concept of \emph{location proof}. 
-In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time.
-A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
-Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-%Seb: to do add the corresponding reference
-However, some location proofs systems such as PROPS exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
-\PRIVO share some similarities with PROPS although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made a user, which is an individual property.
+To counter this threat, \iac{LBS} should ask the requesting device to formally 
+prove that it really is at the claimed location. This notion can be formalized 
+through the concept of \emph{location proof}. In a nutshell, a location proof is 
+a digital certificate attesting that someone was at a particular location at a 
+specific moment in time. A location proof architecture is a system by which 
+users can obtain location proofs from neighboring witnesses (\eg trusted access 
+points or other users) that can later be shown to verifiers who can check the 
+validity of a particular proof. Most of the existing approaches to location 
+proofs require the prover and the witnesses to disclose their identities, thus 
+raising many privacy issues such as the possibility of tracing the movements of 
+users of the location proof architecture.
+\seb{to do add the corresponding reference}
+However, some location proofs systems, such as \ac{PROPS}, exists that provides 
+strong privacy guarantees along with the possibility of verifying the claim of 
+the location. \PRIVO share some similarities with \ac{PROPS}, although their 
+objective is quite different as we aim at verifying a global property of the 
+population (\ie crowd estimation) in contrast to checking the location claim 
+made by a user, which is an individual property.

### 2018-05-23 paper/RelatedWork.tex
Edits related work

@@
 
-The seemingly most commonly used method for counting crowds at protests is \emph{Jacob's method}~\cite[c.f.][]{%
+The seemingly most commonly used method for counting crowds at protests is 
+\emph{Jacobs's method}, \cf~\cite{%
   2016DemonstrationsInSeoul,%
@@
 This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
-They generally based on machine learning, and thus also require a training dataset to work.
+They are generally based on machine learning, and thus also require a training 
+dataset to work.
 In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
@@
 In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
-However, it is still difficult to capture the entire location on surveillance video, which diminishes the argument for an upper bound.
+However, it is still difficult to capture the entire location on surveillance 
+video, which diminishes the argument for an upper bound in practice.
 The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
@@
 
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company has tried to estimate the number of participants using their technology.
+During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical 
+analytics company tried to estimate the number of participants using their 
+technology.
 They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
@@
 However, there are several problems with this approach.
-First, it will be difficult to register only the participants' phones and many bystanders will also be counted.
+First, it will be difficult to register only the participants' phones, as many 
+bystanders will also be counted.
 It is also difficult to differentiate between the protesters and the counter-protesters.
@@
 
+\daniel{I think we can cut this paragraph as it is not directly relevant}
 \Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
-Howeve,r this method is designed for indoor use and does not scale to more than a crowd of 20 persons, which makes it unfit to use in protest.
+However this method is designed for indoor use and does not scale to more than a 
+crowd of 20 persons, which makes it unfit to use in protest.
 In addition, this type of data does not provide verifiability.
@@
 This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Eve's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.
+For instance, if Alice has organized a protest against Grace's regime, who shuts 
+down the cellular network or Internet backbone as a means to censor the protest.
 
-Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which uses epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with highnode mobility and churn.
-There is, however, no consideration of a potentially adverserial setting and thus no verification or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting but again only work for
-honest participants.
+Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which 
+uses epidemic spreading of crowd-size estimates by device-to-device 
+communication to count crowds in dense urban environments with high 
+node-mobility and churn. There is, however, no consideration of a potentially 
+adverserial setting and thus no verification or checks on eligibility. 
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense 
+areas, avoids double counting, but again, only work for honest participants.
 

### 2018-05-23 paper/DB-anon-cred.tex
Edits distance bounding and DB-anon-cred

@@
 Knowledge, instead of \ac{DBPK}.)
-However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie for 
-proving \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need 
-\iac{DBPK} protocol for discrete logarithms.
+However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie 
+protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we 
+need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = 
+  g^\alpha]\)).
 To realize this, we will now introduce such a protocol that will allow us to do 
 \ac{DB} anonymous credentials.
-We note, however, that this protocol only provides \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} and \ac{DBIF} resistance --- but not \ac{DBTF} resistance.
 
-\NewCryptoScheme{\DBS}{DBS}
+\NewScheme{\DBS}{DBS}
 \NewAlgorithm{\DBSprove}{\DBS.\!Prove}
@@
 hijacking~\cite{DistanceHijacking}.
+(It could not fulfil \ac{DBTF} either.)
 We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
-which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and an impersonating 
-verifier (\ie public-key).
-It will not protect against terrorist fraud, although ideally this property should be desirable.
+which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
+impersonating verifier (\ie it is public-key).
 
@@
 
-The protocol is also secure against distance hijacking due to the fact that it is the authenticating bit string that is used 
-during the \ac{DB} phase.
+The protocol is \ac{DBTF} resistant, if the malicious prover gives both 
+responses to the adversary, the adversary can compute the secret key.
+This follows from the fact that it is \iac{ZKPK}, \ie there is an extractor that 
+can extract the secret.
+
+The protocol is also secure against distance hijacking due to the fact that it 
+is the authenticating bit string that is used during the \ac{DB} phase, not the 
+challenge bit string as in Brands-Chaum.

### 2018-05-23 paper/DistanceBounding.tex
Edits distance bounding and DB-anon-cred

@@
 
-\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks contactless communications in which the adversary forwards a communication between a prover and a possibility far-away verifier to authenticate.
-These attacks cannot be prevented by cryptographic tools as they are independent of the semantics of the messages exchanged and mechanisms ensuring the physical proximity between a verifier and a prover must be used.
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent 
+relay attacks in contactless communications in which the adversary forwards a 
+communication between a prover and a possibly far-away verifier to authenticate. 
+These attacks cannot be prevented by cryptographic tools as they are independent 
+of the semantics of the messages exchanged, so mechanisms ensuring the physical 
+proximity between a verifier and a prover must be used.
 \Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
@@
 \end{itemize}
-\daniel{Describe the DB frauds in more detail, i.e. explain them.}
+\daniel{Describe the DB frauds in more detail, \ie explain them.}
 There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
@@
 The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
-Indeed, in this context it does not make sense to protect against the verifier as he can impersonate easily the prover as he has a knowledge of his secret key.
+Indeed, in this context it does not make sense to protect against the verifier 
+as he can easily impersonate the prover as he has a knowledge of his secret key.
 There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
@@
 who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials, which we will describe next.
+More specifically, we must combine such \iac{DB} with anonymous credentials 
+(which we do in \cref{DB-anon-cred}).
 The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-05-23 paper/protocol.tex
Minor edits in intro (only labels in other files)
Updates bibsp and makefiles
Edits protocol section

--- 2018-03-21 paper/protocol.tex
@@
 \section{\PRIVO:\@ A protocol for protest outcome verification}%
-\label{protocol}
+\label{Protocol}
 
-\NewCryptoScheme{\PRIVOscheme}{PRIVO}
+\NewScheme{\PRIVOscheme}{PRIVO}
 
-We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtests.
+We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtest 
+Outcomes.
 The protocol consists of four phases: the setup, join, participation and 
@@
 
-\NewAlgorithm{\PRIVOreg}{Register}
+\NewAlgorithm{\PRIVOreg}{Reg}
 
@@
 one signature per protester but will not know who has which key.
-The protester chooses \(k, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^k 
-  Z^r\) and send \(M\) to the server.
+The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly and sets \(M = g^k 
+  Z^r\) and sends \(M\) to the server.
 The protester acts as prover and the \ac{CA} as verifier while they perform the 
@@
 \]
-If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
+If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = 
   g^a\).
@@
 \NewAlgorithm{\PRIVOjoin}{Join}
+\NewVariable{\mfst}{manifesto}
 
@@
 A participant who wants to join the protest will use the manifesto to compute an 
-identifier for the cause, \(cid\gets \Hash[\text{manifesto}]\).
+identifier for the cause, \(cid\gets \Hash[\mfst]\).
 Then this identifier is used to create the participant's protest-specific 
@@
     \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
+    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
+    storage \(S\).
   }%
@@
 
-\NewAlgorithm{\PRIVOparticipate}{Participate}
+\NewAlgorithm{\PRIVOparticipate}{Prticip}
 \NewAlgorithm{\PRIVOwitness}{Witness}
@@
 The participant reblinds its signature \(\sigma\) on its secret key: choose 
-\(r_1, r_2\gets \ZZ_q^*\) and let \(
+\(r_1, r_2\rgets \ZZ_q^*\) and let \(
   \tilde\sigma = (\tilde A = A^{r_1},
@@
   wsig]]\).
+(This is for redundancy only.)
 Then, without any time requirements, the witness computes \iac{NIZK} proof 

### 2018-05-23 paper/analysis-security.tex
Starts editing security analysis

@@
 
-We will start by giving an overview of the protocol.
-We have a number of participants.
-We have a cothority who provide the storage in a decentralized manner.
-The cothority should consist of independent actors, preferably with conflicting 
-interests so that they will not collude.
-We have Alice the organizer and Bob the participant who are both protesters.
-We have the trustworthy journalist Jane who is present but not participating in 
-the protest.
-The protesters will witness each others participation proofs, \eg Alice will 
-witness Bob's proof and Bob will witness Alice's proof.
-The result of witnessing a proof is a proof share (essentially a witness 
-signature).
-Jane will also participate in witnessing the protesters' proofs.
-The witnessing is done through local interaction.
-As soon as Alice and Bob have departed from the protest they upload their proofs 
-(\ie all proof shares) to the cothority for indefinite storage.
-Since each proof consists of one proof share for each witness, each witness 
-could potentially upload the proof share themselves to the cothority.
-This would have the same effect but with added redundancy, in case Alice or Bob 
-cannot upload them themselves.
-
-We will now describe the protocol in more details.
-We will describe it in the same order as outlined above:
-starting with the construction of the participation proof (shares) and 
-submitting the proof shares to storage.
-Then we will conclude with how to verify the proofs and produce the 
-participation count.
-
 \subsection{Constructing the participation-proof shares}
-
-An overview of the final structure of a proof is given in \cref{fig:ProofFig} 
-and an overview of the communication is given in \cref{fig:ProtocolOverview}.
 
@@
 
+\NewVariable{\sk}{sk}
+
 \Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
 can provide two participation proofs and thus be counted twice.
-That situation should be detectable.
-We can do this by ensuring that Alice cannot produce two valid proofs which
-are unlinkable.
+This is prevented by the use of \(\pid\).
+To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
+\begin{align*}
+\pi_{\pid'} &= \SPK\mleft\{ (\sk') : \mright. \\
+            & \qquad pid = \ACprf[_{\sk'}][cid], \\
+            & \qquad \mleft. \sigma = \ACblind[\ACsign[_{ssk}][\sk']] \mright\} 
+            \\
+            & \qquad\qquad (\cid, \pid', \wid', t_s, t_s', l, wsig').
+\end{align*}
+\daniel{There are several approaches for Alice to do this, we should describe 
+  them.}
+
 \Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
-share) for another event.
-\Eg there might be a counter protest at the same time and place, these would 
-have the same spatial and temporal properties.
-To distinguish them, we also need to prove for which of these events that a 
-proof is designated.
-The idea is to construct a unique identifier for a protest.
-
-We will start with the latter.
-The identifier of the protest must be regulated, for the same reasons as for the 
-user identifiers --- otherwise a counter-protest can simply choose the same 
-protest identifier.
-As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
-root of what defines a protest.
-The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
-the hash value of the manifesto as identifier of the protest (cause).
-(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)
-
-To practically propagate this identifier to the protesters the organizer can 
-have a placard with a large QR code that either contains the entire manifesto or 
-at least links to a website hosting the manifesto.
-The user can scan this QR code with a protesting app which will automatically 
-fetch it, show it to the protester for approval and then compute the identifier 
-\(cid\).
-
-Next we need to consider the protesters' identifiers to prevent Sybil attacks.
-\Citet{HowToWinTheCloneWars} created an \emph{interactive} credential system 
-which allows anonymous authentication at most \(n\) times\footnote{%
-  Possibly there is another scheme that makes it non-interactive, \eg by 
-  \citet{Psignatures}, see issue \#27.
-}, where \(n = 1\) in our scenario.
-Alice has \iac{PRF} key \(k\) and a blind signature on \(k\) included in her 
-national identity-card (by assumption).
-She will use \(k\) to compute \(pid\gets \ACprf[_k][cid]\), which is her 
-anonymous identity during the protest (shown as \(pid\) in \cref{fig:ProofFig}).
+share) for another event --- or someone else using her proof-share for another 
+event.
+This is done with the use of \(\cid\) in the proof shares.
+Thus to reuse the proof share for another protest, with a different manifesto, 
+one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
+  \Hash[\mfst']\).
 

### 2018-05-23 paper/analysis-security.tex
Makes proper multiletter variables

@@
 
-\subsection{Constructing the participation-proof shares}
-
-\subsubsection{Linkability and designated protest}
-
-\NewVariable{\sk}{sk}
+\paragraph{Linkability and designated protest}
 
@@
 To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
-\begin{align*}
-\pi_{\pid'} &= \SPK\mleft\{ (\sk') : \mright. \\
-            & \qquad pid = \ACprf[_{\sk'}][cid], \\
-            & \qquad \mleft. \sigma = \ACblind[\ACsign[_{ssk}][\sk']] \mright\} 
-            \\
-            & \qquad\qquad (\cid, \pid', \wid', t_s, t_s', l, wsig').
-\end{align*}
-\daniel{There are several approaches for Alice to do this, we should describe 
-  them.}
+\begin{multline*}
+\pi_{\pid'} = \SPK\mleft\{ (\sk') : \mright. \\
+  \begin{aligned}
+    \pid' &= \ACprf[_{\sk'}][\cid], \\
+    \sigma &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk']] \mright\}
+  \end{aligned} \\
+    (\cid, \pid', \wid', t_s, t_s', l, \wsig').
+\end{multline*}
+\daniel{There are several approaches for Alice to do this, \eg attacking the 
+  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
+  I think we should describe them.}
 
@@
 
-\subsubsection{Temporal eligibility, created after start}
+\paragraph{Temporal eligibility, created after start}
 
@@
 
-\subsubsection{Location proofs and spatial eligibility}
+\paragraph{Location proofs and spatial eligibility}
 
@@
 
-Alice will send her \(pid\) to Jane to start the witness protocol.
+Alice will send her \(\pid\) to Jane to start the witness protocol.
 Then they do the distance bounding \dots
@@
 If Jane is convinced that Alice's secret is within the desired proximity, she 
-will compute her witness identifier \(wid\) and witness signature \(wsig\) and 
+will compute her witness identifier \(\wid\) and witness signature \(\wsig\) and 
 send them to Alice.
 
-\subsubsection{Temporal eligibility, created before end}
+\paragraph{Temporal eligibility, created before end}
 
@@
 its shares) and then count it if valid.
-To verify the eligibility of a proof share, we must verify that \(pid\), \(wid\) 
-and \(wsig\) are not just randomly generated numbers but they actually depend on 
+To verify the eligibility of a proof share, we must verify that \(\pid\), \(\wid\) 
+and \(\wsig\) are not just randomly generated numbers but they actually depend on 
 the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
@@
 protest.
-Thus \(pid, wid, wsig\) can be used in the proof shares (and all computations 
+Thus \(\pid, \wid, \wsig\) can be used in the proof shares (and all computations 
 above) whereas their respective \ac{NIZK} proof can be computed and published 
@@
 
-Alice must provide \iac{NIZK} proof showing that \(pid = \ACprf[_{k_P}][cid]\) 
+Alice must provide \iac{NIZK} proof showing that \(\pid = \ACprf[_{k_P}][\cid]\) 
 and that she knows a signature by the identity authority on \(k_P\).
@@
 
-In the same manner, each witness must also provide \iac{NIZK} proofs for \(wid = 
-  \ACprf[_{k_W}][pid]\) and \(wsig = \ACprf[_{k_W}][wid, t_s, l]\) as well as 
+In the same manner, each witness must also provide \iac{NIZK} proofs for \(\wid = 
+  \ACprf[_{k_W}][\pid]\) and \(\wsig = \ACprf[_{k_W}][\wid, t_s, l]\) as well as 
 that the witness knows a signature by the identity authority on \(k_W\).
@@
 With this key Grace can verify that Alice has submitted a proof by computing 
-\(pid'\gets \ACprf[_{k_A}][cid]\) and compare \(pid = pid'\).
+\(\pid'\gets \ACprf[_{k_A}][\cid]\) and compare \(\pid = \pid'\).
 

### 2018-05-23 paper/protocol.tex
Makes proper multiletter variables

@@
 \NewAlgorithm{\PRIVOsetup}{Setup}
+\NewVariable{\sk}{sk}
+\NewVariable{\spk}{spk}
+\NewVariable{\ssk}{ssk}
 
-\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
+\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
 The setup phase is for the \ac{CA} to set up all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((spk, ssk)\) as 
+The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as 
 follows.
@@
   g^z\).
-Then the service public key \(spk = (q, G, G_T, g, X, Y, Z)\) and the service 
-private key \(ssk = (x, y, z)\).
+Then the service public key \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service 
+private key \(\ssk = (x, y, z)\).
 
@@
 
-\emph{Registration: \(sk\gets 
-    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
+\emph{Registration: \(\sk\gets 
+    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{CA}][\ssk]}\).}
 During the registration phase, each protester will generate a secret key and 
@@
 \end{align*}
-Upon success, the protester uses \(sk = (\sigma, k, r)\).
+Upon success, the protester uses \(\sk = (\sigma, k, r)\).
 
@@
 \NewVariable{\mfst}{manifesto}
+\NewVariable{\cid}{cid}
+\NewVariable{\pid}{pid}
 
-\emph{Joining participant: \((pid, t_s)\gets 
+\emph{Joining participant: \((\pid, t_s)\gets 
     \PRIVOjoin[_P][\text{manifesto}]\).}
 A participant who wants to join the protest will use the manifesto to compute an 
-identifier for the cause, \(cid\gets \Hash[\mfst]\).
+identifier for the cause, \(\cid\gets \Hash[\mfst]\).
 Then this identifier is used to create the participant's protest-specific 
-identifier, \(pid\gets \ACprf[_{sk}][cid]\) (in 
+identifier, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
 \cref{fig:ProofFig,fig:ProtocolOverview}).
-More specifically, \(pid = g_T^{1/(k+cid)}\) (remember that \(sk = (\sigma, k, 
-  r)\)).
+More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, 
+  k, r)\)).
 The participant should also get a time-correlated random value from the 
 time-stamping service, \(t_s\gets \TSget\).
+
+\NewVariable{\wid}{wid}
+\NewVariable{\wsig}{wsig}
 
@@
     Structure of a proof share.
-    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
+    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
     key \(k_P\).
-    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
+    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
     \(k_W\).
     \(t_s\) is a time interval and \(l\) is the coordinates of an area.
-    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
+    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
   }%
@@
       P\colon & t_s\gets \TSget \\
-        & cid\gets \Hash[\text{manifesto}], \\
-        & pid\gets \ACprf[_{sk_P}][cid] \\
+        & \cid\gets \Hash[\text{manifesto}], \\
+        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
       W\colon & t_s'\gets \TSget
@@
       \\[-3em]
-      P\to W\colon & pid \\
+      P\to W\colon & \pid \\
       P\leftrightarrow W\colon &
-        \DBPK\mleft\{ (sk_P) : \mright. \\
-        & \qquad pid = \ACprf[_{sk_P}][cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
+        \DBPK\mleft\{ (\sk_P) : \mright. \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
         \\
-      W\colon & wid\gets \ACprf[_{sk_W}][pid], \\
-        & wsig\gets \ACprf[_{sk_W}][wid, t_s, t_s', l] \\
-      W\to P\colon & (wid, t_s', l, wsig)
+      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid], \\
+        & \wsig\gets \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \\
+      W\to P\colon & (\wid, t_s', l, \wsig)
       \\[-1em]
@@
       \\[-2em]
-      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
-      W\colon & t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
-      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_{wid, wsig}),\quad 
-      \text{where} \\
-        & \pi_{wid, wsig} = \SPK\mleft\{ (sk_W) : \mright. \\
-        & \qquad wid = \ACprf[_{sk_W}][pid], \\
-        & \qquad wsig = \ACprf[_{sk_W}][wid, t_s, t_s', l], \\
-        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][sk_W]]\mright\} \\
-        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
-      P\to S\colon & (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid}),\quad 
-      \text{where}\\
-        & \pi_{pid} = \SPK\mleft\{ (sk_P) : \mright. \\
-        & \qquad pid = \ACprf[_{sk_P}][cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][sk_P]] \mright\} 
+      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
+      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
+      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\wid, 
+        \wsig}),\quad \text{where} \\
+        & \pi_{\wid, \wsig} = \SPK\mleft\{ (\sk_W) : \mright. \\
+        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
+        & \qquad \wsig = \ACprf[_{\sk_W}][\wid, t_s, t_s', l], \\
+        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
         \\
-        & \qquad\qquad (cid, pid, wid, t_s, t_s', l, wsig)
+        & \qquad\qquad (\pid, \wid, t_s, t_s', l, \wsig) \\
+      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, 
+      \pi_{\pid}),\quad \text{where}\\
+        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+        \\
+        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l, \wsig)
     \end{align*}
@@
 \emph{Participating: \(\pi\gets
-    \Proto{\PRIVOparticipate[cid, sk_P]}{\PRIVOwitness[sk_W, spk]}\),}
+    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
 In the participating phase the participant and the witness constructs the proof 
@@
 \) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
-\(pid\).)
-The participant sends \((pid, \tilde\sigma)\) to the witness.
+\(\pid\).)
+The participant sends \((\pid, \tilde\sigma)\) to the witness.
 The witness verifies that
@@
   \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    pid = g_T^{1/(k+cid)} \right\}.
+    \pid = g_T^{1/(k+\cid)} \right\}.
 \end{multline*}
 where \(r' = 1/r_2\).
-We can rewrite \(pid = g_T^{1/(k+cid)}\) as \(pid^k = g_T g_T^{-cid}\).
+We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
 Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
@@
 sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
-  pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
 The witness replies with a challenge \(c\).
@@
     s_r}, \\
-  \mleft(g_T pid^{-cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} pid^{s_k}.
+  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
+  \pid^{s_k}.
 \end{align*}
-If the proof succeeds the witness will compute \(wid\gets \ACprf[_{sk_W}][pid] = 
-  g_T^{1/(k_W+pid)}\) (as above) and in the same way \(wsig\gets 
-  \ACprf[_{sk_W}][\Hash[pid, wid, t_s, t_s', l]]\).
-Then the witness returns \((wid, t_s', l, wsig)\) to the participant.
-Now both the participant and the witness have the tuple \(\pi = (pid, wid, t_s, 
-  t_s', l, wsig)\) which constitutes a proof share of the participant 
+If the proof succeeds the witness will compute \(\wid\gets 
+  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above) and in the same way 
+\(\wsig\gets \ACprf[_{\sk_W}][\Hash[\pid, \wid, t_s, t_s', l]]\).
+Then the witness returns \((\wid, t_s', l, \wsig)\) to the participant.
+Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
+  t_s, t_s', l, \wsig)\) which constitutes a proof share of the participant 
 (\cref{fig:ProofFig}).
@@
 
-\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][cid, pid, wid, t_s, t_s', l, 
-    wsig]\).}
+\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', l, 
+    \wsig]\).}
 The participant should as soon as possible commit the proof-share data to the 
 time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]]\).
+  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]]\).
 The remaining operations are not time critical.
-The participant computes \iac{NIZK} proof \(\pi_{pid}\) which shows the 
-correctness of \(pid\).
+The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
+correctness of \(\pid\).
 More specifically,
 \begin{multline*}
-  \pi_{pid}\gets \SPK\left\{ (sk_P) : \right. \\
+  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
     \begin{aligned}
-      pid &= \ACprf[_{sk_P}][cid] \quad \land \\
-      \sigma_P' &= \left. \ACblind[\ACsign[_{ssk}][sk_P]] \right\}
+      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
+      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
     \end{aligned} \\
-      (cid, pid, wid, t_s, t_s', l, wsig).
+      (\cid, \pid, \wid, t_s, t_s', l, \wsig).
 \end{multline*}
 Finally, the participant uploads the tuple \[
-  (cid, pid, wid, t_s, t_s', t_e, l, wsig, \pi_{pid})
+  (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\pid})
 \] for permanent storage.
 
-\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][pid, wid, t_s, t_s', l, 
-    wsig]\).}
+\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l, 
+    \wsig]\).}
 The witness should, just as the participant, commit the proof-share data to the 
-time-stamping service, \(t_e'\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, 
-  wsig]]\).
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, 
+  \wsig]]\).
 (This is for redundancy only.)
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
-\(\pi_{wid, wsig}\) as follows:
+\(\pi_{\wid, \wsig}\) as follows:
 \begin{multline*}
-  \pi_{wid, wsig}\gets \SPK\left\{ (sk_W) : \right. \\
+  \pi_{\wid, \wsig}\gets \SPK\left\{ (\sk_W) : \right. \\
     \begin{aligned}
-      wid &= \ACprf[_{sk_W}][pid] \quad \land \\
-      wsig &= \ACprf[_{sk_W}][wid, t_s, t_s', l] \quad \land \\
-      \sigma_W' &= \left. \ACblind[\ACsign[_{ssk}][sk_W]] \right\}
+      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
+      \wsig &= \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \quad \land \\
+      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
     \end{aligned} \\
-      (pid, wid, t_s, t_s', l, wsig).
+      (\pid, \wid, t_s, t_s', l, \wsig).
 \end{multline*}
 Finally, the witness uploads the tuple \[
-  (pid, wid, t_s, t_s', t_e', l, wsig, \pi_{wid, wsig})
+  (\pid, \wid, t_s, t_s', t_e', l, \wsig, \pi_{\wid, \wsig})
 \] for permanent storage.

### 2018-05-23 paper/analysis-security.tex
Cuts useless parts of security analysis

@@
 
+\daniel{Rewrite this paragraph, do proper analysis.}
 Given the properties of the storage (in \cref{StorageProperties}), for 
@@
 
+\daniel{Discuss the two alternative approaches: trusted Jane and collusion 
+  threshold.
+  Do actual security analysis.}
 According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
@@
 were actually in that location.
-The role of the witnesses, \eg Jane, is to provide this property.
-Jane can do this by using a distance-bounding protocol to ensure that the secret 
-associated with Alice or Bob must be within limited physical distance.
-
-Alice will send her \(\pid\) to Jane to start the witness protocol.
-Then they do the distance bounding \dots
-[See issue \#22 for the discussion.]
-If Jane is convinced that Alice's secret is within the desired proximity, she 
-will compute her witness identifier \(\wid\) and witness signature \(\wsig\) and 
-send them to Alice.
+The role of the witnesses is to provide this property.
 
@@
 
-The proofs (shares) can be submitted to storage in two steps:
-first, committing them to the blockchain; second, to submit all the required 
-data.
-This will allow some time for computing all the required \ac{NIZK} proofs 
-(discussed in the following section).
-
-Given the properties of the storage system in \cref{StorageProperties}, 
-\cref{CreatedBeforeEnd} is straight-forward: once a proof share is created it 
-should be committed to the blockchain as soon as possible.
-Thus we can infer that a proof (or proof share) was created at the latest when 
-it was committed.
-
-We note that there are at least two entities who know each proof share, the 
-protester and the witness.
-Alice and Bob simply commit their proofs (\ie all proof shares of their 
-proofs) to the blockchain as soon as possible after they have participated in 
-the protest.
-The witnesses do the same, they commit all the proof shares that they helped 
-create.
-(Shown in \cref{fig:ProtocolOverview}.)
+The proofs are committed to the blockchain, thus they cannot have been created 
+after.
+\daniel{Do a proper security analysis.}
 
@@
 
+\daniel{Rewrite!}
 There are three parts to verifying the participation count.
@@
 
+\daniel{Do actual security analysis.}
 Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
@@
 We will do this with \ac{NIZK} proofs.
-We note that these proofs are not needed until the verification step after the 
-protest.
-Thus \(\pid, \wid, \wsig\) can be used in the proof shares (and all computations 
-above) whereas their respective \ac{NIZK} proof can be computed and published 
-after the protest.
 
-Alice must provide \iac{NIZK} proof showing that \(\pid = \ACprf[_{k_P}][\cid]\) 
-and that she knows a signature by the identity authority on \(k_P\).
-\dots
-[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
-issue \#27 for discussion.]
+\subsubsection{Individual verifiability}
 
-In the same manner, each witness must also provide \iac{NIZK} proofs for \(\wid = 
-  \ACprf[_{k_W}][\pid]\) and \(\wsig = \ACprf[_{k_W}][\wid, t_s, l]\) as well as 
-that the witness knows a signature by the identity authority on \(k_W\).
-With these \ac{NIZK} proofs anyone can verify the validity, \ie the 
-eligibility, of the proof shares and thus also count them.
-
-\subsubsection{Individual verifiability and receipt freeness}
-
+\daniel{Do actual security analysis.
+  This is reduced to the security of the blockchain.}
 The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
@@
 Thus each protester must verify that their own proof is indeed included.
-This can be accomplished as follows.
 After Alice commited to her proof (share) in the blockchain, she stores the hash 
@@
 verifiability.
-
-More specifically, to achieve receipt freeness (\cref{ReceiptFreeness}) Alice 
-must remove her secret \ac{PRF} key, \(k_A\).
-With this key Grace can verify that Alice has submitted a proof by computing 
-\(\pid'\gets \ACprf[_{k_A}][\cid]\) and compare \(\pid = \pid'\).
-
-\subsection{Old}
-
-We note that Alice and Bob do not trust each other, for all they know one or the 
-other could be an agent of Grace the autocrat.
-\begin{itemize}
-  \item Grace the evil autocrat,
-  \item Mallory the foreign nation state, and finally
-\end{itemize}
-
-\subsection{Forging new proofs}
-
-It follows from the digital signatures used that proofs are difficult to forge.
-
-\subsection{Reusing participation proofs}
-
-We consider two ways of reusing participation proofs:
-\begin{enumerate}
-  \item Alice and Bob can reuse old proofs by modifying the identifiers.
-  \item Grace can reuse proofs by creating a manifesto which yields the same 
-    identifier as Alice's protest, then try to create new nodes in the 
-    \ac{tposet} that matches the ones used in the old proofs.
-\end{enumerate}
-We will now estimate the difficulty of both types of attacks.
-
-\subsubsection{Finding second preimages}
-
-Grace (possibly with Mallory's aid) wants to arrange a counter-protest.
-One way to get a higher participation count is to use the same identifier as 
-Alice's protest.
-Since the identifier for the protest is the hash value of the manifest, Grace 
-must find a second preimage for the hash function.
-
-% XXX Rephrase identifier problem as a game
-\begin{proposition}
-  Given \(x\) and \(H(x) = y\), the probability of finding an \(x'\) such that 
-  \(H(x') = y\) is \(\frac{1}{\lambda-1}\).
-\end{proposition}
-
-\begin{question}
-  What if we use a Merkle tree instead of only a hash, will that change the 
-  second preimage property?
-\end{question}
-
-Alice wants to arrange another protest against Grace.
-Her manifesto can remain the same, thus the protest identifier remains the 
-same.
-She wants to reuse some old proofs.
-The head value that are included in the proofs extend them too far back into 
-time.
-The digital signatures prevents her from changing them.
-So an alternative is to create nodes in the \ac{tposet} which has the same 
-hashes.
-
-\subsection{Spoofing locations}
-
-\subsubsection{Trust propagation for witnesses}
-
-\dots
-
-\subsection{Individual verifiability}
-
-Grace and Mallory have an incentive to lower the confidence in the result.
-One way they can do this is to say that the result does not contain all 
-participation proofs.
-Statements such as this should be proved: provide a valid but missing proof.

### 2018-05-23 paper/conclusions.tex
Adds comment to conclusions

@@
 run the protocol. If used today, \PRIVO would result in a
-considerable undercount in most scenarios, but it presents a first
+considerable undercount in most scenarios, \daniel{why?} but it presents a first
 step toward accurate verifiable yet privacy-preserving crowd counting

### 2018-05-24 paper/analysis-security.tex
WIP on security analysis: temporal and spatial left

@@
 
-\paragraph{Linkability and designated protest}
+\subsection{Individual and universal verifiability}%
+\label{analysis-individual}%
+\label{analysis-universal}
 
-\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
-can provide two participation proofs and thus be counted twice.
-This is prevented by the use of \(\pid\).
-To be counted twice, Alice must produce a \(\pid'\neq \pid\) and a signature
-\begin{multline*}
-\pi_{\pid'} = \SPK\mleft\{ (\sk') : \mright. \\
-  \begin{aligned}
-    \pid' &= \ACprf[_{\sk'}][\cid], \\
-    \sigma &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk']] \mright\}
-  \end{aligned} \\
-    (\cid, \pid', \wid', t_s, t_s', l, \wsig').
-\end{multline*}
-\daniel{There are several approaches for Alice to do this, \eg attacking the 
-  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
-  I think we should describe them.}
+\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
+that their participation proofs (proof shares) are indeed included.
+As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \wsig, 
+  \pi_\pid, \pi_{\wid, \wsig}\)) are committed to the blockchain and available 
+from public storage (see \cref{fig:ProtocolOverview}).
+Alice and Bob can simply check that all of their proof shares are indeed there 
+and thus the security of individual verifiability depends on the properties of 
+the blockchain and storage.
 
-\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
-share) for another event --- or someone else using her proof-share for another 
-event.
-This is done with the use of \(\cid\) in the proof shares.
-Thus to reuse the proof share for another protest, with a different manifesto, 
-one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
-  \Hash[\mfst']\).
+\Cref{UniversalVerif} requires that also anyone can verify the result and that 
+all participation proofs counted indeed are eligible.
+As the proof shares are committed and stored publicly, anyone can download them, 
+verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid, \wsig}\)) the proofs and 
+count them.
+As for individual verifiability, the security of universal verifiability is 
+reduced to the properties of the blockchain and storage but also the eligibility 
+verification, which we will discuss next.
+
+\subsection{Eligibility verifiability}%
+\label{analysis-eligibility}
+
+\Cref{EligibilityVerif} states that anyone must be able to determine the 
+authenticity of the relevant attributes of the data.
+We have several attributes that must be verifiable:
+time of creation (temporal eligibility),
+physical location of \(\sk_P\) at creation (spatial eligibility),
+recognize two proofs from the same person (one-proof-per-person eligibility) and 
+that the proof is indeed designated for the event (designated-event 
+eligibility).
+We will now analyse these.
 
@@
 
-\subsection{Verifying the participation count}
+\paragraph{Linkability and designated protest}
 
-\daniel{Rewrite!}
-There are three parts to verifying the participation count.
-First, we must verify the eligibility of each proof, \ie of all its shares.
-Second, we must count these valid proofs.
-Third, each protester must check that their proof is indeed registered so that 
-it can be counted.
+\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
+can provide two participation proofs and thus be counted twice.
+This is prevented by the use of \(\pid\).
+To be counted twice, Alice must produce a \(\pid'\neq \pid\) and two signatures:
+\begin{multline*}
+\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
+  \begin{aligned}
+    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
+    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
+  \end{aligned} \\
+    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
+\end{multline*}
+and
+\begin{multline*}
+  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
+    \begin{aligned}
+      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
+      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
+      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
+    \end{aligned} \\
+      (\pid', \wid', t_s, t_s', l, \wsig').
+\end{multline*}
 
-\subsubsection{Eligibility and universal verifiability}
+\daniel{There are several approaches for Alice to do this, \eg attacking the 
+  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
+  I think we should describe them.}
 
-\daniel{Do actual security analysis.}
-Universal verifiability (\cref{UniversalVerif}) means that anyone should be able 
-to count the valid proofs.
-To do this we must be able to verify the eligibility of a proof (\ie of all 
-its shares) and then count it if valid.
-To verify the eligibility of a proof share, we must verify that \(\pid\), \(\wid\) 
-and \(\wsig\) are not just randomly generated numbers but they actually depend on 
-the keys \(k_P\) and \(k_W\) (as illustrated in \cref{fig:ProofFig}).
-We will do this with \ac{NIZK} proofs.
-
-\subsubsection{Individual verifiability}
-
-\daniel{Do actual security analysis.
-  This is reduced to the security of the blockchain.}
-The purpose of individual verifiability (\cref{IndividualVerif}) is to prevent 
-an adversary from dropping participation proofs.
-Thus each protester must verify that their own proof is indeed included.
-After Alice commited to her proof (share) in the blockchain, she stores the hash 
-of the block.
-At a later time, she can still verify that the block is indeed still there.
-At this point, this hash value is the only thing she must store for individual 
-verifiability.
+\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
+share) for another event --- or someone else using her proof-share for another 
+event.
+This is done with the use of \(\cid\) in the proof shares.
+Thus to reuse the proof share for another protest, with a different manifesto, 
+one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
+  \Hash[\mfst']\).

### 2018-05-24 paper/analysis-security.tex
Writes up sec analysis of temporal; updates linkability, designated
Spatial left to do.

@@
 
-\paragraph{Temporal eligibility, created after start}
+\paragraph{Temporal eligibility}%
+\label{analysis-temporal}
 
-\daniel{Rewrite this paragraph, do proper analysis.}
-Given the properties of the storage (in \cref{StorageProperties}), for 
-\cref{CreatedAfterStart}, each witness must include the hash value of an 
-existing block in the blockchain in each proof share (shown as \(t_s\) in 
-\cref{fig:ProofFig}).
-Then it is clear that the proof must have been created after that block (since 
-predicting such a value is hard).
-This value can either be provided to the witness by the protester or the witness 
-uses the value of the last known block.
+\Cref{TemporallyRelated} ensures freshness, \ie that we cannot simply resubmit 
+an old proof as a new one.
+In general, freshness requires the prover to respond to an unpredictable 
+challenge.
+The challenge here is to include the hash value at the head of the blockchain at 
+the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
+share).
+As per construction of blockchains, the hash value at the head depends on the 
+previous blocks in the chain.
+Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
+which depends on the predictability of the transactions and the nonce needed by 
+the miner.
+The transactions in turn depend on the signatures made by the signing keys 
+corresponding to the used transactions.
+If these were predictable, our adversary could spend arbitrary transactions in 
+the blockchain --- which is designed to be hard.
+Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
+have been published on the blockchain before being included in her proof share.
 
-\paragraph{Location proofs and spatial eligibility}
+According to \cref{TemporallyRelated}, we must also prove that a proof share has 
+not been created after a certain time.
+The hash values of the proof shares are committed to the blockchain, thus there 
+is a negligible probability that they were created after that.
+Alice would have to choose a value \(y\) in the domain of the hash function 
+\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
+a valid proof.
+If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.
+
+\paragraph{Spatial eligibility}%
+\label{analysis-spatial}
 
@@
 
-\paragraph{Temporal eligibility, created before end}
-
-The proofs are committed to the blockchain, thus they cannot have been created 
-after.
-\daniel{Do a proper security analysis.}
-
-\paragraph{Linkability and designated protest}
+\paragraph{Linkability}%
+\label{analysis-linkability}
 
@@
 This is prevented by the use of \(\pid\).
-To be counted twice, Alice must produce a \(\pid'\neq \pid\) and two signatures:
+To be counted twice, Alice must produce a \(\pid'\neq \pid\).
+Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
+\(\sk_P'\) and make the witness accept in the protocol
+\begin{multline*}
+\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid], \mright. \\
+    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
+\end{multline*}
+while she does not know a valid signature on \(\sk_P'\).
+This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
+can get a valid signature on a secret key from the \ac{CA}.
+
+\paragraph{Designated protest}%
+\label{analysis-designated}
+
+\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
+share) for another event --- or someone else using her proof-share for another 
+event.
+This is prevented with the use of \(\cid\) in the proof shares.
+Thus to reuse the proof share for another protest, with a different manifesto, 
+one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
+  \Hash[\mfst']\).
+
+\paragraph{Forging proof shares}
+
+\daniel{This is work-in-progress.}
+Alice can attempt to forge the full proof directly, \ie
 \begin{multline*}
@@
 \end{multline*}
-and
+and consequently
 \begin{multline*}
@@
     \end{aligned} \\
-      (\pid', \wid', t_s, t_s', l, \wsig').
+      (\pid', \wid', t_s, t_s', l, \wsig'),
 \end{multline*}
-
-\daniel{There are several approaches for Alice to do this, \eg attacking the 
-  \(\SPK\)-signature, the \(\AC\)-signature, \etc.
-  I think we should describe them.}
-
-\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
-share) for another event --- or someone else using her proof-share for another 
-event.
-This is done with the use of \(\cid\) in the proof shares.
-Thus to reuse the proof share for another protest, with a different manifesto, 
-one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
-  \Hash[\mfst']\).
+and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).

### 2018-05-24 paper/properties.tex
Writes up sec analysis of temporal; updates linkability, designated
Spatial left to do.

@@
     \begin{requirements}
-    \item\label{CreatedAfterStart} \emph{Temporal eligibility}:
+    \item\label{TemporallyRelated} \emph{Temporal eligibility}:
       prove that the proof was created after the start of the protest and
-      %\label{CreatedBeforeEnd} prove that the proof was created 
       before the end of the protest.

### 2018-05-24 paper/conclusions.tex
Fixes refs to non-existent labels

@@
 protocol to develop distance-bounding anonymous credentials. Except for receipt
-freeness (\cref{ReceiptFreeness}), which we cannot guarantee if the adversary gets access to
+freeness, which we cannot guarantee if the adversary gets access to
 Alice's device and secret PRF key after her participation has
@@
   CountOnce,%
-  CreatedAfterStart,CreatedBeforeEnd,SpatiallyRelated,%
+  TemporallyRelated,SpatiallyRelated,%
 }.

### 2018-05-24 paper/analysis-security.tex
Completes spatial eligibility, privacy left

@@
 
-\Cref{TemporallyRelated} ensures freshness, \ie that we cannot simply resubmit 
-an old proof as a new one.
+\Cref{TemporallyRelated} ensures freshness, \ie that Alice cannot simply 
+resubmit an old proof as a new one.
 In general, freshness requires the prover to respond to an unpredictable 
@@
 not been created after a certain time.
+Otherwise Grace can argue that the proof share was created after the protest.
 The hash values of the proof shares are committed to the blockchain, thus there 
@@
 
-\daniel{Discuss the two alternative approaches: trusted Jane and collusion 
-  threshold.
-  Do actual security analysis.}
-According to \cref{SpatiallyRelated} Alice and Bob must bind their proofs 
-(shares) spatially to the location, which would allow us to verify that they 
-were actually in that location.
-The role of the witnesses is to provide this property.
+\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
+indeed on the location when the proof share was created.
+Thus we must ensure that Alice cannot forge undeserved witness signatures.
+To forge a witness signature, Alice must produce a \(\wid'\) such that
+\begin{multline*}
+  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
+    \begin{aligned}
+      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
+      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
+      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
+    \end{aligned} \\
+      (\pid, \wid', t_s, t_s', l, \wsig'),
+\end{multline*}
+while not knowing a signature on the secret key \(\sk_W'\).
+Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
+on \(\sk_W'\) from the \ac{CA}.
 
@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks, \ie that one individual 
-can provide two participation proofs and thus be counted twice.
+\Cref{CountOnce} is required to prevent Sybil attacks, \ie that Alice can 
+provide two participation proofs and thus be counted twice.
 This is prevented by the use of \(\pid\).
@@
 \begin{multline*}
-\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid], \mright. \\
+\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
     \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
@@
 
-\paragraph{Forging proof shares}
+%\paragraph{Forging proof shares}
+%
+%\daniel{This is work-in-progress.}
+%Alice can attempt to forge the full proof directly, \ie
+%\begin{multline*}
+%\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
+%  \begin{aligned}
+%    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
+%    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
+%  \end{aligned} \\
+%    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
+%\end{multline*}
+%and consequently
+%and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).
+%
 
-\daniel{This is work-in-progress.}
-Alice can attempt to forge the full proof directly, \ie
-\begin{multline*}
-\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
-  \begin{aligned}
-    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
-    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
-  \end{aligned} \\
-    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
-\end{multline*}
-and consequently
-\begin{multline*}
-  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
-    \begin{aligned}
-      \wid' &= \ACprf[_{\sk_W'}][\pid'] \quad \land \\
-      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
-      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
-    \end{aligned} \\
-      (\pid', \wid', t_s, t_s', l, \wsig'),
-\end{multline*}
-and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).
+\subsection{Privacy}
+
+\daniel{Must write up privacy analysis.
+  However, must complement the privacy definition for this.}

### 2018-05-24 paper/analysis-security.tex
Moves linkability before spatial in sec analysis
Adds note that Alice can witness once for herself

@@
 
-\paragraph{Spatial eligibility}%
-\label{analysis-spatial}
-
-\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
-indeed on the location when the proof share was created.
-Thus we must ensure that Alice cannot forge undeserved witness signatures.
-To forge a witness signature, Alice must produce a \(\wid'\) such that
-\begin{multline*}
-  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
-    \begin{aligned}
-      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
-      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
-      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
-    \end{aligned} \\
-      (\pid, \wid', t_s, t_s', l, \wsig'),
-\end{multline*}
-while not knowing a signature on the secret key \(\sk_W'\).
-Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
-on \(\sk_W'\) from the \ac{CA}.
-
 \paragraph{Linkability}%
@@
 can get a valid signature on a secret key from the \ac{CA}.
+
+\paragraph{Spatial eligibility}%
+\label{analysis-spatial}
+
+\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
+indeed on the location when the proof share was created.
+Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
+is ensured using the same linkability mechanism as above.
+To forge a witness signature, Alice must produce a \(\wid'\) such that
+\begin{multline*}
+  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
+    \begin{aligned}
+      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
+      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
+      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
+    \end{aligned} \\
+      (\pid, \wid', t_s, t_s', l, \wsig'),
+\end{multline*}
+while not knowing a signature on the secret key \(\sk_W'\).
+Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
+on \(\sk_W'\) from the \ac{CA}.
+(Note that Alice can produce one witness signature for herself, since she has 
+access to her own \(\sk_P\), but no more.)
 

### 2018-05-24 paper/properties.tex
Updates privacy requirements in properties.tex

@@
 Alice or Bob.
-This is stronger than vote privacy, where Grace may know that Alice voted but 
-not what she voted, whereas here she may not know whether Alice \enquote{voted} 
-or not.
-Thus participants and non-participants must be indistinguishable.
-As this is quite difficult to achieve, we settle for something slightly weaker:
+Furthermore, if Grace has managed to link one proof to Alice's, she should not 
+be able to link another proof as a consequence.
+Hence, we can summarize our needed properties as follows:
 \begin{requirements}[P]
-\item\label{ProtestInd} Participants of two different protests must be 
-  indistinguishable.
+\item\label{ProofUnlink} Participants must be unlinkable to their proofs.
+\item\label{ProtestUnlink} Participants (or proofs for the same participant) 
+  must be unlinkable between different protests.
 \end{requirements}
-Thus Alice can always argue to be part of any counter-protest while actually 
-supporting the protest, which, in fact, is a slight increase in privacy over 
-ordinary protests.
+Thus Alice can always argue to be part of the protest in Grace's favour instead 
+of any protest against Grace, which, in fact, is a slight increase in privacy 
+over ordinary protests.

### 2018-05-24 paper/analysis-security.tex
Adds WIP on privacy analysis

@@
 while not knowing a signature on the secret key \(\sk_W'\).
-Thus she must get break the \(\AC\) scheme to succeed or get a valid signature 
-on \(\sk_W'\) from the \ac{CA}.
+Thus she must break the \(\AC\) scheme to succeed or get a valid signature on 
+\(\sk_W'\) from the \ac{CA}.
 (Note that Alice can produce one witness signature for herself, since she has 
@@
 
-\daniel{Must write up privacy analysis.
-  However, must complement the privacy definition for this.}
+We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable 
+across protests (but linkable within one protest due to \cref{CountOnce}).
+It follows from the properties of \(\ACprf\) that \(\pid = 
+  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are 
+unlinkable if \(\cid\neq \cid'\).
+
+Now to \cref{ProofUnlink}.
+Say that a witness works for Grace.
+This witness interacts with Alice directly, \ie has (physically) identified her.
+The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
+and to verify the \ac{DBPK}.
+\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
+  witness in the \ac{DBPK}.}
+Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
+share.
+The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
+  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
+\daniel{Fix this.}
+Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.

### 2018-05-25 paper/intro.tex
Comments in intro

@@
   on his public key (in the spirit of blind signature)}
+\daniel{That's what we currently do.
+  But the government is the authority, so the government can generate and 
+  certify its own keys.}
 In this case, it does not make sense to verify any pro-government protests in 
-which Grace's authoritarian regime wants to organize a pro-regime protest to 
-demonstrate its wide support, 
+which Grace's authoritarian regime wants to demonstrate its wide support, 
 \eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.

### 2018-05-25 paper/SystemModel.tex
Fixes refs to non-existent labels
Edits definitions in system model

@@
 
+% cause identifier
 \NewVariable{\cid}{cid}
@@
 
+% protest
+\NewVariable{\prtst}{P}
+% subprotest
+\NewVariable{\sprtst}{p}
+
 \begin{definition}[Protest]\label{DefProtest}
@@
     \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
-  \(t = \interval{t_s}{t_e}\subseteq \RR\) is a time interval and \(l \subseteq 
-    \RR^2\) is the location.
+  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location 
+  (topological connectedness is not necessary).
   A \emph{protest} is a set of subprotests sharing the same \(\cid\).
@@
 
-We use other participants, that we called \emph{witnesses} to associate the 
-proof to the location by creating a \emph{proof share}.
+We use \emph{witnesses} to associate the proof to the location by creating a 
+\emph{proof share}.
 A witness is only allowed to create one proof share per protester to avoid the 
@@
 
+% proof share
+\NewVariable{\psh}{s}
+% proof shares
+\NewVariable{\pshs}{S}
+% protester identifier
 \NewVariable{\pid}{pid}
+% witness identifier
 \NewVariable{\wid}{wid}
@@
 \begin{definition}[Participation-proof share]
-  A \emph{participation-proof share} \((\pid, \cid, t, l, \wid)\) is a tuple 
-  where:
+  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
+  tuple where:
   \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a function of the protester's identity and \(\cid\); and
-  \(\wid\) is a function of the witness' identity and 
-  \(\pid\).
-  We let \(W\) be the set of all proof shares.
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
+  and
+  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
+  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
+    \sqsubseteq p\).
+  We let \(\pshs\) be the set of all proof shares.
 \end{definition}
@@
 simultaneously symmetrically j witnesses i?
+\daniel{Not necessarily.}
 Using wid and w is confusing since we changed the terminology to use
@@
 
-\begin{definition}[Participation proof]
-  A \emph{participation proof} of protester \(i\) participating in protest \(j\) 
-  is the set
+% proof
+\NewVariable{\prf}{\pi}
+% proofs
+\NewVariable{\prfs}{\Pi}
+
+\begin{definition}[Participation proof]%
+  \label{DefParticipationProof}
+  A \emph{participation proof} of protester with pseudonym \(\pid\) 
+  participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
   \begin{multline}
     \nonumber
-    p_{i, j} =
-    \left\{ (\pid, \cid, t, l, \wid)\in W \mid \right. \\
-    \left. \pid = i, \cid = j,
-    t \subseteq t_j, l\subseteq l_j \right\},
+    \prf_{\pid, \prtst} =
+    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
+      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
   \end{multline}
-  of all proof shares with the same protester and protest identifiers, witness 
-  time interval \(t\) and location \(l\) is within those of the protest \(j\) 
-  (\ie \(t_j\) and \(l_j\)).
+  of all proof shares with the same protester and protest identifiers, 
+  witnessing time interval \(t\) and location \(l\) is within those of the 
+  protest.
+  We denote by \(\prfs\) the set of all proofs.
 \end{definition}
+
+% strength
+\NewFunction{\str}{\varsigma}
 
@@
 \begin{definition}[Participation count]
-  We define the \emph{participation count} of a protest \(\cid\) as the 
-  cardinality \(|P_{\cid}^{s,\theta}|\) of the set of participation proofs \[
-    P_{\cid}^{s,\theta} = \left\{ p_{i,j} \mid
-      j = \cid, s(p_{i,j})\geq \theta \right\}
-  \] for some strength function \(s\colon \powerset(W)\to \RR_+\) and a 
+  We define the \emph{participation count} of a protest \(\prtst\) (as in 
+  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
+  of the set of participation proofs \[
+    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
+      \str(\prf_{i,j})\geq \theta \right\}
+  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
   threshold \(\theta\).
 \end{definition}
-The strength function \(s\) can be used to regulate trust in witnesses.
-One example would be for \(s\) to return the number of proof shares (\ie witnesses) and thus let \(\theta\) to be the threshold of the number of required witnesses.
+The strength function \(\str\) can be used to regulate trust in witnesses.
+One example would be for \(\str\) to return the number of unique witnesses and 
+thus let \(\theta\) to be the threshold of the number of required witnesses.
 Another example would be to return the number of proof shares issued by trusted 
@@
 using their smartphones (or similar devices) running the protocol described in
-\cref{protocol} and uploading their testimony (\ie proof shares) to a blockchain 
+\cref{Protocol} and uploading their testimony (\ie proof shares) to a blockchain 
 after the protest. During the protest the devices are computationally limited by 

### 2018-05-25 paper/properties.tex
Adds comment to properties

@@
 \seb{we have to justify why Mallory is not captured either by Alice or Grace}
+\daniel{I think that we can move Mallory to the discussion, because Mallory 
+  cannot get valid credentials for herself as a foreign state.}
 In addition, Mallory could also have simply as her objective to cause a 

### 2018-05-25 paper/properties.tex
Edits properties, moves Mallory to conclusions

--- 2018-05-24 paper/properties.tex
@@
 
-In our setting, we have three potential adversaries: Alice, Grace and Mallory.
+In our setting, we have two potential adversaries: Alice and Grace.
 \seb{I changed the name of Grace to Eve to be consistent with the introduction}
@@
 arrest them or forcefully convince them to change their minds.
-Finally, Mallory represents another nation state and has some interest in 
-affecting the stability of Grace's regime, for Mallory's own gain, thus 
-supporting either Grace or Alice as she see fits.
-Thus, the objective of Mallory will also be to either increase or decrease the count.
-\seb{we have to justify why Mallory is not captured either by Alice or Grace}
-In addition, Mallory could also have simply as her objective to cause a 
-denial-of-service attack on the architecture of \PRIVO.
-In the following two subsections, we will formally define some security 
-properties specifying the computational effort needed by the adversaries to 
-succeed.
+In the following two subsections, we will define the desired security 
+properties.
 
@@
 
-Note that in general terms, protesting is very similar to petitions, which in 
-turn are similar to voting: all three situations correspond to many individuals 
-expressing their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there is for voting.
-To draw on this analogy, afterwards we will discuss the relationship between voting and protesting when categorizing the security requirements into verifiability and privacy properties.
+We note that, in general terms, protesting is very similar to petitions, which 
+in turn are similar to voting: all three situations correspond to many 
+individuals expressing their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or 
+persecution), hence we desire to have similar properties of verification and 
+privacy for verifying a protest as there are for voting.
 
@@
 Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different: for protests the eligibility requirement must include temporal and spatial 
-eligibility (\ie each proof of participation satisfies some temporal and spatial relation to the protest).
+The eligibility requirement is slightly different: for protests the eligibility 
+requirement must include temporal and spatial eligibility (\ie each 
+participation proof satisfies some temporal and spatial relation to the 
+protest).
 In essence, the proof must bind the person to the time and location of the protest.
 
-To define these properties more formally in the context of protest, we desire three verifiability requirements, among which eligibility can be further broken up in four subproperties:
+To define these properties more formally in the context of protest, we desire 
+three verifiability requirements, among which eligibility can be further broken 
+up into four subproperties:
 \begin{requirements}[V]
@@
 
-In addition to the verification requirements, we also need to formalize the privacy properties.
-As we indirectly pointed out earlier, we focus on the privacy provided to Alice and the protesters.
-In particular, our objective is that as long as Alice can conceal her identity 
-at the demonstration and escape without arrest, her support is recorded in the 
-data without her privacy being violated.
-\seb{I think this sentence should be clarified}
-
-In voting protocols, there are also three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+In addition to the verification requirements, we also need to define the 
+privacy properties.
+In voting protocols, there are also three levels of 
+privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{description}
 \item[Vote privacy:] the voting does not reveal any individual vote.
-\item\label[Receipt freeness:] the voting system does not provide any data that 
-  can be used as a proof of how the voter voted.
+\item[Receipt freeness:] the voting system does not provide any data that can 
+  be used as a proof of how the voter voted.
 \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the 
@@
 This leaves us with what should correspond to vote privacy.
-We need unlinkability between Alice's identity and Alice's participation proof.
+We need unlinkability between Alice's long-term identity and Alice's 
+participation proof.
 Given a participation proof, Grace will not be able to tell if it belongs to 

### 2018-05-25 paper/RelatedWork.tex
Edits the related works section

@@
 When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
-However, this is prone to cheating and the best we can do is to employ forensic methods to try to detect any modifications or other attempts at fraud.
+However, this is prone to cheating --- and subject to a variety of 
+misinformation techniques --- and the best we can do is to employ forensic 
+methods to try to detect any modifications or other attempts at fraud.
+
 \seb{maybe we should also give information about the privacy level reached by 
   this different method}
+From a privacy perspective, all techniques based on photo or video material are 
+as privacy preserving as the protesters make themselves.
+There is a risk that participants are recognizable from the material if they do 
+not wear masks.
 
@@
   between a min, average, max estimates?}
+\daniel{Yes.}
 This is similar to the method usually used by police (\eg for the protests in Seoul):
@@
 
-\daniel{I think we can cut this paragraph as it is not directly relevant}
-\Citet{WifiCrowdCounting} also relies of Wi-Fi, but they instead use the Wi-Fi signal as a sonar to detect people.
-However this method is designed for indoor use and does not scale to more than a 
-crowd of 20 persons, which makes it unfit to use in protest.
-In addition, this type of data does not provide verifiability.
-
-In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
+In general for all of the above methods, the more a crowd spreads out, the more 
+difficult it will be to determine its size.
 In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.

### 2018-05-25 paper/conclusions.tex

@@
 democracy of slipping down the slope towards dictatorship.
+
+Finally, Mallory represents another nation state and has some interest in 
+affecting the stability of Grace's regime, for Mallory's own gain, thus 
+supporting either Grace or Alice as she see fits.
+Thus, the objective of Mallory will also be to either increase or decrease the count.
+\seb{we have to justify why Mallory is not captured either by Alice or Grace}
+\daniel{I think that we can move Mallory to the discussion, because Mallory 
+  cannot get valid credentials for herself as a foreign state.}
+In addition, Mallory could also have simply as her objective to cause a 
+denial-of-service attack on the architecture of \PRIVO.
+
+She cannot create keys valid in another nation state.

### 2018-05-25 paper/RelatedWork.tex
Removes Seb's comment and dbosk's reply

@@
 Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
-\seb{what are the meaning of the choice of density estimates, it is a way to 
-  specify an apriori assumption about the density of the crowd or to choose 
-  between a min, average, max estimates?}
-\daniel{Yes.}
-This is similar to the method usually used by police (\eg for the protests in Seoul):
+This is similar to the method usually used by police (\eg for the protests in 
+Seoul):
 \blockcquote{2016DemonstrationsInSeoul}{%

### 2018-05-25 paper/intro.tex
quick edits

@@
 Alice is an activist that organizes a protest in some location(s) against the 
-current regime leader Grace.
+current government, represented by Grace.
 On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
-On the other hand, Grace is an autocrat who opposes Alice's cause.
+On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
 Bob, Carol and many others participate in the protest for Alice's cause against Grace.
@@
 differ significantly, sometimes in the order of hundreds of thousands.
-The difference is actually quite natural as both parties have different objectives.
+Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
 More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
-Among the numerous recent examples in which it is difficult to establish the actual number of participants, we can cite the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
+Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
@@
 \emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
-Additionally, this verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
+This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
 
@@
 Our adaptation fulfils all the requirements for modern \ac{DB} protocols, 
-including \ac{DBDH} (which was an attach against Brands-Chaum).
+including \ac{DBDH} (which was an attack against Brands-Chaum).
 More importantly, it is public key (\ie handles malicious, impersonating 
-verifiers), fulfils \ac{DBTF} and provides a \ac{PK} for discrete logarithms.
+verifiers), fulfils \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
 The latter allows us to replace the use of the plain Schnorr protocol in the 
@@
 \emph{Limitations and assumptions.} Some of the assumptions that are required 
-for implementing our proposition are not yet realized (see \cref{assumptions} 
+for implementing our proposition are not yet realized (briefly, use of smartphones, unique identities, distance bounding - see \cref{assumptions} 
 for more detailed descriptions). In particular, not all (or even many) 

### 2018-05-25 paper/DB-anon-cred.tex
Corrects DBS: only one random value

@@
 We present the protocol in \cref{SchnorrFigure}.
-The difference from the original Schnorr protocol is that the prover commits to two random values and the verifier sends two challenges.
-Afterwards, the verifier presents to the prover which commitment and challenge to use during the \ac{DB} phase.
+The difference from the original Schnorr protocol is that the prover commits to 
+one random value but the verifier sends two challenges.
+The verifier presents to the prover which commitment and challenge to use 
+during the \ac{DB} phase.
 
@@
   \centering
-  \begin{tabular}{lcl}
+  \begin{tabular}{p{5cm}cp{5cm}}
     \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
@@
 
-    \(\rho_0\rgets \ZZ_q, \rho_1\rgets \ZZ_q\)
-    &
-    &
-    \\
-
-    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
-    & \(\ProtoSendRight{R_0, R_1}\)
+    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
+    & \(\ProtoSendRight{R}\)
     &
@@
 
-    \(s_0\gets \rho_0 + c_0\alpha\)
-    &
-    &
-    \\
-
-    \(s_1\gets \rho_1 + c_1\alpha\)
-    &
-    &
-    \\
-
-    % null
+    \(s_0\gets \rho + c_0\alpha \pmod q\)
     &
@@
 
-    % null
+    \(s_1\gets \rho + c_1\alpha \pmod q\)
     &
-    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\),
-    \\
-
-    % null
-    &
-    & with \(\ceil{\log_2 q}\) bits set to \(b\)
+    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\), with \(\ceil{\log_2 q}\) bits 
+    set to \(b\).
     \\
@@
     &
-    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\)
+    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
+      b\).
     \\
@@
     &
-    & \(R_b \stackrel{?}{=} g^r A^{c_b}\)
+    & \(R \stackrel{?}{=} g^r A^{c_b}\)
     \\

### 2018-05-25 paper/analysis-security.tex
Adds comment on Alice, Bob indistinguishable to Grace
Removes use of wsig (fixes #92)

@@
 that their participation proofs (proof shares) are indeed included.
-As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \wsig, 
-  \pi_\pid, \pi_{\wid, \wsig}\)) are committed to the blockchain and available 
-from public storage (see \cref{fig:ProtocolOverview}).
+As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, 
+  \pi_{\wid}\)) are committed to the blockchain and available from public 
+storage (see \cref{fig:ProtocolOverview}).
 Alice and Bob can simply check that all of their proof shares are indeed there 
@@
 all participation proofs counted indeed are eligible.
-As the proof shares are committed and stored publicly, anyone can download them, 
-verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid, \wsig}\)) the proofs and 
+As the proof shares are committed and stored publicly, anyone can download 
+them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and 
 count them.
@@
 \begin{multline*}
-  \pi_{\wid', \wsig'}\gets \SPK\left\{ (\sk_W') : \right. \\
+  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
     \begin{aligned}
       \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
-      \wsig' &= \ACprf[_{\sk_W'}][\wid', t_s, t_s', l] \quad \land \\
       \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
     \end{aligned} \\
-      (\pid, \wid', t_s, t_s', l, \wsig'),
+      (\pid, \wid', t_s, t_s', l),
 \end{multline*}
@@
 %  \end{aligned} \\
-%    (\cid, \pid', \wid', t_s, t_s', l, \wsig')
+%    (\cid, \pid', \wid', t_s, t_s', l)
 %\end{multline*}
@@
 Now to \cref{ProofUnlink}.
-Say that a witness works for Grace.
+Given \(\pid\), Grace cannot distinguish whether \(\pid = 
+  \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = 
+  \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).
+
+However, say that a witness works for Grace.
 This witness interacts with Alice directly, \ie has (physically) identified her.

### 2018-05-25 paper/protocol.tex
Adds comments to protocol section
Removes use of wsig (fixes #92)

@@
 \NewVariable{\wid}{wid}
-\NewVariable{\wsig}{wsig}
 
@@
     Structure of a proof share.
+    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
     The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
-    key \(k_P\).
+    key \(\sk_P\) and \(\cid\).
     The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
-    \(k_W\).
-    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
-    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
+    \(\sk_W\) and \(\pid\).
+    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
+    witness, respectively, and \(l\) is an area.
+    All values are signed by the witness while also proving the correctness of 
+    \(\wid\) and knowledge of a signature on \(\sk_W\).
   }%
@@
         \\
-      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid], \\
-        & \wsig\gets \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \\
-      W\to P\colon & (\wid, t_s', l, \wsig)
+      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
+      W\to P\colon & (\wid, t_s', l)
       \\[-1em]
@@
       \\[-2em]
-      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
-      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]] \\
-      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\wid, 
-        \wsig}),\quad \text{where} \\
-        & \pi_{\wid, \wsig} = \SPK\mleft\{ (\sk_W) : \mright. \\
+      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
+      \text{where} \\
+        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
         & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
-        & \qquad \wsig = \ACprf[_{\sk_W}][\wid, t_s, t_s', l], \\
         & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
         \\
-        & \qquad\qquad (\pid, \wid, t_s, t_s', l, \wsig) \\
-      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, 
-      \pi_{\pid}),\quad \text{where}\\
+        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
+      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
+      \text{where}\\
         & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
@@
         \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l, \wsig)
+        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
     \end{align*}
@@
 If the proof succeeds the witness will compute \(\wid\gets 
-  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above) and in the same way 
-\(\wsig\gets \ACprf[_{\sk_W}][\Hash[\pid, \wid, t_s, t_s', l]]\).
-Then the witness returns \((\wid, t_s', l, \wsig)\) to the participant.
+  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
+Then the witness returns \((\wid, t_s', l)\) to the participant.
 Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
-  t_s, t_s', l, \wsig)\) which constitutes a proof share of the participant 
+  t_s, t_s', l)\) which constitutes a proof share of the participant 
 (\cref{fig:ProofFig}).
@@
 
-\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', l, 
-    \wsig]\).}
+\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
+    l]\).}
 The participant should as soon as possible commit the proof-share data to the 
 time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, \wsig]]\).
+  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
 The remaining operations are not time critical.
@@
     \end{aligned} \\
-      (\cid, \pid, \wid, t_s, t_s', l, \wsig).
+      (\cid, \pid, \wid, t_s, t_s', l).
 \end{multline*}
 Finally, the participant uploads the tuple \[
-  (\cid, \pid, \wid, t_s, t_s', t_e, l, \wsig, \pi_{\pid})
+  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
 \] for permanent storage.
+\daniel{Return \(\pi'\), whatever that should be.}
 
-\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l, 
-    \wsig]\).}
+\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
 The witness should, just as the participant, commit the proof-share data to the 
-time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l, 
-  \wsig]]\).
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
 (This is for redundancy only.)
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
-\(\pi_{\wid, \wsig}\) as follows:
+\(\pi_{\wid}\) as follows:
 \begin{multline*}
-  \pi_{\wid, \wsig}\gets \SPK\left\{ (\sk_W) : \right. \\
+  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
     \begin{aligned}
       \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
-      \wsig &= \ACprf[_{\sk_W}][\wid, t_s, t_s', l] \quad \land \\
       \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
     \end{aligned} \\
-      (\pid, \wid, t_s, t_s', l, \wsig).
+      (\pid, \wid, t_s, t_s', l).
 \end{multline*}
 Finally, the witness uploads the tuple \[
-  (\pid, \wid, t_s, t_s', t_e', l, \wsig, \pi_{\wid, \wsig})
+  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
 \] for permanent storage.
+\daniel{Return \(\pi''\), whatever that should be.}

### 2018-05-25 paper/RelatedWork.tex

@@
 
-\seb{maybe we should also give information about the privacy level reached by 
-  this different method}
 From a privacy perspective, all techniques based on photo or video material are 

### 2018-05-25 paper/DB-anon-cred.tex

--- 2018-05-23 paper/DB-anon-cred.tex
@@
 
-We pointed out in \cref{DistanceBounding} that the majority of all \ac{DB} protocols that provide the above security properties assume an \emph{honest} verifier.
-This assumption does not hold in our setting, in which every verifier might also be at some point a (malicious) prover.
-We thus need public-key \ac{DB}, and more specifically \ac{DBPK}.
-
-There is a protocol which provide \ac{DBPK} with all the desired properties from 
-above, ProProx~\cite{ProProx}.
+There is a protocol which provide \ac{DBPK} with all the desired properties 
+from above, ProProx~\cite{ProProx}.
 (Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
@@
 hijacking~\cite{DistanceHijacking}.
-(It could not fulfil \ac{DBTF} either.)
+(It was not secure against terrorist fraud either.)
 We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 

### 2018-05-25 paper/DistanceBounding.tex

@@
 \begin{itemize}
-  \item \ac{DBMF}: the adversary illegitimately authenticates, possibly using a 
-    far-away honest prover.
-  \item\ac{DBTF}: a malicious prover helps an accomplice to authenticate.
-    \item \ac{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \ac{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
-  \item \ac{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
+  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using 
+    a far-away honest prover.
+  \item\acf{DBTF}: a legitimate but malicious prover helps a 
+    close-to-the-verifier accomplice to authenticate.
+  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the 
+    verifier on the distance between them.
+  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an 
+    honest prover close to the verifier.
+  \item \acf{DBIF}: the adversary plays against a simplified version of the 
+    protocol without any distance estimation.
 \end{itemize}
-\daniel{Describe the DB frauds in more detail, \ie explain them.}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+There are two lines of attempts at formalizing the above properties: one by 
+\citet{DB-BMV} and another by \citet{DB-DFKO}.
 

### 2018-05-25 paper/conclusions.tex
Removes fixed comments

--- 2018-05-24 paper/conclusions.tex
@@
 democracy of slipping down the slope towards dictatorship.
+
+Finally, Mallory represents another nation state and has some interest in 
+affecting the stability of Grace's regime, for Mallory's own gain, thus 
+supporting either Grace or Alice as she see fits.
+Thus, the objective of Mallory will also be to either increase or decrease the count.
+\seb{we have to justify why Mallory is not captured either by Alice or Grace}
+In addition, Mallory could also have simply as her objective to cause a 
+denial-of-service attack on the architecture of \PRIVO.
+
+Mallory cannot create keys valid in another nation state.

### 2018-05-25 paper/properties.tex
Removes fixed comments

@@
 In our setting, we have two potential adversaries: Alice and Grace.
-\seb{I changed the name of Grace to Eve to be consistent with the introduction}
-\daniel{Changed back to Grace since that's what's in the intro now.}
-Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
+Alice is a participant to the protest and thus she might be also interested in 
+manipulating the system to increase the count (\eg she might have an incentive 
+to do so as an activist).
 In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 

### 2018-05-25 paper/intro.tex

@@
 privacy to the extent possible given their physical presence at the protest. 
-More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
-Nonetheless, we can ensure that none of the digital traces generated by a participant in our scheme can be associated with their identity and that their actions are also unlinkable.
-\sonja{what actions do we refer to here?}
+More precisely, our solution will not be able to prevent an observer 
+(physically present or looking at photos or videos) from recognizing a 
+particular individual at a protest. Nonetheless, we can ensure that none of the 
+digital traces generated by a participant in our scheme can be associated with 
+their identity and that any witnessing is also unlinkable.
 
-\seb{to do complete the contributions}
-\emph{Contributions.} In this paper, our main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+\emph{Contributions.} In this paper, our main contribution is to propose 
+\PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd 
+count in protests.
 This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
@@
 smartphones.
-In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
-\seb{maybe to prevent the above issue, we could require the individual to 
-  generate his secret key and only use the authority to obtain a certification 
-  on his public key (in the spirit of blind signature)}
-\daniel{That's what we currently do.
-  But the government is the authority, so the government can generate and 
-  certify its own keys.}
+In addition, digital certificates signed by a central authority are not yet 
+widely available and if we rely on government-issued credentials, we cannot 
+prevent the government from performing Sybil attacks --- since it can issue 
+arbitrarily many \emph{valid} credentials.
 In this case, it does not make sense to verify any pro-government protests in 
@@
 
-\seb{to do, update the outline}
-\daniel{done?}
 \emph{Outline.} The paper is organized as follows. First, we define and 
@@
 (impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
-constructed from the building blocks, is presented next (\cref{Protocol}) and we 
-analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
+constructed from the building blocks, is presented next (\cref{Protocol}) and 
+we analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
 performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 

### 2018-05-27 paper/LocationProofs.tex
coincoin

@@
 
-Some \ac{LBS} only grant access to resources to users located at a particular 
-location,  thus raising the issue of verifying the position claimed by a 
-particular user. In most current schemes, the location of a user/device is 
-determined by the device itself (\eg through GPS) and forwarded to the \ac{LBS} 
-provider. One of the main drawback of this approach is that a user can cheat by 
-having his device transmitting a false location. Therefore, it is possible for a 
-user to be inappropriately granted access to a particular resource while being 
-thousands of kilometers away.
+Some LBS only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
+In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
+One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
+Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
 
-To counter this threat, \iac{LBS} should ask the requesting device to formally 
-prove that it really is at the claimed location. This notion can be formalized 
-through the concept of \emph{location proof}. In a nutshell, a location proof is 
-a digital certificate attesting that someone was at a particular location at a 
-specific moment in time. A location proof architecture is a system by which 
-users can obtain location proofs from neighboring witnesses (\eg trusted access 
-points or other users) that can later be shown to verifiers who can check the 
-validity of a particular proof. Most of the existing approaches to location 
-proofs require the prover and the witnesses to disclose their identities, thus 
-raising many privacy issues such as the possibility of tracing the movements of 
-users of the location proof architecture.
+One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
+In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time.
+A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
+Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus 
+raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
 \seb{to do add the corresponding reference}
-However, some location proofs systems, such as \ac{PROPS}, exists that provides 
-strong privacy guarantees along with the possibility of verifying the claim of 
-the location. \PRIVO share some similarities with \ac{PROPS}, although their 
-objective is quite different as we aim at verifying a global property of the 
-population (\ie crowd estimation) in contrast to checking the location claim 
-made by a user, which is an individual property.
+However, some location proofs systems, such as PROPS, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
+\PRIVO share some similarities with PROPS, although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-05-27 paper/TimeStamp.tex
coincoin

--- 2018-03-02 paper/TimeStamp.tex
@@
 
-\NewCryptoScheme{\TS}{TS}
+%\NewScheme{\TS}{TS}
 \NewAlgorithm{\TSget}{\TS.\!Get}
@@
 We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
-The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the block into which \(x\) was included.
+The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
+return the identifier of the block into which \(x\) was included.
 \(\TSget\) will return the hash of the current head of the chain.
@@
 The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
-Having a dedicated blockchain for a protest will not do, and thus it is better to use a blockchain which is also used for other things too.
+Having a dedicated blockchain for a protest will not do, and thus it is better 
+to use a blockchain which is used for other things too.
 
@@
 Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
-For instance using blockchains, we can store the hash of the block in which our data was committed, while this block remains we are sure that our data remains committed --- even if we no longer remember what our data looked like.
-We will use this property to approximate the property of receipt freeness.
+For instance using blockchains, we can store the hash of the block in which our 
+data was committed, while this block remains we are sure that our data remains 
+committed --- even if we no longer remember what our data looked like.

### 2018-05-27 paper/intro.tex
modification of abstract and intro

@@
 
-\emph{Context.} Consider the following illustrative scenario.
-Alice is an activist that organizes a protest in some location(s) against the 
-current government, represented by Grace.
+\emph{Context.} 
+Consider the following illustrative scenario.
+Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
 On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
@@
 However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
-To realize this objective a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
+To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.
 
-Historically, there are many examples of protests in which the count estimated by police and that by the organizers 
-differ significantly, sometimes in the order of hundreds of thousands.
+Historically, there are many examples of protests in which the count estimated by police and that by the organizers differ significantly, sometimes in the order of hundreds of thousands.
 Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
@@
 In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
-In addition, they also lack verifiability.
+In addition, they also lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
 
-Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it is actually an adversarial setting. 
+Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
 Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
-In this case, we are left with two options: either we trust Alice or Grace (or 
-another third party), or we have to be able to verify their claims ourselves.
+In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
 In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
-To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants'
-privacy to the extent possible given their physical presence at the protest. 
-More precisely, our solution will not be able to prevent an observer 
-(physically present or looking at photos or videos) from recognizing a 
-particular individual at a protest. Nonetheless, we can ensure that none of the 
-digital traces generated by a participant in our scheme can be associated with 
+To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
+More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
+Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with 
 their identity and that any witnessing is also unlinkable.
 
-\emph{Contributions.} In this paper, our main contribution is to propose 
-\PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd 
-count in protests.
+\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
-for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfils all the requirements for modern \ac{DB} protocols, 
-including \ac{DBDH} (which was an attack against Brands-Chaum).
-More importantly, it is public key (\ie handles malicious, impersonating 
-verifiers), fulfils \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr protocol in the 
-\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
-knowledge, the first to provide \ac{DB} anonymous credentials.
+Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
+More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
+The latter allows us to replace the use of the plain Schnorr's protocol in the \ac{ZKPK} used in anonymous credentials. 
+%Seb: I have put the following sentence because due to the amount of current work recently in distance-bounding, I believe that our sentence should be made more reasonable 
+%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
 
-\emph{Limitations and assumptions.} Some of the assumptions that are required 
-for implementing our proposition are not yet realized (briefly, use of smartphones, unique identities, distance bounding - see \cref{assumptions} 
-for more detailed descriptions). In particular, not all (or even many) 
-protesters, especially in countries with oppressive regimes, currently possess 
-smartphones.
-In addition, digital certificates signed by a central authority are not yet 
-widely available and if we rely on government-issued credentials, we cannot 
-prevent the government from performing Sybil attacks --- since it can issue 
-arbitrarily many \emph{valid} credentials.
-In this case, it does not make sense to verify any pro-government protests in 
-which Grace's authoritarian regime wants to demonstrate its wide support, 
-\eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Finally, achieving distance-bounding protocols on smartphones is currently not 
-feasible within a meaningful range of distance needed for our scenario.
-They lack the required hardware to do the distance bounding fast enough.
+\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized% (briefly, use of smartphones, unique identities, distance bounding -
+(see \cref{assumptions} for a more detailed description). 
+In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
+In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
+In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to demonstrate its wide support, \eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
+Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.
+Indeed, existing smartphones lack the required hardware to do the distance bounding fast enough.
 
-However, we believe that some assumptions might become sufficiently realistic in 
-the near future, due to the smartphone penetration being on the rise and the 
-increased digitalization and government-issued credentials available in some 
-countries already now (\eg Estonia, Germany and Sweden).
-In addition, the distance-bounding 
-chips\footnote{\url{https://www.3db-access.com}} currently available can already 
-enable proofs of proximity for any range of up to 200 meters.
+However, we believe that some assumptions might become sufficiently realistic in a near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\eg Estonia, Germany and Sweden).
+In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
 One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
 
-\PRIVO achieves privacy, but not receipt freeness.
-This means that there is a way for Grace to efficiently verify that Alice has 
-participated.
-However, this requires Grace to be able to get a copy of Alice's secret key so that she can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
+Another limitation of \PRIVO is that it achieves privacy but not receipt freeness.
+This means that there is a way for Grace to efficiently verify that Alice has participated if she is able to get a copy of Alice's secret key.
+Indeed, in this case Grace can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
 
-\emph{Outline.} The paper is organized as follows. First, we define and 
-formalize the notion of protest and discuss its relationship with electronic 
-voting (\cref{SystemModel}).  We then present the desired security properties 
-for such a system (\cref{Properties}) and subsequently discuss related work in 
-terms of these properties (\cref{RelatedWork}). We give the relevant background 
-on the building blocks of our solution, including our proposal for 
-distance-bounding anonymous credentials that cope with a malicious 
-(impersonating) verifier (\cref{BuildingBlocks}). \PRIVO, the protocol 
-constructed from the building blocks, is presented next (\cref{Protocol}) and 
-we analyze its security and privacy (\cref{SecurityAnalysis}) as well as 
-performance and implementation issues (\cref{PerformanceAnalysis}). We conclude 
-with a discussion.
+\emph{Outline.} 
+The paper is organized as follows. 
+First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
+Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
+terms of these properties (\cref{RelatedWork}). 
+Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}).
+\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}).
+Finally, we conclude with a discussion and futures works in \cref{Conclusion}.

### 2018-05-29 paper/conclusions.tex
modification of abstract and intro
Creates a discussion section (fixes #102)

--- 2018-05-24 paper/conclusions.tex
@@
 some assumptions become more realistic.
-
-When it comes to receipt freeness, our construction does not allow it.
-The very property that prevents Alice from cheating by creating \(\pid, \pid'\), 
-such that \(\pid \neq \pid'\), is the property that allows Grace to verify 
-Alice's participation proof.
-If Grace can perform computations using Alice's key, Grace can input the 
-\(\cid\) of interest and see if the resulting \(\pid\) is available on the 
-blockchain.
-To mitigate this situation, Alice could delete her key, in which case she cannot 
-participate in any future protest.
-
-As implied by the last statement, there is the problem of renewing credentials.
-As with all identity cards, passports \etc, they have a limited lifetime and 
-must be renewed at regular intervals.
-The rate at which Alice is allowed to renew her credentials affects to what 
-extent she can perform Sybil attacks.
-
-Currently, the only problem preventing wide deployment is the lacking hardware 
-in smartphones.
-However, due to the rapid development of \enquote{smart} solutions, we believe 
-this is only a matter of time.
-\Eg mobile payments and public transport tickets that can be used over \ac{NFC} 
-will eventually require \iac{DB} chip.
-Without \ac{DB} for these applications, the user must manually confirm on the 
-screen to prevent attacks.
-We believe that the drive for increased usability will replace this type of 
-confirmation by distance bounding.
-
-The deployment of the needed credentials should not be a problem either.
-There are already countries where national \ac{eID} systems are widely deployed.
-The speed of adoption will depend on the architecture of these systems.
-For instance, the system used in Sweden, BankID, is implemented in software and 
-can thus be easily upgraded to include the anonymous credentials we need.
-As for coverage of the population: more than \SI{95}{\%} of people in the ages 
-21--50 uses BankID, it is \SI{88}{\%} for ages 51--60 and \SI{76}{\%} for ages 
-61--70\footnote{%
-  Official statistics, in Swedish:
-  \url{https://www.bankid.com/assets/bankid/stats/2018/statistik-2018-04.pdf}.
-}.
-
-While the deployment of the necessary technologies are not yet available in 
-authoritarian regimes, they are in several democracies.
-We believe that it as important to implement systems such as ours to prevent any 
-democracy of slipping down the slope towards dictatorship.

### 2018-05-29 paper/SystemModel.tex

@@
 
-% cause identifier
-\NewVariable{\cid}{cid}
-
 Formally, we define a protest as an event that is uniquely identified by its 
@@
 More specifically, we will use the following definition.
-
-% protest
-\NewVariable{\prtst}{P}
-% subprotest
-\NewVariable{\sprtst}{p}
 
@@
 
-% proof share
-\NewVariable{\psh}{s}
-% proof shares
-\NewVariable{\pshs}{S}
-% protester identifier
-\NewVariable{\pid}{pid}
-% witness identifier
-\NewVariable{\wid}{wid}
-
 \begin{definition}[Participation-proof share]
@@
 \end{definition}
-\sonja{do the same pair of people (witness-protester) get the
-same wid on a different protest? The pid is unique for protester-cid
-pair thus the id of a protester at a particular protest. Pid is thus
-derived from the protester id (which has no term) and the protest id
-(cid)? In analogy, wid is derived from pid (and thus cid) of both
-participants, protesters i and j, say, where i witnesses j at cid and
-simultaneously symmetrically j witnesses i?
-\daniel{Not necessarily.}
-Using wid and w is confusing since we changed the terminology to use
-proof shares instead of the previous witness (as in testimony, not
-person). wid sounds like it would be the id of the witness person,
-pid sounds like it would be the id of the protester being witnessed,
-we have defined neither and they might not be needed, but it is
-confusing to read.}
-\daniel{I made some minor changes, any better?}
 
 A subset of the proof shares forms a participation proof for a protester.
-
-% proof
-\NewVariable{\prf}{\pi}
-% proofs
-\NewVariable{\prfs}{\Pi}
 

### 2018-05-29 paper/analysis-security.tex
Adds draft of mechanism reuse prevention

@@
 
+There is also another case of collision that we must prevent.
+Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
+identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
+with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
+Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
+then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
+protest with manifesto \(m\).
+This means that we must separate the mechanisms used for participating and 
+witnessing.
+The protocol achieves this by the fact that \[
+  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
+\]
+does not include \(\cid\) whereas \[
+  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
+\]
+does.
+Thus the verification process differs for the two types of proofs.
+(An alternative approach would have been to compute them differently, \eg 
+\(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC[\overline{PRF}]_{\sk}(x)\).
+
 %\paragraph{Forging proof shares}

### 2018-05-29 paper/SystemModel.tex
Changes back to bibsp's \NewVar, \NewAlg etc.
moved more discussion parts into section

@@
 trusted witness.
-
-\emph{System model and physical assumptions.}\label{assumptions}
-Throughout this text, when we refer to a participant, say Alice, we actually 
-mean an agent which can perform cryptographic operations and communicate with 
-other local devices on Alice's behalf. We assume that every participant has a digital certificate signed by 
-some logically centralized certificate authority.
-\Eg that we can use the cryptographic keys of any national electronic identity 
-system, identity card or passport.
-We need this to prevent Sybil attacks~\cite{SybilAttack}.
-
-In practical terms, participants witness each other's participation
-using their smartphones (or similar devices) running the protocol described in
-\cref{Protocol} and uploading their testimony (\ie proof shares) to a blockchain 
-after the protest. During the protest the devices are computationally limited by 
-their batteries and need local connectivity to each other but no connection to
-any global network such as the Internet is necessary. Before and
-after the protest, we assume that the devices have global connectivity, \ie 
-Internet  connections, and are not computationally limited by any battery.
-
-\include*{MANETs}
-
-%assumptions about smartphones:
-%(This means that we essentially provide a lower bound for the participation 
-%count, since some participants might not have such a device.)
-%Sonja says: is this still true? Given mafia fraud we can't guarantee
-%that, right?

### 2018-05-29 paper/intro.tex
moved more discussion parts into section

@@
 
-\emph{Limitations and assumptions.} Some of the assumptions that are required for implementing our proposition are not yet realized% (briefly, use of smartphones, unique identities, distance bounding -
-(see \cref{assumptions} for a more detailed description). 
-In particular, not all (or even many) protesters, especially in countries with oppressive regimes, currently possess smartphones.
-In addition, digital certificates signed by a central authority are not yet widely available and if we rely on government-issued credentials, we cannot prevent the government from performing Sybil attacks --- since it can issue arbitrarily many \emph{valid} credentials.
-In this case, it does not make sense to verify any pro-government protests in which Grace's authoritarian regime wants to demonstrate its wide support, \eg~\cite{AlJazeeraOnVenezuela2017,VenezuelanStateWorkersCalledToParticipate}.
-Finally, achieving distance-bounding protocols on smartphones is currently not feasible within a meaningful range of distance needed for our scenario.
-Indeed, existing smartphones lack the required hardware to do the distance bounding fast enough.
-
-However, we believe that some assumptions might become sufficiently realistic in a near future, due to the smartphone penetration being on the rise and the increased digitalization and government-issued credentials available in some countries already now (\eg Estonia, Germany and Sweden).
-In addition, the distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
-One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results~\cite{DBonSmartphones}.
-
-Another limitation of \PRIVO is that it achieves privacy but not receipt freeness.
-This means that there is a way for Grace to efficiently verify that Alice has participated if she is able to get a copy of Alice's secret key.
-Indeed, in this case Grace can simply re-do the (deterministic) computations on the same inputs (the probability of collisions being negligible).
-
 \emph{Outline.} 

### 2018-05-29 paper/conclusions.tex
address comment

@@
-\section{Conclusions}%
-\label{Conclusions}
+\section{Conclusion}%
+\label{Conclusion}
 
-We have introduced \PRIVO, a protocol for verifiably counting
-participants at protests. Despite the verification, the privacy of the
+We have introduced \PRIVO, a protocol for verifiably counting participants at protests. Despite the verification, the privacy of the
 participants is preserved to the extent possible by their physical
@@
 and location required for protests.
+
+\sonja{move to related work section?}
 In general, none of the related works fulfills the eligibility verifiability 
@@
 device), some sort of trustworthy credential, and the willingness to
-run the protocol. If used today, \PRIVO would result in a
-considerable undercount in most scenarios, \daniel{why?} but it presents a first
+run the protocol. Owing to the network effect, until used by most participants, \PRIVO would result in a
+considerable undercount. However, it presents a first
 step toward accurate verifiable yet privacy-preserving crowd counting

### 2018-05-29 paper/protocol.tex
Changes back from footnotesize to normalsize in figures
Splits protocol section into subsections

@@
 Outcomes.
-The protocol consists of four phases: the setup, join, participation and 
-submission phases.
+The protocol consists of five phases: the setup, join, participation, 
+submission and verification phases.
+The setup is described in \cref{ProtocolSetup}.
+The join, participation and submission phases are described in 
+\cref{ProtocolDuring}.
+Finally, the verification phase is described in \cref{ProtocolVerification}.
+
 We have several roles.
@@
 identity and a cryptographic key.
-We have the protesters who want to participate in a given protest.
+The \ac{CA} is only involved in the setup phase.
+We also have the protesters who want to participate in a given protest.
 A protester can assume three different roles:
@@
 
-The setup and registration phases are the same as in Anon-Pass~\cite{AnonPass}.
-We have simply adapted their description for our notation, but tried to keep 
-them as similar as possible.
+\subsection{The setup phase}
 
-The join, participation and submission phases are illustrated in 
-\cref{fig:ProtocolOverview}.
-The participation proof share that will be constructed in the participation 
-phase is illustrated in \cref{fig:ProofFig}.
+The setup phase is only run once and is the same as in 
+Anon-Pass~\cite{AnonPass}.
+We have simply adapted their description for our notation, but otherwise tried 
+to keep them as similar as possible.
 
@@
 
+\subsection{Creating, joining, participating in a protest and submitting 
+  proofs}
+
+The join, participation and submission phases are illustrated in 
+\cref{fig:ProtocolOverview}.
+The participation proof share that will be constructed in the participation 
+phase is illustrated in \cref{fig:ProofFig}.
+
 \emph{Creating a protest: the manifesto.}
@@
   \centering
-  \footnotesize
+  %\footnotesize
   \includegraphics{proofshare.tikz}
@@
   \centering
-  \footnotesize
+  %\footnotesize
   \begin{minipage}{\linewidth}
@@
 \] for permanent storage.
-\daniel{Return \(\pi'\), whatever that should be.}
+\daniel{Return \(\pi'\), as specified as output.}
 
@@
 \] for permanent storage.
-\daniel{Return \(\pi''\), whatever that should be.}
+\daniel{Return \(\pi''\), as specified as output.}
+
+\subsection{Verifying the participation count}
+
+\dots

### 2018-05-29 paper/SystemModel.tex
Minor WIP on verification phase of protocol
coincoin

@@
 
-\emph{Defining the concept of protest.} To be able to estimate the participation count for a protest, we first need to define this concept and what should be counted.
+\emph{Defining the concept of protest.} 
+To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
 Let us start by considering some examples.
-During the demonstrations against the South Korean president in Seoul
+During the demonstrations against the South Korean president in Seoul in 2016
 \blockcquote{2016DemonstrationsInSeoul}{%
@@
 }.
-These rallies were all in the same location in the capital and repeated every 
-weekend for the duration of a few weeks.
-The Women's Marches~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
-We also have the Venezuelan demonstrations in which
-\blockcquote{2017VenezuelaProtestFrequency}{%
+These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
+The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
+We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
   anti-government demonstrators have staged daily protests across Venezuela%
@@
 }.
-Judging from these examples, the minimal common part is the cause,%
-\label{CauseIsTheCommonDenominator} but there is also a location (or area) that varies over time.
+Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.
 
 For the rest of the paper, we will refer to the organizer as Alice.
-Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Note that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time, to deploy enough personnel for crowd-control.}.
+Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
 
-Formally, we define a protest as an event that is uniquely identified by its 
-cause (\(\cid\) below), its time interval (\(t\)) and its location (area \(l\)).
+% cause identifier
+\NewVariable{\cid}{cid}
+
+Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
 More specifically, we will use the following definition.
+
+% protest
+\NewVariable{\prtst}{P}
+% subprotest
+\NewVariable{\sprtst}{p}
 
@@
 
+% proof share
+\NewVariable{\psh}{s}
+% proof shares
+\NewVariable{\pshs}{S}
+% protester identifier
+\NewVariable{\pid}{pid}
+% witness identifier
+\NewVariable{\wid}{wid}
+
 \begin{definition}[Participation-proof share]
@@
 A subset of the proof shares forms a participation proof for a protester.
+
+% proof
+\NewVariable{\prf}{\pi}
+% proofs
+\NewVariable{\prfs}{\Pi}
 

### 2018-05-29 paper/SystemModel.tex
modification of system model and properties

@@
 
-\begin{definition}[Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
-    \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
-  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location 
-  (topological connectedness is not necessary).
+\begin{definition}[Subprotest, Protest]\label{DefProtest}
+  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
+  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
   A \emph{protest} is a set of subprotests sharing the same \(\cid\).
@@
 
-The protests described in the previous examples can be captured using this definition by splitting 
-them up into subprotests.
-Each subprotest will then be captured by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
-Similarly for marches, the marching path can be divided into subprotests with 
-locations (or areas) that slightly overlap.
+The protests described in the previous examples can be captured using this definition by decomposing them up into subprotests.
+Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
+Similarly for marches, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.
 
-\emph{Formalizing the notion of crowd estimation.} Each participant who wants to 
-be counted must submit a \emph{participation proof}.
-The proof must be associated with the protest (\ie its identifier \(cid\)), time and location must coincide with any of its subprotests.
+\emph{Formalizing the notion of crowd estimation.} 
+Each participant who wants to be counted must submit a \emph{participation proof}.
+The proof must be associated with the protest (\ie its identifier \(cid\)), and its time and location must coincide with one of the subprotests.
 
-We use \emph{witnesses} to associate the proof to the location by creating a 
-\emph{proof share}.
-A witness is only allowed to create one proof share per protester to avoid the 
-risk of inflation.
+Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
+A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
+Note that a participant to a protest can take the role of a protester but also act as witness for other protesters.
+%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
 The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.
@@
 
-\begin{definition}[Participation-proof share]
-  A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
-  tuple where:
-  \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
-  and
-  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
-  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) iff 
-  \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh 
-    \sqsubseteq p\).
-  We let \(\pshs\) be the set of all proof shares.
+\begin{definition}[Proof share]
+A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: \(\cid, t, l\) are as in \cref{DefProtest};
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh \sqsubseteq p\).
+  We define \(\pshs\) as the set of all proof shares.
 \end{definition}
@@
   \label{DefParticipationProof}
-  A \emph{participation proof} of protester with pseudonym \(\pid\) 
-  participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
+  A \emph{participation proof} of protester with pseudonym \(\pid\) participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
   \begin{multline}
@@
   \end{multline}
-  of all proof shares with the same protester and protest identifiers, 
-  witnessing time interval \(t\) and location \(l\) is within those of the 
-  protest.
+  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) is within those of the protest.
 We denote by \(\prfs\) the set of all proofs.
@@
 We can now define the participation count as follows.
+
 \begin{definition}[Participation count]
@@
       \str(\prf_{i,j})\geq \theta \right\}
-  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
-  threshold \(\theta\).
+  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a threshold \(\theta\).
 \end{definition}
-The strength function \(\str\) can be used to regulate trust in witnesses.
-One example would be for \(\str\) to return the number of unique witnesses and 
-thus let \(\theta\) to be the threshold of the number of required witnesses.
-Another example would be to return the number of proof shares issued by trusted 
-witnesses and set \(\theta = 1\) to require at least one proof share issued by a 
-trusted witness.
+
+The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
+One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
+%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
+Another example would be to return the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

### 2018-05-30 paper/DB-anon-cred.tex
related work, building blocks

@@
-\subsection{Distance bounding anonymous credentials}%
+\subsection{Distance-bounding anonymous credentials}%
 \label{DB-anon-cred}
@@
 
-There is a protocol which provide \ac{DBPK} with all the desired properties 
-from above, ProProx~\cite{ProProx}.
-(Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of 
-Knowledge, instead of \ac{DBPK}.)
-However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie 
-protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we 
-need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = 
-  g^\alpha]\)).
-To realize this, we will now introduce such a protocol that will allow us to do 
-\ac{DB} anonymous credentials.
+One protocol exists in the literature providing \ac{DBPK} with all the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge, instead of \ac{DBPK}.}.
+However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = g^\alpha]\)).
+To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
 
@@
 
-\emph{Reattempting \iacl{DB} Schnorr protocol.}
-In the original \ac{DB} paper by \citet{DistanceBounding}, they show how to 
-design a distance-bounding protocol based on the Schnorr identification 
-scheme~\cite{Schnorr}.
-That \ac{DB} Schnorr protocol was shown to be prone to distance 
-hijacking~\cite{DistanceHijacking}.
-(It was not secure against terrorist fraud either.)
-We now propose another way to turn the Schnorr protocol into \iac{DB} protocol 
-which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an 
-impersonating verifier (\ie it is public-key).
+\emph{Reattempting a distance-bounding Schnorr protocol.}
+In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
+However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
+We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.
 
 We present the protocol in \cref{SchnorrFigure}.
-The difference from the original Schnorr protocol is that the prover commits to 
-one random value but the verifier sends two challenges.
-The verifier presents to the prover which commitment and challenge to use 
-during the \ac{DB} phase.
+The main difference with the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
+The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.
 
@@
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge we must choose \(k\) logarithmically in the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with respect to the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
 This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
@@
 \Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with \(r_i\).
-
 The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
 The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
-Thus the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
+Afterwards, the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
 Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
-However at this point the adversary must wait for \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
+However, at this point the adversary must wait for \(b_{l+1}\) challenge bits from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
 
-The protocol is \ac{DBTF} resistant, if the malicious prover gives both 
-responses to the adversary, the adversary can compute the secret key.
-This follows from the fact that it is \iac{ZKPK}, \ie there is an extractor that 
-can extract the secret.
-
-The protocol is also secure against distance hijacking due to the fact that it 
-is the authenticating bit string that is used during the \ac{DB} phase, not the 
-challenge bit string as in Brands-Chaum.
+The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
+This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can extract the secret.
+The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bit string as in the protocol of Brands-Chaum.

### 2018-05-30 paper/DistanceBounding.tex
related work, building blocks

@@
 
-\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent 
-relay attacks in contactless communications in which the adversary forwards a 
-communication between a prover and a possibly far-away verifier to authenticate. 
-These attacks cannot be prevented by cryptographic tools as they are independent 
-of the semantics of the messages exchanged, so mechanisms ensuring the physical 
-proximity between a verifier and a prover must be used.
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
+These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
+As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
 \Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
 Time critical phases are complemented by slow phases during which the time is not taking into account. 
-At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate and in his vicinity.
+At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
+In this sense, \Ac{DB} protocols combines at the same time the classical properties of authentication protocols with the possibility of verifying the physical proximity.
 
-The main security requirements of \ac{DB} protocols can be summarized as follows:
+The main attacks against \ac{DB} protocols can be summarized as follows:
+%Seb: the following names of attacks should all have the first letters in capital
 \begin{itemize}
-  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using 
-    a far-away honest prover.
-  \item\acf{DBTF}: a legitimate but malicious prover helps a 
-    close-to-the-verifier accomplice to authenticate.
-  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the 
-    verifier on the distance between them.
-  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an 
-    honest prover close to the verifier.
-  \item \acf{DBIF}: the adversary plays against a simplified version of the 
-    protocol without any distance estimation.
+  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
+  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item \acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
+%Seb: the two following properties should be defined more precisely
+  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
+  \item \acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by 
-\citet{DB-BMV} and another by \citet{DB-DFKO}.
+There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
 The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
-Indeed, in this context it does not make sense to protect against the verifier 
-as he can easily impersonate the prover as he has a knowledge of his secret key.
+Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
 There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
@@
 The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier 
-who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials 
-(which we do in \cref{DB-anon-cred}).
-The anonymous credential system will affect what properties we require of the \ac{DBPK}, (\eg that it must be \iac{PKE} for discrete logarithms).
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
+More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
+The choice of the anonymous credential system will affect the properties we require of the \ac{DBPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-05-30 paper/SystemModel.tex
Finishes verification part of protocol
This describes Jane (fixes #101).

--- 2018-05-29 paper/SystemModel.tex
@@
 
+% cause identifier
+\NewVariable{\cid}{cid}
+
 Formally, we define a protest as an event that is uniquely identified by its 
@@
 More specifically, we will use the following definition.
+
+% protest
+\NewVariable{\prtst}{P}
+% subprotest
+\NewVariable{\sprtst}{p}
 
@@
 
-\begin{definition}[Participation-proof share]
+% proof share
+\NewVariable{\psh}{s}
+% proof shares
+\NewVariable{\pshs}{S}
+% protester identifier
+\NewVariable{\pid}{pid}
+% witness identifier
+\NewVariable{\wid}{wid}
+
+\begin{definition}[Participation-proof share]%
+  \label{DefProofShare}\label{DefProofShares}
   A \emph{participation-proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a 
@@
 
+% proof
+\NewVariable{\prf}{\pi}
+% proofs
+\NewVariable{\prfs}{\Pi}
+
 \begin{definition}[Participation proof]%
-  \label{DefParticipationProof}
+  \label{DefParticipationProof}\label{DefParticipationProofs}
   A \emph{participation proof} of protester with pseudonym \(\pid\) 
@@
 We can now define the participation count as follows.
-\begin{definition}[Participation count]
+\begin{definition}[Participation count]%
+  \label{DefParticipationCount}
   We define the \emph{participation count} of a protest \(\prtst\) (as in 
@@
     \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
-      \str(\prf_{i,j})\geq \theta \right\}
+      \str(\prf_{i,P})\geq \theta \right\}
   \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 

### 2018-05-30 paper/protocol.tex
Minor WIP on verification phase of protocol
Finishes verification part of protocol
This describes Jane (fixes #101).

@@
 
-\dots
+There are various ways for verifying the participation count, we will cover the 
+two suggested just after \cref{DefParticipationCount}.
+In the first approach, we do not trust individual witnesses, instead we 
+\emph{assume} that it is difficult for Alice to find more than \(\theta\) 
+witnesses willing to collude.
+Thus we require at least \(\theta\) witnesses to accept a participation proof 
+as valid.
+In the second approach, we trust certain witnesses but not others.
+Thus to accept a participation proof as valid, we require at least one trusted 
+witness.
+
+\paragraph{Without trusted witnesses}
+
+To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
+\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i = 
+  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime 
+    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
+\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
+latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
+\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq 
+  l\).
+Any proof share that does not verify correctly will be discarded.
+At this point, the verifier has constructed the set \(S\) from 
+\cref{DefProofShares} and can thus construct any participation proof 
+\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
+
+Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then 
+the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) 
+as in \cref{DefParticipationCount}.
+
+\paragraph{With trusted witnesses}
+
+For the this approach, we must adapt the selection of proof shares from the 
+blockchain by selecting only proof shares issued by witnesses that the verifier 
+trusts.
+Thus the verifier must be able to recognize proof shares issued by trusted 
+witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
+So trusted witnesses must complement their proofs by a digital signature that 
+the verifier can recognize.
+
+When \(S\) only contains proof shares issued by witnesses the verifier trusts, 
+we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
+Then the verifier can compute the participation count \(|\prfs_P^{\str, 
+    \theta}|\) as in \cref{DefParticipationCount}.

### 2018-05-30 paper/LocationProofs.tex

@@
 
-Some LBS only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
-In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the LBS provider. 
+Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
+In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
 One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
@@
 A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
-Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus 
-raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-\seb{to do add the corresponding reference}
-However, some location proofs systems, such as PROPS, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location. 
-\PRIVO share some similarities with PROPS, although their objective is quite different as we aim at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+\seb{add references to location proof systems} 
+Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
+However, some location proofs systems, such as PROPS \cite{DBLP:conf/srds/GambsKRT14}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location.
+\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-05-30 paper/RelatedWork.tex

@@
 
+In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.
+
 \subsection{Crowd counting methods}
 
-The seemingly most commonly used method for counting crowds at protests is 
-\emph{Jacobs's method}, \cf~\cite{%
-  2016DemonstrationsInSeoul,%
-  BBCHowToCountProtestNumbers,%
-  HowWillWeKnowTrumpInauguralCrowdSize,%
-  TheXManMarch,%
-  TheCrowdNumbersGame,%
-}.
-It is a manual method devised in the 1960s relying on aerial photos of the event.
-The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions and finally sums them up to get an estimate of the global count.
-Clearly this method is prone to errors as it is based on estimates.
-It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same photos.
-However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial photos.}.
+The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
+This manual method devised in the 1960s relies on aerial pictures of the event.
+The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
+Clearly, this method is prone to errors as it is based on estimates.
+It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
+However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
 We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
@@
 When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
-However, this is prone to cheating --- and subject to a variety of 
-misinformation techniques --- and the best we can do is to employ forensic 
-methods to try to detect any modifications or other attempts at fraud.
+However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
+From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
+For instance, there is a risk that participants are recognizable from the material if they do not wear masks.
 
-From a privacy perspective, all techniques based on photo or video material are 
-as privacy preserving as the protesters make themselves.
-There is a risk that participants are recognizable from the material if they do 
-not wear masks.
-
-Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
-based on a selected space.
+Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
 Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
-This is similar to the method usually used by police (\eg for the protests in 
-Seoul):
+This is similar to the method usually used by police (\eg during the protests in Seoul):
 \blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
-  fill a space of 
+  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 
   3.3 square meters
@@
 \citet{NNCrowdCounting}).
-This class of methods requires photos or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
-They are generally based on machine learning, and thus also require a training 
-dataset to work.
-In the work by \citet{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
+This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
+They are generally based on machine learning techniques, and thus also require a training dataset to work.
+In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
 Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
-Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but this might still be difficult. 
-Note also that while automatic face recognition can help verifiability, it has a high impact on privacy.
-Also, it is difficult (if not impossible) to not count people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
+Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
+Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
+In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
 In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
-However, it is still difficult to capture the entire location on surveillance 
-video, which diminishes the argument for an upper bound in practice.
+Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
 The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
 
-Another problem for all the above methods is exemplified by the demonstrations 
-in Seoul:
+Another problem for all the above methods is exemplified by the demonstrations in Seoul:
 \blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{t}he demonstrators not only gather in open space, but also small 
-  alleys and between buildings%
+  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
 }.
 In this situation it is very difficult to faithfully capture the situation.
-Even if the photo material is taken from different angles, we will have the additional problem of not counting people twice.
+Indeed, even if the scene is taken from different angles, there is the additional problem of not counting people twice.
 
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical 
-analytics company tried to estimate the number of participants using their 
-technology.
-They scanned for MAC addresses emitted from the Wi-Fi of participants' smartphones.
-However, this method required many assumptions:
+During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
+In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
+However, in order to work this method makes many additional assumptions:
 \blockcquote{2016DemonstrationsInSeoul}{%
-  The company presumed that about half of smartphone users usually leave their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
+The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
 It also assumed that about 20\% of the smartphone signals were repetition from the same device.
 }
-This method cannot provide any verifiability, as we must trust the company in doing the measurements correctly and to be honest about when and where they did them.
-As MAC address randomization get wider adoption, this will be even more difficult, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.
+This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
+In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.
 
@@
 However, there are several problems with this approach.
-First, it will be difficult to register only the participants' phones, as many 
-bystanders will also be counted.
-It is also difficult to differentiate between the protesters and the counter-protesters.
-Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI will not be
-transmitted in plaintext anymore. %need to cite?
-Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in the relation to the protest.
+First, it will be difficult to register only the participants' phones, as many bystanders will also be counted.
+Thus, it will not be possible to distinguish clearly between the protesters and the counter-protesters.
+Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI number will not be transmitted anymore in plaintext.
+%need to cite?
+Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in relation to the protest.
 
-In general for all of the above methods, the more a crowd spreads out, the more 
-difficult it will be to determine its size.
+In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
 In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulty capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
+These methods also have difficulty to capture the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
 
 One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
-This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the photos.
+This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
 However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
@@
 This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Grace's regime, who shuts 
-down the cellular network or Internet backbone as a means to censor the protest.
+For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.
 
-Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which 
-uses epidemic spreading of crowd-size estimates by device-to-device 
-communication to count crowds in dense urban environments with high 
-node-mobility and churn. There is, however, no consideration of a potentially 
-adverserial setting and thus no verification or checks on eligibility. 
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense 
-areas, avoids double counting, but again, only work for honest participants.
+Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
+However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility. 
+Finally, DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
+\seb{mention the method used by Le Monde}
 

### 2018-05-30 paper/SystemModel.tex

--- 2018-05-29 paper/SystemModel.tex
@@
 }.
-Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.
+Generalizing from these examples, the minimal common part is the cause,%
+\label{CauseIsTheCommonDenominator} while the location (or area) considered 
+varies over time.
 
@@
 
-\begin{definition}[Proof share]
-A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
-  We say that \(\psh\) is part of a subprotest \(p = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by \(\psh \sqsubseteq p\).
+\begin{definition}[Proof share]%
+  \label{DefProofShare}\label{DefProofShares}
+  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
+  \(\cid, t, l\) are as in \cref{DefProtest};
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
+  and
+  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if 
+  and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
+  \(\psh \sqsubseteq \sprtst\).
   We define \(\pshs\) as the set of all proof shares.
@@
 \begin{definition}[Participation proof]%
-  \label{DefParticipationProof}
-  A \emph{participation proof} of protester with pseudonym \(\pid\) participating in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
+  \label{DefParticipationProof}\label{DefParticipationProofs}
+  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
+  participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
   \begin{multline}
@@
 We can now define the participation count as follows.
-
-\begin{definition}[Participation count]
+\begin{definition}[Participation count]%
+  \label{DefParticipationCount}
   We define the \emph{participation count} of a protest \(\prtst\) (as in 
-  \cref{DefParticipationProof}) as the cardinality \(|\prfs_{P}^{\str,\theta}|\) 
-  of the set of participation proofs \[
+  \cref{DefParticipationProof}) as the cardinality 
+  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
     \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
-      \str(\prf_{i,j})\geq \theta \right\}
-  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a threshold \(\theta\).
+      \str(\prf_{i,P})\geq \theta \right\}
+  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
+  threshold \(\theta\).
 \end{definition}

### 2018-05-30 paper/ZKPK.tex
Fixes subsection error
Removes number from non-referenced eqn

@@
-\subsubsection{Zero-knowledge proofs of knowledge}%
+\subsection{Zero-knowledge proofs of knowledge}%
 \label{ZKPK}
@@
 \begin{equation}\label{PKexample}
-  \PK{\alpha, \beta, \gamma}
-  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
+  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma]
 \end{equation}
-which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that 
-\(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), 
-respectively.
-Greek letters are known only to the prover and for which the prover wishes to 
-prove knowledge, all other letters are known by the verifier.
+which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
+Greek letters are known only to the prover and use for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.
 
-When a proof of knowledge is turned into a signature using the Fiat-Shamir 
-heuristic~\cite{FiatShamirHeuristic}, we will denote it as
+When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
 \begin{equation*}\label{SPKexample}
-  \sigma\gets \SPK{\alpha, \beta, \gamma}
-  {y = g^\alpha h^\beta \land y' = \hat g^\gamma}
-  {m},
+  \sigma\gets \SPK[\alpha, \beta, \gamma]%
+  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
+  [m],
 \end{equation*}
-which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knew 
-\(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = 
-  \hat{g}^\gamma\).
+which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).

### 2018-05-30 paper/DistanceBounding.tex
Changes notation from DBPK to PPK (fixes #110)

@@
 The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
 More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
-The choice of the anonymous credential system will affect the properties we require of the \ac{DBPK} (\eg that it must be \iac{PKE} for discrete logarithms).
+The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-05-30 paper/analysis-security.tex
Fixes typo: g_T^{\sk+x} -> g_T^{1/(\sk+x)}
Adds Jane to security analysis too
Changes notation from DBPK to PPK (fixes #110)

@@
 (An alternative approach would have been to compute them differently, \eg 
-\(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC[\overline{PRF}]_{\sk}(x)\).
+\(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = 
+  g_T^{1/(\sk+x+1)}\).)
 
@@
 The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
-and to verify the \ac{DBPK}.
+and to verify the \ac{PPK}.
 \daniel{This assumes that I will do the changes to hide \(\cid\) from the 
-  witness in the \ac{DBPK}.}
+  witness in the \ac{PPK}.}
 Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 

### 2018-05-30 paper/protocol.tex
Changes notation from DBPK to PPK (fixes #110)

--- 2018-05-25 paper/protocol.tex
@@
       P\leftrightarrow W\colon &
-        \DBPK\mleft\{ (\sk_P) : \mright. \\
+        \PPK\mleft\{ (\sk_P) : \mright. \\
         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
@@
 \end{align*}
-Then they run the following \ac{DBPK} with the participant as the prover and the 
+Then they run the following \ac{PPK} with the participant as the prover and the 
 witness as the verifier:
@@
   \mleftright
-  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
     \pid = g_T^{1/(k+\cid)} \right\}.
@@
 Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
-be run as \iac{DBPK} and be repeated multiple times to achieve security).
+be run as \iac{PPK} and be repeated multiple times to achieve security).
 The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
@@
 \] for permanent storage.
-\daniel{Return \(\pi''\), whatever that should be.}
+\daniel{Return \(\pi''\), as specified as output.}

### 2018-05-30 paper/LocationProofs.tex

@@
 Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-However, some location proofs systems, such as PROPS \cite{DBLP:conf/srds/GambsKRT14}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location.
-\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that 
+provides strong privacy guarantees along with the possibility of verifying the 
+claim of the location. \PRIVO share some similarities with PROPS, although 
+their objective is quite different as it aims at verifying a global property of 
+the population (\ie crowd estimation) in contrast to checking the location 
+claim made by a user, which is an individual property.

### 2018-05-30 paper/protocol.tex
WIP on hiding cid

@@
         \PPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid] \quad \land \\
         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
@@
         & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
-        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
+        & \qquad \wid = \ACprf[_{\sk_W}][\pid] \quad \land \\
         & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
@@
         & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid] \quad \land \\
         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
@@
 
-\emph{Participating: \(\pi\gets
+\emph{Participating: \(\psh\gets
     \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
@@
   \mleftright
-  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    \pid = g_T^{1/(k+\cid)} \right\}.
+  \PPK\left\{(k, r, r', \cid, o) : \right. \\
+    v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land \pid = g_T^{1/(k+\cid)} \land 
+    \\
+    \left. c = \ACcommit[\cid, o]
+  \right\}.
 \end{multline*}
@@
 Then the witness returns \((\wid, t_s', l)\) to the participant.
-Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
+Now both the participant and the witness have the tuple \(\psh = (\pid, \wid, 
   t_s, t_s', l)\) which constitutes a proof share of the participant 

### 2018-05-30 paper/RelatedWork.tex
le monde references

@@
 However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.
-Finally, DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
-\seb{mention the method used by Le Monde}
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
+
+Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability of privacy guarantees.
 

### 2018-05-30 paper/RelatedWork.tex
expand requirements in conclusion, leave related work

@@
 
-Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability of privacy guarantees.
+Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
 

### 2018-05-30 paper/conclusions.tex

@@
 
-\sonja{move to related work section?}
-In general, none of the related works fulfills the eligibility verifiability 
+In general, none of the related works fulfills the eligibility
+verifiability (one proof per person, temporal and spatial eligibility -
 \cref{%
@@
   TemporallyRelated,SpatiallyRelated,%
-}.
-To some extent, some techniques do fulfill \cref{DesignatedEvent}, since people 
+}).
+To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent)}, since people 
 usually use placards in the protests.

### 2018-05-30 paper/DistanceBounding.tex
Capitalize DB frauds in list

--- 2018-05-30 paper/DistanceBounding.tex
@@
 \begin{itemize}
-  \item \acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
-  \item \acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
+  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
 %Seb: the two following properties should be defined more precisely
-  \item \acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
-  \item \acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
+  \item \Acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
+  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
 \end{itemize}

### 2018-05-30 paper/conclusions.tex

@@
 In general, none of the related works fulfills the eligibility
-verifiability (one proof per person, temporal and spatial eligibility -
+verifiability (one proof per person, temporal and spatial eligibility ---
 \cref{%
@@
 }).
-To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent)}, since people 
+To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people 
 usually use placards in the protests.

### 2018-05-30 paper/protocol.tex

--- 2018-05-30 paper/protocol.tex
@@
 
-\subsection{Verifying the participation count}
+\subsection{Verifying the participation count}%
+\label{ProtocolVerification}
 

### 2018-05-30 paper/RelatedWork.tex
le monde for marches

@@
 
-Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
+Trusted infrastructure, for example deployed by a collection of  media outlets to count protesters passing a point on marches~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
 

### 2018-05-30 paper/SystemModel.tex
WIP on hiding cid
name Jane

@@
 %Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
-Another example would be to return the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.
+Another example would be to return the number of proof shares issued
+by trusted witnesses (e.g., the independent journalist Jane) and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

### 2018-05-30 paper/protocol.tex
name Jane

--- 2018-05-30 paper/protocol.tex
@@
       P\leftrightarrow W\colon &
-        \PPK\mleft\{ (\sk_P) : \mright. \\
+        \DBPK\mleft\{ (\sk_P) : \mright. \\
         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
@@
 \end{align*}
-Then they run the following \ac{PPK} with the participant as the prover and the 
+Then they run the following \ac{DBPK} with the participant as the prover and the 
 witness as the verifier:
@@
   \mleftright
-  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
     \pid = g_T^{1/(k+\cid)} \right\}.
@@
 Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
-be run as \iac{PPK} and be repeated multiple times to achieve security).
+be run as \iac{DBPK} and be repeated multiple times to achieve security).
 The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
@@
 Thus to accept a participation proof as valid, we require at least one trusted 
-witness.
+witness (journalist Jane).
 

### 2018-05-31 paper/protocol.tex
Adds more WIP on hiding cid (#89)
Fixes two comments in protocol

@@
 Finally, the participant uploads the tuple \[
-  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
+  \pi' = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
 \] for permanent storage.
-\daniel{Return \(\pi'\), as specified as output.}
 
@@
 Finally, the witness uploads the tuple \[
-  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
+  \pi'' = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
 \] for permanent storage.
-\daniel{Return \(\pi''\), as specified as output.}
 

### 2018-05-31 paper/protocol.tex
Adapts names of returns from Submission

@@
 
-\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
+\emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
     l]\).}
@@
 Finally, the participant uploads the tuple \[
-  \pi' = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
+  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
 \] for permanent storage.
 
-\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
+\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
 The witness should, just as the participant, commit the proof-share data to the 
@@
 Finally, the witness uploads the tuple \[
-  \pi'' = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
+  \psh_W = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
 \] for permanent storage.

### 2018-05-31 paper/DB-anon-cred.tex

@@
 
-\ProvideDocumentCommand{\DBPK}{o o}{\ensuremath{%
-    \operatorname{DBPK}%
+\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
+    \operatorname{PPK}%
     \IfValueT{#1}{%
@@
 
-One protocol exists in the literature providing \ac{DBPK} with all the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, for Proof of Proximity of Knowledge, instead of \ac{DBPK}.}.
-However, ProProx provides \iac{DBPK} protocol for quadratic residues (\ie protocols of the form \(\DBPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{DBPK} protocol for discrete logarithms (\ie \(\DBPK[\alpha][a = g^\alpha]\)).
+One protocol exists in the literature that provides \acp{PPK} with all the 
+desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
+  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
+  shorter notation.}.
+However, ProProx provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
 To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.

### 2018-05-31 paper/protocol.tex
Fixes intro in protocol, adds missing labels

@@
 
-We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtest 
-Outcomes.
+We now present \PRIVO, a protocol for securely and privately verifying crowd 
+counts.
 The protocol consists of five phases: the setup, join, participation, 
@@
 
-\subsection{The setup phase}
+\subsection{The setup phase}%
+\label{ProtocolSetup}
 
@@
 \subsection{Creating, joining, participating in a protest and submitting 
-  proofs}
+  proofs}%
+\label{ProtocolDuring}
 

### 2018-05-31 paper/intro.tex
Comment's on Seb's comment in contribution

@@
 More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr's protocol in the \ac{ZKPK} used in anonymous credentials. 
-%Seb: I have put the following sentence because due to the amount of current work recently in distance-bounding, I believe that our sentence should be made more reasonable 
-%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
+The latter allows us to replace the use of the plain Schnorr's protocol in the 
+\ac{ZKPK} used in anonymous credentials.
+\seb{I have put the following sentence because due to the amount of current 
+  work recently in distance-bounding, I believe that our sentence should be 
+  made more reasonable:
+  \enquote{and thus we are, to the best of our knowledge, the first to provide 
+    \ac{DB} anonymous credentials.}}
+\daniel{I quickly looked through the papers from 2015--2018, none seem to do 
+  this, they are more about authenticating identities (possibly anonymously), 
+  but not fully fledged anonymous credentials --- where we can prove \eg that 
+  Alice is indeed older than 18 without revealing her age and that it is not a 
+  relay (due to \ac{DB}).}
 
@@
 \PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}).
-Finally, we conclude with a discussion and futures works in \cref{Conclusion}.
+Finally, we conclude with a discussion and future works in \cref{Conclusion}.

### 2018-05-31 paper/DB-anon-cred.tex
Adds WIP table of security for DB Schnorr
Addresses Seb's comment on describing Anon-Pass

@@
 
-\emph{Reattempting a distance-bounding Schnorr protocol.}
+\emph{Reattempting a distance-bounding Schnorr protocol.}%
+\label{DBSchnorr}
 In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.

### 2018-05-31 paper/conclusions.tex
Highlights contribution of DB anon creds

@@
 and location required for protests.
+
+Of separate interest, we can now provide distance bounding for authenticating 
+more general attributes than provided by previous \ac{DB} protocols.
+All privacy-preserving \ac{DB} protocols have so far focused on identity-based 
+authentication, but not authentication of general attributes, as is the case 
+for anonymous credentials.
+With our contribution, Alice can now prove more complex statements to Bob, \eg 
+that she is older than 18 but younger than 40 without revealing her actual age,  
+and at the same time Bob can be sure that Alice is not just relaying messages 
+from her older sister Carol.
 

### 2018-05-31 paper/intro.tex
Highlights contribution of DB anon creds

--- 2018-05-29 paper/intro.tex
@@
 More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr's protocol in the \ac{ZKPK} used in anonymous credentials. 
-%Seb: I have put the following sentence because due to the amount of current work recently in distance-bounding, I believe that our sentence should be made more reasonable 
-%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
+The latter allows us to replace the use of the plain Schnorr's protocol in the 
+\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
+knowledge, the first to provide \ac{DB} anonymous credentials.
 

### 2018-05-31 paper/conclusions.tex
anon-pass explanation, future work tamarin

@@
 some assumptions become more realistic.
+
+For future work, a recently published model for formal verification
+of distance-bounding protocols~\cite{TamarinDB} looks promising to
+analyze and strengthen the properties of our protocol, especially once
+the model and tool are extended to include terrorist-fraud attacks and
+other formalizations of attacks and protocol properties as outlined as
+future work by the authors.

### 2018-05-31 paper/conclusions.tex
removed redundancies in discussion, made subsections, changed title, added conclusion

@@
 
-Finally, most of the current methods are estimates, with quite some error 
-margins. While \PRIVO is an actual count and not an estimate, its
-accuracy for the total number of participants hinges on the
+Finally, most of the current methods are estimates, with quite some
+error margins. While \PRIVO is an actual count and not an estimate,
+its accuracy for the total number of participants hinges on the
 participants having the necessary equipment (a smartphone or similar
 device), some sort of trustworthy credential, and the willingness to
-run the protocol. Owing to the network effect, until used by most participants, \PRIVO would result in a
-considerable undercount. However, it presents a first
-step toward accurate verifiable yet privacy-preserving crowd counting
-by showing how it can be done in theory at least and in practice once
-some assumptions become more realistic.
+run the protocol. Owing to the network effect, until used by most
+participants, \PRIVO would result in a considerable
+undercount. However, it presents a first step toward accurate
+verifiable yet privacy-preserving crowd counting by showing how it can
+be done in theory at least and in practice once some assumptions
+concerning hardware and e-identities become more realistic. While the
+the necessary technologies are not yet available in most authoritarian
+regimes, some of them are in several democracies. We believe that it
+is important to implement systems such as ours also there to support
+the maintenance of democratic processes.
 

### 2018-06-01 paper/SystemModel.tex
modifications of section up to the analysis

--- 2018-05-30 paper/SystemModel.tex
@@
 Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
-
 % cause identifier
 \NewVariable{\cid}{cid}
-
 Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
@@
   \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); 
-  and
-  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
-  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if 
-  and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
   \(\psh \sqsubseteq \sprtst\).
@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
-  participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
+  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
   \begin{multline}
@@
   \label{DefParticipationCount}
-  We define the \emph{participation count} of a protest \(\prtst\) (as in 
-  \cref{DefParticipationProof}) as the cardinality 
+  We define the \emph{participation count} of a protest \(\prtst\) (as in \cref{DefParticipationProof}) as the cardinality 
   \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
@@
 %Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
-Another example would be to return the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.
+Another possibility would be to also have a particular type of witnesses, called trusted witnesses, participating to the protest. 
+For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
+In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

### 2018-06-01 paper/intro.tex
modifications of section up to the analysis

@@
 
-Our second contribution is an adaptation of the Schnorr's protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
 Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
 More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr's protocol in the 
-\ac{ZKPK} used in anonymous credentials and thus we are, to the best of our 
-knowledge, the first to provide \ac{DB} anonymous credentials.
+The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
+%Seb: once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
+%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
 

### 2018-06-01 paper/conclusions.tex
detailed pass on the paper

@@
 
-We have introduced \PRIVO, a protocol for verifiably counting participants at protests. Despite the verification, the privacy of the
-participants is preserved to the extent possible by their physical
-presence at the protest. To achieve that, we adapted the Schnorr
-protocol to develop distance-bounding anonymous credentials. Except for receipt
-freeness, which we cannot guarantee if the adversary gets access to
-Alice's device and secret PRF key after her participation has
-been witnessed and before she had a chance to
-delete it, \PRIVO
-fulfills all verification and privacy properties we derived from those
-of electronic voting complemented by the specific constraints on time
-and location required for protests.
+In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
+Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
+To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. 
+Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
 
-Of separate interest, we can now provide distance bounding for authenticating 
-more general attributes than provided by previous \ac{DB} protocols.
-All privacy-preserving \ac{DB} protocols have so far focused on identity-based 
-authentication, but not authentication of general attributes, as is the case 
-for anonymous credentials.
-With our contribution, Alice can now prove more complex statements to Bob, \eg 
-that she is older than 18 but younger than 40 without revealing her actual age,  
-and at the same time Bob can be sure that Alice is not just relaying messages 
-from her older sister Carol.
+Of separate interest, we have also build distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
+All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
+With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
 
@@
 }).
-To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people 
-usually use placards in the protests.
-Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
-not individual verifiability (\cref{IndividualVerif}).
-If they would provide individual verifiability, they would likely violate the 
-privacy requirements.
+To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
+Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
+Moreover, if they would provide individual verifiability, they would likely violate the privacy requirements.
 
-Finally, most of the current methods are estimates, with quite some
-error margins. While \PRIVO is an actual count and not an estimate,
-its accuracy for the total number of participants hinges on the
-participants having the necessary equipment (a smartphone or similar
-device), some sort of trustworthy credential, and the willingness to
-run the protocol. Owing to the network effect, until used by most
-participants, \PRIVO would result in a considerable
-undercount. However, it presents a first step toward accurate
-verifiable yet privacy-preserving crowd counting by showing how it can
-be done in theory at least and in practice once some assumptions
-concerning hardware and e-identities become more realistic. While the
-the necessary technologies are not yet available in most authoritarian
-regimes, some of them are in several democracies. We believe that it
-is important to implement systems such as ours also there to support
-the maintenance of democratic processes.
+Finally, most of the current methods are estimates, with quite some error margins. 
+While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on theparticipants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
+Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
+However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
+While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
+We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.
 
-For future work, a recently published model for formal verification
-of distance-bounding protocols~\cite{TamarinDB} looks promising to
-analyze and strengthen the properties of our protocol, especially once
-the model and tool are extended to include terrorist-fraud attacks and
-other formalizations of attacks and protocol properties as outlined as
-future work by the authors.
+For future work, a recently published model for formal verification of distance-bounding protocols~\cite{TamarinDB} looks promising to analyze and strengthen the properties of our protocol, especially once the model and tool are extended to include terrorist-fraud attacks and other formalizations of attacks and protocol properties as outlined as future work by the authors.

### 2018-06-01 paper/DB-anon-cred.tex

--- 2018-05-31 paper/DB-anon-cred.tex
@@
 
-One protocol exists in the literature that provides \acp{PPK} with all the 
-desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
-  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
-  shorter notation.}.
-However, ProProx provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
+One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+However, ProProx is not secure against a malicious verifier and does not provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
 To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
@@
 The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
-This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can extract the secret.
-The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bit string as in the protocol of Brands-Chaum.
+This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
+The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bitstring as in the protocol of Brands-Chaum.

### 2018-06-01 paper/DistanceBounding.tex
Removes Seb's comment that has been fixed

@@
-\subsection{Distance bounding}%
+\subsection{Distance-bounding protocols}%
 \label{DistanceBounding}
@@
 The main attacks against \ac{DB} protocols can be summarized as follows:
-%Seb: the following names of attacks should all have the first letters in capital
 \begin{itemize}
@@
 %Seb: the two following properties should be defined more precisely
-  \item \Acf{DBDH}: similar to \ac{DBDF}, sometimes using the presence of an honest prover close to the verifier.
+  \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
   \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
@@
 There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
+Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
 The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
+This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
 More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).

### 2018-06-01 paper/TimeStamp.tex

@@
 
-%\NewScheme{\TS}{TS}
+\NewScheme{\TS}{TS}
 \NewAlgorithm{\TSget}{\TS.\!Get}
@@
 
-We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
-\(\TSstamp\) and \(\TStime\) such that
+We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), \(\TSstamp\) and \(\TStime\) such that
 \begin{itemize}
@@
 
-We can instantiate \(\TS\) using a blockchain, \eg OmniLedger~\cite{OmniLedger}.
-The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and 
-return the identifier of the block into which \(x\) was included.
+We can instantiate \(\TS\) using a blockchain such as for instance OmniLedger~\cite{OmniLedger}.
+The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the identifier of the block into which \(x\) was included.
 \(\TSget\) will return the hash of the current head of the chain.
-This value is difficult to predict since it depends on all submitted transactions and usually some randomness (\eg nonces and miners' secrets).
+This value is difficult to predict since it depends on all submitted transactions and additional randomness (\eg nonces and miners' secrets).
 The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
-Having a dedicated blockchain for a protest will not do, and thus it is better 
-to use a blockchain which is used for other things too.
+%Seb: why is the idea of using a dedicated blockchain not appropriate? we should give more arguments to justify it
+Having a dedicated blockchain for a protest is not appropriate, and thus it is better to use a generic blockchain that is used also for other things.
 
@@
 First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
-We will use this to ensure verifiability as the data must remain to be verifiable.
+Immutability will also ensure verifiability as the data must remain available to be verifiable.
 Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
-For instance using blockchains, we can store the hash of the block in which our 
-data was committed, while this block remains we are sure that our data remains 
-committed --- even if we no longer remember what our data looked like.
+For instance in a blockchain, we can store the hash of the block in which our data was committed.
+As a consequence as this block will remain, we are also sure that our data stay committed.% --- even if we no longer remember what our data looked like.

### 2018-06-01 paper/intro.tex

@@
 Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}).
-\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}) as well as a discussion of the performance and implementation issues (\cref{PerformanceAnalysis}).
+\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
 Finally, we conclude with a discussion and future works in \cref{Conclusion}.

### 2018-06-04 paper/LocationProofs.tex

@@
 In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
-A location proof architecture is a system by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof.
-\seb{add references to location proof systems} 
+A location proof system is a architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
 Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that 
-provides strong privacy guarantees along with the possibility of verifying the 
-claim of the location. \PRIVO share some similarities with PROPS, although 
-their objective is quite different as it aims at verifying a global property of 
-the population (\ie crowd estimation) in contrast to checking the location 
-claim made by a user, which is an individual property.
+However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location.
+\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-06-04 paper/properties.tex

@@
 
-In our setting, we have two potential adversaries: Alice and Grace.
-Alice is a participant to the protest and thus she might be also interested in 
-manipulating the system to increase the count (\eg she might have an incentive 
-to do so as an activist).
-In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
-count but also additionally to deanonymize some of the participants in order to 
-arrest them or forcefully convince them to change their minds.
-In the following two subsections, we will define the desired security 
-properties.
+To go back to the scenario stated in the introduction in our setting, we have two potential adversaries: Alice and Grace.
+Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
+In contrast, the aim of Grace, the totalitarian dictator, is to decrease the count but also additionally to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
+In the following two subsections, we will define the desired security properties.
 
@@
 
-We note that, in general terms, protesting is very similar to petitions, which 
-in turn are similar to voting: all three situations correspond to many 
-individuals expressing their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or 
-persecution), hence we desire to have similar properties of verification and 
-privacy for verifying a protest as there are for voting.
+We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
+Indeed, all three situations correspond to cases in which many individuals express their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
 
@@
 \begin{description}
-  \item[Eligibility:] anyone can verify that each vote cast is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according 
-    to the cast votes.
-  \item[Individual verifiability:] every voter can verify that their vote is 
-    included in the result.
+  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
+  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
+  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
 \end{description}
-We translate the votes into \emph{participation proofs}.
-Universal and individual verifiability remain the same: anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different: for protests the eligibility 
-requirement must include temporal and spatial eligibility (\ie each 
-participation proof satisfies some temporal and spatial relation to the 
-protest).
+In our context, votes are translated into \emph{participation proofs}.
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
+The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
 In essence, the proof must bind the person to the time and location of the protest.
 
-To define these properties more formally in the context of protest, we desire 
-three verifiability requirements, among which eligibility can be further broken 
-up into four subproperties:
+To define these properties more formally in the context of protest, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
 \begin{requirements}[V]
-  \item\label{EligibilityVerif} \emph{Eligibility}:
-    anyone can verify that each participation proof provides temporal and 
-    spatial eligibility and that only one participation proof is counted per 
-    individual.
+  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
     \begin{requirements}
-    \item\label{TemporallyRelated} \emph{Temporal eligibility}:
-      prove that the proof was created after the start of the protest and
-      before the end of the protest.
-    \item\label{SpatiallyRelated} \emph{Spatial eligibility}:
-      prove that the proof is spatially related to the physical location or 
-      journey of the protest.
-    \item\label{CountOnce} \emph{One-proof-per-person}:
-      prove that no individual can be counted more than once for a particular 
-      protest.
-    \item\label{DesignatedEvent} \emph{Designated event}:
-      prove that the proof is designated for the protest.
+    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
+    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
+    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
+    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
     \end{requirements}
 
-  \item\label{UniversalVerif} \emph{Universal verifiability}:
-    anyone can verify that the result obtained match the submitted participation 
-    proofs.
+  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
 
-  \item\label{IndividualVerif} \emph{Individual verifiability}:
-    each participant can verify that their participation proof is included in 
-    the global count.
+  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that his participation proof is included in the global count.
 \end{requirements}
@@
 
-In addition to the verification requirements, we also need to define the 
-privacy properties.
-In voting protocols, there are also three levels of 
-privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+In addition to the verification requirements, we also need to define the privacy properties.
+In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{description}
 \item[Vote privacy:] the voting does not reveal any individual vote.
-\item[Receipt freeness:] the voting system does not provide any data that can 
-  be used as a proof of how the voter voted.
-\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the 
-  vote was cast in any particular way.
+\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
+\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
 \end{description}
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion 
-resistance implies receipt freeness, which in turn implies vote privacy.
-Coercion resistance is probably not possible to achieve for protests:
-\eg Grace can simply physically bring Alice to a protest against her will.
+\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
+Coercion resistance is probably not possible to achieve for protests.
+For instance, someone could simply physically bring Alice to a protest against her will.
 
-In essence, receipt freeness means that upon completing the protocol, Grace 
-cannot link Alice to Alice's participation proof --- even if she were to 
-compromise Alice's device or Alice collaborates with Grace.
-As we will see, if Grace gets Alice's device, she can re-do the computations on 
-the same inputs.
-Since, in our case, the algorithms are deterministic and collisions are 
-negligible she will get the same result and can thus conclude that Alice is 
-indeed the one she is looking for.
-Thus we cannot provide receipt freeness.
-(See \cref{Conclusions} for further discussion.)
+In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
+As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
+Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
+Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
 
-This leaves us with what should correspond to vote privacy.
-We need unlinkability between Alice's long-term identity and Alice's 
-participation proof.
-Given a participation proof, Grace will not be able to tell if it belongs to 
-Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not 
-be able to link another proof as a consequence.
-Hence, we can summarize our needed properties as follows:
+As a consequence, this leaves us with with what would correspond to vote privacy.
+In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
+Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
+Hence, we can summarize the needed privacy properties as follows:
 \begin{requirements}[P]
-\item\label{ProofUnlink} Participants must be unlinkable to their proofs.
-\item\label{ProtestUnlink} Participants (or proofs for the same participant) 
-  must be unlinkable between different protests.
+\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
+\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
 \end{requirements}
-Thus Alice can always argue to be part of the protest in Grace's favour instead 
-of any protest against Grace, which, in fact, is a slight increase in privacy 
-over ordinary protests.
+
+As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+This is, in fact, is a slight increase in privacy over ordinary protests.

### 2018-06-04 paper/protocol.tex

@@
-\section{\PRIVO:\@ A protocol for protest outcome verification}%
+\section{\PRIVO:\@ A protocol for crowd counting estimation}%
 \label{Protocol}
@@
 
-We now present \PRIVO, a protocol for securely and privately verifying crowd 
-counts.
-The protocol consists of five phases: the setup, join, participation, 
-submission and verification phases.
+We now present \PRIVO, a protocol for securely and privately verifying crowd counts.
+The protocol consists of five phases: setup, join, participation, submission and verification phases.
 The setup is described in \cref{ProtocolSetup}.
-The join, participation and submission phases are described in 
-\cref{ProtocolDuring}.
-Finally, the verification phase is described in \cref{ProtocolVerification}.
+The join, participation and submission phases are detailed in \cref{ProtocolDuring}.
+Finally, the verification phase is presented in \cref{ProtocolVerification}.
 
-We have several roles.
-We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
-identity and a cryptographic key.
+Several entities are involved in our protocol.
+First, the \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
 The \ac{CA} is only involved in the setup phase.
-We also have the protesters who want to participate in a given protest.
+Second, a protester is an individual who wants to participate in a given protest.
 A protester can assume three different roles:
-\begin{enumerate*}
-\item We have the \emph{organizer} who will simply write a manifesto for the 
-  protest and spread to others.
-\item A \emph{participant} participates in the protest (and asks witnesses to 
-  vouch for his presence).
-\item A \emph{witness} provides proofs to participants that state the 
-  participant was indeed participating and the proofs are verifiable by third 
-  parties.
-\end{enumerate*}
-In general, there is one organizer and every protester will act as both 
-participant and witness.
+\begin{enumerate}
+\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
+\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
+\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
+\end{enumerate}
+In general, there is one organizer and every protester will act alternatively as both participant and witness.
 
-\subsection{The setup phase}%
+\subsection{Setup phase}%
 \label{ProtocolSetup}
 
-The setup phase is only run once and is the same as in 
-Anon-Pass~\cite{AnonPass}.
-We have simply adapted their description for our notation, but otherwise tried 
-to keep them as similar as possible.
+The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
+More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.
 
@@
 \emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
-The setup phase is for the \ac{CA} to set up all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as 
-follows.
+During setup phase, the \ac{CA} creates all the needed keys.
+First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
 Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
-Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times 
-  G\to G_T\)\footnote{%
+Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
   \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
@@
 }.
-Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = 
-  g^z\).
-Then the service public key \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service 
-private key \(\ssk = (x, y, z)\).
+Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
+The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).
 
@@
     \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{CA}][\ssk]}\).}
-During the registration phase, each protester will generate a secret key and 
-obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
-Thus each protester will have a signed secret key, the \ac{CA} will issue only 
-one signature per protester but will not know who has which key.
-The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly and sets \(M = g^k 
-  Z^r\) and sends \(M\) to the server.
-The protester acts as prover and the \ac{CA} as verifier while they perform the 
-following \ac{ZKPK} protocol:
+During the registration phase, each protester generates a secret key and obtains a signature on it by the \ac{CA} but without revealing it to the \ac{CA}.
+At the end, each protester will have a signed secret key while the \ac{CA} will issue only one signature per protester but without knowing the association between a particular key and the identity of the user.
+The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
+The protester acts as prover and the \ac{CA} as verifier while they perform the following \ac{ZKPK} protocol:
 \[
@@
 \]
-If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = 
-  g^a\).
-Then it forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
-  M^{axy})\) and sends it to the protester.
-The protester verifies that the following equations hold:
+If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
+Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x M^{axy})\) and sends it to the protester.
+The protester then verifies that the following equations hold:
 \begin{align*}
@@
 \end{align*}
-Upon success, the protester uses \(\sk = (\sigma, k, r)\).
+Upon success, the protester sets \(\sk = (\sigma, k, r)\).
 
-The setup and registration phases can be done once and the keys reused for an 
-arbitrary number of protests.
-Thus it would be suitable to have the registration phase as part of the issuance 
-of \eg national identity cards, passports or \acp{eID}.
+The setup and registration phases can be done once and the keys can be reused for an arbitrary number of protests.
+Thus, the registration phase could be easily integrated as part of the issuance of national identity cards, passports or \acp{eID}.
 
-\subsection{Creating, joining, participating in a protest and submitting 
-  proofs}%
+\subsection{Creation, join and participation to a protest and submission of proofs}%
 \label{ProtocolDuring}
 
-The join, participation and submission phases are illustrated in 
-\cref{fig:ProtocolOverview}.
-The participation proof share that will be constructed in the participation 
-phase is illustrated in \cref{fig:ProofFig}.
+The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
+The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.
 
-\emph{Creating a protest: the manifesto.}
-The organizer will write a manifesto for the protest, \ie to capture the cause.
-This manifesto is simply any intelligible text.
-He will distribute this manifesto to people: on the Web, on placards, \etc.
-If they agree, they will use it to join the protest.
+\emph{Creation of a protest: the manifesto.}
+The organizer will write a manifesto for the protest, which describes its cause.
+This manifesto could take the form of any intelligible text.
+The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
+If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
 
@@
 
-\emph{Joining participant: \((\pid, t_s)\gets 
+\emph{Joining as a participant: \((\pid, t_s)\gets 
     \PRIVOjoin[_P][\text{manifesto}]\).}
-A participant who wants to join the protest will use the manifesto to compute an 
-identifier for the cause, \(\cid\gets \Hash[\mfst]\).
-Then this identifier is used to create the participant's protest-specific 
-identifier, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
+A participant who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
+Afterwards, this identifier is used to create the protest-specific identifier for the participant, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
 \cref{fig:ProofFig,fig:ProtocolOverview}).
-More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, 
-  k, r)\)).
-The participant should also get a time-correlated random value from the 
-time-stamping service, \(t_s\gets \TSget\).
+More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
+The participant should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
 
@@
     The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
-    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
-    key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
-    \(\sk_W\) and \(\pid\).
-    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
-    witness, respectively, and \(l\) is an area.
-    All values are signed by the witness while also proving the correctness of 
-    \(\wid\) and knowledge of a signature on \(\sk_W\).
+    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
+    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key \(\sk_W\) and \(\pid\).
+    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
+    All values are signed by the witness while also proving the correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
   }%
@@
   \caption{%
-    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
+    An overview of the Join, Participation and Submission phases of \PRIVO.\@
     The organizer \(O\) broadcasts the manifesto.
-    The protester \(P\), witness \(W\) and their computations are as in 
-    \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
-    storage \(S\).
+    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+    Finally, both \(P\) and \(W\) submits the proof shares to a permanent storage \(S\).
   }%
@@
 
-\emph{Joining witness: \(t_s'\gets \PRIVOjoin_W\).}
-The witness should simply get a time-correlated random value from the 
-time-stamping service, \(t_s'\gets \TSget\).
-(We do this for redundancy, the newest of \(t_s\) and \(t_s'\) will set the 
-start of the time interval of creation for the proof share.).
+\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
+The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
+Remark that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.
 
@@
 
-\emph{Participating: \(\pi\gets
+\emph{Participation: \(\pi\gets
     \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
-In the participating phase the participant and the witness constructs the proof 
-share of the participant (\cref{fig:ProofFig}).
-The participant reblinds its signature \(\sigma\) on its secret key: choose 
-\(r_1, r_2\rgets \ZZ_q^*\) and let \(
+In the participation phase, the participant and the witness constructs the proof share of the participant (\cref{fig:ProofFig}).
+The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
   \tilde\sigma = (\tilde A = A^{r_1},
@@
                   \hat C = C^{r_1 r_2}).
-\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
-\(\pid\).)
+\) 
+Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
 The participant sends \((\pid, \tilde\sigma)\) to the witness.
@@
 \end{align*}
-Then they run the following \ac{PPK} with the participant as the prover and the 
-witness as the verifier:
+Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
 \begin{multline*}
@@
 \end{multline*}
-where \(r' = 1/r_2\).
+in which \(r' = 1/r_2\).
 We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
-Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
-be run as \iac{PPK} and be repeated multiple times to achieve security).
-The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
-sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
-  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
+The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
 The witness replies with a challenge \(c\).
-The participant then computes
+Afterwards, the participant computes
 \begin{align*}
@@
 \end{align*}
-and sends them to the witness.
+and forwards them to the witness.
 The witness checks whether
@@
 \end{align*}
-If the proof succeeds the witness will compute \(\wid\gets 
-  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
-Then the witness returns \((\wid, t_s', l)\) to the participant.
-Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
-  t_s, t_s', l)\) which constitutes a proof share of the participant 
-(\cref{fig:ProofFig}).
+If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
+Following this, the witness returns \((\wid, t_s', l)\) to the participant.
+As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).
 
@@
 
-\emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
-    l]\).}
-The participant should as soon as possible commit the proof-share data to the 
-time-stamping service and receive the proof of commitment, \(t_e\gets 
+\emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
+The participant should as soon as possible commit the proof-share data to the time-stamping service and receive the proof of commitment, \(t_e\gets 
   \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
 The remaining operations are not time critical.
-The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
-correctness of \(\pid\).
+The participant computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
 More specifically,
@@
 \end{multline*}
-Finally, the participant uploads the tuple \[
-  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
-\] for permanent storage.
+Finally, the participant uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
 
 \emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
-The witness should, just as the participant, commit the proof-share data to the 
-time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
-(This is for redundancy only.)
+The witness should, just as the participant, commit the proof-share data to the time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+(This is only for redundancy.)
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
@@
 \end{multline*}
-Finally, the witness uploads the tuple \[
-  \psh_W = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
-\] for permanent storage.
+Finally, the witness uploads the tuple \[ \psh_W = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid}) \] for permanent storage.
 
-\subsection{Verifying the participation count}%
+\subsection{Verifying the participation count}
 \label{ProtocolVerification}
 
-There are various ways for verifying the participation count, we will cover the 
-two suggested just after \cref{DefParticipationCount}.
-In the first approach, we do not trust individual witnesses, instead we 
-\emph{assume} that it is difficult for Alice to find more than \(\theta\) 
-witnesses willing to collude.
-Thus we require at least \(\theta\) witnesses to accept a participation proof 
-as valid.
-In the second approach, we trust certain witnesses but not others.
-Thus to accept a participation proof as valid, we require at least one trusted 
-witness (journalist Jane).
+While there are various ways for verifying the participation count, hereafter we will detail the two suggested just after \cref{DefParticipationCount}.
+In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
+Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
+In the second approach, we have a higher trust in specific witnesses.
+In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
 
@@
 
-To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
-\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i = 
-  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime 
-    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
-\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
-latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
-\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq 
-  l\).
+To verify the participation count for a protest \(P = (\cid, t, l)\) (see \cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify \(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of \(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
 Any proof share that does not verify correctly will be discarded.
-At this point, the verifier has constructed the set \(S\) from 
-\cref{DefProofShares} and can thus construct any participation proof 
-\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
+At this point, the verifier has constructed the set \(S\) from \cref{DefProofShares} and can thus construct any participation proof \(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
 
-Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then 
-the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) 
-as in \cref{DefParticipationCount}.
+Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.
 
@@
 
-For the this approach, we must adapt the selection of proof shares from the 
-blockchain by selecting only proof shares issued by witnesses that the verifier 
-trusts.
-Thus the verifier must be able to recognize proof shares issued by trusted 
-witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
-So trusted witnesses must complement their proofs by a digital signature that 
-the verifier can recognize.
+For this approach, we must adapt the selection of proof shares from the blockchain by selecting only proof shares issued by witnesses that the verifier trusts.
+Thus the verifier must be able to recognize proof shares issued by trusted witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
+So trusted witnesses must complement their proofs by a digital signature that the verifier can recognize.
 
-When \(S\) only contains proof shares issued by witnesses the verifier trusts, 
-we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
-Then the verifier can compute the participation count \(|\prfs_P^{\str, 
-    \theta}|\) as in \cref{DefParticipationCount}.
+When \(S\) only contains proof shares issued by witnesses the verifier trusts, we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
+Afterwards, the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.

### 2018-06-05 poster/contents.tex
Updates the title
Restructures poster to fit updated figures

--- 2017-11-22 poster/contents-poster.tex
@@
   \begin{column}{0.17\linewidth}
-    \includegraphics[width=0.5\linewidth]{fig/kth_cmyk.eps}
+    \includegraphics[width=0.5\linewidth]{kth_cmyk.eps}
     \hfill
@@
       \Huge\bfseries
-      Securely and Privately Verifiable Protests
+      From grassroots to CROCUS:\\[-0.25em]
+      privacy-preserving CROwd Counting Using Smartphones
     \end{center}
+    \vspace{0.25em}
     \begin{center}
@@
     \hfill
-    \includegraphics[width=0.8\linewidth]{fig/uqam.pdf}
+    \includegraphics[width=0.8\linewidth]{uqam.pdf}
   \end{column}
@@
 
-\includegraphics[width=\linewidth]{art/ProtestVerif.png}
+\includegraphics[width=\linewidth]{ProtestVerif.png}
 
@@
       \centering
-      \includegraphics[width=0.9\linewidth]{fig/trump.jpg}
+      \includegraphics[width=0.9\linewidth]{trump.jpg}
       \caption{%
@@
           privacy-preserving proximity testing.
-        \item The only added risk (over not using this) is if someone can use 
-          your secret key.
         \item Requires only local connectivity during the protest.
@@
 
-    \includegraphics[width=\linewidth]{art/ProtestVerif-UN.png}
+    \includegraphics[width=\linewidth]{ProtestVerif-UN.png}
 
@@
       \centering
-      \includegraphics[width=\linewidth]{fig/Jacobs-method.jpg}
+      \includegraphics[width=\linewidth]{Jacobs-method.jpg}
       \caption{%
@@
 
+%    \begin{block}{More info}
+%      \centering
+%      \includegraphics[width=0.4\linewidth]{qr.eps}
+%    \end{block}
+
   \end{column}
@@
         \item Each protester reads it, approves it, computes a protest (cause) 
-          identifier (\(cid\)) to designate which protest they participate in.
-        \item Each protester computes a personal identifier (\(pid\)), 
+          identifier (\(\cid\)) to designate which protest they participate in.
+        \item Each protester computes a personal identifier (\(\pid\)), 
           unlinkable between protests,
-        \item Each protester acts as witness (\(wid\), unlinkable between 
-          protesters, \(wsig\)) for other protesters by creating 
-          participation-proof shares.
+        \item Each protester acts as witness (\(\wid\), unlinkable between 
+          protesters) for other protesters by creating participation-proof 
+          shares.
         \item Proof shares vouches for temporal and spatial eligibility.
-        \item A threshold-based number of valid shares is a valid proof.
       \end{itemize}
@@
 
-    \begin{blackblock}{Our scheme, after the protest (bottom of 
-        \cref{Protocol})}
-      \begin{itemize}
-        \item Proof shares are committed to a blockchain as soon as possible.
-        \item \Ac{NIZK} proofs of correctness of \(PRF\) computations and 
-          validity of keys are submitted whenever convenient.
-        \item Anyone can verify the proofs: eligibility, universal and 
-          individual verifiability.
-        \item Must be done for all shares and their \ac{NIZK} proofs.
-        \item Count all \(pid\)s with valid proofs.
-      \end{itemize}
-    \end{blackblock}
-
-    \begin{block}{More info}
+    \begin{figure}
       \centering
-      \includegraphics[width=0.4\linewidth]{fig/qr.eps}
-    \end{block}
+      \includegraphics[width=\linewidth]{proofshare.tikz}
+      \caption{\label{ProofShare}%
+        Structure of a proof share.
+        The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
+        The protester \(P\)'s identifier \(\pid\) is computed using the 
+        protester's key \(\sk_P\) and \(\cid\).
+        The witness \(W\)'s identifier \(\wid\) is computed using the witness's 
+        key \(\sk_W\) and \(\pid\).
+        \(t_s, t_s'\) are the last heads of the blockchain seen by the 
+        protester and witness, respectively, and \(l\) is an area.
+        All values are signed by the witness while also proving the correctness 
+        of \(\wid\) and knowledge of a signature on \(\sk_W\).
+      }%
+    \end{figure}%
 
@@
   \begin{column}{0.32\linewidth}
-    \begin{figure}
-      \centering
-      \includegraphics[width=\linewidth]{fig/proofshare.tikz}
-      \caption{%
-        Structure of a proof share.
-        The protester \(P\)'s identifier \(pid\) is computed using the protester's 
-        key \(k_P\).
-        The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
-        \(k_W\).
-        \(t_s\) is a time interval and \(l\) is the coordinates of an area.
-        The protest (cause) identifier \(cid\) is the hash value of the manifesto.
-      }%
-      \label{ProofShare}
-    \end{figure}%
+
+    \begin{blackblock}{Our scheme, after the protest (bottom of 
+        \cref{Protocol})}
+      \begin{itemize}
+        \item Proof shares are committed to a blockchain as soon as possible.
+        \item \Ac{NIZK} proofs of correctness (\(\prf_\pid, \prf_\wid\) in 
+          \cref{Protocol}) of \(\ACprf\) computations and knwoledge of a valid 
+          signature on the key are submitted whenever convenient.
+        \item Anyone can verify the proofs: eligibility, universal and 
+          individual verifiability.
+        \item Must be done for all shares and their \ac{NIZK} proofs.
+        \item Count all \(\pid\)s with valid proofs.
+      \end{itemize}
+    \end{blackblock}
 
@@
           O\to \text{all}\colon & \text{manifesto} \\
-          P\colon & cid\gets H(\text{manifesto}), \\
-          & pid\gets PRF_{k_P}(cid) \\
-          P\to W\colon & pid \\
-          W\leftrightarrow P\colon & \text{perform distance bounding} \\
-          W\colon & wid\gets PRF_{k_W}(pid), \\
-          & wsig\gets PRF_{k_W}(wid, t_s, l) \\
-          W\to P\colon & (wid, t_s, l, wsig) \\[-1em]
-          && \text{during protest} \\ \midrule && \text{after protest} \\[-1em]
-          W\to S\colon & H(pid, wid, t_s, l, wsig) \\
-          P\to S\colon & H(pid, wid, t_s, l, wsig) \\
-          W\to S\colon & (pid, wid, t_s, l, wsig),\\
-          & NIZK( wid = PRF_{k_W}(pid), \\
-          & wsig = PRF_{k_W}(wid, t_s, l), \\
-          & \exists sign(k_W)) \\
-          P\to S\colon & (pid, wid, t_s, l, wsig),\\
-          & NIZK(pid = PRF_{k_P}(cid), \exists sign(k_P))
+          P\colon & t_s\gets \TSget \\
+          & \cid\gets \Hash[\text{manifesto}], \\
+          & \pid\gets \ACprf[_{\sk_P}][\cid] \\
+          W\colon & t_s'\gets \TSget
+          \\[-1em]
+          \noalign{\hfill Join}
+          \midrule
+          \noalign{\hfill Participation}
+          \\[-3em]
+          P\to W\colon & \pid \\
+          P\leftrightarrow W\colon &
+          \PPK\mleft\{ (\sk_P) : \mright. \\
+          & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+          & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+          \\
+          W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
+          W\to P\colon & (\wid, t_s', l)
+          \\[-1em]
+          \noalign{\hfill Participation}
+          \midrule
+          \noalign{\hfill Submission}
+          \\[-2em]
+          P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+          W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+          W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
+          \text{where} \\
+          & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
+          & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
+          & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
+          \\
+          & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
+          P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
+          \text{where}\\
+          & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
+          & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+          & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+          \\
+          & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
         \end{align*}
       \end{minipage}
-      \caption{%
-        An overview of message exchanges.
+      \caption{\label{Protocol}%
+        An overview of the Join, Participation and Submission phases of \PRIVO.\@
         The organizer \(O\) broadcasts the manifesto.
-        \(P\), \(W\) and their computations are as in \cref{ProofShare}.
-        Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
+        The protester \(P\), witness \(W\) and their computations are as in 
+        \cref{ProofShare}.
+        Finally, both \(P\) and \(W\) submits the proof shares to a permanent storage \(S\).
       }%
-      \label{Protocol}
     \end{figure}

### 2018-06-11 paper/SystemModel.tex

@@
 % cause identifier
-\NewVariable{\cid}{cid}
 Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
@@
 % protest
-\NewVariable{\prtst}{P}
 % subprotest
-\NewVariable{\sprtst}{p}
 
@@
 % proof share
-\NewVariable{\psh}{s}
 % proof shares
-\NewVariable{\pshs}{S}
 % protester identifier
-\NewVariable{\pid}{pid}
 % witness identifier
-\NewVariable{\wid}{wid}
 
@@
 % proof
-\NewVariable{\prf}{\pi}
 % proofs
-\NewVariable{\prfs}{\Pi}
 

### 2018-06-11 paper/DB-anon-cred.tex
edited and commented until end of building blocks

@@
 
-\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
-    \operatorname{PPK}%
-    \IfValueT{#1}{%
-      \IfValueTF{#2}{%
-        \mleft\{\mleft(#1\mright) : #2\mright\}%
-      }{%
-        \mleft\{#1\mright\}%
-      }%
-    }%
-  }}
-
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-However, ProProx is not secure against a malicious verifier and does not provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
+One protocol exists in the literature that provides \acp{PPK} with most of the 
+desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
+  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
+  shorter notation.}.
+However, ProProx is not secure against a malicious verifier and does
+not \sonja{I think ``not'' should be removed} provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
 To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
-
-\NewScheme{\DBS}{DBS}
-\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
-\NewAlgorithm{\DBSverify}{\DBS.\!Verify}
 
@@
 In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition of also not being secure against terrorist fraud either.
-We now propose another way to turn the Schnorr protocol into a public-key \iac{DB} protocol which is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating verifier.
+However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
+We now propose another way to turn the Schnorr protocol into a
+public-key \iac{DB} protocol which is secure against \ac{DBMF},
+\ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating
+verifier. \sonja{contrast with \ac{DBIF}}
 
 We present the protocol in \cref{SchnorrFigure}.
-The main difference with the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
+The main difference to the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
 The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.
@@
 Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) in the end of the protocol.
-A sequential repetition of protocol will decrease this probability.
+The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) at the end of the protocol.
+A sequential repetition of the protocol will decrease this probability.
 
@@
 This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
-The protocol is also secure against distance hijacking due to the fact that it is the authenticated bitstring that is used during the \ac{DB} phase, not the challenge bitstring as in the protocol of Brands-Chaum.
+The protocol is also secure against distance hijacking due to the fact
+that it is the authenticated bitstring that is used during the \ac{DB}
+phase, not the challenge bitstring as in the protocol of Brands-Chaum.
+\sonja{this is analysis but not in the analysis section}

### 2018-06-11 paper/SystemModel.tex
edited and commented until end of building blocks

@@
 
-\emph{Defining the concept of protest.} 
+%\emph{Defining the concept of protest.} 
 To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
@@
 For the rest of the paper, we will refer to the organizer as Alice.
-Assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul}\footnote{Remark that the objective does not necessarily align with the definition of the police whose interest could be to determine the maximum crowd at any point in time to deploy enough personnel for crowd-control.}.
+Assume that the objective of Alice is to count everyone who
+participated at any time and in any of the
+locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
+  repetition: %\footnote{Note that the objective does not necessarily
+              %align with the definition of the police whose interest
+              %could be to determine the maximum crowd at any point in
+              %time to deploy enough personnel for crowd-control.
+}.
 % cause identifier
@@
 A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
-Note that a participant to a protest can take the role of a protester but also act as witness for other protesters.
+Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
 %Seb: the sentence below is not very clear, it should be rephrased to make it clearer
@@
   \end{multline}
-  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) is within those of the protest.
+  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
   We denote by \(\prfs\) the set of all proofs.
@@
 %Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
-Another possibility would be to also have a particular type of witnesses, called trusted witnesses, participating to the protest. 
+Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
 For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 

### 2018-06-11 paper/DB-anon-cred.tex

--- 2018-06-01 paper/DB-anon-cred.tex
@@
 
-\ProvideDocumentCommand{\PPK}{o o}{\ensuremath{%
-    \operatorname{PPK}%
-    \IfValueT{#1}{%
-      \IfValueTF{#2}{%
-        \mleft\{\mleft(#1\mright) : #2\mright\}%
-      }{%
-        \mleft\{#1\mright\}%
-      }%
-    }%
-  }}
-
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+One protocol exists in the literature that provides \acp{PPK} with most of the 
+desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
+  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
+  shorter notation.}.
 However, ProProx is not secure against a malicious verifier and does not provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
@@
 
-\NewScheme{\DBS}{DBS}
-\NewAlgorithm{\DBSprove}{\DBS.\!Prove}
-\NewAlgorithm{\DBSverify}{\DBS.\!Verify}
-
-\emph{Reattempting a distance-bounding Schnorr protocol.}
+\emph{Reattempting a distance-bounding Schnorr protocol.}%
+\label{DBSchnorr}
 In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.

### 2018-06-11 paper/RelatedWork.tex

--- 2018-05-30 paper/RelatedWork.tex
@@
 Unfortunately, we can only get the peak participation with this method.
-When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the photos themselves when and where the they were taken).
+When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
 However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
@@
 \blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 
-  3.3 square meters
+  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 3.3 square meters
   \textelp{}
@@
 
-In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of 
-\citet{NNCrowdCounting}).
+In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \citet{NNCrowdCounting}).
 This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
@@
 
+An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}, is another recent development.
+This solution does not offer strong verifiability guarantees and thus has complemented by micro-counts made by humans to estimate his margin of error.
+
 In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
@@
 However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work withhonest participants.
-
-Trusted infrastructure, for example deployed by a collection of  media outlets ~\cite{LeMondeProtestingSolution}, is another recent development, but without verfiability or privacy guarantees.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work with honest participants.
 

### 2018-06-15 paper/TimeStamp.tex
Moves \New{Var,Alg,Scheme} to preamble (fixes #115)

@@
-\subsection{Time-stamping service -- blockchains}%
+\subsection{Time-stamping service -- distributed ledger}%
 \label{StorageProperties}
-
-\NewScheme{\TS}{TS}
-\NewAlgorithm{\TSget}{\TS.\!Get}
-\NewAlgorithm{\TSstamp}{\TS.\!Stamp}
-\NewAlgorithm{\TSverify}{\TS.\!Verify}
-\NewAlgorithm{\TStime}{\TS.\!Time}
 
@@
 
-We can instantiate \(\TS\) using a blockchain such as for instance OmniLedger~\cite{OmniLedger}.
+We can instantiate \(\TS\) using a distributed ledger, for instance a blockchain instance such as OmniLedger~\cite{OmniLedger}.
 The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the identifier of the block into which \(x\) was included.
@@
 For instance in a blockchain, we can store the hash of the block in which our data was committed.
-As a consequence as this block will remain, we are also sure that our data stay committed.% --- even if we no longer remember what our data looked like.
+As a consequence, as this block will remain, we are also sure that our data stay committed.\sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}

### 2018-08-13 paper/DB-anon-cred.tex
Improves DB-schnorr section

--- 2018-06-11 paper/DB-anon-cred.tex
@@
   shorter notation.}.
-However, ProProx is not secure against a malicious verifier and does
-not \sonja{I think ``not'' should be removed} provide \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
+However, ProProx is secure against a malicious verifier and provides \iac{PPK} 
+protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete 
+logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
 To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
@@
 We now propose another way to turn the Schnorr protocol into a
-public-key \iac{DB} protocol which is secure against \ac{DBMF},
-\ac{DBDF}, \ac{DBDH}, \ac{DBTF} and an impersonating
-verifier. \sonja{contrast with \ac{DBIF}}
+public-key \ac{DB} protocol which is secure against \ac{DBMF},
+\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
+The public-key property implies protection against an impersonating
+verifier.
+\sonja{Contrast with \ac{DBIF}}
 
 We present the protocol in \cref{SchnorrFigure}.
-The main difference to the original Schnorr protocol is that the prover commits to one random value but the verifier sends two challenges.
-The verifier presents to the prover which commitments and challenges to use during the \ac{DB} phase.
+The main difference to the original Schnorr protocol is that the prover commits 
+to one random value but the verifier sends \emph{two challenges}.
+This is also different from Brands-Chaum, where the prover and verifier jointly 
+construct the challenge.
+(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
+The verifier will request all \(|q|\) response-bits from one challenge and only 
+\(l\) from the other.
+The prover must know the responses for both challenges to successfully pass the 
+\ac{DB} phase.
 
@@
     &
-    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\), with \(\ceil{\log_2 q}\) bits 
-    set to \(b\).
+    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 
-        \ceil{\log_2 q} + l\)} \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
+        l\)} \\
 
@@
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with respect to the security parameter \(\lambda\) and repeat the protocol until the knowledge error is small enough.
-This will actually also decrease the success probability of \iac{DBMF} adversary in the \ac{DB} step.
-Indeed, the \ac{DBMF} adversary does not know which challenge the verifier will use, thus there is a \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-The prover will only provide one of the responses: even if the adversary re-runs the protocol with the same challenges, the randomly chosen \(\rho_0, \rho_1\) will have changed --- which thus yields another \(R_b\) at the end of the protocol.
-A sequential repetition of the protocol will decrease this probability.
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with 
+respect to the security parameter \(\lambda\) and repeat the protocol \(n\) 
+times, such that the knowledge error, \((2^{-k})^n\), is small enough.
+This will actually also decrease the success probability of the attacks 
+presented below.
 
 The \ac{DB} phase protects against distance fraud.
-\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding with \(r_i\).
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
-The verifier will send \(\ceil{\log_2 q} + l < 2\ceil{\log_2 q}\) challenges.
-Afterwards, the prover reveals all the bits of either \(s_0\) or \(s_1\) but only \(l\) bits of the other.
-Thus, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting them from the prover.
-However, at this point the adversary must wait for \(b_{l+1}\) challenge bits from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
+\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding 
+with \(r_i\).
+The probability of successfully guessing the order of the challenge bits is 
+\(2^{-(|q|+l)}\) per round or, in total, \(2^{-(|q|+l)n}\).
 
-The protocol is \ac{DBTF}-resistant, indeed if the malicious prover gives both responses to the adversary, the adversary can compute his secret key.
-This follows from the fact that it is \iac{ZKPK}, which means there is an extractor that can leak the secret.
+The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
+phase for at least one round.
+The verifier will send \(|q| + l < 2|q|\) challenges.
+By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
+only \(l\) bits of the other.
+The adversary now has two options.
+First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
+them from the prover.
+However, at this point the adversary must wait for the challenge bit 
+\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
+receive the correct \(r_i\) --- this relay will be detected.
+The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
+for this challenge from the prover.
+Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
+adversary will guess it correctly.
+Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
+The adversary can also guess the remaining \(|q|-l\) bits, for which the 
+probability of success is \(2^{-(|q|-l)}\) per round or, in total, 
+\(2^{-(|q|-l)n}\).
+Thus, the success probability of the \ac{DBMF} adversary is 
+\(2^{-n}+2^{-(|q|-l)n}\).
+
+%The prover will only provide one of the responses and \(l\) bits of the other. 
+%Even if the adversary re-runs the protocol with the same challenges, the 
+%randomly chosen \(\rho\) will have changed --- which thus yields another \(R\) 
+%at the end of the protocol.
+
+The protocol is \ac{DBTF}-resistant, indeed, if the malicious prover gives both 
+responses to the adversary, the adversary can compute his secret key.
+In fact, this property is tied to the knowledge extractor used in the proof of 
+the \ac{ZKPK} property of the Schnorr protocol.
+The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie 
+\(1/2\) per round or, in total, \(2^{-n}\).
+
 The protocol is also secure against distance hijacking due to the fact
-that it is the authenticated bitstring that is used during the \ac{DB}
+that it is the authentication bitstring that is used during the \ac{DB}
 phase, not the challenge bitstring as in the protocol of Brands-Chaum.
 \sonja{this is analysis but not in the analysis section}
+\daniel{I prefer to prove the building blocks separately, then prove the full 
+  composite scheme in the analysis section.
+  This protocol with a proof would be a contribution in itself.}
+
+Finally, a malicious verifier who wants to impersonate a prover can guess the 
+remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
+the prover.
+The probability that this succeeds is \(2^{-(|q|-l)}\) or, in total, 
+\(2^{-(|q|-l)n}\).

### 2018-08-13 paper/DB-anon-cred.tex
Minor clarification in DB-Schnorr

@@
 respect to the security parameter \(\lambda\) and repeat the protocol \(n\) 
-times, such that the knowledge error, \((2^{-k})^n\), is small enough.
-This will actually also decrease the success probability of the attacks 
+times, such that the knowledge error, \(2^{-kn}\), becomes small enough.
+This is also needed to decrease the success probability of some of adversaries 
 presented below.

### 2018-08-13 paper/conclusions.tex
edits and comments according to annotations from June 6!

@@
 Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
-To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. 
+To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
 Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
+}
 
-Of separate interest, we have also build distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
+Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
 All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
@@
 Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
-Moreover, if they would provide individual verifiability, they would likely violate the privacy requirements.
+Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.
 
 Finally, most of the current methods are estimates, with quite some error margins. 
-While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on theparticipants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
+While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
 Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 

### 2018-08-13 paper/protocol.tex
edits and comments according to annotations from June 6!

@@
 \label{Protocol}
-
-\NewScheme{\PRIVOscheme}{PRIVO}
 
@@
 Several entities are involved in our protocol.
-First, the \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
+First, \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
 The \ac{CA} is only involved in the setup phase.
@@
 
-\NewAlgorithm{\PRIVOsetup}{Setup}
-\NewVariable{\sk}{sk}
-\NewVariable{\spk}{spk}
-\NewVariable{\ssk}{ssk}
-
 \emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
-During setup phase, the \ac{CA} creates all the needed keys.
+During the setup phase, the \ac{CA} creates all the needed keys.
 First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
@@
 The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).
-
-\NewAlgorithm{\PRIVOreg}{Reg}
 
@@
 
-\subsection{Creation, join and participation to a protest and submission of proofs}%
+\subsection{Creation, join and participation in a protest and submission of proofs}%
 \label{ProtocolDuring}
@@
 
-\NewAlgorithm{\PRIVOjoin}{Join}
-\NewVariable{\mfst}{manifesto}
-\NewVariable{\cid}{cid}
-\NewVariable{\pid}{pid}
-
 \emph{Joining as a participant: \((\pid, t_s)\gets 
@@
 The participant should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
-
-\NewVariable{\wid}{wid}
 
@@
     The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key \(\sk_W\) and \(\pid\).
+    The witness \(W\)'s identifier \(\wid\) is computed using the
+    witness's key \(\sk_W\) and \sonja{the other's?}\(\pid\).
     \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
@@
 The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
-Remark that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.
-
-\NewAlgorithm{\PRIVOparticipate}{Prticip}
-\NewAlgorithm{\PRIVOwitness}{Witness}
+Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.
 
@@
     \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
-In the participation phase, the participant and the witness constructs the proof share of the participant (\cref{fig:ProofFig}).
+In the participation phase, the participant and the witness construct the proof share of the participant (\cref{fig:ProofFig}).
 The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
@@
 As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).
-
-\NewAlgorithm{\PRIVOsubmit}{Submit}
 

### 2018-08-14 paper/DB-anon-cred.tex

@@
 The adversary can also guess the remaining \(|q|-l\) bits, for which the 
-probability of success is \(2^{-(|q|-l)}\) per round or, in total, 
-\(2^{-(|q|-l)n}\).
-Thus, the success probability of the \ac{DBMF} adversary is 
-\(2^{-n}+2^{-(|q|-l)n}\).
+probability of success is \(2^{-(|q|-l)}\) (note that this is independent of 
+the rounds).
+Thus, the success probability of the \ac{DBMF} adversary is \emph{at most} 
+\(2^{-n}+2^{-(|q|-l)}\).
 
@@
 the prover.
-The probability that this succeeds is \(2^{-(|q|-l)}\) or, in total, 
-\(2^{-(|q|-l)n}\).
+The probability that this succeeds is, as above, \(2^{-(|q|-l)}\).

### 2018-08-14 paper/DistanceBounding.tex

@@
 At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
-In this sense, \Ac{DB} protocols combines at the same time the classical properties of authentication protocols with the possibility of verifying the physical proximity.
+In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
 
@@
   \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
-  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation.
+  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation. \sonja{contrast with impersonating verifier}
 \end{itemize}
@@
 
-The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
+The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
 Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
 There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
+Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
 The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.

### 2018-08-14 paper/MANETs.tex
change to intro and system model

@@
 
-Since the cellular network can be shut down to keep protesters from
-accessing the Internet, making phone calls or texting, we require a
-different means of communications between protesters. This can be
-accomplished by Bluetooth or WiFi, as demonstrated by
-Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of apps
-for communication during protests via wireless mesh networking. An
-alternative, although originally designed to work within 5G cellular
-networks, is device-to-device communication (D2D)~\cite{D2D}. Specifically, the
-outband and autonomous version D2D fits our scenario thanks to using
-unlicensed spectrum and working without cellular coverage.
+Since the cellular network could be shut down to keep protesters from accessing the Internet, making phone calls or texting, we require a different means of communications between protesters. 
+This could be accomplished by Bluetooth or WiFi communications, as demonstrated by Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of applications for communication during protests via wireless mesh networking.
+An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
+Specifically, the out-of-band and autonomous version D2D fits our scenario thanks to using unlicensed spectrum and working without cellular coverage.

### 2018-08-14 paper/RelatedWork.tex

@@
 
-An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}, is another recent development.
-This solution does not offer strong verifiability guarantees and thus has complemented by micro-counts made by humans to estimate his margin of error.
+An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}.
+This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.
 
-In general for all of the above methods, the more a crowd spreads out, the more difficult it will be to determine its size.
-In particular, one of the challenge is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulty to capture the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
+In general for all of the above methods, the more a crowd spreads out, the more difficult it is to determine its size.
+In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
+These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
 
@@
 This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
-However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting twice (violating eligibility, \cref{EligibilityVerif}).
+However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
 Another downside is that the service also requires an Internet connection during the event to register as a participant.
@@
 However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only work with honest participants.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.
 

### 2018-08-14 paper/analysis-security.tex

@@
 
-\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
-that their participation proofs (proof shares) are indeed included.
-As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, 
-  \pi_{\wid}\)) are committed to the blockchain and available from public 
-storage (see \cref{fig:ProtocolOverview}).
-Alice and Bob can simply check that all of their proof shares are indeed there 
-and thus the security of individual verifiability depends on the properties of 
-the blockchain and storage.
+\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
+As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
+Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.
 
-\Cref{UniversalVerif} requires that also anyone can verify the result and that 
-all participation proofs counted indeed are eligible.
-As the proof shares are committed and stored publicly, anyone can download 
-them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and 
-count them.
-As for individual verifiability, the security of universal verifiability is 
-reduced to the properties of the blockchain and storage but also the eligibility 
-verification, which we will discuss next.
+\Cref{UniversalVerif} requires also that anyone can check the result and that all participation proofs counted are legitimate.
+As the proof shares are committed and stored publicly, anyone can download them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and count them.
+As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.
 
-\subsection{Eligibility verifiability}%
+\subsection{Eligibility verifiability}
 \label{analysis-eligibility}
 
-\Cref{EligibilityVerif} states that anyone must be able to determine the 
-authenticity of the relevant attributes of the data.
-We have several attributes that must be verifiable:
-time of creation (temporal eligibility),
-physical location of \(\sk_P\) at creation (spatial eligibility),
-recognize two proofs from the same person (one-proof-per-person eligibility) and 
-that the proof is indeed designated for the event (designated-event 
-eligibility).
-We will now analyse these.
+\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
+In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
+We will now analyze these properties.
 
-\paragraph{Temporal eligibility}%
+\paragraph{Temporal eligibility}
 \label{analysis-temporal}
 
-\Cref{TemporallyRelated} ensures freshness, \ie that Alice cannot simply 
-resubmit an old proof as a new one.
-In general, freshness requires the prover to respond to an unpredictable 
-challenge.
-The challenge here is to include the hash value at the head of the blockchain at 
-the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof 
-share).
-As per construction of blockchains, the hash value at the head depends on the 
-previous blocks in the chain.
-Thus the predictability of \(t_s\) depends on the predictability of the blocks, 
-which depends on the predictability of the transactions and the nonce needed by 
-the miner.
-The transactions in turn depend on the signatures made by the signing keys 
-corresponding to the used transactions.
-If these were predictable, our adversary could spend arbitrary transactions in 
-the blockchain --- which is designed to be hard.
-Thus Alice can predict \(t_s\) with negligible probability, \ie \(t_s\) must 
-have been published on the blockchain before being included in her proof share.
+\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an old proof as a new one.
+In general, freshness requires the prover to respond to an unpredictable challenge.
+The challenge here is to include the hash value at the head of the blockchain at the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof share).
+As it is the case in the construction of blockchains, the hash value at the head depends on the previous blocks in the chain.
+Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
+In turn, the transactions depend on the signatures made by the signing keys corresponding to the used transactions.
+If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
+Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.
 
-According to \cref{TemporallyRelated}, we must also prove that a proof share has 
-not been created after a certain time.
-Otherwise Grace can argue that the proof share was created after the protest.
-The hash values of the proof shares are committed to the blockchain, thus there 
-is a negligible probability that they were created after that.
-Alice would have to choose a value \(y\) in the domain of the hash function 
-\(\Hash\) and then find a preimage \(x\) such that \(y = \Hash[x]\) and \(x\) is 
-a valid proof.
-If \(\Hash\) is collision resistant, then finding \emph{any} preimage is hard.
+According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
+Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
+The hash values of the proof shares are committed to the blockchain, which means that there is a negligible probability that they were created after that.
+Alice would have to choose a value \(y\) in the domain of the hash function \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) is a valid proof.
+If \(\Hash\) is collision resistant, finding \emph{any} preimage is hard.
 
-\paragraph{Linkability}%
+\paragraph{Linkability}
 \label{analysis-linkability}
 
-\Cref{CountOnce} is required to prevent Sybil attacks, \ie that Alice can 
-provide two participation proofs and thus be counted twice.
-This is prevented by the use of \(\pid\).
-To be counted twice, Alice must produce a \(\pid'\neq \pid\).
-Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
-\(\sk_P'\) and make the witness accept in the protocol
+\Cref{CountOnce} is required to prevent Sybil attacks, in the sense that Alice cannot provide two participation proofs for specific protest and thus be counted twice.
+This possibility is prevented by the use of \(\pid\).
+Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
+Due to the deterministic property of \(\ACprf\), Alice must produce a new key \(\sk_P'\) and make the witness accept in the protocol
 \begin{multline*}
@@
 while she does not know a valid signature on \(\sk_P'\).
-This is thus reduced to the security of the \(\AC\) scheme and how often Alice 
-can get a valid signature on a secret key from the \ac{CA}.
+As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.
 
-\paragraph{Spatial eligibility}%
+\paragraph{Spatial eligibility}
 \label{analysis-spatial}
 
-\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
-indeed on the location when the proof share was created.
-Thus we must ensure that Alice cannot forge undeserved witness signatures, which 
-is ensured using the same linkability mechanism as above.
+\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
+To realize this, we have to ensure that Alice cannot forge witness signatures, which is realized by using the same linkability mechanism as above.
 To forge a witness signature, Alice must produce a \(\wid'\) such that
@@
 while not knowing a signature on the secret key \(\sk_W'\).
-Thus she must break the \(\AC\) scheme to succeed or get a valid signature on 
-\(\sk_W'\) from the \ac{CA}.
-(Note that Alice can produce one witness signature for herself, since she has 
-access to her own \(\sk_P\), but no more.)
+Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
+The latter could be done if she can find people willing to collude.
+However, due to the assumptions done in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course this two approach could be combine).
+Remark that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.
 
-\paragraph{Designated protest}%
+\paragraph{Designated protest}
 \label{analysis-designated}
 
-\Cref{DesignatedEvent} is to prevent Alice from reusing the same proof (or proof 
-share) for another event --- or someone else using her proof-share for another 
-event.
-This is prevented with the use of \(\cid\) in the proof shares.
-Thus to reuse the proof share for another protest, with a different manifesto, 
-one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
-  \Hash[\mfst']\).
+\Cref{DesignatedEvent} is to prevent Alice (or someone else) from reusing the same proof (or proof share) for another event.
+This possibility is prevented through the use of \(\cid\) in the proof shares.
+To reuse the proof share for another protest, with a different manifesto, one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = \Hash[\mfst']\).
 
-There is also another case of collision that we must prevent.
-Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
-identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
-with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
-Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
-then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
-protest with manifesto \(m\).
-This means that we must separate the mechanisms used for participating and 
-witnessing.
+There exists another case of collision that we must prevent.
+Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
+Now, if Alice construct a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
+This means that we must separate the mechanisms used for participating and witnessing.
 The protocol achieves this by the fact that \[
@@
 does.
-Thus the verification process differs for the two types of proofs.
-(An alternative approach would have been to compute them differently, \eg 
-\(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = 
-  g_T^{1/(\sk+x+1)}\).)
+Thus, the verification process differs for the two types of proofs.
+(An alternative approach would have been to compute them differently, for instance \(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = g_T^{1/(\sk+x+1)}\).)
 
@@
 
-We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable 
-across protests (but linkable within one protest due to \cref{CountOnce}).
-It follows from the properties of \(\ACprf\) that \(\pid = 
-  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are 
-unlinkable if \(\cid\neq \cid'\).
+We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable across protests but linkable within one protest due to \cref{CountOnce}.
+It follows from the properties of \(\ACprf\) that \(\pid =  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are unlinkable if \(\cid\neq \cid'\).
 
-Now to \cref{ProofUnlink}.
-Given \(\pid\), Grace cannot distinguish whether \(\pid = 
-  \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = 
-  \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).
+Afterwards to get the property \cref{ProofUnlink}.
+Given \(\pid\), Grace cannot distinguish whether \(\pid = \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).
 
-However, say that a witness works for Grace.
-This witness interacts with Alice directly, \ie has (physically) identified her.
-The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
-and to verify the \ac{PPK}.
-\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
-  witness in the \ac{PPK}.}
+However, consider the situation in which the witness works for Grace.
+This witness interacts with Alice directly and might have (physically) identified her.
+The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) and to verify the \ac{PPK}.
+\daniel{This assumes that I will do the changes to hide \(\cid\) from the witness in the \ac{PPK}.}
 Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
@@
 \daniel{Fix this.}
-Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.
+If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.

### 2018-08-14 paper/intro.tex

@@
 
-Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in details in \cref{RelatedWork}).
+Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{RelatedWork}).
 However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
 In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
-In addition, they also lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
+In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
 
@@
 \emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
-This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.
+\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
 
@@
 Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
-More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} resistance and provides a \ac{PK} for discrete logarithms.
+More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{DistanceBounding}), and provides a \ac{PK} for discrete logarithms.
 The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
-%Seb: once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
+\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
 %and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
-
+}
 \emph{Outline.} 
@@
 \PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
-Finally, we conclude with a discussion and future works in \cref{Conclusion}.
+Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.

### 2018-08-14 paper/properties.tex

@@
 
-To go back to the scenario stated in the introduction in our setting, we have two potential adversaries: Alice and Grace.
-Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
-In contrast, the aim of Grace, the totalitarian dictator, is to decrease the count but also additionally to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
+To go back to the scenario stated in the introduction, we have two potential adversaries: Alice and Grace.
+Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
+In contrast, the aim of Grace, the government Alice protests against, is to not only decrease the count, but also to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
 In the following two subsections, we will define the desired security properties.
@@
 \end{description}
+\sonja{discussion about applicable properties here, more sources and alternative properties}
 \Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.

### 2018-08-14 paper/analysis-security.tex

@@
 \Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
-As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
+All proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
 Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.
 
-\Cref{UniversalVerif} requires also that anyone can check the result and that all participation proofs counted are legitimate.
-As the proof shares are committed and stored publicly, anyone can download them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and count them.
+\Cref{UniversalVerif}  includes that anyone can check the result and that all participation proofs counted are legitimate.
+As the proof shares are committed and stored publicly, anyone can
+download them, verify eligibility (\ie verify \(\pi_\pid,
+\pi_{\wid}\)) of the proofs and count them.
 As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.
@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks, in the sense that Alice cannot provide two participation proofs for specific protest and thus be counted twice.
+\Cref{CountOnce} is required to prevent Sybil attacks, in the sense
+that Alice cannot provide two (or more) participation proofs for a
+specific protest and thus be counted more than once.
 This possibility is prevented by the use of \(\pid\).
@@
 The latter could be done if she can find people willing to collude.
-However, due to the assumptions done in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course this two approach could be combine).
-Remark that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.
+However, due to the assumptions made in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course these two approaches could be combined).
+Note that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.
 
@@
 Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
-Now, if Alice construct a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
+Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
 This means that we must separate the mechanisms used for participating and witnessing.

### 2018-08-16 paper/intro.tex
Renames building blocks file

@@
 terms of these properties (\cref{RelatedWork}). 
-Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{BuildingBlocks}).
+Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}).
 \PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 

### 2018-08-16 paper/DB-anon-cred.tex
Breaks DB-Schnorr out into its own section

@@
-\subsection{Distance-bounding anonymous credentials}%
+\section{Distance-bounding anonymous credentials}%
 \label{DB-anon-cred}
@@
 
-\emph{Reattempting a distance-bounding Schnorr protocol.}
+\subsection{Reattempting a distance-bounding Schnorr protocol}
+
 In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
@@
 
+\subsection{Security analysis}
+
 The intuition behind the protocol security is as follows.

### 2018-08-17 paper/DB-anon-cred.tex
Renames DistanceBounding.tex to distance-bounding.tex

@@
 
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
+In the original \ac{DB} paper by \citet{distance-bounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
 However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.

### 2018-08-17 paper/distance-bounding.tex
Renames DistanceBounding.tex to distance-bounding.tex

--- 2018-08-14 paper/DistanceBounding.tex
@@
 \subsection{Distance-bounding protocols}%
-\label{DistanceBounding}
+\label{distance-bounding}
 
-\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
+\Ac{DB} protocols were first suggested by \citet{distance-bounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
 These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.

### 2018-08-17 paper/intro.tex
Renames DistanceBounding.tex to distance-bounding.tex

@@
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{distance-bounding}.
 Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
-More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{DistanceBounding}), and provides a \ac{PK} for discrete logarithms.
+More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
 The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.

### 2018-08-17 paper/intro.tex
Renames RelatedWork to related-work

@@
 
-Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{RelatedWork}).
+Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
 However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
@@
 Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
-terms of these properties (\cref{RelatedWork}). 
+terms of these properties (\cref{related-work}). 
 Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}).

### 2018-08-17 paper/location-proofs.tex
Renames LocationProofs to location-proofs

--- 2018-06-04 paper/LocationProofs.tex
@@
 In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
-One of the main drawback of this approach is that a user can cheat by having his device transmitting a false location. 
+One of the main drawbacks of this approach is that a user can cheat by having her device transmit a false location. 
 Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
 
-One possible way to counter this threat is by having the requesting device formally proven that it really is at the claimed location, which give rise to the concept of \emph{location proof}. 
+One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
 In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
-A location proof system is a architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
+A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
 Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-However, some location proofs systems, such as PROPS~\cite{PROPS}, exists that provides strong privacy guarantees along with the possibility of verifying the claim of the location.
-\PRIVO share some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location.
+\PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.

### 2018-08-17 paper/intro.tex
Renames SystemModel to system-model
Bugfix: undo DistanceBounding cite key renamed to distance-bounding

@@
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{distance-bounding}.
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
+for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
 Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
@@
 The paper is organized as follows. 
-First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{SystemModel}).  
+First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
 Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 

### 2018-08-18 paper/security-properties.tex
Merges protest model and security properties into system model

--- 2018-08-14 paper/properties.tex
@@
-\section{Security requirements}%
+\subsection{Security requirements}%
 \label{Properties}
 
-%\subsection{An overview of the adversary}
+%\subsubsection{An overview of the adversary}
 
@@
 
-\subsection{Verifiability}%
+\subsubsection{Verifiability}%
 \label{Verifiability}
@@
 
-\subsection{Privacy}%
+\subsubsection{Privacy}%
 \label{Privacy}
@@
 \end{description}
-\sonja{discussion about applicable properties here, more sources and alternative properties}
+
 \Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
-Coercion resistance is probably not possible to achieve for protests.
+Coercion resistance is not possible to achieve for protests.
 For instance, someone could simply physically bring Alice to a protest against her will.
 
+\sonja{discussion about applicable properties here, more sources and alternative properties}
+\sonja{new}
+Difference to e-voting:
+physical presence means support for a cause if there is one protest.
+If there is a counterprotest, physical presence with that group means support for the counterprotest.
+In our system, it gets more ambiguous as the participants are counted if all of the following is true 1) they participate in the protocol, 2) they use the protest identifier (cause) for which the count is done, 2) they meet the eligibility criteria, and 3) they receive enough proof shares, 4) that are uploaded to the ledger.
+Thus one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.
+
+Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt, because being counted implies support for a cause.
+This also means that besides physical force, coercion can happen by forcing the participate to show a receipt.
+We thus have to decide between individual verifiability and the privacy properties for e-voting or define privacy properties suitable for the scenario.
+The ultimate privacy requirement is thus stronger here: in contrast to voting, where it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.
+
+The privacy properties we need in this context are
+
+involuntary participant unlinkability: unless the participant discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the participant.
+
+involuntary witness unlinkability: unless the witness discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the witness.
+\sonja{old}
 In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.

### 2018-08-18 paper/system-model.tex
Merges protest model and security properties into system model

\section{System model}

\include*{protest-model}
\include*{security-properties}

### 2018-08-20 paper/adversary-model.tex
Updates system, adversary model section

\subsection{Communication and adversary model}%
\label{adversary-model}

\dots

### 2018-08-20 paper/intro.tex
Updates system, adversary model section

@@
 First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
-Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
+Then, we introduce the desired security properties for such a system (\cref{security-properties}) and subsequently discuss related work in 
 terms of these properties (\cref{related-work}). 

### 2018-08-20 paper/system-model.tex
Updates system, adversary model section

@@
-\section{System model}
+\section{System and adversary model}%
+\label{system-model}
+
+We will now describe our system and adversary models.
+We first present an abstraction of a protest and how to count the participation 
+(\cref{protest-model}).
+Next we present the communication and adversary model (\cref{adversary-model}).
+Finally, we present the desired security properties 
+(\cref{security-properties}).
 
 \include*{protest-model}
+\include*{adversary-model}
 \include*{security-properties}

### 2018-08-20 paper/protocol.tex

@@
 
-\subsection{Verifying the participation count}
+\subsection{Verifying the participation count}%
 \label{ProtocolVerification}
@@
 Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
-In the second approach, we have a higher trust in specific witnesses.
+In the second approach, we have a higher trust in specific witnesses and no 
+trust in others.
 In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
 
-\paragraph{Without trusted witnesses}
+To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
+\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
+  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
+    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
+\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
+latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
+\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  
+  l\).
+Any proof share that does not verify correctly will be discarded.
+At this point, the verifier has constructed the set \(S\) from 
+\cref{DefProofShares} and can thus construct any participation proof 
+\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
+Now the verifier can compute the participation count \(|\prfs_P^{\str, 
+    \theta}|\) as in \cref{DefParticipationCount}.
+It is the strength function \(\str\) that differ in the two cases we give.
 
-To verify the participation count for a protest \(P = (\cid, t, l)\) (see \cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify \(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of \(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
-Any proof share that does not verify correctly will be discarded.
-At this point, the verifier has constructed the set \(S\) from \cref{DefProofShares} and can thus construct any participation proof \(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
+In the case \emph{without} trusted witnesses, the verifier simply define 
+\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to our 
+desired thresold.
 
-Now, we simply define \(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and then the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.
-
-\paragraph{With trusted witnesses}
-
-For this approach, we must adapt the selection of proof shares from the blockchain by selecting only proof shares issued by witnesses that the verifier trusts.
-Thus the verifier must be able to recognize proof shares issued by trusted witnesses, but as \(\prf_\wid\) is currently constructed, this is not possible.
-So trusted witnesses must complement their proofs by a digital signature that the verifier can recognize.
-
-When \(S\) only contains proof shares issued by witnesses the verifier trusts, we let \(\str[\prf_{\pid_i, P}] = 1\) and let \(\theta = 1\).
-Afterwards, the verifier can compute the participation count \(|\prfs_P^{\str, \theta}|\) as in \cref{DefParticipationCount}.
+In the case \emph{with} trusted witnesses, each trusted witness must inform the 
+verifier of which proof shares that he or she has signed, \eg by giving a list 
+of all such proof shares or digitally sign each proof share.
+Then the verifier defines \[
+  \str[\prf_{\pid_i, P}] = \begin{cases}
+    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
+    0 & \text{otherwise}
+  \end{cases}
+\] and sets \(\theta = 1\).

### 2018-08-20 paper/system-model.tex

--- 2018-08-18 paper/system-model.tex
@@
-\section{System model}
+\section{Defining and formalizing protest and crowd estimation}%
+\label{system-model}
 
-\include*{protest-model}
-\include*{security-properties}
+%\subsection{What is \protect\emph{a} protest?}%
+%\label{WhatIsAProtest}
+
+%\emph{Defining the concept of protest.} 
+To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
+Let us start by considering some examples.
+During the demonstrations against the South Korean president in Seoul in 2016
+\blockcquote{2016DemonstrationsInSeoul}{%
+  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
+}.
+These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
+The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
+We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
+  anti-government demonstrators have staged daily protests across Venezuela%
+} while
+\blockcquote{AlJazeeraOnVenezuela2017}{%
+  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
+}.
+Generalizing from these examples, the minimal common part is the cause,%
+\label{CauseIsTheCommonDenominator} while the location (or area) considered 
+varies over time.
+
+For the rest of the paper, we will refer to the organizer as Alice.
+Assume that the objective of Alice is to count everyone who
+participated at any time and in any of the
+locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
+  repetition: %\footnote{Note that the objective does not necessarily
+              %align with the definition of the police whose interest
+              %could be to determine the maximum crowd at any point in
+              %time to deploy enough personnel for crowd-control.
+}.
+% cause identifier
+Formally, we define a protest as an event that is uniquely identified by its cause \(\cid\), its time interval \(t\) and its location (area) \(l\).
+More specifically, we will use the following definition.
+
+% protest
+% subprotest
+
+\begin{definition}[Subprotest, Protest]\label{DefProtest}
+  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
+  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
+  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
+\end{definition}
+
+The protests described in the previous examples can be captured using this definition by decomposing them up into subprotests.
+Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
+Similarly for marches, the marching path can be divided into subprotests with locations (or areas) that slightly overlap.
+
+\emph{Formalizing the notion of crowd estimation.} 
+Each participant who wants to be counted must submit a \emph{participation proof}.
+The proof must be associated with the protest (\ie its identifier \(cid\)), and its time and location must coincide with one of the subprotests.
+
+Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
+A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
+Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
+%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
+The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.
+
+% proof share
+% proof shares
+% protester identifier
+% witness identifier
+
+\begin{definition}[Proof share]%
+  \label{DefProofShare}\label{DefProofShares}
+  A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
+  \(\cid, t, l\) are as in \cref{DefProtest};
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
+  \(\psh \sqsubseteq \sprtst\).
+  We define \(\pshs\) as the set of all proof shares.
+\end{definition}
+
+A subset of the proof shares forms a participation proof for a protester.
+
+% proof
+% proofs
+
+\begin{definition}[Participation proof]%
+  \label{DefParticipationProof}\label{DefParticipationProofs}
+  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
+  \begin{multline}
+    \nonumber
+    \prf_{\pid, \prtst} =
+    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
+      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
+  \end{multline}
+  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
+  We denote by \(\prfs\) the set of all proofs.
+\end{definition}
+
+% strength
+\NewFunction{\str}{\varsigma}
+
+We can now define the participation count as follows.
+\begin{definition}[Participation count]%
+  \label{DefParticipationCount}
+  We define the \emph{participation count} of a protest \(\prtst\) (as in \cref{DefParticipationProof}) as the cardinality 
+  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
+    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
+      \str(\prf_{i,P})\geq \theta \right\}
+  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
+  threshold \(\theta\).
+\end{definition}
+
+The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
+One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
+%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
+Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
+For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
+In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.

### 2018-08-20 paper/adversary-model.tex
System model: adds overview figure (hand-drawn)
Writes up new system/adversary model

@@
-\subsection{Communication and adversary model}%
+\subsection{System, communication and adversary model}%
 \label{adversary-model}
 
-\dots
+We provide system model with three adversaries of varying strength.
+We will start with the base model and then successively increase the 
+adversary's strength.
+
+\paragraph{The base protester-privacy model}
+
+There are three players: the protest participant (with identity) \(P\), a 
+witness (with identity) \(W\) and the storage \(S\).
+The adversary \(A\) controls \(W\) and \(S\).
+
+The protester \(P\) and the witness \(W\) communicate.
+Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
+\(t_{P,W}\), but specifically \emph{not} the real identities \(P\) and \(W\) 
+directly --- only if it appears in the data \(d_{P,W}(\cid, P)\).
+The protester \(P\) communicates with \(S\), where \(S\) only learns 
+\(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
+communication (\(t_{P,S}\)) but not the real identities.
+As the adversary controls \(W\) and \(S\) he learns everything that they do, 
+but can additionally correlate what he learns from \(W\) and \(S\).
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{system-model.png}
+  \caption{\label{fig:system-model}%
+    An overview of the system model.
+    The protester with real identity \(P\) and witness with real identity \(W\) 
+    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
+    and the time it happened, \(t_{P,W}\).
+    The protester submit some function of the protocol data \(f(d_{P,W}(\cid, 
+      P))\) to the storage \(S\), who learns only that and the time it 
+    happened, \(t_{P,S}\).
+    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
+    \(A\).
+  }
+\end{figure}
+
+\paragraph{A stronger adversary}
+
+Now we define an adversary \(A^W\), where the witness \(W\) learns the 
+protester \(P\)'s identity.
+(\(P\) will also learn \(W\)'s identity.)
+However, \(S\) still does not learn \(P\)'s identity.
+
+We also define an adversary \(A^{W,S}\), where \(S\) also learns \(P\)'s 
+identity.

### 2018-08-20 paper/security-properties.tex
Updates system, adversary model section
Cleans up a bit in security-properties section

@@
 \subsection{Security requirements}%
-\label{Properties}
+\label{security-properties}
 
-%\subsubsection{An overview of the adversary}
-
-To go back to the scenario stated in the introduction, we have two potential adversaries: Alice and Grace.
+To go back to the scenario stated in the introduction, we have two potential 
+adversaries: Alice and Grace.
 Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
@@
 If there is a counterprotest, physical presence with that group means support for the counterprotest.
-In our system, it gets more ambiguous as the participants are counted if all of the following is true 1) they participate in the protocol, 2) they use the protest identifier (cause) for which the count is done, 2) they meet the eligibility criteria, and 3) they receive enough proof shares, 4) that are uploaded to the ledger.
-Thus one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.
+In our system, it gets more ambiguous as the participants are counted if all of the following is true
+\begin{enumerate*}
+\item they participate in the protocol,
+\item they use the protest identifier (cause) for which the count is done,
+\item they meet the eligibility criteria, and
+\item they receive enough proof shares,
+\item that are uploaded to the ledger.
+\end{enumerate*}
+Thus one could participate in a protest and be counted even when physically 
+present at a counter-protest if the two protests are co-located and the 
+participant chooses the corresponding cause/identifier of the original protest.
 
@@
 The privacy properties we need in this context are
+\begin{description}
+  \item[involuntary participant unlinkability] unless the participant discloses 
+    the receipt (by revealing her identity), there is no link between the 
+    protest data on the ledger and the identity of the participant.
 
-involuntary participant unlinkability: unless the participant discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the participant.
-
-involuntary witness unlinkability: unless the witness discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the witness.
+  \item[involuntary witness unlinkability] unless the witness discloses the 
+    receipt (by revealing her identity), there is no link between the protest 
+    data on the ledger and the identity of the witness.
+\end{description}
 \sonja{old}

### 2018-08-20 paper/security-properties.tex
Prettifying a bit in security-properties

@@
 
-The privacy properties we need in this context are
+The privacy properties we need in this context are the following:
 \begin{description}
-  \item[involuntary participant unlinkability] unless the participant discloses 
-    the receipt (by revealing her identity), there is no link between the 
-    protest data on the ledger and the identity of the participant.
+  \item[Involuntary participant unlinkability:] unless the participant 
+    discloses the receipt (by revealing her identity), there is no link between 
+    the protest data on the ledger and the identity of the participant.
 
-  \item[involuntary witness unlinkability] unless the witness discloses the 
+  \item[Involuntary witness unlinkability:] unless the witness discloses the 
     receipt (by revealing her identity), there is no link between the protest 

### 2018-08-20 paper/privacy-properties.tex
Changes system model outline

--- 2018-08-20 paper/security-properties.tex
@@
-\subsection{Security requirements}%
-\label{security-properties}
-
-To go back to the scenario stated in the introduction, we have two potential 
-adversaries: Alice and Grace.
-Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
-In contrast, the aim of Grace, the government Alice protests against, is to not only decrease the count, but also to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
-In the following two subsections, we will define the desired security properties.
-
-\subsubsection{Verifiability}%
-\label{Verifiability}
-
-We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
-Indeed, all three situations correspond to cases in which many individuals express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
-
-Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
-\end{description}
-In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
-In essence, the proof must bind the person to the time and location of the protest.
-
-To define these properties more formally in the context of protest, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
-\begin{requirements}[V]
-  \item\label{EligibilityVerif} \emph{Eligibility}: anyone can verify that each participation proof provides temporal and spatial eligibility and that only one participation proof is counted per individual.
-    \begin{requirements}
-    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
-    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
-    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
-    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
-    \end{requirements}
-
-  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
-
-  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that his participation proof is included in the global count.
-\end{requirements}
-
-\subsubsection{Privacy}%
-\label{Privacy}
+\subsection{Privacy requirements}%
+\label{privacy-properties}
 

### 2018-08-20 paper/system-model.tex
Changes system model outline

--- 2018-08-18 paper/system-model.tex
@@
-\section{System model}
+\section{System and adversary model}%
+\label{system-model}
+
+We will now describe our system and adversary models.
+We first present an abstraction of a protest and how to count the participation 
+(\cref{protest-model}) and the desired verifiabiltiy properties 
+(\cref{verifiability-properties}).
+Next, we present the communication and adversary model (\cref{adversary-model}) 
+together with the desired privacy properties (\cref{privacy-properties}).
 
 \include*{protest-model}
-\include*{security-properties}
+\include*{verifiability-properties}
+\include*{adversary-model}
+\include*{privacy-properties}

### 2018-08-20 paper/verifiability-properties.tex
Changes system model outline

--- 2018-08-18 paper/security-properties.tex
@@
-\subsection{Security requirements}%
-\label{Properties}
-
-%\subsubsection{An overview of the adversary}
-
-To go back to the scenario stated in the introduction, we have two potential adversaries: Alice and Grace.
-Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
-In contrast, the aim of Grace, the government Alice protests against, is to not only decrease the count, but also to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
-In the following two subsections, we will define the desired security properties.
-
-\subsubsection{Verifiability}%
-\label{Verifiability}
+\subsection{Verifiability requirements}%
+\label{verifiability-properties}
 
@@
 \end{requirements}
-
-\subsubsection{Privacy}%
-\label{Privacy}
-
-In addition to the verification requirements, we also need to define the privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{description}
-\item[Vote privacy:] the voting does not reveal any individual vote.
-\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
-\end{description}
-
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
-Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against her will.
-
-\sonja{discussion about applicable properties here, more sources and alternative properties}
-\sonja{new}
-Difference to e-voting:
-physical presence means support for a cause if there is one protest.
-If there is a counterprotest, physical presence with that group means support for the counterprotest.
-In our system, it gets more ambiguous as the participants are counted if all of the following is true 1) they participate in the protocol, 2) they use the protest identifier (cause) for which the count is done, 2) they meet the eligibility criteria, and 3) they receive enough proof shares, 4) that are uploaded to the ledger.
-Thus one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.
-
-Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt, because being counted implies support for a cause.
-This also means that besides physical force, coercion can happen by forcing the participate to show a receipt.
-We thus have to decide between individual verifiability and the privacy properties for e-voting or define privacy properties suitable for the scenario.
-The ultimate privacy requirement is thus stronger here: in contrast to voting, where it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.
-
-The privacy properties we need in this context are
-
-involuntary participant unlinkability: unless the participant discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the participant.
-
-involuntary witness unlinkability: unless the witness discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the witness.
-\sonja{old}
-In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
-As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
-Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
-Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
-
-As a consequence, this leaves us with with what would correspond to vote privacy.
-In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
-Hence, we can summarize the needed privacy properties as follows:
-\begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
-\end{requirements}
-
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.

### 2018-08-21 paper/adversary-model.tex
Tries to name the different models
Updates names of adversary models

@@
 
-\paragraph{The base protester-privacy model}
+\paragraph{The base malicious witness--storage model}
 
@@
 
-\paragraph{A stronger adversary}
+\paragraph{The stronger malicious witness--storage model}
 
-Now we define an adversary \(A^W\), where the witness \(W\) learns the 
-protester \(P\)'s identity.
+Now the witness \(W\) learns the protester \(P\)'s identity.
 (\(P\) will also learn \(W\)'s identity.)
@@
 
-We also define an adversary \(A^{W,S}\), where \(S\) also learns \(P\)'s 
-identity.
+\paragraph{The strongest malicious witness--storage model}
+
+Now \(S\) also learns \(P\)'s identity.

### 2018-08-21 paper/adversary-model.tex
Improves and clarifies adversary model

--- 2018-08-20 paper/adversary-model.tex
@@
 
-We provide system model with three adversaries of varying strength.
-We will start with the base model and then successively increase the 
-adversary's strength.
+We provide a system model with various adversaries.
+We provide three adversaries of varying strength for the protester and two for 
+the witness.
 
-\paragraph{The base protester-privacy model}
+\paragraph{The protester adversary}
 
@@
 
+\begin{definition}[Base protester adversary]\label{base-protester-adversary}
   The protester \(P\) and the witness \(W\) communicate.
   Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
-\(t_{P,W}\), but specifically \emph{not} the real identities \(P\) and \(W\) 
-directly --- only if it appears in the data \(d_{P,W}(\cid, P)\).
+  \(t_{P,W}\)\footnote{%
+    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
+    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
+  }.
   The protester \(P\) communicates with \(S\), where \(S\) only learns 
@@
   communication (\(t_{P,S}\)) but not the real identities.
-As the adversary controls \(W\) and \(S\) he learns everything that they do, 
-but can additionally correlate what he learns from \(W\) and \(S\).
+  The adversary controls \(W\) and \(S\) and thus learns everything that they 
+  do, but can additionally correlate what he learns from \(W\) and \(S\).
+\end{definition}
+
+This definition is illustrated in \cref{fig:system-model}.
 
@@
 
-\paragraph{A stronger adversary}
+We find \cref{base-protester-adversary} suitable when the protester and witness 
+both move in a crowd and there is no way for the witness to decide exactly with 
+whom he or she communicates with.
+However, in some situations this might not be the case, \eg the crowd is not 
+dense.
+In these situations the witness will likely see the face of the protester.
+We capture this by the following definition.
 
-Now we define an adversary \(A^W\), where the witness \(W\) learns the 
-protester \(P\)'s identity.
+\begin{definition}[Stonger protester adversary]%
+  \label{stronger-protester-adversary}
+  The situation is the same as in \cref{base-protester-adversary}, but now the 
+  witness \(W\) learns the protester \(P\)'s identity.
   (\(P\) will also learn \(W\)'s identity.)
   However, \(S\) still does not learn \(P\)'s identity.
+\end{definition}
 
-We also define an adversary \(A^{W,S}\), where \(S\) also learns \(P\)'s 
-identity.
+One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
+communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
+However, given a strong enough adversary, such anonymous communication might 
+not be possible.
+Hence the following definition.
+
+\begin{definition}[Strongest protester adversary]%
+  \label{strongest-protester-adversary}
+  Everything is the same as in \cref{stronger-protester-adversary}, except that 
+  now \(S\) also learns \(P\)'s identity.
+\end{definition}
+
+\paragraph{The witness adversary}
+
+The players are still the same, but now the adversary controls other players.
+In particular, the adversary controls the protester \(P\) and the storage 
+\(S\).
+
+\dots

### 2018-08-21 paper/adversary-model.tex
Adds tikz figures for system model, adds base witness adversary

@@
 
-This definition is illustrated in \cref{fig:system-model}.
+This definition is illustrated in \cref{fig:protester-adversary}.
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{system-model.png}
-  \caption{\label{fig:system-model}%
-    An overview of the system model.
+  \includegraphics{base-protester-adversary.tikz}
+  \caption{\label{fig:protester-adversary}%
+    An overview of the base protester adversary model.
     The protester with real identity \(P\) and witness with real identity \(W\) 
@@
 
-The players are still the same, but now the adversary controls other players.
-In particular, the adversary controls the protester \(P\) and the storage 
+The players are still the same, but now the adversary controls other players: 
+in particular, the adversary controls the protester \(P\) and the storage 
 \(S\).
 
-\dots
+\begin{definition}[Base witness adversary]\label{base-witness-adversary}
+  The witness \(W\) and the protester \(P\) communicate.
+  They learn some protocol data \(d_{W,P}(W)\).
+  The witness later communicates with \(S\), where \(S\) only learns 
+  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
+  \(t_{W,S}\).
+  The adversary controls \(P\) and \(S\).
+\end{definition}
+
+\Cref{base-witness-adversary} is the analogous to 
+\cref{base-protester-adversary}.
+It is illustrated in \cref{fig:witness-adversary}.
+
+\begin{figure}
+  \centering
+  \includegraphics{base-witness-adversary.tikz}
+  \caption{\label{fig:witness-adversary}%
+    An overview of the base witness adversary model.
+    The protester with real identity \(P\) and witness with real identity \(W\) 
+    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
+    time it happened, \(t_{P,W}\).
+    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
+    the storage \(S\), who learns only that and the time it happened, 
+    \(t_{P,S}\).
+    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
+    \(A\).
+  }
+\end{figure}

### 2018-08-22 paper/adversary-model.tex
Updates adversary figures: makes adversaries red

@@
   The witness \(W\) and the protester \(P\) communicate.
-  They learn some protocol data \(d_{W,P}(W)\).
+  They learn some protocol data \(d_{W,P}(W)\) and the time it took place, 
+  \(t_{P,W}\).
   The witness later communicates with \(S\), where \(S\) only learns 
@@
   \(t_{W,S}\).
-  The adversary controls \(P\) and \(S\).
+  The adversary controls \(S\).
 \end{definition}
@@
 \cref{base-protester-adversary}.
-It is illustrated in \cref{fig:witness-adversary}.
+The rationale is the same as for \cref{base-protester-adversary}, the witness 
+\(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
+\Cref{fig:witness-adversary} illustrates the roles and relations.
 
@@
     the storage \(S\), who learns only that and the time it happened, 
-    \(t_{P,S}\).
+    \(t_{W,S}\).
     Both the protester \(P\) and storage \(S\) are controlled by the adversary 

### 2018-08-22 paper/adversary-model.tex
Improves rationale for witness adversary

@@
 \cref{base-protester-adversary}.
-The rationale is the same as for \cref{base-protester-adversary}, the witness 
-\(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
 \Cref{fig:witness-adversary} illustrates the roles and relations.
@@
 \end{figure}
+
+The base rationale is the same as for \cref{base-protester-adversary}, the 
+witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
+Anyone who is in the same location will learn that \(W\) was present, we want 
+to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
+do not consider the protester as part of the adversary, only \(S\).
+We thus conclude with the strongest adversary against the witness.
+
+\begin{definition}[Strongest witness adversary]
+  Things are the same as in \cref{base-witness-adversary}, except that \(S\) 
+  learns the witness' identity \(W\).
+\end{definition}

### 2018-08-23 paper/adversary-model.tex

@@
   The witness \(W\) and the protester \(P\) communicate.
-  They learn some protocol data \(d_{W,P}(W)\) and the time it took place, 
+  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
   \(t_{P,W}\).
   The witness later communicates with \(S\), where \(S\) only learns 
-  \(f(d_{W,P}(W))\), for some function \(f\), and the time it happened, 
+  \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
   \(t_{W,S}\).
@@
     The protester with real identity \(P\) and witness with real identity \(W\) 
-    communicate and each learn only the protocol data, \(d_{P,W}(W)\), and the 
-    time it happened, \(t_{P,W}\).
+    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
+    the time it happened, \(t_{P,W}\).
     The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 

### 2018-08-23 paper/intro.tex

--- 2018-08-17 paper/intro.tex
@@
 The paper is organized as follows.
-First, we define and formalize the notion of protest and discuss its relationship with the domain of electronic voting (\cref{system-model}).  
-Then, we introduce the desired security properties for such a system (\cref{Properties}) and subsequently discuss related work in 
-terms of these properties (\cref{related-work}). 
-Afterwards, we give the relevant background on the building blocks of our solution, including our proposal for distance-bounding anonymous credentials that cope with a malicious (impersonating) verifier (\cref{building-blocks}).
-\PRIVO, the protocol constructed from these building blocks, is then detailed in \cref{Protocol} before an analysis of its security and privacy (\cref{SecurityAnalysis}). 
-Finally, we conclude with a discussion \cref{Discussion} and future work in \cref{Conclusion}.
+First, in \cref{system-model}, we define and formalize the notion of protest 
+and define the desired verifiability properties.
+We also present our system and adversary model together with desired privacy 
+properties.
+Next, in \cref{related-work}, we discuss related work in terms of these 
+properties.
+In \cref{building-blocks}, we give the relevant background on the building 
+blocks of our solution.
+In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
+protocol, different from that originally proposed by 
+\textcite{DistanceBounding}.
+We provide a proof of its security (all desired \ac{DB} properties) 
+\daniel{Check that this is true before publication.} and formally verify it 
+using Tamarin~\cite{TamarinDB}.
+This version of the Schnorr protocol can then be used to do general \ac{DB} 
+anonymous credentials.
+In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
+building blocks.
+This is followed by an analysis of its security and privacy 
+(\cref{SecurityAnalysis}).
+Finally, we conclude with a discussion in \cref{Discussion} and future work in 
+\cref{Conclusion}.

### 2018-08-23 paper/privacy-properties.tex
Adds comment on core privacy property

@@
 
-In addition to the verification requirements, we also need to define the privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\daniel{The main idea is that the adversary cannot link the protester's real 
+  identity \(P\) to the protest cause \cid.}
+
+In addition to the verification requirements, we also need to define the 
+privacy properties.
+In voting protocols, there are mainly three levels of 
+privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{description}
   \item[Vote privacy:] the voting does not reveal any individual vote.
-\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
+  \item[Receipt freeness:] the voting system does not provide any data that can 
+    be used as a proof of how the voter voted.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
+    the vote was cast in any particular way.
 \end{description}
 
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
 Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against her will.
+For instance, someone could simply physically bring Alice to a protest against 
+her will.
+Receipt freeness, while desirable, is not \emph{always} desirable.
+For instance, the location proof might be useful to prove presence to a third 
+party, \eg for strengthening the authenticity of witness information.
 
-\sonja{discussion about applicable properties here, more sources and alternative properties}
+Thus privacy remains.
+For the protester we want unlinkability between a protester's real identity 
+\(P\) and the cause identifier \(\cid\).
+For the witness, we want unlinkability between a witness's identity \(W\) and a 
+location \(l\).
+
+\daniel{End of edits so far.}
+
+\sonja{discussion about applicable properties here, more sources and 
+  alternative properties}
 \sonja{new}
@@
 
-Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt, because being counted implies support for a cause.
-This also means that besides physical force, coercion can happen by forcing the participate to show a receipt.
-We thus have to decide between individual verifiability and the privacy properties for e-voting or define privacy properties suitable for the scenario.
-The ultimate privacy requirement is thus stronger here: in contrast to voting, where it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.
+Given that all conditions for being counted in a protest are met, individual 
+verifiability implies a receipt \daniel{no, I know my proof is included in 
+  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
+  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
+  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
+  hence receipt-freeness} because being counted implies support for a cause. 
+This also means that besides physical force, coercion can happen by forcing the 
+participate to show a receipt. \daniel{The only receipt we have is the private 
+  key of the protester, with that key the adversary can compute \(\pid = 
+    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
+We thus have to decide between individual verifiability and the privacy 
+properties for e-voting or define privacy properties suitable for the scenario. 
+The ultimate privacy requirement is thus stronger here: in contrast to voting, 
+where it is the content of the vote itself that needs to be unlinkable to the 
+voter, here the fact of having cast a vote at all needs to be unlinkable.
 
@@
 \begin{description}
-  \item[Involuntary participant unlinkability:] unless the participant 
-    discloses the receipt (by revealing her identity), there is no link between 
-    the protest data on the ledger and the identity of the participant.
+  \item[Involuntary participant unlinkability:] \daniel{the name has a 
+      double-negative ring to me} unless the participant discloses the receipt 
+    (by revealing her identity), there is no link between the protest data on 
+    the ledger and the identity of the participant.
 
-  \item[Involuntary witness unlinkability:] unless the witness discloses the 
-    receipt (by revealing her identity), there is no link between the protest 
-    data on the ledger and the identity of the witness.
+  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
+      too of course} unless the witness discloses the receipt (by revealing her 
+    identity), there is no link between the protest data on the ledger and the 
+    identity of the witness.
 \end{description}

### 2018-08-23 paper/verifiability-properties.tex

@@
 These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
+(We discuss privacy in \cref{privacy-properties}.)
 
-Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
+We draw inspiration from the three general desirable properties for 
+verifiability, as summarized by 
+\textcite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{description}
@@
 In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
+Universal and individual verifiability remain the same, in the sense that 
+anyone can verify the participation count by counting the proofs.
 The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
@@
 
-To define these properties more formally in the context of protest, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
+To define these properties more in the context of protests, we define three 
+verifiability requirements, among which eligibility can be further broken up 
+into four subproperties:
 \begin{requirements}[V]

### 2018-08-23 paper/adversary-model.tex
Fixes label for witness-adv def, removes treated comment

@@
 
-\begin{definition}[Strongest witness adversary]
+\begin{definition}[Strongest witness adversary]%
+  \label{strongest-witness-adversary}
   Things are the same as in \cref{base-witness-adversary}, except that \(S\) 

### 2018-08-23 paper/privacy-properties.tex
Fixes label for witness-adv def, removes treated comment
Finalizes privacy properties

@@
 \label{privacy-properties}
-
-\daniel{The main idea is that the adversary cannot link the protester's real 
-  identity \(P\) to the protest cause \cid.}
 
@@
 For the protester we want unlinkability between a protester's real identity 
-\(P\) and the cause identifier \(\cid\).
+\(P\) and the cause identifier \(\cid\) against the adversary.
 For the witness, we want unlinkability between a witness's identity \(W\) and a 
-location \(l\).
+location \(l\) against the adversary.
+To understand what unlinkability means in these two cases, we must consider the 
+system and adversary model, which we will define next.
 
-\daniel{End of edits so far.}
+\daniel{I suggest ending here to continue in \cref{adversary-model}.}
 

### 2018-08-23 paper/adversary-model.tex
Starts to generalize adversaries

@@
 
-We provide a system model with various adversaries.
-We provide three adversaries of varying strength for the protester and two for 
-the witness.
+We provide one system model with two possible adversaries: one who tries to 
+link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
+which tries to link a protester's or a witness's real identity (\(P\) 
+respectively \(W\)) to a location (\(l\)).
+We also define varying strengths of each adversary.
 
-\paragraph{The protester adversary}
+\paragraph{The identity--cause linking adversary}
 
@@
 
-\begin{definition}[Base protester adversary]\label{base-protester-adversary}
+\begin{definition}[Base identity--cause adversary]%
+  \label{base-identity-cause-adversary}
   The protester \(P\) and the witness \(W\) communicate.
@@
 
-This definition is illustrated in \cref{fig:protester-adversary}.
+This definition is illustrated in \cref{fig:identity-cause-adversary}.
 
@@
   \centering
-  \includegraphics{base-protester-adversary.tikz}
-  \caption{\label{fig:protester-adversary}%
+  \includegraphics{base-identity-cause-adversary.tikz}
+  \caption{\label{fig:identity-cause-adversary}%
     An overview of the base protester adversary model.
@@
 
-We find \cref{base-protester-adversary} suitable when the protester and witness 
-both move in a crowd and there is no way for the witness to decide exactly with 
-whom he or she communicates with.
+We find \cref{base-identity-cause-adversary} suitable when the protester and 
+witness both move in a crowd and there is no way for the witness to decide 
+exactly with whom he or she communicates with.
 However, in some situations this might not be the case, \eg the crowd is not 
@@
 
-\begin{definition}[Stonger protester adversary]%
-  \label{stronger-protester-adversary}
-  The situation is the same as in \cref{base-protester-adversary}, but now the 
+\begin{definition}[Stonger identity--cause adversary]%
+  \label{stronger-identity-cause-adversary}
+  The situation is the same as in \cref{base-identity-cause-adversary}, but now the 
   witness \(W\) learns the protester \(P\)'s identity.
@@
 
-\begin{definition}[Strongest protester adversary]%
-  \label{strongest-protester-adversary}
-  Everything is the same as in \cref{stronger-protester-adversary}, except that 
-  now \(S\) also learns \(P\)'s identity.
+\begin{definition}[Strongest identity--cause adversary]%
+  \label{strongest-identity-cause-adversary}
+  Everything is the same as in \cref{stronger-identity-cause-adversary}, except 
+  that now \(S\) also learns \(P\)'s identity.
 \end{definition}
 
-\paragraph{The witness adversary}
+\paragraph{The identity--location adversary}
 
@@
 
-\begin{definition}[Base witness adversary]\label{base-witness-adversary}
+\begin{definition}[Base identity--location adversary]%
+  \label{base-identity-location-adversary}
   The witness \(W\) and the protester \(P\) communicate.
@@
 
-\Cref{base-witness-adversary} is the analogous to 
-\cref{base-protester-adversary}.
-\Cref{fig:witness-adversary} illustrates the roles and relations.
+\Cref{base-identity-location-adversary} is the analogous to 
+\cref{base-identity-cause-adversary}.
+\Cref{fig:identity-location-adversary} illustrates the roles and relations.
 
@@
   \centering
-  \includegraphics{base-witness-adversary.tikz}
-  \caption{\label{fig:witness-adversary}%
+  \includegraphics{base-identity-location-adversary.tikz}
+  \caption{\label{fig:identity-location-adversary}%
     An overview of the base witness adversary model.
@@
 
-The base rationale is the same as for \cref{base-protester-adversary}, the 
+The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
 witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
@@
 \begin{definition}[Strongest witness adversary]%
-  \label{strongest-witness-adversary}
-  Things are the same as in \cref{base-witness-adversary}, except that \(S\) 
-  learns the witness' identity \(W\).
+  \label{strongest-identity-location-adversary}
+  Things are the same as in \cref{base-identity-location-adversary}, except 
+  that \(S\) learns the witness' identity \(W\).
 \end{definition}

### 2018-08-23 paper/privacy-properties.tex
Starts to generalize adversaries

@@
 For the witness, we want unlinkability between a witness's identity \(W\) and a 
-location \(l\) against the adversary.
+location \(l\) against an adversary who is not present in the location.
+Due to the limitations of physical space, two individuals present in the same 
+location will inevitably learn of each other's presence.
+Thus we will only try to prevent individuals who are not present to learn of 
+this presence.
+
 To understand what unlinkability means in these two cases, we must consider the 

### 2018-08-26 paper/adversary-model.tex
Adds that adversary must link IOIs
We must still specify what this linking means (see #127).
Fixes typo in adversary model

@@
   do, but can additionally correlate what he learns from \(W\) and \(S\).
+  The adversary wins if he can link \(\cid\) and \(P\).
 \end{definition}
@@
 The players are still the same, but now the adversary controls other players: 
-in particular, the adversary controls the protester \(P\) and the storage 
-\(S\).
+in particular, the adversary controls only the storage \(S\).
 
@@
   The adversary controls \(S\).
+  The adversary wins if he can link \(W\) and \(l\).
 \end{definition}

### 2018-08-28 paper/adversary-model.tex
Brings adversary fig captions up-to-date

@@
   \caption{\label{fig:identity-cause-adversary}%
-    An overview of the base protester adversary model.
+    An overview of the base identity--cause adversary model.
     The protester with real identity \(P\) and witness with real identity \(W\) 
@@
     and the time it happened, \(t_{P,W}\).
-    The protester submit some function of the protocol data \(f(d_{P,W}(\cid, 
-      P))\) to the storage \(S\), who learns only that and the time it 
-    happened, \(t_{P,S}\).
+    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
+    the storage \(S\), who learns only that and the time it happened, 
+    \(t_{P,S}\).
     Both the witness \(W\) and storage \(S\) are controlled by the adversary 
@@
   \caption{\label{fig:identity-location-adversary}%
-    An overview of the base witness adversary model.
+    An overview of the base identity--location adversary model.
     The protester with real identity \(P\) and witness with real identity \(W\) 
@@
     the time it happened, \(t_{P,W}\).
-    The witness submit some function of the protocol data \(f(d_{P,W}(W))\) to 
-    the storage \(S\), who learns only that and the time it happened, 
-    \(t_{W,S}\).
-    Both the protester \(P\) and storage \(S\) are controlled by the adversary 
-    \(A\).
+    The witness submits \(f(d_{P,W}(W))\), for some function \(f\), and the 
+    protester submits \(g(d_{P,W}(P,l))\), for some function \(g\), to the 
+    storage \(S\), who learns only that and the time it happened, \(t_{W,S}\) 
+    respectively \(t_{P,S}\).
+    Only the storage \(S\) is controlled by the adversary \(A\).
   }

### 2018-08-28 paper/adversary-model.tex
Streamlines the adversary models

@@
 not be possible.
-Hence the following definition.
+We capture such a strong adversary in the following definition.
 
@@
   \label{base-identity-location-adversary}
+  The adversary controls \(S\).
   The witness \(W\) and the protester \(P\) communicate.
-  They learn some protocol data \(d_{W,P}(W, l)\) and the time it took place, 
-  \(t_{P,W}\).
+  They learn some protocol data \(d_{W,P}(W, l)\) and \(d_{W,P}(P,l)\) and the 
+  time it took place, \(t_{P,W}\).
+  \begin{description}
+    \item[The witness case:]
       The witness later communicates with \(S\), where \(S\) only learns 
@@
       \(t_{W,S}\).
-  The adversary controls \(S\).
       The adversary wins if he can link \(W\) and \(l\).
+    \item[The protester case:]
+      The protester later communicates with \(S\), where \(S\) only learns 
+      \(g(d_{W,P}(P, l))\), for some function \(g\), and the time it happened, 
+      \(t_{P,S}\).
+      The adversary wins if he can link \(P\) and \(l\).
+  \end{description}
 \end{definition}
 
-\Cref{base-identity-location-adversary} is the analogous to 
-\cref{base-identity-cause-adversary}.
 \Cref{fig:identity-location-adversary} illustrates the roles and relations.
@@
 do not consider the protester as part of the adversary, only \(S\).
-We thus conclude with the strongest adversary against the witness.
+Analogous to the identity--cause adversary, we conclude with the strongest 
+identity--location adversary.
 
-\begin{definition}[Strongest witness adversary]%
+\begin{definition}[Strongest identity--location adversary]%
   \label{strongest-identity-location-adversary}
   Things are the same as in \cref{base-identity-location-adversary}, except 
-  that \(S\) learns the witness' identity \(W\).
+  that \(S\) learns the witness' and protester's identities \(W\) and \(P\), in 
+  the respective cases.
 \end{definition}

### 2018-08-28 paper/adversary-model.tex
Improves identity--location adversary

@@
   The witness \(W\) and the protester \(P\) communicate.
-  They learn some protocol data \(d_{W,P}(W, l)\) and \(d_{W,P}(P,l)\) and the 
-  time it took place, \(t_{P,W}\).
+  They learn some protocol data \(d_{P,W}(P, W, l)\) and the time it took 
+  place, \(t_{P,W}\).
   \begin{description}
@@
       The witness later communicates with \(S\), where \(S\) only learns 
-      \(f(d_{W,P}(W, l))\), for some function \(f\), and the time it happened, 
-      \(t_{W,S}\).
+      \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
+      happened, \(t_{W,S}\).
       The adversary wins if he can link \(W\) and \(l\).
@@
       The protester later communicates with \(S\), where \(S\) only learns 
-      \(g(d_{W,P}(P, l))\), for some function \(g\), and the time it happened, 
-      \(t_{P,S}\).
+      \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 
+      happened, \(t_{P,S}\).
       The adversary wins if he can link \(P\) and \(l\).
@@
     The protester with real identity \(P\) and witness with real identity \(W\) 
-    communicate and each learn only the protocol data, \(d_{P,W}(W, l)\), and 
-    the time it happened, \(t_{P,W}\).
-    The witness submits \(f(d_{P,W}(W))\), for some function \(f\), and the 
-    protester submits \(g(d_{P,W}(P,l))\), for some function \(g\), to the 
-    storage \(S\), who learns only that and the time it happened, \(t_{W,S}\) 
-    respectively \(t_{P,S}\).
+    communicate and each learn only the protocol data, \(d_{P,W}(P, W, l)\), 
+    and the time it happened, \(t_{P,W}\).
+    The witness submits \(f(d_{P,W}(P, W, l))\), for some function \(f\), and 
+    the protester submits \(g(d_{P,W}(P, W, l))\), for some function \(g\), to 
+    the storage \(S\), who learns only that and the time it happened, 
+    \(t_{W,S}\) respectively \(t_{P,S}\).
     Only the storage \(S\) is controlled by the adversary \(A\).

### 2018-08-28 paper/timestamp.tex
Minor clarifications in timestamping

--- 2018-06-15 paper/TimeStamp.tex
@@
 
-We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), \(\TSstamp\) and \(\TStime\) such that
+We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
+\(\TSstamp\) and \(\TStime\) such that
 \begin{itemize}
   \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
-  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to 1\) and \(\TStime[\pi] = t\).
+  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
+    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
 \end{itemize}
@@
 Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = 1\) and \(\TStime[\rho_{t_0}] = t_0\land \TStime[\pi_{t_1}] = t_1\).
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
+\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
+  \TStime[\pi_{t_1}] = t_1\).
 

### 2018-08-28 paper/DB-anon-cred.tex
Bugfix: fixes indexing in DB-Schnorr protocol figure
Compacts DB-Schnorr figure slightly
Fixes typo in DB-Schnorr figure
Fixes erroneous bound for DF adversary in DB-Schnorr

--- 2018-08-16 paper/DB-anon-cred.tex
@@
 
-\subsection{Reattempting a distance-bounding Schnorr protocol}
+\subsection{Reattempting a distance-bounding Schnorr protocol}%
+\label{DBSchnorr}
 
@@
 The verifier will request all \(|q|\) response-bits from one challenge and only 
-\(l\) from the other.
+\(l > 0\) from the other.
 The prover must know the responses for both challenges to successfully pass the 
@@
   \centering
-  \begin{tabular}{p{5cm}cp{5cm}}
+  \begin{tabular}{p{0.8\columnwidth}cp{0.8\columnwidth}}
     \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
@@
     \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
-        l\)} \\
+        l, j\gets 0\)} \\
 
@@
 
-    \(r_i\gets s_{b_i}[i]\)
+    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
     & \(\ProtoSendRight{r_i}\)
     & Record \(\Delta t_i\)
+    \\
+
+    \(j \gets j + b_i\)
+    &
+    &
     \\
@@
       b\).
-    \\
-
-    % null
-    &
-    & \(R \stackrel{?}{=} g^r A^{c_b}\)
+      Accept if \(R = g^r A^{c_b}\).
     \\
@@
 The \ac{DB} phase protects against distance fraud.
-\Iac{DBDF} prover must wait for the challenge bit \(b_i\) before responding 
-with \(r_i\).
-The probability of successfully guessing the order of the challenge bits is 
-\(2^{-(|q|+l)}\) per round or, in total, \(2^{-(|q|+l)n}\).
+Once the prover has received \(l+1\) challenges set to \(b\), it knows that the 
+remaining challenges must also be \(b\).
+\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before 
+responding with \(r_i\) before at least \(l+1\) challenges.
+Thus, the probability of successfully guessing the order of the challenge bits 
+is \(2^{-(l+1)}\) per round in the worst case or, in total, \(2^{-(l+1)n}\).
 

### 2018-08-28 paper/protocol.tex
Points out proof-of-personhood as alternative CA (WIP #128)

@@
 Several entities are involved in our protocol.
-First, \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
+First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
+person's identity and a cryptographic key\footnote{%
+  This can be done by a centralized authority, such as a nation state, or a 
+  decentralized authority, as in the case of 
+  proof-of-personhood~\cite{proof-of-personhood}.
+}.
 The \ac{CA} is only involved in the setup phase.

### 2018-08-28 paper/protocol.tex
Minor clarification for CA footnote in protocol

--- 2018-08-20 paper/protocol.tex
@@
 Several entities are involved in our protocol.
-First, \iac{CA} is responsible for certifying a one-to-one mapping between a person's identity and a cryptographic key.
+First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
+person's identity and a cryptographic key\footnote{%
+  This can be done by a centralized authority, such as a nation state with, 
+  \eg, passports; or a decentralized authority, as in the case of 
+  proof-of-personhood~\cite{proof-of-personhood}.
+}.
 The \ac{CA} is only involved in the setup phase.

### 2018-08-29 paper/protocol.tex
Makes participant the general term, protester the specialized

@@
 The \ac{CA} is only involved in the setup phase.
-Second, a protester is an individual who wants to participate in a given protest.
-A protester can assume three different roles:
+Second, a participant is an individual who wants to participate in a given 
+protest.
+A participant can assume three different roles:
 \begin{enumerate}
 \item The \emph{organizer} has written a manifesto for the protest and forward it to others.
-\item A \emph{participant} is attending the protest and asks witnesses to vouch for his presence.
-\item A \emph{witness} provides proofs to participants that state the participant was indeed participating and such that the proofs are verifiable by third parties.
+\item A \emph{protester} is attending the protest and asks witnesses to vouch 
+  for his presence.
+\item A \emph{witness} provides proofs to protesters which state that the 
+  protester was indeed participating and such that the proofs are verifiable by 
+  third parties.
 \end{enumerate}
-In general, there is one organizer and every protester will act alternatively as both participant and witness.
+In general, there is one organizer and every participant can act alternatively 
+as both protester and witness.
 
@@
 
-\emph{Joining as a participant: \((\pid, t_s)\gets 
+\emph{Joining as a protester: \((\pid, t_s)\gets 
     \PRIVOjoin[_P][\text{manifesto}]\).}
-A participant who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
-Afterwards, this identifier is used to create the protest-specific identifier for the participant, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
+A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
+Afterwards, this identifier is used to create the protest-specific identifier for the protester, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
 \cref{fig:ProofFig,fig:ProtocolOverview}).
 More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
-The participant should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
+The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
 
@@
     \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
-In the participation phase, the participant and the witness construct the proof share of the participant (\cref{fig:ProofFig}).
-The participant blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
+In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
   \tilde\sigma = (\tilde A = A^{r_1},
@@
 Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
-The participant sends \((\pid, \tilde\sigma)\) to the witness.
+The protester sends \((\pid, \tilde\sigma)\) to the witness.
 The witness verifies that
@@
 \end{align*}
-Both the participant and the witness compute
+Both the protester and the witness compute
 \begin{align*}
@@
 \end{align*}
-Afterwards, they run the following \ac{PPK} with the participant as the prover and the witness as the verifier:
+Afterwards, they run the following \ac{PPK} with the protester as the prover and the witness as the verifier:
 \begin{multline*}
@@
 Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
-The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
 The witness replies with a challenge \(c\).
-Afterwards, the participant computes
+Afterwards, the protester computes
 \begin{align*}
@@
 If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
-Following this, the witness returns \((\wid, t_s', l)\) to the participant.
-As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).
+Following this, the witness returns \((\wid, t_s', l)\) to the protester.
+As a consequence, both the protester and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the protester (\cref{fig:ProofFig}).
 
 \emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The participant should as soon as possible commit the proof-share data to the time-stamping service and receive the proof of commitment, \(t_e\gets 
+The protester should as soon as possible commit the proof-share data to the time-stamping service and receive the proof of commitment, \(t_e\gets 
   \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
 The remaining operations are not time critical.
-The participant computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
+The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
 More specifically,
@@
 \end{multline*}
-Finally, the participant uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
+Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
 
 \emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
-The witness should, just as the participant, commit the proof-share data to the time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+The witness should, just as the protester, commit the proof-share data to the time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
 (This is only for redundancy.)

### 2018-08-29 paper/protocol.tex
Adds \cid to what witnesses upload too

--- 2018-08-28 paper/protocol.tex
@@
       W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
+      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
       \text{where} \\
@@
 \emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The participant should as soon as possible commit the proof-share data to the time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+The participant should as soon as possible commit the proof-share data to the 
+time-stamping service and receive the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
 The remaining operations are not time critical.
@@
 
-\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
-The witness should, just as the participant, commit the proof-share data to the time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
+    l]\).}
+The witness should, just as the participant, commit the proof-share data to the 
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
+  l]]\).
 (This is only for redundancy.)
@@
     \end{aligned} \\
-      (\pid, \wid, t_s, t_s', l).
+      (\cid, \pid, \wid, t_s, t_s', l).
 \end{multline*}
-Finally, the witness uploads the tuple \[ \psh_W = (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid}) \] for permanent storage.
+Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
+  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.
 

### 2018-08-29 paper/protocol.tex

--- 2018-08-29 paper/protocol.tex
@@
 \emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester should as soon as possible commit the proof-share data to the time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+The participant should as soon as possible commit the proof-share data to the 
+time-stamping service and receive the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
 The remaining operations are not time critical.
@@
 
-\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
-The witness should, just as the protester, commit the proof-share data to the time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
+\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
+    l]\).}
+The witness should, just as the participant, commit the proof-share data to the 
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
+  l]]\).
 (This is only for redundancy.)

### 2018-08-29 paper/protocol.tex
Edits protocol: fixes lots of typos

--- 2018-08-29 paper/protocol.tex
@@
 First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
-Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
+Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
 Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
@@
 \emph{Registration: \(\sk\gets 
-    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{CA}][\ssk]}\).}
-During the registration phase, each protester generates a secret key and obtains a signature on it by the \ac{CA} but without revealing it to the \ac{CA}.
-At the end, each protester will have a signed secret key while the \ac{CA} will issue only one signature per protester but without knowing the association between a particular key and the identity of the user.
-The protester chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
-The protester acts as prover and the \ac{CA} as verifier while they perform the following \ac{ZKPK} protocol:
+    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{\CA}][\ssk]}\).}
+During the registration phase, each participant generates a secret key and 
+obtains a signature on it by the \ac{CA} but without revealing it to the 
+\ac{CA}.
+At the end, each participant will have a signed secret key while the \ac{CA} 
+will issue only one signature per participant but without knowing the 
+association between a particular key and the identity of the participant.
+The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
+The participant acts as prover and the \ac{CA} as verifier while they perform 
+the following \ac{ZKPK} protocol:
 \[
@@
 If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
-Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x M^{axy})\) and sends it to the protester.
-The protester then verifies that the following equations hold:
+Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
+  C = A^x M^{axy})\) and sends it to the participant.
+The participant then verifies that the following equations hold:
 \begin{align*}
@@
 \end{align*}
-Upon success, the protester sets \(\sk = (\sigma, k, r)\).
+Upon success, the participant sets \(\sk = (\sigma, k, r)\).
 
-The setup and registration phases can be done once and the keys can be reused for an arbitrary number of protests.
-Thus, the registration phase could be easily integrated as part of the issuance of national identity cards, passports or \acp{eID}.
+The setup and registration phases can be done once and the keys can be reused 
+for an arbitrary number of protests.
+Thus, the registration phase could be easily integrated as part of the issuance 
+of national identity cards, passports or \acp{eID}.
 
@@
   \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    \pid = g_T^{1/(k+\cid)} \right\}.
+    \pid = g_T^{1/(k_P+\cid)} \right\}.
 \end{multline*}
@@
 We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
-Afterwards, the \ac{PK} can be designed as follows\footnote{Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple times to achieve security.}.
-The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+Afterwards, the \ac{PK} can be designed as follows.
+(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
+times to achieve security.)
+The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
 The witness replies with a challenge \(c\).
@@
 If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
-Following this, the witness returns \((\wid, t_s', l)\) to the participant.
-As a consequence, both the participant and the witness have the tuple \(\pi = (\pid, \wid, t_s, t_s', l)\), which forms a proof share of the participant (\cref{fig:ProofFig}).
+Following this, the witness returns \((\wid, t_s', l)\) to the protester.
+As a consequence, both the protester and the witness have the tuple \(\pi = 
+  (\pid, \wid, t_s, t_s', l)\), which forms a proof share for the protester 
+(\cref{fig:ProofFig}).
 
@@
   l]]\).
-(This is only for redundancy.)
+(This is to make the time interval as early as possible, whoever is the faster 
+will submit it.)
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
@@
 
-While there are various ways for verifying the participation count, hereafter we will detail the two suggested just after \cref{DefParticipationCount}.
+While there are various ways for verifying the participation count, hereafter, 
+we will detail the two suggested just after \cref{DefParticipationCount}.
 In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
 Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
-In the second approach, we have a higher trust in specific witnesses and no 
-trust in others.
+In the second approach, we trust specific witnesses, but no others.
 In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
+It is the strength function \(\str\) of \cref{DefParticipationCount} that 
+differ in the two cases.
+We will first give the procedure and then how to construct the two different 
+strength functions.
 
@@
 \cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
-  (\cid, \pid_i, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
-    (i)}, l_i, \prf_{\pid_i}, \prf_{\wid_i})\), from the blockchain and verify 
-\(\prf_{\pid_i}\) and \(\prf_{\wid_i}\) and that the interval starting at the 
-latest of \(t_s^{(i)}, t_s^{\prime (i)}\) and ending at the earliest of 
-\(t_e^{(i)}, t_e^{\prime (i)}\) is a subset of \(t\) and that \(l_i\subseteq  
-  l\).
+  (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
+    (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})\) for each protester \(j\) 
+from the blockchain, verify \(\prf_{\pid_j}^{(i)}\), \(\prf_{\wid_i}\) and that 
+the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime (i)})}{\min(t_e^{(i)}, 
+    t_e^{\prime (i)})}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
 Any proof share that does not verify correctly will be discarded.
@@
 \cref{DefProofShares} and can thus construct any participation proof 
-\(\prf_{\pid_i, P}\) as in \cref{DefParticipationProof}.
+\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
 Now the verifier can compute the participation count \(|\prfs_P^{\str, 
     \theta}|\) as in \cref{DefParticipationCount}.
-It is the strength function \(\str\) that differ in the two cases we give.
 
 In the case \emph{without} trusted witnesses, the verifier simply define 
-\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to our 
-desired thresold.
+\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to the 
+desired threshold.
 
@@
 of all such proof shares or digitally sign each proof share.
-Then the verifier defines \[
+Then the verifier can define \[
   \str[\prf_{\pid_i, P}] = \begin{cases}

### 2018-08-29 paper/protocol.tex

@@
 times to achieve security.)
-The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
+sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
+  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
 The witness replies with a challenge \(c\).
-Afterwards, the participant computes
+Afterwards, the protester computes
 \begin{align*}
@@
 The remaining operations are not time critical.
-The participant computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
+The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
 More specifically,
@@
 \end{multline*}
-Finally, the participant uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
+Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
 

### 2018-08-30 paper/protocol.tex

@@
         \\
-        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
+        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
       P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
@@
 As a consequence, both the protester and the witness have the tuple \(\pi = 
-  (\pid, \wid, t_s, t_s', l)\), which forms a proof share for the protester 
-(\cref{fig:ProofFig}).
+  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
+protester (\cref{fig:ProofFig}).
 

### 2018-08-30 paper/protocol.tex
Improves proof-share figure

@@
     The witness \(W\)'s identifier \(\wid\) is computed using the
-    witness's key \(\sk_W\) and \sonja{the other's?}\(\pid\).
+    witness's key \(\sk_W\) and the protester's \(\pid\).
     \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
-    All values are signed by the witness while also proving the correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
+    All values are signed by the witness (signature \(\prf_W\)) while also 
+    proving the correctness of \(\wid\) and knowledge of a signature on 
+    \(\sk_W\).
+    The protester constructs \(\prf_P\) analogously.
   }%

### 2018-08-30 paper/timestamp.tex

@@
 
-We need a time-stamping service, \(\TS\), with algorithms \(\TSget\), 
-\(\TSstamp\) and \(\TStime\) such that
+We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), 
+\(\TSstamp\) and \(\TStime\) requests such that
 \begin{itemize}
@@
 
-With these building blocks we can ensure that a message \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-After time \(t_0\), request \(\rho_{t_0}\gets \TSget\).
-Before time \(t_1\), submit \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).
+With these building blocks we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
+After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
+Before time \(t_1\), a user submits \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).
 
-Now we can use \((\rho_{t_0}, m, \pi_{t_1})\) to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
+The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
 The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
@@
 
-We can instantiate \(\TS\) using a distributed ledger, for instance a blockchain instance such as OmniLedger~\cite{OmniLedger}.
-The \(\TSstamp[x]\) algorithm will simply include \(x\) in the blockchain and return the identifier of the block into which \(x\) was included.
-\(\TSget\) will return the hash of the current head of the chain.
-This value is difficult to predict since it depends on all submitted transactions and additional randomness (\eg nonces and miners' secrets).
-The blockchain must also be continuously extended, such as in Bitcoin~\cite{Bitcoin}, in which a new block appears approximately every 10 minutes.
-%Seb: why is the idea of using a dedicated blockchain not appropriate? we should give more arguments to justify it
-Having a dedicated blockchain for a protest is not appropriate, and thus it is better to use a generic blockchain that is used also for other things.
+\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
+If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
+The \(\TSget\) request returns the hash of the most recent block of the chain (the head).
+The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).
 
-There are some additional properties that we need from \(\TS\), which are implied by blockchains.
-First, we need \emph{immutability}, to ensure that once we commit something (through \(\TSstamp\)) it will remain there.
-Immutability will also ensure verifiability as the data must remain available to be verifiable.
-Second, once we have committed some data, we do not need to keep the data itself, but we can store some confirmation value instead.
-For instance in a blockchain, we can store the hash of the block in which our data was committed.
-As a consequence, as this block will remain, we are also sure that our data stay committed.\sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}
+Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
+The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
+A similar reasoning can be made with Proof-of-Work consensus where the computing power of the honest participants must outpower the one of malicious participants.
+In both cases, assuming a majority of honest members in the population, the more participants the merrier.
+
+We require a few additional properties from \(\TS\) that are already provided by blockchains.
+First, \(\TS\) must be continuously extended, such as in Bitcoin where blocks are created every 10 minutes on average.
+Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
+Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
+In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her proof and the hash of the proof.
+\sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}

### 2018-08-30 paper/distance-bounding.tex
Fixes typo: PKE to PK

--- 2018-08-14 paper/DistanceBounding.tex
@@
 \subsection{Distance-bounding protocols}%
-\label{DistanceBounding}
+\label{distance-bounding}
 
@@
 More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
-The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).
+The choice of the anonymous credential system will affect the properties we 
+require of the \ac{PPK} (\eg that it must be \iac{PK} for discrete logarithms).

### 2018-08-30 paper/DB-anon-cred.tex
Removes treated comments from DB-Schnorr
some items from the to do list

@@
   shorter notation.}.
-However, ProProx is secure against a malicious verifier and provides \iac{PPK} 
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} 
 protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)) while in our context, we need \iac{PPK} protocol for discrete 
-logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)).
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
+logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of 
+anonymous credentials whose desirable properties we list in
+\cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
 To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
@@
 verifier.
-\sonja{Contrast with \ac{DBIF}}
 
@@
 
-%The prover will only provide one of the responses and \(l\) bits of the other. 
-%Even if the adversary re-runs the protocol with the same challenges, the 
-%randomly chosen \(\rho\) will have changed --- which thus yields another \(R\) 
-%at the end of the protocol.
-
 The protocol is \ac{DBTF}-resistant, indeed, if the malicious prover gives both 
@@
 phase, not the challenge bitstring as in the protocol of Brands-Chaum.
-\sonja{this is analysis but not in the analysis section}
-\daniel{I prefer to prove the building blocks separately, then prove the full 
-  composite scheme in the analysis section.
-  This protocol with a proof would be a contribution in itself.}
 

### 2018-08-30 paper/distance-bounding.tex
some items from the to do list

@@
   \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
   \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
@@
 This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
-The choice of the anonymous credential system will affect the properties we 
-require of the \ac{PPK} (\eg that it must be \iac{PK} for discrete logarithms).
+More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}). \sonja{Daniel, fix this sentence:}
+The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-08-30 paper/DB-anon-cred.tex

@@
 \ac{DB} phase.
+The reason for the two challenges (change from Schnorr) is that
+knowing the responses to both means learning $\alpha$ (for
+\ac{DBTF}). Bundling the authentication into the distance bounding
+phase (additional change from Brands-Chaum) was done for \ac{DBDH},
+and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
 
@@
 
+\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
+  complete this sentence:, our changes don't break Schnorr because ...}
 Finally, a malicious verifier who wants to impersonate a prover can guess the 
@@
 the prover.
-The probability that this succeeds is, as above, \(2^{-(|q|-l)}\).
+The probability that this succeeds is, as above,
+\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
+shared secrets and thus assume an honest verifier, this limits the
+inherent advantage of our public-key
+\ac{DB} scheme.

### 2018-08-30 paper/intro.tex

@@
 More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
-Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration attendance~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
+Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
@@
 }
+\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
+and thus we are, to the best of our knowledge, the first to provide \emph{general} \ac{DB} anonymous credentials.
 \emph{Outline.} 
@@
 \cref{Conclusion}.
+\sonja{add (sub) sections for performance and verification}

### 2018-08-30 paper/protest-model.tex
Merges protest model and security properties into system model

--- 2018-06-11 paper/SystemModel.tex
@@
-\section{Defining and formalizing protest and crowd estimation}%
-\label{SystemModel}
+\subsection{Defining and formalizing protest and crowd estimation}%
+\label{protest-model}
 
@@
 }.
-These rallies were all in the same location in the capital city and repeated every weekend for the duration of a few weeks.
+These rallies were all in the same location in the capital and repeated every weekend for the duration of a few weeks.
 The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
@@
 participated at any time and in any of the
-locations~\cite{2016DemonstrationsInSeoul} \sonja{commented out for
-  repetition: %\footnote{Note that the objective does not necessarily
+locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
+  %repetition: %\footnote{Note that the objective does not necessarily
               %align with the definition of the police whose interest
@@
               %time to deploy enough personnel for crowd-control.
-}.
+%}.
 % cause identifier
@@
 
-The protests described in the previous examples can be captured using this definition by decomposing them up into subprotests.
+The protests described in the previous examples can be captured using this definition by decomposing them into subprotests.
 Each subprotest will then be encapsulated by our definition and to estimate the total participation to the protest we can just sum up the estimates obtained.
@@
 Each participant who wants to be counted must submit a \emph{participation proof}.
-The proof must be associated with the protest (\ie its identifier \(cid\)), and its time and location must coincide with one of the subprotests.
+The proof must be associated with the protest (\ie its cause identifier \(cid\)), and its time and location must coincide with one of the subprotests.
 
 Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
-A witness is only allowed to create one proof share per protester to avoid the risk of inflation.
+A witness is only allowed to create one proof share per protester to
+avoid the risk of count inflation.
 Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
 %Seb: the sentence below is not very clear, it should be rephrased to make it clearer
-The participation proof and its proof shares are stored in a set, as there should be only unique proof shares.
+The participation proof and its proof shares are stored in a set, as
+there should only be unique proof shares.
 
@@
 % proofs
-
+\sonja{what is the subscript i and do we need to have it here?}
 \begin{definition}[Participation proof]%

### 2018-08-30 paper/verifiability-properties.tex

@@
 
-To define these properties more in the context of protests, we define three 
+To adapt these properties to the context of protests, we define three 
 verifiability requirements, among which eligibility can be further broken up 
@@
     \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
-    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
+    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
     \end{requirements}

### 2018-08-30 paper/conclusions.tex
Clarification and typo fix (WIP #133)

@@
 Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
-Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.
+Moreover, if they provided individual verifiability, they would likely violate 
+the privacy requirements --- if people must recognize themselves in photos, 
+others can recognize them too.
 
@@
 However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
-While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
+While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
 We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.

### 2018-08-30 paper/DB-anon-cred.tex
more items

@@
 In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking}, in addition to not being secure against terrorist fraud.
+However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
 We now propose another way to turn the Schnorr protocol into a
@@
 inherent advantage of our public-key
-\ac{DB} scheme.
+\ac{DB} scheme.  \sonja{verifier impersonating prover: vulnerability
+  we introduce against public-key DB schemes, mitigated by limiting
+  size of l (bits of other s). Trade-off: want long l for reducing
+  success of guessing correct sequence of challenge bits, want short l
+  for reducing success of guessing the other s and finding alpha}
+
+\sonja{\subsection{Formal Verification} 
+ verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
+assumed equivalence with Fiat-Shamir model. Not straightforward to
+implement Schnorr in Tamarin due to a lack of expressiveness for
+arithmetic needed to complement Diffie-Hellman. If not done now, left
+for future work. }

### 2018-08-30 paper/conclusions.tex
more items

--- 2018-08-13 paper/conclusions.tex
@@
 }
+With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
 
@@
 Moreover, if they provided individual verifiability, they would likely violate the privacy requirements.
-
+\sonja{Daniel, explain the previous sentence, is that from you?}
 Finally, most of the current methods are estimates, with quite some error margins. 

### 2018-08-30 paper/protocol.tex
Fixes PLR's comment on proof-of-personhood and collective signing
more items

@@
   This can be done by a centralized authority, such as a nation state with, 
-  \eg, passports; or a decentralized authority, as in the case of 
+  \eg, passports; or a decentralized authority, as in the case of a a 
+  collective authority~\cite{collective-signing} powered by 
   proof-of-personhood~\cite{proof-of-personhood}.
@@
     The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s identifier \(\wid\) is computed using the
+    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
     witness's key \(\sk_W\) and the protester's \(\pid\).

### 2018-08-30 paper/protocol.tex
Adds SPK expanation to proof share figure

@@
     The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
+    The witness \(W\)'s identifier \(\wid\) is computed using the
     witness's key \(\sk_W\) and the protester's \(\pid\).
     \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
-    All values are signed by the witness (signature \(\prf_W\)) while also 
-    proving the correctness of \(\wid\) and knowledge of a signature on 
-    \(\sk_W\).
+    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
+      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
+    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
     The protester constructs \(\prf_P\) analogously.

### 2018-08-30 paper/DB-anon-cred.tex
Adds description of DB-Schnorr (WIP #133)

--- 2018-08-30 paper/DB-anon-cred.tex
@@
 We present the protocol in \cref{SchnorrFigure}.
-The main difference to the original Schnorr protocol is that the prover commits 
-to one random value but the verifier sends \emph{two challenges}.
-This is also different from Brands-Chaum, where the prover and verifier jointly 
-construct the challenge.
-(We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.)
-The verifier will request all \(|q|\) response-bits from one challenge and only 
-\(l > 0\) from the other.
+The group with generator \(g\) and order \(q\) are system parameters.
+The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once 
+by the prover in the setup phase.
+
+During one round, the prover generates a random nonce \(\rho\rgets \ZZ_q\), 
+computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
+The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
+and sends them to the prover.
+The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
+This is the main difference to the original Schnorr protocol: the verifier 
+selects two challenges and the prover \emph{computes} two responses --- but 
+still only \emph{one nonce}, \(\rho\).
+(This is also different from Brands-Chaum, where the prover and verifier 
+jointly construct \emph{one} challenge with \emph{one} response.)
+We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
+The verifier will request all \(|q|\) response-bits from one challenge (say 
+\(s_b, b\in \bin\)) and only \(l > 0\) from the other (\(s_{1-b}\)).
+Finally, the verifier has \(s_b\) and can authenticate the prover by checking 
+if \(R = g^{s_b}A^{c_b}\).
+
 The prover must know the responses for both challenges to successfully pass the 
 \ac{DB} phase.
-The reason for the two challenges (change from Schnorr) is that
-knowing the responses to both means learning $\alpha$ (for
-\ac{DBTF}). Bundling the authentication into the distance bounding
-phase (additional change from Brands-Chaum) was done for \ac{DBDH},
+The reason for the two challenges but only one random nonce (change from 
+Schnorr) is that knowing the responses to both means learning \(\alpha\) (for
+\ac{DBTF}).
+Bundling the authentication into the distance bounding phase (difference from 
+Brands-Chaum) was done for \ac{DBDH},
 and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
@@
     &
-    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
+    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
       b\).
-      Accept if \(R = g^r A^{c_b}\).
+      Accept if \(R = g^{s_b} A^{c_b}\).
     \\

### 2018-08-30 paper/DB-anon-cred.tex
Typo fix: s = \rho - c\alpha, not s = \rho + c\alpha

@@
 
-    \(s_0\gets \rho + c_0\alpha \pmod q\)
+    \(s_0\gets \rho - c_0\alpha \pmod q\)
     &
@@
 
-    \(s_1\gets \rho + c_1\alpha \pmod q\)
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
     &

### 2018-08-30 paper/MANETs.tex

@@
 This could be accomplished by Bluetooth or WiFi communications, as demonstrated by Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of applications for communication during protests via wireless mesh networking.
+The crowd-counting scenario likely has higher requirements on capacity and withstanding interference as the participants continuously run the protocol for witnessing each others presence; messages are presumably less frequent.
+5G is intended to cope with billions of devices (IoT), and thus could help cope with the device density in crowds.
 An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 

### 2018-08-30 paper/protocol.tex
and some more

@@
     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submits the proof shares to a permanent storage \(S\).
+    Finally, both \(P\) and \(W\) submit the proof shares to a
+    permanent storage \(S\). Note that \pid always refers to the
+    protester whose presence is being witnessed.
   }%

### 2018-08-31 paper/privacy-properties.tex
Adds P1 and P2 to privacy properties again

@@
 \(P\) and the cause identifier \(\cid\) against the adversary.
+Given a participation proof, Grace will not be able to tell if it belongs to 
+Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice's, she should not 
+be able to link another proof (\eg, from a different protest) as a consequence.
+
 For the witness, we want unlinkability between a witness's identity \(W\) and a 
@@
 
-To understand what unlinkability means in these two cases, we must consider the 
-system and adversary model, which we will define next.
+We can thus summarize the desired privacy properties as follows:
+\begin{requirements}[P]
+\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
+  identities must be unlinkable to their proofs.
+\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
+  unlinkable between protests and witnesses' proofs must be unlinkable between 
+  protesters.
+\end{requirements}
 
-\daniel{I suggest ending here to continue in \cref{adversary-model}.}
+As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+This is, in fact, is a slight increase in privacy over ordinary protests.
+
+\daniel{I suggest ending here to continue in \cref{adversary-model}. I've now 
+  added P1 and P2.}
 

### 2018-09-03 paper/DB-anon-cred.tex
Starts writing about the l bits in DB-Schnorr

@@
 Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
-The adversary can also guess the remaining \(|q|-l\) bits, for which the 
-probability of success is \(2^{-(|q|-l)}\) (note that this is independent of 
-the rounds).
-Thus, the success probability of the \ac{DBMF} adversary is \emph{at most} 
+The adversary can also guess the remaining \(|q|-l\) bits, which we will 
+discuss more below.
+Guessing these bits is independent of the rounds and can be estimated to be 
+\(2^{-(|q|-l)}\) (more details below).
+Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
 \(2^{-n}+2^{-(|q|-l)}\).
@@
 
-\ac{DBIF} resistance follows from Schnorr.\sonja{Daniel, please
-  complete this sentence:, our changes don't break Schnorr because ...}
-Finally, a malicious verifier who wants to impersonate a prover can guess the 
-remaining \(|q|-l\) bits after the protocol finished to compute the secret of 
-the prover.
-The probability that this succeeds is, as above,
-\(2^{-(|q|-l)}\). While the majority of \ac{DB} schemes are based on
+Finally, it follows from the original Schnorr protocol that this is still 
+\iac{PK} and \ac{ZK}.
+The main concern is whether a malicious verifier can guess the remaining 
+\(|q|-l\) bits after the protocol finished to compute the secret of the prover.
+If we \emph{assume} that the adversary learning \(l > 0\) out of \(n\) bits is 
+equivalent to the adversary learning nothing out of \(n-l\) bits, then the 
+probability that the adversary succeeds is, as above, \(2^{-(|q|-l)}\).
+
+\daniel{Not sure I follow exactly in the following.}
+While the majority of \ac{DB} schemes are based on
 shared secrets and thus assume an honest verifier, this limits the
-inherent advantage of our public-key
-\ac{DB} scheme.  \sonja{verifier impersonating prover: vulnerability
+inherent advantage of our public-key \ac{DB} scheme.
+\sonja{verifier impersonating prover: vulnerability
   we introduce against public-key DB schemes, mitigated by limiting

### 2018-10-29 paper/DB-anon-cred.tex

@@
 \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-The public-key property implies protection against an impersonating
-verifier.
+It is important in our setting that the protocol is a public-key protocol, this 
+property implies protection against an impersonating verifiers.
 
 We present the protocol in \cref{SchnorrFigure}.
-The group with generator \(g\) and order \(q\) are system parameters.
+The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
 The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once 
@@
 
-During one round, the prover generates a random nonce \(\rho\rgets \ZZ_q\), 
-computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
-and sends them to the prover.
-The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
-This is the main difference to the original Schnorr protocol: the verifier 
-selects two challenges and the prover \emph{computes} two responses --- but 
-still only \emph{one nonce}, \(\rho\).
-(This is also different from Brands-Chaum, where the prover and verifier 
-jointly construct \emph{one} challenge with \emph{one} response.)
-We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(|q|\) response-bits from one challenge (say 
-\(s_b, b\in \bin\)) and only \(l > 0\) from the other (\(s_{1-b}\)).
-Finally, the verifier has \(s_b\) and can authenticate the prover by checking 
-if \(R = g^{s_b}A^{c_b}\).
-
-The prover must know the responses for both challenges to successfully pass the 
-\ac{DB} phase.
-The reason for the two challenges but only one random nonce (change from 
-Schnorr) is that knowing the responses to both means learning \(\alpha\) (for
-\ac{DBTF}).
-Bundling the authentication into the distance bounding phase (difference from 
-Brands-Chaum) was done for \ac{DBDH},
-and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
-
 \begin{figure*}
   \centering
+  \small
   \begin{tabular}{p{0.8\columnwidth}cp{0.8\columnwidth}}
@@
 
-    \(s_0\gets \rho - c_0\alpha \pmod q\)
+    \(\forall i\in\bin\colon s_i\gets \rho - c_i\alpha \mod q\)
     &
@@
 
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    \(\forall i\in\bin\colon s_i^{(0)} \rgets \ZZ_q, s_i^{(1)} \gets s_i - 
+      s_i^{(0)} \mod q\)
     &
-    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
+    & Prepare \(B\in \bin^{2|q|+l}\), with \(2|q|\) bits set to \(b\).
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
-        l, j\gets 0\)} \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 2|q| 
+        + l, j\gets 0\)} \\
 
@@
 
-    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
+    \(r_i\gets (s_{b_i}^{(0)}\concat s_{b_i}^{(1)})[jb_i + (i-j)(1-b_i)]\)
     & \(\ProtoSendRight{r_i}\)
@@
     &
-    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
-      b\).
+    & Construct \(s_b^{(0)}\concat s_b^{(1)}\) as the concatenation of 
+    \(r_i\)'s for which \(b_i = b\).
+    Compute \(s_b\gets s_b^{(0)} + s_b^{(1)}\).
       Accept if \(R = g^{s_b} A^{c_b}\).
@@
 
+During one round, the prover commits to a random nonce: \ie chooses 
+\(\rho\rgets \ZZ_q\) uniformly randomly, computes \(R\gets g^\rho\) and sends 
+\(R\) to the verifier.
+The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
+and sends them to the prover.
+The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
+This is the main difference to the original Schnorr protocol: the verifier 
+selects two challenges and the prover \emph{computes} two responses --- but 
+still only \emph{one nonce}, \(\rho\).
+(This is also different from Brands-Chaum, where the prover and verifier 
+jointly construct \emph{one} challenge with \emph{one} response.)
+
+Now the prover randomly chooses
+\(s_0^{(0)}, s_1^{(0)}\in \ZZ_q\)
+and computes
+\(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
+\Ie \(s_b, b\in\bin\) can be reconstructed from the two shares \(s_b^{(0)}, 
+  s_b^{(1)}\).
+
+We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
+The verifier will request all \(2|q|\) response-bits from one challenge (say 
+\(s_b^{(0)}\concat s_b^{(1)}, b\in \bin\)) and only \(0 < l\leq |q|\) from the 
+other (\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
+Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally 
+authenticate the prover by checking if \(R = g^{s_b}A^{c_b}\).
+
+The prover must know the responses for both challenges to successfully pass the 
+\ac{DB} phase.
+The reason for the two challenges but only one random nonce (change from 
+Schnorr) is that knowing the responses to both means learning \(\alpha\) (for
+\ac{DBTF}).
+Bundling the authentication into the distance bounding phase (difference from 
+Brands-Chaum) was done for \ac{DBDH},
+and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
+The reason we use secret sharing and not \(s_b\) directly, is to bound the 
+\(l\) bits the verifier must learn of \(s_{1-b}\):
+Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with 
+secret sharing the verifier learns \(l\) bits of \emph{one share} (provided 
+\(l\) is small enough).
+Thus we have information theoretic security although we reveal these \(l\) 
+bits.
+
 \subsection{Security analysis}
@@
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmically with 
-respect to the security parameter \(\lambda\) and repeat the protocol \(n\) 
-times, such that the knowledge error, \(2^{-kn}\), becomes small enough.
-This is also needed to decrease the success probability of some of adversaries 
-presented below.
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
+security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
+the knowledge error, \(2^{-kn}\), becomes small enough.
+Repeating the protocol is also needed to decrease the success probability of 
+some of adversaries presented below.
 
@@
 \Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before 
-responding with \(r_i\) before at least \(l+1\) challenges.
+responding with \(r_i\) for \(l+1\) challenges.
 Thus, the probability of successfully guessing the order of the challenge bits 
-is \(2^{-(l+1)}\) per round in the worst case or, in total, \(2^{-(l+1)n}\).
+is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
 
@@
 By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
-only \(l\) bits of the other.
+none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information 
+theoretically independent \(|q|\)-bit shares.
 The adversary now has two options.
@@
 receive the correct \(r_i\) --- this relay will be detected.
-The (better) alternative is to guess \(b\) and extract the \(|q|\) correct bits 
-for this challenge from the prover.
+The (better) alternative is to guess \(b\) and extract \(s_b\) for this 
+challenge from the prover.
 Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
@@
 Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
-The adversary can also guess the remaining \(|q|-l\) bits, which we will 
+The adversary can also guess the remaining \(2|q|-l\) bits, which we will 
 discuss more below.
-Guessing these bits is independent of the rounds and can be estimated to be 
-\(2^{-(|q|-l)}\) (more details below).
+The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
+However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more 
+expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
 Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-(|q|-l)}\).
+\(2^{-n}+2^{-|q|n}\).
 
 The protocol is \ac{DBTF}-resistant, indeed, if the malicious prover gives both 
-responses to the adversary, the adversary can compute his secret key.
-In fact, this property is tied to the knowledge extractor used in the proof of 
-the \ac{ZKPK} property of the Schnorr protocol.
+responses to the accomplice, the accomplice can compute his secret key.
 The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie 
@@
 The protocol is also secure against distance hijacking due to the fact
-that it is the authentication bitstring that is used during the \ac{DB}
+that it is the authenticating bitstring that is used during the \ac{DB}
 phase, not the challenge bitstring as in the protocol of Brands-Chaum.
@@
 \iac{PK} and \ac{ZK}.
-The main concern is whether a malicious verifier can guess the remaining 
-\(|q|-l\) bits after the protocol finished to compute the secret of the prover.
-If we \emph{assume} that the adversary learning \(l > 0\) out of \(n\) bits is 
-equivalent to the adversary learning nothing out of \(n-l\) bits, then the 
-probability that the adversary succeeds is, as above, \(2^{-(|q|-l)}\).
-
-\daniel{Not sure I follow exactly in the following.}
-While the majority of \ac{DB} schemes are based on
-shared secrets and thus assume an honest verifier, this limits the
-inherent advantage of our public-key \ac{DB} scheme.
-\sonja{verifier impersonating prover: vulnerability
-  we introduce against public-key DB schemes, mitigated by limiting
-  size of l (bits of other s). Trade-off: want long l for reducing
-  success of guessing correct sequence of challenge bits, want short l
-  for reducing success of guessing the other s and finding alpha}
+\daniel{I should prove this for the composed protocol, I should check the 
+  details with Douglas.}
 

### 2018-10-29 performance/charm-crocus.py
Adds basic automation for running Charm stuff

@@ -1,0 +1,121 @@
+from charm.core.engine.protocol import *
+from charm.toolbox.ecgroup import ECGroup,G
+from socket import socket,AF_INET,SOCK_STREAM
+from charm.toolbox.eccurve import prime192v1
+from charm.toolbox.enum import Enum
+import sys
+
+
+#Setup for Prover/Verifier interactions
+party = Enum('Verifier', 'Prover')
+PROVER,VERIFIER = party.Prover, party.Verifier
+HOST, PORT = "", 8082
+
+class SchnorrZK(Protocol):
+    def __init__(self, builtin_cv, common_input=None):
+        Protocol.__init__(self, None)        
+        verifier_states = { 2:self.verifier_state2, 4:self.verifier_state4, 6:self.verifier_state6 }
+        prover_states = { 1:self.prover_state1, 3:self.prover_state3, 5:self.prover_state5 }
+
+        verifier_trans = { 2:4, 4:[2,6] }
+        prover_trans = { 1:3, 3:5, 5:1 }
+        # describe the parties involved and the valid transitions
+        Protocol.addPartyType(self, VERIFIER, verifier_states, verifier_trans)
+        Protocol.addPartyType(self, PROVER, prover_states, prover_trans, True)
+
+        self.group = ECGroup(builtin_cv)
+        #db = {}
+        Protocol.setSubclassVars(self, self.group) #, db)
+        
+    # PROVER states
+    def prover_state1(self):
+        x = self.group.random()
+        r, g = self.group.random(), self.group.random(G)
+        t = g ** r 
+        print('prover: ',"hello to verifier.")
+        Protocol.store(self, ('r',r), ('x',x))
+        Protocol.setState(self, 3)
+        return {'t':t, 'g':g, 'y':g ** x } # output goes to the next state.
+
+     
+    def prover_state3( self, input): #CHALLENGE phase
+        print("state3 => ", input)
+        (r, x, c0, c1) = Protocol.get(self, ['r', 'x', 'c0', 'c1'])
+        s0 = r + c0 * x
+        s0_0 = self.group.random()
+        s0_1 = s0 - s0_0
+        s1 = r + c1 * x
+        s1_0 = self.group.random()
+        s1_1 = s1 - s1_0
+        Protocol.setState(self, 5)
+        return {'s0_0':s0_0, 's0_1':s0_1, 's1_0':s1_0, 's1_1':s1_1}
+
+
+    def prover_state5( self, input ):
+        print("state5 => ", input)
[…]

### 2018-10-29 performance/charm-crocus.py
Python typo, s/SchnorrZK/CROCUS/g

@@ -11,7 +11,7 @@ party = Enum('Verifier', 'Prover')
 PROVER,VERIFIER = party.Prover, party.Verifier
 HOST, PORT = "", 8082
 
-class SchnorrZK(Protocol):
+class CROCUS(Protocol):
     def __init__(self, builtin_cv, common_input=None):
         Protocol.__init__(self, None)        
         verifier_states = { 2:self.verifier_state2, 4:self.verifier_state4, 6:self.verifier_state6 }
@@ -66,7 +66,7 @@ class SchnorrZK(Protocol):
         c0 = self.group.random()
         c1 = self.group.random()
 
-        print("state2 generate c0 := {}, c1 := {}" % (c0, c1))
+        print("state2 generate c0 := {}, c1 := {}".format(c0, c1))
         Protocol.store(self, ('c0',c0), ('c1', c1))
         Protocol.setState(self, 4)
         return {'c0':c0, 'c1':c1}
@@ -96,7 +96,7 @@ class SchnorrZK(Protocol):
 
     
 if __name__ == "__main__":
-    sp = SchnorrZK(prime192v1)
+    sp = CROCUS(prime192v1)
 
     if sys.argv[1] == "-v":
         print("Operating as verifier...")

### 2018-10-29 performance/charm-schnorr.py
Cleans away some comments

@@ -41,7 +41,7 @@ class SchnorrZK(Protocol):
     def prover_state3( self, input): #CHALLENGE phase
         print("state3 => ", input)
         (r, x, c) = Protocol.get(self, ['r', 'x', 'c'])
-        s = r + c * x #We want to duplicate that part since we need two different values of s
+        s = r + c * x
         Protocol.setState(self, 5)
         return {'s':s}
 
@@ -58,7 +58,7 @@ class SchnorrZK(Protocol):
     def verifier_state2(self, input):
         #print("state2 received => ", input)
         # compute challenge c and send to prover
-        c = self.group.random() #We need to create c1 and c2 and send them to the prover
+        c = self.group.random()
         print("state2 generate c :=", c)
         Protocol.store(self, ('c',c))
         Protocol.setState(self, 4)        

### 2018-10-29 performance/charm-schnorr.py
Cleans up main

@@ -88,7 +88,10 @@ class SchnorrZK(Protocol):
 if __name__ == "__main__":
     sp = SchnorrZK(prime192v1)
 
-    if sys.argv[1] == "-v":
+    if len(sys.argv) <= 1:
+        print("Usage: %s [-v or -p]" % sys.argv[0])
+        exit(-1)
+    elif sys.argv[1] == "-v":
         print("Operating as verifier...")
         svr = socket(AF_INET, SOCK_STREAM)
         svr.bind((HOST, PORT))
@@ -96,16 +99,12 @@ if __name__ == "__main__":
         svr_sock, addr = svr.accept()
         print("Connected by ", addr)
         _name, _type, _sock = "verifier", VERIFIER, svr_sock
-#       sp.setup( {'name':"verifier", 'type':_type, 'socket':svr_sock} )
     elif sys.argv[1] == "-p":
         print("Operating as prover...")
         clt = socket(AF_INET, SOCK_STREAM)
         clt.connect((HOST, PORT))
         clt.settimeout(15)
         _name, _type, _sock = "prover", PROVER, clt
-    else:
-        print("Usage: %s [-v or -p]" % sys.argv[0])
-        exit(-1)
     sp.setup( {'name':_name, 'type':_type, 'socket':_sock} )
     # run as a thread...
     sp.execute(_type)

### 2018-10-29 paper/ZKPK.tex

@@
 \begin{equation}\label{PKexample}
-  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma]
+  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
 \end{equation}
 which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
-Greek letters are known only to the prover and use for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.
+Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.
 

### 2018-10-29 paper/conclusions.tex

--- 2018-08-30 paper/conclusions.tex
@@
 others can recognize them too.
-
 Finally, most of the current methods are estimates, with quite some error margins. 

### 2018-10-29 paper/protocol.tex
Changes font size for figures to \small

@@
   \centering
-  %\footnotesize
+  \small
   \includegraphics{proofshare.tikz}
@@
   \centering
-  %\footnotesize
+  \small
   \begin{minipage}{\linewidth}
@@
 
-\emph{Participation: \(\pi\gets
+\emph{Participation: \(\psh\gets
     \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
@@
   \mleftright
-  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    \pid = g_T^{1/(k_P+\cid)} \right\}.
+  \PPK\left\{(k, r, r', \cid, r_\cid) : \right. \\
+    v^{r'} = v_x v_{xy}^{k_P} v_{xy}^{\prime r} \land \pid = g_T^{1/(k_P+\cid)} 
+    \land \\
+    \left. c = g^\cid Z^{r_\cid}
+  \right\}.
 \end{multline*}
@@
 \end{align*}
-If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
+If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
+  = g_T^{1/(k_W+\pid)}\) (as above).
 Following this, the witness returns \((\wid, t_s', l)\) to the protester.
-As a consequence, both the protester and the witness have the tuple \(\pi = 
-  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
-protester (\cref{fig:ProofFig}).
+As a consequence, both the protester and the witness have the tuple \(\psh = 
+  (\pid, \wid, t_s, t_s', l)\), which forms a proof share for the protester 
+(\cref{fig:ProofFig}).
 

### 2018-10-29 paper/distance-bounding.tex

--- 2018-08-30 paper/distance-bounding.tex
@@
   \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using a far-away honest prover.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
   \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
-%Seb: the two following properties should be defined more precisely
-  \item \Acf{DBDH}: similar to \ac{DBDF} but using the presence of an honest prover close to the verifier.
-  \item \Acf{DBIF}: the adversary plays against a simplified version of the protocol without any distance estimation. \sonja{contrast with impersonating verifier}
+  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
+    uses an unsuspecting honest prover close to the verifier to pass as being 
+    close.
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+There are two lines of attempts at formalizing the above properties: one by 
+\citet{DB-BMV} and another by \citet{DB-DFKO}.
 
@@
 This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
+More specifically, we must combine such \iac{DB} with anonymous credentials 
+(which we do in \cref{DB-anon-cred}).
 The choice of the anonymous credential system will affect the properties we 

### 2018-10-29 paper/privacy-properties.tex

@@
 This is, in fact, is a slight increase in privacy over ordinary protests.
-
-\daniel{I suggest ending here to continue in \cref{adversary-model}. I've now 
-  added P1 and P2.}
-
-\sonja{discussion about applicable properties here, more sources and 
-  alternative properties}
-\sonja{new}
-Difference to e-voting:
-physical presence means support for a cause if there is one protest.
-If there is a counterprotest, physical presence with that group means support for the counterprotest.
-In our system, it gets more ambiguous as the participants are counted if all of the following is true
-\begin{enumerate*}
-\item they participate in the protocol,
-\item they use the protest identifier (cause) for which the count is done,
-\item they meet the eligibility criteria, and
-\item they receive enough proof shares,
-\item that are uploaded to the ledger.
-\end{enumerate*}
-Thus one could participate in a protest and be counted even when physically 
-present at a counter-protest if the two protests are co-located and the 
-participant chooses the corresponding cause/identifier of the original protest.
-
-Given that all conditions for being counted in a protest are met, individual 
-verifiability implies a receipt \daniel{no, I know my proof is included in 
-  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
-  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
-  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
-  hence receipt-freeness} because being counted implies support for a cause. 
-This also means that besides physical force, coercion can happen by forcing the 
-participate to show a receipt. \daniel{The only receipt we have is the private 
-  key of the protester, with that key the adversary can compute \(\pid = 
-    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
-We thus have to decide between individual verifiability and the privacy 
-properties for e-voting or define privacy properties suitable for the scenario. 
-The ultimate privacy requirement is thus stronger here: in contrast to voting, 
-where it is the content of the vote itself that needs to be unlinkable to the 
-voter, here the fact of having cast a vote at all needs to be unlinkable.
-
-The privacy properties we need in this context are the following:
-\begin{description}
-  \item[Involuntary participant unlinkability:] \daniel{the name has a 
-      double-negative ring to me} unless the participant discloses the receipt 
-    (by revealing her identity), there is no link between the protest data on 
-    the ledger and the identity of the participant.
-
-  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
-      too of course} unless the witness discloses the receipt (by revealing her 
-    identity), there is no link between the protest data on the ledger and the 
-    identity of the witness.
-\end{description}
-\sonja{old}
-In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
-As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
-Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
-Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
-
-As a consequence, this leaves us with with what would correspond to vote privacy.
-In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
-Hence, we can summarize the needed privacy properties as follows:
-\begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
-\end{requirements}
-
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.

### 2018-10-29 paper/protest-model.tex

@@
 % proofs
-\sonja{what is the subscript i and do we need to have it here?}
 \begin{definition}[Participation proof]%
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst = \{ (\cid, t_i, l_i) \}_i\) is the set
+  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
+  participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
+  set
   \begin{multline}
@@
   \end{multline}
-  of all proof shares with the same protester and protest identifiers, witnessing time interval \(t\) and location \(l\) within those of the protest.
+  of all proof shares with the same protester and protest identifiers, time 
+  interval \(t\) and location \(l\) within those of the protest (\ie any 
+  subprotest).
   We denote by \(\prfs\) the set of all proofs.

### 2018-10-29 paper/protocol.tex
Fixes some typographical mistakes

--- 2018-08-30 paper/protocol.tex
@@
 \end{align*}
-Afterwards, they run the following \ac{PPK} with the protester as the prover and the witness as the verifier:
+Afterwards, they run the following \ac{PPK} with the protester as the prover 
+and the witness as the verifier:
 \begin{multline*}
@@
 \end{align*}
-If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
+If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
+  = g_T^{1/(k_W+\pid)}\) (as above).
 Following this, the witness returns \((\wid, t_s', l)\) to the protester.
-As a consequence, both the protester and the witness have the tuple \(\pi = 
+As a consequence, both the protester and the witness have the tuple \(\psh = 
   (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
@@
 The remaining operations are not time critical.
-The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the correctness of \(\pid\).
+The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the 
+correctness of \(\pid\).
 More specifically,

### 2018-10-31 paper/DB-anon-cred.tex
Tamarin description in V-C + Tamarin code in appendix A

@@
 
+\subsection{Formal Verification}
+
+We wanted to formally verify the protocol security properties.
+We used the Tamarin prover~\cite{meier2013tamarin}.
+Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
+
+The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}.
+It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
+
+Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
+We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
+
 \sonja{\subsection{Formal Verification} 

### 2018-10-31 paper/appendix.tex
Tamarin description in V-C + Tamarin code in appendix A

\appendix

\subsection{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
\label{apdx:tamarin-spec}

\begin{lstlisting}

/* Implementation of the DB protocol */
/* Demonstrating the DB-secure property */

theory crocusclean

begin

functions: adec/2, aenc/2, pk/1

equations: adec(aenc(message, secretkey), 
           pk(secretkey)) = message

builtins: signing

// -------- Tag Initialization --------- //

rule Register_Keypair:
[ Fr(~key) ]
--[ Once($A), Prelim()]->
[ !Pk($A, pk(~key)), !Ltk($A, ~key), 
  Out( pk(~key) ), !Agent($A)
  ]

rule Corrupt_Agent:
[ !Ltk($A, ltk) ]
--[ Corrupt($A), Prelim() ]->
[ Out(ltk), !CorruptAgent($A) ]

rule Corrupt_Fast:
[ !CorruptAgent($A), In(msg) ]
--[ CAction($A), Action($A) ]->
[ FastMsg(msg) ]

// ------- Protocol Rules ---- //

//1. Prover chose r, compute and send R
//2. Verifier chooses two nonces c_0 and c_1,
//   and sends them to Prover
//3. Verifier chooses b = 0 or 1, 
//   sends to Prover
//4. Prover receives + encodes both c_i 
//   with x and sign them with r
//5. Prover receives b,
//   sends back corresponding c
//6. Verifier verifies the signature 
//   and decodes the messsage, 
//   checks it's the correct c

// 1. Prover chose r, compute and send R

rule Prover_1:
[ !Agent($Prover) 
, Fr(~r)
]
--[ ProverStart($Prover)
, Action($Prover)
]->
[ ProverSess($Prover, ~r) 
, Out( pk(~r) )
]

//2. Verifier chooses two nonces c_0 and c_1 
//   and sends them to Prover

rule Verifier_1:
[ In( R ) 
, Fr(~challenge0) , Fr(~challenge1)
]
--[ VerifierCommit( ~challenge0, ~challenge1 ) 
, PreFastPhase( <~challenge0, ~challenge1> )
]->
[ VerifierSess(R, ~challenge0, ~challenge1) 
, Out( <~challenge0, ~challenge1> )
]

//3. Verifier chooses b = c0 or c1, 
//   and sends it to Prover

rule Verifier_2:
[ VerifierSess(R, c0, c1) 
, Fr(~b) 
]
--[ Choose(c0, c1, ~b)
, VerifierSelect(~b) 
, StartFastPhase(c0, c1) 
]->
[ VerifierStartFast(R, c0, c1, ~b)
, FastMsg( ~b ), Out( ~b ) 
]

//4. Prover receives and stores both c_i

rule Prover_2:
[ ProverSess($Prover, r) 
, In( <c0, c1> ) 
]
--[ ProverStore(c0, c1) 
, ReadyFastPhase( c0, c1 ) 
, Action($Prover)
]->
[ ProverStartFast( $Prover, r, c0, c1 ) 
]

//5. Prover receives b and sends it back
//   encoded with x and signed with r

rule Prover_3:
let response = aenc{b, sign(b,x)}r
in
[ ProverStartFast( $Prover, r, c0, c1 ) 
, FastMsg( b ) 
, !Ltk( $Prover, x ) 
]
--[ Choose(c0,c1,b) 
, ProverReply($Prover, c0, c1, b)
, ReplyFastPhase(c0, c1, b)
, Action($Prover)
]->
[ FastMsg( response ), Out( response ) 
]

//6. Verifier verifies the signature and 
//   decodes the messsage,
//   checks it's the correct c

rule Verifier_3:
let clear_text = adec( response, R )
authentication = verify( 
                   snd(clear_text),
                   fst(clear_text),
                   X
                 )
proof = fst(clear_text)
in
[ VerifierStartFast(R, c0, c1, b) 
, FastMsg( response )
, !Pk( $Prover, X )
]
--[ Eq(authentication, true), Eq(proof, b)
, VerifierComplete($Prover, R, c0, c1, b) 
, EndFastPhase(c0,c1,b)  
]->
[]

// ----- Axioms ------- //

restriction at_most_once:
"
All A #t1 #t2. Once(A)@t1 & Once(A)@t2 ==>
(
#t1 = #t2
)
"

restriction equals:
"
All a b #t1. Eq(a,b)@t1 ==>
(
a = b
)
"
// ----- Sanity Check Lemmas ----- //

lemma verif1_exists:
exists-trace
"
Ex c0 c1 #t. (
VerifierCommit( c0, c1 )@t )
"

lemma prover2_exists:
exists-trace
"
Ex Prover c0 c1 b #t. (
ProverReply( Prover, c0, c1, b )  @t )
"

lemma startfast_exists:
exists-trace
"
Ex c0 c1   #t. (
StartFastPhase(c0, c1)@t
) &
not(Ex A #tc. Corrupt(A)@tc)
"

lemma endfast_exists:
exists-trace
"
Ex c0 c1 b  #t. (
EndFastPhase(c0, c1, b)@t
) &
not(Ex A #tc. Corrupt(A)@tc)
"

lemma end_exists:
exists-trace
"
Ex P R c0 c1 b  #t. (
VerifierComplete(P, R, c0, c1, b)@t
) &
not(Ex A #tc. Corrupt(A)@tc)
"

// ----- Security Lemmas ----- //

lemma dbsec:
// Whenever the verifier is complete EITHER:
//  1) There exists t1, t2 and t3 such that
//          The fast phase was between t1 and t3
//          and prover did smthg btwn t1 and t3
//          and verifier completed at/after the
//          end of the fast phase
//OR
//  2) There exist times t5, t6 and t7 such that
//        The fast phase was between t5 and t7
//        and the prover P is dishonest
//        and some dishonest agent did smthg 
//        during the fast phase
//        and the verifier completed at/after the
//        end of the fast phase 
"
All P R c0 c1 b  #t. (
VerifierComplete(P, R, c0, c1, b)@t ) ==>                   
(                                                         
Ex #t1 #t2 #t3. StartFastPhase( c0, c1 )@t1 &              
Action(P)@t2 &                              
EndFastPhase( c0, c1, b )@t3 &            
(#t1 < #t2) &                               
(#t2 < #t3) &                               
( (#t3 < #t ) | (#t3 = #t) )
)|
(              
Ex CAgent #t4 #t5 #t6 #t7.
StartFastPhase( c0, c1 )@t5 &    
EndFastPhase( c0, c1, b )@t7 & 
Corrupt(P)@t4 &             
CAction(CAgent)@t6 &             
(#t5 < #t6)&                     
(#t6 < #t7)&                     
( (#t7 < #t) | (#t7 = #t) )      
) 
"

end
\end{lstlisting}

### 2018-10-31 paper/DB-anon-cred.tex
added a comment command for simon (\simon) in orange, tested it in verification subsection.

@@
 We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
-
-\sonja{\subsection{Formal Verification} 
- verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
-assumed equivalence with Fiat-Shamir model. Not straightforward to
-implement Schnorr in Tamarin due to a lack of expressiveness for
-arithmetic needed to complement Diffie-Hellman. If not done now, left
-for future work. }
+\simon{test by sonja}
+%\sonja{\subsection{Formal Verification} 
+%  verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
+% assumed equivalence with Fiat-Shamir model. Not straightforward to
+% implement Schnorr in Tamarin due to a lack of expressiveness for
+% arithmetic needed to complement Diffie-Hellman. If not done now, left
+% for future work. }

### 2018-10-31 paper/DB-anon-cred.tex
Fixes typo

--- 2018-10-31 paper/DB-anon-cred.tex
@@
 
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}.
+In the original \ac{DB} paper by \citet{DistanceBounding}, one of the 
+distance-bounding protocols is based on the Schnorr identification 
+scheme~\cite{Schnorr}.
 However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.

### 2018-10-31 paper/intro.tex

@@
 More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials.
-\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
-%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.
-}
-\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
-and thus we are, to the best of our knowledge, the first to provide \emph{general} \ac{DB} anonymous credentials.
+The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
+%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
+%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
+%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
+and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
 \emph{Outline.} 

### 2018-10-31 paper/system-model.tex

@@
 
-We will now describe our system and adversary models.
-We first present an abstraction of a protest and how to count the participation 
-(\cref{protest-model}) and the desired verifiabiltiy properties 
-(\cref{verifiability-properties}).
-Next, we present the communication and adversary model (\cref{adversary-model}) 
-together with the desired privacy properties (\cref{privacy-properties}).
+To set the stage, we will now describe our system model including assumptions
+(\cref{assumptions}) and present an abstraction of a protest and how to
+count the participation (\cref{protest-model}). We then formulate the desired verifiability
+(\cref{verifiability-properties}) and privacy properties
+(\cref{privacy-properties}) and adversary model (\cref{adversary-model}).
+
+\subsection{System model and physical assumptions}
+\label{assumptions}
+
+Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf.
+Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
+For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
+This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}.
+
+In practical terms, participants witness each other's participation
+using their smartphones (or similar devices) running the protocol
+described in \cref{Protocol} and uploading their testimony (\ie, proof
+shares) to a ledger (such as a blockchain) after the protest. 
+During the protest, the devices might be limited by their batteries in
+terms of the computations they can perform and only have local connectivity to each other.
+No connection to any global network such as the Internet is
+necessary during this time.  
+Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie, Internet connections) and are not computationally limited by any battery.
+\sonja{another place to put reasons? Or if here, then for all
+  assumptions. ``We need global connectivity before to read the head from the blockchain.
+We need global connectivity after to upload the proof shares to the blockchain.''}
 
@@
 \include*{verifiability-properties}
-\include*{adversary-model}
 \include*{privacy-properties}
+\subsection{Adversary model}
+\label{adversary-model}

### 2018-10-31 paper/privacy-properties.tex
temporariliy restored privacy property text previously removed

--- 2018-08-31 paper/privacy-properties.tex
@@
 
-We can thus summarize the desired privacy properties as follows:
-\begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
-  identities must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
-  unlinkable between protests and witnesses' proofs must be unlinkable between 
-  protesters.
-\end{requirements}
-
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.
-
-\daniel{I suggest ending here to continue in \cref{adversary-model}. I've now 
-  added P1 and P2.}
-
-\sonja{discussion about applicable properties here, more sources and 
-  alternative properties}
 \sonja{new}
@@
 In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
-Hence, we can summarize the needed privacy properties as follows:
+
+We can thus summarize the desired privacy properties as follows:
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
+\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
+  identities must be unlinkable to their proofs.
+\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
+  unlinkable between protests and witnesses' proofs must be unlinkable between 
+  protesters.
 \end{requirements}

### 2018-10-31 paper/intro.tex
intro framing from related work comment

@@
 Next, in \cref{related-work}, we discuss related work in terms of these 
-properties.
+properties. \sonja{add and rephrase: 
+In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.
+}
 In \cref{building-blocks}, we give the relevant background on the building 

### 2018-10-31 paper/privacy-properties.tex
split privacy requirement p2 in two

@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
+\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: participants' real (long-term) 
   identities must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
-  unlinkable between protests and witnesses' proofs must be unlinkable between 
+\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' proofs must be 
+  unlinkable between protests 
+\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' proofs must be unlinkable between 
   protesters.

### 2018-10-31 paper/privacy-properties.tex
first attempt at formalizing the privacy properties

--- 2018-10-31 paper/privacy-properties.tex
@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
-  identities must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
-  unlinkable between protests and witnesses' proofs must be unlinkable between 
-  protesters.
+\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
+  participant's real (long-term) 
+  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
+\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
+  participation proofs $\prf_{\pid, \prtst}$ must be 
+  unlinkable between protests ($\cid, \cid'$)
+\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
+  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
+  protesters. ($\pid, \pid'$)
 \end{requirements}
 
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.
+\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+This is, in fact, is a slight increase in privacy over ordinary protests.}

### 2018-10-31 paper/privacy-properties.tex
now it compiles; added framing for pseudonym reuse

@@
 In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
+Moreover, any temporary identifiers such as pseudonyms may only be
+reused when strictly necessary for the fulfillment of verifiability
+properties listed in \label{verifiability-properties} to prevent
+inference on long-term identities by repeated samples and side information.
 
@@
   participant's real (long-term) 
-  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
+  identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
 \item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
-  participation proofs $\prf_{\pid, \prtst}$ must be 
-  unlinkable between protests ($\cid, \cid'$)
+  participation proofs \(\prf_{\pid, \prtst}\) must be 
+  unlinkable between protests (\(\cid, \cid' \))
 \item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
-  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
-  protesters. ($\pid, \pid'$)
+  participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) 
+must be unlinkable between 
+  protesters. (\(\pid, \pid' \))
 \end{requirements}

### 2018-10-31 paper/privacy-properties.tex
added caveat about threshold, edited blockchain cost in discussion

@@
 her will.
-Receipt freeness, while desirable, is not \emph{always} desirable.
-For instance, the location proof might be useful to prove presence to a third 
-party, \eg for strengthening the authenticity of witness information.
+Receipt freeness, while desirable at first glance, is not desirable
+here as, in contrast to voting, receipt freeness for \emph{how} the
+voter voted (\ie the cause of the protest) implies receipt freeness
+for \emph{that} the voter voted (\ie the protester was there) which
+conflicts with verifiability.  
+%For instance, the location proof might be useful to prove presence to a third 
+%party, \eg for strengthening the authenticity of witness information.
 
@@
 
-For the witness, we want unlinkability between a witness's identity \(W\) and a 
+\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
 location \(l\) against an adversary who is not present in the location.
@@
 Thus we will only try to prevent individuals who are not present to learn of 
-this presence.
+this presence.}
 
-\sonja{new}
+\sonja{start of older thoughts}
 Difference to e-voting:
@@
 \end{description}
-\sonja{old}
+
 In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
@@
 In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
+\sonja{end older thoughts}
 Moreover, any temporary identifiers such as pseudonyms may only be

### 2018-10-31 paper/adversary-model.tex
Removes adversary goal from def (now in P1, P2)
moved system model and physical assumptions to system model section. Moved discussion part of assumptions on MANET to limitations. Moved adversary models (the one with many different types) to security analysis as they already contain analysis.
proofread of the paper

@@
-\subsection{System, communication and adversary model}%
-\label{adversary-model}
+\subsection{Adversary models}%
+\label{adversary-model-different-levels}
 
-We provide one system model with two possible adversaries: one who tries to 
-link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
-which tries to link a protester's or a witness's real identity (\(P\) 
-respectively \(W\)) to a location (\(l\)).
+We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
+that aims at linking a protester's or a witness's real identity (\(P\), respectively \(W\)), to a location (\(l\)).
 We also define varying strengths of each adversary.
@@
 
-There are three players: the protest participant (with identity) \(P\), a 
-witness (with identity) \(W\) and the storage \(S\).
+There are three players: the protest participant (with identity) \(P\), a witness (with identity) \(W\) and the storage \(S\).
 The adversary \(A\) controls \(W\) and \(S\).
@@
   The protester \(P\) and the witness \(W\) communicate.
-  Each learn only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
+  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
   \(t_{P,W}\)\footnote{%
@@
   }.
-  The protester \(P\) communicates with \(S\), where \(S\) only learns 
+  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
   \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
@@
   do, but can additionally correlate what he learns from \(W\) and \(S\).
-  The adversary wins if he can link \(\cid\) and \(P\).
 \end{definition}
@@
 
-We find \cref{base-identity-cause-adversary} suitable when the protester and 
-witness both move in a crowd and there is no way for the witness to decide 
-exactly with whom he or she communicates with.
-However, in some situations this might not be the case, \eg the crowd is not 
-dense.
+We find \cref{base-identity-cause-adversary} suitable when the protester and witness both move in a crowd and there is no way for the witness to decide exactly with whom he or she communicates with.
+However, in some situations this might not be the case, \eg the crowd is not dense.
 In these situations the witness will likely see the face of the protester.
@@
 
-\begin{definition}[Stonger identity--cause adversary]%
+\begin{definition}[Stronger identity--cause adversary]%
   \label{stronger-identity-cause-adversary}
@@
 
-One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
-communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
-However, given a strong enough adversary, such anonymous communication might 
-not be possible.
+One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
+However, given a strong enough adversary, such anonymous communication might not be possible.
 We capture such a strong adversary in the following definition.
@@
   \label{strongest-identity-cause-adversary}
-  Everything is the same as in \cref{stronger-identity-cause-adversary}, except 
-  that now \(S\) also learns \(P\)'s identity.
+  Everything is the same as in \cref{stronger-identity-cause-adversary}, except that now \(S\) also learns \(P\)'s identity.
 \end{definition}
@@
 
-The players are still the same, but now the adversary controls other players: 
-in particular, the adversary controls only the storage \(S\).
+The players are still the same, but now the adversary controls other players.
+In particular, the adversary controls the storage \(S\).
 
@@
     \item[The witness case:]
-      The witness later communicates with \(S\), where \(S\) only learns 
+      The witness later communicates with \(S\), in which \(S\) only learns 
       \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
@@
     \item[The protester case:]
-      The protester later communicates with \(S\), where \(S\) only learns 
+      The protester later communicates with \(S\), in which \(S\) only learns 
       \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 

### 2018-10-31 paper/privacy-properties.tex
proofread of the paper

--- 2018-10-31 paper/privacy-properties.tex
@@
 
-In addition to the verification requirements, we also need to define the 
-privacy properties.
+In addition to the verification requirements, we also need to define the privacy properties.
 In voting protocols, there are mainly three levels of 
@@
   \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can 
-    be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
-    the vote was cast in any particular way.
+  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove that his vote was cast in any particular way.
 \end{description}
@@
 Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against 
-her will.
-Receipt freeness, while desirable, is not \emph{always} desirable.
-For instance, the location proof might be useful to prove presence to a third 
-party, \eg for strengthening the authenticity of witness information.
+For instance, someone could simply physically bring Alice to a protest against her will.
+Receipt freeness is not \emph{always} desirable.
+For instance, the participation proof might be useful to prove presence to a third party, \eg for strengthening the authenticity of witness information.
+%Seb: the above sentence seems to contradict the property of coercion-resistance
 
 Thus privacy remains.
-For the protester we want unlinkability between a protester's real identity 
-\(P\) and the cause identifier \(\cid\) against the adversary.
-Given a participation proof, Grace will not be able to tell if it belongs to 
-Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not 
-be able to link another proof (\eg, from a different protest) as a consequence.
+For the protester we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
+Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice's through some auxiliary knowledge, she should not be able to link another proof (\eg, from a different protest) as a consequence.
 
-For the witness, we want unlinkability between a witness's identity \(W\) and a 
-location \(l\) against an adversary who is not present in the location.
-Due to the limitations of physical space, two individuals present in the same 
-location will inevitably learn of each other's presence.
-Thus we will only try to prevent individuals who are not present to learn of 
-this presence.
+For the witness, we want unlinkability between a witness's identity \(W\) and a location \(l\) against an adversary who is not present in the location.
+Due to the limitations of physical space, two individuals present in the same location will inevitably learn of each other's presence.
+Thus, we will only try to prevent individuals who are not present on the scene to learn this information.
 
 \sonja{new}
-Difference to e-voting:
-physical presence means support for a cause if there is one protest.
-If there is a counterprotest, physical presence with that group means support for the counterprotest.
+To contrast the difference between our context and e-voting: physical presence means support for a cause if there is only one protest. 
+In case of a counterprotest, physical presence with that group means support for the counterprotest. 
 In our system, it gets more ambiguous as the participants are counted if all of the following is true
@@
 \item they participate in the protocol,
-\item they use the protest identifier (cause) for which the count is done,
+\item they use the protest identifier (\ie cause) for which the count is done,
 \item they meet the eligibility criteria, and
@@
 \end{enumerate*}
-Thus one could participate in a protest and be counted even when physically 
-present at a counter-protest if the two protests are co-located and the 
-participant chooses the corresponding cause/identifier of the original protest.
+To summarize, one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.
 
-Given that all conditions for being counted in a protest are met, individual 
-verifiability implies a receipt \daniel{no, I know my proof is included in 
- block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
- sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
- to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
- hence receipt-freeness} because being counted implies support for a cause. 
-This also means that besides physical force, coercion can happen by forcing the 
-participate to show a receipt. \daniel{The only receipt we have is the private 
- key of the protester, with that key the adversary can compute \(\pid = 
-   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
-We thus have to decide between individual verifiability and the privacy 
-properties for e-voting or define privacy properties suitable for the scenario. 
-The ultimate privacy requirement is thus stronger here: in contrast to voting, 
-where it is the content of the vote itself that needs to be unlinkable to the 
-voter, here the fact of having cast a vote at all needs to be unlinkable.
+%Seb: I have put all this part in comment to (1) save on space and (2) also because there is a paper at CCS 2018 that actually shows that individual verifiability is needed to have privacy for e-voting (I agree that it does not mean that it is necessarily the case in our setting)
+%Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt \daniel{no, I know my proof is included in 
+% block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
+% sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
+% to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
+% hence receipt-freeness} because being counted implies support for a cause. 
+%This also means that besides physical force, coercion can happen by forcing the 
+%participate to show a receipt. \daniel{The only receipt we have is the private 
+% key of the protester, with that key the adversary can compute \(\pid = 
+%   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
+%We thus have to decide between individual verifiability and the privacy 
+%properties for e-voting or define privacy properties suitable for the scenario. 
+%Seb: below I would use the term unobservability, rather than unlinkability
+%The ultimate privacy requirement is thus stronger here: in contrast to voting, in which it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.
 
@@
 \begin{description}
+%Seb: while not use the term anonymity instead of unlinkability?
 \item[Involuntary participant unlinkability:] \daniel{the name has a 
@@
    the ledger and the identity of the participant.
-
+%Seb: same comment as above
  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
@@
 \sonja{old}
-In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
+In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to her participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
 As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
@@
 
+%Seb: maybe this sentence should be put before the definition of the properties
 As a consequence, this leaves us with with what would correspond to vote privacy.
@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
-  participant's real (long-term) 
-  identity (\(P\)) must be unlinkable to their participation proofs $\prf_{\pid, \prtst}$
-\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
-  participation proofs $\prf_{\pid, \prtst}$ must be 
-  unlinkable between protests ($\cid, \cid'$)
-\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
-  participation proof shares $\(\psh = (\cid, t, l, \pid, \wid)\)$ must be unlinkable between 
-  protesters. ($\pid, \pid'$)
+\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
+  identities must be unlinkable to their proofs.
+\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
+  unlinkable between protests and witnesses' proofs must be unlinkable between 
+  protesters.
 \end{requirements}
 
-\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.}
+As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+This is, in fact, a slight increase in privacy over ordinary protests.

### 2018-10-31 paper/system-model.tex
proofread of the paper

@@
 
-To set the stage, we will now describe our system model including assumptions
-(\cref{assumptions}) and present an abstraction of a protest and how to
-count the participation (\cref{protest-model}). We then formulate the desired verifiability
-(\cref{verifiability-properties}) and privacy properties
-(\cref{privacy-properties}) and adversary model (\cref{adversary-model}).
+To set the stage, we will now describe our system model including assumptions (\cref{assumptions}) and present an abstraction of a protest and how to
+count the participation (\cref{protest-model}). 
+Afterwards, we formulate the desired verifiability (\cref{verifiability-properties}) and privacy properties
+(\cref{privacy-properties}) as well as the adversary model (\cref{adversary-model}).
 
@@
 For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
-This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}.
+This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.
 
-In practical terms, participants witness each other's participation
-using their smartphones (or similar devices) running the protocol
-described in \cref{Protocol} and uploading their testimony (\ie, proof
-shares) to a ledger (such as a blockchain) after the protest. 
-During the protest, the devices might be limited by their batteries in
-terms of the computations they can perform and only have local connectivity to each other.
-No connection to any global network such as the Internet is
-necessary during this time.  
-Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie, Internet connections) and are not computationally limited by any battery.
-\sonja{another place to put reasons? Or if here, then for all
-  assumptions. ``We need global connectivity before to read the head from the blockchain.
-We need global connectivity after to upload the proof shares to the blockchain.''}
+In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest.
+During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
+No connection to any global network such as the Internet is necessary at that time.  
+Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
+This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.
+%\sonja{another place to put reasons? Or if here, then for all
+%  assumptions. ``We need global connectivity before to read the head from the blockchain.
+%We need global connectivity after to upload the proof shares to the blockchain.''}
 

### 2018-10-31 paper/system-model.tex
added simple adversary model

--- 2018-10-31 paper/system-model.tex
@@
 \label{adversary-model}
+
+We consider two types of adversaries: \begin{enumerate*} \item an honest-but-curious adversary
+of up to national scale representing a government that can observe any
+messages sent, and \item a malicious adversary that can control a
+minority of 
+equipment such as participants' or witnesses' smartphones or servers
+used for the ledger such as miners for a blockchain. \end{enumerate*}

### 2018-10-31 paper/privacy-properties.tex

@@
 %Seb: the above sentence seems to contradict the property of coercion-resistance
+For instance, someone could simply physically bring Alice to a protest against her will.
+Receipt freeness, while appealing at first glance, is not desirable here.
+Indeed in in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{the fact that} the voter voted (\ie the protester was there), thus conflicting with verifiability.
 
@@
 
-\sonja{new}
 To contrast the difference between our context and e-voting: physical presence means support for a cause if there is only one protest. 
@@
 
-The privacy properties we need in this context are the following:
-\begin{description}
-%Seb: while not use the term anonymity instead of unlinkability?
-\item[Involuntary participant unlinkability:] \daniel{the name has a 
-     double-negative ring to me} unless the participant discloses the receipt 
-   (by revealing her identity), there is no link between the protest data on 
-   the ledger and the identity of the participant.
-%Seb: same comment as above
- \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
-     too of course} unless the witness discloses the receipt (by revealing her 
-   identity), there is no link between the protest data on the ledger and the 
-   identity of the witness.
-\end{description}
-\sonja{old}
+%The privacy properties we need in this context are the following:
+%\begin{description}
+%%Seb: while not use the term anonymity instead of unlinkability?
+%\item[Involuntary participant unlinkability:] \daniel{the name has a 
+%     double-negative ring to me} unless the participant discloses the receipt 
+%   (by revealing her identity), there is no link between the protest data on 
+%   the ledger and the identity of the participant.
+%%Seb: same comment as above
+% \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
+%     too of course} unless the witness discloses the receipt (by revealing her 
+%   identity), there is no link between the protest data on the ledger and the 
+%   identity of the witness.
+%\end{description}
+%\sonja{old}
 In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to her participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
@@
 In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
+%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
+%location \(l\) against an adversary who is not present in the location.
+%Due to the limitations of physical space, two individuals present in the same 
+%location will inevitably learn of each other's presence.
+%Thus we will only try to prevent individuals who are not present to learn of 
+%this presence.}
+Moreover, any temporary identifiers such as pseudonyms may only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.
 
@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants' real (long-term) 
-  identities must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: protesters' proofs must be 
-  unlinkable between protests and witnesses' proofs must be unlinkable between 
-  protesters.
+\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: each
+  participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
+\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be 
+  unlinkable between protests (\(\cid, \cid' \))
+\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) 
+must be unlinkable between 
+  protesters. (\(\pid, \pid' \))
 \end{requirements}
 
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, a slight increase in privacy over ordinary protests.
+%As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+%This is, in fact, a slight increase in privacy over ordinary protests.

### 2018-10-31 paper/protest-model.tex

@@
 }.
-These rallies were all in the same location in the capital and repeated every weekend for the duration of a few weeks.
+These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
 The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
@@
 }.
-Generalizing from these examples, the minimal common part is the cause,%
-\label{CauseIsTheCommonDenominator} while the location (or area) considered 
+Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered 
 varies over time.
@@
 For the rest of the paper, we will refer to the organizer as Alice.
-Assume that the objective of Alice is to count everyone who
-participated at any time and in any of the
-locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
+We assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
   %repetition: %\footnote{Note that the objective does not necessarily
@@
 More specifically, we will use the following definition.
-
 % protest
@@
 Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
-A witness is only allowed to create one proof share per protester to
-avoid the risk of count inflation.
+A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
 Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
-%Seb: the sentence below is not very clear, it should be rephrased to make it clearer
-The participation proof and its proof shares are stored in a set, as
-there should only be unique proof shares.
+The participation proof and its proof shares are stored as a set.
+%, as there should only be unique proof shares.
 
@@
 One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
-%Seb: we should define clearly the different type of witnesses (for instance unique and trusted witnesses)
-Another possibility would be to also have a particular type of witness, called trusted witness, participating in the protest. 
+Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
 For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
-In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses and set \(\theta = 1\) to require at least one proof share issued by a trusted witness.
+In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses.
+Setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.

### 2018-10-31 paper/privacy-properties.tex
restores privacy properties from before conflict resolution

--- 2018-10-31 paper/privacy-properties.tex
@@
 
-\sonja{start of older thoughts}
-Difference to e-voting:
-physical presence means support for a cause if there is one protest.
+% \sonja{start of older thoughts}
+% Difference to e-voting:
+% physical presence means support for a cause if there is one protest.
 If there is a counterprotest, physical presence with that group means support for the counterprotest.
 In our system, it gets more ambiguous as the participants are counted if all of the following is true
-\begin{enumerate*}
-\item they participate in the protocol,
-\item they use the protest identifier (cause) for which the count is done,
-\item they meet the eligibility criteria, and
-\item they receive enough proof shares,
-\item that are uploaded to the ledger.
-\end{enumerate*}
-Thus one could participate in a protest and be counted even when physically 
-present at a counter-protest if the two protests are co-located and the 
-participant chooses the corresponding cause/identifier of the original protest.
+% \begin{enumerate*}
+% \item they participate in the protocol,
+% \item they use the protest identifier (cause) for which the count is done,
+% \item they meet the eligibility criteria, and
+% \item they receive enough proof shares,
+% \item that are uploaded to the ledger.
+% \end{enumerate*}
+% Thus one could participate in a protest and be counted even when physically 
+% present at a counter-protest if the two protests are co-located and the 
+% participant chooses the corresponding cause/identifier of the original protest.
 
-Given that all conditions for being counted in a protest are met, individual 
-verifiability implies a receipt \daniel{no, I know my proof is included in 
- block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
- sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
- to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
- hence receipt-freeness} because being counted implies support for a cause. 
-This also means that besides physical force, coercion can happen by forcing the 
-participate to show a receipt. \daniel{The only receipt we have is the private 
- key of the protester, with that key the adversary can compute \(\pid = 
-   \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
-We thus have to decide between individual verifiability and the privacy 
-properties for e-voting or define privacy properties suitable for the scenario. 
-The ultimate privacy requirement is thus stronger here: in contrast to voting, 
-where it is the content of the vote itself that needs to be unlinkable to the 
-voter, here the fact of having cast a vote at all needs to be unlinkable.
+% Given that all conditions for being counted in a protest are met, individual 
+% verifiability implies a receipt \daniel{no, I know my proof is included in 
+%  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
+%  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
+%  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
+%  hence receipt-freeness} because being counted implies support for a cause. 
+% This also means that besides physical force, coercion can happen by forcing the 
+% participate to show a receipt. \daniel{The only receipt we have is the private 
+%  key of the protester, with that key the adversary can compute \(\pid = 
+%    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
+% We thus have to decide between individual verifiability and the privacy 
+% properties for e-voting or define privacy properties suitable for the scenario. 
+% The ultimate privacy requirement is thus stronger here: in contrast to voting, 
+% where it is the content of the vote itself that needs to be unlinkable to the 
+% voter, here the fact of having cast a vote at all needs to be unlinkable.
 
-The privacy properties we need in this context are the following:
-\begin{description}
- \item[Involuntary participant unlinkability:] \daniel{the name has a 
-     double-negative ring to me} unless the participant discloses the receipt 
-   (by revealing her identity), there is no link between the protest data on 
-   the ledger and the identity of the participant.
+% The privacy properties we need in this context are the following:
+% \begin{description}
+%  \item[Involuntary participant unlinkability:] \daniel{the name has a 
+%      double-negative ring to me} unless the participant discloses the receipt 
+%    (by revealing her identity), there is no link between the protest data on 
+%    the ledger and the identity of the participant.
 
- \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
-     too of course} unless the witness discloses the receipt (by revealing her 
-   identity), there is no link between the protest data on the ledger and the 
-   identity of the witness.
-\end{description}
+%  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
+%      too of course} unless the witness discloses the receipt (by revealing her 
+%    identity), there is no link between the protest data on the ledger and the 
+%    identity of the witness.
+% \end{description}
 
-In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
-As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
-Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
-Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
+% In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
+% As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
+% Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
+% Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
 
-As a consequence, this leaves us with with what would correspond to vote privacy.
-In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-\sonja{end older thoughts}
+% As a consequence, this leaves us with with what would correspond to vote privacy.
+% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
+% \sonja{end older thoughts}
 Moreover, any temporary identifiers such as pseudonyms may only be

### 2018-11-01 paper/analysis-performance.tex
Minor edits in intro (only labels in other files)
update of privacy and performance

@@
 \section{Performance and implementation}
+\label{PerformanceAnalysis}
 
-\subsection{Implementation on smartphones or smart-cards}
-Technological progress has enabled more advanced cryptography on Smart-cards and Smartphones which could be used to implement our solution : Benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in  \SI{153}{\milli\second}.
-However, those benchmarks also demonstrate that SmartCards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them).
-While the limited processing power of many embarked systems has been a challenge, Idemix has been succesfully implemented to prove the posession of credentials on Java Cards by Bichsel et al.
-in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation « suitable for real life transactions »~\cite{IRMA} while maintaining security and privacy for its users.
+Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and
+computational power, and are operating on limited network capacity. 
+Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
+For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}.
+However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
+While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.
 
-\subsection{Threshold of witnesses}
+With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
+The first step is only done once and is fairly costly in terms of ressources. 
+This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
+This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
+%Seb: to do add the reference to the following paper at the end of the sentence:
+%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
+%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
+Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
+This can be reduced to 4 random number generations and one exponentiation using precomputation.
+The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
+%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
+%subscriptions. IEEE Security & Privacy, (1), 1.
 
-Assume that every person has 5000 contacts in their contact 
-book~\cite{DifficultyOfPrivateContactDiscovery}.
-Then it would be reasonable to set the threshold of at least 6000 witnesses.
-According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
-signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
-\SI{2.66}{\giga\hertz} Core 2 processor.
-This yields \(
-  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-  \SI{48}{\second}.
-\) of processing.
+%\paragraph{Threshold of witnesses.}
+%Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+%Then it would be reasonable to set the threshold of at least 6000 witnesses.
+%According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
+%signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
+%\SI{2.66}{\giga\hertz} Core 2 processor.
+%This yields \(
+%  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+%  \SI{48}{\second}.
+%\) of processing.

### 2018-11-01 paper/privacy-properties.tex
update of privacy and performance

@@
 
-In addition to the verification requirements, we also need to define the 
-privacy properties.
-In voting protocols, there are mainly three levels of 
-privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+In addition to the verification requirements, we also need to define the privacy properties.
+In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \begin{description}
@@
   \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
-    the vote was cast in any particular way.
+    his vote was cast in any particular way.
 \end{description}
@@
 Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against 
-her will.
-Receipt freeness, while desirable at first glance, is not desirable
-here as, in contrast to voting, receipt freeness for \emph{how} the
-voter voted (\ie the cause of the protest) implies receipt freeness
-for \emph{that} the voter voted (\ie the protester was there) which
-conflicts with verifiability.  
-%For instance, the location proof might be useful to prove presence to a third 
-%party, \eg for strengthening the authenticity of witness information.
+For instance, someone could simply physically bring Alice to a protest against her will.
+Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.
 
-Thus privacy remains.
-For the protester we want unlinkability between a protester's real identity 
-\(P\) and the cause identifier \(\cid\) against the adversary.
-Given a participation proof, Grace will not be able to tell if it belongs to 
-Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not 
-be able to link another proof (\eg, from a different protest) as a consequence.
+Thus, in our context the crucial property is therefore privacy.
+More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
+Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice's due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).
 
-\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
-location \(l\) against an adversary who is not present in the location.
-Due to the limitations of physical space, two individuals present in the same 
-location will inevitably learn of each other's presence.
-Thus we will only try to prevent individuals who are not present to learn of 
-this presence.}
+%Seb: I have put it in comments to save on space
+%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
+%location \(l\) against an adversary who is not present in the location.
+%Due to the limitations of physical space, two individuals present in the same 
+%location will inevitably learn of each other's presence.
+%Thus we will only try to prevent individuals who are not present to learn of 
+%this presence.}
 
@@
 % \sonja{end older thoughts}
-Moreover, any temporary identifiers such as pseudonyms may only be
-reused when strictly necessary for the fulfillment of verifiability
-properties listed in \label{verifiability-properties} to prevent
-inference on long-term identities by repeated samples and side information.
+Finally, any temporary identifiers such as pseudonyms should only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.
 
@@
 \item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
-  participant's real (long-term) 
-  identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
+  participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
 \item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
-  participation proofs \(\prf_{\pid, \prtst}\) must be 
-  unlinkable between protests (\(\cid, \cid' \))
+  participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
 \item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
-  participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) 
-must be unlinkable between 
+  participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between 
   protesters. (\(\pid, \pid' \))

### 2018-11-01 paper/DB-anon-cred.tex
Minor fixes in DB-anon-cred

@@
 This is the main difference to the original Schnorr protocol: the verifier 
-selects two challenges and the prover \emph{computes} two responses --- but 
-still only \emph{one nonce}, \(\rho\).
+selects two challenges and the prover computes two responses --- but still only 
+\emph{one nonce}, \(\rho\).
 (This is also different from Brands-Chaum, where the prover and verifier 
@@
 \(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
-\Ie \(s_b, b\in\bin\) can be reconstructed from the two shares \(s_b^{(0)}, 
+\Ie \(s_b\) can be reconstructed by adding the two shares \(s_b^{(0)}, 
   s_b^{(1)}\).
@@
 The verifier will request all \(2|q|\) response-bits from one challenge (say 
-\(s_b^{(0)}\concat s_b^{(1)}, b\in \bin\)) and only \(0 < l\leq |q|\) from the 
-other (\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
+\(s_b^{(0)}\concat s_b^{(1)}\)) and only \(0 < l\leq |q|\) from the other 
+(\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
 Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally 
@@
 
+\subsection{Security analysis}
+
 The prover must know the responses for both challenges to successfully pass the 
 \ac{DB} phase.
-The reason for the two challenges but only one random nonce (change from 
-Schnorr) is that knowing the responses to both means learning \(\alpha\) (for
-\ac{DBTF}).
+The reason for the two challenges but only one random nonce is that knowing the 
+responses to both means learning \(\alpha\).
+This allows us to prevent \ac{DBTF}.
 Bundling the authentication into the distance bounding phase (difference from 
-Brands-Chaum) was done for \ac{DBDH},
+Brands-Chaum) prevents \ac{DBDH},
 and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
@@
 Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with 
-secret sharing the verifier learns \(l\) bits of \emph{one share} (provided 
-\(l\) is small enough).
-Thus we have information theoretic security although we reveal these \(l\) 
-bits.
-
-\subsection{Security analysis}
+secret sharing the verifier learns \(l\) bits of \emph{one share}.
+Thus we still have information theoretic security for \(s_{1-b}\) although we 
+reveal the \(l\) bits.
 
@@
 The adversary now has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0, s_1\) by requesting 
-them from the prover.
+First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat 
+  s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
 However, at this point the adversary must wait for the challenge bit 
@@
 receive the correct \(r_i\) --- this relay will be detected.
-The (better) alternative is to guess \(b\) and extract \(s_b\) for this 
-challenge from the prover.
-Guessing \(b\) yields \(1/2\) probability \emph{per round} that the \ac{DBMF} 
-adversary will guess it correctly.
+The alternative is to guess \(b\) and extract \(s_b\) for this challenge from 
+the prover.
+Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will 
+guess it correctly.
 Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
@@
 
-The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}.
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}.
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
+Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
 We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.

### 2018-11-01 paper/DB-anon-cred.tex
minor changes to section V-C + tinkering with references.bib re:compilation issues

--- 2018-10-31 paper/DB-anon-cred.tex
@@
 
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the 
-distance-bounding protocols is based on the Schnorr identification 
-scheme~\cite{Schnorr}.
+In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}. 
 However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
@@
 public-key \ac{DB} protocol which is secure against \ac{DBMF},
-\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
+\ac{DBDF}, \ac{DBDH} and \ac{DBTF}. a
 It is important in our setting that the protocol is a public-key protocol, this 
@@
 We wanted to formally verify the protocol security properties.
-We used the Tamarin prover~\cite{meier2013tamarin}.
+We used the Tamarin prover ~\cite{meier2013tamarin}.
 Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
 
-The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}.
+The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}, with a short discussion of the modelization choices we made.
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
+The Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
 We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
-
-\sonja{\subsection{Formal Verification} 
- verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
-assumed equivalence with Fiat-Shamir model. Not straightforward to
-implement Schnorr in Tamarin due to a lack of expressiveness for
-arithmetic needed to complement Diffie-Hellman. If not done now, left
-for future work. }

### 2018-11-01 paper/intro.tex
rephrased related work phrasing in intro

--- 2018-10-31 paper/intro.tex
@@
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
-More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
-Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with 
-their identity and that any witnessing is also unlinkable.
+More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
+Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
 
 \emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
-\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
+%\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
+%Seb: I am ok with the change done
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
-for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
 More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
@@
 The paper is organized as follows.
-First, in \cref{system-model}, we define and formalize the notion of protest 
-and define the desired verifiability properties.
-We also present our system and adversary model together with desired privacy 
-properties.
-Next, in \cref{related-work}, we discuss related work in terms of these 
-properties.
-In \cref{building-blocks}, we give the relevant background on the building 
-blocks of our solution.
-In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
-protocol, different from that originally proposed by 
-\textcite{DistanceBounding}.
-We provide a proof of its security (all desired \ac{DB} properties) 
-\daniel{Check that this is true before publication.} and formally verify it 
-using Tamarin~\cite{TamarinDB}.
+First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
+We also present our system as well as the adversary model together with desired privacy properties.
+Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO.
+In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
+Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
+We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
+%\daniel{Check that this is true before publication.} 
+and formally verify it using Tamarin~\cite{TamarinDB}.
 This version of the Schnorr protocol can then be used to do general \ac{DB} 
 anonymous credentials.
-In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
-building blocks.
-This is followed by an analysis of its security and privacy 
-(\cref{SecurityAnalysis}).
-Finally, we conclude with a discussion in \cref{Discussion} and future work in 
-\cref{Conclusion}.
-\sonja{add (sub) sections for performance and verification}
+Then \cref{Protocol}, we present \PRIVO, the protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
+%\sonja{add (sub) sections for performance and verification}

### 2018-11-01 paper/protest-model.tex

@@
 }.
-Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered 
-varies over time.
+Generalizing from these examples, the minimal common part is the 
+cause,\label{CauseIsTheCommonDenominator} while the location (or area) 
+considered varies over time.
 
@@
 \begin{definition}[Subprotest, Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
+  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
+    \ZZ_{2^\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
+  the cause of the protest,
   \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
-  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
+  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
 \end{definition}

### 2018-11-01 paper/protocol.tex

@@
 A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
-Afterwards, this identifier is used to create the protest-specific identifier for the protester, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
+Afterwards, this identifier is used to create the protest-specific identifier 
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
 \cref{fig:ProofFig,fig:ProtocolOverview}).
@@
     witness's key \(\sk_W\) and the protester's \(\pid\).
-    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
+    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
+    protester and witness, respectively, and \(l\) is an area.
     All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
@@
 The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
-Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.
+Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
+set the start of the time interval of creation for the proof share.
 
@@
 Afterwards, the \ac{PK} can be designed as follows.
-(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
-times to achieve security.)
+(Remember that this \ac{PK} should be run as the \ac{PPK} in 
+\cref{DB-anon-cred} and repeated multiple times to achieve security.)
 The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
@@
 
-To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
-\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
-  (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
-    (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})\) for each protester \(j\) 
-from the blockchain, verify \(\prf_{\pid_j}^{(i)}\), \(\prf_{\wid_i}\) and that 
-the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime (i)})}{\min(t_e^{(i)}, 
-    t_e^{\prime (i)})}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
+To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
+(see \cref{DefProtest}), a verifier must download all the proof shares \[
+  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
+  t_e^{\prime   (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})
+\] for each protester \(j\) from the ledger, verify \(\prf_{\pid_j}^{(i)}\), 
+\(\prf_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime 
+      (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
+\(l_i\subseteq  l\).
 Any proof share that does not verify correctly will be discarded.
@@
 In the case \emph{without} trusted witnesses, the verifier simply define 
-\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to the 
+\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\) and set \(\theta\) to the 
 desired threshold.
@@
 verifier of which proof shares that he or she has signed, \eg by giving a list 
-of all such proof shares or digitally sign each proof share.
+of all such proof shares or digitally sign each proof share\footnote{%
+  To achieve witness privacy in this situation, one could employ a group or 
+  ring signature scheme for all trusted witnesses.
+  Then one learns that at least one trusted witness must have been there.
+}.
 Then the verifier can define \[
-  \str[\prf_{\pid_i, P}] = \begin{cases}
-    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
+  \str[\prf_{\pid_j, P}] = \begin{cases}
+    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
+      share} \\
     0 & \text{otherwise}

### 2018-11-01 paper/privacy-properties.tex
Comments on statements on receipt freeness

@@
 Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.
+\daniel{%
+  No, that implication is not true, counter example:
+  There is receipt freeness for how a elector voted, but not that they voted.
+  As Simon pointed out, they tick me off, so it's visible that I've voted.
+  But no one will ever know for which party I voted.%
+}
+
+\daniel{%
+  This doesn't conflict with verifiability either.
+  I keep track of the ballot box, as long as that and all ballots inside are 
+  treated properly, I know my ballot is safe and counted.%
+}
+
+\daniel{%
+  In our case:
+  I have a key issued on a smartcard and it's tied to my identity.
+  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
+  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
+    \ACprf[_k][\cid']\).
+  I could've downloaded both from the ledger.
+  But I know which is mine, I can submit it, and as long as the block where it 
+  was included is intact I know my proof-share is included as well --- even if 
+  I forget what it looked like.%
+}
 

### 2018-11-01 paper/system-model.tex
Adds comment on CA and Sybil attacks

@@
 For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
-This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.
+This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which 
+would have a disastrous effect on the crowd-counting estimation\footnote{%
+  Of course, this means that the \ac{CA} can perform a Sybil attack on the 
+  system.
+  So, if the \ac{CA} is controlled by the government, then no counts in favour 
+  of the government can be be trusted.
+}.
 

### 2018-11-01 paper/DB-anon-cred.tex

--- 2018-11-01 paper/DB-anon-cred.tex
@@
 We wanted to formally verify the protocol security properties.
-We used the Tamarin prover~\cite{meier2013tamarin}.
+We used the Tamarin prover ~\cite{meier2013tamarin}.
 Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}.
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modelization choices we made.
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
@@
 We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
-\simon{test by sonja}
-%\sonja{\subsection{Formal Verification} 
-%  verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
-% assumed equivalence with Fiat-Shamir model. Not straightforward to
-% implement Schnorr in Tamarin due to a lack of expressiveness for
-% arithmetic needed to complement Diffie-Hellman. If not done now, left
-% for future work. }

### 2018-11-01 paper/appendix.tex

@@
 \label{apdx:tamarin-spec}
+
+The results provided by Tamarin extends to the protocol being modeled 
+only up to the accuracy of the specification of protocol rules (and equational theory).
+Moreover, Tamarin specifications are not always able to reproduce a protocol precisely.
+Consequently, we provide below the full code of our specification and of the various properties we defined, and briefly explain our choices of modelization.
+
+The key point is that Tamarin only provides symbolic modeling, and as such does not work with actual values.
+The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
+However, in some cases, a user can work around this restriction by providing their own equational theory.
+
+The most significant choices we made include:
+\begin{itemize}
+	\item We represented the responses $s_i$ as the challenges $c_i$ encoded with the nonce $\rho$ and signed with the prover long-term secret key $\alpha$; this is faithful to the actual purpose of those values in the protocol, even though the concrete operations executed do not correspond exactly to an encoding and a signature.
+Indeed, $s_i$ includes $\alpha$ to authenticate the prover (signing), and $\rho$ to mask the actual value of $\alpha$ (encoding).
+	\item We used the chosen challenge $c_b$ directly instead of the flag $b$ to represent the choice of the verifier between the two challenge values; this is equivalent because Tamarin does not work with actual values so the size of those values does not matter, and this helps us for the next point.
+	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
+	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
+	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.
+\end{itemize}
+
+Regarding the first point, Tamarin includes a built-in equational theory modeling the exponentiation rules used in Diffie-Hellman.
+Using that as a basis, it is possible to add a custom theory to represent addition and subtraction, and then use it to more accurately model the construction of the responses $s_i$, but this complexifies the specification a lot and we will not show it here.
 

### 2018-11-06 paper/privacy-properties.tex
Fixes typo

@@
 Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).
+Furthermore, if Grace has managed to link one proof to Alice due to some 
+auxiliary knowledge, she should not be able to link it to another proof (\eg, 
+from a different protest).
 

### 2018-11-09 paper/intro.tex
Adds Douglas' comments for abstract and intro

@@
 
-Historically, there are many examples of protests in which the count estimated by police and that by the organizers differ significantly, sometimes in the order of hundreds of thousands.
+Historically, there are many examples of protests in which the count estimated 
+by police and that of the organizers differ significantly, sometimes in the 
+order of hundreds of thousands.
 Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
@@
 In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
-In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
+In this paper, our main objective is to provide a scheme preventing both Alice 
+and Grace from cheating (\ie their claims should be verifiable).
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
@@
 
-\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+\paragraph*{Contributions}
+
+In this paper, our first main contribution is to propose \PRIVO, a 
+privacy-preserving scheme providing a way to securely estimate crowd count in 
+protests.
 %\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
@@
 and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
-\emph{Outline.} 
+
+\paragraph*{Outline}
+
 The paper is organized as follows.

### 2018-11-09 paper/protest-model.tex
Fixes Douglas' comments for the protest model

@@
   A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
-    \ZZ_{2^\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
+    \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
   the cause of the protest,
-  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
+  \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location 
+  (the topological connectedness is not necessary).
   A \emph{protest} is the set of subprotests sharing the same \(\cid\).
@@
 
+We will use the following notation to filter out a subset of \(\pshs\) with 
+specific \(\cid\)s and \(\pid\)s:
+\begin{multline*}
+  \pshs_{\cid_0, \pid_0} = \\
+  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
+\end{multline*}
+
 A subset of the proof shares forms a participation proof for a protester.
@@
   set
-  \begin{multline}
+  \begin{equation}
     \nonumber
     \prf_{\pid, \prtst} =
-    \left\{ \psh = (\cid, t, l, \pid, \wid)\in \pshs \mid
-      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\}
-  \end{multline}
+    \left\{ \psh \in \pshs_{\cid, \pid} \mid
+      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
+  \end{equation}
   of all proof shares with the same protester and protest identifiers, time 

### 2018-11-09 paper/verifiability-properties.tex
Fixes Douglas' comments in verifiability-properties

@@
 We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
-Indeed, all three situations correspond to cases in which many individuals express their opinion.
+Indeed, all three situations correspond to situations in which many individuals express their opinion.
 These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
@@
 
-We draw inspiration from the three general desirable properties for 
-verifiability, as summarized by 
-\textcite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+We draw inspiration from the three traditionally desired properties for 
+verifiability for voting:
+% XXX find a new ref for voting verifiability properties
 \begin{description}
@@
   \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
+    % Douglas: technically this is Sako-Kilian
   \item[Individual verifiability:] each voter can verify that his vote is included in the result.
+    % Douglas: this is much earlier than Sako-Kilian, in essence Fiat-Shamir.
 \end{description}
 In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that 
-anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
+The eligibility requirement is slightly different as for protests it must 
+include temporal\footnote{%
+  Elections also has some temporal aspects, \eg one cannot vote at any time and 
+  a vote in one election should not be reusable in the next election.
+  However, the temporal relation for a protest is not as strictly defined as 
+  for elections, a protest can start at any time and last for an arbitrary 
+  period of time.
+} and spatial eligibility (\ie each participation proof satisfies some temporal 
+and spatial relation to the protest).
 In essence, the proof must bind the person to the time and location of the protest.
 
-To adapt these properties to the context of protests, we define three 
-verifiability requirements, among which eligibility can be further broken up 
-into four subproperties:
+To adapt these properties to the context of protests, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
 \begin{requirements}[V]

### 2018-11-12 paper/intro.tex
coincoin

@@
 
-Historically, there are many examples of protests in which the count estimated 
-by police and that of the organizers differ significantly, sometimes in the 
-order of hundreds of thousands.
+Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes in the order of hundreds of thousands.
 Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
@@
 However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
-In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times, which in turn increases the error of the estimation.
+In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times ---, which in turn increases the error of the estimation.
 In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
@@
 Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
-In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
-In this paper, our main objective is to provide a scheme preventing both Alice 
-and Grace from cheating (\ie their claims should be verifiable).
+In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
+In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claims should be verifiable).
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
@@
 Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
+%Seb: in the sentence above I am not sure that the word unlinkable will be necessary clear
 
@@
 
-In this paper, our first main contribution is to propose \PRIVO, a 
-privacy-preserving scheme providing a way to securely estimate crowd count in 
-protests.
-%\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
-%Seb: I am ok with the change done
+In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 
@@
 and formally verify it using Tamarin~\cite{TamarinDB}.
-This version of the Schnorr protocol can then be used to do general \ac{DB} 
-anonymous credentials.
-Then \cref{Protocol}, we present \PRIVO, the protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+%Seb: we need to be careful about the above sentence
+This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
+Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
 Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.

### 2018-11-12 paper/privacy-properties.tex
coincoin

@@
   \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can 
-    be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove 
-    his vote was cast in any particular way.
+  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
 \end{description}
@@
 For instance, someone could simply physically bring Alice to a protest against her will.
-Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there) which conflicts with verifiability.
+%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
+Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
 \daniel{%
@@
   In our case:
-  I have a key issued on a smartcard and it's tied to my identity.
+  I have a key issued on a smartcard and it is tied to my identity.
   If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
@@
     \ACprf[_k][\cid']\).
-  I could've downloaded both from the ledger.
+  I could have downloaded both from the ledger.
   But I know which is mine, I can submit it, and as long as the block where it 
@@
 Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (\eg, 
-from a different protest).
+Furthermore, if Grace has managed to link one proof to Alice due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).
 
@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every
-  participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
-\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters'
-  participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
-\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses'
-  participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between 
-  protesters. (\(\pid, \pid' \))
+\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
+\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
+\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between protesters. (\(\pid, \pid' \))
 \end{requirements}
 
-\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.}
+%Seb: ok for me, I have put it in comment
+%\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
+%This is, in fact, is a slight increase in privacy over ordinary protests.}

### 2018-11-12 paper/protest-model.tex
coincoin

@@
 }.
-Generalizing from these examples, the minimal common part is the 
-cause,\label{CauseIsTheCommonDenominator} while the location (or area) 
-considered varies over time.
+Generalizing from these examples, the minimal common part is the cause,\label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.
 
@@
 \begin{definition}[Subprotest, Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
-    \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
-  the cause of the protest,
-  \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location 
-  (the topological connectedness is not necessary).
+  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).
   A \emph{protest} is the set of subprotests sharing the same \(\cid\).
@@
 
-We will use the following notation to filter out a subset of \(\pshs\) with 
-specific \(\cid\)s and \(\pid\)s:
+We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
 \begin{multline*}
@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  A \emph{participation proof} of a protester with pseudonym \(\pid\) who 
-  participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
+  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
   set
@@
   \end{equation}
-  of all proof shares with the same protester and protest identifiers, time 
-  interval \(t\) and location \(l\) within those of the protest (\ie any 
-  subprotest).
+  of all proof shares with the same protester and protest identifiers, time interval \(t\) and location \(l\) within those of the protest (\ie any subprotest).
   We denote by \(\prfs\) the set of all proofs.

### 2018-11-12 paper/timestamp.tex
coincoin

@@
 
-We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), 
-\(\TSstamp\) and \(\TStime\) requests such that
+We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
 \begin{itemize}
   \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
-  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
-    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
+  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
 \end{itemize}
 
-With these building blocks we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
+With these building blocks, we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
 After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
@@
 The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
-\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
   \TStime[\pi_{t_1}] = t_1\).
@@
 If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
-The \(\TSget\) request returns the hash of the most recent block of the chain (the head).
+The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
 The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).
@@
 The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
-A similar reasoning can be made with Proof-of-Work consensus where the computing power of the honest participants must outpower the one of malicious participants.
+A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
 In both cases, assuming a majority of honest members in the population, the more participants the merrier.
@@
 We require a few additional properties from \(\TS\) that are already provided by blockchains.
-First, \(\TS\) must be continuously extended, such as in Bitcoin where blocks are created every 10 minutes on average.
+First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
 Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
 Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
-In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her proof and the hash of the proof.
-\sonja{`` --- even if we no longer remember what our data looked like.'' This was commented out, but the question remains: can we still count?}
+In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her participation proof and the hash of the proof.

### 2018-11-12 paper/verifiability-properties.tex
coincoin

@@
 
-We draw inspiration from the three traditionally desired properties for 
-verifiability for voting:
+We draw inspiration from the three traditionally desired properties for verifiability for voting:
 % XXX find a new ref for voting verifiability properties
@@
 Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must 
-include temporal\footnote{%
-  Elections also has some temporal aspects, \eg one cannot vote at any time and 
-  a vote in one election should not be reusable in the next election.
-  However, the temporal relation for a protest is not as strictly defined as 
-  for elections, a protest can start at any time and last for an arbitrary 
-  period of time.
-} and spatial eligibility (\ie each participation proof satisfies some temporal 
-and spatial relation to the protest).
+The eligibility requirement is slightly different as for protests it must include temporal\footnote{
+Elections also have some temporal aspects, such that one cannot vote at any time and a vote in one election should not be reusable in the next election.
+However, the temporal relation for a protest is not as strictly defined as for elections as a protest can start at any time and last for an arbitrary period of time.}
+%Seb: the starting and ending time of the protest could also be included in the manisfest if we wanted to 
+and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
 In essence, the proof must bind the person to the time and location of the protest.
@@
     \begin{requirements}
-    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
-    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
+    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
+    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
     \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
+    %Seb: this property seems to be related to the eligibility property in the sense that if a participant tries to submit a second proof this directly conflicts with the eligibility
     \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.

### 2018-11-13 paper/verifiability-analysis.tex
Changes file structure for security/privacy/verifiability analyses

--- 2018-08-14 paper/analysis-security.tex
@@
-\section{Security and privacy analysis}%
-\label{SecurityAnalysis}
-
 \subsection{Individual and universal verifiability}%
@@
 
-\subsection{Eligibility verifiability}
+\subsection{Eligibility verifiability}%
 \label{analysis-eligibility}
@@
 
-\paragraph{Temporal eligibility}
+\paragraph{Temporal eligibility}%
 \label{analysis-temporal}
@@
 
-\paragraph{Linkability}
+\paragraph{Linkability}%
 \label{analysis-linkability}
@@
 
-\paragraph{Spatial eligibility}
+\paragraph{Spatial eligibility}%
 \label{analysis-spatial}
@@
 
-\paragraph{Designated protest}
+\paragraph{Designated protest}%
 \label{analysis-designated}
@@
 %
-
-\subsection{Privacy}
-
-We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable across protests but linkable within one protest due to \cref{CountOnce}.
-It follows from the properties of \(\ACprf\) that \(\pid =  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are unlinkable if \(\cid\neq \cid'\).
-
-Afterwards to get the property \cref{ProofUnlink}.
-Given \(\pid\), Grace cannot distinguish whether \(\pid = \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).
-
-However, consider the situation in which the witness works for Grace.
-This witness interacts with Alice directly and might have (physically) identified her.
-The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) and to verify the \ac{PPK}.
-\daniel{This assumes that I will do the changes to hide \(\cid\) from the witness in the \ac{PPK}.}
-Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
-share.
-The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
-  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
-\daniel{Fix this.}
-If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.

### 2018-11-13 paper/DB-anon-cred.tex

@@
 
-One protocol exists in the literature that provides \acp{PPK} with most of the 
-desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
-  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
-  shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} 
-protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
-logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of 
-anonymous credentials whose desirable properties we list in
-\cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
-To realize this, we will now introduce such a protocol in order to enable us to have \ac{DB} anonymous credentials.
+One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
+To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
 
@@
 
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the 
-distance-bounding protocols is based on the Schnorr identification 
-scheme~\cite{Schnorr}.
+In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
 However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
-We now propose another way to turn the Schnorr protocol into a
-public-key \ac{DB} protocol which is secure against \ac{DBMF},
-\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-It is important in our setting that the protocol is a public-key protocol, this 
-property implies protection against an impersonating verifiers.
+We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
+It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
 
@@
 The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once 
-by the prover in the setup phase.
+The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
 
@@
     &
-    & Construct \(s_b^{(0)}\concat s_b^{(1)}\) as the concatenation of 
-    \(r_i\)'s for which \(b_i = b\).
+    & Construct \(s_b^{(0)}\concat s_b^{(1)}\) as the concatenation of \(r_i\)'s for which \(b_i = b\).
     Compute \(s_b\gets s_b^{(0)} + s_b^{(1)}\).
@@
 
-During one round, the prover commits to a random nonce: \ie chooses 
-\(\rho\rgets \ZZ_q\) uniformly randomly, computes \(R\gets g^\rho\) and sends 
-\(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) 
-and sends them to the prover.
+During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
+The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
 The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
-This is the main difference to the original Schnorr protocol: the verifier 
-selects two challenges and the prover computes two responses --- but still only 
-\emph{one nonce}, \(\rho\).
-(This is also different from Brands-Chaum, where the prover and verifier 
-jointly construct \emph{one} challenge with \emph{one} response.)
+This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
+This is also different from the original Brands-Chaum protocol, in which the prover and verifier jointly construct \emph{one} challenge with \emph{one} response.)
 
-Now the prover randomly chooses
-\(s_0^{(0)}, s_1^{(0)}\in \ZZ_q\)
-and computes
-\(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
-\Ie \(s_b\) can be reconstructed by adding the two shares \(s_b^{(0)}, 
-  s_b^{(1)}\).
+Now the prover randomly chooses \(s_0^{(0)}, s_1^{(0)}\in \ZZ_q\) and computes \(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
+\Ie \(s_b\) can be reconstructed by adding the two shares \(s_b^{(0)}, s_b^{(1)}\).
 
 We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(2|q|\) response-bits from one challenge (say 
-\(s_b^{(0)}\concat s_b^{(1)}\)) and only \(0 < l\leq |q|\) from the other 
-(\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
-Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally 
-authenticate the prover by checking if \(R = g^{s_b}A^{c_b}\).
+The verifier will request all \(2|q|\) response-bits from one challenge (say \(s_b^{(0)}\concat s_b^{(1)}\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
+Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally authenticate the prover by checking if \(R = g^{s_b}A^{c_b}\).
 
@@
 
-The prover must know the responses for both challenges to successfully pass the 
-\ac{DB} phase.
-The reason for the two challenges but only one random nonce is that knowing the 
-responses to both means learning \(\alpha\).
+The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
+The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
 This allows us to prevent \ac{DBTF}.
-Bundling the authentication into the distance bounding phase (difference from 
-Brands-Chaum) prevents \ac{DBDH},
-and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
-The reason we use secret sharing and not \(s_b\) directly, is to bound the 
-\(l\) bits the verifier must learn of \(s_{1-b}\):
-Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with 
-secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus we still have information theoretic security for \(s_{1-b}\) although we 
-reveal the \(l\) bits.
+Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
+%reducing success of MF according to number of repetitions.
+The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
+Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
+Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
 
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
-security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
 the knowledge error, \(2^{-kn}\), becomes small enough.
-Repeating the protocol is also needed to decrease the success probability of 
-some of adversaries presented below.
+Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
 
 The \ac{DB} phase protects against distance fraud.
-Once the prover has received \(l+1\) challenges set to \(b\), it knows that the 
-remaining challenges must also be \(b\).
-\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before 
-responding with \(r_i\) for \(l+1\) challenges.
-Thus, the probability of successfully guessing the order of the challenge bits 
-is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
+Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
+\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
+Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
 
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} 
-phase for at least one round.
+The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
 The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but 
-none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information 
-theoretically independent \(|q|\)-bit shares.
-The adversary now has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat 
-  s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
-However, at this point the adversary must wait for the challenge bit 
-\(b_{l+1}\) from the verifier and then relay that challenge to the prover to 
-receive the correct \(r_i\) --- this relay will be detected.
-The alternative is to guess \(b\) and extract \(s_b\) for this challenge from 
-the prover.
-Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will 
-guess it correctly.
-Since we must execute the protocol \(n\) times, this is reduced to \(2^{-n}\).
-The adversary can also guess the remaining \(2|q|-l\) bits, which we will 
-discuss more below.
+By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information theoretically independent \(|q|\)-bit shares.
+Now, the adversary has two options.
+First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
+However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
+The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
+Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
+Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
+The adversary can also guess the remaining \(2|q|-l\) bits, which we will discuss in more details below.
 The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
-However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more 
-expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-|q|n}\).
+However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
+Thus the success probability of the \ac{DBMF} adversary is \emph{at most} \(2^{-n}+2^{-|q|n}\).
 
-The protocol is \ac{DBTF}-resistant, indeed, if the malicious prover gives both 
-responses to the accomplice, the accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie 
-\(1/2\) per round or, in total, \(2^{-n}\).
+The protocol is \ac{DBTF}-resistant. 
+Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
+The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
 
-The protocol is also secure against distance hijacking due to the fact
-that it is the authenticating bitstring that is used during the \ac{DB}
-phase, not the challenge bitstring as in the protocol of Brands-Chaum.
+The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
 
-Finally, it follows from the original Schnorr protocol that this is still 
-\iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check the 
-  details with Douglas.}
+Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
+\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
 
@@
 We wanted to formally verify the protocol security properties. 
-We used the Tamarin prover ~\cite{meier2013tamarin}.
-Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
+To realize this, we used the Tamarin prover ~\cite{meier2013tamarin}. 
+Tamarin does not include originally the possibility to reason on time and space in its model.
+However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modelization choices we made.
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true.
-We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
+Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
+This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
+We are currently investigating the Tamarin interactive mode to validate as well the security properties.

### 2018-11-13 paper/ZKPK.tex

@@
 which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
-Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, all other letters are known by the verifier.
+Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.
 

### 2018-11-13 paper/adversary-model.tex

@@
 
-One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as \ac{Tor}, for anonymous communication.
+One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous communication.
 However, given a strong enough adversary, such anonymous communication might not be possible.
@@
 The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
-witness \(W\) can submit to \(S\) over an anonymous channel, such as \ac{Tor}.
+witness \(W\) can submit to \(S\) over an anonymous channel, such as Tor~\cite{Tor}.
 Anyone who is in the same location will learn that \(W\) was present, we want 

### 2018-11-13 paper/analysis-performance.tex

@@
 \label{PerformanceAnalysis}
+\sonja{ Include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
 
-Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and
-computational power, and are operating on limited network capacity. 
+\subsection{Smartphones, smartcards}
+Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
 Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
@@
 
+\subsection{Distance bounding anonymous credentials}
 With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
@@
 %\) of processing.
+
+\subsection{Ledger (blockchain) efficiency}
+As an example, consider a protest with 1\,000\,000 participants.
+If we use trusted witnesses, each participant only needs to acquire one proof share from a trusted witness.
+Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
+If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.
+
+If we do not use trusted witnesses, but a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain.
+While this already takes longer than counting votes in national elections, the threshold is still very low.
+Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses.
+In addition to the ledger computation, we need to consider the creation of the proof shares.
+\sonja{added the previous sentence to explain why anonpass shows up here.
+Shouldn't that be in the performance section?
+}
+According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
+This yields \(
+  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+  \SI{48}{\second}.
+\) of processing.
+For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher.
+Considering that online forums can facilitate mass coordination, the threshold approach seems not only inefficient but also potentially ineffective for verifiability.
+
+%\subsection{Blockchain efficiency}
+
+\sonja{removed for now: One problem can arise in the case in which there is no trusted witnesses.
+In this situation, if we set the threshold too high, we need to submit more proof shares than the blockchain can handle within a reasonable time.}
+
+%assumptions about smartphones:
+%(This means that we essentially provide a lower bound for the participation 
+%count, since some participants might not have such a device.)
+%Sonja says: is this still true? Given mafia fraud we can't guarantee
+%that, right?

### 2018-11-13 paper/conclusions.tex

@@
 We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.
-
-For future work, a recently published model for formal verification of distance-bounding protocols~\cite{TamarinDB} looks promising to analyze and strengthen the properties of our protocol, especially once the model and tool are extended to include terrorist-fraud attacks and other formalizations of attacks and protocol properties as outlined as future work by the authors.

### 2018-11-13 paper/distance-bounding.tex

@@
 Time critical phases are complemented by slow phases during which the time is not taking into account. 
-At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate AND in his vicinity.
+At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in his vicinity.
 In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
@@
   \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
-  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
-    uses an unsuspecting honest prover close to the verifier to pass as being 
-    close.
+  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by 
-\citet{DB-BMV} and another by \citet{DB-DFKO}.
+There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
@@
 This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials 
-(which we do in \cref{DB-anon-cred}).
-The choice of the anonymous credential system will affect the properties we 
-require of the \ac{PPK} (\eg that it must be \iac{PK} for discrete logarithms).
+More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
+The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PK} for discrete logarithms).

### 2018-11-13 paper/privacy-properties.tex

@@
   No, that implication is not true, counter example:
-  There is receipt freeness for how a elector voted, but not that they voted.
+  There is receipt freeness for how an elector voted, but not that they voted.
   As Simon pointed out, they tick me off, so it's visible that I've voted.
@@
 % \sonja{end older thoughts}
-Finally, any temporary identifiers such as pseudonyms should only be reused when strictly necessary for the fulfillment of verifiability properties listed in \label{verifiability-properties} to prevent inference on long-term identities by repeated samples and side information.
+Finally, any temporary identifiers such as pseudonyms should only be reused 
+when strictly necessary for the fulfillment of verifiability properties listed 
+in \cref{verifiability-properties} to prevent inference on long-term identities 
+by repeated samples and side information.
 
@@
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every participant's real (long-term) identity (\(P\)) must be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
+\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every 
+  participant's (protester and witness) real (long-term) identity (\(P\)) must 
+  be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
 \item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))

### 2018-11-13 paper/system-model.tex

--- 2018-10-31 paper/system-model.tex
@@
 
-To set the stage, we will now describe our system model including assumptions (\cref{assumptions}) and present an abstraction of a protest and how to
-count the participation (\cref{protest-model}). 
-Afterwards, we formulate the desired verifiability (\cref{verifiability-properties}) and privacy properties
-(\cref{privacy-properties}) as well as the adversary model (\cref{adversary-model}).
+To set the stage, we will now describe our system model including assumptions (\cref{assumptions}) and present an abstraction of a protest and how to count the participation (\cref{protest-model}). 
+Afterwards, we formulate the desired verifiability (\cref{verifiability-properties}) and privacy properties (\cref{privacy-properties}) as well as the adversary model (\cref{adversary-model}).
 
@@
 For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
-This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation.
+This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation\footnote{
+Of course, this has for consequence that the \ac{CA} can perform a Sybil attack on the system.
+Thus, if the \ac{CA} is controlled by the government, no counts in favor of the government can be be trusted.
+}.
 
@@
 This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.
-%\sonja{another place to put reasons? Or if here, then for all
-%  assumptions. ``We need global connectivity before to read the head from the blockchain.
-%We need global connectivity after to upload the proof shares to the blockchain.''}
 
@@
 
-We consider two types of adversaries: \begin{enumerate*} \item an honest-but-curious adversary
-of up to national scale representing a government that can observe any
-messages sent, and \item a malicious adversary that can control a
-minority of 
-equipment such as participants' or witnesses' smartphones or servers
-used for the ledger such as miners for a blockchain. \end{enumerate*}
+We consider two types of adversaries: 
+\begin{enumerate*} 
+\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
+messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
+\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
+\end{enumerate*}

### 2018-11-13 paper/verifiability-analysis.tex
WIP on rewamping verifiability analysis

@@
 
-\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
-All proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
-Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.
+\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
+that their participation proofs (\ie proof shares) are indeed included in the 
+computed count.
+All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
+  t_e, t_e', l, \pi_\pid, \pi_{\wid})\)) are committed to the ledger and 
+available from a public and permanent storage (see 
+\cref{fig:ProtocolOverview}).
+Thus, Alice and Bob can simply check that all of their proof shares are indeed 
+there and the security of individual verifiability depends on the properties of 
+the ledger and storage (\(\TS\), \cref{timestamp}).
+(As these are the main properties of distributed ledgers, we do not elaborate 
+further.)
 
-\Cref{UniversalVerif}  includes that anyone can check the result and that all participation proofs counted are legitimate.
+\Cref{UniversalVerif} includes that anyone can check the result and that all 
+participation proofs counted are legitimate.
 As the proof shares are committed and stored publicly, anyone can
@@
 \pi_{\wid}\)) of the proofs and count them.
-As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.
+As for individual verifiability, the security of universal verifiability is 
+reduced to the properties of the ledger and storage; but universal 
+verifiability also depends on the eligibility verification, which we will 
+discuss next.
 
@@
 \Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
-In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
+In \PRIVO, we have several attributes that must be verifiable: the time of 
+creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 
+location of \(\sk_P\) at creation (\ie, spatial eligibility, 
+\cref{SpatiallyRelated}), recognition of two proofs originating from the same 
+person (\ie, one-proof-per-person eligibility, \cref{CountOnce}) and that the 
+proof is indeed designated for the event (\ie, designated-event eligibility, 
+\cref{DesignatedEvent}).
 We will now analyze these properties.
@@
 
-\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an old proof as a new one.
-In general, freshness requires the prover to respond to an unpredictable challenge.
-The challenge here is to include the hash value at the head of the blockchain at the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof share).
-As it is the case in the construction of blockchains, the hash value at the head depends on the previous blocks in the chain.
+\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an 
+old proof as a new one or create a proof in advance.
+
+In general, to prevent replays, Alice must respond to an unpredictable 
+challenge.
+The challenge here is the hash value of the head block of the ledger at the 
+time of the proof's creation (\(\TSget\)).
+The response is simply the challenge itself and is included as \(t_s\) and 
+\(t_s'\) in the proof share (see \cref{fig:ProofFig}).
+
+As it is the case in the construction of blockchains, the hash value at the 
+head depends on the previous blocks in the chain.
 Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
-In turn, the transactions depend on the signatures made by the signing keys corresponding to the used transactions.
+In turn, the transactions depend on the signatures made by the signing keys 
+corresponding to the used transactions --- which depends on uniformly random 
+nonces.
 If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
 Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.
+
+Also, the correctness of the challenge must be verifiable by any verifier 
+(\(\TStime\)).
 

### 2018-11-14 paper/verifiability-analysis.tex
Edits eligibility verifiability in security analysis

@@
 
-As it is the case in the construction of blockchains, the hash value at the 
-head depends on the previous blocks in the chain.
-Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
-In turn, the transactions depend on the signatures made by the signing keys 
-corresponding to the used transactions --- which depends on uniformly random 
-nonces.
-If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
-Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.
+As it is the case in the construction of ledgers, the hash value of the head 
+block depends on the previous blocks.
+Thus, the predictability of \(t_s\) depends on the predictability of the 
+blocks, which depends on the predictability of the transactions.
+Assume that Alice can control all transactions going into a block.
+This means that she must find a pre-image of the form of a valid block that is 
+accepted by all nodes in the distributed ledger.
+\Ie it depends on the pre-image resistance of the hash function used.
+Thus, with a collision resistant hash function, Alice can predict \(t_s\) only 
+with negligible probability; and it follows that, with high probability, 
+\(t_s\) was published on the ledger before being included in her proof share.
 
-Also, the correctness of the challenge must be verifiable by any verifier 
+The correctness of the challenge must be verifiable by any verifier 
 (\(\TStime\)).
+This can be done if the ledger is continuously extended at a fixed rate, \eg 
+one new block every 10 minutes, as was the case for Bitcoin.
 
@@
 Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
-The hash values of the proof shares are committed to the blockchain, which means that there is a negligible probability that they were created after that.
-Alice would have to choose a value \(y\) in the domain of the hash function \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) is a valid proof.
-If \(\Hash\) is collision resistant, finding \emph{any} preimage is hard.
+The hash values of the proof shares are committed to the ledger, which means 
+that there is a negligible probability that they were created after that.
+Alice is in the same situation as above:
+she would have to choose a value \(y\) in the domain of the hash function 
+\(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
+is a valid proof for the desired protest, at the desired time.
+If \(\Hash\) is collision resistant, finding \emph{any} pre-image is hard.
 

### 2018-11-14 paper/verifiability-analysis.tex
Edits linkability in verifiability analysis

@@
 Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
-Due to the deterministic property of \(\ACprf\), Alice must produce a new key \(\sk_P'\) and make the witness accept in the protocol
+Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
+\(\sk_P'\) such that the verifier\footnote{%
+  Here the verifier is either the witness during the distance bounding or the 
+  verifier who tries to verify the count.
+} accepts the proof
 \begin{multline*}

### 2018-11-14 paper/verifiability-analysis.tex
Edits linkability/spatial eligibility in verifiability analysis

@@
 while she does not know a valid signature on \(\sk_P'\).
-As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.
+As a consequence, this is reduced to the security of the \(\AC\) scheme and how 
+often Alice can get a valid signature on a secret key from the \ac{CA} --- 
+either by requesting a new key, \eg request a new passport or ID-card, or 
+illicitly use someone else's.
 
@@
 \Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
-To realize this, we have to ensure that Alice cannot forge witness signatures, which is realized by using the same linkability mechanism as above.
+To realize this, we must ensure that Alice cannot forge witness signatures, 
+which is realized by using the same linkability mechanism as above.
 To forge a witness signature, Alice must produce a \(\wid'\) such that
@@
 \end{multline*}
-while not knowing a signature on the secret key \(\sk_W'\).
+is accepted by the verifier while not knowing a signature on the secret key 
+\(\sk_W'\).
 Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
-The latter could be done if she can find people willing to collude.
+As above, the latter could be done if she can find people willing to collude, 
+people unwilling to collude but she can illicitly use their keys anyway or 
+simply request new keys from the \ac{CA}.
+
 However, due to the assumptions made in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course these two approaches could be combined).
-Note that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.
+Note that Alice can produce \emph{one} witness signature for herself, since she 
+has access to her own \(\sk_P\), but no more.
+Thus, \(\theta > 1\) is a requirement in the trust-free case.
 

### 2018-11-14 paper/verifiability-analysis.tex
Better phrasing in eligibility verifiability analysis

@@
 This possibility is prevented through the use of \(\cid\) in the proof shares.
-To reuse the proof share for another protest, with a different manifesto, one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = \Hash[\mfst']\).
+To reuse the proof share for another protest, with a different manifesto, one 
+must find a second pre-image \(\mfst'\) such that \(\cid = \Hash[\mfst] = 
+  \Hash[\mfst']\).
 
@@
 Thus, the verification process differs for the two types of proofs.
-(An alternative approach would have been to compute them differently, for instance \(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = g_T^{1/(\sk+x+1)}\).)
+(An alternative approach would have been to compute them differently, for 
+instance \(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC*[PRF]_{\sk}(x)\), where 
+\(\AC \neq \AC*\) are separate anonymous-credential systems.)
 

### 2018-11-15 paper/distance-bounding.tex

@@
 This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
-The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PK} for discrete logarithms).
+More specifically, we must combine such \iac{PPK} protocol with anonymous 
+credentials.
+The choice of the anonymous-credential system will affect the properties we 
+require of the \ac{PPK}, in particular, for the suggested instantiation it must 
+be \iac{PPK} for discrete logarithms.
+We do not know of any such protocol, but we have strong reasons to believe that 
+such protocols exists.

### 2018-11-15 paper/tamarin-spec.tex
Renames tamarin appendix to tamarin-spec
Changes tamarin-spec to section

--- 2018-10-31 paper/appendix.tex
@@
-\appendix
+\section{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
+\label{apdx:tamarin-spec}
 
-\subsection{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
-\label{apdx:tamarin-spec}
+The results provided by Tamarin extends to the protocol being modeled 
+only up to the accuracy of the specification of protocol rules (and equational theory).
+Moreover, Tamarin specifications are not always able to reproduce a protocol precisely.
+Consequently, we provide below the full code of our specification and of the various properties we defined, and briefly explain our choices of modelization.
+
+The key point is that Tamarin only provides symbolic modeling, and as such does not work with actual values.
+The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
+However, in some cases, a user can work around this restriction by providing their own equational theory.
+
+The most significant choices we made include:
+\begin{itemize}
+	\item We represented the responses $s_i$ as the challenges $c_i$ encoded with the nonce $\rho$ and signed with the prover long-term secret key $\alpha$; this is faithful to the actual purpose of those values in the protocol, even though the concrete operations executed do not correspond exactly to an encoding and a signature.
+Indeed, $s_i$ includes $\alpha$ to authenticate the prover (signing), and $\rho$ to mask the actual value of $\alpha$ (encoding).
+	\item We used the chosen challenge $c_b$ directly instead of the flag $b$ to represent the choice of the verifier between the two challenge values; this is equivalent because Tamarin does not work with actual values so the size of those values does not matter, and this helps us for the next point.
+	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
+	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
+	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.
+\end{itemize}
+
+Regarding the first point, Tamarin includes a built-in equational theory modeling the exponentiation rules used in Diffie-Hellman.
+Using that as a basis, it is possible to add a custom theory to represent addition and subtraction, and then use it to more accurately model the construction of the responses $s_i$, but this complexifies the specification a lot and we will not show it here.
 

### 2018-11-15 paper/verifiability-properties.tex

@@
 We draw inspiration from the three traditionally desired properties for verifiability for voting:
-% XXX find a new ref for voting verifiability properties
+\daniel{Find a new ref for voting verifiability properties, Douglas commented 
+  that the last one is not the origin.}
 \begin{description}
@@
   \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-    % Douglas: technically this is Sako-Kilian
+    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
+      old.}
   \item[Individual verifiability:] each voter can verify that his vote is included in the result.
-    % Douglas: this is much earlier than Sako-Kilian, in essence Fiat-Shamir.
+    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
+      Fiat-Shamir (technically). Non-technically, much older.}
 \end{description}
@@
 Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must include temporal\footnote{
-Elections also have some temporal aspects, such that one cannot vote at any time and a vote in one election should not be reusable in the next election.
-However, the temporal relation for a protest is not as strictly defined as for elections as a protest can start at any time and last for an arbitrary period of time.}
-%Seb: the starting and ending time of the protest could also be included in the manisfest if we wanted to 
+The eligibility requirement is slightly different as for protests it must 
+include temporal\footnote{%
+  Elections also have some temporal aspects, such that one cannot vote at any 
+  time and a vote in one election should not be reusable in the next election.
+  However, the temporal relation for a protest is not as strictly defined as for 
+  elections as a protest can start at any time and last for an arbitrary period 
+  of time.%
+}
+\seb{the starting and ending time of the protest could also be included in the 
+  manifest if we wanted to}
+\daniel{Yes, but it's not a requirement.}
 and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
@@
     \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
-    %Seb: this property seems to be related to the eligibility property in the sense that if a participant tries to submit a second proof this directly conflicts with the eligibility
+      \seb{this property seems to be related to the eligibility property in the 
+        sense that if a participant tries to submit a second proof this 
+        directly conflicts with the eligibility}
+      \daniel{Yes, that's why it's a sub-property of eligibility, we're trying 
+        to make eligibility more concrete.}
     \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.

### 2018-11-15 paper/analysis-performance.tex
s/PRIVO/CROCUS/g

@@
 \subsection{Smartphones, smartcards}
-Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
+Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
 Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
@@
 
-\subsection{Distance bounding anonymous credentials}
-With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
+% \subsection{Distance bounding anonymous credentials}
+% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
 The first step is only done once and is fairly costly in terms of ressources.
-This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
-This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
+% This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
+% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
 %Seb: to do add the reference to the following paper at the end of the sentence:
@@
 Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
-This can be reduced to 4 random number generations and one exponentiation using precomputation.
+% This can be reduced to 4 random number generations and one exponentiation using precomputation.
 The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.

### 2018-11-15 paper/analysis-security.tex
Fixes Syntastic warnings
Bugfix: \include doesn't want .tex suffix
s/PRIVO/CROCUS/g

@@
 \label{SecurityAnalysis}
+
+\sonja{including adversary model with different levels here for now as
+  it already contains some security analysis}
+\daniel{moved it to the top}
+\input{adversary-model.tex}
 
@@
 \Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
-In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
+In \CROCUS, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
 We will now analyze these properties.
 
-\paragraph{Temporal eligibility}
+\paragraph{Temporal eligibility}%
 \label{analysis-temporal}
@@
 If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.
+
+\sonja{anonymity and cause unlinkability missing}

### 2018-11-15 paper/conclusions.tex
s/PRIVO/CROCUS/g

@@
 
-In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
+In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
 Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
-To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
-Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
+%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
+%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
 }
-With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
+%With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
+\sonja{update sec analysis results}
 
-Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
-All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
-With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
+%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
+%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
+%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
 
@@
 Finally, most of the current methods are estimates, with quite some error margins. 
-While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
+While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
+Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
 However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.

### 2018-11-15 paper/intro.tex
s/PRIVO/CROCUS/g

@@
 
-\paragraph*{Contributions}
+%\paragraph*{Contributions}
 
-In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+%In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
-More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
+% Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+% Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
+% More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
+% The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
 %\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
@@
 %\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
-and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
+%and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
 
@@
 We also present our system as well as the adversary model together with desired privacy properties.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO.
+Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
 In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
-Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
+%Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
+%We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
 %\daniel{Check that this is true before publication.} 
-and formally verify it using Tamarin~\cite{TamarinDB}.
+%and formally verify it using Tamarin~\cite{TamarinDB}.
 %Seb: we need to be careful about the above sentence
-This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
+%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
 Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).

### 2018-11-15 paper/intro.tex
s/PRIVO/CROCUS/g

--- 2018-11-12 paper/intro.tex
@@
 We also present our system as well as the adversary model together with desired privacy properties.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO.
+Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
 In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
@@
 This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then \cref{Protocol}, we present \PRIVO, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+Then \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
 Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.

### 2018-11-15 paper/protocol.tex
s/PRIVO/CROCUS/g

@@
-\section{\PRIVO:\@ A protocol for crowd counting estimation}%
+\section{\CROCUS:\@ A protocol for crowd counting estimation}%
 \label{Protocol}
 
-We now present \PRIVO, a protocol for securely and privately verifying crowd counts.
+We now present \CROCUS, a protocol for securely and privately verifying crowd counts.
 The protocol consists of five phases: setup, join, participation, submission and verification phases.
@@
 
-\emph{Setup: \((\spk, \ssk)\gets \PRIVOsetup\).}
+\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
 \emph{Registration: \(\sk\gets 
-    \Proto{\PRIVOreg[_P][\spk]}{\PRIVOreg[_{\CA}][\ssk]}\).}
+    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
 During the registration phase, each participant generates a secret key and 
@@
 \emph{Joining as a protester: \((\pid, t_s)\gets 
-    \PRIVOjoin[_P][\text{manifesto}]\).}
+    \CROCUSjoin[_P][\text{manifesto}]\).}
 A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
@@
   \caption{%
-    An overview of the Join, Participation and Submission phases of \PRIVO.\@
+    An overview of the Join, Participation and Submission phases of \CROCUS.\@
     The organizer \(O\) broadcasts the manifesto.
@@
 
-\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
+\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
 The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
@@
 \emph{Participation: \(\pi\gets
-    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
+    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
 In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
@@
 
-\emph{Submission: \(\psh_P\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
+\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
 The participant should as soon as possible commit the proof-share data to the 
@@
 
-\emph{Submission: \(\psh_W\gets \PRIVOsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
+\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
     l]\).}

### 2018-11-15 paper/intro.tex
Fixes typos and cleans up title code

--- 2018-11-15 paper/intro.tex
@@
 Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
-However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
-In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times ---, which in turn increases the error of the estimation.
+However, most of them lack precision (\ie they have large error margins) and 
+they can only give an estimate for a particular snapshot in time (\eg at the 
+peak of the event). In particular, the existing methods cannot reliably 
+estimate the cumulative participation count --- at least not without counting 
+some persons multiple times --- which in turn increases the error of the 
+estimation.
 In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
@@
 In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
-In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claims should be verifiable).
+In this paper, our main objective is to provide a scheme preventing both Alice 
+and Grace from cheating by providing verifiable claims.
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
@@
 Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
-%Seb: in the sentence above I am not sure that the word unlinkable will be necessary clear
+\seb{in the sentence above I am not sure that the word unlinkable will be 
+  necessary clear}
 
@@
 
-%In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+%In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 

### 2018-11-16 paper/intro.tex

--- 2018-11-15 paper/intro.tex
@@
 
-In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 

### 2018-11-16 paper/verifiability-analysis.tex

@@
 \Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
-In \PRIVO, we have several attributes that must be verifiable: the time of 
+In \CROCUS, we have several attributes that must be verifiable: the time of 
 creation (\ie, temporal eligibility, \cref{TemporallyRelated}), the physical 

### 2018-11-16 paper/privacy-properties.tex
Removes @dbosk's arguments and slightly adapts @sbuc's statements
I remove @dbosk's arguments against @sbuc's statements about receipt
freeness and verifiability.

I also slightly adapts them:

  - Footnote on desirable, stating it's probably impossible without
  violating verifiability.
  - Still don't make clear which verifiability: @dbosk argues
  eligibility, @sbuc individual verifiability.

@@
 For instance, someone could simply physically bring Alice to a protest against her will.
-%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
-Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
-\daniel{%
-  No, that implication is not true, counter example:
-  There is receipt freeness for how an elector voted, but not that they voted.
-  As Simon pointed out, they tick me off, so it's visible that I've voted.
-  But no one will ever know for which party I voted.%
-}
-
-\daniel{%
-  This doesn't conflict with verifiability either.
-  I keep track of the ballot box, as long as that and all ballots inside are 
-  treated properly, I know my ballot is safe and counted.%
-}
-
-\daniel{%
-  In our case:
-  I have a key issued on a smartcard and it is tied to my identity.
-  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
-  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
-    \ACprf[_k][\cid']\).
-  I could have downloaded both from the ledger.
-  But I know which is mine, I can submit it, and as long as the block where it 
-  was included is intact I know my proof-share is included as well --- even if 
-  I forget what it looked like.%
-}
+Receipt freeness, while appealing at first glance, is not desirable\footnote{%
+  Or not possible without violating some of the verifiability 
+  requirements.
+} in our context since this will conflict with verifiability: in contrast to 
+voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the 
+protest) implies receipt freeness for \emph{that} the voter voted (\ie the 
+protester was there), which conflicts with verifiability.
 

### 2018-11-16 paper/distance-bounding.tex
removes text referring to our own DBAC, adds assumption and explanation

@@
 credentials.
-The choice of the anonymous-credential system will affect the properties we 
+The choice of the anonymous-credential system affects the properties we 
 require of the \ac{PPK}, in particular, for the suggested instantiation it must 
 be \iac{PPK} for discrete logarithms.
-We do not know of any such protocol, but we have strong reasons to believe that 
-such protocols exists.
+For this paper, we assume the existence of such a protocol.
+Candidates for such a protocol include modifications of ~\cite{ProProx} or \sonja{cite Seb's, which reference?} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2018-11-16 paper/intro.tex
removes text referring to our own DBAC, adds assumption and explanation

--- 2018-11-15 paper/intro.tex
@@
 Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
-However, most of them lack precision (\ie they have large error margins) and 
-they can only give an estimate for a particular snapshot in time (\eg at the 
-peak of the event). In particular, the existing methods cannot reliably 
-estimate the cumulative participation count --- at least not without counting 
-some persons multiple times --- which in turn increases the error of the 
-estimation.
+However, most of them lack precision (\ie they have large error margins) and they can only give an estimate for a particular snapshot in time (\eg at the peak of the event). 
+In particular, the existing methods cannot reliably estimate the cumulative participation count --- at least not without counting some persons multiple times ---, which in turn increases the error of the estimation.
 In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
@@
 In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
-In this paper, our main objective is to provide a scheme preventing both Alice 
-and Grace from cheating by providing verifiable claims.
+In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claims should be verifiable).
 To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
@@
 Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
-\seb{in the sentence above I am not sure that the word unlinkable will be 
-  necessary clear}
+%Seb: in the sentence above I am not sure that the word unlinkable will be necessary clear
 
@@
 
-%In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+%In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 
@@
 We also present our system as well as the adversary model together with desired privacy properties.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
+Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO.
 In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.

### 2018-11-16 paper/analysis-performance.tex
removes performance of DB

--- 2018-11-15 paper/analysis-performance.tex
@@
 \subsection{Smartphones, smartcards}
-Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
+Performance considerations are crucial during the protests due to the nature of the devices used to run \PRIVO, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
 Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.

### 2018-11-16 paper/protest-model.tex
changing the strength function

@@
 The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
-One example would be for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
+In general, \(\str\) can be defined as a weighted sum of the proof shares, $\str = \sum \omega_i.s_i$, with the weights $\omega_i$ being the trust in the witness corresponding to that proof share $s_i$, and the threshold $\theta$ represents the total trust needed to accept a participant as valid.
+One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
 Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
 For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
-In this situation, the strength function could be defined with respect to the number of proof shares issued by trusted witnesses.
-Setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
+In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
+setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
+Finally, both approaches can be combined by giving a weight of 1 to all non-trusted witnesses and a weight of $\theta$ to trusted witnesses.
+This results in a participant being valid if they are witnessed either by $\theta$ non-trusted witness or by one trusted witness.
+
+\simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}

### 2018-11-16 paper/privacy-properties.tex
Edits verifiability and privacy properties, pseudonyms

@@
 Thus, in our context the crucial property is therefore privacy.
-More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
-Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).
+More precisely, for the protester we want unlinkability (from the adversary's 
+perspective) between a protester's real identity \(P\) and the cause identifier 
+\(\cid\).
+Phrased differently, given a participation proof, Grace should not be able to 
+distinguish if it belongs to Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice due to some 
+auxiliary knowledge, she should not be able to link it to another proof (\eg 
+from a different protest).
 
@@
 % \sonja{end older thoughts}
-Finally, any temporary identifiers such as pseudonyms should only be reused 
-when strictly necessary for the fulfillment of verifiability properties listed 
-in \cref{verifiability-properties} to prevent inference on long-term identities 
+
+Finally, any temporary identifiers, such as pseudonyms, should only be reused 
+when strictly necessary for the fulfillment of verifiability properties (in 
+\cref{verifiability-properties}) to prevent inference on long-term identities 
 by repeated samples and side information.
@@
 
+In light of these definitions, we note that \cref{CountOnce} can be rephrased 
+in terms of pseudonyms as follows:
+\begin{enumerate}
+  \item[V1.3.] \emph{Counted only once}:
+    A protester can create \emph{only one} pseudonym per protest, this 
+    pseudonym is unique except with negligible probability.
+\end{enumerate}
+
 %Seb: ok for me, I have put it in comment

### 2018-11-16 paper/conclusions.tex
removes DB and outdated analysis in conclusions

@@
 
-In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
+In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
 Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
@@
 Finally, most of the current methods are estimates, with quite some error margins. 
-While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
+While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
+Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
 However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.

### 2018-11-16 paper/protest-model.tex
Fixes formulas, math mode for strength function

@@
 
-The strength function \(\str\) can be used to regulate the trust in the participation count estimated.
-In general, \(\str\) can be defined as a weighted sum of the proof shares, $\str = \sum \omega_i.s_i$, with the weights $\omega_i$ being the trust in the witness corresponding to that proof share $s_i$, and the threshold $\theta$ represents the total trust needed to accept a participant as valid.
+The strength function \(\str\) can be used to regulate the trust in the 
+participation count estimated. In general, \(\str\) can be defined as a 
+weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
+weights \(\omega_i\) being the trust in the witness corresponding to that proof 
+share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
+to accept a participant as valid.
 One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
@@
 setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
-Finally, both approaches can be combined by giving a weight of 1 to all non-trusted witnesses and a weight of $\theta$ to trusted witnesses.
-This results in a participant being valid if they are witnessed either by $\theta$ non-trusted witness or by one trusted witness.
+Finally, both approaches can be combined by giving a weight of 1 to all 
+non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
+results in a participant being valid if they are witnessed either by \(\theta\) 
+non-trusted witness or by one trusted witness.
 
 \simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}
+\daniel{Fixed formula, math mode; didn't check Section V though.}

### 2018-11-16 paper/intro.tex
restructures paper, informal models and properties, related work, formal definitions of protest, properties, adversary, then rest

--- 2018-11-16 paper/intro.tex
@@
 \emph{Context.} 
-Consider the following illustrative scenario.
+Consider the following scenario.
 Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
@@
 More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
-Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.
-\seb{in the sentence above I am not sure that the word unlinkable will be 
-  necessary clear}
+Nonetheless, we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
+%\seb{in the sentence above I am not sure that the word unlinkable will be 
+%  necessary clear}
 
@@
 The paper is organized as follows.
-First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
-We also present our system as well as the adversary model together with desired privacy properties.
+First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting.
 Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
-In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
-Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
-%\daniel{Check that this is true before publication.} 
+We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
+Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
+We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
+\daniel{Check that this is true before publication.} 
 and formally verify it using Tamarin~\cite{TamarinDB}.
-%Seb: we need to be careful about the above sentence
-This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
-Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
+\seb{we need to be careful about the above sentence}
+%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
+Then in\cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
 %\sonja{add (sub) sections for performance and verification}

### 2018-11-16 paper/intro.tex
restructures paper, informal models and properties, related work, formal definitions of protest, properties, adversary, then rest

@@
 
-\paragraph*{Contributions}
+%\paragraph*{Contributions}
 
-In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+%In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
-More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
+% Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+% Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
+% More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
+% The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
 %\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing

### 2018-11-16 paper/system-model.tex
restructures paper, informal models and properties, related work, formal definitions of protest, properties, adversary, then rest

@@
 
-To set the stage, we will now describe our system model including assumptions (\cref{assumptions}) and present an abstraction of a protest and how to count the participation (\cref{protest-model}). 
-Afterwards, we formulate the desired verifiability (\cref{verifiability-properties}) and privacy properties (\cref{privacy-properties}) as well as the adversary model (\cref{adversary-model}).
+To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.
 
@@
 
-\include*{protest-model}
-\include*{verifiability-properties}
-\include*{privacy-properties}
+\subsection{Desired properties}
+
+\sonja{here goes an informal summary, enough to understand the related work section}
+
 \subsection{Adversary model}

### 2018-11-16 paper/system-model.tex
adds some comments, moves gvt id remarks from system model to discussion

@@
 Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf.
-Furthermore, we assume that each participant has a digital certificate signed by the \ac{CA}.
-For instance, we could use the cryptographic keys of any national electronic identity system, identity card or passport.
-This assumption is needed to prevent Sybil attacks~\cite{SybilAttack}, which would have a disastrous effect on the crowd-counting estimation\footnote{
-Of course, this has for consequence that the \ac{CA} can perform a Sybil attack on the system.
-Thus, if the \ac{CA} is controlled by the government, no counts in favor of the government can be be trusted.
-}.
+Furthermore, we assume that each participant has a digital certificate of her identity signed by a \ac{CA}.
 

### 2018-11-16 paper/protocol.tex
changing the strength function
edits first part of protocol section

@@
 
-We now present \CROCUS, a protocol for securely and privately verifying crowd counts.
-The protocol consists of five phases: setup, join, participation, submission and verification phases.
-The setup is described in \cref{ProtocolSetup}.
-The join, participation and submission phases are detailed in \cref{ProtocolDuring}.
-Finally, the verification phase is presented in \cref{ProtocolVerification}.
+We now present \CROCUS, a protocol for privately verifyiable crowd counts.
+The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
+join, participation, submission (all in in \cref{ProtocolDuring} ) and
+verification (in \cref{ProtocolVerification}).
 
@@
 
-In the case \emph{without} trusted witnesses, the verifier simply define 
-\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\) and set \(\theta\) to the 
-desired threshold.
+In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
+\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
 

### 2018-11-19 paper/intro.tex
adds some comments, moves gvt id remarks from system model to discussion
Adds missing space

--- 2018-11-16 paper/intro.tex
@@
 \emph{Context.}
+
+\sonja{explain that this is for crowd counting in general, but we choose a scenario where privacy and verifiability (transparency) matter most: protest against oppressive regime}
 Consider the following scenario.
@@
 %This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then in\cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd 
+counting estimation protocol constructed from these building blocks, before 
+analyzing its security and privacy (\cref{SecurityAnalysis}).
 Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.

### 2018-11-20 paper/analysis-performance.tex
update of performance analysis

--- 2018-11-15 paper/analysis-performance.tex
@@
 \label{PerformanceAnalysis}
-\sonja{ Include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
+\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
 
-\subsection{Smartphones, smartcards}
+\subsection{Smartphones and smartcards}
 Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
@@
 
-\subsection{Distance bounding anonymous credentials}
+With respect to its implementation, \CROCUS is actually very similar to Anon-Pass~\cite{AnonPass}, an anonymous subscription system in which a long-term credential can be used to derive a single login for any authentication window (\ie epoch) such that logins are unlinkable across different epochs.
+In particular, the setup and registration phases are almost identical. 
+The evaluation conducted by the authors was using as server a Dell Optiplex 780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz Intel Core 2 CPU but with only 4 GB of RAM.
+The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
+This is typically the type of pairing that could also be used with \CROCUS.
+Not counting the setup that is performed once by the CA, the time reported for the registration on the server (\ie CA) side is 19.8 milliseconds while it is 23.4 milliseconds on the client side.
+With respect to joining and participation phases, with the exception of the distance-bounding they are actually quite similar to the login protocol of Anon-Pass in which the time required to create a message for a protester would be around 13.5 milliseconds while the time needed for the witness would be only 7.9 milliseconds.
+
+\subsection{Distance-bounding anonymous credentials}
+The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
+One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
+For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
+More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode.
+The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
+
 With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
-The first step is only done once and is fairly costly in terms of ressources.
-This means that the best strategy is to precompute the corresponding results and to store them on the prover's device. 
-This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol [1].
+The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
+This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
 %Seb: to do add the reference to the following paper at the end of the sentence:
@@
 %for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
-Considering the entire setup of our protocol, we perform 7 random number generations (one of them being a single bit), two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
-This can be reduced to 4 random number generations and one exponentiation using precomputation.
-The Anon-pass article [2] gives us a total time of 43,2 milliseconds of raw protocol operation time in order to create, sign and verify a given message (the registration phase), and then 21,4 mililseconds to login.
-%[2] Lee, M., Dunn, A., Katz, J., Waters, B., & Witchel, E. (2013). Anon-pass: Practical anonymous
-%subscriptions. IEEE Security & Privacy, (1), 1.
+Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
+However, this can be reduced to four random number generations and one exponentiation using precomputation.
 
@@
 
-If we do not use trusted witnesses, but a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain.
+If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
 While this already takes longer than counting votes in national elections, the threshold is still very low. 
@@
 }
+%Seb: I agree maybe we should move it to the previous subsection
 According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.

### 2018-11-20 paper/DB-anon-cred.tex
Rotates too wide figure

@@
 
-    \(\forall i\in\bin\colon s_i\gets \rho - c_i\alpha \mod q\)
+    \(s_0\gets \rho - c_0\alpha \pmod q\)
     &
@@
 
-    \(\forall i\in\bin\colon s_i^{(0)} \rgets \ZZ_q, s_i^{(1)} \gets s_i - 
-      s_i^{(0)} \mod q\)
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
     &
-    & Prepare \(B\in \bin^{2|q|+l}\), with \(2|q|\) bits set to \(b\).
+    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < 2|q| 
-        + l, j\gets 0\)} \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
+        l, j\gets 0\)} \\
 
@@
 
-    \(r_i\gets (s_{b_i}^{(0)}\concat s_{b_i}^{(1)})[jb_i + (i-j)(1-b_i)]\)
+    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
     & \(\ProtoSendRight{r_i}\)
@@
     &
-    & Construct \(s_b^{(0)}\concat s_b^{(1)}\) as the concatenation of \(r_i\)'s for which \(b_i = b\).
-    Compute \(s_b\gets s_b^{(0)} + s_b^{(1)}\).
+    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
+      b\).
       Accept if \(R = g^{s_b} A^{c_b}\).
@@
 This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
-This is also different from the original Brands-Chaum protocol, in which the prover and verifier jointly construct \emph{one} challenge with \emph{one} response.)
-
-Now the prover randomly chooses \(s_0^{(0)}, s_1^{(0)}\in \ZZ_q\) and computes \(s_0^{(1)} \gets s_0 - s_0^{(0)}, s_1^{(1)} \gets s_1 - s_1^{(0)}\).
-\Ie \(s_b\) can be reconstructed by adding the two shares \(s_b^{(0)}, s_b^{(1)}\).
+This is also different from the original Brands-Chaum protocol, in which the 
+prover and verifier jointly construct \emph{one} challenge with \emph{one} 
+response.
 
 We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(2|q|\) response-bits from one challenge (say \(s_b^{(0)}\concat s_b^{(1)}\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}^{(0)}\concat s_{1-b}^{(1)}\)).
-Then the verifier can compute \(s_b = s_b^{(0)} + s_b^{(1)}\) and finally authenticate the prover by checking if \(R = g^{s_b}A^{c_b}\).
+The verifier will request all \(|q|\) response-bits from one challenge (say 
+\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
+Then the verifier can authenticate the prover by checking if \(R = 
+  g^{s_b}A^{c_b}\).
 
@@
 The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals all the bits of either \(s_0\) or \(s_1\), but none of the other --- only \(l\leq |q|\) bits of \emph{one of two} information theoretically independent \(|q|\)-bit shares.
+By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
+  s_1\).
+\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
+\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
 Now, the adversary has two options.
@@
 Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
-The adversary can also guess the remaining \(2|q|-l\) bits, which we will discuss in more details below.
-The probability of guessing these bits successfully is \(2^{-(2|q|-l)}\).
-However, \(l < |q| \implies 2|q|-l > |q|\) and this might thus be more expensive than guessing \(s_{1-b}\) directly, which is \(2^{-|q|}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} \(2^{-n}+2^{-|q|n}\).
+If the adversary requests \(s_b\) in full, the adversary can also guess the 
+remaining \(|q|-l\) bits of \(s_{1-b}\).
+Based on our assumption above, the probability of guessing these bits 
+successfully is \(2^{-(|q|-l)}\).
+Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
+\(2^{-n}+2^{-(|q|-l)n}\).
 
@@
 The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
+Thus the probability of success is equivalent of a collision for the responses 
+for the chosen challenge --- in each round.
 
@@
 
-We wanted to formally verify the protocol security properties. 
-To realize this, we used the Tamarin prover ~\cite{meier2013tamarin}. 
-Tamarin does not include originally the possibility to reason on time and space in its model.
+We wanted to formally verify the protocol security properties. To realize this, 
+we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
+originally the possibility to reason on time and space in its model.
 However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

### 2018-11-20 paper/analysis-performance.tex

@@
 
-\subsection{Distance-bounding anonymous credentials}
-The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
-One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
-For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
-More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode.
-The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
-
-With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
-The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
-This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
-%Seb: to do add the reference to the following paper at the end of the sentence:
-%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
-%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
-Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
-However, this can be reduced to four random number generations and one exponentiation using precomputation.
+%\subsection{Distance-bounding anonymous credentials}
+%The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
+%One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
+%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
+%More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode.
+%The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
+%
+%With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
+%The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
+%This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
+%%Seb: to do add the reference to the following paper at the end of the sentence:
+%%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
+%%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
+%Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
+%However, this can be reduced to four random number generations and one exponentiation using precomputation.
 

### 2018-11-20 paper/protest-model.tex

@@
 A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
-Note that a participant of a protest can take the role of a protester but also act as witness for other protesters.
-The participation proof and its proof shares are stored as a set.
-%, as there should only be unique proof shares.
+(Note that a participant of a protest can take the role of a protester but also 
+act as witness for other protesters.)
+All the proof shares together form the participation proof.
 
@@
 
+A subset of the proof shares forms a participation proof for a protester.
 We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
@@
 \end{multline*}
-
-A subset of the proof shares forms a participation proof for a protester.
 
@@
 % strength
-\NewFunction{\str}{\varsigma}
 

### 2018-11-20 paper/privacy-properties.tex
Removes old stuff we've settled on

--- 2018-11-13 paper/privacy-properties.tex
@@
 
-%Seb: I have put it in comments to save on space
-%\sonja{removed for now: For the witness, we want unlinkability between a witness's identity \(W\) and a 
-%location \(l\) against an adversary who is not present in the location.
-%Due to the limitations of physical space, two individuals present in the same 
-%location will inevitably learn of each other's presence.
-%Thus we will only try to prevent individuals who are not present to learn of 
-%this presence.}
-
-% \sonja{start of older thoughts}
-% Difference to e-voting:
-% physical presence means support for a cause if there is one protest.
-If there is a counterprotest, physical presence with that group means support for the counterprotest.
-In our system, it gets more ambiguous as the participants are counted if all of the following is true
-% \begin{enumerate*}
-% \item they participate in the protocol,
-% \item they use the protest identifier (cause) for which the count is done,
-% \item they meet the eligibility criteria, and
-% \item they receive enough proof shares,
-% \item that are uploaded to the ledger.
-% \end{enumerate*}
-% Thus one could participate in a protest and be counted even when physically 
-% present at a counter-protest if the two protests are co-located and the 
-% participant chooses the corresponding cause/identifier of the original protest.
-
-% Given that all conditions for being counted in a protest are met, individual 
-% verifiability implies a receipt \daniel{no, I know my proof is included in 
-%  block 0xdeadbeef in the blockchain, so as long as 0xdeadbeef is there I'm 
-%  sure my block is counted (individual verifiability); but if I give 0xdeadbeef 
-%  to you, you cannot know for sure if 0xdeadbeef says anything or I made it up, 
-%  hence receipt-freeness} because being counted implies support for a cause. 
-% This also means that besides physical force, coercion can happen by forcing the 
-% participate to show a receipt. \daniel{The only receipt we have is the private 
-%  key of the protester, with that key the adversary can compute \(\pid = 
-%    \ACprf[_k][\cid]\) and check that \(\pid\) is indeed in the ledger.}
-% We thus have to decide between individual verifiability and the privacy 
-% properties for e-voting or define privacy properties suitable for the scenario. 
-% The ultimate privacy requirement is thus stronger here: in contrast to voting, 
-% where it is the content of the vote itself that needs to be unlinkable to the 
-% voter, here the fact of having cast a vote at all needs to be unlinkable.
-
-% The privacy properties we need in this context are the following:
-% \begin{description}
-%  \item[Involuntary participant unlinkability:] \daniel{the name has a 
-%      double-negative ring to me} unless the participant discloses the receipt 
-%    (by revealing her identity), there is no link between the protest data on 
-%    the ledger and the identity of the participant.
-
-%  \item[Involuntary witness unlinkability:] \daniel{and double-negative here 
-%      too of course} unless the witness discloses the receipt (by revealing her 
-%    identity), there is no link between the protest data on the ledger and the 
-%    identity of the witness.
-% \end{description}
-
-% In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
-% As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
-% Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
-% Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
-
-% As a consequence, this leaves us with with what would correspond to vote privacy.
-% In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-% \sonja{end older thoughts}
-Finally, any temporary identifiers such as pseudonyms should only be reused 
-when strictly necessary for the fulfillment of verifiability properties listed 
-in \cref{verifiability-properties} to prevent inference on long-term identities 
+Finally, any temporary identifiers, such as pseudonyms, should only be reused 
+when strictly necessary for the fulfillment of verifiability properties (in 
+\cref{verifiability-properties}) to prevent inference on long-term identities 
 by repeated samples and side information.

### 2018-11-20 paper/privacy-properties.tex
Removes old stuff we've settled on

@@
 For instance, someone could simply physically bring Alice to a protest against her will.
-%Seb: ok but if Alice can refuse to upload her participation proof then coercion resistance can still be achieved
-Receipt freeness, while appealing at first glance, is not desirable in our context, as in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the protest) implies receipt freeness for \emph{that} the voter voted (\ie the protester was there), which conflicts with verifiability.
-\daniel{%
-  No, that implication is not true, counter example:
-  There is receipt freeness for how an elector voted, but not that they voted.
-  As Simon pointed out, they tick me off, so it's visible that I've voted.
-  But no one will ever know for which party I voted.%
-}
-
-\daniel{%
-  This doesn't conflict with verifiability either.
-  I keep track of the ballot box, as long as that and all ballots inside are 
-  treated properly, I know my ballot is safe and counted.%
-}
-
-\daniel{%
-  In our case:
-  I have a key issued on a smartcard and it is tied to my identity.
-  If the hardware corrupts itself after issuing the \ac{NIZK} proof, then there 
-  is no way to check whether I created \(\pid = \ACprf[_k][\cid]\) or \(\pid' = 
-    \ACprf[_k][\cid']\).
-  I could have downloaded both from the ledger.
-  But I know which is mine, I can submit it, and as long as the block where it 
-  was included is intact I know my proof-share is included as well --- even if 
-  I forget what it looked like.%
-}
+Receipt freeness, while appealing at first glance, is not desirable\footnote{%
+  Or not possible without violating some of the verifiability 
+  requirements.
+} in our context since this will conflict with verifiability: in contrast to 
+voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the 
+protest) implies receipt freeness for \emph{that} the voter voted (\ie the 
+protester was there), which conflicts with verifiability.
 
 Thus, in our context the crucial property is therefore privacy.
-More precisely for the protester, we want unlinkability between a protester's real identity \(P\) and the cause identifier \(\cid\) against the adversary.
-Given a participation proof, Grace should not be able to distinguish if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice due to some auxiliary knowledge, she should not be able to link it to another proof (\eg, from a different protest).
+More precisely, for the protester we want unlinkability (from the adversary's 
+perspective) between a protester's real identity \(P\) and the cause identifier 
+\(\cid\).
+Phrased differently, given a participation proof, Grace should not be able to 
+distinguish if it belongs to Alice or Bob.
+Furthermore, if Grace has managed to link one proof to Alice due to some 
+auxiliary knowledge, she should not be able to link it to another proof (\eg 
+from a different protest).
 

### 2018-11-20 paper/privacy-properties.tex
Moves intuition for properties to system-model

@@
 \label{privacy-properties}
-
-In addition to the verification requirements, we also need to define the privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{description}
-  \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
-\end{description}
-
-Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against her will.
-Receipt freeness, while appealing at first glance, is not desirable\footnote{%
-  Or not possible without violating some of the verifiability 
-  requirements.
-} in our context since this will conflict with verifiability: in contrast to 
-voting, receipt freeness for \emph{how} the voter voted (\ie the cause of the 
-protest) implies receipt freeness for \emph{that} the voter voted (\ie the 
-protester was there), which conflicts with verifiability.
-
-Thus, in our context the crucial property is therefore privacy.
-More precisely, for the protester we want unlinkability (from the adversary's 
-perspective) between a protester's real identity \(P\) and the cause identifier 
-\(\cid\).
-Phrased differently, given a participation proof, Grace should not be able to 
-distinguish if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (\eg 
-from a different protest).
 

### 2018-11-20 paper/system-model.tex
Moves intuition for properties to system-model

@@
 
-\subsection{System model and physical assumptions}
+\subsection{System model and physical assumptions}%
 \label{assumptions}
@@
 
-\sonja{here goes an informal summary, enough to understand the related work section}
+We note that, in general terms, protesting is very similar to petitions, which 
+in turn are similar to voting.
+Indeed, all three situations correspond to situations in which many individuals express their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
 
-\subsection{Adversary model}
+We draw inspiration from the three traditionally desired properties for verifiability for voting:
+\daniel{Find a new ref for voting verifiability properties, Douglas commented 
+  that the last one is not the origin.}
+\begin{description}
+  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
+  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
+    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
+      old.}
+  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
+    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
+      Fiat-Shamir (technically). Non-technically, much older.}
+\end{description}
+In our context, votes are translated into \emph{participation proofs}.
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
+The eligibility requirement is slightly different as for protests it must 
+include temporal\footnote{%
+  Elections also have some temporal aspects, such that one cannot vote at any 
+  time and a vote in one election should not be reusable in the next election.
+  However, the temporal relation for a protest is not as strictly defined as for 
+  elections as a protest can start at any time and last for an arbitrary period 
+  of time.%
+} and spatial eligibility (\ie each participation proof satisfies some temporal 
+and spatial relation to the protest).
+In essence, the proof must bind the person to the time and location of the protest.
+
+In addition to the verification requirements, we also need to define the 
+privacy properties.
+In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\begin{description}
+  \item[Vote privacy:] the voting does not reveal any individual vote.
+  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
+\end{description}
+
+Coercion resistance is not possible to achieve for protests.
+For instance, someone could simply physically bring Alice to a protest against her will.
+Receipt freeness, while appealing at first glance, is not desirable (probably 
+not possible) in our context since this will conflict with verifiability: in 
+contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
+cause of the protest) implies receipt freeness for \emph{that} the voter voted 
+(\ie the protester was there), which conflicts with verifiability.
+
+Thus, in our context the crucial property is therefore privacy.
+More precisely, for the protester we want unlinkability (from the adversary's 
+perspective) between a protester's real identity \(P\) and the participation 
+proof (and thus also the protest itself).
+Phrased differently, given a participation proof, Grace should not be able to 
+distinguish if it was Alice or Bob who participated.
+Furthermore, if Grace has managed to link one proof to Alice due to some 
+auxiliary knowledge, she should not be able to link it to another proof (\eg 
+from a different protest).
+
+\subsection{Adversary model}%
 \label{adversary-model}

### 2018-11-20 paper/verifiability-properties.tex
Edits verifiability and privacy properties, pseudonyms
Moves intuition for properties to system-model

@@
 
-We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
-Indeed, all three situations correspond to situations in which many individuals express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
-(We discuss privacy in \cref{privacy-properties}.)
-
-We draw inspiration from the three traditionally desired properties for verifiability for voting:
-\daniel{Find a new ref for voting verifiability properties, Douglas commented 
-  that the last one is not the origin.}
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
-      old.}
-  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
-    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
-      Fiat-Shamir (technically). Non-technically, much older.}
-\end{description}
-In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must 
-include temporal\footnote{%
-  Elections also have some temporal aspects, such that one cannot vote at any 
-  time and a vote in one election should not be reusable in the next election.
-  However, the temporal relation for a protest is not as strictly defined as for 
-  elections as a protest can start at any time and last for an arbitrary period 
-  of time.%
-}
-\seb{the starting and ending time of the protest could also be included in the 
-  manifest if we wanted to}
-\daniel{Yes, but it's not a requirement.}
-and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
-In essence, the proof must bind the person to the time and location of the protest.
-
-To adapt these properties to the context of protests, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
+To adapt these properties to the context of protests, we define three 
+verifiability requirements, among which eligibility can be further broken up 
+into four subproperties:
 \begin{requirements}[V]
@@
     \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
-    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
+    \item\label{CountOnce} \emph{Counted only once}: prove that no individual 
+      can be counted more than once for a particular protest.
       \seb{this property seems to be related to the eligibility property in the 

### 2018-11-21 paper/privacy-properties.tex
Writes up verifiability and privacy properties (definitions)

@@
 
-Finally, any temporary identifiers, such as pseudonyms, should only be reused 
-when strictly necessary for the fulfillment of verifiability properties (in 
-\cref{verifiability-properties}) to prevent inference on long-term identities 
-by repeated samples and side information.
-
+For privacy, any temporary identifiers, such as pseudonyms, should only be 
+reused when strictly necessary (by the principle of data minimization) for the 
+fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
+prevent inference on long-term identities by repeated samples and side 
+information.
 We can thus summarize the desired privacy properties as follows:
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Proof Unlinkability (Anonymity)}: every 
-  participant's (protester and witness) real (long-term) identity (\(P\)) must 
-  be unlinkable to their participation proofs \(\prf_{\pid, \prtst}\)
-\item\label{ProtestUnlink} \emph{Protest Unlinkability}: protesters' participation proofs \(\prf_{\pid, \prtst}\) must be unlinkable between protests (\(\cid, \cid' \))
-\item\label{WitnessUnlink}\emph{Witness Unlinkability}:  witnesses' participation proof shares \(\psh = (\cid, t, l, \pid,\wid)\) must be unlinkable between protesters. (\(\pid, \pid' \))
+\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
+  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
+  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
+    \pid_{\text{Bob}}\), except with negligible probability.
+\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
+  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
+    \cid'\)) from the adversary's perspective.
+\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
+  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
+    \pid'\)) from the adversary's perspective.
 \end{requirements}
 
-In light of these definitions, we note that \cref{CountOnce} can be rephrased 
-in terms of pseudonyms as follows:
-\begin{enumerate}
-  \item[V1.3.] \emph{Counted only once}:
-    A protester can create \emph{only one} pseudonym per protest, this 
-    pseudonym is unique except with negligible probability.
-\end{enumerate}
-
-%Seb: ok for me, I have put it in comment
-%\sonja{removed for now: As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-%This is, in fact, is a slight increase in privacy over ordinary protests.}
+What these properties say is that pseudonyms must look random 
+(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
+(\cref{ProtestUnlink,WitnessUnlink}).

### 2018-11-21 paper/verifiability-properties.tex
Moves intuition for properties to system-model
Writes up verifiability and privacy properties (definitions)

@@
 
-To adapt these properties to the context of protests, we define three 
-verifiability requirements, among which eligibility can be further broken up 
-into four subproperties:
+We now try to make the properties from \cref{desired-properties} more 
+specific.
+We define three verifiability requirements, among which eligibility can be 
+further broken up into four subproperties:
 \begin{requirements}[V]
@@
     \begin{requirements}
+
     \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
+
     \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
-    \item\label{CountOnce} \emph{Counted only once}: prove that no individual 
-      can be counted more than once for a particular protest.
-      \seb{this property seems to be related to the eligibility property in the 
-        sense that if a participant tries to submit a second proof this 
-        directly conflicts with the eligibility}
-      \daniel{Yes, that's why it's a sub-property of eligibility, we're trying 
-        to make eligibility more concrete.}
+
+    \item\label{CountOnce} \emph{Counted only once}:
+      A protester can create \emph{one and only one} pseudonym per protest 
+      (\(\pid\) in \cref{DefProofShares}), this pseudonym is unique except with 
+      negligible probability.
+      Analogously, a witness can create \emph{one and only one} pseudonym per 
+      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
+      except with negligible probability.
+
     \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
+
     \end{requirements}

### 2018-11-21 paper/adversary-model.tex
Renames identity--cause -> identity--proof-share, removed location adv

@@
-\subsection{Adversary models}%
+\subsection{Privacy adversary}%
 \label{adversary-model-different-levels}
 
-We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest cause (\(\cid\)) and one 
+We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest proof-share (\(\cid\)) and one 
 that aims at linking a protester's or a witness's real identity (\(P\), respectively \(W\)), to a location (\(l\)).
@@
 
-\paragraph{The identity--cause linking adversary}
+\paragraph{The identity--proof share linking adversary}
 
@@
 
-\begin{definition}[Base identity--cause adversary]%
-  \label{base-identity-cause-adversary}
+\begin{definition}[Base identity--proof share adversary]%
+  \label{base-identity-proof-share-adversary}
   The protester \(P\) and the witness \(W\) communicate.
@@
 
-This definition is illustrated in \cref{fig:identity-cause-adversary}.
+This definition is illustrated in \cref{fig:identity-proof-share-adversary}.
 
@@
   \centering
-  \includegraphics{base-identity-cause-adversary.tikz}
-  \caption{\label{fig:identity-cause-adversary}%
-    An overview of the base identity--cause adversary model.
+  \includegraphics{base-identity-proof-share-adversary.tikz}
+  \caption{\label{fig:identity-proof-share-adversary}%
+    An overview of the base identity--proof share adversary model.
     The protester with real identity \(P\) and witness with real identity \(W\) 
@@
 
-We find \cref{base-identity-cause-adversary} suitable when the protester and witness both move in a crowd and there is no way for the witness to decide exactly with whom he or she communicates with.
+We find \cref{base-identity-proof-share-adversary} suitable when the protester and witness both move in a crowd and there is no way for the witness to decide exactly with whom he or she communicates with.
 However, in some situations this might not be the case, \eg the crowd is not dense.
@@
 
-\begin{definition}[Stronger identity--cause adversary]%
-  \label{stronger-identity-cause-adversary}
-  The situation is the same as in \cref{base-identity-cause-adversary}, but now the 
+\begin{definition}[Stronger identity--proof share adversary]%
+  \label{stronger-identity-proof-share-adversary}
+  The situation is the same as in \cref{base-identity-proof-share-adversary}, but now the 
   witness \(W\) learns the protester \(P\)'s identity.
@@
 
-\begin{definition}[Strongest identity--cause adversary]%
-  \label{strongest-identity-cause-adversary}
-  Everything is the same as in \cref{stronger-identity-cause-adversary}, except that now \(S\) also learns \(P\)'s identity.
+\begin{definition}[Strongest identity--proof share adversary]%
+  \label{strongest-identity-proof-share-adversary}
+  Everything is the same as in \cref{stronger-identity-proof-share-adversary}, except that now \(S\) also learns \(P\)'s identity.
 \end{definition}
-
-\paragraph{The identity--location adversary}
-
-The players are still the same, but now the adversary controls other players.
-In particular, the adversary controls the storage \(S\).
-
-\begin{definition}[Base identity--location adversary]%
-  \label{base-identity-location-adversary}
-  The adversary controls \(S\).
-  The witness \(W\) and the protester \(P\) communicate.
-  They learn some protocol data \(d_{P,W}(P, W, l)\) and the time it took 
-  place, \(t_{P,W}\).
-  \begin{description}
-    \item[The witness case:]
-      The witness later communicates with \(S\), in which \(S\) only learns 
-      \(f(d_{P,W}(P, W, l))\), for some function \(f\), and the time it 
-      happened, \(t_{W,S}\).
-      The adversary wins if he can link \(W\) and \(l\).
-    \item[The protester case:]
-      The protester later communicates with \(S\), in which \(S\) only learns 
-      \(g(d_{P,W}(P, W, l))\), for some function \(g\), and the time it 
-      happened, \(t_{P,S}\).
-      The adversary wins if he can link \(P\) and \(l\).
-  \end{description}
-\end{definition}
-
-\Cref{fig:identity-location-adversary} illustrates the roles and relations.
-
-\begin{figure}
-  \centering
-  \includegraphics{base-identity-location-adversary.tikz}
-  \caption{\label{fig:identity-location-adversary}%
-    An overview of the base identity--location adversary model.
-    The protester with real identity \(P\) and witness with real identity \(W\) 
-    communicate and each learn only the protocol data, \(d_{P,W}(P, W, l)\), 
-    and the time it happened, \(t_{P,W}\).
-    The witness submits \(f(d_{P,W}(P, W, l))\), for some function \(f\), and 
-    the protester submits \(g(d_{P,W}(P, W, l))\), for some function \(g\), to 
-    the storage \(S\), who learns only that and the time it happened, 
-    \(t_{W,S}\) respectively \(t_{P,S}\).
-    Only the storage \(S\) is controlled by the adversary \(A\).
-  }
-\end{figure}
-
-The base rationale is the same as for \cref{base-identity-cause-adversary}, the 
-witness \(W\) can submit to \(S\) over an anonymous channel, such as Tor~\cite{Tor}.
-Anyone who is in the same location will learn that \(W\) was present, we want 
-to prevent anyone \emph{not present} to learn that \(W\) was there --- hence we 
-do not consider the protester as part of the adversary, only \(S\).
-Analogous to the identity--cause adversary, we conclude with the strongest 
-identity--location adversary.
-
-\begin{definition}[Strongest identity--location adversary]%
-  \label{strongest-identity-location-adversary}
-  Things are the same as in \cref{base-identity-location-adversary}, except 
-  that \(S\) learns the witness' and protester's identities \(W\) and \(P\), in 
-  the respective cases.
-\end{definition}

### 2018-11-21 paper/adversary-model.tex
Renames identity--cause -> identity--proof-share, removed location adv
Aligns formal adversary model with the rest

@@
-\subsection{Privacy adversary}%
-\label{adversary-model-different-levels}
+\subsection{Adversary model}%
+\label{formal-adversary-model}
 
-We provide one system model with two possible adversaries: one who tries to link a protester's real identity (\(P\)) to a protest proof-share (\(\cid\)) and one 
-that aims at linking a protester's or a witness's real identity (\(P\), respectively \(W\)), to a location (\(l\)).
-We also define varying strengths of each adversary.
+We now provide a concretely defined system and adversary model.
+We give three definitions, each defines an adversary with increasingly stronger 
+capabilities (\ie more auxiliary information).
 
-\paragraph{The identity--proof share linking adversary}
+There are three players: the protest participant (with identity) \(P\), a 
+witness (with identity) \(W\) and the storage \(S\).
+The adversary \(A\) controls \(W\) and \(S\).
+This is illustrated in \cref{fig:base-adversary}.
 
-There are three players: the protest participant (with identity) \(P\), a witness (with identity) \(W\) and the storage \(S\).
-The adversary \(A\) controls \(W\) and \(S\).
+\begin{figure}
+  \centering
+  \includegraphics{base-adversary.tikz}
+  \caption{\label{fig:base-adversary}%
+    An overview of the base adversary model.
+    The protester with real identity \(P\) and witness with real identity \(W\) 
+    communicate.
+    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
+    happened, \(t_{P,W}\).
+    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
+    the storage \(S\), who records the time it happened, \(t_{P,S}\).
+    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
+    \(A\).
+  }
+\end{figure}
 
-\begin{definition}[Base identity--proof share adversary]%
-  \label{base-identity-proof-share-adversary}
+\begin{definition}[Base adversary]%
+  \label{base-adversary}
   The protester \(P\) and the witness \(W\) communicate.
-  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when it happened 
-  \(t_{P,W}\)\footnote{%
+  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
+  communication occurred \(t_{P,W}\)\footnote{%
     Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
-    directly, only if those appear in the data \(d_{P,W}(\cid, P)\).
+    directly from the communication medium, only if those appear in the data 
+    \(d_{P,W}(\cid, P)\).
   }.
@@
 
-This definition is illustrated in \cref{fig:identity-proof-share-adversary}.
+The base adversary (\cref{base-adversary}) represents an adversary that has no 
+access to auxiliary information, \eg inferences that can be done from the 
+communication layer, which means that it has only the protocol data at its 
+disposal.
 
-\begin{figure}
-  \centering
-  \includegraphics{base-identity-proof-share-adversary.tikz}
-  \caption{\label{fig:identity-proof-share-adversary}%
-    An overview of the base identity--proof share adversary model.
-    The protester with real identity \(P\) and witness with real identity \(W\) 
-    communicate and each learn only the protocol data, \(d_{P,W}(\cid, P)\), 
-    and the time it happened, \(t_{P,W}\).
-    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
-    the storage \(S\), who learns only that and the time it happened, 
-    \(t_{P,S}\).
-    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
-    \(A\).
-  }
-\end{figure}
+We find \cref{base-adversary} suitable when the protester and witness both move 
+in a crowd and there is no way for the witness to decide exactly with whom he 
+or she communicates with.
+However, in some situations this might not be the case: \Eg if the crowd is not 
+dense the witness will likely see the face of the protester.
+If the witness is controlled by the adversary, then it is likely that the 
+witness can capture a picture of the face, which can be turned into an identity 
+through face recognition.
+There are various such scenarios leading to the adversary learning the 
+protester's identity, we capture this by the following definition.
 
-We find \cref{base-identity-proof-share-adversary} suitable when the protester and witness both move in a crowd and there is no way for the witness to decide exactly with whom he or she communicates with.
-However, in some situations this might not be the case, \eg the crowd is not dense.
-In these situations the witness will likely see the face of the protester.
-We capture this by the following definition.
-
-\begin{definition}[Stronger identity--proof share adversary]%
-  \label{stronger-identity-proof-share-adversary}
-  The situation is the same as in \cref{base-identity-proof-share-adversary}, but now the 
-  witness \(W\) learns the protester \(P\)'s identity.
+\begin{definition}[Deanonymizing-witness adversary]%
+  \label{deanonymizing-witness-adversary}
+  The situation is the same as in \cref{base-adversary}, but now the witness 
+  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
   (\(P\) will also learn \(W\)'s identity.)
@@
 
-\begin{definition}[Strongest identity--proof share adversary]%
-  \label{strongest-identity-proof-share-adversary}
-  Everything is the same as in \cref{stronger-identity-proof-share-adversary}, except that now \(S\) also learns \(P\)'s identity.
+\begin{definition}[Deanonymizing adversary]%
+  \label{deanonymizing-adversary}
+  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
+  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
 \end{definition}

### 2018-11-22 paper/adversary-model.tex
Changes adversary definitions to A{1,2,3} form

@@
 
-\begin{definition}[Base adversary]%
-  \label{base-adversary}
+\begin{adversaries}
+\item\label{base-adversary}
+  \emph{Base adversary}:
   The protester \(P\) and the witness \(W\) communicate.
@@
   do, but can additionally correlate what he learns from \(W\) and \(S\).
-\end{definition}
+\end{adversaries}
 
@@
 
-\begin{definition}[Deanonymizing-witness adversary]%
-  \label{deanonymizing-witness-adversary}
+\begin{adversaries}
+\item\label{deanonymizing-witness-adversary}
+  \emph{Deanonymizing-witness adversary}:
   The situation is the same as in \cref{base-adversary}, but now the witness 
@@
   However, \(S\) still does not learn \(P\)'s identity.
-\end{definition}
+\end{adversaries}
 
-One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous communication.
+One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
+communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous 
+communication.
 However, given a strong enough adversary, such anonymous communication might not be possible.
@@
 
-\begin{definition}[Deanonymizing adversary]%
-  \label{deanonymizing-adversary}
+\begin{adversaries}
+\item\label{deanonymizing-adversary}
+  \emph{Fully deanonymizing adversary}:
   Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
   that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
-\end{definition}
+\end{adversaries}

### 2018-11-22 paper/adversary-model.tex
Merges the adversaries to one list

@@
   do, but can additionally correlate what he learns from \(W\) and \(S\).
+
+\item\label{deanonymizing-witness-adversary}
+  \emph{Deanonymizing-witness adversary}:
+  The situation is the same as in \cref{base-adversary}, but now the witness 
+  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
+  (\(P\) will also learn \(W\)'s identity.)
+  However, \(S\) still does not learn \(P\)'s identity.
+
+\item\label{deanonymizing-adversary}
+  \emph{Fully deanonymizing adversary}:
+  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
+  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
 \end{adversaries}
@@
 There are various such scenarios leading to the adversary learning the 
-protester's identity, we capture this by the following definition.
-
-\begin{adversaries}
-\item\label{deanonymizing-witness-adversary}
-  \emph{Deanonymizing-witness adversary}:
-  The situation is the same as in \cref{base-adversary}, but now the witness 
-  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
-  (\(P\) will also learn \(W\)'s identity.)
-  However, \(S\) still does not learn \(P\)'s identity.
-\end{adversaries}
+protester's identity, we capture this as 
+\cref{deanonymizing-witness-adversary}.
 
@@
 However, given a strong enough adversary, such anonymous communication might not be possible.
-We capture such a strong adversary in the following definition.
-
-\begin{adversaries}
-\item\label{deanonymizing-adversary}
-  \emph{Fully deanonymizing adversary}:
-  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
-  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
-\end{adversaries}
+We capture such a strong adversary as \cref{deanonymizing-adversary}.

### 2018-11-22 paper/adversary-model.tex
Moves description of communication out of the adversary def

--- 2018-11-22 paper/adversary-model.tex
@@
 witness (with identity) \(W\) and the storage \(S\).
-The adversary \(A\) controls \(W\) and \(S\).
+The protester \(P\) and the witness \(W\) communicate some protocol data,
+\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
+The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
+function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
+  P))\) for some function \(f\), and the time of the communication 
+(\(t_{P,S}\)).
 This is illustrated in \cref{fig:base-adversary}.
@@
     Both the witness \(W\) and storage \(S\) are controlled by the adversary 
-    \(A\).
+    \(A\) (from \cref{base-adversary}).
   }
@@
   \emph{Base adversary}:
-  The protester \(P\) and the witness \(W\) communicate.
-  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
-  communication occurred \(t_{P,W}\)\footnote{%
-    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
-    directly from the communication medium, only if those appear in the data 
-    \(d_{P,W}(\cid, P)\).
-  }.
-  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
-  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
-  communication (\(t_{P,S}\)) but not the real identities.
-  The adversary controls \(W\) and \(S\) and thus learns everything that they 
-  do, but can additionally correlate what he learns from \(W\) and \(S\).
+  The adversary controls \(W\) and \(S\); the adversary thus learns everything 
+  that they do, but can also correlate what he learns from \(W\) and \(S\).
+  \(W\) and \(S\) only learn the protocol data --- no auxiliary data.
 \end{adversaries}

### 2018-11-22 paper/adversary-model.tex

@@
   \(W\) and \(S\) only learn the protocol data --- no auxiliary data.
+
+\item\label{deanonymizing-witness-adversary}
+  \emph{Deanonymizing-witness adversary}:
+  The situation is the same as in \cref{base-adversary}, but now the witness 
+  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
+  (\(P\) will also learn \(W\)'s identity.)
+  However, \(S\) still does not learn \(P\)'s identity.
+
+\item\label{deanonymizing-adversary}
+  \emph{Fully deanonymizing adversary}:
+  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
+  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
 \end{adversaries}

### 2018-11-23 paper/adversary-model.tex
Clarifies the adversary

@@
 
-There are three players: the protest participant (with identity) \(P\), a 
-witness (with identity) \(W\) and the storage \(S\).
+There are three players: the protester (with identity) \(P\), a witness (with 
+identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
+of all proof shares, \(\pshs\)).
 The protester \(P\) and the witness \(W\) communicate some protocol data,
@@
   \emph{Base adversary}:
-  The adversary controls \(W\) and \(S\); the adversary thus learns everything 
-  that they do, but can also correlate what he learns from \(W\) and \(S\).
-  \(W\) and \(S\) only learn the protocol data --- no auxiliary data.
+  The adversary maliciously controls \(W\).
+  The adversary honest-but-curiously controls \(S\).
+  The adversary only learns the protocol data --- \ie what is sent over the 
+  channel, no auxiliary data (such as who sent it).
 
@@
   \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
-  (\(P\) will also learn \(W\)'s identity.)
-  However, \(S\) still does not learn \(P\)'s identity.
+  %(\(P\) will also learn \(W\)'s identity.)
+  However, \(S\) still learns only the protocol data, no auxiliary data.
 
@@
 
-One reason to not allow \(S\) to learn \(P\)'s identity is that for this 
-communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous 
-communication.
-However, given a strong enough adversary, such anonymous communication might not be possible.
+As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
+control the channel between \(P\) and \(S\), \eg when \(P\) uses 
+Tor~\cite{Tor}.
+The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
+\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
+jurisdiction.
+
+However, given a strong enough adversary, such anonymous communication might 
+not be possible; \eg if the adversary can do a time-correlation attack.
 We capture such a strong adversary as \cref{deanonymizing-adversary}.

### 2018-11-27 paper/conclusions.tex
fixes some PRIVO leftovers

--- 2018-11-13 paper/conclusions.tex
@@
 
-In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
+In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
 Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
 To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
-Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
+Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
 }
-With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
+With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
 

### 2018-11-27 paper/privacy-analysis.tex

--- 2018-08-14 paper/analysis-security.tex
@@
-\section{Security and privacy analysis}%
-\label{SecurityAnalysis}
-
-\subsection{Individual and universal verifiability}%
-\label{analysis-individual}%
-\label{analysis-universal}
-
-\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify that their participation proofs (\ie proof shares) are indeed included in the count computed.
-As all proof shares (\ie \(\cid, \pid, \wid, t_s, t_s', t_e, t_e', l, \pi_\pid, \pi_{\wid}\)) are committed to the blockchain and available from a public and permanent storage (see \cref{fig:ProtocolOverview}).
-Thus, Alice and Bob can simply check that all of their proof shares are indeed there and the security of individual verifiability depends on the properties of the blockchain and storage.
-
-\Cref{UniversalVerif} requires also that anyone can check the result and that all participation proofs counted are legitimate.
-As the proof shares are committed and stored publicly, anyone can download them, verify eligibility (\ie verify \(\pi_\pid, \pi_{\wid}\)) the proofs and count them.
-As for individual verifiability, the security of universal verifiability is reduced to the properties of the blockchain and storage but also the eligibility verification, which we will discuss next.
-
-\subsection{Eligibility verifiability}
-\label{analysis-eligibility}
-
-\Cref{EligibilityVerif} states that anyone must be able to determine the authenticity of the relevant attributes of the data.
-In \PRIVO, we have several attributes that must be verifiable: the time of creation (\ie, temporal eligibility), the physical location of \(\sk_P\) at creation (\ie, spatial eligibility), recognition of two proofs originating from the same person (\ie, one-proof-per-person eligibility) and that the proof is indeed designated for the event (\ie, designated-event eligibility).
-We will now analyze these properties.
-
-\paragraph{Temporal eligibility}
-\label{analysis-temporal}
-
-\Cref{TemporallyRelated} ensures freshness, as Alice cannot simply resubmit an old proof as a new one.
-In general, freshness requires the prover to respond to an unpredictable challenge.
-The challenge here is to include the hash value at the head of the blockchain at the time of the proof's creation (included as \(t_s\) and \(t_s'\) in the proof share).
-As it is the case in the construction of blockchains, the hash value at the head depends on the previous blocks in the chain.
-Thus, the predictability of \(t_s\) depends on the predictability of the blocks, which depends on the predictability of the transactions and the nonce needed by the miner.
-In turn, the transactions depend on the signatures made by the signing keys corresponding to the used transactions.
-If these were predictable, the adversary could conduct arbitrary transactions in the blockchain --- which is assumed to be hard by design.
-Thus, Alice can predict \(t_s\) only with negligible probability, as \(t_s\) must have been published on the blockchain before being included in her proof share.
-
-According to \cref{TemporallyRelated}, we must also prove that a proof share has not been created after a certain time.
-Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
-The hash values of the proof shares are committed to the blockchain, which means that there is a negligible probability that they were created after that.
-Alice would have to choose a value \(y\) in the domain of the hash function \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) is a valid proof.
-If \(\Hash\) is collision resistant, finding \emph{any} preimage is hard.
-
-\paragraph{Linkability}
-\label{analysis-linkability}
-
-\Cref{CountOnce} is required to prevent Sybil attacks, in the sense that Alice cannot provide two participation proofs for specific protest and thus be counted twice.
-This possibility is prevented by the use of \(\pid\).
-Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
-Due to the deterministic property of \(\ACprf\), Alice must produce a new key \(\sk_P'\) and make the witness accept in the protocol
-\begin{multline*}
-\PK\mleft\{ (\sk_P') : \pid' = \ACprf[_{\sk_P'}][\cid] \quad \land \mright. \\
-    \sigma_P'' = \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
-\end{multline*}
-while she does not know a valid signature on \(\sk_P'\).
-As a consequence, this is reduced to the security of the \(\AC\) scheme and how often Alice can get a valid signature on a secret key from the \ac{CA}.
-
-\paragraph{Spatial eligibility}
-\label{analysis-spatial}
-
-\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
-To realize this, we have to ensure that Alice cannot forge witness signatures, which is realized by using the same linkability mechanism as above.
-To forge a witness signature, Alice must produce a \(\wid'\) such that
-\begin{multline*}
-  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
-    \begin{aligned}
-      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
-      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
-    \end{aligned} \\
-      (\pid, \wid', t_s, t_s', l),
-\end{multline*}
-while not knowing a signature on the secret key \(\sk_W'\).
-Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
-The latter could be done if she can find people willing to collude.
-However, due to the assumptions done in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course this two approach could be combine).
-Remark that Alice can produce one witness signature for herself, since she has access to her own \(\sk_P\), but no more.
-
-\paragraph{Designated protest}
-\label{analysis-designated}
-
-\Cref{DesignatedEvent} is to prevent Alice (or someone else) from reusing the same proof (or proof share) for another event.
-This possibility is prevented through the use of \(\cid\) in the proof shares.
-To reuse the proof share for another protest, with a different manifesto, one must find a second preimage \(\mfst'\) such that \(\cid = \Hash[\mfst] = \Hash[\mfst']\).
-
-There exists another case of collision that we must prevent.
-Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
-Now, if Alice construct a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
-This means that we must separate the mechanisms used for participating and witnessing.
-The protocol achieves this by the fact that \[
-  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
-\]
-does not include \(\cid\) whereas \[
-  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
-\]
-does.
-Thus, the verification process differs for the two types of proofs.
-(An alternative approach would have been to compute them differently, for instance \(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = g_T^{1/(\sk+x+1)}\).)
-
-%\paragraph{Forging proof shares}
-%
-%\daniel{This is work-in-progress.}
-%Alice can attempt to forge the full proof directly, \ie
-%\begin{multline*}
-%\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
-%  \begin{aligned}
-%    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
-%    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
-%  \end{aligned} \\
-%    (\cid, \pid', \wid', t_s, t_s', l)
-%\end{multline*}
-%and consequently
-%and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).
-%
-
 \subsection{Privacy}

### 2018-11-27 paper/protocol.tex
Removes math details in protocol now in anon-cred section

@@
 During the setup phase, the \ac{CA} creates all the needed keys.
-First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
-Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
-Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
-  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
-    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
-}.
-Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
-The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).
+The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
+  \ACsetup\) (see \cref{CLsignAlg}).
 
@@
 association between a particular key and the identity of the participant.
-The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
-The participant acts as prover and the \ac{CA} as verifier while they perform 
-the following \ac{ZKPK} protocol:
-\[
-  \PK[k,r][M = g^k Z^r].
-\]
-If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
-Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
-  C = A^x M^{axy})\) and sends it to the participant.
-The participant then verifies that the following equations hold:
-\begin{align*}
-  A &\neq 1 \\
-  e(g, B) &= e(Y, A) \\
-  e(g, Z_B) &= e(Z, B) \\
-  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
-\end{align*}
+The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
+\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
+\cref{CLacSigAlg}).
 Upon success, the participant sets \(\sk = (\sigma, k, r)\).
@@
 Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
-\cref{fig:ProofFig,fig:ProtocolOverview}).
-More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
-The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
+\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
+The protester should also receive a time-correlated random value from the 
+time-stamping service, \(t_s\gets \TSget\).
 
@@
     \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
-The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
-  \tilde\sigma = (\tilde A = A^{r_1},
-                  \tilde B = B^{r_1},
-                  \tilde Z_B = Z_B^{r_1},
-                  \hat C = C^{r_1 r_2}).
-\) 
-Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
-The protester sends \((\pid, \tilde\sigma)\) to the witness.
-The witness verifies that
-\begin{align*}
-  \tilde A          &\neq 1 \\
-  e(g, \tilde B)    &= e(Y, \tilde A) \\
-  e(g, \tilde Z_B)  &= e(Z, \tilde B).
-\end{align*}
-Both the protester and the witness compute
-\begin{align*}
-  v &= e(g, \hat C) \\
-  v_x &= e(X, \tilde A) \\
-  v_{xy} &= e(X, \tilde B) \\
-  v_{xy}' &= e(X, \tilde Z_B).
-\end{align*}
-Afterwards, they run the following \ac{PPK} with the protester as the prover 
-and the witness as the verifier:
-\begin{multline*}
-  \mleftright
-  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
-    \pid = g_T^{1/(k_P+\cid)} \right\}.
-\end{multline*}
-in which \(r' = 1/r_2\).
-We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
-Afterwards, the \ac{PK} can be designed as follows.
-(Remember that this \ac{PK} should be run as the \ac{PPK} in 
-\cref{DB-anon-cred} and repeated multiple times to achieve security.)
-The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
-sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
-  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
-The witness replies with a challenge \(c\).
-Afterwards, the protester computes
-\begin{align*}
-  s_k &= -ck + r_k, \\
-  s_r &= -cr + r_r, \\
-  s_{r'} &= cr' + r_{r'}
-\end{align*}
-and forwards them to the witness.
-The witness checks whether
-\begin{align*}
-  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
-    s_r}, \\
-  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
-  \pid^{s_k}.
-\end{align*}
-If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
-  = g_T^{1/(k_W+\pid)}\) (as above).
-Following this, the witness returns \((\wid, t_s', l)\) to the protester.
-As a consequence, both the protester and the witness have the tuple \(\psh = 
-  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
-protester (\cref{fig:ProofFig}).
+In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
+the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+
+The protester sends \(\pid\) to the witness.
+Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
+    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
+Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
+If the protocol succeeds, the witness will compute \(\wid \gets 
+  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
 

### 2018-11-27 paper/protocol.tex
Introduces \corr for the proof of correctness of \pid, \wid

@@
 The remaining operations are not time critical.
-The protester computes \iac{NIZK} proof \(\pi_{\pid}\), which shows the 
+
+The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
 correctness of \(\pid\).
@@
 \begin{multline*}
-  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
+  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
     \begin{aligned}
@@
 \end{multline*}
-Finally, the protester uploads the tuple \[  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})\] for permanent storage.
+Finally, the protester uploads the tuple \[
+  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
+\] for permanent storage.
 
@@
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
-\(\pi_{\wid}\) as follows:
+\(\corr_{\wid}\) as follows:
 \begin{multline*}
-  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
+  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
     \begin{aligned}
@@
 \end{multline*}
-Finally, the witness uploads the tuple \[ \psh_W = (\cid, \pid, \wid, t_s, 
-  t_s', t_e', l, \pi_{\wid}) \] for permanent storage.
+Finally, the witness uploads the tuple \[
+  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
+\] for permanent storage.
 
@@
   \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
-  t_e^{\prime   (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})
-\] for each protester \(j\) from the ledger, verify \(\prf_{\pid_j}^{(i)}\), 
-\(\prf_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime 
-      (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
+  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
+\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
+\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
+    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
 \(l_i\subseteq  l\).

### 2018-11-27 paper/intro.tex
new, short abstract; adds explanation of protest as event instantiation

--- 2018-11-16 paper/intro.tex
@@
 
-\emph{Context.} 
+%\emph{Context.}
+
+While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper.
+We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
 Consider the following scenario.

### 2018-11-27 paper/intro.tex
shortens conclusions, updates outline

@@
 Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
-We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
-Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
-\daniel{Check that this is true before publication.} 
-and formally verify it using Tamarin~\cite{TamarinDB}.
-\seb{we need to be careful about the above sentence}
+We then formalize the notion of protest and the desired verifiability and privacy properties in \cref{definitions}, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
+% Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
+% We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
+% \daniel{Check that this is true before publication.} 
+% and formally verify it using Tamarin~\cite{TamarinDB}.
+% \seb{we need to be careful about the above sentence}
 %This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then in\cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
+Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}) and performance (\cref{PerformanceAnalysis}) .
 Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.

### 2018-11-27 paper/protocol.tex
removes informal adversary model, explains verification and counting, removes old strength function description, adds props reference to assumed DBAC

--- 2018-11-16 paper/protocol.tex
@@
 
-While there are various ways for verifying the participation count, hereafter, 
-we will detail the two suggested just after \cref{DefParticipationCount}.
-In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
-Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
-In the second approach, we trust specific witnesses, but no others.
-In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
-It is the strength function \(\str\) of \cref{DefParticipationCount} that 
-differ in the two cases.
-We will first give the procedure and then how to construct the two different 
-strength functions.
+% While there are various ways for verifying the participation count, hereafter, 
+% we will detail the two suggested just after \cref{DefParticipationCount}.
+% In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
+% Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
+% In the second approach, we trust specific witnesses, but no others.
+% In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
+% It is the strength function \(\str\) of \cref{DefParticipationCount} that 
+% differ in the two cases.
+% We will first give the procedure and then how to construct the two different 
+% strength functions.
 
@@
 
-In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
-\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
+% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
+% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
 
-In the case \emph{with} trusted witnesses, each trusted witness must inform the 
-verifier of which proof shares that he or she has signed, \eg by giving a list 
-of all such proof shares or digitally sign each proof share\footnote{%
+In the case of trusted witnesses, each such trusted witness must
+publish or otherwise inform the 
+verifier of which proof shares she has signed, \eg by giving a list 
+of all such proof shares or digitally signing each proof share\footnote{
  To achieve witness privacy in this situation, one could employ a group or 
@@
 }.
-Then the verifier can define \[
-  \str[\prf_{\pid_j, P}] = \begin{cases}
-    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
-      share} \\
-    0 & \text{otherwise}
-  \end{cases}
-\] and sets \(\theta = 1\).
+
+Note that anyone who does the counting can choose the eligibility
+criteria (time interval, location, number of regular or trusted
+witnesses, who is considered to be a trusted witness) for their count
+and as long as these are published along with the result, any one can
+verify the correctness under those criteria.
+
+% Then the verifier can define \[
+%   \str[\prf_{\pid_j, P}] = \begin{cases}
+%     1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
+%       share} \\
+%     0 & \text{otherwise}
+%   \end{cases}
+% \] and sets \(\theta = 1\).

### 2018-11-27 paper/adversary-model.tex
Clarifies adversary model
Adapts the adversary to "not make things worse"
We want to see if we make things worse, thus we don't consider the
deanonymizing witness since in that situation the adversary can identify
and arrest all participants anyway.

@@
     Both the witness \(W\) and storage \(S\) are controlled by the adversary 
-    \(A\) (from \cref{base-adversary}).
+    \(A\) (from \cref{in-system-adversary}).
   }
@@
 \begin{adversaries}
-\item\label{base-adversary}
-  \emph{Base adversary}:
+\item\label{in-system-adversary}
+  \emph{In-system adversary}:
   The adversary maliciously controls \(W\).
@@
   The adversary only learns the protocol data --- \ie what is sent over the 
-  channel, no auxiliary data (such as who sent it).
+  channel, no auxiliary data\footnote{%
+    By auxiliary data we mean any data outside of the protocol.
+    \Eg meta-data such as who is on the other side of the channel.
+  }
 
-\item\label{deanonymizing-witness-adversary}
-  \emph{Deanonymizing-witness adversary}:
-  The situation is the same as in \cref{base-adversary}, but now the witness 
-  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
-  %(\(P\) will also learn \(W\)'s identity.)
-  However, \(S\) still learns only the protocol data, no auxiliary data.
+\item\label{deanonymizing-storage-adversary}
+  \emph{National eavesdropping adversary}:
+  The situation is the same as in \cref{in-system-adversary}, but now the storage 
+  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
+  However, \(W\) still learns only the protocol data, no auxiliary data.
 
-\item\label{deanonymizing-adversary}
-  \emph{Fully deanonymizing adversary}:
-  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
-  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
+%\item\label{deanonymizing-witness-adversary}
+%  \emph{Deanonymizing-witness adversary}:
+%  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
+%  that now \(W\) also learns \(P\)'s identity from an auxiliary channel.
 \end{adversaries}
 
-The base adversary (\cref{base-adversary}) represents an adversary that has no 
-access to auxiliary information, \eg inferences that can be done from the 
-communication layer, which means that it has only the protocol data at its 
-disposal.
+The in-system adversary (\cref{in-system-adversary}) represents an adversary 
+that has no access to data from outside the system, \eg inferences that can be 
+done from the communication layer (\eg IP-addresses mapped to physical 
+identities), which means that it has only the protocol data at its disposal.
 
-We find \cref{base-adversary} suitable when the protester and witness both move 
-in a crowd and there is no way for the witness to decide exactly with whom he 
-or she communicates with.
-However, in some situations this might not be the case: \Eg if the crowd is not 
-dense the witness will likely see the face of the protester.
-If the witness is controlled by the adversary, then it is likely that the 
-witness can capture a picture of the face, which can be turned into an identity 
-through face recognition.
-There are various such scenarios leading to the adversary learning the 
-protester's identity, we capture this as 
-\cref{deanonymizing-witness-adversary}.
+We find \cref{in-system-adversary} suitable when the protester and witness both 
+move in a crowd and there is no way for the witness to decide exactly with whom 
+he or she communicates with.
+(The protesters could also simply wear masks.)
+We consider this a fair model for our purposes: if the adversary can 
+deanonymize the protesters \emph{at the physical location} and thus arrest 
+them, the adversary can do that independently of whether the protesters use our 
+protocol or not --- thus our protocol cannot make things worse in such a 
+situation.
 
-As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
-control the channel between \(P\) and \(S\), \eg when \(P\) uses 
-Tor~\cite{Tor}.
+As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
+even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
+such as Tor~\cite{Tor}.
 The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
-\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
-jurisdiction.
+\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
+so the adversary cannot control \(S\), but since \(S\) provides public access 
+the adversary can (possibly constantly) query it and learn things with little 
+delay.
+However, it might not be realistic to assume that the channel between \(P\) and 
+\(S\) is unobservable for the adversary.
+\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
+thus perform time-correlation attacks on messages on the network and events 
+observed through \(S\).
+We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
+the identity of the protester.
 
-However, given a strong enough adversary, such anonymous communication might 
-not be possible; \eg if the adversary can do a time-correlation attack.
-We capture such a strong adversary as \cref{deanonymizing-adversary}.
+%However, in some situations this might not be the case: \Eg if the crowd is not 
+%dense the witness will likely see the face of the protester.
+%If the witness is controlled by the adversary, then it is likely that the 
+%witness can capture a picture of the face, which can be turned into an identity 
+%through face recognition.
+%There are various such scenarios leading to the adversary learning the 
+%protester's identity, we capture this as 
+%\cref{deanonymizing-witness-adversary}.

### 2018-11-28 paper/adversary-model.tex
Points out that the adversary is allowed to submit to S
This is for verifiability.

@@
 delay.
-However, it might not be realistic to assume that the channel between \(P\) and 
-\(S\) is unobservable for the adversary.
+Note that the adversary is also allowed to submit data to \(S\) for storage, 
+just like everyone else.
+
+\Cref{deanonymizing-storage-adversary} is a stronger adversary who also can 
+observe the channel between \(P\) and \(S\).
 \Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
 thus perform time-correlation attacks on messages on the network and events 
-observed through \(S\).
+observed from \(S\).
 We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
-the identity of the protester.
+the identity of \(P\).
 

### 2018-11-28 paper/adversary-model.tex
harmonizing submittable

--- 2018-11-23 paper/adversary-model.tex
@@
 We now provide a concretely defined system and adversary model.
-We give three definitions, each defines an adversary with increasingly stronger 
+We give three definitions, each defining an adversary with increasingly stronger 
 capabilities (\ie more auxiliary information).
 
-There are three players: the protester (with identity) \(P\), a witness (with 
-identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
-of all proof shares, \(\pshs\)).
-The protester \(P\) and the witness \(W\) communicate some protocol data,
-\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
-The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
-function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
-  P))\) for some function \(f\), and the time of the communication 
-(\(t_{P,S}\)).
+There are three players: the protest participant (with identity) \(P\), a 
+witness (with identity) \(W\) and the storage \(S\).
+The adversary \(A\) controls \(W\) and \(S\).
 This is illustrated in \cref{fig:base-adversary}.
@@
     Both the witness \(W\) and storage \(S\) are controlled by the adversary 
-    \(A\) (from \cref{base-adversary}).
+    \(A\).
   }
@@
 
-\begin{adversaries}
-\item\label{base-adversary}
-  \emph{Base adversary}:
-  The adversary maliciously controls \(W\).
-  The adversary honest-but-curiously controls \(S\).
-  The adversary only learns the protocol data --- \ie what is sent over the 
-  channel, no auxiliary data (such as who sent it).
-
-\item\label{deanonymizing-witness-adversary}
-  \emph{Deanonymizing-witness adversary}:
-  The situation is the same as in \cref{base-adversary}, but now the witness 
-  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
-  %(\(P\) will also learn \(W\)'s identity.)
-  However, \(S\) still learns only the protocol data, no auxiliary data.
-
-\item\label{deanonymizing-adversary}
-  \emph{Fully deanonymizing adversary}:
-  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
-  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
-\end{adversaries}
+\begin{definition}[Base adversary]%
+  \label{base-adversary}
+  The protester \(P\) and the witness \(W\) communicate.
+  Each learns only the protocol data \(d_{P,W}(\cid, P)\) and when the 
+  communication occurred \(t_{P,W}\)\footnote{%
+    Specifically, they do \emph{not} learn the real identities \(P\) and \(W\) 
+    directly from the communication medium, only if those appear in the data 
+    \(d_{P,W}(\cid, P)\).
+  }.
+  The protester \(P\) communicates with \(S\), in which \(S\) only learns 
+  \(f(d_{P,W}(\cid, P))\), for some function \(f\), and the time of the 
+  communication (\(t_{P,S}\)) but not the real identities.
+  The adversary controls \(W\) and \(S\) and thus learns everything that they 
+  do, but can additionally correlate what he learns from \(W\) and \(S\).
+\end{definition}
 
@@
 There are various such scenarios leading to the adversary learning the 
-protester's identity, we capture this as 
-\cref{deanonymizing-witness-adversary}.
+protester's identity, we capture this by the following definition.
 
-As to \(S\), \cref{base-adversary} corresponds to an adversary who cannot 
-control the channel between \(P\) and \(S\), \eg when \(P\) uses 
-Tor~\cite{Tor}.
-The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
-\(S\) learns it, \eg when \(S\) is operated outside the adversary's 
-jurisdiction.
+\begin{definition}[Deanonymizing-witness adversary]%
+  \label{deanonymizing-witness-adversary}
+  The situation is the same as in \cref{base-adversary}, but now the witness 
+  \(W\) learns the protester \(P\)'s identity from an auxiliary channel.
+  (\(P\) will also learn \(W\)'s identity.)
+  However, \(S\) still does not learn \(P\)'s identity.
+\end{definition}
 
-However, given a strong enough adversary, such anonymous communication might 
-not be possible; \eg if the adversary can do a time-correlation attack.
-We capture such a strong adversary as \cref{deanonymizing-adversary}.
+\daniel{The deanonymizing witness captures: a1, a4, a5. (See Simon's notes on 
+  Slack.)}
+
+One reason to not allow \(S\) to learn \(P\)'s identity is that for this communication \(P\) has options, such as Tor~\cite{Tor}, for anonymous communication.
+However, given a strong enough adversary, such anonymous communication might not be possible.
+We capture such a strong adversary in the following definition.
+
+\begin{definition}[Deanonymizing adversary]%
+  \label{deanonymizing-adversary}
+  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
+  that now \(S\) also learns \(P\)'s identity from an auxiliary channel.
+\end{definition}
+
+\daniel{The deanonymizing adversary additionally captures: a2, a3 (\ie a1, a2, 
+  a3, a4, a5).}

### 2018-11-28 paper/intro.tex
harmonizing submittable

@@
 The paper is organized as follows.
-First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
-We then formalize the notion of protest and the desired verifiability and privacy properties in \cref{definitions}, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
+First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}).
+We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
 % Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
@@
 %This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}) and performance (\cref{PerformanceAnalysis}) .
-Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
+After that, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks (\cref{Protocol}), before analyzing its security and privacy (\cref{SecurityAnalysis}), and its performance (\cref{PerformanceAnalysis}).
+Finally, we discuss our assumptions and results (\cref{Discussion}) and give our conclusions (\cref{Conclusion}).
 %\sonja{add (sub) sections for performance and verification}

### 2018-11-28 paper/protest-model.tex
harmonizing submittable

@@
 }.
-These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
+These rallies were all in the same location in the capital and repeated every weekend for a few weeks.
 The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
@@
 \begin{definition}[Subprotest, Protest]\label{DefProtest}
-  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).
-  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
+  A \emph{subprotest} \(p = (\cid, t, l)\) is a tuple in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).\\
+  A \emph{protest} \(\prtst\) is the set of subprotests sharing the same \(\cid\).
 \end{definition}
@@
 
-Our protocol relies on \emph{witnesses} to certify and associate the proof to the location by creating a \emph{proof share}.
+Our protocol relies on \emph{witnesses} to certify and associate the proof to the time and location by creating a \emph{proof share}.
 A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
@@
 act as witness for other protesters.)
-All the proof shares together form the participation proof.
+Then, the set of all \emph{eligible} proof shares forms the participation proof of a protester.
 
@@
 
-\begin{definition}[Proof share]%
+\begin{definition}[Eligible proof share]%
   \label{DefProofShare}\label{DefProofShares}
@@
   \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
-  We say that \(\psh\) is part of a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
+  Furthermore, we say that \(\psh\) is \emph{eligible} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
   \(\psh \sqsubseteq \sprtst\).
-  We define \(\pshs\) as the set of all proof shares.
+
 \end{definition}
 
-A subset of the proof shares forms a participation proof for a protester.
-We will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
+%A subset of the proof shares forms a participation proof for a protester.
+We denote by \(\pshs\) the set of all proof shares,
+and we will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
 \begin{multline*}
@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  A \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
+  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
   set
@@
   \end{equation}
-  of all proof shares with the same protester and protest identifiers, time interval \(t\) and location \(l\) within those of the protest (\ie any subprotest).
+  of all proof shares with the same protester and protest identifiers, and eligible for any subprotest $p$ of $\prtst$.
   We denote by \(\prfs\) the set of all proofs.
@@
   \label{DefParticipationCount}
-  We define the \emph{participation count} of a protest \(\prtst\) (as in \cref{DefParticipationProof}) as the cardinality 
-  \(|\prfs_{P}^{\str,\theta}|\) of the set of participation proofs \[
-    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,P} \in \prfs \mid
-      \str(\prf_{i,P})\geq \theta \right\}
-  \] for some strength function \(\str\colon \powerset(\pshs)\to \RR_+\) and a 
-  threshold \(\theta\).
+  We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
+  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{valid} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
+    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
+      \str(\prf_{i,\prtst})\geq \theta \right\}
+  \] with \(\str\colon \powerset(\pshs)\to \RR_+\) and  \(\theta \in \RR_+\).
 \end{definition}
@@
 weights \(\omega_i\) being the trust in the witness corresponding to that proof 
-share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
+share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
 to accept a participant as valid.
-One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
+One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
 Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
@@
 
-\simon{check the notation in the weights formula is consistent, check that the description in section V corresponds}
-\daniel{Fixed formula, math mode; didn't check Section V though.}
+\simon{check that the description in section V corresponds}

### 2018-11-28 paper/system-model.tex
harmonizing submittable

@@
-\section{System and adversary model}%
+\section{System model and requirements}%
 \label{system-model}
 
-To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.
+To set the stage, we will now describe our system model including
+assumptions and a summary of the desired properties for crowd
+counting% and the adversary model
+.
 
@@
 
-\subsection{Desired properties}
+\subsection{Desired properties}%
+\label{desired-properties}
 
-We note that, in general terms, protesting is very similar to petitions, which 
-in turn are similar to voting.
-Indeed, all three situations correspond to situations in which many individuals express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
+We note that, in general terms, protesting is very similar to signing petitions, which 
+in turn is similar to voting.
+Indeed, all three practices correspond to situations in which many individuals express their opinion, which can be sensitive (\eg be a cause for discrimination or persecution), and thus need to be protected.
+Hence the desire for similar properties of verification and privacy for a protest as for voting.
 
-We draw inspiration from the three traditionally desired properties for verifiability for voting:
+We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
 \daniel{Find a new ref for voting verifiability properties, Douglas commented 
@@
 In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must 
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
+The eligibility requirement is slightly different as for protests it must also
 include temporal\footnote{%
@@
 
-Coercion resistance is not possible to achieve for protests.
+%Coercion resistance is not possible to achieve for protests.
+Coercion resistance in voting typically relies on physical isolation
+(\eg private voting boots), including for digital systems, 
+and that is by definition not possible for public events.
 For instance, someone could simply physically bring Alice to a protest against her will.
-Receipt freeness, while appealing at first glance, is not desirable (probably 
-not possible) in our context since this will conflict with verifiability: in 
-contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
+As for receipt freeness, while
+desirable \emph{in itself}, it implies a conflict with verifiability in our context:
+%appealing at first glance, is not desirable (probably not possible)
+%in our context since this will conflict with verifiability:
+in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
 cause of the protest) implies receipt freeness for \emph{that} the voter voted 
-(\ie the protester was there), which conflicts with verifiability.
+(\ie the protester was there), which would make verifiability impossible.
 
-Thus, in our context the crucial property is therefore privacy.
+Therefore in our context, the crucial property is  vote privacy.
 More precisely, for the protester we want unlinkability (from the adversary's 
@@
 Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (\eg 
-from a different protest).
+auxiliary knowledge, she should not be able to link it to another proof (from a different protest).
 
-\subsection{Adversary model}%
-\label{adversary-model}
+% \subsection{Adversary model}%
+% \label{adversary-model}
 
-We consider two types of adversaries: 
-\begin{enumerate*} 
-\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
-messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
-\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
-\end{enumerate*}
+% We consider two types of adversaries: 
+% \begin{enumerate*} 
+% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
+% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
+% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
+% \end{enumerate*}

### 2018-11-28 paper/verifiability-analysis.tex
Clarifies adversary model

@@
 the ledger and storage (\(\TS\), \cref{timestamp}).
-(As these are the main properties of distributed ledgers, we do not elaborate 
-further.)
+For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
+an honest-but-curious adversary controlling \(\TS\)\footnote{%
+  We note that, in general, distributed (decentralized) ledgers cannot 
+  withstand a malicious \ac{ISP}.
+  Such an adversary can partition the network and provide Alice and Bob with 
+  different views of the ledger, thus breaking individual verifiability.
+  However, this requires that the adversary \emph{can observe} Alice's and 
+  Bob's channels to the ledger --- which is still not true even for 
+  \cref{deanonymizing-storage-adversary}.
+}.
+This means that Alice can check that her proof share is indeed there.
 
-\Cref{UniversalVerif} includes that anyone can check the result and that all 
+\Cref{UniversalVerif} implies that anyone can check the result and that all 
 participation proofs counted are legitimate.

### 2018-11-28 paper/verifiability-analysis.tex
Edits verifiability analysis, aligns it with adversary

@@
 \cref{DesignatedEvent}).
-We will now analyze these properties.
+It follows from \cref{analysis-individual} that the adversary cannot drop 
+submitted proof shares and thus cannot decrease the count.
+As indicated in \cref{in-system-adversary,deanonymizing-witness-adversary}, the 
+adversary can submit proof shares as everyone else, so the adversary's only 
+option is to increase the count.
+We will thus let Alice pose as the adversary in this section, as she naturally 
+has an incentive to increase the count.
 
@@
 challenge.
-The challenge here is the hash value of the head block of the ledger at the 
-time of the proof's creation (\(\TSget\)).
-The response is simply the challenge itself and is included as \(t_s\) and 
-\(t_s'\) in the proof share (see \cref{fig:ProofFig}).
+The challenge here is \enquote{which is the hash value of the head block of the 
+  ledger at the time of the proof's creation?}.
+The response is simply the hash itself (obtained through \(\TSget\)) and is 
+included as \(t_s\) and \(t_s'\) in the proof share (see \cref{fig:ProofFig}).
 
@@
 \Ie it depends on the pre-image resistance of the hash function used.
-Thus, with a collision resistant hash function, Alice can predict \(t_s\) only 
-with negligible probability; and it follows that, with high probability, 
-\(t_s\) was published on the ledger before being included in her proof share.
+Thus, with a collision resistant hash function (\(\Hash\)), Alice can predict 
+\(t_s\) only with negligible probability; and it follows that, with high 
+probability, \(t_s\) was published on the ledger before Alice included it in 
+her proof share.
 
-The correctness of the challenge must be verifiable by any verifier 
-(\(\TStime\)).
+The correctness of the response must be verifiable by any verifier (verifiable 
+through \(\TStime\)).
 This can be done if the ledger is continuously extended at a fixed rate, \eg 
@@
 Alice is in the same situation as above:
-she would have to choose a value \(y\) in the domain of the hash function 
+she would have to choose a value \(y\) in the range of the hash function 
 \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
@@
 specific protest and thus be counted more than once.
-This possibility is prevented by the use of \(\pid\).
+To do this she must create more than one pseudonym, \(\pid\).
 Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
@@
 \Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
-To realize this, we must ensure that Alice cannot forge witness signatures, 
-which is realized by using the same linkability mechanism as above.
-To forge a witness signature, Alice must produce a \(\wid'\) such that
+To realize this, we must ensure that Alice cannot forge witness signatures.
+
+In the trust-free case (see \cref{ProtocolVerification}), this is realized by 
+using the same linkability mechanism as above.
+\Ie to forge a witness signature, Alice must produce a \(\wid'\) such that
 \begin{multline*}
@@
 
-However, due to the assumptions made in \cref{ProtocolVerification}, we either assume that we can trust (dedicated) witnesses or that Alice cannot collude with more than a threshold \(\theta\) of witnesses (of course these two approaches could be combined).
-Note that Alice can produce \emph{one} witness signature for herself, since she 
-has access to her own \(\sk_P\), but no more.
-Thus, \(\theta > 1\) is a requirement in the trust-free case.
+We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
+witnesses.
+Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
+cheating.
+(Note that Alice can produce \emph{one} witness signature for herself, since 
+she has access to her own \(\sk_P\), but no more.
+Thus, \(\theta > 1\) is a requirement in the trust-free case.)
+
+In the trusted witness case, we assume that we can trust (dedicated) witnesses.
+In this case, Alice must be able to forge statements, \eg digital signatures, 
+from at least one witness that the verifier trusts.
 
@@
 \(\AC \neq \AC*\) are separate anonymous-credential systems.)
-
-%\paragraph{Forging proof shares}
-%
-%\daniel{This is work-in-progress.}
-%Alice can attempt to forge the full proof directly, \ie
-%\begin{multline*}
-%\pi_{\pid'} = \SPK\mleft\{ (\sk_P') : \mright. \\
-%  \begin{aligned}
-%    \pid' &= \ACprf[_{\sk_P'}][\cid], \\
-%    \sigma_P'' &= \mleft. \ACblind[\ACsign[_{\ssk}][\sk_P']] \mright\}
-%  \end{aligned} \\
-%    (\cid, \pid', \wid', t_s, t_s', l)
-%\end{multline*}
-%and consequently
-%and thus solve same problem twice (once for \(pid'\) and once for \(\wid'\)).
-%

### 2018-11-28 paper/verifiability-analysis.tex
Adapts verifiability analysis to \corr

--- 2018-11-16 paper/verifiability-analysis.tex
@@
 All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
-  t_e, t_e', l, \pi_\pid, \pi_{\wid})\)) are committed to the ledger and 
+  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
 available from a public and permanent storage (see 
@@
 As the proof shares are committed and stored publicly, anyone can
-download them, verify eligibility (\ie verify \(\pi_\pid,
-\pi_{\wid}\)) of the proofs and count them.
+download them, verify eligibility (\ie verify \(\corr_\pid,
+\corr_{\wid}\)) of the proofs and count them.
 As for individual verifiability, the security of universal verifiability is 

### 2018-11-29 paper/protocol.tex

--- 2018-11-27 paper/protocol.tex
@@
 During the setup phase, the \ac{CA} creates all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
-  \ACsetup\) (see \cref{CLsignAlg}).
+First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
+Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
+Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
+  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
+    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
+}.
+Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
+The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).
 
@@
 association between a particular key and the identity of the participant.
-The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
-\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
-\cref{CLacSigAlg}).
+The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
+The participant acts as prover and the \ac{CA} as verifier while they perform 
+the following \ac{ZKPK} protocol:
+\[
+  \PK[k,r][M = g^k Z^r].
+\]
+If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
+Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
+  C = A^x M^{axy})\) and sends it to the participant.
+The participant then verifies that the following equations hold:
+\begin{align*}
+  A &\neq 1 \\
+  e(g, B) &= e(Y, A) \\
+  e(g, Z_B) &= e(Z, B) \\
+  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
+\end{align*}
 Upon success, the participant sets \(\sk = (\sigma, k, r)\).
@@
 Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
-\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
-The protester should also receive a time-correlated random value from the 
-time-stamping service, \(t_s\gets \TSget\).
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
+\cref{fig:ProofFig,fig:ProtocolOverview}).
+More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
+The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).
 
@@
     \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
-the witness construct the proof share of the protester (\cref{fig:ProofFig}).
-
-The protester sends \(\pid\) to the witness.
-Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
-    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
-Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
-If the protocol succeeds, the witness will compute \(\wid \gets 
-  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
+In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
+  \tilde\sigma = (\tilde A = A^{r_1},
+                  \tilde B = B^{r_1},
+                  \tilde Z_B = Z_B^{r_1},
+                  \hat C = C^{r_1 r_2}).
+\) 
+Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
+The protester sends \((\pid, \tilde\sigma)\) to the witness.
+The witness verifies that
+\begin{align*}
+  \tilde A          &\neq 1 \\
+  e(g, \tilde B)    &= e(Y, \tilde A) \\
+  e(g, \tilde Z_B)  &= e(Z, \tilde B).
+\end{align*}
+Both the protester and the witness compute
+\begin{align*}
+  v &= e(g, \hat C) \\
+  v_x &= e(X, \tilde A) \\
+  v_{xy} &= e(X, \tilde B) \\
+  v_{xy}' &= e(X, \tilde Z_B).
+\end{align*}
+Afterwards, they run the following \ac{PPK} with the protester as the prover 
+and the witness as the verifier:
+\begin{multline*}
+  \mleftright
+  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+    \pid = g_T^{1/(k_P+\cid)} \right\}.
+\end{multline*}
+in which \(r' = 1/r_2\).
+We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
+Afterwards, the \ac{PK} can be designed as follows.
+(Remember that this \ac{PK} should be run as the \ac{PPK} in 
+\cref{DB-anon-cred} and repeated multiple times to achieve security.)
+The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
+sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
+  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+The witness replies with a challenge \(c\).
+Afterwards, the protester computes
+\begin{align*}
+  s_k &= -ck + r_k, \\
+  s_r &= -cr + r_r, \\
+  s_{r'} &= cr' + r_{r'}
+\end{align*}
+and forwards them to the witness.
+The witness checks whether
+\begin{align*}
+  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
+    s_r}, \\
+  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
+  \pid^{s_k}.
+\end{align*}
+If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
+  = g_T^{1/(k_W+\pid)}\) (as above).
+Following this, the witness returns \((\wid, t_s', l)\) to the protester.
+As a consequence, both the protester and the witness have the tuple \(\psh = 
+  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
+protester (\cref{fig:ProofFig}).
 

### 2018-11-29 paper/conclusions.tex

--- 2018-11-15 paper/conclusions.tex
@@
 %To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
-%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
+%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
 }
-%With respect to privacy, \PRIVO provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \PRIVO).
+%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
 \sonja{update sec analysis results}
@@
 
-In general, none of the related works fulfills the eligibility
-verifiability (one proof per person, temporal and spatial eligibility ---
-\cref{%
-  CountOnce,%
-  TemporallyRelated,SpatiallyRelated,%
-}).
-To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
-Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
-Moreover, if they provided individual verifiability, they would likely violate 
-the privacy requirements --- if people must recognize themselves in photos, 
-others can recognize them too.
-Finally, most of the current methods are estimates, with quite some error margins. 
+% In general, none of the related works fulfills the eligibility
+% verifiability (one proof per person, temporal and spatial eligibility ---
+% \cref{%
+%   CountOnce,%
+%   TemporallyRelated,SpatiallyRelated,%
+% }).
+% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
+% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
+% Moreover, if they provided individual verifiability, they would likely violate 
+% the privacy requirements --- if people must recognize themselves in photos, 
+% others can recognize them too.
+% Finally, most of the current methods are estimates, with quite some error margins. 
 While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
@@
 While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
-We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.
+We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and counter fake news.

### 2018-11-29 paper/distance-bounding.tex

@@
 For this paper, we assume the existence of such a protocol.
-Candidates for such a protocol include modifications of ~\cite{ProProx} or \sonja{cite Seb's, which reference?} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.
+Candidates for such a protocol include modifications of ~\cite{ProProx} or ~\cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2018-11-29 paper/system-model.tex

--- 2018-11-20 paper/system-model.tex
@@
 
-To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.
+To set the stage, we will now describe our system model including
+assumptions and a summary of the desired properties for crowd
+counting% and the adversary model
+.
 
@@
 
-\subsection{Desired properties}
+\subsection{Desired properties}%
+\label{desired-properties}
 
@@
 
-\subsection{Adversary model}%
-\label{adversary-model}
+% \subsection{Adversary model}%
+% \label{adversary-model}
 
-We consider two types of adversaries: 
-\begin{enumerate*} 
-\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
-messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
-\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
-\end{enumerate*}
+% We consider two types of adversaries: 
+% \begin{enumerate*} 
+% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
+% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
+% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
+% \end{enumerate*}

### 2018-11-29 paper/adversary-model.tex

--- 2018-11-28 paper/adversary-model.tex
@@
 We now provide a concretely defined system and adversary model.
-We give three definitions, each defines an adversary with increasingly stronger 
+We give three definitions, each defining an adversary with increasingly stronger 
 capabilities (\ie more auxiliary information).
@@
 
-\Cref{deanonymizing-storage-adversary} is a stronger adversary who also can 
-observe the channel between \(P\) and \(S\).
+\Cref{deanonymizing-storage-adversary} is a stronger adversary.
+Although the adversary cannot observe the channel between \(P\) and \(S\), the 
+adversary can still learn the identity of \(P\).
 \Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
@@
 observed from \(S\).
-We capture this in \cref{deanonymizing-storage-adversary}, where \(S\) learns 
-the identity of \(P\).
+We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
+the identity of \(P\) in the communication with \(S\).
 

### 2018-11-29 paper/location-proofs.tex

@@
 Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
-In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
-One of the main drawbacks of this approach is that a user can cheat by having her device transmit a false location. 
+In most of the existing schemes, the location of a user (or their device) is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
+One of the main drawbacks of this approach is that a user can cheat by having their device transmit a false location. 
 Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
@@
 A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
-Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
+Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location-proof architecture.
 However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location.
-\PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+\CROCUS shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+\sonja{any more differences to ours, relevance of this one?}
+\simon{Yeah, there is a problem here.
+As it currently reads, I see no reason to not use PROPS directly as a building block for CROCUS, instead of devising our own distance-bounding.
+Maybe there is no authentication, it's ONLY a proof of location?
+I don't know, but some detail is missing.}
+
+\sonja{add something on platin.io, details unknown but roughly relying on witnesses and graph theory (unique big cluster, assumption of honest majority)}

### 2018-11-29 paper/related-work.tex
Renames RelatedWork to related-work
Renames LocationProofs to location-proofs
coincoin

--- 2018-08-14 paper/RelatedWork.tex
@@
 \section{Related work}%
-\label{RelatedWork}
-
-In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.
+\label{related-work}
 
@@
 
-The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
+The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
 This manual method devised in the 1960s relies on aerial pictures of the event.
@@
 Clearly, this method is prone to errors as it is based on estimates.
-It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
-However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
-We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
+It provides universal verifiability since anyone can redo the counting using the same pictures.
+However, it is difficult to achieve individual verifiability using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
+We can argue that it also achieves eligibility if all the photos are taken at the same point in time, since then no one can be counted twice.
 Unfortunately, we can only get the peak participation with this method.
-When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
+When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where they were taken).
 However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
@@
 
-In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \citet{NNCrowdCounting}).
+In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \cite{NNCrowdCounting}).
 This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
@@
 In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
-Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
-Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
+Universal verifiability can be provided with this method, since someone can always recount the participants using the recorded video material.
+Some degree of individual verifiability could also be provided,
+if Alice can recognize her own face in the video, but this might still be difficult. 
 Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
-In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
-In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
+In addition, it is difficult (if not impossible) to avoid counting some people twice, thus we cannot argue for eligibility.
+In theory, this class of methods will provide an upper bound
+%, whereas our method outputs a lower bound
+.
 Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
@@
 This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
-In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.
+In addition, as MAC address randomization is now getting a wider adoption precisely to fight against physical tracking, this method will not work any more, although some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough}.
 
@@
 
-One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
-This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
-However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
+One of the works most closely related to our goal is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
+This method has the benefit of counting everyone who has declared their presence, not just the count at the snapshot of the pictures.
+However, there is no verification as the service must be trusted to behave honestly, and even then, nothing prevents Bob from submitting more than once (violating eligibility).
 Another downside is that the service also requires an Internet connection during the event to register as a participant.
 This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.
+For instance, if Alice has organized a protest against Grace's regime, Grace can shut down the cellular network or Internet backbone as a mean to censor the protest.
 
 Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
-However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.
+However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
 DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.
 
-\input{LocationProofs.tex}
+\input{location-proofs.tex}

### 2018-11-29 paper/verifiability-properties.tex
Minor rephrasing for security properties
harmonizing submittable

@@
     \item\label{CountOnce} \emph{Counted only once}:
-      A protester can create \emph{one and only one} pseudonym per protest 
-      (\(\pid\) in \cref{DefProofShares}), this pseudonym is unique except with 
-      negligible probability.
+      A protester can create \emph{one and only one} pseudonym (\(\pid\) in 
+      \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
+      this pseudonym is unique except with negligible probability.
       Analogously, a witness can create \emph{one and only one} pseudonym per 
@@
 
-    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated with particular designated protest.
+    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof 
+      is designated for the particular protest.
 

### 2018-11-29 paper/protocol.tex

--- 2018-11-29 paper/protocol.tex
@@
 The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-join, participation, submission (all in in \cref{ProtocolDuring} ) and
+join, participation, submission (all in in \cref{ProtocolDuring}) and
 verification (in \cref{ProtocolVerification}).

### 2018-11-29 paper/verifiability-analysis.tex
Replaces \paragraph with \subsubsection where necessary

@@
 submitted proof shares and thus cannot decrease the count.
-As indicated in \cref{in-system-adversary,deanonymizing-witness-adversary}, the 
+As indicated in \cref{in-system-adversary,deanonymizing-storage-adversary}, the 
 adversary can submit proof shares as everyone else, so the adversary's only 

### 2018-11-30 paper/protocol.tex
Fixes figure ref typos
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering

@@
-\section{\CROCUS:\@ A protocol for crowd counting estimation}%
+%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
+\section{The \CROCUS Protocol}
 \label{Protocol}
@@
 The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
-  \ACsetup\) (see \cref{CLsignAlg}).
+  \ACsetup\) (see \cref{ACsignAlg}).
 
@@
 \(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
-\cref{CLacSigAlg}).
+\cref{ACacAlg}).
 Upon success, the participant sets \(\sk = (\sigma, k, r)\).
@@
 
-The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
-The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.
+%The join, participation and submission phases are as follows.
+% illustrated in \cref{fig:ProtocolOverview}.
 
-\emph{Creation of a protest: the manifesto.}
-The organizer will write a manifesto for the protest, which describes its cause.
-This manifesto could take the form of any intelligible text.
-The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
-If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
-
-\emph{Joining as a protester: \((\pid, t_s)\gets 
-    \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
-Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
-\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
-The protester should also receive a time-correlated random value from the 
-time-stamping service, \(t_s\gets \TSget\).
+The participation proof share that will be constructed in the
+participation phase is illustrated in \cref{fig:ProofFig}.
 
@@
 
-\begin{figure}
-  \centering
-  \small
-  \begin{minipage}{\linewidth}
-    \begin{align*}
-      O\to \text{all}\colon & \text{manifesto} \\
-      P\colon & t_s\gets \TSget \\
-        & \cid\gets \Hash[\text{manifesto}], \\
-        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
-      W\colon & t_s'\gets \TSget
-      \\[-1em]
-      \noalign{\hfill Join}
-      \midrule
-      \noalign{\hfill Participation}
-      \\[-3em]
-      P\to W\colon & \pid \\
-      P\leftrightarrow W\colon &
-        \PPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
-        \\
-      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
-      W\to P\colon & (\wid, t_s', l)
-      \\[-1em]
-      \noalign{\hfill Participation}
-      \midrule
-      \noalign{\hfill Submission}
-      \\[-2em]
-      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
-      \text{where} \\
-        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
-        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
-        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
-      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
-      \text{where}\\
-        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
-    \end{align*}
-  \end{minipage}
-  \caption{%
-    An overview of the Join, Participation and Submission phases of \CROCUS.\@
-    The organizer \(O\) broadcasts the manifesto.
-    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submit the proof shares to a
-    permanent storage \(S\). Note that \pid always refers to the
-    protester whose presence is being witnessed.
-  }%
-  \label{fig:ProtocolOverview}
-\end{figure}
+\emph{Creation of a protest: the manifesto.}
+The organizer will write a manifesto for the protest, which describes its cause.
+This manifesto could take the form of any intelligible text.
+The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
+If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
+
+\emph{Joining as a protester: \((\pid, t_s)\gets 
+    \CROCUSjoin[_P][\text{manifesto}]\).}
+A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
+Afterwards, this identifier is used to create the protest-specific identifier 
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
+\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
+The protester should also receive a time-correlated random value from the 
+time-stamping service, \(t_s\gets \TSget\).
 
@@
 
+Here is an overview of the protocol.
+
+%\begin{figure}
+% \centering
+  \small
+ % \begin{minipage}{\linewidth}
+    \begin{align*}
+      O\to \text{all}\colon & \text{manifesto} \\
+      P\colon & t_s\gets \TSget \\
+        & \cid\gets \Hash[\text{manifesto}], \\
+        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
+      W\colon & t_s'\gets \TSget
+      \\[-1em]
+      \noalign{\hfill Join}
+      \midrule
+      \noalign{\hfill Participation}
+      \\[-3em]
+      P\to W\colon & \pid \\
+      P\leftrightarrow W\colon &
+        \PPK\mleft\{ (\sk_P) : \mright. \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+        \\
+      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
+      W\to P\colon & (\wid, t_s', l)
+      \\[-1em]
+      \noalign{\hfill Participation}
+      \midrule
+      \noalign{\hfill Submission}
+      \\[-2em]
+      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
+      \text{where} \\
+        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
+        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
+        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
+        \\
+        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
+      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
+      \text{where}\\
+        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
+        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+        \\
+        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
+    \end{align*}
+%  \end{minipage}
+%  \caption{%
+%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
+%     The organizer \(O\) broadcasts the manifesto.
+%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+%     Finally, both \(P\) and \(W\) submit the proof shares to a
+%     permanent storage \(S\). Note that \pid always refers to the
+%     protester whose presence is being witnessed.
+%   }%
+%   \label{fig:ProtocolOverview}
+% \end{figure}
+\normalsize
+
 \subsection{Verifying the participation count}%

### 2018-11-30 paper/system-model.tex
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering

--- 2018-11-28 paper/system-model.tex
@@
-\section{System model and requirements}%
+\section{System model}%
 \label{system-model}
@@
 
-\subsection{System model and physical assumptions}%
+\subsection{Assumptions}%
 \label{assumptions}
@@
 The eligibility requirement is slightly different as for protests it must also
-include temporal\footnote{%
-  Elections also have some temporal aspects, such that one cannot vote at any 
-  time and a vote in one election should not be reusable in the next election.
-  However, the temporal relation for a protest is not as strictly defined as for 
-  elections as a protest can start at any time and last for an arbitrary period 
-  of time.%
-} and spatial eligibility (\ie each participation proof satisfies some temporal 
+include temporal%\footnote{%
+%   Elections also have some temporal aspects, such that one cannot vote at any 
+%   time and a vote in one election should not be reusable in the next election.
+%   However, the temporal relation for a protest is not as strictly defined as for 
+%   elections as a protest can start at any time and last for an arbitrary period 
+%   of time.%
+% }
+and spatial eligibility (\ie each participation proof satisfies some temporal 
 and spatial relation to the protest).

### 2018-11-30 paper/privacy-properties.tex
harmonization, pass 2 (still WIP)

@@
   adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
-    \pid_{\text{Bob}}\), except with negligible probability.
+    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
 \item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
@@
 What these properties say is that pseudonyms must look random 
-(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
+(\cref{PseudonymUnlink}) and that each pseudonym must be used as little as possible to still ensure the verifiability properties defined in the previous subsection
 (\cref{ProtestUnlink,WitnessUnlink}).

### 2018-11-30 paper/protest-model.tex
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering
harmonization, pass 2 (still WIP)

@@
 
-\emph{Formalizing the notion of crowd estimation.} 
+%\emph{Formalizing the notion of crowd estimation.} 
 Each participant who wants to be counted must submit a \emph{participation proof}.
@@
 act as witness for other protesters.)
-Then, the set of all \emph{eligible} proof shares forms the participation proof of a protester.
+Then, the set of all \emph{valid} proof shares forms the participation proof of a protester.
 
@@
 
-\begin{definition}[Eligible proof share]%
+\begin{definition}[Valid proof share]%
   \label{DefProofShare}\label{DefProofShares}
@@
   \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
-  Furthermore, we say that \(\psh\) is \emph{eligible} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
+  Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
   \(\psh \sqsubseteq \sprtst\).
@@
   \end{equation}
-  of all proof shares with the same protester and protest identifiers, and eligible for any subprotest $p$ of $\prtst$.
+  of all proof shares with the same protester and protest identifiers, and valid for any subprotest $p$ of $\prtst$.
   We denote by \(\prfs\) the set of all proofs.
@@
   We define a \emph{participation count} of a protest \(\prtst\) as the cardinality 
-  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{valid} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
+  \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
     \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
@@
 share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
-to accept a participant as valid.
+to accept a participant as eligible.
 One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
@@
 non-trusted witnesses and a weight of \(\theta\) to trusted witnesses. This 
-results in a participant being valid if they are witnessed either by \(\theta\) 
+results in a participant being eligible if they are witnessed either by \(\theta\) 
 non-trusted witness or by one trusted witness.

### 2018-11-30 paper/protocol.tex
harmonization, pass 2 (still WIP)

--- 2018-11-29 paper/protocol.tex
@@
 
-We now present \CROCUS, a protocol for privately verifyiable crowd counts.
-The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-join, participation, submission (all in in \cref{ProtocolDuring}) and
-verification (in \cref{ProtocolVerification}).
+We now present \CROCUS, a protocol for privately verifiable crowd counts.
+The protocol consists of three phases:
+before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
+during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
+and after the protest, with the verification step (in \cref{ProtocolVerification}).
 
 Several entities are involved in our protocol.
-First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
+First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
 person's identity and a cryptographic key\footnote{%
@@
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
+\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
@@
 
-\subsection{Setup phase}%
+\subsection{Pre-protest phase}%
 \label{ProtocolSetup}
 
-The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
-More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.
+The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
+More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
 
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
-During the setup phase, the \ac{CA} creates all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
-  \ACsetup\) (see \cref{CLsignAlg}).
+During the setup step, the \ac{CA} creates all the needed keys.
+First, the \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\) as follows.
+Let \(G = \gen g\) be a group with generator \(g\) and of prime order \(q\).
+Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times G\to G_T\)\footnote{%
+  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
+    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
+}.
+Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = g^z\).
+The service public key is set to \(\spk = (q, G, G_T, g, X, Y, Z)\) and the service private key to \(\ssk = (x, y, z)\).
 
@@
     \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration phase, each participant generates a secret key and 
+During the registration step, each participant generates a secret key and 
 obtains a signature on it by the \ac{CA} but without revealing it to the 
@@
 association between a particular key and the identity of the participant.
-The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
-\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
-\cref{CLacSigAlg}).
+The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly, sets \(M = g^k Z^r\) and sends \(M\) to the server.
+The participant acts as prover and the \ac{CA} as verifier while they perform 
+the following \ac{ZKPK} protocol:
+\[
+  \PK[k,r][M = g^k Z^r].
+\]
+If the proof succeeds, the \ac{CA} chooses \(a\rgets \ZZ_q^*\) and sets \(A = g^a\).
+Afterwards, he forms the signature \(\sigma = (A, B = A^y, Z_B = B^z = Z^{ay}, 
+  C = A^x M^{axy})\) and sends it to the participant.
+The participant then verifies that the following equations hold:
+\begin{align*}
+  A &\neq 1 \\
+  e(g, B) &= e(Y, A) \\
+  e(g, Z_B) &= e(Z, B) \\
+  e(g, C) &= e(X, A) e(X, B)^k e(X, Z_B)^r.
+\end{align*}
 Upon success, the participant sets \(\sk = (\sigma, k, r)\).
 
-The setup and registration phases can be done once and the keys can be reused 
+The setup and registration steps can be done once and the keys can be reused 
 for an arbitrary number of protests.
-Thus, the registration phase could be easily integrated as part of the issuance 
+Thus, the registration step could be easily integrated as part of the issuance 
 of national identity cards, passports or \acp{eID}.
 
-\subsection{Creation, join and participation in a protest and submission of proofs}%
+\subsection{Protest phase}%
 \label{ProtocolDuring}
 
-The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
-The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.
+The join, participation and submission steps are illustrated in \cref{fig:ProtocolOverview}.
+The participation proof share that will be constructed in the participation step is illustrated in \cref{fig:ProofFig}.
 
@@
     Finally, both \(P\) and \(W\) submit the proof shares to a
-    permanent storage \(S\). Note that \pid always refers to the
+    permanent storage \(S\). Note that \pid{} always refers to the
     protester whose presence is being witnessed.
@@
     \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
-the witness construct the proof share of the protester (\cref{fig:ProofFig}).
-
-The protester sends \(\pid\) to the witness.
-Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
-    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
-Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
-If the protocol succeeds, the witness will compute \(\wid \gets 
-  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
+In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
+  \tilde\sigma = (\tilde A = A^{r_1},
+                  \tilde B = B^{r_1},
+                  \tilde Z_B = Z_B^{r_1},
+                  \hat C = C^{r_1 r_2}).
+\) 
+Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
+The protester sends \((\pid, \tilde\sigma)\) to the witness.
+The witness verifies that
+\begin{align*}
+  \tilde A          &\neq 1 \\
+  e(g, \tilde B)    &= e(Y, \tilde A) \\
+  e(g, \tilde Z_B)  &= e(Z, \tilde B).
+\end{align*}
+Both the protester and the witness compute
+\begin{align*}
+  v &= e(g, \hat C) \\
+  v_x &= e(X, \tilde A) \\
+  v_{xy} &= e(X, \tilde B) \\
+  v_{xy}' &= e(X, \tilde Z_B).
+\end{align*}
+Afterwards, they run the following \ac{PPK} with the protester as the prover 
+and the witness as the verifier:
+\begin{multline*}
+  \mleftright
+  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
+    \pid = g_T^{1/(k_P+\cid)} \right\}.
+\end{multline*}
+in which \(r' = 1/r_2\).
+We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
+Afterwards, the \ac{PK} can be designed as follows.
+(Remember that this \ac{PK} should be run as the \ac{PPK} in 
+\cref{DB-anon-cred} and repeated multiple times to achieve security.)
+The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
+sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
+  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
+The witness replies with a challenge \(c\).
+Afterwards, the protester computes
+\begin{align*}
+  s_k &= -ck + r_k, \\
+  s_r &= -cr + r_r, \\
+  s_{r'} &= cr' + r_{r'}
+\end{align*}
+and forwards them to the witness.
+The witness checks whether
+\begin{align*}
+  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
+    s_r}, \\
+  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
+  \pid^{s_k}.
+\end{align*}
+If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
+  = g_T^{1/(k_W+\pid)}\) (as above).
+Following this, the witness returns \((\wid, t_s', l)\) to the protester.
+As a consequence, both the protester and the witness have the tuple \(\psh = 
+  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
+protester (\cref{fig:ProofFig}).
 
 \emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The participant should as soon as possible commit the proof-share data to the 
+The protester should as soon as possible commit the proof-share data to the 
 time-stamping service and receive the proof of commitment, \(t_e\gets 
@@
     l]\).}
-The witness should, just as the participant, commit the proof-share data to the 
+The witness should, just as the protester, commit the proof-share data to the 
 time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
@@
 
-\subsection{Verifying the participation count}%
+\subsection{Post-protest phase}%
 \label{ProtocolVerification}
@@
 
-To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
+To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
 (see \cref{DefProtest}), a verifier must download all the proof shares \[

### 2018-11-30 paper/timestamp.tex
Changes equality to inequality for timestamp comparison
shortens some titles, integrates protocol overview in text, removes keywords etc. turns paragraphs into subsections for correct numbering
harmonization, pass 2 (still WIP)

@@
-\subsection{Time-stamping service -- distributed ledger}%
-\label{StorageProperties}
+\subsection{Time-stamping and storage --- distributed ledger}%
+\label{StorageProperties}\label{timestamp}\label{ledger}
 
 We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
+\simon{"request" feels weird to me. Are we sure that's the right word?}
 \begin{itemize}
@@
 The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] = t_0\land 
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] = t_0\land 
   \TStime[\pi_{t_1}] = t_1\).

### 2018-11-30 paper/intro.tex
Replaces \paragraph with \subsection where necessary

--- 2018-11-27 paper/intro.tex
@@
 
-\paragraph*{Outline}
+% \paragraph*{Outline}
 
-The paper is organized as follows.
-First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
-We then formalize the notion of protest and the desired verifiability and privacy properties in \cref{definitions}, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
+% The paper is organized as follows.
+% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}).
+% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
+
+% After that, we present \CROCUS, a privacy-preserving crowd counting estimation 
+% protocol constructed from these building blocks (\cref{Protocol}), before 
+% analyzing its security and privacy (\cref{SecurityAnalysis}), and its 
+% performance (\cref{PerformanceAnalysis}).
+% Finally, we discuss our assumptions and results (\cref{Discussion}) and give our conclusions (\cref{Conclusion}).
+% \sonja{do not uncomment the following, it's for DBAC}
+%\sonja{add (sub) sections for performance and verification}
 % Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
@@
 %This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting estimation protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}) and performance (\cref{PerformanceAnalysis}) .
-Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
-%\sonja{add (sub) sections for performance and verification}

### 2018-11-30 paper/protocol.tex

--- 2018-11-30 paper/protocol.tex
@@
 
-\subsection{Setup phase}%
+\subsection{Pre-protest phase}%
 \label{ProtocolSetup}
 
-The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
-More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.
+The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
+More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
 
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
+
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
 
-The setup and registration phases can be done once and the keys can be reused 
+The setup and registration steps can be done once and the keys can be reused 
 for an arbitrary number of protests.
-Thus, the registration phase could be easily integrated as part of the issuance 
+Thus, the registration step could be easily integrated as part of the issuance 
 of national identity cards, passports or \acp{eID}.
 
-\subsection{Creation, join and participation in a protest and submission of proofs}%
+\subsection{Protest phase}%
 \label{ProtocolDuring}
@@
 \emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The participant should as soon as possible commit the proof-share data to the 
+The protester should as soon as possible commit the proof-share data to the 
 time-stamping service and receive the proof of commitment, \(t_e\gets 

### 2018-11-30 paper/trust-assumptions.tex

%\subsection{Trust assumptions}
\section{Trust assumptions}

The goal of CROCUS is to be able to count people in a crowd in a verifiable way, without leaking information about the individuals in the crowd.
We believe one of the strongest adversaries in practice, and one of the most dangerous situation, is that of an authoritarian government wanting to learn the identities of protesters,
so we chose a theoretical model that fits this situation well, but it is interesting to see what are the trust relations which are actually needed in various real world situations.

\paragraph{ID issuer} We assumed a trusted third party issued certified IDs to every participant (protesters and witnesses). This hypothesis is important to avoid Sybil attacks,
but only the side protesting (not the side being protested against) has an incentive to perform a Sybil attack.
So in practice, the ID issuer doesn't need to be a trusted 3rd-party, it only needs to not be aligned with the protesters.
In our authoritarian government scenario for instance, the protesters can use IDs issued by said government.
On the other hand however, a pro-government protest cannot use the same IDs and offer a good level of trust in the final count, and it would be better suited to use IDs from a different source
(e.g. a supra-national issuer like the EU).

 \paragraph{Verifier's trust in the count} We proposed a generic way of counting, that relies on two parameters: the strength function and the threshold.
%We then suggested two possible instantiations: every witness is equal and we use a relatively large threshold, or we only trust a minority of independent witnesses with a threshold of 1.
An important point here is that these parameters can be chosen by each verifier independently, so each verifier can make choices that satisfy \emph{their} own level of trust, and can each obtain a different final count, and \CROCUS does not output one definitive answer. The trust in a final count depends only on the trust between the verifier and the witnesses.

\simon{maybe delete that second half}
In practice though, the verifier can be in either of three situations: for the protest, against the protest, or indifferent, which leads to three main categories of choices.
\begin{itemize}
	\item A verifier aligned with the protesters has an incentive to trust any witness and use as low a threshold as possible.
	\item A verifier opposed to the protesters has the opposite incentive to exclude as many witnesses and use as high a threshold as possible.
	\item An indifferent verifier who only cares about the correctness of the result can trust each witness based on their reputation and should use a threshold that is reasonably reachable in practice but high enough to avoid small-scale collusion.
\end{itemize}

\paragraph{Protesters and witnesses} Active participants in a protest do not need to trust anything other than that their app is behaving properly and that their smartphone is not compromised. Indeed, \CROCUS has been designed with their privacy and security as a central concern, and being able to use \CROCUS without any additional risk compared to simply come at the protest was one of our main requirement.

### 2018-11-30 paper/protocol.tex
better notations in verification

@@
 
-To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
-(see \cref{DefProtest}), a verifier must download all the proof shares \[
-  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
-  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
-\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
-\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
-    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
-\(l_i\subseteq  l\).
-Any proof share that does not verify correctly will be discarded.
-At this point, the verifier has constructed the set \(S\) from 
-\cref{DefProofShares} and can thus construct any participation proof 
-\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
-Now the verifier can compute the participation count \(|\prfs_P^{\str, 
-    \theta}|\) as in \cref{DefParticipationCount}.
+To verify the participation count for a protest \(\prtst\) with identifier \(cid_0\),
+a verifier must download from the storage system S the set \(S_{\prtst}\) of all \(s_P\) and \(s_W\) tuples containing \(cid_0\).
+Then from \(S_{\prtst}\), a verifier can build, in succession,
+(a) the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P,s_W)\) corresponding to a witness  \(i\) and a protester \(j\),
+(b) the participation proof \(\prf_{j}\) for each protester \(j\),
+(c) the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs for all protesters in \(P\),
+ and finally the participation count, cardinality of the previous set.
+
+More precisely, given: \\
+\(S_{\prtst} = \{ (cid, pid, wid, l, t_s, t_s', t_c, \corr) \in \pshs \mid \cid = \cid_0 \} \) \\
+and a matching pair \((s_P, s_W) \in {S_{\prtst}}^2\) for a witness \(i\) and a protester \(j\)
+with \(s_P = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c, \psi_i)\)
+and  \(s_W = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c', \psi_j)\),
+%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
+the verifier can build a valid proof share \(s_j^{(i)}\) certified by  \(i\) for \(j\) as follow:
+verify \(\psi_i\) and \(\psi_j\),
+let \(t = [max(t_s, t_s'), min(t_c, t_c')]\),
+let \(s_j^{(i)} = (cid_0, pid_j, wid_i, l, t)\), as in \cref{DefProofShare},
+check that \(s_j^{(i)}\) is valid (i.e. happened during and at the location of the protest), as in \cref{DefProofShare}.
+
+Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
+and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
+Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.
+
+% MOST PROBABLY obsolete below v
+
+%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
+%(see \cref{DefProtest}), a verifier must download all the proof shares \[
+%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
+%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
+%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
+%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
+%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
+%\(l_i\subseteq  l\).
+%Any proof share that does not verify correctly will be discarded.
+%At this point, the verifier has constructed the set \(S\) from 
+%\cref{DefProofShares} and can thus construct any participation proof 
+%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
+%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
+%    \theta}|\) as in \cref{DefParticipationCount}.
+
+%__________________________
 

### 2018-11-30 paper/timestamp.tex
details about inequalities and blockchain forks

@@
-\subsection{Time-stamping and storage --- distributed ledger}%
+\subsection{Time-stamping and storage: ledger}%
 \label{StorageProperties}\label{timestamp}\label{ledger}
@@
 The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] = t_0\land 
-  \TStime[\pi_{t_1}] = t_1\).
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] > t_0\land 
+  \TStime[\pi_{t_1}] < t_1\).
 
@@
 The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
+\footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
 The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).
@@
 Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
-Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
-In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her participation proof and the hash of the proof.
+Note that thanks to \(\TS\) immutability, once a user has committed their data, that user only need to store some confirmation value instead of the data itself.
+For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.

### 2018-11-30 paper/intro.tex
edits language and redundancies in intro

@@
 Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
-On the one hand, Alice wants to estimate the number of participants to prove a certain support for her cause.
-On the other hand, Grace is an autocratic regime leader who opposes Alice's cause.
-Bob, Carol and many others participate in the protest for Alice's cause against Grace.
+Alice wants to estimate the number of participants to prove a certain support for her cause against Grace.
+Bob, Carol and many others participate in the protest.
 However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
-To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved as of today.
+To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
-Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes in the order of hundreds of thousands.
+Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
 Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
@@
 However, most of them lack precision (\ie they have large error margins) and 
-they can only give an estimate for a particular snapshot in time (\eg at the 
-peak of the event). In particular, the existing methods cannot reliably 
+they can only give an estimate for a particular snapshot in time. In particular, the existing methods cannot reliably 
 estimate the cumulative participation count --- at least not without counting 
@@
 Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
-Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
+Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
 In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
 In this paper, our main objective is to provide a scheme preventing both Alice 
-and Grace from cheating by providing verifiable claims.
-To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
-More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
-Nonetheless, we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
+and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
+While one cannot
+prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.
+
+%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
 %\seb{in the sentence above I am not sure that the word unlinkable will be 

### 2018-11-30 paper/system-model.tex
positions the properties as coming from Delaune, not as traditional for voting; other edits.

@@
 
-\subsection{Assumptions}%
+\subsection{Model and assumptions}%
 \label{assumptions}
@@
 In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest.
-During the protest, the devices might be limited by their batteries in terms of the computations they can perform and only have local connectivity to each other.
+During the protest, the devices might be limited by their batteries and computations they can perform and only have local connectivity to each other.
 No connection to any global network such as the Internet is necessary at that time.  
@@
 
-We draw inspiration from the three traditionally desired properties for verifiability in voting systems:
+We draw inspiration from properties for voting systems as formalized
+in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \daniel{Find a new ref for voting verifiability properties, Douglas commented 
@@
 The eligibility requirement is slightly different as for protests it must also
-include temporal%\footnote{%
+include temporal %\footnote{%
 %   Elections also have some temporal aspects, such that one cannot vote at any 
@@
 
-In addition to the verification requirements, we also need to define the 
-privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
+privacy properties for voting protocols are given as:
 \begin{description}
@@
 Coercion resistance in voting typically relies on physical isolation
-(\eg private voting boots), including for digital systems, 
+(\eg private voting booths), including for digital systems, 
 and that is by definition not possible for public events.
@@
 in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
-cause of the protest) implies receipt freeness for \emph{that} the voter voted 
+cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
 (\ie the protester was there), which would make verifiability impossible.

### 2018-11-30 paper/related-work.tex
moves location proofs related work to appendix, adds section title for AC figures
edits in related work

@@
 
-\subsection{Crowd counting methods}
+%\subsection{Crowd counting methods}
 
@@
 It provides universal verifiability since anyone can redo the counting using the same pictures.
-However, it is difficult to achieve individual verifiability using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
+However, it is difficult to achieve individual verifiability using this method since it is hard to verify that oneself is indeed in any of the photos.
+%\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
 We can argue that it also achieves eligibility if all the photos are taken at the same point in time, since then no one can be counted twice.
@@
 
-Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
-Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
+Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd in a selected area.
+Once the user has specified the zone, they select one of three pre-set density estimates: light, medium or dense.
 This is similar to the method usually used by police (\eg during the protests in Seoul):
@@
 if Alice can recognize her own face in the video, but this might still be difficult. 
-Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
+While automatic face recognition can help verifiability, it reduces privacy.
 In addition, it is difficult (if not impossible) to avoid counting some people twice, thus we cannot argue for eligibility.
-In theory, this class of methods will provide an upper bound
-%, whereas our method outputs a lower bound
-.
-Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
-The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
+%In theory, this class of methods will provide an upper bound.
+%, whereas our method outputs a lower bound.
+Furthermore, it is also difficult to capture the entire location on video surveillance, %which diminishes the argument for an upper bound in practice.
+ and the spatial and temporal verifiability properties are reduced to those of the video.
+%, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
 
@@
 
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
+During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one company tried to estimate the number of participants using their physical analytics technology.
 In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
@@
 In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
+%These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
 
@@
 Another downside is that the service also requires an Internet connection during the event to register as a participant.
-This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Grace's regime, Grace can shut down the cellular network or Internet backbone as a mean to censor the protest.
+This makes it vulnerable to a denial-of-service attack, \eg
+%For instance, if Alice has organized a protest against Grace's regime, 
+Grace can shut down the cellular network or Internet backbone as a means to censor the protest.
 
@@
 However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.
 
-\input{location-proofs.tex}
+%\input{location-proofs.tex}

### 2018-11-30 paper/adversary-model.tex
removes framing in definitions, edits, adds to auxilliary data explanation

@@
 
-We now provide a concretely defined system and adversary model.
-We give three definitions, each defining an adversary with increasingly stronger 
-capabilities (\ie more auxiliary information).
+% We now provide a concretely defined system and adversary model.
+% We give three definitions, each defining an adversary with increasingly stronger 
+% capabilities (\ie more auxiliary information).
 
@@
   \caption{\label{fig:base-adversary}%
-    An overview of the base adversary model.
+    An overview of the in-system adversary model.
     The protester with real identity \(P\) and witness with real identity \(W\) 
     communicate.
-    They exchange protocol data, \(d_{P,W}(\cid, P)\), and record the time it 
+    They exchange protocol data as a function \(d\) of the protest and protester, \(d_{P,W}(\cid, P)\), and record the time it 
     happened, \(t_{P,W}\).
     The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
-    the storage \(S\), who records the time it happened, \(t_{P,S}\).
-    Both the witness \(W\) and storage \(S\) are controlled by the adversary 
+    the storage \(S\), who records the time that happened, \(t_{P,S}\).
+    Both the witness \(W\) and the storage \(S\) are controlled by the adversary 
     \(A\) (from \cref{in-system-adversary}).
@@
   channel, no auxiliary data\footnote{%
-    By auxiliary data we mean any data outside of the protocol.
-    \Eg meta-data such as who is on the other side of the channel.
+    By auxiliary data we mean any data outside of the protocol, \ie
+    meta-data such as who is on the other side of the channel obtained
+    as side information, \eg by face recognition or inference from address
+    to identiy.
   }

### 2018-11-30 paper/distance-bounding.tex
harmonization, pass 2 (still WIP)
edits pronouns, moved much of DB to LP in appendix

@@
 
-\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
-These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
-As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
-\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
-Time critical phases are complemented by slow phases during which the time is not taking into account. 
-At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in his vicinity.
-In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
-
-The main attacks against \ac{DB} protocols can be summarized as follows:
-\begin{itemize}
-  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
-  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
-  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
-\end{itemize}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
-
-The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
-There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
 Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
@@
 For this paper, we assume the existence of such a protocol.
-Candidates for such a protocol include modifications of ~\cite{ProProx} or ~\cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.
+Candidates for such a protocol include modifications of ~\cite{ProProx} or \cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2018-11-30 paper/location-proofs.tex
moves location proofs related work to appendix, adds section title for AC figures
edits pronouns, moved much of DB to LP in appendix

@@
-\subsection{Location proofs}
+%\subsection{Location proofs}
+\section{Distance bounding and location proofs}
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
+These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
+As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
+\Ac{DB} protocols enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
+%Time critical phases are complemented by slow phases during which the time is not taking into account. 
+Slow phases, during which the time is not taken into account, complement the time critical phases.
+At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in their vicinity.
+In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
+
+The main attacks against \ac{DB} protocols can be summarized as follows:
+\begin{itemize}
+  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
+  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
+  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
+\end{itemize}
+There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+
+The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
+Indeed, in this context it does not make sense to protect against the verifier as they can easily impersonate the prover as they have knowledge of their secret key.
+There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
 

### 2018-11-30 paper/protocol.tex
edits, points to figures in appendix, removes orphan figure pointers

@@
 during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
-and after the protest, with the verification step (in \cref{ProtocolVerification}).
+and after the protest, with the verification step (in
+\cref{ProtocolVerification}). Note that some of the figures with
+protocol minutae from related work are in the
+appendix.
 
@@
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
-  for his presence.
+  for their presence.
 \item A \emph{witness} provides proofs to protesters which state that the 
-  protester was indeed participating and such that the proofs are verifiable by 
+  protester was indeed participating, constructed such that the proofs are verifiable by 
   third parties.
 \end{enumerate}
-In general, there is one organizer and every participant can act alternatively 
-as both protester and witness.
+In general, there is one organizer and every participant can act as
+either or both protester and witness.
 
@@
 
-The participation proof share that will be constructed in the
+The participation proof share constructed in the
 participation phase is illustrated in \cref{fig:ProofFig}.
@@
 \emph{Creation of a protest: the manifesto.}
-The organizer will write a manifesto for the protest, which describes its cause.
+The organizer writes a manifesto for the protest, which describes its cause.
 This manifesto could take the form of any intelligible text.
-The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
+The organizer will then distribute this manifesto to people through
+any suitable means  (\eg on the Web, on placards, \etc).
 If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
@@
 for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
-\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
+\cref{fig:ProofFig} and \cref{ACprfAlg}).
 The protester should also receive a time-correlated random value from the 
@@
     \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
+In the participation phase, the protester and 
 the witness construct the proof share of the protester (\cref{fig:ProofFig}).

### 2018-11-30 paper/protocol.tex
explains about cid comparison and why it's not in the protocol, swaps eligibility and verifiability in analysis, rephrases threshold to match with strength function, other small edits

@@
 any suitable means  (\eg on the Web, on placards, \etc).
-If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
+If they agree with the cause, they will use the knowledge of the
+manifesto to join the protest.
 
@@
     \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
+A protester who wants to join the protest will use the manifesto to
+compute an identifier for the cause by hashing the manifesto,
+\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
+from the organizer, we omit this in the protocol for readibility).
 Afterwards, this identifier is used to create the protest-specific identifier 
@@
 witnesses, who is considered to be a trusted witness) for their count
-and as long as these are published along with the result, any one can
+and as long as these are published along with the result, anyone can
 verify the correctness under those criteria.

### 2018-11-30 paper/verifiability-analysis.tex
explains about cid comparison and why it's not in the protocol, swaps eligibility and verifiability in analysis, rephrases threshold to match with strength function, other small edits

@@
-\subsection{Individual and universal verifiability}%
-\label{analysis-individual}%
-\label{analysis-universal}
-
-\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
-that their participation proofs (\ie proof shares) are indeed included in the 
-computed count.
-All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
-  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
-available from a public and permanent storage (see 
-\cref{fig:ProtocolOverview}).
-Thus, Alice and Bob can simply check that all of their proof shares are indeed 
-there and the security of individual verifiability depends on the properties of 
-the ledger and storage (\(\TS\), \cref{timestamp}).
-For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
-an honest-but-curious adversary controlling \(\TS\)\footnote{%
-  We note that, in general, distributed (decentralized) ledgers cannot 
-  withstand a malicious \ac{ISP}.
-  Such an adversary can partition the network and provide Alice and Bob with 
-  different views of the ledger, thus breaking individual verifiability.
-  However, this requires that the adversary \emph{can observe} Alice's and 
-  Bob's channels to the ledger --- which is still not true even for 
-  \cref{deanonymizing-storage-adversary}.
-}.
-This means that Alice can check that her proof share is indeed there.
-
-\Cref{UniversalVerif} implies that anyone can check the result and that all 
-participation proofs counted are legitimate.
-As the proof shares are committed and stored publicly, anyone can
-download them, verify eligibility (\ie verify \(\corr_\pid,
-\corr_{\wid}\)) of the proofs and count them.
-As for individual verifiability, the security of universal verifiability is 
-reduced to the properties of the ledger and storage; but universal 
-verifiability also depends on the eligibility verification, which we will 
-discuss next.
-
 \subsection{Eligibility verifiability}%
@@
 \cref{DesignatedEvent}).
-It follows from \cref{analysis-individual} that the adversary cannot drop 
+As we will show, it follows from \cref{analysis-individual} that the adversary cannot drop 
 submitted proof shares and thus cannot decrease the count.
@@
 We will thus let Alice pose as the adversary in this section, as she naturally 
-has an incentive to increase the count.
+has an incentive to increase the count, as the organizer and participant.
 
-\paragraph{Temporal eligibility}%
+\subsubsection{Temporal eligibility}%
 \label{analysis-temporal}
@@
 
-\paragraph{Linkability}%
+\subsubsection{Linkability}%
 \label{analysis-linkability}
@@
 
-\paragraph{Spatial eligibility}%
+\subsubsection{Spatial eligibility}%
 \label{analysis-spatial}
 
-\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed on the location when the proof share was created.
+\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed at the location when the proof share was created.
 To realize this, we must ensure that Alice cannot forge witness signatures.
@@
 As above, the latter could be done if she can find people willing to collude, 
-people unwilling to collude but she can illicitly use their keys anyway or 
+or whose keys she illicitly can use anyway, or 
 simply request new keys from the \ac{CA}.
 
-We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
-witnesses.
-Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
-cheating.
-(Note that Alice can produce \emph{one} witness signature for herself, since 
-she has access to her own \(\sk_P\), but no more.
-Thus, \(\theta > 1\) is a requirement in the trust-free case.)
+% We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
+% witnesses.
+% Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
+% cheating.
+% (Note that Alice can produce \emph{one} witness signature for herself, since 
+% she has access to her own \(\sk_P\), but no more.
+% Thus, \(\theta > 1\) is a requirement in the trust-free case.)
 
-In the trusted witness case, we assume that we can trust (dedicated) witnesses.
-In this case, Alice must be able to forge statements, \eg digital signatures, 
+The strength function from ~\cref{DefParticipationCount} ensures that
+Alice either has to collude with \(\theta - 1\) witnesses (she can
+produce \emph{one} witness signature for herself, since she has access
+to her own \(\sk_P\), but no more) or, in the trusted witness case,
+that Alice must be able to forge statements, \eg digital signatures,
 from at least one witness that the verifier trusts.
 
-\paragraph{Designated protest}%
+\subsubsection{Designated protest}%
 \label{analysis-designated}
@@
 \(\AC \neq \AC*\) are separate anonymous-credential systems.)
+
+\subsection{Individual and universal verifiability}%
+\label{analysis-individual}%
+\label{analysis-universal}
+
+\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
+that their participation proofs (\ie proof shares) are indeed included in the 
+computed count.
+All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
+  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
+available from a public and permanent storage.
+Thus, Alice and Bob can simply check that all of their proof shares are indeed 
+there and the security of individual verifiability depends on the properties of 
+the ledger and storage (\(\TS\), \cref{timestamp}).
+For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
+an honest-but-curious adversary controlling \(\TS\)\footnote{%
+  We note that, in general, distributed (decentralized) ledgers cannot 
+  withstand a malicious \ac{ISP}.
+  Such an adversary can partition the network and provide Alice and Bob with 
+  different views of the ledger, thus breaking individual verifiability.
+  However, this requires that the adversary \emph{can observe} Alice's and 
+  Bob's channels to the ledger --- which is still not true even for 
+  \cref{deanonymizing-storage-adversary}.
+}.
+This means that Alice can check that her proof share is indeed there.
+
+\Cref{UniversalVerif} implies that anyone can check the result and that all 
+participation proofs counted are legitimate.
+As the proof shares are committed and stored publicly, anyone can
+download them, verify eligibility (\ie verify \(\corr_\pid,
+\corr_{\wid}\)) of the proofs and count them.
+As for individual verifiability, the security of universal verifiability is 
+reduced to the properties of the ledger and storage; but universal 
+verifiability also depends on the eligibility verification.

### 2018-11-30 paper/privacy-analysis.tex
Fixes typo
moves timestamp uniquness problem/solution from analysis to building block

@@
 
-We start with \cref{ProtestUnlink}, that Alice's proofs must be unlinkable across protests but linkable within one protest due to \cref{CountOnce}.
-It follows from the properties of \(\ACprf\) that \(\pid =  \ACprf[_{\sk_P}][\cid]\) and \(\pid' = \ACprf[_{\sk_P}][\cid']\) are unlinkable if \(\cid\neq \cid'\).
+We start with \cref{PseudonymUnlink}.
+Given \(\pid\), \cref{in-system-adversary} cannot distinguish whether \(\pid = 
+  \ACprf[_{\sk_A}][\cid]\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the 
+properties of \(\AC\) (see~\cite{HowToWinTheCloneWars}).
+This is not necessarily true for \cref{deanonymizing-storage-adversary}:
+if everyone uploads their own proof shares\footnote{%
+  This is probable due to the proof-of-correctness, \(\corr_\pid\), which is 
+  likely computed after the protest has ended.
+}, \cref{deanonymizing-storage-adversary} will link \(P\) and \(\pid\), and 
+consequently \(P\) and \(\cid\).
 
-Afterwards to get the property \cref{ProofUnlink}.
-Given \(\pid\), Grace cannot distinguish whether \(\pid = \ACprf[_{\sk_A}][\cid]\), \(\pid = \ACprf[_{\sk_A}][\cid']\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the properties of \(\AC\).
+\Cref{ProtestUnlink}, Alice's proofs must be unlinkable across protests.
+This also follows from the properties of 
+\(\ACprf\)~\cite{HowToWinTheCloneWars}: \(\pid =  \ACprf[_{\sk}][\cid]\) and 
+\(\pid' = \ACprf[_{\sk}][\cid']\) (where \(\cid \neq \cid'\)) are unlinkable 
+from the perspective of \cref{in-system-adversary}.
+This is not true for \cref{deanonymizing-storage-adversary}: since 
+\cref{deanonymizing-storage-adversary} can link \(\pid, P\) and \(\pid', P\); 
+then \cref{deanonymizing-storage-adversary} can link \(\pid, \pid'\) too, thus 
+violating \cref{ProtestUnlink}.
+In the same way, \cref{deanonymizing-storage-adversary} can violate 
+\cref{WitnessUnlink}.
 
-However, consider the situation in which the witness works for Grace.
-This witness interacts with Alice directly and might have (physically) identified her.
-The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) and to verify the \ac{PPK}.
-\daniel{This assumes that I will do the changes to hide \(\cid\) from the witness in the \ac{PPK}.}
-Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
-share.
-The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
-  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
-\daniel{Fix this.}
-If this occurs, Grace could link \(\cid\) (and thus the opinions in the manifesto) to Alice.
+However, the statement about \cref{ProtestUnlink,in-system-adversary} is not 
+necessarily true for \cref{WitnessUnlink,in-system-adversary}.
+The proof shares consist of more than only \(\cid, \pid, \wid\); more 
+specifically, each proof share is a tuple \((\cid, \pid, \wid, t_s, t_s', l, 
+  \corr_\pid, \corr_\wid)\).
+Let \(\cid\) be fixed, then \(\pid\) is a unique identifier for \(P\).
 
-\sonja{anonymity and cause unlinkability missing}
+We assume that the location \(l\) is coarse enough so that many non-overlapping 
+\((\pid, \wid)\)-pairs use the same location.
+Thus \(l\) is not unique for any individual (protester or witness).
+This implies some degree of \(k\)-anonymity for the location \(l\).
+
+Likewise, thanks to the constraints in the time-stamp granularity,
+\(t\) is not unique.

### 2018-11-30 paper/timestamp.tex
moves timestamp uniquness problem/solution from analysis to building block

@@
   \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
+\item the time stamp is chosen at a low enough rate to not be unique, \eg by using only every \(n\)th block from the underlying ledger.
 \end{itemize}
@@
 The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
-The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] > t_0\land 
-  \TStime[\pi_{t_1}] < t_1\).
+The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
+\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] \geq t_0\land 
+  \TStime[\pi_{t_1}] \leq t_1\).
 
@@
 For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.
+
+% Since \(\pid\) uniquely identifies \(P\), then if \(t_s^{(\pid)}\) is 
+% \enquote{unique enough}\footnote{%
+%   This can be verified thanks to \cref{CountOnce}.
+%   If there are no tuples \((\pid, t_s)\) and \((\pid, t_s')\) among the proof 
+%   shares such that \(\pid \neq \pid'\) but \(t_s = t_s'\), then \(t_s\) also 
+%   \emph{likely} uniquely identifies \(P\).
+%   \enquote{Likely} depends on the likelihood of there being witnesses who are 
+%   not protesters.
+% }, every \(\wid\) for which \(t_s' = t_s^{(\pid)}\) is \emph{likely} to be 
+% \(P\) acting as a witness.
+% This would allow \cref{in-system-adversary} to link \(\wid, \wid'\) for 
+% different protesters, thus violating \cref{WitnessUnlink}.
+% (The same can be said of \(\pid\) and \cref{ProtestUnlink} if there are 
+% multiple protests, \ie \(\cid\)'s, at the same time and location.
+% However, we deem this as unlikely.)
+
+% Distribution of \(t_s\) depends on the rate of \(\TSget\) and the distribution 
+% of when participants run the algorithm the last time.
+% For example, if we use a six-hour interval and a rate of one new value per 
+% minute, then there are potentially 21600 unique values for \(t_s\).
+% However, we can scale this down by a factor \(n\) by requiring \(\TSget\) to 
+% use only every \(n\)th block from the underlying ledger.
+% Thus it seems reasonable that \(t_s\) will never be \enquote{unique enough}.

### 2018-11-30 paper/analysis-performance.tex
Replaces \paragraph with \subsubsection where necessary
comments out our DB in performance, threshold computations in ledger subsection

--- 2018-11-20 paper/analysis-performance.tex
@@
-\section{Performance and implementation}
+\section{Performance}
 \label{PerformanceAnalysis}
@@
 The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
-One of the short-term objectives is to be able to integrate them in phones or smartcards in the near-future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
+One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
 For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
@@
 
-With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
-The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
-This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
+% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
+% The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
+% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
 %Seb: to do add the reference to the following paper at the end of the sentence:
@@
 %for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
-Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
-However, this can be reduced to four random number generations and one exponentiation using precomputation.
+% Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
+% However, this can be reduced to four random number generations and one exponentiation using precomputation.
 
@@
 While this already takes longer than counting votes in national elections, the threshold is still very low. 
-Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
-If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
-In addition to the ledger computation, we need to consider the creation of the proof shares.
+% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
+% In addition to the ledger computation, we need to consider the creation of the proof shares.
 \sonja{added the previous sentence to explain why anonpass shows up here.
@@
 }
-%Seb: I agree maybe we should move it to the previous subsection
-According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
-This yields \(
-  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-  \SI{48}{\second}.
-\) of processing. 
+% %Seb: I agree maybe we should move it to the previous subsection
+% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
+% This yields \(
+%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+%   \SI{48}{\second}.
+% \) of processing. 
 For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
-Considering that online forums can facilitate mass coordination, the threshold approach seems not only inefficient but also potentially ineffective for verifiability.
+Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
 

### 2018-11-30 paper/protocol.tex
Puts long math on own line

@@
 The protocol consists of three phases:
-before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
-during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
+before the protest, with the setup and registration steps (\cref{ProtocolSetup});
+during the protest, with the creation, join, participation, and submission 
+steps (\cref{ProtocolDuring});
 and after the protest, with the verification step (in
 \cref{ProtocolVerification}). Note that some of the figures with
-protocol minutae from related work are in the
-appendix.
+protocol minutiae from related work are in~\cref{anon-cred-figures}.
 
@@
 First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
-person's identity and a cryptographic key\footnote{%
-  This can be done by a centralized authority, such as a nation state with, 
-  \eg, passports; or a decentralized authority, as in the case of a a 
+person's identity and a cryptographic key
+%\footnote{%
+%  This can be done by a centralized authority, such as a nation state with, 
+%  \eg, passports; or a decentralized authority, as in the case of a a 
+%  collective authority~\cite{collective-signing} powered by 
+%  proof-of-personhood~\cite{proof-of-personhood}.
+%}.
+For simplicity, we assume that the \ac{CA} is a trusted third-party, but its role is only important to prevent Sybil attacks, so in practice we only need the \ac{CA} to not be aligned with the protesters.
+For instance, the role of the \ac{CA} can be assumed by a centralized authority, such as a nation state with,
+\eg, passports, and that would not impact the trust of a participation count for a protest \emph{against} this state.
+However, any pro-state demonstration in that context would be subject to Sybils.
+Another possibility would be to use a decentralized authority, as in the case of a
 collective authority~\cite{collective-signing} powered by 
 proof-of-personhood~\cite{proof-of-personhood}.
-}.
 The \ac{CA} is only involved in the setup phase.
+
 Second, a participant is an individual who wants to participate in a given 
@@
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
-
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
 The protester sends \(\pid\) to the witness.
-Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
-    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
+Then they run the protocol \[
+  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
+\] (see \cref{ACacAlg}).
 Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
@@
 Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
-and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
-Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.
+and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
+Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationCount}.
 
@@
 publish or otherwise inform the 
-verifier of which proof shares she has signed, \eg by giving a list 
+verifier of which proof shares they have signed, \eg by giving a list 
 of all such proof shares or digitally signing each proof share\footnote{
@@
 
-Note that anyone who does the counting can choose the eligibility
+Note that, thanks to the \((\str,\theta)\)-eligibility criterion (\cref{DefParticipationCount}), the method of counting is extremely generic, and each verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses.
+In other words, anyone who does the counting can choose the eligibility
 criteria (time interval, location, number of regular or trusted
-witnesses, who is considered to be a trusted witness) for their count
+witnesses, who is considered to be a trusted witness) for their own count
 and as long as these are published along with the result, anyone can
-verify the correctness under those criteria.
+verify the correctness of the count under those criteria, and potentially question the validity of this choice.
+Biased or partisan verifiers may be tempted to make extreme choices, but they will have to publish those choices and lose credibility.
+Reasonable verifiers on the other hand will try to find a good middle-ground that counts all legitimate protesters while being resistant to isolated malicious agents.
 

### 2018-11-30 paper/conclusions.tex

@@
 
-In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
-Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
-%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
-%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
-}
-%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
-\sonja{update sec analysis results}
+In this paper, we have introduced \CROCUS, a privacy-preserving protocol for 
+verifiably counting participants at protests.
+Despite the verification, the privacy of the participants is preserved to the 
+extent possible by their physical presence at the protest.
 
-%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
-%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
-%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
+We showed that \CROCUS preserves privacy and that the only privacy-threat it 
+adds to protesting without it, is that Grace can use Alice's private key to 
+verify her participation.
+However, this requires that Grace already suspects Alice --- Grace cannot check 
+everyone --- and that Alice has not renewed her digital certificate.
 
-% In general, none of the related works fulfills the eligibility
-% verifiability (one proof per person, temporal and spatial eligibility ---
-% \cref{%
-%   CountOnce,%
-%   TemporallyRelated,SpatiallyRelated,%
-% }).
-% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
-% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
-% Moreover, if they provided individual verifiability, they would likely violate 
-% the privacy requirements --- if people must recognize themselves in photos, 
-% others can recognize them too.
-% Finally, most of the current methods are estimates, with quite some error margins. 
-While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
-However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
-While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
-We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and counter fake news.
+We also showed that \CROCUS provides universally verifiable data.
+With \CROCUS, a journalist can easily count the participation, specify how they 
+counted (time, location \etc) along with the result and everyone can 
+independently verify that the result is correct.
+The only results that cannot be trusted are results aligned with the interests 
+of the \ac{CA}.
+
+%To achieve \CROCUS, we adapted the Schnorr protocol as a distance-bounding 
+%protocol.
+%This is of separate interest, as it allows to construct distance-bounding 
+%general attribute-based authentication, more general attributes than provided 
+%by previous \ac{DB} ones.
+%With our contribution, Alice can now prove more complex statements to Bob; \eg  
+%that she is older than 18 but younger than 40 without revealing her actual 
+%age, and at the same time Bob can be sure that Alice is not just relaying 
+%messages from her older sister Carol.
+
+While \CROCUS is an actual count and not an estimate, its accuracy for the 
+total number of participants hinges on the participants having the necessary 
+equipment (\ie a smartphone or similar device), some sort of trustworthy 
+credential, and the willingness to run the protocol. Owing to the network 
+effect, until used by most participants, \CROCUS would result in a considerable 
+undercount. However, it represents a first step toward accurate verifiable yet 
+privacy-preserving crowd counting by showing how it can be done in theory at 
+least and in practice once some assumptions concerning hardware and 
+e-identities become more realistic. While the necessary technologies are not 
+yet available in most authoritarian regimes, some of them are in several 
+democracies. We believe that it is important to implement systems such as ours 
+also there to support the maintenance of democratic processes and counter fake 
+news.

### 2018-11-30 paper/protocol.tex
adds references to appendices
integrating trust assumptions in the body of the paper

@@
 The protocol consists of three phases:
-before the protest, with the setup and registration steps (\cref{ProtocolSetup});
-during the protest, with the creation, join, participation, and submission 
-steps (\cref{ProtocolDuring});
+before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
+during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
 and after the protest, with the verification step (in
@@
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
+
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
 The protester sends \(\pid\) to the witness.
-Then they run the protocol \[
-  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
-\] (see \cref{ACacAlg}).
+Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
+    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
 Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.

### 2018-11-30 paper/conclusions.tex

--- 2018-11-29 paper/conclusions.tex
@@
 In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
-Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
+Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat.
+Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker.
+For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone.
+This potential difference can thus be considered the price for verifiability.
+Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.
+
 %To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:

### 2018-11-30 paper/conclusions.tex
edits conclusions

--- 2018-11-29 paper/conclusions.tex
@@
 In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests.
-Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
+
+We showed that \CROCUS provides universally verifiable data.
+With \CROCUS, a journalist can easily count the participation, specify how they 
+counted (time, location \etc) along with the result and everyone can 
+independently verify that the result is correct.
+The only results that cannot be trusted are results aligned with the interests 
+of the \ac{CA}.
+
+Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat.
+Grace, the government in our protest scenario, can coerce Alice in some way to reveal her private key and then use it to verify her participation.
+However, this requires that Grace already suspects Alice --- Grace cannot check everyone --- and that Alice has not renewed her digital certificate.
+
+% Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker.
+For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone.
+This potential difference can thus be considered the price for verifiability.
+Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.
+
 %To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
@@
 %With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
-\sonja{update sec analysis results}
 
@@
 While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
+Owing to the flip side of the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
 However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
 While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
-We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and counter fake news.
+We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and increase transparency.

### 2018-11-30 paper/timestamp.tex
Adds that we prefer to share the blockchain with other services

@@
 If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
-The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
+The \(\TSget\) request returns the hash of the most recent block of the chain 
+(\ie the head).%
 \footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
@@
 
-Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
+Regarding consensus resilience, it is advisable to use a blockchain with a high 
+number of participants and preferably sharing the blockchain with other 
+services.
 The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
@@
 In both cases, assuming a majority of honest members in the population, the more participants the merrier.
+We want to share the blockchain with other services due to privacy (and 
+anti-censorship) reasons, analogous to the idea of \enquote{domain fronting}.
 

### 2018-11-30 paper/privacy-analysis.tex
adds a summary sentence at the end of the security evaluation to not have the part of Grace using Alice's private key pop up in the conclusion.

@@
 \(t\) is not unique.
+
+Overall, informally, the digital trace needed for verifiability in \CROCUS could
+conceivably be used to strengthen a suspicion of
+participation. Given A2's (Grace's) inferences from auxiliary information that points
+to Alice having participated in a protest, for example pictures at the
+event, with face recognition and subsequent identification, IP address
+of her home router, etc., then any remaining uncertainty from false
+positives could be reduced by learning from data on the ledger and
+Alice's smartphone. %This potential difference can thus be considered
+                    %the price for verifiability.
+For confirmation of that suspicion, Grace would have to get access to
+and use Alice's private key.

### 2018-11-30 paper/privacy-analysis.tex
Edits privacy analysis

--- 2018-11-30 paper/privacy-analysis.tex
@@
 from the perspective of \cref{in-system-adversary}.
-This is not true for \cref{deanonymizing-storage-adversary}: since 
+The argument is the same for \cref{WitnessUnlink}.
+The same is not true for \cref{deanonymizing-storage-adversary}: since 
 \cref{deanonymizing-storage-adversary} can link \(\pid, P\) and \(\pid', P\); 
@@
 
-However, the statement about \cref{ProtestUnlink,in-system-adversary} is not 
-necessarily true for \cref{WitnessUnlink,in-system-adversary}.
 The proof shares consist of more than only \(\cid, \pid, \wid\); more 
@@
   \corr_\pid, \corr_\wid)\).
-Let \(\cid\) be fixed, then \(\pid\) is a unique identifier for \(P\).
-
 We assume that the location \(l\) is coarse enough so that many non-overlapping 
 \((\pid, \wid)\)-pairs use the same location.
-Thus \(l\) is not unique for any individual (protester or witness).
-This implies some degree of \(k\)-anonymity for the location \(l\).
-
+After all, it is the location of the protest, not the location within the 
+protest that is interesting.
+Thus \(l\) is not uniquely identifying any individual protester or witness.
 Likewise, thanks to the constraints in the time-stamp granularity,
-\(t\) is not unique.
+\(t\) is not uniquely identifying either.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
Adds first PoPETS rebuttal draft

Reviewer 1

1)
a) Therefore anonymous credentials and unlinkability properties: the central authority cannot tell participants from non-participants without extreme measures which are equivalent to arresting people at the protest. Arguably, the chilling effects with this system are no more than that of protests alone already.

b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias. Those who verify results must apply the standard source criticism. e.g. as for detecting bias in scientific research.

2) Petitions have been viable for a long time, but people arrange protests anyway. Our scheme allows for both anonymous verifiable petitions (skip location) and protests (time and location matter).

3) Agreed, but we need all parts.

4) Agreed, we need to present the adversaries better. A2 was to show limitations. Grace can already now make examples of people; crocus cannot make physical protests safer, we only want to not make it worse.

5) That’s the reason for distance bounding. Then any witness will know that it’s within a given distance from the witness’ own position. Why a verifier accepts this is up to the trust assumptions: we give two cases, the verifier trusts the particular witness; or the verifier “trusts” that a threshold of witnesses is probably true.

6) Trusted by a verifier. Anyone can define whom they trust and how they counted. We _do_ use trusted witnesses for counting.

7) Strength: yes.

Reviewer 2

Definitions not entirely formal: working on it.

Single participant gathering proof shares for friends: The distance bounding prevents this being done by relaying messages. The terrorist-fraud assumption from distance bounding also prevents giving the private key (or phone containing it) to someone: the private keys are part of the long-term ID credential, if this ID can be used for other things, as pointed out by Reviewer 1, then you will not allow just anyone to use it.

Reviewer 3)

1) Yes, following the standard assumption in distance bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).  We will look into the possibilities of functional encryption, that might actually violate the terrorist-fraud assumption.

2) This extreme case where no type of wireless communication works, not even the short range needed here, is possible but not heard of. Perhaps NFC could help.

3) No principled way given online mobs, but different counts are possible and as long as the parameters are published, the counts can be verified. Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the eyes of the verifier.

4) 5G is built for scale but currently not for the D2D scenario; again, NFC is 
an option.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
Updates rebuttal about functional encryption

@@
 
-Reviewer 3)
+Reviewer 3
 
-1) Yes, following the standard assumption in distance bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).
-We will look into the possibilities of functional encryption, that might actually violate the terrorist-fraud assumption.
+1) Yes, following the standard assumption in distance bounding to prevent 
+terrorist fraud (which is distance-bounding terminology for this particular 
+case).
+
+Functional encryption will not work against an honest verifier in the general 
+case. We are working on a distance bounding protocol (it requires a separate 
+paper) and in that scheme the private key can be computed by joining two 
+different outputs from the functional encryption of the private key. Hence it's 
+reduced to the terrorist-fraud case again.
 

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
adds remarks about performance and formalization

@@
 
-Definitions not entirely formal: working on it.
+Definitions not entirely formal: if there are specific parts that should be more formalized, we'll be happy to work on that.
 
@@
 
-4) 5G is built for scale but currently not for the D2D scenario; again, NFC is 
-an option.
+4) 5G is built for scale but currently not for the D2D scenario
+without provider; again, NFC is an option. For overall performance, we
+could evaluate AnonPass on phones, example distance-bounding
+computation, collect density and scalability from the literature
+(protests and wireless), and measure NFC delays, if you deem it
+useful.

### 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
update of the rebuttal

--- 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
@@
 
-1)
-a) Therefore anonymous credentials and unlinkability properties: the central authority cannot tell participants from non-participants without extreme measures which are equivalent to arresting people at the protest.
-Arguably, the chilling effects with this system are no more than that of protests alone already.
+1) a) Due to the use of anonymous credentials, the central authority cannot tell participants from non-participants without extreme measures equivalent to arresting people at the protest.
+Arguably, the chilling effects with this system are no more than that of "standard" protests.
+To mitigate the risk of having a central authority responsible the IDs, we could also replace it by a distributed version composed of several independent entities that simulate the work of the central authority is a distributed and private manner.
 
 b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias.
-Those who verify results must apply the standard source criticism.
-e.g.
-as for detecting bias in scientific research.
+In particular, those who verify results must apply the standard source criticism.
+(e.g., for detecting bias in scientific research).
 
-2) Petitions have been viable for a long time, but people arrange protests anyway. Our scheme allows for both anonymous verifiable petitions (skip location) and protests (time and location matter).
+2) Petitions have been viable for a long time but people still arrange protests anyway, in part because going physically to a protest in a sense shows much more involvment.
+Our scheme allows for both anonymous verifiable petitions (not considering location) and protests (time and location matter).
 
-3) Agreed, but we need all parts.
+3-4) We acknowledge that the design of the architecture is complex but we need all parts to reach the desired security and privacy properties.
+To improve the clarity of the paper, we agree that we need to present the adversaries better.
+The objective of introducing A2 was to show the limitations of our approach.
+While Crocus cannot make physical protests safer, we wanted to ensure that it does make it worse.
 
-4) Agreed, we need to present the adversaries better.
-A2 was to show limitations.
-Grace can already now make examples of people; crocus cannot make physical protests safer, we only want to not make it worse.
+5) This is the main reason for distance-bounding as it allows the witness to verify that it is within a given distance from the prover.
+Why a verifier accepts this claim is up to the trust assumptions for which we provide two cases.
+One in which the verifier trusts a particular witness and the other in which the verifier believes that a threshold of witnesses has been reached.
 
-5) That’s the reason for distance bounding.
-Then any witness will know that it’s within a given distance from the witness’ own position.
-Why a verifier accepts this is up to the trust assumptions: we give two cases, the verifier trusts the particular witness; or the verifier “trusts” that a threshold of witnesses is probably true.
-
-6) Trusted by a verifier. Anyone can define whom they trust and how they counted. We _do_ use trusted witnesses for counting.
+6) Trusted by a verifier. Anyone can define whom they trust and how they want to be counted. We _do_ use trusted witnesses for counting.
 
@@
 
-Definitions not entirely formal: working on it.
+If there are specific parts that should be more formalized, we will be happy to do this in the revised version of the paper.
 
-Single participant gathering proof shares for friends: The distance bounding prevents this being done by relaying messages.
-The terrorist-fraud assumption from distance bounding also prevents giving the private key (or phone containing it) to someone: the private keys are part of the long-term ID credential, if this ID can be used for other things, as pointed out by Reviewer 1, then you will not allow just anyone to use it.
+With respect to a single participant gathering proof shares for friends, distance-bounding prevents this to be done by relaying messages.
+In addition, the terrorist-fraud assumption also prevents a user giving his private key (or phone containing it) to someone.
+This is realistic in scenario in which the private keys are part of the long-term ID credential.
+In particular as pointed out by reviewer 1 if this ID can be used for other things, you will not allow just anyone to use it.
 
-Reviewer 3)
+Reviewer 3
 
-1) Yes, following the standard assumption in distance bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).
-We will look into the possibilities of functional encryption, that might actually violate the terrorist-fraud assumption.
+1) Yes, it follows the standard assumption in distance-bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).
 
-2) This extreme case where no type of wireless communication works, not even the short range needed here, is possible but not heard of. Perhaps NFC could help.
+Functional encryption will not work against an honest verifier in the general case.
+We are working on a distance-bounding protocol (in preparation for a separate paper) in which the private key can be computed by joining two different outputs from the functional encryption of the private key, which reduced to the terrorist-fraud case again.
 
-3) No principled way given online mobs, but different counts are possible and as long as the parameters are published, the counts can be verified.
-Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the eyes of the verifier.
+2) This extreme case in which no type of wireless communication works is possible but unheard of. However, it could be potentially solve by using NFC capabilities for instance.
 
-4) 5G is built for scale but currently not for the D2D scenario; again, NFC is 
-an option.
+3) There is principled way given online mobs, but different counts are possible.
+As long as these parameters are published, the counts can be verified.
+Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the verifier's eyes.
+
+4) 5G is built for scale but currently not for the D2D scenario without provider but again NFC is an option.
+For overall performance, we could evaluate AnonPass on phones, example distance-bounding computation, collect density and scalability from the literature (protests and wireless), and measure NFC delays, which we could do if deemed useful by the reviewers.

### 2019-01-11 paper/reviews/popets-2019.3-rebuttal.md
Edits rebuttal

@@
 
-1) a) Due to the use of anonymous credentials, the central authority cannot tell participants from non-participants without extreme measures equivalent to arresting people at the protest.
-Arguably, the chilling effects with this system are no more than that of "standard" protests.
-To mitigate the risk of having a central authority responsible the IDs, we could also replace it by a distributed version composed of several independent entities that simulate the work of the central authority is a distributed and private manner.
+1) a) Due to the use of anonymous credentials, the central authority cannot 
+tell participants from non-participants without extreme measures equivalent to 
+arresting people at the protest. Arguably, the chilling effects with this 
+system are no more than that of "standard" protests.
 
-b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias.
-In particular, those who verify results must apply the standard source criticism.
-(e.g., for detecting bias in scientific research).
+To mitigate the risk of having a central authority responsible the IDs, we 
+could also replace it by a distributed version composed of several independent 
+entities that simulate the work of the central authority in a distributed and 
+private manner.
 
-2) Petitions have been viable for a long time but people still arrange protests anyway, in part because going physically to a protest in a sense shows much more involvment.
-Our scheme allows for both anonymous verifiable petitions (not considering location) and protests (time and location matter).
+b) Yes, but the paper also notes that those are detectable and should be 
+ignored due to their obvious bias. In particular, those who verify results must 
+apply standard source criticism. (c.f., detecting bias in scientific research).
 
-3-4) We acknowledge that the design of the architecture is complex but we need all parts to reach the desired security and privacy properties.
-To improve the clarity of the paper, we agree that we need to present the adversaries better.
+2) Petitions have been viable for a long time but people still arrange protests 
+anyway, in part because going physically to a protest in a sense shows much 
+more involvment. Our scheme allows for both anonymous verifiable petitions (not 
+considering location) and protests (time and location matter).
+
+3-4) We acknowledge that the design of the architecture is complex but we need 
+all parts to reach the desired security and privacy properties. To improve the 
+clarity of the paper, we agree that we need to present the adversaries better. 
 The objective of introducing A2 was to show the limitations of our approach. 
-While Crocus cannot make physical protests safer, we wanted to ensure that it does make it worse.
+While CROCUS cannot make physical protests safer, we wanted to ensure that it 
+does make it worse.
 
-5) This is the main reason for distance-bounding as it allows the witness to verify that it is within a given distance from the prover.
-Why a verifier accepts this claim is up to the trust assumptions for which we provide two cases.
-One in which the verifier trusts a particular witness and the other in which the verifier believes that a threshold of witnesses has been reached.
+5) This is the main reason for distance-bounding as it allows the witness to 
+verify that it is within a given distance from the prover.  Why a verifier 
+accepts this claim is up to the trust assumptions for which we provide two 
+cases. One in which the verifier trusts a particular witness and the other in 
+which the verifier believes that collusion beyond a threshold is not likely.
 
-6) Trusted by a verifier. Anyone can define whom they trust and how they want to be counted. We _do_ use trusted witnesses for counting.
+6) Trusted by a verifier. Anyone can define whom they trust and how they want 
+to be counted. We _do_ use trusted witnesses for counting.
 
@@
 
-If there are specific parts that should be more formalized, we will be happy to do this in the revised version of the paper.
+If there are specific parts that should be more formalized, we will be happy to 
+do this in the revised version of the paper.
 
-With respect to a single participant gathering proof shares for friends, distance-bounding prevents this to be done by relaying messages.
-In addition, the terrorist-fraud assumption also prevents a user giving his private key (or phone containing it) to someone.
-This is realistic in scenario in which the private keys are part of the long-term ID credential.
-In particular as pointed out by reviewer 1 if this ID can be used for other things, you will not allow just anyone to use it.
+With respect to a single participant gathering proof shares for friends, 
+distance-bounding prevents this. In addition, the terrorist-fraud assumption 
+also prevents a user giving his private key (or phone containing it) to 
+someone. This is realistic in scenario in which the private keys are part of 
+the long-term ID credential. In particular as pointed out by reviewer 1 if this 
+ID can be used for other things, you will not allow just anyone to use it.
 
@@
 
-1) Yes, it follows the standard assumption in distance-bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).
+1) Yes, it follows the standard assumption in distance-bounding to prevent 
+terrorist fraud (which is distance-bounding terminology for this particular 
+case).
 
-Functional encryption will not work against an honest verifier in the general case.
-We are working on a distance-bounding protocol (in preparation for a separate paper) in which the private key can be computed by joining two different outputs from the functional encryption of the private key, which reduced to the terrorist-fraud case again.
+Functional encryption will not work against a verifier who performs the 
+distance-bounding. We are working on a distance-bounding protocol (in 
+preparation for a separate paper) in which the private key can be computed by 
+joining two different (required) outputs from the functional encryption of the 
+private key, the terrorist-fraud assumption prevents this.
 
-2) This extreme case in which no type of wireless communication works is possible but unheard of. However, it could be potentially solve by using NFC capabilities for instance.
+2) This is an extreme case: it's possible that an adversary can jam signals for 
+wireless communication, but it's unheard of. However, it could be potentially 
+mitigated by using e.g. NFC.
 
-3) There is principled way given online mobs, but different counts are possible.
-As long as these parameters are published, the counts can be verified.
-Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the verifier's eyes.
+3) There is principled way given online mobs, but different counts are 
+possible. As long as these parameters are published, the counts can be 
+verified. Requests for sizeable collusion are made in public, which risk being 
+found by the verifier --- thus invalidating the count in the verifier's eyes.
 
-4) 5G is built for scale but currently not for the D2D scenario without provider but again NFC is an option.
-For overall performance, we could evaluate AnonPass on phones, example distance-bounding computation, collect density and scalability from the literature (protests and wireless), and measure NFC delays, which we could do if deemed useful by the reviewers.
+4) 5G is built for scale but currently not for the D2D scenario without 
+provider, but again NFC is an option. For overall performance, we could 
+evaluate AnonPass on phones, example distance-bounding computation, collect 
+density and scalability from the literature (protests and wireless), and 
+measure NFC delays, which we could do if deemed useful by the reviewers.

### 2019-01-11 paper/reviews/popets-2019.3-rebuttal.md
Adds # to mark reviewers' sections more clearly
Fixes typo

@@
-Reviewer 1
+# Reviewer 1
 
@@
 anyway, in part because going physically to a protest in a sense shows much 
-more involvment. Our scheme allows for both anonymous verifiable petitions (not 
-considering location) and protests (time and location matter).
+more involvement. Our scheme allows for both anonymous verifiable petitions 
+(not considering location) and protests (time and location matter).
 
@@
 
-Reviewer 2
+# Reviewer 2
 
@@
 
-Reviewer 3
+# Reviewer 3
 

### 2019-02-05 paper/location-proofs.tex

--- 2018-08-17 paper/location-proofs.tex
@@
 However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location.
-\PRIVO shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+\CROCUS shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
+\sonja{any more differences to ours, relevance of this one?} \sonja{add something on platin.io, details unknown but roughly relying on witnesses and graph theory (unique big cluster, assumption of honest majority)}

### 2019-02-05 paper/privacy-analysis.tex

--- 2018-11-30 paper/privacy-analysis.tex
@@
 
-Likewise, thanks to the constraints in the time-stamp granularity,
-\(t\) is not unique.
+Since \(\pid\) uniquely identifies \(P\), then if \(t_s^{(\pid)}\) is 
+\enquote{unique enough}\footnote{%
+  This can be verified thanks to \cref{CountOnce}.
+  If there are no tuples \((\pid, t_s)\) and \((\pid, t_s')\) among the proof 
+  shares such that \(\pid \neq \pid'\) but \(t_s = t_s'\), then \(t_s\) also 
+  \emph{likely} uniquely identifies \(P\).
+  \enquote{Likely} depends on the likelihood of there being witnesses who are 
+  not protesters.
+}, every \(\wid\) for which \(t_s' = t_s^{(\pid)}\) is \emph{likely} to be 
+\(P\) acting as a witness.
+This would allow \cref{in-system-adversary} to link \(\wid, \wid'\) for 
+different protesters, thus violating \cref{WitnessUnlink}.
+(The same can be said of \(\pid\) and \cref{ProtestUnlink} if there are 
+multiple protests, \ie \(\cid\)'s, at the same time and location.
+However, we deem this as unlikely.)
+
+Distribution of \(t_s\) depends on the rate of \(\TSget\) and the distribution 
+of when participants run the algorithm the last time.
+For example, if we use a six-hour interval and a rate of one new value per 
+minute, then there are potentially 21600 unique values for \(t_s\).
+However, we can scale this down by a factor \(n\) by requiring \(\TSget\) to 
+use only every \(n\)th block from the underlying ledger.
+Thus it seems reasonable that \(t_s\) will never be \enquote{unique enough}.

### 2019-02-05 paper/protocol.tex
Changes commas to semi-colons in enumeration
Removes wrongful paragraph break

--- 2018-11-30 paper/protocol.tex
@@
-%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The \CROCUS Protocol}
+\section{\CROCUS:\@ A protocol for crowd counting estimation}%
 \label{Protocol}
 
-We now present \CROCUS, a protocol for privately verifiable crowd counts.
-The protocol consists of three phases:
-before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
-during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
-and after the protest, with the verification step (in
-\cref{ProtocolVerification}). Note that some of the figures with
-protocol minutae from related work are in the
-appendix.
+We now present \CROCUS, a protocol for privately verifyiable crowd counts.
+The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
+join, participation, submission (all in in \cref{ProtocolDuring}) and
+verification (in \cref{ProtocolVerification}).
 
 Several entities are involved in our protocol.
-First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
+First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
 person's identity and a cryptographic key\footnote{%
@@
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
+\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
-  for their presence.
+  for his presence.
 \item A \emph{witness} provides proofs to protesters which state that the 
-  protester was indeed participating, constructed such that the proofs are verifiable by 
+  protester was indeed participating and such that the proofs are verifiable by 
   third parties.
 \end{enumerate}
-In general, there is one organizer and every participant can act as
-either or both protester and witness.
+In general, there is one organizer and every participant can act alternatively 
+as both protester and witness.
 
-\subsection{Pre-protest phase}%
+\subsection{Setup phase}%
 \label{ProtocolSetup}
 
-The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
-More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
+The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
+More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.
 
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
-
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
     \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration step, each participant generates a secret key and 
+During the registration phase, each participant generates a secret key and 
 obtains a signature on it by the \ac{CA} but without revealing it to the 
@@
 
-The setup and registration steps can be done once and the keys can be reused 
+The setup and registration phases can be done once and the keys can be reused 
 for an arbitrary number of protests.
-Thus, the registration step could be easily integrated as part of the issuance 
+Thus, the registration phase could be easily integrated as part of the issuance 
 of national identity cards, passports or \acp{eID}.
 
-\subsection{Protest phase}%
+\subsection{Creation, join and participation in a protest and submission of proofs}%
 \label{ProtocolDuring}
 
-%The join, participation and submission phases are as follows.
-% illustrated in \cref{fig:ProtocolOverview}.
+The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
+The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.
 
-The participation proof share constructed in the
-participation phase is illustrated in \cref{fig:ProofFig}.
+\emph{Creation of a protest: the manifesto.}
+The organizer will write a manifesto for the protest, which describes its cause.
+This manifesto could take the form of any intelligible text.
+The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
+If they agree on the cause, they will use the knowledge of the manifesto to join the protest.
+
+\emph{Joining as a protester: \((\pid, t_s)\gets 
+    \CROCUSjoin[_P][\text{manifesto}]\).}
+A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
+Afterwards, this identifier is used to create the protest-specific identifier 
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
+\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
+The protester should also receive a time-correlated random value from the 
+time-stamping service, \(t_s\gets \TSget\).
 
@@
 
-\emph{Creation of a protest: the manifesto.}
-The organizer writes a manifesto for the protest, which describes its cause.
-This manifesto could take the form of any intelligible text.
-The organizer will then distribute this manifesto to people through
-any suitable means  (\eg on the Web, on placards, \etc).
-If they agree with the cause, they will use the knowledge of the
-manifesto to join the protest.
-
-\emph{Joining as a protester: \((\pid, t_s)\gets 
-    \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest will use the manifesto to
-compute an identifier for the cause by hashing the manifesto,
-\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
-from the organizer, we omit this in the protocol for readibility).
-Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
-\cref{fig:ProofFig} and \cref{ACprfAlg}).
-The protester should also receive a time-correlated random value from the 
-time-stamping service, \(t_s\gets \TSget\).
-
-\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
-The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
-Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
-set the start of the time interval of creation for the proof share.
-
-\emph{Participation: \(\pi\gets
-    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase, the protester and 
-the witness construct the proof share of the protester (\cref{fig:ProofFig}).
-
-The protester sends \(\pid\) to the witness.
-Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
-    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
-Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
-If the protocol succeeds, the witness will compute \(\wid \gets 
-  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
-
-\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester should as soon as possible commit the proof-share data to the 
-time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
-The remaining operations are not time critical.
-
-The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
-correctness of \(\pid\).
-More specifically,
-\begin{multline*}
-  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
-    \begin{aligned}
-      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
-      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
-    \end{aligned} \\
-      (\cid, \pid, \wid, t_s, t_s', l).
-\end{multline*}
-Finally, the protester uploads the tuple \[
-  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
-\] for permanent storage.
-
-\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
-    l]\).}
-The witness should, just as the protester, commit the proof-share data to the 
-time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
-  l]]\).
-(This is to make the time interval as early as possible, whoever is the faster 
-will submit it.)
-Then, without any time requirements, the witness computes \iac{NIZK} proof 
-\(\corr_{\wid}\) as follows:
-\begin{multline*}
-  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
-    \begin{aligned}
-      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
-      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
-    \end{aligned} \\
-      (\cid, \pid, \wid, t_s, t_s', l).
-\end{multline*}
-Finally, the witness uploads the tuple \[
-  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
-\] for permanent storage.
-
-Here is an overview of the protocol.
-
-%\begin{figure}
-% \centering
+\begin{figure}
+  \centering
   \small
- % \begin{minipage}{\linewidth}
+  \begin{minipage}{\linewidth}
     \begin{align*}
@@
     \end{align*}
-%  \end{minipage}
-%  \caption{%
-%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
-%     The organizer \(O\) broadcasts the manifesto.
-%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-%     Finally, both \(P\) and \(W\) submit the proof shares to a
-%     permanent storage \(S\). Note that \pid always refers to the
-%     protester whose presence is being witnessed.
-%   }%
-%   \label{fig:ProtocolOverview}
-% \end{figure}
-\normalsize
+  \end{minipage}
+  \caption{%
+    An overview of the Join, Participation and Submission phases of \CROCUS.\@
+    The organizer \(O\) broadcasts the manifesto.
+    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+    Finally, both \(P\) and \(W\) submit the proof shares to a
+    permanent storage \(S\). Note that \pid always refers to the
+    protester whose presence is being witnessed.
+  }%
+  \label{fig:ProtocolOverview}
+\end{figure}
 
-\subsection{Post-protest phase}%
+\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
+The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
+Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
+set the start of the time interval of creation for the proof share.
+
+\emph{Participation: \(\pi\gets
+    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
+In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
+the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+
+The protester sends \(\pid\) to the witness.
+Then they run the protocol \[
+  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
+\] (see \cref{ACacAlg}).
+Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
+If the protocol succeeds, the witness will compute \(\wid \gets 
+  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
+
+\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
+The participant should as soon as possible commit the proof-share data to the 
+time-stamping service and receive the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
+The remaining operations are not time critical.
+
+The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
+correctness of \(\pid\).
+More specifically,
+\begin{multline*}
+  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
+    \begin{aligned}
+      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
+      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
+    \end{aligned} \\
+      (\cid, \pid, \wid, t_s, t_s', l).
+\end{multline*}
+Finally, the protester uploads the tuple \[
+  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
+\] for permanent storage.
+
+\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
+    l]\).}
+The witness should, just as the participant, commit the proof-share data to the 
+time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
+  l]]\).
+(This is to make the time interval as early as possible, whoever is the faster 
+will submit it.)
+Then, without any time requirements, the witness computes \iac{NIZK} proof 
+\(\corr_{\wid}\) as follows:
+\begin{multline*}
+  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
+    \begin{aligned}
+      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
+      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
+    \end{aligned} \\
+      (\cid, \pid, \wid, t_s, t_s', l).
+\end{multline*}
+Finally, the witness uploads the tuple \[
+  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
+\] for permanent storage.
+
+\subsection{Verifying the participation count}%
 \label{ProtocolVerification}
 
-% While there are various ways for verifying the participation count, hereafter, 
-% we will detail the two suggested just after \cref{DefParticipationCount}.
-% In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
-% Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
-% In the second approach, we trust specific witnesses, but no others.
-% In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
-% It is the strength function \(\str\) of \cref{DefParticipationCount} that 
-% differ in the two cases.
-% We will first give the procedure and then how to construct the two different 
-% strength functions.
+While there are various ways for verifying the participation count, hereafter, 
+we will detail the two suggested just after \cref{DefParticipationCount}.
+In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
+Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
+In the second approach, we trust specific witnesses, but no others.
+In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
+It is the strength function \(\str\) of \cref{DefParticipationCount} that 
+differ in the two cases.
+We will first give the procedure and then how to construct the two different 
+strength functions.
 
-To verify the participation count for a protest \(\prtst\) with identifier \(cid_0\),
-a verifier must download from the storage system S the set \(S_{\prtst}\) of all \(s_P\) and \(s_W\) tuples containing \(cid_0\).
-Then from \(S_{\prtst}\), a verifier can build, in succession,
-(a) the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P,s_W)\) corresponding to a witness  \(i\) and a protester \(j\),
-(b) the participation proof \(\prf_{j}\) for each protester \(j\),
-(c) the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs for all protesters in \(P\),
- and finally the participation count, cardinality of the previous set.
+To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
+(see \cref{DefProtest}), a verifier must download all the proof shares \[
+  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
+  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
+\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
+\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
+    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
+\(l_i\subseteq  l\).
+Any proof share that does not verify correctly will be discarded.
+At this point, the verifier has constructed the set \(S\) from 
+\cref{DefProofShares} and can thus construct any participation proof 
+\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
+Now the verifier can compute the participation count \(|\prfs_P^{\str, 
+    \theta}|\) as in \cref{DefParticipationCount}.
 
-More precisely, given: \\
-\(S_{\prtst} = \{ (cid, pid, wid, l, t_s, t_s', t_c, \corr) \in \pshs \mid \cid = \cid_0 \} \) \\
-and a matching pair \((s_P, s_W) \in {S_{\prtst}}^2\) for a witness \(i\) and a protester \(j\)
-with \(s_P = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c, \psi_i)\)
-and  \(s_W = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c', \psi_j)\),
-%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
-the verifier can build a valid proof share \(s_j^{(i)}\) certified by  \(i\) for \(j\) as follow:
-verify \(\psi_i\) and \(\psi_j\),
-let \(t = [max(t_s, t_s'), min(t_c, t_c')]\),
-let \(s_j^{(i)} = (cid_0, pid_j, wid_i, l, t)\), as in \cref{DefProofShare},
-check that \(s_j^{(i)}\) is valid (i.e. happened during and at the location of the protest), as in \cref{DefProofShare}.
+In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
+\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
 
-Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
-and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
-Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.
-
-% MOST PROBABLY obsolete below v
-
-%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
-%(see \cref{DefProtest}), a verifier must download all the proof shares \[
-%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
-%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
-%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
-%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
-%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
-%\(l_i\subseteq  l\).
-%Any proof share that does not verify correctly will be discarded.
-%At this point, the verifier has constructed the set \(S\) from 
-%\cref{DefProofShares} and can thus construct any participation proof 
-%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
-%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
-%    \theta}|\) as in \cref{DefParticipationCount}.
-
-%__________________________
-
-% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
-% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
-
-In the case of trusted witnesses, each such trusted witness must
-publish or otherwise inform the 
-verifier of which proof shares she has signed, \eg by giving a list 
-of all such proof shares or digitally signing each proof share\footnote{
+In the case \emph{with} trusted witnesses, each trusted witness must inform the 
+verifier of which proof shares that he or she has signed, \eg by giving a list 
+of all such proof shares or digitally sign each proof share\footnote{%
   To achieve witness privacy in this situation, one could employ a group or 
@@
 }.
-
-Note that anyone who does the counting can choose the eligibility
-criteria (time interval, location, number of regular or trusted
-witnesses, who is considered to be a trusted witness) for their count
-and as long as these are published along with the result, anyone can
-verify the correctness under those criteria.
-
-% Then the verifier can define \[
-%   \str[\prf_{\pid_j, P}] = \begin{cases}
-%     1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
-%       share} \\
-%     0 & \text{otherwise}
-%   \end{cases}
-% \] and sets \(\theta = 1\).
+Then the verifier can define \[
+  \str[\prf_{\pid_j, P}] = \begin{cases}
+    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
+      share} \\
+    0 & \text{otherwise}
+  \end{cases}
+\] and sets \(\theta = 1\).

### 2019-02-05 paper/system-model.tex

--- 2018-11-29 paper/system-model.tex
@@
 
-To set the stage, we will now describe our system model including
-assumptions and a summary of the desired properties for crowd
-counting% and the adversary model
-.
+To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.
 
@@
 
-% \subsection{Adversary model}%
-% \label{adversary-model}
+\subsection{Adversary model}%
+\label{adversary-model}
 
-% We consider two types of adversaries: 
-% \begin{enumerate*} 
-% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
-% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
-% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
-% \end{enumerate*}
+We consider two types of adversaries: 
+\begin{enumerate*} 
+\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
+messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
+\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
+\end{enumerate*}

### 2019-02-05 paper/timestamp.tex

--- 2018-11-30 paper/timestamp.tex
@@
-\subsection{Time-stamping and storage: ledger}%
+\subsection{Time-stamping and storage --- distributed ledger}%
 \label{StorageProperties}\label{timestamp}\label{ledger}
@@
 We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
-\simon{"request" feels weird to me. Are we sure that's the right word?}
 \begin{itemize}
@@
 If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
-The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
+The \(\TSget\) request returns the hash of the most recent block of the chain 
+(\ie the head).%
 \footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
-The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).
+The returned hash is difficult to predict since it depends on the content of 
+the block, populated by other users and by the creator of the block with 
+additional randomness (\eg nonces and secrets).
 
-Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
+Regarding consensus resilience, it is advisable to use a blockchain with a high 
+number of participants and preferably sharing the blockchain with other 
+services.
 The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
@@
 Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
-Note that thanks to \(\TS\) immutability, once a user has committed their data, that user only need to store some confirmation value instead of the data itself.
-For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.
+Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
+In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her participation proof and the hash of the proof.

### 2019-02-05 paper/MANETs.tex

@@
-%@sbuc: Can you write a few words about MANETs (file MANETs.tex)?
-%More specifically, why we can assume there is a way for the
-%protesters to communicate locally at the protest without relying on the
-%Internet. Also mention potential privacy problems at this layer, e.g.\
-%MAC-address tracking etc. which is outside of our protocol (this should
-%cover part of issue #58).
-
-Since the cellular network could be shut down to keep protesters from accessing the Internet, making phone calls or texting, we require a different means of communications between protesters. 
-This could be accomplished by Bluetooth or WiFi communications, as demonstrated by Briar~\cite{Briar} and FireChat~\cite{FireChat}, two examples of applications for communication during protests via wireless mesh networking.
-The crowd-counting scenario likely has higher requirements on capacity and withstanding interference as the participants continuously run the protocol for witnessing each others presence; messages are presumably less frequent.
-5G is intended to cope with billions of devices (IoT), and thus could help cope with the device density in crowds.
+We also need the participants to communicate during the protest.
+Since the cellular network could be shut down to keep protesters from accessing 
+the Internet, making phone calls or texting, we require a different means of 
+communications between protesters. This could be accomplished by Bluetooth or 
+WiFi communications, as demonstrated by Briar~\cite{Briar} and 
+FireChat~\cite{FireChat}, two examples of applications for communication during 
+protests via wireless mesh networking. The crowd-counting scenario likely has 
+higher requirements on capacity and withstanding interference as the 
+participants continuously run the protocol for witnessing each others presence; 
+messages are presumably less frequent. 5G is intended to cope with billions of 
+devices (IoT), and thus could help cope with the device density in crowds.
 An alternative, although originally designed to work within 5G cellular networks, is device-to-device communication (D2D)~\cite{D2D}. 
-Specifically, the out-of-band and autonomous version D2D fits our scenario thanks to using unlicensed spectrum and working without cellular coverage.
+Specifically, the out-of-band and autonomous version D2D would fit our
+scenario thanks to using unlicensed spectrum and working without
+cellular coverage. Due to the requirements of lawful intercept and the
+drive for operators to identify the network users, there still is an
+authorization step to communicate in this mode.
+%~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

### 2019-02-05 paper/privacy-analysis.tex

--- 2018-11-30 paper/privacy-analysis.tex
@@
 \(t\) is not uniquely identifying either.
+
+Overall, informally, the digital trace needed for verifiability in \CROCUS could
+conceivably be used to strengthen a suspicion of
+participation.
+Given \cref{deanonymizing-storage-adversary} (Grace's) inferences from 
+auxiliary information that points
+to Alice having participated in a protest, \eg pictures at the
+event, with face recognition and subsequent identification, IP address
+of her home router, \etc, then any remaining uncertainty from false
+positives could be reduced by learning from data on the ledger and
+Alice's smartphone. %This potential difference can thus be considered
+                    %the price for verifiability.
+For confirmation of that suspicion, Grace would have to get access to
+and use Alice's private key.

### 2019-02-05 paper/trust-assumptions.tex

@@
 
-\paragraph{ID issuer} We assumed a trusted third party issued certified IDs to every participant (protesters and witnesses). This hypothesis is important to avoid Sybil attacks,
+\subsection{ID issuer} We assumed a trusted third party issued certified IDs to every participant (protesters and witnesses). This hypothesis is important to avoid Sybil attacks,
 but only the side protesting (not the side being protested against) has an incentive to perform a Sybil attack.
@@
 
- \paragraph{Verifier's trust in the count} We proposed a generic way of counting, that relies on two parameters: the strength function and the threshold.
+ \subsection{Verifier's trust in the count} We proposed a generic way of counting, that relies on two parameters: the strength function and the threshold.
 %We then suggested two possible instantiations: every witness is equal and we use a relatively large threshold, or we only trust a minority of independent witnesses with a threshold of 1.
@@
 
-\paragraph{Protesters and witnesses} Active participants in a protest do not need to trust anything other than that their app is behaving properly and that their smartphone is not compromised.
+\subsection{Protesters and witnesses} Active participants in a protest do not need to trust anything other than that their app is behaving properly and that their smartphone is not compromised.
 Indeed, \CROCUS has been designed with their privacy and security as a central concern, and being able to use \CROCUS without any additional risk compared to simply come at the protest was one of our main requirement.

### 2019-02-05 paper/tamarin-spec.tex
Changes appendix structure
Renames tamarin appendix to tamarin-spec.tex
Includes tamarin spec directly from tamarin directory

@@
-\section{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
+\section{Specification of the distance-bounding protocol used by \CROCUS in 
+  Tamarin}%
 \label{apdx:tamarin-spec}
@@
 
-\begin{lstlisting}
-
-/* Implementation of the DB protocol */
-/* Demonstrating the DB-secure property */
-
-theory crocusclean
-
-begin
-
-functions: adec/2, aenc/2, pk/1
-
-equations: adec(aenc(message, secretkey), 
-           pk(secretkey)) = message
-
-builtins: signing
-
-// -------- Tag Initialization --------- //
-
-rule Register_Keypair:
-[ Fr(~key) ]
---[ Once($A), Prelim()]->
-[ !Pk($A, pk(~key)), !Ltk($A, ~key), 
-  Out( pk(~key) ), !Agent($A)
-  ]
-
-rule Corrupt_Agent:
-[ !Ltk($A, ltk) ]
---[ Corrupt($A), Prelim() ]->
-[ Out(ltk), !CorruptAgent($A) ]
-
-rule Corrupt_Fast:
-[ !CorruptAgent($A), In(msg) ]
---[ CAction($A), Action($A) ]->
-[ FastMsg(msg) ]
-
-// ------- Protocol Rules ---- //
-
-//1. Prover chose r, compute and send R
-//2. Verifier chooses two nonces c_0 and c_1,
-//   and sends them to Prover
-//3. Verifier chooses b = 0 or 1, 
-//   sends to Prover
-//4. Prover receives + encodes both c_i 
-//   with x and sign them with r
-//5. Prover receives b,
-//   sends back corresponding c
-//6. Verifier verifies the signature 
-//   and decodes the messsage, 
-//   checks it's the correct c
-
-// 1. Prover chose r, compute and send R
-
-rule Prover_1:
-[ !Agent($Prover) 
-, Fr(~r)
-]
---[ ProverStart($Prover)
-, Action($Prover)
-]->
-[ ProverSess($Prover, ~r) 
-, Out( pk(~r) )
-]
-
-//2. Verifier chooses two nonces c_0 and c_1 
-//   and sends them to Prover
-
-rule Verifier_1:
-[ In( R ) 
-, Fr(~challenge0) , Fr(~challenge1)
-]
---[ VerifierCommit( ~challenge0, ~challenge1 ) 
-, PreFastPhase( <~challenge0, ~challenge1> )
-]->
-[ VerifierSess(R, ~challenge0, ~challenge1) 
-, Out( <~challenge0, ~challenge1> )
-]
-
-//3. Verifier chooses b = c0 or c1, 
-//   and sends it to Prover
-
-rule Verifier_2:
-[ VerifierSess(R, c0, c1) 
-, Fr(~b) 
-]
---[ Choose(c0, c1, ~b)
-, VerifierSelect(~b) 
-, StartFastPhase(c0, c1) 
-]->
-[ VerifierStartFast(R, c0, c1, ~b)
-, FastMsg( ~b ), Out( ~b ) 
-]
-
-//4. Prover receives and stores both c_i
-
-rule Prover_2:
-[ ProverSess($Prover, r) 
-, In( <c0, c1> ) 
-]
---[ ProverStore(c0, c1) 
-, ReadyFastPhase( c0, c1 ) 
-, Action($Prover)
-]->
-[ ProverStartFast( $Prover, r, c0, c1 ) 
-]
-
-//5. Prover receives b and sends it back
-//   encoded with x and signed with r
-
-rule Prover_3:
-let response = aenc{b, sign(b,x)}r
-in
-[ ProverStartFast( $Prover, r, c0, c1 ) 
-, FastMsg( b ) 
-, !Ltk( $Prover, x ) 
-]
---[ Choose(c0,c1,b) 
-, ProverReply($Prover, c0, c1, b)
-, ReplyFastPhase(c0, c1, b)
-, Action($Prover)
-]->
-[ FastMsg( response ), Out( response ) 
-]
-
-//6. Verifier verifies the signature and 
-//   decodes the messsage,
-//   checks it's the correct c
-
-rule Verifier_3:
-let clear_text = adec( response, R )
-authentication = verify( 
-                   snd(clear_text),
-                   fst(clear_text),
-                   X
-                 )
-proof = fst(clear_text)
-in
-[ VerifierStartFast(R, c0, c1, b) 
-, FastMsg( response )
-, !Pk( $Prover, X )
-]
---[ Eq(authentication, true), Eq(proof, b)
-, VerifierComplete($Prover, R, c0, c1, b) 
-, EndFastPhase(c0,c1,b)  
-]->
-[]
-
-// ----- Axioms ------- //
-
-restriction at_most_once:
-"
-All A #t1 #t2. Once(A)@t1 & Once(A)@t2 ==>
-(
-#t1 = #t2
-)
-"
-
-restriction equals:
-"
-All a b #t1. Eq(a,b)@t1 ==>
-(
-a = b
-)
-"
-// ----- Sanity Check Lemmas ----- //
-
-lemma verif1_exists:
-exists-trace
-"
-Ex c0 c1 #t. (
-VerifierCommit( c0, c1 )@t )
-"
-
-lemma prover2_exists:
-exists-trace
-"
-Ex Prover c0 c1 b #t. (
-ProverReply( Prover, c0, c1, b )  @t )
-"
-
-lemma startfast_exists:
-exists-trace
-"
-Ex c0 c1   #t. (
-StartFastPhase(c0, c1)@t
-) &
-not(Ex A #tc. Corrupt(A)@tc)
-"
-
-lemma endfast_exists:
-exists-trace
-"
-Ex c0 c1 b  #t. (
-EndFastPhase(c0, c1, b)@t
-) &
-not(Ex A #tc. Corrupt(A)@tc)
-"
-
-lemma end_exists:
-exists-trace
-"
-Ex P R c0 c1 b  #t. (
-VerifierComplete(P, R, c0, c1, b)@t
-) &
-not(Ex A #tc. Corrupt(A)@tc)
-"
-
-// ----- Security Lemmas ----- //
-
-lemma dbsec:
-// Whenever the verifier is complete EITHER:
-//  1) There exists t1, t2 and t3 such that
-//          The fast phase was between t1 and t3
-//          and prover did smthg btwn t1 and t3
-//          and verifier completed at/after the
-//          end of the fast phase
-//OR
-//  2) There exist times t5, t6 and t7 such that
-//        The fast phase was between t5 and t7
-//        and the prover P is dishonest
-//        and some dishonest agent did smthg 
-//        during the fast phase
-//        and the verifier completed at/after the
-//        end of the fast phase 
-"
-All P R c0 c1 b  #t. (
-VerifierComplete(P, R, c0, c1, b)@t ) ==>                   
-(                                                         
-Ex #t1 #t2 #t3. StartFastPhase( c0, c1 )@t1 &              
-Action(P)@t2 &                              
-EndFastPhase( c0, c1, b )@t3 &            
-(#t1 < #t2) &                               
-(#t2 < #t3) &                               
-( (#t3 < #t ) | (#t3 = #t) )
-)|
-(              
-Ex CAgent #t4 #t5 #t6 #t7.
-StartFastPhase( c0, c1 )@t5 &    
-EndFastPhase( c0, c1, b )@t7 & 
-Corrupt(P)@t4 &             
-CAction(CAgent)@t6 &             
-(#t5 < #t6)&                     
-(#t6 < #t7)&                     
-( (#t7 < #t) | (#t7 = #t) )      
-) 
-"
-
-end
-\end{lstlisting}
+\lstinputlisting[basicstyle=\small,breaklines]{../tamarin/crocus.spthy}

### 2019-02-06 paper/reviews/popets-2019.3-rebuttal.md

--- 2019-01-10 paper/reviews/popets-2019.3-rebuttal.md
@@
 Reviewer 1
+1) a) Due to  unlinkability properties (anonymous credentials and pseudonyms), the central authority cannot tell participants from non-participants without extreme measures equivalent to arresting people at the protest.
+Arguably, the chilling effects with this system are no more than that of "standard" protests.
+We give the national ID as an example, but any logically centralized entity would work.
 
-1) a) Due to the use of anonymous credentials, the central authority cannot tell participants from non-participants without extreme measures equivalent to arresting people at the protest.
-Arguably, the chilling effects with this system are no more than that of "standard" protests.
-To mitigate the risk of having a central authority responsible the IDs, we could also replace it by a distributed version composed of several independent entities that simulate the work of the central authority is a distributed and private manner.
+b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias (e.g. as for detecting bias in science).
 
-b) Yes, but the paper also notes that those are detectable and should be ignored due to their obvious bias.
-In particular, those who verify results must apply the standard source criticism.
-(e.g., for detecting bias in scientific research).
+2) Petitions have been viable for a long time but people still arrange protests anyway.
+Our scheme allows for both anonymous verifiable petitions (skip location) and protests (time and location matter).
 
-2) Petitions have been viable for a long time but people still arrange protests anyway, in part because going physically to a protest in a sense shows much more involvment.
-Our scheme allows for both anonymous verifiable petitions (not considering location) and protests (time and location matter).
-
-3-4) We acknowledge that the design of the architecture is complex but we need all parts to reach the desired security and privacy properties.
-To improve the clarity of the paper, we agree that we need to present the adversaries better.
-The objective of introducing A2 was to show the limitations of our approach.
-While Crocus cannot make physical protests safer, we wanted to ensure that it does make it worse.
+3-4) We acknowledge that the design of the architecture is complex but we need all parts to reach the desired properties.
+Governments can already now make examples of people; Crocus cannot make physical protests safer, we only want to not make it worse.
 
 5) This is the main reason for distance-bounding as it allows the witness to verify that it is within a given distance from the prover.
-Why a verifier accepts this claim is up to the trust assumptions for which we provide two cases.
-One in which the verifier trusts a particular witness and the other in which the verifier believes that a threshold of witnesses has been reached.
+Why a verifier accepts this claim is up to the trust assumptions for which we provide two cases, trusted witness and threshold.
 
-6) Trusted by a verifier. Anyone can define whom they trust and how they want to be counted. We _do_ use trusted witnesses for counting.
+6) Trusted by a verifier. Anyone can define whom they trust and how they want to be counted. We do use trusted witnesses for counting.
 
@@
 
-With respect to a single participant gathering proof shares for friends, distance-bounding prevents this to be done by relaying messages.
-In addition, the terrorist-fraud assumption also prevents a user giving his private key (or phone containing it) to someone.
-This is realistic in scenario in which the private keys are part of the long-term ID credential.
-In particular as pointed out by reviewer 1 if this ID can be used for other things, you will not allow just anyone to use it.
+With respect to a single participant gathering proof shares for friends, terrorist-fraud resistance in distance bounding prevents relays and users giving  private keys (or phones) to someone.
+As pointed out by Reviewer 1, this is realistic in scenarios in which the private keys are part of the long-term ID credential.
 
@@
 
-1) Yes, it follows the standard assumption in distance-bounding to prevent terrorist fraud (which is distance-bounding terminology for this particular case).
+1) While FE is a valid concern, we need to carefully select DB protocol for terrorist-fraud resistance which includes FE.
+We are working on a distance-bounding protocol (in preparation for a separate paper) in which two outputs from the FE function needed would enable the calculation of the private key, thus again reducing to terrorist-fraud.
 
-Functional encryption will not work against an honest verifier in the general case.
-We are working on a distance-bounding protocol (in preparation for a separate paper) in which the private key can be computed by joining two different outputs from the functional encryption of the private key, which reduced to the terrorist-fraud case again.
+2) This extreme case in which no type of wireless communication works is possible but unheard of. Potentially using NFC solves this, but with usability consequences.
 
-2) This extreme case in which no type of wireless communication works is possible but unheard of. However, it could be potentially solve by using NFC capabilities for instance.
+3) There is no principled way given online mobs, but different counts are possible and as long as the parameters are published, the counts can be verified.
+Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the eyes of the verifier.
 
-3) There is principled way given online mobs, but different counts are possible.
-As long as these parameters are published, the counts can be verified.
-Requests for sizeable collusion are made in public, which risk being found by the verifier --- thus invalidating the count in the verifier's eyes.
-
-4) 5G is built for scale but currently not for the D2D scenario without provider but again NFC is an option.
-For overall performance, we could evaluate AnonPass on phones, example distance-bounding computation, collect density and scalability from the literature (protests and wireless), and measure NFC delays, which we could do if deemed useful by the reviewers.
+4) For overall performance, we could evaluate AnonPass on phones, example distance-bounding computation, collect density and scalability from the literature (protests and wireless), and measure NFC delays, which we could do if deemed useful by the reviewers.
+5G is built for scale but not for the D2D scenario; again, NFC is possible.

### 2019-02-06 paper/intro.tex

--- 2018-11-29 paper/intro.tex
@@
 
-%\paragraph*{Contributions}
+\paragraph*{Contributions}
 
-%In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
 
-% Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-% Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
-% More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
-% The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
+Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
+More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
+The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
 %\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
@@
 %\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
-%and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
+and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
 

### 2019-02-06 paper/ZKPK-instantiations.tex
Changes set notation (\Z -> \ZZ), removes DBIV
Edits ZKPK-instantiations
Minor cosmetic fixes for ZKPK-instantiations
Sets anon-cred, ZKPK figures on page-of-floats (in appendix)
Replaces \paragraph with \subsubsection where necessary

@@
-\subsubsection{Instantiations of the \acs{ZKPK} protocols}
+\paragraph*{Instantiations of the \acs{ZKPK} protocols}
 
-\NewAlgorithm{\PKprove}{PK.\!Prove}
-\NewAlgorithm{\PKverify}{PK.\!Verify}
-
-We will rely on the Schnorr identification scheme~\cite{Schnorr}, which in its 
-original form can be written as \(\PK[\alpha][A = g^\alpha]\).
+For the convenience of the reader, we summarize 
+(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
+discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
+which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
 The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
@@
 \begin{equation*}
-  \PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i] \leftrightarrow
-  \PKverify[\{g_i\}_i, q, A],
+  \Proto%
+  {\PKprove[\{g_i\}_i, q, A, \{\alpha_i\}_i]}%
+  {\PKverify[\{g_i\}_i, q, A]},
 \end{equation*}
@@
 verifier.
-\(\PKverify\) outputs accept (1) or reject (0).
+\(\PKverify\) outputs accept (\(\top\)) or reject (\(\bot\)).
 We give an instance of \(\PKprove\) and \(\PKverify\) in \cref{PKalgorithms}.
@@
 \begin{figure*}
-  \centering
+  %\centering
+  \small
   \begin{tabular}{lcl}
@@
 
-    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)
+    \(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)
     &
@@
 
-    \(1\leq i\leq n\colon s_i\gets \rho_i - c\alpha_i \mod q\)
+    \(\forall i\colon s_i\gets \rho_i - c\alpha_i \mod q\)
     & \(\ProtoSendRight{\{s_i\}_{i=1}^n}\)
@@
   \caption{%
-    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1]^n g_i^{\alpha_i}}\) using 
+    \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
     the Schnorr identification scheme.
@@
 
-\NewAlgorithm{\SPKprove}{SPK.\!Prove}
-\NewAlgorithm{\SPKverify}{SPK.\!Verify}
-
 For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
@@
 
-\begin{figure*}
-  \begin{minipage}[t]{0.49\linewidth}
+\begin{figure}
+  \small
   \begin{algorithmic}
     \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
-        \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \Z_q\)}
+      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
       \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
-        \State{$c \gets H(\{g_i\}_i|A|R|m)$}
+      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
       \For{$1\leq i\leq n$}
@@
   \end{algorithmic}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{0.49\linewidth}
+
   \begin{algorithmic}
@@
       \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
-        \If{$c = H(\{g_i\}_i|A|\hat R|m)$}
-          \State{\Return{1}}
-        \Else{}
-          \State{\Return{0}}
+      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
+        \State{\Return{$\top$}}
       \EndIf{}
+      \State{\Return{$\bot$}}
     \EndFunction{}
   \end{algorithmic}
-  \end{minipage}
   \caption{%
@@
   \label{SPKalgorithms}
-\end{figure*}
+\end{figure}

### 2019-02-07 paper/identity-limits.tex
Adds WIP discussion of limits of identity systems

\section{Limits of current identity systems}

\Textcite{SybilAttack} points out that any identity system must be logically 
centralized to prevent Sybil attacks.
It follows that any system where users themselves can create identities cannot 
provide strong guarantees against Sybil attacks.

The most widely deployed identity system is that of nation states: in essence, 
an identity is created at birth in the form of the equivalent of a birth 
certificate\footnote{%
  Many countries issue birth certificates, but there are other, equivalent, 
  ways.
  \Eg Sweden does not issue birth certificates, it simply creates and entry in 
  the population registry.
} This birth certificate later serves as the root for many authentication 
mechanisms, \eg national identity cards and passports.

Some more \enquote{decentralized}\footnote{%
  Provably, it must be logically centralized anyway.
} methods have been suggested, \eg 
proof-of-personhood~\cite{proof-of-personhood}.
In this particular approach, people gather in a room, \emph{everyone ensures} 
that no one can enter or leave during the process.
Then \emph{everyone ensures} that everyone gets exactly one identity.

We will now discuss the limits and possibilities of these approaches.

\subsection{The \enquote{birth-certificate} system}

This system is logically centralized, it is controlled (enforced) by the 
government.
However, it is usually distributed among a country's hospitals.
It usually works without any problems: citizens --- who have an incentive to 
create more identities, \eg to accumulate various benefits --- cannot create 
new identities without babies.
Someone who has a baby does not want to give that identity to someone else, 
because then their baby will not have one --- usually the biological mechanisms 
that ensures the well-being of our offspring prevents any abuse on this side 
too.
But obviously there exists a possibility to create birth certificates without 
newborn babies, it is just that those who can either do not have any incentive 
to do so or there are other mechanisms, \eg separation of duties and 
accountability.

There is one particular situation where the incentive arises:
to influence democratic processes\footnote{%
  There are a few more, less relevant, \eg to have multiple identities for 
  foreign operatives, as seen on film.
  But those are not significant to our discussion.
}.
If the government can create identities and control them, they can use them to 
vote for themselves in upcoming elections.
In a well-designed system, however, this should be prevented.
This varies from country to country (\ie system to system).

\subsubsection{The case of Sweden}

An identity is created when an entry is made in the population registry.
Each entry in the registry has a unique identification number.
The electoral roll is created from the population 
registry~\cite{Valmyndigheten-ElectoralRoll}.

For a person to cause an entry into the population registry, they have two 
options:
they are in the population registry and give birth to a child, or
they were born abroad and apply to immigrate to Sweden.

In the case of a birth\footnote{%
  Technically, this is the procedure if the child is born abroad.
  If the child is born in Sweden, the hospital will report all these things 
  directly to the population registry without issuing any papers to the 
  parents.
} they need:
\begin{itemize}
  \item passports, to prove the identities of the parents;
  \item a birth certificate where the names of the parents are present;
  \item a pregnancy certificate, to prove who birthed the child;
  \item a certificate of who the father is~\cite{Skatteverket-RegisterBirth}.
\end{itemize}
So the security is reduced to the forgeability of these items.

Obviously the one who creates entries in the population registry can do that 
even without such documents, so there must be some separation of duty, 
accountability or transparency to prevent the agency from performing a Sybil 
attack.
In the case of Sweden, the population registry is public.
This means that in addition to any audit trail in place at the agency, we have 
these properties:
\begin{itemize}
  \item The data must fulfil basic integrity: a person must have parents, who 
    in turn must have parents, \etc.
  \item Anyone can detect extraordinary additions, \eg exceptionally many 
    births, additions of family trees, \etc.
    Individual women and men would also notice if extra children were added to 
    them.
  \item Addition of persons of foreign heritage must have corresponding 
    documentation (audit trail) at the Migration Board.
\end{itemize}
A foreign citizen can prove their identity to the Migration Board in the 
following ways:
\begin{itemize}
  \item showing a national passport in the original or
  \item showing an identity document in the original or
  \item a close relative attesting to the 
    identity~\cite{Migrationsverket-ProvenIdentity}.
\end{itemize}
Thus the security is reduced to subverting one of these methods.

\subsubsection{The case of France}

The French electoral roll is populated by citizens registering at the town 
hall.
They must then be able to authenticate their identity using an identity 
credential.

Whenever a child is born, the hospital reports this to the local town hall.
They register the birth and issues a birth certificate.
While they do not actively maintain the current whereabouts of individuals and 
do not give each an identity number, their identity consists of the tuple of 
name, date and place of birth.
Thus an identity can be verified by asking the specified town hall to verify 
the birth in their records.

This makes the audit trail more complex.
It is also difficult to detect modifications to these records, since they are 
not public.

\subsubsection{Perfectly decentralized and private birth-certificates approach}

There are no audit records, the one who can create authentic birth certificates 
can perform Sybil \dots

\subsection{Issued credentials}

In Sweden, there are several entities that are authorized to issue identity 
cards; \eg the Swedish Tax Agency, the Swedish Police, the banks.
Thus, technically, to detect a Sybil attack by them, \ie fake identities, one 
must check the ID against the population registry.

With anonymous credentials, this becomes a problem.
If two entities issues identity credentials to Alice, there is no problem: if 
she uses the first to authenticate to Bob, and later comes back and uses the 
second, Bob will that she is Alice both times.
With anonymous credentials that prevent multiple use, this is no longer the 
case.
Thus issuers of such credentials must synchronize, so that if one has issued 
such credentials to Alice, the others must not issue another.

One problem here is that there can be no audit trail.
Thus the issuers have the possibility of performing Sybil attacks.

\subsection{Proofs-of-personhood}

Even physically decentralized attempts, such as 
proof-of-personhood~\cite{proof-of-personhood}, are logically centralized.
For a nation-wide proof-of-personhood, everyone in the nation must be at the 
same place at the same time.
This is obviously not possible and to make it feasible we must split across 
multiple locations\footnote{%
  We cannot split across time.
  The base assumption is that we do not have any means of authenticating 
  people, thus we must rely on the physical impossibility of being in two 
  places at the same time.
  Obviously it is not impossible to be in the same place at two times.
} and rely on trust: if Alice is in one location, she must trust that at least 
one in every other location is also honest.

The issue with this system is scalability.
Every time that \emph{anyone} needs a new credential, we must involve 
\emph{everyone}.
Getting everyone to be at some fixed locations at the same time is even 
difficult to achieve during Election Day, it must usually be spread across the 
time of the whole day.
This would solve the problems of the issuance of anonymous credentials 
mentioned above, if it only scaled.

\subsection{Detecting bias}

%> RevA: How is a non-protester, either a voter who intends to figure out
%> their position or a concerned someone in a distant land), who is watching
%> the news supposed to tell which of the pro-government or anti-government
%> protester-counts to believe. Are we to assume that obviously any
%> pro-government activity is absolutely suspicious and all anti activity is
%> legitimate? The solution should make it impossible to nay-say the true
%> counts even if they go against our very beliefs (e.g. as for detecting bias
%> in science).

Despite potentially better audit possibilities, elections are imperfect and so are pro-government protests. Nevertheless, this has not been seen as a valid reason to not have elections or protests anymore at all. Also, if one does not trust the government with identity provision, it stands to reason that one would not trust them to count correctly either. People certainly are skeptical about massive pro-government protests in countries such as North Korea, not only for counting wrong but also because they can coerce people to physically attend a protest.

Due to the flaws inherited in currently deployed identity systems, we 
pointed out in which cases they can be used and in which they cannot: 
when there is an interest for the identity authority to perform a 
Sybil attack, the results cannot be trusted.

As we pointed out, this is similar to detecting bias in science. If the 
authors personally benefit from the results, then they are incentivized 
to bias them. The verifiability properties of our scheme serve the same 
purpose as the methodology section of a scientific paper: anyone is able 
to repeat, reproduce and verify the results --- even if they are in 
distant lands. It is detectable who the CA is for all these people and 
if that CA has incentives to perform a Sybil attack, then the results 
simply cannot be trusted.

The problem lies with the identity system: as long as the identity 
system used has these problems, these are the limits we face in our 
scheme too. If the identity system is not subject to these problems, 
then neither is our scheme.

\subsection{The need for distance bounding}

> RevA: DB does not address the issue raised by the reality of mobile phone
> farms for hire (and the ability of the centralised authority to issue
> credentials falsely) where all the witnesses, and provers could be in a
> room far away from the protests since the location is never actually
> figured out (since location can be faked anyway). How big a protest does
> one need such that the threshold would be beyond the ability of a
> government to afford enough fake mobile phones? As for the trusted witness,
> how does that scale with the size of the protest?

If the identity authority performs a Sybil attack, they 
do not need a mobile phone farm --- they can perform computations 
anywhere on any computation system they like. (Again, as pointed out, 
nothing can prevent this type of Sybil attack and (electronic) voting 
suffers from essentially the same problem.)

We point out that against this strong adversary, the 
trusted-witness approach is the only approach that will work. We provide 
the threshold approach as an alternative that might work in some 
circumstances.

Lastly, and perhaps most importantly: DB protects against exactly this. For 
the government to succeed they would need to do the computations within 
a certain distance of the (trusted) witness --- a distance determined by 
the witness themself. Obviously the government succeeds if they also 
control the trusted witness. But the reason the witness is trusted is 
that they are likely not controlled by the government. And there can be 
several trusted witnesses in parallel --- with different interests to 
prevent a bias situation.

However, in the end, the one who controls the identity system controls 
Sybil. And, unless we get representatives from several nations present 
to sign birth certificates at hospitals, we will probably be stuck in 
this situation.

From the Meta-Review:

> The main concerns were about the deployment scenario which relies on a
> central entity, the complexity of the protocol, and the use of
> yet-to-be-designed primitives like distance bounding protocols while
> leaving existing primitives like functional encryption out of the model.

Distance-bounding protocols were introduced by Chaum in 1993. They are 
very much existing. What is not existing (i.e. not formally proved 
correct yet) is a distance-bounding protocol (with all the desired DB 
properties) which is a proof-of-knowledge for discrete logarithms.

Any DB protocol that is provably secure against terrorist fraud, is 
provably secure against anything along the lines of functional 
encryption. In that sense, functional encryption is part of the model. Our rebuttal response regarding functional encryption does not seem to have been taken into consideration, at least not in the reviews, we have of course no insight into any discussions.

### 2019-02-08 paper/identity-limits.tex

@@
 must check the ID against the population registry.
+With anonymous credentials, this becomes a problem.
 
-With anonymous credentials, this becomes a problem.
-If two entities issues identity credentials to Alice, there is no problem: if 
-she uses the first to authenticate to Bob, and later comes back and uses the 
-second, Bob will that she is Alice both times.
-With anonymous credentials that prevent multiple use, this is no longer the 
-case.
+If two entities issue (non-anonymous) identity credentials to Alice, there is 
+no problem: if she uses the first to authenticate to Bob, and later comes back 
+and uses the second, Bob will know that she is Alice both times.
+In both cases, if Bob doubts the credentials, he can follow the audit trail.
+With anonymous credentials that prevent multiple use, however, this is no 
+longer the case.
 Thus issuers of such credentials must synchronize, so that if one has issued 
@@
 
-One problem here is that there can be no audit trail.
-Thus the issuers have the possibility of performing Sybil attacks.
+This problem is amplified by the fact that there can be no audit trail from the 
+authentication, due to the anonymity.
+Thus, individual issuers have the possibility to perform Sybil attacks.
+However, this problem can be solved.
+Since all individual issuers of credentials must synchronize to not issue more 
+than one anonymous credential to Alice, they might just as well act together 
+(\ac{MPC}) in the issuing process --- thus introducing dual control.
 
@@
 This would solve the problems of the issuance of anonymous credentials 
-mentioned above, if it only scaled.
+mentioned above (it provides the same properties as \ac{MPC} did above), if it 
+only scaled.
 
@@
 
-%> RevA: How is a non-protester, either a voter who intends to figure out
-%> their position or a concerned someone in a distant land), who is watching
-%> the news supposed to tell which of the pro-government or anti-government
-%> protester-counts to believe. Are we to assume that obviously any
-%> pro-government activity is absolutely suspicious and all anti activity is
-%> legitimate? The solution should make it impossible to nay-say the true
-%> counts even if they go against our very beliefs (e.g. as for detecting bias
-%> in science).
+If we do not have \iac{MPC} base solution as suggested above, we can still 
+reduce the problem.
+When a verifier verifies an anonymous authentication, it is clear who the 
+\ac{CA} (\ie the issuer) is.
+In this case the verifier can analyze whether the issuer has any incentives for 
+a Sybil attack.
 
-Despite potentially better audit possibilities, elections are imperfect and so are pro-government protests.
-Nevertheless, this has not been seen as a valid reason to not have elections or protests anymore at all.
-Also, if one does not trust the government with identity provision, it stands to reason that one would not trust them to count correctly either.
-People certainly are skeptical about massive pro-government protests in countries such as North Korea, not only for counting wrong but also because they can coerce people to physically attend a protest.
-
-Due to the flaws inherited in currently deployed identity systems, we 
-pointed out in which cases they can be used and in which they cannot: 
-when there is an interest for the identity authority to perform a 
-Sybil attack, the results cannot be trusted.
-
-As we pointed out, this is similar to detecting bias in science. If the 
-authors personally benefit from the results, then they are incentivized 
-to bias them. The verifiability properties of our scheme serve the same 
-purpose as the methodology section of a scientific paper: anyone is able 
-to repeat, reproduce and verify the results --- even if they are in 
-distant lands. It is detectable who the CA is for all these people and 
-if that CA has incentives to perform a Sybil attack, then the results 
-simply cannot be trusted.
-
-The problem lies with the identity system: as long as the identity 
-system used has these problems, these are the limits we face in our 
-scheme too. If the identity system is not subject to these problems, 
-then neither is our scheme.
-
-\subsection{The need for distance bounding}
-
-> RevA: DB does not address the issue raised by the reality of mobile phone
-> farms for hire (and the ability of the centralised authority to issue
-> credentials falsely) where all the witnesses, and provers could be in a
-> room far away from the protests since the location is never actually
-> figured out (since location can be faked anyway). How big a protest does
-> one need such that the threshold would be beyond the ability of a
-> government to afford enough fake mobile phones? As for the trusted witness,
-> how does that scale with the size of the protest?
-
-If the identity authority performs a Sybil attack, they 
-do not need a mobile phone farm --- they can perform computations 
-anywhere on any computation system they like. (Again, as pointed out, 
-nothing can prevent this type of Sybil attack and (electronic) voting 
-suffers from essentially the same problem.)
-
-We point out that against this strong adversary, the 
-trusted-witness approach is the only approach that will work. We provide 
-the threshold approach as an alternative that might work in some 
-circumstances.
-
-Lastly, and perhaps most importantly: DB protects against exactly this. For 
-the government to succeed they would need to do the computations within 
-a certain distance of the (trusted) witness --- a distance determined by 
-the witness themself. Obviously the government succeeds if they also 
-control the trusted witness. But the reason the witness is trusted is 
-that they are likely not controlled by the government. And there can be 
-several trusted witnesses in parallel --- with different interests to 
-prevent a bias situation.
-
-However, in the end, the one who controls the identity system controls 
-Sybil. And, unless we get representatives from several nations present 
-to sign birth certificates at hospitals, we will probably be stuck in 
-this situation.
-
-From the Meta-Review:
-
-> The main concerns were about the deployment scenario which relies on a
-> central entity, the complexity of the protocol, and the use of
-> yet-to-be-designed primitives like distance bounding protocols while
-> leaving existing primitives like functional encryption out of the model.
-
-Distance-bounding protocols were introduced by Chaum in 1993. They are 
-very much existing. What is not existing (i.e. not formally proved 
-correct yet) is a distance-bounding protocol (with all the desired DB 
-properties) which is a proof-of-knowledge for discrete logarithms.
-
-Any DB protocol that is provably secure against terrorist fraud, is 
-provably secure against anything along the lines of functional 
-encryption.
-In that sense, functional encryption is part of the model.
-Our rebuttal response regarding functional encryption does not seem to have been taken into consideration, at least not in the reviews, we have of course no insight into any discussions.
+This is similar to detecting bias in science.
+If the authors personally benefit from the results, then they are incentivized 
+to bias them.
+The verifiability properties of our scheme serve the same purpose as the 
+methodology section of a scientific paper: anyone is able to repeat, reproduce 
+and verify the results --- even if they are in distant lands.

### 2019-02-12 paper/identity-limits.tex
Adds conclusion to identity-system discussion

@@
 
-\subsection{Detecting bias}
+\section{Conclusions}
 
-If we do not have \iac{MPC} base solution as suggested above, we can still 
-reduce the problem.
-When a verifier verifies an anonymous authentication, it is clear who the 
-\ac{CA} (\ie the issuer) is.
-In this case the verifier can analyze whether the issuer has any incentives for 
-a Sybil attack.
-
-This is similar to detecting bias in science.
-If the authors personally benefit from the results, then they are incentivized 
-to bias them.
-The verifiability properties of our scheme serve the same purpose as the 
-methodology section of a scientific paper: anyone is able to repeat, reproduce 
-and verify the results --- even if they are in distant lands.
+While the decentralized properties of proofs-of-personhood are appealing, it is 
+hard to achieve such a scheme.
+The goal is to have one identity (pseudonym) per physical person.
+This goal is joint with the \enquote{birth-certificate system} which actually 
+achieves the goal quite nicely in practice.
+However, since the birth-certificate system relies on audit trails to function, 
+it cannot deal with issuing anonymous credentials.
+Thus the ideas from proof-of-personhood, where everyone must act jointly, can 
+solve this problem.
+To issue anonymous credentials that certify one physical person behind a 
+pseudonym, all issuers must act jointly, \eg through \ac{MPC}.

### 2019-02-12 paper/intro.tex
Minor edits in intro

@@
 
-In this paper, our first main contribution is to propose \CROCUS, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
+Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
+way to securely estimate crowd counts in protests\footnote{%
+  If location is ignored, it can be reduced to privacy-preserving yet 
+  verifiable petitions.
+}.
 
 Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
-More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
-The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
-%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
-%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
-%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
-and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
+Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
+including \ac{DBDH} (which was an attack against the original protocol of 
+Brands and Chaum) and \ac{DBTF}.
+More importantly, it is public-key, handles malicious impersonating verifiers.
+Since it is based on the Schnorr protocol, it provides a distance-bounded 
+\ac{PK} for discrete logarithms.
+That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
+distance-bounding version and thus make general privacy-preserving, 
+attribute-based credential systems distance bounding.
 

### 2019-02-13 paper/intro.tex
Edits outline

@@
 The paper is organized as follows.
-First, in \cref{system-model}, we describe our system model and summarize the desired properties for crowd counting.
-Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS.
-We then formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give the relevant background on the building blocks of our solution. 
-Afterwards, in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security (\ie the fact that it achieved all desired \ac{DB} properties) 
-\daniel{Check that this is true before publication.} 
-and formally verify it using Tamarin~\cite{TamarinDB}.
-\seb{we need to be careful about the above sentence}
-%This version of the Schnorr protocol can then be used to do general \ac{DB} anonymous credentials.
-Then in \cref{Protocol}, we present \CROCUS, a privacy-preserving crowd 
-counting estimation protocol constructed from these building blocks, before 
-analyzing its security and privacy (\cref{SecurityAnalysis}).
-Finally, we discuss our assumptions and results \cref{Discussion} and give our conclusions in \cref{Conclusion}.
-%\sonja{add (sub) sections for performance and verification}
+\Cref{system-model}, we describe our system model and summarize the desired 
+properties for crowd counting.
+We then discuss related work in terms of these properties in 
+\cref{related-work}:
+we first discuss the crowd counting methods that are classically used, then 
+work on location proof systems and, finally, some work on distance bounding.
+
+\Cref{definitions}, we formalize the notion of protest and the desired 
+verifiability and privacy properties, and in \cref{building-blocks}, we give 
+the relevant background on the building blocks of our solution.
+
+\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+different from that originally proposed by \textcite{DistanceBounding}.
+We provide a proof of its security and formally verify it using 
+Tamarin~\cite{TamarinDB}.
+
+\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
+estimation protocol.
+We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
+in \cref{PerformanceAnalysis}.
+
+Finally, we discuss our assumptions and results in \cref{Discussion} and give 
+our conclusions in \cref{Conclusion}.

### 2019-02-13 paper/location-proofs.tex
Edits location proofs related work

@@
 
-Some location-based services only grant access to resources to users located at a particular location, thus raising the issue of verifying the position claimed by a particular user. 
-In most of the existing schemes, the location of a user/device is determined by the device itself (\eg through GPS) and forwarded to the location-based service provider. 
-One of the main drawbacks of this approach is that a user can cheat by having her device transmit a false location. 
-Therefore, it is possible for a user to be inappropriately granted access to a particular resource while being thousands of kilometers away.
+Some \acp{LBS} only grant access to resources to users located at a particular 
+location, thus raising the issue of verifying the position claimed by a 
+particular user.
+In most of the existing schemes, the location of a user (device) is determined 
+by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
+One of the main drawbacks of this approach is that a user can cheat by having 
+her device transmit a false location.
+Therefore, it is possible for a user to be inappropriately granted access to a 
+particular resource while being thousands of kilometers away.
 
-One possible way to counter this threat is by having the requesting device formally prove that it really is at the claimed location, which gives rise to the concept of \emph{location proof}. 
-In a nutshell, a location proof is a digital certificate attesting that someone was at a particular location at a specific moment in time. 
-A location proof system is an architecture by which users can obtain location proofs from neighboring witnesses (\eg trusted access points or other users) that can later be shown to verifiers who can check the validity of a particular proof \cite{luo2010veriplace, zhu2011applaus}.
-Most of the existing approaches to location proofs require the prover and the witnesses to disclose their identities, thus raising many privacy issues such as the possibility of tracing the movements of users of the location proof architecture.
-However, some location proofs systems, such as PROPS~\cite{PROPS}, exist that provide strong privacy guarantees along with the possibility of verifying the claim of the location.
-\CROCUS shares some similarities with PROPS, although their objective is quite different as it aims at verifying a global property of the population (\ie crowd estimation) in contrast to checking the location claim made by a user, which is an individual property.
-\sonja{any more differences to ours, relevance of this one?} \sonja{add something on platin.io, details unknown but roughly relying on witnesses and graph theory (unique big cluster, assumption of honest majority)}
+One possible way to counter this threat is by having the requesting device 
+formally prove that it really is at the claimed location, which gives rise to 
+the concept of \acp{LP}.
+In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
+a particular location at a specific moment in time.
+\Iac{LPS} is an architecture by which users can obtain \acp{LP} from 
+neighboring witnesses (\eg trusted access points or other users) that can later 
+be shown to verifiers who can check the validity of a particular 
+proof~\cite{luo2010veriplace,zhu2011applaus}.
+Most of the existing approaches to \acp{LP} require the prover and the 
+witnesses to disclose their identities, thus raising many privacy issues such 
+as the possibility of tracing the movements of users of the \ac{LPS}.
+However, some \acp{LPS}, such as PROPS~\cite{PROPS}, exist that provide strong 
+privacy guarantees along with the possibility of verifying the claim of the 
+location.
+
+\CROCUS shares some similarities with PROPS, although their objective is quite 
+different as it aims at verifying a global property of the population (\ie 
+crowd estimation) in contrast to checking the location claim made by a user, 
+which is an individual property.
+
+Another difference is that \CROCUS operates in a more adverse environment.
+\CROCUS must provide \emph{universal verifiability}, this means that all proofs 
+must be available to and verifiable by anyone.
+One problem here is that we have multiple verifiers who might not trust the 
+same witnesses.
+The incentives to cheat are also bigger and consequently the thresholds for 
+collusion are much higher.
+
+\sonja{add something on platin.io, details unknown but roughly relying on 
+  witnesses and graph theory (unique big cluster, assumption of honest 
+  majority)}

### 2019-02-13 paper/protest-model.tex
Minor reformulations in protest model

--- 2018-11-20 paper/protest-model.tex
@@
 The strength function \(\str\) can be used to regulate the trust in the 
-participation count estimated. In general, \(\str\) can be defined as a 
-weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
-weights \(\omega_i\) being the trust in the witness corresponding to that proof 
-share \(s_i\), and the threshold \(\theta\) represents the total trust needed 
-to accept a participant as valid.
+estimated participation count.
+In general, \(\str\) can be defined as a weighted sum of the proof shares, 
+\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
+the witness corresponding to the proof share \(s_i\), and the threshold 
+\(\theta\) represents the total trust needed to accept a participant as valid.
 One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
-Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
-For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
-In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
+Another possibility would be to also have a particular type of witness, called 
+\emph{trusted witness}, participating in the protest. For instance, the role of 
+the trusted witness could be taken by the independent journalist Jane.
+In this situation, the weights would be 1 for trusted witnesses and 
+0 for any other witness, and
 setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.

### 2019-02-13 paper/related-work.tex
Breaks out crowd-counting-methods

--- 2018-11-29 paper/related-work.tex
@@
 \subsection{Crowd counting methods}
+\input{crowd-counting-methods.tex}
 
-The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
-This manual method devised in the 1960s relies on aerial pictures of the event.
-The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
-Clearly, this method is prone to errors as it is based on estimates.
-It provides universal verifiability since anyone can redo the counting using the same pictures.
-However, it is difficult to achieve individual verifiability using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
-We can argue that it also achieves eligibility if all the photos are taken at the same point in time, since then no one can be counted twice.
-Unfortunately, we can only get the peak participation with this method.
-When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where they were taken).
-However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
-From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
-For instance, there is a risk that participants are recognizable from the material if they do not wear masks.
-
-Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
-Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
-This is similar to the method usually used by police (\eg during the protests in Seoul):
-\blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 3.3 square meters
-  \textelp{}
-  The same area would hold nine or 10 people when standing%
-}.
-This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.
-
-In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \cite{NNCrowdCounting}).
-This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
-They are generally based on machine learning techniques, and thus also require a training dataset to work.
-In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
-Universal verifiability can be provided with this method, since someone can always recount the participants using the recorded video material.
-Some degree of individual verifiability could also be provided,
-if Alice can recognize her own face in the video, but this might still be difficult. 
-Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
-In addition, it is difficult (if not impossible) to avoid counting some people twice, thus we cannot argue for eligibility.
-In theory, this class of methods will provide an upper bound
-%, whereas our method outputs a lower bound
-.
-Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
-The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
-
-Another problem for all the above methods is exemplified by the demonstrations in Seoul:
-\blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
-}.
-In this situation it is very difficult to faithfully capture the situation.
-Indeed, even if the scene is taken from different angles, there is the additional problem of not counting people twice.
-
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
-In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
-However, in order to work this method makes many additional assumptions:
-\blockcquote{2016DemonstrationsInSeoul}{%
-The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
-It also assumed that about 20\% of the smartphone signals were repetition from the same device.
-}
-This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
-In addition, as MAC address randomization is now getting a wider adoption precisely to fight against physical tracking, this method will not work any more, although some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough}.
-
-A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
-However, there are several problems with this approach.
-First, it will be difficult to register only the participants' phones, as many bystanders will also be counted.
-Thus, it will not be possible to distinguish clearly between the protesters and the counter-protesters.
-Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI number will not be transmitted anymore in plaintext.
-%need to cite?
-Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in relation to the protest.
-
-An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}.
-This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.
-
-In general for all of the above methods, the more a crowd spreads out, the more difficult it is to determine its size.
-In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
-
-One of the works most closely related to our goal is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
-This method has the benefit of counting everyone who has declared their presence, not just the count at the snapshot of the pictures.
-However, there is no verification as the service must be trusted to behave honestly, and even then, nothing prevents Bob from submitting more than once (violating eligibility).
-Another downside is that the service also requires an Internet connection during the event to register as a participant.
-This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Grace's regime, Grace can shut down the cellular network or Internet backbone as a mean to censor the protest.
-
-Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
-However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.
-
+\subsection{Location proofs}
 \input{location-proofs.tex}

### 2019-02-13 paper/intro.tex
Removes DB from related work in outline

@@
 \cref{related-work}:
-we first discuss the crowd counting methods that are classically used, then 
-work on location proof systems and, finally, some work on distance bounding.
+we first discuss the crowd counting methods that are classically used followed 
+by work on location proof systems.
 

### 2019-02-13 paper/DB-anon-cred.tex
Minor fix in DB-anon-cred

@@
   \small
-  \begin{tabular}{p{0.8\columnwidth}cp{0.8\columnwidth}}
+  \setlength{\ProtoArrowLength}{0.07\linewidth}
+  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
     \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
@@
 originally the possibility to reason on time and space in its model.
-However, thanks to a recent work by Mauw and co-authors~\cite{TamarinDB}, all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.
+However, thanks to a recent work by \textcite{TamarinDB}, all the common 
+properties mentioned in the previous subsection can be equivalently 
+characterized with a causality-based definition relying only on the order of 
+messages.
 

### 2019-02-13 paper/distance-bounding.tex
adds references to appendices
Minor edits about DB protocols in general

--- 2018-11-29 paper/distance-bounding.tex
@@
 
-The main attacks against \ac{DB} protocols can be summarized as follows:
+There are four adversaries for \ac{DB} protocols established in the literature, 
+each of which tries to commit a type of fraud.
+These can be summarized as follows:
 \begin{itemize}
   \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
-  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
-  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
+    possibly honest, prover who is far away from the verifier.
+    (Also known as relaying attack or man-in-the-middle attack.)
+  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
+    who is close to the verifier, to authenticate.
+    \Ac{DBTF} resistance is a very strong property; it implies that if the 
+    accomplice succeeds (with non-negligible probability) he will learn the 
+    prover's secret key.
+  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
+    uses an unsuspecting honest prover close to the verifier to pass as being 
+    close.
+    (This is different from \ac{DBMF} in that the honest prover actually tries 
+    to authenticate to the verifier, but the malicious prover hijacks the 
+    channel at some point(s) during the protocol.)
 \end{itemize}
@@
 Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
-The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
-This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against a verifier who will attempt to impersonate the prover.
-More specifically, we must combine such \iac{PPK} protocol with anonymous 
-credentials.
-The choice of the anonymous-credential system affects the properties we 
-require of the \ac{PPK}, in particular, for the suggested instantiation it must 
-be \iac{PPK} for discrete logarithms.
-For this paper, we assume the existence of such a protocol.
-Candidates for such a protocol include modifications of ~\cite{ProProx} or ~\cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.
+The verifier might also try to track the provers and map their identities to 
+their actions, thus we also require strong privacy.
+In fact, as the construction in \cref{CROCUS} shows, we require \iac{DB} 
+\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.

### 2019-02-13 paper/identity-limits.tex
Adds final comment to conclusions in identity-limits
Makes identity-limits conclusions a subsection
Minor clarification to identity-limits

@@
 \begin{itemize}
-  \item The data must fulfil basic integrity: a person must have parents, who 
-    in turn must have parents, \etc.
+  \item The data must fulfil correctness: a person must have parents, who in 
+    turn must have parents, \etc.
   \item Anyone can detect extraordinary additions, \eg exceptionally many 
@@
     them.
-  \item Addition of persons of foreign heritage must have corresponding 
-    documentation (audit trail) at the Migration Board.
+  \item Addition of persons of foreign heritage must have a corresponding audit 
+    trail at the Migration Board (separate agency).
 \end{itemize}
@@
 
-\section{Conclusions}
+\subsection{Conclusions}
 
@@
 pseudonym, all issuers must act jointly, \eg through \ac{MPC}.
+We do not see this as something impossible, \eg it can be incorporated into the 
+eIDAS regulation already in place in the EU.

### 2019-02-14 paper/protocol.tex
Fixes typo
Minor edits in protocol

@@
 
-We now present \CROCUS, a protocol for privately verifyiable crowd counts.
+We now present \CROCUS, a protocol for privately verifiable crowd counts.
 The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
@@
 person's identity and a cryptographic key\footnote{%
-  This can be done by a centralized authority, such as a nation state with, 
-  \eg, passports; or a decentralized authority, as in the case of a a 
-  collective authority~\cite{collective-signing} powered by 
-  proof-of-personhood~\cite{proof-of-personhood}.
+  This can be done by any \emph{logically} centralized 
+  authority~\cite{SybilAttack}.
+  Although a decentralized authority, as in the case of a collective 
+  authority~\cite{collective-signing} powered by 
+  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
+  that this has scalability issues.
+  See the detailed discussion in \cref{identity-limits}.
+  We will also return to this topic in \cref{Discussion}.
 }.
@@
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
+\item The \emph{organizer} has written a manifesto for the protest and 
+  disseminated it to others.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
@@
     \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration phase, each participant generates a secret key and 
-obtains a signature on it by the \ac{CA} but without revealing it to the 
-\ac{CA}.
+During the registration phase, each participant generates a secret key~\((k, 
+  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
+  it} to the \ac{CA}.
 At the end, each participant will have a signed secret key while the \ac{CA} 
@@
 for an arbitrary number of protests.
-Thus, the registration phase could be easily integrated as part of the issuance 
-of national identity cards, passports or \acp{eID}.
 

### 2019-02-14 paper/system-model.tex
Minor edits in system-model

@@
 
-Throughout this paper, each time we refer to a participant, such as Alice, we actually mean a personal device that can perform cryptographic operations and communicate with other local devices on Alice's behalf.
-Furthermore, we assume that each participant has a digital certificate of her identity signed by a \ac{CA}.
+Throughout this paper, each time we refer to a participant, such as Alice, we 
+actually mean a personal device that can perform cryptographic operations and 
+communicate with other local devices on Alice's behalf.
+Furthermore, we assume that each participant has a digital certificate of her 
+identity signed by \iac{CA}\footnote{%
+  The \ac{CA} must be \emph{logically centralized} to prevent Sybil 
+  attacks~\cite{SybilAttack}.
+  See \cref{identity-limits} for a discussion on existing identity systems and 
+  their limits.
+}.
 

### 2019-02-14 paper/identity-limits.tex
Minor edits in protocol
Edits identity-limits

@@
-\section{Limits of current identity systems}
+\section{Limits of current identity systems}%
+\label{identity-limits}
 
@@
 mechanisms, \eg national identity cards and passports.
+Although this seems centralized at first glance, as we will see below, it is 
+indeed comparable in decentralization to distributed ledgers due to audit 
+trails and separation of duties.
+As we will see, the problem with this system is that its federated structure 
+and reliance on audit trails fails when it comes to issuing a 
+privacy-preserving attribute-based credential for identity (or physical 
+person).
 
-Some more \enquote{decentralized}\footnote{%
-  Provably, it must be logically centralized anyway.
-} methods have been suggested, \eg 
-proof-of-personhood~\cite{proof-of-personhood}.
+Some alternative technologies have been suggested, \eg 
+proofs-of-personhood~\cite{proof-of-personhood}.
+The idea is to ensure a one-to-one mapping between physical persons and some 
+credential.
 In this particular approach, people gather in a room, \emph{everyone ensures} 
 that no one can enter or leave during the process.
-Then \emph{everyone ensures} that everyone gets exactly one identity.
+Then \emph{everyone ensures} that everyone gets exactly one credential.
+This system is independent of existing identities, \eg as established by birth 
+certificates.
+As we will see, the problem with this system is scalability.
 
-We will now discuss the limits and possibilities of these approaches.
+We will now discuss the limits and possibilities of these approaches and in the 
+end conclude with a construction that can solve the problems in practice.
 
@@
 government.
-However, it is usually distributed among a country's hospitals.
+However, it is usually distributed among a country's hospitals (and other 
+agencies).
 It usually works without any problems: citizens --- who have an incentive to 
@@
 But obviously there exists a possibility to create birth certificates without 
-newborn babies, it is just that those who can either do not have any incentive 
-to do so or there are other mechanisms, \eg separation of duties and 
-accountability.
-
-There is one particular situation where the incentive arises:
-to influence democratic processes\footnote{%
-  There are a few more, less relevant, \eg to have multiple identities for 
-  foreign operatives, as seen on film.
-  But those are not significant to our discussion.
-}.
-If the government can create identities and control them, they can use them to 
-vote for themselves in upcoming elections.
-In a well-designed system, however, this should be prevented.
-This varies from country to country (\ie system to system).
+newborn babies, however, there are other mechanisms, \eg separation of duties 
+and audit trails that prevent this.
+This is best illustrated with a case study.
 
@@
 Each entry in the registry has a unique identification number.
-The electoral roll is created from the population 
-registry~\cite{Valmyndigheten-ElectoralRoll}.
+The population registry serves various purposes, one, arguably among the most 
+important, is the generation of the electoral 
+roll~\cite{Valmyndigheten-ElectoralRoll}.
 
@@
 Obviously the one who creates entries in the population registry can do that 
-even without such documents, so there must be some separation of duty, 
-accountability or transparency to prevent the agency from performing a Sybil 
-attack.
+even without such documents, so there must be some separation of duty, audit 
+trail or transparency to prevent the agency from performing a Sybil attack.
 In the case of Sweden, the population registry is public.
@@
     Individual women and men would also notice if extra children were added to 
-    them.
+    them (they would receive additional child benefits).
   \item Addition of persons of foreign heritage must have a corresponding audit 
@@
 
-In Sweden, there are several entities that are authorized to issue identity 
-cards; \eg the Swedish Tax Agency, the Swedish Police, the banks.
+In Sweden, the identity credential system is federated.
+There are several entities that are authorized to issue identity cards; \eg the 
+Swedish Tax Agency, the Swedish Police, the banks.
 Thus, technically, to detect a Sybil attack by them, \ie fake identities, one 
-must check the ID against the population registry.
+must check the ID against the population registry and follow the audit trail.
 With anonymous credentials, this becomes a problem.
 
-If two entities issue (non-anonymous) identity credentials to Alice, there is 
-no problem: if she uses the first to authenticate to Bob, and later comes back 
-and uses the second, Bob will know that she is Alice both times.
+At some point, Alice must get her first ID card.
+By definition, she does not have a previous ID card that can authenticate her 
+identity.
+Thus, for Alice to get her first ID card, she must bring a \emph{close relative 
+  who has an ID card} to vouch for her identity.
+This reduces the problem of audit trail to that of the relative.
+This works because close relatives have strong incentives to be honest, few 
+would allow an identity theft of one of their close relatives.
+
+If two entities issue (non-anonymous, electronic) identity credentials to 
+Alice, there is no problem: if she uses the first to authenticate to Bob, and 
+later comes back and uses the second, Bob will know that she is Alice both 
+times.
 In both cases, if Bob doubts the credentials, he can follow the audit trail.
-With anonymous credentials that prevent multiple use, however, this is no 
-longer the case.
-Thus issuers of such credentials must synchronize, so that if one has issued 
-such credentials to Alice, the others must not issue another.
 
-This problem is amplified by the fact that there can be no audit trail from the 
-authentication, due to the anonymity.
-Thus, individual issuers have the possibility to perform Sybil attacks.
-However, this problem can be solved.
-Since all individual issuers of credentials must synchronize to not issue more 
-than one anonymous credential to Alice, they might just as well act together 
-(\ac{MPC}) in the issuing process --- thus introducing dual control.
+There is one problem in the current system: it is difficult for Alice to detect 
+if the \ac{CA} issues an identity credential (electronic or not) in her name 
+and let someone else use it.
+
+With privacy-preserving attribute-based credentials, we face several problems:
+The first is that there can be no audit trail from the authentication, due to 
+the anonymity.
+For most attributes, \eg age, everything works, the problem is that individual 
+issuers have the possibility to perform Sybil attacks.
+However, one-to-one mappings of credentials to physical persons are not 
+possible.
+Alice can get one credential from \ac{CA} \(A\) and another from \(B\), if Bob 
+must accept credentials issued by both \(A\) and \(B\), then Alice suddenly has 
+two valid credentials instead of only one.
 
@@
 same place at the same time.
+This is the issue of scalability.
 This is obviously not possible and to make it feasible we must split across 
@@
 Getting everyone to be at some fixed locations at the same time is even 
-difficult to achieve during Election Day, it must usually be spread across the 
-time of the whole day.
+difficult to achieve during Election Day, it must usually be spread across 
+several locations and across time of the whole day.
 This would solve the problems of the issuance of anonymous credentials 
-mentioned above (it provides the same properties as \ac{MPC} did above), if it 
-only scaled.
+mentioned above, if it only scaled.
 
@@
 hard to achieve such a scheme.
-The goal is to have one identity (pseudonym) per physical person.
-This goal is joint with the \enquote{birth-certificate system} which actually 
-achieves the goal quite nicely in practice.
-However, since the birth-certificate system relies on audit trails to function, 
-it cannot deal with issuing anonymous credentials.
-Thus the ideas from proof-of-personhood, where everyone must act jointly, can 
-solve this problem.
-To issue anonymous credentials that certify one physical person behind a 
-pseudonym, all issuers must act jointly, \eg through \ac{MPC}.
-We do not see this as something impossible, \eg it can be incorporated into the 
-eIDAS regulation already in place in the EU.
+The birth-certificate system is currently implemented in practice, however, 
+there is a need to bridge an audit trail from electronic credentials to the 
+rest of the birth-certificate system.
+Furthermore, due to the impossibility of an audit trail for anonymous 
+credentials, we must introduce some form of separation of duties.
+
+To bridge electronic credentials to the audit trail of non-electronic 
+identities, an issuer should include a reference in the electronic credential 
+to the credential it is based upon.
+
+The separation of duties for issuing anonymous credentials can be achieved by 
+collective signing~\cite{collective-signing}, \ie that all issuers (and 
+possibly others) must act together to issue every credential.
+This introduces dual control, which makes it harder for any one issuer to 
+perform a Sybil attack.
+This can be connected to the audit trail by requiring that the request for 
+issuance is signed by a valid electronic identity, thus connecting to the audit 
+trail of that.
+Note, however, that this does not connect Alice's anonymous credentials back to 
+her through any audit trail, the use of anonymous credentials is still 
+inauditable.
+The connection to the audit trail simply makes it harder for any individual 
+issuer to cheat the other issuers into jointly issuing Sybil credentials.
+
+We note that the issuing of non-anonymous credentials can be done either using 
+an X.509-style \ac{PKI} (as is currently practiced) or using collective 
+signing, as outlined for anonymous credentials above.
+
+We do not see these requirements as impossible, \eg collective signing can be 
+incorporated into the eIDAS regulation already in place to govern electronic 
+identities in the EU.

### 2019-02-15 paper/system-model.tex
Emphasizes relation to petitions

@@
 
-We note that, in general terms, protesting is very similar to petitions, which 
-in turn are similar to voting.
-Indeed, all three situations correspond to situations in which many individuals express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
+We note that, in general terms, protests are petitions with a given time and 
+location.
+Protests, petitions and elections share that in all three many individuals 
+express their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or 
+persecution).
+For that reason we have strong requirements for verification and privacy for 
+elections, it follows that we should have similar properties for protests
+and petitions.
 

### 2019-02-15 paper/adversary-model.tex
Changes to global, passive adversary

--- 2018-11-29 paper/adversary-model.tex
@@
 We now provide a concretely defined system and adversary model.
-We give three definitions, each defining an adversary with increasingly stronger 
+We give three definitions, each defines an adversary with increasingly stronger 
 capabilities (\ie more auxiliary information).
@@
 \item\label{deanonymizing-storage-adversary}
-  \emph{National eavesdropping adversary}:
+  \emph{Global, passive adversary}:
   The situation is the same as in \cref{in-system-adversary}, but now the storage 
@@
 
-As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
-even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
-such as Tor~\cite{Tor}.
-The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
-\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
-so the adversary cannot control \(S\), but since \(S\) provides public access 
-the adversary can (possibly constantly) query it and learn things with little 
-delay.
+As to \(S\), \cref{in-system-adversary} is equivalent to the adversarial 
+storage \(S\) receiving only perfectly anonymous connections.
+Another way to see it is that the adversary cannot control \(S\) but can learn 
+what \(S\) learns as soon as \(S\) learns it; \eg \(S\) is operated outside the 
+adversary's jurisdiction and so the adversary cannot control \(S\), but since 
+\(S\) provides public access the adversary can (possibly constantly) query it 
+and learn things with little delay.
+Posed like this, the adversary cannot observe the channel between \(P\) and 
+\(S\), \eg when \(P\) uses tools such as Tor~\cite{Tor}.
 Note that the adversary is also allowed to submit data to \(S\) for storage, 
@@
 
-\Cref{deanonymizing-storage-adversary} is a stronger adversary.
-Although the adversary cannot observe the channel between \(P\) and \(S\), the 
-adversary can still learn the identity of \(P\).
-\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
-thus perform time-correlation attacks on messages on the network and events 
-observed from \(S\).
+\Cref{deanonymizing-storage-adversary} is a much stronger adversary.
+Even if the adversary cannot observe the channel between \(P\) and \(S\) (as is 
+the case with Tor), the adversary can still learn the identity of \(P\) through 
+\eg time-correlation attacks (as is the case with Tor).
+A nation state can potentially monitor the traffic of all \acp{ISP} and thus 
+perform time-correlation attacks on messages on the network and events observed 
+from \(S\).
 We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 

### 2019-02-15 paper/distance-bounding.tex
Adds functional encryption explicitly to TF

@@
     accomplice succeeds (with non-negligible probability) he will learn the 
-    prover's secret key.
+    prover's secret key\footnote{%
+      This means that even things like functional encryption will not help.
+    }.
   \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 

### 2019-02-15 paper/adversary-model.tex

@@
 
-We now provide a concretely defined system and adversary model.
-We give three definitions, each defines an adversary with increasingly stronger 
-capabilities (\ie more auxiliary information).
+% We now provide a concretely defined system and adversary model.
+% We give three definitions, each defining an adversary with increasingly stronger 
+% capabilities (\ie more auxiliary information).
 

### 2019-02-15 paper/intro.tex

@@
 
-\paragraph*{Contributions}
+%\paragraph*{Contributions}
 
-Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
-way to securely estimate crowd counts in protests\footnote{%
-  If location is ignored, it can be reduced to privacy-preserving yet 
-  verifiable petitions.
-}.
+%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
+%way to securely estimate crowd counts in protests\footnote{%
+%  If location is ignored, it can be reduced to privacy-preserving yet 
+%  verifiable petitions.
+%}.
+%
+%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
+%including \ac{DBDH} (which was an attack against the original protocol of 
+%Brands and Chaum) and \ac{DBTF}.
+%More importantly, it is public-key, handles malicious impersonating verifiers.
+%Since it is based on the Schnorr protocol, it provides a distance-bounded 
+%\ac{PK} for discrete logarithms.
+%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
+%distance-bounding version and thus make general privacy-preserving, 
+%attribute-based credential systems distance bounding.
 
-Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
-including \ac{DBDH} (which was an attack against the original protocol of 
-Brands and Chaum) and \ac{DBTF}.
-More importantly, it is public-key, handles malicious impersonating verifiers.
-Since it is based on the Schnorr protocol, it provides a distance-bounded 
-\ac{PK} for discrete logarithms.
-That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
-distance-bounding version and thus make general privacy-preserving, 
-attribute-based credential systems distance bounding.
+% The paper is organized as follows.
+% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}).
+% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
 
-\paragraph*{Outline}
-
-The paper is organized as follows.
-\Cref{system-model}, we describe our system model and summarize the desired 
-properties for crowd counting.
-We then discuss related work in terms of these properties in 
-\cref{related-work}:
-we first discuss the crowd counting methods that are classically used followed 
-by work on location proof systems.
-
-\Cref{definitions}, we formalize the notion of protest and the desired 
-verifiability and privacy properties, and in \cref{building-blocks}, we give 
-the relevant background on the building blocks of our solution.
-
-\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
-different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security and formally verify it using 
-Tamarin~\cite{TamarinDB}.
-
-\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
-estimation protocol.
-We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
-in \cref{PerformanceAnalysis}.
-
-Finally, we discuss our assumptions and results in \cref{Discussion} and give 
-our conclusions in \cref{Conclusion}.
+%The paper is organized as follows.
+%\Cref{system-model}, we describe our system model and summarize the desired 
+%properties for crowd counting.
+%We then discuss related work in terms of these properties in 
+%\cref{related-work}:
+%we first discuss the crowd counting methods that are classically used followed 
+%by work on location proof systems.
+%
+%\Cref{definitions}, we formalize the notion of protest and the desired 
+%verifiability and privacy properties, and in \cref{building-blocks}, we give 
+%the relevant background on the building blocks of our solution.
+%
+%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+%different from that originally proposed by \textcite{DistanceBounding}.
+%We provide a proof of its security and formally verify it using 
+%Tamarin~\cite{TamarinDB}.
+%
+%\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
+%estimation protocol.
+%We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
+%in \cref{PerformanceAnalysis}.
+%
+%Finally, we discuss our assumptions and results in \cref{Discussion} and give 
+%our conclusions in \cref{Conclusion}.

### 2019-02-15 paper/location-proofs.tex
Breaks out crowd-counting-methods

@@
-\subsection{Location proofs}
+%\subsection{Location proofs}
+\section{Distance bounding and location proofs}
+\label{db-and-lp}
+\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate.
+These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
+As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
+\Ac{DB} protocols enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
+%Time critical phases are complemented by slow phases during which the time is not taking into account. 
+Slow phases, during which the time is not taken into account, complement the time critical phases.
+At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in their vicinity.
+In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
+
+The main attacks against \ac{DB} protocols can be summarized as follows:
+\begin{itemize}
+  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
+  \item \Acf{DBMF}: the adversary illegitimately authenticates, possibly using an honest prover far away from the verifier.
+  \item \Acf{DBTF}: a legitimate but malicious prover helps an accomplice close to the verifier to authenticate.
+  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but uses an unsuspecting honest prover close to the verifier to pass as being close.
+\end{itemize}
+There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+
+The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
+Indeed, in this context it does not make sense to protect against the verifier as they can easily impersonate the prover as they have knowledge of their secret key.
+There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
 

### 2019-02-15 paper/protest-model.tex

--- 2018-11-30 paper/protest-model.tex
@@
-\subsection{Defining and formalizing protest and crowd estimation}%
+\subsection{Protest,  crowd estimation}%
 \label{protest-model}
@@
 The strength function \(\str\) can be used to regulate the trust in the 
-participation count estimated. In general, \(\str\) can be defined as a 
-weighted sum of the proof shares, \(\str = \sum \omega_i s_i\), with the 
-weights \(\omega_i\) being the trust in the witness corresponding to that proof 
-share \(s_i\), and the threshold \(\theta\) representing the total trust needed 
-to accept a participant as eligible.
-One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) be the number of required witnesses.
-Another possibility would be to also have a particular type of witness, called \emph{trusted witness}, participating in the protest. 
-For instance, the role of the trusted witness could be taken by Jane, the independent journalist. 
-In this situation, the weights would be 1 for trusted witnesses and 0 for any other witness, and
-setting \(\theta = 1\) would require at least one proof share issued by a trusted witness.
+estimated participation count.
+In general, \(\str\) can be defined as a weighted sum of the proof shares, 
+\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
+the witness corresponding to the proof share \(s_i\), and the threshold 
+\(\theta\) represents the total trust needed to accept a participant as valid.
+One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.
+Another possibility would be to also have a particular type of witness, called 
+\emph{trusted witness}, participating in the protest. For instance, the role of 
+the trusted witness could be taken by the independent journalist Jane.
+In this situation, the weights would be 1 for trusted witnesses and 
+0 for any other witness, and
+setting \(\theta = 1\) would require at least one proof share issued by a 
+trusted witness.
 Finally, both approaches can be combined by giving a weight of 1 to all 

### 2019-02-15 paper/protocol.tex

--- 2018-11-30 paper/protocol.tex
@@
 We now present \CROCUS, a protocol for privately verifiable crowd counts.
-The protocol consists of three phases:
-before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
-during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
-and after the protest, with the verification step (in
-\cref{ProtocolVerification}). Note that some of the figures with
-protocol minutiae from related work are in~\cref{anon-cred-figures}.
+The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
+join, participation, submission (all in in \cref{ProtocolDuring}) and
+verification (in \cref{ProtocolVerification}).
 
 Several entities are involved in our protocol.
-First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
-person's identity and a cryptographic key
-%\footnote{%
-%  This can be done by a centralized authority, such as a nation state with, 
-%  \eg, passports; or a decentralized authority, as in the case of a a 
-%  collective authority~\cite{collective-signing} powered by 
-%  proof-of-personhood~\cite{proof-of-personhood}.
-%}.
-For simplicity, we assume that the \ac{CA} is a trusted third-party, but its role is only important to prevent Sybil attacks, so in practice we only need the \ac{CA} to not be aligned with the protesters.
-For instance, the role of the \ac{CA} can be assumed by a centralized authority, such as a nation state with,
-\eg, passports, and that would not impact the trust of a participation count for a protest \emph{against} this state.
-However, any pro-state demonstration in that context would be subject to Sybils.
-Another possibility would be to use a decentralized authority, as in the case of a
-collective authority~\cite{collective-signing} powered by 
-proof-of-personhood~\cite{proof-of-personhood}.
+First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
+person's identity and a cryptographic key\footnote{%
+  This can be done by any \emph{logically} centralized 
+  authority~\cite{SybilAttack}.
+  Although a decentralized authority, as in the case of a collective 
+  authority~\cite{collective-signing} powered by 
+  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
+  that this has scalability issues.
+  See the detailed discussion in \cref{identity-limits}.
+  We will also return to this topic in \cref{Discussion}.
+}.
 The \ac{CA} is only involved in the setup phase.
@@
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
+\item The \emph{organizer} has written a manifesto for the protest and 
+  disseminated it to others.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
@@
     \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration step, each participant generates a secret key and 
-obtains a signature on it by the \ac{CA} but without revealing it to the 
-\ac{CA}.
+During the registration phase, each participant generates a secret key~\((k, 
+  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
+  it} to the \ac{CA}.
 At the end, each participant will have a signed secret key while the \ac{CA} 
@@
 for an arbitrary number of protests.
-Thus, the registration step could be easily integrated as part of the issuance 
-of national identity cards, passports or \acp{eID}.
 

### 2019-02-15 paper/system-model.tex
Adds another pointer to difference to petition

@@
-\section{System and adversary model}%
+\section{System model}%
 \label{system-model}
 
-To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.
+To set the stage, we will now describe our system model including
+assumptions and a summary of the desired properties for crowd
+counting% and the adversary model
+.
 
-\subsection{System model and physical assumptions}%
+\subsection{Model and assumptions}%
 \label{assumptions}
@@
 
-We draw inspiration from the three traditionally desired properties for verifiability for voting:
+We draw inspiration from properties for voting systems as formalized
+in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
 \daniel{Find a new ref for voting verifiability properties, Douglas commented 
@@
 In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must 
-include temporal\footnote{%
-  Elections also have some temporal aspects, such that one cannot vote at any 
-  time and a vote in one election should not be reusable in the next election.
-  However, the temporal relation for a protest is not as strictly defined as for 
-  elections as a protest can start at any time and last for an arbitrary period 
-  of time.%
-} and spatial eligibility (\ie each participation proof satisfies some temporal 
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
+The eligibility requirement is slightly different as for protests it must also
+include temporal %\footnote{%
+%   Elections also have some temporal aspects, such that one cannot vote at any 
+%   time and a vote in one election should not be reusable in the next election.
+%   However, the temporal relation for a protest is not as strictly defined as for 
+%   elections as a protest can start at any time and last for an arbitrary period 
+%   of time.%
+% }
+and spatial eligibility (\ie each participation proof satisfies some temporal 
 and spatial relation to the protest).
 In essence, the proof must bind the person to the time and location of the protest.
+(This is the difference to a petition.)
 
-In addition to the verification requirements, we also need to define the 
-privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
+privacy properties for voting protocols are given as:
 \begin{description}
@@
 
-Coercion resistance is not possible to achieve for protests.
+%Coercion resistance is not possible to achieve for protests.
+Coercion resistance in voting typically relies on physical isolation
+(\eg private voting booths), including for digital systems, 
+and that is by definition not possible for public events.
 For instance, someone could simply physically bring Alice to a protest against her will.
-Receipt freeness, while appealing at first glance, is not desirable (probably 
-not possible) in our context since this will conflict with verifiability: in 
-contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
-cause of the protest) implies receipt freeness for \emph{that} the voter voted 
-(\ie the protester was there), which conflicts with verifiability.
+As for receipt freeness, while
+desirable \emph{in itself}, it implies a conflict with verifiability in our context:
+%appealing at first glance, is not desirable (probably not possible)
+%in our context since this will conflict with verifiability:
+in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
+cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
+(\ie the protester was there), which would make verifiability impossible.
 
-Thus, in our context the crucial property is therefore privacy.
+Therefore in our context, the crucial property is  vote privacy.
 More precisely, for the protester we want unlinkability (from the adversary's 

### 2019-02-18 paper/system-model.tex
Fixes comment on identity systems in system model

--- 2019-02-15 paper/system-model.tex
@@
 communicate with other local devices on Alice's behalf.
-Furthermore, we assume that each participant has a digital certificate of her 
-identity signed by \iac{CA}\footnote{%
-  The \ac{CA} must be \emph{logically centralized} to prevent Sybil 
-  attacks~\cite{SybilAttack}.
+Furthermore, we assume that each participant has a digital certificate signed 
+by \iac{CA}\footnote{%
+  We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
+  do.
+  The \ac{CA} can be centralized or decentralized, but as 
+  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
+    centralized} to prevent Sybil attacks.
   See \cref{identity-limits} for a discussion on existing identity systems and 
   their limits.
+} that ensures a one-to-one mapping between an identity and a cryptographic 
+key\footnote{%
+  For every identity there exists at most one valid digital certificate.
 }.
@@
 In essence, the proof must bind the person to the time and location of the protest.
+(This is the difference to a petition.)
 

### 2019-02-19 paper/identity-limits.tex
Comments out perfectly decentralized, private birth certs

@@
 
-This makes the audit trail more complex.
-It is also difficult to detect modifications to these records, since they are 
-not public.
+This makes the audit trail more complex, but it is still possible to follow the 
+audit trail.
+However, it is difficult to detect modifications to these records, since they 
+are not public.
 
-\subsubsection{Perfectly decentralized and private birth-certificates approach}
-
-There are no audit records, the one who can create authentic birth certificates 
-can perform Sybil \dots
+%\subsubsection{Perfectly decentralized and private birth-certificates approach}
+%
+%In perfectly decentralized system
+%There are no audit records, the one who can create authentic birth certificates 
+%can perform Sybil \dots
 

### 2019-02-19 paper/protocol.tex
Comments out perfectly decentralized, private birth certs

--- 2019-02-14 paper/protocol.tex
@@
 person's identity and a cryptographic key\footnote{%
-  This can be done by any \emph{logically} centralized 
-  authority~\cite{SybilAttack}.
-  Although a decentralized authority, as in the case of a collective 
-  authority~\cite{collective-signing} powered by 
-  proof-of-personhood~\cite{proof-of-personhood}, would be desirable, we think 
-  that this has scalability issues.
-  See the detailed discussion in \cref{identity-limits}.
-  We will also return to this topic in \cref{Discussion}.
+  This can be implemented using any \ac{CA} that prevents Sybil 
+  attacks~\cite{SybilAttack} and ensures a one-to-one mapping between a person 
+  and a cryptographic key.
+  \Ie for each identity it issues one-and-only-one cryptographic key.
 }.

### 2019-02-19 paper/distance-bounding.tex
Fixes typo in \cref to protocol section

@@
 their actions, thus we also require strong privacy.
-In fact, as the construction in \cref{CROCUS} shows, we require \iac{DB} 
+In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
 \ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
+For this paper, we assume the existence of such a protocol.
+Candidates for such a protocol include modifications of ~\cite{ProProx} or \cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2019-02-19 paper/location-proofs.tex
Removes DB from location-proofs

--- 2019-02-13 paper/location-proofs.tex
@@
-\subsection{Location proofs}
-
+\subsection{Distance bounding and location proofs}
+\label{db-and-lp}
 Some \acp{LBS} only grant access to resources to users located at a particular 

### 2019-02-19 paper/adversary-model.tex
Reduces to A1 only, adds discussion of A1, A2, A3 (fixes #164)

--- 2018-11-30 paper/adversary-model.tex
@@
 
-\begin{adversaries}
-\item\label{in-system-adversary}
-  \emph{In-system adversary}:
 The adversary maliciously controls \(W\).
@@
   as side information, \eg by face recognition or inference from address
-    to identiy.
+  to identity.
 }
 
-\item\label{deanonymizing-storage-adversary}
-  \emph{National eavesdropping adversary}:
-  The situation is the same as in \cref{in-system-adversary}, but now the storage 
-  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
-  However, \(W\) still learns only the protocol data, no auxiliary data.
-
-%\item\label{deanonymizing-witness-adversary}
-%  \emph{Deanonymizing-witness adversary}:
-%  Everything is the same as in \cref{deanonymizing-witness-adversary}, except 
-%  that now \(W\) also learns \(P\)'s identity from an auxiliary channel.
-\end{adversaries}
-
-The in-system adversary (\cref{in-system-adversary}) represents an adversary 
-that has no access to data from outside the system, \eg inferences that can be 
-done from the communication layer (\eg IP-addresses mapped to physical 
-identities), which means that it has only the protocol data at its disposal.
-
-We find \cref{in-system-adversary} suitable when the protester and witness both 
-move in a crowd and there is no way for the witness to decide exactly with whom 
-he or she communicates with.
-(The protesters could also simply wear masks.)
-We consider this a fair model for our purposes: if the adversary can 
-deanonymize the protesters \emph{at the physical location} and thus arrest 
-them, the adversary can do that independently of whether the protesters use our 
-protocol or not --- thus our protocol cannot make things worse in such a 
-situation.
-
-As to \(S\), \cref{in-system-adversary} corresponds to an adversary who cannot 
-even observe the channel between \(P\) and \(S\), \eg when \(P\) uses tools 
-such as Tor~\cite{Tor}.
-The adversary cannot control \(S\) but can learn what \(S\) learns as soon as 
-\(S\) learns it; \eg \(S\) is operated outside the adversary's jurisdiction and 
-so the adversary cannot control \(S\), but since \(S\) provides public access 
-the adversary can (possibly constantly) query it and learn things with little 
-delay.
-Note that the adversary is also allowed to submit data to \(S\) for storage, 
-just like everyone else.
-
-\Cref{deanonymizing-storage-adversary} is a stronger adversary.
-Although the adversary cannot observe the channel between \(P\) and \(S\), the 
-adversary can still learn the identity of \(P\).
-\Eg a national state can potentially monitor the traffic of all \acp{ISP} and 
-thus perform time-correlation attacks on messages on the network and events 
-observed from \(S\).
-We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
-the identity of \(P\) in the communication with \(S\).
-
-%However, in some situations this might not be the case: \Eg if the crowd is not 
-%dense the witness will likely see the face of the protester.
-%If the witness is controlled by the adversary, then it is likely that the 
-%witness can capture a picture of the face, which can be turned into an identity 
-%through face recognition.
-%There are various such scenarios leading to the adversary learning the 
-%protester's identity, we capture this as 
-%\cref{deanonymizing-witness-adversary}.
+This adversary represents an adversary that has no access to data from outside 
+the system, \eg inferences that can be made from the communication layer (\eg 
+IP-addresses mapped to physical identities or face recognition), which means 
+that it has only the protocol data at its disposal.

### 2019-02-19 paper/reflections-adversary-models.tex
Renames adversary-model discussion to reflections

\section{Reflections on possible adversary models}%
\label{reflections-adversary-model}

% We now provide a concretely defined system and adversary model.
% We give three definitions, each defining an adversary with increasingly stronger 
% capabilities (\ie more auxiliary information).

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
  P))\) for some function \(f\), and the time of the communication 
(\(t_{P,S}\)).
This is illustrated in \cref{fig:base-adversary}.

\begin{figure}
  \centering
  \includegraphics{base-adversary.tikz}
  \caption{\label{fig:base-adversary}%
    An overview of the in-system adversary model.
    The protester with real identity \(P\) and witness with real identity \(W\) 
    communicate.
    They exchange protocol data as a function \(d\) of the protest and protester, \(d_{P,W}(\cid, P)\), and record the time it 
    happened, \(t_{P,W}\).
    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
    the storage \(S\), who records the time that happened, \(t_{P,S}\).
    Both the witness \(W\) and the storage \(S\) are controlled by the adversary 
    \(A\) (from \cref{in-system-adversary}).
  }
\end{figure}

\begin{adversaries}
\item\label{in-system-adversary}
  \emph{In-system adversary}:
  The adversary maliciously controls \(W\).
  The adversary honest-but-curiously controls \(S\).
  The adversary only learns the protocol data --- \ie what is sent over the 
  channel, no auxiliary data\footnote{%
    By auxiliary data we mean any data outside of the protocol, \ie
    meta-data such as who is on the other side of the channel obtained
    as side information, \eg by face recognition or inference from address
    to identiy.
  }

\item\label{deanonymizing-witness-adversary}
  \emph{Deanonymizing-witness adversary}:
  Everything is the same as in \cref{in-system-adversary}, except that now 
  \(W\) learns \(P\)'s identity from an auxiliary channel.
  However, \(S\) still learns only the protocol data, no auxiliary data.

\item\label{deanonymizing-storage-adversary}
  \emph{Deanonymizing-storage adversary}:
  The situation is the same as in \cref{in-system-adversary}, but now the storage 
  \(S\) learns the protester \(P\)'s identity from an auxiliary channel.
  However, \(W\) still learns only the protocol data, no auxiliary data.

\item\label{deanonymizing-adversary}:
  \emph{Deanonymizing adversary}:
  Everything is the same as in \cref{in-system-model}, except that now both 
  \(W\) and \(S\) learns \(P\)'s identity from an auxiliary channel.
\end{adversaries}

The in-system adversary (\cref{in-system-adversary}) represents an adversary 
that has no access to data from outside the system, \eg inferences that can be 
done from the communication layer (\eg IP-addresses mapped to physical 
identities or face recognition), which means that it has only the protocol data 
at its disposal.

We find \cref{in-system-adversary} suitable when the protester and witness both 
move in a crowd and there is no way for the witness to decide exactly with whom 
he or she communicates with.
(The protesters could also simply wear masks.)
We consider this a fair model for our purposes: if the adversary can 
deanonymize the protesters \emph{at the physical location} and thus arrest 
them, the adversary can do that independently of whether the protesters use our 
protocol or not --- thus our protocol cannot make things worse in such a 
situation.

However, in some situations this might not be the case: \Eg if the crowd is not 
dense the witness will likely see the face of the protester.
If the witness is controlled by the adversary, then it is likely that the 
witness can capture a picture of the face, which can be turned into an identity 
through face recognition.
There are various such scenarios leading to the adversary learning the 
protester's identity, we capture this as 
\cref{deanonymizing-witness-adversary}.

As to \(S\), \cref{in-system-adversary} is equivalent to the adversarial 
storage \(S\) receiving only perfectly anonymous connections.
Another way to see it is that the adversary cannot control \(S\) but can learn 
what \(S\) learns as soon as \(S\) learns it; \eg \(S\) is operated outside the 
adversary's jurisdiction and so the adversary cannot control \(S\), but since 
\(S\) provides public access the adversary can (possibly constantly) query it 
and learn things with little delay.
Posed like this, the adversary cannot observe the channel between \(P\) and 
\(S\), \eg when \(P\) uses tools such as Tor~\cite{Tor}.
Note that the adversary is also allowed to submit data to \(S\) for storage, 
just like everyone else.

\Cref{deanonymizing-storage-adversary} is a much stronger adversary, 
essentially a global, passive adversary.
Even if the adversary cannot observe the channel between \(P\) and \(S\) (as is 
the case with Tor), the adversary can still learn the identity of \(P\) through 
\eg time-correlation attacks (as is the case with Tor).
A nation state can potentially monitor the traffic of all \acp{ISP} and thus 
perform time-correlation attacks on messages on the network and events observed 
from \(S\).
We capture this in \cref{deanonymizing-storage-adversary}, where \(A\) learns 
the identity of \(P\) in the communication with \(S\).

The strongest adversary, \cref{deanonymizing-adversary}, is a combination of 
\cref{deanonymizing-storage-adversary,deanonymizing-wit-adversary}.

\subsection{Security analysis}

We are secure against \cref{in-system-adversary}.

\Cref{deanonymizing-witness-adversary} can link a protester's identity to the 
\(\cid\).
Specifically, the protester proves very strongly that it knows a secret key 
which is used to compute a \(\pid\) based on \(\cid\).

However, we can prevent this attack by hiding the \(\cid\) and blinding the 
\(\pid\) in the \ac{PPK} run with the witness.
We must blind the \(\pid\), otherwise the adversary learns the identity~\(P\) 
corresponding to \(\pid\) from \(W\) and later what \(\cid\) corresponds to 
\(\pid\) from \(S\) --- thus linking \(\cid\) to \(P\).
Hiding \(\cid\) implies that there must be more than one possible \(\cid\), \ie 
that there are both a protest and a counter-protest at the same location.

Hiding the \(\cid\) would also solve the potential problem of biased 
witnessing, \ie that witnesses refuse to act as witnesses for certain 
\(\cid\)'s.

\Cref{deanonymizing-storage-adversary} can link \(\cid\) to \(P\).
Since \(S\) learns the identity \(P\) from the auxiliary channel and learns 
\(\cid\) from the submitted data.
Note that this step cannot use the hiding and blinding above, since that would 
not be verifiable for any third party.

However, we can prevent this attack by submitting proofs in bulk.
If protesters exchange proofs with each other, then they can submit each 
others' proofs --- but this only works if each protester submits proofs for 
more than one \(\cid\)!
This also means that the \ac{NIZK} proofs must be computed during the protest, 
to be exchanged, and not after the protest.

\Cref{deanonymizing-adversary} can always link \(\cid\) to \(P\).
The hiding-and-blinding that protects against \(W\) is not compatible with the 
exchange of unblinded proofs that protects against \(S\).

\subsection{Discussion}

The likelihood of there being both a protest and a counter protest is small, it 
is simply not practiced like that today.
Even if that would be the practice, consider the scenario where skinheads try 
to blend into another crowd.
Thus hiding the \(\cid\) would give minor protection in practice.

### 2019-02-19 paper/adversary-model.tex
Adapts adversary figure to only one adversary

@@
   \caption{\label{fig:base-adversary}%
-    An overview of the in-system adversary model.
-    The protester with real identity \(P\) and witness with real identity \(W\) 
-    communicate.
-    They exchange protocol data as a function \(d\) of the protest and protester, \(d_{P,W}(\cid, P)\), and record the time it 
-    happened, \(t_{P,W}\).
+    An overview of the adversary model.
+    The protester (with real identity) \(P\) and witness (with real identity) 
+    \(W\) communicate.
+    They exchange protocol data as a function~\(d\) of the protest and 
+    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
+    \(t_{P,W}\).
     The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
     the storage \(S\), who records the time that happened, \(t_{P,S}\).
-    Both the witness \(W\) and the storage \(S\) are controlled by the adversary 
-    \(A\) (from \cref{in-system-adversary}).
+    Both the witness \(W\) and the storage \(S\) are controlled by the 
+    adversary.
   }

### 2019-02-19 paper/adversary-model.tex
Minor edits to adversary model

@@
 
-This adversary represents an adversary that has no access to data from outside 
-the system, \eg inferences that can be made from the communication layer (\eg 
-IP-addresses mapped to physical identities or face recognition), which means 
-that it has only the protocol data at its disposal.
+This adversary has no access to data from outside the system, \eg inferences 
+that can be made from the communication layer (\eg IP-addresses mapped to 
+physical identities or face recognition from the protest), which means that it 
+has only the protocol data at its disposal.

### 2019-02-20 paper/protocol.tex
Changes to use \TS instead of S, adds \TSstore

@@
       W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
-      \text{where} \\
+      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+      \pi_{\wid})],\quad \text{where} \\
         & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
@@
         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
-      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
-      \text{where}\\
+      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+      \pi_{\pid})],\quad \text{where}\\
         & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
@@
 
-To verify the participation count for a protest \(\prtst\) with identifier \(cid_0\),
-a verifier must download from the storage system S the set \(S_{\prtst}\) of all \(s_P\) and \(s_W\) tuples containing \(cid_0\).
-Then from \(S_{\prtst}\), a verifier can build, in succession,
-(a) the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P,s_W)\) corresponding to a witness  \(i\) and a protester \(j\),
-(b) the participation proof \(\prf_{j}\) for each protester \(j\),
-(c) the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs for all protesters in \(P\),
- and finally the participation count, cardinality of the previous set.
+To verify the participation count for a protest \(\prtst\) with identifier 
+\(\cid_0\), a verifier must download from the storage system \(\TS\) the set 
+\(\pshs_{\cid_0}\) of all \(s_P\) and \(s_W\) tuples containing \(\cid_0\).
+Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
+\begin{enumerate*}
+\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
+    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
+\item the participation proof \(\prf_{j}\) for each protester \(j\),
+\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
+  for all protesters in \(\prtst\), and finally,
+\item the participation count, \ie the cardinality of 
+  \(\prfs_\prtst^{\str,\theta}\).
+\end{enumerate*}
 
-More precisely, given: \\
-\(S_{\prtst} = \{ (cid, pid, wid, l, t_s, t_s', t_c, \corr) \in \pshs \mid \cid = \cid_0 \} \) \\
-and a matching pair \((s_P, s_W) \in {S_{\prtst}}^2\) for a witness \(i\) and a protester \(j\)
-with \(s_P = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c, \psi_i)\)
-and  \(s_W = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c', \psi_j)\),
+More precisely, given \[
+  \pshs_{\cid_0} = \{ (\cid, \pid, \wid, l, t_s, t_s', t_c, \corr) \in \pshs 
+  \mid \cid = \cid_0 \}
+\] and a matching pair \((s_P, s_W) \in {\pshs_{\cid_0}}^2\) for a witness 
+\(i\) and a protester \(j\) with
+\begin{align*}
+  s_P &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c, \corr_i) &\text{and} \\
+  s_W &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c', \corr_j),
+\end{align*}
 %, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
-the verifier can build a valid proof share \(s_j^{(i)}\) certified by  \(i\) for \(j\) as follow:
-verify \(\psi_i\) and \(\psi_j\),
-let \(t = [max(t_s, t_s'), min(t_c, t_c')]\),
-let \(s_j^{(i)} = (cid_0, pid_j, wid_i, l, t)\), as in \cref{DefProofShare},
-check that \(s_j^{(i)}\) is valid (i.e. happened during and at the location of the protest), as in \cref{DefProofShare}.
+the verifier can build a valid proof share \(s_j^{(i)}\) certified by \(i\) for 
+\(j\) as follows:
+verify \(\corr_i\) and \(\corr_j\),
+let
+\begin{align*}
+  t &= \interval{\max(t_s, t_s')}{\min(t_c, t_c')} &\text{and} \\
+  s_j^{(i)} &= (\cid_0, \pid_j, \wid_i, l, t),
+\end{align*}
+as in \cref{DefProofShare},
+check that \(s_j^{(i)}\) is valid (\ie happened during and at the location of 
+the protest), as in \cref{DefProofShare}.
 
-Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
+Then the set of all valid proof shares for a protester \(j\) constitutes its 
+participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
 and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.

### 2019-02-20 paper/timestamp.tex
Changes to use \TS instead of S, adds \TSstore

--- 2018-11-30 paper/timestamp.tex
@@
 We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
-\simon{"request" feels weird to me. Are we sure that's the right word?}
+\simon{\enquote{request} feels weird to me. Are we sure that's the right word?}
 \begin{itemize}
-  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
-  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
-\item the time stamp is chosen at a low enough rate to not be unique, \eg by using only every \(n\)th block from the underlying ledger.
+  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) 
+    is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
+  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
+    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
+  \item \(\TSstore[x]\) stores \(x\) permanently and publicly readable.
 \end{itemize}
@@
   \TStime[\pi_{t_1}] \leq t_1\).
+
+The value output by \(\TSget\) must be chosen at a low enough rate to not be 
+unique for any individual.
+\Ie there must be a high probability that more than one person gets the same 
+value from \(\TSget\).
+(This can always be scaled, if \(\TSget\) progresses at too high pace, one can 
+resort to only using every \(n\)th output.)
 

### 2019-02-20 paper/protocol.tex
Fixes Syntastic warnings

@@
 %\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The \CROCUS Protocol}
+\section{The \CROCUS Protocol}%
 \label{Protocol}
@@
 publish or otherwise inform the 
-verifier of which proof shares they have signed, \eg by giving a list 
-of all such proof shares or digitally signing each proof share\footnote{
+verifier of which proof shares they have signed, \eg by giving a list of all 
+such proof shares or digitally signing each proof share\footnote{%
   To achieve witness privacy in this situation, one could employ a group or 

### 2019-02-20 paper/verifiability-analysis.tex
Fixes Syntastic warnings

@@
 
-The strength function from ~\cref{DefParticipationCount} ensures that
+The strength function from \cref{DefParticipationCount} ensures that
 Alice either has to collude with \(\theta - 1\) witnesses (she can

### 2019-02-20 paper/verifiability-analysis.tex
Fixes \cref to adversary in verifiability-analysis

@@
 \cref{DesignatedEvent}).
-As we will show, it follows from \cref{analysis-individual} that the adversary cannot drop 
-submitted proof shares and thus cannot decrease the count.
-As indicated in \cref{in-system-adversary,deanonymizing-storage-adversary}, the 
+
+As we will show, it follows from \cref{analysis-individual} that the adversary 
+cannot drop submitted proof shares and thus cannot decrease the count.
+As indicated in the adversary model (\cref{formal-adversary-model}), the 
 adversary can submit proof shares as everyone else, so the adversary's only 
@@
 We will thus let Alice pose as the adversary in this section, as she naturally 
-has an incentive to increase the count, as the organizer and participant.
+has an incentive to increase the count, as the organizer and a participant.
 

### 2019-02-20 paper/verifiability-analysis.tex
Reduces security arguments to assumption, no discussion

@@
 As a consequence, this is reduced to the security of the \(\AC\) scheme and how 
-often Alice can get a valid signature on a secret key from the \ac{CA} --- 
-either by requesting a new key, \eg request a new passport or ID-card, or 
-illicitly use someone else's.
+often Alice can get a valid signature on a secret key from the \ac{CA} --- by 
+assumption the \ac{CA} will issue only one signature for such a key, but she 
+can try to illicitly use someone else's key.
 

### 2019-02-20 paper/verifiability-analysis.tex
Fixes remaining adversary stuff in verifiability-analysis

@@
 
-\subsubsection{Designated protest}%
+\subsubsection{Designated use}%
 \label{analysis-designated}
@@
 the ledger and storage (\(\TS\), \cref{timestamp}).
-For both \cref{in-system-adversary,deanonymizing-storage-adversary} we assumed 
-an honest-but-curious adversary controlling \(\TS\)\footnote{%
+
+We assumed an honest-but-curious adversary controlling \(\TS\)\footnote{%
   We note that, in general, distributed (decentralized) ledgers cannot 
@@
   However, this requires that the adversary \emph{can observe} Alice's and 
-  Bob's channels to the ledger --- which is still not true even for 
-  \cref{deanonymizing-storage-adversary}.
+  Bob's channels to the ledger.
 }.

### 2019-02-21 paper/adversary-model.tex

@@
 There are three players: the protester (with identity) \(P\), a witness (with 
-identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
-of all proof shares, \(\pshs\)).
+identity) \(W\) and the time-stamping storage \(\TS\) (that will contain the 
+set of all proof shares, \(\pshs\)).
 The protester \(P\) and the witness \(W\) communicate some protocol data,
 \(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
-The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
-function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
-  P))\) for some function \(f\), and the time of the communication 
-(\(t_{P,S}\)).
+The protester \(P\) communicates with \(\TS\), in which \(\TS\) only learns 
+some function of the protocol data exchanged with the witness, 
+\(f(d_{P,W}(\cid, P))\) for some function \(f\), and the time of the 
+communication (\(t_{P,\TS}\)).
 This is illustrated in \cref{fig:base-adversary}.
@@
     The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
-    the storage \(S\), who records the time that happened, \(t_{P,S}\).
-    Both the witness \(W\) and the storage \(S\) are controlled by the 
+    the storage \(\TS\), who records the time that happened, \(t_{P,\TS}\).
+    Both the witness \(W\) and the storage \(\TS\) are controlled by the 
     adversary.
@@
 The adversary maliciously controls \(W\).
-The adversary honest-but-curiously controls \(S\).
+The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
+as everyone else.
 The adversary only learns the protocol data --- \ie what is sent over the 

### 2019-02-21 paper/privacy-analysis.tex

--- 2018-11-30 paper/privacy-analysis.tex
@@
 
+The issue at core from a privacy perspective is linkability.
+We must ensure that no part of any proof is linkable to an individual.
+
 We start with \cref{PseudonymUnlink}.
-Given \(\pid\), \cref{in-system-adversary} cannot distinguish whether \(\pid = 
+Given \(\pid\), the adversary cannot distinguish whether \(\pid = 
   \ACprf[_{\sk_A}][\cid]\) or \(\pid = \ACprf[_{\sk_B}][\cid]\) due to the 
 properties of \(\AC\) (see~\cite{HowToWinTheCloneWars}).
-This is not necessarily true for \cref{deanonymizing-storage-adversary}:
-if everyone uploads their own proof shares\footnote{%
-  This is probable due to the proof-of-correctness, \(\corr_\pid\), which is 
-  likely computed after the protest has ended.
-}, \cref{deanonymizing-storage-adversary} will link \(P\) and \(\pid\), and 
-consequently \(P\) and \(\cid\).
 
-\Cref{ProtestUnlink}, Alice's proofs must be unlinkable across protests.
+\Cref{ProtestUnlink} means that Alice's proofs must be unlinkable across 
+protests.
 This also follows from the properties of 
@@
 \(\pid' = \ACprf[_{\sk}][\cid']\) (where \(\cid \neq \cid'\)) are unlinkable 
-from the perspective of \cref{in-system-adversary}.
+from the perspective of the adversary.
 The argument is the same for \cref{WitnessUnlink}.
-The same is not true for \cref{deanonymizing-storage-adversary}: since 
-\cref{deanonymizing-storage-adversary} can link \(\pid, P\) and \(\pid', P\); 
-then \cref{deanonymizing-storage-adversary} can link \(\pid, \pid'\) too, thus 
-violating \cref{ProtestUnlink}.
-In the same way, \cref{deanonymizing-storage-adversary} can violate 
-\cref{WitnessUnlink}.
 
-The proof shares consist of more than only \(\cid, \pid, \wid\); more 
-specifically, each proof share is a tuple \((\cid, \pid, \wid, t_s, t_s', l, 
-  \corr_\pid, \corr_\wid)\).
+However, there are more data than \(\pid, \wid\) used in the protocol.
+The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
+We assume that the \(\cid\) will be used by many individuals, as it is the 
+cause identifier.
+And thus it cannot be used to uniquely identity any individual.
+
 We assume that the location \(l\) is coarse enough so that many non-overlapping 
@@
 Thus \(l\) is not uniquely identifying any individual protester or witness.
-Likewise, thanks to the constraints in the time-stamp granularity,
-\(t\) is not uniquely identifying either.
+Likewise, thanks to the constraints in the time-stamp granularity 
+(\cref{timestamp}), \(t\) is not uniquely identifying either.
+
+%Overall, informally, the digital trace needed for verifiability in \CROCUS could
+%conceivably be used to strengthen a suspicion of participation.
+%Given \cref{deanonymizing-storage-adversary} (Grace's) inferences from 
+%auxiliary information that points
+%to Alice having participated in a protest, \eg pictures at the
+%event, with face recognition and subsequent identification, IP address
+%of her home router, \etc, then any remaining uncertainty from false
+%positives could be reduced by learning from data on the ledger and
+%Alice's smartphone. %This potential difference can thus be considered
+%                    %the price for verifiability.
+%For confirmation of that suspicion, Grace would have to get access to
+%and use Alice's private key.

### 2019-02-21 paper/verifiability-analysis.tex

@@
 Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
-This means that we must separate the mechanisms used for participating and witnessing.
-The protocol achieves this by the fact that \[
-  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
-\]
-does not include \(\cid\) whereas \[
-  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
-\]
-does.
+The protocol prevents such use by the fact that \(\pid\) and \(\wid\) are in 
+fixed positions in both \[
+  \prf_{\wid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
+\] and \[
+  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l],
+\] and the two proofs can thus not be confused.
 Thus, the verification process differs for the two types of proofs.
-(An alternative approach would have been to compute them differently, for 
-instance \(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC*[PRF]_{\sk}(x)\), where 
-\(\AC \neq \AC*\) are separate anonymous-credential systems.)
 

### 2019-02-21 paper/protocol.tex
renames subsections, edits for simplification

@@
 
-We now present \CROCUS, a protocol for privately verifiable crowd counts.
-The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-join, participation, submission (all in in \cref{ProtocolDuring}) and
-verification (in \cref{ProtocolVerification}).
+We now present \CROCUS, a protocol for privately verifiable crowd
+counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
+sybil-proof identity and a cryptographic key, in other words an uncloneable
+subscription to one's identity\footnote{%
+  Given any \ac{CA} that prevents Sybil 
+  attacks~\cite{SybilAttack}, systems such as \cite{clonewars} could
+  be used to make sure that for each identity one-and-only-one
+  cryptographic key is issued. 
+}. Since we assume these properties, we
+present only the result of the process of getting anonymous
+credentials from a \ac{CA}, in \cref{ProtocolSetup}.
 
-Several entities are involved in our protocol.
-First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
-person's identity and a cryptographic key\footnote{%
-  This can be implemented using any \ac{CA} that prevents Sybil 
-  attacks~\cite{SybilAttack} and ensures a one-to-one mapping between a person 
-  and a cryptographic key.
-  \Ie for each identity it issues one-and-only-one cryptographic key.
-}.
-The \ac{CA} is only involved in the setup phase.
+The core of the \CROCUS protocol consists of generating participation
+proofs (joining a protest, participating in witnessing, submitting
+evidence, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
+verification of that count (in \cref{ProtocolVerification}).
 
-Second, a participant is an individual who wants to participate in a given 
+% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
+% join, participation, submission (all in in \cref{ProtocolDuring}) and
+% verification (in \cref{ProtocolVerification}).
+
+The entities involved in our protocol are participants and (count) verifiers.
+
+A participant is an individual who wants to participate in a given 
 protest.
@@
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and 
+\item The \emph{organizer} has written a manifesto (at minimum a name) for the protest and 
   disseminated it to others.
@@
 
-\subsection{Pre-protest phase}%
+After the protest, anyone can count the number of participants (of the protest and the
+protocol) and verify anyone else's count given the relevant meta data
+(which protest, location, time, and witness parameters used in the
+count). We refer to anyone counting or verifying a count as the
+verifier.
+
+\subsection{Prerequisite: anonymous credentials}%
 \label{ProtocolSetup}
 
-The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
-More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
+Before Alice can have her participation in any event counted by
+\CROCUS, she needs to get an anonymous credential and corresponding
+keys. This only needs to be repeated when the credential expires or is
+lost, in analogy to a passport in terms of expected intervals. The
+keys can be reused for an arbitrary number of protests or, given
+careful choices in the PRF used for deriving identifiers, other
+services that work with anonymous credentials.
+
+We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
+getting anonymous credentials, adapting only the notation to fit ours. 
+%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
 
@@
 
-The setup and registration steps can be done once and the keys can be reused 
-for an arbitrary number of protests.
-
-\subsection{Protest phase}%
+\subsection{Participation}%
 \label{ProtocolDuring}
@@
 
-Here is an overview of the protocol.
-
-%\begin{figure}
-% \centering
-  \small
- % \begin{minipage}{\linewidth}
+\begin{figure}
+ \centering
+ % \small
+  \begin{minipage}{\linewidth}
     \begin{align*}
@@
     \end{align*}
-%  \end{minipage}
-%  \caption{%
-%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
-%     The organizer \(O\) broadcasts the manifesto.
-%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-%     Finally, both \(P\) and \(W\) submit the proof shares to a
-%     permanent storage \(S\). Note that \pid always refers to the
-%     protester whose presence is being witnessed.
-%   }%
-%   \label{fig:ProtocolOverview}
-% \end{figure}
-\normalsize
+  \end{minipage}
+  \caption{%
+    An overview of \CROCUS participation.\@
+    The organizer \(O\) broadcasts the manifesto.
+    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+    Finally, both \(P\) and \(W\) submit the proof shares to a
+    permanent storage \(S\). Note that \pid  always refers to the
+    protester whose presence is being witnessed.
+  }%
+  \label{fig:ProtocolOverview}
+\end{figure}
+%\normalsize
 
-\subsection{Post-protest phase}%
+\subsection{Count and Verification}%
 \label{ProtocolVerification}
@@
 
-To verify the participation count for a protest \(\prtst\) with identifier 
+To count or verify the participation count for a protest \(\prtst\) with identifier 
 \(\cid_0\), a verifier must download from the storage system \(\TS\) the set 
@@
 In the case of trusted witnesses, each such trusted witness must
-publish or otherwise inform the 
-verifier of which proof shares they have signed, \eg by giving a list of all 
-such proof shares or digitally signing each proof share\footnote{%
-  To achieve witness privacy in this situation, one could employ a group or 
-  ring signature scheme for all trusted witnesses.
-  Then one learns that at least one trusted witness must have been there.
-}.
+publish or otherwise inform the verifier of which proof shares they
+have signed, \eg by giving a list of all such proof shares or
+digitally signing each proof share\footnote{%
+  To achieve witness privacy in this situation, one could employ a
+  group or ring signature scheme for a set of trusted witnesses, \eg
+  members of an independent journalist association.  Then one learns
+  that at least one member of this set of trusted witnesses must have
+  been there.  }.
 
-Note that, thanks to the \((\str,\theta)\)-eligibility criterion (\cref{DefParticipationCount}), the method of counting is extremely generic, and each verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses.
+Note that, thanks to the \((\str,\theta)\)-eligibility criterion
+(\cref{DefParticipationCount}), the method of counting is extremely
+generic, and each (counting) verifier can make an independent choice to regulate their trust in the final result, based on their initial trust in the witnesses.
 In other words, anyone who does the counting can choose the eligibility

### 2019-02-21 paper/protocol.tex
Changes phrasing in protocol regarding unclonable subscriptions

@@
 counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key, in other words an uncloneable
-subscription to one's identity\footnote{%
+sybil-proof identity and a cryptographic key, more specifically, an anonymous 
+identity credential that provides unlinkability between contexts but 
+linkability for reuse within the same context\footnote{%
   Given any \ac{CA} that prevents Sybil 
-  attacks~\cite{SybilAttack}, systems such as \cite{clonewars} could
+  attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
   be used to make sure that for each identity one-and-only-one
   cryptographic key is issued.
+  In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
+  to one's identity.
 }. Since we assume these properties, we

### 2019-02-26 paper/protocol.tex
clarifying edits, pointer to figure

--- 2019-02-21 paper/protocol.tex
@@
 counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key, in other words an uncloneable
-subscription to one's identity\footnote{%
-  Given any \ac{CA} that prevents Sybil 
-  attacks~\cite{SybilAttack}, systems such as \cite{clonewars} could
-  be used to make sure that for each identity one-and-only-one
-  cryptographic key is issued. 
-}. Since we assume these properties, we
+sybil-proof identity and a cryptographic key
+%, more specifically, an anonymous 
+%identity credential that provides unlinkability between contexts but 
+%linkability for reuse within the same context
+%\sonja{this is actually achieved by our use of prfs for pid and wid,
+%not inherent in the credential}
+% \footnote{%
+%   Given any \ac{CA} that prevents Sybil 
+%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
+%   be used to make sure that for each identity one-and-only-one
+%   cryptographic key is issued.
+%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
+%   to one's identity.
+% }
+. Since we assume these properties, we
 present only the result of the process of getting anonymous
@@
 proofs (joining a protest, participating in witnessing, submitting
-evidence, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
+proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
 verification of that count (in \cref{ProtocolVerification}).
@@
 count). We refer to anyone counting or verifying a count as the
-verifier.
+verifier; the process is the same.
 
@@
 % illustrated in \cref{fig:ProtocolOverview}.
-
-The participation proof share constructed in the
-participation phase is illustrated in \cref{fig:ProofFig}.
+The goal of \CROCUS is to generate and collect privacy-preserving
+participation proofs that can be counted and verified. These proofs
+consist of proof shares that are constructed as depicted in
+\cref{fig:ProofFig}. The protocol phases are given in
+\cref{fig:ProtocolOverview} and described below.
 
@@
 \] (see \cref{ACacAlg}).
-Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
+Note that the proof of knowledge (\ac{PK}) in \cref{ACacAlg} must be
+run as a proof of proximity (\iac{PPK}), which we do by distance bounding.
 If the protocol succeeds, the witness will compute \(\wid \gets 
@@
 \emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester should as soon as possible commit the proof-share data to the 
-time-stamping service and receive the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
+The protester commits the proof-share data to the 
+time-stamping service and receives the proof of commitment, \(t_e\gets 
+  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\). The sooner this
+  is done, the higher the precision for the time-dependent eligibility criterion
+  will be for later counting. 
 The remaining operations are not time critical.
@@
 The witness should, just as the protester, commit the proof-share data to the 
-time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
+time-stamping service (\ie the ledger), \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
   l]]\).
-(This is to make the time interval as early as possible, whoever is the faster 
-will submit it.)
+%(This is to make the time interval as early as possible, whoever is the faster 
+%will submit it.) \sonja{but both do}
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
@@
   \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
-\] for permanent storage.
+\] for permanent storage on the ledger.
 
@@
     Finally, both \(P\) and \(W\) submit the proof shares to a
-    permanent storage \(S\). Note that \pid  always refers to the
+   public ledger for permanent storage \(S\). Note that \pid  always refers to the
     protester whose presence is being witnessed.

### 2019-02-26 paper/protocol.tex
fixes space, acf errors

@@
 counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key
+sybil-proof identity and a cryptographic key%
 %, more specifically, an anonymous 
@@
 \] (see \cref{ACacAlg}).
-Note that the proof of knowledge (\ac{PK}) in \cref{ACacAlg} must be
-run as a proof of proximity (\iac{PPK}), which we do by distance bounding.
+Note that the \acf{PK} in \cref{ACacAlg} must be
+run as a \iacf{PPK}, which we do by distance bounding.
 If the protocol succeeds, the witness will compute \(\wid \gets 

### 2019-02-26 paper/MANETs.tex

@@
-We also need the participants to communicate during the protest.
+We need the participants to communicate during the protest.
 Since the cellular network could be shut down to keep protesters from accessing 
@@
 drive for operators to identify the network users, there still is an
-authorization step to communicate in this mode.
+authorization step to communicate in this
+mode. Near-field-communication (NFC) would
+solve any scalability problem from interference, require no
+infrastructure or provider, but at the price of requiring the
+participant and witness to hold their phones together for each proof
+share. 
 %~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

### 2019-02-26 paper/verifiability-analysis.tex
Edits temporal eligibility in security analysis

@@
 challenge.
-The challenge here is \enquote{which is the hash value of the head block of the 
-  ledger at the time of the proof's creation?}.
-The response is simply the hash itself (obtained through \(\TSget\)) and is 
-included as \(t_s\) and \(t_s'\) in the proof share (see \cref{fig:ProofFig}).
-
-As it is the case in the construction of ledgers, the hash value of the head 
-block depends on the previous blocks.
-Thus, the predictability of \(t_s\) depends on the predictability of the 
-blocks, which depends on the predictability of the transactions.
-Assume that Alice can control all transactions going into a block.
-This means that she must find a pre-image of the form of a valid block that is 
-accepted by all nodes in the distributed ledger.
-\Ie it depends on the pre-image resistance of the hash function used.
-Thus, with a collision resistant hash function (\(\Hash\)), Alice can predict 
-\(t_s\) only with negligible probability; and it follows that, with high 
-probability, \(t_s\) was published on the ledger before Alice included it in 
-her proof share.
-
-The correctness of the response must be verifiable by any verifier (verifiable 
-through \(\TStime\)).
-This can be done if the ledger is continuously extended at a fixed rate, \eg 
-one new block every 10 minutes, as was the case for Bitcoin.
+The challenge here is \enquote{what did \(\TSget\) return at the time of the 
+  proof's creation?}.
+The response is included as \(t_s\) and \(t_s'\) in the proof share (see 
+\cref{fig:ProofFig}).
+The unpredictability of \(\TSget\) ensures that a proof cannot have been 
+created before \(\max\{t_s, t_s'\}\).
+The correctness of the response must be verifiable by any verifier, which is 
+the case with \(\TStime\).
 
@@
 Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
-The hash values of the proof shares are committed to the ledger, which means 
-that there is a negligible probability that they were created after that.
-Alice is in the same situation as above:
-she would have to choose a value \(y\) in the range of the hash function 
+The hash values of the proof shares are committed to the ledger (\(\TSstamp\)), 
+which means that there is a negligible probability that they were created after 
+that:
+Alice would have to choose a value \(y\) in the range of the hash function 
 \(\Hash\) and then find a pre-image \(x\) such that \(y = \Hash[x]\) and \(x\) 
 is a valid proof for the desired protest, at the desired time.
-If \(\Hash\) is collision resistant, finding \emph{any} pre-image is hard.
+If \(\Hash\) is collision resistant, she will succeed with negligible 
+probability.
 

### 2019-02-27 paper/timestamp.tex

@@
 Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
-Note that thanks to \(\TS\) immutability, once a user has committed their data, that user only need to store some confirmation value instead of the data itself.
-For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.
 

### 2019-02-27 paper/verifiability-analysis.tex

@@
 
-\Cref{CountOnce} is required to prevent Sybil attacks, in the sense
+\Cref{CountOnce} prevents Sybil attacks, in the sense
 that Alice cannot provide two (or more) participation proofs for a
@@
 To do this she must create more than one pseudonym, \(\pid\).
-Indeed to be counted twice, Alice must produce a \(\pid'\neq \pid\).
+Indeed, to be counted twice, Alice must produce a \(\pid'\neq \pid\).
 Due to the deterministic property of \(\ACprf\), Alice must produce a new key 
@@
 while she does not know a valid signature on \(\sk_P'\).
-As a consequence, this is reduced to the security of the \(\AC\) scheme and how 
-often Alice can get a valid signature on a secret key from the \ac{CA} --- by 
-assumption the \ac{CA} will issue only one signature for such a key, but she 
-can try to illicitly use someone else's key.
+As a consequence, this is reduced to the security of the \(\AC\) scheme.
+Remember, by assumption the \ac{CA} will issue only one signature for such a 
+key, so Alice cannot ask for a second one.
 
@@
 
-\Cref{SpatiallyRelated} is achieved by having a witness vouch anonymously that Alice was indeed at the location when the proof share was created.
-To realize this, we must ensure that Alice cannot forge witness signatures.
+\Cref{SpatiallyRelated} is achieved by having a witness vouch that Alice was 
+indeed at the location when the proof share was created.
+In essence, the witness performs distance bounding to ensure Alice is close to 
+them, this is then propagated to the verifier through the signature and trust 
+in the witness's honesty.
+Alice has three options:
+\begin{enumerate*}
+\item\label{spatial-DF} relay her communication with an honest witness through 
+  a conspirator,
+\item\label{spatial-forge} forge a witness signature for the proof,
+\item corrupt a witness to issue a proof although neither might be present at 
+  the location.
+\end{enumerate*}
 
-In the trust-free case (see \cref{ProtocolVerification}), this is realized by 
-using the same linkability mechanism as above.
-\Ie to forge a witness signature, Alice must produce a \(\wid'\) such that
-\begin{multline*}
-  \pi_{\wid'}\gets \SPK\left\{ (\sk_W') : \right. \\
-    \begin{aligned}
-      \wid' &= \ACprf[_{\sk_W'}][\pid] \quad \land \\
-      \sigma_W'' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W']] \right\}
-    \end{aligned} \\
-      (\pid, \wid', t_s, t_s', l),
-\end{multline*}
-is accepted by the verifier while not knowing a signature on the secret key 
-\(\sk_W'\).
-Thus, she must break the \(\AC\) scheme to succeed or get a valid signature on \(\sk_W'\) from the \ac{CA}.
-As above, the latter could be done if she can find people willing to collude, 
-or whose keys she illicitly can use anyway, or 
-simply request new keys from the \ac{CA}.
+Relaying the communication is \iac{DBDF} attack against the \ac{DB} protocol.
+We assumed \ac{DBDF} resistance for the \ac{DB} protocol, so Alice cannot 
+succeed with more than negligible probability.
 
-% We assumed that Alice cannot collude with more than a threshold \(\theta\) of 
-% witnesses.
-% Thus, setting the threshold of at least \(\theta+1\) will prevent Alice from 
-% cheating.
-% (Note that Alice can produce \emph{one} witness signature for herself, since 
-% she has access to her own \(\sk_P\), but no more.
-% Thus, \(\theta > 1\) is a requirement in the trust-free case.)
+Forging a witness's signature on a proof is equivalent to breaking linkability 
+above (\cref{analysis-linkability}).
+As above, this is reduced to the security of the \(\AC\) scheme.
 
-The strength function from \cref{DefParticipationCount} ensures that
-Alice either has to collude with \(\theta - 1\) witnesses (she can
-produce \emph{one} witness signature for herself, since she has access
-to her own \(\sk_P\), but no more) or, in the trusted witness case,
-that Alice must be able to forge statements, \eg digital signatures,
-from at least one witness that the verifier trusts.
+Finally, in the case of trusted witnesses, Alice's chance of corrupting 
+witnesses is reduced to the trustworthiness of the witnesses chosen by the 
+verifier.
+In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
+succeeds only if she can corrupt at least \(\theta\) witnesses.
+
+We note that the strength function from \cref{DefParticipationCount} allows the 
+verifier to take different approaches, each of which must be individually 
+analyzed.
+In all of these cases, it is up to the verifier to perform a risk analysis.
 

### 2019-02-27 paper/verifiability-analysis.tex
Minor edit in verifiability-analysis

@@
 
-Finally, in the case of trusted witnesses, Alice's chance of corrupting 
-witnesses is reduced to the trustworthiness of the witnesses chosen by the 
-verifier.
+Finally, Alice can corrupt witnesses.
+In the case of trusted witnesses, Alice's chance of corrupting witnesses is 
+reduced to the trustworthiness of the witnesses chosen by the verifier.
 In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 

### 2019-02-27 paper/verifiability-analysis.tex
Emphasize the malicious protester

@@
 option is to increase the count.
-We will thus let Alice pose as the adversary in this section, as she naturally 
-has an incentive to increase the count, as the organizer and a participant.
+We will thus let Alice pose as the adversary (malicious protester) in this 
+section, as she naturally has an incentive to increase the count, as the 
+organizer and a participant.
 

### 2019-02-27 paper/protocol.tex
turns protocol overview figure into text

@@
 \label{Protocol}
+
+\begin{figure}
+  \centering
+  \small
+  \includegraphics{proofshare.tikz}
+  \caption{%
+    Structure of a proof share.
+    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
+    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
+    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
+    witness's key \(\sk_W\) and the protester's \(\pid\).
+    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
+    protester and witness, respectively, and \(l\) is an area.
+    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
+      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
+    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
+    The protester constructs \(\prf_P\) analogously.
+  }%
+  \label{fig:ProofFig}
+\end{figure}%
 
@@
 proofs (joining a protest, participating in witnessing, submitting
-proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
+proof shares to a ledger, all in \cref{ProtocolDuring}), and then counting and
 verification of that count (in \cref{ProtocolVerification}).
@@
 consist of proof shares that are constructed as depicted in
-\cref{fig:ProofFig}. The protocol phases are given in
-\cref{fig:ProtocolOverview} and described below.
-
-\begin{figure}
-  \centering
-  \small
-  \includegraphics{proofshare.tikz}
-  \caption{%
-    Structure of a proof share.
-    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
-    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
-    witness's key \(\sk_W\) and the protester's \(\pid\).
-    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
-    protester and witness, respectively, and \(l\) is an area.
-    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
-      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
-    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
-    The protester constructs \(\prf_P\) analogously.
-  }%
-  \label{fig:ProofFig}
-\end{figure}%
+\cref{fig:ProofFig}.
 
@@
 
-\begin{figure}
- \centering
+% \begin{figure}
+%  \centering
+%  % \small
+%   \begin{minipage}{\linewidth}
+%     \begin{align*}
+%       O\to \text{all}\colon & \text{manifesto} \\
+%       P\colon & t_s\gets \TSget \\
+%         & \cid\gets \Hash[\text{manifesto}], \\
+%         & \pid\gets \ACprf[_{\sk_P}][\cid] \\
+%       W\colon & t_s'\gets \TSget
+%       \\[-1em]
+%       \noalign{\hfill Join}
+%       \midrule
+%       \noalign{\hfill Participation}
+%       \\[-3em]
+%       P\to W\colon & \pid \\
+%       P\leftrightarrow W\colon &
+%         \PPK\mleft\{ (\sk_P) : \mright. \\
+%         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+%         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+%         \\
+%       W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
+%       W\to P\colon & (\wid, t_s', l)
+%       \\[-1em]
+%       \noalign{\hfill Participation}
+%       \midrule
+%       \noalign{\hfill Submission}
+%       \\[-2em]
+%       P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+%       W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
+%       W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+%       \pi_{\wid})],\quad \text{where} \\
+%         & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
+%         & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
+%         & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
+%         \\
+%         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
+%       P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+%       \pi_{\pid})],\quad \text{where}\\
+%         & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
+%         & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
+%         & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
+%         \\
+%         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
+%     \end{align*}
+%   \end{minipage}
+%   \caption{%
+%     An overview of \CROCUS participation.\@
+%     The organizer \(O\) broadcasts the manifesto.
+%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+%     Finally, both \(P\) and \(W\) submit the proof shares to a
+%    public ledger for permanent storage \(S\). Note that \pid  always refers to the
+%     protester whose presence is being witnessed.
+%   }%
+%   \label{fig:ProtocolOverview}
+% \end{figure}
+% %\normalsize
+
+We now give an overview of \CROCUS participation.\@
+    The organizer \(O\) broadcasts the manifesto.
+    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
+    Finally, both \(P\) and \(W\) submit the proof shares to a
+   public ledger for permanent storage \(S\). Note that \pid  always refers to the
+    protester whose presence is being witnessed. More formally:
+
  % \small
-  \begin{minipage}{\linewidth}
     \begin{align*}
@@
     \end{align*}
-  \end{minipage}
-  \caption{%
-    An overview of \CROCUS participation.\@
-    The organizer \(O\) broadcasts the manifesto.
-    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submit the proof shares to a
-   public ledger for permanent storage \(S\). Note that \pid  always refers to the
-    protester whose presence is being witnessed.
-  }%
-  \label{fig:ProtocolOverview}
-\end{figure}
  %\normalsize

### 2019-02-27 paper/verifiability-analysis.tex
Requirements aims towards something

@@
 
-\Cref{CountOnce} prevents Sybil attacks, in the sense
+\Cref{CountOnce} aims to prevent Sybil attacks, in the sense
 that Alice cannot provide two (or more) participation proofs for a
@@
 
-\Cref{DesignatedEvent} is to prevent Alice (or someone else) from reusing the same proof (or proof share) for another event.
+\Cref{DesignatedEvent} aims to prevent Alice (or someone else) from reusing the 
+same proof (or proof share) for another event.
 This possibility is prevented through the use of \(\cid\) in the proof shares.

### 2019-02-27 paper/verifiability-analysis.tex
It's TF that's the relevant property for Alice's relay

@@
 
-Relaying the communication is \iac{DBDF} attack against the \ac{DB} protocol.
-We assumed \ac{DBDF} resistance for the \ac{DB} protocol, so Alice cannot 
-succeed with more than negligible probability.
+Relaying the communication is an attack against the \ac{DB} protocol.
+We assumed \iac{DB} protocol with \ac{DBTF} resistance (the most relevant 
+property for this situation), so Alice cannot succeed with more than negligible 
+probability.
 

### 2019-02-27 paper/verifiability-analysis.tex
Clarifies effect of other DB properties in security analysis
Emphasize that witness is trusted by verifier

@@
 In essence, the witness performs distance bounding to ensure Alice is close to 
-them, this is then propagated to the verifier through the signature and trust 
-in the witness's honesty.
+them, this is then propagated to the verifier through the signature and founded 
+on trust (remember that the witness is trusted by the verifier).
 Alice has three options:

### 2019-02-28 paper/distance-bounding.tex
Minor clarification on TF-resistance in distance-bounding

@@
     \Ac{DBTF} resistance is a very strong property; it implies that if the 
-    accomplice succeeds (with non-negligible probability) he will learn the 
-    prover's secret key\footnote{%
+    verifier accepts the accomplice with non-negligible probability the 
+    accomplice can compute the prover's secret key\footnote{%
       This means that even things like functional encryption will not help.

### 2019-02-28 paper/verifiability-analysis.tex

@@
 As for individual verifiability, the security of universal verifiability is 
-reduced to the properties of the ledger and storage; but universal 
-verifiability also depends on the eligibility verification.
+reduced to the properties of the ledger; but universal verifiability also 
+depends on the eligibility verification (each proof must be verified as 
+eligible to count).

### 2019-02-28 paper/adversary-model.tex
Fixes missing punctuation
Changes time-stamping and storage to ledger, fixes #176

@@
 There are three players: the protester (with identity) \(P\), a witness (with 
-identity) \(W\) and the time-stamping storage \(\TS\) (that will contain the 
-set of all proof shares, \(\pshs\)).
+identity) \(W\) and a ledger~\(\TS\) (\ie time-stamping storage, that will 
+contain the set of all proof shares, \(\pshs\)).
 The protester \(P\) and the witness \(W\) communicate some protocol data,
@@
 The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
-as everyone else.
+as everyone else (\ie a malicious protester~\(P\)).
 The adversary only learns the protocol data --- \ie what is sent over the 
@@
   to identity.
-}
+}.
 

### 2019-02-28 paper/protocol.tex
Breaks protocol figure into two columns
Breaks join, participation into two subfigures

--- 2019-02-26 paper/protocol.tex
@@
 Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
-\cref{fig:ProofFig} and \cref{ACprfAlg}).
-The protester should also receive a time-correlated random value from the 
-time-stamping service, \(t_s\gets \TSget\).
+for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
+% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
+%the algorithms)%
+.
+The protester should also fetch a time-correlated random value, \(\t_s\), from 
+\(\TS\), \(t_s\gets \TSget\).
 
@@
 
-The protester sends \(\pid\) to the witness.
+The protester sends \(\pid\) and \(t_s\) to the witness.
 Then they run the protocol \[
   \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
-\] (see \cref{ACacAlg}).
+\] (see \cref{ACacAlg}), \(k\) and \(r\) are part of \(\sk_P\).
 Note that the \acf{PK} in \cref{ACacAlg} must be
@@
 \emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester commits the proof-share data to the 
-time-stamping service and receives the proof of commitment, \(t_e\gets 
-  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\). The sooner this
-  is done, the higher the precision for the time-dependent eligibility criterion
-  will be for later counting. 
+The protester commits the proof-share data to the ledger~\(L\) and receives the 
+proof of commitment, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', 
+  l]]\).
+The sooner this is done, the higher the precision for the time-dependent 
+eligibility criterion will be for later counting.
 The remaining operations are not time critical.
@@
   \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
-\] for permanent storage.
+\] for permanent storage, \(\TSsubmit[\psh_P]\).
 
@@
 The witness should, just as the protester, commit the proof-share data to the 
-time-stamping service (\ie the ledger), \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
-  l]]\).
+ledger, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
 %(This is to make the time interval as early as possible, whoever is the faster 
@@
   \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
-\] for permanent storage on the ledger.
+\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).
 
-\begin{figure}
+\begin{figure*}
   \centering
- % \small
-  \begin{minipage}{\linewidth}
+  \small
+  \begin{subfigure}{\columnwidth}
     \begin{align*}
@@
       W\to P\colon & (\wid, t_s', l)
-      \\[-1em]
-      \noalign{\hfill Participation}
-      \midrule
-      \noalign{\hfill Submission}
-      \\[-2em]
+    \end{align*}
+    \caption{Join and participation.}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{\columnwidth}
+    \begin{align*}
       P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
@@
     \end{align*}
-  \end{minipage}
+    \caption{Submission.}
+  \end{subfigure}
   \caption{%
@@
   \label{fig:ProtocolOverview}
-\end{figure}
+\end{figure*}
 %\normalsize
@@
 
-To count or verify the participation count for a protest \(\prtst\) with identifier 
-\(\cid_0\), a verifier must download from the storage system \(\TS\) the set 
-\(\pshs_{\cid_0}\) of all \(s_P\) and \(s_W\) tuples containing \(\cid_0\).
+To count or verify the participation count for a protest \(\prtst\) with 
+identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
+all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
 Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
@@
   that at least one member of this set of trusted witnesses must have
-  been there.  }.
+  been there.
+}.
 

### 2019-02-28 paper/timestamp.tex

@@
 
-We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
-\simon{\enquote{request} feels weird to me. Are we sure that's the right word?}
+We need a robust time-stamping and storage service (\ie a ledger), \(\TS\), 
+which implements the following oracles:
 \begin{itemize}
-  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) 
-    is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
-  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that 
-    \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
-  \item \(\TSstore[x]\) stores \(x\) permanently and publicly readable.
+  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\) such that 
+    \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
+  \item \(\pi\gets \TSsubmit[x]\) stores \(x\) permanently and yields a value 
+    \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and 
+    \(\TStime[\pi] = t\).
 \end{itemize}
 
-With these building blocks, we can ensure that a message \(m\) is created within the time interval \(\interval{t_0}{t_1}\).
-After time \(t_0\), a user requests \(\rho_{t_0}\gets \TSget\).
-Before time \(t_1\), a user submits \(h\gets \Hash[m, \rho_{t_0}]\) to the time-stamping service to get \(\pi_{t_1}\gets \TSstamp[h]\).
-
-The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
+With these building blocks, Alice can prove to a third-party verifier that a 
+message \(m\) was created within the time interval \(\interval{t_0}{t_1}\):
+After time \(t_0\), Alice requests \(\rho_{t_0}\gets \TSget\).
+Before time \(t_1\), Alice submits \(h\gets \Hash[m, \rho_{t_0}]\) to \(\TS\) 
+and gets \(\pi_{t_1}\gets \TSsubmit[h]\).
+The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was 
+created within the time interval \(\interval{t_0}{t_1}\).
 The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
@@
 \(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
-If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
+If a blockchain is used for \(\TS\), the \(\TSsubmit[x]\) request includes 
+\(x\) in the blockchain and returns the identifier of the block into which 
+\(x\) was included.
 The \(\TSget\) request returns the hash of the most recent block of the chain 
@@
 
-Regarding consensus resilience, it is advisable to use a blockchain with a high 
-number of participants and preferably sharing the blockchain with other 
-services.
-The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
-A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
-In both cases, assuming a majority of honest members in the population, the more participants the merrier.
+Regarding consensus resilience, it is advisable to use a ledger with a high 
+number of participants and preferably sharing the ledger with other services.
+%The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
+%A similar reasoning can be made with Proof-of-Work consensus in which the 
+%computing power of the honest participants must be greater than that of the 
+%malicious participants.
+%In both cases, assuming a majority of honest members in the population, the more participants the merrier.
 We want to share the blockchain with other services due to privacy (and 
-anti-censorship) reasons, analogous to the idea of \enquote{domain fronting}.
+anti-censorship) reasons (analogous to the idea of \enquote{domain fronting}).
 
-We require a few additional properties from \(\TS\) that are already provided by blockchains.
-First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
-Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
+We require a few additional properties from \(\TS\) that are already provided 
+by ledgers.
+First, \(\TS\) must be continuously extended, such as in Bitcoin in which 
+blocks are created every 10 minutes on average (this is so that \(\TStime\) can 
+map values from \(\TSget\) to real time).
+Second, \(\TS\) must provide \emph{immutability} and availability to any data 
+committed through \(\TSsubmit\) to ensure verifiability of the data by anyone 
+at any time.
 

### 2019-02-28 paper/verifiability-analysis.tex

@@
 Otherwise, Grace could argue that the proof share was created after the protest, thus defeating the purpose of our protocol.
-The hash values of the proof shares are committed to the ledger (\(\TSstamp\)), 
-which means that there is a negligible probability that they were created after 
-that:
+The hash values of the proof shares are committed to the ledger 
+(\(\TSsubmit\)), which means that there is a negligible probability that they 
+were created after that:
 Alice would have to choose a value \(y\) in the range of the hash function 
@@
 probability.
+(\Ac{DBDF} is captured by \ac{DBTF} in this case, as in \ac{DBTF} she has a 
+colluder.
+\Ac{DBMF} would prevent Alice from relaying unsuspecting bystanders' 
+communication to witnesses.
+\ac{DBDH} is not really useful to Alice in this situation.)
 
@@
 All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
-  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger and 
-available from a public and permanent storage.
+  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger~\(\TS\) 
+and available from a public and permanent storage.
 Thus, Alice and Bob can simply check that all of their proof shares are indeed 
 there and the security of individual verifiability depends on the properties of 
-the ledger and storage (\(\TS\), \cref{timestamp}).
+the ledger (\cf \cref{timestamp}).
 

### 2019-02-28 paper/intro.tex
shortens intro, fixes protocol.tex non-compile problems

@@
 We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
-Consider the following scenario.
-Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
-Alice wants to estimate the number of participants to prove a certain support for her cause against Grace.
-Bob, Carol and many others participate in the protest.
-However, they might only be willing to do so in a manner that does not leave any digital traces because of the fear of retribution against them from Grace's regime. 
-To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
@@
 
-Existing methods for crowd-counting vary significantly in terms of approaches (we will review them in detail in \cref{related-work}).
-However, most of them lack precision (\ie they have large error margins) and 
-they can only give an estimate for a particular snapshot in time. In particular, the existing methods cannot reliably 
-estimate the cumulative participation count --- at least not without counting 
-some persons multiple times --- which in turn increases the error of the 
-estimation.
+Consider the following scenario.
+Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
+Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime.
+To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
+
+Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{related-work}).
+Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.
 In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
@@
 Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting.
-Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
-In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
+Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
+%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
 In this paper, our main objective is to provide a scheme preventing both Alice 

### 2019-02-28 paper/protocol.tex
shortens intro, fixes protocol.tex non-compile problems

@@
 .
-The protester should also fetch a time-correlated random value, \(\t_s\), from 
+The protester should also fetch a time-correlated random value, \(t_s\), from 
 \(\TS\), \(t_s\gets \TSget\).
@@
 The witness should, just as the protester, commit the proof-share data to the 
-ledger, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
+ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
 %(This is to make the time interval as early as possible, whoever is the faster 
@@
     \begin{align*}
-      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+      P\colon & t_e\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\colon & t_e'\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
+      W\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
       \pi_{\wid})],\quad \text{where} \\
@@
         & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
-      P\colon & \TSstore[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
+      P\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
       \pi_{\pid})],\quad \text{where}\\

### 2019-02-28 paper/privacy-properties.tex
removes redundancies, corrects language, adds clarifications

--- 2018-11-21 paper/privacy-properties.tex
@@
 
-For privacy, any temporary identifiers, such as pseudonyms, should only be 
-reused when strictly necessary (by the principle of data minimization) for the 
-fulfillment of verifiability properties (in \cref{verifiability-properties}) to 
-prevent inference on long-term identities by repeated samples and side 
-information.
-We can thus summarize the desired privacy properties as follows:
 \begin{requirements}[P]
@@
 What these properties say is that pseudonyms must look random 
-(\cref{PseudonymUnlink}) and that each pseudonym must be used at most once 
+(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
+more than strictly necessary for the verifiability properties 
 (\cref{ProtestUnlink,WitnessUnlink}).

### 2019-02-28 paper/distance-bounding.tex
edits language, shortens building blocks, adds back hash

@@
 As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
-\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
+\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
 Time critical phases are complemented by slow phases during which the time is not taking into account. 
-At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in his vicinity.
+At the end of a \Ac{DB} protocol, the verifier should be able to
+determine if the prover is legitimate \emph{and} in their vicinity.
 In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
@@
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+% There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
-The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
-There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
+% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
+% Indeed, in this context it does not make sense to protect against the
+% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
+% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
 Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.

### 2019-02-28 paper/privacy-analysis.tex

@@
 The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
-We assume that the \(\cid\) will be used by many individuals, as it is the 
-cause identifier.
-And thus it cannot be used to uniquely identity any individual.
-
-We assume that the location \(l\) is coarse enough so that many non-overlapping 
+The cause identifier \(\cid\) will be used for all proof shares
+pertaining to the same protest and thus it cannot be used to uniquely
+identify any individual. The location \(l\) is coarse enough so that many non-overlapping 
 \((\pid, \wid)\)-pairs use the same location.
 After all, it is the location of the protest, not the location within the 
-protest that is interesting.
+protest that matters.
 Thus \(l\) is not uniquely identifying any individual protester or witness.

### 2019-02-28 paper/protocol.tex

@@
 The entities involved in our protocol are participants and (count) verifiers.
-
-A participant is an individual who wants to participate in a given 
-protest.
 A participant can assume three different roles:
 \begin{enumerate}
-\item The \emph{organizer} has written a manifesto (at minimum a name) for the protest and 
+\item The \emph{organizer} has written a manifesto for the protest and 
   disseminated it to others.
@@
   for their presence.
-\item A \emph{witness} provides proofs to protesters which state that the 
-  protester was indeed participating, constructed such that the proofs are verifiable by 
+\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
   third parties.
@@
   r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
-  it} to the \ac{CA}.
+  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
 At the end, each participant will have a signed secret key while the \ac{CA} 
@@
 The organizer writes a manifesto for the protest, which describes its cause.
-This manifesto could take the form of any intelligible text.
-The organizer will then distribute this manifesto to people through
+This manifesto could take the form of any intelligible text, in
+practice at minimum a name.
+The organizer then distributes this manifesto to people through
 any suitable means  (\eg on the Web, on placards, \etc).
@@
     \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest will use the manifesto to
+A protester who wants to join the protest uses the manifesto to
 compute an identifier for the cause by hashing the manifesto,
@@
 .
-The protester should also fetch a time-correlated random value, \(t_s\), from 
+The protester also fetches a time-correlated random value, \(t_s\), from 
 \(\TS\), \(t_s\gets \TSget\).
@@
 \emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
-The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
+The witness simply gets a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
 Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
@@
     l]\).}
-The witness should, just as the protester, commit the proof-share data to the 
+The witness, like the protester, commits the proof-share data to the 
 ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
@@
 and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
-Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationCount}.
+Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by  \cref{DefParticipationCount}.
 
@@
   To achieve witness privacy in this situation, one could employ a
-  group or ring signature scheme for a set of trusted witnesses, \eg
+  group or ring signature scheme for a set of potentially trusted witnesses, \eg
   members of an independent journalist association.  Then one learns
-  that at least one member of this set of trusted witnesses must have
+  that at least one member of this set must have
   been there.

### 2019-02-28 paper/distance-bounding.tex

@@
     accomplice can compute the prover's secret key\footnote{%
-      This means that even things like functional encryption will not help.
+      This means that even things like functional encryption will not
+      help the adversary.
     }.

### 2019-02-28 paper/verifiability-properties.tex

@@
 
-  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
+  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained matches the submitted participation proofs.
 
-  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that his participation proof is included in the global count.
+  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that their participation proof is included in the global count.
 \end{requirements}

### 2019-03-01 paper/intro.tex
adds outline

@@
 
-%The paper is organized as follows.
-%\Cref{system-model}, we describe our system model and summarize the desired 
-%properties for crowd counting.
-%We then discuss related work in terms of these properties in 
-%\cref{related-work}:
-%we first discuss the crowd counting methods that are classically used followed 
-%by work on location proof systems.
-%
-%\Cref{definitions}, we formalize the notion of protest and the desired 
-%verifiability and privacy properties, and in \cref{building-blocks}, we give 
-%the relevant background on the building blocks of our solution.
+The paper is organized as follows.
+In \Cref{system-model}, we describe our system model and summarize the desired 
+properties for crowd counting, followed by a discussion of related work in \cref{related-work}.
+In \Cref{definitions}, we formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give
+the relevant background on the building blocks of our solution.
 %
@@
 %
-%\Cref{Protocol}, we present \CROCUS, a privacy-preserving crowd counting 
-%estimation protocol.
-%We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
-%in \cref{PerformanceAnalysis}.
-%
-%Finally, we discuss our assumptions and results in \cref{Discussion} and give 
-%our conclusions in \cref{Conclusion}.
+We present \CROCUS, a privacy-preserving crowd counting 
+%estimation 
+protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
+Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
+our conclusions in \cref{Conclusion}.

### 2019-03-01 paper/analysis-performance.tex
Turns footnotes into references

@@
 \subsection{Distance-bounding anonymous credentials}
-The distance-bounding chips\footnote{\url{https://www.3db-access.com}} currently available on the market can already enable proofs of proximity for any range of up to 200 meters.
+The distance-bounding chips~\cite{3dB-access} currently available on the market 
+can already enable proofs of proximity for any range of up to 
+  200 meters.
 One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.

### 2019-04-10 paper/formalization.tex
Adds initial work on formalizing and proving the protocol

--- 2019-02-28 paper/protocol.tex
@@
-%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The \CROCUS Protocol}%
-\label{Protocol}
+\section{Formalization}
 
-We now present \CROCUS, a protocol for privately verifiable crowd
-counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key%
-%, more specifically, an anonymous 
-%identity credential that provides unlinkability between contexts but 
-%linkability for reuse within the same context
-%\sonja{this is actually achieved by our use of prfs for pid and wid,
-%not inherent in the credential}
-% \footnote{%
-%   Given any \ac{CA} that prevents Sybil 
-%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
-%   be used to make sure that for each identity one-and-only-one
-%   cryptographic key is issued.
-%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
-%   to one's identity.
-% }
-. Since we assume these properties, we
-present only the result of the process of getting anonymous
-credentials from a \ac{CA}, in \cref{ProtocolSetup}.
-
-The core of the \CROCUS protocol consists of generating participation
-proofs (joining a protest, participating in witnessing, submitting
-proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
-verification of that count (in \cref{ProtocolVerification}).
-
-% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-% join, participation, submission (all in in \cref{ProtocolDuring}) and
-% verification (in \cref{ProtocolVerification}).
-
-The entities involved in our protocol are participants and (count) verifiers.
-A participant can assume three different roles:
-\begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and 
-  disseminated it to others.
-\item A \emph{protester} is attending the protest and asks witnesses to vouch 
-  for their presence.
-\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
-  third parties.
-\end{enumerate}
-In general, there is one organizer and every participant can act as
-either or both protester and witness.
-
-After the protest, anyone can count the number of participants (of the protest and the
-protocol) and verify anyone else's count given the relevant meta data
-(which protest, location, time, and witness parameters used in the
-count). We refer to anyone counting or verifying a count as the
-verifier; the process is the same.
-
-\subsection{Prerequisite: anonymous credentials}%
-\label{ProtocolSetup}
-
-Before Alice can have her participation in any event counted by
-\CROCUS, she needs to get an anonymous credential and corresponding
-keys. This only needs to be repeated when the credential expires or is
-lost, in analogy to a passport in terms of expected intervals. The
-keys can be reused for an arbitrary number of protests or, given
-careful choices in the PRF used for deriving identifiers, other
-services that work with anonymous credentials.
-
-We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
-getting anonymous credentials, adapting only the notation to fit ours. 
-%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
+\subsection{Setup}
 
 \emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
-During the setup phase, the \ac{CA} creates all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
-  \ACsetup\) (see \cref{ACsignAlg}).
+Generates a service public--private key-pair~\((\spk, \ssk)\).
 
@@
     \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration phase, each participant generates a secret key~\((k, 
-  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
-  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
-At the end, each participant will have a signed secret key while the \ac{CA} 
-will issue only one signature per participant but without knowing the 
-association between a particular key and the identity of the participant.
-The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
-\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
-\cref{ACacAlg}).
-Upon success, the participant sets \(\sk = (\sigma, k, r)\).
+An interactive protocol which returns the secret key~\(\sk\) of the 
+participant~\(P\).
 
@@
 
-%The join, participation and submission phases are as follows.
-% illustrated in \cref{fig:ProtocolOverview}.
-The goal of \CROCUS is to generate and collect privacy-preserving
-participation proofs that can be counted and verified. These proofs
-consist of proof shares that are constructed as depicted in
-\cref{fig:ProofFig}. The protocol phases are given in
-\cref{fig:ProtocolOverview} and described below.
+\emph{Creation of a protest: \(\cid\gets \GenProtest[s]\).}
+Takes a string~\(s\in\{0,1\}^*\) describing the protest cause and returns a 
+unique cause identifier~\(\cid\).
 
-\begin{figure}
-  \centering
-  \small
-  \includegraphics{proofshare.tikz}
-  \caption{%
-    Structure of a proof share.
-    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
-    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
-    witness's key \(\sk_W\) and the protester's \(\pid\).
-    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
-    protester and witness, respectively, and \(l\) is an area.
-    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
-      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
-    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
-    The protester constructs \(\prf_P\) analogously.
-  }%
-  \label{fig:ProofFig}
-\end{figure}%
+\emph{Joining: \((\pid, t_s)\gets \CROCUSjoin[_P][\cid]\).}
+Takes the cause identifier~\(\cid\) of a protest and returns the protester' 
+protest-specific identifier~\(\pid\) along with a time-stamp~\(t_s\).
 
-\emph{Creation of a protest: the manifesto.}
-The organizer writes a manifesto for the protest, which describes its cause.
-This manifesto could take the form of any intelligible text, in
-practice at minimum a name.
-The organizer then distributes this manifesto to people through
-any suitable means  (\eg on the Web, on placards, \etc).
-If they agree with the cause, they will use the knowledge of the
-manifesto to join the protest.
-
-\emph{Joining as a protester: \((\pid, t_s)\gets 
-    \CROCUSjoin[_P][\text{manifesto}]\).}
 A protester who wants to join the protest uses the manifesto to

### 2019-05-02 paper/MANETs.tex

--- 2019-02-05 paper/MANETs.tex
@@
 drive for operators to identify the network users, there still is an
-authorization step to communicate in this mode.
+authorization step to communicate in this
+mode. Near-field-communication (NFC) would
+solve any scalability problem from interference, require no
+infrastructure or provider, but at the price of having
+participant and witness hold their phones together for each proof
+share. 
 %~\footnote{ https://portal.3gpp.org/desktopmodules/Specifications/SpecificationDetails.aspx?specificationId=840}

### 2019-05-02 paper/adversary-model.tex

--- 2019-02-19 paper/adversary-model.tex
@@
 
-% We now provide a concretely defined system and adversary model.
-% We give three definitions, each defining an adversary with increasingly stronger 
-% capabilities (\ie more auxiliary information).
-
 There are three players: the protester (with identity) \(P\), a witness (with 
-identity) \(W\) and the time-stamping storage \(S\) (that will contain the set 
-of all proof shares, \(\pshs\)).
+identity) \(W\), and a ledger~\(\TS\) (\ie time-stamping storage, that will 
+contain the set of all proof shares, \(\pshs\)).
 The protester \(P\) and the witness \(W\) communicate some protocol data,
-\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
-The protester \(P\) communicates with \(S\), in which \(S\) only learns some 
-function of the protocol data exchanged with the witness, \(f(d_{P,W}(\cid, 
-  P))\) for some function \(f\), and the time of the communication 
-(\(t_{P,S}\)).
+\(d_{P,W}(\cid, P)\), and record when the communication occurred \(t_{P,W}\).
+The protester \(P\) communicates with \(\TS\) and \(\TS\) only learns 
+some function \(f\) of the protocol data exchanged with the witness,
+\(f(d_{P,W}(\cid, P))\), and the time of the 
+communication (\(t_{P,\TS}\)).
 This is illustrated in \cref{fig:base-adversary}.
@@
     The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
-    the storage \(S\), who records the time that happened, \(t_{P,S}\).
-    Both the witness \(W\) and the storage \(S\) are controlled by the 
-    adversary.
+    the ledger \(\TS\), who records the time that happened, \(t_{P,\TS}\).
+    %Both the witness \(W\) and the ledger \(\TS\) are controlled by the 
+    %adversary.
   }
@@
 
-The adversary maliciously controls \(W\).
-The adversary honest-but-curiously controls \(S\).
-The adversary only learns the protocol data --- \ie what is sent over the 
-channel, no auxiliary data\footnote{%
-  By auxiliary data we mean any data outside of the protocol, \ie
-  meta-data such as who is on the other side of the channel obtained
+The adversary maliciously controls \(W\) (the strongest role a
+participant can take on).
+The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
+like everyone else (\ie a malicious protester~\(P\)).
+The adversary only learns the protocol data, \ie what is sent over the 
+channel --- no auxiliary data such as who is on the other side of the channel obtained
   as side information, \eg by face recognition or inference from address
   to identity.
-}
-
-This adversary has no access to data from outside the system, \eg inferences 
-that can be made from the communication layer (\eg IP-addresses mapped to 
-physical identities or face recognition from the protest), which means that it 
-has only the protocol data at its disposal.

### 2019-05-02 paper/conclusions.tex

@@
 The only results that cannot be trusted are results aligned with the interests 
-of the \ac{CA}.
+of the \ac{CA} (which can be mitigated by multi-party solutions).
 
@@
 While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the flip side of the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
+Until used by most participants, \CROCUS would result in a considerable undercount. 
 However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.

### 2019-05-02 paper/identity-limits.tex

@@
   \Eg Sweden does not issue birth certificates, it simply creates and entry in 
-  the population registry.
+  the population register.
 } This birth certificate later serves as the root for many authentication 
@@
 
-An identity is created when an entry is made in the population registry.
-Each entry in the registry has a unique identification number.
-The population registry serves various purposes, one, arguably among the most 
+An identity is created when an entry is made in the population register.
+Each entry in the register has a unique identification number.
+The population register serves various purposes, one, arguably among the most 
 important, is the generation of the electoral 
@@
 
-For a person to cause an entry into the population registry, they have two 
+For a person to cause an entry into the population register, they have two 
 options:
-they are in the population registry and give birth to a child, or
+they are in the population register and give birth to a child, or
 they were born abroad and apply to immigrate to Sweden.
@@
   If the child is born in Sweden, the hospital will report all these things 
-  directly to the population registry without issuing any papers to the 
+  directly to the population register without issuing any papers to the 
   parents.
@@
 
-Obviously the one who creates entries in the population registry can do that 
+Obviously the one who creates entries in the population register can do that 
 even without such documents, so there must be some separation of duty, audit 
 trail or transparency to prevent the agency from performing a Sybil attack.
-In the case of Sweden, the population registry is public.
+In the case of Sweden, the population register is public.
 This means that in addition to any audit trail in place at the agency, we have 
@@
 Thus, technically, to detect a Sybil attack by them, \ie fake identities, one 
-must check the ID against the population registry and follow the audit trail.
+must check the ID against the population register and follow the audit trail.
 With anonymous credentials, this becomes a problem.

### 2019-05-02 paper/related-work.tex

@@
 
-\subsection{Crowd counting methods}
-\input{crowd-counting-methods.tex}
+%\subsection{Crowd counting methods}
 
-\subsection{Location proofs}
-\input{location-proofs.tex}
+The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
+This manual method devised in the 1960s relies on aerial pictures of the event.
+The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
+Using pictures makes it difficult to get cumulative counts, verify that the pictures have not been manipulated, and to have both privacy and individual verifiability: either one is included in the picture (privacy problem) or not (verifiability problem).
+Similar limitations exist for estimating the number of persons in a picture or video (\eg the work of \cite{NNCrowdCounting} or  CrowdSize~\cite{CrowdSize}).
+
+Another problem for all the above methods is exemplified by the demonstrations in Seoul:
+\blockcquote{2016DemonstrationsInSeoul}{%
+  \textins*{t}he demonstrators not only gather in open space, but also small alleys and between buildings%
+}.
+In this situation it is very difficult to faithfully capture the situation.
+Taking pictures from different angles risks double counts.
+Another challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
+
+Counting MAC addresses, as done by a company during the protests in Seoul~\cite{2016DemonstrationsInSeoul} suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.
+
+An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}.
+This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.
+
+CrowdCount \citet{CrowdCount} is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
+Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
+However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.
+
+%\input{location-proofs.tex}

### 2019-05-02 paper/system-model.tex

@@
 communicate with other local devices on Alice's behalf.
-Furthermore, we assume that each participant has a digital certificate signed 
+Furthermore, we assume that each participant has a digital identity certificate signed 
 by \iac{CA}\footnote{%
@@
     centralized} to prevent Sybil attacks.
-  See \cref{identity-limits} for a discussion on existing identity systems and 
-  their limits.
  } that ensures a one-to-one mapping between an identity and a cryptographic 
 key\footnote{%
-  For every identity there exists at most one valid digital certificate.
+  For every physical person there exists at most one valid digital certificate.
 }.
 
-In practice, participants witness each other's participation using their smartphones (or similar devices) running the protocol described in \cref{Protocol} and uploading their testimony (\ie, proof shares) to a ledger (such as a blockchain) after the protest.
-During the protest, the devices might be limited by their batteries and computations they can perform and only have local connectivity to each other.
-No connection to any global network such as the Internet is necessary at that time.  
-Nonetheless, before and after the protest, we assume that the devices have global connectivity (\ie Internet connections) and are not computationally limited by any battery.
-This assumption is necessary to ensure that the participants will be able to upload their proof shares to the ledger.
+In practice, participants witness each other's participation using
+their smartphones (or similar devices) running the protocol described
+in \cref{Protocol} and uploading their testimony (\ie, proof shares)
+to a ledger (such as a blockchain) after the protest.  During the
+protest, the devices might be limited by their batteries and
+computations they can perform and only have local connectivity to each
+other.  No connection to any global network such as the Internet is
+necessary at that time.  Nonetheless, before and after the protest, we
+assume that the devices have global connectivity (\ie Internet
+connections) and are not computationally limited by any battery, for
+the participants to be able to upload their proof shares to the
+ledger.
 
@@
       old.}
-  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
+  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
     \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
@@
   \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove his vote was cast in any particular way.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
 \end{description}

### 2019-05-02 paper/timestamp.tex

@@
 We need a robust time-stamping and storage service (\ie a ledger), \(\TS\), 
-which implements the following oracles:
+which implements the following:
 \begin{itemize}
@@
 by ledgers.
-First, \(\TS\) must be continuously extended, such as in Bitcoin in which 
+First, \(\TS\) must be continuously extended, such as in the Bitcoin blockchain in which 
 blocks are created every 10 minutes on average (this is so that \(\TStime\) can 

### 2019-05-02 paper/verifiability-analysis.tex

@@
 
-\subsubsection{Linkability}%
+\subsubsection{Counted only once}%
 \label{analysis-linkability}
@@
 
-Forging a witness's signature on a proof is equivalent to breaking linkability 
+Forging a witness's signature on a proof is equivalent to breaking the 
+counted-only-once property 
 above (\cref{analysis-linkability}).
@@
 reduced to the trustworthiness of the witnesses chosen by the verifier.
-In the \(\theta\)-threshold case, with unknown witnesses, (by assumption) Alice 
-succeeds only if she can corrupt at least \(\theta\) witnesses.
+In the \(\theta\)-threshold case, with unknown witnesses, 
+%(by assumption) 
+Alice succeeds only if she can corrupt at least \(\theta\) witnesses.
 
@@
 
-\Cref{IndividualVerif} requires that Alice and Bob, as participants, can verify 
+\Cref{IndividualVerif} means that Alice and Bob, as participants, can verify 
 that their participation proofs (\ie proof shares) are indeed included in the 
@@
 \corr_{\wid}\)) of the proofs and count them.
-As for individual verifiability, the security of universal verifiability is 
+Like for individual verifiability, the security of universal verifiability is 
 reduced to the properties of the ledger; but universal verifiability also 

### 2019-05-10 cysep-eurosp/abstract.tex
Adds what's needed for CySeP/Euro-SP abstract

describe the problem being addressed
describe in detail the approach to solve the problem
preliminary results is encouraged but not required
describe the envisioned contribution,
motivate how it relates to the event theme and
why it could spark discussions.

It should also provide information about the presenters and their organizations 
and any special needs for the setup/presentation.

### 2019-05-10 cysep-eurosp/notes.tex
Adds article stuff for cysep-eurosp abstract

\documentclass{article}

\usepackage[hyphens]{url}
\usepackage[hidelinks]{hyperref}

\input{preamble.tex}

\usepackage[noamsthm,notheorems]{beamerarticle}
\setjobnamebeamerversion{slides}

\declaretheorem[numbered=unless unique,style=theorem]{theorem}
\declaretheorem[numbered=unless unique,style=definition]{definition}
\declaretheorem[numbered=unless unique,style=definition]{assumption}
\declaretheorem[numbered=unless unique,style=definition]{protocol}
\declaretheorem[numbered=unless unique,style=example]{example}
%\declaretheorem[style=definition,numbered=unless unique,
%  name=Example,refname={example,examples}]{example}
\declaretheorem[numbered=unless unique,style=remark]{remark}
\declaretheorem[numbered=unless unique,style=remark]{idea}
\declaretheorem[numbered=unless unique,style=exercise]{exercise}
\declaretheorem[numbered=unless unique,style=exercise]{question}
\declaretheorem[numbered=unless unique,style=solution]{solution}

\begin{document}
\title{%
  Something
}
\author{Daniel Bosk and Sonja Buchegger\\
KTH Royal Institute of Technology}
\institute{%
  KTH EECS
}

\mode<article>{\maketitle}
\mode<presentation>{%
  \begin{frame}
    \maketitle
  \end{frame}
}

\mode*

\mode<all>{\input{abstract.tex}}

%%% REFERENCES %%%

\begin{frame}[allowframebreaks]
  \printbibliography
\end{frame}
\end{document}

### 2019-05-10 cysep-eurosp/abstract.tex
adds abstract draft, e-mail to notes

@@
-describe the problem being addressed
-describe in detail the approach to solve the problem
-preliminary results is encouraged but not required
-describe the envisioned contribution,
-motivate how it relates to the event theme and
-why it could spark discussions.
+% describe the problem being addressed
+% describe in detail the approach to solve the problem
+% preliminary results is encouraged but not required
+% describe the envisioned contribution,
+% motivate how it relates to the event theme and
+% why it could spark discussions.
 
-It should also provide information about the presenters and their organizations 
-and any special needs for the setup/presentation.
+% It should also provide information about the presenters and their organizations 
+% and any special needs for the setup/presentation.
+
+\textbf{Problem:}
+Crowd counts vary according to who is doing the counting and what
+methods and criteria they use. Current methods have wide margins for
+error, are difficult to verify, and can be privacy-invasive. We
+recognize the potential adversarial setting for crowd counts and thus
+aim for both transparency (in the form of verifiability) and
+privacy. Different counts: Any solution
+
+\textbf{Approach:}
+ In this paper we propose CROCUS, a decentralized system based on
+ smartphones that combines anonymous credentials, witnesses of
+ proximity, and storage of participation proofs on a public ledger
+ (e.g., blockchain) to achieve properties similar to those needed for
+ electronic voting, where, put simply, it is important to count
+ everyone, but only once, not leak private information, and be able to
+ prove that the count was done correctly.
+
+\textbf{More detailed approach:} 
+By running a distance bounding scheme with anonymous credentials,
+physically present persons (such as protest participants) and create proof
+shares. This is done using smartphones with (assumed)
+distance-bounding chips, without Internet connection but using any
+available local communications. Before and after the event (protest), participants (and
+witnesses), interact with a public blockchain (which does require
+Internet access, and anonymization by e.g. Tor). Before the event to get
+a timestamp and after the event to upload proof shares, again with a
+time stamp. The proof shares form verifiable yet privacy-preserving
+participation proofs according to counting criteria. These criteria
+(time interval, location range, number or kind (e.g., anyone, trusted
+journalists) of unique proof shares
+needed for a proof)
+
+\textbf{Preliminary results:} We find that, with some
+ assumptions about the availability of future technology such as
+ distance-bounding chips on smartphones, CROCUS can provide the
+ desired properties at acceptable performance.
+
+\textbf{Relation to theme:} both security and privacy: verifiability
+
+\textbf{Why it could spark discussions:}
+practical problems: sybil-proof identities needed for anonymous
+credentials
+
+\textbf{Information about the presenters:} Daniel Bosk is a PhD
+student and Sonja Buchegger a Computer Science professor, both at the
+division of Theoretical Computer Science at KTH Royal Institute of
+Technology.

### 2019-05-10 cysep-eurosp/abstract.tex
adds some sections in abstract

@@
 available local communications. Before and after the event (protest), participants (and
-witnesses), interact with a public blockchain (which does require
+witnesses), interact with a public ledger such as a blockchain (which does require
 Internet access, and anonymization by e.g. Tor). Before the event to get
@@
 time stamp. The proof shares form verifiable yet privacy-preserving
-participation proofs according to counting criteria. These criteria
-(time interval, location range, number or kind (e.g., anyone, trusted
+participation proofs according to counting eligibility criteria. These criteria, including
+time interval, location range, number or kind (e.g., anyone, trusted
 journalists) of unique proof shares
-needed for a proof)
+needed for a proof, enable verification by recount. Counting is done
+by downloading the proof shares from the ledger, checking the validity
+and eligibility, and summing up. Any published counts need to also
+publish the criteria used to be verified, but anyone could decide on
+their own criteria and count accordingly.
 
@@
 
-\textbf{Relation to theme:} both security and privacy: verifiability
+\textbf{Relation to theme:} This work is concerned with both security
+and privacy: accountability and verifiability (individual, universal, eligibility) and
+privacy (unlinkability to individual, unlinkability between events,
+unlinkability between witnessing instances).
 
 \textbf{Why it could spark discussions:}
-practical problems: sybil-proof identities needed for anonymous
+practical/ideological problems: sybil-proof identities needed for anonymous
 credentials
@@
 division of Theoretical Computer Science at KTH Royal Institute of
-Technology.
+Technology, working on privacy-enhancing technologies.

### 2019-05-10 cysep-eurosp/abstract.tex
some more text

@@
 methods and criteria they use. Current methods have wide margins for
-error, are difficult to verify, and can be privacy-invasive. We
+error, are difficult to verify, and can be
+privacy-invasive. Historically, there are many examples of events such
+as protests in which the count estimated by police and that of the
+organizers differ significantly, sometimes by hundreds of
+thousands. Even without foul play, the difference is quite natural as
+both parties have different objectives and metrics. More precisely,
+the organizers want to count everyone who participated while the
+police want to estimate the count at the peak of participation, due to
+crowd control. We
 recognize the potential adversarial setting for crowd counts and thus
 aim for both transparency (in the form of verifiability) and
-privacy. Different counts: Any solution
+privacy. Since the crowd count could be done at political protests,
+any solution needs to not endanger participants more than what they
+already face by their physical presence.
 
@@
  distance-bounding chips on smartphones, CROCUS can provide the
- desired properties at acceptable performance.
+ desired properties at acceptable performance, except against a truly
+ global passive adversary.
 
@@
 privacy (unlinkability to individual, unlinkability between events,
-unlinkability between witnessing instances).
+unlinkability between witnessing instances). The building blocks are
+anonymous credentials, distance bounding, blockchain (or other public ledger)
 
-\textbf{Why it could spark discussions:}
-practical/ideological problems: sybil-proof identities needed for anonymous
-credentials
+\textbf{Why it could spark discussions:} There are some practical
+problems that might also be ideological problems: to ensure
+verifiability (specifically, eligibitlity of counting only once, in
+analogy to votes or double spending in e-currencies) despite
+unlinkability/privacy properties, we need sybil-proof identities for
+anonymous credentials.
 

### 2019-05-24 paper/reviews/popets-2019.4-rebuttal.md

REVIEWER 1:

-- “the authors need to reconsider their blockchain design. It seems like they aim to set up a blockchain only for this application. It is unclear who runs the blockchain and who pays the miners of the transactions. Given that it is likely a small blockchain, it seems like it would be easy for Grace to take it over and prevent the inclusion of proofs. Even if Grace cannot control the blockchain, she might create congestion on the chain that prevents the inclusion of real proofs. An alternative is running the scheme on a public blockchain but that will definitively cost fees participants are probably unwilling to pay.”

No separate blockchain. Transaction fees are a concern, but solvable by using social (or public-permissioned) blockchains (WWF Consensys/Ethereum for fish-provenance), no-fee-blockchains (Steem, IOTA, Nano), or indirection:  pool (+check) proof-shares at, say, NGOs or volunteers who upload proof-share-batches in transactions to public blockchains (Ethereum at 3cents) with privacy by extending anonymous submission (Tor) to the indirection, integrity by the NIZK-proofs, DOS (dropping) potentially by redundancy.

-- “the proofs are quite informal and mainly just refer to the properties of the anonymous credential scheme”

We are working on formalizing and proving CROCUS. We  currently have model-syntax and some cryptographic games defined. We still need to capture more properties as games before proving the whole. We intend to include this in a long version (beyond page limits of PETS) on arXiv.

-- “The adversarial model is a bit confusing as it does not state adversarial goals and Fig. 1 does not explain the entity A.”

We’ll add objectives and revise the figure. Overhearing all local communications is OK (no proof-shares-to-identities mapping). As established blockchains are international, only a truly global (i.e., international) passive adversary could infer which (home) IP-address (and identity) uploaded a proof share.

REVIEWER 2:

-- “It's not entirely clear that these properties are in fact the right ones to solve the problem the paper purports to solve.”

We used e-voting as a start. Although there is no consensus on properties, we took a widely-accepted formalized set. We added 4.3 to counter the potential attack-surface from interaction-graphs with witnesses, similarly to E-cash, another related, mature concept, and we can likewise map the properties: 
Weak anonymity ~ Pseudonym-unlinkability
Strong anonymity ~ Unlinkability between protests/witnesses
Unforgeability/No double spending ~ Eligibility
Exculpability ~ Verifiability
The building-block properties are motivated in the security analysis; formalization ongoing.  If reviewers identify missing/superfluous properties, we’ll address them.

-- “the paper also postulates a sybil-proof anonymous credential system. While the proposed approach achieves non-linkability across different crowd event, the anonymity set for any participant who contributes to the count is limited to the set of all those who have obtained these credentials. In other words, in order to achieve meaningful privacy for the proposed use case, these credentials need to not just widely available, but also widely issued. That seems like a huge step to simply assume.”

Yes, hence adoption rate examples of the Swedish BankID (98%, ages 21--50) and Estonia’s e-identity (98% of population), which we found encouraging extrapolating to CROCUS.

REVIEWER 3:

-- “I do not see how untrusted witnesses can lead to a secure outcome, even if there is a large number of them, since there is no reason not to believe that all of them are colluding to inflate the crowd size.”

Agreed, we also mention that a large-enough collusion either happens in public forums (e.g., Reddit), thus detectable by or told to any verifier, or secret forums --- still hard to keep completely secret. While potentially useful, we do not know without research.

-- “Using trusted witnesses [...] it is hard to scale this approach to large crowds. Since the distance-bounding protocol is not specified in this paper, it is hard to assess its practical limitations, but typical phone-to-phone communications have relatively small range, so to count all participants in a large protest witnesses need to be deployed throughout the protest.”

Agreed, trusted witnesses need to move around or be easily visible to approach. No need to agree on trusted witnesses (though more scalable); one can limit trust to counts using witnesses one trusts. According to [29], a SamsungGalaxy ran Idemix in 153ms in 2014. 3DB-access says the DB part takes < 1ms and can do > 120m (line of sight, max 200m). Then fixed witnesses can cover 45216m^2 (120m radius), which [42] says fit max 137018 protesters. Thus one witness can witness these in 5.8 h, witness 188235 protesters in 8h and thus 5.3 witnesses could witness 1,000,000 protesters in an 8-h-day. More (sets of) witnesses allow for trust variations.

-- “An important question not considered in this paper is deniability.”

As we argue, for verifiability (no double-counting, Sybil-proof) receipt-freeness is inherently impossible: an adversary that can coerce people, could force them to check whether they participated already. Ideas on how to better deal with the verifiability/receipt-freeness conflict would be welcome.

-- “Finally, the paper acknowledges in section 9.1 that the technologies needed to support it [...] are not yet available. It makes some arguments for why this system may be practical in the near future, by extrapolating some results from prior work. This suggests to me that this paper is better suited for a workshop, such as HotPETS, where these speculative ideas can generate discussion, rather than PETS, which typically expects more fully specified and evaluated work.”

We see workshops-vs-conferences more as how mature the research in the paper itself is, not maturity of technologies needed to use the work or closeness to deployment of research results --- that would preclude many theoretical papers from PETS.

### 2019-05-24 paper/protest-model.tex

@@
 \begin{definition}[Subprotest, Protest]\label{DefProtest}
-  A \emph{subprotest} \(p = (\cid, t, l)\) is a tuple in which \(\cid\in \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of the cause of the protest, \(t \subseteq \TT\) is a time period and \(l \subseteq \LL\) is the location (the topological connectedness is not necessary).\\
+  A \emph{subprotest} \(p = (\cid, t, l)\) is a tuple in which \(\cid\in 
+    \bin^{\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
+  the cause of the protest, \(t \subseteq \TT\) is a time period and \(l 
+    \subseteq \LL\) is the location (topological connectedness is not 
+  necessary).
+
   A \emph{protest} \(\prtst\) is the set of subprotests sharing the same \(\cid\).
@@
   \(\cid, t, l\) are as in \cref{DefProtest};
-  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\); and \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).\\
+  \(\pid\) is a protester's pseudonym for the protest identified by \(\cid\);
+  \(\wid\) is a witness's pseudonym for a protester with pseudonym \(\pid\).
+
   Furthermore, we say that \(\psh\) is \emph{valid} for a subprotest \(\sprtst = (\cid', t', l')\) if and only if \(\cid = \cid', t\subseteq t', l\subseteq l'\) and denote this by 
@@
 \begin{multline*}
-  \pshs_{\cid_0, \pid_0} = \\
-  \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = \cid_0 \land \pid = \pid_0\}.
+  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
+  \cid_0 \land \pid = \pid_0\}.
 \end{multline*}

### 2019-05-24 cysep-eurosp/abstract.tex

@@
 proximity, and storage of participation proofs on a public ledger
- (e.g., blockchain) to achieve properties similar to those needed for
+(e.g., blockchain).
+CROCUS achieves properties similar to those needed for
 electronic voting, where, put simply, it is important to count
@@
 By running a distance bounding scheme with anonymous credentials,
-physically present persons (such as protest participants) and create proof
+physically present persons (such as protest participants) create proof
 shares. This is done using smartphones with (assumed)
@@
 available local communications. Before and after the event (protest), participants (and
-witnesses), interact with a public ledger such as a blockchain (which does require
+witnesses) interact with a public ledger such as a blockchain (which does require
 Internet access, and anonymization by e.g. Tor). Before the event to get

### 2019-05-28 paper/DB-anon-cred.tex
Edits intro to DB-anon-cred

@@
-\section{Distance-bounding anonymous credentials}%
+\section{Distance-bounding \ac*{ZKPK} for discrete logarithms}%
 \label{DB-anon-cred}
 
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
-To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
+We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
+logarithms.
+Our protocol is an adaptation of the Schnorr identification 
+scheme~\cite{Schnorr}, albeit different from that of 
+\textcite{DistanceBounding} in the original \ac{DB} paper.
+(That protocol was shown to be prone to distance 
+hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
+terrorist fraud.)
+We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
+protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
+\ac{DBDH} and \ac{DBTF}.
+This yields strong privacy properties and protection against a malicious, 
+impersonating verifier.
+
+We also deviate from the normal technique of one-bit challenges and responses 
+otherwise used in \ac{DB} protocols.
+\Textcite{UWBwithPulseReordering} proposed a secure encoding for the physical 
+layer which removes the requirement of only using single-bit challenges and 
+responses for distance bounding.
+However, their protocol only works for relay attacks and cannot handle distance 
+fraud.
+This is due to a requirement of the protocol that the prover and verifier must 
+share a secret, and thus must be mutually trusted.
+
+We will first present our version of the \ac{DB} Schnorr protocol for the 
+mutual-trust case, where the prover and verifier have a pre-shared secret.
+Then we will adapt it by introducing \iac{AKE}.
+The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
+\ac{ZKPK} for discrete logarithms.
+If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
+while we authenticate the key.
+This allows us to embed this protocol into tamper resistant hardware to provide 
+security against malicious provers.
 
@@
 \label{DBSchnorr}
-
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
-We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
 

### 2019-05-28 paper/related-work.tex
Edits intro to DB-anon-cred

--- 2019-02-13 paper/related-work.tex
@@
 \label{related-work}
+
+\subsection{Distance bounding}
+
+One protocol exists in the literature that provides \acp{PPK} with most of the 
+desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
+  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
+  shorter notation.}.
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
+logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
+details).
+To realize this, we will now introduce such a protocol to enable us to have 
+\ac{DB} anonymous credentials.
 

### 2019-05-28 paper/DB-anon-cred.tex
Rewrites DB-Schnorr alg description to use UWBPR

@@
 otherwise used in \ac{DB} protocols.
-\Textcite{UWBwithPulseReordering} proposed a secure encoding for the physical 
+\Textcite{UWBPR} proposed a secure encoding for the physical 
 layer which removes the requirement of only using single-bit challenges and 
@@
 
+Thanks to \textcite{UWBPR} we can keep the Schnorr protocol 
+almost as is, relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical 
+layer.
+The only concern, for now, is \acl{DBTF}.
+(We deal with \acl{DBDF} later.)
+
 We present the protocol in \cref{SchnorrFigure}.
@@
 The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
+Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
+Further, let
+\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
+\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
+key~\(k\) and finally
+\(\Delta t\gets \UWBPRtime\) denote the time between sending and receiving.
 
@@
   \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
+    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
     & &
-    \(\DBSverify[g, q, A]\):
+    \(\DBSverify[k, g, q, A]\):
     \\
@@
     \multicolumn{3}{c}{\textbf{Setup}} \\
+
+    Load \(k\) into \(\UWBPR\)
+    &
+    & Load \(k\) into \(\UWBPR\)
+    \\
 
@@
 
-    % null
+    \(s_0\gets \rho - c_0\alpha \pmod q\)
     & \(\ProtoSendLeft{c_0, c_1}\)
@@
 
-    \(s_0\gets \rho - c_0\alpha \pmod q\)
-    &
-    & \(b\rgets \bin\)
-    \\
-
     \(s_1\gets \rho - c_1\alpha \pmod q\)
     &
-    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
+    &
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
-        l, j\gets 0\)} \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
+
+    \text{Ready}
+    & \ProtoSendRight{\text{Ready}}
+    & \\
 
@@
     % null
-    & \(\ProtoSendLeft{b_i}\)
-    & \(b_i\gets B[i]\)
+    & \(\ProtoSendLeft{b}\)
+    & \(b\rgets \bin\)
     \\
 
-    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
-    & \(\ProtoSendRight{r_i}\)
-    & Record \(\Delta t_i\)
-    \\
-
-    \(j \gets j + b_i\)
-    &
-    &
+    Fetch \(s_b\)
+    & \(\ProtoSendRight{s_b}\)
+    & Record \(\Delta t\)
     \\
@@
     &
-    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
-      b\).
-      Accept if \(R = g^{s_b} A^{c_b}\).
+    & Accept if \(R = g^{s_b} A^{c_b}\).
     \\
@@
   \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
+    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
+    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
+    Each transmission (arrow in the diagram) uses \(\UWBPR\).
+    The protocol should be repeated in full to achieve the desired soundness 
+    and distance-bounding errors.
   }%
@@
 
-During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
+During one round, in the setup phase, the prover commits to a random nonce: 
+more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
+\(R\gets g^\rho\) and sends \(R\) to the verifier.
 The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
@@
 
-We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(|q|\) response-bits from one challenge (say 
-\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
-Then the verifier can authenticate the prover by checking if \(R = 
-  g^{s_b}A^{c_b}\).
+In the \ac{DB} phase, the prover notifies the verifier that he has computed 
+\(s_0, s_1\).
+The verifier chooses one bit, \(b\), uniformly randomly and sends it as a 
+challenge to the prover and starts measuring the time of flight.
+The prover replies with \(s_b\).
+The verifier stops the measurement and verifies that \(R = g^{s_b}A^{c_b}\).
 

### 2019-06-11 paper/DB-anon-cred.tex
Changes k to sk in DB-Schnorr
Changes section heading to plural form
Edits DB-Schnorr security analysis

@@
-\section{Distance-bounding \ac*{ZKPK} for discrete logarithms}%
+\section{Distance-bounding \aclp{ZKPK} for discrete logarithms}%
 \label{DB-anon-cred}
@@
 key~\(k\) and finally
-\(\Delta t\gets \UWBPRtime\) denote the time between sending and receiving.
+\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
+and \(\UWBPRrecv\) operations.
 
@@
   \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
+    \(\DBSprove[\sk, g, q, \alpha, A = g^\alpha]\):
     & &
-    \(\DBSverify[k, g, q, A]\):
+    \(\DBSverify[\sk, g, q, A]\):
     \\
@@
 
-    Load \(k\) into \(\UWBPR\)
+    Load \(\sk\) into \(\UWBPR\)
     &
-    & Load \(k\) into \(\UWBPR\)
+    & Load \(\sk\) into \(\UWBPR\)
     \\
@@
 
+This protocol must be repeated \(n\) times.
+
 \subsection{Security analysis}
@@
 The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
-The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
-This allows us to prevent \ac{DBTF}.
-Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
-%reducing success of MF according to number of repetitions.
-The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
-Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
+The reason for having two challenges but only one random nonce is that knowing 
+the responses to both means learning \(\alpha\).
+This gives us the incentives that prevent \ac{DBTF}.
+Bundling the authentication into the distance-bounding phase (difference from 
+Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at 
+\ac{DBMF} resistance.
+We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
+can do \iac{DBEDLC} attack to reduce the distance.
+(We will solve this problem in the next section.)
 
 The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
-the knowledge error, \(2^{-kn}\), becomes small enough.
-Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
+security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
+the soundness error, \(2^{-kn}\), becomes small enough.
+(Repeating the protocol is also needed to decrease the success probability of 
+some of adversaries presented below.)
+
+The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
+distance-reduction through \iac{DBEDLC} attack.
+Thus, any relaying will be detected.
+The adversary could guess the challenge bit \(b\), request \(s_b\) from the 
+prover and guess \(s_{1-b}\).
+The success probability of this is \(\frac{1}{2} + \frac{1}{q}\) per round, 
+thus \((\frac{q + 2}{2q})^n\) in total.
+
+The protocol is also secure against distance hijacking due to the fact that the 
+authenticating bitstring is used during the \ac{DB} phase, not the challenge 
+bitstring, as is the case for the original protocol of Brands-Chaum.
+Thus the probability of success is equivalent of a collision for the responses 
+for the chosen challenge --- in each round.
+
+Finally, it follows from the original Schnorr protocol that this is still 
+\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
+\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
+
+\subsection{Achieving \acl{DBDF} and \acl{DBTF} resistance}
+
+\Acl{DB} protocols requires hardware implementations.
+We will use a trusted hardware implementation to overcome the limitation of 
+\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
+This will also require \iac{PKI} to overcome the shared-key requirement and for 
+a verifier to be able verify the hardware of a prover.
 
@@
 
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
-The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
-  s_1\).
-\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
-\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
-Now, the adversary has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
-However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
-The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
-Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
-If the adversary requests \(s_b\) in full, the adversary can also guess the 
-remaining \(|q|-l\) bits of \(s_{1-b}\).
-Based on our assumption above, the probability of guessing these bits 
-successfully is \(2^{-(|q|-l)}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-(|q|-l)n}\).
-
 The protocol is \ac{DBTF}-resistant.
-Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
+Indeed, if the malicious prover gives both responses to the accomplice, the 
+accomplice can compute his secret key.
 The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
-
-The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
-Thus the probability of success is equivalent of a collision for the responses 
-for the chosen challenge --- in each round.
-
-Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
 
@@
 
-We wanted to formally verify the protocol security properties. To realize this, 
-we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
-originally the possibility to reason on time and space in its model.
-However, thanks to a recent work by \textcite{TamarinDB}, all the common 
-properties mentioned in the previous subsection can be equivalently 
-characterized with a causality-based definition relying only on the order of 
-messages.
-
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
-It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
-
-Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
-This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
-We are currently investigating the Tamarin interactive mode to validate as well the security properties.
+We formally verified these properties with Tamarin~\cite{meier2013tamarin}.
+Thanks to recent work by \textcite{TamarinDB}, all the common properties for 
+\ac{DB} protocols (except \ac{DBTF}) can be characterized with a 
+causality-based definition relying only on the order of messages.
+The whole Tamarin specification for our protocol is provided in 
+\cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that 
+we have made.
+It contains a specification of the distance-bounding protocol described 
+previously, a definition of the soundness and correctness properties that 
+ensure the protocol actually produces the expected result, and a definition of 
+the security properties we want to ensure.

### 2019-06-28 paper/distance-bounding.tex
Improves section titles with \acl*

--- 2019-02-28 paper/distance-bounding.tex
@@
-\subsection{Distance-bounding protocols}%
+\subsection{\Acl*{DB} protocols}%
 \label{distance-bounding}
@@
     \Ac{DBTF} resistance is a very strong property; it implies that if the 
-    verifier accepts the accomplice with non-negligible probability the 
-    accomplice can compute the prover's secret key\footnote{%
+    accomplice succeeds (with non-negligible probability) he will learn the 
+    prover's secret key\footnote{%
       This means that even things like functional encryption will not help.
@@
 \ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
-For this paper, we assume the existence of such a protocol.
-Candidates for such a protocol include modifications of ~\cite{ProProx} or \cite{PROPS} to work for discrete logarithm and to provide general attribute-based anonymous credentials (not restricted to identity-based ones), respectively.

### 2019-06-28 paper/DB-anon-cred.tex
Improves section titles with \acl*
Changes the DB-Schnorr to use k challenges instead of two

@@
-\section{Distance-bounding \aclp{ZKPK} for discrete logarithms}%
+\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
 \label{DB-anon-cred}
@@
 
-    \(s_0\gets \rho - c_0\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_0, c_1}\)
-    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
+    & \(c_1\rgets \bin^k, \dotsc, c_k\rgets \bin^k\)
     \\
 
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    \vdots
+    &
+    &
+    \\[-1em]
+
+    \(s_k\gets \rho - c_k\alpha \pmod q\)
     &
@@
     % null
-    & \(\ProtoSendLeft{b}\)
-    & \(b\rgets \bin\)
+    & \(\ProtoSendLeft{i}\)
+    & \(i\rgets \{1, \dotsc, k\}\), start clock
     \\
 
-    Fetch \(s_b\)
-    & \(\ProtoSendRight{s_b}\)
-    & Record \(\Delta t\)
+    Fetch \(s_i\)
+    & \(\ProtoSendRight{s_i}\)
+    & Stop clock, record \(\Delta t\)
     \\
@@
     &
-    & Accept if \(R = g^{s_b} A^{c_b}\).
+    & Accept if \(R = g^{s_i} A^{c_i}\) and \(\Delta t < t_{\max}\).
     \\
@@
     Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol should be repeated in full to achieve the desired soundness 
-    and distance-bounding errors.
+    The protocol should be repeated \(n\) times to achieve the desired 
+    soundness and distance-bounding errors.
   }%
@@
 \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
-The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
-This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
+The verifier generates \(k\) challenges \(c_1\rgets \bin^k, \dotsc, c_k\rgets 
+  \bin^k\) (bit strings of length \(k\)) and sends them to the prover.
+The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
+  \dotsc, s_k\gets \rho - c_k\alpha\).
+This step is the main difference to the original Schnorr protocol: the verifier 
+selects several challenges and the prover computes several responses --- but 
+still only use \emph{one nonce}, \(\rho\).
+This is needed for \ac{DBTF} resistance.
 This is also different from the original Brands-Chaum protocol, in which the 
@@
 In the \ac{DB} phase, the prover notifies the verifier that he has computed 
-\(s_0, s_1\).
-The verifier chooses one bit, \(b\), uniformly randomly and sends it as a 
-challenge to the prover and starts measuring the time of flight.
-The prover replies with \(s_b\).
-The verifier stops the measurement and verifies that \(R = g^{s_b}A^{c_b}\).
+\(s_1, \dotsc, s_k\).
+The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
+it as a challenge to the prover and starts measuring the time of flight.
+The prover replies with \(s_i\).
+The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
+that the time of flight was within \(t_{\max}\) (determined from the allowed 
+  distance).
 
@@
 
-The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
-The reason for having two challenges but only one random nonce is that knowing 
-the responses to both means learning \(\alpha\).
+The intuition behind the protocol security is as follows.
+The prover must know the responses for all challenges to successfully pass the 
+\ac{DB} phase.
+The reason for having several challenges but only one random nonce is that 
+knowing at least two responses means learning \(\alpha\).
 This gives us the incentives that prevent \ac{DBTF}.
 Bundling the authentication into the distance-bounding phase (difference from 
-Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at 
-\ac{DBMF} resistance.
+Brands-Chaum) prevents \ac{DBDH}.
 We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
@@
 (We will solve this problem in the next section.)
-
-The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
-security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
-the soundness error, \(2^{-kn}\), becomes small enough.
-(Repeating the protocol is also needed to decrease the success probability of 
-some of adversaries presented below.)
+However, the properties of \(\UWBPR\) ensures \ac{DBMF} resistance.
 
@@
 The protocol is also secure against distance hijacking due to the fact that the 
-authenticating bitstring is used during the \ac{DB} phase, not the challenge 
-bitstring, as is the case for the original protocol of Brands-Chaum.
+authenticating bit string is used during the \ac{DB} phase, not the challenge 
+bit string, as is the case for the original protocol of Brands-Chaum.
 Thus the probability of success is equivalent of a collision for the responses 
@@
 
+\Ac{DBDH} requires that the adversary finds a collision between his response 
+and that of the honest prover.
+\dots
+
 Finally, it follows from the original Schnorr protocol that this is still 
 \ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
+security parameter \(\lambda\) and repeat the protocol \(n\) times.
+
 \daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

### 2019-06-28 paper/distance-bounding.tex
Prepares for using the DFKO framework

@@
 There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
+We will use the framework of \citeauthor{DB-DFKO} with extensions by 
+\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
+\cref{DB-definitions}).
 
 The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
+In this context it does not make sense to protect against the verifier as he 
+can easily impersonate the prover as he has a knowledge of his secret key.
 There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
-The verifier might also try to track the provers and map their identities to 
-their actions, thus we also require strong privacy.
-In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
-\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
+We will work in the latter setting; with a \emph{malicious verifier} who will 
+potentially try to \emph{impersonate the prover} after successful verification.
+
+\subsection{\Acl*{DB} security definitions}%
+\label{DB-definitions}
+
+\dots

### 2019-06-28 paper/DB-anon-cred.tex
Adds arguments for DB-Schnorr similar to Schnorr (for proof)

@@
 
-\subsection{Security analysis}
+\subsection{\Acl*{ZK} and \acl*{PK}}
+
+The main difference between this protocol and the Schnorr protocol is that we 
+have the prover compute responses for \(k\) different challenges, \(c_1, 
+  \dotsc, c_k\).
+However, in the authentication step, the verifier chooses only one of those 
+challenges.
+From the simulator's (and extractor's) perspective, there is no difference 
+whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
+challenges, or if the verfifier chooses the one challenge directly;
+the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
+Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
+protocol with soundness error \(2^{-kn}\) still 
+holds~\cite[\eg][]{OnSigmaProtocols}.
+
+\subsection{\acs*{DBMF}, \acs*{DBDH} and \acs*{DBTF} resistance}
 

### 2019-06-28 paper/DB-anon-cred.tex
Prepares remaining security proof (WIP)

@@
 The reason for having several challenges but only one random nonce is that 
-knowing at least two responses means learning \(\alpha\).
+knowing at least two responses means learning the secret~\(\alpha\).
 This gives us the incentives that prevent \ac{DBTF}.
@@
 (We will solve this problem in the next section.)
-However, the properties of \(\UWBPR\) ensures \ac{DBMF} resistance.
+However, the properties of \(\UWBPR\) and the unpredictability of the 
+challenges ensures \ac{DBMF} resistance.
 
 The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
-distance-reduction through \iac{DBEDLC} attack.
+distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
 Thus, any relaying will be detected.
-The adversary could guess the challenge bit \(b\), request \(s_b\) from the 
-prover and guess \(s_{1-b}\).
-The success probability of this is \(\frac{1}{2} + \frac{1}{q}\) per round, 
-thus \((\frac{q + 2}{2q})^n\) in total.
+The adversary could guess the challenge chosen, \(i\), request \(s_i\) from the 
+prover and guess \(s_j\) for \(i\neq j\).
+The success probability of this is \(\frac{1}{k} + \frac{k}{q}\) per round, 
+thus \((\frac{q + k}{kq})^n\) in total.
 
@@
 
-Finally, it follows from the original Schnorr protocol that this is still 
-\ac{ZK} and \iac{PK} with soundness error \(2^{-kn}\).
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the 
-security parameter \(\lambda\) and repeat the protocol \(n\) times.
+\NewAlgorithm{\adv}{A}
 
-\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
+\begin{proof}[\acs*{DBTF} resistance]
+  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
+  provers help with non-negligible advantage~\(\epsilon\), \ie the success 
+  probability is \(\frac{1}{2}+\epsilon\).
+  There is chance that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
+  Thus, there is some case for which \(\adv\) knows both responses.
+  In that case \(\adv\) can simply compute the secret and impersonate with 
+  probability \(1\) forever.
+\end{proof}
 
-\subsection{Achieving \acl{DBDF} and \acl{DBTF} resistance}
+\begin{proof}[\acs*{DBDH} resistance]
+  The adversary must find a collision of challenges for the honest provers 
+  challenges, so that the verifying equation holds at the end.
+\end{proof}
+
+The protocol is \ac{DBTF}-resistant.
+Indeed, if the malicious prover gives both responses to the accomplice, the 
+accomplice can compute his secret key.
+The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
+
+\subsection{Achieving \acl{DBDF} resistance}
 
@@
 \textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
-This will also require \iac{PKI} to overcome the shared-key requirement and for 
-a verifier to be able verify the hardware of a prover.
+We will need \iac{PKI} for the verifier to verify the trusted hardware.
+We will leverage this \ac{PKI} to overcome the shared-key requirement.
+With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
+\ac{ZKPK} which simultaneously proves
+\begin{enumerate*}
+\item that the protocol is run by trusted hardware,
+\item that that trusted hardware is within proximity,
+\item that some \ac{ZKPK} statement holds, and
+\item that that knowledge is within proximity.
+\end{enumerate*}
 
@@
 Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
-
-The protocol is \ac{DBTF}-resistant.
-Indeed, if the malicious prover gives both responses to the accomplice, the 
-accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
 

### 2019-07-01 paper/DB-anon-cred.tex
Minor edit on achieving DF resistance intro
Adds some parentheses

@@
 This gives us the incentives that prevent \ac{DBTF}.
+(We also need it for \ac{DBMF}.)
 Bundling the authentication into the distance-bounding phase (difference from 
@@
 can do \iac{DBEDLC} attack to reduce the distance.
-(We will solve this problem in the next section.)
+(We will solve this problem further down.)
 However, the properties of \(\UWBPR\) and the unpredictability of the 
-challenges ensures \ac{DBMF} resistance.
+challenges ensures \ac{DBMF} resistance (since then the prover is honest).
 
@@
 With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
-\ac{ZKPK} which simultaneously proves
+\ac{ZKPK} which \emph{simultaneously} proves
 \begin{enumerate*}
@@
 \item that that trusted hardware is within proximity,
-\item that some \ac{ZKPK} statement holds, and
+\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
 \item that that knowledge is within proximity.

### 2019-07-02 paper/distance-bounding.tex
Fixes section titles, moves formal stuff
Adds some formal definitions for DB

@@
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
-We will use the framework of \citeauthor{DB-DFKO} with extensions by 
-\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
-\cref{DB-definitions}).
 
@@
 
+There are two lines of attempts at formalizing the above properties: one by 
+\citet{DB-BMV} and another by \citet{DB-DFKO}.
+We will use the framework of \citeauthor{DB-DFKO} with extensions by 
+\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
+\cref{DB-definitions}).
+
+As summarized in by \textcite{TREAD}, there are three types of sessions for an 
+adversary:
+\begin{description}
+  \item[Prover--verifier] The adversary observes an honest execution.
+  \item[Prover--adversary] The adversary runs the protocol as a verifier with 
+    an honest prover.
+  \item[Adversary--verifier] The adversary runs the protocol as a, potentially 
+    malicious, prover with an honest verifier.
+\end{description}
+Each session is associated with a unique identifier \(\sid\).
+Each adversary is defined in terms of
+computational resources, time~\(t\);
+number of prover--verifier sessions observed, \(\qobs\);
+number of prover--adversary sessions initiated, \(\qp\), and
+number of adversary--verifier sessions initiated, \(\qv\).
+
+The DFKO framework~\cite{DB-DFKO} uses an abstract clock~\(\marker\colon \NN\to 
+  \NN\) which is strictly increasing and orders the adversary's actions.
+We let
+\(\Xscript{\sid}{i, \dotsc, j}\)
+denote the sequence of messages
+\((m_i, \dotsc, m_j)\)
+exchanged during the session \(\sid\).
+
+A session consists of three phases: a setup phase, a time-critical phase and a 
+verification phase.
+Both setup and verification can be run slowly, but the time-critical phase must 
+be run as fast as possible.
+
+\paragraph*{\Acl*{DBMF}}
+
+We will now define the conditions for \ac{DBMF} and \ac{DBMF} resistance.
+A tainted session is a session in which the adversary lost because the verifier 
+detected the attempt at cheating, \eg the timing is too long because the 
+adversary is out of range.
+The following definition captures a pure relay and a verifier is assumed to 
+detect such a relay.
+
+\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]
+  A time-critical round
+  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
+  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
+  verifier, is \emph{tainted} by the round
+  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
+  of a prover--adversary session~\(\sid'\) if
+  \begin{align*}
+    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
+    \marker[\sid, k] &< \marker[\sid', k'] \\
+    \marker[\sid, k+1] &> \marker[\sid', k'+1].
+  \end{align*}
+\end{definition}
+
+We will now define what is means for a protocol to be \ac{DBMF} resistant.
+
+\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]
+  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
+  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
+  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
+  which does not have any critical phase tainted by a prover--adversary session 
+  \(\sid'\).
+  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
+  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins the game is negligible in 
+  the security parameter.
+\end{definition}
+
+\paragraph*{\Acl*{DBTF}}
+
+\Acl{DBTF} is similar to \ac{DBMF}, the difference is that during \ac{DBTF} the 
+prover cooperates with the adversary to make the verifier accept.
+
+\daniel{This definition differs slightly from that of 
+  \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
+  \Ie that the number of messages in \(\sid\) is not required to be the same 
+  and in the same order as in \(\sid'\).}
+
+\begin{definition}[Tainted session, \acs*{DBTF}]
+  A time-critical round
+  \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\)
+  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
+  verifier, is \emph{tainted} by the round
+  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
+  of a prover--adversary session~\(\sid'\) if
+  \begin{align*}
+    \marker[\sid, k] &< \marker[\sid', k'] \\
+    \marker[\sid, k'+1] &> \marker[\sid', k'+1].
+  \end{align*}
+\end{definition}
+
+\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]
   \dots
+\end{definition}
+
+\paragraph*{\Acl*{DBDH}}
+
+\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]
+  \dots
+\end{definition}
+
+\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]
+  \dots
+\end{definition}
+
+These definitions for \ac{DBDH} also captures \ac{DBDF} attacks~\cite{TREAD}.

### 2019-07-02 paper/distance-bounding.tex
Puts labels on definitions (distance-bounding)

@@
 
-\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]
+\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
+  \label{TaintedMF}
   A time-critical round
@@
 
-\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]
+\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
+  \label{MFresistance}
   For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
@@
 
-\begin{definition}[Tainted session, \acs*{DBTF}]
+\begin{definition}[Tainted session, \acs*{DBTF}]\label{TaintedTF}
   A time-critical round
@@
 
-\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]
+\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]%
+  \label{TFresistance}
   \dots
@@
 
-\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]
+\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
+  \label{TaintedDH}
   \dots
@@
 
-\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]
+\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
+  \label{DHresistance}
   \dots

### 2019-07-02 paper/DB-anon-cred.tex
Fixes section titles, moves formal stuff
Puts labels on definitions (distance-bounding)
Adds theorem and proof draft for MF

@@
 distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
-Thus, any relaying will be detected.
-The adversary could guess the challenge chosen, \(i\), request \(s_i\) from the 
-prover and guess \(s_j\) for \(i\neq j\).
-The success probability of this is \(\frac{1}{k} + \frac{k}{q}\) per round, 
-thus \((\frac{q + k}{kq})^n\) in total.
+Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.
+
+\begin{theorem}[\acs*{DBMF} resistance]
+  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
+  \(\Adv_{\DBS}^{\text{MF}}(\adv)\) is negligible.
+\end{theorem}
+
+\begin{proof}
+  The adversary has two options:
+  \begin{enumerate*}
+  \item guess which challenge the verifier will use and request the correct 
+    response from the prover, this yields a success with probability 
+    \(\frac{1}{k}\);
+  \item guess the response, this yields success with probability 
+    \(\frac{1}{q}\).
+  \end{enumerate*}
+  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
+  thus \((q + k)^n (kq)^{-n}\) in total.
+  We have that \(k \in \log(\lambda)\), \(q \in \poly[\lambda]\) and it follows 
+  that the success probability is negligible,
+  \[
+    \left( \frac{\log(\lambda) + 
+        \poly[\lambda]}{\log(\lambda)\poly[\lambda]}\right)^n \approx
+    \frac{1}{\log(\lambda)^n} < \frac{1}{\poly[\lambda]}
+  \] for \(n > 2\).
+\end{proof}
 
@@
 \dots
-
-\NewAlgorithm{\adv}{A}
 
@@
 
-\subsection{Achieving \acl{DBDF} resistance}
+\subsection{Achieving \acs*{DBDF} resistance}
 
@@
 
-\subsection{Formal Verification}
+\subsection{Formal verification}
 

### 2019-07-02 paper/DB-anon-cred.tex
Minor clarifications, typo fixes

@@
 \subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DBSchnorr}
+\label{DB-Schnorr}
 
@@
 whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
-challenges, or if the verfifier chooses the one challenge directly;
+challenges, or if the verifier chooses the one challenge directly;
 the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
@@
 holds~\cite[\eg][]{OnSigmaProtocols}.
+(We note that \(k\), which is also the length of the challenge bit string, must 
+be logarithmic in the security parameter, \(\lambda\), for a malicious 
+verifier.)
 
@@
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv)\) is negligible.
+  \(\Adv_{\DBS}^{\text{MF}}(\adv) = (q+k)^n (kq)^{-n}\), where \(k, q\) are as 
+  in \cref{DB-Schnorr}.
 \end{theorem}

### 2019-07-02 paper/intro.tex
adds intro back in, mostly as skeleton

@@
 
-While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper.
-We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
+\paragraph*{Contributions}
 
-Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
-Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
-More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
-Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
+Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
+including \ac{DBDH} (which was an attack against the original protocol of 
+Brands and Chaum) and \ac{DBTF}.
+More importantly, it is public-key, handles malicious impersonating verifiers.
+Since it is based on the Schnorr protocol, it provides a distance-bounded 
+\ac{PK} for discrete logarithms.
+That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
+distance-bounding version and thus make general privacy-preserving, 
+attribute-based credential systems distance bounding.
 
-Consider the following scenario.
-Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
-Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime.
-To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
-
-Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{related-work}).
-Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.
-In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
-
-Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting.
-Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
-%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
-In this paper, our main objective is to provide a scheme preventing both Alice 
-and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
-While one cannot
-prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.
-
-%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
-%\seb{in the sentence above I am not sure that the word unlinkable will be 
-%  necessary clear}
-
-%\paragraph*{Contributions}
-
-%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
-%way to securely estimate crowd counts in protests\footnote{%
-%  If location is ignored, it can be reduced to privacy-preserving yet 
-%  verifiable petitions.
-%}.
-%
-%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
-%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
-%including \ac{DBDH} (which was an attack against the original protocol of 
-%Brands and Chaum) and \ac{DBTF}.
-%More importantly, it is public-key, handles malicious impersonating verifiers.
-%Since it is based on the Schnorr protocol, it provides a distance-bounded 
-%\ac{PK} for discrete logarithms.
-%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
-%distance-bounding version and thus make general privacy-preserving, 
-%attribute-based credential systems distance bounding.
-
-% The paper is organized as follows.
-% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
-Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}).
-% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
+\paragraph*{Outline}
 
 The paper is organized as follows.
-In \Cref{system-model}, we describe our system model and summarize the desired 
-properties for crowd counting, followed by a discussion of related work in \cref{related-work}.
-In \Cref{definitions}, we formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give
+\Cref{system-model}, we describe our system model and summarize the desired 
+properties 
+We then discuss related work in terms of these properties in 
+\cref{related-work}, and in \cref{building-blocks}, we give 
 the relevant background on the building blocks of our solution.
-%
-%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
-%different from that originally proposed by \textcite{DistanceBounding}.
-%We provide a proof of its security and formally verify it using 
-%Tamarin~\cite{TamarinDB}.
-%
-We present \CROCUS, a privacy-preserving crowd counting 
-%estimation 
-protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
-Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
+
+\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+different from that originally proposed by \textcite{DistanceBounding}.
+We provide a proof of its security and formally verify it using 
+Tamarin~\cite{TamarinDB}.
+
+We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
+in \cref{PerformanceAnalysis}.
+
+Finally, we discuss our assumptions and results in \cref{Discussion} and give 
 our conclusions in \cref{Conclusion}.

### 2019-07-10 paper/DB-anon-cred.tex
Moves DH to after TF
Adds space for clarity
Adds WIP on DH proof

@@
   \end{enumerate*}
+
   The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
@@
 bit string, as is the case for the original protocol of Brands-Chaum.
-Thus the probability of success is equivalent of a collision for the responses 
+\Ac{DBDH} requires that the adversary finds a collision between his response 
+and that of the honest prover.
+Thus the probability of success is equivalent to a collision for the responses 
 for the chosen challenge --- in each round.
 
-\Ac{DBDH} requires that the adversary finds a collision between his response 
-and that of the honest prover.
-\dots
+\begin{theorem}[\acs*{DBDH} resistance]
+  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
+  \(\Adv_{DBS}^{\text{DH}}(\adv) = X\).
+\end{theorem}
+
+\begin{proof}
+  The adversary must find a collision of challenges for the honest prover's 
+  challenges, so that the verifying equation holds at the end.
+  Let \(R, c_1, \dotsc, c_k\) be the transcript of the setup between the honest 
+  verifier and the adversary.
+  Let \(R', c_1', \dotsc, c_k'\) be the transcript of the setup between the 
+  honest verifier and honest prover.
+  The verifier will accept if \(R = g^{s_i'} A^{c_i}\), where \(s_i' = \rho' - 
+    c_i'\alpha'\) is the response by the honest prover computed for his 
+  session, \ie \(\rho = \rho' - c_i'\alpha' + c_i\alpha\).
+  Since the verifier and prover are honest, \(\rho', c_i'\), \(\alpha'\) and 
+  \(c_i\) are chosen uniformly randomly.
+  \(\alpha\) is also chosen uniformly randomly and is fixed.
+
+  \daniel{\Ac{DH} is kind of adaptive and concurrent \ac{ZKPK}, I must read up 
+    on that (there is a paper by Bellare).}
+\end{proof}
 
@@
   probability \(1\) forever.
-\end{proof}
-
-\begin{proof}[\acs*{DBDH} resistance]
-  The adversary must find a collision of challenges for the honest provers 
-  challenges, so that the verifying equation holds at the end.
 \end{proof}

### 2019-07-16 paper/distance-bounding.tex
Fixes some spacing

--- 2019-06-28 paper/distance-bounding.tex
@@
-\subsection{\Acl*{DB} protocols}%
+\subsection{Distance-bounding protocols}%
 \label{distance-bounding}
@@
     \Ac{DBTF} resistance is a very strong property; it implies that if the 
-    accomplice succeeds (with non-negligible probability) he will learn the 
-    prover's secret key\footnote{%
-      This means that even things like functional encryption will not help.
+    verifier accepts the accomplice with non-negligible probability the 
+    accomplice can compute the prover's secret key\footnote{%
+      This means that even things like functional encryption will not
+      help the adversary.
     }.
@@
 \end{itemize}
-There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
-We will use the framework of \citeauthor{DB-DFKO} with extensions by 
-\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
-\cref{DB-definitions}).
+% There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
-The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-In this context it does not make sense to protect against the verifier as he 
-can easily impersonate the prover as he has a knowledge of his secret key.
-There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-We will work in the latter setting; with a \emph{malicious verifier} who will 
-potentially try to \emph{impersonate the prover} after successful verification.
-
-\subsection{\Acl*{DB} security definitions}%
-\label{DB-definitions}
-
-\dots
+% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
+% Indeed, in this context it does not make sense to protect against the
+% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
+% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
+Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
+The verifier might also try to track the provers and map their identities to 
+their actions, thus we also require strong privacy.
+In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
+\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
+For this paper, we assume the existence of such a protocol. Candidates for such 
+a protocol include modifications of~\cite{ProProx} or~\cite{PROPS} to work for 
+discrete logarithm and to provide general attribute-based anonymous credentials 
+(not restricted to identity-based ones), respectively.

### 2019-07-16 paper/current-crowd-counting.tex
Breaks up related work from crowd counting methods

--- 2018-08-14 paper/RelatedWork.tex
@@
-\section{Related work}%
-\label{RelatedWork}
+\section{Current crowd counting methods}%
+\label{current-crowd-counting}
 
-In this section, we first describe the crowd counting methods that are classically used to estimate the size of a crowd during a protest before reviewing the related work on location proof systems from which our solution \PRIVO is inspired.
-
-\subsection{Crowd counting methods}
-
-The seemingly most commonly used method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
+The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
 This manual method devised in the 1960s relies on aerial pictures of the event.
 The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
-Clearly, this method is prone to errors as it is based on estimates.
-It provides universal verifiability (\cref{UniversalVerif}) since anyone can redo the counting using the same pictures.
-However, it is difficult to achieve individual verifiability (\cref{IndividualVerif}) using this method since it is hard to verify that oneself is indeed in any of the photos\footnote{It is of course possible with very detailed photos, but not currently realistic to do with aerial pictures.}.
-We can argue that it also achieves eligibility (\cref{EligibilityVerif}) if all the photos are taken at the same point in time with no overlap, since then no one can be counted twice.
-Unfortunately, we can only get the peak participation with this method.
-When it comes to spatial and temporal eligibility, we have to rely on pictures (\eg by determining from the pictures themselves when and where the they were taken).
-However, this is prone to cheating --- and subject to a variety of manipulation techniques --- and the best we can do is to employ forensic methods to try to detect any modifications or other attempts of fraud.
-From a privacy perspective, all techniques based on photo or video material are necessarily not privacy-preserving unless the protesters take actions to protect themselves.
-For instance, there is a risk that participants are recognizable from the material if they do not wear masks.
-
-Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd on a selected area.
-Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
-This is similar to the method usually used by police (\eg during the protests in Seoul):
-\blockcquote{2016DemonstrationsInSeoul}{%
-  \textins*{p}olice presume\textins*{d} that, when sitting, six people would fill a space of 3.3 square meters
-  \textelp{}
-  The same area would hold nine or 10 people when standing%
-}.
-This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.
-
-In the computer vision community, there is a body of work on estimating the number of persons in a picture (\eg the work of \citet{NNCrowdCounting}).
-This class of methods requires pictures or video surveillance of the protest location during the entire protest and are thus highly privacy-invasive.
-They are generally based on machine learning techniques, and thus also require a training dataset to work.
-In the work by \cite{NNCrowdCounting}, they actually train and evaluate their algorithm on different scenes, which might make this method easier to use for protesting.
-Universal verifiability (\cref{UniversalVerif}) can be provided with this method, since someone can always recount the participants using the recorded video material.
-Some degree of individual verifiability could also be provided (\cref{IndividualVerif}), if Alice can recognize her own face in the video, but still this might be difficult. 
-Remark also that while automatic face recognition can help verifiability, it has a high impact on privacy.
-In addition, it is difficult (if not impossible) to avoid to count some people twice, thus we cannot argue for eligibility (\cref{EligibilityVerif}).
-In theory, this class of methods will provide an upper bound, whereas our method outputs a lower bound.
-Furthermore, it is also difficult to capture the entire location on video surveillance, which diminishes the argument for an upper bound in practice.
-The spatial and temporal verifiability properties are reduced to those of the video, which should be similar as in our discussion about the verifiability of photos (\ie, using forensic methods).
+Using pictures makes it difficult to get cumulative counts, verify that the pictures have not been manipulated, and to have both privacy and individual verifiability: either one is included in the picture (privacy problem) or not (verifiability problem).
+Similar limitations exist for estimating the number of persons in a picture or video (\eg the work of \cite{NNCrowdCounting} or  CrowdSize~\cite{CrowdSize}).
 
@@
 In this situation it is very difficult to faithfully capture the situation.
-Indeed, even if the scene is taken from different angles, there is the additional problem of not counting people twice.
+Taking pictures from different angles risks double counts.
+Another challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
 
-During the protests in Seoul~\cite{2016DemonstrationsInSeoul}, one physical analytics company tried to estimate the number of participants using their physical analytics technology.
-In a nutshell, this technology scans the MAC addresses emitted from the participants' smartphones during Wi-Fi probe requests.
-However, in order to work this method makes many additional assumptions:
-\blockcquote{2016DemonstrationsInSeoul}{%
-The company presumed that about half of smartphone users usually leave on their Wi-Fi feature on and the other half switch it off, based on a separate survey on smartphone usage. 
-It also assumed that about 20\% of the smartphone signals were repetition from the same device.
-}
-This method cannot provide any verifiability, as we must trust the company on performing the measurements correctly and to be honest about when and where they conducted them.
-In addition, as MAC address randomization is now getting a wider adoption precisely to fight physical tracking, this method will not work any more, although some tracking of smartphones could still be possible~\cite{WhyMACRandomizationIsNotEnough}.
-
-A better proposal would be to use \emph{IMSI catchers} (or the real cell towers of the mobile network) to count unique phones at a location.
-However, there are several problems with this approach.
-First, it will be difficult to register only the participants' phones, as many bystanders will also be counted.
-Thus, it will not be possible to distinguish clearly between the protesters and the counter-protesters.
-Second, since the phone has a unique identifier, participants might be uncomfortable to be registered in association with the event and might thus turn the device off, even though, at least with 5G, the IMSI number will not be transmitted anymore in plaintext.
-%need to cite?
-Finally, there will be limited verifiability, as the data recorder must be trusted to record all data in relation to the protest.
+Counting MAC addresses, as done by a company during the protests in Seoul~\cite{2016DemonstrationsInSeoul} suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.
 
@@
 
-In general for all of the above methods, the more a crowd spreads out, the more difficult it is to determine its size.
-In particular, one of the challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
-These methods also have difficulties capturing the actual attendance of an event (\ie, the cumulative participation, not just the count at a snapshot around the peak).
-
-One of the most closely related work to our scheme is \citet{CrowdCount}, which is a web service that lets Alice create an event such that anyone can submit his location to register that he is in Alice's event.
-This method has the benefit of counting everyone who has declared his presence, not just the count at the snapshot of the pictures.
-However, there is no verification as the service must be trusted to behave honestly, but even then, nothing prevents Bob from submitting more than once (violating eligibility, \cref{EligibilityVerif}).
-Another downside is that the service also requires an Internet connection during the event to register as a participant.
-This makes it prone to some form of denial-of-service attack.
-For instance, if Alice has organized a protest against Grace's regime, who shuts down the cellular network or Internet backbone as a means to censor the protest.
-
+CrowdCount \citet{CrowdCount} is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
 Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
-However, there is no consideration of a potentially adversarial setting and thus no verification or checks on eligibility.
-DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants.
-
-\input{LocationProofs.tex}
+However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
+DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.

### 2019-07-16 paper/intro.tex
Breaks up related work from crowd counting methods

--- 2019-03-01 paper/intro.tex
@@
 
-Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{related-work}).
+Existing methods for crowd-counting vary significantly in terms of approaches.% (we will review them in detail in \cref{current-crowd-counting}).
 Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.
@@
 % First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
-Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{related-work}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{current-crowd-counting}).
 % We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
@@
 In \Cref{system-model}, we describe our system model and summarize the desired 
-properties for crowd counting, followed by a discussion of related work in \cref{related-work}.
-In \Cref{definitions}, we formalize the notion of protest and the desired verifiability and privacy properties, and in \cref{building-blocks}, we give
-the relevant background on the building blocks of our solution.
+properties for crowd counting, followed by a discussion of current 
+crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
+we formalize the notion of protest and the desired verifiability and privacy 
+properties, and in \cref{building-blocks}, we give the relevant background on 
+the building blocks of our solution.
 %
@@
 protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
+We compare it to related work in \cref{related-work}.
 Finally, we discuss limitations and assumptions in \cref{Discussion} and give 

### 2019-07-16 paper/related-work.tex
Adds related work

--- 2019-02-13 paper/related-work.tex
@@
-\section{Related work}%
-\label{related-work}
+\section{Related work}
 
-\subsection{Crowd counting methods}
-\input{crowd-counting-methods.tex}
+Our scheme relates to several other works: the crowd counting methods already 
+described in \cref{current-crowd-counting}, location-proof systems and 
+Sybil-free pseudonym systems.
 
-\subsection{Location proofs}
-\input{location-proofs.tex}
+\paragraph*{Location-proof systems}%
+\label{db-and-lp}
+
+Some \acp{LBS} only grant access to resources to users located at a particular 
+location, thus raising the issue of verifying the position claimed by a 
+particular user.
+In most of the existing schemes, the location of a user (device) is determined 
+by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
+One of the main drawbacks of this approach is that a user can cheat by having 
+her device transmit a false location.
+
+One possible way to counter this threat is to request the device to prove that 
+it really is at the claimed location, which gives rise to the concept of 
+\acp{LP}.
+In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
+a particular location at a specific moment in time.
+\Iac{LPS} is an architecture by which users can obtain \acp{LP} from 
+neighboring witnesses (\eg trusted access points or other users) that can later 
+be shown to verifiers who can check the validity of a particular 
+proof~\cite{luo2010veriplace,zhu2011applaus}.
+Most of the existing approaches to \acp{LP} require the prover and the 
+witnesses to disclose their identities, thus raising many privacy issues such 
+as the possibility of tracing the movements of users of the \ac{LPS}.
+However, some \acp{LPS}, such as PROPS~\cite{PROPS}, exist that provide strong 
+privacy guarantees along with the possibility of verifying the claim of the 
+location.
+
+\CROCUS shares some similarities with PROPS\@.
+The main difference is that \CROCUS operates in a more adverse environment, and 
+can thus not provide any guarantees using the decentralized, untrusted 
+witnesses that PROPS can.
+The incentives to cheat are also bigger and consequently the thresholds for 
+collusion are much higher.
+(The same can be said in comparison to Platin.io\footnote{%
+  URL: \url{https://platin.io}.
+}.)
+CROCUS must also tie the cause to the location proof, to designate the proof 
+to the protest in which the protester participated.
+
+\paragraph*{Sybil-free pseudonym systems}
+
+Our Sybil-free pseudonym system is very similar to that of 
+\textcite{SybilFreePseudonyms}.
+Both are based on the work of \textcite{HowToWinTheCloneWars}.
+We make the same simplification of~\cite{HowToWinTheCloneWars} as 
+\textcite{SybilFreePseudonyms}, but we also require an interactive version.
+Furthermore, our \acp{PK} must be distance bounding.

### 2019-07-16 paper/protest-model.tex
Cuts location proofs in related work

@@
 estimated participation count.
+\daniel{%
+  The strength function can take the size of the time interval into account 
+  too, smaller time intervals around the event yields stronger proofs.
+}
 In general, \(\str\) can be defined as a weighted sum of the proof shares, 

### 2019-07-16 paper/distance-bounding.tex
Improves comments on future DB protocols for DLs

@@
 \ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
-For this paper, we assume the existence of such a protocol. Candidates for such 
-a protocol include modifications of~\cite{ProProx} or~\cite{PROPS} to work for 
-discrete logarithm and to provide general attribute-based anonymous credentials 
-(not restricted to identity-based ones), respectively.
+For this paper, we assume the existence of such a protocol\footnote{%
+  The authors have such a protocol under submission in another venue.
+}.
+There exists \ac{PPK} schemes, \eg~\cite{ProProx}, just not yet for discrete 
+logarithms.

### 2019-09-06 paper/DB-anon-cred.tex
Fix typo in comment: DH -> DBDH acronym
Adds minor text before TF proof.
Adds Bussard-Bagga where relevant

@@
 scheme~\cite{Schnorr}, albeit different from that of 
-\textcite{DistanceBounding} in the original \ac{DB} paper.
-(That protocol was shown to be prone to distance 
+\textcite{DistanceBounding} in the original \ac{DB} paper\footnote{%
+  The \citeauthor{DistanceBounding} protocol was shown to be prone to distance 
   hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
-terrorist fraud.)
+  terrorist fraud.
+} and that of \textcite{Bussard-Bagga}\footnote{%
+  The \citeauthor{Bussard-Bagga} protocol was also shown to be 
+  vulnerable~\cite{Bussard-Bagga-attack}.
+  Although this time, the protocol could not protect against \ac{DBTF} and 
+  \ac{DBDF} as it claimed.
+}.
 We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
@@
 
-  \daniel{\Ac{DH} is kind of adaptive and concurrent \ac{ZKPK}, I must read up 
-    on that (there is a paper by Bellare).}
+  \daniel{\Ac{DBDH} is kind of adaptive and concurrent \ac{ZKPK}, I must read 
+    up on that (there is a paper by Bellare).}
 \end{proof}
+
+The last property is \ac{DBTF}.
 

### 2019-09-06 paper/intro.tex
Adds Bussard-Bagga where relevant

--- 2019-07-02 paper/intro.tex
@@
 
-%\emph{Context.}
-
 \paragraph*{Contributions}
 
-Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
+for \ac{DB}, but which is different from that of \textcite{DistanceBounding} or 
+\textcite{Bussard-Bagga} (DBPK-Log).
 Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
@@
 Brands and Chaum) and \ac{DBTF}.
-More importantly, it is public-key, handles malicious impersonating verifiers.
+More importantly, it is public-key\footnote{%
+  The majority of published works are in the shared-key setting.
+  However, both the protocol by \textcite{DistanceBounding} and that of 
+  \textcite{Bussard-Bagga} are public key.
+}, handles malicious impersonating verifiers.
 Since it is based on the Schnorr protocol, it provides a distance-bounded 

### 2019-09-06 paper/DB-anon-cred.tex
Concurrent ZK is not an issue
Concurrent ZK is a prover running parallel sessions with multiple
verifiers --- our situation is one verifier with multiple provers.
Removes discussion about negligible for MF resistance

@@
   \end{enumerate*}
-
   The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
-  thus \((q + k)^n (kq)^{-n}\) in total.
-  We have that \(k \in \log(\lambda)\), \(q \in \poly[\lambda]\) and it follows 
-  that the success probability is negligible,
-  \[
-    \left( \frac{\log(\lambda) + 
-        \poly[\lambda]}{\log(\lambda)\poly[\lambda]}\right)^n \approx
-    \frac{1}{\log(\lambda)^n} < \frac{1}{\poly[\lambda]}
-  \] for \(n > 2\).
+  thus \[\left(\frac{1}{k}+\frac{1}{q}\right)^n = (q + k)^n (kq)^{-n}\] in 
+  total per protocol session.
 \end{proof}
@@
   \(\alpha\) is also chosen uniformly randomly and is fixed.
-
-  \daniel{\Ac{DBDH} is kind of adaptive and concurrent \ac{ZKPK}, I must read 
-    up on that (there is a paper by Bellare).}
 \end{proof}

### 2019-09-09 paper/DB-anon-cred.tex
Improves DH resistance proof, still needs to compute probability

@@
   \(\Adv_{DBS}^{\text{DH}}(\adv) = X\).
+  % XXX compute DH resistance probability
 \end{theorem}
@@
 \begin{proof}
-  The adversary must find a collision of challenges for the honest prover's 
-  challenges, so that the verifying equation holds at the end.
-  Let \(R, c_1, \dotsc, c_k\) be the transcript of the setup between the honest 
-  verifier and the adversary.
-  Let \(R', c_1', \dotsc, c_k'\) be the transcript of the setup between the 
-  honest verifier and honest prover.
-  The verifier will accept if \(R = g^{s_i'} A^{c_i}\), where \(s_i' = \rho' - 
-    c_i'\alpha'\) is the response by the honest prover computed for his 
-  session, \ie \(\rho = \rho' - c_i'\alpha' + c_i\alpha\).
-  Since the verifier and prover are honest, \(\rho', c_i'\), \(\alpha'\) and 
-  \(c_i\) are chosen uniformly randomly.
-  \(\alpha\) is also chosen uniformly randomly and is fixed.
+  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
+  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
+  \(R' = R\) to not interfere.
+
+  The verifier will choose \(c_1, \dotsc, c_k\).
+  The adversary can send his own \(c_1', \dotsc, c_k'\) to the prover, or let 
+  \(c_1' = c_1, \dotsc, c_k' = c_k\) to not interfere.
+
+  The verifier will send its challenge \(i\), the prover will reply with \(s_i 
+    = \rho - c_i' \alpha\).
+  The verifier will check that \(R' = g^{s_i} A^{c_i}\).
+
+  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
+      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
+      \alpha'}\).
+  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
+  cannot choose \(c_i\).
+  The adversary needs \(\rho' - \rho = c_i \alpha' - c_i' \alpha\).
+  We thus have that \[\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' 
+      = \rho - c_i' \alpha} = X,\]
+  which concludes the proof.
 \end{proof}

### 2019-09-09 paper/DB-anon-cred.tex
Improves typesetting for MF resistance proof

@@
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = (q+k)^n (kq)^{-n}\), where \(k, q\) are as 
-  in \cref{DB-Schnorr}.
+  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{k}+\frac{1}{q}\right)^n\), 
+  where \(k, q\) are as in \cref{DB-Schnorr}.
 \end{theorem}
@@
   The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
-  thus \[\left(\frac{1}{k}+\frac{1}{q}\right)^n = (q + k)^n (kq)^{-n}\] in 
-  total per protocol session.
+  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
+  session.
 \end{proof}

### 2019-09-11 paper/DB-anon-cred.tex
Adds conclusion to DH resistance proof
Minor fixes for formulations

@@
   \item guess which challenge the verifier will use and request the correct 
-    response from the prover, this yields a success with probability 
+    response from the prover, this yields success with probability 
     \(\frac{1}{k}\);
@@
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = X\).
-  % XXX compute DH resistance probability
+  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q}\).
 \end{theorem}
@@
   cannot choose \(c_i\).
-  The adversary needs \(\rho' - \rho = c_i \alpha' - c_i' \alpha\).
-  We thus have that \[\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' 
-      = \rho - c_i' \alpha} = X,\]
+  The adversary needs \(\rho' = \rho - c_i' \alpha + c_i \alpha'\).
+  Let \(\rho'\) and \(c_i'\) be fixed (say 0), then we have that \(\alpha' = 
+    \rho c_i^{-1}\).
+  We thus have that
+  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' = \rho - c_i' 
+      \alpha} = \frac{1}{q}\),
   which concludes the proof.
@@
 The last property is \ac{DBTF}.
-
-\begin{proof}[\acs*{DBTF} resistance]
-  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
-  provers help with non-negligible advantage~\(\epsilon\), \ie the success 
-  probability is \(\frac{1}{2}+\epsilon\).
-  There is chance that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
-  Thus, there is some case for which \(\adv\) knows both responses.
-  In that case \(\adv\) can simply compute the secret and impersonate with 
-  probability \(1\) forever.
-\end{proof}
-
-The protocol is \ac{DBTF}-resistant.
+The protocol is \ac{DBTF} resistant.
 Indeed, if the malicious prover gives both responses to the accomplice, the 
 accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
+And any help will increase the probability of success of future attempts.
+
+\begin{theorem}[\acs*{DBTF} resistance]
+  \dots
+\end{theorem}
+
+\begin{proof}
+  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
+  provers help with non-negligible advantage~\(\epsilon < \frac{1}{2}\), \ie 
+  the success probability is \(\frac{1}{2}+\epsilon\).
+  The probability that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
+  Since \(\epsilon\) is non-negligible, there is some case for which \(\adv\) 
+  knows both responses.
+  In that case \(\adv\) can simply compute the secret and impersonate with 
+  probability \(1\) forever, which contradicts our assumption about 
+  \(\epsilon\).
+\end{proof}
 

### 2019-09-12 paper/DB-anon-cred.tex
Writes up DBSHW to solve DF resistance

@@
 
-\subsection{Achieving \acs*{DBDF} resistance}
+\subsection{\Iacs*{DBDF} resistant protocol}
 
@@
 
-The \ac{DB} phase protects against distance fraud.
-Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
-\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
-Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
+We will now introduce an extended protocol, \(\DBSHW\), which represents the 
+secure hardware implementation.
+\Cref{DBSHW-overview} presents an overview.
+
+\begin{figure*}
+  \centering
+  \small
+  \setlength{\ProtoArrowLength}{0.07\linewidth}
+  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
+    \(\HWprove[g, q, \alpha]\):
+    & &
+    \(\HWverify[g, q, A]\):
+    \\
+    \midrule
+
+    Static \(\sk_P, \cert_P\colon \pk_P = \hat g^{\sk_P}\)
+    &
+    & \(\sk_V, \pk_V = \hat g^{\sk_V}\)\\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\
+
+    \(\cert_P\)
+    & \(\ProtoSendRight{\cert_P}\)
+    & \(k \gets \pk_P^{\sk_V}\)
+    \\
+
+    \(k \gets \pk_V^{\sk_P}\)
+    & \(\ProtoSendLeft{\pk_V}\)
+    & \(\pk_V\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Setup}} \\
+
+    Load \(k\) into \(\UWBPR\)
+    &
+    & Load \(k\) into \(\UWBPR\)
+    \\
+
+    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho} g^{\hat\rho}\)
+    & \(\ProtoSendRight{R}\)
+    & \(\hat A\gets A \pk_P\)
+    \\
+
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
+    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
+    \\
+
+    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
+    &
+    &
+    \\
+
+    \vdots
+    &
+    &
+    \\[-1em]
+
+    \(s_m\gets \rho - c_m\alpha \pmod q\)
+    &
+    &
+    \\
+
+    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
+    &
+    &
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
+
+    \text{Ready}
+    & \ProtoSendRight{\text{Ready}}
+    & \\
+
+    % null
+    & \(\ProtoSendLeft{i}\)
+    & \(i\rgets \{1, \dotsc, m\}\), start clock
+    \\
+
+    Fetch \(s_i, \hat s_i\)
+    & \(\ProtoSendRight{s_i, \hat s_i}\)
+    & Stop clock, record \(\Delta t\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Verification}}
+    \\
+
+    % null
+    &
+    & Accept if \(R =  \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and \(\Delta t 
+      < t_{\max}\).
+    \\
+
+  \end{tabular}
+  \caption{%
+    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
+    \(\PK[\alpha][A = g^\alpha]\).
+    Each transmission (arrow in the diagram) uses \(\UWBPR\).
+    The protocol should be repeated \(n\) times to achieve the desired 
+    soundness and distance-bounding errors.
+  }%
+  \label{DBSHW-overview}
+\end{figure*}
+
+The \(\DBSHW\) secure hardware device must contain a (static) private 
+key~\(\sk_P\) (for the prover, \(\sk_V\) for the verifier) with a digital 
+certificate~\(\cert_P\) (and \(\cert_V\)) for the public key~\(\pk_P\) (and 
+\(\pk_V\)).
+
+\paragraph*{Pre-setup}
+
+The pre-setup phase consists of an authenticated key agreement.
+We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
+agreement protocol based on discrete logarithms can be used.
+The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
+compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
+If the prover's certificate is invalid, the protocol aborts.
+
+\paragraph*{Setup}
+
+The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
+\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
+\(\PK[\alpha, \sk_P][\hat A = g^\alpha \hat g^{\sk_P}]\).
+\daniel{Or is it better to do \(\PK[\alpha, \sk_P][A = g^\alpha \land \hat A = 
+    \hat g^{\sk_P}]\)?}
+They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
+
+The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets g^\rho 
+  \hat g^{\hat\rho}\).
+The verifier computes \(\hat A\gets A \pk_P\), where \(A\) is the value for 
+which the prover must prove knowledge of the discrete logarithm.
+
+The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
+  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
+The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
+  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
+
+\paragraph*{Distance bounding}
+
+The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
+  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
+The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
+Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
+\(\UWBPR\) reply.
+The verifier stops the clock and records the round-trip time~\(\delta t\).
+
+\paragraph*{Verification}
+
+The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
+the round-trip time \(\delta t < t_{\max}\) does not exceed the 
+limit~\(t_{\max}\).
+
+\subsection{\acs*{DBDF} resistance}
+
+This protocol uses the \ac{DBMF} resistance of \(\DBS\) to ensure \ac{DBDF} 
+resistance against a malicious prover.
+The trusted hardware uses the authenticated key agreement to establish the 
+shared secret \(k\), thus a verifier prevents a malicious prover from learning 
+\(k\) --- the main limit of~\cite{UWBPR}.
 

### 2019-09-12 paper/DB-anon-cred.tex
Adds comments that proofs are not using definitions
Changes to m challenges of length l
Instead of k challenges of length k.

@@
     \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
-    & \(c_1\rgets \bin^k, \dotsc, c_k\rgets \bin^k\)
+    & \(\ProtoSendLeft{c_1, \dotsc, c_m}\)
+    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
     \\
@@
 
-    \(s_k\gets \rho - c_k\alpha \pmod q\)
+    \(s_m\gets \rho - c_m\alpha \pmod q\)
     &
@@
     & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, k\}\), start clock
+    & \(i\rgets \{1, \dotsc, m\}\), start clock
     \\
@@
 \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates \(k\) challenges \(c_1\rgets \bin^k, \dotsc, c_k\rgets 
-  \bin^k\) (bit strings of length \(k\)) and sends them to the prover.
+The verifier generates \(m\) challenges \(c_1\rgets \bin^l, \dotsc, c_m\rgets 
+  \bin^l\) (bit strings of length \(l\)) and sends them to the prover.
 The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
-  \dotsc, s_k\gets \rho - c_k\alpha\).
+  \dotsc, s_m\gets \rho - c_m\alpha\).
 This step is the main difference to the original Schnorr protocol: the verifier 
@@
 In the \ac{DB} phase, the prover notifies the verifier that he has computed 
-\(s_1, \dotsc, s_k\).
+\(s_1, \dotsc, s_m\).
 The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
@@
 The main difference between this protocol and the Schnorr protocol is that we 
-have the prover compute responses for \(k\) different challenges, \(c_1, 
-  \dotsc, c_k\).
+have the prover compute responses for \(m\) different challenges, \(c_1, 
+  \dotsc, c_m\).
 However, in the authentication step, the verifier chooses only one of those 
@@
 From the simulator's (and extractor's) perspective, there is no difference 
-whether the verifier first chooses \(k\) and then chooses one of those \(k\) 
+whether the verifier first chooses \(m\) and then chooses one of those \(m\) 
 challenges, or if the verifier chooses the one challenge directly;
-the distribution is the same, \(\frac{k}{n}\times \frac{1}{k} = \frac{1}{n}\).
+the distribution is the same, \(\frac{m}{n}\times \frac{1}{m} = \frac{1}{n}\).
 Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
-protocol with soundness error \(2^{-kn}\) still 
+protocol with soundness error \(2^{-l n}\) still 
 holds~\cite[\eg][]{OnSigmaProtocols}.
-(We note that \(k\), which is also the length of the challenge bit string, must 
+(We note that \(l\), which is also the length of the challenge bit string, must 
 be logarithmic in the security parameter, \(\lambda\), for a malicious 
@@
 
+\daniel{Still intuition, we need to use the formal definition of security 
+  above.}
 \begin{theorem}[\acs*{DBMF} resistance]
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{k}+\frac{1}{q}\right)^n\), 
-  where \(k, q\) are as in \cref{DB-Schnorr}.
+  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
+  where \(m, q\) are as in \cref{DB-Schnorr}.
 \end{theorem}
@@
     response from the prover, this yields success with probability 
-    \(\frac{1}{k}\);
+    \(\frac{1}{m}\);
   \item guess the response, this yields success with probability 
@@
   \end{enumerate*}
-  The total success probability is \(\frac{1}{k} + \frac{1}{q}\) per round, 
-  thus \(\left(\frac{1}{k}+\frac{1}{q}\right)^n\) in total per protocol 
+  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
+  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
   session.
@@
 
+\daniel{Still intuition, we need to use the formal definition of security 
+  above.}
 \begin{theorem}[\acs*{DBDH} resistance]
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q}\).
+  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q^n}\).
 \end{theorem}
@@
 
+\daniel{Still intuition, we need the formal definition of security above.}
 \begin{theorem}[\acs*{DBTF} resistance]
@@
 \(\UWBPR\) reply.
-The verifier stops the clock and records the round-trip time~\(\delta t\).
+The verifier stops the clock and records the round-trip time~\(\Delta t\).
 
@@
 The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
-the round-trip time \(\delta t < t_{\max}\) does not exceed the 
+the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
 limit~\(t_{\max}\).

### 2019-09-12 paper/DB-anon-cred.tex
Changes UWBPR key from \sk to k in DBS protocol
Adds HW TF argument for the additional PK

@@
   \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[\sk, g, q, \alpha, A = g^\alpha]\):
+    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
     & &
-    \(\DBSverify[\sk, g, q, A]\):
+    \(\DBSverify[k, g, q, A]\):
     \\
@@
 
-    Load \(\sk\) into \(\UWBPR\)
+    Load \(k\) into \(\UWBPR\)
     &
-    & Load \(\sk\) into \(\UWBPR\)
+    & Load \(k\) into \(\UWBPR\)
     \\
@@
     Each transmission (arrow in the diagram) uses \(\UWBPR\).
+    The protocol actually proves \(\PK[\alpha, \sk_P][\hat A = g^\alpha 
+      \hat g^{\sk_P}]\).
+    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
+    \ac{DBTF}.
     The protocol should be repeated \(n\) times to achieve the desired 
@@
 
+The hardware device (\DBSHW) could commit \ac{DBTF}\footnote{%
+  Arguably, this should not be an issue since the device is trusted.
+  However, we include this construction because it is a neat way to provide 
+  \ac{DBTF} resistance for this part of the protocol as well.
+  To not have this feature, one simply adds the authenticated key exchange step 
+  to \cref{SchnorrFigure}.
+} by giving the key~\(k\) to a malicious prover --- this would allow that 
+prover to authenticate once.
+To prevent this possibility we include a proof of knowledge of the device's 
+private key~\(\sk_P\), \ie that \(\pk_P = \hat g^{\sk_P}\).
+This way, an accomplice can only pass if he is given both \(k\) and \(\sk_P\).
+
 \subsection{Formal verification}

### 2019-09-20 paper/DB-anon-cred.tex
Changes to \PK{\alpha, \sk: ... \land ...}

@@
 
-    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho} g^{\hat\rho}\)
-    & \(\ProtoSendRight{R}\)
-    & \(\hat A\gets A \pk_P\)
+    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
+    & \(\ProtoSendRight{R, \hat R}\)
+    & \(\hat A\gets \pk_P\)
     \\
@@
     &
-    & Accept if \(R =  \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and \(\Delta t 
-      < t_{\max}\).
+    & Accept if \(R = A^{c_i} g^{s_i}\), \(\hat R =  \hat A^{c_i} \hat g^{\hat 
+        s_i}\) and \(\Delta t < t_{\max}\).
     \\
@@
     Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol actually proves \(\PK[\alpha, \sk_P][\hat A = g^\alpha 
-      \hat g^{\sk_P}]\).
+    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
+      \hat A = \hat g^{\sk_P}]\).
     This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
@@
 \(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
-\(\PK[\alpha, \sk_P][\hat A = g^\alpha \hat g^{\sk_P}]\).
-\daniel{Or is it better to do \(\PK[\alpha, \sk_P][A = g^\alpha \land \hat A = 
-    \hat g^{\sk_P}]\)?}
+\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
 They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
 
-The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets g^\rho 
-  \hat g^{\hat\rho}\).
-The verifier computes \(\hat A\gets A \pk_P\), where \(A\) is the value for 
-which the prover must prove knowledge of the discrete logarithm.
+The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
+  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
+The verifier computes \(\hat A\gets \pk_P\).
 
@@
 
-The verifier checks if \(R = \hat A^{c_i} g^{s_i} \hat g^{\hat s_i}\) and that 
-the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
-limit~\(t_{\max}\).
+The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
+  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
+not exceed the limit~\(t_{\max}\).
 

### 2019-10-16 paper/distance-bounding.tex
Changes DH title to also include DF, since it does
Minor clarification for comment
Fixes some typos

--- 2019-07-02 paper/distance-bounding.tex
@@
 
-We will now define what is means for a protocol to be \ac{DBMF} resistant.
+We will now define what it means for a protocol to be \ac{DBMF} resistant.
 
@@
   The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
-  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins the game is negligible in 
-  the security parameter.
+  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins is negligible in the 
+  security parameter.
 \end{definition}
@@
 
-\daniel{This definition differs slightly from that of 
+\daniel{The following definition differs slightly from that of 
   \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
@@
 
-\paragraph*{\Acl*{DBDH}}
+\paragraph*{\Acl*{DBDH} and \acl*{DBDF}}
 

### 2019-10-16 paper/distance-bounding.tex
Writes up strSimTF definition

@@
 
-\daniel{The following definition differs slightly from that of 
-  \textcite{FormalTerroristFraud}: we use \(m_{k'}\) instead of \(m_k'\).
-  \Ie that the number of messages in \(\sid\) is not required to be the same 
-  and in the same order as in \(\sid'\).}
-
-\begin{definition}[Tainted session, \acs*{DBTF}]\label{TaintedTF}
+\begin{definition}[Tainted session, \acs*{DBTF} 
+  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
   A time-critical round
-  \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\)
-  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
-  verifier, is \emph{tainted} by the round
-  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
+  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
+  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
+  sent by the verifier, is \emph{tainted} by the round
+  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, m'_{k+2l-1})\]
   of a prover--adversary session~\(\sid'\) if
   \begin{align*}
-    \marker[\sid, k] &< \marker[\sid', k'] \\
-    \marker[\sid, k'+1] &> \marker[\sid', k'+1].
+    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
+    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
   \end{align*}
@@
 
-\begin{definition}[strSimTF resistance~\cite{FormalTerroristFraud}]%
+Then we have the following definition of security.
+
+\begin{definition}[SimTF security~\cite{DB-DFKO}]%
   \label{TFresistance}
-  \dots
+  Let \(\DB\) be an authentication scheme for parameters \((t_{\max}, T_{\max}, 
+    E_{\max}, N_c)\).
+  Let \(\adv\) be a \((t, \qv, q_{\F})\)-SimTF adversary, \(\S\) an algorithm 
+  with runtime \(t_{\S}\) and \(\F\) an algorithm with runtime \(t_{\F}\).
+  Let \[
+    \Adv_{\DB}^{\text{TF}}(\adv, \S, \F) = p_{\adv} - p_{\S},
+  \] where \(p_{\adv}\) is the probability that the verifier~\(v\) accepts in 
+  one of the \(\qv\) adversary--verifier sessions~\(\sid\) such that at 
+  \(T_{\max}\) time-critical phases of \(\sid\) are tainted and \(p_{\S}\) is 
+  the probability that, given the state of \(\adv\), \(\S\) authenticates to 
+  the verifier~\(v\) in one of \(\qv\) subsequent executions.
 \end{definition}

### 2019-10-18 paper/DB-anon-cred.tex
Writes up proof for TF resistance

@@
 \begin{theorem}[\acs*{DBTF} resistance]
-  \dots
+  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
+  \(\S\) an algorithm with runtime \(t_{\S}\).
+  If the verifier's challenges are uniformly drawn, then 
+  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
 \end{theorem}
@@
 \begin{proof}
-  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
-  provers help with non-negligible advantage~\(\epsilon < \frac{1}{2}\), \ie 
-  the success probability is \(\frac{1}{2}+\epsilon\).
-  The probability that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
-  Since \(\epsilon\) is non-negligible, there is some case for which \(\adv\) 
-  knows both responses.
-  In that case \(\adv\) can simply compute the secret and impersonate with 
-  probability \(1\) forever, which contradicts our assumption about 
-  \(\epsilon\).
+  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
+  with non-negligible probability~\(\epsilon\) better than guessing, \ie a 
+  success probability of \(\frac{1}{m^n}+\epsilon\).
+  Say that \(\adv\) has successfully authenticated with the prover's help and 
+  \(\S\) is given \(\adv\)'s state.
+
+  Now \(\S\) will use \(\adv\) in a simulation.
+  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
+  choose another challenge uniformly randomly.
+  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
+  independent (uniformly random), the help provided by the prover must be 
+  independent of the chosen challenge.
+  Thus \(\S\) will provide the same help as before.
+
+  When \(S\) has the second response it can compute the secret of the prover 
+  and thus authenticate to the verifier with probability \(p_{\S} = 1\) in any 
+  successive session.
+  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
 \end{proof}

### 2019-10-18 paper/distance-bounding.tex
Minor cosmetic edits

@@
     \Adv_{\DB}^{\text{TF}}(\adv, \S, \F) = p_{\adv} - p_{\S},
-  \] where \(p_{\adv}\) is the probability that the verifier~\(v\) accepts in 
+  \] where \(p_{\adv}\) is the probability that the verifier~\(V\) accepts in 
   one of the \(\qv\) adversary--verifier sessions~\(\sid\) such that at 
@@
   the probability that, given the state of \(\adv\), \(\S\) authenticates to 
-  the verifier~\(v\) in one of \(\qv\) subsequent executions.
+  the verifier~\(V\) in one of \(\qv\) subsequent executions.
 \end{definition}

### 2019-10-21 paper/DB-anon-cred.tex
Minor cosmetic edits
Improves TF resistance proof

@@
 
-\daniel{Still intuition, we need the formal definition of security above.}
+\daniel{Work in progress!}
 \begin{theorem}[\acs*{DBTF} resistance]
@@
   Now \(\S\) will use \(\adv\) in a simulation.
+  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
   Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
-  choose another challenge uniformly randomly.
+  choose another challenge different from before.
   Since \(\adv\) cannot perform a relay to the prover and each challenge is 
@@
   independent of the chosen challenge.
-  Thus \(\S\) will provide the same help as before.
 
-  When \(S\) has the second response it can compute the secret of the prover 
-  and thus authenticate to the verifier with probability \(p_{\S} = 1\) in any 
-  successive session.
+  Now \(\adv\) will provide a correct response with \(\frac{1}{m^n}+\epsilon\) 
+  probability.
+  When \(S\) has the correct response it can compute the secret of the prover 
+  using the two known correct responses and thus authenticate to the verifier 
+  with probability \(p_{\S} = 1\) in any successive session.
   The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
@@
     &
-    & Accept if \(R = A^{c_i} g^{s_i}\), \(\hat R =  \hat A^{c_i} \hat g^{\hat 
-        s_i}\) and \(\Delta t < t_{\max}\).
+    & Accept if \(R = A^{c_i} g^{s_i}\),
+      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
+      \(\Delta t < t_{\max}\).
     \\

### 2019-11-06 paper/DBSchnorr-n-bit.tex
Moves n-bit DBSchnorr to own section, solves l-bit problem

\section{Bit-by-bit distance-bounding Schnorr protocol}%

One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation. 
To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.

\subsection{Reattempting a distance-bounding Schnorr protocol}%
\label{DBSchnorr-n-bit}

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.

\begin{figure*}
  \centering
  \small
  \setlength{\ProtoArrowLength}{0.07\linewidth}
  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

    \multicolumn{3}{c}{\textbf{Setup}} \\

    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
    & \(\ProtoSendRight{R}\)
    &
    \\

    % null
    & \(\ProtoSendLeft{c_0, c_1}\)
    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
    \\

    \(s_0\gets \rho - c_0\alpha \pmod q\)
    &
    & \(b\rgets \bin\)
    \\

    \(s_1\gets \rho - c_1\alpha \pmod q\)
    &
    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
        l, j\gets 0\)} \\

%    % null
%    &
%    & Random delay
%    \\

    % null
    & \(\ProtoSendLeft{b_i}\)
    & \(b_i\gets B[i]\)
    \\

    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
    & \(\ProtoSendRight{r_i}\)
    & Record \(\Delta t_i\)
    \\

    \(j \gets j + b_i\)
    &
    &
    \\

    \midrule
    \multicolumn{3}{c}{\textbf{Verification}}
    \\

    % null
    &
    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
      Accept if \(R = g^{s_b} A^{c_b}\).
    \\

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
This is also different from the original Brands-Chaum protocol, in which the 
prover and verifier jointly construct \emph{one} challenge with \emph{one} 
response.

We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
The verifier will request all \(|q|\) response-bits from one challenge (say 
\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
Then the verifier can authenticate the prover by checking if \(R = 
  g^{s_b}A^{c_b}\).

\subsection{Security analysis}

The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
This allows us to prevent \ac{DBTF}.
Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance. %reducing success of MF according to number of repetitions.
The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.

The intuition behind the protocol security is as follows.
To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
the knowledge error, \(2^{-kn}\), becomes small enough.
Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.

The \ac{DB} phase protects against distance fraud.
Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).

The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
The verifier will send \(|q| + l < 2|q|\) challenges.
By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
  s_1\).
\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
Now, the adversary has two options.
First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
If the adversary requests \(s_b\) in full, the adversary can also guess the 
remaining \(|q|-l\) bits of \(s_{1-b}\).
Based on our assumption above, the probability of guessing these bits 
successfully is \(2^{-(|q|-l)}\).
Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
\(2^{-n}+2^{-(|q|-l)n}\).

The protocol is \ac{DBTF}-resistant. 
Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).

The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
Thus the probability of success is equivalent of a collision for the responses 
for the chosen challenge --- in each round.

Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}

\subsection{The \(l\)-bit problem}

\paragraph*{A special case}

We will start with a special case of the \(l\)-bit problem.
For a session~\(i\), we have two possible responses to the two challenges:
\(s_i = r_i + c\alpha\) and \(s_i' = r_i + c'\alpha\).
Let \(c = 1\) and \(c' = 0\).
We assume that the adversary learns all \(m\) bits of \(s_i\), but only \(l\) 
bits of \(s_i'\).
This special case yields the linear equation system
\begin{align*}
  s_i &= r_i + \alpha
  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha \\
  s_i'[j_1] &= b_{j_1} \\
  s_i'[j_2] &= b_{j_2} \\
  \vdots \\
  s_i'[j_l] &= b_{j_l},
\end{align*}
where \(s_i'[j]\) denotes the \(j\)th bit of \(s_i'\), and \(j_1, \dotsc, 
j_l\in \{0, \dotsc, m-1\}\) are indices for the bits chosen by the adversary 
and \(b_{j_1}, \dotsc, b_{j_l}\in \bin\) are the bit values.

\begin{lemma}
  Assume the special case given above.
  If \(l \leq \frac{m+\frac{1}{n}-1}{2}\), then the equation system is 
  underdetermined and we cannot solve for \(\alpha\).
\end{lemma}
\begin{proof}
  The equation system above yields \(l+1\) equations and \(m-l+1\) unknowns.
  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
  This yields an equation system of \(n(l+1)\) equations and \(n(m-1)+1\) 
  unknowns (the unknown \(\alpha\) is not repeated).
  If \(n(l+1) < n(m-l)+1\), this system is underdetermined and cannot be 
  solved.
  After some rewriting we find that
  \begin{align*}
    n(l+1) &< n(m-l)+1 \\
    n(2l+1) &< nm+1 \\
    2l+1 &< m + \frac{1}{n} \\
    2l &< m + \frac{1}{n} -1 \\
    l &< \frac{m + \frac{1}{n} -1}{2}.
  \end{align*}
  Which concludes the proof.
\end{proof}

The number of possible solutions is vital for us, since that is an estimate of 
how difficult it is for the adversary to guess \(\alpha\).

\begin{lemma}\label{l-bit-advantage}
  Assume the special case above.
  There are \(m-l\) free variables, each taking a value from \(\bin\).
  This yields \(2^{m-l}\) possible solutions for each session.
\end{lemma}
\begin{proof}
  The result directly follows from the fact that there are \(m-l\) free 
  variables.
  Each free variable can only take two possible values (0 or 1), consequently 
  there are \(2^{m-l}\) possible combinations.
\end{proof}

\paragraph*{The general \(l\)-bit problem}

For any choice of \(c\) and \(c'\), we have
\begin{align}
  \label{eqn:general-c}
  s_i &= r_i + c\alpha \\
  \label{eqn:general-cprime}
  s_i' &= r_i + c'\alpha.
\end{align}
We can transform this system of equations into our special case above by 
Gaussian elimination: add \cref{eqn:general-c} multiplied by \(\frac{c'}{c}\) 
to \cref{eqn:general-cprime}.
This proves the following lemma.

\begin{lemma}
  Any choice of \(c, c'\) can be turned into our special case of \(c = 1, c' = 
  0\).
\end{lemma}

This means that \cref{l-bit-advantage} is also true for the general case.

\subsection{Formal Verification}

We wanted to formally verify the protocol security properties. To realize this, 
we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
originally the possibility to reason on time and space in its model.
However, thanks to a recent work by \textcite{TamarinDB}, all the common 
properties mentioned in the previous subsection can be equivalently 
characterized with a causality-based definition relying only on the order of 
messages.

The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
We are currently investigating the Tamarin interactive mode to validate as well the security properties.

### 2019-11-15 paper/DBSchnorr-n-bit.tex
Writes up the most general form of l-bit problem

@@
 
+\paragraph*{The most general \(l\)-bit problem}
+
+We run the protocol \(n\) times and let the adversary learn \(m+l\) bits of the 
+result~\(s_i, s_i'\).
+This yields the following equation system:
+\begin{align*}
+  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha \\
+  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha \\
+  \vdots \\
+  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha \\
+  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha,
+\end{align*}
+where \(m+l\) of \(s_i[j]\)'s and \(s_i'[j']\)'s for each \(i\) are known by 
+the adversary.
+
+\begin{theorem}
+  If \[l < m-1+\frac{1}{n}-\frac{f(\lambda)}{n},\] then there are at least 
+  \(2^{f(\lambda)}\) possible solutions, for some function~\(f\) of the 
+  security parameter~\(\lambda\).
+\end{theorem}
+\begin{proof}
+  Consider one instance of the protocol:
+  \begin{align*}
+    s_i[0]2^0 + \dotsb + s_i[m-1]2^{m-1} &= r_i + c\alpha \\
+    s_i'[0]2^0 + \dotsb + s_i'[m-1]2^{m-1} &= r_i + c'\alpha.
+  \end{align*}
+  This yields \(2m+2\) variables with two equations, thus \(2m\) free variables.
+  Let the adversary learn \(m+l\) of the bits, \ie left-hand side \(s_i[j]\)'s or 
+  \(s_i'[j']\)'s.
+  This leaves \(2m-(m+l) = m-l\) free variables and \(2^{m-l}\) possible 
+  solutions.
+
+  Repeat this \(n\) times.
+  This yields \(n(2m+1)+1\) variables and \(2n\) equations, thus \(2nm+n+1-2n = 
+  2mn - n +1 = n(2m-1)+1\) free variables.
+  Let the adversary learn \(m+l\) bits in each round, thus \(n(m+l)\) in total.
+  This yields \(n(2m-1)+1 -n(m+l) = 2nm-n+1-nm-nl = nm-n+1-nl = n(m-1-l)+1\) 
+  free variables and \(2^{n(m-1-l)+1}\) possible solutions.
+  Consequently, if we want \(f(\lambda)\) possible solutions, we have that
+  \begin{equation*}
+    nm-n-nl+1 > f(\lambda) \iff m-1+\frac{1}{n}-\frac{f(\lambda)}{n} > l.
+  \end{equation*}
+  Which concludes the proof.
+\end{proof}
+
 \subsection{Formal Verification}

### 2019-11-15 paper/DBSchnorr-n-bit.tex
Fixes typos in calculation of simplified l-bit lemma

@@
   Assume the special case given above.
-  If \(l \leq \frac{m+\frac{1}{n}-1}{2}\), then the equation system is 
-  underdetermined and we cannot solve for \(\alpha\).
+  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
+  we cannot solve for \(\alpha\).
 \end{lemma}
 \begin{proof}
-  The equation system above yields \(l+1\) equations and \(m-l+1\) unknowns.
+  The equation system above yields \(l+1\) equations and \(m+1\) variables.
   If we repeat the protocol \(n\) times, we get \(n\) such sessions.
-  This yields an equation system of \(n(l+1)\) equations and \(n(m-1)+1\) 
-  unknowns (the unknown \(\alpha\) is not repeated).
-  If \(n(l+1) < n(m-l)+1\), this system is underdetermined and cannot be 
-  solved.
+  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
+  (\(\alpha\) is not repeated).
+  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
   After some rewriting we find that
   \begin{align*}
-    n(l+1) &< n(m-l)+1 \\
-    n(2l+1) &< nm+1 \\
-    2l+1 &< m + \frac{1}{n} \\
-    2l &< m + \frac{1}{n} -1 \\
-    l &< \frac{m + \frac{1}{n} -1}{2}.
+    n(l+1) &< nm+1 \\
+    l+1 &< m + \frac{1}{n} \\
+    l &< m + \frac{1}{n} -1.
   \end{align*}

### 2019-11-15 paper/DBSchnorr-n-bit.tex
Adds \pmod q, fixes unique solutions (2^x-1)

@@
   s_i &= r_i + \alpha
-  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha \\
-  s_i'[j_1] &= b_{j_1} \\
-  s_i'[j_2] &= b_{j_2} \\
-  \vdots \\
-  s_i'[j_l] &= b_{j_l},
+  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha &\pmod q\\
+  s_i'[j_1] &= b_{j_1} &\pmod 2\\
+  s_i'[j_2] &= b_{j_2} &\pmod 2\\
+            &\vdots \\
+  s_i'[j_l] &= b_{j_l}, &\pmod 2
 \end{align*}
@@
 
-\begin{lemma}\label{l-bit-advantage}
+\begin{lemma}\label{simple-l-bit-advantage}
   Assume the special case above.
   There are \(m-l\) free variables, each taking a value from \(\bin\).
-  This yields \(2^{m-l}\) possible solutions for each session.
+  This yields \(2^{m-l}-1\) unique solutions for each session.
 \end{lemma}
@@
   Each free variable can only take two possible values (0 or 1), consequently 
-  there are \(2^{m-l}\) possible combinations.
+  there are \(2^{m-l}-1\) unique solutions.
 \end{proof}
 
-\paragraph*{The general \(l\)-bit problem}
+\paragraph*{Arbitrarily chosen \(c\neq c'\)}
 
-For any choice of \(c\) and \(c'\), we have
+For any choice of \(c\) and \(c'\) such that \(c\neq c'\), we have
 \begin{align}
   \label{eqn:general-c}
-  s_i &= r_i + c\alpha \\
+  s_i &= r_i + c\alpha &\pmod q\\
   \label{eqn:general-cprime}
-  s_i' &= r_i + c'\alpha.
+  s_i' &= r_i + c'\alpha. &\pmod q
 \end{align}
@@
 to \cref{eqn:general-cprime}.
+The multiplicative inverse \(\frac{1}{c}\) exists since \(q\) is prime.
 This proves the following lemma.
@@
 
-This means that \cref{l-bit-advantage} is also true for the general case.
+This means that \cref{simple-l-bit-advantage} is also true for the general case.
 
-\paragraph*{The most general \(l\)-bit problem}
+\paragraph*{The general \(l\)-bit problem}
 
@@
 \begin{align*}
-  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha \\
-  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha \\
+  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha &\pmod q\\
+  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha &\pmod q\\
   \vdots \\
-  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha \\
-  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha,
+  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha &\pmod q\\
+  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha, &\pmod 
+  q
 \end{align*}
@@
 
-\begin{theorem}
+\begin{lemma}\label{l-bit-advantage}
   If \[l < m-1+\frac{1}{n}-\frac{f(\lambda)}{n},\] then there are at least 
-  \(2^{f(\lambda)}\) possible solutions, for some function~\(f\) of the 
+  \(2^{f(\lambda)}-1\) unique solutions, for some function~\(f\) of the 
   security parameter~\(\lambda\).
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
   \(s_i'[j']\)'s.
-  This leaves \(2m-(m+l) = m-l\) free variables and \(2^{m-l}\) possible 
+  This leaves \(2m-(m+l) = m-l\) free variables and \(2^{m-l}-1\) possible 
   solutions.
@@
   This yields \(n(2m-1)+1 -n(m+l) = 2nm-n+1-nm-nl = nm-n+1-nl = n(m-1-l)+1\) 
-  free variables and \(2^{n(m-1-l)+1}\) possible solutions.
-  Consequently, if we want \(f(\lambda)\) possible solutions, we have that
+  free variables and \(2^{n(m-1-l)+1}-1\) unique solutions.
+  Consequently, if we want at least \(2^{f(\lambda)}-1\) unique solutions, we 
+  have that
   \begin{equation*}

### 2019-12-02 paper/DBSchnorr-n-bit.tex
Adds sketch of l-bit problem with commitments

@@
 
-\paragraph*{The general \(l\)-bit problem}
+\paragraph*{The unconditional \(l\)-bit problem}
 
@@
 
+\paragraph*{The \(l\)-bit problem with commitments}
+
+The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
+g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
+This means that
+\begin{align*}
+  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
+                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
+                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
+\end{align*}
+We will now show that finding \(s'_\text{unknown}\) is as hard as finding 
+discrete logarithms.
+
+\begin{definition}[\Acl*{DLP}]
+  Let \(g\) be a generator for a group of prime order~\(q\).
+  Given \(g, q, A = g^\alpha\), compute \(\alpha\).
+\end{definition}
+
+\begin{definition}[DB-Schnorr Problem]%
+  \label{DBSchnorr-problem}
+  Let \(g\) be a generator for a group of prime order~\(q\).
+  Give \(g, q, R = g^\rho A = g^\alpha\) to the adversary.
+  Let the adversary choose \(c\) and additionally give him \(\hat s\) such that 
+  \(\hat s\) are the \(l\) \emph{least significant} bits of \(s = \rho + 
+  c\alpha \pmod q\).
+  The adversary wins if he returns \(\hat s'\) such that \(\hat s + \hat s' = s 
+  \pmod q\).
+\end{definition}
+
+\begin{lemma}
+  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
+  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
+  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
+  \((1-\frac{1}{2^{X}}) \epsilon\).
+\end{lemma}
+
+\begin{proof}
+  We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
+  \(\algA_{\DBS}\).
+  Given \(g, q, A_{\text{DL}}\):
+%  Let \(\rho\rgets \ZZ_q\), \(c\gets \algA_{\DBS}(R, A_{\DBS})\), where \(R = 
+%  g^\rho\) and \(A_{\DBS} = g^\alpha\).
+  Choose \(s\rgets \ZZ_q\) and let \(\rho\gets s - c\alpha\)
+\end{proof}
+
 \subsection{Formal Verification}

### 2019-12-03 paper/intro.tex
Renames DB-anon-cred to DB-Schnorr-UWB

@@
 
-\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+\Cref{DB-Schnorr-UWB}, we present a new \ac{DB} version of the Schnorr protocol, 
 different from that originally proposed by \textcite{DistanceBounding}.

### 2019-12-05 paper/DBSchnorr-n-bit.tex
Completes proof for DBS -> DL reduction
l-bit: Fixes typo, adds clarification
Adds minor clarifications

@@
     &
-    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
+    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\) and the 
+    remaining \(l\) bits to \(1-b\).
     \\
@@
     One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
+    The protocol should be repeated in full to achieve the desired soundness 
+    and distance-bounding errors.
   }%
@@
   algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
-  \((1-\frac{1}{2^{X}}) \epsilon\).
+  \(\epsilon 2^{-l-k}\).
 \end{lemma}
@@
   We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
-  \(\algA_{\DBS}\).
-  Given \(g, q, A_{\text{DL}}\):
-%  Let \(\rho\rgets \ZZ_q\), \(c\gets \algA_{\DBS}(R, A_{\DBS})\), where \(R = 
-%  g^\rho\) and \(A_{\DBS} = g^\alpha\).
-  Choose \(s\rgets \ZZ_q\) and let \(\rho\gets s - c\alpha\)
+  \(\algA_{\DBS}\) and the \ac{DLP} challenge \(g, q, A_{\text{DL}}\).
+  Assume that \(\algA_{\DBS}\) succeeds with probability \(\epsilon\).
+
+  We proceed as follows.
+  Guess \(c\rgets \ZZ_k\), choose \(\hat s\rgets \ZZ_{2^l}\).
+  Let \(\hat R\gets A_{\DBS}^c A_{\text{DL}} g^{\hat s}\) and give
+  \(\hat R\) to \(\algA_{\DBS}\).
+  If \(c'\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R)\) returns \(c'\neq c\), 
+  abort.
+  The probability of success is \(2^{-k}\).
+  Otherwise, give \(\hat s\) to \(\algA_{\DBS}\).
+  Now, by construction, we have that \(
+    \hat R = A_{\DBS}^c g^{\hat s} A_{\text{DL}}.
+  \)
+
+  If \(A_{\text{DL}} = g^{\alpha_{\text{DL}}}\) is chosen such that 
+  \(\alpha_{\text{DL}}\) has the \(l\) least significant bits set to zero 
+  (probability \(2^{-l}\)), then will have \(
+    \alpha_{\text{DL}}\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R, \hat s)
+  \) with probability \(\epsilon\).
+  Thus, the total probability of success is \(
+    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-l-k}.
+  \)
 \end{proof}

### 2020-02-12 paper/DBSchnorr-n-bit.tex
Minor clarifications for l-bit reduction to DLP
Minor rephrasing about relation between DBSP and DLP

@@
 \end{align*}
-We will now show that finding \(s'_\text{unknown}\) is as hard as finding 
-discrete logarithms.
+We will now show how the hardenss of finding \(s'_\text{unknown}\) relates to 
+the hardness of finding discrete logarithms.
 
@@
   algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
-  \(\epsilon 2^{-l-k}\).
+  \(\epsilon 2^{-(l+k)}\).
 \end{lemma}
@@
   Thus, the total probability of success is \(
-    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-l-k}.
+    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-(l+k)}.
   \)
 \end{proof}
+
+As mentioned above, both \(l\) and \(k\) are logarithmic in the security 
+parameter.
 

### 2020-02-17 paper/lwe.tex
Adds summary of LWE investigation

\mode*

\section{The \acl*{LWE} problem}

The l-bit problem is related to the \ac{LWE} problem.
In the \ac{LWE} problem we have a secret vector \(\vec s \in \ZZ_q^n\).
Given
\begin{align*}
  \langle \vec s, \vec a_i\rangle + \epsilon_i \pmod q,
\end{align*}
where \(\vec a_i \in_R \ZZ_q^n\) is a set of random vectors and \(\epsilon_i 
\in \ZZ_q\) are errors according to some distribution (usually Gaussian), the 
adversary must find \(\vec s\).

The l-bit problem is the case of \(\ZZ_q^1\), \ie with \(n = 1\).
All hardness results depends on \(n\).
This means that the problem becomes easier.
However, the size of the set of equations also depends on \(n\), which brings 
some balance.

However, the major difference is the blinding factor.
The format of the l-bit equations is \(\rho_i + c_i\alpha\) and \(\rho_i + 
c_i'\alpha\), where \(\alpha\) is the secret and \(\rho_i\) is uniformly 
randomly chosen in \(\ZZ_q\) and \(c_i, c_i'\) take the role of \(\vec a\) 
above.
These equations come in pairs with an error that is related between the pair of 
equations.

Considering this, it's hard to map the \ac{LWE} problem to the l-bit problem.

### 2020-02-21 paper/distance-bounding.tex
Improved phrasing for DH and DF
Fixes typo: missing ellipses
Adds definitions for DH/DF from Cristina's model

@@
   sent by the verifier, is \emph{tainted} by the round
-  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, m'_{k+2l-1})\]
+  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, \dotsc, m'_{k+2l-1})\]
   of a prover--adversary session~\(\sid'\) if
@@
 
+The final property is \ac{DBDH} and \ac{DBDF}.
+The following definitions for \ac{DBDH} also captures \ac{DBDF} 
+attacks~\cite{TREAD}.
+We first define what the adversary can and cannot do by defining a tainted 
+session for \ac{DBDH}.
+
 \begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
   \label{TaintedDH}
-  \dots
+  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
+  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
+  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
+  \begin{itemize}
+    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
+      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker{\sid, k} > 
+      \marker{\sid_{\Commit}, j}\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
+      such \(j\) exists).
+
+    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
+      m_{k+1}')\) for \(m_{k+1}' = \Prompt\) satisfies \(m_{k+1} \neq 
+      m_{k+1}^{\Prompt}\), in which \(m_{k+1}^{\Prompt}\) denotes the message 
+      \(m_{k+1}\) in \(\sid_{\Prompt}\).
+  \end{itemize}
 \end{definition}
+
+To win, the adversary must convince a verifier that he is close when he 
+actually is not and without tainting any of the sessions.
 
@@
   \label{DHresistance}
-  \dots
+  For \iac{DB} authentication scheme~\(\DB\) with \ac{DB} threshold 
+  \(t_{\max}\), a \((t, \qp, \qv, \qobs)\)-\ac{DBDH} adversary \(\adv\) wins 
+  against \(\DB\) if the verifier accepts \(\adv\) in one of the \(\qv\) 
+  adversary--verifier sessions without any critical round being tainted.
+  Thus, \ac{DBDH} resistance is defined as the probability 
+  \(\Adv_{\DB}^{\text{DH}}(\adv)\) that \(\adv\) wins the game.
 \end{definition}
-
-These definitions for \ac{DBDH} also captures \ac{DBDF} attacks~\cite{TREAD}.

### 2020-02-25 paper/DBSchnorr-n-bit.tex
Comments out Tamarin spec
removes redundancy of proprox descriptions, frames l-bit problem briefly

@@
 
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
-To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
+As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
+protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
 
@@
 Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
+Thus, we still have information theoretic security for \(s_{1-b}\)
+although we reveal the \(l\) bits. (See \cref{l-bit-problem for an
+  in-depth treatment of what we call the \(l\)-bit problem.)
 
@@
 Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
+\daniel{I should prove this for the composed protocol, I should check
+  the details with Douglas.}
+
+Besides the security against the standard attacks on distance-bounding
+protocols, we also need to ensure that our modification does not leak
+any information to the adversary via the aforementioned \(l\) bits.
 
 \subsection{The \(l\)-bit problem}
+\label{l-bit-problem}
+
+We will now systematically investigate the concern of the adversary
+gaining any advantage from learning \(l\) bits from one of the two challenges.
 
@@
 
+\endinput
 \subsection{Formal Verification}

### 2020-02-25 paper/DBSchnorr-n-bit.tex

@@
 
-We wanted to formally verify the protocol security properties. To realize this, 
-we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
-originally the possibility to reason on time and space in its model.
-However, thanks to a recent work by \textcite{TamarinDB}, all the common 
-properties mentioned in the previous subsection can be equivalently 
-characterized with a causality-based definition relying only on the order of 
-messages.
+We formally verify the protocol security properties using the Tamarin
+prover~\cite{meier2013tamarin}. Tamarin does not originally include
+the possibility to reason on time and space in its model.  However,
+thanks to a recent work by \textcite{TamarinDB}, the common properties
+can be equivalently characterized with a causality-based definition
+relying only on the order of messages.
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we made. 
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
-This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
-We are currently investigating the Tamarin interactive mode to validate as well the security properties.
+Tamarin's auto-prover validated the soundness and correctness
+properties (in negligible computation time) and proved the security
+properties used in~\cite{TamarinDB}. In the meantime,
+\textcite{TamarinDBTF} introduced the notion of post-collusion
+security which enabled them to prove \ac{DBTF}. In future work, we
+will use this extension on our protocol.

### 2020-02-25 paper/conclusions.tex

--- 2018-11-30 paper/conclusions.tex
@@
 
-In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests. 
-Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat.
-Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker.
-For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone.
-This potential difference can thus be considered the price for verifiability.
-Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.
-
-%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
-%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
-}
-%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
-\sonja{update sec analysis results}
-
-%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
-%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
-%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
-
-% In general, none of the related works fulfills the eligibility
-% verifiability (one proof per person, temporal and spatial eligibility ---
-% \cref{%
-%   CountOnce,%
-%   TemporallyRelated,SpatiallyRelated,%
-% }).
-% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
-% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
-% Moreover, if they provided individual verifiability, they would likely violate 
-% the privacy requirements --- if people must recognize themselves in photos, 
-% others can recognize them too.
-% Finally, most of the current methods are estimates, with quite some error margins. 
-While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
-Owing to the network effect, until used by most participants, \CROCUS would result in a considerable undercount. 
-However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
-While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
-We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and counter fake news.
+In this paper, we have adapted the Schnorr protocol as a
+distance-bounding protocol.  It allows to construct distance-bounding
+general attribute-based authentication, more general attributes than
+provided by previous \ac{DB} ones.  With our contribution, Alice can
+now prove more complex statements to Bob; \eg that she is older than
+18 but younger than 40 without revealing her actual age, and at the
+same time Bob can be sure that Alice is not just relaying messages
+from her older sister Carol.

### 2020-02-25 paper/related-work.tex
removes .DS_Store, reinstates conclusions and related work from crocus with only relevant parts included

--- 2019-05-28 paper/related-work.tex
@@
 
-\subsection{Distance bounding}
+One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
 
-One protocol exists in the literature that provides \acp{PPK} with most of the 
-desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
-  that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
-  shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
-logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
-details).
-To realize this, we will now introduce such a protocol to enable us to have 
-\ac{DB} anonymous credentials.
-
-\subsection{Crowd counting methods}
-\input{crowd-counting-methods.tex}
-
-\subsection{Location proofs}
-\input{location-proofs.tex}
+% One protocol exists in the literature that provides \acp{PPK} with most of the 
+% desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
+%   that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
+%   shorter notation.}.
+% ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+%   \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
+% logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
+% details).

### 2020-02-25 paper/DB-Schnorr-UWB.tex
Renames DB-anon-cred to DB-Schnorr-UWB
Retitles DB-Schnorr-UWB to "UWB DB Schnorr protocol"
Comments out Tamarin spec
Improves UWB-MF proof (#9)

--- 2019-10-21 paper/DB-anon-cred.tex
@@
 \section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
-\label{DB-anon-cred}
+\label{DB-Schnorr-UWB}
 
@@
 
-\subsection{\Acl*{ZK} and \acl*{PK}}
+\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}
 
@@
 
-\daniel{Still intuition, we need to use the formal definition of security 
-  above.}
 \begin{theorem}[\acs*{DBMF} resistance]
@@
 \begin{proof}
-  The adversary has two options:
+  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
+  cannot learn anything by observation.
+  This leaves the adversary with two options:
   \begin{enumerate*}
   \item guess which challenge the verifier will use and request the correct 
-    response from the prover, this yields success with probability 
-    \(\frac{1}{m}\);
-  \item guess the response, this yields success with probability 
-    \(\frac{1}{q}\).
+    response from the prover, receiving the challenge first would taint the 
+    session (\cref{TaintedMF});
+  \item guess the response.
   \end{enumerate*}
+  The first option yields success with probability \(\frac{1}{m}\), since the 
+  choice is uniformly distributed.
+  The second option yields success with probability \(\frac{1}{q}\): since the 
+  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
+  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
+  \(\ZZ_q\).
+
   The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 

### 2020-02-25 paper/distance-bounding.tex
Adds intuition behind DH/DF definition

@@
 
+The intuition is that an adversary (malicious, far-away prover) must commit to 
+an action: either respond with an own message, which is determined before 
+seeing the challenge, or to prompt a nearby prover to respond (with a message 
+chosen by the adversary).
+Technically, this adversary can do more than \iac{DBDH} adversary normally can.
+\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
+\(\sid_{\Prompt}\).
+The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
+m'_{k+1})\) in dummy session \(\sid_{\Commit}\).
+If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
+session \(\sid_{\Prompt}\), which is the message the nearby prover will send.
+
 \begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%

### 2020-02-25 paper/DB-Schnorr-UWB.tex
Clarifies comment on Brands-Chaum

@@
 The protocol is also secure against distance hijacking due to the fact that the 
-authenticating bit string is used during the \ac{DB} phase, not the challenge 
-bit string, as is the case for the original protocol of Brands-Chaum.
+authenticating bit string is used during the \ac{DB} phase.
+(Brands-Chaum used the challenge bit string, something that made their protocol 
+vulnerable.)
 \Ac{DBDH} requires that the adversary finds a collision between his response 

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Adds \paragraph to delimit MF, DH, TF proofs
Improves SimTF proof for UWB

@@
 
+\paragraph{\Acl{DBMF}}
+
 The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
@@
 \end{proof}
+
+\paragraph{\Acl{DBDH}}
 
@@
 
+\paragraph{\Acl{DBTF}}
+
 The last property is \ac{DBTF}.
 The protocol is \ac{DBTF} resistant.
-Indeed, if the malicious prover gives both responses to the accomplice, the 
-accomplice can compute his secret key.
+Indeed, if the malicious prover gives more than one response to the accomplice, 
+the accomplice can compute the secret key and, thus, impersonate forever.
 And any help will increase the probability of success of future attempts.
@@
   If the verifier's challenges are uniformly drawn, then 
-  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S}\) is negligible.
+  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} = 0\).
 \end{theorem}
@@
   Assume that the adversary~\(\adv\) can authenticate with the prover's help 
-  with non-negligible probability~\(\epsilon\) better than guessing, \ie a 
-  success probability of \(\frac{1}{m^n}+\epsilon\).
+  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
+  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
+  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
   Say that \(\adv\) has successfully authenticated with the prover's help and 
@@
   choose another challenge different from before.
-  Since \(\adv\) cannot perform a relay to the prover and each challenge is 
-  independent (uniformly random), the help provided by the prover must be 
-  independent of the chosen challenge.
-
-  Now \(\adv\) will provide a correct response with \(\frac{1}{m^n}+\epsilon\) 
-  probability.
-  When \(S\) has the correct response it can compute the secret of the prover 
-  using the two known correct responses and thus authenticate to the verifier 
-  with probability \(p_{\S} = 1\) in any successive session.
-  The same is true for \(\adv\) and thus \(p_{\adv} = p_{\S}\).
+  Since \(\adv\) cannot perform a relay to the prover without tainting the 
+  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
+  provided by the prover must be independent from the chosen challenge.
+  Now \(\adv\) will provide a correct response with probability~\(p_{\adv}\).
+  Hence, \(p_{\S} = p_{\adv}\).
 \end{proof}

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Adds a result about the maximum advantage of any TF adversary (UWB)

@@
 
+However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
+\(m p_{\adv}\) responses.
+Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
+correct responses and \(p_{\S} = 1\) for any successive authentication.
+This contradicts that the key is not leaked.
+Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
+secret leaks.
+This proves the following theorem.
+
+\begin{theorem}
+  The maximum advantage over random guessing for any \ac{DBTF} adversary is 
+  strictly less than \(\frac{1}{m}\) per round.
+\end{theorem}
+
 \subsection{\Iacs*{DBDF} resistant protocol}

### 2020-02-26 paper/DB-Schnorr-UWB.tex
Perfects the SimTF UWB proof
Includes the advantage and that it's negligible in the main TF theorem.

--- 2020-02-26 paper/DB-Schnorr-UWB.tex
@@
   If the verifier's challenges are uniformly drawn, then 
-  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} = 0\).
+  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \frac{1}{m^n}\).
 \end{theorem}
@@
   provided by the prover must be independent from the chosen challenge.
-  Now \(\adv\) will provide a correct response with probability~\(p_{\adv}\).
-  Hence, \(p_{\S} = p_{\adv}\).
+  Now \(\adv\) will again provide a correct response with 
+  probability~\(p_{\adv}\).
+
+  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
+  \(m p_{\adv}\) responses.
+  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
+  correct responses and, thus, \(p_{\S} = 1\) for any successive 
+  authentication.
+  This would also make \(p_{\adv} = 1\).
+  This contradicts that the secret is not leaked.
+  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
+  secret leaks.
+  This makes the \ac{DBTF} advantage negligible.
 \end{proof}

### 2020-02-26 paper/related-work.tex
adds hobbits and Chaum to related work, updates tamarin text

@@
 \label{related-work}
+
+\textcite{DistanceBounding} were the first to adapt the Schnorr
+protocol to achieve distance-bounding anonymous credentials. Their
+approach has been shown to be vulnerable to \ac{DBDH} \cite{TamarinDB}.
+
+  The Bussard-Bagga protocol also uses Schnorr, but slightly
+  differently. It generates a sesson key, encrypts the private key
+  with this session key. Then commits to each bit of the session key
+  and each bit of the ciphertext.
+During the fast phase the verifier requests some bits from the session key and some from the ciphertext.
+Terrorist fraud is based on that knowing both session key and ciphertext one can compute the private key.
+The prover then opens the commits, the verifier verifies them.
+The prover and verifier run a PK that ties the commits to the private key.
+A malicious prover can reduce all the N challenges in the fast phase
+to 1. This allows both distance and terrorist
+fraud~\cite{AttacksBussardBagga}.
 

### 2020-02-26 paper/DBSchnorr-n-bit.tex
Fixes missing } for a \cref

@@
 Thus, we still have information theoretic security for \(s_{1-b}\)
-although we reveal the \(l\) bits. (See \cref{l-bit-problem for an
+although we reveal the \(l\) bits. (See \cref{l-bit-problem} for an
   in-depth treatment of what we call the \(l\)-bit problem.)
@@
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we made. 
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

### 2020-02-26 paper/distance-bounding.tex
Fixes typos in DH definition

@@
 The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
-m'_{k+1})\) in dummy session \(\sid_{\Commit}\).
+m'_{k+1})\) in dummy session \(\sid_{\Commit}\) before receiving the challenge 
+in message \(k\) in session \(\sid\) (making message \(k+1\) in \(\sid\) his 
+response to the challenge).
 If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
@@
     \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
-      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker{\sid, k} > 
-      \marker{\sid_{\Commit}, j}\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
+      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker[\sid, k] > 
+      \marker[\sid_{\Commit}, j]\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
       such \(j\) exists).

### 2020-02-27 paper/DB-Schnorr-UWB.tex
Removes WIP on TF resistance UWB
Updates SimTF UWB result
Updates proof for DH UWB slightly (clarifications)
Finalizes UWB DH proof

@@
 
-\daniel{Still intuition, we need to use the formal definition of security 
-  above.}
-\begin{theorem}[\acs*{DBDH} resistance]
+\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q^n}\).
+  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
 \end{theorem}
@@
   The verifier will choose \(c_1, \dotsc, c_k\).
-  The adversary can send his own \(c_1', \dotsc, c_k'\) to the prover, or let 
-  \(c_1' = c_1, \dotsc, c_k' = c_k\) to not interfere.
+  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
+  is his \enquote{private key}\footnote{%
+    In Schnorr's original protocol this was called the private key.
+    But in our general use, it's the discrete logarithm for which the prover 
+    wants to prove knowledge.
+  }.
+  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
+  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
+  If the adversary didn't choose \(R'\), he can only guess the values for 
+  \(s_i'\).
 
-  The verifier will send its challenge \(i\), the prover will reply with \(s_i 
-    = \rho - c_i' \alpha\).
-  The verifier will check that \(R' = g^{s_i} A^{c_i}\).
+  Now the adversary has two options:
+  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.
 
-  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
-      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
-      \alpha'}\).
-  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
-  cannot choose \(c_i\).
-  The adversary needs \(\rho' = \rho - c_i' \alpha + c_i \alpha'\).
-  Let \(\rho'\) and \(c_i'\) be fixed (say 0), then we have that \(\alpha' = 
-    \rho c_i^{-1}\).
+  If the adversary \(\Commit\)s:
+  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
+  = \rho' - c_i \alpha'\) for all \(i\).
+  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
+  choice \(j\).
+  The probability of committing to the right one is \(\frac{1}{m}\).
+  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
+  the probability of success is \(\frac{1}{q}\) --- since he must guess 
+  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
+  might just as well guess the final outcome (\(\frac{1}{q}\)).
+  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
+  The success of committing is \(\frac{1}{m}\).
+
+  If the adversary \(\Prompt\)s:
+  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
+  \enquote{public key}\footnote{%
+    In Schnorr's original protocol this was a public key.
+    In our more general use, it is the value for which the adversary wants to 
+    prove knowledge of a discrete logarithm.
+  } of the adversary.
+  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
+  - c_i \alpha + c_i \alpha'}\).
+  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
+  accept if \(\alpha = \alpha'\), the probability for which is 
+  \(\frac{1}{q^2}\).
+  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
+  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
+  \frac{1}{q}\).
+
+  Obviously, the better strategy for the adversary is to choose \(R' = 
+  g^{\rho'}\).
+  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
+  \(\Prompt\) (\ac{DBDH}).
   We thus have that
-  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' = \rho - c_i' 
-      \alpha} = \frac{1}{q}\),
+  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
   which concludes the proof.
@@
 
-\daniel{Work in progress!}
 \begin{theorem}[\acs*{DBTF} resistance]
@@
   If the verifier's challenges are uniformly drawn, then 
-  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \frac{1}{m^n}\).
+  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
 \end{theorem}
@@
   secret leaks.
-  This makes the \ac{DBTF} advantage negligible.
 \end{proof}

### 2020-03-03 paper/DB-Schnorr-UWB.tex
Improves UWB section text

@@
 mutual-trust case, where the prover and verifier have a pre-shared secret.
-Then we will adapt it by introducing \iac{AKE}.
+Then we will adapt it by introducing \iac{AKE} protocol.
 The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
@@
 while we authenticate the key.
-This allows us to embed this protocol into tamper resistant hardware to provide 
-security against malicious provers.
+This allows us to embed this protocol into tamper resistant hardware to remove 
+the mutual-trust requirement.
 
@@
 
-Thanks to \textcite{UWBPR} we can keep the Schnorr protocol 
-almost as is, relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical 
-layer.
+Thanks to \textcite{UWBPR} we can keep the Schnorr protocol almost as is, since 
+relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical layer.
+\Ac{DBDF} is not a concern either, since the prover is trusted.
 The only concern, for now, is \acl{DBTF}.
-(We deal with \acl{DBDF} later.)
+(However, we will still prove those properties, as they will be useful later.)
 
@@
 
+\paragraph{\Acl{DBTF}}
+
+The protocol is \ac{DBTF} resistant.
+Indeed, if the malicious prover gives more than one response to the accomplice, 
+the accomplice can compute the secret key and, thus, impersonate forever.
+And any help will increase the probability of success of future attempts.
+
+\begin{theorem}[\acs*{DBTF} resistance]
+  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
+  \(\S\) an algorithm with runtime \(t_{\S}\).
+  If the verifier's challenges are uniformly drawn, then 
+  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
+\end{theorem}
+
+\begin{proof}
+  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
+  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
+  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
+  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
+  Say that \(\adv\) has successfully authenticated with the prover's help and 
+  \(\S\) is given \(\adv\)'s state.
+
+  Now \(\S\) will use \(\adv\) in a simulation.
+  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
+  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
+  choose another challenge different from before.
+  Since \(\adv\) cannot perform a relay to the prover without tainting the 
+  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
+  provided by the prover must be independent from the chosen challenge.
+  Now \(\adv\) will again provide a correct response with 
+  probability~\(p_{\adv}\).
+
+  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
+  \(m p_{\adv}\) responses.
+  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
+  correct responses and, thus, \(p_{\S} = 1\) for any successive 
+  authentication.
+  This would also make \(p_{\adv} = 1\).
+  This contradicts that the secret is not leaked.
+  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
+  secret leaks.
+\end{proof}
+
 \paragraph{\Acl{DBDH}}
@@
 
-\paragraph{\Acl{DBTF}}
-
-The last property is \ac{DBTF}.
-The protocol is \ac{DBTF} resistant.
-Indeed, if the malicious prover gives more than one response to the accomplice, 
-the accomplice can compute the secret key and, thus, impersonate forever.
-And any help will increase the probability of success of future attempts.
-
-\begin{theorem}[\acs*{DBTF} resistance]
-  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
-  \(\S\) an algorithm with runtime \(t_{\S}\).
-  If the verifier's challenges are uniformly drawn, then 
-  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
-\end{theorem}
-
-\begin{proof}
-  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
-  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
-  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
-  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
-  Say that \(\adv\) has successfully authenticated with the prover's help and 
-  \(\S\) is given \(\adv\)'s state.
-
-  Now \(\S\) will use \(\adv\) in a simulation.
-  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
-  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
-  choose another challenge different from before.
-  Since \(\adv\) cannot perform a relay to the prover without tainting the 
-  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
-  provided by the prover must be independent from the chosen challenge.
-  Now \(\adv\) will again provide a correct response with 
-  probability~\(p_{\adv}\).
-
-  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
-  \(m p_{\adv}\) responses.
-  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
-  correct responses and, thus, \(p_{\S} = 1\) for any successive 
-  authentication.
-  This would also make \(p_{\adv} = 1\).
-  This contradicts that the secret is not leaked.
-  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
-  secret leaks.
-\end{proof}
-
-\subsection{\Iacs*{DBDF} resistant protocol}
+\subsection{From mutual trust to \acs*{PKI}}
 
 \Acl{DB} protocols requires hardware implementations.
-We will use a trusted hardware implementation to overcome the limitation of 
-\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
+We will use a \emph{trusted} hardware implementation to overcome the limitation 
+of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
 We will need \iac{PKI} for the verifier to verify the trusted hardware.
-We will leverage this \ac{PKI} to overcome the shared-key requirement.
+We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
+any two devices in this \ac{PKI} to perform \acl{DB}.
 With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 

### 2020-03-03 paper/DB-Schnorr-UWB.tex
Fixes order of properties in section title
Reorders UWB: puts proofs last

@@
 
+\subsection{From mutual trust to \acs*{PKI}}
+
+All \acl{DB} protocols requires hardware 
+implementations~\cite{DBonSmartphones}.
+We will use a \emph{trusted} hardware implementation to overcome the limitation 
+of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
+We will need \iac{PKI} for the verifier to verify the trusted hardware.
+We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
+any two devices in this \ac{PKI} to perform \acl{DB}.
+With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
+\ac{ZKPK} which \emph{simultaneously} proves
+\begin{enumerate*}
+\item that the protocol is run by trusted hardware,
+\item that that trusted hardware is within proximity,
+\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
+\item that that knowledge is within proximity.
+\end{enumerate*}
+
+We will now introduce an extended protocol, \(\DBSHW\), which represents the 
+secure hardware implementation.
+The \ac{PKI} is based on CL04~\cite{CLsignatures} signatures.
+\Cref{DBSHW-overview} presents an overview.
+
+\begin{figure*}
+  \centering
+  \small
+  \setlength{\ProtoArrowLength}{0.07\linewidth}
+  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
+    \(\HWprove[g, q, \alpha]\):
+    & &
+    \(\HWverify[g, q, A]\):
+    \\
+    \midrule
+
+    \multicolumn{2}{l}{%
+      Static \(\hat g, \hat q, \sk_P\in \ZZ_q, \pk_P = \hat g^{\sk_P}, \sigma\)
+    }
+    & Static \(\hat g, \hat q\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\
+
+    \(x\rgets \ZZ_q\)
+    & \(\ProtoSendRight{g^x}\)
+    & \(k \gets \pk_P^{\sk_V}\)
+    \\
+
+    \(k \gets \pk_V^{\sk_P}\)
+    & \(\ProtoSendLeft{\pk_V}\)
+    & \(\pk_V\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Setup}} \\
+
+    Load \(k\) into \(\UWBPR\)
+    &
+    & Load \(k\) into \(\UWBPR\)
+    \\
+
+    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
+    & \(\ProtoSendRight{R, \hat R}\)
+    & \(\hat A\gets \pk_P\)
+    \\
+
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
+    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
+    \\
+
+    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
+    &
+    &
+    \\
+
+    \vdots
+    &
+    &
+    \\[-1em]
+
+    \(s_m\gets \rho - c_m\alpha \pmod q\)
+    &
+    &
+    \\
+
+    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
+    &
+    &
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
+
+    \text{Ready}
+    & \ProtoSendRight{\text{Ready}}
+    & \\
+
+    % null
+    & \(\ProtoSendLeft{i}\)
+    & \(i\rgets \{1, \dotsc, m\}\), start clock
+    \\
+
+    Fetch \(s_i, \hat s_i\)
+    & \(\ProtoSendRight{s_i, \hat s_i}\)
+    & Stop clock, record \(\Delta t\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Verification}}
+    \\
+
+    % null
+    &
+    & Accept if \(R = A^{c_i} g^{s_i}\),
+      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
+      \(\Delta t < t_{\max}\).
+    \\
+
+  \end{tabular}
+  \caption{%
+    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
+    \(\PK[\alpha][A = g^\alpha]\).
+    Each transmission (arrow in the diagram) uses \(\UWBPR\).
+    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
+      \hat A = \hat g^{\sk_P}]\).
+    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
+    \ac{DBTF}.
+    The protocol should be repeated \(n\) times to achieve the desired 
+    soundness and distance-bounding errors.
+  }%
+  \label{DBSHW-overview}
+\end{figure*}
+
+The \(\DBSHW\) secure hardware device must contain a (static) private 
+key~\(\sk_P\) for the prover with a digital certificate~\(\cert_P\) (and 
+\(\cert_V\)) for the public key~\(\pk_P\) (and \(\pk_V\)).
+
+\paragraph*{Pre-setup}
+
+The pre-setup phase consists of an authenticated key agreement.
+We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
+agreement protocol based on discrete logarithms can be used.
+The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
+compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
+If the prover's certificate is invalid, the protocol aborts.
+
+\paragraph*{Setup}
+
+The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
+\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
+\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
+They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
+
+The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
+  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
+The verifier computes \(\hat A\gets \pk_P\).
+
+The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
+  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
+The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
+  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
+
+\paragraph*{Distance bounding}
+
+The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
+  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
+The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
+Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
+\(\UWBPR\) reply.
+The verifier stops the clock and records the round-trip time~\(\Delta t\).
+
+\paragraph*{Verification}
+
+The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
+  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
+not exceed the limit~\(t_{\max}\).
+
 \subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}
@@
 
-\subsection{\acs*{DBMF}, \acs*{DBDH} and \acs*{DBTF} resistance}
+\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}
 
@@
 
-\subsection{From mutual trust to \acs*{PKI}}
-
-\Acl{DB} protocols requires hardware implementations.
-We will use a \emph{trusted} hardware implementation to overcome the limitation 
-of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
-We will need \iac{PKI} for the verifier to verify the trusted hardware.
-We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
-any two devices in this \ac{PKI} to perform \acl{DB}.
-With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
-\ac{ZKPK} which \emph{simultaneously} proves
-\begin{enumerate*}
-\item that the protocol is run by trusted hardware,
-\item that that trusted hardware is within proximity,
-\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
-\item that that knowledge is within proximity.
-\end{enumerate*}
-
-We will now introduce an extended protocol, \(\DBSHW\), which represents the 
-secure hardware implementation.
-\Cref{DBSHW-overview} presents an overview.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\HWprove[g, q, \alpha]\):
-    & &
-    \(\HWverify[g, q, A]\):
-    \\
-    \midrule
-
-    Static \(\sk_P, \cert_P\colon \pk_P = \hat g^{\sk_P}\)
-    &
-    & \(\sk_V, \pk_V = \hat g^{\sk_V}\)\\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\
-
-    \(\cert_P\)
-    & \(\ProtoSendRight{\cert_P}\)
-    & \(k \gets \pk_P^{\sk_V}\)
-    \\
-
-    \(k \gets \pk_V^{\sk_P}\)
-    & \(\ProtoSendLeft{\pk_V}\)
-    & \(\pk_V\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
-
-    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
-    & \(\ProtoSendRight{R, \hat R}\)
-    & \(\hat A\gets \pk_P\)
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
-    \\
-
-    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \vdots
-    &
-    &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
-    &
-    &
-    \\
-
-    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
-
-    % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
-    \\
-
-    Fetch \(s_i, \hat s_i\)
-    & \(\ProtoSendRight{s_i, \hat s_i}\)
-    & Stop clock, record \(\Delta t\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Accept if \(R = A^{c_i} g^{s_i}\),
-      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
-      \(\Delta t < t_{\max}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
-    \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
-      \hat A = \hat g^{\sk_P}]\).
-    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
-    \ac{DBTF}.
-    The protocol should be repeated \(n\) times to achieve the desired 
-    soundness and distance-bounding errors.
-  }%
-  \label{DBSHW-overview}
-\end{figure*}
-
-The \(\DBSHW\) secure hardware device must contain a (static) private 
-key~\(\sk_P\) (for the prover, \(\sk_V\) for the verifier) with a digital 
-certificate~\(\cert_P\) (and \(\cert_V\)) for the public key~\(\pk_P\) (and 
-\(\pk_V\)).
-
-\paragraph*{Pre-setup}
-
-The pre-setup phase consists of an authenticated key agreement.
-We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
-agreement protocol based on discrete logarithms can be used.
-The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
-compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
-If the prover's certificate is invalid, the protocol aborts.
-
-\paragraph*{Setup}
-
-The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
-\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
-\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
-They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
-
-The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
-  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
-The verifier computes \(\hat A\gets \pk_P\).
-
-The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
-The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
-  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
-
-\paragraph*{Distance bounding}
-
-The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
-  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
-The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
-Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
-\(\UWBPR\) reply.
-The verifier stops the clock and records the round-trip time~\(\Delta t\).
-
-\paragraph*{Verification}
-
-The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
-  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
-not exceed the limit~\(t_{\max}\).
-
 \subsection{\acs*{DBDF} resistance}

### 2020-03-03 paper/DB-Schnorr-UWB.tex
Removes formal verification for UWB

@@
 This way, an accomplice can only pass if he is given both \(k\) and \(\sk_P\).
-
-\subsection{Formal verification}
-
-We formally verified these properties with Tamarin~\cite{meier2013tamarin}.
-Thanks to recent work by \textcite{TamarinDB}, all the common properties for 
-\ac{DB} protocols (except \ac{DBTF}) can be characterized with a 
-causality-based definition relying only on the order of messages.
-The whole Tamarin specification for our protocol is provided in 
-\cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that 
-we have made.
-It contains a specification of the distance-bounding protocol described 
-previously, a definition of the soundness and correctness properties that 
-ensure the protocol actually produces the expected result, and a definition of 
-the security properties we want to ensure.

### 2020-03-04 paper/DB-Schnorr-UWB.tex
Starts adapting UWB-AKE for DAA/CL04
Reorders UWB again, improves DBSHW overview

@@
 mutual-trust case, where the prover and verifier have a pre-shared secret.
-Then we will adapt it by introducing \iac{AKE} protocol.
-The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
-\ac{ZKPK} for discrete logarithms.
-If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
+Then we will adapt it by introducing \iac{PKI}.
+We will use this \ac{PKI} to create \iac{AKE} which leverages that our protocol 
+is \iac{DB} \ac{ZKPK} for discrete logarithms.
+If the \ac{PKI} is based on discrete logarithms we can prove the distance bound 
 while we authenticate the key.
-This allows us to embed this protocol into tamper resistant hardware to remove 
-the mutual-trust requirement.
+This turns the mutual-trust by shared-key into mutual trust by 
+\ac{PKI}.
 
@@
 This protocol must be repeated \(n\) times.
-
-\subsection{From mutual trust to \acs*{PKI}}
-
-All \acl{DB} protocols requires hardware 
-implementations~\cite{DBonSmartphones}.
-We will use a \emph{trusted} hardware implementation to overcome the limitation 
-of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
-We will need \iac{PKI} for the verifier to verify the trusted hardware.
-We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
-any two devices in this \ac{PKI} to perform \acl{DB}.
-With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
-\ac{ZKPK} which \emph{simultaneously} proves
-\begin{enumerate*}
-\item that the protocol is run by trusted hardware,
-\item that that trusted hardware is within proximity,
-\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
-\item that that knowledge is within proximity.
-\end{enumerate*}
-
-We will now introduce an extended protocol, \(\DBSHW\), which represents the 
-secure hardware implementation.
-The \ac{PKI} is based on CL04~\cite{CLsignatures} signatures.
-\Cref{DBSHW-overview} presents an overview.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\HWprove[g, q, \alpha]\):
-    & &
-    \(\HWverify[g, q, A]\):
-    \\
-    \midrule
-
-    \multicolumn{2}{l}{%
-      Static \(\hat g, \hat q, \sk_P\in \ZZ_q, \pk_P = \hat g^{\sk_P}, \sigma\)
-    }
-    & Static \(\hat g, \hat q\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\
-
-    \(x\rgets \ZZ_q\)
-    & \(\ProtoSendRight{g^x}\)
-    & \(k \gets \pk_P^{\sk_V}\)
-    \\
-
-    \(k \gets \pk_V^{\sk_P}\)
-    & \(\ProtoSendLeft{\pk_V}\)
-    & \(\pk_V\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
-
-    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
-    & \(\ProtoSendRight{R, \hat R}\)
-    & \(\hat A\gets \pk_P\)
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
-    \\
-
-    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \vdots
-    &
-    &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
-    &
-    &
-    \\
-
-    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
-
-    % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
-    \\
-
-    Fetch \(s_i, \hat s_i\)
-    & \(\ProtoSendRight{s_i, \hat s_i}\)
-    & Stop clock, record \(\Delta t\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Accept if \(R = A^{c_i} g^{s_i}\),
-      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
-      \(\Delta t < t_{\max}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
-    \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
-      \hat A = \hat g^{\sk_P}]\).
-    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
-    \ac{DBTF}.
-    The protocol should be repeated \(n\) times to achieve the desired 
-    soundness and distance-bounding errors.
-  }%
-  \label{DBSHW-overview}
-\end{figure*}
-
-The \(\DBSHW\) secure hardware device must contain a (static) private 
-key~\(\sk_P\) for the prover with a digital certificate~\(\cert_P\) (and 
-\(\cert_V\)) for the public key~\(\pk_P\) (and \(\pk_V\)).
-
-\paragraph*{Pre-setup}
-
-The pre-setup phase consists of an authenticated key agreement.
-We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
-agreement protocol based on discrete logarithms can be used.
-The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
-compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
-If the prover's certificate is invalid, the protocol aborts.
-
-\paragraph*{Setup}
-
-The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
-\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
-\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
-They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
-
-The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
-  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
-The verifier computes \(\hat A\gets \pk_P\).
-
-The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
-The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
-  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
-
-\paragraph*{Distance bounding}
-
-The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
-  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
-The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
-Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
-\(\UWBPR\) reply.
-The verifier stops the clock and records the round-trip time~\(\Delta t\).
-
-\paragraph*{Verification}
-
-The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
-  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
-not exceed the limit~\(t_{\max}\).
 
@@
 
-\subsection{\acs*{DBDF} resistance}
+\subsection{From mutual trust to \acs*{PKI}}
 
-This protocol uses the \ac{DBMF} resistance of \(\DBS\) to ensure \ac{DBDF} 
-resistance against a malicious prover.
-The trusted hardware uses the authenticated key agreement to establish the 
-shared secret \(k\), thus a verifier prevents a malicious prover from learning 
-\(k\) --- the main limit of~\cite{UWBPR}.
+All \acl{DB} protocols requires hardware 
+implementations~\cite{DBonSmartphones}.
+We will use a \emph{trusted} hardware implementation to overcome the limitation 
+of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
+We will need \iac{PKI} for the verifier to verify the trusted hardware.
+We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
+any two devices in this \ac{PKI} to perform \acl{DB}.
+With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
+\ac{ZKPK} which \emph{simultaneously} proves
+\begin{enumerate*}
+\item that the protocol is run by trusted hardware,
+\item that that trusted hardware is within proximity,
+\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
+\item that that knowledge is within proximity.
+\end{enumerate*}
 
-The hardware device (\DBSHW) could commit \ac{DBTF}\footnote{%
-  Arguably, this should not be an issue since the device is trusted.
-  However, we include this construction because it is a neat way to provide 
-  \ac{DBTF} resistance for this part of the protocol as well.
-  To not have this feature, one simply adds the authenticated key exchange step 
-  to \cref{SchnorrFigure}.
-} by giving the key~\(k\) to a malicious prover --- this would allow that 
-prover to authenticate once.
-To prevent this possibility we include a proof of knowledge of the device's 
-private key~\(\sk_P\), \ie that \(\pk_P = \hat g^{\sk_P}\).
-This way, an accomplice can only pass if he is given both \(k\) and \(\sk_P\).
+We will now introduce an extended protocol, \(\DBSHW\), which represents the 
+secure hardware implementation.
+\Cref{DBSHW-overview} presents an overview of our protocol.
+For simplicity of exposition, we present a \ac{PKI} based on plain 
+CL04~\cite{CLsignatures} signatures.
+However, CL04 is the base for the \ac{DAA} protocol, which is used for 
+\ac{TPM}, so our approach can make \ac{DAA} \acl{DB}.
+
+In summary, the difference is as follows.
+\(\DBS\) has a shared key~\(k\) and performs \(
+  \PK[\alpha][A = g^\alpha]
+\) with a distance bound.
+\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
+\hat g^{xy}\) from \(X = \hat g^x, Y = \hat g^y\), then performs \[
+  \PK[\alpha, x, \sk_P, \sigma][
+    A = g^\alpha \land
+    X = \hat g^x \land
+    \Blind[\sigma] = \Sign[_\sk][\sk_P]
+  ],
+\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
+\(\sigma\) is a signature issued with signing key~\(sk\) and \(\Blind\) 
+reblinds a signature.
+Proving knowledge of \(x\) prevents any \ac{MITM} attack against the \ac{DHKE}.
+Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
+key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
+\ac{CA}.
+
+\Cref{DBSHW-overview} provides an overview.
+
+\begin{figure*}
+  \centering
+  \small
+  \setlength{\ProtoArrowLength}{0.07\linewidth}
+  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
+    \(\HWprove[g, q, \alpha]\):
+    & &
+    \(\HWverify[g, q, A]\):
+    \\
+    \midrule
+
+    \multicolumn{2}{l}{%
+      Static \(\sk_P\in \ZZ_q, \sigma = (a, A, b, B, c)\)
+    }
+    & Static \(\pk\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Pre-setup key-agreement}} \\
+
+    \(x\rgets \ZZ_q\)
+    & \(\ProtoSendRight{g^x}\)
+    & \(y\rgets \ZZ_q\)
+    \\
+
+    \(k \gets (g^y)^x\)
+    & \(\ProtoSendLeft{g^y}\)
+    & \(k \gets (g^{x})^y\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Setup}} \\
+
+    Load \(k\) into \(\UWBPR\)
+    &
+    & Load \(k\) into \(\UWBPR\)
+    \\
+
+    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
+    & \(\ProtoSendRight{R, \hat R}\)
+    & \(\hat A\gets g^x\)
+    \\
+
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
+    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
+    \\
+
+    \(\hat s_1\gets \hat\rho - c_1 x \pmod q\)
+    &
+    &
+    \\
+
+    \vdots
+    &
+    &
+    \\[-1em]
+
+    \(s_m\gets \rho - c_m\alpha \pmod q\)
+    &
+    &
+    \\
+
+    \(\hat s_m\gets \hat\rho - c_m x \pmod q\)
+    &
+    &
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
+
+    \text{Ready}
+    & \ProtoSendRight{\text{Ready}}
+    & \\
+
+    % null
+    & \(\ProtoSendLeft{i}\)
+    & \(i\rgets \{1, \dotsc, m\}\), start clock
+    \\
+
+    Fetch \(s_i, \hat s_i\)
+    & \(\ProtoSendRight{s_i, \hat s_i}\)
+    & Stop clock, record \(\Delta t\)
+    \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Verification}}
+    \\
+
+    % null
+    &
+    & Accept if \(R = A^{c_i} g^{s_i}\),
+      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
+      \(\Delta t < t_{\max}\).
+    \\
+
+  \end{tabular}
+  \caption{%
+    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
+    \(\PK[\alpha][A = g^\alpha]\).
+    Each transmission (arrow in the diagram) uses \(\UWBPR\) (except in the 
+    pre-setup phase).
+    The protocol actually proves \(\PK[\alpha, x][A = g^\alpha \land
+      \hat A = \hat g^x]\).
+    This is ties \(x\), and consequently \(k\), to \(\alpha\).
+    The protocol (setup, distance-bounding and verification phases) should be 
+    repeated \(n\) times to achieve the desired soundness and distance-bounding 
+    errors.
+  }%
+  \label{DBSHW-overview}
+\end{figure*}
+
+\paragraph*{One-time initialization}
+
+The prover's \(\DBSHW\) device must be initialized with a (static) private 
+key~\(\sk_P\) and a signature~\(\sigma\) on that key by some \ac{CA} with 
+public key~\(\pk\) and signing key~\(\sk\).
+These are computed as follows~\cite[cf.][Sect.~4.2]{CLsignatures}.
+
+We have public parameters \(q, G, g, \G, \g, e\); where \(e\colon G\times G\to 
+\G\) is a bilinear map, \(g\in G\) and \(\g\in \G\) are generators of prime 
+order \(q\) (hence \(e(g, g) = \g\)).
+
+We let the \acg{CA} signing key be \(\sk = (x, y, z)\rgets \ZZ_q^3\) and the 
+public key be \(\pk = (q, G, \G, g, \g, e, X, Y, Z)\), where \(X = g^x, Y = 
+g^y, Z = g^z\).
+
+The prover chooses \(\sk_P\rgets \ZZ_q\) and computes a commitment \(M = 
+g^{\sk_P} Z^r\), where \(r\rgets \ZZ_q\).
+Now the prover convinces the \ac{CA} that he knows the key by running the 
+following \ac{ZKPK} protocol: \(
+  \PK[\sk_P, r][M = g^{\sk_P} Z^r].
+\)
+
+Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where
+\begin{itemize}
+  \item \(a\gets g^\alpha\), where \(\alpha\rgets \ZZ_q\),
+  \item \(A\gets g^z, b\gets a^y, B\gets A^y\),
+  \item \(c\gets a^x M^{\alpha x y}\).
+\end{itemize}
+and gives to the prover.
+
+\paragraph*{Pre-setup key-agreement}
+
+The pre-setup phase consists of a key agreement, the prover and verifier must 
+agree on a shared key~\(k\) to use for the \(\UWBPR\) protocol on the physical 
+layer.
+
+To establish \(k\), we use the \ac{DHKE}.
+The prover chooses \(x\rgets \ZZ_q\), the verifier chooses \(y\rgets \ZZ_q\) 
+and they exchange \(X = \hat g^x, Y = \hat g^y\) and both compute
+\(k = \hat g^{xy}\), for some generator \(\hat g\) in \iac{DH} group of prime 
+order \(q\).
+
+We will see later that if the adversary attempted \iac{MITM} attack, our 
+\(\DBSHW\) protocol will detect this, because the adversary will fail 
+\iac{ZKPK}.
+
+\paragraph*{Setup}
+
+The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
+They use the agreed upon key~\(k = g^{xy}\) as the key for \(\UWBPR\).
+\(\DBS\) performs \(
+  \PK[\alpha][A = g^\alpha]
+\) (with a distance bound) whereas \(\DBSHW\) must perform \(
+  \PK[\alpha, x][\hat A = g^\alpha \land X = \hat g^x]
+\) (also with a distance bound).
+
+The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
+  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
+The verifier computes \(\hat A\gets \pk_P\).
+
+The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
+  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
+The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
+  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
+
+\paragraph*{Distance bounding}
+
+The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
+  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
+The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
+Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
+\(\UWBPR\) reply.
+The verifier stops the clock and records the round-trip time~\(\Delta t\).
+
+\paragraph*{Verification}
+
+The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
+  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
+not exceed the limit~\(t_{\max}\).

### 2020-03-06 paper/DB-Schnorr-UWB.tex
Updates UWB description to use CL04 for AKE

@@
 However, CL04 is the base for the \ac{DAA} protocol, which is used for 
-\ac{TPM}, so our approach can make \ac{DAA} \acl{DB}.
+\ac{TPM}, so our protocol can be modified into \iacl{DB} \ac{DAA} protocol.
 
 In summary, the difference is as follows.
-\(\DBS\) has a shared key~\(k\) and performs \(
+\(\DBS\) has a static shared key~\(k\) and performs \(
   \PK[\alpha][A = g^\alpha]
@@
 \(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
-\hat g^{xy}\) from \(X = \hat g^x, Y = \hat g^y\), then performs \[
-  \PK[\alpha, x, \sk_P, \sigma][
+\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
+performs \[
+  \PK[\alpha, \xDH, \sk_P, \sigma][
     A = g^\alpha \land
-    X = \hat g^x \land
-    \Blind[\sigma] = \Sign[_\sk][\sk_P]
+    \XDH = \gDH^{\xDH} \land
+    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
   ],
 \] also with a distance bound; where \(\sk_P\) is the prover's private key, 
-\(\sigma\) is a signature issued with signing key~\(sk\) and \(\Blind\) 
+\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
 reblinds a signature.
-Proving knowledge of \(x\) prevents any \ac{MITM} attack against the \ac{DHKE}.
+Proving knowledge of \(\xDH\) prevents any \ac{MITM} attack against the 
+\ac{DHKE}.
 Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
@@
 \Cref{DBSHW-overview} provides an overview.
+For simplicity of the exposition, we present a version of \(\DBSHW\) that 
+allows the user to run \(\PK[\alpha][A = g^\alpha]\) (the Schnorr 
+identification scheme) with a distance bound.
+This can, of course, be generalized to any \ac{ZKPK} for discrete logarithms, 
+for instance, CL04~\cite{CLsignatures}.
 
@@
     }
-    & Static \(\pk\)
+    & Static \(\pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL)\)
     \\
@@
 
-    \(x\rgets \ZZ_q\)
-    & \(\ProtoSendRight{g^x}\)
-    & \(y\rgets \ZZ_q\)
+    \(\xDH\rgets \ZZ_{\qDH}\)
+    & \(\ProtoSendRight{\XDH = \gDH^{\xDH}}\)
+    & \(\yDH\rgets \ZZ_{\qDH}\)
     \\
 
-    \(k \gets (g^y)^x\)
-    & \(\ProtoSendLeft{g^y}\)
-    & \(k \gets (g^{x})^y\)
+    \(k \gets \YDH^{\xDH}\)
+    & \(\ProtoSendLeft{\YDH = \gDH^{\yDH}}\)
+    & \(k \gets \XDH^{\yDH}\)
     \\
@@
 
-    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
-    & \(\ProtoSendRight{R, \hat R}\)
-    & \(\hat A\gets g^x\)
+    \(r_1, r_2\rgets \ZZ_{\qCL}\)
+    &
+    &
     \\
 
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
+    \(\tilde a = a^{r_1},
+      \tilde A = A^{r_1},
+      \tilde b = b^{r_1},
+      \tilde B = B^{r_1},
+      \tilde c = (c^{r_1})^{r_2}\)
+    & \(\ProtoSendRight{
+        \tilde \sigma = (\tilde a, \tilde A, \tilde b, \tilde B, \tilde c)
+      }\)
+    &
+    \\[0.5em]
+
+    \(v_x = e(\XCL, \tilde a),
+      v_{xy} = e(\XCL, \tilde b),
+      V_{xy} = e(\XCL, \tilde B),
+      v_s = e(\gCL, \tilde c)\)
+    &
+    & \(v_x = e(\XCL, \tilde a),
+      v_{xy} = e(\XCL, \tilde b),
+      V_{xy} = e(\XCL, \tilde B),
+      v_s = e(\gCL, \tilde c)\)
+    \\[0.5em]
+
+    \(\rho\rgets \ZZ_q,
+      \rhoDH \rgets \ZZ_{\qDH},
+      \rhoCL_{\sk} \rgets \ZZ_{\qCL},
+      \rhoCL_{r} \rgets \ZZ_{\qCL},
+      \rhoCL_{r'} \rgets \ZZ_{\qCL}\)
+    &
+    &
+    \\
+
+    \(R\gets g^{\rho},
+      \RDH\gets \gDH^{\rhoDH},
+      \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
+    & \(\ProtoSendRight{R, \RDH, \RCL}\)
+    &
+    \\
+
+    \(\forall i\in \{1, \dotsc, m\}\):
     & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
@@
 
-    \(\hat s_1\gets \hat\rho - c_1 x \pmod q\)
+    \(s_i\gets \rho - c_i\alpha \pmod q\)
     &
@@
 
-    \vdots
-    &
-    &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
+    \(\sDH_i\gets \rhoDH - c_i \xDH \pmod \qDH\)
     &
@@
 
-    \(\hat s_m\gets \hat\rho - c_m x \pmod q\)
+    \(\sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r' \pmod \qCL\)
+    &
+    &
+    \\
+
+    \(\sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk \pmod \qCL\)
+    &
+    &
+    \\
+
+    \(\sCL_i^{(r)}\gets \rhoCL_{r} - c_i r \pmod \qCL\)
     &
@@
 
-    Fetch \(s_i, \hat s_i\)
-    & \(\ProtoSendRight{s_i, \hat s_i}\)
+    Fetch \(s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}\)
+    & \(\ProtoSendRight{
+      s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}}\)
     & Stop clock, record \(\Delta t\)
@@
     &
-    & Accept if \(R = A^{c_i} g^{s_i}\),
-      \(\hat R =  \hat A^{c_i} \hat g^{\hat s_i}\) and
-      \(\Delta t < t_{\max}\).
+    & Accept if \(\Delta t < t_{\max}\) and
+    \\
+
+    % null
+    &
+    & \(R = A^{c_i} g^{s_i}\),
+    \\
+
+    % null
+    &
+    & \(\RDH = \XDH^{c_i} \gDH^{\sDH_i}\),
+    \\
+
+    % null
+    &
+    & \(v_x^{c_i} \RCL =
+          v_s^{\sCL_i^{(r')}} v_{xy}^{\sCL_i^{(\sk)}} V_{xy}^{\sCL_i^{(r)}}\),
+    \\
+
+    %
+    &
+    & \(e(\tilde a, \ZCL) = e(\gCL, \tilde A)\),
+    \\
+
+    %
+    &
+    & \(e(\tilde a, \YCL) = e(\gCL, \tilde b)\),
+    \\
+
+    %
+    &
+    & \(e(\tilde A, \YCL) = e(\gCL, \tilde B)\).
     \\
@@
     pre-setup phase).
-    The protocol actually proves \(\PK[\alpha, x][A = g^\alpha \land
-      \hat A = \hat g^x]\).
-    This is ties \(x\), and consequently \(k\), to \(\alpha\).
+    The protocol actually proves \(
+      \PK[\alpha, \xDH, \sk, \sigma][
+        A = g^\alpha \land
+        \XDH = \gDH^{\xDH} \land
+        \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
+      ].
+    \)
+    This is ties \(\xDH\), and consequently \(k\), to \(\sk_P\) and \(\alpha\).
     The protocol (setup, distance-bounding and verification phases) should be 
@@
 
-We have public parameters \(q, G, g, \G, \g, e\); where \(e\colon G\times G\to 
-\G\) is a bilinear map, \(g\in G\) and \(\g\in \G\) are generators of prime 
-order \(q\) (hence \(e(g, g) = \g\)).
+We have public parameters \(\qCL, \gCL\in\GCL, \ggCL\in\GGCL, e\); where 
+\(e\colon \GCL\times \GCL\to \GGCL\) is a bilinear map, \(\gCL\in \GCL\) and 
+\(\ggCL\in \GGCL\) are generators of prime order \(\qCL\) (hence \(e(\gCL, 
+\gCL) = \ggCL\)).
 
-We let the \acg{CA} signing key be \(\sk = (x, y, z)\rgets \ZZ_q^3\) and the 
-public key be \(\pk = (q, G, \G, g, \g, e, X, Y, Z)\), where \(X = g^x, Y = 
-g^y, Z = g^z\).
+We let the \acg{CA} signing key be \[
+  \sk = (\xCL, \yCL, \zCL)\rgets \ZZ_{\qCL}^3
+\] and the public key be \[
+  \pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL),
+\] where \[
+  \XCL = \gCL^{\xCL}, \quad
+  \YCL = \gCL^{\yCL}, \quad
+  \ZCL = \gCL^{\zCL}.
+\]
 
-The prover chooses \(\sk_P\rgets \ZZ_q\) and computes a commitment \(M = 
-g^{\sk_P} Z^r\), where \(r\rgets \ZZ_q\).
+The prover chooses \(\sk_P\rgets \ZZ_{\qCL}\) and computes a commitment \(M = 
+\gCL^{\sk_P} Z^r\), where \(r\rgets \ZZ_{\qCL}\).
 Now the prover convinces the \ac{CA} that he knows the key by running the 
 following \ac{ZKPK} protocol: \(
-  \PK[\sk_P, r][M = g^{\sk_P} Z^r].
+  \PK[\sk_P, r][M = \gCL^{\sk_P} Z^r].
 \)
 
-Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where
-\begin{itemize}
-  \item \(a\gets g^\alpha\), where \(\alpha\rgets \ZZ_q\),
-  \item \(A\gets g^z, b\gets a^y, B\gets A^y\),
-  \item \(c\gets a^x M^{\alpha x y}\).
-\end{itemize}
-and gives to the prover.
+Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where \[
+  \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
+  A\gets \gCL^{\zCL}, \quad
+  b\gets a^{\yCL}, \quad
+  B\gets A^{\yCL}, \quad
+  c\gets a^{\xCL} M^{\alpha \xCL \yCL}
+\] and gives to the prover.
 
@@
 To establish \(k\), we use the \ac{DHKE}.
-The prover chooses \(x\rgets \ZZ_q\), the verifier chooses \(y\rgets \ZZ_q\) 
-and they exchange \(X = \hat g^x, Y = \hat g^y\) and both compute
-\(k = \hat g^{xy}\), for some generator \(\hat g\) in \iac{DH} group of prime 
-order \(q\).
-
-We will see later that if the adversary attempted \iac{MITM} attack, our 
-\(\DBSHW\) protocol will detect this, because the adversary will fail 
-\iac{ZKPK}.
+The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
+\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
+\gDH^{\yDH}\) and both compute
+\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
+prime order \(\qDH\).
 
@@
 The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
-They use the agreed upon key~\(k = g^{xy}\) as the key for \(\UWBPR\).
+They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
+\(\UWBPR\), instead of a static \(k\).
 \(\DBS\) performs \(
   \PK[\alpha][A = g^\alpha]
-\) (with a distance bound) whereas \(\DBSHW\) must perform \(
-  \PK[\alpha, x][\hat A = g^\alpha \land X = \hat g^x]
-\) (also with a distance bound).
+\) (with a distance bound) whereas \(\DBSHW\) must perform \[
+  \PK[\alpha, \xDH, \sk_P, \sigma][
+    A = g^\alpha \land
+    \XDH = \gDH^{\xDH} \land
+    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
+  ].
+\] This means that the prover (and verifier) must prepare for the other proofs 
+too.
 
-The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
-  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
-The verifier computes \(\hat A\gets \pk_P\).
+The prover blinds the signature~\(\sigma\):
+Choose \(r_1, r_2\rgets \ZZ_{\qCL}\) and compute \(\tilde \sigma = (\tilde a, 
+\tilde A, \tilde b, \tilde B, \tilde c)\), where \[
+  \tilde a = a^{r_1}, \quad
+  \tilde A = A^{r_1}, \quad
+  \tilde b = b^{r_1}, \quad
+  \tilde B = B^{r_1}, \quad
+  \tilde c = (c^{r_1})^{r_2}.
+\]
+The prover sends \(\tilde \sigma\) to the verifier.
+Now, the prover and verifier each compute \[
+  v_x\gets e(\XCL, \tilde a), \quad
+  v_{xy}\gets e(\XCL, \tilde b), \quad
+  V_{xy}\gets e(\XCL, \tilde B), \quad
+  v_s\gets e(\gCL, \tilde c).
+\]
+
+The prover chooses \[
+  \rho\rgets \ZZ_q, \quad
+  \rhoDH\rgets \ZZ_{\qDH}, \quad
+  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
+  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
+  \rhoCL_{r'}\rgets \ZZ_{\qCL}
+\] computes \[
+  R\gets g^\rho, \quad
+  \RDH\gets \gDH^{\rhoDH}, \quad
+  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
+\] and sends \(R, \RDH, \RCL\) to the verifier.
 
 The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
-The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
-  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
+\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
+The prover computes responses
+\begin{multline*}
+  s_i\gets \rho - c_i\alpha, \quad
+  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
+  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
+  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
+  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
+\end{multline*}
+for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).
 
@@
 \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
-The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
-Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
-\(\UWBPR\) reply.
+The prover instantly replies with the pre-computed \(s_i, \sDH_i, 
+\sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r')}\).
+Note that these values must be sent as a concatenation in \emph{one} \(\UWBPR\) 
+reply.
 The verifier stops the clock and records the round-trip time~\(\Delta t\).
@@
 
-The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
-  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
-not exceed the limit~\(t_{\max}\).
+The verifier checks that \[
+  R = A^{c_i} g^{s_i}, \quad
+  \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
+  v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
+\] and that the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
+time-limit~\(t_{\max}\) (corresponding to the desired distance bound).
+Finally, the verifier checks the validity of \(\tilde \sigma\): \[
+  e(\tilde a, \ZCL) = e(\gCL, \tilde A), \quad
+  e(\tilde a, \YCL) = e(\gCL, \tilde b), \quad
+  e(\tilde A, \YCL) = e(\gCL, \tilde B).
+\]

### 2020-03-10 paper/DB-Schnorr-UWB.tex
Fixes UWB KE MITM problem: ties DH exponent to secret key
No proofs though.

@@
     \XDH = \gDH^{\xDH} \land
+    \XDHCL = \XDH^{\sk} \land
     \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
@@
 reblinds a signature.
-Proving knowledge of \(\xDH\) prevents any \ac{MITM} attack against the 
-\ac{DHKE}.
+Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
+prevents any \ac{MITM} attack against the \ac{DHKE}.
 Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
@@
 
-    \(\xDH\rgets \ZZ_{\qDH}\)
-    & \(\ProtoSendRight{\XDH = \gDH^{\xDH}}\)
+    \(\xDH\rgets \ZZ_{\qDH}, \XDH\gets \gDH^{\xDH}, \XDHCL\gets \XDH^{\sk}\)
+    & \(\ProtoSendRight{\XDH, \XDHCL}\)
     & \(\yDH\rgets \ZZ_{\qDH}\)
@@
       \RDH\gets \gDH^{\rhoDH},
+      \RDHCL\gets \XDH^{\rhoCL_{\sk}},
       \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
-    & \(\ProtoSendRight{R, \RDH, \RCL}\)
+    & \(\ProtoSendRight{R, \RDH, \RDHCL, \RCL}\)
     &
@@
     &
+    & \(\RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}\),
+    \\
+
+    % null
+    &
     & \(v_x^{c_i} \RCL =
@@
         \XDH = \gDH^{\xDH} \land
+        \XDHCL = \XDH^{\sk} \land
         \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
@@
 prime order \(\qDH\).
+The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.
 
@@
   \RDH\gets \gDH^{\rhoDH}, \quad
+  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
   \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
@@
   \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
+  \RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}, \quad
   v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
@@
 \]
+
+\subsection{Security analysis}
+
+There are two questions we must answer about this protocol:
+\begin{enumerate}
+  \item Can the adversary perform \iac{MITM} attack against the \ac{DHKE}?
+  \item Does \(\XDHCL\) break anonymity?
+\end{enumerate}

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Adds proof sketches (informal proofs) for UWB MITM and anon

@@
 \begin{enumerate}
-  \item Can the adversary perform \iac{MITM} attack against the \ac{DHKE}?
-  \item Does \(\XDHCL\) break anonymity?
+  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
+    the \ac{DHKE}?
+  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
 \end{enumerate}
+
+To answer the first question, by \textcite{Camenisch-phdthesis}, the above 
+protocol is \iac{ZKPK}.
+In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
+\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
+adversary.
+The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
+impersonate real hardware).
+The \(\sk\) must be the same \(\sk\) throughout the 
+subproofs~\cite{Camenisch-phdthesis}.
+In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
+If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
+proof will fail.
+
+\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
+chosen base~\(\XDH\).
+If an adversary can use this to tell one device from another, then the 
+adversary can solve the \ac{DDH} problem.
+Consider the following reduction.
+
+Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
+probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
+We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\).
+Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to the adversary, for \(1\leq i\leq 
+n\).
+Finally, give the adversary the challenge \(g, Y, Z\).
+If the adversary recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
+\ac{DDH} with the same advantage \(\epsilon\).

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Slight clarification to UWB anon argument
Further clarification to UWB anon argument

@@
 probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
-We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\).
-Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to the adversary, for \(1\leq i\leq 
-n\).
-Finally, give the adversary the challenge \(g, Y, Z\).
-If the adversary recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
+We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\) and must 
+decide if \(Z = g^{xy}\) or not.
+Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to \(\adv\), for \(1\leq i\leq n\).
+Finally, give \(\adv\) the challenge \(g, Y, Z\).
+If \(\adv\) recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
 \ac{DDH} with the same advantage \(\epsilon\).

### 2020-03-11 paper/tamarin-spec.tex

--- 2018-11-15 paper/tamarin-spec.tex
@@
-\section{Specification of the distance-bounding protocol used by \PRIVO in Tamarin}
+\section{Specification in Tamarin}%
 \label{apdx:tamarin-spec}
 
+\sonja{Clarification of these explanations needed. Split up some text
+  to go into the body of the paper and leave details (or even just the
+  code) in the appendix.}
 The results provided by Tamarin extends to the protocol being modeled 

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Renames DBSchnorr-n-bit to DB-Schnorr-nbit to sync with UWB

--- 2020-02-25 paper/DBSchnorr-n-bit.tex
@@
 
-As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
-protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
+One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
+To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
 
 \subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DBSchnorr-n-bit}
+\label{DB-Schnorr-nbit}
 
@@
 Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\)
-although we reveal the \(l\) bits. (See \cref{l-bit-problem for an
-  in-depth treatment of what we call the \(l\)-bit problem.)
+Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
 
@@
 Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check
-  the details with Douglas.}
-
-Besides the security against the standard attacks on distance-bounding
-protocols, we also need to ensure that our modification does not leak
-any information to the adversary via the aforementioned \(l\) bits.
+\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
 
 \subsection{The \(l\)-bit problem}
-\label{l-bit-problem}
-
-We will now systematically investigate the concern of the adversary
-gaining any advantage from learning \(l\) bits from one of the two challenges.
 
@@
 
-\endinput
 \subsection{Formal Verification}

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Edits nbit section
Edits protocol description, l-bit problem section.

@@
 \section{Bit-by-bit distance-bounding Schnorr protocol}%
-
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
-To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
-
-\subsection{Reattempting a distance-bounding Schnorr protocol}%
 \label{DB-Schnorr-nbit}
 
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
-We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
+We will now continue with a more traditional (in \ac{DB} terms) version of the 
+protocol, one that uses bit-by-bit communication.
 
-We present the protocol in \cref{SchnorrFigure}.
-The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
+%One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+%ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+%  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
+%To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
+
+We present the protocol in \cref{DB-Schnorr-nbit-figure}.
+We will present the protocol as \iac{DB} version of the Schnorr identification 
+scheme (\(\PK[\alpha][A = g^\alpha]\)), this is for the sake of exposition.
+It can be generalized to \eg CL04~\cite{CLsignatures}.
+
+The (cyclic) group with generator~\(g\) with prime order~\(q\) is a system 
+parameter.
+The private key~\(\alpha\) with public key~\(A = g^\alpha\) are generated once 
+by the prover in the setup phase.
+The verifier has a copy of the public key~\(A\) and wants to verify that the 
+private key~\(\alpha\) is within a certain distance-bound.
 
@@
     One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired soundness 
-    and distance-bounding errors.
+    The protocol should be repeated \(n\) times to achieve the desired 
+    soundness and distance-bounding errors.
   }%
-  \label{SchnorrFigure}
+  \label{DB-Schnorr-nbit-figure}
 \end{figure*}
 
-During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
-The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
+During one round, the prover commits to a random nonce: more precisely he 
+chooses \(
+  \rho\rgets \ZZ_q
+\) uniformly at random, computes \(
+  R\gets g^\rho
+\) and sends \(R\) to the verifier.
+The verifier generates two challenges \(
+  c_0\rgets \bin^k,
+  c_1\rgets \bin^k
+\) and sends them to the prover.
+The prover computes \(
+  s_0\gets \rho - c_0\alpha,
+  s_1\gets \rho - c_1\alpha.
+\)
 This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
@@
 
-We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
+We let \(|q|\) denote the length of \(q\) in bits, so any element~\(z\in 
+\ZZ_q\) can be represented by \(|q|\) bits.
 The verifier will request all \(|q|\) response-bits from one challenge (say 
 \(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
-Then the verifier can authenticate the prover by checking if \(R = 
-  g^{s_b}A^{c_b}\).
+Then the verifier can authenticate the prover by checking if \(
+  R = g^{s_b}A^{c_b}.
+\)
 
-\subsection{Security analysis}
+This must be repeated for \(n\) rounds.
 
-The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
-The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
-This allows us to prevent \ac{DBTF}.
-Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
-%reducing success of MF according to number of repetitions.
-The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
-Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
+\subsection{Security of the \(l\) bits}
 
-The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
-the knowledge error, \(2^{-kn}\), becomes small enough.
-Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
-
-The \ac{DB} phase protects against distance fraud.
-Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
-\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
-Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
-
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
-The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
-  s_1\).
-\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
-\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
-Now, the adversary has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
-However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
-The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
-Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
-If the adversary requests \(s_b\) in full, the adversary can also guess the 
-remaining \(|q|-l\) bits of \(s_{1-b}\).
-Based on our assumption above, the probability of guessing these bits 
-successfully is \(2^{-(|q|-l)}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-(|q|-l)n}\).
-
-The protocol is \ac{DBTF}-resistant. 
-Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
-
-The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
-Thus the probability of success is equivalent of a collision for the responses 
-for the chosen challenge --- in each round.
-
-Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
-
-\subsection{The \(l\)-bit problem}
+Before we proceed to other security properties, we will start with the 
+\(l\)-bit problem.
+We will now analyse how much damage leaking those \(l\) bits of the second 
+response does.
 
@@
 \begin{definition}[DB-Schnorr Problem]%
-  \label{DBSchnorr-problem}
+  \label{DBSP}
   Let \(g\) be a generator for a group of prime order~\(q\).
@@
 
-\begin{lemma}
+\begin{lemma}\label{DBSPtoDLP}
   Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
-  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
+  (\cref{DBSP}) with probability \(\epsilon\), we can construct an 
   algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Adds proof for nbit ZKPK (#9)

@@
 
+\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}
+
+The main difference between this protocol and the Schnorr protocol is that we 
+have the prover compute responses for two different challenges, \(c_0, c_1\).
+In the authentication step, the verifier chooses only one of those challenges.
+However, the verifier requests all \(|q|\) bits of \(s_b\) and \(l\) bits of 
+\(s_{1-b}\).
+
+This is \iacl{PK}:
+Completeness and soundness follows from the Schnorr protocol.
+The knowledge extractor works exactly the same.
+It does not matter that the verifier first chooses two challenges and later 
+reveals which one to use and the prover sends the response bit-by-bit.
+
+This is \emph{computational} \acl{ZK}:
+The simulator chooses \[
+  s_0, s_1\rgets \ZZ_q; \quad
+  c_0, c_1\rgets \bin^k; \quad
+  b\rgets \bin.
+\]
+Then it can set \[
+  R_0\gets g^{s_0} A^{c_0}, \quad
+  R_1\gets g^{s_1} A^{c_1}.
+\]
+Now the simulator must come up with those \(l\) bits.
+\Cref{l-bit-advantage,DBSPtoDLP} say that distinguishing these bits from random 
+is as hard as the \ac{DLP}.
+So, the simulator can simply choose the \(l\) bits~\(L\rgets \bin^l\) uniformly 
+at random.
+
+The simulator outputs \(R_b, c_0, c_1, s_b, L\).
+
+%Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
+%protocol with soundness error \(2^{-k n}\) still 
+%holds~\cite[\eg][]{OnSigmaProtocols}.
+%(We note that \(l\), which is also the length of the challenge bit string, must 
+%be logarithmic in the security parameter, \(\lambda\), for a malicious 
+%verifier.)
+
 \subsection{Formal Verification}

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Renames label for DBS-UWB figure
Fixes error in UWB MF proof

@@
 
-We present the protocol in \cref{SchnorrFigure}.
+We present the protocol in \cref{DB-Schnorr-UWB-figure}.
 The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
@@
   }%
-  \label{SchnorrFigure}
+  \label{DB-Schnorr-UWB-figure}
 \end{figure*}
@@
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
-  where \(m, q\) are as in \cref{DB-Schnorr}.
+  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
+  \cref{DB-Schnorr}.
 \end{theorem}
@@
 
-  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
-  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
-  session.
+  Since \(m \leq q\), the best strategy is to guess which challenge the 
+  verifier will use.
+  Thus, the total success probability is \(\frac{1}{m^n}\).
 \end{proof}
@@
 
-The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
+The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
 They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
@@
 
-To answer the first question, by \textcite{Camenisch-phdthesis}, the above 
-protocol is \iac{ZKPK}.
+To answer the first question,
+by \textcite{Camenisch-phdthesis}, the above protocol is \iac{ZKPK}.
 In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
@@
 
+To answer the second question,
 \(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 

### 2020-03-11 paper/DB-Schnorr-nbit.tex
Adds nbit MF proof

@@
 
+\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}
+
+\paragraph{\Acl{DBMF}}
+
+In \ac{DBMF}, the adversary will try to authenticate to a verifier by querying 
+a far-away prover.
+By \cref{TaintedMF}, pure relaying will be detected by the verifier.
+So the adversary must resort to things like querying in advance \etc.
+
+\begin{theorem}[\acs*{DBMF} resistance]
+  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
+  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{2^n}\), where \(m, q\) are as in 
+  \cref{DB-Schnorr}.
+\end{theorem}
+
+\begin{proof}
+  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
+  cannot learn anything by observation.
+  This leaves the adversary with two options:
+  \begin{enumerate}
+  \item guess which challenge the verifier will use and request the correct 
+    response from the prover, receiving the challenge first would taint the 
+    session (\cref{TaintedMF});
+  \item guess the response.
+  \end{enumerate}
+
+  The first option yields success with probability \(\frac{1}{2}\), since the 
+  choice is uniformly distributed over the two challenges.
+
+  The second option yields a lower success probability:
+  Assume that each bit reveals some information about the future bits.
+  The first bit must still be guessed, this is yields a probability of \emph{at 
+  most} \(\frac{1}{2}\).
+
+  The best strategy is to guess which challenge the verifier will select.
+  Thus, the success probability is \(\frac{1}{2}\) per round, or 
+  \(\frac{1}{2^n}\) in total.
+\end{proof}
+
 \subsection{Formal Verification}

### 2020-03-12 paper/DB-Schnorr-nbit.tex
Updates nbit MF proof
This takes the distribution of the bits into consideration.

@@
   cannot learn anything by observation.
-  This leaves the adversary with two options:
+  This leaves the adversary with the following:
   \begin{enumerate}
@@
       session (\cref{TaintedMF});
-  \item guess the response.
+    \item guess the second response.
   \end{enumerate}
 
-  The first option yields success with probability \(\frac{1}{2}\), since the 
+  The first case yields success with probability \(\frac{1}{2}\), since the 
   choice is uniformly distributed over the two challenges.
+  The adversary requests all \(|q|\) bits of the response~\(s_{\hat b}\) and 
+  \(l\) bits of \(s_{1-\hat b}\).
+  When the verifier sends challenge bit \(b_i = \hat b\), the adversary replies 
+  with a bit from \(s_{\hat b}\).
+  If \(b_i = 1-\hat b\), then the adversary uses the \(l\) bits.
 
-  The second option yields a lower success probability:
-  Assume that each bit reveals some information about the future bits.
-  The first bit must still be guessed, this is yields a probability of \emph{at 
-  most} \(\frac{1}{2}\).
+  If the adversary guessed \(\hat b = b\) correctly, then the verifier will 
+  accept.
+  Otherwise, the adversary must compute the remaining \(|q|-l\) bits of 
+  \(s_{1-\hat b}\).
 
-  The best strategy is to guess which challenge the verifier will select.
-  Thus, the success probability is \(\frac{1}{2}\) per round, or 
-  \(\frac{1}{2^n}\) in total.
+  Guessing the remaining bits yield a success probability of 
+  \(\frac{1}{2^{|q|-l}}\).
+  \Cref{DBSPtoDLP} states that any algorithm that can compute the remaining 
+  bits can also solve a corresponding \ac{DLP}.
+  It follows that the adversary cannot do non-negligibly better than guessing 
+  the remaining bits.
+
+  Thus, the success probability is \(\frac{1}{2}+\frac{1}{2^{|q|-l}}\) per 
+  round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.
+
 \end{proof}

### 2020-03-12 paper/DB-Schnorr-nbit.tex
Fixes refs, nbit MF thm
Writes up nbit DH proof

@@
 \begin{theorem}[\acs*{DBMF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{2^n}\), where \(m, q\) are as in 
-  \cref{DB-Schnorr}.
+  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then \(
+    \Adv_{\DBS}^{\text{MF}}(\adv) =
+      \left(\frac{1}{2} + \frac{1}{2^{|q|-l}}\right)^n,
+  \) where \(m, q\) are as in \cref{DB-Schnorr-nbit}.
 \end{theorem}
@@
   round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.
+\end{proof}
 
+\paragraph{\Acl{DBDH}}
+
+The protocol is also secure against distance hijacking due to the fact that the 
+authenticating bit string is used during the \ac{DB} phase.
+(Brands-Chaum used the challenge bit string, something that made their protocol 
+vulnerable.)
+\Ac{DBDH} requires that the adversary finds a collision between his response 
+and that of the honest prover.
+Thus the probability of success is equivalent to a collision for the responses 
+for the chosen challenge --- in each round.
+
+\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
+  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
+  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\).
+\end{theorem}
+
+\begin{proof}
+  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
+  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
+  \(R' = R\) to not interfere.
+
+  The verifier will choose \(c_0, \dotsc, c_1\).
+  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
+  is his secret.
+  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
+  c_i \alpha'\), where \(\alpha'\) is the adversary's secret.
+  If the adversary didn't choose \(R'\), he can only guess the values for 
+  \(s_i'\).
+
+  During the fast phase, the adversary has two options:
+  for each challenge bit, the adversary can \(\Commit\) to a response bit or to 
+  \(\Prompt\) the honest prover to send a bit.
+
+  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute the 
+  correct \(s_i' = \rho' - c_i \alpha'\) for \(i\in \bin\).
+  If the adversary \(\Commit\)s:
+  Now, the adversary must commit to one bit of \(s_0'\) or \(s_1'\) before 
+  seeing the verifier's choice \(b_i\).
+  He can make a guess~\(\hat b\) at the verifier's choice~\(b\).
+  Then he commits to the next bit of \(s_{\hat b}'\).
+  If the challenge~\(b_i \neq \hat b\), he will commit to the same bit for the 
+  next round.
+  If indeed \(\hat b = b\), the verifier will accept.
+  The success probability is \(\frac{1}{2}\) over all bits.
+
+  If the adversary \(\Prompt\)s:
+  The prover computed \(s_0\) and \(s_1\) using \(\rho\) and \(\alpha\).
+  However, the verifier will use \(R'\) and \(A'\) in the verification step.
+  This will succeed if \(s_b = s_b'\), the probability of which is 
+  \(\frac{1}{q}\).
+  This means that the probability of success for prompting a bit is 
+  \(\frac{1}{2}\), or \(\frac{1}{2^{|q|}}\) over all bits.
+
+  If the adversary didn't choose \(R'\) he consequently doesn't know \(\rho\) 
+  and cannot compute the correct \(s_0\) and \(s_1\).
+  Thus, committing yields \(\frac{1}{2}\) probability per bit.
+  The same applies for prompting.
+
+  Obviously, the better strategy for the adversary is to choose \(R' = 
+  g^{\rho'}\).
+  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
+  \(\Prompt\) (\ac{DBDH}).
+  We thus have that
+  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\) for \(n\) rounds,
+  which concludes the proof.
 \end{proof}

### 2020-03-12 paper/DB-Schnorr-nbit.tex

@@
 
+\paragraph{\Acl{DBTF}}
+
+We cannot achieve \ac{DBTF} resistance.
+Indeed, the prover can send \(l+\nu\) bits of both response strings, \(s_0\) 
+and \(s_1\), to the adversary.
+When the adversary receives the \(l+1\)th bit, he learns \(b\).
+He can send \(b\) to the prover and answer correctly to the verifier, provided 
+\(\nu \geq 1\).
+By the time he receives the next challenge from the verifier, the prover will 
+have sent him the remaining bits of \(s_b\) without revealing more bits about 
+\(s_{1-b}\).
+This would not taint the session.
+As long as \(l+\nu\) is sufficiently small, the adversary cannot compute the 
+remaining bits of \(s_{1-b}\) to compute the prover's secret.
+
 \paragraph{\Acl{DBDH}}

### 2020-03-12 paper/DB-Schnorr-nbit.tex

@@
 protocol, one that uses bit-by-bit communication.
+As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
+protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
 
@@
 
-We wanted to formally verify the protocol security properties. To realize this, 
-we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
-originally the possibility to reason on time and space in its model.
-However, thanks to a recent work by \textcite{TamarinDB}, all the common 
-properties mentioned in the previous subsection can be equivalently 
-characterized with a causality-based definition relying only on the order of 
-messages.
+We formally verify the protocol security properties using the Tamarin
+prover~\cite{meier2013tamarin}. Tamarin does not originally include
+the possibility to reason on time and space in its model.  However,
+thanks to a recent work by \textcite{TamarinDB}, the common properties
+can be equivalently characterized with a causality-based definition
+relying only on the order of messages.
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
 It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
-This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
-We are currently investigating the Tamarin interactive mode to validate as well the security properties.
+Tamarin's auto-prover validated the soundness and correctness
+properties (in negligible computation time) and proved the security
+properties used in~\cite{TamarinDB}. In the meantime,
+\textcite{TamarinDBTF} introduced the notion of post-collusion
+security which enabled them to prove \ac{DBTF}. In future work, we
+will use this extension on our protocol.

### 2020-03-13 paper/DB-Schnorr-PKI.tex
Breaks out PKI, frees first version from any UWB stuff (#34)

--- 2020-03-11 paper/DB-Schnorr-UWB.tex
@@
-\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
-\label{DB-Schnorr-UWB}
-
-We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
-logarithms.
-Our protocol is an adaptation of the Schnorr identification 
-scheme~\cite{Schnorr}, albeit different from that of 
-\textcite{DistanceBounding} in the original \ac{DB} paper\footnote{%
-  The \citeauthor{DistanceBounding} protocol was shown to be prone to distance 
-  hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
-  terrorist fraud.
-} and that of \textcite{Bussard-Bagga}\footnote{%
-  The \citeauthor{Bussard-Bagga} protocol was also shown to be 
-  vulnerable~\cite{Bussard-Bagga-attack}.
-  Although this time, the protocol could not protect against \ac{DBTF} and 
-  \ac{DBDF} as it claimed.
-}.
-We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
-protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} and \ac{DBTF}.
-This yields strong privacy properties and protection against a malicious, 
-impersonating verifier.
-
-We also deviate from the normal technique of one-bit challenges and responses 
-otherwise used in \ac{DB} protocols.
-\Textcite{UWBPR} proposed a secure encoding for the physical 
-layer which removes the requirement of only using single-bit challenges and 
-responses for distance bounding.
-However, their protocol only works for relay attacks and cannot handle distance 
-fraud.
-This is due to a requirement of the protocol that the prover and verifier must 
-share a secret, and thus must be mutually trusted.
-
-We will first present our version of the \ac{DB} Schnorr protocol for the 
-mutual-trust case, where the prover and verifier have a pre-shared secret.
-Then we will adapt it by introducing \iac{PKI}.
-We will use this \ac{PKI} to create \iac{AKE} which leverages that our protocol 
-is \iac{DB} \ac{ZKPK} for discrete logarithms.
-If the \ac{PKI} is based on discrete logarithms we can prove the distance bound 
-while we authenticate the key.
-This turns the mutual-trust by shared-key into mutual trust by 
-\ac{PKI}.
-
-\subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DB-Schnorr}
-
-Thanks to \textcite{UWBPR} we can keep the Schnorr protocol almost as is, since 
-relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical layer.
-\Ac{DBDF} is not a concern either, since the prover is trusted.
-The only concern, for now, is \acl{DBTF}.
-(However, we will still prove those properties, as they will be useful later.)
-
-We present the protocol in \cref{DB-Schnorr-UWB-figure}.
-The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
-Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
-Further, let
-\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
-\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
-key~\(k\) and finally
-\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
-and \(\UWBPRrecv\) operations.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
-    & &
-    \(\DBSverify[k, g, q, A]\):
-    \\
-    \midrule
-
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
-
-    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
-    & \(\ProtoSendRight{R}\)
-    &
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_m}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
-    \\
-
-    \vdots
-    &
-    &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
-
-%    % null
-%    &
-%    & Random delay
-%    \\
-
-    % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
-    \\
-
-    Fetch \(s_i\)
-    & \(\ProtoSendRight{s_i}\)
-    & Stop clock, record \(\Delta t\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Accept if \(R = g^{s_i} A^{c_i}\) and \(\Delta t < t_{\max}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
-    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol should be repeated \(n\) times to achieve the desired 
-    soundness and distance-bounding errors.
-  }%
-  \label{DB-Schnorr-UWB-figure}
-\end{figure*}
-
-During one round, in the setup phase, the prover commits to a random nonce: 
-more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
-\(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates \(m\) challenges \(c_1\rgets \bin^l, \dotsc, c_m\rgets 
-  \bin^l\) (bit strings of length \(l\)) and sends them to the prover.
-The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
-  \dotsc, s_m\gets \rho - c_m\alpha\).
-This step is the main difference to the original Schnorr protocol: the verifier 
-selects several challenges and the prover computes several responses --- but 
-still only use \emph{one nonce}, \(\rho\).
-This is needed for \ac{DBTF} resistance.
-This is also different from the original Brands-Chaum protocol, in which the 
-prover and verifier jointly construct \emph{one} challenge with \emph{one} 
-response.
-
-In the \ac{DB} phase, the prover notifies the verifier that he has computed 
-\(s_1, \dotsc, s_m\).
-The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
-it as a challenge to the prover and starts measuring the time of flight.
-The prover replies with \(s_i\).
-The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
-that the time of flight was within \(t_{\max}\) (determined from the allowed 
-  distance).
-
-This protocol must be repeated \(n\) times.
-
-\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}
-
-The main difference between this protocol and the Schnorr protocol is that we 
-have the prover compute responses for \(m\) different challenges, \(c_1, 
-  \dotsc, c_m\).
-However, in the authentication step, the verifier chooses only one of those 
-challenges.
-From the simulator's (and extractor's) perspective, there is no difference 
-whether the verifier first chooses \(m\) and then chooses one of those \(m\) 
-challenges, or if the verifier chooses the one challenge directly;
-the distribution is the same, \(\frac{m}{n}\times \frac{1}{m} = \frac{1}{n}\).
-Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
-protocol with soundness error \(2^{-l n}\) still 
-holds~\cite[\eg][]{OnSigmaProtocols}.
-(We note that \(l\), which is also the length of the challenge bit string, must 
-be logarithmic in the security parameter, \(\lambda\), for a malicious 
-verifier.)
-
-\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}
-
-The intuition behind the protocol security is as follows.
-The prover must know the responses for all challenges to successfully pass the 
-\ac{DB} phase.
-The reason for having several challenges but only one random nonce is that 
-knowing at least two responses means learning the secret~\(\alpha\).
-This gives us the incentives that prevent \ac{DBTF}.
-(We also need it for \ac{DBMF}.)
-Bundling the authentication into the distance-bounding phase (difference from 
-Brands-Chaum) prevents \ac{DBDH}.
-We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
-can do \iac{DBEDLC} attack to reduce the distance.
-(We will solve this problem further down.)
-However, the properties of \(\UWBPR\) and the unpredictability of the 
-challenges ensures \ac{DBMF} resistance (since then the prover is honest).
-
-\paragraph{\Acl{DBMF}}
-
-The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
-distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
-Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.
-
-\begin{theorem}[\acs*{DBMF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
-  \cref{DB-Schnorr}.
-\end{theorem}
-
-\begin{proof}
-  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
-  cannot learn anything by observation.
-  This leaves the adversary with two options:
-  \begin{enumerate*}
-  \item guess which challenge the verifier will use and request the correct 
-    response from the prover, receiving the challenge first would taint the 
-    session (\cref{TaintedMF});
-  \item guess the response.
-  \end{enumerate*}
-  The first option yields success with probability \(\frac{1}{m}\), since the 
-  choice is uniformly distributed.
-  The second option yields success with probability \(\frac{1}{q}\): since the 
-  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
-  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
-  \(\ZZ_q\).
-
-  Since \(m \leq q\), the best strategy is to guess which challenge the 
-  verifier will use.
-  Thus, the total success probability is \(\frac{1}{m^n}\).
-\end{proof}
-
-\paragraph{\Acl{DBTF}}
-
-The protocol is \ac{DBTF} resistant.
-Indeed, if the malicious prover gives more than one response to the accomplice, 
-the accomplice can compute the secret key and, thus, impersonate forever.
-And any help will increase the probability of success of future attempts.
-
-\begin{theorem}[\acs*{DBTF} resistance]
-  Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
-  \(\S\) an algorithm with runtime \(t_{\S}\).
-  If the verifier's challenges are uniformly drawn, then 
-  \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
-\end{theorem}
-
-\begin{proof}
-  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
-  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
-  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
-  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
-  Say that \(\adv\) has successfully authenticated with the prover's help and 
-  \(\S\) is given \(\adv\)'s state.
-
-  Now \(\S\) will use \(\adv\) in a simulation.
-  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
-  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
-  choose another challenge different from before.
-  Since \(\adv\) cannot perform a relay to the prover without tainting the 
-  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
-  provided by the prover must be independent from the chosen challenge.
-  Now \(\adv\) will again provide a correct response with 
-  probability~\(p_{\adv}\).
-
-  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
-  \(m p_{\adv}\) responses.
-  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
-  correct responses and, thus, \(p_{\S} = 1\) for any successive 
-  authentication.
-  This would also make \(p_{\adv} = 1\).
-  This contradicts that the secret is not leaked.
-  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
-  secret leaks.
-\end{proof}
-
-\paragraph{\Acl{DBDH}}
-
-The protocol is also secure against distance hijacking due to the fact that the 
-authenticating bit string is used during the \ac{DB} phase.
-(Brands-Chaum used the challenge bit string, something that made their protocol 
-vulnerable.)
-\Ac{DBDH} requires that the adversary finds a collision between his response 
-and that of the honest prover.
-Thus the probability of success is equivalent to a collision for the responses 
-for the chosen challenge --- in each round.
-
-\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
-\end{theorem}
-
-\begin{proof}
-  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
-  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
-  \(R' = R\) to not interfere.
-
-  The verifier will choose \(c_1, \dotsc, c_k\).
-  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
-  is his \enquote{private key}\footnote{%
-    In Schnorr's original protocol this was called the private key.
-    But in our general use, it's the discrete logarithm for which the prover 
-    wants to prove knowledge.
-  }.
-  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
-  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
-  If the adversary didn't choose \(R'\), he can only guess the values for 
-  \(s_i'\).
-
-  Now the adversary has two options:
-  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.
-
-  If the adversary \(\Commit\)s:
-  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
-  = \rho' - c_i \alpha'\) for all \(i\).
-  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
-  choice \(j\).
-  The probability of committing to the right one is \(\frac{1}{m}\).
-  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
-  the probability of success is \(\frac{1}{q}\) --- since he must guess 
-  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
-  might just as well guess the final outcome (\(\frac{1}{q}\)).
-  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
-  The success of committing is \(\frac{1}{m}\).
-
-  If the adversary \(\Prompt\)s:
-  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
-  \enquote{public key}\footnote{%
-    In Schnorr's original protocol this was a public key.
-    In our more general use, it is the value for which the adversary wants to 
-    prove knowledge of a discrete logarithm.
-  } of the adversary.
-  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
-  - c_i \alpha + c_i \alpha'}\).
-  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
-  accept if \(\alpha = \alpha'\), the probability for which is 
-  \(\frac{1}{q^2}\).
-  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
-  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
-  \frac{1}{q}\).
-
-  Obviously, the better strategy for the adversary is to choose \(R' = 
-  g^{\rho'}\).
-  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
-  \(\Prompt\) (\ac{DBDH}).
-  We thus have that
-  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
-  which concludes the proof.
-\end{proof}
-
-\subsection{From mutual trust to \acs*{PKI}}
+\section{From mutual trust to \acs*{PKI}}%
+\label{DB-Schnorr-PKI}
 

### 2020-03-13 paper/ZKPK-instantiations.tex

@@
   \begin{tabular}{lcl}
-    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
+    \(\PKprove[\{g_i\}_{i=1}^n, q, \{\alpha_i\}_{i=1}^n]\):
     &
@@
     \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
-    the Schnorr identification scheme.
+    the Schnorr identification scheme~\cite{Camenisch-phdthesis}.
   }%
@@
     \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
-    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
+    using the Fiat-Shamir heuristic on the Schnorr identification 
+    scheme~\cite{Camenisch-phdthesis}.
   }%

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Breaks out formal verification to own section (fixes #38)

--- 2020-03-12 paper/DB-Schnorr-nbit.tex
@@
 
-\subsection{\Acl*{ZK} and \acl*{PK}}\label{UWB-ZKPK}
+\subsection{\Acl*{ZK} and \acl*{PK}}\label{nbit-ZKPK}
 
@@
 \begin{proof}
-  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
+  It follows from the \ac{ZK} property (\cref{nbit-ZKPK}) that the adversary 
   cannot learn anything by observation.
@@
 \end{proof}
-
-\subsection{Formal Verification}
-
-We wanted to formally verify the protocol security properties. To realize this, 
-we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
-originally the possibility to reason on time and space in its model.
-However, thanks to a recent work by \textcite{TamarinDB}, all the common 
-properties mentioned in the previous subsection can be equivalently 
-characterized with a causality-based definition relying only on the order of 
-messages.
-
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
-It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
-
-Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
-This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
-We are currently investigating the Tamarin interactive mode to validate as well the security properties.

### 2020-03-13 paper/intro.tex
Adds WIP contributions to intro

@@
 \paragraph*{Contributions}
+
+We make three contributions.
+First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
+\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
+model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
+This version is based on the assumption that we can transmit all bits at once, 
+not bit-by-bit as normally required for \ac{DB}.
+This assumption is reasonable by the results of \textcite{UWBPR}.
+
+Second, for the assumption about sending all bits at once to hold, 
+\textcite{UWBPR} requires that two devices shared a symmetric key~\(k\).
+Our second contribution is \iac{PKI} and \ac{AKE} scheme for any device in 
+the \ac{PKI} to convince a verifier that this is the case.
+The solution relies on our first contribution.
+
+Our last contribution is another version of the protocol, one which uses 
+bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
+We achieve all properties except \ac{DBTF} resistance.
+
+The first (and second) contribution enables us to do \ac{DB} \ac{ABC}.
+The third enables us also to do \ac{DB} \ac{ABC}, just without \ac{DBTF} 
+resistance.
 

### 2020-03-13 paper/DB-Schnorr-PKI.tex

@@
 We will use a \emph{trusted} hardware implementation to overcome the limitation 
-of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
-We will need \iac{PKI} for the verifier to verify the trusted hardware.
+of \textcite{UWBPR}, \ie that the prover and verifier must share a key.
+We will provide \iac{PKI} for the verifier to verify the trusted hardware.
 We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
@@
 In summary, the difference is as follows.
-\(\DBS\) has a static shared key~\(k\) and performs \(
+\(\DBS\) performs \(
   \PK[\alpha][A = g^\alpha]
-\) with a distance bound.
-\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
+\) with a distance bound on the user's behalf.
+\(\DBSHW\) first runs \iac{DHKE} to establish a shared key~\(k =
 \gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
@@
   ],
-\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
-\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
-reblinds a signature.
+\] also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
+\(\sk_P\) is the prover's private key, \(\sigma\) is a signature issued with 
+signing key~\(\sk\) and \(\Blind\) reblinds a signature.
 Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
@@
 The \(\sk\) must be the same \(\sk\) throughout the 
-subproofs~\cite{Camenisch-phdthesis}.
+subprotocols~\cite{Camenisch-phdthesis}.
 In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).

### 2020-03-13 paper/DB-Schnorr-UWB.tex
Fixes refs, nbit MF thm

@@
 \section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
-\label{DB-Schnorr-UWB}
+\label{DB-Schnorr}
 
@@
 
-We also deviate from the normal technique of one-bit challenges and responses 
-otherwise used in \ac{DB} protocols.
-\Textcite{UWBPR} proposed a secure encoding for the physical 
-layer which removes the requirement of only using single-bit challenges and 
-responses for distance bounding.
-However, their protocol only works for relay attacks and cannot handle distance 
-fraud.
-This is due to a requirement of the protocol that the prover and verifier must 
-share a secret, and thus must be mutually trusted.
+We will provide two versions of the protocol.
+In the first (\cref{DB-Schnorr-UWB}), we will assume that we can send as many 
+bits in parallel as we like.
+This is a reasonable assumption thanks to the results of \textcite{UWBPR}.
 
-We will first present our version of the \ac{DB} Schnorr protocol for the 
-mutual-trust case, where the prover and verifier have a pre-shared secret.
-Then we will adapt it by introducing \iac{PKI}.
-We will use this \ac{PKI} to create \iac{AKE} which leverages that our protocol 
-is \iac{DB} \ac{ZKPK} for discrete logarithms.
-If the \ac{PKI} is based on discrete logarithms we can prove the distance bound 
-while we authenticate the key.
-This turns the mutual-trust by shared-key into mutual trust by 
-\ac{PKI}.
+Next (\cref{DB-Schnorr-PKI}), we will provide \iac{PKI} construction to make 
+the shared-key requirement of \textcite{UWBPR} more practical.
+This would allow any two devices to run our protocol as long as they are both 
+part of the \ac{PKI}.
+We use the first version of our protocol to ensure correctness of the \ac{PKI}.
+
+Finally (\cref{DB-Schnorr-nbit}), we provide a classical bit-by-bit version of 
+our protocol.
 
 \subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DB-Schnorr}
+\label{DB-Schnorr-UWB}
 
-Thanks to \textcite{UWBPR} we can keep the Schnorr protocol almost as is, since 
-relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical layer.
-\Ac{DBDF} is not a concern either, since the prover is trusted.
-The only concern, for now, is \acl{DBTF}.
-(However, we will still prove those properties, as they will be useful later.)
+In this version, we assume that we can simply send as many bits in parallel as 
+we like.
+This allows us to keep the Schnorr protocol almost as is.
 
@@
 The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
-Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
-Further, let
-\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
-\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
-key~\(k\) and finally
-\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
-and \(\UWBPRrecv\) operations.
+%Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
+%Further, let
+%\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
+%\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
+%key~\(k\) and finally
+%\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
+%and \(\UWBPRrecv\) operations.
 
@@
   \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
+    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
     & &
-    \(\DBSverify[k, g, q, A]\):
+    \(\DBSverify[g, q, A]\):
     \\
@@
     \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
 
@@
     protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
     The protocol should be repeated \(n\) times to achieve the desired 
@@
 This gives us the incentives that prevent \ac{DBTF}.
-(We also need it for \ac{DBMF}.)
+(We also need it for \ac{DBMF} and \ac{DBDF}.)
 Bundling the authentication into the distance-bounding phase (difference from 
 Brands-Chaum) prevents \ac{DBDH}.
-We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
-can do \iac{DBEDLC} attack to reduce the distance.
-(We will solve this problem further down.)
-However, the properties of \(\UWBPR\) and the unpredictability of the 
-challenges ensures \ac{DBMF} resistance (since then the prover is honest).
 
@@
 
-The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
-distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
-Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.
+By \cref{TaintedMF}, any relaying will be detected by the verifier.
+This means that the adversary must use a different strategy.
 
@@
   \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
-  \cref{DB-Schnorr}.
+  \cref{DB-Schnorr-UWB}.
 \end{theorem}
@@
 the accomplice can compute the secret key and, thus, impersonate forever.
-And any help will increase the probability of success of future attempts.
+And we show that any useful help will ensure this.
 
@@
 \end{proof}
-
-\subsection{From mutual trust to \acs*{PKI}}
-
-All \acl{DB} protocols requires hardware 
-implementations~\cite{DBonSmartphones}.
-We will use a \emph{trusted} hardware implementation to overcome the limitation 
-of \textcite{UWBPR}, \ie that the prover and verifier must be mutually trusted.
-We will need \iac{PKI} for the verifier to verify the trusted hardware.
-We will leverage this \ac{PKI} to overcome the shared-key requirement to allow 
-any two devices in this \ac{PKI} to perform \acl{DB}.
-With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
-\ac{ZKPK} which \emph{simultaneously} proves
-\begin{enumerate*}
-\item that the protocol is run by trusted hardware,
-\item that that trusted hardware is within proximity,
-\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
-\item that that knowledge is within proximity.
-\end{enumerate*}
-
-We will now introduce an extended protocol, \(\DBSHW\), which represents the 
-secure hardware implementation.
-\Cref{DBSHW-overview} presents an overview of our protocol.
-For simplicity of exposition, we present a \ac{PKI} based on plain 
-CL04~\cite{CLsignatures} signatures.
-However, CL04 is the base for the \ac{DAA} protocol, which is used for 
-\ac{TPM}, so our protocol can be modified into \iacl{DB} \ac{DAA} protocol.
-
-In summary, the difference is as follows.
-\(\DBS\) has a static shared key~\(k\) and performs \(
-  \PK[\alpha][A = g^\alpha]
-\) with a distance bound.
-\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
-\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
-performs \[
-  \PK[\alpha, \xDH, \sk_P, \sigma][
-    A = g^\alpha \land
-    \XDH = \gDH^{\xDH} \land
-    \XDHCL = \XDH^{\sk} \land
-    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
-  ],
-\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
-\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
-reblinds a signature.
-Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
-prevents any \ac{MITM} attack against the \ac{DHKE}.
-Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
-key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
-\ac{CA}.
-
-\Cref{DBSHW-overview} provides an overview.
-For simplicity of the exposition, we present a version of \(\DBSHW\) that 
-allows the user to run \(\PK[\alpha][A = g^\alpha]\) (the Schnorr 
-identification scheme) with a distance bound.
-This can, of course, be generalized to any \ac{ZKPK} for discrete logarithms, 
-for instance, CL04~\cite{CLsignatures}.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\HWprove[g, q, \alpha]\):
-    & &
-    \(\HWverify[g, q, A]\):
-    \\
-    \midrule
-
-    \multicolumn{2}{l}{%
-      Static \(\sk_P\in \ZZ_q, \sigma = (a, A, b, B, c)\)
-    }
-    & Static \(\pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL)\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Pre-setup key-agreement}} \\
-
-    \(\xDH\rgets \ZZ_{\qDH}, \XDH\gets \gDH^{\xDH}, \XDHCL\gets \XDH^{\sk}\)
-    & \(\ProtoSendRight{\XDH, \XDHCL}\)
-    & \(\yDH\rgets \ZZ_{\qDH}\)
-    \\
-
-    \(k \gets \YDH^{\xDH}\)
-    & \(\ProtoSendLeft{\YDH = \gDH^{\yDH}}\)
-    & \(k \gets \XDH^{\yDH}\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
-
-    \(r_1, r_2\rgets \ZZ_{\qCL}\)
-    &
-    &
-    \\
-
-    \(\tilde a = a^{r_1},
-      \tilde A = A^{r_1},
-      \tilde b = b^{r_1},
-      \tilde B = B^{r_1},
-      \tilde c = (c^{r_1})^{r_2}\)
-    & \(\ProtoSendRight{
-        \tilde \sigma = (\tilde a, \tilde A, \tilde b, \tilde B, \tilde c)
-      }\)
-    &
-    \\[0.5em]
-
-    \(v_x = e(\XCL, \tilde a),
-      v_{xy} = e(\XCL, \tilde b),
-      V_{xy} = e(\XCL, \tilde B),
-      v_s = e(\gCL, \tilde c)\)
-    &
-    & \(v_x = e(\XCL, \tilde a),
-      v_{xy} = e(\XCL, \tilde b),
-      V_{xy} = e(\XCL, \tilde B),
-      v_s = e(\gCL, \tilde c)\)
-    \\[0.5em]
-
-    \(\rho\rgets \ZZ_q,
-      \rhoDH \rgets \ZZ_{\qDH},
-      \rhoCL_{\sk} \rgets \ZZ_{\qCL},
-      \rhoCL_{r} \rgets \ZZ_{\qCL},
-      \rhoCL_{r'} \rgets \ZZ_{\qCL}\)
-    &
-    &
-    \\
-
-    \(R\gets g^{\rho},
-      \RDH\gets \gDH^{\rhoDH},
-      \RDHCL\gets \XDH^{\rhoCL_{\sk}},
-      \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
-    & \(\ProtoSendRight{R, \RDH, \RDHCL, \RCL}\)
-    &
-    \\
-
-    \(\forall i\in \{1, \dotsc, m\}\):
-    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
-    \\
-
-    \(s_i\gets \rho - c_i\alpha \pmod q\)
-    &
-    &
-    \\
-
-    \(\sDH_i\gets \rhoDH - c_i \xDH \pmod \qDH\)
-    &
-    &
-    \\
-
-    \(\sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r' \pmod \qCL\)
-    &
-    &
-    \\
-
-    \(\sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk \pmod \qCL\)
-    &
-    &
-    \\
-
-    \(\sCL_i^{(r)}\gets \rhoCL_{r} - c_i r \pmod \qCL\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
-
-    % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
-    \\
-
-    Fetch \(s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}\)
-    & \(\ProtoSendRight{
-      s_i, \sDH_i, \sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r)}}\)
-    & Stop clock, record \(\Delta t\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Accept if \(\Delta t < t_{\max}\) and
-    \\
-
-    % null
-    &
-    & \(R = A^{c_i} g^{s_i}\),
-    \\
-
-    % null
-    &
-    & \(\RDH = \XDH^{c_i} \gDH^{\sDH_i}\),
-    \\
-
-    % null
-    &
-    & \(\RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}\),
-    \\
-
-    % null
-    &
-    & \(v_x^{c_i} \RCL =
-          v_s^{\sCL_i^{(r')}} v_{xy}^{\sCL_i^{(\sk)}} V_{xy}^{\sCL_i^{(r)}}\),
-    \\
-
-    %
-    &
-    & \(e(\tilde a, \ZCL) = e(\gCL, \tilde A)\),
-    \\
-
-    %
-    &
-    & \(e(\tilde a, \YCL) = e(\gCL, \tilde b)\),
-    \\
-
-    %
-    &
-    & \(e(\tilde A, \YCL) = e(\gCL, \tilde B)\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
-    \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\) (except in the 
-    pre-setup phase).
-    The protocol actually proves \(
-      \PK[\alpha, \xDH, \sk, \sigma][
-        A = g^\alpha \land
-        \XDH = \gDH^{\xDH} \land
-        \XDHCL = \XDH^{\sk} \land
-        \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
-      ].
-    \)
-    This is ties \(\xDH\), and consequently \(k\), to \(\sk_P\) and \(\alpha\).
-    The protocol (setup, distance-bounding and verification phases) should be 
-    repeated \(n\) times to achieve the desired soundness and distance-bounding 
-    errors.
-  }%
-  \label{DBSHW-overview}
-\end{figure*}
-
-\paragraph*{One-time initialization}
-
-The prover's \(\DBSHW\) device must be initialized with a (static) private 
-key~\(\sk_P\) and a signature~\(\sigma\) on that key by some \ac{CA} with 
-public key~\(\pk\) and signing key~\(\sk\).
-These are computed as follows~\cite[cf.][Sect.~4.2]{CLsignatures}.
-
-We have public parameters \(\qCL, \gCL\in\GCL, \ggCL\in\GGCL, e\); where 
-\(e\colon \GCL\times \GCL\to \GGCL\) is a bilinear map, \(\gCL\in \GCL\) and 
-\(\ggCL\in \GGCL\) are generators of prime order \(\qCL\) (hence \(e(\gCL, 
-\gCL) = \ggCL\)).
-
-We let the \acg{CA} signing key be \[
-  \sk = (\xCL, \yCL, \zCL)\rgets \ZZ_{\qCL}^3
-\] and the public key be \[
-  \pk = (\qCL, \gCL, \ggCL, e, \XCL, \YCL, \ZCL),
-\] where \[
-  \XCL = \gCL^{\xCL}, \quad
-  \YCL = \gCL^{\yCL}, \quad
-  \ZCL = \gCL^{\zCL}.
-\]
-
-The prover chooses \(\sk_P\rgets \ZZ_{\qCL}\) and computes a commitment \(M = 
-\gCL^{\sk_P} Z^r\), where \(r\rgets \ZZ_{\qCL}\).
-Now the prover convinces the \ac{CA} that he knows the key by running the 
-following \ac{ZKPK} protocol: \(
-  \PK[\sk_P, r][M = \gCL^{\sk_P} Z^r].
-\)
-
-Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where \[
-  \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
-  A\gets \gCL^{\zCL}, \quad
-  b\gets a^{\yCL}, \quad
-  B\gets A^{\yCL}, \quad
-  c\gets a^{\xCL} M^{\alpha \xCL \yCL}
-\] and gives to the prover.
-
-\paragraph*{Pre-setup key-agreement}
-
-The pre-setup phase consists of a key agreement, the prover and verifier must 
-agree on a shared key~\(k\) to use for the \(\UWBPR\) protocol on the physical 
-layer.
-
-To establish \(k\), we use the \ac{DHKE}.
-The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
-\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
-\gDH^{\yDH}\) and both compute
-\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
-prime order \(\qDH\).
-The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.
-
-\paragraph*{Setup}
-
-The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
-They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
-\(\UWBPR\), instead of a static \(k\).
-\(\DBS\) performs \(
-  \PK[\alpha][A = g^\alpha]
-\) (with a distance bound) whereas \(\DBSHW\) must perform \[
-  \PK[\alpha, \xDH, \sk_P, \sigma][
-    A = g^\alpha \land
-    \XDH = \gDH^{\xDH} \land
-    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
-  ].
-\] This means that the prover (and verifier) must prepare for the other proofs 
-too.
-
-The prover blinds the signature~\(\sigma\):
-Choose \(r_1, r_2\rgets \ZZ_{\qCL}\) and compute \(\tilde \sigma = (\tilde a, 
-\tilde A, \tilde b, \tilde B, \tilde c)\), where \[
-  \tilde a = a^{r_1}, \quad
-  \tilde A = A^{r_1}, \quad
-  \tilde b = b^{r_1}, \quad
-  \tilde B = B^{r_1}, \quad
-  \tilde c = (c^{r_1})^{r_2}.
-\]
-The prover sends \(\tilde \sigma\) to the verifier.
-Now, the prover and verifier each compute \[
-  v_x\gets e(\XCL, \tilde a), \quad
-  v_{xy}\gets e(\XCL, \tilde b), \quad
-  V_{xy}\gets e(\XCL, \tilde B), \quad
-  v_s\gets e(\gCL, \tilde c).
-\]
-
-The prover chooses \[
-  \rho\rgets \ZZ_q, \quad
-  \rhoDH\rgets \ZZ_{\qDH}, \quad
-  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
-  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
-  \rhoCL_{r'}\rgets \ZZ_{\qCL}
-\] computes \[
-  R\gets g^\rho, \quad
-  \RDH\gets \gDH^{\rhoDH}, \quad
-  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
-  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
-\] and sends \(R, \RDH, \RCL\) to the verifier.
-
-The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
-The prover computes responses
-\begin{multline*}
-  s_i\gets \rho - c_i\alpha, \quad
-  \sDH_i\gets \rhoDH - c_i \xDH, \\%\quad
-  \sCL_i^{(r')}\gets \rhoCL_{r'} + c_i r', \quad
-  \sCL_i^{(\sk)}\gets \rhoCL_{\sk} - c_i \sk, \quad
-  \sCL_i^{(r)}\gets \rhoCL_r - c_i r
-\end{multline*}
-for \(i\in \{1, \dotsc, m\}\), where \(r' = r_2^{-1}\).
-
-\paragraph*{Distance bounding}
-
-The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
-\dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
-The prover instantly replies with the pre-computed \(s_i, \sDH_i, 
-\sCL_i^{(r')}, \sCL_i^{(\sk)}, \sCL_i^{(r')}\).
-Note that these values must be sent as a concatenation in \emph{one} \(\UWBPR\) 
-reply.
-The verifier stops the clock and records the round-trip time~\(\Delta t\).
-
-\paragraph*{Verification}
-
-The verifier checks that \[
-  R = A^{c_i} g^{s_i}, \quad
-  \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
-  \RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}, \quad
-  v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
-\] and that the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
-time-limit~\(t_{\max}\) (corresponding to the desired distance bound).
-Finally, the verifier checks the validity of \(\tilde \sigma\): \[
-  e(\tilde a, \ZCL) = e(\gCL, \tilde A), \quad
-  e(\tilde a, \YCL) = e(\gCL, \tilde b), \quad
-  e(\tilde A, \YCL) = e(\gCL, \tilde B).
-\]
-
-\subsection{Security analysis}
-
-There are two questions we must answer about this protocol:
-\begin{enumerate}
-  \item\label{DBSHW-MITM} Can the adversary perform \iac{MITM} attack against 
-    the \ac{DHKE}?
-  \item\label{DBSHW-anon} Does \(\XDHCL\) break anonymity?
-\end{enumerate}
-
-To answer the first question,
-by \textcite{Camenisch-phdthesis}, the above protocol is \iac{ZKPK}.
-In the case of \iac{MITM}, the prover will run the protocol using \(\XDH\) and 
-\(\sk\), while the verifier will use \(\XDH'\), possibly modified by the 
-adversary.
-The adversary's goal is to pass as knowing \(\sk\) and its signature (to 
-impersonate real hardware).
-The \(\sk\) must be the same \(\sk\) throughout the 
-subproofs~\cite{Camenisch-phdthesis}.
-In one subprotocol, the prover will prove knowledge of \(\XDH^{\sk}\).
-If \(\XDH' \neq \XDH\) used by the verifier is wrong, then by soundness the 
-proof will fail.
-
-To answer the second question,
-\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
-chosen base~\(\XDH\).
-If an adversary can use this to tell one device from another, then the 
-adversary can solve the \ac{DDH} problem.
-Consider the following reduction.
-
-Assume that \(\adv\) can tell \(\XDH^{\sk}\) from \(\XDH^{\sk'}\) with 
-probability \(\frac{1}{2} + \epsilon\) (\ie \(\epsilon\) better than guessing).
-We get the \ac{DDH} challenge tuple \(g, X = g^x, Y = g^y, Z = g^z\) and must 
-decide if \(Z = g^{xy}\) or not.
-Give \(g, R_i = g^{r_i}\) and \(X^{r_i}\) to \(\adv\), for \(1\leq i\leq n\).
-Finally, give \(\adv\) the challenge \(g, Y, Z\).
-If \(\adv\) recognizes \(Z\), then \(Z = g^{xy}\), and we will solve the 
-\ac{DDH} with the same advantage \(\epsilon\).

### 2020-03-13 paper/formal-verification.tex

--- 2020-02-26 paper/DBSchnorr-n-bit.tex
@@
-\section{Bit-by-bit distance-bounding Schnorr protocol}%
-
-As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
-protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
-
-\subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DBSchnorr-n-bit}
-
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
-We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
-
-We present the protocol in \cref{SchnorrFigure}.
-The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
-    & &
-    \(\DBSverify[g, q, A]\):
-    \\
-    \midrule
-
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
-    & \(\ProtoSendRight{R}\)
-    &
-    \\
-
-    % null
-    & \(\ProtoSendLeft{c_0, c_1}\)
-    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
-    \\
-
-    \(s_0\gets \rho - c_0\alpha \pmod q\)
-    &
-    & \(b\rgets \bin\)
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    &
-    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\) and the 
-    remaining \(l\) bits to \(1-b\).
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
-        l, j\gets 0\)} \\
-
-%    % null
-%    &
-%    & Random delay
-%    \\
-
-    % null
-    & \(\ProtoSendLeft{b_i}\)
-    & \(b_i\gets B[i]\)
-    \\
-
-    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
-    & \(\ProtoSendRight{r_i}\)
-    & Record \(\Delta t_i\)
-    \\
-
-    \(j \gets j + b_i\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
-      b\).
-      Accept if \(R = g^{s_b} A^{c_b}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired soundness 
-    and distance-bounding errors.
-  }%
-  \label{SchnorrFigure}
-\end{figure*}
-
-During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
-The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
-This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
-This is also different from the original Brands-Chaum protocol, in which the 
-prover and verifier jointly construct \emph{one} challenge with \emph{one} 
-response.
-
-We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(|q|\) response-bits from one challenge (say 
-\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
-Then the verifier can authenticate the prover by checking if \(R = 
-  g^{s_b}A^{c_b}\).
-
-\subsection{Security analysis}
-
-The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
-The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
-This allows us to prevent \ac{DBTF}.
-Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
-%reducing success of MF according to number of repetitions.
-The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
-Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\)
-although we reveal the \(l\) bits. (See \cref{l-bit-problem} for an
-  in-depth treatment of what we call the \(l\)-bit problem.)
-
-The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
-the knowledge error, \(2^{-kn}\), becomes small enough.
-Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
-
-The \ac{DB} phase protects against distance fraud.
-Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
-\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
-Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
-
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
-The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
-  s_1\).
-\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
-\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
-Now, the adversary has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
-However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
-The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
-Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
-If the adversary requests \(s_b\) in full, the adversary can also guess the 
-remaining \(|q|-l\) bits of \(s_{1-b}\).
-Based on our assumption above, the probability of guessing these bits 
-successfully is \(2^{-(|q|-l)}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-(|q|-l)n}\).
-
-The protocol is \ac{DBTF}-resistant. 
-Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
-
-The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
-Thus the probability of success is equivalent of a collision for the responses 
-for the chosen challenge --- in each round.
-
-Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check
-  the details with Douglas.}
-
-Besides the security against the standard attacks on distance-bounding
-protocols, we also need to ensure that our modification does not leak
-any information to the adversary via the aforementioned \(l\) bits.
-
-\subsection{The \(l\)-bit problem}
-\label{l-bit-problem}
-
-We will now systematically investigate the concern of the adversary
-gaining any advantage from learning \(l\) bits from one of the two challenges.
-
-\paragraph*{A special case}
-
-We will start with a special case of the \(l\)-bit problem.
-For a session~\(i\), we have two possible responses to the two challenges:
-\(s_i = r_i + c\alpha\) and \(s_i' = r_i + c'\alpha\).
-Let \(c = 1\) and \(c' = 0\).
-We assume that the adversary learns all \(m\) bits of \(s_i\), but only \(l\) 
-bits of \(s_i'\).
-This special case yields the linear equation system
-\begin{align*}
-  s_i &= r_i + \alpha
-  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha &\pmod q\\
-  s_i'[j_1] &= b_{j_1} &\pmod 2\\
-  s_i'[j_2] &= b_{j_2} &\pmod 2\\
-            &\vdots \\
-  s_i'[j_l] &= b_{j_l}, &\pmod 2
-\end{align*}
-where \(s_i'[j]\) denotes the \(j\)th bit of \(s_i'\), and \(j_1, \dotsc, 
-j_l\in \{0, \dotsc, m-1\}\) are indices for the bits chosen by the adversary 
-and \(b_{j_1}, \dotsc, b_{j_l}\in \bin\) are the bit values.
-
-\begin{lemma}
-  Assume the special case given above.
-  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
-  we cannot solve for \(\alpha\).
-\end{lemma}
-\begin{proof}
-  The equation system above yields \(l+1\) equations and \(m+1\) variables.
-  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
-  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
-  (\(\alpha\) is not repeated).
-  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
-  After some rewriting we find that
-  \begin{align*}
-    n(l+1) &< nm+1 \\
-    l+1 &< m + \frac{1}{n} \\
-    l &< m + \frac{1}{n} -1.
-  \end{align*}
-  Which concludes the proof.
-\end{proof}
-
-The number of possible solutions is vital for us, since that is an estimate of 
-how difficult it is for the adversary to guess \(\alpha\).
-
-\begin{lemma}\label{simple-l-bit-advantage}
-  Assume the special case above.
-  There are \(m-l\) free variables, each taking a value from \(\bin\).
-  This yields \(2^{m-l}-1\) unique solutions for each session.
-\end{lemma}
-\begin{proof}
-  The result directly follows from the fact that there are \(m-l\) free 
-  variables.
-  Each free variable can only take two possible values (0 or 1), consequently 
-  there are \(2^{m-l}-1\) unique solutions.
-\end{proof}
-
-\paragraph*{Arbitrarily chosen \(c\neq c'\)}
-
-For any choice of \(c\) and \(c'\) such that \(c\neq c'\), we have
-\begin{align}
-  \label{eqn:general-c}
-  s_i &= r_i + c\alpha &\pmod q\\
-  \label{eqn:general-cprime}
-  s_i' &= r_i + c'\alpha. &\pmod q
-\end{align}
-We can transform this system of equations into our special case above by 
-Gaussian elimination: add \cref{eqn:general-c} multiplied by \(\frac{c'}{c}\) 
-to \cref{eqn:general-cprime}.
-The multiplicative inverse \(\frac{1}{c}\) exists since \(q\) is prime.
-This proves the following lemma.
-
-\begin{lemma}
-  Any choice of \(c, c'\) can be turned into our special case of \(c = 1, c' = 
-  0\).
-\end{lemma}
-
-This means that \cref{simple-l-bit-advantage} is also true for the general case.
-
-\paragraph*{The unconditional \(l\)-bit problem}
-
-We run the protocol \(n\) times and let the adversary learn \(m+l\) bits of the 
-result~\(s_i, s_i'\).
-This yields the following equation system:
-\begin{align*}
-  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha &\pmod q\\
-  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha &\pmod q\\
-  \vdots \\
-  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha &\pmod q\\
-  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha, &\pmod 
-  q
-\end{align*}
-where \(m+l\) of \(s_i[j]\)'s and \(s_i'[j']\)'s for each \(i\) are known by 
-the adversary.
-
-\begin{lemma}\label{l-bit-advantage}
-  If \[l < m-1+\frac{1}{n}-\frac{f(\lambda)}{n},\] then there are at least 
-  \(2^{f(\lambda)}-1\) unique solutions, for some function~\(f\) of the 
-  security parameter~\(\lambda\).
-\end{lemma}
-\begin{proof}
-  Consider one instance of the protocol:
-  \begin{align*}
-    s_i[0]2^0 + \dotsb + s_i[m-1]2^{m-1} &= r_i + c\alpha \\
-    s_i'[0]2^0 + \dotsb + s_i'[m-1]2^{m-1} &= r_i + c'\alpha.
-  \end{align*}
-  This yields \(2m+2\) variables with two equations, thus \(2m\) free variables.
-  Let the adversary learn \(m+l\) of the bits, \ie left-hand side \(s_i[j]\)'s or 
-  \(s_i'[j']\)'s.
-  This leaves \(2m-(m+l) = m-l\) free variables and \(2^{m-l}-1\) possible 
-  solutions.
-
-  Repeat this \(n\) times.
-  This yields \(n(2m+1)+1\) variables and \(2n\) equations, thus \(2nm+n+1-2n = 
-  2mn - n +1 = n(2m-1)+1\) free variables.
-  Let the adversary learn \(m+l\) bits in each round, thus \(n(m+l)\) in total.
-  This yields \(n(2m-1)+1 -n(m+l) = 2nm-n+1-nm-nl = nm-n+1-nl = n(m-1-l)+1\) 
-  free variables and \(2^{n(m-1-l)+1}-1\) unique solutions.
-  Consequently, if we want at least \(2^{f(\lambda)}-1\) unique solutions, we 
-  have that
-  \begin{equation*}
-    nm-n-nl+1 > f(\lambda) \iff m-1+\frac{1}{n}-\frac{f(\lambda)}{n} > l.
-  \end{equation*}
-  Which concludes the proof.
-\end{proof}
-
-\paragraph*{The \(l\)-bit problem with commitments}
-
-The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
-g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
-This means that
-\begin{align*}
-  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
-                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
-                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
-\end{align*}
-We will now show how the hardenss of finding \(s'_\text{unknown}\) relates to 
-the hardness of finding discrete logarithms.
-
-\begin{definition}[\Acl*{DLP}]
-  Let \(g\) be a generator for a group of prime order~\(q\).
-  Given \(g, q, A = g^\alpha\), compute \(\alpha\).
-\end{definition}
-
-\begin{definition}[DB-Schnorr Problem]%
-  \label{DBSchnorr-problem}
-  Let \(g\) be a generator for a group of prime order~\(q\).
-  Give \(g, q, R = g^\rho A = g^\alpha\) to the adversary.
-  Let the adversary choose \(c\) and additionally give him \(\hat s\) such that 
-  \(\hat s\) are the \(l\) \emph{least significant} bits of \(s = \rho + 
-  c\alpha \pmod q\).
-  The adversary wins if he returns \(\hat s'\) such that \(\hat s + \hat s' = s 
-  \pmod q\).
-\end{definition}
-
-\begin{lemma}
-  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
-  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
-  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
-  \(\epsilon 2^{-(l+k)}\).
-\end{lemma}
-
-\begin{proof}
-  We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
-  \(\algA_{\DBS}\) and the \ac{DLP} challenge \(g, q, A_{\text{DL}}\).
-  Assume that \(\algA_{\DBS}\) succeeds with probability \(\epsilon\).
-
-  We proceed as follows.
-  Guess \(c\rgets \ZZ_k\), choose \(\hat s\rgets \ZZ_{2^l}\).
-  Let \(\hat R\gets A_{\DBS}^c A_{\text{DL}} g^{\hat s}\) and give
-  \(\hat R\) to \(\algA_{\DBS}\).
-  If \(c'\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R)\) returns \(c'\neq c\), 
-  abort.
-  The probability of success is \(2^{-k}\).
-  Otherwise, give \(\hat s\) to \(\algA_{\DBS}\).
-  Now, by construction, we have that \(
-    \hat R = A_{\DBS}^c g^{\hat s} A_{\text{DL}}.
-  \)
-
-  If \(A_{\text{DL}} = g^{\alpha_{\text{DL}}}\) is chosen such that 
-  \(\alpha_{\text{DL}}\) has the \(l\) least significant bits set to zero 
-  (probability \(2^{-l}\)), then will have \(
-    \alpha_{\text{DL}}\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R, \hat s)
-  \) with probability \(\epsilon\).
-  Thus, the total probability of success is \(
-    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-(l+k)}.
-  \)
-\end{proof}
-
-As mentioned above, both \(l\) and \(k\) are logarithmic in the security 
-parameter.
-
-\endinput
-\subsection{Formal Verification}
+\section{Formal Verification}
 

### 2020-03-13 paper/intro.tex
Edits intro: contributions and outline

@@
 
-The first (and second) contribution enables us to do \ac{DB} \ac{ABC}.
-The third enables us also to do \ac{DB} \ac{ABC}, just without \ac{DBTF} 
-resistance.
-
-Our main contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
-for \ac{DB}, but which is different from that of \textcite{DistanceBounding} or 
-\textcite{Bussard-Bagga} (DBPK-Log).
-Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
-including \ac{DBDH} (which was an attack against the original protocol of 
-Brands and Chaum) and \ac{DBTF}.
-More importantly, it is public-key\footnote{%
-  The majority of published works are in the shared-key setting.
-  However, both the protocol by \textcite{DistanceBounding} and that of 
-  \textcite{Bussard-Bagga} are public key.
-}, handles malicious impersonating verifiers.
-Since it is based on the Schnorr protocol, it provides a distance-bounded 
-\ac{PK} for discrete logarithms.
-That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
-distance-bounding version and thus make general privacy-preserving, 
-attribute-based credential systems distance bounding.
+The first (and second) contribution enables us to do distance-bounding 
+privacy-preserving attribute-based credentials based on discrete logarithms, 
+\eg~\cite{Camenisch-phdthesis} and~\cite{CLsignatures}.
+To our knowledge, no other distance-bounding protocol achieves this.
+The third contribution (bit-by-bit version) also enables us to do the same, 
+just without \ac{DBTF} resistance.
 
@@
 The paper is organized as follows.
-\Cref{system-model}, we describe our system model and summarize the desired 
-properties 
-We then discuss related work in terms of these properties in 
-\cref{related-work}, and in \cref{building-blocks}, we give 
-the relevant background on the building blocks of our solution.
-
-\Cref{DB-Schnorr-UWB}, we present a new \ac{DB} version of the Schnorr protocol, 
-different from that originally proposed by \textcite{DistanceBounding}.
-We provide a proof of its security and formally verify it using 
-Tamarin~\cite{TamarinDB}.
-
-We analyze its security in \cref{SecurityAnalysis} and estimate its performance 
-in \cref{PerformanceAnalysis}.
-
-Finally, we discuss our assumptions and results in \cref{Discussion} and give 
-our conclusions in \cref{Conclusion}.
+\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
+\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
+send all bits at the same time.
+\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
+version of the protocol in practice.
+\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
+Finally, we conclude with a discussion of our results in \cref{Conclusion}.

### 2020-03-13 paper/related-work.tex

@@
 \textcite{DistanceBounding} were the first to adapt the Schnorr
-protocol to achieve distance-bounding anonymous credentials. Their
-approach has been shown to be vulnerable to \ac{DBDH} \cite{TamarinDB}.
+protocol to achieve distance-bounding.
+Unfortunately, their approach has been shown to be vulnerable to 
+\ac{DBDH}~\cite[\eg][]{TamarinDB}.
 
@@
 The prover and verifier run a PK that ties the commits to the private key.
-A malicious prover can reduce all the N challenges in the fast phase
+However, a malicious prover can reduce all the N challenges in the fast phase
 to 1. This allows both distance and terrorist
-fraud~\cite{AttacksBussardBagga}.
+fraud~\cite{Bussard-Bagga-attack}.
 
 One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
-
-% One protocol exists in the literature that provides \acp{PPK} with most of the 
-% desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
-%   that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
-%   shorter notation.}.
-% ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-%   \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
-% logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
-% details).
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} 
+protocol for quadratic residues (\ie protocols of the form \(
+  \PPK[\alpha][a = \alpha^2]
+\)), while in our context, we need \iac{PPK} protocol for discrete logarithms 
+(\ie \(\PPK[\alpha][a = g^\alpha]\)).
+Also, ProProx's proofs of knowledge are only for \emph{bit commitments} of the 
+above form.

### 2020-03-13 paper/DB-Schnorr-PKI.tex

@@
 \end{enumerate}
+To justify the first question, we use a plain \ac{DHKE} to agree on \(k\), 
+start using \(k\) for \ac{DB} and during the \ac{DB} do the authentication.
+To justify the second question, we use CL04 anonymous 
+credentials~\cite{CLsignatures}.
+These provide anonymity.
+However, revealing \(\XDHCL = \XDH^{\sk}\) is not part of CL04.
+So we must show that \(\XDHCL\) maintains anonymity.
 

### 2020-03-13 paper/distance-bounding.tex
Changes some equations to display, fixes bugs in eqns

@@
   \label{TaintedMF}
-  A time-critical round
-  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
-  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
-  verifier, is \emph{tainted} by the round
-  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
-  of a prover--adversary session~\(\sid'\) if
+  A time-critical round \[
+    \Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})
+  \] of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
+  verifier, is \emph{tainted} by the round \[
+    \Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})
+  \] of a prover--adversary session~\(\sid'\) if
   \begin{align*}
@@
 prover cooperates with the adversary to make the verifier accept.
+This means that we must disallow relay \emph{scheduling}: with 
+\cref{TaintedMF}, the prover and adversary could relay a function of every 
+answer, then the adversary could just apply the inverse function before sending 
+the answer to the verifier.
 

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Changes some equations to display, fixes bugs in eqns

@@
 \end{align*}
-We will now show how the hardenss of finding \(s'_\text{unknown}\) relates to 
+We will now show how the hardenss of finding \(s'_{\text{unknown}}\) relates to 
 the hardness of finding discrete logarithms.

### 2020-03-13 paper/DB-Schnorr-PKI.tex
Changes some equations to display, fixes bugs in eqns
Fixes some equations that breaks boxes

@@
 \gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
-performs \[
-  \PK[\alpha, \xDH, \sk_P, \sigma][
+performs
+\begin{multline*}
+  \PK\big\{ (\alpha, \xDH, \sk_P, \sigma) : \\
     A = g^\alpha \land
     \XDH = \gDH^{\xDH} \land
-    \XDHCL = \XDH^{\sk} \land
+    \XDHCL = \XDH^{\sk} \land \\
     \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
-  ],
-\] also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
+  \big\},
+\end{multline*}
+also with a distance bound and \(A = g^\alpha\) on behalf of the user; where 
 \(\sk_P\) is the prover's private key, \(\sigma\) is a signature issued with 
@@
 
-Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where \[
+Now the \ac{CA} computes the signature~\(\sigma = (a, A, b, B, c)\), where
+\begin{multline*}
   \alpha\rgets \ZZ_{\qCL}, \quad a\gets \gCL^\alpha, \quad
   A\gets \gCL^{\zCL}, \quad
-  b\gets a^{\yCL}, \quad
+  b\gets a^{\yCL}, \\
   B\gets A^{\yCL}, \quad
   c\gets a^{\xCL} M^{\alpha \xCL \yCL}
-\] and gives to the prover.
+\end{multline*}
+and gives to the prover.
 
@@
 
-The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-\dotsc, c_m\rgets \bin^l\), and sends these to the prover.
+The verifier chooses \(m\) challenges of length \(l\), \[
+  c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l,
+\] and sends these to the prover.
 The prover computes responses

### 2020-03-13 paper/ZKPK.tex
Expands PK in ZKPK section

@@
 \end{equation}
-which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
+is \iac{PK} protocol where the prover proves knowledge of \(\alpha, \beta, 
+\gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and 
+\(y' = \hat g^\gamma\), respectively.
 Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.

### 2020-03-13 paper/intro.tex
Removes non-breaking spaces in intro
Clarifies second contribution

@@
 the \ac{PKI} to convince a verifier that this is the case.
+This replaces everyone having the same static key~\(k\) with everyone having a 
+unique key which is signed by \iac{CA} of the \ac{PKI}, which allows for 
+revocation.
 The solution relies on our first contribution.
@@
 privacy-preserving attribute-based credentials based on discrete logarithms, 
-\eg~\cite{Camenisch-phdthesis} and~\cite{CLsignatures}.
+\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
 To our knowledge, no other distance-bounding protocol achieves this.
@@
 \Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
-Finally, we conclude with a discussion of our results in \cref{Conclusion}.
+\Cref{formal-verification} describes our effort to formally verify the protocol 
+using Tamarin.
+Finally, we conclude with discussion and conclusions in 
+\cref{Discussion,Conclusion}.

### 2020-03-13 paper/distance-bounding.tex
Uses acro for DFKO model

@@
 \citet{DB-BMV} and another by \citet{DB-DFKO}.
-We will use the framework of \citeauthor{DB-DFKO} with extensions by 
-\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
-\cref{DB-definitions}).
+We will use the model of \citeauthor{DB-DFKO} (the \acs*{DFKOmodel}) with 
+extensions by \textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions 
+in \cref{DB-definitions}).
 
@@
 
-The DFKO framework~\cite{DB-DFKO} uses an abstract clock~\(\marker\colon \NN\to 
-  \NN\) which is strictly increasing and orders the adversary's actions.
+The \ac{DFKOmodel} uses an abstract clock~\(\marker\colon \NN\to \NN\) which is 
+strictly increasing and orders the adversary's actions.
 We let

### 2020-03-13 paper/ZKPK.tex
Comments out SPK (not used in this paper)

@@
 
-When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
-\begin{equation*}\label{SPKexample}
-  \sigma\gets \SPK[\alpha, \beta, \gamma]%
-  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
-  [m],
-\end{equation*}
-which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).
+%When a proof of knowledge is turned into a signature using the Fiat-Shamir heuristic~\cite{FiatShamirHeuristic}, we will denote it as
+%\begin{equation*}\label{SPKexample}
+%  \sigma\gets \SPK[\alpha, \beta, \gamma]%
+%  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
+%  [m],
+%\end{equation*}
+%(Signature based on Proofs of Knowledge) which yields a signature \(\sigma\) on 
+%\(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = 
+%g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).

### 2020-03-13 paper/intro.tex
adds reference to related work section in outline
Adds brief intro

@@
 \label{Introduction}
+
+Although there are numerous contributions in the field of \ac{DB} 
+authentication protocols, the majority of them are shared-key protocols.
+This means that the prover and the verifier must share a secret.
+This might work for key-less entry protocols for cars, where the car and keyfob 
+can share a key.
+But it does not work for ubiquitous \ac{DB} authentication.
+
+Our work present contributions in the area of \ac{DB} public-key protocols, 
+particularly \ac{DB} \ac{ZKPK}.
+This allows anyone to act as a verifier, unlike in the shared-key scenario 
+where the verifier must be trusted.
+The \ac{ZK} property also enables privacy properties such as anonymity.
 
@@
 First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
-\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
-model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
+\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
 This version is based on the assumption that we can transmit all bits at once, 

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Fixes some equations that breaks boxes
Better framing of l-bits problem (fixes #44)

@@
 
-Before we proceed to other security properties, we will start with the 
-\(l\)-bit problem.
-We will now analyse how much damage leaking those \(l\) bits of the second 
-response does.
+Before we proceed to other security properties, we will address the \(l\)-bit 
+problem:
+what advantage does the adversary get from those \(l\) leaked bits of the 
+second response?
 

### 2020-03-13 paper/intro.tex

@@
 Our work present contributions in the area of \ac{DB} public-key protocols, 
-particularly \ac{DB} \ac{ZKPK}.
+particularly \ac{DB} \acp{ZKPK}.
 This allows anyone to act as a verifier, unlike in the shared-key scenario 
 where the verifier must be trusted.
-The \ac{ZK} property also enables privacy properties such as anonymity.
+The \ac{ZK} property also enables a variety of privacy properties, such as 
+anonymity.
 
@@
 not bit-by-bit as normally required for \ac{DB}.
-This assumption is reasonable by the results of \textcite{UWBPR}.
+This assumption is motivated by the results of \textcite{UWBPR}.
 
@@
 The paper is organized as follows.
+\Cref{related-work} discusses related work.
 \Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Fixes typo
Removes less necessary part of l-bits section

@@
 
-\paragraph*{A special case}
-
-We will start with a special case of the \(l\)-bit problem.
-For a session~\(i\), we have two possible responses to the two challenges:
-\(s_i = r_i + c\alpha\) and \(s_i' = r_i + c'\alpha\).
-Let \(c = 1\) and \(c' = 0\).
-We assume that the adversary learns all \(m\) bits of \(s_i\), but only \(l\) 
-bits of \(s_i'\).
-This special case yields the linear equation system
-\begin{align*}
-  s_i &= r_i + \alpha
-  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha &\pmod q\\
-  s_i'[j_1] &= b_{j_1} &\pmod 2\\
-  s_i'[j_2] &= b_{j_2} &\pmod 2\\
-            &\vdots \\
-  s_i'[j_l] &= b_{j_l}, &\pmod 2
-\end{align*}
-where \(s_i'[j]\) denotes the \(j\)th bit of \(s_i'\), and \(j_1, \dotsc, 
-j_l\in \{0, \dotsc, m-1\}\) are indices for the bits chosen by the adversary 
-and \(b_{j_1}, \dotsc, b_{j_l}\in \bin\) are the bit values.
-
-\begin{lemma}
-  Assume the special case given above.
-  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
-  we cannot solve for \(\alpha\).
-\end{lemma}
-\begin{proof}
-  The equation system above yields \(l+1\) equations and \(m+1\) variables.
-  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
-  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
-  (\(\alpha\) is not repeated).
-  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
-  After some rewriting we find that
-  \begin{align*}
-    n(l+1) &< nm+1 \\
-    l+1 &< m + \frac{1}{n} \\
-    l &< m + \frac{1}{n} -1.
-  \end{align*}
-  Which concludes the proof.
-\end{proof}
-
-The number of possible solutions is vital for us, since that is an estimate of 
-how difficult it is for the adversary to guess \(\alpha\).
-
-\begin{lemma}\label{simple-l-bit-advantage}
-  Assume the special case above.
-  There are \(m-l\) free variables, each taking a value from \(\bin\).
-  This yields \(2^{m-l}-1\) unique solutions for each session.
-\end{lemma}
-\begin{proof}
-  The result directly follows from the fact that there are \(m-l\) free 
-  variables.
-  Each free variable can only take two possible values (0 or 1), consequently 
-  there are \(2^{m-l}-1\) unique solutions.
-\end{proof}
-
-\paragraph*{Arbitrarily chosen \(c\neq c'\)}
-
-For any choice of \(c\) and \(c'\) such that \(c\neq c'\), we have
-\begin{align}
-  \label{eqn:general-c}
-  s_i &= r_i + c\alpha &\pmod q\\
-  \label{eqn:general-cprime}
-  s_i' &= r_i + c'\alpha. &\pmod q
-\end{align}
-We can transform this system of equations into our special case above by 
-Gaussian elimination: add \cref{eqn:general-c} multiplied by \(\frac{c'}{c}\) 
-to \cref{eqn:general-cprime}.
-The multiplicative inverse \(\frac{1}{c}\) exists since \(q\) is prime.
-This proves the following lemma.
-
-\begin{lemma}
-  Any choice of \(c, c'\) can be turned into our special case of \(c = 1, c' = 
-  0\).
-\end{lemma}
-
-This means that \cref{simple-l-bit-advantage} is also true for the general case.
-
 \paragraph*{The unconditional \(l\)-bit problem}
@@
 \end{align*}
-We will now show how the hardenss of finding \(s'_{\text{unknown}}\) relates to 
+We will now show how the hardness of finding \(s'_{\text{unknown}}\) relates to 
 the hardness of finding discrete logarithms.

### 2020-03-13 paper/DB-Schnorr-nbit.tex
Moves l-bits proofs to appendix

@@
 \end{lemma}
-\begin{proof}
-  Consider one instance of the protocol:
-  \begin{align*}
-    s_i[0]2^0 + \dotsb + s_i[m-1]2^{m-1} &= r_i + c\alpha \\
-    s_i'[0]2^0 + \dotsb + s_i'[m-1]2^{m-1} &= r_i + c'\alpha.
-  \end{align*}
-  This yields \(2m+2\) variables with two equations, thus \(2m\) free variables.
-  Let the adversary learn \(m+l\) of the bits, \ie left-hand side \(s_i[j]\)'s or 
-  \(s_i'[j']\)'s.
-  This leaves \(2m-(m+l) = m-l\) free variables and \(2^{m-l}-1\) possible 
-  solutions.
 
-  Repeat this \(n\) times.
-  This yields \(n(2m+1)+1\) variables and \(2n\) equations, thus \(2nm+n+1-2n = 
-  2mn - n +1 = n(2m-1)+1\) free variables.
-  Let the adversary learn \(m+l\) bits in each round, thus \(n(m+l)\) in total.
-  This yields \(n(2m-1)+1 -n(m+l) = 2nm-n+1-nm-nl = nm-n+1-nl = n(m-1-l)+1\) 
-  free variables and \(2^{n(m-1-l)+1}-1\) unique solutions.
-  Consequently, if we want at least \(2^{f(\lambda)}-1\) unique solutions, we 
-  have that
-  \begin{equation*}
-    nm-n-nl+1 > f(\lambda) \iff m-1+\frac{1}{n}-\frac{f(\lambda)}{n} > l.
-  \end{equation*}
-  Which concludes the proof.
-\end{proof}
+The proof is in \cref{proofs-lbit}.
 
@@
 
-\begin{proof}
-  We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
-  \(\algA_{\DBS}\) and the \ac{DLP} challenge \(g, q, A_{\text{DL}}\).
-  Assume that \(\algA_{\DBS}\) succeeds with probability \(\epsilon\).
-
-  We proceed as follows.
-  Guess \(c\rgets \ZZ_k\), choose \(\hat s\rgets \ZZ_{2^l}\).
-  Let \(\hat R\gets A_{\DBS}^c A_{\text{DL}} g^{\hat s}\) and give
-  \(\hat R\) to \(\algA_{\DBS}\).
-  If \(c'\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R)\) returns \(c'\neq c\), 
-  abort.
-  The probability of success is \(2^{-k}\).
-  Otherwise, give \(\hat s\) to \(\algA_{\DBS}\).
-  Now, by construction, we have that \(
-    \hat R = A_{\DBS}^c g^{\hat s} A_{\text{DL}}.
-  \)
-
-  If \(A_{\text{DL}} = g^{\alpha_{\text{DL}}}\) is chosen such that 
-  \(\alpha_{\text{DL}}\) has the \(l\) least significant bits set to zero 
-  (probability \(2^{-l}\)), then will have \(
-    \alpha_{\text{DL}}\gets \algA_{\DBS}(g, q, A_{\DBS}, \hat R, \hat s)
-  \) with probability \(\epsilon\).
-  Thus, the total probability of success is \(
-    \epsilon 2^{-l} 2^{-k} = \epsilon 2^{-(l+k)}.
-  \)
-\end{proof}
+The proof is in \cref{proofs-lbit}.
 

### 2020-03-13 paper/ZKPK-instantiations.tex
Changes some equations to display, fixes bugs in eqns
Moves ZKPK instantiations to the appendix

@@
-\paragraph*{Instantiations of the \acs{ZKPK} protocols}
+\section{Instantiations of the \acs{ZKPK} protocols}%
+\label{ZKPK-instantiations}
 
-For the convenience of the reader, we summarize 
-(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
-discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
-which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
-The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
-    \prod_{i=1}^n g_i^{\alpha_i}]\).
+Following is a brief summary from~\cite{Camenisch-phdthesis} of how to 
+instantiate general \acp{ZKPK} for discrete logarithms based on the Schnorr 
+identification scheme~\cite{Schnorr}, which, in its original form, can be 
+written as \(\PK[\alpha][A = g^\alpha]\).
+The generalized form would be \[
+  \PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}].
+\]
 This could equivalently be written as
@@
 
-For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
-Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
-illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
-
-\begin{figure}
-  \small
-  \begin{algorithmic}
-    \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
-      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
-      \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
-      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
-      \For{$1\leq i\leq n$}
-        \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
-      \EndFor{}
-      \State{\Return{$(\{s_i\}_i, c)$}}
-    \EndFunction{}
-  \end{algorithmic}
-
-  \begin{algorithmic}
-    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
-      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
-      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
-        \State{\Return{$\top$}}
-      \EndIf{}
-      \State{\Return{$\bot$}}
-    \EndFunction{}
-  \end{algorithmic}
-  \caption{%
-    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
-    using the Fiat-Shamir heuristic on the Schnorr identification 
-    scheme~\cite{Camenisch-phdthesis}.
-  }%
-  \label{SPKalgorithms}
-\end{figure}
+%For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
+%Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
+%illustrated as \(\SPKprove\) and \(\SPKverify\) in \cref{SPKalgorithms}.
+%
+%\begin{figure}
+%  \small
+%  \begin{algorithmic}
+%    \Function{$\SPKprove$}{$\{g_i\}_i, q, A, \{\alpha_i\}_i, m$}
+%      \State{\(\forall i, 1\leq i\leq n\colon \rho_i\rgets \ZZ_q\)}
+%      \State{\(R\gets \prod_{i=1}^n g_i^{\rho_i}\)}
+%      \State{$c \gets H(\{g_i\}_i\concat A\concat R\concat m)$}
+%      \For{$1\leq i\leq n$}
+%        \State{$s_i \gets \rho_i - c\alpha_i \mod q$}
+%      \EndFor{}
+%      \State{\Return{$(\{s_i\}_i, c)$}}
+%    \EndFunction{}
+%  \end{algorithmic}
+%
+%  \begin{algorithmic}
+%    \Function{$\SPKverify$}{$\{g_i\}_i, q, A, m, \{s_i\}_i, c$}
+%      \State{$\hat R \gets A^c \prod_{i=1}^n g_i^{s_i}$}
+%      \If{$c = H(\{g_i\}_i\concat A\concat \hat R\concat m)$}
+%        \State{\Return{$\top$}}
+%      \EndIf{}
+%      \State{\Return{$\bot$}}
+%    \EndFunction{}
+%  \end{algorithmic}
+%  \caption{%
+%    \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
+%    using the Fiat-Shamir heuristic on the Schnorr identification 
+%    scheme~\cite{Camenisch-phdthesis}.
+%  }%
+%  \label{SPKalgorithms}
+%\end{figure}

### 2020-03-13 paper/proofs-lbit.tex

--- 2020-02-26 paper/DBSchnorr-n-bit.tex
@@
-\section{Bit-by-bit distance-bounding Schnorr protocol}%
+\section{Proofs for the l-bit problem results}%
+\label{proofs-lbit}
 
-As mentioned in \cref{related-work}, while there exists a \iac{PPK} 
-protocol~\cite{ProProx}, there is none for discrete logarithms. We will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
-
-\subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DBSchnorr-n-bit}
-
-In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
-However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
-We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
-It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
-
-We present the protocol in \cref{SchnorrFigure}.
-The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
-    & &
-    \(\DBSverify[g, q, A]\):
-    \\
-    \midrule
-
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
-    & \(\ProtoSendRight{R}\)
-    &
-    \\
-
-    % null
-    & \(\ProtoSendLeft{c_0, c_1}\)
-    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
-    \\
-
-    \(s_0\gets \rho - c_0\alpha \pmod q\)
-    &
-    & \(b\rgets \bin\)
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    &
-    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\) and the 
-    remaining \(l\) bits to \(1-b\).
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
-        l, j\gets 0\)} \\
-
-%    % null
-%    &
-%    & Random delay
-%    \\
-
-    % null
-    & \(\ProtoSendLeft{b_i}\)
-    & \(b_i\gets B[i]\)
-    \\
-
-    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
-    & \(\ProtoSendRight{r_i}\)
-    & Record \(\Delta t_i\)
-    \\
-
-    \(j \gets j + b_i\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
-      b\).
-      Accept if \(R = g^{s_b} A^{c_b}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^\alpha]\).
-    The protocol should be repeated in full to achieve the desired soundness 
-    and distance-bounding errors.
-  }%
-  \label{SchnorrFigure}
-\end{figure*}
-
-During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
-The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
-This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
-This is also different from the original Brands-Chaum protocol, in which the 
-prover and verifier jointly construct \emph{one} challenge with \emph{one} 
-response.
-
-We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
-The verifier will request all \(|q|\) response-bits from one challenge (say 
-\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
-Then the verifier can authenticate the prover by checking if \(R = 
-  g^{s_b}A^{c_b}\).
-
-\subsection{Security analysis}
-
-The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
-The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
-This allows us to prevent \ac{DBTF}.
-Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
-%reducing success of MF according to number of repetitions.
-The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
-Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
-Thus, we still have information theoretic security for \(s_{1-b}\)
-although we reveal the \(l\) bits. (See \cref{l-bit-problem} for an
-  in-depth treatment of what we call the \(l\)-bit problem.)
-
-The intuition behind the protocol security is as follows.
-To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
-the knowledge error, \(2^{-kn}\), becomes small enough.
-Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
-
-The \ac{DB} phase protects against distance fraud.
-Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
-\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
-Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
-
-The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
-The verifier will send \(|q| + l < 2|q|\) challenges.
-By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
-  s_1\).
-\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
-\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
-Now, the adversary has two options.
-First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
-However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
-The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
-Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
-Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
-If the adversary requests \(s_b\) in full, the adversary can also guess the 
-remaining \(|q|-l\) bits of \(s_{1-b}\).
-Based on our assumption above, the probability of guessing these bits 
-successfully is \(2^{-(|q|-l)}\).
-Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
-\(2^{-n}+2^{-(|q|-l)n}\).
-
-The protocol is \ac{DBTF}-resistant. 
-Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
-The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
-
-The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
-Thus the probability of success is equivalent of a collision for the responses 
-for the chosen challenge --- in each round.
-
-Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
-\daniel{I should prove this for the composed protocol, I should check
-  the details with Douglas.}
-
-Besides the security against the standard attacks on distance-bounding
-protocols, we also need to ensure that our modification does not leak
-any information to the adversary via the aforementioned \(l\) bits.
-
-\subsection{The \(l\)-bit problem}
-\label{l-bit-problem}
-
-We will now systematically investigate the concern of the adversary
-gaining any advantage from learning \(l\) bits from one of the two challenges.
-
-\paragraph*{A special case}
-
-We will start with a special case of the \(l\)-bit problem.
-For a session~\(i\), we have two possible responses to the two challenges:
-\(s_i = r_i + c\alpha\) and \(s_i' = r_i + c'\alpha\).
-Let \(c = 1\) and \(c' = 0\).
-We assume that the adversary learns all \(m\) bits of \(s_i\), but only \(l\) 
-bits of \(s_i'\).
-This special case yields the linear equation system
-\begin{align*}
-  s_i &= r_i + \alpha
-  = s_i'[m-1] 2^{m-1} + \dotsb + s_i'[1] 2^1 + s_i'[0] 2^0 + \alpha &\pmod q\\
-  s_i'[j_1] &= b_{j_1} &\pmod 2\\
-  s_i'[j_2] &= b_{j_2} &\pmod 2\\
-            &\vdots \\
-  s_i'[j_l] &= b_{j_l}, &\pmod 2
-\end{align*}
-where \(s_i'[j]\) denotes the \(j\)th bit of \(s_i'\), and \(j_1, \dotsc, 
-j_l\in \{0, \dotsc, m-1\}\) are indices for the bits chosen by the adversary 
-and \(b_{j_1}, \dotsc, b_{j_l}\in \bin\) are the bit values.
-
-\begin{lemma}
-  Assume the special case given above.
-  If \(l < m+\frac{1}{n}-1\), then the equation system is underdetermined and 
-  we cannot solve for \(\alpha\).
-\end{lemma}
-\begin{proof}
-  The equation system above yields \(l+1\) equations and \(m+1\) variables.
-  If we repeat the protocol \(n\) times, we get \(n\) such sessions.
-  This yields an equation system of \(n(l+1)\) equations and \(nm+1\) variables 
-  (\(\alpha\) is not repeated).
-  If \(n(l+1) < nm+1\), this system is underdetermined and cannot be solved.
-  After some rewriting we find that
-  \begin{align*}
-    n(l+1) &< nm+1 \\
-    l+1 &< m + \frac{1}{n} \\
-    l &< m + \frac{1}{n} -1.
-  \end{align*}
-  Which concludes the proof.
-\end{proof}
-
-The number of possible solutions is vital for us, since that is an estimate of 
-how difficult it is for the adversary to guess \(\alpha\).
-
-\begin{lemma}\label{simple-l-bit-advantage}
-  Assume the special case above.
-  There are \(m-l\) free variables, each taking a value from \(\bin\).
-  This yields \(2^{m-l}-1\) unique solutions for each session.
-\end{lemma}
-\begin{proof}
-  The result directly follows from the fact that there are \(m-l\) free 
-  variables.
-  Each free variable can only take two possible values (0 or 1), consequently 
-  there are \(2^{m-l}-1\) unique solutions.
-\end{proof}
-
-\paragraph*{Arbitrarily chosen \(c\neq c'\)}
-
-For any choice of \(c\) and \(c'\) such that \(c\neq c'\), we have
-\begin{align}
-  \label{eqn:general-c}
-  s_i &= r_i + c\alpha &\pmod q\\
-  \label{eqn:general-cprime}
-  s_i' &= r_i + c'\alpha. &\pmod q
-\end{align}
-We can transform this system of equations into our special case above by 
-Gaussian elimination: add \cref{eqn:general-c} multiplied by \(\frac{c'}{c}\) 
-to \cref{eqn:general-cprime}.
-The multiplicative inverse \(\frac{1}{c}\) exists since \(q\) is prime.
-This proves the following lemma.
-
-\begin{lemma}
-  Any choice of \(c, c'\) can be turned into our special case of \(c = 1, c' = 
-  0\).
-\end{lemma}
-
-This means that \cref{simple-l-bit-advantage} is also true for the general case.
-
-\paragraph*{The unconditional \(l\)-bit problem}
-
-We run the protocol \(n\) times and let the adversary learn \(m+l\) bits of the 
-result~\(s_i, s_i'\).
-This yields the following equation system:
-\begin{align*}
-  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha &\pmod q\\
-  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha &\pmod q\\
-  \vdots \\
-  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha &\pmod q\\
-  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha, &\pmod 
-  q
-\end{align*}
-where \(m+l\) of \(s_i[j]\)'s and \(s_i'[j']\)'s for each \(i\) are known by 
-the adversary.
-
-\begin{lemma}\label{l-bit-advantage}
-  If \[l < m-1+\frac{1}{n}-\frac{f(\lambda)}{n},\] then there are at least 
-  \(2^{f(\lambda)}-1\) unique solutions, for some function~\(f\) of the 
-  security parameter~\(\lambda\).
-\end{lemma}
-\begin{proof}
+\begin{proof}[Proof of \cref{l-bit-advantage}]
   Consider one instance of the protocol:
@@
 
-\paragraph*{The \(l\)-bit problem with commitments}
-
-The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
-g^{r_i}\) and a commitment to \(\alpha\) in the form of \(A = g^\alpha\).
-This means that
-\begin{align*}
-  R = A^{-c'} g^{s'} &= A^{-c'} g^{s'[0] 2^0 + \dotsb + s'[m-1] 2^{m-1}} \\
-                     &= A^{-c'} g^{s'[0] 2^0} \dotsb g^{s'[m-1] 2^{m-1}} \\
-                     &= A^{-c'} g^{s'_{\text{known}}} g^{s'_{\text{unknown}}}.
-\end{align*}
-We will now show how the hardenss of finding \(s'_\text{unknown}\) relates to 
-the hardness of finding discrete logarithms.
-
-\begin{definition}[\Acl*{DLP}]
-  Let \(g\) be a generator for a group of prime order~\(q\).
-  Given \(g, q, A = g^\alpha\), compute \(\alpha\).
-\end{definition}
-
-\begin{definition}[DB-Schnorr Problem]%
-  \label{DBSchnorr-problem}
-  Let \(g\) be a generator for a group of prime order~\(q\).
-  Give \(g, q, R = g^\rho A = g^\alpha\) to the adversary.
-  Let the adversary choose \(c\) and additionally give him \(\hat s\) such that 
-  \(\hat s\) are the \(l\) \emph{least significant} bits of \(s = \rho + 
-  c\alpha \pmod q\).
-  The adversary wins if he returns \(\hat s'\) such that \(\hat s + \hat s' = s 
-  \pmod q\).
-\end{definition}
-
-\begin{lemma}
-  Given an algorithm~\(\algA_{\DBS}\) that solves the DB-Schnorr Problem 
-  (\cref{DBSchnorr-problem}) with probability \(\epsilon\), we can construct an 
-  algorithm \(\algA_{\text{DL}}\) that solves the \ac{DLP} with probability 
-  \(\epsilon 2^{-(l+k)}\).
-\end{lemma}
-
-\begin{proof}
+\begin{proof}[Proof of \cref{DBSPtoDLP}]
   We will now construct the algorithm \(\algA_{\text{DL}}\) given the algorithm 
@@
 \end{proof}
-
-As mentioned above, both \(l\) and \(k\) are logarithmic in the security 
-parameter.
-
-\endinput
-\subsection{Formal Verification}
-
-We formally verify the protocol security properties using the Tamarin
-prover~\cite{meier2013tamarin}. Tamarin does not originally include
-the possibility to reason on time and space in its model.  However,
-thanks to a recent work by \textcite{TamarinDB}, the common properties
-can be equivalently characterized with a causality-based definition
-relying only on the order of messages.
-
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
-It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
-
-Tamarin's auto-prover validated the soundness and correctness
-properties (in negligible computation time) and proved the security
-properties used in~\cite{TamarinDB}. In the meantime,
-\textcite{TamarinDBTF} introduced the notion of post-collusion
-security which enabled them to prove \ac{DBTF}. In future work, we
-will use this extension on our protocol.

### 2020-03-13 paper/ZKPK-instantiations.tex

@@
-\section{Instantiations of the \acs{ZKPK} protocols}%
-\label{ZKPK-instantiations}
+\paragraph*{Instantiations of the \acs{ZKPK} protocols}
 
-Following is a brief summary from~\cite{Camenisch-phdthesis} of how to 
-instantiate general \acp{ZKPK} for discrete logarithms based on the Schnorr 
-identification scheme~\cite{Schnorr}, which, in its original form, can be 
-written as \(\PK[\alpha][A = g^\alpha]\).
+For the convenience of the reader, we summarize 
+(from~\cite{Camenisch-phdthesis}) how to instantiate general \acp{ZKPK} for 
+discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
+which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
 The generalized form would be \[

### 2020-03-13 paper/formal-verification.tex
Adds formal verification section to outline

@@
-\section{Formal Verification}
+\section{Formal Verification}\label{formal-verification}
 
@@
 
-The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices we made. 
-It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
+The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%, with a short discussion of the modeling choices we made. 
+ contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
@@
 properties (in negligible computation time) and proved the security
-properties used in~\cite{TamarinDB}. In the meantime,
-\textcite{TamarinDBTF} introduced the notion of post-collusion
-security which enabled them to prove \ac{DBTF}. In future work, we
-will use this extension on our protocol.
+properties used in~\cite{TamarinDB} and
+\textcite{TamarinDBTF}. The latter introduced the notion of post-collusion
+security which enabled them to prove \ac{DBTF}.
+
+Note that proofs of formal verification are always limited by how well the specification captures reality.
+The abstraction does not capture the details of the bit-by-bit version that prevent \ac{DBTF} resistance.

### 2020-03-13 paper/conclusions.tex
Improves conclusion scenario (fixes #46)

@@
 provided by previous \ac{DB} ones.  With our contribution, Alice can
-now prove more complex statements to Bob; \eg that she is older than
-18 but younger than 40 without revealing her actual age, and at the
-same time Bob can be sure that Alice is not just relaying messages
-from her older sister Carol.
+now prove more complex statements to Bob; \eg that she is older than 18 
+(without revealing her actual age), has a cinema subscription which is not 
+\enquote{double spent} by someone else at the same time and, at the same time, 
+Bob can be sure that Alice is not just relaying messages from her older sister 
+Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.

### 2020-03-13 paper/conclusions.tex

@@
 (without revealing her actual age), has a cinema subscription which is not 
-\enquote{double spent} by someone else at the same time and, at the same time, 
-Bob can be sure that Alice is not just relaying messages from her older sister 
-Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.
+\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
+and, at the same time, Bob can be sure that Alice is not just relaying messages 
+from her older sister Carol or \ac{DBMF} relaying the subscription from some 
+unsuspecting stranger.

### 2020-03-14 paper/formal-verification.tex

@@
 
-We formally verify the protocol security properties using the Tamarin
+We formally verify the distance-bounding protocol security properties using the Tamarin
 prover~\cite{meier2013tamarin}. Tamarin does not originally include
@@
 thanks to a recent work by \textcite{TamarinDB}, the common properties
-can be equivalently characterized with a causality-based definition
-relying only on the order of messages.
+(mafia fraud, and distance fraud/distance hi-jacking) can be equivalently 
+characterized with a causality-based definition relying only on the order
+of messages.
+Another work by the same team \textcite{TamarinDBTF} also introduces a
+notion of post-collusion security that can be used to partially automate
+proofs regarding terrorist fraud, provided a manual proof of a least-disclosing
+message needed for collusion.
 
-The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%, with a short discussion of the modeling choices we made. 
- contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
+The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%,
+ contains a specification of the distance-bounding protocol described previously, a definition 
+ of the soundness and correctness properties that ensure the protocol actually produces the
+ expected result, and a definition of the security properties we want to ensure.
 
 Tamarin's auto-prover validated the soundness and correctness
-properties (in negligible computation time) and proved the security
-properties used in~\cite{TamarinDB} and
-\textcite{TamarinDBTF}. The latter introduced the notion of post-collusion
-security which enabled them to prove \ac{DBTF}.
+properties and proved all the security
+properties used in~\cite{TamarinDB} and \textcite{TamarinDBTF}: resistance to distance fraud, distance hi-jacking, mafia fraud, and terrorist fraud, all in less than 10 seconds.
 
 Note that proofs of formal verification are always limited by how well the specification captures reality.
-The abstraction does not capture the details of the bit-by-bit version that prevent \ac{DBTF} resistance.
+In particular, Tamarin only provides symbolic modeling, and as such does not work with actual values.
+The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
+Similarly, the details of the bit-by-bit version are lost in the abstraction, and its specification is identical to the simultaneous version; that's why Tamarin does not detect the terrorist fraud attack we mention about the bit-by-bit version.
+Notable differences between the specification and reality include:
+\begin{itemize}
+	\item We represented the responses $s_i$ as the challenges $c_i$ signed with the prover long-term secret key $\alpha$ and then encoded with the nonce $\rho$; this is faithful to the actual purpose of those values in the protocol, even though the concrete operations executed do not correspond exactly to an encoding and a signature.
+Indeed, $s_i$ includes $\alpha$ to authenticate the prover (signing), and $\rho$ to mask the actual value of $\alpha$ (encoding).
+	\item We used the chosen challenge $c_b$ directly instead of the flag $b$ to represent the choice of the verifier between the two challenge values; this is equivalent because Tamarin does not work with actual values so the size of those values does not matter, and this helps us for the challenge verification later.
+	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
+	\item Additionally, to model the challenge as unpredictable, we added a fresh nonce $b_{nonce}$ to the challenge specification.
+This is important due to Tamarin having no proper concept of time, only a notion of causal dependency between messages.
+Without this nonce there is no such dependency and the prover is able to send the actual response before receiving the challenge, which is detected by Tamarin as a distance fraud attack but is not possible in practice.
+	\item We indicated $\alpha$ as least-disclosing message for collusion.
+In reality, a colluding prover can leak the responses $s_i$ instead, but the attacker can trivially reconstruct $\alpha$ from two $s_i$ using basic arithmetic.
+But Tamarin's attacker is not able to manipulate arithmetic this way, so we provide him $\alpha$ directly.
+	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
+\simon{not sure if this is still relevant, or obsoleted by the bit-by-bit version}
+	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.
+\end{itemize}

### 2020-03-14 paper/formal-verif-appendix.tex
Moves part of the formal verif discussion to appendix

--- 2020-03-14 paper/formal-verification.tex
@@
-\section{Formal Verification}\label{formal-verification}
+\section{Differences in formal models}%
+\label{formal-verif-appendix}
 
-We formally verify the distance-bounding protocol security properties using the Tamarin
-prover~\cite{meier2013tamarin}. Tamarin does not originally include
-the possibility to reason on time and space in its model.  However,
-thanks to a recent work by \textcite{TamarinDB}, the common properties
-(mafia fraud, and distance fraud/distance hi-jacking) can be equivalently 
-characterized with a causality-based definition relying only on the order
-of messages.
-Another work by the same team \textcite{TamarinDBTF} also introduces a
-notion of post-collusion security that can be used to partially automate
-proofs regarding terrorist fraud, provided a manual proof of a least-disclosing
-message needed for collusion.
-
-The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%,
- contains a specification of the distance-bounding protocol described previously, a definition 
- of the soundness and correctness properties that ensure the protocol actually produces the
- expected result, and a definition of the security properties we want to ensure.
-
-Tamarin's auto-prover validated the soundness and correctness
-properties and proved all the security
-properties used in~\cite{TamarinDB} and \textcite{TamarinDBTF}: resistance to distance fraud, distance hi-jacking, mafia fraud, and terrorist fraud, all in less than 10 seconds.
-
-Note that proofs of formal verification are always limited by how well the specification captures reality.
-In particular, Tamarin only provides symbolic modeling, and as such does not work with actual values.
-The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
-Similarly, the details of the bit-by-bit version are lost in the abstraction, and its specification is identical to the simultaneous version; that's why Tamarin does not detect the terrorist fraud attack we mention about the bit-by-bit version.
 Notable differences between the specification and reality include:

### 2020-03-14 paper/formal-verification.tex
Moves part of the formal verif discussion to appendix

@@
 Similarly, the details of the bit-by-bit version are lost in the abstraction, and its specification is identical to the simultaneous version; that's why Tamarin does not detect the terrorist fraud attack we mention about the bit-by-bit version.
-Notable differences between the specification and reality include:
-\begin{itemize}
-	\item We represented the responses $s_i$ as the challenges $c_i$ signed with the prover long-term secret key $\alpha$ and then encoded with the nonce $\rho$; this is faithful to the actual purpose of those values in the protocol, even though the concrete operations executed do not correspond exactly to an encoding and a signature.
-Indeed, $s_i$ includes $\alpha$ to authenticate the prover (signing), and $\rho$ to mask the actual value of $\alpha$ (encoding).
-	\item We used the chosen challenge $c_b$ directly instead of the flag $b$ to represent the choice of the verifier between the two challenge values; this is equivalent because Tamarin does not work with actual values so the size of those values does not matter, and this helps us for the challenge verification later.
-	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
-	\item Additionally, to model the challenge as unpredictable, we added a fresh nonce $b_{nonce}$ to the challenge specification.
-This is important due to Tamarin having no proper concept of time, only a notion of causal dependency between messages.
-Without this nonce there is no such dependency and the prover is able to send the actual response before receiving the challenge, which is detected by Tamarin as a distance fraud attack but is not possible in practice.
-	\item We indicated $\alpha$ as least-disclosing message for collusion.
-In reality, a colluding prover can leak the responses $s_i$ instead, but the attacker can trivially reconstruct $\alpha$ from two $s_i$ using basic arithmetic.
-But Tamarin's attacker is not able to manipulate arithmetic this way, so we provide him $\alpha$ directly.
-	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
-\simon{not sure if this is still relevant, or obsoleted by the bit-by-bit version}
-	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.
-\end{itemize}
+Notable differences can be found in \cref{formal-verif-appendix}.

### 2020-04-15 paper/adversary-model.tex

@@
 
-The adversary maliciously controls \(W\) (the strongest role a
-participant can take on).
+The goal of the adversary is to link a protester's real identity~\(P\) to a 
+protest identifier~\(\cid\).
+The adversary maliciously controls \(W\).
 The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
-like everyone else (\ie a malicious protester~\(P\)).
-The adversary only learns the protocol data, \ie what is sent over the 
-channel --- no auxiliary data such as who is on the other side of the channel obtained
+like everyone else (\eg a malicious protester~\(P\)).
+The adversary only learns the protocol data, \ie what is sent over the channel 
+--- no auxiliary data such as who is on the other side of the channel obtained
   as side information, \eg by face recognition or inference from address

### 2020-04-15 paper/distance-bounding.tex
Fixes authors in a row

--- 2020-02-26 paper/distance-bounding.tex
@@
 \end{itemize}
+% There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
 
-The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-In this context it does not make sense to protect against the verifier as he 
-can easily impersonate the prover as he has a knowledge of his secret key.
-There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-We will work in the latter setting; with a \emph{malicious verifier} who will 
-potentially try to \emph{impersonate the prover} after successful verification.
-
-\subsection{\Acl*{DB} security definitions}%
-\label{DB-definitions}
-
-There are two lines of attempts at formalizing the above properties: one by 
-\citet{DB-BMV} and another by \citet{DB-DFKO}.
-We will use the framework of \citeauthor{DB-DFKO} with extensions by 
-\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
-\cref{DB-definitions}).
-
-As summarized in by \textcite{TREAD}, there are three types of sessions for an 
-adversary:
-\begin{description}
-  \item[Prover--verifier] The adversary observes an honest execution.
-  \item[Prover--adversary] The adversary runs the protocol as a verifier with 
-    an honest prover.
-  \item[Adversary--verifier] The adversary runs the protocol as a, potentially 
-    malicious, prover with an honest verifier.
-\end{description}
-Each session is associated with a unique identifier \(\sid\).
-Each adversary is defined in terms of
-computational resources, time~\(t\);
-number of prover--verifier sessions observed, \(\qobs\);
-number of prover--adversary sessions initiated, \(\qp\), and
-number of adversary--verifier sessions initiated, \(\qv\).
-
-The DFKO framework~\cite{DB-DFKO} uses an abstract clock~\(\marker\colon \NN\to 
-  \NN\) which is strictly increasing and orders the adversary's actions.
-We let
-\(\Xscript{\sid}{i, \dotsc, j}\)
-denote the sequence of messages
-\((m_i, \dotsc, m_j)\)
-exchanged during the session \(\sid\).
-
-A session consists of three phases: a setup phase, a time-critical phase and a 
-verification phase.
-Both setup and verification can be run slowly, but the time-critical phase must 
-be run as fast as possible.
-
-\paragraph*{\Acl*{DBMF}}
-
-We will now define the conditions for \ac{DBMF} and \ac{DBMF} resistance.
-A tainted session is a session in which the adversary lost because the verifier 
-detected the attempt at cheating, \eg the timing is too long because the 
-adversary is out of range.
-The following definition captures a pure relay and a verifier is assumed to 
-detect such a relay.
-
-\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
-  \label{TaintedMF}
-  A time-critical round
-  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
-  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
-  verifier, is \emph{tainted} by the round
-  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
-  of a prover--adversary session~\(\sid'\) if
-  \begin{align*}
-    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
-    \marker[\sid, k] &< \marker[\sid', k'] \\
-    \marker[\sid, k+1] &> \marker[\sid', k'+1].
-  \end{align*}
-\end{definition}
-
-We will now define what it means for a protocol to be \ac{DBMF} resistant.
-
-\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
-  \label{MFresistance}
-  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
-  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
-  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
-  which does not have any critical phase tainted by a prover--adversary session 
-  \(\sid'\).
-  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
-  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins is negligible in the 
-  security parameter.
-\end{definition}
-
-\paragraph*{\Acl*{DBTF}}
-
-\Acl{DBTF} is similar to \ac{DBMF}, the difference is that during \ac{DBTF} the 
-prover cooperates with the adversary to make the verifier accept.
-
-\begin{definition}[Tainted session, \acs*{DBTF} 
-  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
-  A time-critical round
-  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
-  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
-  sent by the verifier, is \emph{tainted} by the round
-  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, \dotsc, m'_{k+2l-1})\]
-  of a prover--adversary session~\(\sid'\) if
-  \begin{align*}
-    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
-    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
-  \end{align*}
-\end{definition}
-
-Then we have the following definition of security.
-
-\begin{definition}[SimTF security~\cite{DB-DFKO}]%
-  \label{TFresistance}
-  Let \(\DB\) be an authentication scheme for parameters \((t_{\max}, T_{\max}, 
-    E_{\max}, N_c)\).
-  Let \(\adv\) be a \((t, \qv, q_{\F})\)-SimTF adversary, \(\S\) an algorithm 
-  with runtime \(t_{\S}\) and \(\F\) an algorithm with runtime \(t_{\F}\).
-  Let \[
-    \Adv_{\DB}^{\text{TF}}(\adv, \S, \F) = p_{\adv} - p_{\S},
-  \] where \(p_{\adv}\) is the probability that the verifier~\(V\) accepts in 
-  one of the \(\qv\) adversary--verifier sessions~\(\sid\) such that at 
-  \(T_{\max}\) time-critical phases of \(\sid\) are tainted and \(p_{\S}\) is 
-  the probability that, given the state of \(\adv\), \(\S\) authenticates to 
-  the verifier~\(V\) in one of \(\qv\) subsequent executions.
-\end{definition}
-
-\paragraph*{\Acl*{DBDH} and \acl*{DBDF}}
-
-The final property is \ac{DBDH} and \ac{DBDF}.
-The following definitions for \ac{DBDH} also captures \ac{DBDF} 
-attacks~\cite{TREAD}.
-We first define what the adversary can and cannot do by defining a tainted 
-session for \ac{DBDH}.
-
-The intuition is that an adversary (malicious, far-away prover) must commit to 
-an action: either respond with an own message, which is determined before 
-seeing the challenge, or to prompt a nearby prover to respond (with a message 
-chosen by the adversary).
-Technically, this adversary can do more than \iac{DBDH} adversary normally can.
-\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
-\(\sid_{\Prompt}\).
-The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
-m'_{k+1})\) in dummy session \(\sid_{\Commit}\) before receiving the challenge 
-in message \(k\) in session \(\sid\) (making message \(k+1\) in \(\sid\) his 
-response to the challenge).
-If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
-session \(\sid_{\Prompt}\), which is the message the nearby prover will send.
-
-\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
-  \label{TaintedDH}
-  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
-  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
-  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
-  \begin{itemize}
-    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
-      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker[\sid, k] > 
-      \marker[\sid_{\Commit}, j]\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
-      such \(j\) exists).
-
-    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
-      m_{k+1}')\) for \(m_{k+1}' = \Prompt\) satisfies \(m_{k+1} \neq 
-      m_{k+1}^{\Prompt}\), in which \(m_{k+1}^{\Prompt}\) denotes the message 
-      \(m_{k+1}\) in \(\sid_{\Prompt}\).
-  \end{itemize}
-\end{definition}
-
-To win, the adversary must convince a verifier that he is close when he 
-actually is not and without tainting any of the sessions.
-
-\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
-  \label{DHresistance}
-  For \iac{DB} authentication scheme~\(\DB\) with \ac{DB} threshold 
-  \(t_{\max}\), a \((t, \qp, \qv, \qobs)\)-\ac{DBDH} adversary \(\adv\) wins 
-  against \(\DB\) if the verifier accepts \(\adv\) in one of the \(\qv\) 
-  adversary--verifier sessions without any critical round being tainted.
-  Thus, \ac{DBDH} resistance is defined as the probability 
-  \(\Adv_{\DB}^{\text{DH}}(\adv)\) that \(\adv\) wins the game.
-\end{definition}
+% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
+% Indeed, in this context it does not make sense to protect against the
+% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
+% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
+Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
+The verifier might also try to track the provers and map their identities to 
+their actions, thus we also require strong privacy.
+In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
+\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
+For this paper, we assume the existence of such a protocol.
+There exists \ac{PPK} schemes, \eg~\cite{ProProx}, just no published scheme for 
+discrete logarithms yet\footnote{%
+  The authors have such a protocol under submission in another venue.
+}.

### 2020-04-15 paper/intro.tex

--- 2020-03-13 paper/intro.tex
@@
 
-\paragraph*{Contributions}
+%\emph{Context.}
 
-We make three contributions.
-First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
-\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
-model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
-This version is based on the assumption that we can transmit all bits at once, 
-not bit-by-bit as normally required for \ac{DB}.
-This assumption is reasonable by the results of \textcite{UWBPR}.
+While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper.
+We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
 
-Second, for the assumption about sending all bits at once to hold, 
-\textcite{UWBPR} requires that two devices shared a symmetric key~\(k\).
-Our second contribution is \iac{PKI} and \ac{AKE} scheme for any device in 
-the \ac{PKI} to convince a verifier that this is the case.
-This replaces everyone having the same static key~\(k\) with everyone having a 
-unique key which is signed by \iac{CA} of the \ac{PKI}, which allows for 
-revocation.
-The solution relies on our first contribution.
+Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
+Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
+More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
+Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
-Our last contribution is another version of the protocol, one which uses 
-bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
-We achieve all properties except \ac{DBTF} resistance.
+Consider the following scenario.
+Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
+Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime.
+To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
-The first (and second) contribution enables us to do distance-bounding 
-privacy-preserving attribute-based credentials based on discrete logarithms, 
-\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
-To our knowledge, no other distance-bounding protocol achieves this.
-The third contribution (bit-by-bit version) also enables us to do the same, 
-just without \ac{DBTF} resistance.
+Existing methods for crowd-counting vary significantly in terms of approaches.
+% (we will review them in detail in \cref{current-crowd-counting}).
+Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.
+In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
 
-\paragraph*{Outline}
+Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting.
+Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
+%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
+In this paper, our main objective is to provide a scheme preventing both Alice 
+and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
+While one cannot
+prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.
+
+%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
+%\seb{in the sentence above I am not sure that the word unlinkable will be 
+%  necessary clear}
+
+%\paragraph*{Contributions}
+
+%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
+%way to securely estimate crowd counts in protests\footnote{%
+%  If location is ignored, it can be reduced to privacy-preserving yet 
+%  verifiable petitions.
+%}.
+%
+%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
+%including \ac{DBDH} (which was an attack against the original protocol of 
+%Brands and Chaum) and \ac{DBTF}.
+%More importantly, it is public-key, handles malicious impersonating verifiers.
+%Since it is based on the Schnorr protocol, it provides a distance-bounded 
+%\ac{PK} for discrete logarithms.
+%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
+%distance-bounding version and thus make general privacy-preserving, 
+%attribute-based credential systems distance bounding.
+
+% The paper is organized as follows.
+% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{current-crowd-counting}).
+% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
 
 The paper is organized as follows.
-\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
-\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
-send all bits at the same time.
-\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
-version of the protocol in practice.
-\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
-\Cref{formal-verification} describes our effort to formally verify the protocol 
-using Tamarin.
-Finally, we conclude with discussion and conclusions in 
-\cref{Discussion,Conclusion}.
+In \Cref{system-model}, we describe our system model and summarize the desired 
+properties for crowd counting, followed by a discussion of current 
+crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
+we formalize the notion of protest and the desired verifiability and privacy 
+properties, and in \cref{building-blocks}, we give the relevant background on 
+the building blocks of our solution.
+%
+%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+%different from that originally proposed by \textcite{DistanceBounding}.
+%We provide a proof of its security and formally verify it using 
+%Tamarin~\cite{TamarinDB}.
+%
+We present \CROCUS, a privacy-preserving crowd counting 
+%estimation 
+protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
+We compare it to related work in \cref{related-work}.
+Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
+our conclusions in \cref{Conclusion}.

### 2020-04-15 paper/performance.tex

--- 2019-03-01 paper/analysis-performance.tex
@@
-\section{Performance}
+\section{Performance}%
 \label{PerformanceAnalysis}
+
 \sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
 
+Performance considerations are crucial during the protests due to the nature of 
+the devices used to run \CROCUS, which are resource-constrained in terms of 
+energy, storage and computational power, and are operating on limited network 
+capacity.
+
 \subsection{Smartphones and smartcards}
-Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
-Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
-For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}.
-However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
-While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.
 
-With respect to its implementation, \CROCUS is actually very similar to Anon-Pass~\cite{AnonPass}, an anonymous subscription system in which a long-term credential can be used to derive a single login for any authentication window (\ie epoch) such that logins are unlinkable across different epochs.
+Recent technological progress has enabled the deployment of advanced 
+cryptographic primitives on smartcards and smartphones that could be used to 
+implement our solution.
+For instance, benchmarks~\cite{Benchmarking} have shown that Android devices 
+are now fast enough to efficiently implement \acp{PET}, with a Samsung Galaxy S 
+i9000 (back in 2014) able to execute Idemix in \SI{153}{\milli\second}. 
+However, those benchmarks also demonstrate that smartcards remain slow to 
+process complex protocols such as Idemix or U-Prove (taking between 
+\SI{4}{\second} and \SI{8}{\second} to process them). While the limited 
+processing power of many embarked systems has been a challenge, Idemix has been 
+successfully implemented to prove the possession of credentials on Java Cards 
+by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released 
+in 2014, aimed to achieve an implementation ``suitable for real life 
+transactions''~\cite{IRMA} while maintaining security and privacy for its 
+users.
+
+With respect to its implementation, \CROCUS is very similar to the 
+implementation of Anon-Pass~\cite{AnonPass}, an anonymous subscription system 
+in which a long-term credential can be used to derive a single login for any 
+authentication window (\ie epoch) such that logins are unlinkable across 
+different epochs.
 In particular, the setup and registration phases are almost identical.
-The evaluation conducted by the authors was using as server a Dell Optiplex 780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz Intel Core 2 CPU but with only 4 GB of RAM.
+The evaluation conducted by \textcite{AnonPass} used as server a Dell Optiplex 
+780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses 
+Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz 
+Intel Core 2 CPU but with only 4 GB of RAM\@.
 The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
-This is typically the type of pairing that could also be used with \CROCUS.
-Not counting the setup that is performed once by the CA, the time reported for the registration on the server (\ie CA) side is 19.8 milliseconds while it is 23.4 milliseconds on the client side.
-With respect to joining and participation phases, with the exception of the distance-bounding they are actually quite similar to the login protocol of Anon-Pass in which the time required to create a message for a protester would be around 13.5 milliseconds while the time needed for the witness would be only 7.9 milliseconds.
+This is typically the type of pairing that could also be used with \CROCUS\@.
+Not counting the setup that is performed once by the \ac{CA}, the time reported 
+for the registration on the server (\ie \ac{CA}) side is 
+\SI{19.8}{\milli\second} while it is \SI{23.4}{\milli\second} on the client 
+side.
+With respect to joining and participation phases, with the exception of the 
+distance-bounding they are actually quite similar to the login protocol of 
+Anon-Pass in which the time required to create a message for a protester would 
+be around \SI{13.5}{\milli\second} while the time needed for the witness would 
+be only \SI{7.9}{\milli\second}.
 
-\subsection{Distance-bounding anonymous credentials}
-The distance-bounding chips~\cite{3dB-access} currently available on the market 
-can already enable proofs of proximity for any range of up to 
-  200 meters.
-One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
-For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
-More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode.
-The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
+%\subsection{Distance bounding}
+%
+%The distance-bounding chips~\cite{3db-access} currently available on the market 
+%can already enable proofs of proximity for any range of up to 
+%  200 meters.
+%One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
+%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
+%More precisely, they have proposed three different implementations of the 
+%Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic 
+%implementation running at the application layer to an advanced one running in 
+%RFID-emulation mode. The results obtained already show that a relay attack can 
+%be detected if the adversary introduces a delay of more than 1.5 ms when 
+%performing such an attack (most of the existing attacks introduce delays of at 
+%least tens of milliseconds).
 
@@
 
+\subsection{Witness processing}
+
+As above, assume we have one trusted witness.
+A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
+3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
+\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
+maximum \SI{200}{\metre}).
+Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
+(\SI{120}{\metre} radius), which fits 137018~protesters according to 
+\textcite{2016DemonstrationsInSeoul}.
+It would take this witness \SI{5.8}{\hour} to witness all of them.
+Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
+witnesses.
+
 \subsection{Ledger (blockchain) efficiency}
-As an example, consider a protest with 1\,000\,000 participants.
-If we use trusted witnesses, each participant only needs to acquire one proof share from a trusted witness.
+
+For the example of 1\,000\,000 participants, with trusted witnesses, each 
+participant only needs to acquire one proof share from a trusted witness.
 Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
@@
 
-If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
-While this already takes longer than counting votes in national elections, the threshold is still very low. 
-% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
-% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
-% In addition to the ledger computation, we need to consider the creation of the proof shares.
+%If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
+%While this already takes longer than counting votes in national elections, the threshold is still very low. 
+%% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+%% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
+%% In addition to the ledger computation, we need to consider the creation of the proof shares.
 \sonja{added the previous sentence to explain why anonpass shows up here.
@@
 }
-% %Seb: I agree maybe we should move it to the previous subsection
-% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
-% This yields \(
-%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-%   \SI{48}{\second}.
-% \) of processing. 
-For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
-Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
+%% %Seb: I agree maybe we should move it to the previous subsection
+%% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
+%% This yields \(
+%%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+%%   \SI{48}{\second}.
+%% \) of processing. 
+%For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
+%Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
 

### 2020-04-15 paper/related-work.tex

--- 2020-02-25 paper/related-work.tex
@@
-\section{Related work}%
-\label{related-work}
+\section{Related work}
 
-One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
-ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
+Our scheme relates to several other works: the crowd counting methods already 
+described in \cref{current-crowd-counting}, location-proof systems and 
+Sybil-free pseudonym systems.
 
-% One protocol exists in the literature that provides \acp{PPK} with most of the 
-% desired properties described previously, ProProx~\cite{ProProx}\footnote{Note 
-%   that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for 
-%   shorter notation.}.
-% ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
-%   \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete 
-% logarithms (\ie \(\PPK[\alpha][a = g^\alpha]\), see \cref{ZK-anon-cred} for 
-% details).
+\paragraph*{Location-proof systems}%
+\label{db-and-lp}
+
+In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
+a particular location at a specific moment in time.
+\Iac{LPS} is an architecture by which users can obtain \acp{LP} from 
+neighboring witnesses (\eg trusted access points or other users) that can later 
+be shown to verifiers who can check the validity of a particular 
+proof~\cite{luo2010veriplace,zhu2011applaus}.
+Most of the existing approaches to \acp{LP} require the prover and the 
+witnesses to disclose their identities, thus raising many privacy issues such 
+as the possibility of tracing the movements of users of the \ac{LPS}.
+However, some \acp{LPS}, such as PROPS~\cite{PROPS}, exist that provide strong 
+privacy guarantees along with the possibility of verifying the claim of the 
+location.
+
+\CROCUS shares some similarities with PROPS\@.
+The main difference is that \CROCUS operates in a more adverse environment, and 
+can thus not provide any guarantees using the decentralized, untrusted 
+witnesses that PROPS can.
+The incentives to cheat are also bigger and consequently the thresholds for 
+collusion are much higher.
+CROCUS must also tie the cause to the location proof, to designate the proof to 
+the protest in which the protester participated.
+
+The same can be said in comparison to Platin.io\footnote{%
+  URL: \url{https://platin.io}.
+}.
+
+\paragraph*{Sybil-free pseudonym systems}
+
+Our Sybil-free pseudonym system is very similar to that of 
+\textcite{SybilFreePseudonyms}.
+Both are based on the work of \textcite{HowToWinTheCloneWars}.
+We make the same simplification of~\cite{HowToWinTheCloneWars} as 
+\textcite{SybilFreePseudonyms}, but we also require an interactive version.
+Furthermore, our \acp{PK} must be distance bounding.

### 2020-04-15 paper/security-properties.tex

--- 2018-08-18 paper/security-properties.tex
@@
-\subsection{Security requirements}%
-\label{Properties}
+\subsection{Verifiability and privacy requirements}%
+\label{verifiability-properties}
 
-%\subsubsection{An overview of the adversary}
-
-To go back to the scenario stated in the introduction, we have two potential adversaries: Alice and Grace.
-Alice is a participant of the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
-In contrast, the aim of Grace, the government Alice protests against, is to not only decrease the count, but also to re-identify some of the participants in order to arrest them or forcefully convince them to change their minds.
-In the following two subsections, we will define the desired security properties.
-
-\subsubsection{Verifiability}%
-\label{Verifiability}
-
-We note that, in general terms, protesting is very similar to petitions, which in turn are similar to voting.
-Indeed, all three situations correspond to cases in which many individuals express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or persecution), hence we desire to have similar properties of verification and privacy for verifying a protest as there are for voting.
-
-Voting has (generally) three desirable requirements for verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-  \item[Individual verifiability:] each voter can verify that his vote is included in the result.
-\end{description}
-In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs.
-The eligibility requirement is slightly different as for protests it must include temporal and spatial eligibility (\ie each participation proof satisfies some temporal and spatial relation to the protest).
-In essence, the proof must bind the person to the time and location of the protest.
-
-To define these properties more formally in the context of protest, we define three verifiability requirements, among which eligibility can be further broken up into four subproperties:
+We now try to make the properties from \cref{desired-properties} more 
+specific.
+We define three verifiability requirements, among which eligibility can be 
+further broken up into four subproperties:
 \begin{requirements}[V]
@@
     \begin{requirements}
-    \item\label{TemporallyRelated} \emph{Temporal eligibility}: prove that the proof was created after the start of the protest and before the end of the protest.
-    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: prove that the proof is spatially related to the physical location or journey of the protest.
-    \item\label{CountOnce} \emph{One-proof-per-person}: prove that no individual can be counted more than once for a particular protest.
-    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof is associated to particular designated protest.
+
+    \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
+
+    \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
+
+    \item\label{CountOnce} \emph{Counted only once}:
+      A protester can create \emph{one and only one} pseudonym (\(\pid\) in 
+      \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
+      this pseudonym is unique except with negligible probability.
+      Analogously, a witness can create \emph{one and only one} pseudonym per 
+      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
+      except with negligible probability.
+
+    \item\label{DesignatedEvent} \emph{Designated event}: prove that the proof 
+      is designated for the particular protest.
+
     \end{requirements}
 
-  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained match the submitted participation proofs.
+  \item\label{UniversalVerif} \emph{Universal verifiability}: anyone can verify that the result obtained matches the submitted participation proofs.
 
-  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that his participation proof is included in the global count.
+  \item\label{IndividualVerif} \emph{Individual verifiability}: each participant can verify that their participation proof is included in the global count.
 \end{requirements}
 
-\subsubsection{Privacy}%
-\label{Privacy}
-
-In addition to the verification requirements, we also need to define the privacy properties.
-In voting protocols, there are mainly three levels of privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\begin{description}
-\item[Vote privacy:] the voting does not reveal any individual vote.
-\item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-\item[Coercion resistance:] a voter cannot cooperate with a coercer to prove the vote was cast in any particular way.
-\end{description}
-
-\Citet{VerifyingPrivacyPropertiesOfVotingProtocols} showed that coercion resistance implies receipt freeness, which in turn implies vote privacy.
-Coercion resistance is not possible to achieve for protests.
-For instance, someone could simply physically bring Alice to a protest against her will.
-
-\sonja{discussion about applicable properties here, more sources and alternative properties}
-\sonja{new}
-Difference to e-voting:
-physical presence means support for a cause if there is one protest.
-If there is a counterprotest, physical presence with that group means support for the counterprotest.
-In our system, it gets more ambiguous as the participants are counted if all of the following is true 1) they participate in the protocol, 2) they use the protest identifier (cause) for which the count is done, 2) they meet the eligibility criteria, and 3) they receive enough proof shares, 4) that are uploaded to the ledger.
-Thus one could participate in a protest and be counted even when physically present at a counter-protest if the two protests are co-located and the participant chooses the corresponding cause/identifier of the original protest.
-
-Given that all conditions for being counted in a protest are met, individual verifiability implies a receipt, because being counted implies support for a cause.
-This also means that besides physical force, coercion can happen by forcing the participate to show a receipt.
-We thus have to decide between individual verifiability and the privacy properties for e-voting or define privacy properties suitable for the scenario.
-The ultimate privacy requirement is thus stronger here: in contrast to voting, where it is the content of the vote itself that needs to be unlinkable to the voter, here the fact of having cast a vote at all needs to be unlinkable.
-
-The privacy properties we need in this context are
-
-involuntary participant unlinkability: unless the participant discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the participant.
-
-involuntary witness unlinkability: unless the witness discloses the receipt (by revealing her identity), there is no link between the protest data on the ledger and the identity of the witness.
-\sonja{old}
-In essence, receipt freeness means that upon completing the protocol, Grace cannot link Alice to Alice's participation proof --- even if she were to compromise Alice's device or Alice accepts to collaborate with Grace.
-As we will see, if Grace gets Alice's device, she can re-do the computations on the same inputs.
-Since, in our case, the algorithms are deterministic and collisions are negligible, she will produce the same output and can thus conclude that Alice is indeed the one she is looking for.
-Thus, we cannot provide receipt freeness (see \cref{Conclusion} for further discussions on this issue).
-
-As a consequence, this leaves us with with what would correspond to vote privacy.
-In particular, we need unlinkability between Alice's long-term identity and Alice's participation proof.
-Given a participation proof, Grace will not be able to tell if it belongs to Alice or Bob.
-Furthermore, if Grace has managed to link one proof to Alice's, she should not be able to link another proof (\eg, from a different protest) as a consequence.
-Hence, we can summarize the needed privacy properties as follows:
+For privacy, we require a set of unlinkability properties:%
+\label{privacy-properties}
 \begin{requirements}[P]
-\item\label{ProofUnlink} \emph{Anonymity}: participants must be unlinkable to their proofs.
-\item\label{ProtestUnlink} \emph{Unlinkability}: participants (or proofs issued by the same participant) must be unlinkable between different protests.
+\item\label{PseudonymUnlink} \emph{Pseudonym unlinkability}: given a protest 
+  (identifier \cid), protesters Alice and Bob, and a pseudonym \(\pid_b\), the 
+  adversary cannot tell if \(\pid_b = \pid_{\text{Alice}}\) or \(\pid_b = 
+    \pid_{\text{Bob}}\), except with negligible probability. And similarly with $wid$ if Alice and Bob act as witnesses.
+\item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
+  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
+    \cid'\)) from the adversary's perspective.
+\item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
+  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
+    \pid'\)) from the adversary's perspective.
 \end{requirements}
 
-As a result of these properties, if there are two protests in parallel (\eg, one against Grace's regime and one in favor) Alice can always argue to be part of the protest in Grace's favor instead of any protest against Grace.
-This is, in fact, is a slight increase in privacy over ordinary protests.
+What these properties say is that pseudonyms must look random 
+(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
+more than strictly necessary for the verifiability properties 
+(\cref{ProtestUnlink,WitnessUnlink}). In Pfitzmann-Hansen
+terminology~\cite{pfitzmann-hansen}, they are role-relationship
+pseudonyms, but with increasingly narrowed notions of roles and
+relationships (participant of particular protest, witness of a
+particular participant at a particular protest).
+In the terminology of \textcite{SybilFreePseudonyms}, for each protester a 
+protest is a context or identity domain whereas for each witness every 
+protester is a context (or identity domain).

### 2020-04-16 paper/system-model.tex
Moves system model

@@
 
-\subsection{Desired properties}%
-\label{desired-properties}
-
-We note that, in general terms, protests are petitions with a given time and 
-location.
-Protests, petitions and elections share that in all three many individuals 
-express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or 
-persecution).
-For that reason we have strong requirements for verification and privacy for 
-elections, it follows that we should have similar properties for protests
-and petitions.
-
-We draw inspiration from properties for voting systems as formalized
-in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\daniel{Find a new ref for voting verifiability properties, Douglas commented 
-  that the last one is not the origin.}
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
-      old.}
-  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
-    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
-      Fiat-Shamir (technically). Non-technically, much older.}
-\end{description}
-In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
-The eligibility requirement is slightly different as for protests it must also
-include temporal %\footnote{%
-%   Elections also have some temporal aspects, such that one cannot vote at any 
-%   time and a vote in one election should not be reusable in the next election.
-%   However, the temporal relation for a protest is not as strictly defined as for 
-%   elections as a protest can start at any time and last for an arbitrary period 
-%   of time.%
-% }
-and spatial eligibility (\ie each participation proof satisfies some temporal 
-and spatial relation to the protest).
-In essence, the proof must bind the person to the time and location of the protest.
-(This is the difference to a petition.)
-
-In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
-privacy properties for voting protocols are given as:
-\begin{description}
-  \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
-\end{description}
-
-%Coercion resistance is not possible to achieve for protests.
-Coercion resistance in voting typically relies on physical isolation
-(\eg private voting booths), including for digital systems, 
-and that is by definition not possible for public events.
-For instance, someone could simply physically bring Alice to a protest against her will.
-As for receipt freeness, while
-desirable \emph{in itself}, it implies a conflict with verifiability in our context:
-%appealing at first glance, is not desirable (probably not possible)
-%in our context since this will conflict with verifiability:
-in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
-cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
-(\ie the protester was there), which would make verifiability impossible.
-
-Therefore in our context, the crucial property is  vote privacy.
-More precisely, for the protester we want unlinkability (from the adversary's 
-perspective) between a protester's real identity \(P\) and the participation 
-proof (and thus also the protest itself).
-Phrased differently, given a participation proof, Grace should not be able to 
-distinguish if it was Alice or Bob who participated.
-Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (from a different protest).
-
 % \subsection{Adversary model}%

### 2020-04-17 paper/sybil-free-pseudonyms.tex
Adds ref to SelfCertifiedSybilFreePseudonyms (fixes #192)

\subsection{Sybil-free pseudonyms}%
\label{sybil-free-pseudonyms}

We must protect against Sybil attacks~\cite{SybilAttack}.
We use the idea of identity domains and self-certified Sybil-free pseudonyms 
proposed by \textcite{SelfCertifiedSybilFreePseudonyms}.
However, we don't need the ability to (nor want to be able to) deanonymize 
pseudonyms, so we don't use the entire e-token dispenser scheme by 
\textcite{HowToWinTheCloneWars} that 
\textcite{SelfCertifiedSybilFreePseudonyms} use, but rather just what they call 
the token serial number.

### 2020-04-20 paper/protocol-trusted.tex
Starts splitting protocol into trusted/untrusted
Improves intro to trusted witnesses protocol

--- 2019-02-28 paper/protocol.tex
@@
 %\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The \CROCUS Protocol}%
-\label{Protocol}
+\section{The trusted-witnesses protocol}%
+\label{trusted-witnesses-protocol}
 
-We now present \CROCUS, a protocol for privately verifiable crowd
-counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key%
-%, more specifically, an anonymous 
-%identity credential that provides unlinkability between contexts but 
-%linkability for reuse within the same context
-%\sonja{this is actually achieved by our use of prfs for pid and wid,
-%not inherent in the credential}
-% \footnote{%
-%   Given any \ac{CA} that prevents Sybil 
-%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
-%   be used to make sure that for each identity one-and-only-one
-%   cryptographic key is issued.
-%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
-%   to one's identity.
-% }
-. Since we assume these properties, we
-present only the result of the process of getting anonymous
-credentials from a \ac{CA}, in \cref{ProtocolSetup}.
+We now present a protocol for privacy-preserving but verifiable crowd
+counts.
+This version of the protocol relies on trusted entities to act as witnesses for 
+\iac{LP}.
 
-The core of the \CROCUS protocol consists of generating participation
-proofs (joining a protest, participating in witnessing, submitting
-proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
-verification of that count (in \cref{ProtocolVerification}).
+A prerequisite for this protocol is a one-to-one mapping between a persons real 
+identity and a certificate (\ie a cryptographic key).
+\Cref{ProtocolSetup} covers how Alice can obtain such a certificate.
+It is a lighter version than in \cite{SelfCertifiedSybilFreePseudonyms} and not 
+the full protocol of \cite{HowToWinTheCloneWars}.
 
-% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-% join, participation, submission (all in in \cref{ProtocolDuring}) and
-% verification (in \cref{ProtocolVerification}).
+At the core of our construction, witnesses generate participation proofs for 
+the protesters (in \cref{ProtocolDuring}), these are essentially augmented 
+\acp{LP}\footnote{%
+  \Iac{LP} certifies that its owner was at a given location at a given time.
+  In \cref{protest-model}, we point out that we also need a cause identifier.
+}.
+Then whoever wants to verify the participation count, will count and verify 
+those participation proofs (in \cref{ProtocolVerification}).
 
@@
   disseminated it to others.
+  Anyone can do this.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
   for their presence.
-\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
-  third parties.
+\item A \emph{witness} provides proofs of participation to protesters.
+  The proofs are constructed such that they are verifiable by third parties.
+  The witness must be trusted by the verifier.
 \end{enumerate}
@@
 
-After the protest, anyone can count the number of participants (of the protest and the
-protocol) and verify anyone else's count given the relevant meta data
-(which protest, location, time, and witness parameters used in the
-count). We refer to anyone counting or verifying a count as the
-verifier; the process is the same.
+Anyone can be a verifier (we required universal verifiability, 
+\cref{desired-properties}).
+The verifier defines the protest to be counted by setting the cause, time 
+(interval) and location (area), \cf \cref{DefProtest}.
+Now the verifier counts all proofs that verify correctly and fulfils the cause, 
+time and location criteria.
+The verifier can publish, \eg in a news paper, the final count together with 
+the cause, time and location and anyone can verify this count (by the same 
+procedure).
 
-\subsection{Prerequisite: anonymous credentials}%
+\subsection{Prerequisite: self-certified, Sybil-free pseudonyms}%
 \label{ProtocolSetup}

### 2020-04-21 paper/protocol-trusted.tex
Rewrites the trusted-witness protocol up to verification section

@@
 \Cref{ProtocolSetup} covers how Alice can obtain such a certificate.
-It is a lighter version than in \cite{SelfCertifiedSybilFreePseudonyms} and not 
-the full protocol of \cite{HowToWinTheCloneWars}.
+It is a lighter version than in~\cite{SelfCertifiedSybilFreePseudonyms} and not 
+the full protocol of~\cite{HowToWinTheCloneWars}.
 
@@
 
-Before Alice can have her participation in any event counted by
-\CROCUS, she needs to get an anonymous credential and corresponding
-keys. This only needs to be repeated when the credential expires or is
-lost, in analogy to a passport in terms of expected intervals. The
-keys can be reused for an arbitrary number of protests or, given
-careful choices in the PRF used for deriving identifiers, other
+Before Alice can have her participation in any event counted, she must get a 
+certificate that ensures Sybil-freeness.
+This is only done once\footnote{%
+  It is repeated when the credential expires, in analogy to a passport in terms 
+  of expected intervals.
+}.
+The keys can be reused for an arbitrary number of protests or, given
+careful choices in the \ac{PRF} used for deriving identifiers, other
 services that work with anonymous credentials.
 
-We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
-getting anonymous credentials, adapting only the notation to fit ours. 
+We use the setup and registration phases of 
+Anon-Pass~\cite{AnonPass}\footnote{%
+  This version is slightly adapted (improves efficiency) from the original 
+  version by \textcite{HowToWinTheCloneWars}.
+} for getting the certificate, adapting only the notation to fit ours. 
 %More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
 
-\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
+\paragraph*{Setup: \((\spk, \ssk)\gets \CROCUSsetup\)}
+
 During the setup phase, the \ac{CA} creates all the needed keys.
@@
 
-\emph{Registration: \(\sk\gets 
-    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration phase, each participant generates a secret key~\((k, 
-  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
-  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
+\paragraph*{Registration: \(\sk\gets 
+\Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\)}
+
+During the registration phase, each participant
+generates a secret key~\((k, r)\) and
+obtains a signature on it by the \ac{CA} \emph{but without revealing it} to the 
+\ac{CA} (or to any part thereof in a decentralized \ac{CA} scenario).
 At the end, each participant will have a signed secret key while the \ac{CA} 
@@
 %The join, participation and submission phases are as follows.
-% illustrated in \cref{fig:ProtocolOverview}.
-The goal of \CROCUS is to generate and collect privacy-preserving
+% illustrated in \cref{protocol-overview-trusted}.
+The goal of our protocol is to generate and collect privacy-preserving
 participation proofs that can be counted and verified. These proofs
 consist of proof shares that are constructed as depicted in
-\cref{fig:ProofFig}. The protocol phases are given in
-\cref{fig:ProtocolOverview} and described below.
+\cref{fig:ProofFig}.
+They are constructed through an interactive protocol between the protester and 
+the witness, as depicted in \cref{protocol-overview-trusted} and described below.
 
@@
 
-\emph{Creation of a protest: the manifesto.}
+\paragraph*{Creation of a protest: the manifesto}
+
 The organizer writes a manifesto for the protest, which describes its cause.
@@
 
-\emph{Joining as a protester: \((\pid, t_s)\gets 
-    \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest uses the manifesto to
-compute an identifier for the cause by hashing the manifesto,
-\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
-from the organizer, we omit this in the protocol for readibility).
-Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
+\paragraph*{Joining as a protester:
+  \((\pid)\gets \CROCUSjoin[_P][\mfst]\)}
+
+In the terminology of \textcite{SelfCertifiedSybilFreePseudonyms}, the 
+manifesto~\(\mfst\) is the context and it yields an identity domain.
+A protester who wants to join the protest uses the manifesto~\(\mfst\) to
+compute an identifier for the cause (the context) by hashing the manifesto,
+\(\cid\gets \Hash[\mfst]\)\footnote{%
+  The result should be compared to that received from the organizer to check 
+  that the \(\cid\) indeed is correct.
+  This is to avoid that protesters use different \(\cid\)s for semantically 
+  equivalent manifestos~\(\mfst\).
+  However, we omit this in the protocol for readability.
+}.
+Afterwards, this is used to create the protester's protest-specific 
+pseudonym~\(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
 % (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
@@
 .
-The protester also fetches a time-correlated random value, \(t_s\), from 
-\(\TS\), \(t_s\gets \TSget\).
 
-\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
-The witness simply gets a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
-Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
-set the start of the time interval of creation for the proof share.
+\paragraph*{Joining as a witness}
 
-\emph{Participation: \(\pi\gets
-    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
+The witness does not have to do anything to join as a witness.
+That the witness is trusted by the verifier means that the verifier trusts that 
+the witness can
+\begin{enumerate*}
+  \item determine the time of an interaction with a protester,
+  \item determine the its own location during that interaction
+    and
+  \item will run the protocol as an honest witness with the potentially 
+    malicious protester.
+\end{enumerate*}
+
+\paragraph*{Participation:
+  \(\pi\gets
+    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\)}
+
 In the participation phase, the protester and 
@@
 
-The protester sends \(\pid\) and \(t_s\) to the witness.
+The protester sends \(\pid\) to the witness.
 Then they run the protocol \[
@@
 Note that the \acf{PK} in \cref{ACacAlg} must be
-run as a \iacf{PPK}, which we do by distance bounding.
+\iacf{PPK} (\ie a \acl{PK} with distance bounding).
+We use the protocol of \textcite{DB-Schnorr}, which does exactly this.
 If the protocol succeeds, the witness will compute \(\wid \gets 
-  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
+\ACprf[_{\sk_W}][\pid]\) and send \((\wid, t, l)\) to the protester, where 
+\(t\) is the current time and \(l\) is the witness' current location.
 
-\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester commits the proof-share data to the ledger~\(L\) and receives the 
-proof of commitment, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', 
-  l]]\).
-The sooner this is done, the higher the precision for the time-dependent 
-eligibility criterion will be for later counting.
-The remaining operations are not time critical.
+\paragraph*{Submission:
+  \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}
 
-The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
-correctness of \(\pid\).
-More specifically,
-\begin{multline*}
-  \corr_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
-    \begin{aligned}
-      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
-      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
-    \end{aligned} \\
-      (\cid, \pid, \wid, t_s, t_s', l).
-\end{multline*}
-Finally, the protester uploads the tuple \[
-  \psh_P = (\cid, \pid, \wid, t_s, t_s', t_e, l, \corr_{\pid})
-\] for permanent storage, \(\TSsubmit[\psh_P]\).
+In the submission phase, the proof shares are be made available for the 
+verifier.
+\Ie the verifier must be able to verify that a proof was actually issued by a 
+witness.
 
-\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
-    l]\).}
-The witness, like the protester, commits the proof-share data to the 
-ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
-%(This is to make the time interval as early as possible, whoever is the faster 
-%will submit it.) \sonja{but both do}
-Then, without any time requirements, the witness computes \iac{NIZK} proof 
-\(\corr_{\wid}\) as follows:
+To achieve this, the witness computes \iac{NIZK} proof~\(\corr_{\wid}\), 
+proving the correctness of \(\wid\) while also signing the time~\(t\) and 
+location~\(l\).
+More specifically, we have that
 \begin{multline*}
@@
       \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
-      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
+      \sigma_W' &= \left. \ACblind[\ACsign[_{\sskw}][\sk_W]] \right\}
     \end{aligned} \\
-      (\cid, \pid, \wid, t_s, t_s', l).
+      (\cid, \pid, \wid, t, l).
 \end{multline*}
-Finally, the witness uploads the tuple \[
-  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
-\] for permanent storage on the ledger, \(\TSsubmit[\psh_W]\).
+Finally, the complete proof share is the tuple \[
+  \psh_W = (\cid, \pid, \wid, t, l, \corr_{\wid}).
+\]
+
+For individual and universal verifiability, the proof should be published on 
+some permanent storage, such as the ledger~\(\TS\) by running 
+\(\TSsubmit[\psh_W]\) (\cref{ledger}).
+
+Note that it does not matter if it is the witness or the protester who makes 
+\(\psh_W\) available to the verifier.
+The witness could compute \(\psh_W\) during the protest and give to the 
+protester immediately, but we separate these steps to show that the witness can 
+postpone those extra computations while potentially running on battery.
+
+Now, the witness is anonymous here.
+For the verifier to recognize a proof on some publicly available storage as 
+issued by a trusted witness there could be another \ac{CA}, say \(\CA'\), which 
+issues credentials to witnesses.
+\(\CA'\) could be run by a news paper, trusted to only issue credentials to 
+trustworthy witnesses.
+
+Another solution would be that the witness simply signs the tuple \((\cid, 
+\pid, t, l)\) with a key that is tied to the witness' identity.
+However, that would allow tracking and thus the anonymity set of the protester 
+would shrink.
+
+Note also that the prover need not compute any \ac{NIZK} proof of the 
+correctness of \(\pid\) since the witness is trusted to have verified this (as 
+part of the distance bounding).
 
@@
       O\to \text{all}\colon & \text{manifesto} \\
-      P\colon & t_s\gets \TSget \\
+      P\colon
         & \cid\gets \Hash[\text{manifesto}], \\
-        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
-      W\colon & t_s'\gets \TSget
+        & \pid\gets \ACprf[_{\sk_P}][\cid]
       \\[-1em]
@@
       W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
-      W\to P\colon & (\wid, t_s', l)
+      %W\to P\colon & (\wid, t, l)
     \end{align*}
-    \caption{Join and participation.}
+    \caption{Join and participation}
   \end{subfigure}
@@
     \begin{align*}
-      P\colon & t_e\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & t_e'\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
-      \pi_{\wid})],\quad \text{where} \\
-        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
+      W\colon & \TSsubmit[(\cid, \pid, \wid, t, l, \corr_{\wid})],\quad 
+      \text{where} \\
+        & \corr_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
         & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
-        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
-      P\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
-      \pi_{\pid})],\quad \text{where}\\
-        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
+        & \qquad \mleft. \sigma_W' =
+              \ACblind[\ACsign[_{\sskw}][\sk_W]]\mright\} \\
+        & \qquad\qquad (\cid, \pid, \wid, t, l)
     \end{align*}
-    \caption{Submission.}
+    \caption{Submission}
   \end{subfigure}
   \caption{%
-    An overview of \CROCUS participation.\@
-    The organizer \(O\) broadcasts the manifesto.
-    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submit the proof shares to a
-   public ledger for permanent storage \(S\). Note that \pid  always refers to the
-    protester whose presence is being witnessed.
+    An overview of the protocol with trusted witnesses.
+    The organizer~\(O\) broadcasts the manifesto.
+    The protester~\(P\) with pseudonym~\(\pid\) in the context of the protest 
+    (\(\cid\)),
+    the witness~\(W\) with pseudonym~\(\wid\) in the context of that protester 
+    and
+    their computations are as in \cref{fig:ProofFig}.
+    Finally, \(W\) submits the proof share to a public ledger~\(\TS\) for 
+    permanent storage.
   }%
-  \label{fig:ProtocolOverview}
+  \label{protocol-overview-trusted}
 \end{figure*}

### 2020-04-21 paper/protocol-trusted.tex
Edits trusted-witness counting section

@@
 
-\subsection{Count and Verification}%
+\subsection{Count and verification}%
 \label{ProtocolVerification}
@@
 
-To count or verify the participation count for a protest \(\prtst\) with 
-identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
-all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
-Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
-\begin{enumerate*}
-\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
-    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
-\item the participation proof \(\prf_{j}\) for each protester \(j\),
-\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
-  for all protesters in \(\prtst\), and finally,
-\item the participation count, \ie the cardinality of 
-  \(\prfs_\prtst^{\str,\theta}\).
-\end{enumerate*}
+Assume that the verifier wants to verify the count for a protest~\(\prtst\).
+The first thing the verifier will do, is to download all the proof 
+shares~\(\psh\) from the ledger~\(\TS\), such that \(\psh \sqsubseteq \sprtst\) 
+is a valid proof share for some subprotest~\(\sprtst\in\prtst\) of the 
+protest~\(\prtst\).
+Next, the verifier selects only those proof shares~\(\psh = (\cid, \pid, \wid, 
+t, l, \corr_{\wid})\) such that \(\corr_\wid\) proves knowledge of a signature 
+by \(\sskw\), where \(\CA'\) is someone the verifier trusts\footnote{%
+  We note that there can be more than one \ac{CA} which the verifier trusts 
+  will issue credential only to trustworthy witnesses,
+  but we keep to one for the simplicity of our exposition.
+}.
+We denote this set of proof shares by \(\pshs\).
 
-More precisely, given \[
-  \pshs_{\cid_0} = \{ (\cid, \pid, \wid, l, t_s, t_s', t_c, \corr) \in \pshs 
-  \mid \cid = \cid_0 \}
-\] and a matching pair \((s_P, s_W) \in {\pshs_{\cid_0}}^2\) for a witness 
-\(i\) and a protester \(j\) with
-\begin{align*}
-  s_P &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c, \corr_i) &\text{and} \\
-  s_W &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c', \corr_j),
-\end{align*}
-%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
-the verifier can build a valid proof share \(s_j^{(i)}\) certified by \(i\) for 
-\(j\) as follows:
-verify \(\corr_i\) and \(\corr_j\),
-let
-\begin{align*}
-  t &= \interval{\max(t_s, t_s')}{\min(t_c, t_c')} &\text{and} \\
-  s_j^{(i)} &= (\cid_0, \pid_j, \wid_i, l, t),
-\end{align*}
-as in \cref{DefProofShare},
-check that \(s_j^{(i)}\) is valid (\ie happened during and at the location of 
-the protest), as in \cref{DefProofShare}.
+Next, the verifier partitions the set of proof shares~\(\pshs\) using the 
+relation~\(=_\pid\) such that \(
+  (\cid, \pid, \wid, t, l) =_\pid (\cid', \pid', \wid', t', l')
+\) is true if \(\pid = \pid'\).
+Each equivalence class \(\prf_{i, \prtst} \in \pshs/=_\pid\) is a proof of 
+participation for participant \(i\).
+In terms of \cref{DefParticipationCount}, the set of 
+proofs~\(\prfs_\prtst^{\str, \theta} = \pshs/=_\pid\), where \(\theta = 1\) and 
+\(\str(\cdot) = 1\).
+Consequently, the total participation count is \(|\pshs/=_\pid|\).
 
-Then the set of all valid proof shares for a protester \(j\) constitutes its 
-participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
-and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
-Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by  \cref{DefParticipationCount}.
-
-% MOST PROBABLY obsolete below v
-
-%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
-%(see \cref{DefProtest}), a verifier must download all the proof shares \[
-%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
-%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
-%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
-%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
-%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
-%\(l_i\subseteq  l\).
-%Any proof share that does not verify correctly will be discarded.
-%At this point, the verifier has constructed the set \(S\) from 
-%\cref{DefProofShares} and can thus construct any participation proof 
-%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
-%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
-%    \theta}|\) as in \cref{DefParticipationCount}.
-
-%__________________________
-
-% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
-% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
-
-In the case of trusted witnesses, each such trusted witness must
-publish or otherwise inform the verifier of which proof shares they
-have signed, \eg by giving a list of all such proof shares or
-digitally signing each proof share\footnote{%
-  To achieve witness privacy in this situation, one could employ a
-  group or ring signature scheme for a set of potentially trusted witnesses, \eg
-  members of an independent journalist association.  Then one learns
-  that at least one member of this set must have
-  been there.
-}.
+\endinput
 

### 2020-04-22 paper/protest-model.tex
Improves description of protest model

@@
   \(\psh \sqsubseteq \sprtst\).
-
 \end{definition}
@@
 %A subset of the proof shares forms a participation proof for a protester.
-We denote by \(\pshs\) the set of all proof shares,
-and we will use the following notation to filter out a subset of \(\pshs\) with specific \(\cid\)s and \(\pid\)s:
-\begin{multline*}
-  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
-  \cid_0 \land \pid = \pid_0\}.
-\end{multline*}
+We let \(\pshs\) denote the set of all proof shares.
+Let \(
+  \pshs_\prtst = \{ \psh \in \pshs \mid
+    \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
+\) be the subset of proof shares related to a protest~\(\prtst\).
+We denote by \(=_\pid\) the equivalence relation on \(\pshs\) where \((\cid, t, 
+l, \pid, \wid) =_\pid (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
+%and we will use the following notation to filter out a subset of \(\pshs\) with 
+%specific \(\cid\)s and \(\pid\)s:
+%\begin{multline*}
+%  \pshs_{\cid_0, \pid_0} = \{(\cid, t, l, \pid, \wid)\in \pshs\mid \cid = 
+%  \cid_0 \land \pid = \pid_0\}.
+%\end{multline*}
 
@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  The \emph{participation proof} of a protester with pseudonym \(\pid\) who participates in a protest \(\prtst\) with cause identifier \(\cid\) is the 
-  set
+  We denote by \(\prfs_\prtst = \pshs_\prtst/=_\pid\) the \emph{set of all 
+  proofs of participation for the protest~\(\prtst\)}.
+  The \emph{participation proof} of a protester with pseudonym~\(i\) who 
+  participates in a protest~\(\prtst\) is the set
   \begin{equation}
     \nonumber
-    \prf_{\pid, \prtst} =
-    \left\{ \psh \in \pshs_{\cid, \pid} \mid
-      \exists \sprtst\in \prtst\colon \psh\sqsubseteq \sprtst \right\},
+    \prf_{i, \prtst} =
+    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_\prtst \mid
+      \pid = i\right\},
   \end{equation}
-  of all proof shares with the same protester and protest identifiers, and valid for any subprotest $p$ of $\prtst$.
-  We denote by \(\prfs\) the set of all proofs.
+  of all proof shares with the same protester and valid for any subprotest of 
+  \(\prtst\).
 \end{definition}

### 2020-04-22 paper/protocol-trusted.tex
No need for W subscript when P doesn't do anything
Updates protocol section title
Removes extra \\ in protocol figure
Updates proofshare figure

@@
 %\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The trusted-witnesses protocol}%
+\section{Crowd counting with trusted witnesses}%
 \label{trusted-witnesses-protocol}
@@
 consist of proof shares that are constructed as depicted in
-\cref{fig:ProofFig}.
+\cref{proofshare-trusted-fig}.
 They are constructed through an interactive protocol between the protester and 
@@
   \small
-  \includegraphics{proofshare.tikz}
+  \includegraphics{proofshare-trusted.tikz}
   \caption{%
@@
     The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
-    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
-    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
-    witness's key \(\sk_W\) and the protester's \(\pid\).
-    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
-    protester and witness, respectively, and \(l\) is an area.
+    The protester~\(P\)'s protest-specific pseudonym~\(\pid\) is computed using 
+    the protester's key~\(\sk_P\) and \(\cid\).
+    The witness \(W\)'s \emph{protester}-specific identifier \(\wid\) is 
+    computed using the witness's key~\(\sk_W\) and the protester's 
+    pseudonym~\(\pid\).
+    \(t\) is the time (interval) and \(l\) is the location (area) as determined 
+    by the trusted witness~\(W\).
     All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
-      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
-    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
-    The protester constructs \(\prf_P\) analogously.
+    = \dotsb][\cid, \pid, \wid, t, l]\)) while also proving the correctness of 
+    \(\wid\) and knowledge of a signature on \(\sk_W\) by some \ac{CA}.
   }%
-  \label{fig:ProofFig}
+  \label{proofshare-trusted-fig}
 \end{figure}%
@@
 pseudonym~\(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
-% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
+% (see \cref{proofshare-trusted-fig} and \cref{ACprfAlg} in the appendix for details of 
 %the algorithms)%
@@
 In the participation phase, the protester and 
-the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+the witness construct the proof share of the protester (\cref{proofshare-trusted-fig}).
 
@@
 Finally, the complete proof share is the tuple \[
-  \psh_W = (\cid, \pid, \wid, t, l, \corr_{\wid}).
+  \psh = (\cid, \pid, \wid, t, l, \corr_{\wid}).
 \]
@@
         \\
-      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
+      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid]% \\
       %W\to P\colon & (\wid, t, l)
@@
     and
-    their computations are as in \cref{fig:ProofFig}.
+    their computations are as in \cref{proofshare-trusted-fig}.
     Finally, \(W\) submits the proof share to a public ledger~\(\TS\) for 

### 2020-04-29 paper/protocol-trusted.tex
Fixes typo in trusted (\psh_W -> \psh)

@@
 \paragraph*{Submission:
-  \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}
+  \(\psh\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t, l]\)}
 
@@
 some permanent storage, such as the ledger~\(\TS\) by running 
-\(\TSsubmit[\psh_W]\) (\cref{ledger}).
+\(\TSsubmit[\psh]\) (\cref{ledger}).
 
 Note that it does not matter if it is the witness or the protester who makes 
-\(\psh_W\) available to the verifier.
-The witness could compute \(\psh_W\) during the protest and give to the 
+\(\psh\) available to the verifier.
+The witness could compute \(\psh\) during the protest and give to the 
 protester immediately, but we separate these steps to show that the witness can 
@@
 t, l, \corr_{\wid})\) such that \(\corr_\wid\) proves knowledge of a signature 
-by \(\sskw\), where \(\CA'\) is someone the verifier trusts\footnote{%
-  We note that there can be more than one \ac{CA} which the verifier trusts 
-  will issue credential only to trustworthy witnesses,
-  but we keep to one for the simplicity of our exposition.
-}.
+by \(\sskw\).
 We denote this set of proof shares by \(\pshs\).
@@
 \) is true if \(\pid = \pid'\).
-Each equivalence class \(\prf_{i, \prtst} \in \pshs/=_\pid\) is a proof of 
+Each equivalence class \(\prf_{i, \prtst} \in \pshs/{=_\pid}\) is a proof of 
 participation for participant \(i\).
-In terms of \cref{DefParticipationCount}, the set of 
-proofs~\(\prfs_\prtst^{\str, \theta} = \pshs/=_\pid\), where \(\theta = 1\) and 
-\(\str(\cdot) = 1\).
-Consequently, the total participation count is \(|\pshs/=_\pid|\).
+In terms of \cref{DefParticipationCount}, we let \(\theta = 1\) and \[
+  \str(\psh) =
+    \begin{cases}
+      1 & \text{if the verifier trusts \(\CA'\) to issue only to trustworthy 
+        witnesses} \\
+      0 & \text{otherwise}
+    \end{cases}.
+\] Consequently, the total participation count is \(|\prfs_\prtst^{\str, 
+\theta}|\).
 

### 2020-05-07 paper/protocol-trusted.tex
Slight clarifications

@@
 Upon success, the participant sets \(\sk = (\sigma, k, r)\).
+
+The key~\(\sk\) can be used together with \(\ACprf\) to create a 
+pseudonym~\(p\gets \ACprf[_k][c]\) in a particular context~\(c\) (see 
+\cref{ACprfAlg}).
+There exists \iac{PK} such that one can prove that \(p\) is computed correctly 
+from \(c\) with a valid key~\(\sk\) (see \cref{ACprfPKalg} or \cite{AnonPass} 
+for details).
 

### 2020-05-08 paper/performance.tex
Adds performance analysis

--- 2019-03-01 paper/analysis-performance.tex
@@
-\section{Performance}
-\label{PerformanceAnalysis}
-\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
+\section{Performance}%
+\label{performance}
 
-\subsection{Smartphones and smartcards}
-Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity.
-Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
-For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}.
-However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
-While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.
+We will now review the performance of the proposed protocols.
+Since the construction is designed as a drop-in replacement for the Schnorr 
+identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
+how much we must \enquote{pay} for the \ac{DB} property.
 
-With respect to its implementation, \CROCUS is actually very similar to Anon-Pass~\cite{AnonPass}, an anonymous subscription system in which a long-term credential can be used to derive a single login for any authentication window (\ie epoch) such that logins are unlinkable across different epochs.
-In particular, the setup and registration phases are almost identical. 
-The evaluation conducted by the authors was using as server a Dell Optiplex 780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz Intel Core 2 CPU but with only 4 GB of RAM.
-The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
-This is typically the type of pairing that could also be used with \CROCUS.
-Not counting the setup that is performed once by the CA, the time reported for the registration on the server (\ie CA) side is 19.8 milliseconds while it is 23.4 milliseconds on the client side.
-With respect to joining and participation phases, with the exception of the distance-bounding they are actually quite similar to the login protocol of Anon-Pass in which the time required to create a message for a protester would be around 13.5 milliseconds while the time needed for the witness would be only 7.9 milliseconds.
+\paragraph*{Mutual trust}
 
-\subsection{Distance-bounding anonymous credentials}
-The distance-bounding chips~\cite{3dB-access} currently available on the market 
-can already enable proofs of proximity for any range of up to 
-  200 meters.
-One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
-For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
-More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode.
-The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).
+We start with the mutual-trust version of the protocol in \cref{DB-Schnorr-UWB} 
+(see \cref{DB-Schnorr-UWB-figure}).
 
-% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
-% The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
-% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
-%Seb: to do add the reference to the following paper at the end of the sentence:
-%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
-%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
-% Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
-% However, this can be reduced to four random number generations and one exponentiation using precomputation.
+In \emph{one round} of the protocol, the cost of the verifier is that of 
+generating \(m\) number of \(l\)-bit strings, instead of only one.
+This costs the verifier a factor \(m\) of randomness.
+The cost of the prover is that of computing \(m\) number of replies (\(s\gets 
+\rho - c \alpha \mod q\)), instead of only one.
 
-%\paragraph{Threshold of witnesses.}
-%Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
-%Then it would be reasonable to set the threshold of at least 6000 witnesses.
-%According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
-%signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
-%\SI{2.66}{\giga\hertz} Core 2 processor.
-%This yields \(
-%  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-%  \SI{48}{\second}.
-%\) of processing.
+To achieve security, the protocol must be repeated \(n\) times.
+We have the \(l\)-parameter which controls the soundness of the \ac{ZKPK} and 
+the \(m\)-parameter controls the soundness of the \acl{DB}.
+If we want to achieve 80 bits of security, we can let \(l = m = 6\) (remember, 
+\(l\) must be logarithmic in the security parameter) and \(n = 14\).
+This makes \acl{DB} a factor \(6\) more expensive over the 
+\emph{malicious-verifier secure} Schnorr protocol.
 
-\subsection{Ledger (blockchain) efficiency}
-As an example, consider a protest with 1\,000\,000 participants.
-If we use trusted witnesses, each participant only needs to acquire one proof share from a trusted witness.
-Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
-If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.
+\paragraph*{\acs*{PKI}}
 
-If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
-While this already takes longer than counting votes in national elections, the threshold is still very low. 
-% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
-% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
-% In addition to the ledger computation, we need to consider the creation of the proof shares.
-\sonja{added the previous sentence to explain why anonpass shows up here.
-Shouldn't that be in the performance section?
-}
-% %Seb: I agree maybe we should move it to the previous subsection
-% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
-% This yields \(
-%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
-%   \SI{48}{\second}.
-% \) of processing. 
-For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
-Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
+The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
+performs one signature verification and four additional proofs in parallel.
+The cost for the verifier is one signature verification in addition to the 
+factor \(m\) of randomness used.
+On the prover side, we have the computations for the signature verification and 
+four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
+for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
+\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).
 
-%\subsection{Blockchain efficiency}
+The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
+implements a public transport pass using this signature scheme.
+The signature need not be reverified \(n\) times, it is sufficient to verify 
+that once and reuse the same blinding for all \(n\) repetitions of the 
+protocol.
+Thus it is only the \acl{PK} that must be rerun \(n\) times.
 
-\sonja{removed for now: One problem can arise in the case in which there is no trusted witnesses.
-In this situation, if we set the threshold too high, we need to submit more proof shares than the blockchain can handle within a reasonable time.}
+\paragraph*{Bit-by-bit}
 
-%assumptions about smartphones:
-%(This means that we essentially provide a lower bound for the participation 
-%count, since some participants might not have such a device.)
-%Sonja says: is this still true? Given mafia fraud we can't guarantee
-%that, right?
+The traditional bit-by-bit version of the protocol 
+(\cref{DB-Schnorr-nbit,DB-Schnorr-nbit-figure}) is not as efficient.
+That is due to \(m = 2\) being fixed in this case (there are only two responses 
+to choose from), and consequently, we must have a larger value for \(n\) to 
+achieve the desired security.

### 2020-05-08 paper/DB-Schnorr-PKI.tex

--- 2020-03-13 paper/DB-Schnorr-PKI.tex
@@
 
-    \midrule
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
     Load \(k\) into \(\UWBPR\)
@@
     \\
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Signature reblinding}} \\
 
@@
     \\[0.5em]
+
+    \midrule
+    \multicolumn{3}{c}{\textbf{Setup}} \\
 
@@
 The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.
+They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
+\(\UWBPR\), instead of a static \(k\).
 
-\paragraph*{Setup}
+\paragraph*{Signature reblinding}
 
 The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
-They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
-\(\UWBPR\), instead of a static \(k\).
 \(\DBS\) performs \(
@@
 
+This blinding procedure can be done once, there is no point in presenting the 
+verifier with several different blindings of the same signature.
+
+\paragraph*{Setup}
+
+Now we prepare for the actual \acl{DB}.
 The prover chooses \[
@@
 \]
+
+The setup, distance bounding and verification phases are repeated \(n\) times.
 

### 2020-05-08 paper/formal-verification.tex
Removes comments on secret sharing (fixes #49)

--- 2020-03-14 paper/formal-verification.tex
@@
 But Tamarin's attacker is not able to manipulate arithmetic this way, so we provide him $\alpha$ directly.
-	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
-\simon{not sure if this is still relevant, or obsoleted by the bit-by-bit version}
 	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.

### 2020-05-08 paper/tamarin-spec.tex
updating comment in tamarin spec
Removes comments on secret sharing (fixes #49)

@@
 
-\sonja{Clarification of these explanations needed. Split up some text
+\sonja{Old comment, probably for crocus: Clarification of these explanations needed. Split up some text
   to go into the body of the paper and leave details (or even just the
@@
 	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
-	\item We ignored the secret sharing step; it is aimed at not leaking any information about the prover's secret key --not even the first $l$ bits--, which is not a property we are trying to formally prove with Tamarin here.
 	\item We represented the challenge/response as a single-round step; the multi-round process is designed to resist against probabilistic attacks where a dishonest prover simply guess the response values in advance, but this type of attacks isn't covered by Tamarin's model anyway.

### 2020-06-01 slides/contents.tex
Updates slides to focus on DB-Schnorr

\mode*

\section{Distance bounding}

\subsection{Some scenarios}

\begin{frame}
  \begin{figure}
    \includegraphics[width=0.8\columnwidth]{keyless-car-theft.jpg}
    \caption{%
      How does the car know the key is close to the car?
      Image: Business Motoring.
    }
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=0.8\columnwidth]{v2v-communication.jpg}
    \caption{%
      How can a car know that the other car is \emph{actually} there?
      Image: NHTSA.
    }
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=0.8\columnwidth]{sensor-networks.jpg}
    \caption{%
      How does a sensor in a sensor network know the other sensors are where 
      they claim?
      Image: Toshiba.
    }
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=0.5\columnwidth]{trump.jpg}
    \caption{%
      How can someone prove they were there?
      Image: reddit.
    }%
  \end{figure}
\end{frame}

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Protection from \acs{MITM} doesn't prevent relaying.
    \end{itemize}
  \end{remark}
\end{frame}

\subsection{Distance-bounding essentials}

\Cref{DBMF,DBTF,DBDH,DBDF} illustrate the four frauds against which \ac{DB} 
should protect.
These frauds are all variants of relay attacks.
Let Alice and Bob be guards, Carol and David wants to enter, but David is not 
authorized to do so.
In the \ac{DBMF} attack (\cref{DBMF}), Alice collaborates with David to pass 
Bob's authentication step.
When Bob gives David the challenge \(C\), he calls Alice to say he got the 
challenge \(C\) from Bob.
Alice asks Carol the same challenge.
Carol honestly responds with the correct response \(R\) and Alice replies \(R\) 
to David.
Now David can tell Bob the correct response \(R\) to enter.

Common \ac{DBMF} attack scenarios are to make someone else pay for something or 
to steal premium cars with passive keyless entry (by relaying the communication 
between the keyfob and the car).

\begin{frame}
  \begin{figure}
    \includegraphics[width=\textwidth]{MF.png}
    \caption{\Acl{DBMF}}\label{DBMF}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=\textwidth]{TF.png}
    \caption{\Acl{DBTF}}\label{DBTF}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=\textwidth]{DH.png}
    \caption{\Acl{DBDH}}\label{DBDH}
  \end{figure}
\end{frame}

\begin{frame}
  \begin{figure}
    \includegraphics[width=\textwidth]{DF.png}
    \caption{\Acl{DBDF}}\label{DBDF}
  \end{figure}
\end{frame}

The key observation here is that Bob would notice that David calls Alice.
The important part is how we model this detection.
The way Bob will detect that David is talking to Alice, and effectively 
relaying Carol's response to Bob, is by time.
The relay will make David slower to answer the challenge.
If we detect relays by time of flight, we can detect any type of relaying: no 
matter if Bob calls Alice with his phone in plain sight or wears a 
secret-agent-like ear-piece.

Technically, it will be electronics that run the protocol, which means that we 
can do things very fast.
Bob will measure the round-trip time from when he sent the challenge to when he 
received the reply.
If Bob wants to be sure that it is actually David who responds, he can set a 
maximum limit of \eg one metre distance.
Then this round-trip time cannot be longer than the time it would take an 
electro-magnetic wave to travel one metre there and one metre back.
Since electro-magnetic waves travel with the speed of light, the round-trip 
time must be \emph{very small}.

In the \ac{DBTF} attack (\cref{DBTF}), David doesn't need Alice, instead Carol 
collaborates directly with David.
We see that, although we have removed Alice, any form of relay will still be 
detected due to time.
One option for David and Carol is that Carol simply gives her cryptographic key 
to David.
Then David can compute any responses he needs and pass Bob's challenge.
However, we \emph{assume} that Carol wouldn't do that.
Is this a realistic assumption?
If Carol completely trusts David, then it's not.
But there are circumstances when it arguably is.
If this cryptographic key is use to more things than just pass Bob's 
authentication, \eg it is Carol's electronic ID (\eg the Swedish BankID).
Then David could do anything in Carol's name once he has her key, like he could 
transfer all her money to his own account.
If Carol doesn't trust David to not do this, then it is realistic to assume 
that she wouldn't give David a copy of her key.

An example of where this is a realistic attack scenario is public transport.
Where David and Carol can share a single subscription.
However, if the two cannot use the subscription simultaneously, David's 
unlimited use might temporarily lock Carol out.
This inconvenience can serve as the incentive that validates the assumption.

In the \ac{DBDH} attack (\cref{DBDH}), David tries to authenticate to Bob.
But Alice wants to trick Bob into believing that David is Alice (against 
David's will).
By letting David do the bulk of timed responses, Alice might be able to time 
just a few key parts to make Bob believe that he is talking to her instead of 
David.
\Ac{DBDH} is sort of a special case of \ac{DBDF} (\cref{DBDF}), where Alice is 
simply trying to convince Bob that she is close when she actually isn't.

Both of these attacks are realistic when Alice, \eg, must register that she was 
physically present.
For instance, she must prove to her employer that she was at the office.
(For this scenario we find \ac{DBTF} also very relevant, since Alice might 
collaborate with a colleague at the office otherwise.)

\mode<presentation>{%
\begin{frame}
  \begin{question}
    \begin{itemize}
      \item How does a device know that another device is \emph{actually} 
        present?
    \end{itemize}
  \end{question}

  \pause

  \begin{idea}[\Acl*{DB}~\cite{DistanceBounding}]
    \begin{itemize}
      \item Measure round-trip time to estimate maximum distance.
      \item \dots for the authentication.
    \end{itemize}
  \end{idea}
\end{frame}
}

\section{Distance-bounding proofs-of-knowledge}

Now we will turn to the problem of \ac{DB} and the contribution of the paper in 
\cref{db-schnorr-paper}.
Above, we left the problem of how does a witness know that the protester is 
actually present?
\Ac{MITM} protection does not protect from \emph{relaying}, for this we need 
\ac{DB}.

\subsection{Our contribution}

Most protocols in the area of \acl{DB} are symmetric.
This means that the verifier must be trusted.
This doesn't work with the crowd counting scenario above, since by design the 
witnesses must be trusted to keep the protester's \ac{eID} keys secret.
The alternative approach is asymmetric, or public-key based.
However, all are identity-based, but possibly anonymous (as in group or ring 
signatures).
We need Sybil-proof pseudonymity, which none of the existing schemes can 
provide.

\Textcite{SelfCertifiedSybilFreePseudonyms} constructed such self-certified 
Sybil-free pseudonyms from the anonymous-credential scheme by 
\textcite{HowToWinTheCloneWars}.
These are based on \ac{ZKPK} for discrete logarithms.
While \citeauthor{SelfCertifiedSybilFreePseudonyms} worked purely in the 
non-interactive domain, the foundation by \citeauthor{HowToWinTheCloneWars} 
could be both interactive and non-interactive.
The protocol by which they achieve the \ac{ZKPK} property they need is the 
Schnorr identification scheme~\cite{Schnorr}.
This protocol is \iac{ZKPK} for discrete logarithms, but not \acl{DB}.
Our contribution is \iac{DB} version of the Schnorr protocol.
Hence, by replacing the Schnorr protocol by our DB-Schnorr version in any 
protocol where it is used, we make that protocol \acl{DB} --- and hence 
resistant to the relay attacks presented above 
(\cref{illustrations-DB-frauds}).
From the work of 
\textcite{SelfCertifiedSybilFreePseudonyms,HowToWinTheCloneWars} we can then 
construct the \emph{\acl{DB}} Sybil-proof pseudonyms that we need for the crowd 
counting.

\mode<presentation>{%
\begin{frame}
  \begin{solution}
    \begin{itemize}
      \item Adds protection against \acs{DB} attacks to Schnorr~\cite{Schnorr}:
        \begin{itemize}
          \item \Acl{DBDF}
          \item \Acl{DBDH}
          \item \Acl{DBMF}
          \item \Acl{DBTF}
        \end{itemize}

      \item Two versions:
        \begin{enumerate}
          \item Mutual trust
          \item \acs{PKI} based
        \end{enumerate}
    \end{itemize}
  \end{solution}
\end{frame}

\begin{frame}
  \begin{example}[Use cases]
    \begin{itemize}
      \item Distance bounding Direct Anonymous Attestation (TPM standard).
      \item Distance bounding, privacy-preserving attribute-based credentials 
        (CL04 \etc).
      \item BankID to enter the pub or buy from Systembolaget?
    \end{itemize}
  \end{example}
\end{frame}
}

\subsection{Performance}%
\label{performance}

\mode<presentation>{%
  \begin{frame}
    \begin{question}
      \begin{itemize}
        \item How costly is this compared to non-\acs{DB} Schnorr?
      \end{itemize}
    \end{question}
  \end{frame}
}

We will now review the performance of the proposed protocols.
Since the construction is designed as a drop-in replacement for the Schnorr 
identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
how much we must \enquote{pay} for the \ac{DB} property.
We summarize the results in \cref{performance-overview}.

\begin{frame}
  \begin{table}
    \caption{%
      A summary of how costly \acl*{DB} is in terms of performance.
      The \acs*{PKI} version additionally needs one signature verification.
      \(m, l\in \mathcal{O}(\log \lambda)\).
    }\label{performance-overview}
    \begin{tabular}{lrrrr}
      \toprule
      Protocol
      & Rand.
      & Arith.
      & Exp.
      & Pairings\\
      \midrule
      Schnorr             & \(l\)             & 3    & 3      & 0\\
      DB, mutual          & \(ml\)            & 3m   & 3      & 0\\
      DB, \acs*{PKI} \(\sum\)
                          & \(8\lambda + ml\)
                          & \(10m+8\)
                          & \(25\)
                          & \(14\)\\
      ---\acs*{DHKE}      & \(\lambda\)       & 0    & 4      & 0\\
      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
      ---DB               & \(5\lambda + ml\)    & \(10m + 2\) & 6 & 0\\
      ---Verification     & 0    & 6 & 10 & 6\\
      \bottomrule
    \end{tabular}
  \end{table}
\end{frame}

\paragraph*{Mutual trust}

We start with the mutual-trust version of the protocol in \cref{DB-Schnorr-UWB} 
(see \cref{DB-Schnorr-UWB-figure}).

In \emph{one round} of the protocol, the cost of the verifier is that of 
generating \(m\) number of \(l\)-bit strings, instead of only one.
This costs the verifier a factor \(m\) of randomness.
The cost of the prover is that of computing \(m\) number of replies (\(s\gets 
\rho - c \alpha \mod q\)), instead of only one.

To achieve security, the protocol must be repeated \(n\) times.
We have the \(l\)-parameter which controls the soundness of the \ac{ZKPK} and 
the \(m\)-parameter controls the soundness of the \acl{DB}.
If we want to achieve 80 bits of security, we can let \(l = m = 6\) (remember, 
\(l\) must be logarithmic in the security parameter) and \(n = 14\).
This makes \acl{DB} a factor \(6\) more expensive over the 
\emph{malicious-verifier secure} Schnorr protocol.

\paragraph*{\acs*{PKI}}

The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
performs one signature verification and four additional proofs in parallel.
The cost for the verifier is one signature verification in addition to the 
factor \(m\) of randomness used.
On the prover side, we have the computations for the signature verification and 
four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).

The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
implements a public transport pass using this signature scheme.
The signature need not be reverified \(n\) times, it is sufficient to verify 
that once and reuse the same blinding for all \(n\) repetitions of the 
protocol.
Thus it is only the \acl{PK} that must be rerun \(n\) times.

\paragraph*{Bit-by-bit}

The traditional bit-by-bit version of the protocol 
(\cref{DB-Schnorr-nbit,DB-Schnorr-nbit-figure}) is not as efficient.
That is due to \(m = 2\) being fixed in this case (there are only two responses 
to choose from), and consequently, we must have a larger value for \(n\) to 
achieve the desired security.

\section{Conclusions}

\mode<presentation>{%
\begin{frame}
  \begin{block}{Contributions}
    \begin{itemize}
      \item Distance-bounding Schnorr protocol
      \item Drop in replacement for Schnorr to add \acl{DB} to any protocol.
      \item \Eg distance-bounding privacy-preserving attribute-based 
        credentials based on \cite{HowToWinTheCloneWars}
    \end{itemize}
  \end{block}
\end{frame}
}

One insight is that we cannot provide deniability in the crowd counting 
scenario.
Deniability is at odds with Sybil resistance.
Since the pseudonym of the protester is a deterministic function of the 
protester's key and the protest's cause identifier, Eve can use that pseudonym 
as a commitment.
She can recompute the pseudonym, see if it is in the set of pseudonyms that 
claimed participation or not.
However, Eve must have access to Alice's key to do this verification.
Due to anonymity, to learn who participated Eve must do this verification for 
the entire population that she is interested in, this is expensive.

Another potential attack to consider is framing:
Eve dislikes the head-of-opposition~Alice, it is not unlikely that she would 
like to frame Alice for participating in a protest to smear Alice.
When Eve verifies if Alice participated in a particular protest, as outlined 
above, she could take the opportunity to try to generate a proof of 
participation.
While the cryptographic aspects of the proof would verify correctly, Eve cannot 
control the time-stamping service.
So any honest verifier would reject it since its time interval would not verify 
correctly.
So even if Eve has access to Alice's key, she cannot forge the temporal 
eligibility\footnote{%
  At the very least, she might not be able to forge a witnessing for spatial 
  eligibility either.
}.

How does this differ with voting?
In voting it is well-established that Alice must be able to deny voting in any 
particular way.
Participation in a vote is also \emph{undeniable}, it is how the vote was cast 
that is deniable.
This works for questions with a few given alternative answers, Alice can deny 
what she answered, but not that she answered.
This is different for petitions or protests, where Alice's mere participation 
implies her opinions.

%\begin{frame}
%  \begin{greenblock}{Possibilities}
%    \begin{itemize}
%      \item We can implement this by extending BankID.
%      \item There are blockchains (ledgers) with reasonable transaction 
%        throughput, \eg OmniLedger.
%    \end{itemize}
%  \end{greenblock}
%
%  \pause
%
%  \begin{alertblock}{Limits}
%    \begin{itemize}
%      \item Cannot trust results that are pro-government if government issues 
%        credentials (Sybil).
%
%      \item Needs transparency and accountability in issuing.
%
%      \item Requires a chip in smartphones for distance bounding.
%    \end{itemize}
%  \end{alertblock}
%\end{frame}

\paragraph*{Future work}

%\mode<presentation>{%
%\begin{frame}
%  \begin{block}{Future work}
%    \begin{itemize}
%      \item Formally prove the protocols.
%      \item How hard to Sybil attack the parliamentary election?
%      \item Turn analog IDs into digital ones?
%    \end{itemize}
%  \end{block}
%\end{frame}
%}

While working on this topic, the following question emerged:
how difficult would it be for a nation state, \eg Sweden, to perform a Sybil 
attack on the identity system?
Certainly, it is easier to cheat in the elections in some states and more 
difficult in others.
But how difficult is it to cheat significantly in an election in a Western 
democracy, such as Sweden?

Now, this type of \enquote{analogue} identity management that are used for 
paper-based elections has been well established for a long time in most parts 
of the world.
Digital identities, however, are not as well established.
There are only certain countries which has a coverage of more than \SI{90}{\%} 
of the population.
How can we turn these \enquote{analogue} identity certificates (\eg passports) 
into digital ones, while preserving privacy and without introducing additional 
trust?
For instance, with the Swedish BankID we convert an analogue ID to a digital 
one, but the way this is done introduces another entity (the banks) that a 
verifier must trust to do the check of the analogue ID correctly.
Can we at least reduce the amount of new trust that we must introduce?
There are suggestions such as proof-of-personhood~\cite{proof-of-personhood} 
that will never scale.

\mode<presentation>{%
  \begin{frame}
    \begin{center}
      Questions, comment, other thoughts?
    \end{center}
  \end{frame}
}

### 2020-06-03 paper/performance.tex
Adds a table summarizing the performance

@@
 \label{performance}
+
+\mode<presentation>{%
+  \begin{frame}
+    \begin{question}
+      \begin{itemize}
+        \item How costly is this compared to non-\acs{DB} Schnorr?
+      \end{itemize}
+    \end{question}
+  \end{frame}
+}
 
@@
 how much we must \enquote{pay} for the \ac{DB} property.
+We summarize the results in \cref{performance-overview}.
+
+\begin{frame}
+  \begin{table}
+    \caption{%
+      A summary of how costly \acl*{DB} is in terms of performance.
+      \(m, l\in \mathcal{O}(\log \lambda)\).
+    }\label{performance-overview}
+    \begin{tabular}{lrrrr}
+      \toprule
+      Protocol
+      & Rand.
+      & Arith.
+      & Exp.
+      & Pairings\\
+      \midrule
+      Schnorr             & \(l\)             & 3    & 3      & 0\\
+      DB, mutual          & \(ml\)            & 3m   & 3      & 0\\
+      DB, \acs*{PKI} \(\sum\)
+                          & \(8\lambda + ml\)
+                          & \(10m+8\)
+                          & \(25\)
+                          & \(14\)\\
+      ---\acs*{DHKE}      & \(\lambda\)       & 0    & 4      & 0\\
+      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
+      ---DB               & \(5\lambda + ml\)    & \(10m + 2\) & 6 & 0\\
+      ---Verification     & 0    & 6 & 10 & 6\\
+      \bottomrule
+    \end{tabular}
+  \end{table}
+\end{frame}
 

### 2020-06-03 paper/performance.tex
Improves performance table

--- 2020-05-08 paper/performance.tex
@@
 how much we must \enquote{pay} for the \ac{DB} property.
+We summarize the results in \cref{performance-overview}.
+
+\begin{frame}
+  \begin{table}
+    \centering
+    \caption{%
+      A summary of how costly \acl*{DB} is in terms of randomness, arithmetic 
+      operations (addition, multiplication), exponentiations and pairing 
+      operations.
+      \(m, l\in \mathcal{O}(\log \lambda)\) and we must repeat the protocol 
+      \(n\) times to achieve desired soundness.
+    }\label{performance-overview}
+    \begin{tabular}{lrrrr}
+      \toprule
+      Protocol
+      & Rand.~(\si{\bit})
+      & Arith.~(\(+, \times\))
+      & Exp.
+      & Pairings\\
+      \midrule
+      Schnorr             & \((\lambda+l)n\)  & \(3n\) & \(3n\) & 0\\
+      DB, mutual          & \((\lambda+ml)n\) & \(3mn\)& \(3n\) & 0\\
+      DB, \acs*{PKI} \(\sum\)
+                          & \(4\lambda + (5\lambda + ml)n\)
+                          & \((10m+8)n\)
+                          & \(9 + 16n\)
+                          & \(14\)\\
+      ---\acs*{DHKE}      & \(2\lambda\)      & 0    & 4      & 0\\
+      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
+      ---DB               & \(5\lambda + ml\) & \(10m + 2\) & 6 & 0\\
+      ---Verification     & 0    & 6 & 10 & 6\\
+      \bottomrule
+    \end{tabular}
+  \end{table}
+\end{frame}
 
@@
 performs one signature verification and four additional proofs in parallel.
-The cost for the verifier is one signature verification in addition to the 
-factor \(m\) of randomness used.
+The cost for the verifier is one signature verification 
+(CL04~\cite{CLsignatures}) in addition to the factor \(m\) of randomness used.
 On the prover side, we have the computations for the signature verification and 
@@
 implements a public transport pass using this signature scheme.
-The signature need not be reverified \(n\) times, it is sufficient to verify 
-that once and reuse the same blinding for all \(n\) repetitions of the 
-protocol.
+This signature verification introduces more additions, multiplications, 
+exponentiations and pairing operations.
+However, the signature will only be blinded and verified once, so this 
+represents a constant factor.
+It is sufficient to verify it once and reuse the same blinding for all \(n\) 
+repetitions of the protocol.
+(The same is true for the \ac{DHKE}.)
 Thus it is only the \acl{PK} that must be rerun \(n\) times.

### 2020-07-02 paper/intro.tex

--- 2020-03-13 paper/intro.tex
@@
 We achieve all properties except \ac{DBTF} resistance.
+We see this contribution as merely for the sake of completion, as the previous 
+contributions are slightly more efficient.
 
@@
 \eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
+We can do this by simply replacing their use of the Schnorr 
+protocol~\cite{Schnorr} for \acp{ZKPK} with our protocol in this paper.
 To our knowledge, no other distance-bounding protocol achieves this.
 The third contribution (bit-by-bit version) also enables us to do the same, 
-just without \ac{DBTF} resistance.
+just without (full) \ac{DBTF} resistance.
 
@@
 The paper is organized as follows.
-\Cref{related-work} discusses related work.
+\Cref{related-work} discusses some related work.
 \Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.

### 2020-07-02 slides/contents.tex
Points out proven in DFKO and Tamarin, highlights speaker
Shortens one section title

@@
 
-\section{Distance-bounding proofs-of-knowledge}
+\section[\acs*{DB} \acsp*{ZKPK}]{Distance-bounding \aclp*{ZKPK}}
 
@@
         \end{enumerate}
+
+      \item Proven in the DFKO model and Tamarin.
     \end{itemize}
@@
         (CL04 \etc).
-      \item BankID to enter the pub or buy from Systembolaget?
     \end{itemize}
@@
 
-\mode<presentation>{%
-  \begin{frame}
-    \begin{question}
-      \begin{itemize}
-        \item How costly is this compared to non-\acs{DB} Schnorr?
-      \end{itemize}
-    \end{question}
-  \end{frame}
-}
-
-We will now review the performance of the proposed protocols.
-Since the construction is designed as a drop-in replacement for the Schnorr 
-identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
-how much we must \enquote{pay} for the \ac{DB} property.
-We summarize the results in \cref{performance-overview}.
-
-\begin{frame}
-  \begin{table}
-    \caption{%
-      A summary of how costly \acl*{DB} is in terms of performance.
-      The \acs*{PKI} version additionally needs one signature verification.
-      \(m, l\in \mathcal{O}(\log \lambda)\).
-    }\label{performance-overview}
-    \begin{tabular}{lrrrr}
-      \toprule
-      Protocol
-      & Rand.
-      & Arith.
-      & Exp.
-      & Pairings\\
-      \midrule
-      Schnorr             & \(l\)             & 3    & 3      & 0\\
-      DB, mutual          & \(ml\)            & 3m   & 3      & 0\\
-      DB, \acs*{PKI} \(\sum\)
-                          & \(8\lambda + ml\)
-                          & \(10m+8\)
-                          & \(25\)
-                          & \(14\)\\
-      ---\acs*{DHKE}      & \(\lambda\)       & 0    & 4      & 0\\
-      ---CL04 blind       & \(2\lambda\)      & 0    & 5      & 8\\
-      ---DB               & \(5\lambda + ml\)    & \(10m + 2\) & 6 & 0\\
-      ---Verification     & 0    & 6 & 10 & 6\\
-      \bottomrule
-    \end{tabular}
-  \end{table}
-\end{frame}
-
-\paragraph*{Mutual trust}
-
-We start with the mutual-trust version of the protocol in \cref{DB-Schnorr-UWB} 
-(see \cref{DB-Schnorr-UWB-figure}).
-
-In \emph{one round} of the protocol, the cost of the verifier is that of 
-generating \(m\) number of \(l\)-bit strings, instead of only one.
-This costs the verifier a factor \(m\) of randomness.
-The cost of the prover is that of computing \(m\) number of replies (\(s\gets 
-\rho - c \alpha \mod q\)), instead of only one.
-
-To achieve security, the protocol must be repeated \(n\) times.
-We have the \(l\)-parameter which controls the soundness of the \ac{ZKPK} and 
-the \(m\)-parameter controls the soundness of the \acl{DB}.
-If we want to achieve 80 bits of security, we can let \(l = m = 6\) (remember, 
-\(l\) must be logarithmic in the security parameter) and \(n = 14\).
-This makes \acl{DB} a factor \(6\) more expensive over the 
-\emph{malicious-verifier secure} Schnorr protocol.
-
-\paragraph*{\acs*{PKI}}
-
-The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
-performs one signature verification and four additional proofs in parallel.
-The cost for the verifier is one signature verification in addition to the 
-factor \(m\) of randomness used.
-On the prover side, we have the computations for the signature verification and 
-four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
-for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
-\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).
-
-The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
-implements a public transport pass using this signature scheme.
-The signature need not be reverified \(n\) times, it is sufficient to verify 
-that once and reuse the same blinding for all \(n\) repetitions of the 
-protocol.
-Thus it is only the \acl{PK} that must be rerun \(n\) times.
-
-\paragraph*{Bit-by-bit}
-
-The traditional bit-by-bit version of the protocol 
-(\cref{DB-Schnorr-nbit,DB-Schnorr-nbit-figure}) is not as efficient.
-That is due to \(m = 2\) being fixed in this case (there are only two responses 
-to choose from), and consequently, we must have a larger value for \(n\) to 
-achieve the desired security.
+\input{../performance.tex}
 

### 2020-07-03 paper/DB-Schnorr-nbit.tex
Cuts bit-by-bit version

@@
 
-\subsection{Security of the \(l\) bits}
+\subsection{Security analysis}
 
-Before we proceed to other security properties, we will address the \(l\)-bit 
-problem:
-what advantage does the adversary get from those \(l\) leaked bits of the 
-second response?
+We can prove this protocol secure against \ac{DBMF}, \ac{DBDH} and \ac{DBDF}; 
+but not against \ac{DBTF}.
+Those proofs are available in the full version of the paper.
+Here, we will discuss only the most crucial differences.
 
-\paragraph*{The unconditional \(l\)-bit problem}
+\paragraph*{The \(l\)-bit problem}
 
-We run the protocol \(n\) times and let the adversary learn \(m+l\) bits of the 
-result~\(s_i, s_i'\).
-This yields the following equation system:
-\begin{align*}
-  s_0[0]2^0 + \dotsb + s_0[m-1]2^{m-1} &= r_0 + c\alpha &\pmod q\\
-  s_0'[0]2^0 + \dotsb + s_0'[m-1]2^{m-1} &= r_0 + c'\alpha &\pmod q\\
-  \vdots \\
-  s_{n-1}[0]2^0 + \dotsb + s_{n-1}[m-1]2^{m-1} &= r_{n-1} + c\alpha &\pmod q\\
-  s_{n-1}'[0]2^0 + \dotsb + s_{n-1}'[m-1]2^{m-1} &= r_{n-1} + c'\alpha, &\pmod 
-  q
-\end{align*}
-where \(m+l\) of \(s_i[j]\)'s and \(s_i'[j']\)'s for each \(i\) are known by 
-the adversary.
-
-\begin{lemma}\label{l-bit-advantage}
-  If \[l < m-1+\frac{1}{n}-\frac{f(\lambda)}{n},\] then there are at least 
-  \(2^{f(\lambda)}-1\) unique solutions, for some function~\(f\) of the 
-  security parameter~\(\lambda\).
-\end{lemma}
-
-The proof is in \cref{proofs-lbit}.
-
-\paragraph*{The \(l\)-bit problem with commitments}
-
+We can show that the system of linear equations created by the protocol and 
+consisting of leaked bits from the second reply is underdetermined.
+However, we cannot get information theoretic security, that would require 
+leaking no bits, but we leak some bits.
+The only lead an adversary get to those remaining unknown bits are the 
+commitments.
 The adversary has a commitment to the randomness~\(r_i\) in the form of \(R_i = 
@@
 
-The proof is in \cref{proofs-lbit}.
+The proof of this lemma can be found in the full version of the paper.
 
-As mentioned above, both \(l\) and \(k\) are logarithmic in the security 
-parameter.
-
-\subsection{\Acl*{ZK} and \acl*{PK}}\label{nbit-ZKPK}
+\paragraph*{\Acl*{ZK} and \acl*{PK}}\label{nbit-ZKPK}
 
@@
 
+The change is with the \acl{ZK} property.
 This is \emph{computational} \acl{ZK}:
@@
 Now the simulator must come up with those \(l\) bits.
-\Cref{l-bit-advantage,DBSPtoDLP} say that distinguishing these bits from random 
-is as hard as the \ac{DLP}.
+By \cref{DBSPtoDLP} and some lemmas in the full version of the paper, we can 
+see that distinguishing these bits from random is comparable to solving the 
+\ac{DLP}.
 So, the simulator can simply choose the \(l\) bits~\(L\rgets \bin^l\) uniformly 
@@
 
-%Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
-%protocol with soundness error \(2^{-k n}\) still 
-%holds~\cite[\eg][]{OnSigmaProtocols}.
-%(We note that \(l\), which is also the length of the challenge bit string, must 
-%be logarithmic in the security parameter, \(\lambda\), for a malicious 
-%verifier.)
+\paragraph*{Why not \acs*{DBTF}?}
 
-\subsection{\acs*{DBMF}, \acs*{DBTF} and \acs*{DBDH} resistance}
-
-\paragraph{\Acl{DBMF}}
-
-In \ac{DBMF}, the adversary will try to authenticate to a verifier by querying 
-a far-away prover.
-By \cref{TaintedMF}, pure relaying will be detected by the verifier.
-So the adversary must resort to things like querying in advance \etc.
-
-\begin{theorem}[\acs*{DBMF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then \(
-    \Adv_{\DBS}^{\text{MF}}(\adv) =
-      \left(\frac{1}{2} + \frac{1}{2^{|q|-l}}\right)^n,
-  \) where \(m, q\) are as in \cref{DB-Schnorr-nbit}.
-\end{theorem}
-
-\begin{proof}
-  It follows from the \ac{ZK} property (\cref{nbit-ZKPK}) that the adversary 
-  cannot learn anything by observation.
-  This leaves the adversary with the following:
-  \begin{enumerate}
-    \item guess which challenge the verifier will use and request the correct 
-      response from the prover, receiving the challenge first would taint the 
-      session (\cref{TaintedMF});
-    \item guess the second response.
-  \end{enumerate}
-
-  The first case yields success with probability \(\frac{1}{2}\), since the 
-  choice is uniformly distributed over the two challenges.
-  The adversary requests all \(|q|\) bits of the response~\(s_{\hat b}\) and 
-  \(l\) bits of \(s_{1-\hat b}\).
-  When the verifier sends challenge bit \(b_i = \hat b\), the adversary replies 
-  with a bit from \(s_{\hat b}\).
-  If \(b_i = 1-\hat b\), then the adversary uses the \(l\) bits.
-
-  If the adversary guessed \(\hat b = b\) correctly, then the verifier will 
-  accept.
-  Otherwise, the adversary must compute the remaining \(|q|-l\) bits of 
-  \(s_{1-\hat b}\).
-
-  Guessing the remaining bits yield a success probability of 
-  \(\frac{1}{2^{|q|-l}}\).
-  \Cref{DBSPtoDLP} states that any algorithm that can compute the remaining 
-  bits can also solve a corresponding \ac{DLP}.
-  It follows that the adversary cannot do non-negligibly better than guessing 
-  the remaining bits.
-
-  Thus, the success probability is \(\frac{1}{2}+\frac{1}{2^{|q|-l}}\) per 
-  round, or \(\left(\frac{1}{2}+\frac{1}{2^{|q|-l}}\right)^n\) in total.
-\end{proof}
-
-\paragraph{\Acl{DBTF}}
-
-We cannot achieve \ac{DBTF} resistance.
-Indeed, the prover can send \(l+\nu\) bits of both response strings, \(s_0\) 
-and \(s_1\), to the adversary.
-When the adversary receives the \(l+1\)th bit, he learns \(b\).
-He can send \(b\) to the prover and answer correctly to the verifier, provided 
-\(\nu \geq 1\).
-By the time he receives the next challenge from the verifier, the prover will 
-have sent him the remaining bits of \(s_b\) without revealing more bits about 
-\(s_{1-b}\).
-This would not taint the session.
-As long as \(l+\nu\) is sufficiently small, the adversary cannot compute the 
-remaining bits of \(s_{1-b}\) to compute the prover's secret.
-
-\paragraph{\Acl{DBDH}}
-
-The protocol is also secure against distance hijacking due to the fact that the 
-authenticating bit string is used during the \ac{DB} phase.
-(Brands-Chaum used the challenge bit string, something that made their protocol 
-vulnerable.)
-\Ac{DBDH} requires that the adversary finds a collision between his response 
-and that of the honest prover.
-Thus the probability of success is equivalent to a collision for the responses 
-for the chosen challenge --- in each round.
-
-\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\).
-\end{theorem}
-
-\begin{proof}
-  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
-  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
-  \(R' = R\) to not interfere.
-
-  The verifier will choose \(c_0, \dotsc, c_1\).
-  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
-  is his secret.
-  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
-  c_i \alpha'\), where \(\alpha'\) is the adversary's secret.
-  If the adversary didn't choose \(R'\), he can only guess the values for 
-  \(s_i'\).
-
-  During the fast phase, the adversary has two options:
-  for each challenge bit, the adversary can \(\Commit\) to a response bit or to 
-  \(\Prompt\) the honest prover to send a bit.
-
-  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute the 
-  correct \(s_i' = \rho' - c_i \alpha'\) for \(i\in \bin\).
-  If the adversary \(\Commit\)s:
-  Now, the adversary must commit to one bit of \(s_0'\) or \(s_1'\) before 
-  seeing the verifier's choice \(b_i\).
-  He can make a guess~\(\hat b\) at the verifier's choice~\(b\).
-  Then he commits to the next bit of \(s_{\hat b}'\).
-  If the challenge~\(b_i \neq \hat b\), he will commit to the same bit for the 
-  next round.
-  If indeed \(\hat b = b\), the verifier will accept.
-  The success probability is \(\frac{1}{2}\) over all bits.
-
-  If the adversary \(\Prompt\)s:
-  The prover computed \(s_0\) and \(s_1\) using \(\rho\) and \(\alpha\).
-  However, the verifier will use \(R'\) and \(A'\) in the verification step.
-  This will succeed if \(s_b = s_b'\), the probability of which is 
-  \(\frac{1}{q}\).
-  This means that the probability of success for prompting a bit is 
-  \(\frac{1}{2}\), or \(\frac{1}{2^{|q|}}\) over all bits.
-
-  If the adversary didn't choose \(R'\) he consequently doesn't know \(\rho\) 
-  and cannot compute the correct \(s_0\) and \(s_1\).
-  Thus, committing yields \(\frac{1}{2}\) probability per bit.
-  The same applies for prompting.
-
-  Obviously, the better strategy for the adversary is to choose \(R' = 
-  g^{\rho'}\).
-  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
-  \(\Prompt\) (\ac{DBDH}).
-  We thus have that
-  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{2^n}\) for \(n\) rounds,
-  which concludes the proof.
-\end{proof}
+The problem is that asymptotically, \(l\) and \(l+1\) are rather close.
+So the colluding parties can exchange \(l+1\) bits instead of just \(l\).
+This way they can create a buffer of responses.
+However, this means that they can stretch the distance bound; at some point, 
+\(l+\epsilon\) will be too large and make \(\alpha\) easy enough to guess.
+So the incentive changes from the legitimate party not wanting to cheat, into 
+the legitimate party not wanting to cheat \enquote{too much}.
+However, we have not formally treated this part more than concluding that we 
+cannot prove \ac{DBTF} resistance in terms of \cref{TaintedTF,TFresistance}.

### 2020-07-03 paper/DB-Schnorr-UWB.tex
Changes some equations to display, fixes bugs in eqns

@@
 
-    \vdots
+    \(\vdots\)
     &
@@
 
-\begin{theorem}[\acs*{DBMF} resistance]
+\begin{restatable}[\acs*{DBMF} resistance]{theorem}{UWBMFresistance}
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
@@
   \cref{DB-Schnorr-UWB}.
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
-  cannot learn anything by observation.
-  This leaves the adversary with two options:
-  \begin{enumerate*}
-  \item guess which challenge the verifier will use and request the correct 
-    response from the prover, receiving the challenge first would taint the 
-    session (\cref{TaintedMF});
-  \item guess the response.
-  \end{enumerate*}
-  The first option yields success with probability \(\frac{1}{m}\), since the 
-  choice is uniformly distributed.
-  The second option yields success with probability \(\frac{1}{q}\): since the 
-  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
-  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
-  \(\ZZ_q\).
-
-  Since \(m \leq q\), the best strategy is to guess which challenge the 
-  verifier will use.
-  Thus, the total success probability is \(\frac{1}{m^n}\).
-\end{proof}
+The proof is found in \cref{ProofUWBMFresistance}.
 
@@
 
-\begin{theorem}[\acs*{DBTF} resistance]
+\begin{restatable}[\acs*{DBTF} resistance]{theorem}{UWBTFresistance}
   Let \(\adv\) be a \((t, \qv)\)-strSimTF adversary (aided by the prover), 
@@
   \(\Adv_{\DB}^{\text{TF}} = p_{\adv} - p_{\S} < \left(\frac{2}{m}\right)^n\).
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
-  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
-  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
-  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
-  Say that \(\adv\) has successfully authenticated with the prover's help and 
-  \(\S\) is given \(\adv\)'s state.
-
-  Now \(\S\) will use \(\adv\) in a simulation.
-  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
-  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
-  choose another challenge different from before.
-  Since \(\adv\) cannot perform a relay to the prover without tainting the 
-  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
-  provided by the prover must be independent from the chosen challenge.
-  Now \(\adv\) will again provide a correct response with 
-  probability~\(p_{\adv}\).
-
-  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
-  \(m p_{\adv}\) responses.
-  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
-  correct responses and, thus, \(p_{\S} = 1\) for any successive 
-  authentication.
-  This would also make \(p_{\adv} = 1\).
-  This contradicts that the secret is not leaked.
-  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
-  secret leaks.
-\end{proof}
+The proof is found in \cref{ProofUWBTFresistance}.
 
@@
 
-\begin{theorem}[\acs*{DBDH}/\acs*{DBDF} resistance]
+\begin{restatable}[\acs*{DBDH}/\acs*{DBDF} 
+  resistance]{theorem}{UWBDFresistance}
   Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
   \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\).
-\end{theorem}
+\end{restatable}
 
-\begin{proof}
-  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
-  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
-  \(R' = R\) to not interfere.
-
-  The verifier will choose \(c_1, \dotsc, c_k\).
-  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
-  is his \enquote{private key}\footnote{%
-    In Schnorr's original protocol this was called the private key.
-    But in our general use, it's the discrete logarithm for which the prover 
-    wants to prove knowledge.
-  }.
-  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
-  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
-  If the adversary didn't choose \(R'\), he can only guess the values for 
-  \(s_i'\).
-
-  Now the adversary has two options:
-  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.
-
-  If the adversary \(\Commit\)s:
-  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
-  = \rho' - c_i \alpha'\) for all \(i\).
-  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
-  choice \(j\).
-  The probability of committing to the right one is \(\frac{1}{m}\).
-  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
-  the probability of success is \(\frac{1}{q}\) --- since he must guess 
-  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
-  might just as well guess the final outcome (\(\frac{1}{q}\)).
-  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
-  The success of committing is \(\frac{1}{m}\).
-
-  If the adversary \(\Prompt\)s:
-  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
-  \enquote{public key}\footnote{%
-    In Schnorr's original protocol this was a public key.
-    In our more general use, it is the value for which the adversary wants to 
-    prove knowledge of a discrete logarithm.
-  } of the adversary.
-  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
-  - c_i \alpha + c_i \alpha'}\).
-  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
-  accept if \(\alpha = \alpha'\), the probability for which is 
-  \(\frac{1}{q^2}\).
-  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
-  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
-  \frac{1}{q}\).
-
-  Obviously, the better strategy for the adversary is to choose \(R' = 
-  g^{\rho'}\).
-  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
-  \(\Prompt\) (\ac{DBDH}).
-  We thus have that
-  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
-  which concludes the proof.
-\end{proof}
+The proof is found in \cref{ProofUWBDFresistance}.

### 2020-07-03 paper/proofs.tex

\section{Proofs for \cref{DB-Schnorr}}

\UWBMFresistance*

\begin{proof}\label{ProofUWBMFresistance}
  It follows from the \ac{ZK} property (\cref{UWB-ZKPK}) that the adversary 
  cannot learn anything by observation.
  This leaves the adversary with two options:
  \begin{enumerate*}
  \item guess which challenge the verifier will use and request the correct 
    response from the prover, receiving the challenge first would taint the 
    session (\cref{TaintedMF});
  \item guess the response.
  \end{enumerate*}
  The first option yields success with probability \(\frac{1}{m}\), since the 
  choice is uniformly distributed.
  The second option yields success with probability \(\frac{1}{q}\): since the 
  response~\(s_i\) depends on \(\rho\), which is uniformly distributed in 
  \(\ZZ_q\), it follows that \(s_i\) is also uniformly distributed in 
  \(\ZZ_q\).

  Since \(m \leq q\), the best strategy is to guess which challenge the 
  verifier will use.
  Thus, the total success probability is \(\frac{1}{m^n}\).
\end{proof}

\UWBTFresistance*

\begin{proof}\label{ProofUWBTFresistance}
  Assume that the adversary~\(\adv\) can authenticate with the prover's help 
  with probability~\(p_{\adv}\) non-negligibly better than guessing (\(p_{\adv} 
  = \frac{1}{m}+\epsilon, \epsilon\) non-negligible), without tainting the 
  session (\cref{TaintedTF}) and leaking the secret~\(\alpha\).
  Say that \(\adv\) has successfully authenticated with the prover's help and 
  \(\S\) is given \(\adv\)'s state.

  Now \(\S\) will use \(\adv\) in a simulation.
  \(\S\) will rewind \(\adv\) to just before \(\adv\) received the challenge.
  Since the challenge is chosen uniformly randomly by the verifier, \(\S\) will 
  choose another challenge different from before.
  Since \(\adv\) cannot perform a relay to the prover without tainting the 
  session (\cref{TaintedTF}) and each challenge is uniformly random, the help 
  provided by the prover must be independent from the chosen challenge.
  Now \(\adv\) will again provide a correct response with 
  probability~\(p_{\adv}\).

  However, since there are \(m\) challenges, \(\S\) can probabilistically extract 
  \(m p_{\adv}\) responses.
  Once \(m p_{\adv} \geq 2\), \(\S\) can compute the secret~\(\alpha\) from two 
  correct responses and, thus, \(p_{\S} = 1\) for any successive 
  authentication.
  This would also make \(p_{\adv} = 1\).
  This contradicts that the secret is not leaked.
  Hence, \(\epsilon < \frac{1}{m}\) or the adversary taints the session or the 
  secret leaks.
\end{proof}

\UWBDFresistance*

\begin{proof}\label{ProofUWBDFresistance}
  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
  \(R' = R\) to not interfere.

  The verifier will choose \(c_1, \dotsc, c_k\).
  The honest prover will compute \(s_i = \rho - c_i \alpha\), where \(\alpha\) 
  is his \enquote{private key}\footnote{%
    In Schnorr's original protocol this was called the private key.
    But in our general use, it's the discrete logarithm for which the prover 
    wants to prove knowledge.
  }.
  If the adversary chose \(R' = g^{\rho'}\), he can compute \(s_i' = \rho' - 
  c_i \alpha'\), where \(\alpha'\) is the adversary's \enquote{private key}.
  If the adversary didn't choose \(R'\), he can only guess the values for 
  \(s_i'\).

  Now the adversary has two options:
  to \(\Commit\) to a response or to \(\Prompt\) the honest prover to respond.

  If the adversary \(\Commit\)s:
  If the adversary chose \(R'\), then he knows \(\rho'\) and can compute \(s_i 
  = \rho' - c_i \alpha'\) for all \(i\).
  Now, the adversary must commit to one \(s_i\) before seeing the verifier's 
  choice \(j\).
  The probability of committing to the right one is \(\frac{1}{m}\).
  If the adversary didn't choose \(R'\) and consequently doesn't know \(\rho\), 
  the probability of success is \(\frac{1}{q}\) --- since he must guess 
  \(\rho\) (\(\frac{1}{q}\)) and then guess the challenge (\(\frac{1}{m}\)) he 
  might just as well guess the final outcome (\(\frac{1}{q}\)).
  By design, \(m \leq q\), so \(\frac{1}{m} \geq \frac{1}{q}\).
  The success of committing is \(\frac{1}{m}\).

  If the adversary \(\Prompt\)s:
  The verifier will check that \(R' = g^{s_i} {A'}^{c_i}\), where \(A'\) is the 
  \enquote{public key}\footnote{%
    In Schnorr's original protocol this was a public key.
    In our more general use, it is the value for which the adversary wants to 
    prove knowledge of a discrete logarithm.
  } of the adversary.
  Now, \(g^{s_i} {A'}^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = 
  g^{\rho - c_i \alpha + c_i \alpha'}\).
  If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 
  accept if \(\alpha = \alpha'\), the probability for which is 
  \(\frac{1}{q^2}\).
  If \(R' = g^{\rho'}\), chosen by the adversary, then the verifier accepts 
  with probability \(\Pr[\rho' - c_i \alpha' = \rho - c_i' \alpha] = 
  \frac{1}{q}\).

  Obviously, the better strategy for the adversary is to choose \(R' = 
  g^{\rho'}\).
  It's also a better strategy to \(\Commit\) (\ac{DBDF}) rather than 
  \(\Prompt\) (\ac{DBDH}).
  We thus have that
  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \frac{1}{m^n}\),
  which concludes the proof.
\end{proof}

### 2020-07-03 paper/formal-short.tex
Moves formal verification to appendix

--- 2020-03-14 paper/formal-verification.tex
@@
 message needed for collusion.
-
-The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%,
- contains a specification of the distance-bounding protocol described previously, a definition 
- of the soundness and correctness properties that ensure the protocol actually produces the
- expected result, and a definition of the security properties we want to ensure.
-
-Tamarin's auto-prover validated the soundness and correctness
-properties and proved all the security
-properties used in~\cite{TamarinDB} and \textcite{TamarinDBTF}: resistance to distance fraud, distance hi-jacking, mafia fraud, and terrorist fraud, all in less than 10 seconds.
-
-Note that proofs of formal verification are always limited by how well the specification captures reality.
-In particular, Tamarin only provides symbolic modeling, and as such does not work with actual values.
-The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
-Similarly, the details of the bit-by-bit version are lost in the abstraction, and its specification is identical to the simultaneous version; that's why Tamarin does not detect the terrorist fraud attack we mention about the bit-by-bit version.
-Notable differences can be found in \cref{formal-verif-appendix}.
+We have successfully verified all the protocols presented in this paper with 
+Tamarin.
+More details can be found in \cref{formal-verification-full}.

### 2020-07-03 paper/formal-verification.tex
Moves formal verification to appendix

@@
-\section{Formal Verification}\label{formal-verification}
+\section{Formal Verification}\label{formal-verification-full}
 
@@
 
-The Tamarin code we wrote\footnote{provided in \url{https://doi.org/10.5281/zenodo.3709442}}%,
+The Tamarin code we wrote\footnote{Provided in \url{https://doi.org/10.5281/zenodo.3709442}}%,
  contains a specification of the distance-bounding protocol described previously, a definition 
@@
 properties and proved all the security
-properties used in~\cite{TamarinDB} and \textcite{TamarinDBTF}: resistance to distance fraud, distance hi-jacking, mafia fraud, and terrorist fraud, all in less than 10 seconds.
+properties used in \cite{TamarinDB} and \cite{TamarinDBTF}: resistance to 
+distance fraud, distance hijacking, mafia fraud, and terrorist fraud, all in 
+less than 10 seconds.
 
 Note that proofs of formal verification are always limited by how well the specification captures reality.
-In particular, Tamarin only provides symbolic modeling, and as such does not work with actual values.
-The tool, for instance, has no notion of arithmetic, and the equations used in \cref{SchnorrFigure} cannot be modeled directly.
-Similarly, the details of the bit-by-bit version are lost in the abstraction, and its specification is identical to the simultaneous version; that's why Tamarin does not detect the terrorist fraud attack we mention about the bit-by-bit version.
+In particular, Tamarin only provides symbolic modeling, and as such does not 
+work with actual values. The tool, for instance, has no notion of arithmetic, 
+and the equations used in \cref{DB-Schnorr-UWB-figure} cannot be modeled 
+directly. Similarly, the details of the bit-by-bit version are lost in the 
+abstraction, and its specification is identical to the simultaneous version; 
+that's why Tamarin does not detect the terrorist fraud attack we mention about 
+the bit-by-bit version.
 Notable differences between the specification and reality include:
@@
 	\item We used the chosen challenge $c_b$ directly instead of the flag $b$ to represent the choice of the verifier between the two challenge values; this is equivalent because Tamarin does not work with actual values so the size of those values does not matter, and this helps us for the challenge verification later.
-	\item Conversely to the first point, checking the equality $R = g^{s_b}.A^{c_b}$ is represented as decoding and verifying the signature of the response message $s_b$, which should return $c_b$, and then verifying the trivial equality that $c_b = c_b$, thanks to the previous point.
+  \item Conversely to the first point, checking the equality $R = g^{s_b} 
+    A^{c_b}$ is represented as decoding and verifying the signature of the 
+    response message $s_b$, which should return $c_b$, and then verifying the 
+    trivial equality that $c_b = c_b$, thanks to the previous point.
 	\item Additionally, to model the challenge as unpredictable, we added a fresh nonce $b_{nonce}$ to the challenge specification.

### 2020-07-03 paper/conclusions.tex
Adds scenario from conclusions to intro

--- 2020-03-13 paper/conclusions.tex
@@
 (without revealing her actual age), has a cinema subscription which is not 
-\enquote{double spent} by someone else at the same time and, at the same time, 
-Bob can be sure that Alice is not just relaying messages from her older sister 
-Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.
+\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
+and, at the same time, Bob can be sure that Alice is not just relaying messages 
+from her older sister Carol or \ac{DBMF} relaying the subscription from some 
+unsuspecting stranger also waiting in the queue to enter.

### 2020-07-03 paper/intro.tex
Moves formal verification completely to the appendix
Adds scenario from conclusions to intro

@@
 anonymity.
+With our contribution, Alice can
+now prove more complex statements to Bob; \eg that she is older than 18 
+(without revealing her actual age), has a cinema subscription which is not 
+\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
+and, at the same time, Bob can be sure that Alice is not just relaying messages 
+from her older sister Carol or \ac{DBMF} relaying the subscription from some 
+unsuspecting stranger also waiting in the queue to enter.
 

### 2020-07-03 paper/intro.tex
Emphasizes that we don't achieve _full_ TF

@@
 bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
-We achieve all properties except \ac{DBTF} resistance.
+We achieve all properties except (full) \ac{DBTF} resistance.
 We see this contribution as merely for the sake of completion, as the previous 
-contributions are slightly more efficient.
+contributions are more efficient.
 

### 2020-07-03 paper/DB-Schnorr-UWB.tex
Briefly explains Singh et al.'s paper

--- 2020-03-13 paper/DB-Schnorr-UWB.tex
@@
 bits in parallel as we like.
-This is a reasonable assumption thanks to the results of \textcite{UWBPR}.
+This is a reasonable assumption thanks to the results of \textcite{UWBPR}, we 
+briefly explain why.
+\Ic{DBMF} adversary can listen in on the communications.
+Each symbol of the communication is encoded using signal pulses.
+However, such an encoded symbol can usually be inferred \emph{before} all 
+pulses are received.
+Before the contribution of \citeauthor{UWBPR}, the only countermeasure to this 
+attack was to make the symbols short, \ie to send one bit at a time.
+\Textcite{UWBPR} use a symmetric key, shared between prover and verifier, to 
+scramble the pulses and hence the symbols.
+This way, the \ac{DBMF} adversary cannot infer an incoming symbol in advance, 
+and thus cannot start relaying the symbol in advance either.
+The prover and verifier, on the other hand, can do this since they have the 
+symmetric key.
+Consequently they must have mutual trust, so \ac{DBDF} cannot happen by 
+assumption.
 
@@
   If the adversary \(\Prompt\)s:
-  The verifier will check that \(R' = g^{s_i} A'^{c_i}\), where \(A'\) is the 
+  The verifier will check that \(R' = g^{s_i} {A'}^{c_i}\), where \(A'\) is the 
   \enquote{public key}\footnote{%
@@
   } of the adversary.
-  Now, \(g^{s_i} A'^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = g^{\rho 
-  - c_i \alpha + c_i \alpha'}\).
+  Now, \(g^{s_i} {A'}^{c_i} = g^{\rho - c_i \alpha} (g^{\alpha'})^{c_i} = 
+  g^{\rho - c_i \alpha + c_i \alpha'}\).
   If \(R' = R = g^\rho\), chosen by the prover, then the verifier will only 

### 2020-07-03 paper/conclusions.tex
Edits conclusions

--- 2020-03-13 paper/conclusions.tex
@@
 
-In this paper, we have adapted the Schnorr protocol as a
-distance-bounding protocol.  It allows to construct distance-bounding
-general attribute-based authentication, more general attributes than
-provided by previous \ac{DB} ones.  With our contribution, Alice can
-now prove more complex statements to Bob; \eg that she is older than 18 
-(without revealing her actual age), has a cinema subscription which is not 
-\enquote{double spent} by someone else at the same time and, at the same time, 
-Bob can be sure that Alice is not just relaying messages from her older sister 
-Carol or \ac{DBMF} relaying the subscription from some unsuspecting stranger.
+In this paper, we have adapted the Schnorr protocol as \iac{DB} protocol.
+It allows us to construct \ac{DB}, general attribute-based authentication; more 
+general attributes than provided by previous \ac{DB} ones.
+With our contribution, Alice can now prove more complex statements to Bob; \eg 
+that she is older than 18 (without revealing her actual age), has a cinema 
+subscription which is not \enquote{double spent} by someone else at the same 
+time~\cite[\eg][]{AnonPass} and, at the same time, Bob can be sure that Alice 
+is not just relaying messages from her older sister Carol or \ac{DBMF} relaying 
+the subscription from some unsuspecting stranger also waiting in the queue to 
+enter.

### 2020-07-05 paper/intro.tex
Makes related work a part of the intro
makes scenario location-relevant, fixes language in intro

--- 2020-07-02 paper/intro.tex
@@
 This means that the prover and the verifier must share a secret.
-This might work for key-less entry protocols for cars, where the car and keyfob 
+This works for scenarios like key-less entry protocols for cars, where the car and keyfob 
 can share a key.
-But it does not work for ubiquitous \ac{DB} authentication.
+It does, however, not work for ubiquitous \ac{DB} authentication where
+the prover and verifier may not have met before.
 
@@
 anonymity.
+With our contribution, Alice can
+now prove more complex statements to Bob; \eg that she is close to a specific car, has a valid driver's license, is older than 18 
+(without revealing her actual age), has the relevant car-sharing subscription which is not 
+\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
+and  Bob can be sure that Alice is not just relaying messages 
+from her older sister Carol or \ac{DBMF} relaying the subscription from some 
+unsuspecting stranger also waiting in the parking lot.
 

### 2020-07-05 paper/related-work.tex
Adds missing related-work label
Makes related work a part of the intro
edits related work, reference still missing, questions in comments

--- 2020-03-13 paper/related-work.tex
@@
 Unfortunately, their approach has been shown to be vulnerable to 
-\ac{DBDH}~\cite[\eg][]{TamarinDB}.
+\ac{DBDH}~\cite{DistanceBounding,TamarinDB}.
+Furthermore, it is also vulnerable to \ac{DBTF}.
 
-The Bussard-Bagga protocol also uses Schnorr, but slightly
-differently. It generates a sesson key, encrypts the private key
-with this session key. Then commits to each bit of the session key
+The Bussard-Bagga~\cite{BussardBagga} protocol aims to overcome these
+vulnerabilities and also uses Schnorr, but slightly
+differently. It generates a sesson key and encrypts the private key
+with this session key. Then it commits to each bit of the session key
 and each bit of the ciphertext.
-During the fast phase the verifier requests some bits from the session key and some from the ciphertext.
+During the fast phase, the verifier requests some bits from the session key and some from the ciphertext.
 Terrorist fraud is based on that knowing both session key and ciphertext one can compute the private key.
 The prover then opens the commits, the verifier verifies them.
-The prover and verifier run a PK that ties the commits to the private key.
+The prover and verifier run a \acp{PK} that ties the commits to the private key.
 However, a malicious prover can reduce all the N challenges in the fast phase
@@
 \)), while in our context, we need \iac{PPK} protocol for discrete logarithms 
-(\ie \(\PPK[\alpha][a = g^\alpha]\)).
-Also, ProProx's proofs of knowledge are only for \emph{bit commitments} of the 
-above form.
+(\ie \(\PPK[\alpha][a = g^\alpha]\)). %to take advantage of abc
+                                %systems that use Schnorr?
+Moreover, ProProx's proofs of knowledge are only for \emph{bit commitments} of the 
+above form. %what does this imply?

### 2020-07-05 paper/conclusions.tex
edits conclusion, removes example, repeats contributions (rephrased)

--- 2020-03-13 paper/conclusions.tex
@@
 
-In this paper, we have adapted the Schnorr protocol as a
-distance-bounding protocol.  It allows to construct distance-bounding
-general attribute-based authentication, more general attributes than
-provided by previous \ac{DB} ones.  With our contribution, Alice can
-now prove more complex statements to Bob; \eg that she is older than 18 
-(without revealing her actual age), has a cinema subscription which is not 
-\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
-and, at the same time, Bob can be sure that Alice is not just relaying messages 
-from her older sister Carol or \ac{DBMF} relaying the subscription from some 
-unsuspecting stranger.
+In this paper, we have adapted the Schnorr protocol to work as a
+distance-bounding protocol.  It allows us to construct distance-bounding
+general attribute-based authentication, with more general attributes than
+provided by previous \ac{DB} protocols.  We made and formally verified two versions of the
+protocol, one that is more efficient and resistant to the attacks
+leveled at \ac{DB} protocols but that assumes that more than one
+bit at a time can be sent in the fast phase (as demonstrated by
+\textcite{UWBPR}). We also developed a PKI scheme to generalize~\cite{UWBPR} to work for scenarios such as ours where the prover and verifier do
+not trust or even know each other. The second version is a classic bit-by-bit
+protocol that is not fully \ac{DBTF} resistant but otherwise fulfills
+all requirements.

### 2020-07-06 paper/related-work.tex
fixes acronym
Fixes ref to Bussard-Bagga

@@
 
-The Bussard-Bagga~\cite{BussardBagga} protocol aims to overcome these
+The Bussard-Bagga~\cite{Bussard-Bagga} protocol aims to overcome these
 vulnerabilities and also uses Schnorr, but slightly
@@
 The prover then opens the commits, the verifier verifies them.
-The prover and verifier run a \acp{PK} that ties the commits to the private key.
+The prover and verifier run a \ac{PK} that ties the commits to the private key.
 However, a malicious prover can reduce all the N challenges in the fast phase

### 2020-07-06 paper/intro.tex

@@
 
-Our work present contributions in the area of \ac{DB} public-key protocols, 
+Our work presents contributions in the area of \ac{DB} public-key protocols, 
 particularly \ac{DB} \acp{ZKPK}.
@@
 (without revealing her actual age), has the relevant car-sharing subscription which is not 
-\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
+\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass}, 
 and  Bob can be sure that Alice is not just relaying messages 
@@
 This version is based on the assumption that we can transmit all bits at once, 
-not bit-by-bit as normally required for \ac{DB}.
+not bit-by-bit as normally done for \ac{DB}.
 This assumption is motivated by the results of \textcite{UWBPR}.
@@
 The third contribution (bit-by-bit version) also enables us to do the same, 
-just without (full) \ac{DBTF} resistance.
+just without (full) \ac{DBTF} resistance. %How does the tamarin
+                                %contrib come in?
 
@@
 The paper is organized as follows.
-\Cref{related-work} discusses some related work.
+%\Cref{related-work} discusses some related work.
 \Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
@@
 \Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
-\Cref{formal-verification} describes our effort to formally verify the protocol 
-using Tamarin.
-Finally, we conclude with discussion and conclusions in 
-\cref{Discussion,Conclusion}.
+%\Cref{formal-verification} describes our effort to formally verify the protocol 
+%using Tamarin.
+%Finally, we conclude with discussion and conclusions
+%in \cref{Discussion,Conclusion}.
+\cref{Conclusion} concludes the paper.

### 2020-07-06 paper/conclusions.tex

@@
 
-In this paper, we have adapted the Schnorr protocol to work as a
-distance-bounding protocol.  It allows us to construct distance-bounding
-general attribute-based authentication, with more general attributes than
-provided by previous \ac{DB} protocols.  We made and formally verified two versions of the
-protocol, one that is more efficient and resistant to the attacks
-leveled at \ac{DB} protocols but that assumes that more than one
-bit at a time can be sent in the fast phase (as demonstrated by
-\textcite{UWBPR}). We also developed a PKI scheme to generalize~\cite{UWBPR} to work for scenarios such as ours where the prover and verifier do
-not trust or even know each other. The second version is a classic bit-by-bit
-protocol that is not fully \ac{DBTF} resistant but otherwise fulfills
-all requirements.
+In this paper, we have adapted the Schnorr protocol to work as \iac{DB} 
+protocol.
+It allows us to construct \ac{DB}, general attribute-based authentication; with 
+more general attributes than provided by previous \ac{DB} protocols.
+We made and formally verified two versions of the protocol, one that is more 
+efficient and resistant to the attacks leveled at \ac{DB} protocols, but that 
+assumes that more than one bit at a time can be sent in the fast phase (as 
+demonstrated by \textcite{UWBPR}).
+We also developed a \ac{PKI} scheme to generalize~\cite{UWBPR} to work for 
+scenarios such as ours, where the prover and verifier do not trust or even know 
+each other.
+The second version is a classic bit-by-bit protocol that is not fully \ac{DBTF} 
+resistant but otherwise fulfills all requirements.

### 2021-06-14 paper/distance-bounding.tex
Adds DB-Schnorr ref

@@
 For this paper, we assume the existence of such a protocol.
-There exists \ac{PPK} schemes, \eg~\cite{ProProx}, just no published scheme for 
-discrete logarithms yet\footnote{%
-  The authors have such a protocol under submission in another venue.
-}.
+There exists one such protocol in the literature, namely one by 
+\textcite{DB-Schnorr}, we refer to that paper for a detailed discussion.

### 2021-06-15 paper/distance-bounding.tex
Fixes dead crefs, clarifications for trusted/untrusted

@@
 their actions, thus we also require strong privacy.
-In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
-\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
+In fact, as the construction in 
+\cref{untrusted-witnesses-protocol,trusted-witnesses-protocol} shows, we 
+require \iac{DB} \ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
 For this paper, we assume the existence of such a protocol.

### 2021-06-15 paper/intro.tex
Fixes dead crefs, clarifications for trusted/untrusted

--- 2020-07-03 paper/intro.tex
@@
 
-Although there are numerous contributions in the field of \ac{DB} 
-authentication protocols, the majority of them are shared-key protocols.
-This means that the prover and the verifier must share a secret.
-This might work for key-less entry protocols for cars, where the car and keyfob 
-can share a key.
-But it does not work for ubiquitous \ac{DB} authentication.
+%\emph{Context.}
 
-Our work present contributions in the area of \ac{DB} public-key protocols, 
-particularly \ac{DB} \acp{ZKPK}.
-This allows anyone to act as a verifier, unlike in the shared-key scenario 
-where the verifier must be trusted.
-The \ac{ZK} property also enables a variety of privacy properties, such as 
-anonymity.
-With our contribution, Alice can
-now prove more complex statements to Bob; \eg that she is older than 18 
-(without revealing her actual age), has a cinema subscription which is not 
-\enquote{double spent} by someone else at the same time~\cite[\eg][]{AnonPass} 
-and, at the same time, Bob can be sure that Alice is not just relaying messages 
-from her older sister Carol or \ac{DBMF} relaying the subscription from some 
-unsuspecting stranger also waiting in the queue to enter.
+While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper.
+We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).
 
-\paragraph*{Contributions}
+Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
+Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
+More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
+Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.
 
-We make three contributions.
-First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
-\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the \ac{DFKOmodel}.
-This version is based on the assumption that we can transmit all bits at once, 
-not bit-by-bit as normally required for \ac{DB}.
-This assumption is motivated by the results of \textcite{UWBPR}.
+Consider the following scenario.
+Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
+Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime.
+To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.
 
-Second, for the assumption about sending all bits at once to hold, 
-\textcite{UWBPR} requires that two devices shared a symmetric key~\(k\).
-Our second contribution is \iac{PKI} and \ac{AKE} scheme for any device in 
-the \ac{PKI} to convince a verifier that this is the case.
-This replaces everyone having the same static key~\(k\) with everyone having a 
-unique key which is signed by \iac{CA} of the \ac{PKI}, which allows for 
-revocation.
-The solution relies on our first contribution.
+Existing methods for crowd-counting vary significantly in terms of approaches.
+% (we will review them in detail in \cref{current-crowd-counting}).
+Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.
+In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.
 
-Our last contribution is another version of the protocol, one which uses 
-bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
-We achieve all properties except (full) \ac{DBTF} resistance.
-We see this contribution as merely for the sake of completion, as the previous 
-contributions are more efficient.
+Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting.
+Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
+%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
+In this paper, our main objective is to provide a scheme preventing both Alice 
+and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest.
+While one cannot
+prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.
 
-The first (and second) contribution enables us to do distance-bounding 
-privacy-preserving attribute-based credentials based on discrete logarithms, 
-\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
-We can do this by simply replacing their use of the Schnorr 
-protocol~\cite{Schnorr} for \acp{ZKPK} with our protocol in this paper.
-To our knowledge, no other distance-bounding protocol achieves this.
-The third contribution (bit-by-bit version) also enables us to do the same, 
-just without (full) \ac{DBTF} resistance.
+%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
+%\seb{in the sentence above I am not sure that the word unlinkable will be 
+%  necessary clear}
 
-\paragraph*{Outline}
+%\paragraph*{Contributions}
+
+%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
+%way to securely estimate crowd counts in protests\footnote{%
+%  If location is ignored, it can be reduced to privacy-preserving yet 
+%  verifiable petitions.
+%}.
+%
+%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
+%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
+%including \ac{DBDH} (which was an attack against the original protocol of 
+%Brands and Chaum) and \ac{DBTF}.
+%More importantly, it is public-key, handles malicious impersonating verifiers.
+%Since it is based on the Schnorr protocol, it provides a distance-bounded 
+%\ac{PK} for discrete logarithms.
+%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
+%distance-bounding version and thus make general privacy-preserving, 
+%attribute-based credential systems distance bounding.
+
+% The paper is organized as follows.
+% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}).
+Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{current-crowd-counting}).
+% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).
 
 The paper is organized as follows.
-\Cref{related-work} discusses some related work.
-\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
-\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
-send all bits at the same time.
-\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
-version of the protocol in practice.
-\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
-\Cref{formal-verification} describes our effort to formally verify the protocol 
-using Tamarin.
-Finally, we conclude with discussion and conclusions in 
-\cref{Discussion,Conclusion}.
+In \Cref{system-model}, we describe our system model and summarize the desired 
+properties for crowd counting, followed by a discussion of current 
+crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
+we formalize the notion of protest and the desired verifiability and privacy 
+properties, and in \cref{building-blocks}, we give the relevant background on 
+the building blocks of our solution.
+%
+%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
+%different from that originally proposed by \textcite{DistanceBounding}.
+%We provide a proof of its security and formally verify it using 
+%Tamarin~\cite{TamarinDB}.
+%
+We present \CROCUS, a privacy-preserving crowd counting 
+%estimation 
+protocol in in \cref{trusted-witnesses-protocol,untrusted-witnesses-protocol}, 
+analyze its security in \cref{SecurityAnalysis}, and estimate its performance 
+in \cref{PerformanceAnalysis}.
+We compare it to related work in \cref{related-work}.
+Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
+our conclusions in \cref{Conclusion}.

### 2021-06-15 paper/protocol-trusted.tex
Removes the ref to Anon-Pass in protocol description
Fixes dead crefs, clarifications for trusted/untrusted

@@
 At the core of our construction, witnesses generate participation proofs for 
-the protesters (in \cref{ProtocolDuring}), these are essentially augmented 
-\acp{LP}\footnote{%
+the protesters (in \cref{TrustedProtocolDuring}), these are essentially 
+augmented \acp{LP}\footnote{%
   \Iac{LP} certifies that its owner was at a given location at a given time.
@@
 Then whoever wants to verify the participation count, will count and verify 
-those participation proofs (in \cref{ProtocolVerification}).
+those participation proofs (in \cref{TrustedProtocolVerification}).
 
@@
 
-We use the setup and registration phases of 
-Anon-Pass~\cite{AnonPass}\footnote{%
-  This version is slightly adapted (improves efficiency) from the original 
-  version by \textcite{HowToWinTheCloneWars}.
-} for getting the certificate, adapting only the notation to fit ours. 
-%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
-
 \paragraph*{Setup: \((\spk, \ssk)\gets \CROCUSsetup\)}
@@
 \subsection{Participation}%
-\label{ProtocolDuring}
+\label{TrustedProtocolDuring}
 
@@
 \subsection{Count and verification}%
-\label{ProtocolVerification}
+\label{TrustedProtocolVerification}
 

### 2021-06-15 paper/system-model.tex
Fixes dead crefs, clarifications for trusted/untrusted

@@
 their smartphones (or similar devices) running the protocol described
-in \cref{Protocol} and uploading their testimony (\ie, proof shares)
+in \cref{untrusted-witnesses-protocol,trusted-witnesses-protocol} and uploading 
+their testimony (\ie, proof shares)
 to a ledger (such as a blockchain) after the protest.  During the

### 2021-06-15 paper/intro.tex
Adds outline as titled paragraph in intro

@@
 
+\paragraph{Outline}
+
 The paper is organized as follows.
@@
 %estimation 
-protocol in in \cref{trusted-witnesses-protocol,untrusted-witnesses-protocol}, 
-analyze its security in \cref{SecurityAnalysis}, and estimate its performance 
-in \cref{PerformanceAnalysis}.
+protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
 We compare it to related work in \cref{related-work}.

### 2021-06-15 paper/verifiability-analysis.tex
Clarifies confusion about trust in security analysis

@@
 In essence, the witness performs distance bounding to ensure Alice is close to 
-them, this is then propagated to the verifier through the signature and founded 
-on trust (remember that the witness is trusted by the verifier).
-Alice has three options:
+them, this is then propagated to the verifier through the signature.
+This leaves Alice with three options to cheat:
 \begin{enumerate*}

### 2021-06-16 paper/current-crowd-counting.tex

@@
-\section{Current crowd counting methods}%
+\section{Desired properties and current crowd-counting methods}%
 \label{current-crowd-counting}
+
+\subsection{Desired properties}%
+\label{desired-properties}
+
+We note that, in general terms, protests are petitions with a given time and 
+location.
+Protests, petitions and elections share that in all three many individuals 
+express their opinion.
+These opinions can be sensitive (\eg be a cause for discrimination or 
+persecution).
+For that reason we have strong requirements for verification and privacy for 
+elections, it follows that we should have similar properties for protests
+and petitions.
+
+We draw inspiration from properties for voting systems as formalized
+in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
+\daniel{Find a new ref for voting verifiability properties, Douglas commented 
+  that the last one is not the origin.}
+\begin{description}
+  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
+  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
+    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
+      old.}
+  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
+    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
+      Fiat-Shamir (technically). Non-technically, much older.}
+\end{description}
+In our context, votes are translated into \emph{participation proofs}.
+Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
+The eligibility requirement is slightly different as for protests it must also
+include temporal %\footnote{%
+%   Elections also have some temporal aspects, such that one cannot vote at any 
+%   time and a vote in one election should not be reusable in the next election.
+%   However, the temporal relation for a protest is not as strictly defined as for 
+%   elections as a protest can start at any time and last for an arbitrary period 
+%   of time.%
+% }
+and spatial eligibility (\ie each participation proof satisfies some temporal 
+and spatial relation to the protest).
+In essence, the proof must bind the person to the time and location of the protest.
+(This is the difference to a petition.)
+
+In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
+privacy properties for voting protocols are given as:
+\begin{description}
+  \item[Vote privacy:] the voting does not reveal any individual vote.
+  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
+  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
+\end{description}
+
+%Coercion resistance is not possible to achieve for protests.
+Coercion resistance in voting typically relies on physical isolation
+(\eg private voting booths), including for digital systems, 
+and that is by definition not possible for public events.
+For instance, someone could simply physically bring Alice to a protest against her will.
+As for receipt freeness, while
+desirable \emph{in itself}, it implies a conflict with verifiability in our context:
+%appealing at first glance, is not desirable (probably not possible)
+%in our context since this will conflict with verifiability:
+in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
+cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
+(\ie the protester was there), which would make verifiability impossible.
+
+Therefore in our context, the crucial property is  vote privacy.
+More precisely, for the protester we want unlinkability (from the adversary's 
+perspective) between a protester's real identity \(P\) and the participation 
+proof (and thus also the protest itself).
+Phrased differently, given a participation proof, Grace should not be able to 
+distinguish if it was Alice or Bob who participated.
+Furthermore, if Grace has managed to link one proof to Alice due to some 
+auxiliary knowledge, she should not be able to link it to another proof (from a different protest).
+
+\subsection{Current crowd-counting methods}
 

### 2021-06-16 paper/protest-model.tex

@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  We denote by \(\prfs_\prtst = \pshs_\prtst/=_\pid\) the \emph{set of all 
+  We denote by \(\prfs_\prtst = \pshs_\prtst/{=_\pid}\) the \emph{set of all 
   proofs of participation for the protest~\(\prtst\)}.

### 2021-06-16 paper/location-proofs.tex
Undoes PoPETS format

--- 2019-02-13 paper/location-proofs.tex
@@
 \subsection{Location proofs}
-
+\label{location-proofs}
 Some \acp{LBS} only grant access to resources to users located at a particular 
@@
 particular user.
-In most of the existing schemes, the location of a user (device) is determined 
-by the device itself (\eg through GPS) and forwarded to the \ac{LBS} provider.
-One of the main drawbacks of this approach is that a user can cheat by having 
-her device transmit a false location.
-Therefore, it is possible for a user to be inappropriately granted access to a 
-particular resource while being thousands of kilometers away.
-
 One possible way to counter this threat is by having the requesting device 
@@
 
-\CROCUS shares some similarities with PROPS, although their objective is quite 
-different as it aims at verifying a global property of the population (\ie 
-crowd estimation) in contrast to checking the location claim made by a user, 
-which is an individual property.
-
-Another difference is that \CROCUS operates in a more adverse environment.
-\CROCUS must provide \emph{universal verifiability}, this means that all proofs 
-must be available to and verifiable by anyone.
-One problem here is that we have multiple verifiers who might not trust the 
-same witnesses.
-The incentives to cheat are also bigger and consequently the thresholds for 
-collusion are much higher.
-
+%\CROCUS shares some similarities with PROPS, although their objective is quite 
+%different as it aims at verifying a global property of the population (\ie 
+%crowd estimation) in contrast to checking the location claim made by a user, 
+%which is an individual property.
+%
+%Another difference is that \CROCUS operates in a more adverse environment.
+%\CROCUS must provide \emph{universal verifiability}, this means that all proofs 
+%must be available to and verifiable by anyone.
+%One problem here is that we have multiple verifiers who might not trust the 
+%same witnesses.
+%The incentives to cheat are also bigger and consequently the thresholds for 
+%collusion are much higher.
+%
 \sonja{add something on platin.io, details unknown but roughly relying on 

### 2021-06-16 paper/protocol-untrusted.tex
Starts splitting protocol into trusted/untrusted

--- 2019-02-28 paper/protocol.tex
@@
 %\section{\CROCUS:\@ A protocol for crowd counting estimation}%
-\section{The \CROCUS Protocol}%
-\label{Protocol}
+\section{Crowd counting with potentially untrusted witnesses}%
+\label{untrusted-witnesses-protocol}
 
-We now present \CROCUS, a protocol for privately verifiable crowd
-counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
-sybil-proof identity and a cryptographic key%
-%, more specifically, an anonymous 
-%identity credential that provides unlinkability between contexts but 
-%linkability for reuse within the same context
-%\sonja{this is actually achieved by our use of prfs for pid and wid,
-%not inherent in the credential}
-% \footnote{%
-%   Given any \ac{CA} that prevents Sybil 
-%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
-%   be used to make sure that for each identity one-and-only-one
-%   cryptographic key is issued.
-%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
-%   to one's identity.
-% }
-. Since we assume these properties, we
-present only the result of the process of getting anonymous
-credentials from a \ac{CA}, in \cref{ProtocolSetup}.
-
-The core of the \CROCUS protocol consists of generating participation
-proofs (joining a protest, participating in witnessing, submitting
-proof shares to a ledger, all in \cref{ProtocolDuring}) with an overview in \cref{fig:ProtocolOverview}, and then counting and
-verification of that count (in \cref{ProtocolVerification}).
-
-% The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
-% join, participation, submission (all in in \cref{ProtocolDuring}) and
-% verification (in \cref{ProtocolVerification}).
-
-The entities involved in our protocol are participants and (count) verifiers.
-A participant can assume three different roles:
-\begin{enumerate}
-\item The \emph{organizer} has written a manifesto for the protest and 
-  disseminated it to others.
-\item A \emph{protester} is attending the protest and asks witnesses to vouch 
-  for their presence.
-\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
-  third parties.
-\end{enumerate}
-In general, there is one organizer and every participant can act as
-either or both protester and witness.
-
-After the protest, anyone can count the number of participants (of the protest and the
-protocol) and verify anyone else's count given the relevant meta data
-(which protest, location, time, and witness parameters used in the
-count). We refer to anyone counting or verifying a count as the
-verifier; the process is the same.
-
-\subsection{Prerequisite: anonymous credentials}%
-\label{ProtocolSetup}
-
-Before Alice can have her participation in any event counted by
-\CROCUS, she needs to get an anonymous credential and corresponding
-keys. This only needs to be repeated when the credential expires or is
-lost, in analogy to a passport in terms of expected intervals. The
-keys can be reused for an arbitrary number of protests or, given
-careful choices in the PRF used for deriving identifiers, other
-services that work with anonymous credentials.
-
-We use the setup and registration phases of Anon-Pass~\cite{AnonPass} for
-getting anonymous credentials, adapting only the notation to fit ours. 
-%More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.
-
-\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
-During the setup phase, the \ac{CA} creates all the needed keys.
-The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
-  \ACsetup\) (see \cref{ACsignAlg}).
-
-\emph{Registration: \(\sk\gets 
-    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
-During the registration phase, each participant generates a secret key~\((k, 
-  r)\) and obtains a signature on it by the \ac{CA} \emph{but without revealing 
-  it} to the \ac{CA} (or to any part thereof in a multi-party scenario).
-At the end, each participant will have a signed secret key while the \ac{CA} 
-will issue only one signature per participant but without knowing the 
-association between a particular key and the identity of the participant.
-The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
-\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
-\cref{ACacAlg}).
-Upon success, the participant sets \(\sk = (\sigma, k, r)\).
+In line with some \ac{LPS}, \eg \ac{PROPS}, we now provide a version where we 
+reduce the trust in the witnesses.
+The entities and roles involved in this version of the protocol are still the 
+same, but we reduce the possibility to create new proofs before and after an 
+event.
 
@@
 
-%The join, participation and submission phases are as follows.
-% illustrated in \cref{fig:ProtocolOverview}.
-The goal of \CROCUS is to generate and collect privacy-preserving
-participation proofs that can be counted and verified. These proofs
-consist of proof shares that are constructed as depicted in
-\cref{fig:ProofFig}. The protocol phases are given in
-\cref{fig:ProtocolOverview} and described below.
+The main change to participate is the use of the time-stamping property of 
+\(\TS\).
+Instead of the witness determining the time~\(t\), the witness and protester 
+each determine a time interval for the creation of the proof.
+The witness gets \(t_s\gets \TSget\) and the protester gets \(t_s'\gets 
+\TSget\) from the ledger~\(\TS\).
+They close the interval by committing the proof share to the ledger using 
+\(\TSsubmit\).
+This adapted structure of a proof-share is depicted in \cref{fig:ProofFig}.
+The updated protocol phases are given in \cref{fig:ProtocolOverview} and 
+described below.
 
@@
     witness's key \(\sk_W\) and the protester's \(\pid\).
-    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
-    protester and witness, respectively, and \(l\) is an area.
+    \(t_s, t_s'\) are the outputs from \(\TSget\), \eg hashes of the head 
+    blocks in the ledger seen by the protester and witness, respectively, and 
+    \(l\) is an area.
     All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
@@
 
-\emph{Creation of a protest: the manifesto.}
-The organizer writes a manifesto for the protest, which describes its cause.
-This manifesto could take the form of any intelligible text, in
-practice at minimum a name.
-The organizer then distributes this manifesto to people through
-any suitable means  (\eg on the Web, on placards, \etc).
-If they agree with the cause, they will use the knowledge of the
-manifesto to join the protest.
+The creation of the protest is the same: the organizer publishes the manifesto 
+in some way.
 
-\emph{Joining as a protester: \((\pid, t_s)\gets 
-    \CROCUSjoin[_P][\text{manifesto}]\).}
-A protester who wants to join the protest uses the manifesto to
-compute an identifier for the cause by hashing the manifesto,
-\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
-from the organizer, we omit this in the protocol for readibility).
-Afterwards, this identifier is used to create the protest-specific identifier 
-for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\)%
-% (see \cref{fig:ProofFig} and \cref{ACprfAlg} in the appendix for details of 
-%the algorithms)%
-.
-The protester also fetches a time-correlated random value, \(t_s\), from 
+\paragraph*{Joining}
+
+The join procedure is the same, except we add fetching \(t_s\).
+So the protester computes \(
+  \cid\gets \Hash[\mfst]
+\) and \(
+  \pid\gets \ACprf[_{\sk_P}][\cid].
+\) The protester also fetches a time-correlated random value, \(t_s\), from 
 \(\TS\), \(t_s\gets \TSget\).
 
-\emph{Joining as a witness: \(t_s'\gets \CROCUSjoin_W\).}
-The witness simply gets a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
+The witness simply gets a time-correlated random value from the time-stamping 
+service, \(t_s'\gets \TSget\).
 Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
@@
 
-\emph{Participation: \(\pi\gets
-    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
-In the participation phase, the protester and 
-the witness construct the proof share of the protester (\cref{fig:ProofFig}).
+\paragraph*{Participation}
+
+In the participation phase, the only difference is the use of \(t_s\) and 
+\(t_s'\) instead of \(t\).
 
@@
   \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
-\] (see \cref{ACacAlg}), \(k\) and \(r\) are part of \(\sk_P\).
-Note that the \acf{PK} in \cref{ACacAlg} must be
-run as a \iacf{PPK}, which we do by distance bounding.
+\] to verify the correctness of \(\pid\) and do the distance bounding, same as 
+before.
 If the protocol succeeds, the witness will compute \(\wid \gets 
@@
 
-\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
-The protester commits the proof-share data to the ledger~\(L\) and receives the 
-proof of commitment, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', 
-  l]]\).
+\paragraph*{Submission}
+
+The submission phase differs in what constitutes the proof share.
+The protester commits the proof-share data to the ledger~\(\TS\) and receives 
+the proof of commitment~\(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', 
+l]]\), which ends the time interval.
 The sooner this is done, the higher the precision for the time-dependent 
 eligibility criterion will be for later counting.
+(The witness can also do this, the important part is to do it as soon as 
+possible.)
 The remaining operations are not time critical.
@@
 The protester computes \iac{NIZK} proof \(\corr_{\pid}\), which shows the 
-correctness of \(\pid\).
+correctness of \(\pid\) to a third party.
 More specifically,
@@
 
-\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
-    l]\).}
-The witness, like the protester, commits the proof-share data to the 
-ledger, \(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
-%(This is to make the time interval as early as possible, whoever is the faster 
-%will submit it.) \sonja{but both do}
+The witness, like the protester, commits the proof-share data to the ledger, 
+\(t_e\gets \TSsubmit[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
+(This is to close the time interval as early as possible, whoever is the faster 
+will submit it first, so both submit it.) \sonja{but both do}
 Then, without any time requirements, the witness computes \iac{NIZK} proof 
@@
 
-% While there are various ways for verifying the participation count, hereafter, 
-% we will detail the two suggested just after \cref{DefParticipationCount}.
-% In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
-% Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
-% In the second approach, we trust specific witnesses, but no others.
-% In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
-% It is the strength function \(\str\) of \cref{DefParticipationCount} that 
-% differ in the two cases.
-% We will first give the procedure and then how to construct the two different 
-% strength functions.
+The set of proofs is constructed the same way as before.
+What differs is what we do with \(\theta\) and \(\str\).
 
-To count or verify the participation count for a protest \(\prtst\) with 
-identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
-all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
-Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
-\begin{enumerate*}
-\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
-    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
-\item the participation proof \(\prf_{j}\) for each protester \(j\),
-\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
-  for all protesters in \(\prtst\), and finally,
-\item the participation count, \ie the cardinality of 
-  \(\prfs_\prtst^{\str,\theta}\).
-\end{enumerate*}
+We have the set of proof shares~\(\pshs\), as before.
+We also have the partitioning of the set of proof shares using the 
+relation~\(=_\pid\) such that \(
+  (\cid, \pid, \wid, t, l) =_\pid (\cid', \pid', \wid', t', l')
+\) is true if \(\pid = \pid'\).
+Each equivalence class \(\prf_{i, \prtst} \in \pshs/{=_\pid}\) is a proof of 
+participation for participant \(i\).
+This is the same as before.
 
-More precisely, given \[
-  \pshs_{\cid_0} = \{ (\cid, \pid, \wid, l, t_s, t_s', t_c, \corr) \in \pshs 
-  \mid \cid = \cid_0 \}
-\] and a matching pair \((s_P, s_W) \in {\pshs_{\cid_0}}^2\) for a witness 
-\(i\) and a protester \(j\) with
-\begin{align*}
-  s_P &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c, \corr_i) &\text{and} \\
-  s_W &= (\cid_0, \pid_j, \wid_i, l, t_s, t_s', t_c', \corr_j),
-\end{align*}
-%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
-the verifier can build a valid proof share \(s_j^{(i)}\) certified by \(i\) for 
-\(j\) as follows:
-verify \(\corr_i\) and \(\corr_j\),
-let
-\begin{align*}
-  t &= \interval{\max(t_s, t_s')}{\min(t_c, t_c')} &\text{and} \\
-  s_j^{(i)} &= (\cid_0, \pid_j, \wid_i, l, t),
-\end{align*}
-as in \cref{DefProofShare},
-check that \(s_j^{(i)}\) is valid (\ie happened during and at the location of 
-the protest), as in \cref{DefProofShare}.
+However, in terms of \cref{DefParticipationCount}, the total participation 
+count is still \(|\prfs_\prtst^{\str, \theta}|\), but this time the verifier 
+might set \(\theta\) and \(\str\) differently.
+The verifier can still set \(\theta\) and \(\str\) the same as before and get 
+the trusted witnesses scenario.
+But this time the verifier knows when the proofs were constructed (in 
+\(\interval{t_s}{t_e}\)), due to trusting \(\TS\) to provide correct 
+time-stamping and immutability.
 
-Then the set of all valid proof shares for a protester \(j\) constitutes its 
-participation proof \(\prf_{j}\), as in \cref{DefParticipationProof},
-and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst\), as in \cref{DefParticipationCount}.
-Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by  \cref{DefParticipationCount}.
-
-% MOST PROBABLY obsolete below v
-
-%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
-%(see \cref{DefProtest}), a verifier must download all the proof shares \[
-%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
-%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
-%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
-%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
-%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
-%\(l_i\subseteq  l\).
-%Any proof share that does not verify correctly will be discarded.
-%At this point, the verifier has constructed the set \(S\) from 
-%\cref{DefProofShares} and can thus construct any participation proof 
-%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
-%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
-%    \theta}|\) as in \cref{DefParticipationCount}.
-
-%__________________________
-
-% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
-% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).
-
-In the case of trusted witnesses, each such trusted witness must
-publish or otherwise inform the verifier of which proof shares they
-have signed, \eg by giving a list of all such proof shares or
-digitally signing each proof share\footnote{%
-  To achieve witness privacy in this situation, one could employ a
-  group or ring signature scheme for a set of potentially trusted witnesses, \eg
-  members of an independent journalist association.  Then one learns
-  that at least one member of this set must have
-  been there.
-}.
-
+\daniel{The following should be edited to fit.} 
 Note that, thanks to the \((\str,\theta)\)-eligibility criterion
@@
 criteria (time interval, location, number of regular or trusted
-witnesses, who is considered to be a trusted witness) for their own count
-and as long as these are published along with the result, anyone can
-verify the correctness of the count under those criteria, and potentially question the validity of this choice.
-Biased or partisan verifiers may be tempted to make extreme choices, but they will have to publish those choices and lose credibility.
-Reasonable verifiers on the other hand will try to find a good middle-ground that counts all legitimate protesters while being resistant to isolated malicious agents.
+witnesses, who is considered to be a trusted witness) for their own count.
+As long as \emph{these assumptions/criteria are published along with the 
+result}, anyone can verify the correctness of the count under those criteria, 
+and potentially question the validity of this choice. Biased or partisan 
+verifiers may be tempted to make extreme choices, but they will have to publish 
+those choices and lose credibility. Reasonable verifiers on the other hand will 
+try to find a good middle-ground that counts all legitimate protesters while 
+being resistant to isolated malicious agents.
 

### 2021-06-16 paper/intro.tex

@@
 The paper is organized as follows.
-In \Cref{system-model}, we describe our system model and summarize the desired 
-properties for crowd counting, followed by a discussion of current 
-crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
-we formalize the notion of protest and the desired verifiability and privacy 
-properties, and in \cref{building-blocks}, we give the relevant background on 
-the building blocks of our solution.
+In \cref{current-crowd-counting}, we describe current crowd counting and the 
+desired properties.
+In \cref{definitions}, we describe our system model and formalize the notion of 
+protest and the desired verifiability and privacy properties.
+In \cref{building-blocks}, we give the relevant background on the building 
+blocks of our solution.
 %

### 2021-06-16 paper/intro.tex
Breaks out outline, CANSifies intro

@@
 
-\paragraph{Outline}
-
-The paper is organized as follows.
-In \cref{current-crowd-counting}, we describe current crowd counting and the 
-desired properties.
-In \cref{definitions}, we describe our system model and formalize the notion of 
-protest and the desired verifiability and privacy properties.
-In \cref{building-blocks}, we give the relevant background on the building 
-blocks of our solution.
-%
-%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
-%different from that originally proposed by \textcite{DistanceBounding}.
-%We provide a proof of its security and formally verify it using 
-%Tamarin~\cite{TamarinDB}.
-%
-We present \CROCUS, a privacy-preserving crowd counting 
-%estimation 
-protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
-We compare it to related work in \cref{related-work}.
-Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
-our conclusions in \cref{Conclusion}.
+\input{current-crowd-counting}
+\input{outline.tex}

### 2021-06-16 paper/current-crowd-counting.tex
Breaks out outline, CANSifies intro
Removes ref on voting properties due to Doug's comments

@@
 
-We draw inspiration from properties for voting systems as formalized
-in ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
-\daniel{Find a new ref for voting verifiability properties, Douglas commented 
-  that the last one is not the origin.}
+We draw inspiration from properties for voting systems:
 \begin{description}
@@
   \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-    \daniel{Douglas: technically this is Sako-Kilian, non-technically, it's 
-      old.}
-  \item[Individual verifiability:] each voter can verify that their vote is included in the result.
-    \daniel{Douglas: this is much earlier than Sako-Kilian, in essence 
-      Fiat-Shamir (technically). Non-technically, much older.}
+  \item[Individual verifiability:] each voter can verify that their vote is 
+    included in the result.
 \end{description}
@@
 
-In ~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}, the main three
-privacy properties for voting protocols are given as:
+The main three privacy properties for voting protocols are given as:
 \begin{description}

### 2021-06-16 paper/current-crowd-counting.tex
Minor clarification on spatial eligibility
Fixes typos

@@
 % }
-and spatial eligibility (\ie each participation proof satisfies some temporal 
-and spatial relation to the protest).
+and spatial eligibility (\ie the protester must have been present at the 
+protest).
 In essence, the proof must bind the person to the time and location of the protest.
@@
 More precisely, for the protester we want unlinkability (from the adversary's 
-perspective) between a protester's real identity \(P\) and the participation 
-proof (and thus also the protest itself).
+perspective) between a protester's real identity and the participation proof 
+(and thus also the protest itself).
 Phrased differently, given a participation proof, Grace should not be able to 
@@
 In this situation it is very difficult to faithfully capture the situation.
-Taking pictures from different angles risks double counts.
-Another challenges is determining whether people near the event's perimeter are participants or simply bystanders~\cite{HowToEstimateCrowdSize}.
+Taking pictures from different angles risks double counts. Another challenge is 
+determining whether people near the event's perimeter are participants or 
+simply bystanders~\cite{HowToEstimateCrowdSize}.
 
@@
 
-CrowdCount \citet{CrowdCount} is a web service that lets Alice create an event such that anyone can submit their location to register that they are in Alice's event.
+\Textcite{CrowdCount} is a web service that lets Alice create an event such 
+that anyone can submit their location to register that they are in Alice's 
+event.
 Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.

### 2021-06-16 paper/related-work.tex
Adds LPS to current-crowd-counting, cleans related-work

--- 2020-04-15 paper/related-work.tex
@@
-\section{Related work}
+\section{Related work}%
+\label{related-work}
 
-Our scheme relates to several other works: the crowd counting methods already 
-described in \cref{current-crowd-counting}, location-proof systems and 
+Our scheme relates to several other works: the crowd counting methods and 
+location proof systems already described in \cref{current-crowd-counting}, and 
 Sybil-free pseudonym systems.
-
-\paragraph*{Location-proof systems}%
-\label{db-and-lp}
-
-In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
-a particular location at a specific moment in time.
-\Iac{LPS} is an architecture by which users can obtain \acp{LP} from 
-neighboring witnesses (\eg trusted access points or other users) that can later 
-be shown to verifiers who can check the validity of a particular 
-proof~\cite{luo2010veriplace,zhu2011applaus}.
-Most of the existing approaches to \acp{LP} require the prover and the 
-witnesses to disclose their identities, thus raising many privacy issues such 
-as the possibility of tracing the movements of users of the \ac{LPS}.
-However, some \acp{LPS}, such as PROPS~\cite{PROPS}, exist that provide strong 
-privacy guarantees along with the possibility of verifying the claim of the 
-location.
-
-\CROCUS shares some similarities with PROPS\@.
-The main difference is that \CROCUS operates in a more adverse environment, and 
-can thus not provide any guarantees using the decentralized, untrusted 
-witnesses that PROPS can.
-The incentives to cheat are also bigger and consequently the thresholds for 
-collusion are much higher.
-CROCUS must also tie the cause to the location proof, to designate the proof to 
-the protest in which the protester participated.
-
-The same can be said in comparison to Platin.io\footnote{%
-  URL: \url{https://platin.io}.
-}.
-
-\paragraph*{Sybil-free pseudonym systems}
 

### 2021-06-16 paper/protest-model.tex
Fixes typo and clarifies in protest definitions

@@
 }.
-Generalizing from these examples, the minimal common part is the cause,\label{CauseIsTheCommonDenominator} while the location (or area) considered varies over time.
+Generalizing from these examples, the minimal common part is the 
+cause,\label{CauseIsTheCommonDenominator} while the location (or area) 
+considered varies over several intervals of time.
 
 For the rest of the paper, we will refer to the organizer as Alice.
-We assume that the objective of Alice is to count everyone who participated at any time and in any of the locations~\cite{2016DemonstrationsInSeoul} %\sonja{commented out for
+We assume that the objective of Alice is to count everyone who participated at 
+any time and in any of the locations~\cite{2016DemonstrationsInSeoul}. 
+%\sonja{commented out for
   %repetition: %\footnote{Note that the objective does not necessarily

### 2021-06-16 paper/practical-considerations.tex
adds practical-considerations section including short version of discussion and performance as subsections

\section{Practical Considerations}%
\label{Practical}

We now briefly list some issues for deploying
CROCUS, regarding implementability and realistic adversaries\footnote{see the long version of the paper for a more thorough
discussion of these topics. }, and then analyze its performance.

\subsection{Implementability}

Some of the assumptions that are required for implementing our proposition are 
not yet realized, however, we believe that they soon will be:
ubiquitous usage of smartphones, with an identity credential
signed by some \ac{CA}\footnote{based on \eg governmental ID on a chip as in Estonia, national
  but private as BankID in Sweden, eIDAS in the EU, or self-sovereign
  identities} ,  distance-bounding capabilities\footnote{based on \eg
  3DBS or key-fob technology integration with phones}, and
infrastructure-independent wireless communications\footnote{based on
  \eg NFC (available but inconvenient), bluetooth or WIFI (Briar and
  FireChat have been used in protests), 5G D2D (scalable but needs
  authorization step)}.

\subsection{Realistic adversary model}
Our adversary model considers only protocol data, no auxiliary data.
Against this adversary our scheme is secure.
The question is how this adversary model maps to real
adversaries. Side-channels such as taking photos, a global passive adversary
controlling all national ISPs doing time-correlation attacks (though
may not be able to observe all ledger input or \eg Tor exit nodes), or
protocol violations in protests organized by the \ac{CA} are
not prevented.

\include{performance-subsection}

### 2021-06-16 paper/location-proof-systems.tex

--- 2021-06-16 paper/location-proofs.tex
@@
-\subsection{Location proofs}
-\label{location-proofs}
-Some \acp{LBS} only grant access to resources to users located at a particular 
-location, thus raising the issue of verifying the position claimed by a 
-particular user.
-One possible way to counter this threat is by having the requesting device 
-formally prove that it really is at the claimed location, which gives rise to 
-the concept of \acp{LP}.
+\subsection{Location-proof systems}%
+\label{location-proof-systems}
+
 In a nutshell, \iac{LP} is a digital certificate attesting that someone was at 
@@
 
-%\CROCUS shares some similarities with PROPS, although their objective is quite 
-%different as it aims at verifying a global property of the population (\ie 
-%crowd estimation) in contrast to checking the location claim made by a user, 
-%which is an individual property.
-%
-%Another difference is that \CROCUS operates in a more adverse environment.
-%\CROCUS must provide \emph{universal verifiability}, this means that all proofs 
-%must be available to and verifiable by anyone.
-%One problem here is that we have multiple verifiers who might not trust the 
-%same witnesses.
-%The incentives to cheat are also bigger and consequently the thresholds for 
-%collusion are much higher.
-%
-\sonja{add something on platin.io, details unknown but roughly relying on 
-  witnesses and graph theory (unique big cluster, assumption of honest 
-  majority)}
+Our work is very related to \acp{LPS}.
+The crucial differences are how the \ac{LP} is used and the more adverse 
+environment.
+CROCUS must tie the cause of the protest to the location proof to designate the 
+proof to the protest in which the protester participated.
+Due to the adverse environment, \CROCUS cannot provide any guarantees using the 
+decentralized, untrusted witnesses that, \eg, PROPS can.
+The incentives to cheat are also bigger and consequently the thresholds for 
+collusion are much higher.
+
+In PASPORT~\cite{PASPORT}, the verifier is trusted and also known in advance.
+This does not work with universal verifiability.
+(The verifier chooses the subset of witnesses that can vouch for a prover. 
+Which makes it an interactive protocol. And the verifier must know which 
+witnesses are on location in advance.)
+
+\Textcite{ProofOfWitnessPresence} does not treat the adverse setting and, 
+particularly, the problem of \ac{DB} (see \cref{distance-bounding}).

### 2021-06-16 paper/outline.tex

\subsection{Outline}

The paper is organized as follows.
In \cref{definitions}, we describe our system model and formalize the notion of 
protest and the desired verifiability and privacy properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

### 2021-06-16 paper/related-work.tex
Updates relatd-work.tex with broken out parts

@@
 
-Our scheme relates to several other works: the crowd counting methods and 
-location proof systems already described in \cref{current-crowd-counting}, and 
-Sybil-free pseudonym systems.
+Our scheme relates to several other works: crowd counting methods, location 
+proof systems, and Sybil-free pseudonym systems.
 
-Our Sybil-free pseudonym system is very similar to that of 
-\textcite{SybilFreePseudonyms}.
-Both are based on the work of \textcite{HowToWinTheCloneWars}.
-We make the same simplification of~\cite{HowToWinTheCloneWars} as 
-\textcite{SybilFreePseudonyms}, but we also require an interactive version.
-Furthermore, our \acp{PK} must be distance bounding.
+\input{current-crowd-counting}
+\input{location-proof-systems}
+\input{sybil-free-systems}

### 2021-06-16 paper/outline.tex

@@
 %estimation 
-protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
-We compare it to related work in \cref{related-work}.
-Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
+protocol in in \Cref{Protocol}, analyze its security in
+\cref{SecurityAnalysis}, and discuss practical considerations including performance in \cref{Practical}.
+%We compare it to related work in \cref{related-work}.
+%Finally, we discuss limitations and assumptions in \cref{Discussion}
+Finally, we state
 our conclusions in \cref{Conclusion}.

### 2021-06-16 paper/performance-subsection.tex

\subsection{Performance}%
\label{PerformanceAnalysis}

\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

Performance considerations are crucial during the protests due to the nature of 
the devices used to run \CROCUS, which are resource-constrained in terms of 
energy, storage and computational power, and are operating on limited network 
capacity.

\subsubsection{Smartphones and smartcards}

Recent technological progress has enabled the deployment of advanced 
cryptographic primitives on smartcards and smartphones that could be used to 
implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices 
are now fast enough to efficiently implement \acp{PET}, with a Samsung Galaxy S 
i9000 (back in 2014) able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to 
process complex protocols such as Idemix or U-Prove (taking between 
\SI{4}{\second} and \SI{8}{\second} to process them). While the limited 
processing power of many embarked systems has been a challenge, Idemix has been 
successfully implemented to prove the possession of credentials on Java Cards 
by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released 
in 2014, aimed to achieve an implementation ``suitable for real life 
transactions''~\cite{IRMA} while maintaining security and privacy for its 
users.

With respect to its implementation, \CROCUS is very similar to the 
implementation of Anon-Pass~\cite{AnonPass}, an anonymous subscription system 
in which a long-term credential can be used to derive a single login for any 
authentication window (\ie epoch) such that logins are unlinkable across 
different epochs.
In particular, the setup and registration phases are almost identical.
The evaluation conducted by \textcite{AnonPass} used as server a Dell Optiplex 
780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses 
Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz 
Intel Core 2 CPU but with only 4 GB of RAM\@.
The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
This is typically the type of pairing that could also be used with \CROCUS\@.
Not counting the setup that is performed once by the \ac{CA}, the time reported 
for the registration on the server (\ie \ac{CA}) side is 
\SI{19.8}{\milli\second} while it is \SI{23.4}{\milli\second} on the client 
side.
With respect to joining and participation phases, with the exception of the 
distance-bounding they are actually quite similar to the login protocol of 
Anon-Pass in which the time required to create a message for a protester would 
be around \SI{13.5}{\milli\second} while the time needed for the witness would 
be only \SI{7.9}{\milli\second}.

%\subsection{Distance bounding}
%
%The distance-bounding chips~\cite{3db-access} currently available on the market 
%can already enable proofs of proximity for any range of up to 
%  200 meters.
%One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
%More precisely, they have proposed three different implementations of the 
%Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic 
%implementation running at the application layer to an advanced one running in 
%RFID-emulation mode. The results obtained already show that a relay attack can 
%be detected if the adversary introduces a delay of more than 1.5 ms when 
%performing such an attack (most of the existing attacks introduce delays of at 
%least tens of milliseconds).

% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated. 
% The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
%Seb: to do add the reference to the following paper at the end of the sentence:
%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
% Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$). 
% However, this can be reduced to four random number generations and one exponentiation using precomputation.

%\paragraph{Threshold of witnesses.}
%Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
%Then it would be reasonable to set the threshold of at least 6000 witnesses.
%According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
%signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
%\SI{2.66}{\giga\hertz} Core 2 processor.
%This yields \(
%  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%  \SI{48}{\second}.
%\) of processing.

\subsubsection{Witness processing}

As above, assume we have one trusted witness.
A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
maximum \SI{200}{\metre}).
Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
(\SI{120}{\metre} radius), which fits 137018~protesters according to 
\textcite{2016DemonstrationsInSeoul}.
It would take this witness \SI{5.8}{\hour} to witness all of them.
Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
witnesses.

\subsubsection{Ledger (blockchain) efficiency}

For the example of 1\,000\,000 participants, with trusted witnesses, each 
participant only needs to acquire one proof share from a trusted witness.
Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.

%If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
%While this already takes longer than counting votes in national elections, the threshold is still very low. 
%% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
%% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
%% In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
%% %Seb: I agree maybe we should move it to the previous subsection
%% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
%% This yields \(
%%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%%   \SI{48}{\second}.
%% \) of processing. 
%For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
%Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.

%\subsection{Blockchain efficiency}

\sonja{removed for now: One problem can arise in the case in which there is no trusted witnesses.
In this situation, if we set the threshold too high, we need to submit more proof shares than the blockchain can handle within a reasonable time.}

%assumptions about smartphones:
%(This means that we essentially provide a lower bound for the participation 
%count, since some participants might not have such a device.)
%Sonja says: is this still true? Given mafia fraud we can't guarantee
%that, right?

### 2021-06-16 paper/current-crowd-counting.tex
changes subsections, textbf to paragraph, adds related work subsection in intro, breaks out desired properties

@@
-\section{Desired properties and current crowd-counting methods}%
-\label{current-crowd-counting}
-
-\subsection{Desired properties}%
-\label{desired-properties}
-
-We note that, in general terms, protests are petitions with a given time and 
-location.
-Protests, petitions and elections share that in all three many individuals 
-express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or 
-persecution).
-For that reason we have strong requirements for verification and privacy for 
-elections, it follows that we should have similar properties for protests
-and petitions.
-
-We draw inspiration from properties for voting systems:
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-  \item[Individual verifiability:] each voter can verify that their vote is 
-    included in the result.
-\end{description}
-In our context, votes are translated into \emph{participation proofs}.
-Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
-The eligibility requirement is slightly different as for protests it must also
-include temporal %\footnote{%
-%   Elections also have some temporal aspects, such that one cannot vote at any 
-%   time and a vote in one election should not be reusable in the next election.
-%   However, the temporal relation for a protest is not as strictly defined as for 
-%   elections as a protest can start at any time and last for an arbitrary period 
-%   of time.%
-% }
-and spatial eligibility (\ie the protester must have been present at the 
-protest).
-In essence, the proof must bind the person to the time and location of the protest.
-(This is the difference to a petition.)
-
-The main three privacy properties for voting protocols are given as:
-\begin{description}
-  \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
-\end{description}
-
-%Coercion resistance is not possible to achieve for protests.
-Coercion resistance in voting typically relies on physical isolation
-(\eg private voting booths), including for digital systems, 
-and that is by definition not possible for public events.
-For instance, someone could simply physically bring Alice to a protest against her will.
-As for receipt freeness, while
-desirable \emph{in itself}, it implies a conflict with verifiability in our context:
-%appealing at first glance, is not desirable (probably not possible)
-%in our context since this will conflict with verifiability:
-in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
-cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
-(\ie the protester was there), which would make verifiability impossible.
-
-Therefore in our context, the crucial property is  vote privacy.
-More precisely, for the protester we want unlinkability (from the adversary's 
-perspective) between a protester's real identity and the participation proof 
-(and thus also the protest itself).
-Phrased differently, given a participation proof, Grace should not be able to 
-distinguish if it was Alice or Bob who participated.
-Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (from a different protest).
-
-\subsection{Current crowd-counting methods}
+\paragraph{Current crowd-counting methods}
 

### 2021-06-16 paper/desired-properties.tex
changes subsections, textbf to paragraph, adds related work subsection in intro, breaks out desired properties

\subsection{Desired properties}%
\label{desired-properties}

We note that, in general terms, protests are petitions with a given time and 
location.
Protests, petitions and elections share that in all three many individuals 
express their opinion.
These opinions can be sensitive (\eg be a cause for discrimination or 
persecution).
For that reason we have strong requirements for verification and privacy for 
elections, it follows that we should have similar properties for protests
and petitions.

We draw inspiration from properties for voting systems:
\begin{description}
  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
  \item[Individual verifiability:] each voter can verify that their vote is 
    included in the result.
\end{description}
In our context, votes are translated into \emph{participation proofs}.
Universal and individual verifiability remain the same, in the sense that anyone can verify the participation count by counting the proofs and a participant can verify their proof is included.
The eligibility requirement is slightly different as for protests it must also
include temporal %\footnote{%
%   Elections also have some temporal aspects, such that one cannot vote at any 
%   time and a vote in one election should not be reusable in the next election.
%   However, the temporal relation for a protest is not as strictly defined as for 
%   elections as a protest can start at any time and last for an arbitrary period 
%   of time.%
% }
and spatial eligibility (\ie the protester must have been present at the 
protest).
In essence, the proof must bind the person to the time and location of the protest.
(This is the difference to a petition.)

The main three privacy properties for voting protocols are given as:
\begin{description}
  \item[Vote privacy:] the voting does not reveal any individual vote.
  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
\end{description}

%Coercion resistance is not possible to achieve for protests.
Coercion resistance in voting typically relies on physical isolation
(\eg private voting booths), including for digital systems, 
and that is by definition not possible for public events.
For instance, someone could simply physically bring Alice to a protest against her will.
As for receipt freeness, while
desirable \emph{in itself}, it implies a conflict with verifiability in our context:
%appealing at first glance, is not desirable (probably not possible)
%in our context since this will conflict with verifiability:
in contrast to voting, receipt freeness for \emph{how} the voter voted (\ie the 
cause of the protest) here implies receipt freeness for \emph{that} the voter voted 
(\ie the protester was there), which would make verifiability impossible.

Therefore in our context, the crucial property is  vote privacy.
More precisely, for the protester we want unlinkability (from the adversary's 
perspective) between a protester's real identity and the participation proof 
(and thus also the protest itself).
Phrased differently, given a participation proof, Grace should not be able to 
distinguish if it was Alice or Bob who participated.
Furthermore, if Grace has managed to link one proof to Alice due to some 
auxiliary knowledge, she should not be able to link it to another proof (from a different protest).

### 2021-06-16 paper/practical-considerations.tex
changes \include to \input in practical-considerations to prevent page breaks

@@
   identities} ,  distance-bounding capabilities\footnote{based on \eg
-  3DBS or key-fob technology integration with phones}, and
+  3DB-access or key-fob technology integration with phones}, and
 infrastructure-independent wireless communications\footnote{based on
@@
 
-\include{performance-subsection}
+\input{performance-subsection}

### 2021-06-16 paper/protest-model.tex

@@
 Our protocol relies on \emph{witnesses} to certify and associate the proof to the time and location by creating a \emph{proof share}.
-A witness is only allowed to create one proof share per protester to avoid the risk of count inflation.
-(Note that a participant of a protest can take the role of a protester but also 
-act as witness for other protesters.)
+%A witness is only allowed to create one proof share per protester to avoid the 
+%risk of count inflation.
+%(Note that a participant of a protest can take the role of a protester but 
+%also act as witness for other protesters.)
 Then, the set of all \emph{valid} proof shares forms the participation proof of a protester.
@@
   \(\psh \sqsubseteq \sprtst\).
+  We let \(\pshs\) denote the set of all proof shares and \(
+    \pshs_\prtst = \{ \psh \in \pshs \mid
+      \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
+  \) be the subset of valid proof shares related to a protest~\(\prtst\).
 \end{definition}
 
-%A subset of the proof shares forms a participation proof for a protester.
-We let \(\pshs\) denote the set of all proof shares.
-Let \(
-  \pshs_\prtst = \{ \psh \in \pshs \mid
-    \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
-\) be the subset of proof shares related to a protest~\(\prtst\).
 We denote by \(=_\pid\) the equivalence relation on \(\pshs\) where \((\cid, t, 
@@
   \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
-    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs \mid
+    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs_\prtst
+      \mid
       \str(\prf_{i,\prtst})\geq \theta \right\}
@@
 }
-In general, \(\str\) can be defined as a weighted sum of the proof shares, 
-\(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) being the trust in 
-the witness corresponding to the proof share \(s_i\), and the threshold 
-\(\theta\) represents the total trust needed to accept a participant as valid.
+For the examples in this paper, \(\str\) can be defined as a weighted sum of 
+the proof shares, \(\str = \sum \omega_i s_i\), with the weights \(\omega_i\) 
+being the trust in the witness corresponding to the proof share \(s_i\), and 
+the threshold \(\theta\) represents the total trust needed to accept a proof of 
+particiption as valid.
 One example would be to set all weights to 1 for \(\str\) to return the number of unique witnesses and thus let \(\theta\) to be the threshold of the number of required witnesses.

### 2021-06-16 paper/protest-model.tex

@@
 \begin{definition}[Valid proof share]%
-  \label{DefProofShare}\label{DefProofShares}
+  \label{DefProofShare}\label{DefProofShares}\label{ValidProofShare}
   A \emph{proof share} \(\psh = (\cid, t, l, \pid, \wid)\) is a tuple in which: 
@@
   We let \(\pshs\) denote the set of all proof shares and \(
-    \pshs_\prtst = \{ \psh \in \pshs \mid
+    \pshs_{\prtst} = \{ \psh \in \pshs \mid
       \exists \sprtst \in \prtst, \psh \sqsubseteq \sprtst \}
@@
 
-We denote by \(=_\pid\) the equivalence relation on \(\pshs\) where \((\cid, t, 
-l, \pid, \wid) =_\pid (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
+We denote by \(=_{\pid}\) the equivalence relation on \(\pshs\) where \((\cid, 
+t, l, \pid, \wid) =_{\pid} (\cid', t', l', \pid', \wid')\) if \(\pid = \pid'\).
 %and we will use the following notation to filter out a subset of \(\pshs\) with 
@@
   \label{DefParticipationProof}\label{DefParticipationProofs}
-  We denote by \(\prfs_\prtst = \pshs_\prtst/{=_\pid}\) the \emph{set of all 
-  proofs of participation for the protest~\(\prtst\)}.
+  We denote by \(\prfs_{\prtst} = \pshs_{\prtst}/{=_{\pid}}\) the \emph{set of 
+  all proofs of participation for the protest~\(\prtst\)}.
   The \emph{participation proof} of a protester with pseudonym~\(i\) who 
@@
     \prf_{i, \prtst} =
-    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_\prtst \mid
+    \left\{ (\cid, t, l, \pid, \wid) \in \pshs_{\prtst} \mid
       \pid = i\right\},
@@
   \(|\prfs_{\prtst}^{\str,\theta}|\) of the set of \emph{eligible} participation proofs respectively to a strength function $\str$ and a threshold $\theta$: \[
-    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs_\prtst
+    \prfs_{\prtst}^{\str,\theta} = \left\{ \prf_{i,\prtst} \in \prfs_{\prtst}
       \mid

### 2021-06-16 paper/security-properties.tex
Clarifies security properties (relates them to protest model)

@@
     \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
+      \Ie \(t\subseteq t_\prtst\) in \cref{ValidProofShare}.
 
     \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
+      \Ie \(l\subseteq l_\prtst\) in \cref{ValidProofShare}.
 
@@
       is designated for the particular protest.
+      \Ie designated to \(\cid\) in \cref{ValidProofShare}.
 
@@
 particular participant at a particular protest).
-In the terminology of \textcite{SybilFreePseudonyms}, for each protester a 
-protest is a context or identity domain whereas for each witness every 
+In the terminology of \textcite{SybilFreePseudonyms}; for each protester a 
+protest is a context or identity domain, whereas for each witness every 
 protester is a context (or identity domain).

### 2021-06-16 paper/security-properties.tex
Updates data in adversary model

@@
     \item\label{TemporallyRelated} \emph{Temporal eligibility}: demonstrate that the proof was created after the start of the protest and before the end of the protest.
-      \Ie \(t\subseteq t_\prtst\) in \cref{ValidProofShare}.
+      \Ie \(t\subseteq t_{\prtst}\) in \cref{ValidProofShare}.
 
     \item\label{SpatiallyRelated} \emph{Spatial eligibility}: demonstrate that the proof is spatially related to the physical location or journey of the protest.
-      \Ie \(l\subseteq l_\prtst\) in \cref{ValidProofShare}.
+      \Ie \(l\subseteq l_{\prtst}\) in \cref{ValidProofShare}.
 
@@
 \item\label{ProtestUnlink} \emph{Protest unlinkability}: protesters' pseudonyms 
-  (\(\pid_\cid, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
+  (\(\pid_{\cid}, \pid_{\cid'}\)) must be unlinkable between protests (\(\cid, 
   \cid'\)) from the adversary's perspective.
 \item\label{WitnessUnlink}\emph{Witness unlinkability}:  witnesses' pseudonyms 
-  (\(\wid_\pid, \wid_{\pid'}\)) must be unlinkable between protesters (\(\pid, 
-    \pid'\)) from the adversary's perspective.
+  (\(\wid_{\pid}, \wid_{\pid'}\)) must be unlinkable between protesters 
+  (\(\pid, \pid'\)) from the adversary's perspective.
 \end{requirements}

### 2021-06-16 paper/verifiability-analysis.tex
Updates data in adversary model

@@
 There exists another case of collision that we must prevent.
-Consider the situation in which Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
+Consider the situation in which Alice computes \(\pid = \ACprf[_{\sk}][\cid]\) 
+for some cause identifier \(\cid\) and some witnesses computes \(\wid_1, 
+\dotsc, \wid_n\), with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
 Now, if Alice constructs a manifesto \(m\) such that \(\Hash[m] = \pid\), then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the protest with manifesto \(m\).
@@
 All proof shares (\ie \(\prf_{\pid, \prtst} = (\cid, \pid, \wid, t_s, t_s', 
-  t_e, t_e', l, \corr_\pid, \corr_\wid)\)) are committed to the ledger~\(\TS\) 
-and available from a public and permanent storage.
+t_e, t_e', l, \corr_{\pid}, \corr_{\wid})\)) are committed to the 
+ledger~\(\TS\) and available from a public and permanent storage.
 Thus, Alice and Bob can simply check that all of their proof shares are indeed 
@@
 As the proof shares are committed and stored publicly, anyone can
-download them, verify eligibility (\ie verify \(\corr_\pid,
+download them, verify eligibility (\ie verify \(\corr_{\pid},
 \corr_{\wid}\)) of the proofs and count them.

### 2021-06-16 paper/adversary-model.tex

@@
 The protester \(P\) and the witness \(W\) communicate some protocol data,
-\(d_{P,W}(\cid, P)\), and record when the communication occurred \(t_{P,W}\).
+\(d_{P,W}(\cid, P, W)\), and record when the communication occurred 
+\(t_{P,W}\).
 The protester \(P\) communicates with \(\TS\) and \(\TS\) only learns 
 some function \(f\) of the protocol data exchanged with the witness,
-\(f(d_{P,W}(\cid, P))\), and the time of the 
-communication (\(t_{P,\TS}\)).
+\(f(d_{P,W}(\cid, P, W))\), and the time of the communication (\(t_{P,\TS}\)).
 This is illustrated in \cref{fig:base-adversary}.
@@
     \(W\) communicate.
-    They exchange protocol data as a function~\(d\) of the protest and 
-    protester, \(d_{P,W}(\cid, P)\), and record the time it happened, 
+    They exchange protocol data as a function~\(d\) of the protest, protester, 
+    and the witness, \(d_{P,W}(\cid, P, W)\), and record the time it happened, 
     \(t_{P,W}\).
-    The protester submits \(f(d_{P,W}(\cid, P))\), for some function \(f\), to 
-    the ledger \(\TS\), who records the time that happened, \(t_{P,\TS}\).
+    The protester submits \(f(d_{P,W}(\cid, P, W))\), for some function \(f\), 
+    to the ledger \(\TS\), who records the time that happened, \(t_{P,\TS}\).
     %Both the witness \(W\) and the ledger \(\TS\) are controlled by the 

### 2021-06-16 paper/P-signatures.tex
Changes "i.e.\ " and "e.g.\ " to \ie and \eg
More workaround: wrap sub- and superscripts in {}

--- 2018-02-06 paper/NIZK-anon-cred.tex
@@
 \label{NIZK-anon-cred}
-
-\NewCryptoScheme{\Psig}{Psig}
 
@@
 
-\NewCryptoFunction{\PSetup}{\Psig.\!Setup}
-
-\(params\gets \PSetup[1^\lambda]\): generates the global parameters \(params\), 
+\(params\gets \PSetup[1^{\lambda}]\): generates the global parameters \(params\), 
 which contains parameters for the underlying algorithms.
 For ease of notation we will omit \(params\) from all functions.
-
-\NewCryptoFunction{\PCommit}{\Psig.\!Commit}
 
@@
 information-theoretically hiding commitments.
-I.e.\ the adversary cannot tell which setup algorithm has been used.
-
-\NewCryptoFunction{\PObtainSig}{\Psig.\!ObtainSig}
-\NewCryptoFunction{\PIssueSig}{\Psig.\!IssueSig}
+\Ie the adversary cannot tell which setup algorithm has been used.
 
@@
 
-\NewCryptoFunction{\PProve}{\Psig.\!Prove}
-
 \((comm, \pi, open)\gets \PProve[pk, m, \sigma]\): outputs a commitment 
@@
 made by the owner of \(pk\).
-
-\NewCryptoFunction{\PVerifyProof}{\Psig.\!VerifyProof}
 
@@
 
-\NewCryptoFunction{\PEqCommProve}{\Psig.\!EqCommProve}
-
 \(\pi\gets \PEqCommProve[m, open, open']\): outputs a proof \(\pi\) saying that 
@@
 
-\NewCryptoFunction{\PVerEqComm}{\Psig.\!VerEqComm}
-
 \(\bin\ni \PVerEqComm[comm, comm', \pi]\): outputs \(1\) (accept) if the proof 

### 2021-06-16 paper/ZKPK-instantiations.tex
More workaround: wrap sub- and superscripts in {}

--- 2020-03-13 paper/ZKPK-instantiations.tex
@@
 discrete logarithms based on the Schnorr identification scheme~\cite{Schnorr}, 
-which, in its original form, can be written as \(\PK[\alpha][A = g^\alpha]\).
+which, in its original form, can be written as \(\PK[\alpha][A = g^{\alpha}]\).
 The generalized form would be \(\PK[\alpha_1, \dotsc, \alpha_n][A = 
@@
 \begin{multline*}
-  \PK[\alpha, \beta][A = g^\alpha \land B = g^\beta] = \\
-  \PK[\alpha][A = g^\alpha] \land \PK[\beta][B = g^\beta],
+  \PK[\alpha, \beta][A = g^{\alpha} \land B = g^{\beta}] = \\
+  \PK[\alpha][A = g^{\alpha}] \land \PK[\beta][B = g^{\beta}],
 \end{multline*}
@@
   \begin{tabular}{lcl}
-    \(\PKprove[\{g_i\}_{i=1}^n, q, \{\alpha_i\}_{i=1}^n]\):
+    \(\PKprove[\{g_i\}_{i=1}^n, q, A, \{\alpha_i\}_{i=1}^n]\):
     &
@@
     \(\PK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}]\) using 
-    the Schnorr identification scheme~\cite{Camenisch-phdthesis}.
+    the Schnorr identification scheme.
   }%
@@
 
-For the non-interactive instance, \(\SPK[\alpha][A = g^\alpha][m]\), we use the 
+For the non-interactive instance, \(\SPK[\alpha][A = g^{\alpha}][m]\), we use the 
 Fiat-Shamir heuristic~\cite{FiatShamirHeuristic} on the above protocol, 
@@
     \(\SPK[\alpha_1, \dotsc, \alpha_n][A = \prod_{i=1}^n g_i^{\alpha_i}][m]\) 
-    using the Fiat-Shamir heuristic on the Schnorr identification 
-    scheme~\cite{Camenisch-phdthesis}.
+    using the Fiat-Shamir heuristic on the Schnorr identification scheme.
   }%

### 2021-06-16 paper/ZKPK.tex
Moves ZKPK instantiations to the appendix
More workaround: wrap sub- and superscripts in {}

--- 2018-11-13 paper/ZKPK.tex
@@
 \begin{equation}\label{PKexample}
-  \PK[\alpha, \beta, \gamma][y = g^\alpha h^\beta \land y' = \hat g^\gamma],
+  \PK[\alpha, \beta, \gamma][y = g^{\alpha} h^{\beta} \land y' = \hat g^{\gamma}],
 \end{equation}
-which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^\alpha h^\beta\) and \(y' = \hat g^\gamma\), respectively.
+which means that we prove knowledge of \(\alpha, \beta, \gamma\) ensuring that \(y, y'\) are of the form \(y = g^{\alpha} h^{\beta}\) and \(y' = \hat g^{\gamma}\), respectively.
 Greek letters are known only to the prover and used for the information for which the prover wishes to prove knowledge, while all other letters are known by the verifier.
@@
   \sigma\gets \SPK[\alpha, \beta, \gamma]%
-  [y = g^\alpha h^\beta \land y' = \hat g^\gamma]%
+  [y = g^{\alpha} h^{\beta} \land y' = \hat g^{\gamma}]%
   [m],
 \end{equation*}
-which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^\alpha h^\beta\) and \(y' = \hat{g}^\gamma\).
+which yields a signature \(\sigma\) on \(m\), ensuring that the issuer knows \(\alpha, \beta, \gamma\) such that \(y = g^{\alpha} h^{\beta}\) and \(y' = \hat{g}^{\gamma}\).

### 2021-06-16 paper/DB-anon-cred.tex

--- 2019-09-20 paper/DB-anon-cred.tex
@@
-\section{Distance-bounding \aclp*{ZKPK} for discrete logarithms}%
+\section{Distance-bounding anonymous credentials}%
 \label{DB-anon-cred}
 
-We will now introduce \iac{DB} protocol which is a \ac{ZKPK} for discrete 
-logarithms.
-Our protocol is an adaptation of the Schnorr identification 
-scheme~\cite{Schnorr}, albeit different from that of 
-\textcite{DistanceBounding} in the original \ac{DB} paper\footnote{%
-  The \citeauthor{DistanceBounding} protocol was shown to be prone to distance 
-  hijacking~\cite{DistanceHijacking,TamarinDB} and was not secure against 
-  terrorist fraud.
-} and that of \textcite{Bussard-Bagga}\footnote{%
-  The \citeauthor{Bussard-Bagga} protocol was also shown to be 
-  vulnerable~\cite{Bussard-Bagga-attack}.
-  Although this time, the protocol could not protect against \ac{DBTF} and 
-  \ac{DBDF} as it claimed.
-}.
-We propose another way to turn the Schnorr protocol into a public-key \ac{DB} 
-protocol which is \iac{ZKPK} that is secure against \ac{DBMF}, \ac{DBDF}, 
-\ac{DBDH} and \ac{DBTF}.
-This yields strong privacy properties and protection against a malicious, 
-impersonating verifier.
-
-We also deviate from the normal technique of one-bit challenges and responses 
-otherwise used in \ac{DB} protocols.
-\Textcite{UWBPR} proposed a secure encoding for the physical 
-layer which removes the requirement of only using single-bit challenges and 
-responses for distance bounding.
-However, their protocol only works for relay attacks and cannot handle distance 
-fraud.
-This is due to a requirement of the protocol that the prover and verifier must 
-share a secret, and thus must be mutually trusted.
-
-We will first present our version of the \ac{DB} Schnorr protocol for the 
-mutual-trust case, where the prover and verifier have a pre-shared secret.
-Then we will adapt it by introducing \iac{AKE}.
-The authentication in this \ac{AKE} will leverage that our protocol is \iac{DB} 
-\ac{ZKPK} for discrete logarithms.
-If the \ac{AKE} is based on discrete logarithms we can prove the distance bound 
-while we authenticate the key.
-This allows us to embed this protocol into tamper resistant hardware to provide 
-security against malicious provers.
+One protocol exists in the literature that provides \acp{PPK} with most of the desired properties described previously, ProProx~\cite{ProProx}\footnote{Note that~\cite{ProProx} uses the abbreviation PoPoK, we prefer \acs{PPK} for shorter notation.}.
+ProProx is secure against a malicious verifier, but it provides \iac{PPK} protocol for quadratic residues (\ie protocols of the form \(\PPK[\alpha][a = 
+  \alpha^2]\)), while in our context, we need \iac{PPK} protocol for discrete logarithms (\ie \(\PPK[\alpha][a = g^{\alpha}]\)) due to our choice of anonymous credentials whose desirable properties we list in \cref{ZK-anon-cred}.%, which in turn is due to their \ac{PRF} for deriving identifiers from a long-term ID with unlinkability to the original ID but with proof of validity of this derivation.
+To realize this, we will now introduce such a protocol to enable us to have \ac{DB} anonymous credentials.
 
 \subsection{Reattempting a distance-bounding Schnorr protocol}%
-\label{DB-Schnorr}
+\label{DBSchnorr}
 
-Thanks to \textcite{UWBPR} we can keep the Schnorr protocol 
-almost as is, relays (\ac{DBMF}, \ac{DBDH}) are dealt with on the physical 
-layer.
-The only concern, for now, is \acl{DBTF}.
-(We deal with \acl{DBDF} later.)
+In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocols is based on the Schnorr identification scheme~\cite{Schnorr}.
+However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
+We now propose another way to turn the Schnorr protocol into a public-key \ac{DB} protocol that is secure against \ac{DBMF}, \ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
+It is important in our setting that the protocol is a public-key protocol, both to reach strong privacy properties and also because this property implies protection against an impersonating verifier.
 
@@
 The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
-The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
-Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
-Further, let
-\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
-\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
-key~\(k\) and finally
-\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
-and \(\UWBPRrecv\) operations.
+The private key \(\alpha\) with public key \(A = g^{\alpha}\) are generated once by the prover in the setup phase.
 
@@
   \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\DBSprove[k, g, q, \alpha, A = g^\alpha]\):
+  \begin{tabular}{p{0.8\columnwidth}cp{0.8\columnwidth}}
+    \(\DBSprove[g, q, \alpha, A = g^{\alpha}]\):
     & &
-    \(\DBSverify[k, g, q, A]\):
+    \(\DBSverify[g, q, A]\):
     \\
@@
 
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_m}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
+    % null
+    & \(\ProtoSendLeft{c_0, c_1}\)
+    & \(c_0\rgets \bin^k, c_1\rgets \bin^k\)
     \\
 
-    \vdots
+    \(s_0\gets \rho - c_0\alpha \pmod q\)
     &
+    & \(b\rgets \bin\)
+    \\
+
+    \(s_1\gets \rho - c_1\alpha \pmod q\)
     &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
-    &
-    &
+    & Prepare \(B\in \bin^{|q|+l}\), with \(|q|\) bits set to \(b\).
     \\
@@
     \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
+    \multicolumn{3}{c}{\textbf{Distance-bounding}: \(\forall i: 0\leq i < |q| + 
+        l, j\gets 0\)} \\
 
@@
     % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
+    & \(\ProtoSendLeft{b_i}\)
+    & \(b_i\gets B[i]\)
     \\
 
-    Fetch \(s_i\)
-    & \(\ProtoSendRight{s_i}\)
-    & Stop clock, record \(\Delta t\)
+    \(r_i\gets s_{b_i}[jb_i + (i-j)(1-b_i)]\)
+    & \(\ProtoSendRight{r_i}\)
+    & Record \(\Delta t_i\)
+    \\
+
+    \(j \gets j + b_i\)
+    &
+    &
     \\
@@
     &
-    & Accept if \(R = g^{s_i} A^{c_i}\) and \(\Delta t < t_{\max}\).
+    & Construct \(s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
+      b\).
+      Accept if \(R = g^{s_b} A^{c_b}\).
     \\
@@
   \caption{%
-    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
-    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol should be repeated \(n\) times to achieve the desired 
-    soundness and distance-bounding errors.
+    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) \ac{DB} Schnorr protocol for \(\PK[\alpha][A = g^{\alpha}]\).
+    The protocol should be repeated in full to achieve the desired knowledge and distance-bounding errors.
   }%
@@
 
-During one round, in the setup phase, the prover commits to a random nonce: 
-more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes 
-\(R\gets g^\rho\) and sends \(R\) to the verifier.
-The verifier generates \(m\) challenges \(c_1\rgets \bin^l, \dotsc, c_m\rgets 
-  \bin^l\) (bit strings of length \(l\)) and sends them to the prover.
-The prover computes one response per challenge, \(s_1\gets \rho - c_1\alpha, 
-  \dotsc, s_m\gets \rho - c_m\alpha\).
-This step is the main difference to the original Schnorr protocol: the verifier 
-selects several challenges and the prover computes several responses --- but 
-still only use \emph{one nonce}, \(\rho\).
-This is needed for \ac{DBTF} resistance.
+During one round, the prover commits to a random nonce: more precisely he chooses \(\rho\rgets \ZZ_q\) uniformly at random, computes \(R\gets g^{\rho}\) and sends \(R\) to the verifier.
+The verifier generates two challenges \(c_0\rgets \bin^k, c_1\rgets \bin^k\) and sends them to the prover.
+The prover computes \(s_0\gets \rho - c_0\alpha, s_1\gets \rho - c_1\alpha\).
+This step is the main difference to the original Schnorr protocol: the verifier selects two challenges and the prover computes two responses --- but still only \emph{one nonce}, \(\rho\).
 This is also different from the original Brands-Chaum protocol, in which the 
@@
 
-In the \ac{DB} phase, the prover notifies the verifier that he has computed 
-\(s_1, \dotsc, s_m\).
-The verifier chooses one of the challenges, \(i\), uniformly randomly and sends 
-it as a challenge to the prover and starts measuring the time of flight.
-The prover replies with \(s_i\).
-The verifier stops the measurement and verifies that \(R = g^{s_i}A^{c_i}\) and 
-that the time of flight was within \(t_{\max}\) (determined from the allowed 
-  distance).
+We let \(|q| = \ceil{\log_2 q}\) denote the length of \(q\) in bits.
+The verifier will request all \(|q|\) response-bits from one challenge (say 
+\(s_b\)) and only \(0 < l\leq |q|\) from the other (\(s_{1-b}\)).
+Then the verifier can authenticate the prover by checking if \(R = 
+  g^{s_b}A^{c_b}\).
 
-This protocol must be repeated \(n\) times.
+\subsection{Security analysis}
 
-\subsection{\Acl*{ZK} and \acl*{PK}}
-
-The main difference between this protocol and the Schnorr protocol is that we 
-have the prover compute responses for \(m\) different challenges, \(c_1, 
-  \dotsc, c_m\).
-However, in the authentication step, the verifier chooses only one of those 
-challenges.
-From the simulator's (and extractor's) perspective, there is no difference 
-whether the verifier first chooses \(m\) and then chooses one of those \(m\) 
-challenges, or if the verifier chooses the one challenge directly;
-the distribution is the same, \(\frac{m}{n}\times \frac{1}{m} = \frac{1}{n}\).
-Therefore the standard proof for Schnorr as a malicious-verifier \ac{ZKPK} 
-protocol with soundness error \(2^{-l n}\) still 
-holds~\cite[\eg][]{OnSigmaProtocols}.
-(We note that \(l\), which is also the length of the challenge bit string, must 
-be logarithmic in the security parameter, \(\lambda\), for a malicious 
-verifier.)
-
-\subsection{\acs*{DBMF}, \acs*{DBDH} and \acs*{DBTF} resistance}
+The prover must know the responses for both challenges to successfully pass the \ac{DB} phase.
+The reason for the two challenges but only one random nonce is that knowing the responses to both means learning \(\alpha\).
+This allows us to prevent \ac{DBTF}.
+Bundling the authentication into the distance-bounding phase (difference from Brands-Chaum) prevents \ac{DBDH}, and both adaptations together aim at \ac{DBMF} resistance.
+%reducing success of MF according to number of repetitions.
+The reason we use secret sharing and not \(s_b\) directly, is to bound the \(l\) bits the verifier must learn of \(s_{1-b}\).
+Without secret sharing, the verifier learns \(l\) bits of \(s_{1-b}\), but with secret sharing the verifier learns \(l\) bits of \emph{one share}.
+Thus, we still have information theoretic security for \(s_{1-b}\) although we reveal the \(l\) bits.
 
 The intuition behind the protocol security is as follows.
-The prover must know the responses for all challenges to successfully pass the 
-\ac{DB} phase.
-The reason for having several challenges but only one random nonce is that 
-knowing at least two responses means learning the secret~\(\alpha\).
-This gives us the incentives that prevent \ac{DBTF}.
-(We also need it for \ac{DBMF}.)
-Bundling the authentication into the distance-bounding phase (difference from 
-Brands-Chaum) prevents \ac{DBDH}.
-We do not consider \ac{DBDF} here; since the prover knows the key~\(\sk\), she 
-can do \iac{DBEDLC} attack to reduce the distance.
-(We will solve this problem further down.)
-However, the properties of \(\UWBPR\) and the unpredictability of the 
-challenges ensures \ac{DBMF} resistance (since then the prover is honest).
+To achieve malicious-verifier zero-knowledge, choose \(k\) logarithmic in the security parameter \(\lambda\) and repeat the protocol \(n\) times, such that 
+the knowledge error, \(2^{-kn}\), becomes small enough.
+Repeating the protocol is also needed to decrease the success probability of some of adversaries presented below.
 
-The \(\UWBPR\) prevents \iac{DBMF} adversary from performing a 
-distance-reduction through \iac{DBEDLC} attack~\cite{UWBPR}.
-Thus, any relaying will be detected, \ie this justifies \cref{TaintedMF}.
+The \ac{DB} phase protects against distance fraud.
+Once the prover has received \(l+1\) challenges set to \(b\), it knows that the remaining challenges must also be \(b\).
+\Iac{DBDF} prover must thus wait for the challenge bit \(b_i\) before responding with \(r_i\) for \(l+1\) challenges.
+Thus, the probability of successfully guessing the order of the challenge bits is \(2^{-(l+1)}\) per round or, in total, \(2^{-(l+1)n}\).
 
-\daniel{Still intuition, we need to use the formal definition of security 
-  above.}
-\begin{theorem}[\acs*{DBMF} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
-  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
-  where \(m, q\) are as in \cref{DB-Schnorr}.
-\end{theorem}
+The \ac{DB} phase also ensures that \iac{DBMF} adversary will fail the \ac{DB} phase for at least one round.
+The verifier will send \(|q| + l < 2|q|\) challenges.
+By replying, the prover reveals \(|q|+l\) bits distributed over \(s_0, 
+  s_1\).
+\emph{We assume} that learning \(\ceil{(|q|+l)/2}\) bits of \(s_0\) and 
+\(\floor{(|q|+l)/2}\) bits of \(s_1\) yields no advantage for the adversary.
+Now, the adversary has two options.
+First, the adversary can buffer \(l\) bits of both \(s_0^{(0)}\concat s_0^{(1)}, s_1^{(0)}\concat s_1^{(1)}\) by requesting them from the prover.
+However, at this point the adversary must wait for the challenge bit \(b_{l+1}\) from the verifier and then relay that challenge to the prover to receive the correct \(r_i\) --- this relay will be detected.
+The alternative is to guess \(b\) and extract \(s_b\) for this challenge from the prover.
+Guessing \(b\) yields \(1/2\) probability that the \ac{DBMF} adversary will guess it correctly.
+Since we must execute the protocol \(n\) times, the probability to pass all these rounds is reduced to \(2^{-n}\).
+If the adversary requests \(s_b\) in full, the adversary can also guess the 
+remaining \(|q|-l\) bits of \(s_{1-b}\).
+Based on our assumption above, the probability of guessing these bits 
+successfully is \(2^{-(|q|-l)}\).
+Thus the success probability of the \ac{DBMF} adversary is \emph{at most} 
+\(2^{-n}+2^{-(|q|-l)n}\).
 
-\begin{proof}
-  The adversary has two options:
-  \begin{enumerate*}
-  \item guess which challenge the verifier will use and request the correct 
-    response from the prover, this yields success with probability 
-    \(\frac{1}{m}\);
-  \item guess the response, this yields success with probability 
-    \(\frac{1}{q}\).
-  \end{enumerate*}
-  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
-  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
-  session.
-\end{proof}
+The protocol is \ac{DBTF}-resistant. 
+Indeed, if the malicious prover gives both responses to the accomplice, the accomplice can compute his secret key.
+The probability of success of \ac{DBTF} is thus reduced to guessing \(b\), \ie \(1/2\) per round or, in total, \(2^{-n}\).
 
-The protocol is also secure against distance hijacking due to the fact that the 
-authenticating bit string is used during the \ac{DB} phase, not the challenge 
-bit string, as is the case for the original protocol of Brands-Chaum.
-\Ac{DBDH} requires that the adversary finds a collision between his response 
-and that of the honest prover.
-Thus the probability of success is equivalent to a collision for the responses 
+The protocol is also secure against distance hijacking due to the fact that the authenticated bitstring is used during the \ac{DB} phase, not the challenge bitstring as it is the case for the original protocol of Brands-Chaum.
+Thus the probability of success is equivalent of a collision for the responses 
 for the chosen challenge --- in each round.
 
-\daniel{Still intuition, we need to use the formal definition of security 
-  above.}
-\begin{theorem}[\acs*{DBDH} resistance]
-  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-DH adversary, then 
-  \(\Adv_{DBS}^{\text{DH}}(\adv) = \frac{1}{q^n}\).
-\end{theorem}
+Finally, it follows from the original Schnorr protocol that this is still \iac{PK} and \ac{ZK}.
+\daniel{I should prove this for the composed protocol, I should check the details with Douglas.}
 
-\begin{proof}
-  The honest prover will choose \(\rho\) such that \(R = g^\rho\).
-  The adversary can send his own \(R' = g^{\rho'}\) to the verifier, or let 
-  \(R' = R\) to not interfere.
+\subsection{Formal Verification}
 
-  The verifier will choose \(c_1, \dotsc, c_k\).
-  The adversary can send his own \(c_1', \dotsc, c_k'\) to the prover, or let 
-  \(c_1' = c_1, \dotsc, c_k' = c_k\) to not interfere.
+We wanted to formally verify the protocol security properties. To realize this, 
+we used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include 
+originally the possibility to reason on time and space in its model.
+However, thanks to a recent work by \textcite{TamarinDB}, all the common 
+properties mentioned in the previous subsection can be equivalently 
+characterized with a causality-based definition relying only on the order of 
+messages.
 
-  The verifier will send its challenge \(i\), the prover will reply with \(s_i 
-    = \rho - c_i' \alpha\).
-  The verifier will check that \(R' = g^{s_i} A^{c_i}\).
+The whole Tamarin code we wrote is provided in \cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that we have made. 
+It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.
 
-  This yields that \(R' = g^{\rho'}\) should equal \(g^{s_i} A'^{c_i} = g^{\rho 
-      - c_i' \alpha} (g^{\alpha'})^{c_i} = g^{\rho - c_i' \alpha + c_i 
-      \alpha'}\).
-  Both \(\rho\) and \(\alpha\) are unknown to the adversary and the adversary 
-  cannot choose \(c_i\).
-  The adversary needs \(\rho' = \rho - c_i' \alpha + c_i \alpha'\).
-  Let \(\rho'\) and \(c_i'\) be fixed (say 0), then we have that \(\alpha' = 
-    \rho c_i^{-1}\).
-  We thus have that
-  \(\Adv_{\DBS}^{\text{DH}}(\adv) = \Prob{\rho' - c_i \alpha' = \rho - c_i' 
-      \alpha} = \frac{1}{q}\),
-  which concludes the proof.
-\end{proof}
-
-The last property is \ac{DBTF}.
-The protocol is \ac{DBTF} resistant.
-Indeed, if the malicious prover gives both responses to the accomplice, the 
-accomplice can compute his secret key.
-And any help will increase the probability of success of future attempts.
-
-\daniel{Still intuition, we need the formal definition of security above.}
-\begin{theorem}[\acs*{DBTF} resistance]
-  \dots
-\end{theorem}
-
-\begin{proof}
-  Assume that there is an algorithm~\(\adv\) that can authenticate without the 
-  provers help with non-negligible advantage~\(\epsilon < \frac{1}{2}\), \ie 
-  the success probability is \(\frac{1}{2}+\epsilon\).
-  The probability that \(\adv\) predicts the challenge is \(\frac{1}{2}\).
-  Since \(\epsilon\) is non-negligible, there is some case for which \(\adv\) 
-  knows both responses.
-  In that case \(\adv\) can simply compute the secret and impersonate with 
-  probability \(1\) forever, which contradicts our assumption about 
-  \(\epsilon\).
-\end{proof}
-
-\subsection{\Iacs*{DBDF} resistant protocol}
-
-\Acl{DB} protocols requires hardware implementations.
-We will use a trusted hardware implementation to overcome the limitation of 
-\textcite{UWBPR}, \ie that the prover and verifier be mutually trusted.
-We will need \iac{PKI} for the verifier to verify the trusted hardware.
-We will leverage this \ac{PKI} to overcome the shared-key requirement.
-With \iac{PKI} based on discrete logarithms we will be able to perform \iac{DB} 
-\ac{ZKPK} which \emph{simultaneously} proves
-\begin{enumerate*}
-\item that the protocol is run by trusted hardware,
-\item that that trusted hardware is within proximity,
-\item that some \ac{ZKPK} statement about some discrete logarithms holds, and
-\item that that knowledge is within proximity.
-\end{enumerate*}
-
-We will now introduce an extended protocol, \(\DBSHW\), which represents the 
-secure hardware implementation.
-\Cref{DBSHW-overview} presents an overview.
-
-\begin{figure*}
-  \centering
-  \small
-  \setlength{\ProtoArrowLength}{0.07\linewidth}
-  \begin{tabular}{p{0.40\linewidth}cp{0.40\linewidth}}
-    \(\HWprove[g, q, \alpha]\):
-    & &
-    \(\HWverify[g, q, A]\):
-    \\
-    \midrule
-
-    Static \(\sk_P, \cert_P\colon \pk_P = \hat g^{\sk_P}\)
-    &
-    & \(\sk_V, \pk_V = \hat g^{\sk_V}\)\\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Pre-setup, authenticated key agreement}} \\
-
-    \(\cert_P\)
-    & \(\ProtoSendRight{\cert_P}\)
-    & \(k \gets \pk_P^{\sk_V}\)
-    \\
-
-    \(k \gets \pk_V^{\sk_P}\)
-    & \(\ProtoSendLeft{\pk_V}\)
-    & \(\pk_V\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Setup}} \\
-
-    Load \(k\) into \(\UWBPR\)
-    &
-    & Load \(k\) into \(\UWBPR\)
-    \\
-
-    \(\rho, \hat\rho \rgets \ZZ_q, R\gets g^{\rho}, \hat R\gets g^{\hat\rho}\)
-    & \(\ProtoSendRight{R, \hat R}\)
-    & \(\hat A\gets \pk_P\)
-    \\
-
-    \(s_1\gets \rho - c_1\alpha \pmod q\)
-    & \(\ProtoSendLeft{c_1, \dotsc, c_k}\)
-    & \(c_1\rgets \bin^l, \dotsc, c_m\rgets \bin^l\)
-    \\
-
-    \(\hat s_1\gets \hat\rho - c_1\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \vdots
-    &
-    &
-    \\[-1em]
-
-    \(s_m\gets \rho - c_m\alpha \pmod q\)
-    &
-    &
-    \\
-
-    \(\hat s_m\gets \hat\rho - c_m\sk_P \pmod q\)
-    &
-    &
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Distance-bounding}} \\
-
-    \text{Ready}
-    & \ProtoSendRight{\text{Ready}}
-    & \\
-
-    % null
-    & \(\ProtoSendLeft{i}\)
-    & \(i\rgets \{1, \dotsc, m\}\), start clock
-    \\
-
-    Fetch \(s_i, \hat s_i\)
-    & \(\ProtoSendRight{s_i, \hat s_i}\)
-    & Stop clock, record \(\Delta t\)
-    \\
-
-    \midrule
-    \multicolumn{3}{c}{\textbf{Verification}}
-    \\
-
-    % null
-    &
-    & Accept if \(R = A^{c_i} g^{s_i}\), \(\hat R =  \hat A^{c_i} \hat g^{\hat 
-        s_i}\) and \(\Delta t < t_{\max}\).
-    \\
-
-  \end{tabular}
-  \caption{%
-    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
-    \(\PK[\alpha][A = g^\alpha]\).
-    Each transmission (arrow in the diagram) uses \(\UWBPR\).
-    The protocol actually proves \(\PK[\alpha, \sk_P][A = g^\alpha \land
-      \hat A = \hat g^{\sk_P}]\).
-    This is for the device to prove knowledge of the key~\(\sk_P\) to prevent 
-    \ac{DBTF}.
-    The protocol should be repeated \(n\) times to achieve the desired 
-    soundness and distance-bounding errors.
-  }%
-  \label{DBSHW-overview}
-\end{figure*}
-
-The \(\DBSHW\) secure hardware device must contain a (static) private 
-key~\(\sk_P\) (for the prover, \(\sk_V\) for the verifier) with a digital 
-certificate~\(\cert_P\) (and \(\cert_V\)) for the public key~\(\pk_P\) (and 
-\(\pk_V\)).
-
-\paragraph*{Pre-setup}
-
-The pre-setup phase consists of an authenticated key agreement.
-We use the static \ac{DHKE} to simplify the explanation, any authenticated key 
-agreement protocol based on discrete logarithms can be used.
-The prover and verifier exchange certificates, \(\cert_P\) and \(\cert_V\), and 
-compute the agreed key~\(k = \pk_V^{\sk_P} = \pk_P^{\sk_V}\).
-If the prover's certificate is invalid, the protocol aborts.
-
-\paragraph*{Setup}
-
-The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
-\(\DBS\) performs \(\PK[\alpha][A = g^\alpha]\) whereas \(\DBSHW\) must perform 
-\(\PK[\alpha, \sk_P][\hat A = g^\alpha \land \hat g^{\sk_P}]\).
-They use the agreed upon key~\(k\) as the key for \(\UWBPR\).
-
-The prover chooses \(\rho, \hat\rho\rgets \ZZ_q\) and computes \(R\gets 
-  g^\rho\) and \(\hat R\gets \hat g^{\hat\rho}\).
-The verifier computes \(\hat A\gets \pk_P\).
-
-The verifier chooses \(m\) challenges of length \(l\), \(c_1\rgets \bin^l, 
-  \dotsc, c_m\gets \bin^l\), and sends these to the prover.
-The prover computes responses~\(s_i\gets \rho - c_i\alpha\) and \(\hat s\gets 
-  \hat\rho - c_i\sk_P\) for \(i\in \{1, \dotsc, m\}\).
-
-\paragraph*{Distance bounding}
-
-The verifier decides which of the \(m\) challenges to use, \(i\rgets \{1, 
-  \dotsc, m\}\), sends its decision~\(i\) to the prover and starts its clock.
-The prover instantly replies with the pre-computed \(s_i, \hat s_i\).
-Note that \(s_i, \hat s_i\) must be sent as a concatenation in \emph{one} 
-\(\UWBPR\) reply.
-The verifier stops the clock and records the round-trip time~\(\Delta t\).
-
-\paragraph*{Verification}
-
-The verifier checks if \(R = \hat A^{c_i} g^{s_i}\) and that \(\hat R =
-  \hat g^{\hat s_i}\) and that the round-trip time \(\Delta t < t_{\max}\) does 
-not exceed the limit~\(t_{\max}\).
-
-\subsection{\acs*{DBDF} resistance}
-
-This protocol uses the \ac{DBMF} resistance of \(\DBS\) to ensure \ac{DBDF} 
-resistance against a malicious prover.
-The trusted hardware uses the authenticated key agreement to establish the 
-shared secret \(k\), thus a verifier prevents a malicious prover from learning 
-\(k\) --- the main limit of~\cite{UWBPR}.
-
-The hardware device (\DBSHW) could commit \ac{DBTF}\footnote{%
-  Arguably, this should not be an issue since the device is trusted.
-  However, we include this construction because it is a neat way to provide 
-  \ac{DBTF} resistance for this part of the protocol as well.
-  To not have this feature, one simply adds the authenticated key exchange step 
-  to \cref{SchnorrFigure}.
-} by giving the key~\(k\) to a malicious prover --- this would allow that 
-prover to authenticate once.
-To prevent this possibility we include a proof of knowledge of the device's 
-private key~\(\sk_P\), \ie that \(\pk_P = \hat g^{\sk_P}\).
-This way, an accomplice can only pass if he is given both \(k\) and \(\sk_P\).
-
-\subsection{Formal verification}
-
-We formally verified these properties with Tamarin~\cite{meier2013tamarin}.
-Thanks to recent work by \textcite{TamarinDB}, all the common properties for 
-\ac{DB} protocols (except \ac{DBTF}) can be characterized with a 
-causality-based definition relying only on the order of messages.
-The whole Tamarin specification for our protocol is provided in 
-\cref{apdx:tamarin-spec}, with a short discussion of the modeling choices that 
-we have made.
-It contains a specification of the distance-bounding protocol described 
-previously, a definition of the soundness and correctness properties that 
-ensure the protocol actually produces the expected result, and a definition of 
-the security properties we want to ensure.
+Tamarin's auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties.
+This means that no trace violating the security properties is found, but the prover cannot conclusively validate that the desired properties are true. 
+We are currently investigating the Tamarin interactive mode to validate as well the security properties.

### 2021-06-16 paper/system-model.tex
Merges system model into definitions section
Just say we want Sybil proofness; no more, no less.

--- 2020-04-16 paper/system-model.tex
@@
-\section{System model}%
-\label{system-model}
-
-To set the stage, we will now describe our system model including
-assumptions and a summary of the desired properties for crowd
-counting% and the adversary model
-.
-
-\subsection{Model and assumptions}%
+\subsection{System model and assumptions}%
 \label{assumptions}
@@
   do.
-  The \ac{CA} can be centralized or decentralized, but as 
-  \textcite{SybilAttack} points out, the \ac{CA} must be \emph{logically 
-    centralized} to prevent Sybil attacks.
 } that ensures a one-to-one mapping between an identity and a cryptographic 

### 2021-06-16 paper/distance-bounding.tex
Shortens DB section in building blocks

--- 2021-06-14 paper/distance-bounding.tex
@@
 
-There are four adversaries for \ac{DB} protocols established in the literature, 
-each of which tries to commit a type of fraud.
-These can be summarized as follows:
-\begin{itemize}
-  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
-  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
-    possibly honest, prover who is far away from the verifier.
-    (Also known as relaying attack or man-in-the-middle attack.)
-  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
-    who is close to the verifier, to authenticate.
-    \Ac{DBTF} resistance is a very strong property; it implies that if the 
-    verifier accepts the accomplice with non-negligible probability the 
-    accomplice can compute the prover's secret key\footnote{%
-      This means that even things like functional encryption will not
-      help the adversary.
-    }.
-  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
-    uses an unsuspecting honest prover close to the verifier to pass as being 
-    close.
-    (This is different from \ac{DBMF} in that the honest prover actually tries 
-    to authenticate to the verifier, but the malicious prover hijacks the 
-    channel at some point(s) during the protocol.)
-\end{itemize}
-% There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.
-
-% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
-% Indeed, in this context it does not make sense to protect against the
-% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
-% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
-Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
+Our setting requires a public-key \ac{DB} protocol with a \emph{malicious 
+verifier} who will potentially try to \emph{impersonate the prover}.
 The verifier might also try to track the provers and map their identities to 
@@
 \ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
-For this paper, we assume the existence of such a protocol.
 There exists one such protocol in the literature, namely one by 

### 2021-06-16 paper/protocol.tex
Makes subfigures tiny to fit next to each other
Updates data in adversary model
Clarifies intro to protocol

@@
   disseminated it to others.
+  Anyone can do this, but in general, there is only one organizer.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
@@
 \end{enumerate}
-In general, there is one organizer and every participant can act as
-either or both protester and witness.
-
-After the protest, anyone can count the number of participants (of the protest and the
-protocol) and verify anyone else's count given the relevant meta data
-(which protest, location, time, and witness parameters used in the
+After the protest, anyone can be a verifier (universal verifiability, 
+\cref{security-properties}), \ie count the number of participants (of the 
+protest and the protocol) or verify anyone else's count given the relevant meta 
+data (which protest, location, time, and witness parameters used in the
 count). We refer to anyone counting or verifying a count as the
@@
 \item the participation count, \ie the cardinality of 
-  \(\prfs_\prtst^{\str,\theta}\).
+  \(\prfs_{\prtst}^{\str,\theta}\).
 \end{enumerate*}

### 2021-06-16 paper/protocol.tex
Clarifies protocol intro further

@@
 After the protest, anyone can be a verifier (universal verifiability, 
-\cref{security-properties}), \ie count the number of participants (of the 
-protest and the protocol) or verify anyone else's count given the relevant meta 
-data (which protest, location, time, and witness parameters used in the
+\cref{UniversalVerif} in \cref{verifiability-properties}), \ie count the number 
+of participants (of the protest and the protocol) or verify anyone else's count 
+given the relevant meta data (which protest, location, time, and witness 
+parameters used in the
 count). We refer to anyone counting or verifying a count as the
 verifier; the process is the same.
+
+Any participant can verify their inclusion (individual verifiability, 
+\cref{IndividualVerif} in \cref{verifiability-properties}) by repeating the 
+count (the verification process) but also checking that their proof is included 
+while counting.
 

### 2021-06-17 paper/protocol-trusted.tex
Minor clarification for trusted protocol intro

@@
   disseminated it to others.
-  Anyone can do this.
+  Anyone can do this, but in general, there is only one organizer.
 \item A \emph{protester} is attending the protest and asks witnesses to vouch 
@@
 \end{enumerate}
-In general, there is one organizer and every participant can act as
-either or both protester and witness.
-
 Anyone can be a verifier (we required universal verifiability, 

### 2021-06-17 paper/protocol-trusted.tex
Clarifies intro to trusted protocol

@@
 The verifier can publish, \eg in a news paper, the final count together with 
-the cause, time and location and anyone can verify this count (by the same 
-procedure).
+the cause, time and location and anyone can verify this count (by repeating the 
+same procedure).
+Any participant can confirm their inclusion by repeating the count and checking 
+that their proof is included.
 

### 2021-06-17 paper/protocol-trusted.tex
More clarifications to trusted protocol

@@
 This is only done once\footnote{%
-  It is repeated when the credential expires, in analogy to a passport in terms 
-  of expected intervals.
+  It is repeated when the credential expires, in analogy to a passport that 
+  must be renewed at regular intervals.
 }.
@@
 During the registration phase, each participant
-generates a secret key~\((k, r)\) and
+generates a secret key~\(\sk = (k, r)\) and
 obtains a signature on it by the \ac{CA} \emph{but without revealing it} to the 
-\ac{CA} (or to any part thereof in a decentralized \ac{CA} scenario).
+\ac{CA}.
 At the end, each participant will have a signed secret key while the \ac{CA} 
@@
 postpone those extra computations while potentially running on battery.
+(Remember, the witness is assumed trusted.)
 

### 2021-06-17 paper/protocol-untrusted.tex
Clarifications to untrusted protocol

@@
 \) The protester also fetches a time-correlated random value, \(t_s\), from 
-\(\TS\), \(t_s\gets \TSget\).
+\(\TS\); \(t_s\gets \TSget\).
 
@@
 In other words, anyone who does the counting can choose the eligibility
-criteria (time interval, location, number of regular or trusted
-witnesses, who is considered to be a trusted witness) for their own count.
+criteria (time interval, location, number of trusted or untrusted witnesses, 
+who is considered to be a trusted witness) for their own count.
 As long as \emph{these assumptions/criteria are published along with the 
@@
 verifiers may be tempted to make extreme choices, but they will have to publish 
-those choices and lose credibility. Reasonable verifiers on the other hand will 
-try to find a good middle-ground that counts all legitimate protesters while 
-being resistant to isolated malicious agents.
+those choices and lose credibility. Reasonable verifiers, on the other hand, 
+will try to find a good middle-ground that counts all legitimate protesters 
+while being resistant to isolated malicious agents.
+However, what exactly this choice would be is out of scope and, in fact, would 
+fall under a different area of research.
 

### 2021-06-17 paper/privacy-analysis.tex
Updates data in adversary model
Clarifies privacy analysis

@@
 However, there are more data than \(\pid, \wid\) used in the protocol.
-The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
+The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_{\pid}, 
+\corr_{\wid}\).
 The cause identifier \(\cid\) will be used for all proof shares
 pertaining to the same protest and thus it cannot be used to uniquely
-identify any individual. The location \(l\) is coarse enough so that many non-overlapping 
-\((\pid, \wid)\)-pairs use the same location.
+identify any individual. The location \(l\) must be coarse enough so that many 
+non-overlapping \((\pid, \wid)\)-pairs use the same location.
 After all, it is the location of the protest, not the location within the 
 protest that matters.
-Thus \(l\) is not uniquely identifying any individual protester or witness.
+Thus \(l\) can be made to not uniquely identify any individual protester or 
+witness.
 Likewise, thanks to the constraints in the time-stamp granularity 
-(\cref{timestamp}), \(t\) is not uniquely identifying either.
+(\cref{timestamp}), \(t\) can be made to not uniquely identify either.
 

### 2021-06-17 paper/verifiability-analysis.tex

@@
 Relaying the communication is an attack against the \ac{DB} protocol.
-We assumed \iac{DB} protocol with \ac{DBTF} resistance (the most relevant 
-property for this situation), so Alice cannot succeed with more than negligible 
-probability.
-(\Ac{DBDF} is captured by \ac{DBTF} in this case, as in \ac{DBTF} she has a 
-colluder.
-\Ac{DBMF} would prevent Alice from relaying unsuspecting bystanders' 
-communication to witnesses.
-\ac{DBDH} is not really useful to Alice in this situation.)
+Due to the construction of \textcite{DB-Schnorr}, Alice cannot succeed with 
+more than negligible probability.
 

### 2021-06-17 paper/performance.tex
Add comment on Idemix being based on CL as us

--- 2020-05-08 paper/performance.tex
@@
 \section{Performance}%
-\label{performance}
+\label{PerformanceAnalysis}
 
-We will now review the performance of the proposed protocols.
-Since the construction is designed as a drop-in replacement for the Schnorr 
-identification-scheme~\cite{Schnorr} as \iac{ZKPK} protocol, we will focus on 
-how much we must \enquote{pay} for the \ac{DB} property.
+\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}
 
-\paragraph*{Mutual trust}
+Performance considerations are crucial during the protests due to the nature of 
+the devices used to run \CROCUS, which are resource-constrained in terms of 
+energy, storage and computational power, and are operating on limited network 
+capacity.
 
-We start with the mutual-trust version of the protocol in \cref{DB-Schnorr-UWB} 
-(see \cref{DB-Schnorr-UWB-figure}).
+\subsection{Smartphones and smartcards}
 
-In \emph{one round} of the protocol, the cost of the verifier is that of 
-generating \(m\) number of \(l\)-bit strings, instead of only one.
-This costs the verifier a factor \(m\) of randomness.
-The cost of the prover is that of computing \(m\) number of replies (\(s\gets 
-\rho - c \alpha \mod q\)), instead of only one.
+Recent technological progress has enabled the deployment of advanced 
+cryptographic primitives on smartcards and smartphones that could be used to 
+implement our solution.
+For instance, benchmarks~\cite{Benchmarking} have shown that Android devices 
+are now fast enough to efficiently implement \acp{PET}, with a Samsung Galaxy S 
+i9000 (back in 2014) able to execute Idemix\footnote{%
+  Idemix is based on CL anonymous credentials, same as our scheme.
+} in \SI{153}{\milli\second}. However, those benchmarks also demonstrate that 
+smartcards remain slow to process complex protocols such as Idemix or U-Prove 
+(taking between \SI{4}{\second} and \SI{8}{\second} to process them). While the 
+limited processing power of many embarked systems has been a challenge, Idemix 
+has been successfully implemented to prove the possession of credentials on 
+Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA 
+project, released in 2014, aimed to achieve an implementation ``suitable for 
+real life transactions''~\cite{IRMA} while maintaining security and privacy for 
+its users.
 
-To achieve security, the protocol must be repeated \(n\) times.
-We have the \(l\)-parameter which controls the soundness of the \ac{ZKPK} and 
-the \(m\)-parameter controls the soundness of the \acl{DB}.
-If we want to achieve 80 bits of security, we can let \(l = m = 6\) (remember, 
-\(l\) must be logarithmic in the security parameter) and \(n = 14\).
-This makes \acl{DB} a factor \(6\) more expensive over the 
-\emph{malicious-verifier secure} Schnorr protocol.
+With respect to its implementation, \CROCUS is very similar to the 
+implementation of Anon-Pass~\cite{AnonPass}, an anonymous subscription system 
+in which a long-term credential can be used to derive a single login for any 
+authentication window (\ie epoch) such that logins are unlinkable across 
+different epochs.
+In particular, the setup and registration phases are almost identical.
+The evaluation conducted by \textcite{AnonPass} used as server a Dell Optiplex 
+780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses 
+Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz 
+Intel Core 2 CPU but with only 4 GB of RAM\@.
+The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
+This is typically the type of pairing that could also be used with \CROCUS\@.
+Not counting the setup that is performed once by the \ac{CA}, the time reported 
+for the registration on the server (\ie \ac{CA}) side is 
+\SI{19.8}{\milli\second} while it is \SI{23.4}{\milli\second} on the client 
+side.
+With respect to joining and participation phases, with the exception of the 
+distance-bounding they are actually quite similar to the login protocol of 
+Anon-Pass in which the time required to create a message for a protester would 
+be around \SI{13.5}{\milli\second} while the time needed for the witness would 
+be only \SI{7.9}{\milli\second}.
 
-\paragraph*{\acs*{PKI}}
+%\subsection{Distance bounding}
+%
+%The distance-bounding chips~\cite{3db-access} currently available on the market 
+%can already enable proofs of proximity for any range of up to 
+%  200 meters.
+%One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
+%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
+%More precisely, they have proposed three different implementations of the 
+%Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic 
+%implementation running at the application layer to an advanced one running in 
+%RFID-emulation mode. The results obtained already show that a relay attack can 
+%be detected if the adversary introduces a delay of more than 1.5 ms when 
+%performing such an attack (most of the existing attacks introduce delays of at 
+%least tens of milliseconds).
 
-The \ac{PKI} version of the protocol (\cref{DB-Schnorr-PKI,DBSHW-overview}) 
-performs one signature verification and four additional proofs in parallel.
-The cost for the verifier is one signature verification in addition to the 
-factor \(m\) of randomness used.
-On the prover side, we have the computations for the signature verification and 
-four additional proofs in parallel, this changes the cost to a factor of \(5m\) 
-for the prover: the prover must compute \(s_i = \rho - c_j \alpha_i\) for 
-\(i\in \{1, \dotsc, 5\}, j\in \{1, \dotsc, m\}\).
+% With respect to the distance-bounding protocol we have proposed, the initial prover phase can be split in two parts: (1) the setup phase during which $g$, $q$ and $\alpha$ are generated and $A$ is computed and (2) the online phase during which $\theta$ and $R$ are generated.
+% The first step is only done once and while being fairly costly in terms of ressources, the corresponding results can be precomputed and store them on the prover's device. 
+% This method is commonly found in Schnorr variants in order to save time on multiple instances of the protocol.
+%Seb: to do add the reference to the following paper at the end of the sentence:
+%[1] Chin, J. J., Tan, S. Y., Heng, S. H., & Phan, R. C. W. (2015). Twin-Schnorr: a security upgrade
+%for the schnorr identity-based identification scheme. The Scientific World Journal, 2015.
+% Considering the entire setup of the DB protocol, it requires in its basic version to generate seven random numbers (one of them being a single bit), and also perform two modular exponentiations ($A$ and $R$), two multiplications and two substractions (when computing $s_0$ and $s_1$).
+% However, this can be reduced to four random number generations and one exponentiation using precomputation.
 
-The cost of the signature is the same as for Anon-Pass~\cite{AnonPass}, which 
-implements a public transport pass using this signature scheme.
-The signature need not be reverified \(n\) times, it is sufficient to verify 
-that once and reuse the same blinding for all \(n\) repetitions of the 
-protocol.
-Thus it is only the \acl{PK} that must be rerun \(n\) times.
+%\paragraph{Threshold of witnesses.}
+%Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+%Then it would be reasonable to set the threshold of at least 6000 witnesses.
+%According to the Anon-Pass performance measures~\cite{AnonPass} each witness 
+%signature would require \SI{8}{\milli\second} per core on a quad-core Intel 
+%\SI{2.66}{\giga\hertz} Core 2 processor.
+%This yields \(
+%  \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+%  \SI{48}{\second}.
+%\) of processing.
 
-\paragraph*{Bit-by-bit}
+\subsection{Witness processing}
 
-The traditional bit-by-bit version of the protocol 
-(\cref{DB-Schnorr-nbit,DB-Schnorr-nbit-figure}) is not as efficient.
-That is due to \(m = 2\) being fixed in this case (there are only two responses 
-to choose from), and consequently, we must have a larger value for \(n\) to 
-achieve the desired security.
+As above, assume we have one trusted witness.
+A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
+3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
+\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
+maximum \SI{200}{\metre}).
+Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
+(\SI{120}{\metre} radius), which fits 137018~protesters according to 
+\textcite{2016DemonstrationsInSeoul}.
+It would take this witness \SI{5.8}{\hour} to witness all of them.
+Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
+witnesses.
+
+\subsection{Ledger (blockchain) efficiency}
+
+For the example of 1\,000\,000 participants, with trusted witnesses, each 
+participant only needs to acquire one proof share from a trusted witness.
+Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
+If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.
+
+%If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
+%While this already takes longer than counting votes in national elections, the threshold is still very low. 
+%% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
+%% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
+%% In addition to the ledger computation, we need to consider the creation of the proof shares.
+\sonja{added the previous sentence to explain why anonpass shows up here.
+Shouldn't that be in the performance section?
+}
+%% %Seb: I agree maybe we should move it to the previous subsection
+%% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
+%% This yields \(
+%%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
+%%   \SI{48}{\second}.
+%% \) of processing. 
+%For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
+%Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
+
+%\subsection{Blockchain efficiency}
+
+\sonja{removed for now: One problem can arise in the case in which there is no trusted witnesses.
+In this situation, if we set the threshold too high, we need to submit more proof shares than the blockchain can handle within a reasonable time.}
+
+%assumptions about smartphones:
+%(This means that we essentially provide a lower bound for the participation 
+%count, since some participants might not have such a device.)
+%Sonja says: is this still true? Given mafia fraud we can't guarantee
+%that, right?

### 2021-06-17 paper/performance.tex

@@
 \SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
-maximum \SI{200}{\metre}).
+maximum \SI{200}{\metre})\footnote{%
+  These numbers are representative of what \textcite{DB-Schnorr} use for 
+  underlying communication technology.
+}.
 Then a witness fixed in one position can cover \SI{45216}{\square\metre} 

### 2021-06-17 paper/conclusions.tex

--- 2020-07-03 paper/conclusions.tex
@@
 
-In this paper, we have adapted the Schnorr protocol as \iac{DB} protocol.
-It allows us to construct \ac{DB}, general attribute-based authentication; more 
-general attributes than provided by previous \ac{DB} ones.
-With our contribution, Alice can now prove more complex statements to Bob; \eg 
-that she is older than 18 (without revealing her actual age), has a cinema 
-subscription which is not \enquote{double spent} by someone else at the same 
-time~\cite[\eg][]{AnonPass} and, at the same time, Bob can be sure that Alice 
-is not just relaying messages from her older sister Carol or \ac{DBMF} relaying 
-the subscription from some unsuspecting stranger also waiting in the queue to 
-enter.
+In this paper, we have introduced \CROCUS, a privacy-preserving protocol for verifiably counting participants at protests.
+
+We showed that \CROCUS provides universally verifiable data.
+With \CROCUS, a journalist can easily count the participation, specify how they 
+counted (time, location \etc) along with the result and everyone can 
+independently verify that the result is correct.
+%The only results that cannot be trusted are results aligned with the interests 
+%of the \ac{CA} (which can be mitigated by multi-party solutions).
+
+Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest, with the following caveat.
+Grace, the government in our protest scenario, can coerce Alice in some way to reveal her private key and then use it to verify her participation.
+However, this requires that Grace already suspects Alice --- Grace cannot check everyone --- and that Alice has not renewed her digital certificate.
+
+% Given the conflict between verifiability and receipt-freeness when counting presence, any digital trace needed for verifiability could conceivably be used to substantiate a claim that was by itself weaker.
+For instance if there is auxiliary information that points to a person having participated in a protest, for example pictures at the event, with face recognition and subsequent identification, IP address of the person's home router, etc., then any remaining uncertainty from false positives could be reduced by learning from data on the ledger and the person's smartphone.
+This potential difference can thus be considered the price for verifiability.
+Against an attacker without such side information, \CROCUS preserves the participants' privacy, expressed in terms of unlinkability to their identity and between events.
+
+%To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. \sonja{Rephrase the following after we have requirements and results:
+%Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \CROCUS fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.
+}
+%With respect to privacy, \CROCUS provides anonymity (of participants)  and unlinkability (between protests) unless the adversary gets access to the private key/ID or has side information (she also needs the private key for proof of the cause (cid) supported by the protester, otherwise she does not learn more than without \CROCUS).
+
+%Of separate interest, we have also built distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
+%All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
+%With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.
+
+% In general, none of the related works fulfills the eligibility
+% verifiability (one proof per person, temporal and spatial eligibility ---
+% \cref{%
+%   CountOnce,%
+%   TemporallyRelated,SpatiallyRelated,%
+% }).
+% To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
+% Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
+% Moreover, if they provided individual verifiability, they would likely violate 
+% the privacy requirements --- if people must recognize themselves in photos, 
+% others can recognize them too.
+% Finally, most of the current methods are estimates, with quite some error margins. 
+While \CROCUS is an actual count and not an estimate, its accuracy for the total number of participants hinges on the participants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol.
+Until used by most participants, \CROCUS would result in a considerable undercount. 
+However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic.
+While the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies.
+We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes and increase transparency.

### 2021-06-17 paper/current-crowd-counting-short.tex
adds short related work inputs, uses them

--- 2021-06-16 paper/current-crowd-counting.tex
@@
 
-The seemingly most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers,HowWillWeKnowTrumpInauguralCrowdSize,TheXManMarch,TheCrowdNumbersGame}.
-This manual method devised in the 1960s relies on aerial pictures of the event.
-The verifier divides the protest venue into regions and then estimates the density of the crowd in the different regions before summing them up to get an estimate of the global count.
+The most common method for counting crowds at protests is \emph{Jacobs's method}~\cite{2016DemonstrationsInSeoul,BBCHowToCountProtestNumbers}, estimating crowd density in different regions seen from aerial pictures and summing up.
 Using pictures makes it difficult to get cumulative counts, verify that the pictures have not been manipulated, and to have both privacy and individual verifiability: either one is included in the picture (privacy problem) or not (verifiability problem).
-Similar limitations exist for estimating the number of persons in a picture or video (\eg the work of \cite{NNCrowdCounting} or  CrowdSize~\cite{CrowdSize}).
-
+Similar limitations exist for estimating the number of persons in a picture or video (\eg CrowdSize~\cite{CrowdSize}).
 Another problem for all the above methods is exemplified by the demonstrations in Seoul:
@@
 }.
-In this situation it is very difficult to faithfully capture the situation.
-Taking pictures from different angles risks double counts. Another challenge is 
+Compensating with pictures from different angles risks double counts. Another challenge is 
 determining whether people near the event's perimeter are participants or 
@@
 
-An approach that relies on a trusted infrastructure was recently deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}.
+Trusted infrastructure was deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}. 
 This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.
 
-\Textcite{CrowdCount} is a web service that lets Alice create an event such 
-that anyone can submit their location to register that they are in Alice's 
-event.
-Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
-However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
+% \Textcite{CrowdCount} is a web service that lets Alice create an event such 
+% that anyone can submit their location to register that they are in Alice's 
+% event.
+% Another related approach based on devices is UrbanCount~\cite{UrbanCount}, which relies on epidemic spreading of crowd-size estimates by device-to-device communication to count crowds in dense urban environments with high node-mobility and churn.
+% However, there is no consideration of a potentially adversarial setting and thus no verifiability or checks on eligibility.
 DiVote~\cite{DiVote}, a prior work by the same authors for polling in dense areas, avoids double counting, but again only works with honest participants and thus does not suit an adversarial setting.

### 2021-06-17 paper/protocol.tex
Moves protocol overview figure to appendix

@@
 
-\begin{figure*}
-  \centering
-  \small
-  \begin{subfigure}{\columnwidth}
-    \begin{align*}
-      O\to \text{all}\colon & \text{manifesto} \\
-      P\colon & t_s\gets \TSget \\
-        & \cid\gets \Hash[\text{manifesto}], \\
-        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
-      W\colon & t_s'\gets \TSget
-      \\[-1em]
-      \noalign{\hfill Join}
-      \midrule
-      \noalign{\hfill Participation}
-      \\[-3em]
-      P\to W\colon & \pid \\
-      P\leftrightarrow W\colon &
-        \PPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
-        \\
-      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
-      W\to P\colon & (\wid, t_s', l)
-    \end{align*}
-    \caption{Join and participation.}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{\columnwidth}
-    \begin{align*}
-      P\colon & t_e\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & t_e'\gets \TSsubmit[\Hash[\pid, \wid, t_s, t_s', l]] \\
-      W\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
-      \pi_{\wid})],\quad \text{where} \\
-        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
-        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
-        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
-      P\colon & \TSsubmit[(\cid, \pid, \wid, t_s, t_s', t_e, l, 
-      \pi_{\pid})],\quad \text{where}\\
-        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
-        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
-        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
-        \\
-        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
-    \end{align*}
-    \caption{Submission.}
-  \end{subfigure}
-  \caption{%
-    An overview of \CROCUS participation.\@
-    The organizer \(O\) broadcasts the manifesto.
-    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
-    Finally, both \(P\) and \(W\) submit the proof shares to a
-   public ledger for permanent storage \(S\). Note that \pid  always refers to the
-    protester whose presence is being witnessed.
-  }%
-  \label{fig:ProtocolOverview}
-\end{figure*}
-%\normalsize
-
 \subsection{Count and Verification}%

### 2021-06-17 paper/location-proof-systems-short.tex

\paragraph{Location-proof systems}%
\label{location-proof-systems}

Our work is very related to \acp{LPS}~\cite{luo2010veriplace,zhu2011applaus}, a digital certificate attesting that someone was at 
a particular location at a specific moment in time, except we need to
tie the cause of the protest to the location proof and cannot trust
the verifier. Most of the existing  \acp{LPS} approaches require the prover and the 
witnesses to disclose their identities, thus raising many privacy
issues.
PROPS~\cite{PROPS} is  an exception, but like PASPORT~\cite{PASPORT}
and \Textcite{ProofOfWitnessPresence}, does not treat the adversarial
setting needed for \CROCUS.

### 2021-06-17 paper/desired-properties.tex
Cuts desired and security properties sections

@@
 express their opinion.
-These opinions can be sensitive (\eg be a cause for discrimination or 
-persecution).
-For that reason we have strong requirements for verification and privacy for 
-elections, it follows that we should have similar properties for protests
+To support democracy, we need strong requirements for verification and privacy 
+for elections, it follows that we should have similar properties for protests
 and petitions.
@@
 Coercion resistance in voting typically relies on physical isolation
-(\eg private voting booths), including for digital systems, 
-and that is by definition not possible for public events.
+(\eg private voting booths), including for digital systems, and that is by 
+definition not possible in our context.
 For instance, someone could simply physically bring Alice to a protest against her will.
@@
 
-Therefore in our context, the crucial property is  vote privacy.
+Privacy remains as the crucial property.
 More precisely, for the protester we want unlinkability (from the adversary's 
@@
 (and thus also the protest itself).
-Phrased differently, given a participation proof, Grace should not be able to 
-distinguish if it was Alice or Bob who participated.
-Furthermore, if Grace has managed to link one proof to Alice due to some 
-auxiliary knowledge, she should not be able to link it to another proof (from a different protest).

### 2021-06-17 paper/security-properties.tex
Cuts desired and security properties sections

@@
       \cref{DefProofShares}) per protest (\(\cid\) in \cref{DefProofShares}), 
-      this pseudonym is unique except with negligible probability.
-      Analogously, a witness can create \emph{one and only one} pseudonym per 
-      protester (\(\wid\) in \cref{DefProofShares}), this pseudonym is unique 
-      except with negligible probability.
+      this pseudonym is unique.
 
@@
 
-What these properties say is that pseudonyms must look random 
-(\cref{PseudonymUnlink}) and that each psdeudonym must not be reused
-more than strictly necessary for the verifiability properties 
-(\cref{ProtestUnlink,WitnessUnlink}). In Pfitzmann-Hansen
-terminology~\cite{pfitzmann-hansen}, they are role-relationship
-pseudonyms, but with increasingly narrowed notions of roles and
-relationships (participant of particular protest, witness of a
-particular participant at a particular protest).
 In the terminology of \textcite{SybilFreePseudonyms}; for each protester a 

### 2021-06-17 paper/desired-properties.tex
Turns description into inline enumeration

@@
 
-We draw inspiration from properties for voting systems:
-\begin{description}
-  \item[Eligibility:] anyone can verify that each cast vote is legitimate.
-  \item[Universal verifiability:] anyone can verify that the result is according to the cast votes.
-  \item[Individual verifiability:] each voter can verify that their vote is 
-    included in the result.
-\end{description}
+We draw inspiration from three properties for voting systems:
+\begin{enumerate*}
+  \item \emph{eligibility}, anyone can verify that each cast vote is 
+    legitimate;
+  \item \emph{universal verifiability}, anyone can verify that the result is 
+    according to the cast votes;
+  \item \emph{individual verifiability}, each voter can verify that their vote 
+    is included in the result.
+\end{enumerate*}
 In our context, votes are translated into \emph{participation proofs}.
@@
 The main three privacy properties for voting protocols are given as:
-\begin{description}
-  \item[Vote privacy:] the voting does not reveal any individual vote.
-  \item[Receipt freeness:] the voting system does not provide any data that can be used as a proof of how the voter voted.
-  \item[Coercion resistance:] a voter cannot cooperate with a coercer to prove their vote was cast in any particular way.
-\end{description}
+\begin{enumerate*}
+  \item \emph{vote privacy}, the voting does not reveal any individual vote;
+  \item \emph{receipt freeness}, the voting system does not provide any data 
+    that can be used as a proof of how the voter voted;
+  \item \emph{coercion resistance}, a voter cannot cooperate with a coercer to 
+    prove their vote was cast in any particular way.
+\end{enumerate*}
 

### 2021-06-17 paper/distance-bounding.tex
Fixes typo in DB section
Cuts distance bounding further

@@
 As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
-\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases.
-Time critical phases are complemented by slow phases during which the time is not taking into account. 
-At the end of a \Ac{DB} protocol, the verifier should be able to
-determine if the prover is legitimate \emph{and} in their vicinity.
-In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
-
+\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on 
+their distance to the prover during authentication.
+%by measuring the time-of-flight of short challenge-response messages (or 
+%rounds) exchanged during time-critical phases. Time critical phases are 
+%complemented by slow phases during which the time is not taken into account. At 
+%the end of a \Ac{DB} protocol, the verifier should be able to
+%determine if the prover is legitimate \emph{and} in their vicinity.
+%In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.
+%
 Our setting requires a public-key \ac{DB} protocol with a \emph{malicious 
@@
 their actions, thus we also require strong privacy.
-In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
-\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
 There exists one such protocol in the literature, namely one by 

### 2021-06-17 paper/sybil-free-pseudonyms.tex
Removes redundant anon-cred text
Puts \input for anon-creds.tex in a better place
Cuts in Sybil-free pseudonyms/anon cred
Changes to use the same ref to Leonardo's work

@@
 We use the idea of identity domains and self-certified Sybil-free pseudonyms 
-proposed by \textcite{SelfCertifiedSybilFreePseudonyms}.
+proposed by \textcite{SybilFreePseudonyms}.
 However, we don't need the ability to (nor want to be able to) deanonymize 
@@
 \textcite{HowToWinTheCloneWars} that 
-\textcite{SelfCertifiedSybilFreePseudonyms} use, but rather just what they call 
+\textcite{SybilFreePseudonyms} use, but rather just what they call 
 the token serial number.
+More specifically, what we need is an anonymous credential system with the 
+following properties.
+
+\input{anon-cred.tex}

### 2021-06-17 paper/system-model.tex
adds implementability snippets (footnotes) to system model

@@
 
+Some of the assumptions that are required for implementing and deploying our proposition are 
+not yet realized, however, we believe that they soon will
+be:\footnote{see the long version of the paper for a more thorough discussion}
+ubiquitous usage of smartphones, with an identity credential
+signed by some \ac{CA}\footnote{based on \eg governmental ID on a chip as in Estonia, national
+  but private as BankID in Sweden, eIDAS in the EU, or self-sovereign
+  identities} ,  distance-bounding capabilities\footnote{based on \eg
+  3DB-access or key-fob technology integration with phones}, and
+infrastructure-independent wireless communications\footnote{based on
+  \eg NFC (available but inconvenient), bluetooth or WIFI (Briar and
+  FireChat have been used in protests), 5G D2D (scalable but needs
+  authorization step)}.
+
 % \subsection{Adversary model}%

### 2021-06-17 paper/system-model.tex
merges sybil footnotes in system model

@@
 Furthermore, we assume that each participant has a digital identity certificate signed 
-by \iac{CA}\footnote{%
+by \iac{CA} that ensures a one-to-one mapping between an identity and
+a cryptographic key\footnote{%
+  For every physical person there exists at most one valid digital
+  certificate. 
   We note that any system that prevents Sybil attacks~\cite{SybilAttack} will 
   do. 
-} that ensures a one-to-one mapping between an identity and a cryptographic 
-key\footnote{%
-  For every physical person there exists at most one valid digital certificate.
 }.

### 2021-06-17 paper/outline.tex
removes practical considerations and performance from outline
adds appendix to outline, mainly to get a pointer to performance

@@
 %estimation 
-protocol in in \Cref{Protocol}, analyze its security in
-\cref{SecurityAnalysis}, and discuss practical considerations including performance in \cref{Practical}.
+protocol in in \Cref{Protocol} and analyze its security in
+\cref{SecurityAnalysis}.
+%and discuss practical considerations including performance in \cref{Practical}.
 %We compare it to related work in \cref{related-work}.
@@
 Finally, we state
-our conclusions in \cref{Conclusion}.
+our conclusions in \cref{Conclusion}. The appendix contains some
+protocol details of anonymous-credentials that we build on, a compact
+summary of the \CROCUS protocol, and a
+performance estimation.

### 2021-06-17 paper/current-crowd-counting-short.tex
shortens current crowd counting

@@
 Similar limitations exist for estimating the number of persons in a picture or video (\eg CrowdSize~\cite{CrowdSize}).
-Another problem for all the above methods is exemplified by the demonstrations in Seoul:
+Edge cases are difficult: determining whether people near the event's perimeter are participants or 
+simply bystanders~\cite{HowToEstimateCrowdSize}, and as noted with demonstrations in Seoul:
 \blockcquote{2016DemonstrationsInSeoul}{%
@@
 }.
-Compensating with pictures from different angles risks double counts. Another challenge is 
-determining whether people near the event's perimeter are participants or 
-simply bystanders~\cite{HowToEstimateCrowdSize}.
-
-Counting MAC addresses, as done by a company during the protests in Seoul~\cite{2016DemonstrationsInSeoul} suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.
-
+Counting MAC addresses, as done by a company there, suffers from MAC randomization, though some tracking of smartphones could still be possible with a different method~\cite{WhyMACRandomizationIsNotEnough} or using \emph{IMSI catchers}; none of which is verifiable.
 Trusted infrastructure was deployed by a collection of media outlets to count protesters passing the line defined by a trusted sensor on marches~\cite{LeMondeProtestingSolution}.
-This solution does not offer strong verifiability guarantees and thus is complemented by micro-counts made by humans to estimate their margin of error.
+Again, due to the lack of
+strong verifiability guarantees it was complemented by micro-counts made by humans. %to estimate their margin of error.
 
